### 2023-12-03 projects/london-clojurians-dec-2023-talk/docs/notebooks.commits.qmd
initial exploration of commit logs

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: notebooks.commits.html}
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.commits_files/md-default0.js" type="text/javascript"></script><script src="notebooks.commits_files/md-default1.js" type="text/javascript"></script><script src="notebooks.commits_files/vega2.js" type="text/javascript"></script><script src="notebooks.commits_files/vega3.js" type="text/javascript"></script><script src="notebooks.commits_files/vega4.js" type="text/javascript"></script>

<div class="sourceClojure">
```clojure
(ns notebooks.commits
  (:require [tablecloth.api :as tc]
            [scicloj.noj.v1.vis :as vis]
            [aerial.hanami.templates :as ht]
            [tech.v3.datatype.datetime :as datetime]
            [tech.v3.datatype.rolling :as rolling]
            [tech.v3.datatype.functional :as fun]
            [data.generate-dataset]))
```
</div>

<div class="sourceClojure">
```clojure
(def date-counts
  (-> data.generate-dataset/commit-dates
      (tc/group-by [:date])
      (tc/aggregate {:n tc/row-count})
      (tc/order-by [:date])))
```
</div>

<div class="sourceClojure">
```clojure
date-counts
```
</div>

_unnamed [5654 2]:

|      :date |  :n |
|------------|----:|
| 2008-03-29 |   7 |
| 2008-04-02 |   4 |
| 2008-04-03 |   9 |
| 2008-04-05 |   2 |
| 2008-04-06 |   1 |
| 2008-04-07 |   5 |
| 2008-04-08 |   9 |
| 2008-04-10 |   1 |
| 2008-04-11 |   1 |
| 2008-04-16 |   1 |
|        ... | ... |
| 2023-11-23 |  86 |
| 2023-11-24 |  95 |
| 2023-11-25 |  32 |
| 2023-11-26 |  54 |
| 2023-11-27 |  66 |
| 2023-11-28 |  95 |
| 2023-11-29 |  87 |
| 2023-11-30 |  91 |
| 2023-12-01 |  43 |
| 2023-12-02 |  32 |
| 2023-12-03 |  19 |

<div class="sourceClojure">
```clojure
(-> date-counts
    (vis/hanami-plot ht/line-chart
                     {:X "date"
                      :XTYPE "temporal"
                      :Y "n"}))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"date","type":"temporal"}},"mark":{"type":"line","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"values":"date,n\n2008-03-29,7\n2008-04-02,4\n2008-04-03,9\n2008-04-05,2\n2008-04-06,1\n2008-04-07,5\n2008-04-08,9\n2008-04-10,1\n2008-04-11,1\n2008-04-16,1\n2008-04-18,1\n2008-04-19,1\n2008-04-21,1\n2008-04-24,3\n2008-04-25,1\n2008-04-29,1\n2008-04-30,4\n2008-05-01,1\n2008-05-02,2\n2008-05-03,2\n2008-05-07,3\n2008-05-08,2\n2008-05-10,6\n2008-05-11,1\n2008-05-12,1\n2008-05-13,2\n2008-05-14,1\n2008-05-15,1\n2008-05-16,2\n2008-05-17,9\n2008-05-18,12\n2008-05-22,1\n2008-05-24,3\n2008-05-25,2\n2008-05-26,1\n2008-05-27,1\n2008-05-28,1\n2008-05-29,4\n2008-05-31,1\n2008-06-01,2\n2008-06-02,1\n2008-06-03,3\n2008-06-04,2\n2008-06-05,1\n2008-06-06,1\n2008-06-07,1\n2008-06-08,5\n2008-06-09,3\n2008-06-11,2\n2008-06-12,2\n2008-06-13,2\n2008-06-14,4\n2008-06-15,5\n2008-06-18,1\n2008-06-19,3\n2008-06-27,1\n2008-06-28,6\n2008-06-29,6\n2008-06-30,2\n2008-07-03,2\n2008-07-04,1\n2008-07-06,5\n2008-07-07,2\n2008-07-08,1\n2008-07-09,8\n2008-07-10,5\n2008-07-11,6\n2008-07-12,4\n2008-07-13,3\n2008-07-14,1\n2008-07-15,5\n2008-07-21,1\n2008-07-22,5\n2008-07-24,2\n2008-07-25,2\n2008-07-26,7\n2008-07-27,3\n2008-07-29,8\n2008-08-05,1\n2008-08-06,4\n2008-08-07,7\n2008-08-08,1\n2008-08-09,1\n2008-08-10,1\n2008-08-11,1\n2008-08-12,4\n2008-08-13,1\n2008-08-14,1\n2008-08-15,3\n2008-08-16,9\n2008-08-17,4\n2008-08-19,7\n2008-08-20,3\n2008-08-21,1\n2008-08-25,2\n2008-08-27,2\n2008-08-28,2\n2008-08-29,5\n2008-08-30,8\n2008-09-02,8\n2008-09-03,7\n2008-09-04,1\n2008-09-05,1\n2008-09-06,2\n2008-09-07,3\n2008-09-08,29\n2008-09-09,4\n2008-09-10,3\n2008-09-11,2\n2008-09-12,3\n2008-09-13,11\n2008-09-14,2\n2008-09-15,8\n2008-09-16,11\n2008-09-17,8\n2008-09-18,1\n2008-09-19,2\n2008-09-20,8\n2008-09-21,7\n2008-09-22,3\n2008-09-23,4\n2008-09-24,4\n2008-09-25,6\n2008-09-26,4\n2008-09-27,2\n2008-09-28,7\n2008-10-01,6\n2008-10-02,10\n2008-10-03,5\n2008-10-04,3\n2008-10-05,5\n2008-10-06,11\n2008-10-07,2\n2008-10-08,6\n2008-10-09,3\n2008-10-10,4\n2008-10-11,2\n2008-10-12,4\n2008-10-13,2\n2008-10-14,1\n2008-10-15,10\n2008-10-16,1\n2008-10-17,4\n2008-10-18,2\n2008-10-19,8\n2008-10-21,1\n2008-10-22,5\n2008-10-23,4\n2008-10-25,2\n2008-10-26,3\n2008-10-27,1\n2008-10-28,2\n2008-10-29,1\n2008-10-30,5\n2008-10-31,5\n2008-11-01,9\n2008-11-02,1\n2008-11-03,7\n2008-11-08,3\n2008-11-09,5\n2008-11-11,1\n2008-11-12,5\n2008-11-13,23\n2008-11-14,2\n2008-11-15,8\n2008-11-16,17\n2008-11-17,3\n2008-11-18,25\n2008-11-19,3\n2008-11-20,2\n2008-11-21,3\n2008-11-22,3\n2008-11-23,7\n2008-11-24,1\n2008-11-25,6\n2008-11-26,3\n2008-11-27,3\n2008-11-28,5\n2008-11-29,5\n2008-11-30,5\n2008-12-01,7\n2008-12-02,3\n2008-12-03,7\n2008-12-04,5\n2008-12-05,6\n2008-12-07,3\n2008-12-08,4\n2008-12-09,1\n2008-12-10,6\n2008-12-11,5\n2008-12-12,1\n2008-12-13,12\n2008-12-14,8\n2008-12-15,9\n2008-12-16,6\n2008-12-17,6\n2008-12-19,18\n2008-12-20,1\n2008-12-21,3\n2008-12-22,3\n2008-12-23,10\n2008-12-24,3\n2008-12-25,1\n2008-12-26,1\n2008-12-27,13\n2008-12-28,13\n2008-12-29,15\n2008-12-30,10\n2008-12-31,2\n2009-01-01,4\n2009-01-02,5\n2009-01-03,2\n2009-01-04,14\n2009-01-05,3\n2009-01-06,7\n2009-01-07,1\n2009-01-08,17\n2009-01-09,4\n2009-01-10,3\n2009-01-11,9\n2009-01-12,19\n2009-01-13,5\n2009-01-14,4\n2009-01-15,11\n2009-01-16,10\n2009-01-17,36\n2009-01-18,36\n2009-01-19,22\n2009-01-20,12\n2009-01-21,16\n2009-01-22,8\n2009-01-23,13\n2009-01-24,7\n2009-01-25,15\n2009-01-26,13\n2009-01-27,6\n2009-01-28,5\n2009-01-29,7\n2009-01-30,5\n2009-01-31,2\n2009-02-01,2\n2009-02-02,4\n2009-02-03,1\n2009-02-04,3\n2009-02-05,1\n2009-02-06,8\n2009-02-07,3\n2009-02-08,3\n2009-02-10,22\n2009-02-11,14\n2009-02-12,18\n2009-02-13,6\n2009-02-14,5\n2009-02-15,9\n2009-02-16,5\n2009-02-17,8\n2009-02-18,7\n2009-02-19,4\n2009-02-20,8\n2009-02-21,10\n2009-02-22,15\n2009-02-23,12\n2009-02-24,27\n2009-02-25,7\n2009-02-26,11\n2009-02-27,19\n2009-02-28,3\n2009-03-01,5\n2009-03-02,3\n2009-03-03,8\n2009-03-04,7\n2009-03-05,2\n2009-03-06,6\n2009-03-07,3\n2009-03-08,2\n2009-03-09,6\n2009-03-10,4\n2009-03-11,7\n2009-03-12,13\n2009-03-13,4\n2009-03-14,8\n2009-03-15,7\n2009-03-16,9\n2009-03-17,9\n2009-03-18,11\n2009-03-19,13\n2009-03-20,8\n2009-03-21,13\n2009-03-22,11\n2009-03-23,8\n2009-03-24,4\n2009-03-25,4\n2009-03-26,4\n2009-03-27,9\n2009-03-28,10\n2009-03-29,17\n2009-03-30,9\n2009-03-31,7\n2009-04-01,8\n2009-04-02,1\n2009-04-03,5\n2009-04-04,8\n2009-04-05,16\n2009-04-06,15\n2009-04-07,5\n2009-04-08,7\n2009-04-09,15\n2009-04-10,5\n2009-04-11,2\n2009-04-12,3\n2009-04-13,1\n2009-04-14,9\n2009-04-15,17\n2009-04-16,9\n2009-04-17,19\n2009-04-18,8\n2009-04-19,21\n2009-04-20,28\n2009-04-21,24\n2009-04-22,13\n2009-04-23,25\n2009-04-24,8\n2009-04-25,8\n2009-04-26,6\n2009-04-27,4\n2009-04-28,2\n2009-04-29,6\n2009-04-30,1\n2009-05-01,8\n2009-05-02,1\n2009-05-03,12\n2009-05-04,17\n2009-05-05,7\n2009-05-06,9\n2009-05-07,13\n2009-05-08,4\n2009-05-09,15\n2009-05-10,7\n2009-05-11,13\n2009-05-12,3\n2009-05-13,2\n2009-05-14,17\n2009-05-15,3\n2009-05-16,5\n2009-05-17,5\n2009-05-18,6\n2009-05-19,6\n2009-05-20,3\n2009-05-21,5\n2009-05-22,2\n2009-05-23,16\n2009-05-24,7\n2009-05-25,7\n2009-05-26,4\n2009-05-27,7\n2009-05-28,3\n2009-05-29,7\n2009-05-30,4\n2009-05-31,19\n2009-06-01,7\n2009-06-02,10\n2009-06-03,13\n2009-06-04,7\n2009-06-05,17\n2009-06-06,8\n2009-06-07,1\n2009-06-08,11\n2009-06-09,8\n2009-06-10,4\n2009-06-11,7\n2009-06-12,4\n2009-06-13,12\n2009-06-14,4\n2009-06-15,3\n2009-06-16,8\n2009-06-17,2\n2009-06-18,2\n2009-06-19,18\n2009-06-20,1\n2009-06-21,1\n2009-06-22,9\n2009-06-23,13\n2009-06-24,14\n2009-06-25,3\n2009-06-26,17\n2009-06-27,7\n2009-06-28,10\n2009-06-29,3\n2009-06-30,6\n2009-07-01,9\n2009-07-02,17\n2009-07-03,6\n2009-07-04,4\n2009-07-05,6\n2009-07-06,9\n2009-07-07,7\n2009-07-08,13\n2009-07-09,7\n2009-07-10,6\n2009-07-11,2\n2009-07-12,8\n2009-07-13,5\n2009-07-14,7\n2009-07-15,5\n2009-07-16,6\n2009-07-17,3\n2009-07-18,5\n2009-07-19,4\n2009-07-20,14\n2009-07-21,6\n2009-07-23,10\n2009-07-24,11\n2009-07-25,3\n2009-07-26,9\n2009-07-27,5\n2009-07-28,21\n2009-07-29,17\n2009-07-30,5\n2009-07-31,6\n2009-08-01,11\n2009-08-02,4\n2009-08-03,9\n2009-08-04,5\n2009-08-05,3\n2009-08-06,1\n2009-08-07,7\n2009-08-08,7\n2009-08-09,1\n2009-08-10,4\n2009-08-11,2\n2009-08-12,5\n2009-08-13,4\n2009-08-14,9\n2009-08-15,6\n2009-08-16,2\n2009-08-17,21\n2009-08-18,14\n2009-08-19,13\n2009-08-20,6\n2009-08-21,5\n2009-08-22,1\n2009-08-23,9\n2009-08-24,4\n2009-08-25,10\n2009-08-26,2\n2009-08-27,5\n2009-08-28,7\n2009-08-29,8\n2009-08-30,3\n2009-08-31,4\n2009-09-01,8\n2009-09-02,8\n2009-09-03,19\n2009-09-04,22\n2009-09-05,4\n2009-09-06,8\n2009-09-07,15\n2009-09-08,16\n2009-09-09,14\n2009-09-10,16\n2009-09-11,17\n2009-09-12,4\n2009-09-13,11\n2009-09-14,12\n2009-09-15,12\n2009-09-16,10\n2009-09-17,9\n2009-09-18,19\n2009-09-19,9\n2009-09-20,4\n2009-09-21,4\n2009-09-22,6\n2009-09-23,21\n2009-09-25,2\n2009-09-26,4\n2009-09-27,2\n2009-09-28,8\n2009-09-29,5\n2009-09-30,4\n2009-10-01,6\n2009-10-02,2\n2009-10-03,12\n2009-10-04,4\n2009-10-05,10\n2009-10-06,12\n2009-10-07,30\n2009-10-08,8\n2009-10-09,9\n2009-10-10,2\n2009-10-11,1\n2009-10-13,2\n2009-10-14,5\n2009-10-15,4\n2009-10-16,8\n2009-10-17,3\n2009-10-18,5\n2009-10-19,5\n2009-10-21,4\n2009-10-22,7\n2009-10-23,15\n2009-10-24,29\n2009-10-25,7\n2009-10-26,20\n2009-10-27,9\n2009-10-28,8\n2009-10-29,5\n2009-10-30,2\n2009-10-31,10\n2009-11-01,17\n2009-11-02,24\n2009-11-03,7\n2009-11-04,9\n2009-11-05,8\n2009-11-06,10\n2009-11-07,2\n2009-11-08,16\n2009-11-09,14\n2009-11-10,13\n2009-11-11,19\n2009-11-12,12\n2009-11-13,11\n2009-11-14,33\n2009-11-15,18\n2009-11-16,13\n2009-11-17,15\n2009-11-18,23\n2009-11-19,23\n2009-11-20,20\n2009-11-21,23\n2009-11-22,18\n2009-11-23,22\n2009-11-24,12\n2009-11-25,14\n2009-11-26,17\n2009-11-27,18\n2009-11-28,26\n2009-11-29,14\n2009-11-30,16\n2009-12-01,27\n2009-12-02,22\n2009-12-03,9\n2009-12-04,8\n2009-12-05,10\n2009-12-06,10\n2009-12-07,8\n2009-12-08,9\n2009-12-09,9\n2009-12-10,22\n2009-12-11,10\n2009-12-12,9\n2009-12-13,6\n2009-12-14,8\n2009-12-15,8\n2009-12-16,14\n2009-12-17,5\n2009-12-18,15\n2009-12-19,19\n2009-12-20,12\n2009-12-21,16\n2009-12-22,12\n2009-12-23,12\n2009-12-24,13\n2009-12-25,11\n2009-12-26,32\n2009-12-27,25\n2009-12-28,16\n2009-12-29,21\n2009-12-30,27\n2009-12-31,13\n2010-01-01,14\n2010-01-02,14\n2010-01-03,12\n2010-01-04,28\n2010-01-05,7\n2010-01-06,4\n2010-01-07,5\n2010-01-08,18\n2010-01-09,10\n2010-01-10,20\n2010-01-11,39\n2010-01-12,31\n2010-01-13,21\n2010-01-14,27\n2010-01-15,6\n2010-01-16,11\n2010-01-17,7\n2010-01-18,10\n2010-01-19,11\n2010-01-20,26\n2010-01-21,16\n2010-01-22,20\n2010-01-23,8\n2010-01-24,18\n2010-01-25,24\n2010-01-26,46\n2010-01-27,32\n2010-01-28,28\n2010-01-29,30\n2010-01-30,43\n2010-01-31,20\n2010-02-01,43\n2010-02-02,14\n2010-02-03,8\n2010-02-04,6\n2010-02-05,10\n2010-02-06,16\n2010-02-07,11\n2010-02-08,13\n2010-02-09,26\n2010-02-10,26\n2010-02-11,49\n2010-02-12,38\n2010-02-13,20\n2010-02-14,9\n2010-02-15,19\n2010-02-16,24\n2010-02-17,20\n2010-02-18,25\n2010-02-19,29\n2010-02-20,24\n2010-02-21,37\n2010-02-22,44\n2010-02-23,24\n2010-02-24,14\n2010-02-25,10\n2010-02-26,12\n2010-02-27,14\n2010-02-28,45\n2010-03-01,35\n2010-03-02,50\n2010-03-03,31\n2010-03-04,20\n2010-03-05,15\n2010-03-06,20\n2010-03-07,25\n2010-03-08,24\n2010-03-09,18\n2010-03-10,24\n2010-03-11,13\n2010-03-12,17\n2010-03-13,8\n2010-03-14,35\n2010-03-15,33\n2010-03-16,23\n2010-03-17,40\n2010-03-18,25\n2010-03-19,13\n2010-03-20,6\n2010-03-21,8\n2010-03-22,9\n2010-03-23,15\n2010-03-24,28\n2010-03-25,15\n2010-03-26,40\n2010-03-27,10\n2010-03-28,20\n2010-03-29,34\n2010-03-30,39\n2010-03-31,26\n2010-04-01,39\n2010-04-02,36\n2010-04-03,20\n2010-04-04,19\n2010-04-05,31\n2010-04-06,36\n2010-04-07,31\n2010-04-08,30\n2010-04-09,22\n2010-04-10,26\n2010-04-11,26\n2010-04-12,62\n2010-04-13,41\n2010-04-14,30\n2010-04-15,36\n2010-04-16,40\n2010-04-17,34\n2010-04-18,30\n2010-04-19,21\n2010-04-20,25\n2010-04-21,23\n2010-04-22,30\n2010-04-23,32\n2010-04-24,23\n2010-04-25,44\n2010-04-26,29\n2010-04-27,22\n2010-04-28,42\n2010-04-29,55\n2010-04-30,19\n2010-05-01,21\n2010-05-02,39\n2010-05-03,42\n2010-05-04,32\n2010-05-05,42\n2010-05-06,41\n2010-05-07,16\n2010-05-08,14\n2010-05-09,13\n2010-05-10,16\n2010-05-11,21\n2010-05-12,13\n2010-05-13,17\n2010-05-14,37\n2010-05-15,25\n2010-05-16,7\n2010-05-17,18\n2010-05-18,19\n2010-05-19,15\n2010-05-20,24\n2010-05-21,28\n2010-05-22,26\n2010-05-23,6\n2010-05-24,7\n2010-05-25,19\n2010-05-26,26\n2010-05-27,22\n2010-05-28,20\n2010-05-29,24\n2010-05-30,29\n2010-05-31,4\n2010-06-01,14\n2010-06-02,20\n2010-06-03,22\n2010-06-04,14\n2010-06-05,14\n2010-06-06,20\n2010-06-07,31\n2010-06-08,30\n2010-06-09,36\n2010-06-10,20\n2010-06-11,37\n2010-06-12,34\n2010-06-13,17\n2010-06-14,27\n2010-06-15,17\n2010-06-16,34\n2010-06-17,44\n2010-06-18,30\n2010-06-19,23\n2010-06-20,24\n2010-06-21,24\n2010-06-22,25\n2010-06-23,24\n2010-06-24,29\n2010-06-25,33\n2010-06-26,28\n2010-06-27,21\n2010-06-28,13\n2010-06-29,43\n2010-06-30,36\n2010-07-01,17\n2010-07-02,14\n2010-07-03,16\n2010-07-04,21\n2010-07-05,14\n2010-07-06,24\n2010-07-07,23\n2010-07-08,42\n2010-07-09,19\n2010-07-10,19\n2010-07-11,11\n2010-07-12,22\n2010-07-13,25\n2010-07-14,28\n2010-07-15,13\n2010-07-16,38\n2010-07-17,12\n2010-07-18,12\n2010-07-19,19\n2010-07-20,41\n2010-07-21,28\n2010-07-22,24\n2010-07-23,36\n2010-07-24,21\n2010-07-25,7\n2010-07-26,46\n2010-07-27,25\n2010-07-28,32\n2010-07-29,16\n2010-07-30,25\n2010-07-31,21\n2010-08-01,40\n2010-08-02,20\n2010-08-03,20\n2010-08-04,19\n2010-08-05,28\n2010-08-06,24\n2010-08-07,34\n2010-08-08,18\n2010-08-09,28\n2010-08-10,19\n2010-08-11,23\n2010-08-12,24\n2010-08-13,32\n2010-08-14,16\n2010-08-15,30\n2010-08-16,48\n2010-08-17,38\n2010-08-18,23\n2010-08-19,36\n2010-08-20,33\n2010-08-21,60\n2010-08-22,17\n2010-08-23,50\n2010-08-24,38\n2010-08-25,47\n2010-08-26,50\n2010-08-27,51\n2010-08-28,33\n2010-08-29,43\n2010-08-30,38\n2010-08-31,29\n2010-09-01,22\n2010-09-02,20\n2010-09-03,20\n2010-09-04,16\n2010-09-05,9\n2010-09-06,29\n2010-09-07,20\n2010-09-08,15\n2010-09-09,40\n2010-09-10,34\n2010-09-11,32\n2010-09-12,18\n2010-09-13,42\n2010-09-14,39\n2010-09-15,24\n2010-09-16,33\n2010-09-17,59\n2010-09-18,35\n2010-09-19,37\n2010-09-20,61\n2010-09-21,43\n2010-09-22,49\n2010-09-23,44\n2010-09-24,53\n2010-09-25,33\n2010-09-26,21\n2010-09-27,42\n2010-09-28,22\n2010-09-29,49\n2010-09-30,28\n2010-10-01,33\n2010-10-02,32\n2010-10-03,30\n2010-10-04,41\n2010-10-05,40\n2010-10-06,30\n2010-10-07,26\n2010-10-08,24\n2010-10-09,10\n2010-10-10,18\n2010-10-11,31\n2010-10-12,47\n2010-10-13,24\n2010-10-14,33\n2010-10-15,34\n2010-10-16,31\n2010-10-17,18\n2010-10-18,25\n2010-10-19,47\n2010-10-20,42\n2010-10-21,13\n2010-10-22,13\n2010-10-23,17\n2010-10-24,31\n2010-10-25,38\n2010-10-26,41\n2010-10-27,34\n2010-10-28,37\n2010-10-29,36\n2010-10-30,15\n2010-10-31,26\n2010-11-01,32\n2010-11-02,42\n2010-11-03,33\n2010-11-04,32\n2010-11-05,18\n2010-11-06,39\n2010-11-07,37\n2010-11-08,45\n2010-11-09,60\n2010-11-10,62\n2010-11-11,47\n2010-11-12,45\n2010-11-13,24\n2010-11-14,43\n2010-11-15,38\n2010-11-16,46\n2010-11-17,33\n2010-11-18,51\n2010-11-19,48\n2010-11-20,50\n2010-11-21,13\n2010-11-22,43\n2010-11-23,60\n2010-11-24,50\n2010-11-25,35\n2010-11-26,60\n2010-11-27,76\n2010-11-28,61\n2010-11-29,28\n2010-11-30,47\n2010-12-01,40\n2010-12-02,36\n2010-12-03,32\n2010-12-04,34\n2010-12-05,38\n2010-12-06,37\n2010-12-07,28\n2010-12-08,24\n2010-12-09,26\n2010-12-10,5\n2010-12-11,17\n2010-12-12,21\n2010-12-13,32\n2010-12-14,23\n2010-12-15,29\n2010-12-16,33\n2010-12-17,30\n2010-12-18,38\n2010-12-19,19\n2010-12-20,18\n2010-12-21,35\n2010-12-22,42\n2010-12-23,34\n2010-12-24,17\n2010-12-25,13\n2010-12-26,15\n2010-12-27,31\n2010-12-28,40\n2010-12-29,67\n2010-12-30,18\n2010-12-31,19\n2011-01-01,20\n2011-01-02,39\n2011-01-03,50\n2011-01-04,38\n2011-01-05,45\n2011-01-06,37\n2011-01-07,27\n2011-01-08,38\n2011-01-09,33\n2011-01-10,43\n2011-01-11,49\n2011-01-12,45\n2011-01-13,53\n2011-01-14,45\n2011-01-15,29\n2011-01-16,7\n2011-01-17,35\n2011-01-18,26\n2011-01-19,31\n2011-01-20,26\n2011-01-21,57\n2011-01-22,28\n2011-01-23,44\n2011-01-24,26\n2011-01-25,26\n2011-01-26,38\n2011-01-27,39\n2011-01-28,23\n2011-01-29,21\n2011-01-30,52\n2011-01-31,19\n2011-02-01,28\n2011-02-02,31\n2011-02-03,24\n2011-02-04,16\n2011-02-05,34\n2011-02-06,16\n2011-02-07,36\n2011-02-08,24\n2011-02-09,22\n2011-02-10,38\n2011-02-11,19\n2011-02-12,17\n2011-02-13,28\n2011-02-14,20\n2011-02-15,20\n2011-02-16,30\n2011-02-17,39\n2011-02-18,31\n2011-02-19,12\n2011-02-20,11\n2011-02-21,29\n2011-02-22,29\n2011-02-23,24\n2011-02-24,49\n2011-02-25,12\n2011-02-26,10\n2011-02-27,19\n2011-02-28,14\n2011-03-01,22\n2011-03-02,48\n2011-03-03,28\n2011-03-04,26\n2011-03-05,13\n2011-03-06,19\n2011-03-07,15\n2011-03-08,30\n2011-03-09,28\n2011-03-10,22\n2011-03-11,31\n2011-03-12,24\n2011-03-13,26\n2011-03-14,71\n2011-03-15,54\n2011-03-16,22\n2011-03-17,42\n2011-03-18,22\n2011-03-19,17\n2011-03-20,31\n2011-03-21,46\n2011-03-22,44\n2011-03-23,55\n2011-03-24,44\n2011-03-25,40\n2011-03-26,22\n2011-03-27,28\n2011-03-28,18\n2011-03-29,44\n2011-03-30,48\n2011-03-31,51\n2011-04-01,49\n2011-04-02,30\n2011-04-03,10\n2011-04-04,29\n2011-04-05,27\n2011-04-06,8\n2011-04-07,20\n2011-04-08,27\n2011-04-09,36\n2011-04-10,14\n2011-04-11,25\n2011-04-12,40\n2011-04-13,16\n2011-04-14,15\n2011-04-15,50\n2011-04-16,28\n2011-04-17,47\n2011-04-18,65\n2011-04-19,56\n2011-04-20,47\n2011-04-21,80\n2011-04-22,59\n2011-04-23,65\n2011-04-24,50\n2011-04-25,62\n2011-04-26,51\n2011-04-27,37\n2011-04-28,59\n2011-04-29,54\n2011-04-30,23\n2011-05-01,50\n2011-05-02,49\n2011-05-03,27\n2011-05-04,52\n2011-05-05,33\n2011-05-06,26\n2011-05-07,12\n2011-05-08,18\n2011-05-09,22\n2011-05-10,26\n2011-05-11,34\n2011-05-12,27\n2011-05-13,29\n2011-05-14,12\n2011-05-15,22\n2011-05-16,25\n2011-05-17,20\n2011-05-18,36\n2011-05-19,27\n2011-05-20,14\n2011-05-21,14\n2011-05-22,45\n2011-05-23,37\n2011-05-24,43\n2011-05-25,23\n2011-05-26,18\n2011-05-27,42\n2011-05-28,79\n2011-05-29,57\n2011-05-30,39\n2011-05-31,73\n2011-06-01,37\n2011-06-02,58\n2011-06-03,30\n2011-06-04,58\n2011-06-05,10\n2011-06-06,30\n2011-06-07,44\n2011-06-08,59\n2011-06-09,38\n2011-06-10,101\n2011-06-11,36\n2011-06-12,46\n2011-06-13,50\n2011-06-14,83\n2011-06-15,37\n2011-06-16,67\n2011-06-17,116\n2011-06-18,98\n2011-06-19,49\n2011-06-20,71\n2011-06-21,68\n2011-06-22,82\n2011-06-23,58\n2011-06-24,131\n2011-06-25,51\n2011-06-26,34\n2011-06-27,88\n2011-06-28,81\n2011-06-29,64\n2011-06-30,46\n2011-07-01,118\n2011-07-02,49\n2011-07-03,37\n2011-07-04,29\n2011-07-05,50\n2011-07-06,42\n2011-07-07,44\n2011-07-08,57\n2011-07-09,27\n2011-07-10,26\n2011-07-11,40\n2011-07-12,56\n2011-07-13,55\n2011-07-14,59\n2011-07-15,160\n2011-07-16,83\n2011-07-17,147\n2011-07-18,139\n2011-07-19,105\n2011-07-20,94\n2011-07-21,28\n2011-07-22,80\n2011-07-23,35\n2011-07-24,28\n2011-07-25,42\n2011-07-26,73\n2011-07-27,76\n2011-07-28,48\n2011-07-29,66\n2011-07-30,66\n2011-07-31,54\n2011-08-01,45\n2011-08-02,79\n2011-08-03,70\n2011-08-04,81\n2011-08-05,85\n2011-08-06,36\n2011-08-07,73\n2011-08-08,25\n2011-08-09,60\n2011-08-10,58\n2011-08-11,73\n2011-08-12,70\n2011-08-13,34\n2011-08-14,38\n2011-08-15,37\n2011-08-16,66\n2011-08-17,35\n2011-08-18,51\n2011-08-19,54\n2011-08-20,36\n2011-08-21,65\n2011-08-22,40\n2011-08-23,33\n2011-08-24,65\n2011-08-25,59\n2011-08-26,66\n2011-08-27,31\n2011-08-28,45\n2011-08-29,32\n2011-08-30,38\n2011-08-31,60\n2011-09-01,58\n2011-09-02,63\n2011-09-03,38\n2011-09-04,25\n2011-09-05,40\n2011-09-06,62\n2011-09-07,91\n2011-09-08,64\n2011-09-09,56\n2011-09-10,37\n2011-09-11,51\n2011-09-12,41\n2011-09-13,40\n2011-09-14,69\n2011-09-15,48\n2011-09-16,44\n2011-09-17,14\n2011-09-18,28\n2011-09-19,29\n2011-09-20,59\n2011-09-21,48\n2011-09-22,34\n2011-09-23,104\n2011-09-24,84\n2011-09-25,48\n2011-09-26,81\n2011-09-27,84\n2011-09-28,88\n2011-09-29,99\n2011-09-30,110\n2011-10-01,120\n2011-10-02,90\n2011-10-03,57\n2011-10-04,67\n2011-10-05,71\n2011-10-06,48\n2011-10-07,74\n2011-10-08,59\n2011-10-09,69\n2011-10-10,75\n2011-10-11,78\n2011-10-12,72\n2011-10-13,82\n2011-10-14,61\n2011-10-15,61\n2011-10-16,41\n2011-10-17,104\n2011-10-18,62\n2011-10-19,88\n2011-10-20,75\n2011-10-21,97\n2011-10-22,45\n2011-10-23,58\n2011-10-24,85\n2011-10-25,109\n2011-10-26,66\n2011-10-27,45\n2011-10-28,57\n2011-10-29,53\n2011-10-30,50\n2011-10-31,89\n2011-11-01,61\n2011-11-02,78\n2011-11-03,74\n2011-11-04,85\n2011-11-05,84\n2011-11-06,43\n2011-11-07,53\n2011-11-08,48\n2011-11-09,71\n2011-11-10,35\n2011-11-11,72\n2011-11-12,115\n2011-11-13,90\n2011-11-14,64\n2011-11-15,49\n2011-11-16,45\n2011-11-17,79\n2011-11-18,61\n2011-11-19,81\n2011-11-20,78\n2011-11-21,63\n2011-11-22,89\n2011-11-23,66\n2011-11-24,60\n2011-11-25,90\n2011-11-26,108\n2011-11-27,88\n2011-11-28,64\n2011-11-29,72\n2011-11-30,76\n2011-12-01,107\n2011-12-02,73\n2011-12-03,65\n2011-12-04,74\n2011-12-05,80\n2011-12-06,116\n2011-12-07,96\n2011-12-08,113\n2011-12-09,101\n2011-12-10,88\n2011-12-11,142\n2011-12-12,121\n2011-12-13,118\n2011-12-14,86\n2011-12-15,73\n2011-12-16,84\n2011-12-17,56\n2011-12-18,86\n2011-12-19,85\n2011-12-20,89\n2011-12-21,58\n2011-12-22,46\n2011-12-23,65\n2011-12-24,39\n2011-12-25,18\n2011-12-26,39\n2011-12-27,55\n2011-12-28,47\n2011-12-29,71\n2011-12-30,85\n2011-12-31,73\n2012-01-01,56\n2012-01-02,76\n2012-01-03,60\n2012-01-04,121\n2012-01-05,77\n2012-01-06,65\n2012-01-07,60\n2012-01-08,82\n2012-01-09,72\n2012-01-10,106\n2012-01-11,96\n2012-01-12,82\n2012-01-13,145\n2012-01-14,65\n2012-01-15,64\n2012-01-16,71\n2012-01-17,79\n2012-01-18,88\n2012-01-19,82\n2012-01-20,71\n2012-01-21,57\n2012-01-22,61\n2012-01-23,69\n2012-01-24,107\n2012-01-25,99\n2012-01-26,92\n2012-01-27,70\n2012-01-28,44\n2012-01-29,84\n2012-01-30,54\n2012-01-31,71\n2012-02-01,95\n2012-02-02,86\n2012-02-03,87\n2012-02-04,82\n2012-02-05,115\n2012-02-06,189\n2012-02-07,116\n2012-02-08,122\n2012-02-09,106\n2012-02-10,97\n2012-02-11,94\n2012-02-12,90\n2012-02-13,91\n2012-02-14,106\n2012-02-15,93\n2012-02-16,119\n2012-02-17,122\n2012-02-18,109\n2012-02-19,161\n2012-02-20,120\n2012-02-21,144\n2012-02-22,117\n2012-02-23,78\n2012-02-24,68\n2012-02-25,104\n2012-02-26,81\n2012-02-27,87\n2012-02-28,110\n2012-02-29,71\n2012-03-01,83\n2012-03-02,65\n2012-03-03,82\n2012-03-04,133\n2012-03-05,139\n2012-03-06,107\n2012-03-07,77\n2012-03-08,102\n2012-03-09,111\n2012-03-10,100\n2012-03-11,166\n2012-03-12,78\n2012-03-13,100\n2012-03-14,57\n2012-03-15,53\n2012-03-16,99\n2012-03-17,88\n2012-03-18,67\n2012-03-19,160\n2012-03-20,100\n2012-03-21,101\n2012-03-22,99\n2012-03-23,123\n2012-03-24,93\n2012-03-25,142\n2012-03-26,111\n2012-03-27,84\n2012-03-28,67\n2012-03-29,76\n2012-03-30,99\n2012-03-31,109\n2012-04-01,118\n2012-04-02,124\n2012-04-03,109\n2012-04-04,175\n2012-04-05,118\n2012-04-06,92\n2012-04-07,147\n2012-04-08,80\n2012-04-09,135\n2012-04-10,120\n2012-04-11,166\n2012-04-12,77\n2012-04-13,67\n2012-04-14,94\n2012-04-15,102\n2012-04-16,123\n2012-04-17,88\n2012-04-18,130\n2012-04-19,86\n2012-04-20,108\n2012-04-21,117\n2012-04-22,95\n2012-04-23,112\n2012-04-24,106\n2012-04-25,95\n2012-04-26,85\n2012-04-27,107\n2012-04-28,120\n2012-04-29,165\n2012-04-30,127\n2012-05-01,86\n2012-05-02,107\n2012-05-03,92\n2012-05-04,107\n2012-05-05,80\n2012-05-06,103\n2012-05-07,131\n2012-05-08,73\n2012-05-09,105\n2012-05-10,81\n2012-05-11,140\n2012-05-12,83\n2012-05-13,109\n2012-05-14,67\n2012-05-15,71\n2012-05-16,86\n2012-05-17,118\n2012-05-18,101\n2012-05-19,77\n2012-05-20,110\n2012-05-21,77\n2012-05-22,81\n2012-05-23,70\n2012-05-24,79\n2012-05-25,60\n2012-05-26,65\n2012-05-27,46\n2012-05-28,74\n2012-05-29,48\n2012-05-30,90\n2012-05-31,95\n2012-06-01,84\n2012-06-02,31\n2012-06-03,73\n2012-06-04,98\n2012-06-05,63\n2012-06-06,66\n2012-06-07,57\n2012-06-08,78\n2012-06-09,54\n2012-06-10,122\n2012-06-11,95\n2012-06-12,87\n2012-06-13,113\n2012-06-14,79\n2012-06-15,107\n2012-06-16,106\n2012-06-17,96\n2012-06-18,55\n2012-06-19,79\n2012-06-20,94\n2012-06-21,54\n2012-06-22,44\n2012-06-23,67\n2012-06-24,64\n2012-06-25,96\n2012-06-26,73\n2012-06-27,108\n2012-06-28,40\n2012-06-29,87\n2012-06-30,44\n2012-07-01,61\n2012-07-02,91\n2012-07-03,118\n2012-07-04,96\n2012-07-05,123\n2012-07-06,170\n2012-07-07,117\n2012-07-08,136\n2012-07-09,81\n2012-07-10,74\n2012-07-11,96\n2012-07-12,97\n2012-07-13,74\n2012-07-14,83\n2012-07-15,64\n2012-07-16,95\n2012-07-17,119\n2012-07-18,102\n2012-07-19,70\n2012-07-20,66\n2012-07-21,102\n2012-07-22,96\n2012-07-23,107\n2012-07-24,100\n2012-07-25,76\n2012-07-26,96\n2012-07-27,81\n2012-07-28,93\n2012-07-29,74\n2012-07-30,61\n2012-07-31,73\n2012-08-01,100\n2012-08-02,128\n2012-08-03,79\n2012-08-04,106\n2012-08-05,72\n2012-08-06,109\n2012-08-07,107\n2012-08-08,119\n2012-08-09,82\n2012-08-10,100\n2012-08-11,60\n2012-08-12,77\n2012-08-13,68\n2012-08-14,88\n2012-08-15,116\n2012-08-16,94\n2012-08-17,99\n2012-08-18,141\n2012-08-19,46\n2012-08-20,61\n2012-08-21,75\n2012-08-22,84\n2012-08-23,76\n2012-08-24,102\n2012-08-25,71\n2012-08-26,83\n2012-08-27,91\n2012-08-28,80\n2012-08-29,60\n2012-08-30,78\n2012-08-31,61\n2012-09-01,57\n2012-09-02,41\n2012-09-03,86\n2012-09-04,88\n2012-09-05,73\n2012-09-06,100\n2012-09-07,106\n2012-09-08,57\n2012-09-09,40\n2012-09-10,65\n2012-09-11,59\n2012-09-12,99\n2012-09-13,55\n2012-09-14,64\n2012-09-15,40\n2012-09-16,52\n2012-09-17,57\n2012-09-18,51\n2012-09-19,38\n2012-09-20,47\n2012-09-21,53\n2012-09-22,69\n2012-09-23,40\n2012-09-24,32\n2012-09-25,45\n2012-09-26,54\n2012-09-27,59\n2012-09-28,61\n2012-09-29,58\n2012-09-30,62\n2012-10-01,96\n2012-10-02,101\n2012-10-03,98\n2012-10-04,78\n2012-10-05,107\n2012-10-06,59\n2012-10-07,48\n2012-10-08,60\n2012-10-09,76\n2012-10-10,126\n2012-10-11,58\n2012-10-12,70\n2012-10-13,37\n2012-10-14,70\n2012-10-15,79\n2012-10-16,77\n2012-10-17,33\n2012-10-18,86\n2012-10-19,62\n2012-10-20,36\n2012-10-21,18\n2012-10-22,55\n2012-10-23,78\n2012-10-24,58\n2012-10-25,87\n2012-10-26,112\n2012-10-27,48\n2012-10-28,53\n2012-10-29,38\n2012-10-30,92\n2012-10-31,54\n2012-11-01,109\n2012-11-02,119\n2012-11-03,71\n2012-11-04,59\n2012-11-05,91\n2012-11-06,39\n2012-11-07,56\n2012-11-08,66\n2012-11-09,56\n2012-11-10,39\n2012-11-11,20\n2012-11-12,68\n2012-11-13,66\n2012-11-14,58\n2012-11-15,47\n2012-11-16,70\n2012-11-17,67\n2012-11-18,38\n2012-11-19,95\n2012-11-20,114\n2012-11-21,87\n2012-11-22,49\n2012-11-23,80\n2012-11-24,70\n2012-11-25,35\n2012-11-26,71\n2012-11-27,79\n2012-11-28,64\n2012-11-29,58\n2012-11-30,36\n2012-12-01,56\n2012-12-02,58\n2012-12-03,84\n2012-12-04,103\n2012-12-05,118\n2012-12-06,46\n2012-12-07,58\n2012-12-08,98\n2012-12-09,43\n2012-12-10,70\n2012-12-11,91\n2012-12-12,74\n2012-12-13,88\n2012-12-14,74\n2012-12-15,54\n2012-12-16,81\n2012-12-17,121\n2012-12-18,111\n2012-12-19,112\n2012-12-20,103\n2012-12-21,63\n2012-12-22,59\n2012-12-23,91\n2012-12-24,99\n2012-12-25,60\n2012-12-26,61\n2012-12-27,90\n2012-12-28,59\n2012-12-29,69\n2012-12-30,66\n2012-12-31,110\n2013-01-01,65\n2013-01-02,73\n2013-01-03,92\n2013-01-04,93\n2013-01-05,67\n2013-01-06,84\n2013-01-07,176\n2013-01-08,150\n2013-01-09,143\n2013-01-10,195\n2013-01-11,158\n2013-01-12,99\n2013-01-13,156\n2013-01-14,114\n2013-01-15,109\n2013-01-16,182\n2013-01-17,139\n2013-01-18,96\n2013-01-19,82\n2013-01-20,116\n2013-01-21,88\n2013-01-22,124\n2013-01-23,120\n2013-01-24,108\n2013-01-25,143\n2013-01-26,142\n2013-01-27,69\n2013-01-28,128\n2013-01-29,114\n2013-01-30,120\n2013-01-31,96\n2013-02-01,69\n2013-02-02,104\n2013-02-03,156\n2013-02-04,90\n2013-02-05,116\n2013-02-06,81\n2013-02-07,117\n2013-02-08,123\n2013-02-09,80\n2013-02-10,83\n2013-02-11,100\n2013-02-12,115\n2013-02-13,153\n2013-02-14,95\n2013-02-15,146\n2013-02-16,111\n2013-02-17,118\n2013-02-18,119\n2013-02-19,120\n2013-02-20,142\n2013-02-21,127\n2013-02-22,120\n2013-02-23,44\n2013-02-24,131\n2013-02-25,166\n2013-02-26,176\n2013-02-27,113\n2013-02-28,116\n2013-03-01,112\n2013-03-02,72\n2013-03-03,73\n2013-03-04,123\n2013-03-05,111\n2013-03-06,102\n2013-03-07,99\n2013-03-08,109\n2013-03-09,108\n2013-03-10,130\n2013-03-11,121\n2013-03-12,85\n2013-03-13,118\n2013-03-14,129\n2013-03-15,139\n2013-03-16,98\n2013-03-17,137\n2013-03-18,139\n2013-03-19,114\n2013-03-20,153\n2013-03-21,88\n2013-03-22,151\n2013-03-23,105\n2013-03-24,107\n2013-03-25,137\n2013-03-26,114\n2013-03-27,107\n2013-03-28,113\n2013-03-29,150\n2013-03-30,83\n2013-03-31,95\n2013-04-01,124\n2013-04-02,132\n2013-04-03,116\n2013-04-04,135\n2013-04-05,80\n2013-04-06,90\n2013-04-07,149\n2013-04-08,178\n2013-04-09,164\n2013-04-10,120\n2013-04-11,111\n2013-04-12,138\n2013-04-13,123\n2013-04-14,132\n2013-04-15,111\n2013-04-16,90\n2013-04-17,90\n2013-04-18,143\n2013-04-19,110\n2013-04-20,79\n2013-04-21,128\n2013-04-22,93\n2013-04-23,70\n2013-04-24,85\n2013-04-25,83\n2013-04-26,95\n2013-04-27,82\n2013-04-28,96\n2013-04-29,91\n2013-04-30,130\n2013-05-01,117\n2013-05-02,134\n2013-05-03,113\n2013-05-04,97\n2013-05-05,124\n2013-05-06,120\n2013-05-07,98\n2013-05-08,112\n2013-05-09,155\n2013-05-10,135\n2013-05-11,88\n2013-05-12,64\n2013-05-13,123\n2013-05-14,88\n2013-05-15,162\n2013-05-16,136\n2013-05-17,143\n2013-05-18,71\n2013-05-19,89\n2013-05-20,106\n2013-05-21,136\n2013-05-22,115\n2013-05-23,91\n2013-05-24,148\n2013-05-25,70\n2013-05-26,47\n2013-05-27,135\n2013-05-28,150\n2013-05-29,88\n2013-05-30,102\n2013-05-31,82\n2013-06-01,79\n2013-06-02,86\n2013-06-03,87\n2013-06-04,100\n2013-06-05,121\n2013-06-06,112\n2013-06-07,167\n2013-06-08,103\n2013-06-09,83\n2013-06-10,132\n2013-06-11,109\n2013-06-12,133\n2013-06-13,160\n2013-06-14,178\n2013-06-15,73\n2013-06-16,138\n2013-06-17,111\n2013-06-18,112\n2013-06-19,126\n2013-06-20,146\n2013-06-21,122\n2013-06-22,122\n2013-06-23,98\n2013-06-24,86\n2013-06-25,128\n2013-06-26,160\n2013-06-27,115\n2013-06-28,103\n2013-06-29,57\n2013-06-30,76\n2013-07-01,132\n2013-07-02,134\n2013-07-03,95\n2013-07-04,62\n2013-07-05,131\n2013-07-06,90\n2013-07-07,92\n2013-07-08,142\n2013-07-09,111\n2013-07-10,109\n2013-07-11,93\n2013-07-12,104\n2013-07-13,39\n2013-07-14,67\n2013-07-15,125\n2013-07-16,114\n2013-07-17,89\n2013-07-18,107\n2013-07-19,142\n2013-07-20,50\n2013-07-21,58\n2013-07-22,166\n2013-07-23,149\n2013-07-24,169\n2013-07-25,71\n2013-07-26,160\n2013-07-27,50\n2013-07-28,100\n2013-07-29,108\n2013-07-30,206\n2013-07-31,181\n2013-08-01,188\n2013-08-02,143\n2013-08-03,121\n2013-08-04,82\n2013-08-05,117\n2013-08-06,138\n2013-08-07,143\n2013-08-08,117\n2013-08-09,149\n2013-08-10,69\n2013-08-11,68\n2013-08-12,98\n2013-08-13,89\n2013-08-14,108\n2013-08-15,115\n2013-08-16,99\n2013-08-17,62\n2013-08-18,66\n2013-08-19,157\n2013-08-20,126\n2013-08-21,129\n2013-08-22,122\n2013-08-23,124\n2013-08-24,101\n2013-08-25,109\n2013-08-26,175\n2013-08-27,155\n2013-08-28,159\n2013-08-29,116\n2013-08-30,133\n2013-08-31,112\n2013-09-01,103\n2013-09-02,83\n2013-09-03,115\n2013-09-04,141\n2013-09-05,115\n2013-09-06,77\n2013-09-07,99\n2013-09-08,93\n2013-09-09,163\n2013-09-10,143\n2013-09-11,86\n2013-09-12,137\n2013-09-13,135\n2013-09-14,83\n2013-09-15,130\n2013-09-16,123\n2013-09-17,104\n2013-09-18,97\n2013-09-19,104\n2013-09-20,118\n2013-09-21,88\n2013-09-22,88\n2013-09-23,105\n2013-09-24,219\n2013-09-25,188\n2013-09-26,108\n2013-09-27,123\n2013-09-28,81\n2013-09-29,83\n2013-09-30,99\n2013-10-01,80\n2013-10-02,99\n2013-10-03,110\n2013-10-04,121\n2013-10-05,103\n2013-10-06,141\n2013-10-07,155\n2013-10-08,177\n2013-10-09,117\n2013-10-10,117\n2013-10-11,202\n2013-10-12,103\n2013-10-13,140\n2013-10-14,94\n2013-10-15,128\n2013-10-16,167\n2013-10-17,96\n2013-10-18,148\n2013-10-19,89\n2013-10-20,122\n2013-10-21,113\n2013-10-22,160\n2013-10-23,115\n2013-10-24,134\n2013-10-25,160\n2013-10-26,58\n2013-10-27,110\n2013-10-28,191\n2013-10-29,113\n2013-10-30,169\n2013-10-31,143\n2013-11-01,119\n2013-11-02,161\n2013-11-03,104\n2013-11-04,103\n2013-11-05,165\n2013-11-06,121\n2013-11-07,156\n2013-11-08,177\n2013-11-09,85\n2013-11-10,81\n2013-11-11,194\n2013-11-12,180\n2013-11-13,163\n2013-11-14,106\n2013-11-15,97\n2013-11-16,39\n2013-11-17,93\n2013-11-18,127\n2013-11-19,129\n2013-11-20,126\n2013-11-21,109\n2013-11-22,124\n2013-11-23,76\n2013-11-24,107\n2013-11-25,117\n2013-11-26,136\n2013-11-27,233\n2013-11-28,37\n2013-11-29,94\n2013-11-30,138\n2013-12-01,94\n2013-12-02,119\n2013-12-03,152\n2013-12-04,123\n2013-12-05,141\n2013-12-06,144\n2013-12-07,131\n2013-12-08,116\n2013-12-09,149\n2013-12-10,173\n2013-12-11,118\n2013-12-12,172\n2013-12-13,165\n2013-12-14,115\n2013-12-15,84\n2013-12-16,122\n2013-12-17,150\n2013-12-18,124\n2013-12-19,140\n2013-12-20,131\n2013-12-21,106\n2013-12-22,97\n2013-12-23,82\n2013-12-24,50\n2013-12-25,29\n2013-12-26,60\n2013-12-27,98\n2013-12-28,66\n2013-12-29,106\n2013-12-30,173\n2013-12-31,167\n2014-01-01,74\n2014-01-02,128\n2014-01-03,201\n2014-01-04,123\n2014-01-05,93\n2014-01-06,155\n2014-01-07,237\n2014-01-08,207\n2014-01-09,202\n2014-01-10,203\n2014-01-11,124\n2014-01-12,112\n2014-01-13,135\n2014-01-14,119\n2014-01-15,186\n2014-01-16,197\n2014-01-17,107\n2014-01-18,105\n2014-01-19,150\n2014-01-20,116\n2014-01-21,143\n2014-01-22,164\n2014-01-23,234\n2014-01-24,136\n2014-01-25,123\n2014-01-26,102\n2014-01-27,164\n2014-01-28,166\n2014-01-29,151\n2014-01-30,136\n2014-01-31,102\n2014-02-01,73\n2014-02-02,122\n2014-02-03,167\n2014-02-04,209\n2014-02-05,171\n2014-02-06,161\n2014-02-07,137\n2014-02-08,131\n2014-02-09,208\n2014-02-10,227\n2014-02-11,212\n2014-02-12,135\n2014-02-13,191\n2014-02-14,161\n2014-02-15,152\n2014-02-16,101\n2014-02-17,184\n2014-02-18,307\n2014-02-19,165\n2014-02-20,122\n2014-02-21,183\n2014-02-22,139\n2014-02-23,132\n2014-02-24,181\n2014-02-25,173\n2014-02-26,161\n2014-02-27,113\n2014-02-28,103\n2014-03-01,91\n2014-03-02,76\n2014-03-03,126\n2014-03-04,109\n2014-03-05,119\n2014-03-06,162\n2014-03-07,115\n2014-03-08,118\n2014-03-09,73\n2014-03-10,140\n2014-03-11,158\n2014-03-12,119\n2014-03-13,139\n2014-03-14,179\n2014-03-15,110\n2014-03-16,80\n2014-03-17,144\n2014-03-18,114\n2014-03-19,132\n2014-03-20,129\n2014-03-21,167\n2014-03-22,132\n2014-03-23,102\n2014-03-24,187\n2014-03-25,148\n2014-03-26,223\n2014-03-27,145\n2014-03-28,162\n2014-03-29,91\n2014-03-30,100\n2014-03-31,147\n2014-04-01,116\n2014-04-02,154\n2014-04-03,107\n2014-04-04,103\n2014-04-05,94\n2014-04-06,86\n2014-04-07,140\n2014-04-08,142\n2014-04-09,118\n2014-04-10,149\n2014-04-11,90\n2014-04-12,82\n2014-04-13,94\n2014-04-14,76\n2014-04-15,128\n2014-04-16,157\n2014-04-17,130\n2014-04-18,191\n2014-04-19,127\n2014-04-20,102\n2014-04-21,179\n2014-04-22,153\n2014-04-23,167\n2014-04-24,232\n2014-04-25,182\n2014-04-26,119\n2014-04-27,187\n2014-04-28,161\n2014-04-29,190\n2014-04-30,170\n2014-05-01,137\n2014-05-02,151\n2014-05-03,107\n2014-05-04,108\n2014-05-05,193\n2014-05-06,114\n2014-05-07,247\n2014-05-08,230\n2014-05-09,264\n2014-05-10,175\n2014-05-11,127\n2014-05-12,144\n2014-05-13,212\n2014-05-14,236\n2014-05-15,154\n2014-05-16,155\n2014-05-17,140\n2014-05-18,105\n2014-05-19,145\n2014-05-20,156\n2014-05-21,149\n2014-05-22,190\n2014-05-23,196\n2014-05-24,102\n2014-05-25,150\n2014-05-26,124\n2014-05-27,134\n2014-05-28,148\n2014-05-29,185\n2014-05-30,174\n2014-05-31,119\n2014-06-01,182\n2014-06-02,133\n2014-06-03,195\n2014-06-04,183\n2014-06-05,186\n2014-06-06,254\n2014-06-07,141\n2014-06-08,130\n2014-06-09,230\n2014-06-10,203\n2014-06-11,164\n2014-06-12,212\n2014-06-13,169\n2014-06-14,129\n2014-06-15,100\n2014-06-16,160\n2014-06-17,175\n2014-06-18,154\n2014-06-19,197\n2014-06-20,146\n2014-06-21,44\n2014-06-22,81\n2014-06-23,153\n2014-06-24,174\n2014-06-25,174\n2014-06-26,168\n2014-06-27,173\n2014-06-28,96\n2014-06-29,63\n2014-06-30,139\n2014-07-01,160\n2014-07-02,179\n2014-07-03,151\n2014-07-04,134\n2014-07-05,121\n2014-07-06,144\n2014-07-07,151\n2014-07-08,120\n2014-07-09,160\n2014-07-10,160\n2014-07-11,198\n2014-07-12,116\n2014-07-13,125\n2014-07-14,115\n2014-07-15,127\n2014-07-16,242\n2014-07-17,147\n2014-07-18,199\n2014-07-19,103\n2014-07-20,159\n2014-07-21,241\n2014-07-22,189\n2014-07-23,149\n2014-07-24,215\n2014-07-25,136\n2014-07-26,105\n2014-07-27,80\n2014-07-28,126\n2014-07-29,176\n2014-07-30,145\n2014-07-31,108\n2014-08-01,205\n2014-08-02,125\n2014-08-03,93\n2014-08-04,162\n2014-08-05,229\n2014-08-06,253\n2014-08-07,226\n2014-08-08,177\n2014-08-09,133\n2014-08-10,164\n2014-08-11,199\n2014-08-12,162\n2014-08-13,121\n2014-08-14,157\n2014-08-15,123\n2014-08-16,96\n2014-08-17,139\n2014-08-18,134\n2014-08-19,186\n2014-08-20,182\n2014-08-21,205\n2014-08-22,169\n2014-08-23,93\n2014-08-24,110\n2014-08-25,167\n2014-08-26,218\n2014-08-27,188\n2014-08-28,237\n2014-08-29,163\n2014-08-30,126\n2014-08-31,127\n2014-09-01,181\n2014-09-02,240\n2014-09-03,195\n2014-09-04,181\n2014-09-05,177\n2014-09-06,119\n2014-09-07,226\n2014-09-08,133\n2014-09-09,176\n2014-09-10,207\n2014-09-11,146\n2014-09-12,145\n2014-09-13,89\n2014-09-14,125\n2014-09-15,205\n2014-09-16,189\n2014-09-17,165\n2014-09-18,232\n2014-09-19,192\n2014-09-20,124\n2014-09-21,143\n2014-09-22,171\n2014-09-23,192\n2014-09-24,207\n2014-09-25,183\n2014-09-26,201\n2014-09-27,268\n2014-09-28,335\n2014-09-29,244\n2014-09-30,256\n2014-10-01,321\n2014-10-02,241\n2014-10-03,199\n2014-10-04,118\n2014-10-05,93\n2014-10-06,149\n2014-10-07,173\n2014-10-08,169\n2014-10-09,337\n2014-10-10,155\n2014-10-11,89\n2014-10-12,128\n2014-10-13,135\n2014-10-14,190\n2014-10-15,181\n2014-10-16,187\n2014-10-17,181\n2014-10-18,139\n2014-10-19,157\n2014-10-20,155\n2014-10-21,165\n2014-10-22,124\n2014-10-23,211\n2014-10-24,158\n2014-10-25,86\n2014-10-26,65\n2014-10-27,132\n2014-10-28,135\n2014-10-29,227\n2014-10-30,187\n2014-10-31,156\n2014-11-01,86\n2014-11-02,81\n2014-11-03,152\n2014-11-04,167\n2014-11-05,216\n2014-11-06,229\n2014-11-07,208\n2014-11-08,110\n2014-11-09,205\n2014-11-10,161\n2014-11-11,165\n2014-11-12,167\n2014-11-13,162\n2014-11-14,174\n2014-11-15,153\n2014-11-16,204\n2014-11-17,219\n2014-11-18,203\n2014-11-19,180\n2014-11-20,129\n2014-11-21,168\n2014-11-22,164\n2014-11-23,141\n2014-11-24,109\n2014-11-25,176\n2014-11-26,154\n2014-11-27,90\n2014-11-28,93\n2014-11-29,116\n2014-11-30,174\n2014-12-01,184\n2014-12-02,134\n2014-12-03,129\n2014-12-04,126\n2014-12-05,132\n2014-12-06,115\n2014-12-07,160\n2014-12-08,218\n2014-12-09,158\n2014-12-10,127\n2014-12-11,140\n2014-12-12,135\n2014-12-13,136\n2014-12-14,160\n2014-12-15,196\n2014-12-16,191\n2014-12-17,138\n2014-12-18,104\n2014-12-19,205\n2014-12-20,147\n2014-12-21,196\n2014-12-22,194\n2014-12-23,142\n2014-12-24,124\n2014-12-25,70\n2014-12-26,112\n2014-12-27,193\n2014-12-28,118\n2014-12-29,103\n2014-12-30,214\n2014-12-31,134\n2015-01-01,103\n2015-01-02,223\n2015-01-03,188\n2015-01-04,143\n2015-01-05,165\n2015-01-06,185\n2015-01-07,145\n2015-01-08,252\n2015-01-09,185\n2015-01-10,160\n2015-01-11,146\n2015-01-12,186\n2015-01-13,211\n2015-01-14,131\n2015-01-15,187\n2015-01-16,174\n2015-01-17,164\n2015-01-18,148\n2015-01-19,233\n2015-01-20,139\n2015-01-21,160\n2015-01-22,156\n2015-01-23,161\n2015-01-24,134\n2015-01-25,120\n2015-01-26,174\n2015-01-27,166\n2015-01-28,217\n2015-01-29,146\n2015-01-30,205\n2015-01-31,185\n2015-02-01,126\n2015-02-02,182\n2015-02-03,148\n2015-02-04,182\n2015-02-05,256\n2015-02-06,218\n2015-02-07,156\n2015-02-08,163\n2015-02-09,195\n2015-02-10,232\n2015-02-11,189\n2015-02-12,216\n2015-02-13,152\n2015-02-14,120\n2015-02-15,203\n2015-02-16,177\n2015-02-17,215\n2015-02-18,241\n2015-02-19,190\n2015-02-20,266\n2015-02-21,285\n2015-02-22,205\n2015-02-23,278\n2015-02-24,197\n2015-02-25,285\n2015-02-26,175\n2015-02-27,185\n2015-02-28,158\n2015-03-01,140\n2015-03-02,247\n2015-03-03,230\n2015-03-04,200\n2015-03-05,283\n2015-03-06,271\n2015-03-07,187\n2015-03-08,117\n2015-03-09,267\n2015-03-10,204\n2015-03-11,276\n2015-03-12,207\n2015-03-13,289\n2015-03-14,155\n2015-03-15,107\n2015-03-16,314\n2015-03-17,266\n2015-03-18,183\n2015-03-19,228\n2015-03-20,217\n2015-03-21,101\n2015-03-22,187\n2015-03-23,230\n2015-03-24,254\n2015-03-25,222\n2015-03-26,228\n2015-03-27,242\n2015-03-28,157\n2015-03-29,108\n2015-03-30,252\n2015-03-31,201\n2015-04-01,237\n2015-04-02,175\n2015-04-03,222\n2015-04-04,107\n2015-04-05,91\n2015-04-06,198\n2015-04-07,181\n2015-04-08,215\n2015-04-09,230\n2015-04-10,141\n2015-04-11,94\n2015-04-12,72\n2015-04-13,180\n2015-04-14,258\n2015-04-15,178\n2015-04-16,210\n2015-04-17,246\n2015-04-18,111\n2015-04-19,139\n2015-04-20,134\n2015-04-21,160\n2015-04-22,186\n2015-04-23,193\n2015-04-24,201\n2015-04-25,140\n2015-04-26,164\n2015-04-27,185\n2015-04-28,176\n2015-04-29,262\n2015-04-30,216\n2015-05-01,188\n2015-05-02,142\n2015-05-03,172\n2015-05-04,173\n2015-05-05,174\n2015-05-06,202\n2015-05-07,157\n2015-05-08,222\n2015-05-09,97\n2015-05-10,97\n2015-05-11,193\n2015-05-12,176\n2015-05-13,193\n2015-05-14,235\n2015-05-15,190\n2015-05-16,116\n2015-05-17,159\n2015-05-18,312\n2015-05-19,185\n2015-05-20,242\n2015-05-21,164\n2015-05-22,175\n2015-05-23,75\n2015-05-24,115\n2015-05-25,141\n2015-05-26,248\n2015-05-27,220\n2015-05-28,196\n2015-05-29,196\n2015-05-30,152\n2015-05-31,109\n2015-06-01,193\n2015-06-02,184\n2015-06-03,155\n2015-06-04,134\n2015-06-05,128\n2015-06-06,98\n2015-06-07,105\n2015-06-08,161\n2015-06-09,176\n2015-06-10,267\n2015-06-11,184\n2015-06-12,195\n2015-06-13,108\n2015-06-14,182\n2015-06-15,195\n2015-06-16,240\n2015-06-17,279\n2015-06-18,209\n2015-06-19,251\n2015-06-20,157\n2015-06-21,120\n2015-06-22,282\n2015-06-23,223\n2015-06-24,233\n2015-06-25,199\n2015-06-26,156\n2015-06-27,79\n2015-06-28,159\n2015-06-29,192\n2015-06-30,234\n2015-07-01,252\n2015-07-02,191\n2015-07-03,151\n2015-07-04,107\n2015-07-05,95\n2015-07-06,155\n2015-07-07,224\n2015-07-08,201\n2015-07-09,189\n2015-07-10,184\n2015-07-11,142\n2015-07-12,130\n2015-07-13,149\n2015-07-14,235\n2015-07-15,166\n2015-07-16,258\n2015-07-17,236\n2015-07-18,182\n2015-07-19,129\n2015-07-20,237\n2015-07-21,275\n2015-07-22,151\n2015-07-23,211\n2015-07-24,181\n2015-07-25,125\n2015-07-26,125\n2015-07-27,206\n2015-07-28,211\n2015-07-29,176\n2015-07-30,194\n2015-07-31,210\n2015-08-01,134\n2015-08-02,153\n2015-08-03,224\n2015-08-04,221\n2015-08-05,221\n2015-08-06,217\n2015-08-07,163\n2015-08-08,99\n2015-08-09,95\n2015-08-10,197\n2015-08-11,186\n2015-08-12,225\n2015-08-13,203\n2015-08-14,170\n2015-08-15,93\n2015-08-16,108\n2015-08-17,112\n2015-08-18,170\n2015-08-19,198\n2015-08-20,200\n2015-08-21,203\n2015-08-22,105\n2015-08-23,119\n2015-08-24,186\n2015-08-25,175\n2015-08-26,205\n2015-08-27,197\n2015-08-28,174\n2015-08-29,52\n2015-08-30,127\n2015-08-31,199\n2015-09-01,219\n2015-09-02,168\n2015-09-03,251\n2015-09-04,153\n2015-09-05,102\n2015-09-06,82\n2015-09-07,114\n2015-09-08,196\n2015-09-09,272\n2015-09-10,228\n2015-09-11,241\n2015-09-12,136\n2015-09-13,108\n2015-09-14,216\n2015-09-15,197\n2015-09-16,199\n2015-09-17,209\n2015-09-18,197\n2015-09-19,148\n2015-09-20,168\n2015-09-21,194\n2015-09-22,193\n2015-09-23,152\n2015-09-24,166\n2015-09-25,215\n2015-09-26,161\n2015-09-27,139\n2015-09-28,253\n2015-09-29,211\n2015-09-30,232\n2015-10-01,206\n2015-10-02,213\n2015-10-03,129\n2015-10-04,114\n2015-10-05,227\n2015-10-06,240\n2015-10-07,202\n2015-10-08,219\n2015-10-09,190\n2015-10-10,146\n2015-10-11,145\n2015-10-12,125\n2015-10-13,218\n2015-10-14,247\n2015-10-15,201\n2015-10-16,184\n2015-10-17,112\n2015-10-18,128\n2015-10-19,276\n2015-10-20,190\n2015-10-21,251\n2015-10-22,145\n2015-10-23,159\n2015-10-24,104\n2015-10-25,153\n2015-10-26,212\n2015-10-27,179\n2015-10-28,166\n2015-10-29,180\n2015-10-30,188\n2015-10-31,65\n2015-11-01,120\n2015-11-02,225\n2015-11-03,196\n2015-11-04,229\n2015-11-05,211\n2015-11-06,181\n2015-11-07,111\n2015-11-08,167\n2015-11-09,213\n2015-11-10,256\n2015-11-11,297\n2015-11-12,223\n2015-11-13,290\n2015-11-14,139\n2015-11-15,131\n2015-11-16,221\n2015-11-17,189\n2015-11-18,208\n2015-11-19,235\n2015-11-20,245\n2015-11-21,160\n2015-11-22,150\n2015-11-23,212\n2015-11-24,316\n2015-11-25,256\n2015-11-26,96\n2015-11-27,114\n2015-11-28,152\n2015-11-29,160\n2015-11-30,165\n2015-12-01,230\n2015-12-02,192\n2015-12-03,171\n2015-12-04,149\n2015-12-05,138\n2015-12-06,268\n2015-12-07,200\n2015-12-08,248\n2015-12-09,213\n2015-12-10,241\n2015-12-11,232\n2015-12-12,95\n2015-12-13,120\n2015-12-14,220\n2015-12-15,258\n2015-12-16,230\n2015-12-17,262\n2015-12-18,226\n2015-12-19,163\n2015-12-20,131\n2015-12-21,220\n2015-12-22,153\n2015-12-23,192\n2015-12-24,96\n2015-12-25,53\n2015-12-26,85\n2015-12-27,96\n2015-12-28,139\n2015-12-29,166\n2015-12-30,156\n2015-12-31,128\n2016-01-01,131\n2016-01-02,151\n2016-01-03,154\n2016-01-04,185\n2016-01-05,226\n2016-01-06,276\n2016-01-07,310\n2016-01-08,242\n2016-01-09,197\n2016-01-10,159\n2016-01-11,330\n2016-01-12,212\n2016-01-13,261\n2016-01-14,294\n2016-01-15,263\n2016-01-16,228\n2016-01-17,200\n2016-01-18,203\n2016-01-19,214\n2016-01-20,195\n2016-01-21,268\n2016-01-22,209\n2016-01-23,169\n2016-01-24,214\n2016-01-25,251\n2016-01-26,224\n2016-01-27,211\n2016-01-28,238\n2016-01-29,316\n2016-01-30,187\n2016-01-31,253\n2016-02-01,271\n2016-02-02,307\n2016-02-03,221\n2016-02-04,209\n2016-02-05,201\n2016-02-06,165\n2016-02-07,163\n2016-02-08,191\n2016-02-09,217\n2016-02-10,192\n2016-02-11,218\n2016-02-12,291\n2016-02-13,137\n2016-02-14,145\n2016-02-15,182\n2016-02-16,249\n2016-02-17,238\n2016-02-18,224\n2016-02-19,258\n2016-02-20,136\n2016-02-21,168\n2016-02-22,211\n2016-02-23,256\n2016-02-24,232\n2016-02-25,242\n2016-02-26,232\n2016-02-27,179\n2016-02-28,246\n2016-02-29,257\n2016-03-01,208\n2016-03-02,178\n2016-03-03,208\n2016-03-04,208\n2016-03-05,127\n2016-03-06,119\n2016-03-07,208\n2016-03-08,236\n2016-03-09,191\n2016-03-10,136\n2016-03-11,180\n2016-03-12,98\n2016-03-13,97\n2016-03-14,142\n2016-03-15,180\n2016-03-16,245\n2016-03-17,232\n2016-03-18,188\n2016-03-19,119\n2016-03-20,159\n2016-03-21,216\n2016-03-22,200\n2016-03-23,228\n2016-03-24,184\n2016-03-25,272\n2016-03-26,145\n2016-03-27,101\n2016-03-28,241\n2016-03-29,204\n2016-03-30,153\n2016-03-31,177\n2016-04-01,245\n2016-04-02,175\n2016-04-03,175\n2016-04-04,206\n2016-04-05,190\n2016-04-06,189\n2016-04-07,174\n2016-04-08,182\n2016-04-09,182\n2016-04-10,124\n2016-04-11,205\n2016-04-12,218\n2016-04-13,233\n2016-04-14,231\n2016-04-15,155\n2016-04-16,174\n2016-04-17,61\n2016-04-18,197\n2016-04-19,197\n2016-04-20,270\n2016-04-21,174\n2016-04-22,166\n2016-04-23,131\n2016-04-24,89\n2016-04-25,185\n2016-04-26,155\n2016-04-27,147\n2016-04-28,129\n2016-04-29,182\n2016-04-30,114\n2016-05-01,114\n2016-05-02,268\n2016-05-03,157\n2016-05-04,184\n2016-05-05,176\n2016-05-06,162\n2016-05-07,147\n2016-05-08,80\n2016-05-09,190\n2016-05-10,205\n2016-05-11,190\n2016-05-12,140\n2016-05-13,192\n2016-05-14,77\n2016-05-15,98\n2016-05-16,187\n2016-05-17,144\n2016-05-18,160\n2016-05-19,197\n2016-05-20,183\n2016-05-21,135\n2016-05-22,150\n2016-05-23,211\n2016-05-24,236\n2016-05-25,167\n2016-05-26,160\n2016-05-27,131\n2016-05-28,97\n2016-05-29,118\n2016-05-30,162\n2016-05-31,206\n2016-06-01,280\n2016-06-02,224\n2016-06-03,255\n2016-06-04,130\n2016-06-05,119\n2016-06-06,176\n2016-06-07,212\n2016-06-08,211\n2016-06-09,209\n2016-06-10,195\n2016-06-11,178\n2016-06-12,129\n2016-06-13,292\n2016-06-14,211\n2016-06-15,196\n2016-06-16,192\n2016-06-17,199\n2016-06-18,116\n2016-06-19,103\n2016-06-20,271\n2016-06-21,233\n2016-06-22,220\n2016-06-23,175\n2016-06-24,165\n2016-06-25,67\n2016-06-26,116\n2016-06-27,271\n2016-06-28,214\n2016-06-29,193\n2016-06-30,243\n2016-07-01,218\n2016-07-02,170\n2016-07-03,102\n2016-07-04,123\n2016-07-05,148\n2016-07-06,222\n2016-07-07,204\n2016-07-08,172\n2016-07-09,115\n2016-07-10,115\n2016-07-11,175\n2016-07-12,189\n2016-07-13,168\n2016-07-14,164\n2016-07-15,159\n2016-07-16,91\n2016-07-17,135\n2016-07-18,210\n2016-07-19,208\n2016-07-20,199\n2016-07-21,155\n2016-07-22,184\n2016-07-23,98\n2016-07-24,117\n2016-07-25,200\n2016-07-26,233\n2016-07-27,221\n2016-07-28,267\n2016-07-29,219\n2016-07-30,122\n2016-07-31,133\n2016-08-01,178\n2016-08-02,170\n2016-08-03,131\n2016-08-04,230\n2016-08-05,155\n2016-08-06,71\n2016-08-07,105\n2016-08-08,158\n2016-08-09,205\n2016-08-10,227\n2016-08-11,206\n2016-08-12,194\n2016-08-13,66\n2016-08-14,97\n2016-08-15,165\n2016-08-16,170\n2016-08-17,191\n2016-08-18,180\n2016-08-19,181\n2016-08-20,126\n2016-08-21,143\n2016-08-22,207\n2016-08-23,227\n2016-08-24,206\n2016-08-25,242\n2016-08-26,140\n2016-08-27,104\n2016-08-28,111\n2016-08-29,192\n2016-08-30,182\n2016-08-31,254\n2016-09-01,265\n2016-09-02,143\n2016-09-03,74\n2016-09-04,122\n2016-09-05,130\n2016-09-06,213\n2016-09-07,177\n2016-09-08,169\n2016-09-09,174\n2016-09-10,65\n2016-09-11,89\n2016-09-12,153\n2016-09-13,119\n2016-09-14,141\n2016-09-15,179\n2016-09-16,190\n2016-09-17,85\n2016-09-18,150\n2016-09-19,200\n2016-09-20,169\n2016-09-21,149\n2016-09-22,170\n2016-09-23,131\n2016-09-24,76\n2016-09-25,78\n2016-09-26,163\n2016-09-27,187\n2016-09-28,259\n2016-09-29,154\n2016-09-30,150\n2016-10-01,98\n2016-10-02,103\n2016-10-03,199\n2016-10-04,213\n2016-10-05,263\n2016-10-06,212\n2016-10-07,226\n2016-10-08,135\n2016-10-09,93\n2016-10-10,181\n2016-10-11,166\n2016-10-12,224\n2016-10-13,221\n2016-10-14,194\n2016-10-15,97\n2016-10-16,126\n2016-10-17,141\n2016-10-18,146\n2016-10-19,114\n2016-10-20,142\n2016-10-21,182\n2016-10-22,95\n2016-10-23,124\n2016-10-24,132\n2016-10-25,140\n2016-10-26,148\n2016-10-27,124\n2016-10-28,123\n2016-10-29,156\n2016-10-30,81\n2016-10-31,82\n2016-11-01,127\n2016-11-02,146\n2016-11-03,156\n2016-11-04,148\n2016-11-05,78\n2016-11-06,103\n2016-11-07,156\n2016-11-08,120\n2016-11-09,147\n2016-11-10,148\n2016-11-11,114\n2016-11-12,76\n2016-11-13,158\n2016-11-14,179\n2016-11-15,214\n2016-11-16,142\n2016-11-17,184\n2016-11-18,162\n2016-11-19,97\n2016-11-20,103\n2016-11-21,162\n2016-11-22,112\n2016-11-23,86\n2016-11-24,75\n2016-11-25,56\n2016-11-26,47\n2016-11-27,78\n2016-11-28,141\n2016-11-29,169\n2016-11-30,138\n2016-12-01,137\n2016-12-02,147\n2016-12-03,123\n2016-12-04,107\n2016-12-05,214\n2016-12-06,213\n2016-12-07,190\n2016-12-08,168\n2016-12-09,156\n2016-12-10,87\n2016-12-11,106\n2016-12-12,210\n2016-12-13,227\n2016-12-14,192\n2016-12-15,163\n2016-12-16,89\n2016-12-17,95\n2016-12-18,90\n2016-12-19,144\n2016-12-20,138\n2016-12-21,152\n2016-12-22,159\n2016-12-23,122\n2016-12-24,67\n2016-12-25,57\n2016-12-26,75\n2016-12-27,111\n2016-12-28,117\n2016-12-29,129\n2016-12-30,75\n2016-12-31,23\n2017-01-01,59\n2017-01-02,113\n2017-01-03,135\n2017-01-04,186\n2017-01-05,137\n2017-01-06,141\n2017-01-07,80\n2017-01-08,85\n2017-01-09,111\n2017-01-10,183\n2017-01-11,188\n2017-01-12,157\n2017-01-13,159\n2017-01-14,58\n2017-01-15,124\n2017-01-16,116\n2017-01-17,156\n2017-01-18,146\n2017-01-19,98\n2017-01-20,103\n2017-01-21,83\n2017-01-22,133\n2017-01-23,166\n2017-01-24,133\n2017-01-25,183\n2017-01-26,135\n2017-01-27,153\n2017-01-28,103\n2017-01-29,65\n2017-01-30,154\n2017-01-31,137\n2017-02-01,125\n2017-02-02,143\n2017-02-03,102\n2017-02-04,73\n2017-02-05,100\n2017-02-06,131\n2017-02-07,134\n2017-02-08,128\n2017-02-09,122\n2017-02-10,114\n2017-02-11,65\n2017-02-12,116\n2017-02-13,110\n2017-02-14,151\n2017-02-15,109\n2017-02-16,84\n2017-02-17,96\n2017-02-18,86\n2017-02-19,72\n2017-02-20,109\n2017-02-21,153\n2017-02-22,166\n2017-02-23,109\n2017-02-24,117\n2017-02-25,58\n2017-02-26,77\n2017-02-27,102\n2017-02-28,125\n2017-03-01,135\n2017-03-02,144\n2017-03-03,139\n2017-03-04,85\n2017-03-05,71\n2017-03-06,149\n2017-03-07,132\n2017-03-08,149\n2017-03-09,152\n2017-03-10,194\n2017-03-11,118\n2017-03-12,63\n2017-03-13,102\n2017-03-14,204\n2017-03-15,166\n2017-03-16,131\n2017-03-17,147\n2017-03-18,83\n2017-03-19,96\n2017-03-20,111\n2017-03-21,201\n2017-03-22,140\n2017-03-23,163\n2017-03-24,157\n2017-03-25,102\n2017-03-26,79\n2017-03-27,146\n2017-03-28,157\n2017-03-29,130\n2017-03-30,121\n2017-03-31,105\n2017-04-01,35\n2017-04-02,109\n2017-04-03,149\n2017-04-04,129\n2017-04-05,201\n2017-04-06,169\n2017-04-07,195\n2017-04-08,63\n2017-04-09,66\n2017-04-10,152\n2017-04-11,168\n2017-04-12,235\n2017-04-13,189\n2017-04-14,148\n2017-04-15,93\n2017-04-16,69\n2017-04-17,128\n2017-04-18,196\n2017-04-19,198\n2017-04-20,133\n2017-04-21,131\n2017-04-22,81\n2017-04-23,66\n2017-04-24,148\n2017-04-25,171\n2017-04-26,176\n2017-04-27,169\n2017-04-28,181\n2017-04-29,84\n2017-04-30,81\n2017-05-01,161\n2017-05-02,182\n2017-05-03,193\n2017-05-04,170\n2017-05-05,122\n2017-05-06,80\n2017-05-07,127\n2017-05-08,180\n2017-05-09,152\n2017-05-10,225\n2017-05-11,111\n2017-05-12,173\n2017-05-13,76\n2017-05-14,52\n2017-05-15,134\n2017-05-16,140\n2017-05-17,161\n2017-05-18,175\n2017-05-19,199\n2017-05-20,102\n2017-05-21,145\n2017-05-22,170\n2017-05-23,158\n2017-05-24,141\n2017-05-25,132\n2017-05-26,181\n2017-05-27,83\n2017-05-28,78\n2017-05-29,122\n2017-05-30,188\n2017-05-31,152\n2017-06-01,189\n2017-06-02,201\n2017-06-03,91\n2017-06-04,113\n2017-06-05,164\n2017-06-06,125\n2017-06-07,175\n2017-06-08,184\n2017-06-09,154\n2017-06-10,86\n2017-06-11,37\n2017-06-12,179\n2017-06-13,196\n2017-06-14,169\n2017-06-15,178\n2017-06-16,149\n2017-06-17,89\n2017-06-18,85\n2017-06-19,142\n2017-06-20,157\n2017-06-21,143\n2017-06-22,152\n2017-06-23,185\n2017-06-24,77\n2017-06-25,77\n2017-06-26,140\n2017-06-27,239\n2017-06-28,181\n2017-06-29,154\n2017-06-30,162\n2017-07-01,99\n2017-07-02,108\n2017-07-03,129\n2017-07-04,162\n2017-07-05,180\n2017-07-06,174\n2017-07-07,153\n2017-07-08,67\n2017-07-09,76\n2017-07-10,184\n2017-07-11,200\n2017-07-12,204\n2017-07-13,181\n2017-07-14,157\n2017-07-15,115\n2017-07-16,152\n2017-07-17,117\n2017-07-18,168\n2017-07-19,162\n2017-07-20,150\n2017-07-21,142\n2017-07-22,86\n2017-07-23,94\n2017-07-24,113\n2017-07-25,152\n2017-07-26,97\n2017-07-27,139\n2017-07-28,108\n2017-07-29,55\n2017-07-30,60\n2017-07-31,132\n2017-08-01,175\n2017-08-02,107\n2017-08-03,118\n2017-08-04,123\n2017-08-05,88\n2017-08-06,36\n2017-08-07,131\n2017-08-08,119\n2017-08-09,116\n2017-08-10,71\n2017-08-11,116\n2017-08-12,40\n2017-08-13,94\n2017-08-14,149\n2017-08-15,146\n2017-08-16,167\n2017-08-17,160\n2017-08-18,120\n2017-08-19,31\n2017-08-20,43\n2017-08-21,84\n2017-08-22,114\n2017-08-23,144\n2017-08-24,114\n2017-08-25,118\n2017-08-26,48\n2017-08-27,85\n2017-08-28,94\n2017-08-29,119\n2017-08-30,135\n2017-08-31,127\n2017-09-01,116\n2017-09-02,84\n2017-09-03,70\n2017-09-04,113\n2017-09-05,123\n2017-09-06,99\n2017-09-07,95\n2017-09-08,125\n2017-09-09,59\n2017-09-10,56\n2017-09-11,148\n2017-09-12,127\n2017-09-13,123\n2017-09-14,120\n2017-09-15,129\n2017-09-16,40\n2017-09-17,59\n2017-09-18,115\n2017-09-19,137\n2017-09-20,98\n2017-09-21,96\n2017-09-22,82\n2017-09-23,88\n2017-09-24,86\n2017-09-25,144\n2017-09-26,169\n2017-09-27,150\n2017-09-28,151\n2017-09-29,136\n2017-09-30,95\n2017-10-01,94\n2017-10-02,138\n2017-10-03,165\n2017-10-04,114\n2017-10-05,95\n2017-10-06,113\n2017-10-07,80\n2017-10-08,95\n2017-10-09,122\n2017-10-10,175\n2017-10-11,127\n2017-10-12,179\n2017-10-13,197\n2017-10-14,84\n2017-10-15,60\n2017-10-16,128\n2017-10-17,138\n2017-10-18,154\n2017-10-19,163\n2017-10-20,118\n2017-10-21,82\n2017-10-22,49\n2017-10-23,96\n2017-10-24,142\n2017-10-25,160\n2017-10-26,140\n2017-10-27,126\n2017-10-28,81\n2017-10-29,99\n2017-10-30,107\n2017-10-31,157\n2017-11-01,157\n2017-11-02,151\n2017-11-03,136\n2017-11-04,76\n2017-11-05,63\n2017-11-06,155\n2017-11-07,124\n2017-11-08,153\n2017-11-09,119\n2017-11-10,90\n2017-11-11,57\n2017-11-12,86\n2017-11-13,129\n2017-11-14,142\n2017-11-15,137\n2017-11-16,147\n2017-11-17,175\n2017-11-18,101\n2017-11-19,95\n2017-11-20,140\n2017-11-21,127\n2017-11-22,152\n2017-11-23,98\n2017-11-24,90\n2017-11-25,59\n2017-11-26,86\n2017-11-27,95\n2017-11-28,114\n2017-11-29,140\n2017-11-30,131\n2017-12-01,129\n2017-12-02,98\n2017-12-03,85\n2017-12-04,150\n2017-12-05,174\n2017-12-06,168\n2017-12-07,96\n2017-12-08,71\n2017-12-09,96\n2017-12-10,106\n2017-12-11,133\n2017-12-12,144\n2017-12-13,96\n2017-12-14,102\n2017-12-15,133\n2017-12-16,69\n2017-12-17,80\n2017-12-18,83\n2017-12-19,107\n2017-12-20,137\n2017-12-21,132\n2017-12-22,108\n2017-12-23,34\n2017-12-24,37\n2017-12-25,35\n2017-12-26,65\n2017-12-27,129\n2017-12-28,126\n2017-12-29,86\n2017-12-30,99\n2017-12-31,60\n2018-01-01,44\n2018-01-02,79\n2018-01-03,93\n2018-01-04,131\n2018-01-05,125\n2018-01-06,63\n2018-01-07,58\n2018-01-08,180\n2018-01-09,139\n2018-01-10,155\n2018-01-11,128\n2018-01-12,92\n2018-01-13,116\n2018-01-14,92\n2018-01-15,116\n2018-01-16,106\n2018-01-17,145\n2018-01-18,152\n2018-01-19,110\n2018-01-20,100\n2018-01-21,67\n2018-01-22,154\n2018-01-23,122\n2018-01-24,215\n2018-01-25,153\n2018-01-26,127\n2018-01-27,81\n2018-01-28,79\n2018-01-29,146\n2018-01-30,159\n2018-01-31,128\n2018-02-01,97\n2018-02-02,124\n2018-02-03,51\n2018-02-04,82\n2018-02-05,163\n2018-02-06,183\n2018-02-07,107\n2018-02-08,151\n2018-02-09,174\n2018-02-10,147\n2018-02-11,131\n2018-02-12,135\n2018-02-13,170\n2018-02-14,151\n2018-02-15,180\n2018-02-16,128\n2018-02-17,125\n2018-02-18,119\n2018-02-19,128\n2018-02-20,148\n2018-02-21,115\n2018-02-22,136\n2018-02-23,173\n2018-02-24,103\n2018-02-25,115\n2018-02-26,168\n2018-02-27,174\n2018-02-28,180\n2018-03-01,126\n2018-03-02,168\n2018-03-03,112\n2018-03-04,76\n2018-03-05,164\n2018-03-06,123\n2018-03-07,143\n2018-03-08,138\n2018-03-09,161\n2018-03-10,111\n2018-03-11,47\n2018-03-12,175\n2018-03-13,146\n2018-03-14,175\n2018-03-15,141\n2018-03-16,135\n2018-03-17,116\n2018-03-18,113\n2018-03-19,199\n2018-03-20,199\n2018-03-21,207\n2018-03-22,147\n2018-03-23,145\n2018-03-24,161\n2018-03-25,131\n2018-03-26,170\n2018-03-27,160\n2018-03-28,192\n2018-03-29,142\n2018-03-30,152\n2018-03-31,151\n2018-04-01,79\n2018-04-02,150\n2018-04-03,229\n2018-04-04,209\n2018-04-05,157\n2018-04-06,221\n2018-04-07,119\n2018-04-08,162\n2018-04-09,133\n2018-04-10,196\n2018-04-11,172\n2018-04-12,206\n2018-04-13,203\n2018-04-14,89\n2018-04-15,98\n2018-04-16,176\n2018-04-17,166\n2018-04-18,155\n2018-04-19,140\n2018-04-20,166\n2018-04-21,69\n2018-04-22,91\n2018-04-23,156\n2018-04-24,199\n2018-04-25,144\n2018-04-26,148\n2018-04-27,147\n2018-04-28,145\n2018-04-29,161\n2018-04-30,176\n2018-05-01,197\n2018-05-02,175\n2018-05-03,162\n2018-05-04,159\n2018-05-05,68\n2018-05-06,100\n2018-05-07,184\n2018-05-08,227\n2018-05-09,129\n2018-05-10,150\n2018-05-11,195\n2018-05-12,115\n2018-05-13,77\n2018-05-14,178\n2018-05-15,194\n2018-05-16,178\n2018-05-17,198\n2018-05-18,150\n2018-05-19,70\n2018-05-20,68\n2018-05-21,140\n2018-05-22,175\n2018-05-23,186\n2018-05-24,152\n2018-05-25,116\n2018-05-26,38\n2018-05-27,136\n2018-05-28,169\n2018-05-29,149\n2018-05-30,170\n2018-05-31,229\n2018-06-01,228\n2018-06-02,50\n2018-06-03,58\n2018-06-04,167\n2018-06-05,150\n2018-06-06,200\n2018-06-07,232\n2018-06-08,186\n2018-06-09,113\n2018-06-10,88\n2018-06-11,160\n2018-06-12,216\n2018-06-13,180\n2018-06-14,176\n2018-06-15,178\n2018-06-16,93\n2018-06-17,51\n2018-06-18,112\n2018-06-19,117\n2018-06-20,135\n2018-06-21,126\n2018-06-22,94\n2018-06-23,73\n2018-06-24,81\n2018-06-25,137\n2018-06-26,208\n2018-06-27,127\n2018-06-28,152\n2018-06-29,134\n2018-06-30,98\n2018-07-01,128\n2018-07-02,144\n2018-07-03,127\n2018-07-04,70\n2018-07-05,117\n2018-07-06,115\n2018-07-07,55\n2018-07-08,57\n2018-07-09,104\n2018-07-10,133\n2018-07-11,238\n2018-07-12,135\n2018-07-13,244\n2018-07-14,74\n2018-07-15,86\n2018-07-16,178\n2018-07-17,195\n2018-07-18,201\n2018-07-19,149\n2018-07-20,122\n2018-07-21,89\n2018-07-22,81\n2018-07-23,169\n2018-07-24,170\n2018-07-25,134\n2018-07-26,136\n2018-07-27,135\n2018-07-28,79\n2018-07-29,79\n2018-07-30,144\n2018-07-31,120\n2018-08-01,150\n2018-08-02,108\n2018-08-03,147\n2018-08-04,65\n2018-08-05,66\n2018-08-06,139\n2018-08-07,142\n2018-08-08,117\n2018-08-09,79\n2018-08-10,84\n2018-08-11,103\n2018-08-12,79\n2018-08-13,99\n2018-08-14,126\n2018-08-15,106\n2018-08-16,143\n2018-08-17,114\n2018-08-18,68\n2018-08-19,34\n2018-08-20,83\n2018-08-21,75\n2018-08-22,108\n2018-08-23,84\n2018-08-24,85\n2018-08-25,66\n2018-08-26,50\n2018-08-27,77\n2018-08-28,114\n2018-08-29,116\n2018-08-30,112\n2018-08-31,114\n2018-09-01,99\n2018-09-02,92\n2018-09-03,87\n2018-09-04,122\n2018-09-05,125\n2018-09-06,104\n2018-09-07,139\n2018-09-08,83\n2018-09-09,57\n2018-09-10,110\n2018-09-11,119\n2018-09-12,119\n2018-09-13,141\n2018-09-14,147\n2018-09-15,67\n2018-09-16,96\n2018-09-17,104\n2018-09-18,140\n2018-09-19,159\n2018-09-20,125\n2018-09-21,141\n2018-09-22,61\n2018-09-23,84\n2018-09-24,139\n2018-09-25,107\n2018-09-26,159\n2018-09-27,140\n2018-09-28,144\n2018-09-29,92\n2018-09-30,95\n2018-10-01,157\n2018-10-02,173\n2018-10-03,186\n2018-10-04,155\n2018-10-05,137\n2018-10-06,65\n2018-10-07,35\n2018-10-08,135\n2018-10-09,172\n2018-10-10,130\n2018-10-11,119\n2018-10-12,140\n2018-10-13,98\n2018-10-14,66\n2018-10-15,134\n2018-10-16,183\n2018-10-17,152\n2018-10-18,150\n2018-10-19,146\n2018-10-20,125\n2018-10-21,146\n2018-10-22,134\n2018-10-23,152\n2018-10-24,143\n2018-10-25,116\n2018-10-26,133\n2018-10-27,136\n2018-10-28,119\n2018-10-29,149\n2018-10-30,250\n2018-10-31,174\n2018-11-01,251\n2018-11-02,168\n2018-11-03,86\n2018-11-04,287\n2018-11-05,157\n2018-11-06,161\n2018-11-07,157\n2018-11-08,158\n2018-11-09,205\n2018-11-10,168\n2018-11-11,235\n2018-11-12,95\n2018-11-13,179\n2018-11-14,205\n2018-11-15,171\n2018-11-16,171\n2018-11-17,86\n2018-11-18,67\n2018-11-19,160\n2018-11-20,210\n2018-11-21,177\n2018-11-22,80\n2018-11-23,121\n2018-11-24,92\n2018-11-25,117\n2018-11-26,131\n2018-11-27,143\n2018-11-28,169\n2018-11-29,177\n2018-11-30,188\n2018-12-01,153\n2018-12-02,128\n2018-12-03,225\n2018-12-04,137\n2018-12-05,219\n2018-12-06,163\n2018-12-07,169\n2018-12-08,59\n2018-12-09,67\n2018-12-10,142\n2018-12-11,130\n2018-12-12,214\n2018-12-13,115\n2018-12-14,110\n2018-12-15,95\n2018-12-16,91\n2018-12-17,166\n2018-12-18,164\n2018-12-19,129\n2018-12-20,132\n2018-12-21,82\n2018-12-22,75\n2018-12-23,49\n2018-12-24,47\n2018-12-25,25\n2018-12-26,50\n2018-12-27,103\n2018-12-28,123\n2018-12-29,60\n2018-12-30,92\n2018-12-31,91\n2019-01-01,73\n2019-01-02,133\n2019-01-03,107\n2019-01-04,141\n2019-01-05,74\n2019-01-06,93\n2019-01-07,113\n2019-01-08,137\n2019-01-09,178\n2019-01-10,185\n2019-01-11,133\n2019-01-12,102\n2019-01-13,83\n2019-01-14,155\n2019-01-15,149\n2019-01-16,139\n2019-01-17,175\n2019-01-18,165\n2019-01-19,158\n2019-01-20,101\n2019-01-21,181\n2019-01-22,186\n2019-01-23,164\n2019-01-24,173\n2019-01-25,112\n2019-01-26,61\n2019-01-27,83\n2019-01-28,103\n2019-01-29,106\n2019-01-30,117\n2019-01-31,93\n2019-02-01,156\n2019-02-02,101\n2019-02-03,101\n2019-02-04,138\n2019-02-05,129\n2019-02-06,158\n2019-02-07,123\n2019-02-08,175\n2019-02-09,115\n2019-02-10,122\n2019-02-11,150\n2019-02-12,151\n2019-02-13,157\n2019-02-14,150\n2019-02-15,164\n2019-02-16,178\n2019-02-17,100\n2019-02-18,161\n2019-02-19,226\n2019-02-20,197\n2019-02-21,217\n2019-02-22,154\n2019-02-23,91\n2019-02-24,102\n2019-02-25,241\n2019-02-26,164\n2019-02-27,191\n2019-02-28,164\n2019-03-01,117\n2019-03-02,43\n2019-03-03,150\n2019-03-04,129\n2019-03-05,128\n2019-03-06,113\n2019-03-07,109\n2019-03-08,101\n2019-03-09,109\n2019-03-10,85\n2019-03-11,133\n2019-03-12,110\n2019-03-13,104\n2019-03-14,104\n2019-03-15,116\n2019-03-16,66\n2019-03-17,66\n2019-03-18,105\n2019-03-19,119\n2019-03-20,137\n2019-03-21,172\n2019-03-22,118\n2019-03-23,73\n2019-03-24,50\n2019-03-25,141\n2019-03-26,159\n2019-03-27,107\n2019-03-28,100\n2019-03-29,134\n2019-03-30,92\n2019-03-31,70\n2019-04-01,139\n2019-04-02,114\n2019-04-03,113\n2019-04-04,97\n2019-04-05,125\n2019-04-06,37\n2019-04-07,51\n2019-04-08,154\n2019-04-09,118\n2019-04-10,169\n2019-04-11,109\n2019-04-12,107\n2019-04-13,42\n2019-04-14,58\n2019-04-15,108\n2019-04-16,135\n2019-04-17,73\n2019-04-18,114\n2019-04-19,112\n2019-04-20,92\n2019-04-21,70\n2019-04-22,104\n2019-04-23,84\n2019-04-24,100\n2019-04-25,115\n2019-04-26,92\n2019-04-27,44\n2019-04-28,106\n2019-04-29,126\n2019-04-30,78\n2019-05-01,116\n2019-05-02,108\n2019-05-03,78\n2019-05-04,50\n2019-05-05,85\n2019-05-06,115\n2019-05-07,120\n2019-05-08,124\n2019-05-09,108\n2019-05-10,80\n2019-05-11,86\n2019-05-12,69\n2019-05-13,102\n2019-05-14,100\n2019-05-15,80\n2019-05-16,99\n2019-05-17,89\n2019-05-18,51\n2019-05-19,64\n2019-05-20,111\n2019-05-21,97\n2019-05-22,103\n2019-05-23,141\n2019-05-24,68\n2019-05-25,75\n2019-05-26,75\n2019-05-27,58\n2019-05-28,79\n2019-05-29,87\n2019-05-30,125\n2019-05-31,120\n2019-06-01,69\n2019-06-02,74\n2019-06-03,112\n2019-06-04,88\n2019-06-05,138\n2019-06-06,95\n2019-06-07,100\n2019-06-08,95\n2019-06-09,88\n2019-06-10,97\n2019-06-11,105\n2019-06-12,104\n2019-06-13,88\n2019-06-14,89\n2019-06-15,47\n2019-06-16,41\n2019-06-17,78\n2019-06-18,68\n2019-06-19,115\n2019-06-20,86\n2019-06-21,105\n2019-06-22,43\n2019-06-23,79\n2019-06-24,92\n2019-06-25,77\n2019-06-26,97\n2019-06-27,96\n2019-06-28,92\n2019-06-29,92\n2019-06-30,57\n2019-07-01,94\n2019-07-02,164\n2019-07-03,101\n2019-07-04,89\n2019-07-05,67\n2019-07-06,59\n2019-07-07,37\n2019-07-08,146\n2019-07-09,89\n2019-07-10,136\n2019-07-11,109\n2019-07-12,102\n2019-07-13,78\n2019-07-14,65\n2019-07-15,122\n2019-07-16,142\n2019-07-17,113\n2019-07-18,103\n2019-07-19,102\n2019-07-20,92\n2019-07-21,41\n2019-07-22,97\n2019-07-23,82\n2019-07-24,124\n2019-07-25,129\n2019-07-26,115\n2019-07-27,70\n2019-07-28,67\n2019-07-29,98\n2019-07-30,106\n2019-07-31,76\n2019-08-01,140\n2019-08-02,77\n2019-08-03,86\n2019-08-04,52\n2019-08-05,159\n2019-08-06,132\n2019-08-07,142\n2019-08-08,154\n2019-08-09,146\n2019-08-10,87\n2019-08-11,124\n2019-08-12,175\n2019-08-13,204\n2019-08-14,204\n2019-08-15,150\n2019-08-16,149\n2019-08-17,114\n2019-08-18,116\n2019-08-19,131\n2019-08-20,135\n2019-08-21,162\n2019-08-22,159\n2019-08-23,193\n2019-08-24,115\n2019-08-25,59\n2019-08-26,106\n2019-08-27,123\n2019-08-28,172\n2019-08-29,120\n2019-08-30,86\n2019-08-31,75\n2019-09-01,87\n2019-09-02,126\n2019-09-03,125\n2019-09-04,144\n2019-09-05,145\n2019-09-06,109\n2019-09-07,105\n2019-09-08,111\n2019-09-09,131\n2019-09-10,144\n2019-09-11,148\n2019-09-12,104\n2019-09-13,161\n2019-09-14,83\n2019-09-15,75\n2019-09-16,109\n2019-09-17,131\n2019-09-18,112\n2019-09-19,115\n2019-09-20,167\n2019-09-21,156\n2019-09-22,94\n2019-09-23,107\n2019-09-24,147\n2019-09-25,138\n2019-09-26,144\n2019-09-27,119\n2019-09-28,29\n2019-09-29,50\n2019-09-30,132\n2019-10-01,142\n2019-10-02,138\n2019-10-03,129\n2019-10-04,110\n2019-10-05,74\n2019-10-06,70\n2019-10-07,118\n2019-10-08,114\n2019-10-09,123\n2019-10-10,137\n2019-10-11,151\n2019-10-12,70\n2019-10-13,103\n2019-10-14,110\n2019-10-15,170\n2019-10-16,130\n2019-10-17,122\n2019-10-18,122\n2019-10-19,85\n2019-10-20,51\n2019-10-21,126\n2019-10-22,94\n2019-10-23,99\n2019-10-24,154\n2019-10-25,119\n2019-10-26,105\n2019-10-27,92\n2019-10-28,130\n2019-10-29,146\n2019-10-30,164\n2019-10-31,184\n2019-11-01,187\n2019-11-02,102\n2019-11-03,110\n2019-11-04,121\n2019-11-05,161\n2019-11-06,123\n2019-11-07,119\n2019-11-08,131\n2019-11-09,71\n2019-11-10,85\n2019-11-11,113\n2019-11-12,94\n2019-11-13,124\n2019-11-14,100\n2019-11-15,135\n2019-11-16,97\n2019-11-17,110\n2019-11-18,111\n2019-11-19,123\n2019-11-20,127\n2019-11-21,115\n2019-11-22,92\n2019-11-23,61\n2019-11-24,90\n2019-11-25,114\n2019-11-26,106\n2019-11-27,144\n2019-11-28,114\n2019-11-29,115\n2019-11-30,116\n2019-12-01,103\n2019-12-02,141\n2019-12-03,116\n2019-12-04,122\n2019-12-05,157\n2019-12-06,158\n2019-12-07,95\n2019-12-08,110\n2019-12-09,113\n2019-12-10,149\n2019-12-11,142\n2019-12-12,187\n2019-12-13,145\n2019-12-14,113\n2019-12-15,89\n2019-12-16,125\n2019-12-17,201\n2019-12-18,176\n2019-12-19,206\n2019-12-20,180\n2019-12-21,90\n2019-12-22,79\n2019-12-23,49\n2019-12-24,110\n2019-12-25,76\n2019-12-26,78\n2019-12-27,124\n2019-12-28,117\n2019-12-29,60\n2019-12-30,156\n2019-12-31,126\n2020-01-01,99\n2020-01-02,142\n2020-01-03,95\n2020-01-04,120\n2020-01-05,81\n2020-01-06,125\n2020-01-07,161\n2020-01-08,169\n2020-01-09,192\n2020-01-10,251\n2020-01-11,164\n2020-01-12,219\n2020-01-13,224\n2020-01-14,193\n2020-01-15,248\n2020-01-16,255\n2020-01-17,247\n2020-01-18,117\n2020-01-19,187\n2020-01-20,138\n2020-01-21,139\n2020-01-22,199\n2020-01-23,185\n2020-01-24,143\n2020-01-25,64\n2020-01-26,89\n2020-01-27,135\n2020-01-28,101\n2020-01-29,114\n2020-01-30,155\n2020-01-31,165\n2020-02-01,89\n2020-02-02,111\n2020-02-03,141\n2020-02-04,120\n2020-02-05,145\n2020-02-06,133\n2020-02-07,149\n2020-02-08,137\n2020-02-09,119\n2020-02-10,152\n2020-02-11,162\n2020-02-12,134\n2020-02-13,170\n2020-02-14,149\n2020-02-15,95\n2020-02-16,66\n2020-02-17,129\n2020-02-18,175\n2020-02-19,133\n2020-02-20,128\n2020-02-21,133\n2020-02-22,99\n2020-02-23,165\n2020-02-24,153\n2020-02-25,146\n2020-02-26,155\n2020-02-27,144\n2020-02-28,115\n2020-02-29,54\n2020-03-01,56\n2020-03-02,166\n2020-03-03,142\n2020-03-04,120\n2020-03-05,148\n2020-03-06,119\n2020-03-07,92\n2020-03-08,143\n2020-03-09,112\n2020-03-10,111\n2020-03-11,110\n2020-03-12,82\n2020-03-13,76\n2020-03-14,74\n2020-03-15,80\n2020-03-16,91\n2020-03-17,106\n2020-03-18,132\n2020-03-19,92\n2020-03-20,115\n2020-03-21,89\n2020-03-22,105\n2020-03-23,138\n2020-03-24,144\n2020-03-25,116\n2020-03-26,99\n2020-03-27,112\n2020-03-28,123\n2020-03-29,76\n2020-03-30,107\n2020-03-31,177\n2020-04-01,158\n2020-04-02,160\n2020-04-03,145\n2020-04-04,130\n2020-04-05,95\n2020-04-06,152\n2020-04-07,157\n2020-04-08,217\n2020-04-09,160\n2020-04-10,151\n2020-04-11,127\n2020-04-12,106\n2020-04-13,208\n2020-04-14,175\n2020-04-15,146\n2020-04-16,149\n2020-04-17,110\n2020-04-18,148\n2020-04-19,151\n2020-04-20,155\n2020-04-21,141\n2020-04-22,147\n2020-04-23,146\n2020-04-24,136\n2020-04-25,98\n2020-04-26,139\n2020-04-27,180\n2020-04-28,118\n2020-04-29,166\n2020-04-30,220\n2020-05-01,237\n2020-05-02,133\n2020-05-03,142\n2020-05-04,132\n2020-05-05,218\n2020-05-06,229\n2020-05-07,184\n2020-05-08,160\n2020-05-09,152\n2020-05-10,160\n2020-05-11,187\n2020-05-12,158\n2020-05-13,200\n2020-05-14,212\n2020-05-15,199\n2020-05-16,113\n2020-05-17,142\n2020-05-18,161\n2020-05-19,162\n2020-05-20,186\n2020-05-21,122\n2020-05-22,142\n2020-05-23,128\n2020-05-24,134\n2020-05-25,143\n2020-05-26,220\n2020-05-27,144\n2020-05-28,100\n2020-05-29,108\n2020-05-30,213\n2020-05-31,86\n2020-06-01,115\n2020-06-02,107\n2020-06-03,169\n2020-06-04,147\n2020-06-05,115\n2020-06-06,107\n2020-06-07,93\n2020-06-08,116\n2020-06-09,143\n2020-06-10,84\n2020-06-11,177\n2020-06-12,125\n2020-06-13,61\n2020-06-14,98\n2020-06-15,191\n2020-06-16,157\n2020-06-17,199\n2020-06-18,192\n2020-06-19,146\n2020-06-20,60\n2020-06-21,116\n2020-06-22,128\n2020-06-23,130\n2020-06-24,160\n2020-06-25,120\n2020-06-26,167\n2020-06-27,164\n2020-06-28,113\n2020-06-29,167\n2020-06-30,155\n2020-07-01,126\n2020-07-02,134\n2020-07-03,146\n2020-07-04,59\n2020-07-05,102\n2020-07-06,120\n2020-07-07,124\n2020-07-08,154\n2020-07-09,164\n2020-07-10,171\n2020-07-11,79\n2020-07-12,63\n2020-07-13,85\n2020-07-14,90\n2020-07-15,129\n2020-07-16,138\n2020-07-17,95\n2020-07-18,71\n2020-07-19,99\n2020-07-20,140\n2020-07-21,189\n2020-07-22,212\n2020-07-23,176\n2020-07-24,183\n2020-07-25,55\n2020-07-26,100\n2020-07-27,137\n2020-07-28,190\n2020-07-29,118\n2020-07-30,147\n2020-07-31,139\n2020-08-01,91\n2020-08-02,99\n2020-08-03,168\n2020-08-04,168\n2020-08-05,151\n2020-08-06,167\n2020-08-07,155\n2020-08-08,78\n2020-08-09,111\n2020-08-10,126\n2020-08-11,111\n2020-08-12,121\n2020-08-13,97\n2020-08-14,137\n2020-08-15,54\n2020-08-16,56\n2020-08-17,162\n2020-08-18,98\n2020-08-19,139\n2020-08-20,128\n2020-08-21,133\n2020-08-22,93\n2020-08-23,68\n2020-08-24,149\n2020-08-25,165\n2020-08-26,201\n2020-08-27,135\n2020-08-28,108\n2020-08-29,84\n2020-08-30,42\n2020-08-31,100\n2020-09-01,134\n2020-09-02,120\n2020-09-03,100\n2020-09-04,110\n2020-09-05,53\n2020-09-06,62\n2020-09-07,129\n2020-09-08,153\n2020-09-09,148\n2020-09-10,141\n2020-09-11,162\n2020-09-12,78\n2020-09-13,58\n2020-09-14,133\n2020-09-15,126\n2020-09-16,134\n2020-09-17,94\n2020-09-18,102\n2020-09-19,65\n2020-09-20,86\n2020-09-21,136\n2020-09-22,144\n2020-09-23,137\n2020-09-24,146\n2020-09-25,148\n2020-09-26,78\n2020-09-27,82\n2020-09-28,158\n2020-09-29,122\n2020-09-30,108\n2020-10-01,146\n2020-10-02,125\n2020-10-03,55\n2020-10-04,62\n2020-10-05,99\n2020-10-06,95\n2020-10-07,137\n2020-10-08,125\n2020-10-09,117\n2020-10-10,67\n2020-10-11,62\n2020-10-12,133\n2020-10-13,80\n2020-10-14,115\n2020-10-15,104\n2020-10-16,122\n2020-10-17,106\n2020-10-18,86\n2020-10-19,156\n2020-10-20,156\n2020-10-21,162\n2020-10-22,180\n2020-10-23,93\n2020-10-24,81\n2020-10-25,75\n2020-10-26,125\n2020-10-27,130\n2020-10-28,147\n2020-10-29,118\n2020-10-30,99\n2020-10-31,93\n2020-11-01,103\n2020-11-02,103\n2020-11-03,121\n2020-11-04,86\n2020-11-05,153\n2020-11-06,129\n2020-11-07,116\n2020-11-08,51\n2020-11-09,129\n2020-11-10,150\n2020-11-11,112\n2020-11-12,117\n2020-11-13,161\n2020-11-14,69\n2020-11-15,95\n2020-11-16,144\n2020-11-17,155\n2020-11-18,142\n2020-11-19,119\n2020-11-20,113\n2020-11-21,77\n2020-11-22,69\n2020-11-23,97\n2020-11-24,107\n2020-11-25,122\n2020-11-26,131\n2020-11-27,120\n2020-11-28,93\n2020-11-29,116\n2020-11-30,139\n2020-12-01,89\n2020-12-02,152\n2020-12-03,130\n2020-12-04,128\n2020-12-05,112\n2020-12-06,69\n2020-12-07,153\n2020-12-08,110\n2020-12-09,122\n2020-12-10,124\n2020-12-11,107\n2020-12-12,78\n2020-12-13,90\n2020-12-14,87\n2020-12-15,125\n2020-12-16,143\n2020-12-17,114\n2020-12-18,96\n2020-12-19,55\n2020-12-20,66\n2020-12-21,150\n2020-12-22,129\n2020-12-23,134\n2020-12-24,70\n2020-12-25,38\n2020-12-26,68\n2020-12-27,93\n2020-12-28,116\n2020-12-29,151\n2020-12-30,114\n2020-12-31,53\n2021-01-01,67\n2021-01-02,70\n2021-01-03,60\n2021-01-04,113\n2021-01-05,108\n2021-01-06,106\n2021-01-07,133\n2021-01-08,133\n2021-01-09,99\n2021-01-10,114\n2021-01-11,115\n2021-01-12,119\n2021-01-13,167\n2021-01-14,178\n2021-01-15,184\n2021-01-16,116\n2021-01-17,130\n2021-01-18,115\n2021-01-19,155\n2021-01-20,204\n2021-01-21,137\n2021-01-22,141\n2021-01-23,130\n2021-01-24,67\n2021-01-25,132\n2021-01-26,180\n2021-01-27,161\n2021-01-28,162\n2021-01-29,207\n2021-01-30,95\n2021-01-31,149\n2021-02-01,176\n2021-02-02,157\n2021-02-03,191\n2021-02-04,156\n2021-02-05,214\n2021-02-06,159\n2021-02-07,94\n2021-02-08,121\n2021-02-09,134\n2021-02-10,126\n2021-02-11,138\n2021-02-12,115\n2021-02-13,121\n2021-02-14,115\n2021-02-15,148\n2021-02-16,127\n2021-02-17,149\n2021-02-18,153\n2021-02-19,130\n2021-02-20,120\n2021-02-21,98\n2021-02-22,160\n2021-02-23,150\n2021-02-24,185\n2021-02-25,171\n2021-02-26,162\n2021-02-27,130\n2021-02-28,189\n2021-03-01,218\n2021-03-02,138\n2021-03-03,172\n2021-03-04,202\n2021-03-05,152\n2021-03-06,128\n2021-03-07,115\n2021-03-08,195\n2021-03-09,161\n2021-03-10,190\n2021-03-11,172\n2021-03-12,149\n2021-03-13,141\n2021-03-14,77\n2021-03-15,167\n2021-03-16,161\n2021-03-17,115\n2021-03-18,144\n2021-03-19,145\n2021-03-20,88\n2021-03-21,150\n2021-03-22,110\n2021-03-23,157\n2021-03-24,145\n2021-03-25,116\n2021-03-26,126\n2021-03-27,153\n2021-03-28,111\n2021-03-29,178\n2021-03-30,178\n2021-03-31,170\n2021-04-01,170\n2021-04-02,152\n2021-04-03,100\n2021-04-04,119\n2021-04-05,129\n2021-04-06,200\n2021-04-07,164\n2021-04-08,120\n2021-04-09,178\n2021-04-10,136\n2021-04-11,106\n2021-04-12,155\n2021-04-13,114\n2021-04-14,138\n2021-04-15,175\n2021-04-16,130\n2021-04-17,100\n2021-04-18,80\n2021-04-19,137\n2021-04-20,107\n2021-04-21,174\n2021-04-22,136\n2021-04-23,141\n2021-04-24,94\n2021-04-25,124\n2021-04-26,190\n2021-04-27,96\n2021-04-28,131\n2021-04-29,135\n2021-04-30,166\n2021-05-01,80\n2021-05-02,94\n2021-05-03,71\n2021-05-04,96\n2021-05-05,117\n2021-05-06,162\n2021-05-07,133\n2021-05-08,131\n2021-05-09,94\n2021-05-10,151\n2021-05-11,159\n2021-05-12,156\n2021-05-13,172\n2021-05-14,181\n2021-05-15,75\n2021-05-16,94\n2021-05-17,144\n2021-05-18,117\n2021-05-19,157\n2021-05-20,195\n2021-05-21,160\n2021-05-22,104\n2021-05-23,75\n2021-05-24,141\n2021-05-25,177\n2021-05-26,186\n2021-05-27,141\n2021-05-28,146\n2021-05-29,66\n2021-05-30,83\n2021-05-31,120\n2021-06-01,151\n2021-06-02,132\n2021-06-03,171\n2021-06-04,98\n2021-06-05,63\n2021-06-06,64\n2021-06-07,133\n2021-06-08,117\n2021-06-09,181\n2021-06-10,166\n2021-06-11,100\n2021-06-12,56\n2021-06-13,54\n2021-06-14,89\n2021-06-15,95\n2021-06-16,134\n2021-06-17,149\n2021-06-18,116\n2021-06-19,48\n2021-06-20,60\n2021-06-21,115\n2021-06-22,122\n2021-06-23,136\n2021-06-24,116\n2021-06-25,110\n2021-06-26,68\n2021-06-27,104\n2021-06-28,118\n2021-06-29,110\n2021-06-30,129\n2021-07-01,154\n2021-07-02,91\n2021-07-03,49\n2021-07-04,81\n2021-07-05,139\n2021-07-06,141\n2021-07-07,113\n2021-07-08,96\n2021-07-09,118\n2021-07-10,111\n2021-07-11,104\n2021-07-12,131\n2021-07-13,126\n2021-07-14,174\n2021-07-15,140\n2021-07-16,102\n2021-07-17,68\n2021-07-18,55\n2021-07-19,87\n2021-07-20,145\n2021-07-21,125\n2021-07-22,118\n2021-07-23,107\n2021-07-24,37\n2021-07-25,45\n2021-07-26,80\n2021-07-27,152\n2021-07-28,145\n2021-07-29,148\n2021-07-30,118\n2021-07-31,98\n2021-08-01,81\n2021-08-02,137\n2021-08-03,129\n2021-08-04,129\n2021-08-05,103\n2021-08-06,143\n2021-08-07,112\n2021-08-08,94\n2021-08-09,102\n2021-08-10,106\n2021-08-11,140\n2021-08-12,113\n2021-08-13,113\n2021-08-14,109\n2021-08-15,71\n2021-08-16,124\n2021-08-17,95\n2021-08-18,148\n2021-08-19,124\n2021-08-20,93\n2021-08-21,94\n2021-08-22,80\n2021-08-23,156\n2021-08-24,135\n2021-08-25,170\n2021-08-26,125\n2021-08-27,122\n2021-08-28,89\n2021-08-29,80\n2021-08-30,125\n2021-08-31,160\n2021-09-01,158\n2021-09-02,106\n2021-09-03,125\n2021-09-04,96\n2021-09-05,89\n2021-09-06,128\n2021-09-07,124\n2021-09-08,99\n2021-09-09,145\n2021-09-10,132\n2021-09-11,80\n2021-09-12,82\n2021-09-13,148\n2021-09-14,129\n2021-09-15,146\n2021-09-16,183\n2021-09-17,157\n2021-09-18,103\n2021-09-19,133\n2021-09-20,133\n2021-09-21,146\n2021-09-22,146\n2021-09-23,145\n2021-09-24,84\n2021-09-25,108\n2021-09-26,64\n2021-09-27,122\n2021-09-28,170\n2021-09-29,143\n2021-09-30,142\n2021-10-01,104\n2021-10-02,73\n2021-10-03,123\n2021-10-04,96\n2021-10-05,141\n2021-10-06,190\n2021-10-07,152\n2021-10-08,118\n2021-10-09,158\n2021-10-10,118\n2021-10-11,137\n2021-10-12,139\n2021-10-13,110\n2021-10-14,100\n2021-10-15,114\n2021-10-16,87\n2021-10-17,51\n2021-10-18,152\n2021-10-19,135\n2021-10-20,126\n2021-10-21,156\n2021-10-22,137\n2021-10-23,68\n2021-10-24,63\n2021-10-25,126\n2021-10-26,92\n2021-10-27,130\n2021-10-28,112\n2021-10-29,135\n2021-10-30,70\n2021-10-31,86\n2021-11-01,116\n2021-11-02,129\n2021-11-03,163\n2021-11-04,188\n2021-11-05,145\n2021-11-06,116\n2021-11-07,57\n2021-11-08,143\n2021-11-09,128\n2021-11-10,178\n2021-11-11,140\n2021-11-12,98\n2021-11-13,54\n2021-11-14,63\n2021-11-15,136\n2021-11-16,146\n2021-11-17,175\n2021-11-18,133\n2021-11-19,148\n2021-11-20,38\n2021-11-21,72\n2021-11-22,114\n2021-11-23,135\n2021-11-24,120\n2021-11-25,81\n2021-11-26,96\n2021-11-27,67\n2021-11-28,72\n2021-11-29,128\n2021-11-30,101\n2021-12-01,124\n2021-12-02,100\n2021-12-03,79\n2021-12-04,49\n2021-12-05,64\n2021-12-06,122\n2021-12-07,113\n2021-12-08,104\n2021-12-09,125\n2021-12-10,122\n2021-12-11,38\n2021-12-12,94\n2021-12-13,144\n2021-12-14,107\n2021-12-15,143\n2021-12-16,145\n2021-12-17,102\n2021-12-18,62\n2021-12-19,88\n2021-12-20,120\n2021-12-21,126\n2021-12-22,163\n2021-12-23,107\n2021-12-24,48\n2021-12-25,16\n2021-12-26,29\n2021-12-27,111\n2021-12-28,95\n2021-12-29,133\n2021-12-30,88\n2021-12-31,44\n2022-01-01,33\n2022-01-02,44\n2022-01-03,85\n2022-01-04,147\n2022-01-05,120\n2022-01-06,110\n2022-01-07,127\n2022-01-08,95\n2022-01-09,85\n2022-01-10,150\n2022-01-11,118\n2022-01-12,180\n2022-01-13,153\n2022-01-14,157\n2022-01-15,74\n2022-01-16,86\n2022-01-17,151\n2022-01-18,150\n2022-01-19,182\n2022-01-20,156\n2022-01-21,156\n2022-01-22,92\n2022-01-23,115\n2022-01-24,141\n2022-01-25,125\n2022-01-26,158\n2022-01-27,109\n2022-01-28,130\n2022-01-29,103\n2022-01-30,67\n2022-01-31,152\n2022-02-01,153\n2022-02-02,160\n2022-02-03,104\n2022-02-04,124\n2022-02-05,38\n2022-02-06,70\n2022-02-07,129\n2022-02-08,133\n2022-02-09,152\n2022-02-10,144\n2022-02-11,110\n2022-02-12,48\n2022-02-13,43\n2022-02-14,108\n2022-02-15,138\n2022-02-16,140\n2022-02-17,171\n2022-02-18,108\n2022-02-19,63\n2022-02-20,82\n2022-02-21,165\n2022-02-22,120\n2022-02-23,163\n2022-02-24,168\n2022-02-25,122\n2022-02-26,37\n2022-02-27,42\n2022-02-28,97\n2022-03-01,90\n2022-03-02,122\n2022-03-03,103\n2022-03-04,112\n2022-03-05,92\n2022-03-06,62\n2022-03-07,118\n2022-03-08,96\n2022-03-09,110\n2022-03-10,131\n2022-03-11,101\n2022-03-12,54\n2022-03-13,53\n2022-03-14,133\n2022-03-15,121\n2022-03-16,129\n2022-03-17,123\n2022-03-18,121\n2022-03-19,62\n2022-03-20,49\n2022-03-21,94\n2022-03-22,126\n2022-03-23,152\n2022-03-24,152\n2022-03-25,145\n2022-03-26,133\n2022-03-27,103\n2022-03-28,170\n2022-03-29,125\n2022-03-30,146\n2022-03-31,152\n2022-04-01,123\n2022-04-02,92\n2022-04-03,77\n2022-04-04,174\n2022-04-05,182\n2022-04-06,118\n2022-04-07,114\n2022-04-08,156\n2022-04-09,105\n2022-04-10,93\n2022-04-11,135\n2022-04-12,153\n2022-04-13,118\n2022-04-14,149\n2022-04-15,169\n2022-04-16,70\n2022-04-17,55\n2022-04-18,125\n2022-04-19,126\n2022-04-20,108\n2022-04-21,147\n2022-04-22,173\n2022-04-23,90\n2022-04-24,100\n2022-04-25,101\n2022-04-26,150\n2022-04-27,158\n2022-04-28,134\n2022-04-29,107\n2022-04-30,50\n2022-05-01,62\n2022-05-02,106\n2022-05-03,104\n2022-05-04,133\n2022-05-05,167\n2022-05-06,140\n2022-05-07,44\n2022-05-08,71\n2022-05-09,147\n2022-05-10,119\n2022-05-11,151\n2022-05-12,132\n2022-05-13,112\n2022-05-14,96\n2022-05-15,47\n2022-05-16,149\n2022-05-17,141\n2022-05-18,117\n2022-05-19,158\n2022-05-20,112\n2022-05-21,85\n2022-05-22,83\n2022-05-23,154\n2022-05-24,149\n2022-05-25,113\n2022-05-26,113\n2022-05-27,102\n2022-05-28,99\n2022-05-29,56\n2022-05-30,107\n2022-05-31,106\n2022-06-01,130\n2022-06-02,173\n2022-06-03,134\n2022-06-04,70\n2022-06-05,88\n2022-06-06,110\n2022-06-07,113\n2022-06-08,139\n2022-06-09,142\n2022-06-10,109\n2022-06-11,56\n2022-06-12,76\n2022-06-13,95\n2022-06-14,94\n2022-06-15,127\n2022-06-16,200\n2022-06-17,202\n2022-06-18,49\n2022-06-19,62\n2022-06-20,116\n2022-06-21,112\n2022-06-22,131\n2022-06-23,114\n2022-06-24,110\n2022-06-25,52\n2022-06-26,56\n2022-06-27,76\n2022-06-28,72\n2022-06-29,120\n2022-06-30,118\n2022-07-01,87\n2022-07-02,32\n2022-07-03,39\n2022-07-04,89\n2022-07-05,120\n2022-07-06,106\n2022-07-07,138\n2022-07-08,109\n2022-07-09,42\n2022-07-10,44\n2022-07-11,92\n2022-07-12,135\n2022-07-13,157\n2022-07-14,124\n2022-07-15,177\n2022-07-16,56\n2022-07-17,41\n2022-07-18,143\n2022-07-19,119\n2022-07-20,211\n2022-07-21,128\n2022-07-22,162\n2022-07-23,44\n2022-07-24,99\n2022-07-25,152\n2022-07-26,158\n2022-07-27,133\n2022-07-28,214\n2022-07-29,133\n2022-07-30,79\n2022-07-31,70\n2022-08-01,130\n2022-08-02,123\n2022-08-03,105\n2022-08-04,125\n2022-08-05,127\n2022-08-06,71\n2022-08-07,55\n2022-08-08,108\n2022-08-09,99\n2022-08-10,145\n2022-08-11,115\n2022-08-12,110\n2022-08-13,100\n2022-08-14,95\n2022-08-15,133\n2022-08-16,130\n2022-08-17,131\n2022-08-18,116\n2022-08-19,143\n2022-08-20,82\n2022-08-21,78\n2022-08-22,110\n2022-08-23,130\n2022-08-24,181\n2022-08-25,132\n2022-08-26,105\n2022-08-27,79\n2022-08-28,66\n2022-08-29,173\n2022-08-30,174\n2022-08-31,174\n2022-09-01,137\n2022-09-02,135\n2022-09-03,63\n2022-09-04,81\n2022-09-05,168\n2022-09-06,207\n2022-09-07,194\n2022-09-08,162\n2022-09-09,135\n2022-09-10,54\n2022-09-11,53\n2022-09-12,123\n2022-09-13,120\n2022-09-14,137\n2022-09-15,158\n2022-09-16,110\n2022-09-17,77\n2022-09-18,86\n2022-09-19,165\n2022-09-20,177\n2022-09-21,156\n2022-09-22,113\n2022-09-23,137\n2022-09-24,94\n2022-09-25,44\n2022-09-26,122\n2022-09-27,121\n2022-09-28,159\n2022-09-29,139\n2022-09-30,122\n2022-10-01,81\n2022-10-02,57\n2022-10-03,155\n2022-10-04,127\n2022-10-05,114\n2022-10-06,139\n2022-10-07,88\n2022-10-08,61\n2022-10-09,66\n2022-10-10,130\n2022-10-11,138\n2022-10-12,126\n2022-10-13,128\n2022-10-14,147\n2022-10-15,70\n2022-10-16,65\n2022-10-17,125\n2022-10-18,192\n2022-10-19,107\n2022-10-20,121\n2022-10-21,90\n2022-10-22,66\n2022-10-23,60\n2022-10-24,99\n2022-10-25,84\n2022-10-26,79\n2022-10-27,95\n2022-10-28,79\n2022-10-29,43\n2022-10-30,34\n2022-10-31,133\n2022-11-01,101\n2022-11-02,124\n2022-11-03,105\n2022-11-04,86\n2022-11-05,62\n2022-11-06,67\n2022-11-07,101\n2022-11-08,117\n2022-11-09,109\n2022-11-10,152\n2022-11-11,89\n2022-11-12,43\n2022-11-13,67\n2022-11-14,122\n2022-11-15,115\n2022-11-16,171\n2022-11-17,149\n2022-11-18,123\n2022-11-19,77\n2022-11-20,100\n2022-11-21,133\n2022-11-22,142\n2022-11-23,154\n2022-11-24,114\n2022-11-25,116\n2022-11-26,32\n2022-11-27,42\n2022-11-28,155\n2022-11-29,130\n2022-11-30,149\n2022-12-01,124\n2022-12-02,157\n2022-12-03,51\n2022-12-04,56\n2022-12-05,123\n2022-12-06,133\n2022-12-07,125\n2022-12-08,111\n2022-12-09,139\n2022-12-10,66\n2022-12-11,81\n2022-12-12,102\n2022-12-13,143\n2022-12-14,96\n2022-12-15,163\n2022-12-16,159\n2022-12-17,70\n2022-12-18,68\n2022-12-19,93\n2022-12-20,132\n2022-12-21,119\n2022-12-22,119\n2022-12-23,84\n2022-12-24,54\n2022-12-25,22\n2022-12-26,44\n2022-12-27,64\n2022-12-28,57\n2022-12-29,85\n2022-12-30,55\n2022-12-31,39\n2023-01-01,40\n2023-01-02,93\n2023-01-03,99\n2023-01-04,109\n2023-01-05,114\n2023-01-06,110\n2023-01-07,60\n2023-01-08,56\n2023-01-09,144\n2023-01-10,104\n2023-01-11,144\n2023-01-12,117\n2023-01-13,154\n2023-01-14,60\n2023-01-15,40\n2023-01-16,118\n2023-01-17,111\n2023-01-18,128\n2023-01-19,175\n2023-01-20,169\n2023-01-21,68\n2023-01-22,88\n2023-01-23,154\n2023-01-24,103\n2023-01-25,117\n2023-01-26,128\n2023-01-27,135\n2023-01-28,47\n2023-01-29,74\n2023-01-30,149\n2023-01-31,175\n2023-02-01,136\n2023-02-02,159\n2023-02-03,79\n2023-02-04,80\n2023-02-05,54\n2023-02-06,125\n2023-02-07,142\n2023-02-08,132\n2023-02-09,119\n2023-02-10,102\n2023-02-11,47\n2023-02-12,50\n2023-02-13,129\n2023-02-14,110\n2023-02-15,101\n2023-02-16,116\n2023-02-17,75\n2023-02-18,59\n2023-02-19,73\n2023-02-20,103\n2023-02-21,100\n2023-02-22,115\n2023-02-23,99\n2023-02-24,155\n2023-02-25,61\n2023-02-26,43\n2023-02-27,128\n2023-02-28,138\n2023-03-01,106\n2023-03-02,101\n2023-03-03,127\n2023-03-04,44\n2023-03-05,46\n2023-03-06,129\n2023-03-07,113\n2023-03-08,97\n2023-03-09,104\n2023-03-10,129\n2023-03-11,59\n2023-03-12,54\n2023-03-13,104\n2023-03-14,109\n2023-03-15,109\n2023-03-16,132\n2023-03-17,96\n2023-03-18,79\n2023-03-19,65\n2023-03-20,71\n2023-03-21,75\n2023-03-22,118\n2023-03-23,105\n2023-03-24,87\n2023-03-25,45\n2023-03-26,41\n2023-03-27,119\n2023-03-28,138\n2023-03-29,123\n2023-03-30,148\n2023-03-31,137\n2023-04-01,67\n2023-04-02,52\n2023-04-03,116\n2023-04-04,101\n2023-04-05,124\n2023-04-06,94\n2023-04-07,79\n2023-04-08,53\n2023-04-09,47\n2023-04-10,80\n2023-04-11,103\n2023-04-12,134\n2023-04-13,149\n2023-04-14,100\n2023-04-15,52\n2023-04-16,60\n2023-04-17,86\n2023-04-18,117\n2023-04-19,86\n2023-04-20,71\n2023-04-21,79\n2023-04-22,45\n2023-04-23,38\n2023-04-24,119\n2023-04-25,111\n2023-04-26,120\n2023-04-27,82\n2023-04-28,84\n2023-04-29,66\n2023-04-30,22\n2023-05-01,71\n2023-05-02,85\n2023-05-03,72\n2023-05-04,92\n2023-05-05,94\n2023-05-06,27\n2023-05-07,34\n2023-05-08,88\n2023-05-09,88\n2023-05-10,115\n2023-05-11,116\n2023-05-12,113\n2023-05-13,28\n2023-05-14,14\n2023-05-15,96\n2023-05-16,98\n2023-05-17,95\n2023-05-18,124\n2023-05-19,97\n2023-05-20,44\n2023-05-21,70\n2023-05-22,118\n2023-05-23,106\n2023-05-24,108\n2023-05-25,73\n2023-05-26,106\n2023-05-27,42\n2023-05-28,37\n2023-05-29,54\n2023-05-30,98\n2023-05-31,95\n2023-06-01,103\n2023-06-02,92\n2023-06-03,42\n2023-06-04,35\n2023-06-05,68\n2023-06-06,71\n2023-06-07,61\n2023-06-08,84\n2023-06-09,83\n2023-06-10,37\n2023-06-11,29\n2023-06-12,78\n2023-06-13,78\n2023-06-14,90\n2023-06-15,80\n2023-06-16,98\n2023-06-17,54\n2023-06-18,30\n2023-06-19,80\n2023-06-20,115\n2023-06-21,121\n2023-06-22,104\n2023-06-23,73\n2023-06-24,38\n2023-06-25,41\n2023-06-26,126\n2023-06-27,94\n2023-06-28,74\n2023-06-29,102\n2023-06-30,118\n2023-07-01,46\n2023-07-02,35\n2023-07-03,107\n2023-07-04,67\n2023-07-05,90\n2023-07-06,132\n2023-07-07,110\n2023-07-08,25\n2023-07-09,26\n2023-07-10,85\n2023-07-11,90\n2023-07-12,83\n2023-07-13,113\n2023-07-14,121\n2023-07-15,27\n2023-07-16,23\n2023-07-17,48\n2023-07-18,63\n2023-07-19,52\n2023-07-20,67\n2023-07-21,78\n2023-07-22,38\n2023-07-23,41\n2023-07-24,113\n2023-07-25,99\n2023-07-26,103\n2023-07-27,88\n2023-07-28,88\n2023-07-29,52\n2023-07-30,36\n2023-07-31,86\n2023-08-01,84\n2023-08-02,104\n2023-08-03,94\n2023-08-04,89\n2023-08-05,46\n2023-08-06,41\n2023-08-07,53\n2023-08-08,100\n2023-08-09,111\n2023-08-10,180\n2023-08-11,82\n2023-08-12,84\n2023-08-13,33\n2023-08-14,100\n2023-08-15,93\n2023-08-16,177\n2023-08-17,118\n2023-08-18,93\n2023-08-19,57\n2023-08-20,61\n2023-08-21,90\n2023-08-22,75\n2023-08-23,115\n2023-08-24,109\n2023-08-25,78\n2023-08-26,48\n2023-08-27,45\n2023-08-28,104\n2023-08-29,79\n2023-08-30,129\n2023-08-31,104\n2023-09-01,82\n2023-09-02,39\n2023-09-03,25\n2023-09-04,43\n2023-09-05,114\n2023-09-06,90\n2023-09-07,120\n2023-09-08,72\n2023-09-09,74\n2023-09-10,43\n2023-09-11,74\n2023-09-12,76\n2023-09-13,59\n2023-09-14,79\n2023-09-15,76\n2023-09-16,55\n2023-09-17,24\n2023-09-18,99\n2023-09-19,77\n2023-09-20,65\n2023-09-21,71\n2023-09-22,54\n2023-09-23,26\n2023-09-24,49\n2023-09-25,79\n2023-09-26,80\n2023-09-27,113\n2023-09-28,91\n2023-09-29,76\n2023-09-30,33\n2023-10-01,28\n2023-10-02,80\n2023-10-03,80\n2023-10-04,88\n2023-10-05,77\n2023-10-06,96\n2023-10-07,51\n2023-10-08,48\n2023-10-09,88\n2023-10-10,76\n2023-10-11,56\n2023-10-12,90\n2023-10-13,73\n2023-10-14,30\n2023-10-15,34\n2023-10-16,97\n2023-10-17,118\n2023-10-18,125\n2023-10-19,93\n2023-10-20,81\n2023-10-21,55\n2023-10-22,44\n2023-10-23,53\n2023-10-24,84\n2023-10-25,102\n2023-10-26,97\n2023-10-27,89\n2023-10-28,44\n2023-10-29,69\n2023-10-30,127\n2023-10-31,134\n2023-11-01,112\n2023-11-02,85\n2023-11-03,84\n2023-11-04,52\n2023-11-05,63\n2023-11-06,114\n2023-11-07,140\n2023-11-08,99\n2023-11-09,99\n2023-11-10,98\n2023-11-11,67\n2023-11-12,52\n2023-11-13,100\n2023-11-14,106\n2023-11-15,122\n2023-11-16,113\n2023-11-17,107\n2023-11-18,47\n2023-11-19,35\n2023-11-20,84\n2023-11-21,108\n2023-11-22,91\n2023-11-23,86\n2023-11-24,95\n2023-11-25,32\n2023-11-26,54\n2023-11-27,66\n2023-11-28,95\n2023-11-29,87\n2023-11-30,91\n2023-12-01,43\n2023-12-02,32\n2023-12-03,19\n","format":{"type":"csv"}}});</script></div>

<div class="sourceClojure">
```clojure
(defn add-temporal-field [ds tf]
  (-> ds
      (tc/add-column tf (fn [ds]
                          (->> ds
                               :date
                               (datetime/long-temporal-field tf))))))
```
</div>

<div class="sourceClojure">
```clojure
(def processed-date-counts
  (-> date-counts
      (add-temporal-field :day-of-week)
      (add-temporal-field :day-of-year)
      (add-temporal-field :years)))
```
</div>

<div class="sourceClojure">
```clojure
(-> processed-date-counts
    :day-of-year
    fun/reduce-max)
```
</div>

<div class="printedClojure">
```clojure
366

```
</div>

<div class="sourceClojure">
```clojure
(-> processed-date-counts
    (tc/select-rows (fn [row]
                      (-> row :years (#{2008 2012 2016 2020}))))
    (vis/hanami-plot ht/line-chart
                     {:X "day-of-year"
                      :Y "n"
                      :COLOR "years"
                      :OPACITY 0.5}))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"color":{"field":"years","type":"nominal"},"opacity":{"value":0.5},"x":{"field":"day-of-year","type":"quantitative"}},"mark":{"type":"line","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"values":"date,n,day-of-week,day-of-year,years\n2008-03-29,7,6,89,2008\n2008-04-02,4,3,93,2008\n2008-04-03,9,4,94,2008\n2008-04-05,2,6,96,2008\n2008-04-06,1,7,97,2008\n2008-04-07,5,1,98,2008\n2008-04-08,9,2,99,2008\n2008-04-10,1,4,101,2008\n2008-04-11,1,5,102,2008\n2008-04-16,1,3,107,2008\n2008-04-18,1,5,109,2008\n2008-04-19,1,6,110,2008\n2008-04-21,1,1,112,2008\n2008-04-24,3,4,115,2008\n2008-04-25,1,5,116,2008\n2008-04-29,1,2,120,2008\n2008-04-30,4,3,121,2008\n2008-05-01,1,4,122,2008\n2008-05-02,2,5,123,2008\n2008-05-03,2,6,124,2008\n2008-05-07,3,3,128,2008\n2008-05-08,2,4,129,2008\n2008-05-10,6,6,131,2008\n2008-05-11,1,7,132,2008\n2008-05-12,1,1,133,2008\n2008-05-13,2,2,134,2008\n2008-05-14,1,3,135,2008\n2008-05-15,1,4,136,2008\n2008-05-16,2,5,137,2008\n2008-05-17,9,6,138,2008\n2008-05-18,12,7,139,2008\n2008-05-22,1,4,143,2008\n2008-05-24,3,6,145,2008\n2008-05-25,2,7,146,2008\n2008-05-26,1,1,147,2008\n2008-05-27,1,2,148,2008\n2008-05-28,1,3,149,2008\n2008-05-29,4,4,150,2008\n2008-05-31,1,6,152,2008\n2008-06-01,2,7,153,2008\n2008-06-02,1,1,154,2008\n2008-06-03,3,2,155,2008\n2008-06-04,2,3,156,2008\n2008-06-05,1,4,157,2008\n2008-06-06,1,5,158,2008\n2008-06-07,1,6,159,2008\n2008-06-08,5,7,160,2008\n2008-06-09,3,1,161,2008\n2008-06-11,2,3,163,2008\n2008-06-12,2,4,164,2008\n2008-06-13,2,5,165,2008\n2008-06-14,4,6,166,2008\n2008-06-15,5,7,167,2008\n2008-06-18,1,3,170,2008\n2008-06-19,3,4,171,2008\n2008-06-27,1,5,179,2008\n2008-06-28,6,6,180,2008\n2008-06-29,6,7,181,2008\n2008-06-30,2,1,182,2008\n2008-07-03,2,4,185,2008\n2008-07-04,1,5,186,2008\n2008-07-06,5,7,188,2008\n2008-07-07,2,1,189,2008\n2008-07-08,1,2,190,2008\n2008-07-09,8,3,191,2008\n2008-07-10,5,4,192,2008\n2008-07-11,6,5,193,2008\n2008-07-12,4,6,194,2008\n2008-07-13,3,7,195,2008\n2008-07-14,1,1,196,2008\n2008-07-15,5,2,197,2008\n2008-07-21,1,1,203,2008\n2008-07-22,5,2,204,2008\n2008-07-24,2,4,206,2008\n2008-07-25,2,5,207,2008\n2008-07-26,7,6,208,2008\n2008-07-27,3,7,209,2008\n2008-07-29,8,2,211,2008\n2008-08-05,1,2,218,2008\n2008-08-06,4,3,219,2008\n2008-08-07,7,4,220,2008\n2008-08-08,1,5,221,2008\n2008-08-09,1,6,222,2008\n2008-08-10,1,7,223,2008\n2008-08-11,1,1,224,2008\n2008-08-12,4,2,225,2008\n2008-08-13,1,3,226,2008\n2008-08-14,1,4,227,2008\n2008-08-15,3,5,228,2008\n2008-08-16,9,6,229,2008\n2008-08-17,4,7,230,2008\n2008-08-19,7,2,232,2008\n2008-08-20,3,3,233,2008\n2008-08-21,1,4,234,2008\n2008-08-25,2,1,238,2008\n2008-08-27,2,3,240,2008\n2008-08-28,2,4,241,2008\n2008-08-29,5,5,242,2008\n2008-08-30,8,6,243,2008\n2008-09-02,8,2,246,2008\n2008-09-03,7,3,247,2008\n2008-09-04,1,4,248,2008\n2008-09-05,1,5,249,2008\n2008-09-06,2,6,250,2008\n2008-09-07,3,7,251,2008\n2008-09-08,29,1,252,2008\n2008-09-09,4,2,253,2008\n2008-09-10,3,3,254,2008\n2008-09-11,2,4,255,2008\n2008-09-12,3,5,256,2008\n2008-09-13,11,6,257,2008\n2008-09-14,2,7,258,2008\n2008-09-15,8,1,259,2008\n2008-09-16,11,2,260,2008\n2008-09-17,8,3,261,2008\n2008-09-18,1,4,262,2008\n2008-09-19,2,5,263,2008\n2008-09-20,8,6,264,2008\n2008-09-21,7,7,265,2008\n2008-09-22,3,1,266,2008\n2008-09-23,4,2,267,2008\n2008-09-24,4,3,268,2008\n2008-09-25,6,4,269,2008\n2008-09-26,4,5,270,2008\n2008-09-27,2,6,271,2008\n2008-09-28,7,7,272,2008\n2008-10-01,6,3,275,2008\n2008-10-02,10,4,276,2008\n2008-10-03,5,5,277,2008\n2008-10-04,3,6,278,2008\n2008-10-05,5,7,279,2008\n2008-10-06,11,1,280,2008\n2008-10-07,2,2,281,2008\n2008-10-08,6,3,282,2008\n2008-10-09,3,4,283,2008\n2008-10-10,4,5,284,2008\n2008-10-11,2,6,285,2008\n2008-10-12,4,7,286,2008\n2008-10-13,2,1,287,2008\n2008-10-14,1,2,288,2008\n2008-10-15,10,3,289,2008\n2008-10-16,1,4,290,2008\n2008-10-17,4,5,291,2008\n2008-10-18,2,6,292,2008\n2008-10-19,8,7,293,2008\n2008-10-21,1,2,295,2008\n2008-10-22,5,3,296,2008\n2008-10-23,4,4,297,2008\n2008-10-25,2,6,299,2008\n2008-10-26,3,7,300,2008\n2008-10-27,1,1,301,2008\n2008-10-28,2,2,302,2008\n2008-10-29,1,3,303,2008\n2008-10-30,5,4,304,2008\n2008-10-31,5,5,305,2008\n2008-11-01,9,6,306,2008\n2008-11-02,1,7,307,2008\n2008-11-03,7,1,308,2008\n2008-11-08,3,6,313,2008\n2008-11-09,5,7,314,2008\n2008-11-11,1,2,316,2008\n2008-11-12,5,3,317,2008\n2008-11-13,23,4,318,2008\n2008-11-14,2,5,319,2008\n2008-11-15,8,6,320,2008\n2008-11-16,17,7,321,2008\n2008-11-17,3,1,322,2008\n2008-11-18,25,2,323,2008\n2008-11-19,3,3,324,2008\n2008-11-20,2,4,325,2008\n2008-11-21,3,5,326,2008\n2008-11-22,3,6,327,2008\n2008-11-23,7,7,328,2008\n2008-11-24,1,1,329,2008\n2008-11-25,6,2,330,2008\n2008-11-26,3,3,331,2008\n2008-11-27,3,4,332,2008\n2008-11-28,5,5,333,2008\n2008-11-29,5,6,334,2008\n2008-11-30,5,7,335,2008\n2008-12-01,7,1,336,2008\n2008-12-02,3,2,337,2008\n2008-12-03,7,3,338,2008\n2008-12-04,5,4,339,2008\n2008-12-05,6,5,340,2008\n2008-12-07,3,7,342,2008\n2008-12-08,4,1,343,2008\n2008-12-09,1,2,344,2008\n2008-12-10,6,3,345,2008\n2008-12-11,5,4,346,2008\n2008-12-12,1,5,347,2008\n2008-12-13,12,6,348,2008\n2008-12-14,8,7,349,2008\n2008-12-15,9,1,350,2008\n2008-12-16,6,2,351,2008\n2008-12-17,6,3,352,2008\n2008-12-19,18,5,354,2008\n2008-12-20,1,6,355,2008\n2008-12-21,3,7,356,2008\n2008-12-22,3,1,357,2008\n2008-12-23,10,2,358,2008\n2008-12-24,3,3,359,2008\n2008-12-25,1,4,360,2008\n2008-12-26,1,5,361,2008\n2008-12-27,13,6,362,2008\n2008-12-28,13,7,363,2008\n2008-12-29,15,1,364,2008\n2008-12-30,10,2,365,2008\n2008-12-31,2,3,366,2008\n2012-01-01,56,7,1,2012\n2012-01-02,76,1,2,2012\n2012-01-03,60,2,3,2012\n2012-01-04,121,3,4,2012\n2012-01-05,77,4,5,2012\n2012-01-06,65,5,6,2012\n2012-01-07,60,6,7,2012\n2012-01-08,82,7,8,2012\n2012-01-09,72,1,9,2012\n2012-01-10,106,2,10,2012\n2012-01-11,96,3,11,2012\n2012-01-12,82,4,12,2012\n2012-01-13,145,5,13,2012\n2012-01-14,65,6,14,2012\n2012-01-15,64,7,15,2012\n2012-01-16,71,1,16,2012\n2012-01-17,79,2,17,2012\n2012-01-18,88,3,18,2012\n2012-01-19,82,4,19,2012\n2012-01-20,71,5,20,2012\n2012-01-21,57,6,21,2012\n2012-01-22,61,7,22,2012\n2012-01-23,69,1,23,2012\n2012-01-24,107,2,24,2012\n2012-01-25,99,3,25,2012\n2012-01-26,92,4,26,2012\n2012-01-27,70,5,27,2012\n2012-01-28,44,6,28,2012\n2012-01-29,84,7,29,2012\n2012-01-30,54,1,30,2012\n2012-01-31,71,2,31,2012\n2012-02-01,95,3,32,2012\n2012-02-02,86,4,33,2012\n2012-02-03,87,5,34,2012\n2012-02-04,82,6,35,2012\n2012-02-05,115,7,36,2012\n2012-02-06,189,1,37,2012\n2012-02-07,116,2,38,2012\n2012-02-08,122,3,39,2012\n2012-02-09,106,4,40,2012\n2012-02-10,97,5,41,2012\n2012-02-11,94,6,42,2012\n2012-02-12,90,7,43,2012\n2012-02-13,91,1,44,2012\n2012-02-14,106,2,45,2012\n2012-02-15,93,3,46,2012\n2012-02-16,119,4,47,2012\n2012-02-17,122,5,48,2012\n2012-02-18,109,6,49,2012\n2012-02-19,161,7,50,2012\n2012-02-20,120,1,51,2012\n2012-02-21,144,2,52,2012\n2012-02-22,117,3,53,2012\n2012-02-23,78,4,54,2012\n2012-02-24,68,5,55,2012\n2012-02-25,104,6,56,2012\n2012-02-26,81,7,57,2012\n2012-02-27,87,1,58,2012\n2012-02-28,110,2,59,2012\n2012-02-29,71,3,60,2012\n2012-03-01,83,4,61,2012\n2012-03-02,65,5,62,2012\n2012-03-03,82,6,63,2012\n2012-03-04,133,7,64,2012\n2012-03-05,139,1,65,2012\n2012-03-06,107,2,66,2012\n2012-03-07,77,3,67,2012\n2012-03-08,102,4,68,2012\n2012-03-09,111,5,69,2012\n2012-03-10,100,6,70,2012\n2012-03-11,166,7,71,2012\n2012-03-12,78,1,72,2012\n2012-03-13,100,2,73,2012\n2012-03-14,57,3,74,2012\n2012-03-15,53,4,75,2012\n2012-03-16,99,5,76,2012\n2012-03-17,88,6,77,2012\n2012-03-18,67,7,78,2012\n2012-03-19,160,1,79,2012\n2012-03-20,100,2,80,2012\n2012-03-21,101,3,81,2012\n2012-03-22,99,4,82,2012\n2012-03-23,123,5,83,2012\n2012-03-24,93,6,84,2012\n2012-03-25,142,7,85,2012\n2012-03-26,111,1,86,2012\n2012-03-27,84,2,87,2012\n2012-03-28,67,3,88,2012\n2012-03-29,76,4,89,2012\n2012-03-30,99,5,90,2012\n2012-03-31,109,6,91,2012\n2012-04-01,118,7,92,2012\n2012-04-02,124,1,93,2012\n2012-04-03,109,2,94,2012\n2012-04-04,175,3,95,2012\n2012-04-05,118,4,96,2012\n2012-04-06,92,5,97,2012\n2012-04-07,147,6,98,2012\n2012-04-08,80,7,99,2012\n2012-04-09,135,1,100,2012\n2012-04-10,120,2,101,2012\n2012-04-11,166,3,102,2012\n2012-04-12,77,4,103,2012\n2012-04-13,67,5,104,2012\n2012-04-14,94,6,105,2012\n2012-04-15,102,7,106,2012\n2012-04-16,123,1,107,2012\n2012-04-17,88,2,108,2012\n2012-04-18,130,3,109,2012\n2012-04-19,86,4,110,2012\n2012-04-20,108,5,111,2012\n2012-04-21,117,6,112,2012\n2012-04-22,95,7,113,2012\n2012-04-23,112,1,114,2012\n2012-04-24,106,2,115,2012\n2012-04-25,95,3,116,2012\n2012-04-26,85,4,117,2012\n2012-04-27,107,5,118,2012\n2012-04-28,120,6,119,2012\n2012-04-29,165,7,120,2012\n2012-04-30,127,1,121,2012\n2012-05-01,86,2,122,2012\n2012-05-02,107,3,123,2012\n2012-05-03,92,4,124,2012\n2012-05-04,107,5,125,2012\n2012-05-05,80,6,126,2012\n2012-05-06,103,7,127,2012\n2012-05-07,131,1,128,2012\n2012-05-08,73,2,129,2012\n2012-05-09,105,3,130,2012\n2012-05-10,81,4,131,2012\n2012-05-11,140,5,132,2012\n2012-05-12,83,6,133,2012\n2012-05-13,109,7,134,2012\n2012-05-14,67,1,135,2012\n2012-05-15,71,2,136,2012\n2012-05-16,86,3,137,2012\n2012-05-17,118,4,138,2012\n2012-05-18,101,5,139,2012\n2012-05-19,77,6,140,2012\n2012-05-20,110,7,141,2012\n2012-05-21,77,1,142,2012\n2012-05-22,81,2,143,2012\n2012-05-23,70,3,144,2012\n2012-05-24,79,4,145,2012\n2012-05-25,60,5,146,2012\n2012-05-26,65,6,147,2012\n2012-05-27,46,7,148,2012\n2012-05-28,74,1,149,2012\n2012-05-29,48,2,150,2012\n2012-05-30,90,3,151,2012\n2012-05-31,95,4,152,2012\n2012-06-01,84,5,153,2012\n2012-06-02,31,6,154,2012\n2012-06-03,73,7,155,2012\n2012-06-04,98,1,156,2012\n2012-06-05,63,2,157,2012\n2012-06-06,66,3,158,2012\n2012-06-07,57,4,159,2012\n2012-06-08,78,5,160,2012\n2012-06-09,54,6,161,2012\n2012-06-10,122,7,162,2012\n2012-06-11,95,1,163,2012\n2012-06-12,87,2,164,2012\n2012-06-13,113,3,165,2012\n2012-06-14,79,4,166,2012\n2012-06-15,107,5,167,2012\n2012-06-16,106,6,168,2012\n2012-06-17,96,7,169,2012\n2012-06-18,55,1,170,2012\n2012-06-19,79,2,171,2012\n2012-06-20,94,3,172,2012\n2012-06-21,54,4,173,2012\n2012-06-22,44,5,174,2012\n2012-06-23,67,6,175,2012\n2012-06-24,64,7,176,2012\n2012-06-25,96,1,177,2012\n2012-06-26,73,2,178,2012\n2012-06-27,108,3,179,2012\n2012-06-28,40,4,180,2012\n2012-06-29,87,5,181,2012\n2012-06-30,44,6,182,2012\n2012-07-01,61,7,183,2012\n2012-07-02,91,1,184,2012\n2012-07-03,118,2,185,2012\n2012-07-04,96,3,186,2012\n2012-07-05,123,4,187,2012\n2012-07-06,170,5,188,2012\n2012-07-07,117,6,189,2012\n2012-07-08,136,7,190,2012\n2012-07-09,81,1,191,2012\n2012-07-10,74,2,192,2012\n2012-07-11,96,3,193,2012\n2012-07-12,97,4,194,2012\n2012-07-13,74,5,195,2012\n2012-07-14,83,6,196,2012\n2012-07-15,64,7,197,2012\n2012-07-16,95,1,198,2012\n2012-07-17,119,2,199,2012\n2012-07-18,102,3,200,2012\n2012-07-19,70,4,201,2012\n2012-07-20,66,5,202,2012\n2012-07-21,102,6,203,2012\n2012-07-22,96,7,204,2012\n2012-07-23,107,1,205,2012\n2012-07-24,100,2,206,2012\n2012-07-25,76,3,207,2012\n2012-07-26,96,4,208,2012\n2012-07-27,81,5,209,2012\n2012-07-28,93,6,210,2012\n2012-07-29,74,7,211,2012\n2012-07-30,61,1,212,2012\n2012-07-31,73,2,213,2012\n2012-08-01,100,3,214,2012\n2012-08-02,128,4,215,2012\n2012-08-03,79,5,216,2012\n2012-08-04,106,6,217,2012\n2012-08-05,72,7,218,2012\n2012-08-06,109,1,219,2012\n2012-08-07,107,2,220,2012\n2012-08-08,119,3,221,2012\n2012-08-09,82,4,222,2012\n2012-08-10,100,5,223,2012\n2012-08-11,60,6,224,2012\n2012-08-12,77,7,225,2012\n2012-08-13,68,1,226,2012\n2012-08-14,88,2,227,2012\n2012-08-15,116,3,228,2012\n2012-08-16,94,4,229,2012\n2012-08-17,99,5,230,2012\n2012-08-18,141,6,231,2012\n2012-08-19,46,7,232,2012\n2012-08-20,61,1,233,2012\n2012-08-21,75,2,234,2012\n2012-08-22,84,3,235,2012\n2012-08-23,76,4,236,2012\n2012-08-24,102,5,237,2012\n2012-08-25,71,6,238,2012\n2012-08-26,83,7,239,2012\n2012-08-27,91,1,240,2012\n2012-08-28,80,2,241,2012\n2012-08-29,60,3,242,2012\n2012-08-30,78,4,243,2012\n2012-08-31,61,5,244,2012\n2012-09-01,57,6,245,2012\n2012-09-02,41,7,246,2012\n2012-09-03,86,1,247,2012\n2012-09-04,88,2,248,2012\n2012-09-05,73,3,249,2012\n2012-09-06,100,4,250,2012\n2012-09-07,106,5,251,2012\n2012-09-08,57,6,252,2012\n2012-09-09,40,7,253,2012\n2012-09-10,65,1,254,2012\n2012-09-11,59,2,255,2012\n2012-09-12,99,3,256,2012\n2012-09-13,55,4,257,2012\n2012-09-14,64,5,258,2012\n2012-09-15,40,6,259,2012\n2012-09-16,52,7,260,2012\n2012-09-17,57,1,261,2012\n2012-09-18,51,2,262,2012\n2012-09-19,38,3,263,2012\n2012-09-20,47,4,264,2012\n2012-09-21,53,5,265,2012\n2012-09-22,69,6,266,2012\n2012-09-23,40,7,267,2012\n2012-09-24,32,1,268,2012\n2012-09-25,45,2,269,2012\n2012-09-26,54,3,270,2012\n2012-09-27,59,4,271,2012\n2012-09-28,61,5,272,2012\n2012-09-29,58,6,273,2012\n2012-09-30,62,7,274,2012\n2012-10-01,96,1,275,2012\n2012-10-02,101,2,276,2012\n2012-10-03,98,3,277,2012\n2012-10-04,78,4,278,2012\n2012-10-05,107,5,279,2012\n2012-10-06,59,6,280,2012\n2012-10-07,48,7,281,2012\n2012-10-08,60,1,282,2012\n2012-10-09,76,2,283,2012\n2012-10-10,126,3,284,2012\n2012-10-11,58,4,285,2012\n2012-10-12,70,5,286,2012\n2012-10-13,37,6,287,2012\n2012-10-14,70,7,288,2012\n2012-10-15,79,1,289,2012\n2012-10-16,77,2,290,2012\n2012-10-17,33,3,291,2012\n2012-10-18,86,4,292,2012\n2012-10-19,62,5,293,2012\n2012-10-20,36,6,294,2012\n2012-10-21,18,7,295,2012\n2012-10-22,55,1,296,2012\n2012-10-23,78,2,297,2012\n2012-10-24,58,3,298,2012\n2012-10-25,87,4,299,2012\n2012-10-26,112,5,300,2012\n2012-10-27,48,6,301,2012\n2012-10-28,53,7,302,2012\n2012-10-29,38,1,303,2012\n2012-10-30,92,2,304,2012\n2012-10-31,54,3,305,2012\n2012-11-01,109,4,306,2012\n2012-11-02,119,5,307,2012\n2012-11-03,71,6,308,2012\n2012-11-04,59,7,309,2012\n2012-11-05,91,1,310,2012\n2012-11-06,39,2,311,2012\n2012-11-07,56,3,312,2012\n2012-11-08,66,4,313,2012\n2012-11-09,56,5,314,2012\n2012-11-10,39,6,315,2012\n2012-11-11,20,7,316,2012\n2012-11-12,68,1,317,2012\n2012-11-13,66,2,318,2012\n2012-11-14,58,3,319,2012\n2012-11-15,47,4,320,2012\n2012-11-16,70,5,321,2012\n2012-11-17,67,6,322,2012\n2012-11-18,38,7,323,2012\n2012-11-19,95,1,324,2012\n2012-11-20,114,2,325,2012\n2012-11-21,87,3,326,2012\n2012-11-22,49,4,327,2012\n2012-11-23,80,5,328,2012\n2012-11-24,70,6,329,2012\n2012-11-25,35,7,330,2012\n2012-11-26,71,1,331,2012\n2012-11-27,79,2,332,2012\n2012-11-28,64,3,333,2012\n2012-11-29,58,4,334,2012\n2012-11-30,36,5,335,2012\n2012-12-01,56,6,336,2012\n2012-12-02,58,7,337,2012\n2012-12-03,84,1,338,2012\n2012-12-04,103,2,339,2012\n2012-12-05,118,3,340,2012\n2012-12-06,46,4,341,2012\n2012-12-07,58,5,342,2012\n2012-12-08,98,6,343,2012\n2012-12-09,43,7,344,2012\n2012-12-10,70,1,345,2012\n2012-12-11,91,2,346,2012\n2012-12-12,74,3,347,2012\n2012-12-13,88,4,348,2012\n2012-12-14,74,5,349,2012\n2012-12-15,54,6,350,2012\n2012-12-16,81,7,351,2012\n2012-12-17,121,1,352,2012\n2012-12-18,111,2,353,2012\n2012-12-19,112,3,354,2012\n2012-12-20,103,4,355,2012\n2012-12-21,63,5,356,2012\n2012-12-22,59,6,357,2012\n2012-12-23,91,7,358,2012\n2012-12-24,99,1,359,2012\n2012-12-25,60,2,360,2012\n2012-12-26,61,3,361,2012\n2012-12-27,90,4,362,2012\n2012-12-28,59,5,363,2012\n2012-12-29,69,6,364,2012\n2012-12-30,66,7,365,2012\n2012-12-31,110,1,366,2012\n2016-01-01,131,5,1,2016\n2016-01-02,151,6,2,2016\n2016-01-03,154,7,3,2016\n2016-01-04,185,1,4,2016\n2016-01-05,226,2,5,2016\n2016-01-06,276,3,6,2016\n2016-01-07,310,4,7,2016\n2016-01-08,242,5,8,2016\n2016-01-09,197,6,9,2016\n2016-01-10,159,7,10,2016\n2016-01-11,330,1,11,2016\n2016-01-12,212,2,12,2016\n2016-01-13,261,3,13,2016\n2016-01-14,294,4,14,2016\n2016-01-15,263,5,15,2016\n2016-01-16,228,6,16,2016\n2016-01-17,200,7,17,2016\n2016-01-18,203,1,18,2016\n2016-01-19,214,2,19,2016\n2016-01-20,195,3,20,2016\n2016-01-21,268,4,21,2016\n2016-01-22,209,5,22,2016\n2016-01-23,169,6,23,2016\n2016-01-24,214,7,24,2016\n2016-01-25,251,1,25,2016\n2016-01-26,224,2,26,2016\n2016-01-27,211,3,27,2016\n2016-01-28,238,4,28,2016\n2016-01-29,316,5,29,2016\n2016-01-30,187,6,30,2016\n2016-01-31,253,7,31,2016\n2016-02-01,271,1,32,2016\n2016-02-02,307,2,33,2016\n2016-02-03,221,3,34,2016\n2016-02-04,209,4,35,2016\n2016-02-05,201,5,36,2016\n2016-02-06,165,6,37,2016\n2016-02-07,163,7,38,2016\n2016-02-08,191,1,39,2016\n2016-02-09,217,2,40,2016\n2016-02-10,192,3,41,2016\n2016-02-11,218,4,42,2016\n2016-02-12,291,5,43,2016\n2016-02-13,137,6,44,2016\n2016-02-14,145,7,45,2016\n2016-02-15,182,1,46,2016\n2016-02-16,249,2,47,2016\n2016-02-17,238,3,48,2016\n2016-02-18,224,4,49,2016\n2016-02-19,258,5,50,2016\n2016-02-20,136,6,51,2016\n2016-02-21,168,7,52,2016\n2016-02-22,211,1,53,2016\n2016-02-23,256,2,54,2016\n2016-02-24,232,3,55,2016\n2016-02-25,242,4,56,2016\n2016-02-26,232,5,57,2016\n2016-02-27,179,6,58,2016\n2016-02-28,246,7,59,2016\n2016-02-29,257,1,60,2016\n2016-03-01,208,2,61,2016\n2016-03-02,178,3,62,2016\n2016-03-03,208,4,63,2016\n2016-03-04,208,5,64,2016\n2016-03-05,127,6,65,2016\n2016-03-06,119,7,66,2016\n2016-03-07,208,1,67,2016\n2016-03-08,236,2,68,2016\n2016-03-09,191,3,69,2016\n2016-03-10,136,4,70,2016\n2016-03-11,180,5,71,2016\n2016-03-12,98,6,72,2016\n2016-03-13,97,7,73,2016\n2016-03-14,142,1,74,2016\n2016-03-15,180,2,75,2016\n2016-03-16,245,3,76,2016\n2016-03-17,232,4,77,2016\n2016-03-18,188,5,78,2016\n2016-03-19,119,6,79,2016\n2016-03-20,159,7,80,2016\n2016-03-21,216,1,81,2016\n2016-03-22,200,2,82,2016\n2016-03-23,228,3,83,2016\n2016-03-24,184,4,84,2016\n2016-03-25,272,5,85,2016\n2016-03-26,145,6,86,2016\n2016-03-27,101,7,87,2016\n2016-03-28,241,1,88,2016\n2016-03-29,204,2,89,2016\n2016-03-30,153,3,90,2016\n2016-03-31,177,4,91,2016\n2016-04-01,245,5,92,2016\n2016-04-02,175,6,93,2016\n2016-04-03,175,7,94,2016\n2016-04-04,206,1,95,2016\n2016-04-05,190,2,96,2016\n2016-04-06,189,3,97,2016\n2016-04-07,174,4,98,2016\n2016-04-08,182,5,99,2016\n2016-04-09,182,6,100,2016\n2016-04-10,124,7,101,2016\n2016-04-11,205,1,102,2016\n2016-04-12,218,2,103,2016\n2016-04-13,233,3,104,2016\n2016-04-14,231,4,105,2016\n2016-04-15,155,5,106,2016\n2016-04-16,174,6,107,2016\n2016-04-17,61,7,108,2016\n2016-04-18,197,1,109,2016\n2016-04-19,197,2,110,2016\n2016-04-20,270,3,111,2016\n2016-04-21,174,4,112,2016\n2016-04-22,166,5,113,2016\n2016-04-23,131,6,114,2016\n2016-04-24,89,7,115,2016\n2016-04-25,185,1,116,2016\n2016-04-26,155,2,117,2016\n2016-04-27,147,3,118,2016\n2016-04-28,129,4,119,2016\n2016-04-29,182,5,120,2016\n2016-04-30,114,6,121,2016\n2016-05-01,114,7,122,2016\n2016-05-02,268,1,123,2016\n2016-05-03,157,2,124,2016\n2016-05-04,184,3,125,2016\n2016-05-05,176,4,126,2016\n2016-05-06,162,5,127,2016\n2016-05-07,147,6,128,2016\n2016-05-08,80,7,129,2016\n2016-05-09,190,1,130,2016\n2016-05-10,205,2,131,2016\n2016-05-11,190,3,132,2016\n2016-05-12,140,4,133,2016\n2016-05-13,192,5,134,2016\n2016-05-14,77,6,135,2016\n2016-05-15,98,7,136,2016\n2016-05-16,187,1,137,2016\n2016-05-17,144,2,138,2016\n2016-05-18,160,3,139,2016\n2016-05-19,197,4,140,2016\n2016-05-20,183,5,141,2016\n2016-05-21,135,6,142,2016\n2016-05-22,150,7,143,2016\n2016-05-23,211,1,144,2016\n2016-05-24,236,2,145,2016\n2016-05-25,167,3,146,2016\n2016-05-26,160,4,147,2016\n2016-05-27,131,5,148,2016\n2016-05-28,97,6,149,2016\n2016-05-29,118,7,150,2016\n2016-05-30,162,1,151,2016\n2016-05-31,206,2,152,2016\n2016-06-01,280,3,153,2016\n2016-06-02,224,4,154,2016\n2016-06-03,255,5,155,2016\n2016-06-04,130,6,156,2016\n2016-06-05,119,7,157,2016\n2016-06-06,176,1,158,2016\n2016-06-07,212,2,159,2016\n2016-06-08,211,3,160,2016\n2016-06-09,209,4,161,2016\n2016-06-10,195,5,162,2016\n2016-06-11,178,6,163,2016\n2016-06-12,129,7,164,2016\n2016-06-13,292,1,165,2016\n2016-06-14,211,2,166,2016\n2016-06-15,196,3,167,2016\n2016-06-16,192,4,168,2016\n2016-06-17,199,5,169,2016\n2016-06-18,116,6,170,2016\n2016-06-19,103,7,171,2016\n2016-06-20,271,1,172,2016\n2016-06-21,233,2,173,2016\n2016-06-22,220,3,174,2016\n2016-06-23,175,4,175,2016\n2016-06-24,165,5,176,2016\n2016-06-25,67,6,177,2016\n2016-06-26,116,7,178,2016\n2016-06-27,271,1,179,2016\n2016-06-28,214,2,180,2016\n2016-06-29,193,3,181,2016\n2016-06-30,243,4,182,2016\n2016-07-01,218,5,183,2016\n2016-07-02,170,6,184,2016\n2016-07-03,102,7,185,2016\n2016-07-04,123,1,186,2016\n2016-07-05,148,2,187,2016\n2016-07-06,222,3,188,2016\n2016-07-07,204,4,189,2016\n2016-07-08,172,5,190,2016\n2016-07-09,115,6,191,2016\n2016-07-10,115,7,192,2016\n2016-07-11,175,1,193,2016\n2016-07-12,189,2,194,2016\n2016-07-13,168,3,195,2016\n2016-07-14,164,4,196,2016\n2016-07-15,159,5,197,2016\n2016-07-16,91,6,198,2016\n2016-07-17,135,7,199,2016\n2016-07-18,210,1,200,2016\n2016-07-19,208,2,201,2016\n2016-07-20,199,3,202,2016\n2016-07-21,155,4,203,2016\n2016-07-22,184,5,204,2016\n2016-07-23,98,6,205,2016\n2016-07-24,117,7,206,2016\n2016-07-25,200,1,207,2016\n2016-07-26,233,2,208,2016\n2016-07-27,221,3,209,2016\n2016-07-28,267,4,210,2016\n2016-07-29,219,5,211,2016\n2016-07-30,122,6,212,2016\n2016-07-31,133,7,213,2016\n2016-08-01,178,1,214,2016\n2016-08-02,170,2,215,2016\n2016-08-03,131,3,216,2016\n2016-08-04,230,4,217,2016\n2016-08-05,155,5,218,2016\n2016-08-06,71,6,219,2016\n2016-08-07,105,7,220,2016\n2016-08-08,158,1,221,2016\n2016-08-09,205,2,222,2016\n2016-08-10,227,3,223,2016\n2016-08-11,206,4,224,2016\n2016-08-12,194,5,225,2016\n2016-08-13,66,6,226,2016\n2016-08-14,97,7,227,2016\n2016-08-15,165,1,228,2016\n2016-08-16,170,2,229,2016\n2016-08-17,191,3,230,2016\n2016-08-18,180,4,231,2016\n2016-08-19,181,5,232,2016\n2016-08-20,126,6,233,2016\n2016-08-21,143,7,234,2016\n2016-08-22,207,1,235,2016\n2016-08-23,227,2,236,2016\n2016-08-24,206,3,237,2016\n2016-08-25,242,4,238,2016\n2016-08-26,140,5,239,2016\n2016-08-27,104,6,240,2016\n2016-08-28,111,7,241,2016\n2016-08-29,192,1,242,2016\n2016-08-30,182,2,243,2016\n2016-08-31,254,3,244,2016\n2016-09-01,265,4,245,2016\n2016-09-02,143,5,246,2016\n2016-09-03,74,6,247,2016\n2016-09-04,122,7,248,2016\n2016-09-05,130,1,249,2016\n2016-09-06,213,2,250,2016\n2016-09-07,177,3,251,2016\n2016-09-08,169,4,252,2016\n2016-09-09,174,5,253,2016\n2016-09-10,65,6,254,2016\n2016-09-11,89,7,255,2016\n2016-09-12,153,1,256,2016\n2016-09-13,119,2,257,2016\n2016-09-14,141,3,258,2016\n2016-09-15,179,4,259,2016\n2016-09-16,190,5,260,2016\n2016-09-17,85,6,261,2016\n2016-09-18,150,7,262,2016\n2016-09-19,200,1,263,2016\n2016-09-20,169,2,264,2016\n2016-09-21,149,3,265,2016\n2016-09-22,170,4,266,2016\n2016-09-23,131,5,267,2016\n2016-09-24,76,6,268,2016\n2016-09-25,78,7,269,2016\n2016-09-26,163,1,270,2016\n2016-09-27,187,2,271,2016\n2016-09-28,259,3,272,2016\n2016-09-29,154,4,273,2016\n2016-09-30,150,5,274,2016\n2016-10-01,98,6,275,2016\n2016-10-02,103,7,276,2016\n2016-10-03,199,1,277,2016\n2016-10-04,213,2,278,2016\n2016-10-05,263,3,279,2016\n2016-10-06,212,4,280,2016\n2016-10-07,226,5,281,2016\n2016-10-08,135,6,282,2016\n2016-10-09,93,7,283,2016\n2016-10-10,181,1,284,2016\n2016-10-11,166,2,285,2016\n2016-10-12,224,3,286,2016\n2016-10-13,221,4,287,2016\n2016-10-14,194,5,288,2016\n2016-10-15,97,6,289,2016\n2016-10-16,126,7,290,2016\n2016-10-17,141,1,291,2016\n2016-10-18,146,2,292,2016\n2016-10-19,114,3,293,2016\n2016-10-20,142,4,294,2016\n2016-10-21,182,5,295,2016\n2016-10-22,95,6,296,2016\n2016-10-23,124,7,297,2016\n2016-10-24,132,1,298,2016\n2016-10-25,140,2,299,2016\n2016-10-26,148,3,300,2016\n2016-10-27,124,4,301,2016\n2016-10-28,123,5,302,2016\n2016-10-29,156,6,303,2016\n2016-10-30,81,7,304,2016\n2016-10-31,82,1,305,2016\n2016-11-01,127,2,306,2016\n2016-11-02,146,3,307,2016\n2016-11-03,156,4,308,2016\n2016-11-04,148,5,309,2016\n2016-11-05,78,6,310,2016\n2016-11-06,103,7,311,2016\n2016-11-07,156,1,312,2016\n2016-11-08,120,2,313,2016\n2016-11-09,147,3,314,2016\n2016-11-10,148,4,315,2016\n2016-11-11,114,5,316,2016\n2016-11-12,76,6,317,2016\n2016-11-13,158,7,318,2016\n2016-11-14,179,1,319,2016\n2016-11-15,214,2,320,2016\n2016-11-16,142,3,321,2016\n2016-11-17,184,4,322,2016\n2016-11-18,162,5,323,2016\n2016-11-19,97,6,324,2016\n2016-11-20,103,7,325,2016\n2016-11-21,162,1,326,2016\n2016-11-22,112,2,327,2016\n2016-11-23,86,3,328,2016\n2016-11-24,75,4,329,2016\n2016-11-25,56,5,330,2016\n2016-11-26,47,6,331,2016\n2016-11-27,78,7,332,2016\n2016-11-28,141,1,333,2016\n2016-11-29,169,2,334,2016\n2016-11-30,138,3,335,2016\n2016-12-01,137,4,336,2016\n2016-12-02,147,5,337,2016\n2016-12-03,123,6,338,2016\n2016-12-04,107,7,339,2016\n2016-12-05,214,1,340,2016\n2016-12-06,213,2,341,2016\n2016-12-07,190,3,342,2016\n2016-12-08,168,4,343,2016\n2016-12-09,156,5,344,2016\n2016-12-10,87,6,345,2016\n2016-12-11,106,7,346,2016\n2016-12-12,210,1,347,2016\n2016-12-13,227,2,348,2016\n2016-12-14,192,3,349,2016\n2016-12-15,163,4,350,2016\n2016-12-16,89,5,351,2016\n2016-12-17,95,6,352,2016\n2016-12-18,90,7,353,2016\n2016-12-19,144,1,354,2016\n2016-12-20,138,2,355,2016\n2016-12-21,152,3,356,2016\n2016-12-22,159,4,357,2016\n2016-12-23,122,5,358,2016\n2016-12-24,67,6,359,2016\n2016-12-25,57,7,360,2016\n2016-12-26,75,1,361,2016\n2016-12-27,111,2,362,2016\n2016-12-28,117,3,363,2016\n2016-12-29,129,4,364,2016\n2016-12-30,75,5,365,2016\n2016-12-31,23,6,366,2016\n2020-01-01,99,3,1,2020\n2020-01-02,142,4,2,2020\n2020-01-03,95,5,3,2020\n2020-01-04,120,6,4,2020\n2020-01-05,81,7,5,2020\n2020-01-06,125,1,6,2020\n2020-01-07,161,2,7,2020\n2020-01-08,169,3,8,2020\n2020-01-09,192,4,9,2020\n2020-01-10,251,5,10,2020\n2020-01-11,164,6,11,2020\n2020-01-12,219,7,12,2020\n2020-01-13,224,1,13,2020\n2020-01-14,193,2,14,2020\n2020-01-15,248,3,15,2020\n2020-01-16,255,4,16,2020\n2020-01-17,247,5,17,2020\n2020-01-18,117,6,18,2020\n2020-01-19,187,7,19,2020\n2020-01-20,138,1,20,2020\n2020-01-21,139,2,21,2020\n2020-01-22,199,3,22,2020\n2020-01-23,185,4,23,2020\n2020-01-24,143,5,24,2020\n2020-01-25,64,6,25,2020\n2020-01-26,89,7,26,2020\n2020-01-27,135,1,27,2020\n2020-01-28,101,2,28,2020\n2020-01-29,114,3,29,2020\n2020-01-30,155,4,30,2020\n2020-01-31,165,5,31,2020\n2020-02-01,89,6,32,2020\n2020-02-02,111,7,33,2020\n2020-02-03,141,1,34,2020\n2020-02-04,120,2,35,2020\n2020-02-05,145,3,36,2020\n2020-02-06,133,4,37,2020\n2020-02-07,149,5,38,2020\n2020-02-08,137,6,39,2020\n2020-02-09,119,7,40,2020\n2020-02-10,152,1,41,2020\n2020-02-11,162,2,42,2020\n2020-02-12,134,3,43,2020\n2020-02-13,170,4,44,2020\n2020-02-14,149,5,45,2020\n2020-02-15,95,6,46,2020\n2020-02-16,66,7,47,2020\n2020-02-17,129,1,48,2020\n2020-02-18,175,2,49,2020\n2020-02-19,133,3,50,2020\n2020-02-20,128,4,51,2020\n2020-02-21,133,5,52,2020\n2020-02-22,99,6,53,2020\n2020-02-23,165,7,54,2020\n2020-02-24,153,1,55,2020\n2020-02-25,146,2,56,2020\n2020-02-26,155,3,57,2020\n2020-02-27,144,4,58,2020\n2020-02-28,115,5,59,2020\n2020-02-29,54,6,60,2020\n2020-03-01,56,7,61,2020\n2020-03-02,166,1,62,2020\n2020-03-03,142,2,63,2020\n2020-03-04,120,3,64,2020\n2020-03-05,148,4,65,2020\n2020-03-06,119,5,66,2020\n2020-03-07,92,6,67,2020\n2020-03-08,143,7,68,2020\n2020-03-09,112,1,69,2020\n2020-03-10,111,2,70,2020\n2020-03-11,110,3,71,2020\n2020-03-12,82,4,72,2020\n2020-03-13,76,5,73,2020\n2020-03-14,74,6,74,2020\n2020-03-15,80,7,75,2020\n2020-03-16,91,1,76,2020\n2020-03-17,106,2,77,2020\n2020-03-18,132,3,78,2020\n2020-03-19,92,4,79,2020\n2020-03-20,115,5,80,2020\n2020-03-21,89,6,81,2020\n2020-03-22,105,7,82,2020\n2020-03-23,138,1,83,2020\n2020-03-24,144,2,84,2020\n2020-03-25,116,3,85,2020\n2020-03-26,99,4,86,2020\n2020-03-27,112,5,87,2020\n2020-03-28,123,6,88,2020\n2020-03-29,76,7,89,2020\n2020-03-30,107,1,90,2020\n2020-03-31,177,2,91,2020\n2020-04-01,158,3,92,2020\n2020-04-02,160,4,93,2020\n2020-04-03,145,5,94,2020\n2020-04-04,130,6,95,2020\n2020-04-05,95,7,96,2020\n2020-04-06,152,1,97,2020\n2020-04-07,157,2,98,2020\n2020-04-08,217,3,99,2020\n2020-04-09,160,4,100,2020\n2020-04-10,151,5,101,2020\n2020-04-11,127,6,102,2020\n2020-04-12,106,7,103,2020\n2020-04-13,208,1,104,2020\n2020-04-14,175,2,105,2020\n2020-04-15,146,3,106,2020\n2020-04-16,149,4,107,2020\n2020-04-17,110,5,108,2020\n2020-04-18,148,6,109,2020\n2020-04-19,151,7,110,2020\n2020-04-20,155,1,111,2020\n2020-04-21,141,2,112,2020\n2020-04-22,147,3,113,2020\n2020-04-23,146,4,114,2020\n2020-04-24,136,5,115,2020\n2020-04-25,98,6,116,2020\n2020-04-26,139,7,117,2020\n2020-04-27,180,1,118,2020\n2020-04-28,118,2,119,2020\n2020-04-29,166,3,120,2020\n2020-04-30,220,4,121,2020\n2020-05-01,237,5,122,2020\n2020-05-02,133,6,123,2020\n2020-05-03,142,7,124,2020\n2020-05-04,132,1,125,2020\n2020-05-05,218,2,126,2020\n2020-05-06,229,3,127,2020\n2020-05-07,184,4,128,2020\n2020-05-08,160,5,129,2020\n2020-05-09,152,6,130,2020\n2020-05-10,160,7,131,2020\n2020-05-11,187,1,132,2020\n2020-05-12,158,2,133,2020\n2020-05-13,200,3,134,2020\n2020-05-14,212,4,135,2020\n2020-05-15,199,5,136,2020\n2020-05-16,113,6,137,2020\n2020-05-17,142,7,138,2020\n2020-05-18,161,1,139,2020\n2020-05-19,162,2,140,2020\n2020-05-20,186,3,141,2020\n2020-05-21,122,4,142,2020\n2020-05-22,142,5,143,2020\n2020-05-23,128,6,144,2020\n2020-05-24,134,7,145,2020\n2020-05-25,143,1,146,2020\n2020-05-26,220,2,147,2020\n2020-05-27,144,3,148,2020\n2020-05-28,100,4,149,2020\n2020-05-29,108,5,150,2020\n2020-05-30,213,6,151,2020\n2020-05-31,86,7,152,2020\n2020-06-01,115,1,153,2020\n2020-06-02,107,2,154,2020\n2020-06-03,169,3,155,2020\n2020-06-04,147,4,156,2020\n2020-06-05,115,5,157,2020\n2020-06-06,107,6,158,2020\n2020-06-07,93,7,159,2020\n2020-06-08,116,1,160,2020\n2020-06-09,143,2,161,2020\n2020-06-10,84,3,162,2020\n2020-06-11,177,4,163,2020\n2020-06-12,125,5,164,2020\n2020-06-13,61,6,165,2020\n2020-06-14,98,7,166,2020\n2020-06-15,191,1,167,2020\n2020-06-16,157,2,168,2020\n2020-06-17,199,3,169,2020\n2020-06-18,192,4,170,2020\n2020-06-19,146,5,171,2020\n2020-06-20,60,6,172,2020\n2020-06-21,116,7,173,2020\n2020-06-22,128,1,174,2020\n2020-06-23,130,2,175,2020\n2020-06-24,160,3,176,2020\n2020-06-25,120,4,177,2020\n2020-06-26,167,5,178,2020\n2020-06-27,164,6,179,2020\n2020-06-28,113,7,180,2020\n2020-06-29,167,1,181,2020\n2020-06-30,155,2,182,2020\n2020-07-01,126,3,183,2020\n2020-07-02,134,4,184,2020\n2020-07-03,146,5,185,2020\n2020-07-04,59,6,186,2020\n2020-07-05,102,7,187,2020\n2020-07-06,120,1,188,2020\n2020-07-07,124,2,189,2020\n2020-07-08,154,3,190,2020\n2020-07-09,164,4,191,2020\n2020-07-10,171,5,192,2020\n2020-07-11,79,6,193,2020\n2020-07-12,63,7,194,2020\n2020-07-13,85,1,195,2020\n2020-07-14,90,2,196,2020\n2020-07-15,129,3,197,2020\n2020-07-16,138,4,198,2020\n2020-07-17,95,5,199,2020\n2020-07-18,71,6,200,2020\n2020-07-19,99,7,201,2020\n2020-07-20,140,1,202,2020\n2020-07-21,189,2,203,2020\n2020-07-22,212,3,204,2020\n2020-07-23,176,4,205,2020\n2020-07-24,183,5,206,2020\n2020-07-25,55,6,207,2020\n2020-07-26,100,7,208,2020\n2020-07-27,137,1,209,2020\n2020-07-28,190,2,210,2020\n2020-07-29,118,3,211,2020\n2020-07-30,147,4,212,2020\n2020-07-31,139,5,213,2020\n2020-08-01,91,6,214,2020\n2020-08-02,99,7,215,2020\n2020-08-03,168,1,216,2020\n2020-08-04,168,2,217,2020\n2020-08-05,151,3,218,2020\n2020-08-06,167,4,219,2020\n2020-08-07,155,5,220,2020\n2020-08-08,78,6,221,2020\n2020-08-09,111,7,222,2020\n2020-08-10,126,1,223,2020\n2020-08-11,111,2,224,2020\n2020-08-12,121,3,225,2020\n2020-08-13,97,4,226,2020\n2020-08-14,137,5,227,2020\n2020-08-15,54,6,228,2020\n2020-08-16,56,7,229,2020\n2020-08-17,162,1,230,2020\n2020-08-18,98,2,231,2020\n2020-08-19,139,3,232,2020\n2020-08-20,128,4,233,2020\n2020-08-21,133,5,234,2020\n2020-08-22,93,6,235,2020\n2020-08-23,68,7,236,2020\n2020-08-24,149,1,237,2020\n2020-08-25,165,2,238,2020\n2020-08-26,201,3,239,2020\n2020-08-27,135,4,240,2020\n2020-08-28,108,5,241,2020\n2020-08-29,84,6,242,2020\n2020-08-30,42,7,243,2020\n2020-08-31,100,1,244,2020\n2020-09-01,134,2,245,2020\n2020-09-02,120,3,246,2020\n2020-09-03,100,4,247,2020\n2020-09-04,110,5,248,2020\n2020-09-05,53,6,249,2020\n2020-09-06,62,7,250,2020\n2020-09-07,129,1,251,2020\n2020-09-08,153,2,252,2020\n2020-09-09,148,3,253,2020\n2020-09-10,141,4,254,2020\n2020-09-11,162,5,255,2020\n2020-09-12,78,6,256,2020\n2020-09-13,58,7,257,2020\n2020-09-14,133,1,258,2020\n2020-09-15,126,2,259,2020\n2020-09-16,134,3,260,2020\n2020-09-17,94,4,261,2020\n2020-09-18,102,5,262,2020\n2020-09-19,65,6,263,2020\n2020-09-20,86,7,264,2020\n2020-09-21,136,1,265,2020\n2020-09-22,144,2,266,2020\n2020-09-23,137,3,267,2020\n2020-09-24,146,4,268,2020\n2020-09-25,148,5,269,2020\n2020-09-26,78,6,270,2020\n2020-09-27,82,7,271,2020\n2020-09-28,158,1,272,2020\n2020-09-29,122,2,273,2020\n2020-09-30,108,3,274,2020\n2020-10-01,146,4,275,2020\n2020-10-02,125,5,276,2020\n2020-10-03,55,6,277,2020\n2020-10-04,62,7,278,2020\n2020-10-05,99,1,279,2020\n2020-10-06,95,2,280,2020\n2020-10-07,137,3,281,2020\n2020-10-08,125,4,282,2020\n2020-10-09,117,5,283,2020\n2020-10-10,67,6,284,2020\n2020-10-11,62,7,285,2020\n2020-10-12,133,1,286,2020\n2020-10-13,80,2,287,2020\n2020-10-14,115,3,288,2020\n2020-10-15,104,4,289,2020\n2020-10-16,122,5,290,2020\n2020-10-17,106,6,291,2020\n2020-10-18,86,7,292,2020\n2020-10-19,156,1,293,2020\n2020-10-20,156,2,294,2020\n2020-10-21,162,3,295,2020\n2020-10-22,180,4,296,2020\n2020-10-23,93,5,297,2020\n2020-10-24,81,6,298,2020\n2020-10-25,75,7,299,2020\n2020-10-26,125,1,300,2020\n2020-10-27,130,2,301,2020\n2020-10-28,147,3,302,2020\n2020-10-29,118,4,303,2020\n2020-10-30,99,5,304,2020\n2020-10-31,93,6,305,2020\n2020-11-01,103,7,306,2020\n2020-11-02,103,1,307,2020\n2020-11-03,121,2,308,2020\n2020-11-04,86,3,309,2020\n2020-11-05,153,4,310,2020\n2020-11-06,129,5,311,2020\n2020-11-07,116,6,312,2020\n2020-11-08,51,7,313,2020\n2020-11-09,129,1,314,2020\n2020-11-10,150,2,315,2020\n2020-11-11,112,3,316,2020\n2020-11-12,117,4,317,2020\n2020-11-13,161,5,318,2020\n2020-11-14,69,6,319,2020\n2020-11-15,95,7,320,2020\n2020-11-16,144,1,321,2020\n2020-11-17,155,2,322,2020\n2020-11-18,142,3,323,2020\n2020-11-19,119,4,324,2020\n2020-11-20,113,5,325,2020\n2020-11-21,77,6,326,2020\n2020-11-22,69,7,327,2020\n2020-11-23,97,1,328,2020\n2020-11-24,107,2,329,2020\n2020-11-25,122,3,330,2020\n2020-11-26,131,4,331,2020\n2020-11-27,120,5,332,2020\n2020-11-28,93,6,333,2020\n2020-11-29,116,7,334,2020\n2020-11-30,139,1,335,2020\n2020-12-01,89,2,336,2020\n2020-12-02,152,3,337,2020\n2020-12-03,130,4,338,2020\n2020-12-04,128,5,339,2020\n2020-12-05,112,6,340,2020\n2020-12-06,69,7,341,2020\n2020-12-07,153,1,342,2020\n2020-12-08,110,2,343,2020\n2020-12-09,122,3,344,2020\n2020-12-10,124,4,345,2020\n2020-12-11,107,5,346,2020\n2020-12-12,78,6,347,2020\n2020-12-13,90,7,348,2020\n2020-12-14,87,1,349,2020\n2020-12-15,125,2,350,2020\n2020-12-16,143,3,351,2020\n2020-12-17,114,4,352,2020\n2020-12-18,96,5,353,2020\n2020-12-19,55,6,354,2020\n2020-12-20,66,7,355,2020\n2020-12-21,150,1,356,2020\n2020-12-22,129,2,357,2020\n2020-12-23,134,3,358,2020\n2020-12-24,70,4,359,2020\n2020-12-25,38,5,360,2020\n2020-12-26,68,6,361,2020\n2020-12-27,93,7,362,2020\n2020-12-28,116,1,363,2020\n2020-12-29,151,2,364,2020\n2020-12-30,114,3,365,2020\n2020-12-31,53,4,366,2020\n","format":{"type":"csv"}}});</script></div>

<div class="sourceClojure">
```clojure
(defn plot-average-by-temporal-field [tf template]
  (-> date-counts
      (tc/add-column tf (fn [ds]
                          (->> ds
                               :date
                               (datetime/long-temporal-field tf))))
      (tc/group-by [tf])
      (tc/aggregate {:n (fn [ds]
                          (-> ds
                              :n
                              fun/mean))})
      (tc/order-by [tf])
      (vis/hanami-plot template
                       {:X tf
                        :Y "n"})))
```
</div>

<div class="sourceClojure">
```clojure
(plot-average-by-temporal-field :day-of-week
                                ht/bar-chart)
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"day-of-week","type":"quantitative"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"values":"day-of-week,n\n1,113.39775561097257\n2,117.70931677018633\n3,119.55569306930693\n4,114.44389642416769\n5,112.25990099009901\n6,75.59062885326757\n7,77.97775030902349\n","format":{"type":"csv"}}});</script></div>

<div class="sourceClojure">
```clojure
(plot-average-by-temporal-field :day-of-year
                                ht/line-chart)
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"day-of-year","type":"quantitative"}},"mark":{"type":"line","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"values":"day-of-year,n\n1,58.8\n2,92.2\n3,95.53333333333333\n4,112.8\n5,96.13333333333334\n6,104.06666666666666\n7,112.86666666666666\n8,124.06666666666666\n9,119.6\n10,135.4\n11,129.4\n12,118.13333333333334\n13,136.2\n14,112.8\n15,119.33333333333333\n16,121.06666666666666\n17,125.46666666666667\n18,112.33333333333333\n19,126.0\n20,111.46666666666667\n21,109.06666666666666\n22,117.53333333333333\n23,123.6\n24,115.0\n25,112.46666666666667\n26,113.93333333333334\n27,107.6\n28,104.93333333333334\n29,112.26666666666667\n30,113.2\n31,116.46666666666667\n32,109.26666666666667\n33,120.33333333333333\n34,105.4\n35,104.66666666666667\n36,116.46666666666667\n37,120.86666666666666\n38,107.8\n39,116.46666666666667\n40,127.78571428571429\n41,121.6\n42,113.2\n43,111.26666666666667\n44,111.86666666666666\n45,106.33333333333333\n46,117.26666666666667\n47,110.33333333333333\n48,119.26666666666667\n49,128.26666666666668\n50,117.6\n51,114.4\n52,130.93333333333334\n53,122.0\n54,119.86666666666666\n55,125.46666666666667\n56,127.53333333333333\n57,110.93333333333334\n58,109.33333333333333\n59,120.2\n60,105.26666666666667\n61,103.93333333333334\n62,113.86666666666666\n63,104.33333333333333\n64,110.46666666666667\n65,113.2\n66,101.26666666666667\n67,103.53333333333333\n68,118.53333333333333\n69,118.53333333333333\n70,105.53333333333333\n71,101.73333333333333\n72,99.46666666666667\n73,110.13333333333334\n74,102.86666666666666\n75,107.53333333333333\n76,115.73333333333333\n77,104.33333333333333\n78,106.0\n79,104.66666666666667\n80,113.06666666666666\n81,113.26666666666667\n82,114.26666666666667\n83,124.33333333333333\n84,111.13333333333334\n85,124.6\n86,112.26666666666667\n87,109.66666666666667\n88,113.8\n89,108.1875\n90,111.4\n91,109.93333333333334\n92,114.53333333333333\n93,107.9375\n94,104.25\n95,117.86666666666666\n96,104.8125\n97,105.125\n98,111.875\n99,107.5\n100,117.2\n101,96.0625\n102,117.875\n103,111.4\n104,114.0\n105,114.33333333333333\n106,105.13333333333334\n107,101.3125\n108,106.26666666666667\n109,109.3125\n110,95.4375\n111,119.8\n112,99.8125\n113,102.33333333333333\n114,116.53333333333333\n115,101.1875\n116,107.4375\n117,106.13333333333334\n118,116.73333333333333\n119,113.6\n120,102.875\n121,104.5625\n122,106.5\n123,103.9375\n124,98.25\n125,109.93333333333334\n126,107.33333333333333\n127,111.93333333333334\n128,117.875\n129,99.9375\n130,116.2\n131,109.125\n132,106.4375\n133,95.3125\n134,109.3125\n135,96.1875\n136,98.1875\n137,106.3125\n138,106.0\n139,102.875\n140,107.53333333333333\n141,111.46666666666667\n142,109.33333333333333\n143,100.9375\n144,106.0\n145,96.75\n146,96.125\n147,98.0\n148,95.375\n149,85.1875\n150,96.8125\n151,112.86666666666666\n152,110.625\n153,105.875\n154,92.0625\n155,97.9375\n156,95.25\n157,92.8125\n158,103.3125\n159,103.875\n160,108.875\n161,107.4375\n162,95.0\n163,111.5625\n164,96.875\n165,111.125\n166,95.125\n167,116.3125\n168,120.33333333333333\n169,103.93333333333334\n170,99.5\n171,96.5625\n172,101.73333333333333\n173,110.0\n174,108.06666666666666\n175,103.53333333333333\n176,98.06666666666666\n177,102.73333333333333\n178,105.0\n179,105.9375\n180,94.1875\n181,104.5\n182,108.75\n183,104.2\n184,93.53333333333333\n185,80.1875\n186,88.0625\n187,104.26666666666667\n188,104.0\n189,95.125\n190,89.4375\n191,97.8125\n192,105.25\n193,98.875\n194,103.125\n195,97.25\n196,100.0625\n197,109.4375\n198,102.66666666666667\n199,115.06666666666666\n200,103.73333333333333\n201,117.26666666666667\n202,109.6\n203,109.26666666666667\n204,101.5\n205,110.8\n206,93.5625\n207,96.25\n208,99.6875\n209,105.0625\n210,111.6\n211,100.1875\n212,99.46666666666667\n213,115.2\n214,103.26666666666667\n215,107.53333333333333\n216,102.06666666666666\n217,118.4\n218,100.625\n219,102.0\n220,94.3125\n221,92.1875\n222,98.9375\n223,105.3125\n224,97.6875\n225,95.125\n226,94.5625\n227,89.125\n228,102.9375\n229,91.75\n230,98.4375\n231,105.53333333333333\n232,90.8125\n233,98.0\n234,90.75\n235,108.93333333333334\n236,107.6\n237,109.8\n238,104.875\n239,105.46666666666667\n240,101.625\n241,87.625\n242,97.9375\n243,99.6875\n244,112.33333333333333\n245,108.0\n246,90.3125\n247,87.75\n248,95.75\n249,85.6875\n250,107.4375\n251,99.0\n252,108.125\n253,98.125\n254,91.8125\n255,89.0\n256,94.375\n257,92.625\n258,100.4375\n259,96.5\n260,93.6875\n261,94.1875\n262,100.5625\n263,100.25\n264,99.75\n265,89.75\n266,99.4375\n267,109.33333333333333\n268,96.6875\n269,99.4375\n270,107.625\n271,116.3125\n272,113.25\n273,112.13333333333334\n274,112.8\n275,105.125\n276,107.125\n277,94.5\n278,96.125\n279,110.4375\n280,97.5625\n281,102.5\n282,111.6875\n283,98.0\n284,103.25\n285,100.46666666666667\n286,108.8125\n287,94.1875\n288,98.1875\n289,99.875\n290,96.625\n291,105.375\n292,106.9375\n293,103.06666666666666\n294,108.8\n295,86.3125\n296,89.875\n297,95.3125\n298,102.06666666666666\n299,88.25\n300,97.8125\n301,91.375\n302,98.75\n303,104.75\n304,102.125\n305,99.5625\n306,107.375\n307,101.1875\n308,111.875\n309,109.73333333333333\n310,112.06666666666666\n311,102.4\n312,112.8\n313,101.1875\n314,107.25\n315,122.13333333333334\n316,91.0625\n317,103.6875\n318,106.5625\n319,100.625\n320,111.0625\n321,112.6875\n322,104.0\n323,106.3125\n324,103.8125\n325,100.0\n326,99.25\n327,91.5625\n328,95.3125\n329,91.25\n330,80.9375\n331,89.25\n332,89.5\n333,97.75\n334,108.75\n335,104.75\n336,95.0625\n337,93.3125\n338,91.46666666666667\n339,107.93333333333334\n340,125.6\n341,110.64285714285714\n342,105.8\n343,105.06666666666666\n344,104.2\n345,98.0\n346,106.86666666666666\n347,105.53333333333333\n348,103.8\n349,108.8\n350,107.6\n351,105.26666666666667\n352,98.8\n353,110.78571428571429\n354,103.86666666666666\n355,99.2\n356,97.06666666666666\n357,80.0\n358,66.13333333333334\n359,40.46666666666667\n360,51.0\n361,82.26666666666667\n362,83.4\n363,84.2\n364,101.8\n365,77.26666666666667\n366,47.0\n","format":{"type":"csv"}}});</script></div>

<div class="sourceClojure">
```clojure
(-> processed-date-counts
    (tc/add-column :smoothed-n
                   (fn [ds]
                     (-> ds
                         :n
                         (rolling/fixed-rolling-window
                          30
                          fun/mean
                          {:relative-window-position :left}))))
    (vis/hanami-layers {}
                       [(vis/hanami-plot nil
                                         ht/line-chart
                                         {:X "date"
                                          :XTYPE "temporal"
                                          :Y "n"})
                        (vis/hanami-plot nil
                                         ht/line-chart
                                         {:X "date"
                                          :XTYPE "temporal"
                                          :Y "smoothed-n"
                                          :MCOLOR "brown"})]))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","layer":[{"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"date","type":"temporal"}},"mark":{"type":"line","tooltip":true},"width":400,"background":"floralwhite","height":300},{"encoding":{"y":{"field":"smoothed-n","type":"quantitative"},"x":{"field":"date","type":"temporal"}},"mark":{"type":"line","color":"brown","tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300,"data":{"values":"date,n,day-of-week,day-of-year,years,smoothed-n\n2008-03-29,7,6,89,2008,7.0\n2008-04-02,4,3,93,2008,6.9\n2008-04-03,9,4,94,2008,6.966666666666667\n2008-04-05,2,6,96,2008,6.8\n2008-04-06,1,7,97,2008,6.6\n2008-04-07,5,1,98,2008,6.533333333333333\n2008-04-08,9,2,99,2008,6.6\n2008-04-10,1,4,101,2008,6.4\n2008-04-11,1,5,102,2008,6.2\n2008-04-16,1,3,107,2008,6.0\n2008-04-18,1,5,109,2008,5.8\n2008-04-19,1,6,110,2008,5.6\n2008-04-21,1,1,112,2008,5.4\n2008-04-24,3,4,115,2008,5.266666666666667\n2008-04-25,1,5,116,2008,5.066666666666666\n2008-04-29,1,2,120,2008,4.866666666666666\n2008-04-30,4,3,121,2008,4.766666666666667\n2008-05-01,1,4,122,2008,4.566666666666666\n2008-05-02,2,5,123,2008,4.4\n2008-05-03,2,6,124,2008,4.233333333333333\n2008-05-07,3,3,128,2008,4.1\n2008-05-08,2,4,129,2008,3.933333333333333\n2008-05-10,6,6,131,2008,3.9\n2008-05-11,1,7,132,2008,3.7\n2008-05-12,1,1,133,2008,3.5\n2008-05-13,2,2,134,2008,3.3333333333333335\n2008-05-14,1,3,135,2008,3.1333333333333333\n2008-05-15,1,4,136,2008,2.933333333333333\n2008-05-16,2,5,137,2008,2.7666666666666666\n2008-05-17,9,6,138,2008,2.8333333333333335\n2008-05-18,12,7,139,2008,3.0\n2008-05-22,1,4,143,2008,2.9\n2008-05-24,3,6,145,2008,2.7\n2008-05-25,2,7,146,2008,2.7\n2008-05-26,1,1,147,2008,2.7\n2008-05-27,1,2,148,2008,2.566666666666667\n2008-05-28,1,3,149,2008,2.3\n2008-05-29,4,4,150,2008,2.4\n2008-05-31,1,6,152,2008,2.4\n2008-06-01,2,7,153,2008,2.433333333333333\n2008-06-02,1,1,154,2008,2.433333333333333\n2008-06-03,3,2,155,2008,2.5\n2008-06-04,2,3,156,2008,2.533333333333333\n2008-06-05,1,4,157,2008,2.466666666666667\n2008-06-06,1,5,158,2008,2.466666666666667\n2008-06-07,1,6,159,2008,2.466666666666667\n2008-06-08,5,7,160,2008,2.5\n2008-06-09,3,1,161,2008,2.566666666666667\n2008-06-11,2,3,163,2008,2.566666666666667\n2008-06-12,2,4,164,2008,2.566666666666667\n2008-06-13,2,5,165,2008,2.533333333333333\n2008-06-14,4,6,166,2008,2.6\n2008-06-15,5,7,167,2008,2.566666666666667\n2008-06-18,1,3,170,2008,2.566666666666667\n2008-06-19,3,4,171,2008,2.6333333333333333\n2008-06-27,1,5,179,2008,2.6\n2008-06-28,6,6,180,2008,2.7666666666666666\n2008-06-29,6,7,181,2008,2.933333333333333\n2008-06-30,2,1,182,2008,2.933333333333333\n2008-07-03,2,4,185,2008,2.7\n2008-07-04,1,5,186,2008,2.3333333333333335\n2008-07-06,5,7,188,2008,2.466666666666667\n2008-07-07,2,1,189,2008,2.433333333333333\n2008-07-08,1,2,190,2008,2.4\n2008-07-09,8,3,191,2008,2.6333333333333333\n2008-07-10,5,4,192,2008,2.7666666666666666\n2008-07-11,6,5,193,2008,2.933333333333333\n2008-07-12,4,6,194,2008,2.933333333333333\n2008-07-13,3,7,195,2008,3.0\n2008-07-14,1,1,196,2008,2.966666666666667\n2008-07-15,5,2,197,2008,3.1\n2008-07-21,1,1,203,2008,3.033333333333333\n2008-07-22,5,2,204,2008,3.1333333333333333\n2008-07-24,2,4,206,2008,3.1666666666666665\n2008-07-25,2,5,207,2008,3.2\n2008-07-26,7,6,208,2008,3.4\n2008-07-27,3,7,209,2008,3.3333333333333335\n2008-07-29,8,2,211,2008,3.5\n2008-08-05,1,2,218,2008,3.466666666666667\n2008-08-06,4,3,219,2008,3.533333333333333\n2008-08-07,7,4,220,2008,3.7\n2008-08-08,1,5,221,2008,3.6\n2008-08-09,1,6,222,2008,3.466666666666667\n2008-08-10,1,7,223,2008,3.466666666666667\n2008-08-11,1,1,224,2008,3.4\n2008-08-12,4,2,225,2008,3.5\n2008-08-13,1,3,226,2008,3.3333333333333335\n2008-08-14,1,4,227,2008,3.1666666666666665\n2008-08-15,3,5,228,2008,3.2\n2008-08-16,9,6,229,2008,3.433333333333333\n2008-08-17,4,7,230,2008,3.533333333333333\n2008-08-19,7,2,232,2008,3.6\n2008-08-20,3,3,233,2008,3.6333333333333333\n2008-08-21,1,4,234,2008,3.6333333333333333\n2008-08-25,2,1,238,2008,3.433333333333333\n2008-08-27,2,3,240,2008,3.3333333333333335\n2008-08-28,2,4,241,2008,3.2\n2008-08-29,5,5,242,2008,3.2333333333333334\n2008-08-30,8,6,243,2008,3.4\n2008-09-02,8,2,246,2008,3.6333333333333333\n2008-09-03,7,3,247,2008,3.7\n2008-09-04,1,4,248,2008,3.7\n2008-09-05,1,5,249,2008,3.566666666666667\n2008-09-06,2,6,250,2008,3.566666666666667\n2008-09-07,3,7,251,2008,3.6\n2008-09-08,29,1,252,2008,4.333333333333333\n2008-09-09,4,2,253,2008,4.366666666666666\n2008-09-10,3,3,254,2008,4.2\n2008-09-11,2,4,255,2008,4.233333333333333\n2008-09-12,3,5,256,2008,4.2\n2008-09-13,11,6,257,2008,4.333333333333333\n2008-09-14,2,7,258,2008,4.366666666666666\n2008-09-15,8,1,259,2008,4.6\n2008-09-16,11,2,260,2008,4.933333333333334\n2008-09-17,8,3,261,2008,5.166666666666667\n2008-09-18,1,4,262,2008,5.066666666666666\n2008-09-19,2,5,263,2008,5.1\n2008-09-20,8,6,264,2008,5.333333333333333\n2008-09-21,7,7,265,2008,5.466666666666667\n2008-09-22,3,1,266,2008,5.266666666666667\n2008-09-23,4,2,267,2008,5.266666666666667\n2008-09-24,4,3,268,2008,5.166666666666667\n2008-09-25,6,4,269,2008,5.266666666666667\n2008-09-26,4,5,270,2008,5.366666666666666\n2008-09-27,2,6,271,2008,5.366666666666666\n2008-09-28,7,7,272,2008,5.533333333333333\n2008-10-01,6,3,275,2008,5.666666666666667\n2008-10-02,10,4,276,2008,5.833333333333333\n2008-10-03,5,5,277,2008,5.733333333333333\n2008-10-04,3,6,278,2008,5.566666666666666\n2008-10-05,5,7,279,2008,5.5\n2008-10-06,11,1,280,2008,5.833333333333333\n2008-10-07,2,2,281,2008,5.866666666666666\n2008-10-08,6,3,282,2008,6.0\n2008-10-09,3,4,283,2008,6.0\n2008-10-10,4,5,284,2008,5.166666666666667\n2008-10-11,2,6,285,2008,5.1\n2008-10-12,4,7,286,2008,5.133333333333334\n2008-10-13,2,1,287,2008,5.133333333333334\n2008-10-14,1,2,288,2008,5.066666666666666\n2008-10-15,10,3,289,2008,5.033333333333333\n2008-10-16,1,4,290,2008,5.0\n2008-10-17,4,5,291,2008,4.866666666666666\n2008-10-18,2,6,292,2008,4.566666666666666\n2008-10-19,8,7,293,2008,4.566666666666666\n2008-10-21,1,2,295,2008,4.566666666666666\n2008-10-22,5,3,296,2008,4.666666666666667\n2008-10-23,4,4,297,2008,4.533333333333333\n2008-10-25,2,6,299,2008,4.366666666666666\n2008-10-26,3,7,300,2008,4.366666666666666\n2008-10-27,1,1,301,2008,4.266666666666667\n2008-10-28,2,2,302,2008,4.2\n2008-10-29,1,3,303,2008,4.033333333333333\n2008-10-30,5,4,304,2008,4.066666666666666\n2008-10-31,5,5,305,2008,4.166666666666667\n2008-11-01,9,6,306,2008,4.233333333333333\n2008-11-02,1,7,307,2008,4.066666666666666\n2008-11-03,7,1,308,2008,3.966666666666667\n2008-11-08,3,6,313,2008,3.9\n2008-11-09,5,7,314,2008,3.966666666666667\n2008-11-11,1,2,316,2008,3.8333333333333335\n2008-11-12,5,3,317,2008,3.6333333333333333\n2008-11-13,23,4,318,2008,4.333333333333333\n2008-11-14,2,5,319,2008,4.2\n2008-11-15,8,6,320,2008,4.366666666666666\n2008-11-16,17,7,321,2008,4.8\n2008-11-17,3,1,322,2008,4.833333333333333\n2008-11-18,25,2,323,2008,5.533333333333333\n2008-11-19,3,3,324,2008,5.566666666666666\n2008-11-20,2,4,325,2008,5.6\n2008-11-21,3,5,326,2008,5.366666666666666\n2008-11-22,3,6,327,2008,5.433333333333334\n2008-11-23,7,7,328,2008,5.533333333333333\n2008-11-24,1,1,329,2008,5.5\n2008-11-25,6,2,330,2008,5.433333333333334\n2008-11-26,3,3,331,2008,5.5\n2008-11-27,3,4,332,2008,5.433333333333334\n2008-11-28,5,5,333,2008,5.466666666666667\n2008-11-29,5,6,334,2008,5.566666666666666\n2008-11-30,5,7,335,2008,5.633333333333334\n2008-12-01,7,1,336,2008,5.833333333333333\n2008-12-02,3,2,337,2008,5.866666666666666\n2008-12-03,7,3,338,2008,6.066666666666666\n2008-12-04,5,4,339,2008,6.066666666666666\n2008-12-05,6,5,340,2008,6.1\n2008-12-07,3,7,342,2008,5.9\n2008-12-08,4,1,343,2008,6.0\n2008-12-09,1,2,344,2008,5.8\n2008-12-10,6,3,345,2008,5.9\n2008-12-11,5,4,346,2008,5.9\n2008-12-12,1,5,347,2008,5.9\n2008-12-13,12,6,348,2008,6.133333333333334\n2008-12-14,8,7,349,2008,5.633333333333334\n2008-12-15,9,1,350,2008,5.866666666666666\n2008-12-16,6,2,351,2008,5.8\n2008-12-17,6,3,352,2008,5.433333333333334\n2008-12-19,18,5,354,2008,5.933333333333334\n2008-12-20,1,6,355,2008,5.133333333333334\n2008-12-21,3,7,356,2008,5.133333333333334\n2008-12-22,3,1,357,2008,5.166666666666667\n2008-12-23,10,2,358,2008,5.4\n2008-12-24,3,3,359,2008,5.4\n2008-12-25,1,4,360,2008,5.2\n2008-12-26,1,5,361,2008,5.2\n2008-12-27,13,6,362,2008,5.433333333333334\n2008-12-28,13,7,363,2008,5.766666666666667\n2008-12-29,15,1,364,2008,6.166666666666667\n2008-12-30,10,2,365,2008,6.333333333333333\n2008-12-31,2,3,366,2008,6.233333333333333\n2009-01-01,4,4,1,2009,6.2\n2009-01-02,5,5,2,2009,6.133333333333334\n2009-01-03,2,6,3,2009,6.1\n2009-01-04,14,7,4,2009,6.333333333333333\n2009-01-05,3,1,5,2009,6.266666666666667\n2009-01-06,7,2,6,2009,6.3\n2009-01-07,1,3,7,2009,6.233333333333333\n2009-01-08,17,4,8,2009,6.666666666666667\n2009-01-09,4,5,9,2009,6.766666666666667\n2009-01-10,3,6,10,2009,6.666666666666667\n2009-01-11,9,7,11,2009,6.8\n2009-01-12,19,1,12,2009,7.4\n2009-01-13,5,2,13,2009,7.166666666666667\n2009-01-14,4,3,14,2009,7.033333333333333\n2009-01-15,11,4,15,2009,7.1\n2009-01-16,10,5,16,2009,7.233333333333333\n2009-01-17,36,6,17,2009,8.233333333333333\n2009-01-18,36,7,18,2009,8.833333333333334\n2009-01-19,22,1,19,2009,9.533333333333333\n2009-01-20,12,2,20,2009,9.833333333333334\n2009-01-21,16,3,21,2009,10.266666666666667\n2009-01-22,8,4,22,2009,10.2\n2009-01-23,13,5,23,2009,10.533333333333333\n2009-01-24,7,6,24,2009,10.733333333333333\n2009-01-25,15,7,25,2009,11.2\n2009-01-26,13,1,26,2009,11.2\n2009-01-27,6,2,27,2009,10.966666666666667\n2009-01-28,5,3,28,2009,10.633333333333333\n2009-01-29,7,4,29,2009,10.533333333333333\n2009-01-30,5,5,30,2009,10.633333333333333\n2009-01-31,2,6,31,2009,10.566666666666666\n2009-02-01,2,7,32,2009,10.466666666666667\n2009-02-02,4,1,33,2009,10.533333333333333\n2009-02-03,1,2,34,2009,10.1\n2009-02-04,3,3,35,2009,10.1\n2009-02-05,1,4,36,2009,9.9\n2009-02-06,8,5,37,2009,10.133333333333333\n2009-02-07,3,6,38,2009,9.666666666666666\n2009-02-08,3,7,39,2009,9.633333333333333\n2009-02-10,22,2,41,2009,10.266666666666667\n2009-02-11,14,3,42,2009,10.433333333333334\n2009-02-12,18,4,43,2009,10.4\n2009-02-13,6,5,44,2009,10.433333333333334\n2009-02-14,5,6,45,2009,10.466666666666667\n2009-02-15,9,7,46,2009,10.4\n2009-02-16,5,1,47,2009,10.233333333333333\n2009-02-17,8,2,48,2009,9.3\n2009-02-18,7,3,49,2009,8.333333333333334\n2009-02-19,4,4,50,2009,7.733333333333333\n2009-02-20,8,5,51,2009,7.6\n2009-02-21,10,6,52,2009,7.4\n2009-02-22,15,7,53,2009,7.633333333333334\n2009-02-23,12,1,54,2009,7.6\n2009-02-24,27,2,55,2009,8.266666666666667\n2009-02-25,7,3,56,2009,8.0\n2009-02-26,11,4,57,2009,7.933333333333334\n2009-02-27,19,5,58,2009,8.366666666666667\n2009-02-28,3,6,59,2009,8.3\n2009-03-01,5,7,60,2009,8.233333333333333\n2009-03-02,3,1,61,2009,8.166666666666666\n2009-03-03,8,2,62,2009,8.366666666666667\n2009-03-04,7,3,63,2009,8.533333333333333\n2009-03-05,2,4,64,2009,8.466666666666667\n2009-03-06,6,5,65,2009,8.633333333333333\n2009-03-07,3,6,66,2009,8.633333333333333\n2009-03-08,2,7,67,2009,8.666666666666666\n2009-03-09,6,1,68,2009,8.6\n2009-03-10,4,2,69,2009,8.633333333333333\n2009-03-11,7,3,70,2009,8.766666666666667\n2009-03-12,13,4,71,2009,8.466666666666667\n2009-03-13,4,5,72,2009,8.133333333333333\n2009-03-14,8,6,73,2009,7.8\n2009-03-15,7,7,74,2009,7.833333333333333\n2009-03-16,9,1,75,2009,7.966666666666667\n2009-03-17,9,2,76,2009,7.966666666666667\n2009-03-18,11,3,77,2009,8.166666666666666\n2009-03-19,13,4,78,2009,8.333333333333334\n2009-03-20,8,5,79,2009,8.366666666666667\n2009-03-21,13,6,80,2009,8.666666666666666\n2009-03-22,11,7,81,2009,8.766666666666667\n2009-03-23,8,1,82,2009,8.7\n2009-03-24,4,2,83,2009,8.333333333333334\n2009-03-25,4,3,84,2009,8.066666666666666\n2009-03-26,4,4,85,2009,7.3\n2009-03-27,9,5,86,2009,7.366666666666666\n2009-03-28,10,6,87,2009,7.333333333333333\n2009-03-29,17,7,88,2009,7.266666666666667\n2009-03-30,9,1,89,2009,7.466666666666667\n2009-03-31,7,2,90,2009,7.533333333333333\n2009-04-01,8,3,91,2009,7.7\n2009-04-02,1,4,92,2009,7.466666666666667\n2009-04-03,5,5,93,2009,7.4\n2009-04-04,8,6,94,2009,7.6\n2009-04-05,16,7,95,2009,7.933333333333334\n2009-04-06,15,1,96,2009,8.333333333333334\n2009-04-07,5,2,97,2009,8.433333333333334\n2009-04-08,7,3,98,2009,8.466666666666667\n2009-04-09,15,4,99,2009,8.833333333333334\n2009-04-10,5,5,100,2009,8.766666666666667\n2009-04-11,2,6,101,2009,8.4\n2009-04-12,3,7,102,2009,8.366666666666667\n2009-04-13,1,1,103,2009,8.133333333333333\n2009-04-14,9,2,104,2009,8.2\n2009-04-15,17,3,105,2009,8.466666666666667\n2009-04-16,9,4,106,2009,8.466666666666667\n2009-04-17,19,5,107,2009,8.733333333333333\n2009-04-18,8,6,108,2009,8.566666666666666\n2009-04-19,21,7,109,2009,9.0\n2009-04-20,28,1,110,2009,9.5\n2009-04-21,24,2,111,2009,9.933333333333334\n2009-04-22,13,3,112,2009,10.1\n2009-04-23,25,4,113,2009,10.8\n2009-04-24,8,5,114,2009,10.933333333333334\n2009-04-25,8,6,115,2009,11.066666666666666\n2009-04-26,6,7,116,2009,10.966666666666667\n2009-04-27,4,1,117,2009,10.766666666666667\n2009-04-28,2,2,118,2009,10.266666666666667\n2009-04-29,6,3,119,2009,10.166666666666666\n2009-04-30,1,4,120,2009,9.966666666666667\n2009-05-01,8,5,121,2009,9.966666666666667\n2009-05-02,1,6,122,2009,9.966666666666667\n2009-05-03,12,7,123,2009,10.2\n2009-05-04,17,1,124,2009,10.5\n2009-05-05,7,2,125,2009,10.2\n2009-05-06,9,3,126,2009,10.0\n2009-05-07,13,4,127,2009,10.266666666666667\n2009-05-08,4,5,128,2009,10.166666666666666\n2009-05-09,15,6,129,2009,10.166666666666666\n2009-05-10,7,7,130,2009,10.233333333333333\n2009-05-11,13,1,131,2009,10.6\n2009-05-12,3,2,132,2009,10.6\n2009-05-13,2,3,133,2009,10.633333333333333\n2009-05-14,17,4,134,2009,10.9\n2009-05-15,3,5,135,2009,10.433333333333334\n2009-05-16,5,6,136,2009,10.3\n2009-05-17,5,7,137,2009,9.833333333333334\n2009-05-18,6,1,138,2009,9.766666666666667\n2009-05-19,6,2,139,2009,9.266666666666667\n2009-05-20,3,3,140,2009,8.433333333333334\n2009-05-21,5,4,141,2009,7.8\n2009-05-22,2,5,142,2009,7.433333333333334\n2009-05-23,16,6,143,2009,7.133333333333334\n2009-05-24,7,7,144,2009,7.1\n2009-05-25,7,1,145,2009,7.066666666666666\n2009-05-26,4,2,146,2009,7.0\n2009-05-27,7,3,147,2009,7.1\n2009-05-28,3,4,148,2009,7.133333333333334\n2009-05-29,7,5,149,2009,7.166666666666667\n2009-05-30,4,6,150,2009,7.266666666666667\n2009-05-31,19,7,151,2009,7.633333333333334\n2009-06-01,7,1,152,2009,7.833333333333333\n2009-06-02,10,2,153,2009,7.766666666666667\n2009-06-03,13,3,154,2009,7.633333333333334\n2009-06-04,7,4,155,2009,7.633333333333334\n2009-06-05,17,5,156,2009,7.9\n2009-06-06,8,6,157,2009,7.733333333333333\n2009-06-07,1,7,158,2009,7.633333333333334\n2009-06-08,11,1,159,2009,7.5\n2009-06-09,8,2,160,2009,7.533333333333333\n2009-06-10,4,3,161,2009,7.233333333333333\n2009-06-11,7,4,162,2009,7.366666666666666\n2009-06-12,4,5,163,2009,7.433333333333334\n2009-06-13,12,6,164,2009,7.266666666666667\n2009-06-14,4,7,165,2009,7.3\n2009-06-15,3,1,166,2009,7.233333333333333\n2009-06-16,8,2,167,2009,7.333333333333333\n2009-06-17,2,3,168,2009,7.2\n2009-06-18,2,4,169,2009,7.066666666666666\n2009-06-19,18,5,170,2009,7.566666666666666\n2009-06-20,1,6,171,2009,7.433333333333334\n2009-06-21,1,7,172,2009,7.4\n2009-06-22,9,1,173,2009,7.166666666666667\n2009-06-23,13,2,174,2009,7.366666666666666\n2009-06-24,14,3,175,2009,7.6\n2009-06-25,3,4,176,2009,7.566666666666666\n2009-06-26,17,5,177,2009,7.9\n2009-06-27,7,6,178,2009,8.033333333333333\n2009-06-28,10,7,179,2009,8.133333333333333\n2009-06-29,3,1,180,2009,8.1\n2009-06-30,6,2,181,2009,7.666666666666667\n2009-07-01,9,3,182,2009,7.733333333333333\n2009-07-02,17,4,183,2009,7.966666666666667\n2009-07-03,6,5,184,2009,7.733333333333333\n2009-07-04,4,6,185,2009,7.633333333333334\n2009-07-05,6,7,186,2009,7.266666666666667\n2009-07-06,9,1,187,2009,7.3\n2009-07-07,7,2,188,2009,7.5\n2009-07-08,13,3,189,2009,7.566666666666666\n2009-07-09,7,4,190,2009,7.533333333333333\n2009-07-10,6,5,191,2009,7.6\n2009-07-11,2,6,192,2009,7.433333333333334\n2009-07-12,8,7,193,2009,7.566666666666666\n2009-07-13,5,1,194,2009,7.333333333333333\n2009-07-14,7,2,195,2009,7.433333333333334\n2009-07-15,5,3,196,2009,7.5\n2009-07-16,6,4,197,2009,7.433333333333334\n2009-07-17,3,5,198,2009,7.466666666666667\n2009-07-18,5,6,199,2009,7.566666666666666\n2009-07-19,4,7,200,2009,7.1\n2009-07-20,14,1,201,2009,7.533333333333333\n2009-07-21,6,2,202,2009,7.7\n2009-07-23,10,4,204,2009,7.733333333333333\n2009-07-24,11,5,205,2009,7.666666666666667\n2009-07-25,3,6,206,2009,7.3\n2009-07-26,9,7,207,2009,7.5\n2009-07-27,5,1,208,2009,7.1\n2009-07-28,21,2,209,2009,7.566666666666666\n2009-07-29,17,3,210,2009,7.8\n2009-07-30,5,4,211,2009,7.866666666666666\n2009-07-31,6,5,212,2009,7.866666666666666\n2009-08-01,11,6,213,2009,7.933333333333334\n2009-08-02,4,7,214,2009,7.5\n2009-08-03,9,1,215,2009,7.6\n2009-08-04,5,2,216,2009,7.633333333333334\n2009-08-05,3,3,217,2009,7.533333333333333\n2009-08-06,1,4,218,2009,7.266666666666667\n2009-08-07,7,5,219,2009,7.266666666666667\n2009-08-08,7,6,220,2009,7.066666666666666\n2009-08-09,1,7,221,2009,6.866666666666666\n2009-08-10,4,1,222,2009,6.8\n2009-08-11,2,2,223,2009,6.8\n2009-08-12,5,3,224,2009,6.7\n2009-08-13,4,4,225,2009,6.666666666666667\n2009-08-14,9,5,226,2009,6.733333333333333\n2009-08-15,6,6,227,2009,6.766666666666667\n2009-08-16,2,7,228,2009,6.633333333333334\n2009-08-17,21,1,229,2009,7.233333333333333\n2009-08-18,14,2,230,2009,7.533333333333333\n2009-08-19,13,3,231,2009,7.833333333333333\n2009-08-20,6,4,232,2009,7.566666666666666\n2009-08-21,5,5,233,2009,7.533333333333333\n2009-08-22,1,6,234,2009,7.233333333333333\n2009-08-23,9,7,235,2009,7.166666666666667\n2009-08-24,4,1,236,2009,7.2\n2009-08-25,10,2,237,2009,7.233333333333333\n2009-08-26,2,3,238,2009,7.133333333333334\n2009-08-27,5,4,239,2009,6.6\n2009-08-28,7,5,240,2009,6.266666666666667\n2009-08-29,8,6,241,2009,6.366666666666666\n2009-08-30,3,7,242,2009,6.266666666666667\n2009-08-31,4,1,243,2009,6.033333333333333\n2009-09-01,8,2,244,2009,6.166666666666667\n2009-09-02,8,3,245,2009,6.133333333333334\n2009-09-03,19,4,246,2009,6.6\n2009-09-04,22,5,247,2009,7.233333333333333\n2009-09-05,4,6,248,2009,7.333333333333333\n2009-09-06,8,7,249,2009,7.366666666666666\n2009-09-07,15,1,250,2009,7.633333333333334\n2009-09-08,16,2,251,2009,8.133333333333333\n2009-09-09,14,3,252,2009,8.466666666666667\n2009-09-10,16,4,253,2009,8.933333333333334\n2009-09-11,17,5,254,2009,9.333333333333334\n2009-09-12,4,6,255,2009,9.333333333333334\n2009-09-13,11,7,256,2009,9.4\n2009-09-14,12,1,257,2009,9.6\n2009-09-15,12,2,258,2009,9.933333333333334\n2009-09-16,10,3,259,2009,9.566666666666666\n2009-09-17,9,4,260,2009,9.4\n2009-09-18,19,5,261,2009,9.6\n2009-09-19,9,6,262,2009,9.7\n2009-09-20,4,7,263,2009,9.666666666666666\n2009-09-21,4,1,264,2009,9.766666666666667\n2009-09-22,6,2,265,2009,9.666666666666666\n2009-09-23,21,3,266,2009,10.233333333333333\n2009-09-25,2,5,268,2009,9.966666666666667\n2009-09-26,4,6,269,2009,10.033333333333333\n2009-09-27,2,7,270,2009,9.933333333333334\n2009-09-28,8,1,271,2009,9.966666666666667\n2009-09-29,5,2,272,2009,9.866666666666667\n2009-09-30,4,3,273,2009,9.9\n2009-10-01,6,4,274,2009,9.966666666666667\n2009-10-02,2,5,275,2009,9.766666666666667\n2009-10-03,12,6,276,2009,9.9\n2009-10-04,4,7,277,2009,9.4\n2009-10-05,10,1,278,2009,9.0\n2009-10-06,12,2,279,2009,9.266666666666667\n2009-10-07,30,3,280,2009,10.0\n2009-10-08,8,4,281,2009,9.766666666666667\n2009-10-09,9,5,282,2009,9.533333333333333\n2009-10-10,2,6,283,2009,9.133333333333333\n2009-10-11,1,7,284,2009,8.633333333333333\n2009-10-13,2,2,286,2009,8.133333333333333\n2009-10-14,5,3,287,2009,8.166666666666666\n2009-10-15,4,4,288,2009,7.933333333333334\n2009-10-16,8,5,289,2009,7.8\n2009-10-17,3,6,290,2009,7.5\n2009-10-18,5,7,291,2009,7.333333333333333\n2009-10-19,5,1,292,2009,7.2\n2009-10-21,4,3,294,2009,6.7\n2009-10-22,7,4,295,2009,6.633333333333334\n2009-10-23,15,5,296,2009,7.0\n2009-10-24,29,6,297,2009,7.833333333333333\n2009-10-25,7,7,298,2009,7.866666666666666\n2009-10-26,20,1,299,2009,7.833333333333333\n2009-10-27,9,2,300,2009,8.066666666666666\n2009-10-28,8,3,301,2009,8.2\n2009-10-29,5,4,302,2009,8.3\n2009-10-30,2,5,303,2009,8.1\n2009-10-31,10,6,304,2009,8.266666666666667\n2009-11-01,17,7,305,2009,8.7\n2009-11-02,24,1,306,2009,9.3\n2009-11-03,7,2,307,2009,9.466666666666667\n2009-11-04,9,3,308,2009,9.366666666666667\n2009-11-05,8,4,309,2009,9.5\n2009-11-06,10,5,310,2009,9.5\n2009-11-07,2,6,311,2009,9.166666666666666\n2009-11-08,16,7,312,2009,8.7\n2009-11-09,14,1,313,2009,8.9\n2009-11-10,13,2,314,2009,9.033333333333333\n2009-11-11,19,3,315,2009,9.6\n2009-11-12,12,4,316,2009,9.966666666666667\n2009-11-13,11,5,317,2009,10.266666666666667\n2009-11-14,33,6,318,2009,11.2\n2009-11-15,18,7,319,2009,11.666666666666666\n2009-11-16,13,1,320,2009,11.833333333333334\n2009-11-17,15,2,321,2009,12.233333333333333\n2009-11-18,23,3,322,2009,12.833333333333334\n2009-11-19,23,4,323,2009,13.433333333333334\n2009-11-20,20,5,324,2009,13.966666666666667\n2009-11-21,23,6,325,2009,14.5\n2009-11-22,18,7,326,2009,14.6\n2009-11-23,22,1,327,2009,14.366666666666667\n2009-11-24,12,2,328,2009,14.533333333333333\n2009-11-25,14,3,329,2009,14.333333333333334\n2009-11-26,17,4,330,2009,14.6\n2009-11-27,18,5,331,2009,14.933333333333334\n2009-11-28,26,6,332,2009,15.633333333333333\n2009-11-29,14,7,333,2009,16.033333333333335\n2009-11-30,16,1,334,2009,16.233333333333334\n2009-12-01,27,2,335,2009,16.566666666666666\n2009-12-02,22,3,336,2009,16.5\n2009-12-03,9,4,337,2009,16.566666666666666\n2009-12-04,8,5,338,2009,16.533333333333335\n2009-12-05,10,6,339,2009,16.6\n2009-12-06,10,7,340,2009,16.6\n2009-12-07,8,1,341,2009,16.8\n2009-12-08,9,2,342,2009,16.566666666666666\n2009-12-09,9,3,343,2009,16.4\n2009-12-10,22,4,344,2009,16.7\n2009-12-11,10,5,345,2009,16.4\n2009-12-12,9,6,346,2009,16.3\n2009-12-13,6,7,347,2009,16.133333333333333\n2009-12-14,8,1,348,2009,15.3\n2009-12-15,8,2,349,2009,14.966666666666667\n2009-12-16,14,3,350,2009,15.0\n2009-12-17,5,4,351,2009,14.666666666666666\n2009-12-18,15,5,352,2009,14.4\n2009-12-19,19,6,353,2009,14.266666666666667\n2009-12-20,12,7,354,2009,14.0\n2009-12-21,16,1,355,2009,13.766666666666667\n2009-12-22,12,2,356,2009,13.566666666666666\n2009-12-23,12,3,357,2009,13.233333333333333\n2009-12-24,13,4,358,2009,13.266666666666667\n2009-12-25,11,5,359,2009,13.166666666666666\n2009-12-26,32,6,360,2009,13.666666666666666\n2009-12-27,25,7,361,2009,13.9\n2009-12-28,16,1,362,2009,13.566666666666666\n2009-12-29,21,2,363,2009,13.8\n2009-12-30,27,3,364,2009,14.166666666666666\n2009-12-31,13,4,365,2009,13.7\n2010-01-01,14,5,1,2010,13.433333333333334\n2010-01-02,14,6,2,2010,13.6\n2010-01-03,12,7,3,2010,13.733333333333333\n2010-01-04,28,1,4,2010,14.333333333333334\n2010-01-05,7,2,5,2010,14.233333333333333\n2010-01-06,4,3,6,2010,14.1\n2010-01-07,5,4,7,2010,13.966666666666667\n2010-01-08,18,5,8,2010,14.266666666666667\n2010-01-09,10,6,9,2010,13.866666666666667\n2010-01-10,20,7,10,2010,14.2\n2010-01-11,39,1,11,2010,15.2\n2010-01-12,31,2,12,2010,16.033333333333335\n2010-01-13,21,3,13,2010,16.466666666666665\n2010-01-14,27,4,14,2010,17.1\n2010-01-15,6,5,15,2010,16.833333333333332\n2010-01-16,11,6,16,2010,17.033333333333335\n2010-01-17,7,7,17,2010,16.766666666666666\n2010-01-18,10,1,18,2010,16.466666666666665\n2010-01-19,11,2,19,2010,16.433333333333334\n2010-01-20,26,3,20,2010,16.766666666666666\n2010-01-21,16,4,21,2010,16.9\n2010-01-22,20,5,22,2010,17.166666666666668\n2010-01-23,8,6,23,2010,17.0\n2010-01-24,18,7,24,2010,17.233333333333334\n2010-01-25,24,1,25,2010,16.966666666666665\n2010-01-26,46,2,26,2010,17.666666666666668\n2010-01-27,32,3,27,2010,18.2\n2010-01-28,28,4,28,2010,18.433333333333334\n2010-01-29,30,5,29,2010,18.533333333333335\n2010-01-30,43,6,30,2010,19.533333333333335\n2010-01-31,20,7,31,2010,19.733333333333334\n2010-02-01,43,1,32,2010,20.7\n2010-02-02,14,2,33,2010,20.766666666666666\n2010-02-03,8,3,34,2010,20.1\n2010-02-04,6,4,35,2010,20.066666666666666\n2010-02-05,10,5,36,2010,20.266666666666666\n2010-02-06,16,6,37,2010,20.633333333333333\n2010-02-07,11,7,38,2010,20.4\n2010-02-08,13,1,39,2010,20.5\n2010-02-09,26,2,40,2010,20.7\n2010-02-10,26,3,41,2010,20.266666666666666\n2010-02-11,49,4,42,2010,20.866666666666667\n2010-02-12,38,5,43,2010,21.433333333333334\n2010-02-13,20,6,44,2010,21.2\n2010-02-14,9,7,45,2010,21.3\n2010-02-15,19,1,46,2010,21.566666666666666\n2010-02-16,24,2,47,2010,22.133333333333333\n2010-02-17,20,3,48,2010,22.466666666666665\n2010-02-18,25,4,49,2010,22.933333333333334\n2010-02-19,29,5,50,2010,23.033333333333335\n2010-02-20,24,6,51,2010,23.3\n2010-02-21,37,7,52,2010,23.866666666666667\n2010-02-22,44,1,53,2010,25.066666666666666\n2010-02-23,24,2,54,2010,25.266666666666666\n2010-02-24,14,3,55,2010,24.933333333333334\n2010-02-25,10,4,56,2010,23.733333333333334\n2010-02-26,12,5,57,2010,23.066666666666666\n2010-02-27,14,6,58,2010,22.6\n2010-02-28,45,7,59,2010,23.1\n2010-03-01,35,1,60,2010,22.833333333333332\n2010-03-02,50,2,61,2010,23.833333333333332\n2010-03-03,31,3,62,2010,23.433333333333334\n2010-03-04,20,4,63,2010,23.633333333333333\n2010-03-05,15,5,64,2010,23.866666666666667\n2010-03-06,20,6,65,2010,24.333333333333332\n2010-03-07,25,7,66,2010,24.833333333333332\n2010-03-08,24,1,67,2010,25.1\n2010-03-09,18,2,68,2010,25.333333333333332\n2010-03-10,24,3,69,2010,25.7\n2010-03-11,13,4,70,2010,25.266666666666666\n2010-03-12,17,5,71,2010,24.966666666666665\n2010-03-13,8,6,72,2010,23.6\n2010-03-14,35,7,73,2010,23.5\n2010-03-15,33,1,74,2010,23.933333333333334\n2010-03-16,23,2,75,2010,24.4\n2010-03-17,40,3,76,2010,25.1\n2010-03-18,25,4,77,2010,25.133333333333333\n2010-03-19,13,5,78,2010,24.9\n2010-03-20,6,6,79,2010,24.266666666666666\n2010-03-21,8,7,80,2010,23.566666666666666\n2010-03-22,9,1,81,2010,23.066666666666666\n2010-03-23,15,2,82,2010,22.333333333333332\n2010-03-24,28,3,83,2010,21.8\n2010-03-25,15,4,84,2010,21.5\n2010-03-26,40,5,85,2010,22.366666666666667\n2010-03-27,10,6,86,2010,22.366666666666667\n2010-03-28,20,7,87,2010,22.633333333333333\n2010-03-29,34,1,88,2010,23.3\n2010-03-30,39,2,89,2010,23.1\n2010-03-31,26,3,90,2010,22.8\n2010-04-01,39,4,91,2010,22.433333333333334\n2010-04-02,36,5,92,2010,22.6\n2010-04-03,20,6,93,2010,22.6\n2010-04-04,19,7,94,2010,22.733333333333334\n2010-04-05,31,1,95,2010,23.1\n2010-04-06,36,2,96,2010,23.466666666666665\n2010-04-07,31,3,97,2010,23.7\n2010-04-08,30,4,98,2010,24.1\n2010-04-09,22,5,99,2010,24.033333333333335\n2010-04-10,26,6,100,2010,24.466666666666665\n2010-04-11,26,7,101,2010,24.766666666666666\n2010-04-12,62,1,102,2010,26.566666666666666\n2010-04-13,41,2,103,2010,26.766666666666666\n2010-04-14,30,3,104,2010,26.666666666666668\n2010-04-15,36,4,105,2010,27.1\n2010-04-16,40,5,106,2010,27.1\n2010-04-17,34,6,107,2010,27.4\n2010-04-18,30,7,108,2010,27.966666666666665\n2010-04-19,21,1,109,2010,28.466666666666665\n2010-04-20,25,2,110,2010,29.033333333333335\n2010-04-21,23,3,111,2010,29.5\n2010-04-22,30,4,112,2010,30.0\n2010-04-23,32,5,113,2010,30.133333333333333\n2010-04-24,23,6,114,2010,30.4\n2010-04-25,44,7,115,2010,30.533333333333335\n2010-04-26,29,1,116,2010,31.166666666666668\n2010-04-27,22,2,117,2010,31.233333333333334\n2010-04-28,42,3,118,2010,31.5\n2010-04-29,55,4,119,2010,32.03333333333333\n2010-04-30,19,5,120,2010,31.8\n2010-05-01,21,6,121,2010,31.2\n2010-05-02,39,7,122,2010,31.3\n2010-05-03,42,1,123,2010,32.03333333333333\n2010-05-04,32,2,124,2010,32.46666666666667\n2010-05-05,42,3,125,2010,32.833333333333336\n2010-05-06,41,4,126,2010,33.0\n2010-05-07,16,5,127,2010,32.5\n2010-05-08,14,6,128,2010,31.966666666666665\n2010-05-09,13,7,129,2010,31.666666666666668\n2010-05-10,16,1,130,2010,31.333333333333332\n2010-05-11,21,2,131,2010,31.166666666666668\n2010-05-12,13,3,132,2010,29.533333333333335\n2010-05-13,17,4,133,2010,28.733333333333334\n2010-05-14,37,5,134,2010,28.966666666666665\n2010-05-15,25,6,135,2010,28.6\n2010-05-16,7,7,136,2010,27.5\n2010-05-17,18,1,137,2010,26.966666666666665\n2010-05-18,19,2,138,2010,26.6\n2010-05-19,15,3,139,2010,26.4\n2010-05-20,24,4,140,2010,26.366666666666667\n2010-05-21,28,5,141,2010,26.533333333333335\n2010-05-22,26,6,142,2010,26.4\n2010-05-23,6,7,143,2010,25.533333333333335\n2010-05-24,7,1,144,2010,25.0\n2010-05-25,19,2,145,2010,24.166666666666668\n2010-05-26,26,3,146,2010,24.066666666666666\n2010-05-27,22,4,147,2010,24.066666666666666\n2010-05-28,20,5,148,2010,23.333333333333332\n2010-05-29,24,6,149,2010,22.3\n2010-05-30,29,7,150,2010,22.633333333333333\n2010-05-31,4,1,151,2010,22.066666666666666\n2010-06-01,14,2,152,2010,21.233333333333334\n2010-06-02,20,3,153,2010,20.5\n2010-06-03,22,4,154,2010,20.166666666666668\n2010-06-04,14,5,155,2010,19.233333333333334\n2010-06-05,14,6,156,2010,18.333333333333332\n2010-06-06,20,7,157,2010,18.466666666666665\n2010-06-07,31,1,158,2010,19.033333333333335\n2010-06-08,30,2,159,2010,19.6\n2010-06-09,36,3,160,2010,20.266666666666666\n2010-06-10,20,4,161,2010,20.233333333333334\n2010-06-11,37,5,162,2010,21.033333333333335\n2010-06-12,34,6,163,2010,21.6\n2010-06-13,17,7,164,2010,20.933333333333334\n2010-06-14,27,1,165,2010,21.0\n2010-06-15,17,2,166,2010,21.333333333333332\n2010-06-16,34,3,167,2010,21.866666666666667\n2010-06-17,44,4,168,2010,22.7\n2010-06-18,30,5,169,2010,23.2\n2010-06-19,23,6,170,2010,23.166666666666668\n2010-06-20,24,7,171,2010,23.033333333333335\n2010-06-21,24,1,172,2010,22.966666666666665\n2010-06-22,25,2,173,2010,23.6\n2010-06-23,24,3,174,2010,24.166666666666668\n2010-06-24,29,4,175,2010,24.5\n2010-06-25,33,5,176,2010,24.733333333333334\n2010-06-26,28,6,177,2010,24.933333333333334\n2010-06-27,21,7,178,2010,24.966666666666665\n2010-06-28,13,1,179,2010,24.6\n2010-06-29,43,2,180,2010,25.066666666666666\n2010-06-30,36,3,181,2010,26.133333333333333\n2010-07-01,17,4,182,2010,26.233333333333334\n2010-07-02,14,5,183,2010,26.033333333333335\n2010-07-03,16,6,184,2010,25.833333333333332\n2010-07-04,21,7,185,2010,26.066666666666666\n2010-07-05,14,1,186,2010,26.066666666666666\n2010-07-06,24,2,187,2010,26.2\n2010-07-07,23,3,188,2010,25.933333333333334\n2010-07-08,42,4,189,2010,26.333333333333332\n2010-07-09,19,5,190,2010,25.766666666666666\n2010-07-10,19,6,191,2010,25.733333333333334\n2010-07-11,11,7,192,2010,24.866666666666667\n2010-07-12,22,1,193,2010,24.466666666666665\n2010-07-13,25,2,194,2010,24.733333333333334\n2010-07-14,28,3,195,2010,24.766666666666666\n2010-07-15,13,4,196,2010,24.633333333333333\n2010-07-16,38,5,197,2010,24.766666666666666\n2010-07-17,12,6,198,2010,23.7\n2010-07-18,12,7,199,2010,23.1\n2010-07-19,19,1,200,2010,22.966666666666665\n2010-07-20,41,2,201,2010,23.533333333333335\n2010-07-21,28,3,202,2010,23.666666666666668\n2010-07-22,24,4,203,2010,23.633333333333333\n2010-07-23,36,5,204,2010,24.033333333333335\n2010-07-24,21,6,205,2010,23.766666666666666\n2010-07-25,7,7,206,2010,22.9\n2010-07-26,46,1,207,2010,23.5\n2010-07-27,25,2,208,2010,23.633333333333333\n2010-07-28,32,3,209,2010,24.266666666666666\n2010-07-29,16,4,210,2010,23.366666666666667\n2010-07-30,25,5,211,2010,23.0\n2010-07-31,21,6,212,2010,23.133333333333333\n2010-08-01,40,7,213,2010,24.0\n2010-08-02,20,1,214,2010,24.133333333333333\n2010-08-03,20,2,215,2010,24.1\n2010-08-04,19,3,216,2010,24.266666666666666\n2010-08-05,28,4,217,2010,24.4\n2010-08-06,24,5,218,2010,24.433333333333334\n2010-08-07,34,6,219,2010,24.166666666666668\n2010-08-08,18,7,220,2010,24.133333333333333\n2010-08-09,28,1,221,2010,24.433333333333334\n2010-08-10,19,2,222,2010,24.7\n2010-08-11,23,3,223,2010,24.733333333333334\n2010-08-12,24,4,224,2010,24.7\n2010-08-13,32,5,225,2010,24.833333333333332\n2010-08-14,16,6,226,2010,24.933333333333334\n2010-08-15,30,7,227,2010,24.666666666666668\n2010-08-16,48,1,228,2010,25.866666666666667\n2010-08-17,38,2,229,2010,26.733333333333334\n2010-08-18,23,3,230,2010,26.866666666666667\n2010-08-19,36,4,231,2010,26.7\n2010-08-20,33,5,232,2010,26.866666666666667\n2010-08-21,60,6,233,2010,28.066666666666666\n2010-08-22,17,7,234,2010,27.433333333333334\n2010-08-23,50,1,235,2010,28.4\n2010-08-24,38,2,236,2010,29.433333333333334\n2010-08-25,47,3,237,2010,29.466666666666665\n2010-08-26,50,4,238,2010,30.3\n2010-08-27,51,5,239,2010,30.933333333333334\n2010-08-28,33,6,240,2010,31.5\n2010-08-29,43,7,241,2010,32.1\n2010-08-30,38,1,242,2010,32.666666666666664\n2010-08-31,29,2,243,2010,32.3\n2010-09-01,22,3,244,2010,32.36666666666667\n2010-09-02,20,4,245,2010,32.36666666666667\n2010-09-03,20,5,246,2010,32.4\n2010-09-04,16,6,247,2010,32.0\n2010-09-05,9,7,248,2010,31.5\n2010-09-06,29,1,249,2010,31.333333333333332\n2010-09-07,20,2,250,2010,31.4\n2010-09-08,15,3,251,2010,30.966666666666665\n2010-09-09,40,4,252,2010,31.666666666666668\n2010-09-10,34,5,253,2010,32.03333333333333\n2010-09-11,32,6,254,2010,32.3\n2010-09-12,18,7,255,2010,31.833333333333332\n2010-09-13,42,1,256,2010,32.7\n2010-09-14,39,2,257,2010,33.0\n2010-09-15,24,3,258,2010,32.2\n2010-09-16,33,4,259,2010,32.03333333333333\n2010-09-17,59,5,260,2010,33.233333333333334\n2010-09-18,35,6,261,2010,33.2\n2010-09-19,37,7,262,2010,33.333333333333336\n2010-09-20,61,1,263,2010,33.36666666666667\n2010-09-21,43,2,264,2010,34.233333333333334\n2010-09-22,49,3,265,2010,34.2\n2010-09-23,44,4,266,2010,34.4\n2010-09-24,53,5,267,2010,34.6\n2010-09-25,33,6,268,2010,34.03333333333333\n2010-09-26,21,7,269,2010,33.03333333333333\n2010-09-27,42,1,270,2010,33.333333333333336\n2010-09-28,22,2,271,2010,32.63333333333333\n2010-09-29,49,3,272,2010,33.0\n2010-09-30,28,4,273,2010,32.96666666666667\n2010-10-01,33,5,274,2010,33.333333333333336\n2010-10-02,32,6,275,2010,33.733333333333334\n2010-10-03,30,7,276,2010,34.06666666666667\n2010-10-04,41,1,277,2010,34.9\n2010-10-05,40,2,278,2010,35.93333333333333\n2010-10-06,30,3,279,2010,35.96666666666667\n2010-10-07,26,4,280,2010,36.166666666666664\n2010-10-08,24,5,281,2010,36.46666666666667\n2010-10-09,10,6,282,2010,35.46666666666667\n2010-10-10,18,7,283,2010,34.93333333333333\n2010-10-11,31,1,284,2010,34.9\n2010-10-12,47,2,285,2010,35.86666666666667\n2010-10-13,24,3,286,2010,35.266666666666666\n2010-10-14,33,4,287,2010,35.06666666666667\n2010-10-15,34,5,288,2010,35.4\n2010-10-16,31,6,289,2010,35.333333333333336\n2010-10-17,18,7,290,2010,33.96666666666667\n2010-10-18,25,1,291,2010,33.63333333333333\n2010-10-19,47,2,292,2010,33.96666666666667\n2010-10-20,42,3,293,2010,33.333333333333336\n2010-10-21,13,4,294,2010,32.333333333333336\n2010-10-22,13,5,295,2010,31.133333333333333\n2010-10-23,17,6,296,2010,30.233333333333334\n2010-10-24,31,7,297,2010,29.5\n2010-10-25,38,1,298,2010,29.666666666666668\n2010-10-26,41,2,299,2010,30.333333333333332\n2010-10-27,34,3,300,2010,30.066666666666666\n2010-10-28,37,4,301,2010,30.566666666666666\n2010-10-29,36,5,302,2010,30.133333333333333\n2010-10-30,15,6,303,2010,29.7\n2010-10-31,26,7,304,2010,29.466666666666665\n2010-11-01,32,1,305,2010,29.466666666666665\n2010-11-02,42,2,306,2010,29.866666666666667\n2010-11-03,33,3,307,2010,29.6\n2010-11-04,32,4,308,2010,29.333333333333332\n2010-11-05,18,5,309,2010,28.933333333333334\n2010-11-06,39,6,310,2010,29.366666666666667\n2010-11-07,37,7,311,2010,29.8\n2010-11-08,45,1,312,2010,30.966666666666665\n2010-11-09,60,2,313,2010,32.36666666666667\n2010-11-10,62,3,314,2010,33.4\n2010-11-11,47,4,315,2010,33.4\n2010-11-12,45,5,316,2010,34.1\n2010-11-13,24,6,317,2010,33.8\n2010-11-14,43,7,318,2010,34.1\n2010-11-15,38,1,319,2010,34.333333333333336\n2010-11-16,46,2,320,2010,35.266666666666666\n2010-11-17,33,3,321,2010,35.53333333333333\n2010-11-18,51,4,322,2010,35.666666666666664\n2010-11-19,48,5,323,2010,35.86666666666667\n2010-11-20,50,6,324,2010,37.1\n2010-11-21,13,7,325,2010,37.1\n2010-11-22,43,1,326,2010,37.96666666666667\n2010-11-23,60,2,327,2010,38.93333333333333\n2010-11-24,50,3,328,2010,39.333333333333336\n2010-11-25,35,4,329,2010,39.13333333333333\n2010-11-26,60,5,330,2010,40.0\n2010-11-27,76,6,331,2010,41.3\n2010-11-28,61,7,332,2010,42.13333333333333\n2010-11-29,28,1,333,2010,42.56666666666667\n2010-11-30,47,2,334,2010,43.266666666666666\n2010-12-01,40,3,335,2010,43.53333333333333\n2010-12-02,36,4,336,2010,43.333333333333336\n2010-12-03,32,5,337,2010,43.3\n2010-12-04,34,6,338,2010,43.36666666666667\n2010-12-05,38,7,339,2010,44.03333333333333\n2010-12-06,37,1,340,2010,43.96666666666667\n2010-12-07,28,2,341,2010,43.666666666666664\n2010-12-08,24,3,342,2010,42.96666666666667\n2010-12-09,26,4,343,2010,41.833333333333336\n2010-12-10,5,5,344,2010,39.93333333333333\n2010-12-11,17,6,345,2010,38.93333333333333\n2010-12-12,21,7,346,2010,38.13333333333333\n2010-12-13,32,1,347,2010,38.4\n2010-12-14,23,2,348,2010,37.733333333333334\n2010-12-15,29,3,349,2010,37.43333333333333\n2010-12-16,33,4,350,2010,37.0\n2010-12-17,30,5,351,2010,36.9\n2010-12-18,38,6,352,2010,36.46666666666667\n2010-12-19,19,7,353,2010,35.5\n2010-12-20,18,1,354,2010,34.43333333333333\n2010-12-21,35,2,355,2010,35.166666666666664\n2010-12-22,42,3,356,2010,35.13333333333333\n2010-12-23,34,4,357,2010,34.266666666666666\n2010-12-24,17,5,358,2010,33.166666666666664\n2010-12-25,13,6,359,2010,32.43333333333333\n2010-12-26,15,7,360,2010,30.933333333333334\n2010-12-27,31,1,361,2010,29.433333333333334\n2010-12-28,40,2,362,2010,28.733333333333334\n2010-12-29,67,3,363,2010,30.033333333333335\n2010-12-30,18,4,364,2010,29.066666666666666\n2010-12-31,19,5,365,2010,28.366666666666667\n2011-01-01,20,6,1,2011,27.833333333333332\n2011-01-02,39,7,2,2011,28.066666666666666\n2011-01-03,50,1,3,2011,28.6\n2011-01-04,38,2,4,2011,28.6\n2011-01-05,45,3,5,2011,28.866666666666667\n2011-01-06,37,4,6,2011,29.166666666666668\n2011-01-07,27,5,7,2011,29.266666666666666\n2011-01-08,38,6,8,2011,29.666666666666668\n2011-01-09,33,7,9,2011,30.6\n2011-01-10,43,1,10,2011,31.466666666666665\n2011-01-11,49,2,11,2011,32.4\n2011-01-12,45,3,12,2011,32.833333333333336\n2011-01-13,53,4,13,2011,33.833333333333336\n2011-01-14,45,5,14,2011,34.36666666666667\n2011-01-15,29,6,15,2011,34.233333333333334\n2011-01-16,7,7,16,2011,33.46666666666667\n2011-01-17,35,1,17,2011,33.36666666666667\n2011-01-18,26,2,18,2011,33.6\n2011-01-19,31,3,19,2011,34.03333333333333\n2011-01-20,26,4,20,2011,33.733333333333334\n2011-01-21,57,5,21,2011,34.233333333333334\n2011-01-22,28,6,22,2011,34.03333333333333\n2011-01-23,44,7,23,2011,34.93333333333333\n2011-01-24,26,1,24,2011,35.36666666666667\n2011-01-25,26,2,25,2011,35.733333333333334\n2011-01-26,38,3,26,2011,35.96666666666667\n2011-01-27,39,4,27,2011,35.93333333333333\n2011-01-28,23,5,28,2011,34.46666666666667\n2011-01-29,21,6,29,2011,34.56666666666667\n2011-01-30,52,7,30,2011,35.666666666666664\n2011-01-31,19,1,31,2011,35.63333333333333\n2011-02-01,28,2,32,2011,35.266666666666666\n2011-02-02,31,3,33,2011,34.63333333333333\n2011-02-03,24,4,34,2011,34.166666666666664\n2011-02-04,16,5,35,2011,33.2\n2011-02-05,34,6,36,2011,33.1\n2011-02-06,16,7,37,2011,32.733333333333334\n2011-02-07,36,1,38,2011,32.666666666666664\n2011-02-08,24,2,39,2011,32.36666666666667\n2011-02-09,22,3,40,2011,31.666666666666668\n2011-02-10,38,4,41,2011,31.3\n2011-02-11,19,5,42,2011,30.433333333333334\n2011-02-12,17,6,43,2011,29.233333333333334\n2011-02-13,28,7,44,2011,28.666666666666668\n2011-02-14,20,1,45,2011,28.366666666666667\n2011-02-15,20,2,46,2011,28.8\n2011-02-16,30,3,47,2011,28.633333333333333\n2011-02-17,39,4,48,2011,29.066666666666666\n2011-02-18,31,5,49,2011,29.066666666666666\n2011-02-19,12,6,50,2011,28.6\n2011-02-20,11,7,51,2011,27.066666666666666\n2011-02-21,29,1,52,2011,27.1\n2011-02-22,29,2,53,2011,26.6\n2011-02-23,24,3,54,2011,26.533333333333335\n2011-02-24,49,4,55,2011,27.3\n2011-02-25,12,5,56,2011,26.433333333333334\n2011-02-26,10,6,57,2011,25.466666666666665\n2011-02-27,19,7,58,2011,25.333333333333332\n2011-02-28,14,1,59,2011,25.1\n2011-03-01,22,2,60,2011,24.1\n2011-03-02,48,3,61,2011,25.066666666666666\n2011-03-03,28,4,62,2011,25.066666666666666\n2011-03-04,26,5,63,2011,24.9\n2011-03-05,13,6,64,2011,24.533333333333335\n2011-03-06,19,7,65,2011,24.633333333333333\n2011-03-07,15,1,66,2011,24.0\n2011-03-08,30,2,67,2011,24.466666666666665\n2011-03-09,28,3,68,2011,24.2\n2011-03-10,22,4,69,2011,24.133333333333333\n2011-03-11,31,5,70,2011,24.433333333333334\n2011-03-12,24,6,71,2011,23.966666666666665\n2011-03-13,26,7,72,2011,24.2\n2011-03-14,71,1,73,2011,26.0\n2011-03-15,54,2,74,2011,26.866666666666667\n2011-03-16,22,3,75,2011,26.933333333333334\n2011-03-17,42,4,76,2011,27.666666666666668\n2011-03-18,22,5,77,2011,27.4\n2011-03-19,17,6,78,2011,26.666666666666668\n2011-03-20,31,7,79,2011,26.666666666666668\n2011-03-21,46,1,80,2011,27.8\n2011-03-22,44,2,81,2011,28.9\n2011-03-23,55,3,82,2011,29.766666666666666\n2011-03-24,44,4,83,2011,30.266666666666666\n2011-03-25,40,5,84,2011,30.8\n2011-03-26,22,6,85,2011,29.9\n2011-03-27,28,7,86,2011,30.433333333333334\n2011-03-28,18,1,87,2011,30.7\n2011-03-29,44,2,88,2011,31.533333333333335\n2011-03-30,48,3,89,2011,32.666666666666664\n2011-03-31,51,4,90,2011,33.63333333333333\n2011-04-01,49,5,91,2011,33.666666666666664\n2011-04-02,30,6,92,2011,33.733333333333334\n2011-04-03,10,7,93,2011,33.2\n2011-04-04,29,1,94,2011,33.733333333333334\n2011-04-05,27,2,95,2011,34.0\n2011-04-06,8,3,96,2011,33.766666666666666\n2011-04-07,20,4,97,2011,33.43333333333333\n2011-04-08,27,5,98,2011,33.4\n2011-04-09,36,6,99,2011,33.86666666666667\n2011-04-10,14,7,100,2011,33.3\n2011-04-11,25,1,101,2011,33.333333333333336\n2011-04-12,40,2,102,2011,33.8\n2011-04-13,16,3,103,2011,31.966666666666665\n2011-04-14,15,4,104,2011,30.666666666666668\n2011-04-15,50,5,105,2011,31.6\n2011-04-16,28,6,106,2011,31.133333333333333\n2011-04-17,47,7,107,2011,31.966666666666665\n2011-04-18,65,1,108,2011,33.56666666666667\n2011-04-19,56,2,109,2011,34.4\n2011-04-20,47,3,110,2011,34.43333333333333\n2011-04-21,80,4,111,2011,35.63333333333333\n2011-04-22,59,5,112,2011,35.766666666666666\n2011-04-23,65,6,113,2011,36.46666666666667\n2011-04-24,50,7,114,2011,36.8\n2011-04-25,62,1,115,2011,38.13333333333333\n2011-04-26,51,2,116,2011,38.9\n2011-04-27,37,3,117,2011,39.53333333333333\n2011-04-28,59,4,118,2011,40.03333333333333\n2011-04-29,54,5,119,2011,40.233333333333334\n2011-04-30,23,6,120,2011,39.3\n2011-05-01,50,7,121,2011,39.333333333333336\n2011-05-02,49,1,122,2011,39.96666666666667\n2011-05-03,27,2,123,2011,40.53333333333333\n2011-05-04,52,3,124,2011,41.3\n2011-05-05,33,4,125,2011,41.5\n2011-05-06,26,5,126,2011,42.1\n2011-05-07,12,6,127,2011,41.833333333333336\n2011-05-08,18,7,128,2011,41.53333333333333\n2011-05-09,22,1,129,2011,41.06666666666667\n2011-05-10,26,2,130,2011,41.46666666666667\n2011-05-11,34,3,131,2011,41.766666666666666\n2011-05-12,27,4,132,2011,41.333333333333336\n2011-05-13,29,5,133,2011,41.766666666666666\n2011-05-14,12,6,134,2011,41.666666666666664\n2011-05-15,22,7,135,2011,40.733333333333334\n2011-05-16,25,1,136,2011,40.63333333333333\n2011-05-17,20,2,137,2011,39.733333333333334\n2011-05-18,36,3,138,2011,38.766666666666666\n2011-05-19,27,4,139,2011,37.8\n2011-05-20,14,5,140,2011,36.7\n2011-05-21,14,6,141,2011,34.5\n2011-05-22,45,7,142,2011,34.03333333333333\n2011-05-23,37,1,143,2011,33.1\n2011-05-24,43,2,144,2011,32.86666666666667\n2011-05-25,23,3,145,2011,31.566666666666666\n2011-05-26,18,4,146,2011,30.466666666666665\n2011-05-27,42,5,147,2011,30.633333333333333\n2011-05-28,79,6,148,2011,31.3\n2011-05-29,57,7,149,2011,31.4\n2011-05-30,39,1,150,2011,31.933333333333334\n2011-05-31,73,2,151,2011,32.7\n2011-06-01,37,3,152,2011,32.3\n2011-06-02,58,4,153,2011,33.333333333333336\n2011-06-03,30,5,154,2011,32.6\n2011-06-04,58,6,155,2011,33.43333333333333\n2011-06-05,10,7,156,2011,32.9\n2011-06-06,30,1,157,2011,33.5\n2011-06-07,44,2,158,2011,34.36666666666667\n2011-06-08,59,3,159,2011,35.6\n2011-06-09,38,4,160,2011,36.0\n2011-06-10,101,5,161,2011,38.233333333333334\n2011-06-11,36,6,162,2011,38.53333333333333\n2011-06-12,46,7,163,2011,39.1\n2011-06-13,50,1,164,2011,40.36666666666667\n2011-06-14,83,2,165,2011,42.4\n2011-06-15,37,3,166,2011,42.8\n2011-06-16,67,4,167,2011,44.36666666666667\n2011-06-17,116,5,168,2011,47.03333333333333\n2011-06-18,98,6,169,2011,49.4\n2011-06-19,49,7,170,2011,50.56666666666667\n2011-06-20,71,1,171,2011,52.46666666666667\n2011-06-21,68,2,172,2011,53.233333333333334\n2011-06-22,82,3,173,2011,54.733333333333334\n2011-06-23,58,4,174,2011,55.233333333333334\n2011-06-24,131,5,175,2011,58.833333333333336\n2011-06-25,51,6,176,2011,59.93333333333333\n2011-06-26,34,7,177,2011,59.666666666666664\n2011-06-27,88,1,178,2011,59.96666666666667\n2011-06-28,81,2,179,2011,60.766666666666666\n2011-06-29,64,3,180,2011,61.6\n2011-06-30,46,4,181,2011,60.7\n2011-07-01,118,5,182,2011,63.4\n2011-07-02,49,6,183,2011,63.1\n2011-07-03,37,7,184,2011,63.333333333333336\n2011-07-04,29,1,185,2011,62.36666666666667\n2011-07-05,50,2,186,2011,63.7\n2011-07-06,42,3,187,2011,64.1\n2011-07-07,44,4,188,2011,64.1\n2011-07-08,57,5,189,2011,64.03333333333333\n2011-07-09,27,6,190,2011,63.666666666666664\n2011-07-10,26,7,191,2011,61.166666666666664\n2011-07-11,40,1,192,2011,61.3\n2011-07-12,56,2,193,2011,61.63333333333333\n2011-07-13,55,3,194,2011,61.8\n2011-07-14,59,4,195,2011,61.0\n2011-07-15,160,5,196,2011,65.1\n2011-07-16,83,6,197,2011,65.63333333333334\n2011-07-17,147,7,198,2011,66.66666666666667\n2011-07-18,139,1,199,2011,68.03333333333333\n2011-07-19,105,2,200,2011,69.9\n2011-07-20,94,3,201,2011,70.66666666666667\n2011-07-21,28,4,202,2011,69.33333333333333\n2011-07-22,80,5,203,2011,69.26666666666667\n2011-07-23,35,6,204,2011,68.5\n2011-07-24,28,7,205,2011,65.06666666666666\n2011-07-25,42,1,206,2011,64.76666666666667\n2011-07-26,73,2,207,2011,66.06666666666666\n2011-07-27,76,3,208,2011,65.66666666666667\n2011-07-28,48,4,209,2011,64.56666666666666\n2011-07-29,66,5,210,2011,64.63333333333334\n2011-07-30,66,6,211,2011,65.3\n2011-07-31,54,7,212,2011,63.166666666666664\n2011-08-01,45,1,213,2011,63.03333333333333\n2011-08-02,79,2,214,2011,64.43333333333334\n2011-08-03,70,3,215,2011,65.8\n2011-08-04,81,4,216,2011,66.83333333333333\n2011-08-05,85,5,217,2011,68.26666666666667\n2011-08-06,36,6,218,2011,68.0\n2011-08-07,73,7,219,2011,68.53333333333333\n2011-08-08,25,1,220,2011,68.46666666666667\n2011-08-09,60,2,221,2011,69.6\n2011-08-10,58,3,222,2011,70.2\n2011-08-11,73,4,223,2011,70.76666666666667\n2011-08-12,70,5,224,2011,71.26666666666667\n2011-08-13,34,6,225,2011,70.43333333333334\n2011-08-14,38,7,226,2011,66.36666666666666\n2011-08-15,37,1,227,2011,64.83333333333333\n2011-08-16,66,2,228,2011,62.13333333333333\n2011-08-17,35,3,229,2011,58.666666666666664\n2011-08-18,51,4,230,2011,56.86666666666667\n2011-08-19,54,5,231,2011,55.53333333333333\n2011-08-20,36,6,232,2011,55.8\n2011-08-21,65,7,233,2011,55.3\n2011-08-22,40,1,234,2011,55.46666666666667\n2011-08-23,33,2,235,2011,55.63333333333333\n2011-08-24,65,3,236,2011,56.4\n2011-08-25,59,4,237,2011,55.93333333333333\n2011-08-26,66,5,238,2011,55.6\n2011-08-27,31,6,239,2011,55.03333333333333\n2011-08-28,45,7,240,2011,54.333333333333336\n2011-08-29,32,1,241,2011,53.2\n2011-08-30,38,2,242,2011,52.666666666666664\n2011-08-31,60,3,243,2011,53.166666666666664\n2011-09-01,58,4,244,2011,52.46666666666667\n2011-09-02,63,5,245,2011,52.233333333333334\n2011-09-03,38,6,246,2011,50.8\n2011-09-04,25,7,247,2011,48.8\n2011-09-05,40,1,248,2011,48.93333333333333\n2011-09-06,62,2,249,2011,48.56666666666667\n2011-09-07,91,3,250,2011,50.766666666666666\n2011-09-08,64,4,251,2011,50.9\n2011-09-09,56,5,252,2011,50.833333333333336\n2011-09-10,37,6,253,2011,49.63333333333333\n2011-09-11,51,7,254,2011,49.0\n2011-09-12,41,1,255,2011,49.233333333333334\n2011-09-13,40,2,256,2011,49.3\n2011-09-14,69,3,257,2011,50.36666666666667\n2011-09-15,48,4,258,2011,49.766666666666666\n2011-09-16,44,5,259,2011,50.06666666666667\n2011-09-17,14,6,260,2011,48.833333333333336\n2011-09-18,28,7,261,2011,47.96666666666667\n2011-09-19,29,1,262,2011,47.733333333333334\n2011-09-20,59,2,263,2011,47.53333333333333\n2011-09-21,48,3,264,2011,47.8\n2011-09-22,34,4,265,2011,47.833333333333336\n2011-09-23,104,5,266,2011,49.13333333333333\n2011-09-24,84,6,267,2011,49.96666666666667\n2011-09-25,48,7,268,2011,49.36666666666667\n2011-09-26,81,1,269,2011,51.03333333333333\n2011-09-27,84,2,270,2011,52.333333333333336\n2011-09-28,88,3,271,2011,54.2\n2011-09-29,99,4,272,2011,56.233333333333334\n2011-09-30,110,5,273,2011,57.9\n2011-10-01,120,6,274,2011,59.96666666666667\n2011-10-02,90,7,275,2011,60.86666666666667\n2011-10-03,57,1,276,2011,61.5\n2011-10-04,67,2,277,2011,62.9\n2011-10-05,71,3,278,2011,63.93333333333333\n2011-10-06,48,4,279,2011,63.46666666666667\n2011-10-07,74,5,280,2011,62.9\n2011-10-08,59,6,281,2011,62.733333333333334\n2011-10-09,69,7,282,2011,63.166666666666664\n2011-10-10,75,1,283,2011,64.43333333333334\n2011-10-11,78,2,284,2011,65.33333333333333\n2011-10-12,72,3,285,2011,66.36666666666666\n2011-10-13,82,4,286,2011,67.76666666666667\n2011-10-14,61,5,287,2011,67.5\n2011-10-15,61,6,288,2011,67.93333333333334\n2011-10-16,41,7,289,2011,67.83333333333333\n2011-10-17,104,1,290,2011,70.83333333333333\n2011-10-18,62,2,291,2011,71.96666666666667\n2011-10-19,88,3,292,2011,73.93333333333334\n2011-10-20,75,4,293,2011,74.46666666666667\n2011-10-21,97,5,294,2011,76.1\n2011-10-22,45,6,295,2011,76.46666666666667\n2011-10-23,58,7,296,2011,74.93333333333334\n2011-10-24,85,1,297,2011,74.96666666666667\n2011-10-25,109,2,298,2011,77.0\n2011-10-26,66,3,299,2011,76.5\n2011-10-27,45,4,300,2011,75.2\n2011-10-28,57,5,301,2011,74.16666666666667\n2011-10-29,53,6,302,2011,72.63333333333334\n2011-10-30,50,7,303,2011,70.63333333333334\n2011-10-31,89,1,304,2011,69.6\n2011-11-01,61,2,305,2011,68.63333333333334\n2011-11-02,78,3,306,2011,69.33333333333333\n2011-11-03,74,4,307,2011,69.56666666666666\n2011-11-04,85,5,308,2011,70.03333333333333\n2011-11-05,84,6,309,2011,71.23333333333333\n2011-11-06,43,7,310,2011,70.2\n2011-11-07,53,1,311,2011,70.0\n2011-11-08,48,2,312,2011,69.3\n2011-11-09,71,3,313,2011,69.16666666666667\n2011-11-10,35,4,314,2011,67.73333333333333\n2011-11-11,72,5,315,2011,67.73333333333333\n2011-11-12,115,6,316,2011,68.83333333333333\n2011-11-13,90,7,317,2011,69.8\n2011-11-14,64,1,318,2011,69.9\n2011-11-15,49,2,319,2011,70.16666666666667\n2011-11-16,45,3,320,2011,68.2\n2011-11-17,79,4,321,2011,68.76666666666667\n2011-11-18,61,5,322,2011,67.86666666666666\n2011-11-19,81,6,323,2011,68.06666666666666\n2011-11-20,78,7,324,2011,67.43333333333334\n2011-11-21,63,1,325,2011,68.03333333333333\n2011-11-22,89,2,326,2011,69.06666666666666\n2011-11-23,66,3,327,2011,68.43333333333334\n2011-11-24,60,4,328,2011,66.8\n2011-11-25,90,5,329,2011,67.6\n2011-11-26,108,6,330,2011,69.7\n2011-11-27,88,7,331,2011,70.73333333333333\n2011-11-28,64,1,332,2011,71.1\n2011-11-29,72,2,333,2011,71.83333333333333\n2011-11-30,76,3,334,2011,71.4\n2011-12-01,107,4,335,2011,72.93333333333334\n2011-12-02,73,5,336,2011,72.76666666666667\n2011-12-03,65,6,337,2011,72.46666666666667\n2011-12-04,74,7,338,2011,72.1\n2011-12-05,80,1,339,2011,71.96666666666667\n2011-12-06,116,2,340,2011,74.4\n2011-12-07,96,3,341,2011,75.83333333333333\n2011-12-08,113,4,342,2011,78.0\n2011-12-09,101,5,343,2011,79.0\n2011-12-10,88,6,344,2011,80.76666666666667\n2011-12-11,142,7,345,2011,83.1\n2011-12-12,121,1,346,2011,83.3\n2011-12-13,118,2,347,2011,84.23333333333333\n2011-12-14,86,3,348,2011,84.96666666666667\n2011-12-15,73,4,349,2011,85.76666666666667\n2011-12-16,84,5,350,2011,87.06666666666666\n2011-12-17,56,6,351,2011,86.3\n2011-12-18,86,7,352,2011,87.13333333333334\n2011-12-19,85,1,353,2011,87.26666666666667\n2011-12-20,89,2,354,2011,87.63333333333334\n2011-12-21,58,3,355,2011,87.46666666666667\n2011-12-22,46,4,356,2011,86.03333333333333\n2011-12-23,65,5,357,2011,86.0\n2011-12-24,39,6,358,2011,85.3\n2011-12-25,18,7,359,2011,82.9\n2011-12-26,39,1,360,2011,80.6\n2011-12-27,55,2,361,2011,79.5\n2011-12-28,47,3,362,2011,78.93333333333334\n2011-12-29,71,4,363,2011,78.9\n2011-12-30,85,5,364,2011,79.2\n2011-12-31,73,6,365,2011,78.06666666666666\n2012-01-01,56,7,1,2012,77.5\n2012-01-02,76,1,2,2012,77.86666666666666\n2012-01-03,60,2,3,2012,77.4\n2012-01-04,121,3,4,2012,78.76666666666667\n2012-01-05,77,4,5,2012,77.46666666666667\n2012-01-06,65,5,6,2012,76.43333333333334\n2012-01-07,60,6,7,2012,74.66666666666667\n2012-01-08,82,7,8,2012,74.03333333333333\n2012-01-09,72,1,9,2012,73.5\n2012-01-10,106,2,10,2012,72.3\n2012-01-11,96,3,11,2012,71.46666666666667\n2012-01-12,82,4,12,2012,70.26666666666667\n2012-01-13,145,5,13,2012,72.23333333333333\n2012-01-14,65,6,14,2012,71.96666666666667\n2012-01-15,64,7,15,2012,71.3\n2012-01-16,71,1,16,2012,71.8\n2012-01-17,79,2,17,2012,71.56666666666666\n2012-01-18,88,3,18,2012,71.66666666666667\n2012-01-19,82,4,19,2012,71.43333333333334\n2012-01-20,71,5,20,2012,71.86666666666666\n2012-01-21,57,6,21,2012,72.23333333333333\n2012-01-22,61,7,22,2012,72.1\n2012-01-23,69,1,23,2012,73.1\n2012-01-24,107,2,24,2012,76.06666666666666\n2012-01-25,99,3,25,2012,78.06666666666666\n2012-01-26,92,4,26,2012,79.3\n2012-01-27,70,5,27,2012,80.06666666666666\n2012-01-28,44,6,28,2012,79.16666666666667\n2012-01-29,84,7,29,2012,79.13333333333334\n2012-01-30,54,1,30,2012,78.5\n2012-01-31,71,2,31,2012,79.0\n2012-02-01,95,3,32,2012,79.63333333333334\n2012-02-02,86,4,33,2012,80.5\n2012-02-03,87,5,34,2012,79.36666666666666\n2012-02-04,82,6,35,2012,79.53333333333333\n2012-02-05,115,7,36,2012,81.2\n2012-02-06,189,1,37,2012,85.5\n2012-02-07,116,2,38,2012,86.63333333333334\n2012-02-08,122,3,39,2012,88.3\n2012-02-09,106,4,40,2012,88.3\n2012-02-10,97,5,41,2012,88.33333333333333\n2012-02-11,94,6,42,2012,88.73333333333333\n2012-02-12,90,7,43,2012,86.9\n2012-02-13,91,1,44,2012,87.76666666666667\n2012-02-14,106,2,45,2012,89.16666666666667\n2012-02-15,93,3,46,2012,89.9\n2012-02-16,119,4,47,2012,91.23333333333333\n2012-02-17,122,5,48,2012,92.36666666666666\n2012-02-18,109,6,49,2012,93.26666666666667\n2012-02-19,161,7,50,2012,96.26666666666667\n2012-02-20,120,1,51,2012,98.36666666666666\n2012-02-21,144,2,52,2012,101.13333333333334\n2012-02-22,117,3,53,2012,102.73333333333333\n2012-02-23,78,4,54,2012,101.76666666666667\n2012-02-24,68,5,55,2012,100.73333333333333\n2012-02-25,104,6,56,2012,101.13333333333334\n2012-02-26,81,7,57,2012,101.5\n2012-02-27,87,1,58,2012,102.93333333333334\n2012-02-28,110,2,59,2012,103.8\n2012-02-29,71,3,60,2012,104.36666666666666\n2012-03-01,83,4,61,2012,104.76666666666667\n2012-03-02,65,5,62,2012,103.76666666666667\n2012-03-03,82,6,63,2012,103.63333333333334\n2012-03-04,133,7,64,2012,105.16666666666667\n2012-03-05,139,1,65,2012,107.06666666666666\n2012-03-06,107,2,66,2012,106.8\n2012-03-07,77,3,67,2012,103.06666666666666\n2012-03-08,102,4,68,2012,102.6\n2012-03-09,111,5,69,2012,102.23333333333333\n2012-03-10,100,6,70,2012,102.03333333333333\n2012-03-11,166,7,71,2012,104.33333333333333\n2012-03-12,78,1,72,2012,103.8\n2012-03-13,100,2,73,2012,104.13333333333334\n2012-03-14,57,3,74,2012,103.0\n2012-03-15,53,4,75,2012,101.23333333333333\n2012-03-16,99,5,76,2012,101.43333333333334\n2012-03-17,88,6,77,2012,100.4\n2012-03-18,67,7,78,2012,98.56666666666666\n2012-03-19,160,1,79,2012,100.26666666666667\n2012-03-20,100,2,80,2012,98.23333333333333\n2012-03-21,101,3,81,2012,97.6\n2012-03-22,99,4,82,2012,96.1\n2012-03-23,123,5,83,2012,96.3\n2012-03-24,93,6,84,2012,96.8\n2012-03-25,142,7,85,2012,99.26666666666667\n2012-03-26,111,1,86,2012,99.5\n2012-03-27,84,2,87,2012,99.6\n2012-03-28,67,3,88,2012,98.93333333333334\n2012-03-29,76,4,89,2012,97.8\n2012-03-30,99,5,90,2012,98.73333333333333\n2012-03-31,109,6,91,2012,99.6\n2012-04-01,118,7,92,2012,101.36666666666666\n2012-04-02,124,1,93,2012,102.76666666666667\n2012-04-03,109,2,94,2012,101.96666666666667\n2012-04-04,175,3,95,2012,103.16666666666667\n2012-04-05,118,4,96,2012,103.53333333333333\n2012-04-06,92,5,97,2012,104.03333333333333\n2012-04-07,147,6,98,2012,105.53333333333333\n2012-04-08,80,7,99,2012,104.5\n2012-04-09,135,1,100,2012,105.66666666666667\n2012-04-10,120,2,101,2012,104.13333333333334\n2012-04-11,166,3,102,2012,107.06666666666666\n2012-04-12,77,4,103,2012,106.3\n2012-04-13,67,5,104,2012,106.63333333333334\n2012-04-14,94,6,105,2012,108.0\n2012-04-15,102,7,106,2012,108.1\n2012-04-16,123,1,107,2012,109.26666666666667\n2012-04-17,88,2,108,2012,109.96666666666667\n2012-04-18,130,3,109,2012,108.96666666666667\n2012-04-19,86,4,110,2012,108.5\n2012-04-20,108,5,111,2012,108.73333333333333\n2012-04-21,117,6,112,2012,109.33333333333333\n2012-04-22,95,7,113,2012,108.4\n2012-04-23,112,1,114,2012,109.03333333333333\n2012-04-24,106,2,115,2012,107.83333333333333\n2012-04-25,95,3,116,2012,107.3\n2012-04-26,85,4,117,2012,107.33333333333333\n2012-04-27,107,5,118,2012,108.66666666666667\n2012-04-28,120,6,119,2012,110.13333333333334\n2012-04-29,165,7,120,2012,112.33333333333333\n2012-04-30,127,1,121,2012,112.93333333333334\n2012-05-01,86,2,122,2012,111.86666666666666\n2012-05-02,107,3,123,2012,111.3\n2012-05-03,92,4,124,2012,110.73333333333333\n2012-05-04,107,5,125,2012,108.46666666666667\n2012-05-05,80,6,126,2012,107.2\n2012-05-06,103,7,127,2012,107.56666666666666\n2012-05-07,131,1,128,2012,107.03333333333333\n2012-05-08,73,2,129,2012,106.8\n2012-05-09,105,3,130,2012,105.8\n2012-05-10,81,4,131,2012,104.5\n2012-05-11,140,5,132,2012,103.63333333333334\n2012-05-12,83,6,133,2012,103.83333333333333\n2012-05-13,109,7,134,2012,105.23333333333333\n2012-05-14,67,1,135,2012,104.33333333333333\n2012-05-15,71,2,136,2012,103.3\n2012-05-16,86,3,137,2012,102.06666666666666\n2012-05-17,118,4,138,2012,103.06666666666666\n2012-05-18,101,5,139,2012,102.1\n2012-05-19,77,6,140,2012,101.8\n2012-05-20,110,7,141,2012,101.86666666666666\n2012-05-21,77,1,142,2012,100.53333333333333\n2012-05-22,81,2,143,2012,100.06666666666666\n2012-05-23,70,3,144,2012,98.66666666666667\n2012-05-24,79,4,145,2012,97.76666666666667\n2012-05-25,60,5,146,2012,96.6\n2012-05-26,65,6,147,2012,95.93333333333334\n2012-05-27,46,7,148,2012,93.9\n2012-05-28,74,1,149,2012,92.36666666666666\n2012-05-29,48,2,150,2012,88.46666666666667\n2012-05-30,90,3,151,2012,87.23333333333333\n2012-05-31,95,4,152,2012,87.53333333333333\n2012-06-01,84,5,153,2012,86.76666666666667\n2012-06-02,31,6,154,2012,84.73333333333333\n2012-06-03,73,7,155,2012,83.6\n2012-06-04,98,1,156,2012,84.2\n2012-06-05,63,2,157,2012,82.86666666666666\n2012-06-06,66,3,158,2012,80.7\n2012-06-07,57,4,159,2012,80.16666666666667\n2012-06-08,78,5,160,2012,79.26666666666667\n2012-06-09,54,6,161,2012,78.36666666666666\n2012-06-10,122,7,162,2012,77.76666666666667\n2012-06-11,95,1,163,2012,78.16666666666667\n2012-06-12,87,2,164,2012,77.43333333333334\n2012-06-13,113,3,165,2012,78.96666666666667\n2012-06-14,79,4,166,2012,79.23333333333333\n2012-06-15,107,5,167,2012,79.93333333333334\n2012-06-16,106,6,168,2012,79.53333333333333\n2012-06-17,96,7,169,2012,79.36666666666666\n2012-06-18,55,1,170,2012,78.63333333333334\n2012-06-19,79,2,171,2012,77.6\n2012-06-20,94,3,172,2012,78.16666666666667\n2012-06-21,54,4,173,2012,77.26666666666667\n2012-06-22,44,5,174,2012,76.4\n2012-06-23,67,6,175,2012,76.0\n2012-06-24,64,7,176,2012,76.13333333333334\n2012-06-25,96,1,177,2012,77.16666666666667\n2012-06-26,73,2,178,2012,78.06666666666666\n2012-06-27,108,3,179,2012,79.2\n2012-06-28,40,4,180,2012,78.93333333333334\n2012-06-29,87,5,181,2012,78.83333333333333\n2012-06-30,44,6,182,2012,77.13333333333334\n2012-07-01,61,7,183,2012,76.36666666666666\n2012-07-02,91,1,184,2012,78.36666666666666\n2012-07-03,118,2,185,2012,79.86666666666666\n2012-07-04,96,3,186,2012,79.8\n2012-07-05,123,4,187,2012,81.8\n2012-07-06,170,5,188,2012,85.26666666666667\n2012-07-07,117,6,189,2012,87.26666666666667\n2012-07-08,136,7,190,2012,89.2\n2012-07-09,81,1,191,2012,90.1\n2012-07-10,74,2,192,2012,88.5\n2012-07-11,96,3,193,2012,88.53333333333333\n2012-07-12,97,4,194,2012,88.86666666666666\n2012-07-13,74,5,195,2012,87.56666666666666\n2012-07-14,83,6,196,2012,87.7\n2012-07-15,64,7,197,2012,86.26666666666667\n2012-07-16,95,1,198,2012,85.9\n2012-07-17,119,2,199,2012,86.66666666666667\n2012-07-18,102,3,200,2012,88.23333333333333\n2012-07-19,70,4,201,2012,87.93333333333334\n2012-07-20,66,5,202,2012,87.0\n2012-07-21,102,6,203,2012,88.6\n2012-07-22,96,7,204,2012,90.33333333333333\n2012-07-23,107,1,205,2012,91.66666666666667\n2012-07-24,100,2,206,2012,92.86666666666666\n2012-07-25,76,3,207,2012,92.2\n2012-07-26,96,4,208,2012,92.96666666666667\n2012-07-27,81,5,209,2012,92.06666666666666\n2012-07-28,93,6,210,2012,93.83333333333333\n2012-07-29,74,7,211,2012,93.4\n2012-07-30,61,1,212,2012,93.96666666666667\n2012-07-31,73,2,213,2012,94.36666666666666\n2012-08-01,100,3,214,2012,94.66666666666667\n2012-08-02,128,4,215,2012,95.0\n2012-08-03,79,5,216,2012,94.43333333333334\n2012-08-04,106,6,217,2012,93.86666666666666\n2012-08-05,72,7,218,2012,90.6\n2012-08-06,109,1,219,2012,90.33333333333333\n2012-08-07,107,2,220,2012,89.36666666666666\n2012-08-08,119,3,221,2012,90.63333333333334\n2012-08-09,82,4,222,2012,90.9\n2012-08-10,100,5,223,2012,91.03333333333333\n2012-08-11,60,6,224,2012,89.8\n2012-08-12,77,7,225,2012,89.9\n2012-08-13,68,1,226,2012,89.4\n2012-08-14,88,2,227,2012,90.2\n2012-08-15,116,3,228,2012,90.9\n2012-08-16,94,4,229,2012,90.06666666666666\n2012-08-17,99,5,230,2012,89.96666666666667\n2012-08-18,141,6,231,2012,92.33333333333333\n2012-08-19,46,7,232,2012,91.66666666666667\n2012-08-20,61,1,233,2012,90.3\n2012-08-21,75,2,234,2012,89.6\n2012-08-22,84,3,235,2012,88.83333333333333\n2012-08-23,76,4,236,2012,88.03333333333333\n2012-08-24,102,5,237,2012,88.9\n2012-08-25,71,6,238,2012,88.06666666666666\n2012-08-26,83,7,239,2012,88.13333333333334\n2012-08-27,91,1,240,2012,88.06666666666666\n2012-08-28,80,2,241,2012,88.26666666666667\n2012-08-29,60,3,242,2012,88.23333333333333\n2012-08-30,78,4,243,2012,88.4\n2012-08-31,61,5,244,2012,87.1\n2012-09-01,57,6,245,2012,84.73333333333333\n2012-09-02,41,7,246,2012,83.46666666666667\n2012-09-03,86,1,247,2012,82.8\n2012-09-04,88,2,248,2012,83.33333333333333\n2012-09-05,73,3,249,2012,82.13333333333334\n2012-09-06,100,4,250,2012,81.9\n2012-09-07,106,5,251,2012,81.46666666666667\n2012-09-08,57,6,252,2012,80.63333333333334\n2012-09-09,40,7,253,2012,78.63333333333334\n2012-09-10,65,1,254,2012,78.8\n2012-09-11,59,2,255,2012,78.2\n2012-09-12,99,3,256,2012,79.23333333333333\n2012-09-13,55,4,257,2012,78.13333333333334\n2012-09-14,64,5,258,2012,76.4\n2012-09-15,40,6,259,2012,74.6\n2012-09-16,52,7,260,2012,73.03333333333333\n2012-09-17,57,1,261,2012,70.23333333333333\n2012-09-18,51,2,262,2012,70.4\n2012-09-19,38,3,263,2012,69.63333333333334\n2012-09-20,47,4,264,2012,68.7\n2012-09-21,53,5,265,2012,67.66666666666667\n2012-09-22,69,6,266,2012,67.43333333333334\n2012-09-23,40,7,267,2012,65.36666666666666\n2012-09-24,32,1,268,2012,64.06666666666666\n2012-09-25,45,2,269,2012,62.8\n2012-09-26,54,3,270,2012,61.56666666666667\n2012-09-27,59,4,271,2012,60.86666666666667\n2012-09-28,61,5,272,2012,60.9\n2012-09-29,58,6,273,2012,60.233333333333334\n2012-09-30,62,7,274,2012,60.266666666666666\n2012-10-01,96,1,275,2012,61.56666666666667\n2012-10-02,101,2,276,2012,63.56666666666667\n2012-10-03,98,3,277,2012,63.96666666666667\n2012-10-04,78,4,278,2012,63.63333333333333\n2012-10-05,107,5,279,2012,64.76666666666667\n2012-10-06,59,6,280,2012,63.4\n2012-10-07,48,7,281,2012,61.46666666666667\n2012-10-08,60,1,282,2012,61.56666666666667\n2012-10-09,76,2,283,2012,62.766666666666666\n2012-10-10,126,3,284,2012,64.8\n2012-10-11,58,4,285,2012,64.76666666666667\n2012-10-12,70,5,286,2012,63.8\n2012-10-13,37,6,287,2012,63.2\n2012-10-14,70,7,288,2012,63.4\n2012-10-15,79,1,289,2012,64.7\n2012-10-16,77,2,290,2012,65.53333333333333\n2012-10-17,33,3,291,2012,64.73333333333333\n2012-10-18,86,4,292,2012,65.9\n2012-10-19,62,5,293,2012,66.7\n2012-10-20,36,6,294,2012,66.33333333333333\n2012-10-21,18,7,295,2012,65.16666666666667\n2012-10-22,55,1,296,2012,64.7\n2012-10-23,78,2,297,2012,65.96666666666667\n2012-10-24,58,3,298,2012,66.83333333333333\n2012-10-25,87,4,299,2012,68.23333333333333\n2012-10-26,112,5,300,2012,70.16666666666667\n2012-10-27,48,6,301,2012,69.8\n2012-10-28,53,7,302,2012,69.53333333333333\n2012-10-29,38,1,303,2012,68.86666666666666\n2012-10-30,92,2,304,2012,69.86666666666666\n2012-10-31,54,3,305,2012,68.46666666666667\n2012-11-01,109,4,306,2012,68.73333333333333\n2012-11-02,119,5,307,2012,69.43333333333334\n2012-11-03,71,6,308,2012,69.2\n2012-11-04,59,7,309,2012,67.6\n2012-11-05,91,1,310,2012,68.66666666666667\n2012-11-06,39,2,311,2012,68.36666666666666\n2012-11-07,56,3,312,2012,68.23333333333333\n2012-11-08,66,4,313,2012,67.9\n2012-11-09,56,5,314,2012,65.56666666666666\n2012-11-10,39,6,315,2012,64.93333333333334\n2012-11-11,20,7,316,2012,63.266666666666666\n2012-11-12,68,1,317,2012,64.3\n2012-11-13,66,2,318,2012,64.16666666666667\n2012-11-14,58,3,319,2012,63.46666666666667\n2012-11-15,47,4,320,2012,62.46666666666667\n2012-11-16,70,5,321,2012,63.7\n2012-11-17,67,6,322,2012,63.06666666666667\n2012-11-18,38,7,323,2012,62.266666666666666\n2012-11-19,95,1,324,2012,64.23333333333333\n2012-11-20,114,2,325,2012,67.43333333333334\n2012-11-21,87,3,326,2012,68.5\n2012-11-22,49,4,327,2012,67.53333333333333\n2012-11-23,80,5,328,2012,68.26666666666667\n2012-11-24,70,6,329,2012,67.7\n2012-11-25,35,7,330,2012,65.13333333333334\n2012-11-26,71,1,331,2012,65.9\n2012-11-27,79,2,332,2012,66.76666666666667\n2012-11-28,64,3,333,2012,67.63333333333334\n2012-11-29,58,4,334,2012,66.5\n2012-11-30,36,5,335,2012,65.9\n2012-12-01,56,6,336,2012,64.13333333333334\n2012-12-02,58,7,337,2012,62.1\n2012-12-03,84,1,338,2012,62.53333333333333\n2012-12-04,103,2,339,2012,64.0\n2012-12-05,118,3,340,2012,64.9\n2012-12-06,46,4,341,2012,65.13333333333334\n2012-12-07,58,5,342,2012,65.2\n2012-12-08,98,6,343,2012,66.26666666666667\n2012-12-09,43,7,344,2012,65.83333333333333\n2012-12-10,70,1,345,2012,66.86666666666666\n2012-12-11,91,2,346,2012,69.23333333333333\n2012-12-12,74,3,347,2012,69.43333333333334\n2012-12-13,88,4,348,2012,70.16666666666667\n2012-12-14,74,5,349,2012,70.7\n2012-12-15,54,6,350,2012,70.93333333333334\n2012-12-16,81,7,351,2012,71.3\n2012-12-17,121,1,352,2012,73.1\n2012-12-18,111,2,353,2012,75.53333333333333\n2012-12-19,112,3,354,2012,76.1\n2012-12-20,103,4,355,2012,75.73333333333333\n2012-12-21,63,5,356,2012,74.93333333333334\n2012-12-22,59,6,357,2012,75.26666666666667\n2012-12-23,91,7,358,2012,75.63333333333334\n2012-12-24,99,1,359,2012,76.6\n2012-12-25,60,2,360,2012,77.43333333333334\n2012-12-26,61,3,361,2012,77.1\n2012-12-27,90,4,362,2012,77.46666666666667\n2012-12-28,59,5,363,2012,77.3\n2012-12-29,69,6,364,2012,77.66666666666667\n2012-12-30,66,7,365,2012,78.66666666666667\n2012-12-31,110,1,366,2012,80.46666666666667\n2013-01-01,65,2,1,2013,80.7\n2013-01-02,73,3,2,2013,80.33333333333333\n2013-01-03,92,4,3,2013,79.96666666666667\n2013-01-04,93,5,4,2013,79.13333333333334\n2013-01-05,67,6,5,2013,79.83333333333333\n2013-01-06,84,7,6,2013,80.7\n2013-01-07,176,1,7,2013,83.3\n2013-01-08,150,2,8,2013,86.86666666666666\n2013-01-09,143,3,9,2013,89.3\n2013-01-10,195,4,10,2013,92.76666666666667\n2013-01-11,158,5,11,2013,95.56666666666666\n2013-01-12,99,6,12,2013,95.93333333333334\n2013-01-13,156,7,13,2013,98.66666666666667\n2013-01-14,114,1,14,2013,100.66666666666667\n2013-01-15,109,2,15,2013,101.6\n2013-01-16,182,3,16,2013,103.63333333333334\n2013-01-17,139,4,17,2013,104.56666666666666\n2013-01-18,96,5,18,2013,104.03333333333333\n2013-01-19,82,6,19,2013,103.33333333333333\n2013-01-20,116,7,20,2013,105.1\n2013-01-21,88,1,21,2013,106.06666666666666\n2013-01-22,124,2,22,2013,107.16666666666667\n2013-01-23,120,3,23,2013,107.86666666666666\n2013-01-24,108,4,24,2013,109.46666666666667\n2013-01-25,143,5,25,2013,112.2\n2013-01-26,142,6,26,2013,113.93333333333334\n2013-01-27,69,7,27,2013,114.26666666666667\n2013-01-28,128,1,28,2013,116.23333333333333\n2013-01-29,114,2,29,2013,117.83333333333333\n2013-01-30,120,3,30,2013,118.16666666666667\n2013-01-31,96,4,31,2013,119.2\n2013-02-01,69,5,32,2013,119.06666666666666\n2013-02-02,104,6,33,2013,119.46666666666667\n2013-02-03,156,7,34,2013,121.56666666666666\n2013-02-04,90,1,35,2013,122.33333333333333\n2013-02-05,116,2,36,2013,123.4\n2013-02-06,81,3,37,2013,120.23333333333333\n2013-02-07,117,4,38,2013,119.13333333333334\n2013-02-08,123,5,39,2013,118.46666666666667\n2013-02-09,80,6,40,2013,114.63333333333334\n2013-02-10,83,7,41,2013,112.13333333333334\n2013-02-11,100,1,42,2013,112.16666666666667\n2013-02-12,115,2,43,2013,110.8\n2013-02-13,153,3,44,2013,112.1\n2013-02-14,95,4,45,2013,111.63333333333334\n2013-02-15,146,5,46,2013,110.43333333333334\n2013-02-16,111,6,47,2013,109.5\n2013-02-17,118,7,48,2013,110.23333333333333\n2013-02-18,119,1,49,2013,111.46666666666667\n2013-02-19,120,2,50,2013,111.6\n2013-02-20,142,3,51,2013,113.4\n2013-02-21,127,4,52,2013,113.5\n2013-02-22,120,5,53,2013,113.5\n2013-02-23,44,6,54,2013,111.36666666666666\n2013-02-24,131,7,55,2013,110.96666666666667\n2013-02-25,166,1,56,2013,111.76666666666667\n2013-02-26,176,2,57,2013,115.33333333333333\n2013-02-27,113,3,58,2013,114.83333333333333\n2013-02-28,116,4,59,2013,114.9\n2013-03-01,112,5,60,2013,114.63333333333334\n2013-03-02,72,6,61,2013,113.83333333333333\n2013-03-03,73,7,62,2013,113.96666666666667\n2013-03-04,123,1,63,2013,114.6\n2013-03-05,111,2,64,2013,113.1\n2013-03-06,102,3,65,2013,113.5\n2013-03-07,99,4,66,2013,112.93333333333334\n2013-03-08,109,5,67,2013,113.86666666666666\n2013-03-09,108,6,68,2013,113.56666666666666\n2013-03-10,130,7,69,2013,113.8\n2013-03-11,121,1,70,2013,115.16666666666667\n2013-03-12,85,2,71,2013,115.23333333333333\n2013-03-13,118,3,72,2013,115.83333333333333\n2013-03-14,129,4,73,2013,116.3\n2013-03-15,139,5,74,2013,115.83333333333333\n2013-03-16,98,6,75,2013,115.93333333333334\n2013-03-17,137,7,76,2013,115.63333333333334\n2013-03-18,139,1,77,2013,116.56666666666666\n2013-03-19,114,2,78,2013,116.43333333333334\n2013-03-20,153,3,79,2013,117.56666666666666\n2013-03-21,88,4,80,2013,116.5\n2013-03-22,151,5,81,2013,116.8\n2013-03-23,105,6,82,2013,116.06666666666666\n2013-03-24,107,7,83,2013,115.63333333333334\n2013-03-25,137,1,84,2013,118.73333333333333\n2013-03-26,114,2,85,2013,118.16666666666667\n2013-03-27,107,3,86,2013,116.2\n2013-03-28,113,4,87,2013,114.1\n2013-03-29,150,5,88,2013,115.33333333333333\n2013-03-30,83,6,89,2013,114.23333333333333\n2013-03-31,95,7,90,2013,113.66666666666667\n2013-04-01,124,1,91,2013,115.4\n2013-04-02,132,2,92,2013,117.36666666666666\n2013-04-03,116,3,93,2013,117.13333333333334\n2013-04-04,135,4,94,2013,117.93333333333334\n2013-04-05,80,5,95,2013,117.2\n2013-04-06,90,6,96,2013,116.9\n2013-04-07,149,7,97,2013,118.23333333333333\n2013-04-08,178,1,98,2013,120.56666666666666\n2013-04-09,164,2,99,2013,121.7\n2013-04-10,120,3,100,2013,121.66666666666667\n2013-04-11,111,4,101,2013,122.53333333333333\n2013-04-12,138,5,102,2013,123.2\n2013-04-13,123,6,103,2013,123.0\n2013-04-14,132,7,104,2013,122.76666666666667\n2013-04-15,111,1,105,2013,123.2\n2013-04-16,90,2,106,2013,121.63333333333334\n2013-04-17,90,3,107,2013,120.0\n2013-04-18,143,4,108,2013,120.96666666666667\n2013-04-19,110,5,109,2013,119.53333333333333\n2013-04-20,79,6,110,2013,119.23333333333333\n2013-04-21,128,7,111,2013,118.46666666666667\n2013-04-22,93,1,112,2013,118.06666666666666\n2013-04-23,70,2,113,2013,116.83333333333333\n2013-04-24,85,3,114,2013,115.1\n2013-04-25,83,4,115,2013,114.06666666666666\n2013-04-26,95,5,116,2013,113.66666666666667\n2013-04-27,82,6,117,2013,112.63333333333334\n2013-04-28,96,7,118,2013,110.83333333333333\n2013-04-29,91,1,119,2013,111.1\n2013-04-30,130,2,120,2013,112.26666666666667\n2013-05-01,117,3,121,2013,112.03333333333333\n2013-05-02,134,4,122,2013,112.1\n2013-05-03,113,5,123,2013,112.0\n2013-05-04,97,6,124,2013,110.73333333333333\n2013-05-05,124,7,125,2013,112.2\n2013-05-06,120,1,126,2013,113.2\n2013-05-07,98,2,127,2013,111.5\n2013-05-08,112,3,128,2013,109.3\n2013-05-09,155,4,129,2013,109.0\n2013-05-10,135,5,130,2013,109.5\n2013-05-11,88,6,131,2013,108.73333333333333\n2013-05-12,64,7,132,2013,106.26666666666667\n2013-05-13,123,1,133,2013,106.26666666666667\n2013-05-14,88,2,134,2013,104.8\n2013-05-15,162,3,135,2013,106.5\n2013-05-16,136,4,136,2013,108.03333333333333\n2013-05-17,143,5,137,2013,109.8\n2013-05-18,71,6,138,2013,107.4\n2013-05-19,89,7,139,2013,106.7\n2013-05-20,106,1,140,2013,107.6\n2013-05-21,136,2,141,2013,107.86666666666666\n2013-05-22,115,3,142,2013,108.6\n2013-05-23,91,4,143,2013,109.3\n2013-05-24,148,5,144,2013,111.4\n2013-05-25,70,6,145,2013,110.96666666666667\n2013-05-26,47,7,146,2013,109.36666666666666\n2013-05-27,135,1,147,2013,111.13333333333334\n2013-05-28,150,2,148,2013,112.93333333333334\n2013-05-29,88,3,149,2013,112.83333333333333\n2013-05-30,102,4,150,2013,111.9\n2013-05-31,82,5,151,2013,110.73333333333333\n2013-06-01,79,6,152,2013,108.9\n2013-06-02,86,7,153,2013,108.0\n2013-06-03,87,1,154,2013,107.66666666666667\n2013-06-04,100,2,155,2013,106.86666666666666\n2013-06-05,121,3,156,2013,106.9\n2013-06-06,112,4,157,2013,107.36666666666666\n2013-06-07,167,5,158,2013,109.2\n2013-06-08,103,6,159,2013,107.46666666666667\n2013-06-09,83,7,160,2013,105.73333333333333\n2013-06-10,132,1,161,2013,107.2\n2013-06-11,109,2,162,2013,108.7\n2013-06-12,133,3,163,2013,109.03333333333333\n2013-06-13,160,4,164,2013,111.43333333333334\n2013-06-14,178,5,165,2013,111.96666666666667\n2013-06-15,73,6,166,2013,109.86666666666666\n2013-06-16,138,7,167,2013,109.7\n2013-06-17,111,1,168,2013,111.03333333333333\n2013-06-18,112,2,169,2013,111.8\n2013-06-19,126,3,170,2013,112.46666666666667\n2013-06-20,146,4,171,2013,112.8\n2013-06-21,122,5,172,2013,113.03333333333333\n2013-06-22,122,6,173,2013,114.06666666666666\n2013-06-23,98,7,174,2013,112.4\n2013-06-24,86,1,175,2013,112.93333333333334\n2013-06-25,128,2,176,2013,115.63333333333334\n2013-06-26,160,3,177,2013,116.46666666666667\n2013-06-27,115,4,178,2013,115.3\n2013-06-28,103,5,179,2013,115.8\n2013-06-29,57,6,180,2013,114.3\n2013-06-30,76,7,181,2013,114.1\n2013-07-01,132,1,182,2013,115.86666666666666\n2013-07-02,134,2,183,2013,117.46666666666667\n2013-07-03,95,3,184,2013,117.73333333333333\n2013-07-04,62,4,185,2013,116.46666666666667\n2013-07-05,131,5,186,2013,116.8\n2013-07-06,90,6,187,2013,116.06666666666666\n2013-07-07,92,7,188,2013,113.56666666666666\n2013-07-08,142,1,189,2013,114.86666666666666\n2013-07-09,111,2,190,2013,115.8\n2013-07-10,109,3,191,2013,115.03333333333333\n2013-07-11,93,4,192,2013,114.5\n2013-07-12,104,5,193,2013,113.53333333333333\n2013-07-13,39,6,194,2013,109.5\n2013-07-14,67,7,195,2013,105.8\n2013-07-15,125,1,196,2013,107.53333333333333\n2013-07-16,114,2,197,2013,106.73333333333333\n2013-07-17,89,3,198,2013,106.0\n2013-07-18,107,4,199,2013,105.83333333333333\n2013-07-19,142,5,200,2013,106.36666666666666\n2013-07-20,50,6,201,2013,103.16666666666667\n2013-07-21,58,7,202,2013,101.03333333333333\n2013-07-22,166,1,203,2013,102.5\n2013-07-23,149,2,204,2013,104.2\n2013-07-24,169,3,205,2013,106.96666666666667\n2013-07-25,71,4,206,2013,105.06666666666666\n2013-07-26,160,5,207,2013,105.06666666666666\n2013-07-27,50,6,208,2013,102.9\n2013-07-28,100,7,209,2013,102.8\n2013-07-29,108,1,210,2013,104.5\n2013-07-30,206,2,211,2013,108.83333333333333\n2013-07-31,181,3,212,2013,110.46666666666667\n2013-08-01,188,4,213,2013,112.26666666666667\n2013-08-02,143,5,214,2013,113.86666666666666\n2013-08-03,121,6,215,2013,115.83333333333333\n2013-08-04,82,7,216,2013,114.2\n2013-08-05,117,1,217,2013,115.1\n2013-08-06,138,2,218,2013,116.63333333333334\n2013-08-07,143,3,219,2013,116.66666666666667\n2013-08-08,117,4,220,2013,116.86666666666666\n2013-08-09,149,5,221,2013,118.2\n2013-08-10,69,6,222,2013,117.4\n2013-08-11,68,7,223,2013,116.2\n2013-08-12,98,1,224,2013,118.16666666666667\n2013-08-13,89,2,225,2013,118.9\n2013-08-14,108,3,226,2013,118.33333333333333\n2013-08-15,115,4,227,2013,118.36666666666666\n2013-08-16,99,5,228,2013,118.7\n2013-08-17,62,6,229,2013,117.2\n2013-08-18,66,7,230,2013,114.66666666666667\n2013-08-19,157,1,231,2013,118.23333333333333\n2013-08-20,126,2,232,2013,120.5\n2013-08-21,129,3,233,2013,119.26666666666667\n2013-08-22,122,4,234,2013,118.36666666666666\n2013-08-23,124,5,235,2013,116.86666666666666\n2013-08-24,101,6,236,2013,117.86666666666666\n2013-08-25,109,7,237,2013,116.16666666666667\n2013-08-26,175,1,238,2013,120.33333333333333\n2013-08-27,155,2,239,2013,122.16666666666667\n2013-08-28,159,3,240,2013,123.86666666666666\n2013-08-29,116,4,241,2013,120.86666666666666\n2013-08-30,133,5,242,2013,119.26666666666667\n2013-08-31,112,6,243,2013,116.73333333333333\n2013-09-01,103,7,244,2013,115.4\n2013-09-02,83,1,245,2013,114.13333333333334\n2013-09-03,115,2,246,2013,115.23333333333333\n2013-09-04,141,3,247,2013,116.03333333333333\n2013-09-05,115,4,248,2013,115.26666666666667\n2013-09-06,77,5,249,2013,113.06666666666666\n2013-09-07,99,6,250,2013,112.46666666666667\n2013-09-08,93,7,251,2013,110.6\n2013-09-09,163,1,252,2013,113.73333333333333\n2013-09-10,143,2,253,2013,116.23333333333333\n2013-09-11,86,3,254,2013,115.83333333333333\n2013-09-12,137,4,255,2013,117.43333333333334\n2013-09-13,135,5,256,2013,118.33333333333333\n2013-09-14,83,6,257,2013,117.26666666666667\n2013-09-15,130,7,258,2013,118.3\n2013-09-16,123,1,259,2013,120.33333333333333\n2013-09-17,104,2,260,2013,121.6\n2013-09-18,97,3,261,2013,119.6\n2013-09-19,104,4,262,2013,118.86666666666666\n2013-09-20,118,5,263,2013,118.5\n2013-09-21,88,6,264,2013,117.36666666666666\n2013-09-22,88,7,265,2013,116.16666666666667\n2013-09-23,105,1,266,2013,116.3\n2013-09-24,219,2,267,2013,119.96666666666667\n2013-09-25,188,3,268,2013,120.4\n2013-09-26,108,4,269,2013,118.83333333333333\n2013-09-27,123,5,270,2013,117.63333333333334\n2013-09-28,81,6,271,2013,116.46666666666667\n2013-09-29,83,7,272,2013,114.8\n2013-09-30,99,1,273,2013,114.36666666666666\n2013-10-01,80,2,274,2013,113.6\n2013-10-02,99,3,275,2013,114.13333333333334\n2013-10-03,110,4,276,2013,113.96666666666667\n2013-10-04,121,5,277,2013,113.3\n2013-10-05,103,6,278,2013,112.9\n2013-10-06,141,7,279,2013,115.03333333333333\n2013-10-07,155,1,280,2013,116.9\n2013-10-08,177,2,281,2013,119.7\n2013-10-09,117,3,282,2013,118.16666666666667\n2013-10-10,117,4,283,2013,117.3\n2013-10-11,202,5,284,2013,121.16666666666667\n2013-10-12,103,6,285,2013,120.03333333333333\n2013-10-13,140,7,286,2013,120.2\n2013-10-14,94,1,287,2013,120.56666666666666\n2013-10-15,128,2,288,2013,120.5\n2013-10-16,167,3,289,2013,121.96666666666667\n2013-10-17,96,4,290,2013,121.7\n2013-10-18,148,5,291,2013,123.4\n2013-10-19,89,6,292,2013,122.9\n2013-10-20,122,7,293,2013,123.03333333333333\n2013-10-21,113,1,294,2013,123.86666666666666\n2013-10-22,160,2,295,2013,126.26666666666667\n2013-10-23,115,3,296,2013,126.6\n2013-10-24,134,4,297,2013,123.76666666666667\n2013-10-25,160,5,298,2013,122.83333333333333\n2013-10-26,58,6,299,2013,121.16666666666667\n2013-10-27,110,7,300,2013,120.73333333333333\n2013-10-28,191,1,301,2013,124.4\n2013-10-29,113,2,302,2013,125.4\n2013-10-30,169,3,303,2013,127.73333333333333\n2013-10-31,143,4,304,2013,129.83333333333334\n2013-11-01,119,5,305,2013,130.5\n2013-11-02,161,6,306,2013,132.2\n2013-11-03,104,7,307,2013,131.63333333333333\n2013-11-04,103,1,308,2013,131.63333333333333\n2013-11-05,165,2,309,2013,132.43333333333334\n2013-11-06,121,3,310,2013,131.3\n2013-11-07,156,4,311,2013,130.6\n2013-11-08,177,5,312,2013,132.6\n2013-11-09,85,6,313,2013,131.53333333333333\n2013-11-10,81,7,314,2013,127.5\n2013-11-11,194,1,315,2013,130.53333333333333\n2013-11-12,180,2,316,2013,131.86666666666667\n2013-11-13,163,3,317,2013,134.16666666666666\n2013-11-14,106,4,318,2013,133.43333333333334\n2013-11-15,97,5,319,2013,131.1\n2013-11-16,39,6,320,2013,129.2\n2013-11-17,93,7,321,2013,127.36666666666666\n2013-11-18,127,1,322,2013,128.63333333333333\n2013-11-19,129,2,323,2013,128.86666666666667\n2013-11-20,126,3,324,2013,129.3\n2013-11-21,109,4,325,2013,127.6\n2013-11-22,124,5,326,2013,127.9\n2013-11-23,76,6,327,2013,125.96666666666667\n2013-11-24,107,7,328,2013,124.2\n2013-11-25,117,1,329,2013,126.16666666666667\n2013-11-26,136,2,330,2013,127.03333333333333\n2013-11-27,233,3,331,2013,128.43333333333334\n2013-11-28,37,4,332,2013,125.9\n2013-11-29,94,5,333,2013,123.4\n2013-11-30,138,6,334,2013,123.23333333333333\n2013-12-01,94,7,335,2013,122.4\n2013-12-02,119,1,336,2013,121.0\n2013-12-03,152,2,337,2013,122.6\n2013-12-04,123,3,338,2013,123.26666666666667\n2013-12-05,141,4,339,2013,122.46666666666667\n2013-12-06,144,5,340,2013,123.23333333333333\n2013-12-07,131,6,341,2013,122.4\n2013-12-08,116,7,342,2013,120.36666666666666\n2013-12-09,149,1,343,2013,122.5\n2013-12-10,173,2,344,2013,125.56666666666666\n2013-12-11,118,3,345,2013,123.03333333333333\n2013-12-12,172,4,346,2013,122.76666666666667\n2013-12-13,165,5,347,2013,122.83333333333333\n2013-12-14,115,6,348,2013,123.13333333333334\n2013-12-15,84,7,349,2013,122.7\n2013-12-16,122,1,350,2013,125.46666666666667\n2013-12-17,150,2,351,2013,127.36666666666666\n2013-12-18,124,3,352,2013,127.26666666666667\n2013-12-19,140,4,353,2013,127.63333333333334\n2013-12-20,131,5,354,2013,127.8\n2013-12-21,106,6,355,2013,127.7\n2013-12-22,97,7,356,2013,126.8\n2013-12-23,82,1,357,2013,127.0\n2013-12-24,50,2,358,2013,125.1\n2013-12-25,29,3,359,2013,122.16666666666667\n2013-12-26,60,4,360,2013,119.63333333333334\n2013-12-27,98,5,361,2013,115.13333333333334\n2013-12-28,66,6,362,2013,116.1\n2013-12-29,106,7,363,2013,116.5\n2013-12-30,173,1,364,2013,117.66666666666667\n2013-12-31,167,2,365,2013,120.1\n2014-01-01,74,3,1,2014,118.6\n2014-01-02,128,4,2,2014,117.8\n2014-01-03,201,5,3,2014,120.4\n2014-01-04,123,6,4,2014,119.8\n2014-01-05,93,7,5,2014,118.1\n2014-01-06,155,1,6,2014,118.9\n2014-01-07,237,2,7,2014,122.93333333333334\n2014-01-08,207,3,8,2014,124.86666666666666\n2014-01-09,202,4,9,2014,125.83333333333333\n2014-01-10,203,5,10,2014,128.66666666666666\n2014-01-11,124,6,11,2014,127.06666666666666\n2014-01-12,112,7,12,2014,125.3\n2014-01-13,135,1,13,2014,125.96666666666667\n2014-01-14,119,2,14,2014,127.13333333333334\n2014-01-15,186,3,15,2014,129.26666666666668\n2014-01-16,197,4,16,2014,130.83333333333334\n2014-01-17,107,5,17,2014,130.26666666666668\n2014-01-18,105,6,18,2014,129.1\n2014-01-19,150,7,19,2014,129.73333333333332\n2014-01-20,116,1,20,2014,130.06666666666666\n2014-01-21,143,2,21,2014,131.6\n2014-01-22,164,3,22,2014,134.33333333333334\n2014-01-23,234,4,23,2014,140.46666666666667\n2014-01-24,136,5,24,2014,144.03333333333333\n2014-01-25,123,6,25,2014,146.13333333333333\n2014-01-26,102,7,26,2014,146.26666666666668\n2014-01-27,164,1,27,2014,149.53333333333333\n2014-01-28,166,2,28,2014,151.53333333333333\n2014-01-29,151,3,29,2014,150.8\n2014-01-30,136,4,30,2014,149.76666666666668\n2014-01-31,102,5,31,2014,150.7\n2014-02-01,73,6,32,2014,148.86666666666667\n2014-02-02,122,7,33,2014,146.23333333333332\n2014-02-03,167,1,34,2014,147.7\n2014-02-04,209,2,35,2014,151.56666666666666\n2014-02-05,171,3,36,2014,152.1\n2014-02-06,161,4,37,2014,149.56666666666666\n2014-02-07,137,5,38,2014,147.23333333333332\n2014-02-08,131,6,39,2014,144.86666666666667\n2014-02-09,208,7,40,2014,145.03333333333333\n2014-02-10,227,1,41,2014,148.46666666666667\n2014-02-11,212,2,42,2014,151.8\n2014-02-12,135,3,43,2014,151.8\n2014-02-13,191,4,44,2014,154.2\n2014-02-14,161,5,45,2014,153.36666666666667\n2014-02-15,152,6,46,2014,151.86666666666667\n2014-02-16,101,7,47,2014,151.66666666666666\n2014-02-17,184,1,48,2014,154.3\n2014-02-18,307,2,49,2014,159.53333333333333\n2014-02-19,165,3,50,2014,161.16666666666666\n2014-02-20,122,4,51,2014,160.46666666666667\n2014-02-21,183,5,52,2014,161.1\n2014-02-22,139,6,53,2014,157.93333333333334\n2014-02-23,132,7,54,2014,157.8\n2014-02-24,181,1,55,2014,159.73333333333332\n2014-02-25,173,2,56,2014,162.1\n2014-02-26,161,3,57,2014,162.0\n2014-02-27,113,4,58,2014,160.23333333333332\n2014-02-28,103,5,59,2014,158.63333333333333\n2014-03-01,91,6,60,2014,157.13333333333333\n2014-03-02,76,7,61,2014,156.26666666666668\n2014-03-03,126,1,62,2014,158.03333333333333\n2014-03-04,109,2,63,2014,157.6\n2014-03-05,119,3,64,2014,156.0\n2014-03-06,162,4,65,2014,154.43333333333334\n2014-03-07,115,5,66,2014,152.56666666666666\n2014-03-08,118,6,67,2014,151.13333333333333\n2014-03-09,73,7,68,2014,149.0\n2014-03-10,140,1,69,2014,149.3\n2014-03-11,158,2,70,2014,147.63333333333333\n2014-03-12,119,3,71,2014,144.03333333333333\n2014-03-13,139,4,72,2014,141.6\n2014-03-14,179,5,73,2014,143.06666666666666\n2014-03-15,110,6,74,2014,140.36666666666667\n2014-03-16,80,7,75,2014,137.66666666666666\n2014-03-17,144,1,76,2014,137.4\n2014-03-18,114,2,77,2014,137.83333333333334\n2014-03-19,132,3,78,2014,136.1\n2014-03-20,129,4,79,2014,130.16666666666666\n2014-03-21,167,5,80,2014,130.23333333333332\n2014-03-22,132,6,81,2014,130.56666666666666\n2014-03-23,102,7,82,2014,127.86666666666666\n2014-03-24,187,1,83,2014,129.46666666666667\n2014-03-25,148,2,84,2014,130.0\n2014-03-26,223,3,85,2014,131.4\n2014-03-27,145,4,86,2014,130.46666666666667\n2014-03-28,162,5,87,2014,130.5\n2014-03-29,91,6,88,2014,129.76666666666668\n2014-03-30,100,7,89,2014,129.66666666666666\n2014-03-31,147,1,90,2014,131.53333333333333\n2014-04-01,116,2,91,2014,132.86666666666667\n2014-04-02,154,3,92,2014,133.8\n2014-04-03,107,4,93,2014,133.73333333333332\n2014-04-04,103,5,94,2014,133.2\n2014-04-05,94,6,95,2014,130.93333333333334\n2014-04-06,86,7,96,2014,129.96666666666667\n2014-04-07,140,1,97,2014,130.7\n2014-04-08,142,2,98,2014,133.0\n2014-04-09,118,3,99,2014,132.26666666666668\n2014-04-10,149,4,100,2014,131.96666666666667\n2014-04-11,90,5,101,2014,131.0\n2014-04-12,82,6,102,2014,129.1\n2014-04-13,94,7,103,2014,126.26666666666667\n2014-04-14,76,1,104,2014,125.13333333333334\n2014-04-15,128,2,105,2014,126.73333333333333\n2014-04-16,157,3,106,2014,127.16666666666667\n2014-04-17,130,4,107,2014,127.7\n2014-04-18,191,5,108,2014,129.66666666666666\n2014-04-19,127,6,109,2014,129.6\n2014-04-20,102,7,110,2014,127.43333333333334\n2014-04-21,179,1,111,2014,129.0\n2014-04-22,153,2,112,2014,130.7\n2014-04-23,167,3,113,2014,130.03333333333333\n2014-04-24,232,4,114,2014,132.83333333333334\n2014-04-25,182,5,115,2014,131.46666666666667\n2014-04-26,119,6,116,2014,130.6\n2014-04-27,187,7,117,2014,131.43333333333334\n2014-04-28,161,1,118,2014,133.76666666666668\n2014-04-29,190,2,119,2014,136.76666666666668\n2014-04-30,170,3,120,2014,137.53333333333333\n2014-05-01,137,4,121,2014,138.23333333333332\n2014-05-02,151,5,122,2014,138.13333333333333\n2014-05-03,107,6,123,2014,138.13333333333333\n2014-05-04,108,7,124,2014,138.3\n2014-05-05,193,1,125,2014,141.6\n2014-05-06,114,2,126,2014,142.53333333333333\n2014-05-07,247,3,127,2014,146.1\n2014-05-08,230,4,128,2014,149.03333333333333\n2014-05-09,264,5,129,2014,153.9\n2014-05-10,175,6,130,2014,154.76666666666668\n2014-05-11,127,7,131,2014,156.0\n2014-05-12,144,1,132,2014,158.06666666666666\n2014-05-13,212,2,133,2014,162.0\n2014-05-14,236,3,134,2014,167.33333333333334\n2014-05-15,154,4,135,2014,168.2\n2014-05-16,155,5,136,2014,168.13333333333333\n2014-05-17,140,6,137,2014,168.46666666666667\n2014-05-18,105,7,138,2014,165.6\n2014-05-19,145,1,139,2014,166.2\n2014-05-20,156,2,140,2014,168.0\n2014-05-21,149,3,141,2014,167.0\n2014-05-22,190,4,142,2014,168.23333333333332\n2014-05-23,196,5,143,2014,169.2\n2014-05-24,102,6,144,2014,164.86666666666667\n2014-05-25,150,7,145,2014,163.8\n2014-05-26,124,1,146,2014,163.96666666666667\n2014-05-27,134,2,147,2014,162.2\n2014-05-28,148,3,148,2014,161.76666666666668\n2014-05-29,185,4,149,2014,161.6\n2014-05-30,174,5,150,2014,161.73333333333332\n2014-05-31,119,6,151,2014,161.13333333333333\n2014-06-01,182,7,152,2014,162.16666666666666\n2014-06-02,133,1,153,2014,163.03333333333333\n2014-06-03,195,2,154,2014,165.93333333333334\n2014-06-04,183,3,155,2014,165.6\n2014-06-05,186,4,156,2014,168.0\n2014-06-06,254,5,157,2014,168.23333333333332\n2014-06-07,141,6,158,2014,165.26666666666668\n2014-06-08,130,7,159,2014,160.8\n2014-06-09,230,1,160,2014,162.63333333333333\n2014-06-10,203,2,161,2014,165.16666666666666\n2014-06-11,164,3,162,2014,165.83333333333334\n2014-06-12,212,4,163,2014,165.83333333333334\n2014-06-13,169,5,164,2014,163.6\n2014-06-14,129,6,165,2014,162.76666666666668\n2014-06-15,100,7,166,2014,160.93333333333334\n2014-06-16,160,1,167,2014,161.6\n2014-06-17,175,2,168,2014,163.93333333333334\n2014-06-18,154,3,169,2014,164.23333333333332\n2014-06-19,197,4,170,2014,165.6\n2014-06-20,146,5,171,2014,165.5\n2014-06-21,44,6,172,2014,160.63333333333333\n2014-06-22,81,7,173,2014,156.8\n2014-06-23,153,1,174,2014,158.5\n2014-06-24,174,2,175,2014,159.3\n2014-06-25,174,3,176,2014,160.96666666666667\n2014-06-26,168,4,177,2014,162.1\n2014-06-27,173,5,178,2014,162.93333333333334\n2014-06-28,96,6,179,2014,159.96666666666667\n2014-06-29,63,7,180,2014,156.26666666666668\n2014-06-30,139,1,181,2014,156.93333333333334\n2014-07-01,160,2,182,2014,156.2\n2014-07-02,179,3,183,2014,157.73333333333332\n2014-07-03,151,4,184,2014,156.26666666666668\n2014-07-04,134,5,185,2014,154.63333333333333\n2014-07-05,121,6,186,2014,152.46666666666667\n2014-07-06,144,7,187,2014,148.8\n2014-07-07,151,1,188,2014,149.13333333333333\n2014-07-08,120,2,189,2014,148.8\n2014-07-09,160,3,190,2014,146.46666666666667\n2014-07-10,160,4,191,2014,145.03333333333333\n2014-07-11,198,5,192,2014,146.16666666666666\n2014-07-12,116,6,193,2014,142.96666666666667\n2014-07-13,125,7,194,2014,141.5\n2014-07-14,115,1,195,2014,141.03333333333333\n2014-07-15,127,2,196,2014,141.93333333333334\n2014-07-16,242,3,197,2014,144.66666666666666\n2014-07-17,147,4,198,2014,143.73333333333332\n2014-07-18,199,5,199,2014,145.23333333333332\n2014-07-19,103,6,200,2014,142.1\n2014-07-20,159,7,201,2014,142.53333333333333\n2014-07-21,241,1,202,2014,149.1\n2014-07-22,189,2,203,2014,152.7\n2014-07-23,149,3,204,2014,152.56666666666666\n2014-07-24,215,4,205,2014,153.93333333333334\n2014-07-25,136,5,206,2014,152.66666666666666\n2014-07-26,105,6,207,2014,150.56666666666666\n2014-07-27,80,7,208,2014,147.46666666666667\n2014-07-28,126,1,209,2014,148.46666666666667\n2014-07-29,176,2,210,2014,152.23333333333332\n2014-07-30,145,3,211,2014,152.43333333333334\n2014-07-31,108,4,212,2014,150.7\n2014-08-01,205,5,213,2014,151.56666666666666\n2014-08-02,125,6,214,2014,150.7\n2014-08-03,93,7,215,2014,149.33333333333334\n2014-08-04,162,1,216,2014,150.7\n2014-08-05,229,2,217,2014,153.53333333333333\n2014-08-06,253,3,218,2014,156.93333333333334\n2014-08-07,226,4,219,2014,160.46666666666667\n2014-08-08,177,5,220,2014,161.03333333333333\n2014-08-09,133,6,221,2014,160.13333333333333\n2014-08-10,164,7,222,2014,159.0\n2014-08-11,199,1,223,2014,161.76666666666668\n2014-08-12,162,2,224,2014,163.0\n2014-08-13,121,3,225,2014,163.2\n2014-08-14,157,4,226,2014,164.2\n2014-08-15,123,5,227,2014,160.23333333333332\n2014-08-16,96,6,228,2014,158.53333333333333\n2014-08-17,139,7,229,2014,156.53333333333333\n2014-08-18,134,1,230,2014,157.56666666666666\n2014-08-19,186,2,231,2014,158.46666666666667\n2014-08-20,182,3,232,2014,156.5\n2014-08-21,205,4,233,2014,157.03333333333333\n2014-08-22,169,5,234,2014,157.7\n2014-08-23,93,6,235,2014,153.63333333333333\n2014-08-24,110,7,236,2014,152.76666666666668\n2014-08-25,167,1,237,2014,154.83333333333334\n2014-08-26,218,2,238,2014,159.43333333333334\n2014-08-27,188,3,239,2014,161.5\n2014-08-28,237,4,240,2014,163.53333333333333\n2014-08-29,163,5,241,2014,164.13333333333333\n2014-08-30,126,6,242,2014,164.73333333333332\n2014-08-31,127,7,243,2014,162.13333333333333\n2014-09-01,181,1,244,2014,164.0\n2014-09-02,240,2,245,2014,168.9\n2014-09-03,195,3,246,2014,170.0\n2014-09-04,181,4,247,2014,168.4\n2014-09-05,177,5,248,2014,165.86666666666667\n2014-09-06,119,6,249,2014,162.3\n2014-09-07,226,7,250,2014,163.93333333333334\n2014-09-08,133,1,251,2014,163.93333333333334\n2014-09-09,176,2,252,2014,164.33333333333334\n2014-09-10,207,3,253,2014,164.6\n2014-09-11,146,4,254,2014,164.06666666666666\n2014-09-12,145,5,255,2014,164.86666666666667\n2014-09-13,89,6,256,2014,162.6\n2014-09-14,125,7,257,2014,162.66666666666666\n2014-09-15,205,1,258,2014,166.3\n2014-09-16,189,2,259,2014,167.96666666666667\n2014-09-17,165,3,260,2014,169.0\n2014-09-18,232,4,261,2014,170.53333333333333\n2014-09-19,192,5,262,2014,170.86666666666667\n2014-09-20,124,6,263,2014,168.16666666666666\n2014-09-21,143,7,264,2014,167.3\n2014-09-22,171,1,265,2014,169.9\n2014-09-23,192,2,266,2014,172.63333333333333\n2014-09-24,207,3,267,2014,173.96666666666667\n2014-09-25,183,4,268,2014,172.8\n2014-09-26,201,5,269,2014,173.23333333333332\n2014-09-27,268,6,270,2014,174.26666666666668\n2014-09-28,335,7,271,2014,180.0\n2014-09-29,244,1,272,2014,183.93333333333334\n2014-09-30,256,2,273,2014,188.23333333333332\n2014-10-01,321,3,274,2014,192.9\n2014-10-02,241,4,275,2014,192.93333333333334\n2014-10-03,199,5,276,2014,193.06666666666666\n2014-10-04,118,6,277,2014,190.96666666666667\n2014-10-05,93,7,278,2014,188.16666666666666\n2014-10-06,149,1,279,2014,189.16666666666666\n2014-10-07,173,2,280,2014,187.4\n2014-10-08,169,3,281,2014,188.6\n2014-10-09,337,4,282,2014,193.96666666666667\n2014-10-10,155,5,283,2014,192.23333333333332\n2014-10-11,89,6,284,2014,190.33333333333334\n2014-10-12,128,7,285,2014,189.76666666666668\n2014-10-13,135,1,286,2014,191.3\n2014-10-14,190,2,287,2014,193.46666666666667\n2014-10-15,181,3,288,2014,192.66666666666666\n2014-10-16,187,4,289,2014,192.6\n2014-10-17,181,5,290,2014,193.13333333333333\n2014-10-18,139,6,291,2014,190.03333333333333\n2014-10-19,157,7,292,2014,188.86666666666667\n2014-10-20,155,1,293,2014,189.9\n2014-10-21,165,2,294,2014,190.63333333333333\n2014-10-22,124,3,295,2014,189.06666666666666\n2014-10-23,211,4,296,2014,189.7\n2014-10-24,158,5,297,2014,188.06666666666666\n2014-10-25,86,6,298,2014,184.83333333333334\n2014-10-26,65,7,299,2014,180.3\n2014-10-27,132,1,300,2014,175.76666666666668\n2014-10-28,135,2,301,2014,169.1\n2014-10-29,227,3,302,2014,168.53333333333333\n2014-10-30,187,4,303,2014,166.23333333333332\n2014-10-31,156,5,304,2014,160.73333333333332\n2014-11-01,86,6,305,2014,155.56666666666666\n2014-11-02,81,7,306,2014,151.63333333333333\n2014-11-03,152,1,307,2014,152.76666666666668\n2014-11-04,167,2,308,2014,155.23333333333332\n2014-11-05,216,3,309,2014,157.46666666666667\n2014-11-06,229,4,310,2014,159.33333333333334\n2014-11-07,208,5,311,2014,160.63333333333333\n2014-11-08,110,6,312,2014,153.06666666666666\n2014-11-09,205,7,313,2014,154.73333333333332\n2014-11-10,161,1,314,2014,157.13333333333333\n2014-11-11,165,2,315,2014,158.36666666666667\n2014-11-12,167,3,316,2014,159.43333333333334\n2014-11-13,162,4,317,2014,158.5\n2014-11-14,174,5,318,2014,158.26666666666668\n2014-11-15,153,6,319,2014,157.13333333333333\n2014-11-16,204,7,320,2014,157.9\n2014-11-17,219,1,321,2014,160.56666666666666\n2014-11-18,203,2,322,2014,162.1\n2014-11-19,180,3,323,2014,162.93333333333334\n2014-11-20,129,4,324,2014,161.73333333333332\n2014-11-21,168,5,325,2014,163.2\n2014-11-22,164,6,326,2014,161.63333333333333\n2014-11-23,141,7,327,2014,161.06666666666666\n2014-11-24,109,1,328,2014,161.83333333333334\n2014-11-25,176,2,329,2014,165.53333333333333\n2014-11-26,154,3,330,2014,166.26666666666668\n2014-11-27,90,4,331,2014,164.76666666666668\n2014-11-28,93,5,332,2014,160.3\n2014-11-29,116,6,333,2014,157.93333333333334\n2014-11-30,174,7,334,2014,158.53333333333333\n2014-12-01,184,1,335,2014,161.8\n2014-12-02,134,2,336,2014,163.56666666666666\n2014-12-03,129,3,337,2014,162.8\n2014-12-04,126,4,338,2014,161.43333333333334\n2014-12-05,132,5,339,2014,158.63333333333333\n2014-12-06,115,6,340,2014,154.83333333333334\n2014-12-07,160,7,341,2014,153.23333333333332\n2014-12-08,218,1,342,2014,156.83333333333334\n2014-12-09,158,2,343,2014,155.26666666666668\n2014-12-10,127,3,344,2014,154.13333333333333\n2014-12-11,140,4,345,2014,153.3\n2014-12-12,135,5,346,2014,152.23333333333332\n2014-12-13,136,6,347,2014,151.36666666666667\n2014-12-14,160,7,348,2014,150.9\n2014-12-15,196,1,349,2014,152.33333333333334\n2014-12-16,191,2,350,2014,151.9\n2014-12-17,138,3,351,2014,149.2\n2014-12-18,104,4,352,2014,145.9\n2014-12-19,205,5,353,2014,146.73333333333332\n2014-12-20,147,6,354,2014,147.33333333333334\n2014-12-21,196,7,355,2014,148.26666666666668\n2014-12-22,194,1,356,2014,149.26666666666668\n2014-12-23,142,2,357,2014,149.3\n2014-12-24,124,3,358,2014,149.8\n2014-12-25,70,4,359,2014,146.26666666666668\n2014-12-26,112,5,360,2014,144.86666666666667\n2014-12-27,193,6,361,2014,148.3\n2014-12-28,118,7,362,2014,149.13333333333333\n2014-12-29,103,1,363,2014,148.7\n2014-12-30,214,2,364,2014,150.03333333333333\n2014-12-31,134,3,365,2014,148.36666666666667\n2015-01-01,103,4,1,2015,147.33333333333334\n2015-01-02,223,5,2,2015,150.46666666666667\n2015-01-03,188,6,3,2015,152.53333333333333\n2015-01-04,143,7,4,2015,152.9\n2015-01-05,165,1,5,2015,154.56666666666666\n2015-01-06,185,2,6,2015,155.4\n2015-01-07,145,3,7,2015,152.96666666666667\n2015-01-08,252,4,8,2015,156.1\n2015-01-09,185,5,9,2015,158.03333333333333\n2015-01-10,160,6,10,2015,158.7\n2015-01-11,146,7,11,2015,159.06666666666666\n2015-01-12,186,1,12,2015,160.73333333333332\n2015-01-13,211,2,13,2015,162.43333333333334\n2015-01-14,131,3,14,2015,160.26666666666668\n2015-01-15,187,4,15,2015,160.13333333333333\n2015-01-16,174,5,16,2015,161.33333333333334\n2015-01-17,164,6,17,2015,163.33333333333334\n2015-01-18,148,7,18,2015,161.43333333333334\n2015-01-19,233,1,19,2015,164.3\n2015-01-20,139,2,20,2015,162.4\n2015-01-21,160,3,21,2015,161.26666666666668\n2015-01-22,156,4,22,2015,161.73333333333332\n2015-01-23,161,5,23,2015,162.96666666666667\n2015-01-24,134,6,24,2015,165.1\n2015-01-25,120,7,25,2015,165.36666666666667\n2015-01-26,174,1,26,2015,164.73333333333332\n2015-01-27,166,2,27,2015,166.33333333333334\n2015-01-28,217,3,28,2015,170.13333333333333\n2015-01-29,146,4,29,2015,167.86666666666667\n2015-01-30,205,5,30,2015,170.23333333333332\n2015-01-31,185,6,31,2015,172.96666666666667\n2015-02-01,126,7,32,2015,169.73333333333332\n2015-02-02,182,1,33,2015,169.53333333333333\n2015-02-03,148,2,34,2015,169.7\n2015-02-04,182,3,35,2015,170.26666666666668\n2015-02-05,256,4,36,2015,172.63333333333333\n2015-02-06,218,5,37,2015,175.06666666666666\n2015-02-07,156,6,38,2015,171.86666666666667\n2015-02-08,163,7,39,2015,171.13333333333333\n2015-02-09,195,1,40,2015,172.3\n2015-02-10,232,2,41,2015,175.16666666666666\n2015-02-11,189,3,42,2015,175.26666666666668\n2015-02-12,216,4,43,2015,175.43333333333334\n2015-02-13,152,5,44,2015,176.13333333333333\n2015-02-14,120,6,45,2015,173.9\n2015-02-15,203,7,46,2015,174.86666666666667\n2015-02-16,177,1,47,2015,175.3\n2015-02-17,215,2,48,2015,177.53333333333333\n2015-02-18,241,3,49,2015,177.8\n2015-02-19,190,4,50,2015,179.5\n2015-02-20,266,5,51,2015,183.03333333333333\n2015-02-21,285,6,52,2015,187.33333333333334\n2015-02-22,205,7,53,2015,188.8\n2015-02-23,278,1,54,2015,193.6\n2015-02-24,197,2,55,2015,196.16666666666666\n2015-02-25,285,3,56,2015,199.86666666666667\n2015-02-26,175,4,57,2015,200.16666666666666\n2015-02-27,185,5,58,2015,199.1\n2015-02-28,158,6,59,2015,199.5\n2015-03-01,140,7,60,2015,197.33333333333334\n2015-03-02,247,1,61,2015,199.4\n2015-03-03,230,2,62,2015,202.86666666666667\n2015-03-04,200,3,63,2015,203.46666666666667\n2015-03-05,283,4,64,2015,207.96666666666667\n2015-03-06,271,5,65,2015,210.93333333333334\n2015-03-07,187,6,66,2015,208.63333333333333\n2015-03-08,117,7,67,2015,205.26666666666668\n2015-03-09,267,1,68,2015,208.96666666666667\n2015-03-10,204,2,69,2015,210.33333333333334\n2015-03-11,276,3,70,2015,213.03333333333333\n2015-03-12,207,4,71,2015,212.2\n2015-03-13,289,5,72,2015,215.53333333333333\n2015-03-14,155,6,73,2015,213.5\n2015-03-15,107,7,74,2015,212.0\n2015-03-16,314,1,75,2015,218.46666666666667\n2015-03-17,266,2,76,2015,220.56666666666666\n2015-03-18,183,3,77,2015,220.76666666666668\n2015-03-19,228,4,78,2015,221.2\n2015-03-20,217,5,79,2015,220.4\n2015-03-21,101,6,80,2015,217.43333333333334\n2015-03-22,187,7,81,2015,214.8\n2015-03-23,230,1,82,2015,212.96666666666667\n2015-03-24,254,2,83,2015,214.6\n2015-03-25,222,3,84,2015,212.73333333333332\n2015-03-26,228,4,85,2015,213.76666666666668\n2015-03-27,242,5,86,2015,212.33333333333334\n2015-03-28,157,6,87,2015,211.73333333333332\n2015-03-29,108,7,88,2015,209.16666666666666\n2015-03-30,252,1,89,2015,212.3\n2015-03-31,201,2,90,2015,214.33333333333334\n2015-04-01,237,3,91,2015,214.0\n2015-04-02,175,4,92,2015,212.16666666666666\n2015-04-03,222,5,93,2015,212.9\n2015-04-04,107,6,94,2015,207.03333333333333\n2015-04-05,91,7,95,2015,201.03333333333333\n2015-04-06,198,1,96,2015,201.4\n2015-04-07,181,2,97,2015,203.53333333333333\n2015-04-08,215,3,98,2015,201.8\n2015-04-09,230,4,99,2015,202.66666666666666\n2015-04-10,141,5,100,2015,198.16666666666666\n2015-04-11,94,6,101,2015,194.4\n2015-04-12,72,7,102,2015,187.16666666666666\n2015-04-13,180,1,103,2015,188.0\n2015-04-14,258,2,104,2015,193.03333333333333\n2015-04-15,178,3,105,2015,188.5\n2015-04-16,210,4,106,2015,186.63333333333333\n2015-04-17,246,5,107,2015,188.73333333333332\n2015-04-18,111,6,108,2015,184.83333333333334\n2015-04-19,139,7,109,2015,182.23333333333332\n2015-04-20,134,1,110,2015,183.33333333333334\n2015-04-21,160,2,111,2015,182.43333333333334\n2015-04-22,186,3,112,2015,180.96666666666667\n2015-04-23,193,4,113,2015,178.93333333333334\n2015-04-24,201,5,114,2015,178.23333333333332\n2015-04-25,140,6,115,2015,175.3\n2015-04-26,164,7,116,2015,172.7\n2015-04-27,185,1,117,2015,173.63333333333333\n2015-04-28,176,2,118,2015,175.9\n2015-04-29,262,3,119,2015,176.23333333333332\n2015-04-30,216,4,120,2015,176.73333333333332\n2015-05-01,188,5,121,2015,175.1\n2015-05-02,142,6,122,2015,174.0\n2015-05-03,172,7,123,2015,172.33333333333334\n2015-05-04,173,1,124,2015,174.53333333333333\n2015-05-05,174,2,125,2015,177.3\n2015-05-06,202,3,126,2015,177.43333333333334\n2015-05-07,157,4,127,2015,176.63333333333333\n2015-05-08,222,5,128,2015,176.86666666666667\n2015-05-09,97,6,129,2015,172.43333333333334\n2015-05-10,97,7,130,2015,170.96666666666667\n2015-05-11,193,1,131,2015,174.26666666666668\n2015-05-12,176,2,132,2015,177.73333333333332\n2015-05-13,193,3,133,2015,178.16666666666666\n2015-05-14,235,4,134,2015,177.4\n2015-05-15,190,5,135,2015,177.8\n2015-05-16,116,6,136,2015,174.66666666666666\n2015-05-17,159,7,137,2015,171.76666666666668\n2015-05-18,312,1,138,2015,178.46666666666667\n2015-05-19,185,2,139,2015,180.0\n2015-05-20,242,3,140,2015,183.6\n2015-05-21,164,4,141,2015,183.73333333333332\n2015-05-22,175,5,142,2015,183.36666666666667\n2015-05-23,75,6,143,2015,179.43333333333334\n2015-05-24,115,7,144,2015,176.56666666666666\n2015-05-25,141,1,145,2015,176.6\n2015-05-26,248,2,146,2015,179.4\n2015-05-27,220,3,147,2015,180.56666666666666\n2015-05-28,196,4,148,2015,181.23333333333332\n2015-05-29,196,5,149,2015,179.03333333333333\n2015-05-30,152,6,150,2015,176.9\n2015-05-31,109,7,151,2015,174.26666666666668\n2015-06-01,193,1,152,2015,175.96666666666667\n2015-06-02,184,2,153,2015,176.36666666666667\n2015-06-03,155,3,154,2015,175.76666666666668\n2015-06-04,134,4,155,2015,174.43333333333334\n2015-06-05,128,5,156,2015,171.96666666666667\n2015-06-06,98,6,157,2015,170.0\n2015-06-07,105,7,158,2015,166.1\n2015-06-08,161,1,159,2015,168.23333333333332\n2015-06-09,176,2,160,2015,170.86666666666667\n2015-06-10,267,3,161,2015,173.33333333333334\n2015-06-11,184,4,162,2015,173.6\n2015-06-12,195,5,163,2015,173.66666666666666\n2015-06-13,108,6,164,2015,169.43333333333334\n2015-06-14,182,7,165,2015,169.16666666666666\n2015-06-15,195,1,166,2015,171.8\n2015-06-16,240,2,167,2015,174.5\n2015-06-17,279,3,168,2015,173.4\n2015-06-18,209,4,169,2015,174.2\n2015-06-19,251,5,170,2015,174.5\n2015-06-20,157,6,171,2015,174.26666666666668\n2015-06-21,120,7,172,2015,172.43333333333334\n2015-06-22,282,1,173,2015,179.33333333333334\n2015-06-23,223,2,174,2015,182.93333333333334\n2015-06-24,233,3,175,2015,186.0\n2015-06-25,199,4,176,2015,184.36666666666667\n2015-06-26,156,5,177,2015,182.23333333333332\n2015-06-27,79,6,178,2015,178.33333333333334\n2015-06-28,159,7,179,2015,177.1\n2015-06-29,192,1,180,2015,178.43333333333334\n2015-06-30,234,2,181,2015,182.6\n2015-07-01,252,3,182,2015,184.56666666666666\n2015-07-02,191,4,183,2015,184.8\n2015-07-03,151,5,184,2015,184.66666666666666\n2015-07-04,107,6,185,2015,183.76666666666668\n2015-07-05,95,7,186,2015,182.66666666666666\n2015-07-06,155,1,187,2015,184.56666666666666\n2015-07-07,224,2,188,2015,188.53333333333333\n2015-07-08,201,3,189,2015,189.86666666666667\n2015-07-09,189,4,190,2015,190.3\n2015-07-10,184,5,191,2015,187.53333333333333\n2015-07-11,142,6,192,2015,186.13333333333333\n2015-07-12,130,7,193,2015,183.96666666666667\n2015-07-13,149,1,194,2015,185.33333333333334\n2015-07-14,235,2,195,2015,187.1\n2015-07-15,166,3,196,2015,186.13333333333333\n2015-07-16,258,4,197,2015,186.73333333333332\n2015-07-17,236,5,198,2015,185.3\n2015-07-18,182,6,199,2015,184.4\n2015-07-19,129,7,200,2015,180.33333333333334\n2015-07-20,237,1,201,2015,183.0\n2015-07-21,275,2,202,2015,188.16666666666666\n2015-07-22,151,3,203,2015,183.8\n2015-07-23,211,4,204,2015,183.4\n2015-07-24,181,5,205,2015,181.66666666666666\n2015-07-25,125,6,206,2015,179.2\n2015-07-26,125,7,207,2015,178.16666666666666\n2015-07-27,206,1,208,2015,182.4\n2015-07-28,211,2,209,2015,184.13333333333333\n2015-07-29,176,3,210,2015,183.6\n2015-07-30,194,4,211,2015,182.26666666666668\n2015-07-31,210,5,212,2015,180.86666666666667\n2015-08-01,134,6,213,2015,178.96666666666667\n2015-08-02,153,7,214,2015,179.03333333333333\n2015-08-03,224,1,215,2015,182.93333333333334\n2015-08-04,221,2,216,2015,187.13333333333333\n2015-08-05,221,3,217,2015,189.33333333333334\n2015-08-06,217,4,218,2015,189.1\n2015-08-07,163,5,219,2015,187.83333333333334\n2015-08-08,99,6,220,2015,184.83333333333334\n2015-08-09,95,7,221,2015,181.86666666666667\n2015-08-10,197,1,222,2015,183.7\n2015-08-11,186,2,223,2015,185.56666666666666\n2015-08-12,225,3,224,2015,188.1\n2015-08-13,203,4,225,2015,187.03333333333333\n2015-08-14,170,5,226,2015,187.16666666666666\n2015-08-15,93,6,227,2015,181.66666666666666\n2015-08-16,108,7,228,2015,177.4\n2015-08-17,112,1,229,2015,175.06666666666666\n2015-08-18,170,2,230,2015,176.43333333333334\n2015-08-19,198,3,231,2015,175.13333333333333\n2015-08-20,200,4,232,2015,172.63333333333333\n2015-08-21,203,5,233,2015,174.36666666666667\n2015-08-22,105,6,234,2015,170.83333333333334\n2015-08-23,119,7,235,2015,168.76666666666668\n2015-08-24,186,1,236,2015,170.8\n2015-08-25,175,2,237,2015,172.46666666666667\n2015-08-26,205,3,238,2015,172.43333333333334\n2015-08-27,197,4,239,2015,171.96666666666667\n2015-08-28,174,5,240,2015,171.9\n2015-08-29,52,6,241,2015,167.16666666666666\n2015-08-30,127,7,242,2015,164.4\n2015-08-31,199,1,243,2015,166.56666666666666\n2015-09-01,219,2,244,2015,168.76666666666668\n2015-09-02,168,3,245,2015,166.9\n2015-09-03,251,4,246,2015,167.9\n2015-09-04,153,5,247,2015,165.63333333333333\n2015-09-05,102,6,248,2015,161.8\n2015-09-06,82,7,249,2015,159.1\n2015-09-07,114,1,250,2015,159.6\n2015-09-08,196,2,251,2015,162.96666666666667\n2015-09-09,272,3,252,2015,165.46666666666667\n2015-09-10,228,4,253,2015,166.86666666666667\n2015-09-11,241,5,254,2015,167.4\n2015-09-12,136,6,255,2015,165.16666666666666\n2015-09-13,108,7,256,2015,163.1\n2015-09-14,216,1,257,2015,167.2\n2015-09-15,197,2,258,2015,170.16666666666666\n2015-09-16,199,3,259,2015,173.06666666666666\n2015-09-17,209,4,260,2015,174.36666666666667\n2015-09-18,197,5,261,2015,174.33333333333334\n2015-09-19,148,6,262,2015,172.6\n2015-09-20,168,7,263,2015,171.43333333333334\n2015-09-21,194,1,264,2015,174.4\n2015-09-22,193,2,265,2015,176.86666666666667\n2015-09-23,152,3,266,2015,175.73333333333332\n2015-09-24,166,4,267,2015,175.43333333333334\n2015-09-25,215,5,268,2015,175.76666666666668\n2015-09-26,161,6,269,2015,174.56666666666666\n2015-09-27,139,7,270,2015,173.4\n2015-09-28,253,1,271,2015,180.1\n2015-09-29,211,2,272,2015,182.9\n2015-09-30,232,3,273,2015,184.0\n2015-10-01,206,4,274,2015,183.56666666666666\n2015-10-02,213,5,275,2015,185.06666666666666\n2015-10-03,129,6,276,2015,181.0\n2015-10-04,114,7,277,2015,179.7\n2015-10-05,227,1,278,2015,183.86666666666667\n2015-10-06,240,2,279,2015,189.13333333333333\n2015-10-07,202,3,280,2015,192.06666666666666\n2015-10-08,219,4,281,2015,192.83333333333334\n2015-10-09,190,5,282,2015,190.1\n2015-10-10,146,6,283,2015,187.36666666666667\n2015-10-11,145,7,284,2015,184.16666666666666\n2015-10-12,125,1,285,2015,183.8\n2015-10-13,218,2,286,2015,187.46666666666667\n2015-10-14,247,3,287,2015,188.5\n2015-10-15,201,4,288,2015,188.63333333333333\n2015-10-16,184,5,289,2015,188.13333333333333\n2015-10-17,112,6,290,2015,184.9\n2015-10-18,128,7,291,2015,182.6\n2015-10-19,276,1,292,2015,186.86666666666667\n2015-10-20,190,2,293,2015,187.6\n2015-10-21,251,3,294,2015,189.5\n2015-10-22,145,4,295,2015,187.9\n2015-10-23,159,5,296,2015,188.13333333333333\n2015-10-24,104,6,297,2015,186.06666666666666\n2015-10-25,153,7,298,2015,184.0\n2015-10-26,212,1,299,2015,185.7\n2015-10-27,179,2,300,2015,187.03333333333333\n2015-10-28,166,3,301,2015,184.13333333333333\n2015-10-29,180,4,302,2015,183.1\n2015-10-30,188,5,303,2015,181.63333333333333\n2015-10-31,65,6,304,2015,176.93333333333334\n2015-11-01,120,7,305,2015,173.83333333333334\n2015-11-02,225,1,306,2015,177.03333333333333\n2015-11-03,196,2,307,2015,179.76666666666668\n2015-11-04,229,3,308,2015,179.83333333333334\n2015-11-05,211,4,309,2015,178.86666666666667\n2015-11-06,181,5,310,2015,178.16666666666666\n2015-11-07,111,6,311,2015,174.56666666666666\n2015-11-08,167,7,312,2015,173.8\n2015-11-09,213,1,313,2015,176.03333333333333\n2015-11-10,256,2,314,2015,179.73333333333332\n2015-11-11,297,3,315,2015,185.46666666666667\n2015-11-12,223,4,316,2015,185.63333333333333\n2015-11-13,290,5,317,2015,187.06666666666666\n2015-11-14,139,6,318,2015,185.0\n2015-11-15,131,7,319,2015,183.23333333333332\n2015-11-16,221,1,320,2015,186.86666666666667\n2015-11-17,189,2,321,2015,188.9\n2015-11-18,208,3,322,2015,186.63333333333333\n2015-11-19,235,4,323,2015,188.13333333333333\n2015-11-20,245,5,324,2015,187.93333333333334\n2015-11-21,160,6,325,2015,188.43333333333334\n2015-11-22,150,7,326,2015,188.13333333333333\n2015-11-23,212,1,327,2015,191.73333333333332\n2015-11-24,316,2,328,2015,197.16666666666666\n2015-11-25,256,3,329,2015,198.63333333333333\n2015-11-26,96,4,330,2015,195.86666666666667\n2015-11-27,114,5,331,2015,194.13333333333333\n2015-11-28,152,6,332,2015,193.2\n2015-11-29,160,7,333,2015,192.26666666666668\n2015-11-30,165,1,334,2015,195.6\n2015-12-01,230,2,335,2015,199.26666666666668\n2015-12-02,192,3,336,2015,198.16666666666666\n2015-12-03,171,4,337,2015,197.33333333333334\n2015-12-04,149,5,338,2015,194.66666666666666\n2015-12-05,138,6,339,2015,192.23333333333332\n2015-12-06,268,7,340,2015,195.13333333333333\n2015-12-07,200,1,341,2015,198.1\n2015-12-08,248,2,342,2015,200.8\n2015-12-09,213,3,343,2015,200.8\n2015-12-10,241,4,344,2015,200.3\n2015-12-11,232,5,345,2015,198.13333333333333\n2015-12-12,95,6,346,2015,193.86666666666667\n2015-12-13,120,7,347,2015,188.2\n2015-12-14,220,1,348,2015,190.9\n2015-12-15,258,2,349,2015,195.13333333333333\n2015-12-16,230,3,350,2015,195.43333333333334\n2015-12-17,262,4,351,2015,197.86666666666667\n2015-12-18,226,5,352,2015,198.46666666666667\n2015-12-19,163,6,353,2015,196.06666666666666\n2015-12-20,131,7,354,2015,192.26666666666668\n2015-12-21,220,1,355,2015,194.26666666666668\n2015-12-22,153,2,356,2015,194.36666666666667\n2015-12-23,192,3,357,2015,193.7\n2015-12-24,96,4,358,2015,186.36666666666667\n2015-12-25,53,5,359,2015,179.6\n2015-12-26,85,6,360,2015,179.23333333333332\n2015-12-27,96,7,361,2015,178.63333333333333\n2015-12-28,139,1,362,2015,178.2\n2015-12-29,166,2,363,2015,178.4\n2015-12-30,156,3,364,2015,178.1\n2015-12-31,128,4,365,2015,174.7\n2016-01-01,131,5,1,2016,172.66666666666666\n2016-01-02,151,6,2,2016,172.0\n2016-01-03,154,7,3,2016,172.16666666666666\n2016-01-04,185,1,4,2016,173.73333333333332\n2016-01-05,226,2,5,2016,172.33333333333334\n2016-01-06,276,3,6,2016,174.86666666666667\n2016-01-07,310,4,7,2016,176.93333333333334\n2016-01-08,242,5,8,2016,177.9\n2016-01-09,197,6,9,2016,176.43333333333334\n2016-01-10,159,7,10,2016,174.0\n2016-01-11,330,1,11,2016,181.83333333333334\n2016-01-12,212,2,12,2016,184.9\n2016-01-13,261,3,13,2016,186.26666666666668\n2016-01-14,294,4,14,2016,187.46666666666667\n2016-01-15,263,5,15,2016,188.56666666666666\n2016-01-16,228,6,16,2016,187.43333333333334\n2016-01-17,200,7,17,2016,186.56666666666666\n2016-01-18,203,1,18,2016,187.9\n2016-01-19,214,2,19,2016,190.66666666666666\n2016-01-20,195,3,20,2016,189.83333333333334\n2016-01-21,268,4,21,2016,193.66666666666666\n2016-01-22,209,5,22,2016,194.23333333333332\n2016-01-23,169,6,23,2016,196.66666666666666\n2016-01-24,214,7,24,2016,202.03333333333333\n2016-01-25,251,1,25,2016,207.56666666666666\n2016-01-26,224,2,26,2016,211.83333333333334\n2016-01-27,211,3,27,2016,214.23333333333332\n2016-01-28,238,4,28,2016,216.63333333333333\n2016-01-29,316,5,29,2016,221.96666666666667\n2016-01-30,187,6,30,2016,223.93333333333334\n2016-01-31,253,7,31,2016,228.0\n2016-02-01,271,1,32,2016,232.0\n2016-02-02,307,2,33,2016,237.1\n2016-02-03,221,3,34,2016,238.3\n2016-02-04,209,4,35,2016,237.73333333333332\n2016-02-05,201,5,36,2016,235.23333333333332\n2016-02-06,165,6,37,2016,230.4\n2016-02-07,163,7,38,2016,227.76666666666668\n2016-02-08,191,1,39,2016,227.56666666666666\n2016-02-09,217,2,40,2016,229.5\n2016-02-10,192,3,41,2016,224.9\n2016-02-11,218,4,42,2016,225.1\n2016-02-12,291,5,43,2016,226.1\n2016-02-13,137,6,44,2016,220.86666666666667\n2016-02-14,145,7,45,2016,216.93333333333334\n2016-02-15,182,1,46,2016,215.4\n2016-02-16,249,2,47,2016,217.03333333333333\n2016-02-17,238,3,48,2016,218.2\n2016-02-18,224,4,49,2016,218.53333333333333\n2016-02-19,258,5,50,2016,220.63333333333333\n2016-02-20,136,6,51,2016,216.23333333333332\n2016-02-21,168,7,52,2016,214.86666666666667\n2016-02-22,211,1,53,2016,216.26666666666668\n2016-02-23,256,2,54,2016,217.66666666666666\n2016-02-24,232,3,55,2016,217.03333333333333\n2016-02-25,242,4,56,2016,217.63333333333333\n2016-02-26,232,5,57,2016,218.33333333333334\n2016-02-27,179,6,58,2016,216.36666666666667\n2016-02-28,246,7,59,2016,214.03333333333333\n2016-02-29,257,1,60,2016,216.36666666666667\n2016-03-01,208,2,61,2016,214.86666666666667\n2016-03-02,178,3,62,2016,211.76666666666668\n2016-03-03,208,4,63,2016,208.46666666666667\n2016-03-04,208,5,64,2016,208.03333333333333\n2016-03-05,127,6,65,2016,205.3\n2016-03-06,119,7,66,2016,202.56666666666666\n2016-03-07,208,1,67,2016,204.0\n2016-03-08,236,2,68,2016,206.43333333333334\n2016-03-09,191,3,69,2016,206.43333333333334\n2016-03-10,136,4,70,2016,203.73333333333332\n2016-03-11,180,5,71,2016,203.33333333333334\n2016-03-12,98,6,72,2016,199.33333333333334\n2016-03-13,97,7,73,2016,192.86666666666667\n2016-03-14,142,1,74,2016,193.03333333333333\n2016-03-15,180,2,75,2016,194.2\n2016-03-16,245,3,76,2016,196.3\n2016-03-17,232,4,77,2016,195.73333333333332\n2016-03-18,188,5,78,2016,194.06666666666666\n2016-03-19,119,6,79,2016,190.56666666666666\n2016-03-20,159,7,80,2016,187.26666666666668\n2016-03-21,216,1,81,2016,189.93333333333334\n2016-03-22,200,2,82,2016,191.0\n2016-03-23,228,3,83,2016,191.56666666666666\n2016-03-24,184,4,84,2016,189.16666666666666\n2016-03-25,272,5,85,2016,190.5\n2016-03-26,145,6,86,2016,187.26666666666668\n2016-03-27,101,7,87,2016,182.9\n2016-03-28,241,1,88,2016,184.96666666666667\n2016-03-29,204,2,89,2016,183.56666666666666\n2016-03-30,153,3,90,2016,180.1\n2016-03-31,177,4,91,2016,179.06666666666666\n2016-04-01,245,5,92,2016,181.3\n2016-04-02,175,6,93,2016,180.2\n2016-04-03,175,7,94,2016,179.1\n2016-04-04,206,1,95,2016,181.73333333333332\n2016-04-05,190,2,96,2016,184.1\n2016-04-06,189,3,97,2016,183.46666666666667\n2016-04-07,174,4,98,2016,181.4\n2016-04-08,182,5,99,2016,181.1\n2016-04-09,182,6,100,2016,182.63333333333333\n2016-04-10,124,7,101,2016,180.76666666666668\n2016-04-11,205,1,102,2016,184.33333333333334\n2016-04-12,218,2,103,2016,188.36666666666667\n2016-04-13,233,3,104,2016,191.4\n2016-04-14,231,4,105,2016,193.1\n2016-04-15,155,5,106,2016,190.1\n2016-04-16,174,6,107,2016,188.16666666666666\n2016-04-17,61,7,108,2016,183.93333333333334\n2016-04-18,197,1,109,2016,186.53333333333333\n2016-04-19,197,2,110,2016,187.8\n2016-04-20,270,3,111,2016,189.6\n2016-04-21,174,4,112,2016,188.73333333333332\n2016-04-22,166,5,113,2016,186.66666666666666\n2016-04-23,131,6,114,2016,184.9\n2016-04-24,89,7,115,2016,178.8\n2016-04-25,185,1,116,2016,180.13333333333333\n2016-04-26,155,2,117,2016,181.93333333333334\n2016-04-27,147,3,118,2016,178.8\n2016-04-28,129,4,119,2016,176.3\n2016-04-29,182,5,120,2016,177.26666666666668\n2016-04-30,114,6,121,2016,175.16666666666666\n2016-05-01,114,7,122,2016,170.8\n2016-05-02,268,1,123,2016,173.9\n2016-05-03,157,2,124,2016,173.3\n2016-05-04,184,3,125,2016,172.56666666666666\n2016-05-05,176,4,126,2016,172.1\n2016-05-06,162,5,127,2016,171.2\n2016-05-07,147,6,128,2016,170.3\n2016-05-08,80,7,129,2016,166.9\n2016-05-09,190,1,130,2016,167.16666666666666\n2016-05-10,205,2,131,2016,169.86666666666667\n2016-05-11,190,3,132,2016,169.36666666666667\n2016-05-12,140,4,133,2016,166.76666666666668\n2016-05-13,192,5,134,2016,165.4\n2016-05-14,77,6,135,2016,160.26666666666668\n2016-05-15,98,7,136,2016,158.36666666666667\n2016-05-16,187,1,137,2016,158.8\n2016-05-17,144,2,138,2016,161.56666666666666\n2016-05-18,160,3,139,2016,160.33333333333334\n2016-05-19,197,4,140,2016,160.33333333333334\n2016-05-20,183,5,141,2016,157.43333333333334\n2016-05-21,135,6,142,2016,156.13333333333333\n2016-05-22,150,7,143,2016,155.6\n2016-05-23,211,1,144,2016,158.26666666666668\n2016-05-24,236,2,145,2016,163.16666666666666\n2016-05-25,167,3,146,2016,162.56666666666666\n2016-05-26,160,4,147,2016,162.73333333333332\n2016-05-27,131,5,148,2016,162.2\n2016-05-28,97,6,149,2016,161.13333333333333\n2016-05-29,118,7,150,2016,159.0\n2016-05-30,162,1,151,2016,160.6\n2016-05-31,206,2,152,2016,163.66666666666666\n2016-06-01,280,3,153,2016,164.06666666666666\n2016-06-02,224,4,154,2016,166.3\n2016-06-03,255,5,155,2016,168.66666666666666\n2016-06-04,130,6,156,2016,167.13333333333333\n2016-06-05,119,7,157,2016,165.7\n2016-06-06,176,1,158,2016,166.66666666666666\n2016-06-07,212,2,159,2016,171.06666666666666\n2016-06-08,211,3,160,2016,171.76666666666668\n2016-06-09,209,4,161,2016,171.9\n2016-06-10,195,5,162,2016,172.06666666666666\n2016-06-11,178,6,163,2016,173.33333333333334\n2016-06-12,129,7,164,2016,171.23333333333332\n2016-06-13,292,1,165,2016,178.4\n2016-06-14,211,2,166,2016,182.16666666666666\n2016-06-15,196,3,167,2016,182.46666666666667\n2016-06-16,192,4,168,2016,184.06666666666666\n2016-06-17,199,5,169,2016,185.36666666666667\n2016-06-18,116,6,170,2016,182.66666666666666\n2016-06-19,103,7,171,2016,180.0\n2016-06-20,271,1,172,2016,184.53333333333333\n2016-06-21,233,2,173,2016,187.3\n2016-06-22,220,3,174,2016,187.6\n2016-06-23,175,4,175,2016,185.56666666666666\n2016-06-24,165,5,176,2016,185.5\n2016-06-25,67,6,177,2016,182.4\n2016-06-26,116,7,178,2016,181.9\n2016-06-27,271,1,179,2016,187.7\n2016-06-28,214,2,180,2016,190.9\n2016-06-29,193,3,181,2016,191.93333333333334\n2016-06-30,243,4,182,2016,193.16666666666666\n2016-07-01,218,5,183,2016,191.1\n2016-07-02,170,6,184,2016,189.3\n2016-07-03,102,7,185,2016,184.2\n2016-07-04,123,1,186,2016,183.96666666666667\n2016-07-05,148,2,187,2016,184.93333333333334\n2016-07-06,222,3,188,2016,186.46666666666667\n2016-07-07,204,4,189,2016,186.2\n2016-07-08,172,5,190,2016,184.9\n2016-07-09,115,6,191,2016,181.76666666666668\n2016-07-10,115,7,192,2016,179.1\n2016-07-11,175,1,193,2016,179.0\n2016-07-12,189,2,194,2016,181.0\n2016-07-13,168,3,195,2016,176.86666666666667\n2016-07-14,164,4,196,2016,175.3\n2016-07-15,159,5,197,2016,174.06666666666666\n2016-07-16,91,6,198,2016,170.7\n2016-07-17,135,7,199,2016,168.56666666666666\n2016-07-18,210,1,200,2016,171.7\n2016-07-19,208,2,201,2016,175.2\n2016-07-20,199,3,202,2016,172.8\n2016-07-21,155,4,203,2016,170.2\n2016-07-22,184,5,204,2016,169.0\n2016-07-23,98,6,205,2016,166.43333333333334\n2016-07-24,117,7,206,2016,164.83333333333334\n2016-07-25,200,1,207,2016,169.26666666666668\n2016-07-26,233,2,208,2016,173.16666666666666\n2016-07-27,221,3,209,2016,171.5\n2016-07-28,267,4,210,2016,173.26666666666668\n2016-07-29,219,5,211,2016,174.13333333333333\n2016-07-30,122,6,212,2016,170.1\n2016-07-31,133,7,213,2016,167.26666666666668\n2016-08-01,178,1,214,2016,167.53333333333333\n2016-08-02,170,2,215,2016,169.8\n2016-08-03,131,3,216,2016,170.06666666666666\n2016-08-04,230,4,217,2016,172.8\n2016-08-05,155,5,218,2016,170.56666666666666\n2016-08-06,71,6,219,2016,166.13333333333333\n2016-08-07,105,7,220,2016,163.9\n2016-08-08,158,1,221,2016,165.33333333333334\n2016-08-09,205,2,222,2016,168.33333333333334\n2016-08-10,227,3,223,2016,170.06666666666666\n2016-08-11,206,4,224,2016,170.63333333333333\n2016-08-12,194,5,225,2016,171.5\n2016-08-13,66,6,226,2016,168.23333333333332\n2016-08-14,97,7,227,2016,166.16666666666666\n2016-08-15,165,1,228,2016,168.63333333333333\n2016-08-16,170,2,229,2016,169.8\n2016-08-17,191,3,230,2016,169.16666666666666\n2016-08-18,180,4,231,2016,168.23333333333332\n2016-08-19,181,5,232,2016,167.63333333333333\n2016-08-20,126,6,233,2016,166.66666666666666\n2016-08-21,143,7,234,2016,165.3\n2016-08-22,207,1,235,2016,168.93333333333334\n2016-08-23,227,2,236,2016,172.6\n2016-08-24,206,3,237,2016,172.8\n2016-08-25,242,4,238,2016,173.1\n2016-08-26,140,5,239,2016,170.4\n2016-08-27,104,6,240,2016,164.96666666666667\n2016-08-28,111,7,241,2016,161.36666666666667\n2016-08-29,192,1,242,2016,163.7\n2016-08-30,182,2,243,2016,165.33333333333334\n2016-08-31,254,3,244,2016,167.86666666666667\n2016-09-01,265,4,245,2016,171.03333333333333\n2016-09-02,143,5,246,2016,171.43333333333334\n2016-09-03,74,6,247,2016,166.23333333333332\n2016-09-04,122,7,248,2016,165.13333333333333\n2016-09-05,130,1,249,2016,167.1\n2016-09-06,213,2,250,2016,170.7\n2016-09-07,177,3,251,2016,171.33333333333334\n2016-09-08,169,4,252,2016,170.13333333333333\n2016-09-09,174,5,253,2016,168.36666666666667\n2016-09-10,65,6,254,2016,163.66666666666666\n2016-09-11,89,7,255,2016,160.16666666666666\n2016-09-12,153,1,256,2016,163.06666666666666\n2016-09-13,119,2,257,2016,163.8\n2016-09-14,141,3,258,2016,163.0\n2016-09-15,179,4,259,2016,163.3\n2016-09-16,190,5,260,2016,163.26666666666668\n2016-09-17,85,6,261,2016,160.1\n2016-09-18,150,7,262,2016,159.06666666666666\n2016-09-19,200,1,263,2016,161.53333333333333\n2016-09-20,169,2,264,2016,162.4\n2016-09-21,149,3,265,2016,160.46666666666667\n2016-09-22,170,4,266,2016,158.56666666666666\n2016-09-23,131,5,267,2016,156.06666666666666\n2016-09-24,76,6,268,2016,150.53333333333333\n2016-09-25,78,7,269,2016,148.46666666666667\n2016-09-26,163,1,270,2016,150.43333333333334\n2016-09-27,187,2,271,2016,152.96666666666667\n2016-09-28,259,3,272,2016,155.2\n2016-09-29,154,4,273,2016,154.26666666666668\n2016-09-30,150,5,274,2016,150.8\n2016-10-01,98,6,275,2016,145.23333333333332\n2016-10-02,103,7,276,2016,143.9\n2016-10-03,199,1,277,2016,148.06666666666666\n2016-10-04,213,2,278,2016,151.1\n2016-10-05,263,3,279,2016,155.53333333333333\n2016-10-06,212,4,280,2016,155.5\n2016-10-07,226,5,281,2016,157.13333333333333\n2016-10-08,135,6,282,2016,156.0\n2016-10-09,93,7,283,2016,153.3\n2016-10-10,181,1,284,2016,157.16666666666666\n2016-10-11,166,2,285,2016,159.73333333333332\n2016-10-12,224,3,286,2016,162.1\n2016-10-13,221,4,287,2016,165.5\n2016-10-14,194,5,288,2016,167.26666666666668\n2016-10-15,97,6,289,2016,164.53333333333333\n2016-10-16,126,7,290,2016,162.4\n2016-10-17,141,1,291,2016,164.26666666666668\n2016-10-18,146,2,292,2016,164.13333333333333\n2016-10-19,114,3,293,2016,161.26666666666668\n2016-10-20,142,4,294,2016,160.36666666666667\n2016-10-21,182,5,295,2016,161.46666666666667\n2016-10-22,95,6,296,2016,158.96666666666667\n2016-10-23,124,7,297,2016,158.73333333333332\n2016-10-24,132,1,298,2016,160.6\n2016-10-25,140,2,299,2016,162.66666666666666\n2016-10-26,148,3,300,2016,162.16666666666666\n2016-10-27,124,4,301,2016,160.06666666666666\n2016-10-28,123,5,302,2016,155.53333333333333\n2016-10-29,156,6,303,2016,155.6\n2016-10-30,81,7,304,2016,153.3\n2016-10-31,82,1,305,2016,152.76666666666668\n2016-11-01,127,2,306,2016,153.56666666666666\n2016-11-02,146,3,307,2016,151.8\n2016-11-03,156,4,308,2016,149.9\n2016-11-04,148,5,309,2016,146.06666666666666\n2016-11-05,78,6,310,2016,141.6\n2016-11-06,103,7,311,2016,137.5\n2016-11-07,156,1,312,2016,138.2\n2016-11-08,120,2,313,2016,139.1\n2016-11-09,147,3,314,2016,137.96666666666667\n2016-11-10,148,4,315,2016,137.36666666666667\n2016-11-11,114,5,316,2016,133.7\n2016-11-12,76,6,317,2016,128.86666666666667\n2016-11-13,158,7,318,2016,127.66666666666667\n2016-11-14,179,1,319,2016,130.4\n2016-11-15,214,2,320,2016,133.33333333333334\n2016-11-16,142,3,321,2016,133.36666666666667\n2016-11-17,184,4,322,2016,134.63333333333333\n2016-11-18,162,5,323,2016,136.23333333333332\n2016-11-19,97,6,324,2016,134.73333333333332\n2016-11-20,103,7,325,2016,132.1\n2016-11-21,162,1,326,2016,134.33333333333334\n2016-11-22,112,2,327,2016,133.93333333333334\n2016-11-23,86,3,328,2016,132.4\n2016-11-24,75,4,329,2016,130.23333333333332\n2016-11-25,56,5,330,2016,127.16666666666667\n2016-11-26,47,6,331,2016,124.6\n2016-11-27,78,7,332,2016,123.1\n2016-11-28,141,1,333,2016,122.6\n2016-11-29,169,2,334,2016,125.53333333333333\n2016-11-30,138,3,335,2016,127.4\n2016-12-01,137,4,336,2016,127.73333333333333\n2016-12-02,147,5,337,2016,127.76666666666667\n2016-12-03,123,6,338,2016,126.66666666666667\n2016-12-04,107,7,339,2016,125.3\n2016-12-05,214,1,340,2016,129.83333333333334\n2016-12-06,213,2,341,2016,133.5\n2016-12-07,190,3,342,2016,134.63333333333333\n2016-12-08,168,4,343,2016,136.23333333333332\n2016-12-09,156,5,344,2016,136.53333333333333\n2016-12-10,87,6,345,2016,134.5\n2016-12-11,106,7,346,2016,134.23333333333332\n2016-12-12,210,1,347,2016,138.7\n2016-12-13,227,2,348,2016,141.0\n2016-12-14,192,3,349,2016,141.43333333333334\n2016-12-15,163,4,350,2016,139.73333333333332\n2016-12-16,89,5,351,2016,137.96666666666667\n2016-12-17,95,6,352,2016,135.0\n2016-12-18,90,7,353,2016,132.6\n2016-12-19,144,1,354,2016,134.16666666666666\n2016-12-20,138,2,355,2016,135.33333333333334\n2016-12-21,152,3,356,2016,135.0\n2016-12-22,159,4,357,2016,136.56666666666666\n2016-12-23,122,5,358,2016,137.76666666666668\n2016-12-24,67,6,359,2016,137.5\n2016-12-25,57,7,360,2016,137.53333333333333\n2016-12-26,75,1,361,2016,138.46666666666667\n2016-12-27,111,2,362,2016,139.56666666666666\n2016-12-28,117,3,363,2016,138.76666666666668\n2016-12-29,129,4,364,2016,137.43333333333334\n2016-12-30,75,5,365,2016,135.33333333333334\n2016-12-31,23,6,366,2016,131.53333333333333\n2017-01-01,59,7,1,2017,128.6\n2017-01-02,113,1,2,2017,128.26666666666668\n2017-01-03,135,2,3,2017,129.2\n2017-01-04,186,3,4,2017,128.26666666666668\n2017-01-05,137,4,5,2017,125.73333333333333\n2017-01-06,141,5,6,2017,124.1\n2017-01-07,80,6,7,2017,121.16666666666667\n2017-01-08,85,7,8,2017,118.8\n2017-01-09,111,1,9,2017,119.6\n2017-01-10,183,2,10,2017,122.16666666666667\n2017-01-11,188,3,11,2017,121.43333333333334\n2017-01-12,157,4,12,2017,119.1\n2017-01-13,159,5,13,2017,118.0\n2017-01-14,58,6,14,2017,114.5\n2017-01-15,124,7,15,2017,115.66666666666667\n2017-01-16,116,1,16,2017,116.36666666666666\n2017-01-17,156,2,17,2017,118.56666666666666\n2017-01-18,146,3,18,2017,118.63333333333334\n2017-01-19,98,4,19,2017,117.3\n2017-01-20,103,5,20,2017,115.66666666666667\n2017-01-21,83,6,21,2017,113.13333333333334\n2017-01-22,133,7,22,2017,113.5\n2017-01-23,166,1,23,2017,116.8\n2017-01-24,133,2,24,2017,119.33333333333333\n2017-01-25,183,3,25,2017,122.93333333333334\n2017-01-26,135,4,26,2017,123.73333333333333\n2017-01-27,153,5,27,2017,124.93333333333334\n2017-01-28,103,6,28,2017,124.06666666666666\n2017-01-29,65,7,29,2017,123.73333333333333\n2017-01-30,154,1,30,2017,128.1\n2017-01-31,137,2,31,2017,130.7\n2017-02-01,125,3,32,2017,131.1\n2017-02-02,143,4,33,2017,131.36666666666667\n2017-02-03,102,5,34,2017,128.56666666666666\n2017-02-04,73,6,35,2017,126.43333333333334\n2017-02-05,100,7,36,2017,125.06666666666666\n2017-02-06,131,1,37,2017,126.76666666666667\n2017-02-07,134,2,38,2017,128.4\n2017-02-08,128,3,39,2017,128.96666666666667\n2017-02-09,122,4,40,2017,126.93333333333334\n2017-02-10,114,5,41,2017,124.46666666666667\n2017-02-11,65,6,42,2017,121.4\n2017-02-12,116,7,43,2017,119.96666666666667\n2017-02-13,110,1,44,2017,121.7\n2017-02-14,151,2,45,2017,122.6\n2017-02-15,109,3,46,2017,122.36666666666666\n2017-02-16,84,4,47,2017,119.96666666666667\n2017-02-17,96,5,48,2017,118.3\n2017-02-18,86,6,49,2017,117.9\n2017-02-19,72,7,50,2017,116.86666666666666\n2017-02-20,109,1,51,2017,117.73333333333333\n2017-02-21,153,2,52,2017,118.4\n2017-02-22,166,3,53,2017,118.4\n2017-02-23,109,4,54,2017,117.6\n2017-02-24,117,5,55,2017,115.4\n2017-02-25,58,6,56,2017,112.83333333333333\n2017-02-26,77,7,57,2017,110.3\n2017-02-27,102,1,58,2017,110.26666666666667\n2017-02-28,125,2,59,2017,112.26666666666667\n2017-03-01,135,3,60,2017,111.63333333333334\n2017-03-02,144,4,61,2017,111.86666666666666\n2017-03-03,139,5,62,2017,112.33333333333333\n2017-03-04,85,6,63,2017,110.4\n2017-03-05,71,7,64,2017,109.36666666666666\n2017-03-06,149,1,65,2017,111.9\n2017-03-07,132,2,66,2017,112.96666666666667\n2017-03-08,149,3,67,2017,113.56666666666666\n2017-03-09,152,4,68,2017,114.16666666666667\n2017-03-10,194,5,69,2017,116.36666666666666\n2017-03-11,118,6,70,2017,116.23333333333333\n2017-03-12,63,7,71,2017,114.53333333333333\n2017-03-13,102,1,72,2017,115.76666666666667\n2017-03-14,204,2,73,2017,118.7\n2017-03-15,166,3,74,2017,120.56666666666666\n2017-03-16,131,4,75,2017,119.9\n2017-03-17,147,5,76,2017,121.16666666666667\n2017-03-18,83,6,77,2017,121.13333333333334\n2017-03-19,96,7,78,2017,121.13333333333334\n2017-03-20,111,1,79,2017,121.96666666666667\n2017-03-21,201,2,80,2017,126.26666666666667\n2017-03-22,140,3,81,2017,127.3\n2017-03-23,163,4,82,2017,127.63333333333334\n2017-03-24,157,5,83,2017,127.33333333333333\n2017-03-25,102,6,84,2017,127.1\n2017-03-26,79,7,85,2017,125.83333333333333\n2017-03-27,146,1,86,2017,128.76666666666668\n2017-03-28,157,2,87,2017,131.43333333333334\n2017-03-29,130,3,88,2017,132.36666666666667\n2017-03-30,121,4,89,2017,132.23333333333332\n2017-03-31,105,5,90,2017,131.23333333333332\n2017-04-01,35,6,91,2017,127.6\n2017-04-02,109,7,92,2017,126.6\n2017-04-03,149,1,93,2017,128.73333333333332\n2017-04-04,129,2,94,2017,130.66666666666666\n2017-04-05,201,3,95,2017,132.4\n2017-04-06,169,4,96,2017,133.63333333333333\n2017-04-07,195,5,97,2017,135.16666666666666\n2017-04-08,63,6,98,2017,132.2\n2017-04-09,66,7,99,2017,127.93333333333334\n2017-04-10,152,1,100,2017,129.06666666666666\n2017-04-11,168,2,101,2017,132.56666666666666\n2017-04-12,235,3,102,2017,137.0\n2017-04-13,189,4,103,2017,136.5\n2017-04-14,148,5,104,2017,135.9\n2017-04-15,93,6,105,2017,134.63333333333333\n2017-04-16,69,7,106,2017,132.03333333333333\n2017-04-17,128,1,107,2017,133.53333333333333\n2017-04-18,196,2,108,2017,136.86666666666667\n2017-04-19,198,3,109,2017,139.76666666666668\n2017-04-20,133,4,110,2017,137.5\n2017-04-21,131,5,111,2017,137.2\n2017-04-22,81,6,112,2017,134.46666666666667\n2017-04-23,66,7,113,2017,131.43333333333334\n2017-04-24,148,1,114,2017,132.96666666666667\n2017-04-25,171,2,115,2017,136.03333333333333\n2017-04-26,176,3,116,2017,137.03333333333333\n2017-04-27,169,4,117,2017,137.43333333333334\n2017-04-28,181,5,118,2017,139.13333333333333\n2017-04-29,84,6,119,2017,137.9\n2017-04-30,81,7,120,2017,137.1\n2017-05-01,161,1,121,2017,141.3\n2017-05-02,182,2,122,2017,143.73333333333332\n2017-05-03,193,3,123,2017,145.2\n2017-05-04,170,4,124,2017,146.56666666666666\n2017-05-05,122,5,125,2017,143.93333333333334\n2017-05-06,80,6,126,2017,140.96666666666667\n2017-05-07,127,7,127,2017,138.7\n2017-05-08,180,1,128,2017,142.6\n2017-05-09,152,2,129,2017,145.46666666666667\n2017-05-10,225,3,130,2017,147.9\n2017-05-11,111,4,131,2017,146.0\n2017-05-12,173,5,132,2017,143.93333333333334\n2017-05-13,76,6,133,2017,140.16666666666666\n2017-05-14,52,7,134,2017,136.96666666666667\n2017-05-15,134,1,135,2017,138.33333333333334\n2017-05-16,140,2,136,2017,140.7\n2017-05-17,161,3,137,2017,141.8\n2017-05-18,175,4,138,2017,141.1\n2017-05-19,199,5,139,2017,141.13333333333333\n2017-05-20,102,6,140,2017,140.1\n2017-05-21,145,7,141,2017,140.56666666666666\n2017-05-22,170,1,142,2017,143.53333333333333\n2017-05-23,158,2,143,2017,146.6\n2017-05-24,141,3,144,2017,146.36666666666667\n2017-05-25,132,4,145,2017,145.06666666666666\n2017-05-26,181,5,146,2017,145.23333333333332\n2017-05-27,83,6,147,2017,142.36666666666667\n2017-05-28,78,7,148,2017,138.93333333333334\n2017-05-29,122,1,149,2017,140.2\n2017-05-30,188,2,150,2017,143.76666666666668\n2017-05-31,152,3,151,2017,143.46666666666667\n2017-06-01,189,4,152,2017,143.7\n2017-06-02,201,5,153,2017,143.96666666666667\n2017-06-03,91,6,154,2017,141.33333333333334\n2017-06-04,113,7,155,2017,141.03333333333333\n2017-06-05,164,1,156,2017,143.83333333333334\n2017-06-06,125,2,157,2017,143.76666666666668\n2017-06-07,175,3,158,2017,143.6\n2017-06-08,184,4,159,2017,144.66666666666666\n2017-06-09,154,5,160,2017,142.3\n2017-06-10,86,6,161,2017,141.46666666666667\n2017-06-11,37,7,162,2017,136.93333333333334\n2017-06-12,179,1,163,2017,140.36666666666667\n2017-06-13,196,2,164,2017,145.16666666666666\n2017-06-14,169,3,165,2017,146.33333333333334\n2017-06-15,178,4,166,2017,147.6\n2017-06-16,149,5,167,2017,147.2\n2017-06-17,89,6,168,2017,144.33333333333334\n2017-06-18,85,7,169,2017,140.53333333333333\n2017-06-19,142,1,170,2017,141.86666666666667\n2017-06-20,157,2,171,2017,142.26666666666668\n2017-06-21,143,3,172,2017,141.36666666666667\n2017-06-22,152,4,173,2017,141.16666666666666\n2017-06-23,185,5,174,2017,142.63333333333333\n2017-06-24,77,6,175,2017,140.8\n2017-06-25,77,7,176,2017,137.33333333333334\n2017-06-26,140,1,177,2017,139.23333333333332\n2017-06-27,239,2,178,2017,144.6\n2017-06-28,181,3,179,2017,146.56666666666666\n2017-06-29,154,4,180,2017,145.43333333333334\n2017-06-30,162,5,181,2017,145.76666666666668\n2017-07-01,99,6,182,2017,142.76666666666668\n2017-07-02,108,7,183,2017,139.66666666666666\n2017-07-03,129,1,184,2017,140.93333333333334\n2017-07-04,162,2,185,2017,142.56666666666666\n2017-07-05,180,3,186,2017,143.1\n2017-07-06,174,4,187,2017,144.73333333333332\n2017-07-07,153,5,188,2017,144.0\n2017-07-08,67,6,189,2017,140.1\n2017-07-09,76,7,190,2017,137.5\n2017-07-10,184,1,191,2017,140.76666666666668\n2017-07-11,200,2,192,2017,146.2\n2017-07-12,204,3,193,2017,147.03333333333333\n2017-07-13,181,4,194,2017,146.53333333333333\n2017-07-14,157,5,195,2017,146.13333333333333\n2017-07-15,115,6,196,2017,144.03333333333333\n2017-07-16,152,7,197,2017,144.13333333333333\n2017-07-17,117,1,198,2017,145.06666666666666\n2017-07-18,168,2,199,2017,147.83333333333334\n2017-07-19,162,3,200,2017,148.5\n2017-07-20,150,4,201,2017,148.26666666666668\n2017-07-21,142,5,202,2017,148.23333333333332\n2017-07-22,86,6,203,2017,146.03333333333333\n2017-07-23,94,7,204,2017,143.0\n2017-07-24,113,1,205,2017,144.2\n2017-07-25,152,2,206,2017,146.7\n2017-07-26,97,3,207,2017,145.26666666666668\n2017-07-27,139,4,208,2017,141.93333333333334\n2017-07-28,108,5,209,2017,139.5\n2017-07-29,55,6,210,2017,136.2\n2017-07-30,60,7,211,2017,132.8\n2017-07-31,132,1,212,2017,133.9\n2017-08-01,175,2,213,2017,136.13333333333333\n2017-08-02,107,3,214,2017,135.4\n2017-08-03,118,4,215,2017,133.93333333333334\n2017-08-04,123,5,216,2017,132.03333333333333\n2017-08-05,88,6,217,2017,129.16666666666666\n2017-08-06,36,7,218,2017,125.26666666666667\n2017-08-07,131,1,219,2017,127.4\n2017-08-08,119,2,220,2017,128.83333333333334\n2017-08-09,116,3,221,2017,126.56666666666666\n2017-08-10,71,4,222,2017,122.26666666666667\n2017-08-11,116,5,223,2017,119.33333333333333\n2017-08-12,40,6,224,2017,114.63333333333334\n2017-08-13,94,7,225,2017,112.53333333333333\n2017-08-14,149,1,226,2017,113.66666666666667\n2017-08-15,146,2,227,2017,113.46666666666667\n2017-08-16,167,3,228,2017,115.13333333333334\n2017-08-17,160,4,229,2017,114.86666666666666\n2017-08-18,120,5,230,2017,113.46666666666667\n2017-08-19,31,6,231,2017,109.5\n2017-08-20,43,7,232,2017,106.2\n2017-08-21,84,1,233,2017,106.13333333333334\n2017-08-22,114,2,234,2017,106.8\n2017-08-23,144,3,235,2017,107.83333333333333\n2017-08-24,114,4,236,2017,106.56666666666666\n2017-08-25,118,5,237,2017,107.26666666666667\n2017-08-26,48,6,238,2017,104.23333333333333\n2017-08-27,85,7,239,2017,103.46666666666667\n2017-08-28,94,1,240,2017,104.76666666666667\n2017-08-29,119,2,241,2017,106.73333333333333\n2017-08-30,135,3,242,2017,106.83333333333333\n2017-08-31,127,4,243,2017,105.23333333333333\n2017-09-01,116,5,244,2017,105.53333333333333\n2017-09-02,84,6,245,2017,104.4\n2017-09-03,70,7,246,2017,102.63333333333334\n2017-09-04,113,1,247,2017,103.46666666666667\n2017-09-05,123,2,248,2017,106.36666666666666\n2017-09-06,99,3,249,2017,105.3\n2017-09-07,95,4,250,2017,104.5\n2017-09-08,125,5,251,2017,104.8\n2017-09-09,59,6,252,2017,104.4\n2017-09-10,56,7,253,2017,102.4\n2017-09-11,148,1,254,2017,106.0\n2017-09-12,127,2,255,2017,107.1\n2017-09-13,123,3,256,2017,106.23333333333333\n2017-09-14,120,4,257,2017,105.36666666666666\n2017-09-15,129,5,258,2017,104.1\n2017-09-16,40,6,259,2017,100.1\n2017-09-17,59,7,260,2017,98.06666666666666\n2017-09-18,115,1,261,2017,100.86666666666666\n2017-09-19,137,2,262,2017,104.0\n2017-09-20,98,3,263,2017,104.46666666666667\n2017-09-21,96,4,264,2017,103.86666666666666\n2017-09-22,82,5,265,2017,101.8\n2017-09-23,88,6,266,2017,100.93333333333334\n2017-09-24,86,7,267,2017,99.86666666666666\n2017-09-25,144,1,268,2017,103.06666666666666\n2017-09-26,169,2,269,2017,105.86666666666666\n2017-09-27,150,3,270,2017,107.73333333333333\n2017-09-28,151,4,271,2017,108.8\n2017-09-29,136,5,272,2017,108.83333333333333\n2017-09-30,95,6,273,2017,107.76666666666667\n2017-10-01,94,7,274,2017,107.03333333333333\n2017-10-02,138,1,275,2017,108.83333333333333\n2017-10-03,165,2,276,2017,112.0\n2017-10-04,114,3,277,2017,112.03333333333333\n2017-10-05,95,4,278,2017,111.1\n2017-10-06,113,5,279,2017,111.56666666666666\n2017-10-07,80,6,280,2017,111.06666666666666\n2017-10-08,95,7,281,2017,110.06666666666666\n2017-10-09,122,1,282,2017,112.16666666666667\n2017-10-10,175,2,283,2017,116.13333333333334\n2017-10-11,127,3,284,2017,115.43333333333334\n2017-10-12,179,4,285,2017,117.16666666666667\n2017-10-13,197,5,286,2017,119.63333333333334\n2017-10-14,84,6,287,2017,118.43333333333334\n2017-10-15,60,7,288,2017,116.13333333333334\n2017-10-16,128,1,289,2017,119.06666666666666\n2017-10-17,138,2,290,2017,121.7\n2017-10-18,154,3,291,2017,123.0\n2017-10-19,163,4,292,2017,123.86666666666666\n2017-10-20,118,5,293,2017,124.53333333333333\n2017-10-21,82,6,294,2017,124.06666666666666\n2017-10-22,49,7,295,2017,122.96666666666667\n2017-10-23,96,1,296,2017,123.23333333333333\n2017-10-24,142,2,297,2017,125.1\n2017-10-25,160,3,298,2017,125.63333333333334\n2017-10-26,140,4,299,2017,124.66666666666667\n2017-10-27,126,5,300,2017,123.86666666666666\n2017-10-28,81,6,301,2017,121.53333333333333\n2017-10-29,99,7,302,2017,120.3\n2017-10-30,107,1,303,2017,120.7\n2017-10-31,157,2,304,2017,122.8\n2017-11-01,157,3,305,2017,123.43333333333334\n2017-11-02,151,4,306,2017,122.96666666666667\n2017-11-03,136,5,307,2017,123.7\n2017-11-04,76,6,308,2017,123.06666666666666\n2017-11-05,63,7,309,2017,121.4\n2017-11-06,155,1,310,2017,123.9\n2017-11-07,124,2,311,2017,124.86666666666666\n2017-11-08,153,3,312,2017,125.9\n2017-11-09,119,4,313,2017,124.03333333333333\n2017-11-10,90,5,314,2017,122.8\n2017-11-11,57,6,315,2017,118.73333333333333\n2017-11-12,86,7,316,2017,115.03333333333333\n2017-11-13,129,1,317,2017,116.53333333333333\n2017-11-14,142,2,318,2017,119.26666666666667\n2017-11-15,137,3,319,2017,119.56666666666666\n2017-11-16,147,4,320,2017,119.86666666666666\n2017-11-17,175,5,321,2017,120.56666666666666\n2017-11-18,101,6,322,2017,118.5\n2017-11-19,95,7,323,2017,117.73333333333333\n2017-11-20,140,1,324,2017,119.66666666666667\n2017-11-21,127,2,325,2017,122.26666666666667\n2017-11-22,152,3,326,2017,124.13333333333334\n2017-11-23,98,4,327,2017,122.66666666666667\n2017-11-24,90,5,328,2017,120.33333333333333\n2017-11-25,59,6,329,2017,117.63333333333334\n2017-11-26,86,7,330,2017,116.3\n2017-11-27,95,1,331,2017,116.76666666666667\n2017-11-28,114,2,332,2017,117.26666666666667\n2017-11-29,140,3,333,2017,118.36666666666666\n2017-11-30,131,4,334,2017,117.5\n2017-12-01,129,5,335,2017,116.56666666666666\n2017-12-02,98,6,336,2017,114.8\n2017-12-03,85,7,337,2017,113.1\n2017-12-04,150,1,338,2017,115.56666666666666\n2017-12-05,174,2,339,2017,119.26666666666667\n2017-12-06,168,3,340,2017,119.7\n2017-12-07,96,4,341,2017,118.76666666666667\n2017-12-08,71,5,342,2017,116.03333333333333\n2017-12-09,96,6,343,2017,115.26666666666667\n2017-12-10,106,7,344,2017,115.8\n2017-12-11,133,1,345,2017,118.33333333333333\n2017-12-12,144,2,346,2017,120.26666666666667\n2017-12-13,96,3,347,2017,119.16666666666667\n2017-12-14,102,4,348,2017,117.83333333333333\n2017-12-15,133,5,349,2017,117.7\n2017-12-16,69,6,350,2017,115.1\n2017-12-17,80,7,351,2017,111.93333333333334\n2017-12-18,83,1,352,2017,111.33333333333333\n2017-12-19,107,2,353,2017,111.73333333333333\n2017-12-20,137,3,354,2017,111.63333333333334\n2017-12-21,132,4,355,2017,111.8\n2017-12-22,108,5,356,2017,110.33333333333333\n2017-12-23,34,6,357,2017,108.2\n2017-12-24,37,7,358,2017,106.43333333333334\n2017-12-25,35,1,359,2017,105.63333333333334\n2017-12-26,65,2,360,2017,104.93333333333334\n2017-12-27,129,3,361,2017,106.06666666666666\n2017-12-28,126,4,362,2017,106.46666666666667\n2017-12-29,86,5,363,2017,104.66666666666667\n2017-12-30,99,6,364,2017,103.6\n2017-12-31,60,7,365,2017,101.3\n2018-01-01,44,1,1,2018,99.5\n2018-01-02,79,2,2,2018,99.3\n2018-01-03,93,3,3,2018,97.4\n2018-01-04,131,4,4,2018,95.96666666666667\n2018-01-05,125,5,5,2018,94.53333333333333\n2018-01-06,63,6,6,2018,93.43333333333334\n2018-01-07,58,7,7,2018,93.0\n2018-01-08,180,1,8,2018,95.8\n2018-01-09,139,2,9,2018,96.9\n2018-01-10,155,3,10,2018,97.63333333333334\n2018-01-11,128,4,11,2018,97.1\n2018-01-12,92,5,12,2018,96.96666666666667\n2018-01-13,116,6,13,2018,97.43333333333334\n2018-01-14,92,7,14,2018,96.06666666666666\n2018-01-15,116,1,15,2018,97.63333333333334\n2018-01-16,106,2,16,2018,98.5\n2018-01-17,145,3,17,2018,100.56666666666666\n2018-01-18,152,4,18,2018,102.06666666666666\n2018-01-19,110,5,19,2018,101.16666666666667\n2018-01-20,100,6,20,2018,100.1\n2018-01-21,67,7,21,2018,98.73333333333333\n2018-01-22,154,1,22,2018,102.73333333333333\n2018-01-23,122,2,23,2018,105.56666666666666\n2018-01-24,215,3,24,2018,111.56666666666666\n2018-01-25,153,4,25,2018,114.5\n2018-01-26,127,5,26,2018,114.43333333333334\n2018-01-27,81,6,27,2018,112.93333333333334\n2018-01-28,79,7,28,2018,112.7\n2018-01-29,146,1,29,2018,114.26666666666667\n2018-01-30,159,2,30,2018,117.56666666666666\n2018-01-31,128,3,31,2018,120.36666666666666\n2018-02-01,97,4,32,2018,120.96666666666667\n2018-02-02,124,5,33,2018,122.0\n2018-02-03,51,6,34,2018,119.33333333333333\n2018-02-04,82,7,35,2018,117.9\n2018-02-05,163,1,36,2018,121.23333333333333\n2018-02-06,183,2,37,2018,125.4\n2018-02-07,107,3,38,2018,122.96666666666667\n2018-02-08,151,4,39,2018,123.36666666666666\n2018-02-09,174,5,40,2018,124.0\n2018-02-10,147,6,41,2018,124.63333333333334\n2018-02-11,131,7,42,2018,125.93333333333334\n2018-02-12,135,1,43,2018,126.56666666666666\n2018-02-13,170,2,44,2018,129.16666666666666\n2018-02-14,151,3,45,2018,130.33333333333334\n2018-02-15,180,4,46,2018,132.8\n2018-02-16,128,5,47,2018,132.23333333333332\n2018-02-17,125,6,48,2018,131.33333333333334\n2018-02-18,119,7,49,2018,131.63333333333333\n2018-02-19,128,1,50,2018,132.56666666666666\n2018-02-20,148,2,51,2018,135.26666666666668\n2018-02-21,115,3,52,2018,133.96666666666667\n2018-02-22,136,4,53,2018,134.43333333333334\n2018-02-23,173,5,54,2018,133.03333333333333\n2018-02-24,103,6,55,2018,131.36666666666667\n2018-02-25,115,7,56,2018,130.96666666666667\n2018-02-26,168,1,57,2018,133.86666666666667\n2018-02-27,174,2,58,2018,137.03333333333333\n2018-02-28,180,3,59,2018,138.16666666666666\n2018-03-01,126,4,60,2018,137.06666666666666\n2018-03-02,168,5,61,2018,138.4\n2018-03-03,112,6,62,2018,138.9\n2018-03-04,76,7,63,2018,137.3\n2018-03-05,164,1,64,2018,141.06666666666666\n2018-03-06,123,2,65,2018,142.43333333333334\n2018-03-07,143,3,66,2018,141.76666666666668\n2018-03-08,138,4,67,2018,140.26666666666668\n2018-03-09,161,5,68,2018,142.06666666666666\n2018-03-10,111,6,69,2018,140.73333333333332\n2018-03-11,47,7,70,2018,136.5\n2018-03-12,175,1,71,2018,137.43333333333334\n2018-03-13,146,2,72,2018,137.93333333333334\n2018-03-14,175,3,73,2018,139.26666666666668\n2018-03-15,141,4,74,2018,138.3\n2018-03-16,135,5,75,2018,137.76666666666668\n2018-03-17,116,6,76,2018,135.63333333333333\n2018-03-18,113,7,77,2018,135.13333333333333\n2018-03-19,199,1,78,2018,137.6\n2018-03-20,199,2,79,2018,140.26666666666668\n2018-03-21,207,3,80,2018,142.9\n2018-03-22,147,4,81,2018,142.86666666666667\n2018-03-23,145,5,82,2018,143.86666666666667\n2018-03-24,161,6,83,2018,144.7\n2018-03-25,131,7,84,2018,143.3\n2018-03-26,170,1,85,2018,145.53333333333333\n2018-03-27,160,2,86,2018,147.03333333333333\n2018-03-28,192,3,87,2018,147.83333333333334\n2018-03-29,142,4,88,2018,146.76666666666668\n2018-03-30,152,5,89,2018,145.83333333333334\n2018-03-31,151,6,90,2018,146.66666666666666\n2018-04-01,79,7,91,2018,143.7\n2018-04-02,150,1,92,2018,144.96666666666667\n2018-04-03,229,2,93,2018,150.06666666666666\n2018-04-04,209,3,94,2018,151.56666666666666\n2018-04-05,157,4,95,2018,152.7\n2018-04-06,221,5,96,2018,155.3\n2018-04-07,119,6,97,2018,154.66666666666666\n2018-04-08,162,7,98,2018,154.7\n2018-04-09,133,1,99,2018,155.43333333333334\n2018-04-10,196,2,100,2018,160.4\n2018-04-11,172,3,101,2018,160.3\n2018-04-12,206,4,102,2018,162.3\n2018-04-13,203,5,103,2018,163.23333333333332\n2018-04-14,89,6,104,2018,161.5\n2018-04-15,98,7,105,2018,160.26666666666668\n2018-04-16,176,1,106,2018,162.26666666666668\n2018-04-17,166,2,107,2018,164.03333333333333\n2018-04-18,155,3,108,2018,162.56666666666666\n2018-04-19,140,4,109,2018,160.6\n2018-04-20,166,5,110,2018,159.23333333333332\n2018-04-21,69,6,111,2018,156.63333333333333\n2018-04-22,91,7,112,2018,154.83333333333334\n2018-04-23,156,1,113,2018,154.66666666666666\n2018-04-24,199,2,114,2018,156.93333333333334\n2018-04-25,144,3,115,2018,156.06666666666666\n2018-04-26,148,4,116,2018,155.66666666666666\n2018-04-27,147,5,117,2018,154.16666666666666\n2018-04-28,145,6,118,2018,154.26666666666668\n2018-04-29,161,7,119,2018,154.56666666666666\n2018-04-30,176,1,120,2018,155.4\n2018-05-01,197,2,121,2018,159.33333333333334\n2018-05-02,175,3,122,2018,160.16666666666666\n2018-05-03,162,4,123,2018,157.93333333333334\n2018-05-04,159,5,124,2018,156.26666666666668\n2018-05-05,68,6,125,2018,153.3\n2018-05-06,100,7,126,2018,149.26666666666668\n2018-05-07,184,1,127,2018,151.43333333333334\n2018-05-08,227,2,128,2018,153.6\n2018-05-09,129,3,129,2018,153.46666666666667\n2018-05-10,150,4,130,2018,151.93333333333334\n2018-05-11,195,5,131,2018,152.7\n2018-05-12,115,6,132,2018,149.66666666666666\n2018-05-13,77,7,133,2018,145.46666666666667\n2018-05-14,178,1,134,2018,148.43333333333334\n2018-05-15,194,2,135,2018,151.63333333333333\n2018-05-16,178,3,136,2018,151.7\n2018-05-17,198,4,137,2018,152.76666666666668\n2018-05-18,150,5,138,2018,152.6\n2018-05-19,70,6,139,2018,150.26666666666668\n2018-05-20,68,7,140,2018,147.0\n2018-05-21,140,1,141,2018,149.36666666666667\n2018-05-22,175,2,142,2018,152.16666666666666\n2018-05-23,186,3,143,2018,153.16666666666666\n2018-05-24,152,4,144,2018,151.6\n2018-05-25,116,5,145,2018,150.66666666666666\n2018-05-26,38,6,146,2018,147.0\n2018-05-27,136,7,147,2018,146.63333333333333\n2018-05-28,169,1,148,2018,147.43333333333334\n2018-05-29,149,2,149,2018,147.03333333333333\n2018-05-30,170,3,150,2018,146.83333333333334\n2018-05-31,229,4,151,2018,147.9\n2018-06-01,228,5,152,2018,149.66666666666666\n2018-06-02,50,6,153,2018,145.93333333333334\n2018-06-03,58,7,154,2018,142.56666666666666\n2018-06-04,167,1,155,2018,145.86666666666667\n2018-06-05,150,2,156,2018,147.53333333333333\n2018-06-06,200,3,157,2018,148.06666666666666\n2018-06-07,232,4,158,2018,148.23333333333332\n2018-06-08,186,5,159,2018,150.13333333333333\n2018-06-09,113,6,160,2018,148.9\n2018-06-10,88,7,161,2018,145.33333333333334\n2018-06-11,160,1,162,2018,146.83333333333334\n2018-06-12,216,2,163,2018,151.46666666666667\n2018-06-13,180,3,164,2018,151.53333333333333\n2018-06-14,176,4,165,2018,150.93333333333334\n2018-06-15,178,5,166,2018,150.93333333333334\n2018-06-16,93,6,167,2018,147.43333333333334\n2018-06-17,51,7,168,2018,144.13333333333333\n2018-06-18,112,1,169,2018,145.53333333333333\n2018-06-19,117,2,170,2018,147.16666666666666\n2018-06-20,135,3,171,2018,147.0\n2018-06-21,126,4,172,2018,145.36666666666667\n2018-06-22,94,5,173,2018,142.3\n2018-06-23,73,6,174,2018,139.66666666666666\n2018-06-24,81,7,175,2018,138.5\n2018-06-25,137,1,176,2018,141.8\n2018-06-26,208,2,177,2018,144.2\n2018-06-27,127,3,178,2018,142.8\n2018-06-28,152,4,179,2018,142.9\n2018-06-29,134,5,180,2018,141.7\n2018-06-30,98,6,181,2018,137.33333333333334\n2018-07-01,128,7,182,2018,134.0\n2018-07-02,144,1,183,2018,137.13333333333333\n2018-07-03,127,2,184,2018,139.43333333333334\n2018-07-04,70,3,185,2018,136.2\n2018-07-05,117,4,186,2018,135.1\n2018-07-06,115,5,187,2018,132.26666666666668\n2018-07-07,55,6,188,2018,126.36666666666666\n2018-07-08,57,7,189,2018,122.06666666666666\n2018-07-09,104,1,190,2018,121.76666666666667\n2018-07-10,133,2,191,2018,123.26666666666667\n2018-07-11,238,3,192,2018,125.86666666666666\n2018-07-12,135,4,193,2018,123.16666666666667\n2018-07-13,244,5,194,2018,125.3\n2018-07-14,74,6,195,2018,121.9\n2018-07-15,86,7,196,2018,118.83333333333333\n2018-07-16,178,1,197,2018,121.66666666666667\n2018-07-17,195,2,198,2018,126.46666666666667\n2018-07-18,201,3,199,2018,129.43333333333334\n2018-07-19,149,4,200,2018,130.5\n2018-07-20,122,5,201,2018,130.06666666666666\n2018-07-21,89,6,202,2018,128.83333333333334\n2018-07-22,81,7,203,2018,128.4\n2018-07-23,169,1,204,2018,131.6\n2018-07-24,170,2,205,2018,134.56666666666666\n2018-07-25,134,3,206,2018,134.46666666666667\n2018-07-26,136,4,207,2018,132.06666666666666\n2018-07-27,135,5,208,2018,132.33333333333334\n2018-07-28,79,6,209,2018,129.9\n2018-07-29,79,7,210,2018,128.06666666666666\n2018-07-30,144,1,211,2018,129.6\n2018-07-31,120,2,212,2018,129.33333333333334\n2018-08-01,150,3,213,2018,129.53333333333333\n2018-08-02,108,4,214,2018,128.9\n2018-08-03,147,5,215,2018,131.46666666666667\n2018-08-04,65,6,216,2018,129.73333333333332\n2018-08-05,66,7,217,2018,128.1\n2018-08-06,139,1,218,2018,130.9\n2018-08-07,142,2,219,2018,133.73333333333332\n2018-08-08,117,3,220,2018,134.16666666666666\n2018-08-09,79,4,221,2018,132.36666666666667\n2018-08-10,84,5,222,2018,127.23333333333333\n2018-08-11,103,6,223,2018,126.16666666666667\n2018-08-12,79,7,224,2018,120.66666666666667\n2018-08-13,99,1,225,2018,121.5\n2018-08-14,126,2,226,2018,122.83333333333333\n2018-08-15,106,3,227,2018,120.43333333333334\n2018-08-16,143,4,228,2018,118.7\n2018-08-17,114,5,229,2018,115.8\n2018-08-18,68,6,230,2018,113.1\n2018-08-19,34,7,231,2018,110.16666666666667\n2018-08-20,83,1,232,2018,109.96666666666667\n2018-08-21,75,2,233,2018,109.76666666666667\n2018-08-22,108,3,234,2018,107.73333333333333\n2018-08-23,84,4,235,2018,104.86666666666666\n2018-08-24,85,5,236,2018,103.23333333333333\n2018-08-25,66,6,237,2018,100.9\n2018-08-26,50,7,238,2018,98.06666666666666\n2018-08-27,77,1,239,2018,98.0\n2018-08-28,114,2,240,2018,99.16666666666667\n2018-08-29,116,3,241,2018,98.23333333333333\n2018-08-30,112,4,242,2018,97.96666666666667\n2018-08-31,114,5,243,2018,96.76666666666667\n2018-09-01,99,6,244,2018,96.46666666666667\n2018-09-02,92,7,245,2018,94.63333333333334\n2018-09-03,87,1,246,2018,95.36666666666666\n2018-09-04,122,2,247,2018,97.23333333333333\n2018-09-05,125,3,248,2018,96.76666666666667\n2018-09-06,104,4,249,2018,95.5\n2018-09-07,139,5,250,2018,96.23333333333333\n2018-09-08,83,6,251,2018,96.36666666666666\n2018-09-09,57,7,252,2018,95.46666666666667\n2018-09-10,110,1,253,2018,95.7\n2018-09-11,119,2,254,2018,97.03333333333333\n2018-09-12,119,3,255,2018,97.7\n2018-09-13,141,4,256,2018,98.2\n2018-09-14,147,5,257,2018,99.56666666666666\n2018-09-15,67,6,258,2018,97.03333333333333\n2018-09-16,96,7,259,2018,96.43333333333334\n2018-09-17,104,1,260,2018,97.63333333333334\n2018-09-18,140,2,261,2018,101.16666666666667\n2018-09-19,159,3,262,2018,103.7\n2018-09-20,125,4,263,2018,105.36666666666666\n2018-09-21,141,5,264,2018,106.46666666666667\n2018-09-22,61,6,265,2018,105.7\n2018-09-23,84,7,266,2018,105.66666666666667\n2018-09-24,139,1,267,2018,108.1\n2018-09-25,107,2,268,2018,110.0\n2018-09-26,159,3,269,2018,112.73333333333333\n2018-09-27,140,4,270,2018,113.6\n2018-09-28,144,5,271,2018,114.53333333333333\n2018-09-29,92,6,272,2018,113.86666666666666\n2018-09-30,95,7,273,2018,113.23333333333333\n2018-10-01,157,1,274,2018,115.16666666666667\n2018-10-02,173,2,275,2018,117.86666666666666\n2018-10-03,186,3,276,2018,121.16666666666667\n2018-10-04,155,4,277,2018,122.26666666666667\n2018-10-05,137,5,278,2018,122.66666666666667\n2018-10-06,65,6,279,2018,121.36666666666666\n2018-10-07,35,7,280,2018,117.9\n2018-10-08,135,1,281,2018,119.63333333333334\n2018-10-09,172,2,282,2018,123.46666666666667\n2018-10-10,130,3,283,2018,124.13333333333334\n2018-10-11,119,4,284,2018,124.13333333333334\n2018-10-12,140,5,285,2018,124.83333333333333\n2018-10-13,98,6,286,2018,123.4\n2018-10-14,66,7,287,2018,120.7\n2018-10-15,134,1,288,2018,122.93333333333334\n2018-10-16,183,2,289,2018,125.83333333333333\n2018-10-17,152,3,290,2018,127.43333333333334\n2018-10-18,150,4,291,2018,127.76666666666667\n2018-10-19,146,5,292,2018,127.33333333333333\n2018-10-20,125,6,293,2018,127.33333333333333\n2018-10-21,146,7,294,2018,127.5\n2018-10-22,134,1,295,2018,129.93333333333334\n2018-10-23,152,2,296,2018,132.2\n2018-10-24,143,3,297,2018,132.33333333333334\n2018-10-25,116,4,298,2018,132.63333333333333\n2018-10-26,133,5,299,2018,131.76666666666668\n2018-10-27,136,6,300,2018,131.63333333333333\n2018-10-28,119,7,301,2018,130.8\n2018-10-29,149,1,302,2018,132.7\n2018-10-30,250,2,303,2018,137.86666666666667\n2018-10-31,174,3,304,2018,138.43333333333334\n2018-11-01,251,4,305,2018,141.03333333333333\n2018-11-02,168,5,306,2018,140.43333333333334\n2018-11-03,86,6,307,2018,138.13333333333333\n2018-11-04,287,7,308,2018,143.13333333333333\n2018-11-05,157,1,309,2018,146.2\n2018-11-06,161,2,310,2018,150.4\n2018-11-07,157,3,311,2018,151.13333333333333\n2018-11-08,158,4,312,2018,150.66666666666666\n2018-11-09,205,5,313,2018,153.16666666666666\n2018-11-10,168,6,314,2018,154.8\n2018-11-11,235,7,315,2018,157.96666666666667\n2018-11-12,95,1,316,2018,157.86666666666667\n2018-11-13,179,2,317,2018,161.63333333333333\n2018-11-14,205,3,318,2018,164.0\n2018-11-15,171,4,319,2018,163.6\n2018-11-16,171,5,320,2018,164.23333333333332\n2018-11-17,86,6,321,2018,162.1\n2018-11-18,67,7,322,2018,159.46666666666667\n2018-11-19,160,1,323,2018,160.63333333333333\n2018-11-20,210,2,324,2018,162.76666666666668\n2018-11-21,177,3,325,2018,164.2\n2018-11-22,80,4,326,2018,161.8\n2018-11-23,121,5,327,2018,161.06666666666666\n2018-11-24,92,6,328,2018,160.26666666666668\n2018-11-25,117,7,329,2018,159.73333333333332\n2018-11-26,131,1,330,2018,159.56666666666666\n2018-11-27,143,2,331,2018,160.36666666666667\n2018-11-28,169,3,332,2018,161.03333333333333\n2018-11-29,177,4,333,2018,158.6\n2018-11-30,188,5,334,2018,159.06666666666666\n2018-12-01,153,6,335,2018,155.8\n2018-12-02,128,7,336,2018,154.46666666666667\n2018-12-03,225,1,337,2018,159.1\n2018-12-04,137,2,338,2018,154.1\n2018-12-05,219,3,339,2018,156.16666666666666\n2018-12-06,163,4,340,2018,156.23333333333332\n2018-12-07,169,5,341,2018,156.63333333333333\n2018-12-08,59,6,342,2018,153.33333333333334\n2018-12-09,67,7,343,2018,148.73333333333332\n2018-12-10,142,1,344,2018,147.86666666666667\n2018-12-11,130,2,345,2018,144.36666666666667\n2018-12-12,214,3,346,2018,148.33333333333334\n2018-12-13,115,4,347,2018,146.2\n2018-12-14,110,5,348,2018,143.03333333333333\n2018-12-15,95,6,349,2018,140.5\n2018-12-16,91,7,350,2018,137.83333333333334\n2018-12-17,166,1,351,2018,140.5\n2018-12-18,164,2,352,2018,143.73333333333332\n2018-12-19,129,3,353,2018,142.7\n2018-12-20,132,4,354,2018,140.1\n2018-12-21,82,5,355,2018,136.93333333333334\n2018-12-22,75,6,356,2018,136.76666666666668\n2018-12-23,49,7,357,2018,134.36666666666667\n2018-12-24,47,1,358,2018,132.86666666666667\n2018-12-25,25,2,359,2018,129.8\n2018-12-26,50,3,360,2018,127.1\n2018-12-27,103,4,361,2018,125.76666666666667\n2018-12-28,123,5,362,2018,124.23333333333333\n2018-12-29,60,6,363,2018,120.33333333333333\n2018-12-30,92,7,364,2018,117.13333333333334\n2018-12-31,91,1,365,2018,115.06666666666666\n2019-01-01,73,2,1,2019,113.23333333333333\n2019-01-02,133,3,2,2019,110.16666666666667\n2019-01-03,107,4,3,2019,109.16666666666667\n2019-01-04,141,5,4,2019,106.56666666666666\n2019-01-05,74,6,5,2019,103.6\n2019-01-06,93,7,6,2019,101.06666666666666\n2019-01-07,113,1,7,2019,102.86666666666666\n2019-01-08,137,2,8,2019,105.2\n2019-01-09,178,3,9,2019,106.4\n2019-01-10,185,4,10,2019,108.23333333333333\n2019-01-11,133,5,11,2019,105.53333333333333\n2019-01-12,102,6,12,2019,105.1\n2019-01-13,83,7,13,2019,104.2\n2019-01-14,155,1,14,2019,106.2\n2019-01-15,149,2,15,2019,108.13333333333334\n2019-01-16,139,3,16,2019,107.23333333333333\n2019-01-17,175,4,17,2019,107.6\n2019-01-18,165,5,18,2019,108.8\n2019-01-19,158,6,19,2019,109.66666666666667\n2019-01-20,101,7,20,2019,110.3\n2019-01-21,181,1,21,2019,113.83333333333333\n2019-01-22,186,2,22,2019,118.4\n2019-01-23,164,3,23,2019,122.3\n2019-01-24,173,4,24,2019,127.23333333333333\n2019-01-25,112,5,25,2019,129.3\n2019-01-26,61,6,26,2019,127.9\n2019-01-27,83,7,27,2019,126.56666666666666\n2019-01-28,103,1,28,2019,128.0\n2019-01-29,106,2,29,2019,128.46666666666667\n2019-01-30,117,3,30,2019,129.33333333333334\n2019-01-31,93,4,31,2019,130.0\n2019-02-01,156,5,32,2019,130.76666666666668\n2019-02-02,101,6,33,2019,130.56666666666666\n2019-02-03,101,7,34,2019,129.23333333333332\n2019-02-04,138,1,35,2019,131.36666666666667\n2019-02-05,129,2,36,2019,132.56666666666666\n2019-02-06,158,3,37,2019,134.06666666666666\n2019-02-07,123,4,38,2019,133.6\n2019-02-08,175,5,39,2019,133.5\n2019-02-09,115,6,40,2019,131.16666666666666\n2019-02-10,122,7,41,2019,130.8\n2019-02-11,150,1,42,2019,132.4\n2019-02-12,151,2,43,2019,134.66666666666666\n2019-02-13,157,3,44,2019,134.73333333333332\n2019-02-14,150,4,45,2019,134.76666666666668\n2019-02-15,164,5,46,2019,135.6\n2019-02-16,178,6,47,2019,135.7\n2019-02-17,100,7,48,2019,133.53333333333333\n2019-02-18,161,1,49,2019,133.63333333333333\n2019-02-19,226,2,50,2019,137.8\n2019-02-20,197,3,51,2019,138.33333333333334\n2019-02-21,217,4,52,2019,139.36666666666667\n2019-02-22,154,5,53,2019,139.03333333333333\n2019-02-23,91,6,54,2019,136.3\n2019-02-24,102,7,55,2019,135.96666666666667\n2019-02-25,241,1,56,2019,141.96666666666667\n2019-02-26,164,2,57,2019,144.66666666666666\n2019-02-27,191,3,58,2019,147.6\n2019-02-28,164,4,59,2019,149.53333333333333\n2019-03-01,117,5,60,2019,149.53333333333333\n2019-03-02,43,6,61,2019,147.86666666666667\n2019-03-03,150,7,62,2019,147.66666666666666\n2019-03-04,129,1,63,2019,148.6\n2019-03-05,128,2,64,2019,149.5\n2019-03-06,113,3,65,2019,148.66666666666666\n2019-03-07,109,4,66,2019,148.0\n2019-03-08,101,5,67,2019,146.1\n2019-03-09,109,6,68,2019,145.63333333333333\n2019-03-10,85,7,69,2019,142.63333333333333\n2019-03-11,133,1,70,2019,143.23333333333332\n2019-03-12,110,2,71,2019,142.83333333333334\n2019-03-13,104,3,72,2019,141.3\n2019-03-14,104,4,73,2019,139.73333333333332\n2019-03-15,116,5,74,2019,138.36666666666667\n2019-03-16,66,6,75,2019,135.56666666666666\n2019-03-17,66,7,76,2019,132.3\n2019-03-18,105,1,77,2019,129.86666666666667\n2019-03-19,119,2,78,2019,130.5\n2019-03-20,137,3,79,2019,129.7\n2019-03-21,172,4,80,2019,127.9\n2019-03-22,118,5,81,2019,125.26666666666667\n2019-03-23,73,6,82,2019,120.46666666666667\n2019-03-24,50,7,83,2019,117.0\n2019-03-25,141,1,84,2019,118.66666666666667\n2019-03-26,159,2,85,2019,120.56666666666666\n2019-03-27,107,3,86,2019,116.1\n2019-03-28,100,4,87,2019,113.96666666666667\n2019-03-29,134,5,88,2019,112.06666666666666\n2019-03-30,92,6,89,2019,109.66666666666667\n2019-03-31,70,7,90,2019,108.1\n2019-04-01,139,1,91,2019,111.3\n2019-04-02,114,2,92,2019,110.1\n2019-04-03,113,3,93,2019,109.56666666666666\n2019-04-04,97,4,94,2019,108.53333333333333\n2019-04-05,125,5,95,2019,108.93333333333334\n2019-04-06,37,6,96,2019,106.53333333333333\n2019-04-07,51,7,97,2019,104.86666666666666\n2019-04-08,154,1,98,2019,106.36666666666666\n2019-04-09,118,2,99,2019,107.46666666666667\n2019-04-10,169,3,100,2019,108.66666666666667\n2019-04-11,109,4,101,2019,108.63333333333334\n2019-04-12,107,5,102,2019,108.73333333333333\n2019-04-13,42,6,103,2019,106.66666666666667\n2019-04-14,58,7,104,2019,104.73333333333333\n2019-04-15,108,1,105,2019,106.13333333333334\n2019-04-16,135,2,106,2019,108.43333333333334\n2019-04-17,73,3,107,2019,107.36666666666666\n2019-04-18,114,4,108,2019,107.2\n2019-04-19,112,5,109,2019,106.36666666666666\n2019-04-20,92,6,110,2019,103.7\n2019-04-21,70,7,111,2019,102.1\n2019-04-22,104,1,112,2019,103.13333333333334\n2019-04-23,84,2,113,2019,104.26666666666667\n2019-04-24,100,3,114,2019,102.9\n2019-04-25,115,4,115,2019,101.43333333333334\n2019-04-26,92,5,116,2019,100.93333333333334\n2019-04-27,44,6,117,2019,99.06666666666666\n2019-04-28,106,7,118,2019,98.13333333333334\n2019-04-29,126,1,119,2019,99.26666666666667\n2019-04-30,78,2,120,2019,99.53333333333333\n2019-05-01,116,3,121,2019,98.76666666666667\n2019-05-02,108,4,122,2019,98.56666666666666\n2019-05-03,78,5,123,2019,97.4\n2019-05-04,50,6,124,2019,95.83333333333333\n2019-05-05,85,7,125,2019,94.5\n2019-05-06,115,1,126,2019,97.1\n2019-05-07,120,2,127,2019,99.4\n2019-05-08,124,3,128,2019,98.4\n2019-05-09,108,4,129,2019,98.06666666666666\n2019-05-10,80,5,130,2019,95.1\n2019-05-11,86,6,131,2019,94.33333333333333\n2019-05-12,69,7,132,2019,93.06666666666666\n2019-05-13,102,1,133,2019,95.06666666666666\n2019-05-14,100,2,134,2019,96.46666666666667\n2019-05-15,80,3,135,2019,95.53333333333333\n2019-05-16,99,4,136,2019,94.33333333333333\n2019-05-17,89,5,137,2019,94.86666666666666\n2019-05-18,51,6,138,2019,92.76666666666667\n2019-05-19,64,7,139,2019,91.16666666666667\n2019-05-20,111,1,140,2019,91.8\n2019-05-21,97,2,141,2019,92.7\n2019-05-22,103,3,142,2019,92.66666666666667\n2019-05-23,141,4,143,2019,94.56666666666666\n2019-05-24,68,5,144,2019,93.5\n2019-05-25,75,6,145,2019,92.16666666666667\n2019-05-26,75,7,146,2019,91.6\n2019-05-27,58,1,147,2019,92.06666666666666\n2019-05-28,79,2,148,2019,91.16666666666667\n2019-05-29,87,3,149,2019,89.86666666666666\n2019-05-30,125,4,150,2019,91.43333333333334\n2019-05-31,120,5,151,2019,91.56666666666666\n2019-06-01,69,6,152,2019,90.26666666666667\n2019-06-02,74,7,153,2019,90.13333333333334\n2019-06-03,112,1,154,2019,92.2\n2019-06-04,88,2,155,2019,92.3\n2019-06-05,138,3,156,2019,93.06666666666666\n2019-06-06,95,4,157,2019,92.23333333333333\n2019-06-07,100,5,158,2019,91.43333333333334\n2019-06-08,95,6,159,2019,91.0\n2019-06-09,88,7,160,2019,91.26666666666667\n2019-06-10,97,1,161,2019,91.63333333333334\n2019-06-11,105,2,162,2019,92.83333333333333\n2019-06-12,104,3,163,2019,92.9\n2019-06-13,88,4,164,2019,92.5\n2019-06-14,89,5,165,2019,92.8\n2019-06-15,47,6,166,2019,91.06666666666666\n2019-06-16,41,7,167,2019,89.46666666666667\n2019-06-17,78,1,168,2019,90.36666666666666\n2019-06-18,68,2,169,2019,90.5\n2019-06-19,115,3,170,2019,90.63333333333334\n2019-06-20,86,4,171,2019,90.26666666666667\n2019-06-21,105,5,172,2019,90.33333333333333\n2019-06-22,43,6,173,2019,87.06666666666666\n2019-06-23,79,7,174,2019,87.43333333333334\n2019-06-24,92,1,175,2019,88.0\n2019-06-25,77,2,176,2019,88.06666666666666\n2019-06-26,97,3,177,2019,89.36666666666666\n2019-06-27,96,4,178,2019,89.93333333333334\n2019-06-28,92,5,179,2019,90.1\n2019-06-29,92,6,180,2019,89.0\n2019-06-30,57,7,181,2019,86.9\n2019-07-01,94,1,182,2019,87.73333333333333\n2019-07-02,164,2,183,2019,90.73333333333333\n2019-07-03,101,3,184,2019,90.36666666666666\n2019-07-04,89,4,185,2019,90.4\n2019-07-05,67,5,186,2019,88.03333333333333\n2019-07-06,59,6,187,2019,86.83333333333333\n2019-07-07,37,7,188,2019,84.73333333333333\n2019-07-08,146,1,189,2019,86.43333333333334\n2019-07-09,89,2,190,2019,86.46666666666667\n2019-07-10,136,3,191,2019,87.76666666666667\n2019-07-11,109,4,192,2019,87.9\n2019-07-12,102,5,193,2019,87.83333333333333\n2019-07-13,78,6,194,2019,87.5\n2019-07-14,65,7,195,2019,86.7\n2019-07-15,122,1,196,2019,89.2\n2019-07-16,142,2,197,2019,92.56666666666666\n2019-07-17,113,3,198,2019,93.73333333333333\n2019-07-18,103,4,199,2019,94.9\n2019-07-19,102,5,200,2019,94.46666666666667\n2019-07-20,92,6,201,2019,94.66666666666667\n2019-07-21,41,7,202,2019,92.53333333333333\n2019-07-22,97,1,203,2019,94.33333333333333\n2019-07-23,82,2,204,2019,94.43333333333334\n2019-07-24,124,3,205,2019,95.5\n2019-07-25,129,4,206,2019,97.23333333333333\n2019-07-26,115,5,207,2019,97.83333333333333\n2019-07-27,70,6,208,2019,96.96666666666667\n2019-07-28,67,7,209,2019,96.13333333333334\n2019-07-29,98,1,210,2019,96.33333333333333\n2019-07-30,106,2,211,2019,97.96666666666667\n2019-07-31,76,3,212,2019,97.36666666666666\n2019-08-01,140,4,213,2019,96.56666666666666\n2019-08-02,77,5,214,2019,95.76666666666667\n2019-08-03,86,6,215,2019,95.66666666666667\n2019-08-04,52,7,216,2019,95.16666666666667\n2019-08-05,159,1,217,2019,98.5\n2019-08-06,132,2,218,2019,101.66666666666667\n2019-08-07,142,3,219,2019,101.53333333333333\n2019-08-08,154,4,220,2019,103.7\n2019-08-09,146,5,221,2019,104.03333333333333\n2019-08-10,87,6,222,2019,103.3\n2019-08-11,124,7,223,2019,104.03333333333333\n2019-08-12,175,1,224,2019,107.26666666666667\n2019-08-13,204,2,225,2019,111.9\n2019-08-14,204,3,226,2019,114.63333333333334\n2019-08-15,150,4,227,2019,114.9\n2019-08-16,149,5,228,2019,116.1\n2019-08-17,114,6,229,2019,116.46666666666667\n2019-08-18,116,7,230,2019,116.93333333333334\n2019-08-19,131,1,231,2019,118.23333333333333\n2019-08-20,135,2,232,2019,121.36666666666666\n2019-08-21,162,3,233,2019,123.53333333333333\n2019-08-22,159,4,234,2019,126.1\n2019-08-23,193,5,235,2019,128.4\n2019-08-24,115,6,236,2019,127.93333333333334\n2019-08-25,59,7,237,2019,126.06666666666666\n2019-08-26,106,1,238,2019,127.26666666666667\n2019-08-27,123,2,239,2019,129.13333333333333\n2019-08-28,172,3,240,2019,131.6\n2019-08-29,120,4,241,2019,132.06666666666666\n2019-08-30,86,5,242,2019,132.4\n2019-08-31,75,6,243,2019,130.23333333333332\n2019-09-01,87,7,244,2019,130.56666666666666\n2019-09-02,126,1,245,2019,131.9\n2019-09-03,125,2,246,2019,134.33333333333334\n2019-09-04,144,3,247,2019,133.83333333333334\n2019-09-05,145,4,248,2019,134.26666666666668\n2019-09-06,109,5,249,2019,133.16666666666666\n2019-09-07,105,6,250,2019,131.53333333333333\n2019-09-08,111,7,251,2019,130.36666666666667\n2019-09-09,131,1,252,2019,131.83333333333334\n2019-09-10,144,2,253,2019,132.5\n2019-09-11,148,3,254,2019,131.6\n2019-09-12,104,4,255,2019,128.26666666666668\n2019-09-13,161,5,256,2019,126.83333333333333\n2019-09-14,83,6,257,2019,124.6\n2019-09-15,75,7,258,2019,122.13333333333334\n2019-09-16,109,1,259,2019,121.96666666666667\n2019-09-17,131,2,260,2019,122.46666666666667\n2019-09-18,112,3,261,2019,121.83333333333333\n2019-09-19,115,4,262,2019,121.16666666666667\n2019-09-20,167,5,263,2019,121.33333333333333\n2019-09-21,156,6,264,2019,121.23333333333333\n2019-09-22,94,7,265,2019,117.93333333333334\n2019-09-23,107,1,266,2019,117.66666666666667\n2019-09-24,147,2,267,2019,120.6\n2019-09-25,138,3,268,2019,121.66666666666667\n2019-09-26,144,4,269,2019,122.36666666666666\n2019-09-27,119,5,270,2019,120.6\n2019-09-28,29,6,271,2019,117.56666666666666\n2019-09-29,50,7,272,2019,116.36666666666666\n2019-09-30,132,1,273,2019,118.26666666666667\n2019-10-01,142,2,274,2019,120.1\n2019-10-02,138,3,275,2019,120.5\n2019-10-03,129,4,276,2019,120.63333333333334\n2019-10-04,110,5,277,2019,119.5\n2019-10-05,74,6,278,2019,117.13333333333334\n2019-10-06,70,7,279,2019,115.83333333333333\n2019-10-07,118,1,280,2019,116.26666666666667\n2019-10-08,114,2,281,2019,116.36666666666666\n2019-10-09,123,3,282,2019,116.1\n2019-10-10,137,4,283,2019,115.86666666666666\n2019-10-11,151,5,284,2019,115.96666666666667\n2019-10-12,70,6,285,2019,114.83333333333333\n2019-10-13,103,7,286,2019,112.9\n2019-10-14,110,1,287,2019,113.8\n2019-10-15,170,2,288,2019,116.96666666666667\n2019-10-16,130,3,289,2019,117.66666666666667\n2019-10-17,122,4,290,2019,117.36666666666666\n2019-10-18,122,5,291,2019,117.7\n2019-10-19,85,6,292,2019,116.7\n2019-10-20,51,7,293,2019,112.83333333333333\n2019-10-21,126,1,294,2019,111.83333333333333\n2019-10-22,94,2,295,2019,111.83333333333333\n2019-10-23,99,3,296,2019,111.56666666666666\n2019-10-24,154,4,297,2019,111.8\n2019-10-25,119,5,298,2019,111.16666666666667\n2019-10-26,105,6,299,2019,109.86666666666666\n2019-10-27,92,7,300,2019,108.96666666666667\n2019-10-28,130,1,301,2019,112.33333333333333\n2019-10-29,146,2,302,2019,115.53333333333333\n2019-10-30,164,3,303,2019,116.6\n2019-10-31,184,4,304,2019,118.0\n2019-11-01,187,5,305,2019,119.63333333333334\n2019-11-02,102,6,306,2019,118.73333333333333\n2019-11-03,110,7,307,2019,118.73333333333333\n2019-11-04,121,1,308,2019,120.3\n2019-11-05,161,2,309,2019,123.33333333333333\n2019-11-06,123,3,310,2019,123.5\n2019-11-07,119,4,311,2019,123.66666666666667\n2019-11-08,131,5,312,2019,123.93333333333334\n2019-11-09,71,6,313,2019,121.73333333333333\n2019-11-10,85,7,314,2019,119.53333333333333\n2019-11-11,113,1,315,2019,120.96666666666667\n2019-11-12,94,2,316,2019,120.66666666666667\n2019-11-13,124,3,317,2019,121.13333333333334\n2019-11-14,100,4,318,2019,118.8\n2019-11-15,135,5,319,2019,118.96666666666667\n2019-11-16,97,6,320,2019,118.13333333333334\n2019-11-17,110,7,321,2019,117.73333333333333\n2019-11-18,111,1,322,2019,118.6\n2019-11-19,123,2,323,2019,121.0\n2019-11-20,127,3,324,2019,121.03333333333333\n2019-11-21,115,4,325,2019,121.73333333333333\n2019-11-22,92,5,326,2019,121.5\n2019-11-23,61,6,327,2019,118.4\n2019-11-24,90,7,328,2019,117.43333333333334\n2019-11-25,114,1,329,2019,117.73333333333333\n2019-11-26,106,2,330,2019,118.2\n2019-11-27,144,3,331,2019,118.66666666666667\n2019-11-28,114,4,332,2019,117.6\n2019-11-29,115,5,333,2019,115.96666666666667\n2019-11-30,116,6,334,2019,113.7\n2019-12-01,103,7,335,2019,110.9\n2019-12-02,141,1,336,2019,112.2\n2019-12-03,116,2,337,2019,112.4\n2019-12-04,122,3,338,2019,112.43333333333334\n2019-12-05,157,4,339,2019,112.3\n2019-12-06,158,5,340,2019,113.46666666666667\n2019-12-07,95,6,341,2019,112.66666666666667\n2019-12-08,110,7,342,2019,111.96666666666667\n2019-12-09,113,1,343,2019,113.36666666666666\n2019-12-10,149,2,344,2019,115.5\n2019-12-11,142,3,345,2019,116.46666666666667\n2019-12-12,187,4,346,2019,119.56666666666666\n2019-12-13,145,5,347,2019,120.26666666666667\n2019-12-14,113,6,348,2019,120.7\n2019-12-15,89,7,349,2019,119.16666666666667\n2019-12-16,125,1,350,2019,120.1\n2019-12-17,201,2,351,2019,123.13333333333334\n2019-12-18,176,3,352,2019,125.3\n2019-12-19,206,4,353,2019,128.06666666666666\n2019-12-20,180,5,354,2019,129.83333333333334\n2019-12-21,90,6,355,2019,129.0\n2019-12-22,79,7,356,2019,128.56666666666666\n2019-12-23,49,1,357,2019,128.16666666666666\n2019-12-24,110,2,358,2019,128.83333333333334\n2019-12-25,76,3,359,2019,127.56666666666666\n2019-12-26,78,4,360,2019,126.63333333333334\n2019-12-27,124,5,361,2019,125.96666666666667\n2019-12-28,117,6,362,2019,126.06666666666666\n2019-12-29,60,7,363,2019,124.23333333333333\n2019-12-30,156,1,364,2019,125.56666666666666\n2019-12-31,126,2,365,2019,126.33333333333333\n2020-01-01,99,3,1,2020,124.93333333333334\n2020-01-02,142,4,2,2020,125.8\n2020-01-03,95,5,3,2020,124.9\n2020-01-04,120,6,4,2020,123.66666666666667\n2020-01-05,81,7,5,2020,121.1\n2020-01-06,125,1,6,2020,122.1\n2020-01-07,161,2,7,2020,123.8\n2020-01-08,169,3,8,2020,125.66666666666667\n2020-01-09,192,4,9,2020,127.1\n2020-01-10,251,5,10,2020,130.73333333333332\n2020-01-11,164,6,11,2020,129.96666666666667\n2020-01-12,219,7,12,2020,132.43333333333334\n2020-01-13,224,1,13,2020,136.13333333333333\n2020-01-14,193,2,14,2020,139.6\n2020-01-15,248,3,15,2020,143.7\n2020-01-16,255,4,16,2020,145.5\n2020-01-17,247,5,17,2020,147.86666666666667\n2020-01-18,117,6,18,2020,144.9\n2020-01-19,187,7,19,2020,145.13333333333333\n2020-01-20,138,1,20,2020,146.73333333333332\n2020-01-21,139,2,21,2020,148.73333333333332\n2020-01-22,199,3,22,2020,153.73333333333332\n2020-01-23,185,4,23,2020,156.23333333333332\n2020-01-24,143,5,24,2020,158.46666666666667\n2020-01-25,64,6,25,2020,158.0\n2020-01-26,89,7,26,2020,156.83333333333334\n2020-01-27,135,1,27,2020,157.43333333333334\n2020-01-28,101,2,28,2020,158.8\n2020-01-29,114,3,29,2020,157.4\n2020-01-30,155,4,30,2020,158.36666666666667\n2020-01-31,165,5,31,2020,160.56666666666666\n2020-02-01,89,6,32,2020,158.8\n2020-02-02,111,7,33,2020,159.33333333333334\n2020-02-03,141,1,34,2020,160.03333333333333\n2020-02-04,120,2,35,2020,161.33333333333334\n2020-02-05,145,3,36,2020,162.0\n2020-02-06,133,4,37,2020,161.06666666666666\n2020-02-07,149,5,38,2020,160.4\n2020-02-08,137,6,39,2020,158.56666666666666\n2020-02-09,119,7,40,2020,154.16666666666666\n2020-02-10,152,1,41,2020,153.76666666666668\n2020-02-11,162,2,42,2020,151.86666666666667\n2020-02-12,134,3,43,2020,148.86666666666667\n2020-02-13,170,4,44,2020,148.1\n2020-02-14,149,5,45,2020,144.8\n2020-02-15,95,6,46,2020,139.46666666666667\n2020-02-16,66,7,47,2020,133.43333333333334\n2020-02-17,129,1,48,2020,133.83333333333334\n2020-02-18,175,2,49,2020,133.43333333333334\n2020-02-19,133,3,50,2020,133.26666666666668\n2020-02-20,128,4,51,2020,132.9\n2020-02-21,133,5,52,2020,130.7\n2020-02-22,99,6,53,2020,127.83333333333333\n2020-02-23,165,7,54,2020,128.56666666666666\n2020-02-24,153,1,55,2020,131.53333333333333\n2020-02-25,146,2,56,2020,133.43333333333334\n2020-02-26,155,3,57,2020,134.1\n2020-02-27,144,4,58,2020,135.53333333333333\n2020-02-28,115,5,59,2020,135.56666666666666\n2020-02-29,54,6,60,2020,132.2\n2020-03-01,56,7,61,2020,128.56666666666666\n2020-03-02,166,1,62,2020,131.13333333333333\n2020-03-03,142,2,63,2020,132.16666666666666\n2020-03-04,120,3,64,2020,131.46666666666667\n2020-03-05,148,4,65,2020,132.4\n2020-03-06,119,5,66,2020,131.53333333333333\n2020-03-07,92,6,67,2020,130.16666666666666\n2020-03-08,143,7,68,2020,129.96666666666667\n2020-03-09,112,1,69,2020,129.13333333333333\n2020-03-10,111,2,70,2020,128.86666666666667\n2020-03-11,110,3,71,2020,127.46666666666667\n2020-03-12,82,4,72,2020,124.8\n2020-03-13,76,5,73,2020,122.86666666666666\n2020-03-14,74,6,74,2020,119.66666666666667\n2020-03-15,80,7,75,2020,117.36666666666666\n2020-03-16,91,1,76,2020,117.23333333333333\n2020-03-17,106,2,77,2020,118.56666666666666\n2020-03-18,132,3,78,2020,118.66666666666667\n2020-03-19,92,4,79,2020,115.9\n2020-03-20,115,5,80,2020,115.3\n2020-03-21,89,6,81,2020,114.0\n2020-03-22,105,7,82,2020,113.06666666666666\n2020-03-23,138,1,83,2020,114.36666666666666\n2020-03-24,144,2,84,2020,113.66666666666667\n2020-03-25,116,3,85,2020,112.43333333333334\n2020-03-26,99,4,86,2020,110.86666666666666\n2020-03-27,112,5,87,2020,109.43333333333334\n2020-03-28,123,6,88,2020,108.73333333333333\n2020-03-29,76,7,89,2020,107.43333333333334\n2020-03-30,107,1,90,2020,109.2\n2020-03-31,177,2,91,2020,113.23333333333333\n2020-04-01,158,3,92,2020,112.96666666666667\n2020-04-02,160,4,93,2020,113.56666666666666\n2020-04-03,145,5,94,2020,114.4\n2020-04-04,130,6,95,2020,113.8\n2020-04-05,95,7,96,2020,113.0\n2020-04-06,152,1,97,2020,115.0\n2020-04-07,157,2,98,2020,115.46666666666667\n2020-04-08,217,3,99,2020,118.96666666666667\n2020-04-09,160,4,100,2020,120.6\n2020-04-10,151,5,101,2020,121.96666666666667\n2020-04-11,127,6,102,2020,123.46666666666667\n2020-04-12,106,7,103,2020,124.46666666666667\n2020-04-13,208,1,104,2020,128.93333333333334\n2020-04-14,175,2,105,2020,132.1\n2020-04-15,146,3,106,2020,133.93333333333334\n2020-04-16,149,4,107,2020,135.36666666666667\n2020-04-17,110,5,108,2020,134.63333333333333\n2020-04-18,148,6,109,2020,136.5\n2020-04-19,151,7,110,2020,137.7\n2020-04-20,155,1,111,2020,139.9\n2020-04-21,141,2,112,2020,141.1\n2020-04-22,147,3,113,2020,141.4\n2020-04-23,146,4,114,2020,141.46666666666667\n2020-04-24,136,5,115,2020,142.13333333333333\n2020-04-25,98,6,116,2020,142.1\n2020-04-26,139,7,117,2020,143.0\n2020-04-27,180,1,118,2020,144.9\n2020-04-28,118,2,119,2020,146.3\n2020-04-29,166,3,120,2020,148.26666666666668\n2020-04-30,220,4,121,2020,149.7\n2020-05-01,237,5,122,2020,152.33333333333334\n2020-05-02,133,6,123,2020,151.43333333333334\n2020-05-03,142,7,124,2020,151.33333333333334\n2020-05-04,132,1,125,2020,151.4\n2020-05-05,218,2,126,2020,155.5\n2020-05-06,229,3,127,2020,158.06666666666666\n2020-05-07,184,4,128,2020,158.96666666666667\n2020-05-08,160,5,129,2020,157.06666666666666\n2020-05-09,152,6,130,2020,156.8\n2020-05-10,160,7,131,2020,157.1\n2020-05-11,187,1,132,2020,159.1\n2020-05-12,158,2,133,2020,160.83333333333334\n2020-05-13,200,3,134,2020,160.56666666666666\n2020-05-14,212,4,135,2020,161.8\n2020-05-15,199,5,136,2020,163.56666666666666\n2020-05-16,113,6,137,2020,162.36666666666667\n2020-05-17,142,7,138,2020,163.43333333333334\n2020-05-18,161,1,139,2020,163.86666666666667\n2020-05-19,162,2,140,2020,164.23333333333332\n2020-05-20,186,3,141,2020,165.26666666666668\n2020-05-21,122,4,142,2020,164.63333333333333\n2020-05-22,142,5,143,2020,164.46666666666667\n2020-05-23,128,6,144,2020,163.86666666666667\n2020-05-24,134,7,145,2020,163.8\n2020-05-25,143,1,146,2020,165.3\n2020-05-26,220,2,147,2020,168.0\n2020-05-27,144,3,148,2020,166.8\n2020-05-28,100,4,149,2020,166.2\n2020-05-29,108,5,150,2020,164.26666666666668\n2020-05-30,213,6,151,2020,164.03333333333333\n2020-05-31,86,7,152,2020,159.0\n2020-06-01,115,1,153,2020,158.4\n2020-06-02,107,2,154,2020,157.23333333333332\n2020-06-03,169,3,155,2020,158.46666666666667\n2020-06-04,147,4,156,2020,156.1\n2020-06-05,115,5,157,2020,152.3\n2020-06-06,107,6,158,2020,149.73333333333332\n2020-06-07,93,7,159,2020,147.5\n2020-06-08,116,1,160,2020,146.3\n2020-06-09,143,2,161,2020,145.73333333333332\n2020-06-10,84,3,162,2020,142.3\n2020-06-11,177,4,163,2020,142.93333333333334\n2020-06-12,125,5,164,2020,140.43333333333334\n2020-06-13,61,6,165,2020,135.4\n2020-06-14,98,7,166,2020,132.03333333333333\n2020-06-15,191,1,167,2020,134.63333333333333\n2020-06-16,157,2,168,2020,135.13333333333333\n2020-06-17,199,3,169,2020,136.4\n2020-06-18,192,4,170,2020,137.4\n2020-06-19,146,5,171,2020,136.06666666666666\n2020-06-20,60,6,172,2020,134.0\n2020-06-21,116,7,173,2020,133.13333333333333\n2020-06-22,128,1,174,2020,133.13333333333333\n2020-06-23,130,2,175,2020,133.0\n2020-06-24,160,3,176,2020,133.56666666666666\n2020-06-25,120,4,177,2020,130.23333333333332\n2020-06-26,167,5,178,2020,131.0\n2020-06-27,164,6,179,2020,133.13333333333333\n2020-06-28,113,7,180,2020,133.3\n2020-06-29,167,1,181,2020,131.76666666666668\n2020-06-30,155,2,182,2020,134.06666666666666\n2020-07-01,126,3,183,2020,134.43333333333334\n2020-07-02,134,4,184,2020,135.33333333333334\n2020-07-03,146,5,185,2020,134.56666666666666\n2020-07-04,59,6,186,2020,131.63333333333333\n2020-07-05,102,7,187,2020,131.2\n2020-07-06,120,1,188,2020,131.63333333333333\n2020-07-07,124,2,189,2020,132.66666666666666\n2020-07-08,154,3,190,2020,133.93333333333334\n2020-07-09,164,4,191,2020,134.63333333333333\n2020-07-10,171,5,192,2020,137.53333333333333\n2020-07-11,79,6,193,2020,134.26666666666668\n2020-07-12,63,7,194,2020,132.2\n2020-07-13,85,1,195,2020,133.0\n2020-07-14,90,2,196,2020,132.73333333333332\n2020-07-15,129,3,197,2020,130.66666666666666\n2020-07-16,138,4,198,2020,130.03333333333333\n2020-07-17,95,5,199,2020,126.56666666666666\n2020-07-18,71,6,200,2020,122.53333333333333\n2020-07-19,99,7,201,2020,120.96666666666667\n2020-07-20,140,1,202,2020,123.63333333333334\n2020-07-21,189,2,203,2020,126.06666666666666\n2020-07-22,212,3,204,2020,128.86666666666667\n2020-07-23,176,4,205,2020,130.4\n2020-07-24,183,5,206,2020,131.16666666666666\n2020-07-25,55,6,207,2020,129.0\n2020-07-26,100,7,208,2020,126.76666666666667\n2020-07-27,137,1,209,2020,125.86666666666666\n2020-07-28,190,2,210,2020,128.43333333333334\n2020-07-29,118,3,211,2020,126.8\n2020-07-30,147,4,212,2020,126.53333333333333\n2020-07-31,139,5,213,2020,126.96666666666667\n2020-08-01,91,6,214,2020,125.53333333333333\n2020-08-02,99,7,215,2020,123.96666666666667\n2020-08-03,168,1,216,2020,127.6\n2020-08-04,168,2,217,2020,129.8\n2020-08-05,151,3,218,2020,130.83333333333334\n2020-08-06,167,4,219,2020,132.26666666666668\n2020-08-07,155,5,220,2020,132.3\n2020-08-08,78,6,221,2020,129.43333333333334\n2020-08-09,111,7,222,2020,127.43333333333334\n2020-08-10,126,1,223,2020,129.0\n2020-08-11,111,2,224,2020,130.6\n2020-08-12,121,3,225,2020,131.8\n2020-08-13,97,4,226,2020,132.03333333333333\n2020-08-14,137,5,227,2020,132.3\n2020-08-15,54,6,228,2020,129.5\n2020-08-16,56,7,229,2020,128.2\n2020-08-17,162,1,230,2020,131.23333333333332\n2020-08-18,98,2,231,2020,131.2\n2020-08-19,139,3,232,2020,131.16666666666666\n2020-08-20,128,4,233,2020,129.13333333333333\n2020-08-21,133,5,234,2020,126.5\n2020-08-22,93,6,235,2020,123.73333333333333\n2020-08-23,68,7,236,2020,119.9\n2020-08-24,149,1,237,2020,123.03333333333333\n2020-08-25,165,2,238,2020,125.2\n2020-08-26,201,3,239,2020,127.33333333333333\n2020-08-27,135,4,240,2020,125.5\n2020-08-28,108,5,241,2020,125.16666666666667\n2020-08-29,84,6,242,2020,123.06666666666666\n2020-08-30,42,7,243,2020,119.83333333333333\n2020-08-31,100,1,244,2020,120.13333333333334\n2020-09-01,134,2,245,2020,121.3\n2020-09-02,120,3,246,2020,119.7\n2020-09-03,100,4,247,2020,117.43333333333334\n2020-09-04,110,5,248,2020,116.06666666666666\n2020-09-05,53,6,249,2020,112.26666666666667\n2020-09-06,62,7,250,2020,109.16666666666667\n2020-09-07,129,1,251,2020,110.86666666666666\n2020-09-08,153,2,252,2020,112.26666666666667\n2020-09-09,148,3,253,2020,113.0\n2020-09-10,141,4,254,2020,114.0\n2020-09-11,162,5,255,2020,115.36666666666666\n2020-09-12,78,6,256,2020,114.73333333333333\n2020-09-13,58,7,257,2020,112.1\n2020-09-14,133,1,258,2020,114.73333333333333\n2020-09-15,126,2,259,2020,117.06666666666666\n2020-09-16,134,3,260,2020,116.13333333333334\n2020-09-17,94,4,261,2020,116.0\n2020-09-18,102,5,262,2020,114.76666666666667\n2020-09-19,65,6,263,2020,112.66666666666667\n2020-09-20,86,7,264,2020,111.1\n2020-09-21,136,1,265,2020,112.53333333333333\n2020-09-22,144,2,266,2020,115.06666666666666\n2020-09-23,137,3,267,2020,114.66666666666667\n2020-09-24,146,4,268,2020,114.03333333333333\n2020-09-25,148,5,269,2020,112.26666666666667\n2020-09-26,78,6,270,2020,110.36666666666666\n2020-09-27,82,7,271,2020,109.5\n2020-09-28,158,1,272,2020,111.96666666666667\n2020-09-29,122,2,273,2020,114.63333333333334\n2020-09-30,108,3,274,2020,114.9\n2020-10-01,146,4,275,2020,115.3\n2020-10-02,125,5,276,2020,115.46666666666667\n2020-10-03,55,6,277,2020,113.96666666666667\n2020-10-04,62,7,278,2020,112.36666666666666\n2020-10-05,99,1,279,2020,113.9\n2020-10-06,95,2,280,2020,115.0\n2020-10-07,137,3,281,2020,115.26666666666667\n2020-10-08,125,4,282,2020,114.33333333333333\n2020-10-09,117,5,283,2020,113.3\n2020-10-10,67,6,284,2020,110.83333333333333\n2020-10-11,62,7,285,2020,107.5\n2020-10-12,133,1,286,2020,109.33333333333333\n2020-10-13,80,2,287,2020,110.06666666666666\n2020-10-14,115,3,288,2020,109.46666666666667\n2020-10-15,104,4,289,2020,108.73333333333333\n2020-10-16,122,5,290,2020,108.33333333333333\n2020-10-17,106,6,291,2020,108.73333333333333\n2020-10-18,86,7,292,2020,108.2\n2020-10-19,156,1,293,2020,111.23333333333333\n2020-10-20,156,2,294,2020,113.56666666666666\n2020-10-21,162,3,295,2020,114.43333333333334\n2020-10-22,180,4,296,2020,115.63333333333334\n2020-10-23,93,5,297,2020,114.16666666666667\n2020-10-24,81,6,298,2020,112.0\n2020-10-25,75,7,299,2020,109.56666666666666\n2020-10-26,125,1,300,2020,111.13333333333334\n2020-10-27,130,2,301,2020,112.73333333333333\n2020-10-28,147,3,302,2020,112.36666666666666\n2020-10-29,118,4,303,2020,112.23333333333333\n2020-10-30,99,5,304,2020,111.93333333333334\n2020-10-31,93,6,305,2020,110.16666666666667\n2020-11-01,103,7,306,2020,109.43333333333334\n2020-11-02,103,1,307,2020,111.03333333333333\n2020-11-03,121,2,308,2020,113.0\n2020-11-04,86,3,309,2020,112.56666666666666\n2020-11-05,153,4,310,2020,114.5\n2020-11-06,129,5,311,2020,114.23333333333333\n2020-11-07,116,6,312,2020,113.93333333333334\n2020-11-08,51,7,313,2020,111.73333333333333\n2020-11-09,129,1,314,2020,113.8\n2020-11-10,150,2,315,2020,116.73333333333333\n2020-11-11,112,3,316,2020,116.03333333333333\n2020-11-12,117,4,317,2020,117.26666666666667\n2020-11-13,161,5,318,2020,118.8\n2020-11-14,69,6,319,2020,117.63333333333334\n2020-11-15,95,7,320,2020,116.73333333333333\n2020-11-16,144,1,321,2020,118.0\n2020-11-17,155,2,322,2020,120.3\n2020-11-18,142,3,323,2020,119.83333333333333\n2020-11-19,119,4,324,2020,118.6\n2020-11-20,113,5,325,2020,116.96666666666667\n2020-11-21,77,6,326,2020,113.53333333333333\n2020-11-22,69,7,327,2020,112.73333333333333\n2020-11-23,97,1,328,2020,113.26666666666667\n2020-11-24,107,2,329,2020,114.33333333333333\n2020-11-25,122,3,330,2020,114.23333333333333\n2020-11-26,131,4,331,2020,114.26666666666667\n2020-11-27,120,5,332,2020,113.36666666666666\n2020-11-28,93,6,333,2020,112.53333333333333\n2020-11-29,116,7,334,2020,113.1\n2020-11-30,139,1,335,2020,114.63333333333334\n2020-12-01,89,2,336,2020,114.16666666666667\n2020-12-02,152,3,337,2020,115.8\n2020-12-03,130,4,338,2020,116.1\n2020-12-04,128,5,339,2020,117.5\n2020-12-05,112,6,340,2020,116.13333333333334\n2020-12-06,69,7,341,2020,114.13333333333334\n2020-12-07,153,1,342,2020,115.36666666666666\n2020-12-08,110,2,343,2020,117.33333333333333\n2020-12-09,122,3,344,2020,117.1\n2020-12-10,124,4,345,2020,116.23333333333333\n2020-12-11,107,5,346,2020,116.06666666666666\n2020-12-12,78,6,347,2020,114.76666666666667\n2020-12-13,90,7,348,2020,112.4\n2020-12-14,87,1,349,2020,113.0\n2020-12-15,125,2,350,2020,114.0\n2020-12-16,143,3,351,2020,113.96666666666667\n2020-12-17,114,4,352,2020,112.6\n2020-12-18,96,5,353,2020,111.06666666666666\n2020-12-19,55,6,354,2020,108.93333333333334\n2020-12-20,66,7,355,2020,107.36666666666666\n2020-12-21,150,1,356,2020,109.8\n2020-12-22,129,2,357,2020,111.8\n2020-12-23,134,3,358,2020,113.03333333333333\n2020-12-24,70,4,359,2020,111.8\n2020-12-25,38,5,360,2020,109.0\n2020-12-26,68,6,361,2020,106.9\n2020-12-27,93,7,362,2020,106.0\n2020-12-28,116,1,363,2020,106.76666666666667\n2020-12-29,151,2,364,2020,107.93333333333334\n2020-12-30,114,3,365,2020,107.1\n2020-12-31,53,4,366,2020,105.9\n2021-01-01,67,5,1,2021,103.06666666666666\n2021-01-02,70,6,2,2021,101.06666666666666\n2021-01-03,60,7,3,2021,98.8\n2021-01-04,113,1,4,2021,98.83333333333333\n2021-01-05,108,2,5,2021,100.13333333333334\n2021-01-06,106,3,6,2021,98.56666666666666\n2021-01-07,133,4,7,2021,99.33333333333333\n2021-01-08,133,5,8,2021,99.7\n2021-01-09,99,6,9,2021,98.86666666666666\n2021-01-10,114,7,10,2021,99.1\n2021-01-11,115,1,11,2021,100.33333333333333\n2021-01-12,119,2,12,2021,101.3\n2021-01-13,167,3,13,2021,103.96666666666667\n2021-01-14,178,4,14,2021,105.73333333333333\n2021-01-15,184,5,15,2021,107.1\n2021-01-16,116,6,16,2021,107.16666666666667\n2021-01-17,130,7,17,2021,108.3\n2021-01-18,115,1,18,2021,110.3\n2021-01-19,155,2,19,2021,113.26666666666667\n2021-01-20,204,3,20,2021,115.06666666666666\n2021-01-21,137,4,21,2021,115.33333333333333\n2021-01-22,141,5,22,2021,115.56666666666666\n2021-01-23,130,6,23,2021,117.56666666666666\n2021-01-24,67,7,24,2021,118.53333333333333\n2021-01-25,132,1,25,2021,120.66666666666667\n2021-01-26,180,2,26,2021,123.56666666666666\n2021-01-27,161,3,27,2021,125.06666666666666\n2021-01-28,162,4,28,2021,125.43333333333334\n2021-01-29,207,5,29,2021,128.53333333333333\n2021-01-30,95,6,30,2021,129.93333333333334\n2021-01-31,149,7,31,2021,132.66666666666666\n2021-02-01,176,1,32,2021,136.2\n2021-02-02,157,2,33,2021,139.43333333333334\n2021-02-03,191,3,34,2021,142.03333333333333\n2021-02-04,156,4,35,2021,143.63333333333333\n2021-02-05,214,5,36,2021,147.23333333333332\n2021-02-06,159,6,37,2021,148.1\n2021-02-07,94,7,38,2021,146.8\n2021-02-08,121,1,39,2021,147.53333333333333\n2021-02-09,134,2,40,2021,148.2\n2021-02-10,126,3,41,2021,148.56666666666666\n2021-02-11,138,4,42,2021,149.2\n2021-02-12,115,5,43,2021,147.46666666666667\n2021-02-13,121,6,44,2021,145.56666666666666\n2021-02-14,115,7,45,2021,143.26666666666668\n2021-02-15,148,1,46,2021,144.33333333333334\n2021-02-16,127,2,47,2021,144.23333333333332\n2021-02-17,149,3,48,2021,145.36666666666667\n2021-02-18,153,4,49,2021,145.3\n2021-02-19,130,5,50,2021,142.83333333333334\n2021-02-20,120,6,51,2021,142.26666666666668\n2021-02-21,98,7,52,2021,140.83333333333334\n2021-02-22,160,1,53,2021,141.83333333333334\n2021-02-23,150,2,54,2021,144.6\n2021-02-24,185,3,55,2021,146.36666666666667\n2021-02-25,171,4,56,2021,146.06666666666666\n2021-02-26,162,5,57,2021,146.1\n2021-02-27,130,6,58,2021,145.03333333333333\n2021-02-28,189,7,59,2021,144.43333333333334\n2021-03-01,218,1,60,2021,148.53333333333333\n2021-03-02,138,2,61,2021,148.16666666666666\n2021-03-03,172,3,62,2021,148.03333333333333\n2021-03-04,202,4,63,2021,149.53333333333333\n2021-03-05,152,5,64,2021,148.23333333333332\n2021-03-06,128,6,65,2021,147.3\n2021-03-07,115,7,66,2021,144.0\n2021-03-08,195,1,67,2021,145.2\n2021-03-09,161,2,68,2021,147.43333333333334\n2021-03-10,190,3,69,2021,149.73333333333332\n2021-03-11,172,4,70,2021,151.0\n2021-03-12,149,5,71,2021,151.76666666666668\n2021-03-13,141,6,72,2021,151.86666666666667\n2021-03-14,77,7,73,2021,150.6\n2021-03-15,167,1,74,2021,152.13333333333333\n2021-03-16,161,2,75,2021,153.66666666666666\n2021-03-17,115,3,76,2021,152.56666666666666\n2021-03-18,144,4,77,2021,153.13333333333333\n2021-03-19,145,5,78,2021,153.0\n2021-03-20,88,6,79,2021,150.83333333333334\n2021-03-21,150,7,80,2021,151.5\n2021-03-22,110,1,81,2021,151.16666666666666\n2021-03-23,157,2,82,2021,153.13333333333333\n2021-03-24,145,3,83,2021,152.63333333333333\n2021-03-25,116,4,84,2021,151.5\n2021-03-26,126,5,85,2021,149.53333333333333\n2021-03-27,153,6,86,2021,148.93333333333334\n2021-03-28,111,7,87,2021,147.23333333333332\n2021-03-29,178,1,88,2021,148.83333333333334\n2021-03-30,178,2,89,2021,148.46666666666667\n2021-03-31,170,3,90,2021,146.86666666666667\n2021-04-01,170,4,91,2021,147.93333333333334\n2021-04-02,152,5,92,2021,147.26666666666668\n2021-04-03,100,6,93,2021,143.86666666666667\n2021-04-04,119,7,94,2021,142.76666666666668\n2021-04-05,129,1,95,2021,142.8\n2021-04-06,200,2,96,2021,145.63333333333333\n2021-04-07,164,3,97,2021,144.6\n2021-04-08,120,4,98,2021,143.23333333333332\n2021-04-09,178,5,99,2021,142.83333333333334\n2021-04-10,136,6,100,2021,141.63333333333333\n2021-04-11,106,7,101,2021,140.2\n2021-04-12,155,1,102,2021,140.66666666666666\n2021-04-13,114,2,103,2021,141.9\n2021-04-14,138,3,104,2021,140.93333333333334\n2021-04-15,175,4,105,2021,141.4\n2021-04-16,130,5,106,2021,141.9\n2021-04-17,100,6,107,2021,140.43333333333334\n2021-04-18,80,7,108,2021,138.26666666666668\n2021-04-19,137,1,109,2021,139.9\n2021-04-20,107,2,110,2021,138.46666666666667\n2021-04-21,174,3,111,2021,140.6\n2021-04-22,136,4,112,2021,139.9\n2021-04-23,141,5,113,2021,139.76666666666668\n2021-04-24,94,6,114,2021,139.03333333333333\n2021-04-25,124,7,115,2021,138.96666666666667\n2021-04-26,190,1,116,2021,140.2\n2021-04-27,96,2,117,2021,139.7\n2021-04-28,131,3,118,2021,138.13333333333333\n2021-04-29,135,4,119,2021,136.7\n2021-04-30,166,5,120,2021,136.56666666666666\n2021-05-01,80,6,121,2021,133.56666666666666\n2021-05-02,94,7,122,2021,131.63333333333333\n2021-05-03,71,1,123,2021,130.66666666666666\n2021-05-04,96,2,124,2021,129.9\n2021-05-05,117,3,125,2021,129.5\n2021-05-06,162,4,126,2021,128.23333333333332\n2021-05-07,133,5,127,2021,127.2\n2021-05-08,131,6,128,2021,127.56666666666666\n2021-05-09,94,7,129,2021,124.76666666666667\n2021-05-10,151,1,130,2021,125.26666666666667\n2021-05-11,159,2,131,2021,127.03333333333333\n2021-05-12,156,3,132,2021,127.06666666666666\n2021-05-13,172,4,133,2021,129.0\n2021-05-14,181,5,134,2021,130.43333333333334\n2021-05-15,75,6,135,2021,127.1\n2021-05-16,94,7,136,2021,125.9\n2021-05-17,144,1,137,2021,127.36666666666666\n2021-05-18,117,2,138,2021,128.6\n2021-05-19,157,3,139,2021,129.26666666666668\n2021-05-20,195,4,140,2021,132.2\n2021-05-21,160,5,141,2021,131.73333333333332\n2021-05-22,104,6,142,2021,130.66666666666666\n2021-05-23,75,7,143,2021,128.46666666666667\n2021-05-24,141,1,144,2021,130.03333333333333\n2021-05-25,177,2,145,2021,131.8\n2021-05-26,186,3,146,2021,131.66666666666666\n2021-05-27,141,4,147,2021,133.16666666666666\n2021-05-28,146,5,148,2021,133.66666666666666\n2021-05-29,66,6,149,2021,131.36666666666667\n2021-05-30,83,7,150,2021,128.6\n2021-05-31,120,1,151,2021,129.93333333333334\n2021-06-01,151,2,152,2021,131.83333333333334\n2021-06-02,132,3,153,2021,133.86666666666667\n2021-06-03,171,4,154,2021,136.36666666666667\n2021-06-04,98,5,155,2021,135.73333333333332\n2021-06-05,63,6,156,2021,132.43333333333334\n2021-06-06,64,7,157,2021,130.13333333333333\n2021-06-07,133,1,158,2021,130.2\n2021-06-08,117,2,159,2021,130.96666666666667\n2021-06-09,181,3,160,2021,131.96666666666667\n2021-06-10,166,4,161,2021,132.2\n2021-06-11,100,5,162,2021,130.33333333333334\n2021-06-12,56,6,163,2021,126.46666666666667\n2021-06-13,54,7,164,2021,122.23333333333333\n2021-06-14,89,1,165,2021,122.7\n2021-06-15,95,2,166,2021,122.73333333333333\n2021-06-16,134,3,167,2021,122.4\n2021-06-17,149,4,168,2021,123.46666666666667\n2021-06-18,116,5,169,2021,122.1\n2021-06-19,48,6,170,2021,117.2\n2021-06-20,60,7,171,2021,113.86666666666666\n2021-06-21,115,1,172,2021,114.23333333333333\n2021-06-22,122,2,173,2021,115.8\n2021-06-23,136,3,174,2021,115.63333333333334\n2021-06-24,116,4,175,2021,113.6\n2021-06-25,110,5,176,2021,111.06666666666666\n2021-06-26,68,6,177,2021,108.63333333333334\n2021-06-27,104,7,178,2021,107.23333333333333\n2021-06-28,118,1,179,2021,108.96666666666667\n2021-06-29,110,2,180,2021,109.86666666666666\n2021-06-30,129,3,181,2021,110.16666666666667\n2021-07-01,154,4,182,2021,110.26666666666667\n2021-07-02,91,5,183,2021,108.9\n2021-07-03,49,6,184,2021,104.83333333333333\n2021-07-04,81,7,185,2021,104.26666666666667\n2021-07-05,139,1,186,2021,106.8\n2021-07-06,141,2,187,2021,109.36666666666666\n2021-07-07,113,3,188,2021,108.7\n2021-07-08,96,4,189,2021,108.0\n2021-07-09,118,5,190,2021,105.9\n2021-07-10,111,6,191,2021,104.06666666666666\n2021-07-11,104,7,192,2021,104.2\n2021-07-12,131,1,193,2021,106.7\n2021-07-13,126,2,194,2021,109.1\n2021-07-14,174,3,195,2021,111.93333333333334\n2021-07-15,140,4,196,2021,113.43333333333334\n2021-07-16,102,5,197,2021,112.36666666666666\n2021-07-17,68,6,198,2021,109.66666666666667\n2021-07-18,55,7,199,2021,107.63333333333334\n2021-07-19,87,1,200,2021,108.93333333333334\n2021-07-20,145,2,201,2021,111.76666666666667\n2021-07-21,125,3,202,2021,112.1\n2021-07-22,118,4,203,2021,111.96666666666667\n2021-07-23,107,5,204,2021,111.0\n2021-07-24,37,6,205,2021,108.36666666666666\n2021-07-25,45,7,206,2021,106.2\n2021-07-26,80,1,207,2021,106.6\n2021-07-27,152,2,208,2021,108.2\n2021-07-28,145,3,209,2021,109.1\n2021-07-29,148,4,210,2021,110.36666666666666\n2021-07-30,118,5,211,2021,110.0\n2021-07-31,98,6,212,2021,108.13333333333334\n2021-08-01,81,7,213,2021,107.8\n2021-08-02,137,1,214,2021,110.73333333333333\n2021-08-03,129,2,215,2021,112.33333333333333\n2021-08-04,129,3,216,2021,112.0\n2021-08-05,103,4,217,2021,110.73333333333333\n2021-08-06,143,5,218,2021,111.73333333333333\n2021-08-07,112,6,219,2021,112.26666666666667\n2021-08-08,94,7,220,2021,111.46666666666667\n2021-08-09,102,1,221,2021,111.16666666666667\n2021-08-10,106,2,222,2021,111.23333333333333\n2021-08-11,140,3,223,2021,111.53333333333333\n2021-08-12,113,4,224,2021,111.1\n2021-08-13,113,5,225,2021,109.06666666666666\n2021-08-14,109,6,226,2021,108.03333333333333\n2021-08-15,71,7,227,2021,107.0\n2021-08-16,124,1,228,2021,108.86666666666666\n2021-08-17,95,2,229,2021,110.2\n2021-08-18,148,3,230,2021,112.23333333333333\n2021-08-19,124,4,231,2021,111.53333333333333\n2021-08-20,93,5,232,2021,110.46666666666667\n2021-08-21,94,6,233,2021,109.66666666666667\n2021-08-22,80,7,234,2021,108.76666666666667\n2021-08-23,156,1,235,2021,112.73333333333333\n2021-08-24,135,2,236,2021,115.73333333333333\n2021-08-25,170,3,237,2021,118.73333333333333\n2021-08-26,125,4,238,2021,117.83333333333333\n2021-08-27,122,5,239,2021,117.06666666666666\n2021-08-28,89,6,240,2021,115.1\n2021-08-29,80,7,241,2021,113.83333333333333\n2021-08-30,125,1,242,2021,114.73333333333333\n2021-08-31,160,2,243,2021,117.36666666666666\n2021-09-01,158,3,244,2021,118.06666666666666\n2021-09-02,106,4,245,2021,117.3\n2021-09-03,125,5,246,2021,117.16666666666667\n2021-09-04,96,6,247,2021,116.93333333333334\n2021-09-05,89,7,248,2021,115.13333333333334\n2021-09-06,128,1,249,2021,115.66666666666667\n2021-09-07,124,2,250,2021,116.66666666666667\n2021-09-08,99,3,251,2021,116.56666666666666\n2021-09-09,145,4,252,2021,117.86666666666666\n2021-09-10,132,5,253,2021,117.6\n2021-09-11,80,6,254,2021,116.5\n2021-09-12,82,7,255,2021,115.46666666666667\n2021-09-13,148,1,256,2021,116.76666666666667\n2021-09-14,129,2,257,2021,118.7\n2021-09-15,146,3,258,2021,119.43333333333334\n2021-09-16,183,4,259,2021,122.36666666666666\n2021-09-17,157,5,260,2021,122.66666666666667\n2021-09-18,103,6,261,2021,121.96666666666667\n2021-09-19,133,7,262,2021,123.3\n2021-09-20,133,1,263,2021,124.6\n2021-09-21,146,2,264,2021,126.8\n2021-09-22,146,3,265,2021,126.46666666666667\n2021-09-23,145,4,266,2021,126.8\n2021-09-24,84,5,267,2021,123.93333333333334\n2021-09-25,108,6,268,2021,123.36666666666666\n2021-09-26,64,7,269,2021,121.43333333333334\n2021-09-27,122,1,270,2021,122.53333333333333\n2021-09-28,170,2,271,2021,125.53333333333333\n2021-09-29,143,3,272,2021,126.13333333333334\n2021-09-30,142,4,273,2021,125.53333333333333\n2021-10-01,104,5,274,2021,123.73333333333333\n2021-10-02,73,6,275,2021,122.63333333333334\n2021-10-03,123,7,276,2021,122.56666666666666\n2021-10-04,96,1,277,2021,122.56666666666666\n2021-10-05,141,2,278,2021,124.3\n2021-10-06,190,3,279,2021,126.36666666666666\n2021-10-07,152,4,280,2021,127.3\n2021-10-08,118,5,281,2021,127.93333333333334\n2021-10-09,158,6,282,2021,128.36666666666667\n2021-10-10,118,7,283,2021,127.9\n2021-10-11,137,1,284,2021,129.8\n2021-10-12,139,2,285,2021,131.7\n2021-10-13,110,3,286,2021,130.43333333333334\n2021-10-14,100,4,287,2021,129.46666666666667\n2021-10-15,114,5,288,2021,128.4\n2021-10-16,87,6,289,2021,125.2\n2021-10-17,51,7,290,2021,121.66666666666667\n2021-10-18,152,1,291,2021,123.3\n2021-10-19,135,2,292,2021,123.36666666666666\n2021-10-20,126,3,293,2021,123.13333333333334\n2021-10-21,156,4,294,2021,123.46666666666667\n2021-10-22,137,5,295,2021,123.16666666666667\n2021-10-23,68,6,296,2021,120.6\n2021-10-24,63,7,297,2021,119.9\n2021-10-25,126,1,298,2021,120.5\n2021-10-26,92,2,299,2021,121.43333333333334\n2021-10-27,130,3,300,2021,121.7\n2021-10-28,112,4,301,2021,119.76666666666667\n2021-10-29,135,5,302,2021,119.5\n2021-10-30,70,6,303,2021,117.1\n2021-10-31,86,7,304,2021,116.5\n2021-11-01,116,1,305,2021,117.93333333333334\n2021-11-02,129,2,306,2021,118.13333333333334\n2021-11-03,163,3,307,2021,120.36666666666666\n2021-11-04,188,4,308,2021,121.93333333333334\n2021-11-05,145,5,309,2021,120.43333333333334\n2021-11-06,116,6,310,2021,119.23333333333333\n2021-11-07,57,7,311,2021,117.2\n2021-11-08,143,1,312,2021,116.7\n2021-11-09,128,2,313,2021,117.03333333333333\n2021-11-10,178,3,314,2021,118.4\n2021-11-11,140,4,315,2021,118.43333333333334\n2021-11-12,98,5,316,2021,118.03333333333333\n2021-11-13,54,6,317,2021,116.5\n2021-11-14,63,7,318,2021,114.8\n2021-11-15,136,1,319,2021,116.43333333333334\n2021-11-16,146,2,320,2021,119.6\n2021-11-17,175,3,321,2021,120.36666666666666\n2021-11-18,133,4,322,2021,120.3\n2021-11-19,148,5,323,2021,121.03333333333333\n2021-11-20,38,6,324,2021,117.1\n2021-11-21,72,7,325,2021,114.93333333333334\n2021-11-22,114,1,326,2021,116.46666666666667\n2021-11-23,135,2,327,2021,118.86666666666666\n2021-11-24,120,3,328,2021,118.66666666666667\n2021-11-25,81,4,329,2021,118.3\n2021-11-26,96,5,330,2021,117.16666666666667\n2021-11-27,67,6,331,2021,115.66666666666667\n2021-11-28,72,7,332,2021,113.56666666666666\n2021-11-29,128,1,333,2021,115.5\n2021-11-30,101,2,334,2021,116.0\n2021-12-01,124,3,335,2021,116.26666666666667\n2021-12-02,100,4,336,2021,115.3\n2021-12-03,79,5,337,2021,112.5\n2021-12-04,49,6,338,2021,107.86666666666666\n2021-12-05,64,7,339,2021,105.16666666666667\n2021-12-06,122,1,340,2021,105.36666666666666\n2021-12-07,113,2,341,2021,107.23333333333333\n2021-12-08,104,3,342,2021,105.93333333333334\n2021-12-09,125,4,343,2021,105.83333333333333\n2021-12-10,122,5,344,2021,103.96666666666667\n2021-12-11,38,6,345,2021,100.56666666666666\n2021-12-12,94,7,346,2021,100.43333333333334\n2021-12-13,144,1,347,2021,103.43333333333334\n2021-12-14,107,2,348,2021,104.9\n2021-12-15,143,3,349,2021,105.13333333333334\n2021-12-16,145,4,350,2021,105.1\n2021-12-17,102,5,351,2021,102.66666666666667\n2021-12-18,62,6,352,2021,100.3\n2021-12-19,88,7,353,2021,98.3\n2021-12-20,120,1,354,2021,101.03333333333333\n2021-12-21,126,2,355,2021,102.83333333333333\n2021-12-22,163,3,356,2021,104.46666666666667\n2021-12-23,107,4,357,2021,103.53333333333333\n2021-12-24,48,5,358,2021,101.13333333333334\n2021-12-25,16,6,359,2021,98.96666666666667\n2021-12-26,29,7,360,2021,96.73333333333333\n2021-12-27,111,1,361,2021,98.2\n2021-12-28,95,2,362,2021,98.96666666666667\n2021-12-29,133,3,363,2021,99.13333333333334\n2021-12-30,88,4,364,2021,98.7\n2021-12-31,44,5,365,2021,96.03333333333333\n2022-01-01,33,6,1,2022,93.8\n2022-01-02,44,7,2,2022,92.63333333333334\n2022-01-03,85,1,3,2022,93.83333333333333\n2022-01-04,147,2,4,2022,96.6\n2022-01-05,120,3,5,2022,96.53333333333333\n2022-01-06,110,4,6,2022,96.43333333333334\n2022-01-07,127,5,7,2022,97.2\n2022-01-08,95,6,8,2022,96.2\n2022-01-09,85,7,9,2022,94.96666666666667\n2022-01-10,150,1,10,2022,98.7\n2022-01-11,118,2,11,2022,99.5\n2022-01-12,180,3,12,2022,100.7\n2022-01-13,153,4,13,2022,102.23333333333333\n2022-01-14,157,5,14,2022,102.7\n2022-01-15,74,6,15,2022,100.33333333333333\n2022-01-16,86,7,16,2022,99.8\n2022-01-17,151,1,17,2022,102.76666666666667\n2022-01-18,150,2,18,2022,104.83333333333333\n2022-01-19,182,3,19,2022,106.9\n2022-01-20,156,4,20,2022,107.9\n2022-01-21,156,5,21,2022,107.66666666666667\n2022-01-22,92,6,22,2022,107.16666666666667\n2022-01-23,115,7,23,2022,109.4\n2022-01-24,141,1,24,2022,113.56666666666666\n2022-01-25,125,2,25,2022,116.76666666666667\n2022-01-26,158,3,26,2022,118.33333333333333\n2022-01-27,109,4,27,2022,118.8\n2022-01-28,130,5,28,2022,118.7\n2022-01-29,103,6,29,2022,119.2\n2022-01-30,67,7,30,2022,119.96666666666667\n2022-01-31,152,1,31,2022,123.93333333333334\n2022-02-01,153,2,32,2022,127.56666666666666\n2022-02-02,160,3,33,2022,130.06666666666666\n2022-02-03,104,4,34,2022,128.63333333333333\n2022-02-04,124,5,35,2022,128.76666666666668\n2022-02-05,38,6,36,2022,126.36666666666666\n2022-02-06,70,7,37,2022,124.46666666666667\n2022-02-07,129,1,38,2022,125.6\n2022-02-08,133,2,39,2022,127.2\n2022-02-09,152,3,40,2022,127.26666666666667\n2022-02-10,144,4,41,2022,128.13333333333333\n2022-02-11,110,5,42,2022,125.8\n2022-02-12,48,6,43,2022,122.3\n2022-02-13,43,7,44,2022,118.5\n2022-02-14,108,1,45,2022,119.63333333333334\n2022-02-15,138,2,46,2022,121.36666666666666\n2022-02-16,140,3,47,2022,121.0\n2022-02-17,171,4,48,2022,121.7\n2022-02-18,108,5,49,2022,119.23333333333333\n2022-02-19,63,6,50,2022,116.13333333333334\n2022-02-20,82,7,51,2022,113.66666666666667\n2022-02-21,165,1,52,2022,116.1\n2022-02-22,120,2,53,2022,116.26666666666667\n2022-02-23,163,3,54,2022,117.0\n2022-02-24,168,4,55,2022,118.43333333333334\n2022-02-25,122,5,56,2022,117.23333333333333\n2022-02-26,37,6,57,2022,114.83333333333333\n2022-02-27,42,7,58,2022,111.9\n2022-02-28,97,1,59,2022,111.7\n2022-03-01,90,2,60,2022,112.46666666666667\n2022-03-02,122,3,61,2022,111.46666666666667\n2022-03-03,103,4,62,2022,109.8\n2022-03-04,112,5,63,2022,108.2\n2022-03-05,92,6,64,2022,107.8\n2022-03-06,62,7,65,2022,105.73333333333333\n2022-03-07,118,1,66,2022,108.4\n2022-03-08,96,2,67,2022,109.26666666666667\n2022-03-09,110,3,68,2022,108.63333333333334\n2022-03-10,131,4,69,2022,108.56666666666666\n2022-03-11,101,5,70,2022,106.86666666666666\n2022-03-12,54,6,71,2022,103.86666666666666\n2022-03-13,53,7,72,2022,101.96666666666667\n2022-03-14,133,1,73,2022,104.8\n2022-03-15,121,2,74,2022,107.4\n2022-03-16,129,3,75,2022,108.1\n2022-03-17,123,4,76,2022,107.6\n2022-03-18,121,5,77,2022,106.96666666666667\n2022-03-19,62,6,78,2022,103.33333333333333\n2022-03-20,49,7,79,2022,101.36666666666666\n2022-03-21,94,1,80,2022,102.4\n2022-03-22,126,2,81,2022,103.86666666666666\n2022-03-23,152,3,82,2022,103.43333333333334\n2022-03-24,152,4,83,2022,104.5\n2022-03-25,145,5,84,2022,103.9\n2022-03-26,133,6,85,2022,102.73333333333333\n2022-03-27,103,7,86,2022,102.1\n2022-03-28,170,1,87,2022,106.53333333333333\n2022-03-29,125,2,88,2022,109.3\n2022-03-30,146,3,89,2022,110.93333333333334\n2022-03-31,152,4,90,2022,113.0\n2022-04-01,123,5,91,2022,113.03333333333333\n2022-04-02,92,6,92,2022,112.66666666666667\n2022-04-03,77,7,93,2022,111.5\n2022-04-04,174,1,94,2022,114.23333333333333\n2022-04-05,182,2,95,2022,118.23333333333333\n2022-04-06,118,3,96,2022,118.23333333333333\n2022-04-07,114,4,97,2022,118.83333333333333\n2022-04-08,156,5,98,2022,120.36666666666666\n2022-04-09,105,6,99,2022,119.5\n2022-04-10,93,7,100,2022,119.23333333333333\n2022-04-11,135,1,101,2022,121.93333333333334\n2022-04-12,153,2,102,2022,125.26666666666667\n2022-04-13,118,3,103,2022,124.76666666666667\n2022-04-14,149,4,104,2022,125.7\n2022-04-15,169,5,105,2022,127.03333333333333\n2022-04-16,70,6,106,2022,125.26666666666667\n2022-04-17,55,7,107,2022,123.06666666666666\n2022-04-18,125,1,108,2022,125.16666666666667\n2022-04-19,126,2,109,2022,127.73333333333333\n2022-04-20,108,3,110,2022,128.2\n2022-04-21,147,4,111,2022,128.9\n2022-04-22,173,5,112,2022,129.6\n2022-04-23,90,6,113,2022,127.53333333333333\n2022-04-24,100,7,114,2022,126.03333333333333\n2022-04-25,101,1,115,2022,124.96666666666667\n2022-04-26,150,2,116,2022,126.53333333333333\n2022-04-27,158,3,117,2022,126.13333333333334\n2022-04-28,134,4,118,2022,126.43333333333334\n2022-04-29,107,5,119,2022,125.13333333333334\n2022-04-30,50,6,120,2022,121.73333333333333\n2022-05-01,62,7,121,2022,119.7\n2022-05-02,106,1,122,2022,120.16666666666667\n2022-05-03,104,2,123,2022,121.06666666666666\n2022-05-04,133,3,124,2022,119.7\n2022-05-05,167,4,125,2022,119.2\n2022-05-06,140,5,126,2022,119.93333333333334\n2022-05-07,44,6,127,2022,117.6\n2022-05-08,71,7,128,2022,114.76666666666667\n2022-05-09,147,1,129,2022,116.16666666666667\n2022-05-10,119,2,130,2022,117.03333333333333\n2022-05-11,151,3,131,2022,117.56666666666666\n2022-05-12,132,4,132,2022,116.86666666666666\n2022-05-13,112,5,133,2022,116.66666666666667\n2022-05-14,96,6,134,2022,114.9\n2022-05-15,47,7,135,2022,110.83333333333333\n2022-05-16,149,1,136,2022,113.46666666666667\n2022-05-17,141,2,137,2022,116.33333333333333\n2022-05-18,117,3,138,2022,116.06666666666666\n2022-05-19,158,4,139,2022,117.13333333333334\n2022-05-20,112,5,140,2022,117.26666666666667\n2022-05-21,85,6,141,2022,115.2\n2022-05-22,83,7,142,2022,112.2\n2022-05-23,154,1,143,2022,114.33333333333333\n2022-05-24,149,2,144,2022,115.96666666666667\n2022-05-25,113,3,145,2022,116.36666666666666\n2022-05-26,113,4,146,2022,115.13333333333334\n2022-05-27,102,5,147,2022,113.26666666666667\n2022-05-28,99,6,148,2022,112.1\n2022-05-29,56,7,149,2022,110.4\n2022-05-30,107,1,150,2022,112.3\n2022-05-31,106,2,151,2022,113.76666666666667\n2022-06-01,130,3,152,2022,114.56666666666666\n2022-06-02,173,4,153,2022,116.86666666666666\n2022-06-03,134,5,154,2022,116.9\n2022-06-04,70,6,155,2022,113.66666666666667\n2022-06-05,88,7,156,2022,111.93333333333334\n2022-06-06,110,1,157,2022,114.13333333333334\n2022-06-07,113,2,158,2022,115.53333333333333\n2022-06-08,139,3,159,2022,115.26666666666667\n2022-06-09,142,4,160,2022,116.03333333333333\n2022-06-10,109,5,161,2022,114.63333333333334\n2022-06-11,56,6,162,2022,112.1\n2022-06-12,76,7,163,2022,110.9\n2022-06-13,95,1,164,2022,110.86666666666666\n2022-06-14,94,2,165,2022,112.43333333333334\n2022-06-15,127,3,166,2022,111.7\n2022-06-16,200,4,167,2022,113.66666666666667\n2022-06-17,202,5,168,2022,116.5\n2022-06-18,49,6,169,2022,112.86666666666666\n2022-06-19,62,7,170,2022,111.2\n2022-06-20,116,1,171,2022,112.23333333333333\n2022-06-21,112,2,172,2022,113.2\n2022-06-22,131,3,173,2022,112.43333333333334\n2022-06-23,114,4,174,2022,111.26666666666667\n2022-06-24,110,5,175,2022,111.16666666666667\n2022-06-25,52,6,176,2022,109.13333333333334\n2022-06-26,56,7,177,2022,107.6\n2022-06-27,76,1,178,2022,106.83333333333333\n2022-06-28,72,2,179,2022,107.36666666666666\n2022-06-29,120,3,180,2022,107.8\n2022-06-30,118,4,181,2022,108.2\n2022-07-01,87,5,182,2022,106.76666666666667\n2022-07-02,32,6,183,2022,102.06666666666666\n2022-07-03,39,7,184,2022,98.9\n2022-07-04,89,1,185,2022,99.53333333333333\n2022-07-05,120,2,186,2022,100.6\n2022-07-06,106,3,187,2022,100.46666666666667\n2022-07-07,138,4,188,2022,101.3\n2022-07-08,109,5,189,2022,100.3\n2022-07-09,42,6,190,2022,96.96666666666667\n2022-07-10,44,7,191,2022,94.8\n2022-07-11,92,1,192,2022,96.0\n2022-07-12,135,2,193,2022,97.96666666666667\n2022-07-13,157,3,194,2022,100.03333333333333\n2022-07-14,124,4,195,2022,101.03333333333333\n2022-07-15,177,5,196,2022,102.7\n2022-07-16,56,6,197,2022,97.9\n2022-07-17,41,7,198,2022,92.53333333333333\n2022-07-18,143,1,199,2022,95.66666666666667\n2022-07-19,119,2,200,2022,97.56666666666666\n2022-07-20,211,3,201,2022,100.73333333333333\n2022-07-21,128,4,202,2022,101.26666666666667\n2022-07-22,162,5,203,2022,102.3\n2022-07-23,44,6,204,2022,99.96666666666667\n2022-07-24,99,7,205,2022,99.6\n2022-07-25,152,1,206,2022,102.93333333333334\n2022-07-26,158,2,207,2022,106.33333333333333\n2022-07-27,133,3,208,2022,108.23333333333333\n2022-07-28,214,4,209,2022,112.96666666666667\n2022-07-29,133,5,210,2022,113.4\n2022-07-30,79,6,211,2022,112.1\n2022-07-31,70,7,212,2022,111.53333333333333\n2022-08-01,130,1,213,2022,114.8\n2022-08-02,123,2,214,2022,117.6\n2022-08-03,105,3,215,2022,118.13333333333334\n2022-08-04,125,4,216,2022,118.3\n2022-08-05,127,5,217,2022,119.0\n2022-08-06,71,6,218,2022,116.76666666666667\n2022-08-07,55,7,219,2022,114.96666666666667\n2022-08-08,108,1,220,2022,117.16666666666667\n2022-08-09,99,2,221,2022,119.0\n2022-08-10,145,3,222,2022,120.76666666666667\n2022-08-11,115,4,223,2022,120.1\n2022-08-12,110,5,224,2022,118.53333333333333\n2022-08-13,100,6,225,2022,117.73333333333333\n2022-08-14,95,7,226,2022,115.0\n2022-08-15,133,1,227,2022,117.56666666666666\n2022-08-16,130,2,228,2022,120.53333333333333\n2022-08-17,131,3,229,2022,120.13333333333334\n2022-08-18,116,4,230,2022,120.03333333333333\n2022-08-19,143,5,231,2022,117.76666666666667\n2022-08-20,82,6,232,2022,116.23333333333333\n2022-08-21,78,7,233,2022,113.43333333333334\n2022-08-22,110,1,234,2022,115.63333333333334\n2022-08-23,130,2,235,2022,116.66666666666667\n2022-08-24,181,3,236,2022,117.63333333333334\n2022-08-25,132,4,237,2022,116.76666666666667\n2022-08-26,105,5,238,2022,115.83333333333333\n2022-08-27,79,6,239,2022,111.33333333333333\n2022-08-28,66,7,240,2022,109.1\n2022-08-29,173,1,241,2022,112.23333333333333\n2022-08-30,174,2,242,2022,115.7\n2022-08-31,174,3,243,2022,117.16666666666667\n2022-09-01,137,4,244,2022,117.63333333333334\n2022-09-02,135,5,245,2022,118.63333333333334\n2022-09-03,63,6,246,2022,116.56666666666666\n2022-09-04,81,7,247,2022,115.03333333333333\n2022-09-05,168,1,248,2022,118.26666666666667\n2022-09-06,207,2,249,2022,123.33333333333333\n2022-09-07,194,3,250,2022,126.2\n2022-09-08,162,4,251,2022,128.3\n2022-09-09,135,5,252,2022,127.96666666666667\n2022-09-10,54,6,253,2022,125.93333333333334\n2022-09-11,53,7,254,2022,124.03333333333333\n2022-09-12,123,1,255,2022,124.8\n2022-09-13,120,2,256,2022,125.63333333333334\n2022-09-14,137,3,257,2022,125.76666666666667\n2022-09-15,158,4,258,2022,126.7\n2022-09-16,110,5,259,2022,126.0\n2022-09-17,77,6,260,2022,124.7\n2022-09-18,86,7,261,2022,122.8\n2022-09-19,165,1,262,2022,125.56666666666666\n2022-09-20,177,2,263,2022,128.86666666666667\n2022-09-21,156,3,264,2022,130.4\n2022-09-22,113,4,265,2022,129.83333333333334\n2022-09-23,137,5,266,2022,128.36666666666667\n2022-09-24,94,6,267,2022,127.1\n2022-09-25,44,7,268,2022,125.06666666666666\n2022-09-26,122,1,269,2022,126.5\n2022-09-27,121,2,270,2022,128.33333333333334\n2022-09-28,159,3,271,2022,127.86666666666666\n2022-09-29,139,4,272,2022,126.7\n2022-09-30,122,5,273,2022,124.96666666666667\n2022-10-01,81,6,274,2022,123.1\n2022-10-02,57,7,275,2022,120.5\n2022-10-03,155,1,276,2022,123.56666666666666\n2022-10-04,127,2,277,2022,125.1\n2022-10-05,114,3,278,2022,123.3\n2022-10-06,139,4,279,2022,121.03333333333333\n2022-10-07,88,5,280,2022,117.5\n2022-10-08,61,6,281,2022,114.13333333333334\n2022-10-09,66,7,282,2022,111.83333333333333\n2022-10-10,130,1,283,2022,114.36666666666666\n2022-10-11,138,2,284,2022,117.2\n2022-10-12,126,3,285,2022,117.3\n2022-10-13,128,4,286,2022,117.56666666666666\n2022-10-14,147,5,287,2022,117.9\n2022-10-15,70,6,288,2022,114.96666666666667\n2022-10-16,65,7,289,2022,113.46666666666667\n2022-10-17,125,1,290,2022,115.06666666666666\n2022-10-18,192,2,291,2022,118.6\n2022-10-19,107,3,292,2022,116.66666666666667\n2022-10-20,121,4,293,2022,114.8\n2022-10-21,90,5,294,2022,112.6\n2022-10-22,66,6,295,2022,111.03333333333333\n2022-10-23,60,7,296,2022,108.46666666666667\n2022-10-24,99,1,297,2022,108.63333333333334\n2022-10-25,84,2,298,2022,109.96666666666667\n2022-10-26,79,3,299,2022,108.53333333333333\n2022-10-27,95,4,300,2022,107.66666666666667\n2022-10-28,79,5,301,2022,105.0\n2022-10-29,43,6,302,2022,101.8\n2022-10-30,34,7,303,2022,98.86666666666666\n2022-10-31,133,1,304,2022,100.6\n2022-11-01,101,2,305,2022,102.06666666666666\n2022-11-02,124,3,306,2022,101.03333333333333\n2022-11-03,105,4,307,2022,100.3\n2022-11-04,86,5,308,2022,99.36666666666666\n2022-11-05,62,6,309,2022,96.8\n2022-11-06,67,7,310,2022,96.1\n2022-11-07,101,1,311,2022,97.43333333333334\n2022-11-08,117,2,312,2022,99.13333333333334\n2022-11-09,109,3,313,2022,98.43333333333334\n2022-11-10,152,4,314,2022,98.9\n2022-11-11,89,5,315,2022,97.66666666666667\n2022-11-12,43,6,316,2022,94.83333333333333\n2022-11-13,67,7,317,2022,92.16666666666667\n2022-11-14,122,1,318,2022,93.9\n2022-11-15,115,2,319,2022,95.56666666666666\n2022-11-16,171,3,320,2022,97.1\n2022-11-17,149,4,321,2022,95.66666666666667\n2022-11-18,123,5,322,2022,96.2\n2022-11-19,77,6,323,2022,94.73333333333333\n2022-11-20,100,7,324,2022,95.06666666666666\n2022-11-21,133,1,325,2022,97.3\n2022-11-22,142,2,326,2022,100.03333333333333\n2022-11-23,154,3,327,2022,101.86666666666666\n2022-11-24,114,4,328,2022,102.86666666666666\n2022-11-25,116,5,329,2022,104.1\n2022-11-26,32,6,330,2022,102.0\n2022-11-27,42,7,331,2022,100.76666666666667\n2022-11-28,155,1,332,2022,104.5\n2022-11-29,130,2,333,2022,107.7\n2022-11-30,149,3,334,2022,108.23333333333333\n2022-12-01,124,4,335,2022,109.0\n2022-12-02,157,5,336,2022,110.1\n2022-12-03,51,6,337,2022,108.3\n2022-12-04,56,7,338,2022,107.3\n2022-12-05,123,1,339,2022,109.33333333333333\n2022-12-06,133,2,340,2022,111.53333333333333\n2022-12-07,125,3,341,2022,112.33333333333333\n2022-12-08,111,4,342,2022,112.13333333333334\n2022-12-09,139,5,343,2022,113.13333333333334\n2022-12-10,66,6,344,2022,110.26666666666667\n2022-12-11,81,7,345,2022,110.0\n2022-12-12,102,1,346,2022,111.96666666666667\n2022-12-13,143,2,347,2022,114.5\n2022-12-14,96,3,348,2022,113.63333333333334\n2022-12-15,163,4,349,2022,115.23333333333333\n2022-12-16,159,5,350,2022,114.83333333333333\n2022-12-17,70,6,351,2022,112.2\n2022-12-18,68,7,352,2022,110.36666666666666\n2022-12-19,93,1,353,2022,110.9\n2022-12-20,132,2,354,2022,111.96666666666667\n2022-12-21,119,3,355,2022,111.5\n2022-12-22,119,4,356,2022,110.73333333333333\n2022-12-23,84,5,357,2022,108.4\n2022-12-24,54,6,358,2022,106.4\n2022-12-25,22,7,359,2022,103.26666666666667\n2022-12-26,44,1,360,2022,103.66666666666667\n2022-12-27,64,2,361,2022,104.4\n2022-12-28,57,3,362,2022,101.13333333333334\n2022-12-29,85,4,363,2022,99.63333333333334\n2022-12-30,55,5,364,2022,96.5\n2022-12-31,39,6,365,2022,93.66666666666667\n2023-01-01,40,7,1,2023,89.76666666666667\n2023-01-02,93,1,2,2023,91.16666666666667\n2023-01-03,99,2,3,2023,92.6\n2023-01-04,109,3,4,2023,92.13333333333334\n2023-01-05,114,4,5,2023,91.5\n2023-01-06,110,5,6,2023,91.0\n2023-01-07,60,6,7,2023,89.3\n2023-01-08,56,7,8,2023,86.53333333333333\n2023-01-09,144,1,9,2023,89.13333333333334\n2023-01-10,104,2,10,2023,89.9\n2023-01-11,144,3,11,2023,91.3\n2023-01-12,117,4,12,2023,90.43333333333334\n2023-01-13,154,5,13,2023,92.36666666666666\n2023-01-14,60,6,14,2023,88.93333333333334\n2023-01-15,40,7,15,2023,84.96666666666667\n2023-01-16,118,1,16,2023,86.56666666666666\n2023-01-17,111,2,17,2023,88.0\n2023-01-18,128,3,18,2023,89.16666666666667\n2023-01-19,175,4,19,2023,90.6\n2023-01-20,169,5,20,2023,92.26666666666667\n2023-01-21,68,6,21,2023,90.56666666666666\n2023-01-22,88,7,22,2023,90.7\n2023-01-23,154,1,23,2023,94.03333333333333\n2023-01-24,103,2,24,2023,96.73333333333333\n2023-01-25,117,3,25,2023,99.16666666666667\n2023-01-26,128,4,26,2023,101.3\n2023-01-27,135,5,27,2023,103.9\n2023-01-28,47,6,28,2023,102.63333333333334\n2023-01-29,74,7,29,2023,103.26666666666667\n2023-01-30,149,1,30,2023,106.93333333333334\n2023-01-31,175,2,31,2023,111.43333333333334\n2023-02-01,136,3,32,2023,112.86666666666666\n2023-02-02,159,4,33,2023,114.86666666666666\n2023-02-03,79,5,34,2023,113.86666666666666\n2023-02-04,80,6,35,2023,112.73333333333333\n2023-02-05,54,7,36,2023,110.86666666666666\n2023-02-06,125,1,37,2023,113.03333333333333\n2023-02-07,142,2,38,2023,115.9\n2023-02-08,132,3,39,2023,115.5\n2023-02-09,119,4,40,2023,116.0\n2023-02-10,102,5,41,2023,114.6\n2023-02-11,47,6,42,2023,112.26666666666667\n2023-02-12,50,7,43,2023,108.8\n2023-02-13,129,1,44,2023,111.1\n2023-02-14,110,2,45,2023,113.43333333333334\n2023-02-15,101,3,46,2023,112.86666666666666\n2023-02-16,116,4,47,2023,113.03333333333333\n2023-02-17,75,5,48,2023,111.26666666666667\n2023-02-18,59,6,49,2023,107.4\n2023-02-19,73,7,50,2023,104.2\n2023-02-20,103,1,51,2023,105.36666666666666\n2023-02-21,100,2,52,2023,105.76666666666667\n2023-02-22,115,3,53,2023,104.46666666666667\n2023-02-23,99,4,54,2023,104.33333333333333\n2023-02-24,155,5,55,2023,105.6\n2023-02-25,61,6,56,2023,103.36666666666666\n2023-02-26,43,7,57,2023,100.3\n2023-02-27,128,1,58,2023,103.0\n2023-02-28,138,2,59,2023,105.13333333333334\n2023-03-01,106,3,60,2023,103.7\n2023-03-02,101,4,61,2023,101.23333333333333\n2023-03-03,127,5,62,2023,100.93333333333334\n2023-03-04,44,6,63,2023,97.1\n2023-03-05,46,7,64,2023,96.0\n2023-03-06,129,1,65,2023,97.63333333333334\n2023-03-07,113,2,66,2023,99.6\n2023-03-08,97,3,67,2023,98.66666666666667\n2023-03-09,104,4,68,2023,97.4\n2023-03-10,129,5,69,2023,97.3\n2023-03-11,59,6,70,2023,95.3\n2023-03-12,54,7,71,2023,93.7\n2023-03-13,104,1,72,2023,95.6\n2023-03-14,109,2,73,2023,97.56666666666666\n2023-03-15,109,3,74,2023,96.9\n2023-03-16,132,4,75,2023,97.63333333333334\n2023-03-17,96,5,76,2023,97.46666666666667\n2023-03-18,79,6,77,2023,96.23333333333333\n2023-03-19,65,7,78,2023,95.9\n2023-03-20,71,1,79,2023,96.3\n2023-03-21,75,2,80,2023,96.36666666666666\n2023-03-22,118,3,81,2023,96.86666666666666\n2023-03-23,105,4,82,2023,97.03333333333333\n2023-03-24,87,5,83,2023,96.1\n2023-03-25,45,6,84,2023,94.3\n2023-03-26,41,7,85,2023,90.5\n2023-03-27,119,1,86,2023,92.43333333333334\n2023-03-28,138,2,87,2023,95.6\n2023-03-29,123,3,88,2023,95.43333333333334\n2023-03-30,148,4,89,2023,95.76666666666667\n2023-03-31,137,5,90,2023,96.8\n2023-04-01,67,6,91,2023,95.66666666666667\n2023-04-02,52,7,92,2023,93.16666666666667\n2023-04-03,116,1,93,2023,95.56666666666666\n2023-04-04,101,2,94,2023,97.4\n2023-04-05,124,3,95,2023,97.23333333333333\n2023-04-06,94,4,96,2023,96.6\n2023-04-07,79,5,97,2023,96.0\n2023-04-08,53,6,98,2023,94.3\n2023-04-09,47,7,99,2023,91.56666666666666\n2023-04-10,80,1,100,2023,92.26666666666667\n2023-04-11,103,2,101,2023,93.9\n2023-04-12,134,3,102,2023,94.9\n2023-04-13,149,4,103,2023,96.23333333333333\n2023-04-14,100,5,104,2023,95.93333333333334\n2023-04-15,52,6,105,2023,93.26666666666667\n2023-04-16,60,7,106,2023,92.06666666666666\n2023-04-17,86,1,107,2023,92.3\n2023-04-18,117,2,108,2023,94.03333333333333\n2023-04-19,86,3,109,2023,94.53333333333333\n2023-04-20,71,4,110,2023,94.4\n2023-04-21,79,5,111,2023,93.1\n2023-04-22,45,6,112,2023,91.1\n2023-04-23,38,7,113,2023,89.46666666666667\n2023-04-24,119,1,114,2023,91.93333333333334\n2023-04-25,111,2,115,2023,94.26666666666667\n2023-04-26,120,3,116,2023,94.3\n2023-04-27,82,4,117,2023,92.43333333333334\n2023-04-28,84,5,118,2023,91.13333333333334\n2023-04-29,66,6,119,2023,88.4\n2023-04-30,22,7,120,2023,84.56666666666666\n2023-05-01,71,1,121,2023,84.7\n2023-05-02,85,2,122,2023,85.8\n2023-05-03,72,3,123,2023,84.33333333333333\n2023-05-04,92,4,124,2023,84.03333333333333\n2023-05-05,94,5,125,2023,83.03333333333333\n2023-05-06,27,6,126,2023,80.8\n2023-05-07,34,7,127,2023,79.3\n2023-05-08,88,1,128,2023,80.46666666666667\n2023-05-09,88,2,129,2023,81.83333333333333\n2023-05-10,115,3,130,2023,83.0\n2023-05-11,116,4,131,2023,83.43333333333334\n2023-05-12,113,5,132,2023,82.73333333333333\n2023-05-13,28,6,133,2023,78.7\n2023-05-14,14,7,134,2023,75.83333333333333\n2023-05-15,96,1,135,2023,77.3\n2023-05-16,98,2,136,2023,78.56666666666666\n2023-05-17,95,3,137,2023,78.86666666666666\n2023-05-18,124,4,138,2023,79.1\n2023-05-19,97,5,139,2023,79.46666666666667\n2023-05-20,44,6,140,2023,78.56666666666666\n2023-05-21,70,7,141,2023,78.26666666666667\n2023-05-22,118,1,142,2023,80.7\n2023-05-23,106,2,143,2023,82.96666666666667\n2023-05-24,108,3,144,2023,82.6\n2023-05-25,73,4,145,2023,81.33333333333333\n2023-05-26,106,5,146,2023,80.86666666666666\n2023-05-27,42,6,147,2023,79.53333333333333\n2023-05-28,37,7,148,2023,77.96666666666667\n2023-05-29,54,1,149,2023,77.56666666666666\n2023-05-30,98,2,150,2023,80.1\n2023-05-31,95,3,151,2023,80.9\n2023-06-01,103,4,152,2023,81.5\n2023-06-02,92,5,153,2023,82.16666666666667\n2023-06-03,42,6,154,2023,80.5\n2023-06-04,35,7,155,2023,78.53333333333333\n2023-06-05,68,1,156,2023,79.9\n2023-06-06,71,2,157,2023,81.13333333333334\n2023-06-07,61,3,158,2023,80.23333333333333\n2023-06-08,84,4,159,2023,80.1\n2023-06-09,83,5,160,2023,79.03333333333333\n2023-06-10,37,6,161,2023,76.4\n2023-06-11,29,7,162,2023,73.6\n2023-06-12,78,1,163,2023,75.26666666666667\n2023-06-13,78,2,164,2023,77.4\n2023-06-14,90,3,165,2023,77.2\n2023-06-15,80,4,166,2023,76.6\n2023-06-16,98,5,167,2023,76.7\n2023-06-17,54,6,168,2023,74.36666666666666\n2023-06-18,30,7,169,2023,72.13333333333334\n2023-06-19,80,1,170,2023,73.33333333333333\n2023-06-20,115,2,171,2023,74.83333333333333\n2023-06-21,121,3,172,2023,74.93333333333334\n2023-06-22,104,4,173,2023,74.86666666666666\n2023-06-23,73,5,174,2023,73.7\n2023-06-24,38,6,175,2023,72.53333333333333\n2023-06-25,41,7,176,2023,70.36666666666666\n2023-06-26,126,1,177,2023,73.16666666666667\n2023-06-27,94,2,178,2023,75.06666666666666\n2023-06-28,74,3,179,2023,75.73333333333333\n2023-06-29,102,4,180,2023,75.86666666666666\n2023-06-30,118,5,181,2023,76.63333333333334\n2023-07-01,46,6,182,2023,74.73333333333333\n2023-07-02,35,7,183,2023,72.83333333333333\n2023-07-03,107,1,184,2023,75.0\n2023-07-04,67,2,185,2023,76.06666666666666\n2023-07-05,90,3,186,2023,76.8\n2023-07-06,132,4,187,2023,78.83333333333333\n2023-07-07,110,5,188,2023,80.46666666666667\n2023-07-08,25,6,189,2023,78.5\n2023-07-09,26,7,190,2023,76.6\n2023-07-10,85,1,191,2023,78.2\n2023-07-11,90,2,192,2023,80.23333333333333\n2023-07-12,83,3,193,2023,80.4\n2023-07-13,113,4,194,2023,81.56666666666666\n2023-07-14,121,5,195,2023,82.6\n2023-07-15,27,6,196,2023,80.83333333333333\n2023-07-16,23,7,197,2023,78.33333333333333\n2023-07-17,48,1,198,2023,78.13333333333334\n2023-07-18,63,2,199,2023,79.23333333333333\n2023-07-19,52,3,200,2023,78.3\n2023-07-20,67,4,201,2023,76.7\n2023-07-21,78,5,202,2023,75.26666666666667\n2023-07-22,38,6,203,2023,73.06666666666666\n2023-07-23,41,7,204,2023,72.0\n2023-07-24,113,1,205,2023,74.5\n2023-07-25,99,2,206,2023,76.43333333333334\n2023-07-26,103,3,207,2023,75.66666666666667\n2023-07-27,88,4,208,2023,75.46666666666667\n2023-07-28,88,5,209,2023,75.93333333333334\n2023-07-29,52,6,210,2023,74.26666666666667\n2023-07-30,36,7,211,2023,71.53333333333333\n2023-07-31,86,1,212,2023,72.86666666666666\n2023-08-01,84,2,213,2023,74.5\n2023-08-02,104,3,214,2023,74.4\n2023-08-03,94,4,215,2023,75.3\n2023-08-04,89,5,216,2023,75.26666666666667\n2023-08-05,46,6,217,2023,72.4\n2023-08-06,41,7,218,2023,70.1\n2023-08-07,53,1,219,2023,71.03333333333333\n2023-08-08,100,2,220,2023,73.5\n2023-08-09,111,3,221,2023,74.36666666666666\n2023-08-10,180,4,222,2023,77.36666666666666\n2023-08-11,82,5,223,2023,77.33333333333333\n2023-08-12,84,6,224,2023,76.36666666666666\n2023-08-13,33,7,225,2023,73.43333333333334\n2023-08-14,100,1,226,2023,75.86666666666666\n2023-08-15,93,2,227,2023,78.2\n2023-08-16,177,3,228,2023,82.5\n2023-08-17,118,4,229,2023,84.33333333333333\n2023-08-18,93,5,230,2023,85.7\n2023-08-19,57,6,231,2023,85.36666666666666\n2023-08-20,61,7,232,2023,84.8\n2023-08-21,90,1,233,2023,86.53333333333333\n2023-08-22,75,2,234,2023,87.66666666666667\n2023-08-23,115,3,235,2023,87.73333333333333\n2023-08-24,109,4,236,2023,88.06666666666666\n2023-08-25,78,5,237,2023,87.23333333333333\n2023-08-26,48,6,238,2023,85.9\n2023-08-27,45,7,239,2023,84.46666666666667\n2023-08-28,104,1,240,2023,86.2\n2023-08-29,79,2,241,2023,87.63333333333334\n2023-08-30,129,3,242,2023,89.06666666666666\n2023-08-31,104,4,243,2023,89.73333333333333\n2023-09-01,82,5,244,2023,89.0\n2023-09-02,39,6,245,2023,87.16666666666667\n2023-09-03,25,7,246,2023,85.03333333333333\n2023-09-04,43,1,247,2023,84.93333333333334\n2023-09-05,114,2,248,2023,87.36666666666666\n2023-09-06,90,3,249,2023,88.6\n2023-09-07,120,4,250,2023,89.26666666666667\n2023-09-08,72,5,251,2023,87.96666666666667\n2023-09-09,74,6,252,2023,84.43333333333334\n2023-09-10,43,7,253,2023,83.13333333333334\n2023-09-11,74,1,254,2023,82.8\n2023-09-12,76,2,255,2023,84.23333333333333\n2023-09-13,59,3,256,2023,82.86666666666666\n2023-09-14,79,4,257,2023,82.4\n2023-09-15,76,5,258,2023,79.03333333333333\n2023-09-16,55,6,259,2023,76.93333333333334\n2023-09-17,24,7,260,2023,74.63333333333334\n2023-09-18,99,1,261,2023,76.03333333333333\n2023-09-19,77,2,262,2023,76.56666666666666\n2023-09-20,65,3,263,2023,75.73333333333333\n2023-09-21,71,4,264,2023,75.6\n2023-09-22,54,5,265,2023,73.56666666666666\n2023-09-23,26,6,266,2023,70.8\n2023-09-24,49,7,267,2023,69.83333333333333\n2023-09-25,79,1,268,2023,70.86666666666666\n2023-09-26,80,2,269,2023,72.03333333333333\n2023-09-27,113,3,270,2023,72.33333333333333\n2023-09-28,91,4,271,2023,72.73333333333333\n2023-09-29,76,5,272,2023,70.96666666666667\n2023-09-30,33,6,273,2023,68.6\n2023-10-01,28,7,274,2023,66.8\n2023-10-02,80,1,275,2023,68.16666666666667\n2023-10-03,80,2,276,2023,70.0\n2023-10-04,88,3,277,2023,71.5\n2023-10-05,77,4,278,2023,70.26666666666667\n2023-10-06,96,5,279,2023,70.46666666666667\n2023-10-07,51,6,280,2023,68.16666666666667\n2023-10-08,48,7,281,2023,67.36666666666666\n2023-10-09,88,1,282,2023,67.83333333333333\n2023-10-10,76,2,283,2023,68.93333333333334\n2023-10-11,56,3,284,2023,68.33333333333333\n2023-10-12,90,4,285,2023,68.8\n2023-10-13,73,5,286,2023,69.26666666666667\n2023-10-14,30,6,287,2023,67.63333333333334\n2023-10-15,34,7,288,2023,66.23333333333333\n2023-10-16,97,1,289,2023,67.63333333333334\n2023-10-17,118,2,290,2023,70.76666666666667\n2023-10-18,125,3,291,2023,71.63333333333334\n2023-10-19,93,4,292,2023,72.16666666666667\n2023-10-20,81,5,293,2023,72.7\n2023-10-21,55,6,294,2023,72.16666666666667\n2023-10-22,44,7,295,2023,71.83333333333333\n2023-10-23,53,1,296,2023,72.73333333333333\n2023-10-24,84,2,297,2023,73.9\n2023-10-25,102,3,298,2023,74.66666666666667\n2023-10-26,97,4,299,2023,75.23333333333333\n2023-10-27,89,5,300,2023,74.43333333333334\n2023-10-28,44,6,301,2023,72.86666666666666\n2023-10-29,69,7,302,2023,72.63333333333334\n2023-10-30,127,1,303,2023,75.76666666666667\n2023-10-31,134,2,304,2023,79.3\n2023-11-01,112,3,305,2023,80.36666666666666\n2023-11-02,85,4,306,2023,80.53333333333333\n2023-11-03,84,5,307,2023,80.4\n2023-11-04,52,6,308,2023,79.56666666666666\n2023-11-05,63,7,309,2023,78.46666666666667\n2023-11-06,114,1,310,2023,80.56666666666666\n2023-11-07,140,2,311,2023,83.63333333333334\n2023-11-08,99,3,312,2023,84.0\n2023-11-09,99,4,313,2023,84.76666666666667\n2023-11-10,98,5,314,2023,86.16666666666667\n2023-11-11,67,6,315,2023,85.4\n2023-11-12,52,7,316,2023,84.7\n2023-11-13,100,1,317,2023,87.03333333333333\n2023-11-14,106,2,318,2023,89.43333333333334\n2023-11-15,122,3,319,2023,90.26666666666667\n2023-11-16,113,4,320,2023,90.1\n2023-11-17,107,5,321,2023,89.5\n2023-11-18,47,6,322,2023,87.96666666666667\n2023-11-19,35,7,323,2023,86.43333333333334\n2023-11-20,84,1,324,2023,87.4\n2023-11-21,108,2,325,2023,89.53333333333333\n2023-11-22,91,3,326,2023,90.8\n2023-11-23,86,4,327,2023,90.86666666666666\n2023-11-24,95,5,328,2023,90.63333333333334\n2023-11-25,32,6,329,2023,88.46666666666667\n2023-11-26,54,7,330,2023,87.3\n2023-11-27,66,1,331,2023,88.03333333333333\n2023-11-28,95,2,332,2023,88.9\n2023-11-29,87,3,333,2023,87.56666666666666\n2023-11-30,91,4,334,2023,86.13333333333334\n2023-12-01,43,5,335,2023,83.83333333333333\n2023-12-02,32,6,336,2023,82.06666666666666\n2023-12-03,19,7,337,2023,79.9\n","format":{"type":"csv"}}});</script></div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk/projects/london-clojurians-dec-2023-talk/src/notebooks/commits.clj">projects/london-clojurians-dec-2023-talk/src/notebooks/commits.clj</a></small></small></pre></div>

### 2023-12-03 projects/london-clojurians-dec-2023-talk/docs/notebooks.explore-revealjs.qmd
initial exploration of commit logs

---
format:
  revealjs:
    theme: [default, src/notebooks/custom.scss]
    include-in-header: [text, <link rel="shortcut icon" href="Cookbook.svg" />]
    navigation-mode: vertical
    transition: slide
    background-transition: fade
    incremental: true
    output-file: notebooks.explore-revealjs.html
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.explore-revealjs.html_files/md-default0.js" type="text/javascript"></script><script src="notebooks.explore-revealjs.html_files/md-default1.js" type="text/javascript"></script>

<div class="sourceClojure">
```clojure
(ns notebooks.explore
  (:require [scicloj.clay.v2.config :as config]))
```
</div>

<div class="sourceClojure">
```clojure
(+ 1 2)
```
</div>

<div class="printedClojure">
```clojure
3

```
</div>

# A1

## B1

## B2

# A2

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk//home/daslu/projects/scicloj/clojure-data-scrapbook/projects/london-clojurians-dec-2023-talk/src/notebooks/explore.clj">/home/daslu/projects/scicloj/clojure-data-scrapbook/projects/london-clojurians-dec-2023-talk/src/notebooks/explore.clj</a></small></small></pre></div>

### 2023-12-03 projects/london-clojurians-dec-2023-talk/docs/notebooks.explore.qmd
initial exploration of commit logs

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: notebooks.explore.html}
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.explore_files/md-default0.js" type="text/javascript"></script><script src="notebooks.explore_files/md-default1.js" type="text/javascript"></script>

<div class="sourceClojure">
```clojure
(ns notebooks.explore
  (:require [data.generate-dataset]
            [scicloj.kindly.v4.kind :as kind]
            [scicloj.noj.v1.vis :as vis]
            [tablecloth.api :as tc]
            [clojure.string :as string]))
```
</div>

<div class="sourceClojure">
```clojure
(def processed-data
  (-> (->> data.generate-dataset/data
           (mapcat (comp :items :items))
           (map #(select-keys % [:html_url :open_issues_count :watchers :forks_count])))
      tc/dataset
      (tc/map-columns :user [:html_url]
                      (fn [html-url]
                        (-> html-url
                            (string/split #"/")
                            (->> (drop 3)
                                 first))))))
```
</div>

<div class="sourceClojure">
```clojure
(-> processed-data
    (tc/group-by [:user])
    (tc/aggregate {:n tc/row-count})
    (tc/order-by [:n] :desc))
```
</div>

_unnamed [580 2]:

|              :user |  :n |
|--------------------|----:|
|            clojure |  30 |
|        clj-commons |  26 |
|        weavejester |  22 |
|              oakes |  13 |
|            metosin |  12 |
|           taoensso |  11 |
|               juxt |  10 |
|           babashka |   9 |
|        swannodette |   9 |
|            yogthos |   8 |
|                ... | ... |
|         congomongo |   1 |
|          ReactiveX |   1 |
|        ingesolvoll |   1 |
|         hashobject |   1 |
|         jsa-aerial |   1 |
|          jonromero |   1 |
| alexander-yakushev |   1 |
|               l3nz |   1 |
|                gcv |   1 |
|          MastodonC |   1 |
|          gnarroway |   1 |

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk/projects/london-clojurians-dec-2023-talk/src/notebooks/explore.clj">projects/london-clojurians-dec-2023-talk/src/notebooks/explore.clj</a></small></small></pre></div>

### 2023-12-20 book/prepare.sh
cleanup of obsolete book setup

@@ -1,21 +1,0 @@
-#! /bin/bash
-
-rm -rf copies_of_projects
-
-cat base.yml > _quarto.yml
-
-files=$(find ../projects/ -name '*.qmd' | sed -e 's/^..\///' | sort)
-echo $files
-
-for file in $files
-do
-    target="copies_of_"$file
-    source="../"$file
-    mkdir -p "${target%/*}"
-    cp $source $target
-    echo "    - "$target >> _quarto.yml
-done
-
-cat _quarto.yml
-
-quarto preview

### 2023-12-21 projects/visual-tools/clay-calva-demo-20231216/docs/scratch-revealjs.qmd
visual-tools demos: clay & calva, clay & cider

---
format:
  revealjs: {theme: solarized, navigation-mode: vertical, transition: slide, background-transition: fade, incremental: true, output-file: scratch-revealjs.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scratch-revealjs_files/md-default1.js" type="text/javascript"></script><script src="scratch-revealjs_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega3.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega4.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />

<div class="sourceClojure">
```clojure
(ns scratch
  (:require [scicloj.noj.v1.datasets
             :as datasets]
            [scicloj.noj.v1.vis.hanami
             :as hanami]
            [scicloj.kindly.v4.kind
             :as kind]))
```
</div>

# Intro

## Arithmetic

<div class="sourceClojure">
```clojure
(+ 1 2)
```
</div>

<div class="printedClojure">
```clojure
3

```
</div>

## Datasets

<div class="sourceClojure">
```clojure
datasets/iris
```
</div>

_unnamed [150 5]:

| :sepal-length | :sepal-width | :petal-length | :petal-width |  :species |
|--------------:|-------------:|--------------:|-------------:|-----------|
|           5.1 |          3.5 |           1.4 |          0.2 |    setosa |
|           4.9 |          3.0 |           1.4 |          0.2 |    setosa |
|           4.7 |          3.2 |           1.3 |          0.2 |    setosa |
|           4.6 |          3.1 |           1.5 |          0.2 |    setosa |
|           5.0 |          3.6 |           1.4 |          0.2 |    setosa |
|           5.4 |          3.9 |           1.7 |          0.4 |    setosa |
|           4.6 |          3.4 |           1.4 |          0.3 |    setosa |
|           5.0 |          3.4 |           1.5 |          0.2 |    setosa |
|           4.4 |          2.9 |           1.4 |          0.2 |    setosa |
|           4.9 |          3.1 |           1.5 |          0.1 |    setosa |
|           ... |          ... |           ... |          ... |       ... |
|           6.9 |          3.1 |           5.4 |          2.1 | virginica |
|           6.7 |          3.1 |           5.6 |          2.4 | virginica |
|           6.9 |          3.1 |           5.1 |          2.3 | virginica |
|           5.8 |          2.7 |           5.1 |          1.9 | virginica |
|           6.8 |          3.2 |           5.9 |          2.3 | virginica |
|           6.7 |          3.3 |           5.7 |          2.5 | virginica |
|           6.7 |          3.0 |           5.2 |          2.3 | virginica |
|           6.3 |          2.5 |           5.0 |          1.9 | virginica |
|           6.5 |          3.0 |           5.2 |          2.0 | virginica |
|           6.2 |          3.4 |           5.4 |          2.3 | virginica |
|           5.9 |          3.0 |           5.1 |          1.8 | virginica |

## Tables

<div class="sourceClojure">
```clojure
(-> datasets/iris
    kind/table)
```
</div>

<table class="table"><thead><tr><th>sepal-length</th><th>sepal-width</th><th>petal-length</th><th>petal-width</th><th>species</th></tr></thead><tbody><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.3</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.0</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.5</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.6</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.3</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>7.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.7</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>6.0</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.7</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>6.3</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.6</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.3</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>6.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.9</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.2</p></div></td><td><div><p>6.0</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.9</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.4</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.6</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr></tbody><script>new DataTable(document.currentScript.parentElement,
 {"sPaginationType": "full_numbers", "order": []});</script>datatables</table>

## Visualization

<div class="sourceClojure">
```clojure
(-> datasets/iris
    (hanami/linear-regression-plot
     :petal-length
     :petal-width
     {:line-options {:MCOLOR "brown"
                     :MSIZE 10
                     :OPACITY 0.5}
      :point-options {:MSIZE 100}}))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"scratch-revealjs_files\/0.csv","format":{"type":"csv"}}});</script></div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: projects/visual-tools/clay-calva-demo-20231216/notebooks/scratch.clj</small></small></pre></div>

### 2023-12-21 projects/visual-tools/clay-cider-demo-20231217/docs/scratch.qmd
visual-tools demos: clay & calva, clay & cider

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scratch.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scratch_files/md-default13.js" type="text/javascript"></script><script src="scratch_files/md-default14.js" type="text/javascript"></script>

# Image processing

<div class="sourceClojure">
```clojure
(ns scratch
  (:require [tech.v3.libs.buffered-image :as bufimg]
            [tech.v3.datatype :as dtype]
            [tech.v3.tensor :as tensor]
            [tech.v3.datatype.functional :as fun]
            [scicloj.noj.v1.vis.image :as vis.image]
            [scicloj.kindly.v4.kind :as kind]))
```
</div>

## Arithmetic

<div class="sourceClojure">
```clojure
(+ 1 2)
```
</div>

<div class="printedClojure">
```clojure
3

```
</div>

## Loading data

<div class="sourceClojure">
```clojure
(defonce raw-image
  (bufimg/load
   "https://upload.wikimedia.org/wikipedia/commons/1/1e/Gay_head_cliffs_MV.JPG"))
```
</div>

<div class="sourceClojure">
```clojure
(type raw-image)
```
</div>

<div class="printedClojure">
```clojure
java.awt.image.BufferedImage

```
</div>

<div class="sourceClojure">
```clojure
(bufimg/image-type raw-image)
```
</div>

<div class="printedClojure">
```clojure
:byte-bgr

```
</div>

## Displaying images

<div class="sourceClojure">
```clojure
raw-image
```
</div>

<img src="scratch_files/0.png" style="width:100%;" />

## Tensors

<div class="sourceClojure">
```clojure
(defonce raw-tensor
  (-> raw-image
      bufimg/as-ubyte-tensor))
```
</div>

<div class="sourceClojure">
```clojure
(dtype/shape raw-tensor)
```
</div>

<div class="printedClojure">
```clojure
[1478 2006 3]

```
</div>

## Processing

<div class="sourceClojure">
```clojure
[raw-image
 (-> raw-tensor
     (fun/* 0.5)
     (vis.image/tensor->image :byte-bgr))]
```
</div>

<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="scratch_files/0.png" style="width:100%;" /><img src="scratch_files/1.png" style="width:100%;" /></div><p>\]</p></div>

## Hiccup

<div class="sourceClojure">
```clojure
(kind/hiccup
 [:div
  [:h3 "raw image"]
  raw-image
  [:h3 "darkened image"]
  (-> raw-tensor
      (fun/* 0.5)
      (vis.image/tensor->image :byte-bgr))])
```
</div>

<div><h3>raw image</h3><img src="scratch_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="scratch_files/2.png" style="width:100%;" /></div>

## Colour channels

<div class="sourceClojure">
```clojure
(def colour-channels
  (-> raw-tensor
      (tensor/slice-right 1)))
```
</div>

<div class="sourceClojure">
```clojure
(def blue (colour-channels 0))
```
</div>

<div class="sourceClojure">
```clojure
(def green (colour-channels 1))
```
</div>

<div class="sourceClojure">
```clojure
(def red (colour-channels 2))
```
</div>

<div class="sourceClojure">
```clojure
(count colour-channels)
```
</div>

<div class="printedClojure">
```clojure
3

```
</div>

<div class="sourceClojure">
```clojure
(mapv dtype/shape colour-channels)
```
</div>

<div class="printedClojure">
```clojure
[[1478 2006] [1478 2006] [1478 2006]]

```
</div>

<div class="sourceClojure">
```clojure
(-> (tensor/compute-tensor (dtype/shape raw-tensor)
                           (fn [i j k]
                             (if (= k 2)
                               (raw-tensor i j k)
                               0))
                           :uint8)
    (vis.image/tensor->image :byte-bgr))
```
</div>

<img src="scratch_files/3.png" style="width:100%;" />

## Conditioned processing

<div class="sourceClojure">
```clojure
(-> (tensor/compute-tensor (dtype/shape raw-tensor)
                           (fn [i j k]
                             (*
                              (raw-tensor i j k)
                              (if (> (green i j)
                                     (blue i j))
                                0.3
                                1)))
                           :uint8)
    (vis.image/tensor->image :byte-bgr))
```
</div>

<img src="scratch_files/4.png" style="width:100%;" />

<div class="sourceClojure">
```clojure
(-> (tensor/compute-tensor (dtype/shape raw-tensor)
                           (fn [i j k]
                             (*
                              (raw-tensor i j k)
                              (if (> (green i j)
                                     (* 1.2 (blue i j)))
                                0.3
                                1)))
                           :uint8)
    (vis.image/tensor->image :byte-bgr))
```
</div>

<img src="scratch_files/5.png" style="width:100%;" />

<div class="sourceClojure">
```clojure
(->> [0.7 0.8 0.9 1 1.1 1.2 1.3]
     (map (fn [factor]
            [factor
             (-> (tensor/compute-tensor (dtype/shape raw-tensor)
                                        (fn [i j k]
                                          (*
                                           (raw-tensor i j k)
                                           (if (> (green i j)
                                                  (* factor (blue i j)))
                                             0.3
                                             1)))
                                        :uint8)
                 (vis.image/tensor->image :byte-bgr))])))
```
</div>

<div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.7
</code></pre></div><img src="scratch_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
</code></pre></div><img src="scratch_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
</code></pre></div><img src="scratch_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
</code></pre></div><img src="scratch_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
</code></pre></div><img src="scratch_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
</code></pre></div><img src="scratch_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
</code></pre></div><img src="scratch_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: projects/visual-tools/clay-cider-demo-20231217/notebooks/scratch.clj</small></small></pre></div>

### 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/notebooks.combining_tools-revealjs.qmd
moved docs for github pages

---
format:
  revealjs:
    theme: [default, src/notebooks/custom.scss]
    include-in-header: [text, <link rel="shortcut icon" href="Cookbook.svg" />]
    navigation-mode: vertical
    transition: slide
    background-transition: fade
    incremental: true
    output-file: notebooks.combining_tools-revealjs.html
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.combining_tools-revealjs_files/md-default0.js" type="text/javascript"></script><script src="notebooks.combining_tools-revealjs_files/md-default1.js" type="text/javascript"></script>
# Combining tools for data exploration

##
![](https://scicloj.github.io/sci-cloj-logo-transparent.png)

[scicloj.org](http://scicloj.org)

##
![](https://raw.githubusercontent.com/practicalli-john/london-clojurians-logo/master/london-clojurians-logo.svg)

##
![](https://sessionize.com/image/68c6-1140o400o3-Boo2pA28xQfvKskyXqwcmd.jpg)

## Plan
- Dynamic report making with slow processes
- Data processing & visualization in harmony

## Use case: analysing commit logs
- Which projects are encouraging community conributions?

## Data pipeline
- take the 1000 most popular Clojure repos (according to Github's API)
- .. and also the Python ones
- clone them
- look into the commit logs
- process & visualize

## Limitations
- a biased data sample
- descriptive statistics, not statistical inference
- interpretation is not obvious

# Dynamic report making with slow processes

## Slow processes
- collecting remote data
- fetching API responses
- applying slow AI models

# Data processing & visualization in harmony

## Lots of existing functionality

- dtype-next - array processing
- tech.ml.dataset - high-performance datasets
- Tablecloth - dataset ergonomics
- Fasthmath - lots of math & stats
- scicloj.ml - machine learning, data modelling
- Hanami - data visualization
- Libpython-clj, ClojisR - interop
- Visual tools
- etc.

## Noj
- collecting the relevant dependencies
- composing them for common use cases

# Thanks

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk/projects/london-clojurians-dec-2023-talk/src/notebooks/combining_tools.clj">projects/london-clojurians-dec-2023-talk/src/notebooks/combining_tools.clj</a></small></small></pre></div>

### 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/notebooks.combining_tools.qmd
moved docs for github pages

--- 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/notebooks.combining_tools-revealjs.qmd
@@
 format:
-  revealjs:
-    theme: [default, src/notebooks/custom.scss]
-    include-in-header: [text, <link rel="shortcut icon" href="Cookbook.svg" />]
-    navigation-mode: vertical
-    transition: slide
-    background-transition: fade
-    incremental: true
-    output-file: notebooks.combining_tools-revealjs.html
+  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: notebooks.combining_tools.html}
 highlight-style: solarized
@@
 </style>
-<script src="notebooks.combining_tools-revealjs_files/md-default0.js" type="text/javascript"></script><script src="notebooks.combining_tools-revealjs_files/md-default1.js" type="text/javascript"></script>
+<script src="notebooks.combining_tools_files/md-default0.js" type="text/javascript"></script><script src="notebooks.combining_tools_files/md-default1.js" type="text/javascript"></script>
 # Combining tools for data exploration

### 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/notebooks.commit_details.qmd
moved docs for github pages

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: notebooks.commit_details.html}
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.commit_details_files/md-default5.js" type="text/javascript"></script><script src="notebooks.commit_details_files/md-default6.js" type="text/javascript"></script><script src="notebooks.commit_details_files/vega7.js" type="text/javascript"></script><script src="notebooks.commit_details_files/vega8.js" type="text/javascript"></script><script src="notebooks.commit_details_files/vega9.js" type="text/javascript"></script>

<div class="sourceClojure">
```clojure
(ns notebooks.commit-details
  (:require [tablecloth.api :as tc]
            [scicloj.noj.v1.vis.hanami :as hanami]
            [aerial.hanami.templates :as ht]
            [tech.v3.datatype.datetime :as datetime]
            [tech.v3.datatype.rolling :as rolling]
            [tech.v3.datatype.functional :as fun]
            [tech.v3.dataset.print :as print]
            [data.generate-dataset]
            [clojure.math :as math]
            [scicloj.kindly.v4.kind :as kind]
            [scicloj.noj.v1.stats :as stats]))
```
</div>

<div class="sourceClojure">
```clojure
(delay
  (-> data.generate-dataset/commit-details
      (tc/group-by [:language :html_url])
      (tc/aggregate {:n-contributors (fn [ds]
                                       (-> ds
                                           :email
                                           distinct
                                           count))})
      (tc/order-by [:n-contributors] :desc)))
```
</div>

_unnamed [1891 3]:

| :language |                                                     :html_url | :n-contributors |
|-----------|---------------------------------------------------------------|----------------:|
|   Clojure |                      https://github.com/technomancy/leiningen |             474 |
|   Clojure |                          https://github.com/metabase/metabase |             417 |
|    Python |                                https://github.com/qtile/qtile |             407 |
|    Python |                       https://github.com/stephenmcd/mezzanine |             341 |
|   Clojure |                    https://github.com/status-im/status-mobile |             331 |
|    Python |                            https://github.com/aws/aws-sam-cli |             308 |
|    Python |                          https://github.com/NCSC-NL/log4shell |             299 |
|   Clojure |                              https://github.com/logseq/logseq |             282 |
|    Python |                             https://github.com/StackStorm/st2 |             250 |
|    Python |                                  https://github.com/dipy/dipy |             236 |
|       ... |                                                           ... |             ... |
|    Python | https://github.com/khanhnamle1994/natural-language-processing |               1 |
|   Clojure |                https://github.com/dlebrero/wireshark-plantuml |               1 |
|    Python |                           https://github.com/ptoomey3/evilarc |               1 |
|    Python |                https://github.com/clcarwin/focal_loss_pytorch |               1 |
|    Python |                         https://github.com/dr0op/WeblogicScan |               1 |
|   Clojure |                        https://github.com/BrunoBonacci/safely |               1 |
|   Clojure |                              https://github.com/aphyr/dom-top |               1 |
|   Clojure |                   https://github.com/thheller/shadow-arborist |               1 |
|    Python | https://github.com/leeguandong/Interview-code-practice-python |               1 |
|   Clojure |                     https://github.com/Yuppiechef/cqrs-server |               1 |
|   Clojure |                    https://github.com/stuartsierra/dependency |               1 |

<div class="sourceClojure">
```clojure
(delay
  (-> data.generate-dataset/commit-details
      (tc/select-rows #(-> % :html_url (= "https://github.com/technomancy/leiningen")))
      (tc/group-by [:email])
      (tc/aggregate {:n tc/row-count})
      (tc/order-by [:n] :desc)))
```
</div>

_unnamed [474 2]:

|                                 :email |   :n |
|----------------------------------------|-----:|
|                  technomancy@gmail.com | 2127 |
|                        phil@hagelb.org |  499 |
|                  jeannikl@hypirion.com |  419 |
|                    trptcolin@gmail.com |  117 |
|                michael@defprotocol.org |   78 |
|                       mtyaka@gmail.com |   70 |
|                            i@raynes.me |   61 |
|                 git@justinbalthrop.com |   56 |
|                 mtopolnik@inge-mark.hr |   55 |
|                michael@novemberain.com |   49 |
|                                    ... |  ... |
|           ulrich.moritz@googlemail.com |    1 |
|                eric.hanchrow@gmail.com |    1 |
|                       tim@dysinger.net |    1 |
| visionary.software.solutions@gmail.com |    1 |
|                  romanandreg@gmail.com |    1 |
|                       self@sungpae.com |    1 |
|          julian.birch@colourcoding.net |    1 |
|             david@deadpansincerity.com |    1 |
|                    jaderholm@gmail.com |    1 |
|                 acgetchell@ucdavis.edu |    1 |
|                     heinz@licenser.net |    1 |

<div class="sourceClojure">
```clojure
(delay
  (-> data.generate-dataset/commit-details
      (tc/group-by [:language :html_url])
      (tc/aggregate {:n-contributors (fn [ds]
                                       (-> ds
                                           :email
                                           distinct
                                           count))})
      (tc/order-by [:n-contributors] :desc)
      (tc/left-join data.generate-dataset/repos-ds [:html_url])
      (tc/select-rows #(-> % :n-contributors (> 20)))
      (hanami/plot ht/point-chart
                   {:X :n-contributors
                    :XSCALE {:type "log"}
                    :Y :stargazers_count
                    :YSCALE {:type "log"}
                    :COLOR "language"})))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"scale":{"type":"log"},"field":"stargazers_count","type":"quantitative"},"color":{"field":"language","type":"nominal"},"x":{"scale":{"type":"log"},"field":"n-contributors","type":"quantitative"}},"mark":{"type":"circle","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"notebooks.commit_details_files\/0.csv","format":{"type":"csv"}}});</script></div>

<div class="sourceClojure">
```clojure
(delay
  (-> data.generate-dataset/commit-details
      (tc/group-by [:language :html_url])
      (tc/aggregate {:n-contributors (fn [ds]
                                       (-> ds
                                           :email
                                           distinct
                                           count))})
      (tc/order-by [:n-contributors] :desc)
      (tc/left-join data.generate-dataset/repos-ds [:html_url])
      (tc/select-rows #(-> % :n-contributors (> 20)))
      (tc/group-by [:language])
      (hanami/plot ht/point-chart
                   {:X :n-contributors
                    :XSCALE {:type "log"}
                    :Y :stargazers_count
                    :YSCALE {:type "log"}})))
```
</div>

<table class="table"><thead><tr><th>language</th><th>plot-0</th></tr></thead><tbody><tr><td><div><p>Python</p></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"scale":{"type":"log"},"field":"stargazers_count","type":"quantitative"},"x":{"scale":{"type":"log"},"field":"n-contributors","type":"quantitative"}},"mark":{"type":"circle","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"notebooks.commit_details_files\/1.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td><div><p>Clojure</p></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"scale":{"type":"log"},"field":"stargazers_count","type":"quantitative"},"x":{"scale":{"type":"log"},"field":"n-contributors","type":"quantitative"}},"mark":{"type":"circle","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"notebooks.commit_details_files\/2.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>

<div class="sourceClojure">
```clojure
(delay
  (-> data.generate-dataset/commit-details
      (tc/group-by [:language :html_url])
      (tc/aggregate {:n-contributors (fn [ds]
                                       (-> ds
                                           :email
                                           distinct
                                           count))})
      (tc/order-by [:n-contributors] :desc)
      (tc/left-join data.generate-dataset/repos-ds [:html_url])
      (tc/select-rows #(-> % :n-contributors (> 20)))
      (tc/group-by [:language])
      (tc/add-columns {:log-stargazers #(-> %
                                            :stargazers_count
                                            fun/log)
                       :log-contributors #(-> %
                                              :n-contributors
                                              fun/log)})
      (stats/add-predictions :log-stargazers
                             [:log-contributors]
                             {:model-type :smile.regression/ordinary-least-square})
      (hanami/linear-regression-plot
       :log-stargazers
       :log-contributors
       {:X :log-contributors
        :XSCALE {:zero false}
        :YSCALE {:zero false
                 :domain [5 12]}
        :line-options {:MCOLOR "brown"}})))
```
</div>

<table class="table"><thead><tr><th>language</th><th>plot-0</th></tr></thead><tbody><tr><td><div><p>Python</p></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","layer":[{"encoding":{"y":{"scale":{"zero":false,"domain":[5,12]},"field":"log-stargazers","type":"quantitative"},"x":{"scale":{"zero":false},"field":"log-contributors","type":"quantitative"}},"mark":{"type":"circle","tooltip":true},"width":400,"background":"floralwhite","height":300},{"encoding":{"y":{"scale":{"zero":false,"domain":[5,12]},"field":"log-stargazers-prediction","type":"quantitative","axis":{"title":"log-stargazers"}},"x":{"scale":{"zero":false},"field":"log-contributors","type":"quantitative"}},"mark":{"type":"line","color":"brown","tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300,"data":{"url":"notebooks.commit_details_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td><div><p>Clojure</p></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","layer":[{"encoding":{"y":{"scale":{"zero":false,"domain":[5,12]},"field":"log-stargazers","type":"quantitative"},"x":{"scale":{"zero":false},"field":"log-contributors","type":"quantitative"}},"mark":{"type":"circle","tooltip":true},"width":400,"background":"floralwhite","height":300},{"encoding":{"y":{"scale":{"zero":false,"domain":[5,12]},"field":"log-stargazers-prediction","type":"quantitative","axis":{"title":"log-stargazers"}},"x":{"scale":{"zero":false},"field":"log-contributors","type":"quantitative"}},"mark":{"type":"line","color":"brown","tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300,"data":{"url":"notebooks.commit_details_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk/projects/london-clojurians-dec-2023-talk/src/notebooks/commit_details.clj">projects/london-clojurians-dec-2023-talk/src/notebooks/commit_details.clj</a></small></small></pre></div>

### 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/notebooks.commit_details_gradually.qmd
moved docs for github pages

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: notebooks.commit_details_gradually.html}
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.commit_details_gradually_files/md-default1.js" type="text/javascript"></script><script src="notebooks.commit_details_gradually_files/md-default2.js" type="text/javascript"></script><script src="notebooks.commit_details_gradually_files/vega3.js" type="text/javascript"></script><script src="notebooks.commit_details_gradually_files/vega4.js" type="text/javascript"></script><script src="notebooks.commit_details_gradually_files/vega5.js" type="text/javascript"></script>

<div class="sourceClojure">
```clojure
(ns notebooks.commit-details-gradually
  (:require [tablecloth.api :as tc]
            [scicloj.noj.v1.vis.hanami :as hanami]
            [aerial.hanami.templates :as ht]
            [tech.v3.datatype.datetime :as datetime]
            [tech.v3.datatype.rolling :as rolling]
            [tech.v3.datatype.functional :as fun]
            [tech.v3.dataset.print :as print]
            [data.generate-dataset]
            [clojure.math :as math]
            [scicloj.kindly.v4.kind :as kind]
            [scicloj.noj.v1.stats :as stats]
            [scicloj.clay.v2.api :as clay]
            [clojure.string :as string]
            [clojure.java.shell :as shell]
            [scicloj.kind-portal.v1.api :as kind-portal]
            [portal.api :as portal]
            [clojure.java.io :as io]
            [scicloj.kind-portal.v1.api :as kind-portal]))
```
</div>

<div class="sourceClojure">
```clojure
(defn url->clone-path [url]
  (-> url
      (string/replace #"^https://github.com/" "")
      (string/replace #"/" "__")
      (->> (str "/workspace/clones-for-gradual-analysis/"))))
```
</div>

<div class="sourceClojure">
```clojure
(defn clone! [{:keys [html_url clone-path]}]
  (io/make-parents clone-path)
  (when-not (-> clone-path
                io/file
                (.exists))
    (prn [:git-clone html_url clone-path])
    (shell/sh "git"
              "clone"
              html_url
              clone-path)))
```
</div>

<div class="sourceClojure">
```clojure
(defn clone-all! [])
```
</div>

<div class="sourceClojure">
```clojure
(defn git-log [{:as repo
                :keys [html_url clone-path]}]
  (prn [:git-log clone-path])
  (-> clone-path
      (->> (format "--git-dir=%s/.git"))
      (#(shell/sh "git" %
                  "log"
                  "--pretty=format:\"%ad,%ae\""
                  "--date=short"))
      :out
      (string/replace #"\"" "")
      string/split-lines
      (->> (map (fn [line]
                  (-> line
                      (string/split #",")
                      ((fn [[date email]]
                         (merge repo
                                {:date date
                                 :email email})))))))
      tc/dataset
      (tc/set-dataset-name html_url)))
```
</div>

<div class="sourceClojure">
```clojure
(defonce *stop (atom false))
```
</div>

<div class="sourceClojure">
```clojure
(defonce *raw-commit-logs (atom []))
```
</div>

<div class="sourceClojure">
```clojure
(defonce *portal-commit-logs (atom []))
```
</div>

<div class="sourceClojure">
```clojure
(defn collect! [limit]
  (prn [:DBG1])
  (reset! *stop false)
  (prn [:DBG2])
  (reset! *raw-commit-logs [])
  (prn [:DBG2])
  (reset! *portal-commit-logs [])
  (prn [:DBG3])
  (-> data.generate-dataset/repos-ds
      (tc/map-columns :clone-path [:html_url]
                      url->clone-path)
      (tc/select-rows #(and (-> % :size (< 100000))
                            (-> % :language (= "Clojure"))))
      (tc/rows :as-maps)
      (->> (take limit)
           (mapv (fn [repo]
                   (prn repo)
                   (when-not @*stop
                     (clone! repo)
                     (let [log (git-log repo)]
                       (swap! *raw-commit-logs
                              conj log)
                       (swap! *portal-commit-logs
                              #(-> %
                                   (conj (kind-portal/prepare
                                          {:value log}))
                                   reverse))))))))
  (prn [:stopped]))
```
</div>

<div class="sourceClojure">
```clojure
(comment
  (future (collect! 220))

  (reset! *stop true)

  (portal/open)
  (portal/submit *portal-commit-logs))
```
</div>

<div class="sourceClojure">
```clojure
(defn report []
  (let [raw-commit-logs @*raw-commit-logs
        n (count raw-commit-logs)]
    [(kind/hiccup
      [:h1 n " repos"])
     (when (> n 10)
       (-> raw-commit-logs
           (->> (apply tc/concat))
           (tc/group-by [:language :html_url])
           (tc/aggregate {:n-contributors (fn [ds]
                                            (-> ds
                                                :email
                                                distinct
                                                count))})
           (tc/order-by [:n-contributors] :desc)
           (tc/left-join data.generate-dataset/repos-ds [:html_url])
           (tc/select-rows #(-> % :n-contributors (> 20)))
           (tc/add-columns {:log-stargazers #(-> %
                                                 :stargazers_count
                                                 fun/log)
                            :log-contributors #(-> %
                                                   :n-contributors
                                                   fun/log)})
           (stats/add-predictions :log-stargazers
                                  [:log-contributors]
                                  {:model-type :smile.regression/ordinary-least-square})
           (hanami/linear-regression-plot
            :log-contributors
            :log-stargazers
            {:XSCALE {:zero false
                      :domain [5 12]}
             :YSCALE {:zero false}
             :point-options {:MSIZE 100}
             :line-options {:MCOLOR "brown"
                            :MSIZE 10
                            :OPACITY 0.5}})
           (assoc-in [:encoding :tooltip]
                     {:field "html_url"})))]))
```
</div>

<div class="sourceClojure">
```clojure
(def *report (atom nil))
```
</div>

<div class="sourceClojure">
```clojure
(defn update-report! []
  (prn [:update-report])
  (reset! *report (kind-portal/prepare
                   {:value (report)})))
```
</div>

<div class="sourceClojure">
```clojure
(comment

  (report)

  (update-report!)

  (add-watch *raw-commit-logs
             :report
             (fn [_ _ _ _]
               (update-report!)))

  (portal/submit *report))
```
</div>

<div class="sourceClojure">
```clojure
(report)
```
</div>

<div><p>\[</p><div style="margin-left:10%;width:110%;"><h1>194 repos</h1><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"tooltip":{"field":"html_url"}},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.213"},"layer":[{"encoding":{"y":{"scale":{"zero":false},"field":"log-contributors","type":"quantitative"},"x":{"scale":{"zero":false,"domain":[5,12]},"field":"log-stargazers","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.213"},"height":300},{"encoding":{"y":{"scale":{"zero":false},"field":"log-contributors-prediction","type":"quantitative","axis":{"title":"log-contributors"}},"opacity":{"value":0.5},"x":{"scale":{"zero":false,"domain":[5,12]},"field":"log-stargazers","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.213"},"height":300}],"height":300,"data":{"url":"notebooks.commit_details_gradually_files\/0.csv","format":{"type":"csv"}}});</script></div></div><p>\]</p></div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk/projects/london-clojurians-dec-2023-talk/src/notebooks/commit_details_gradually.clj">projects/london-clojurians-dec-2023-talk/src/notebooks/commit_details_gradually.clj</a></small></small></pre></div>

### 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/notebooks.exploring_commit_logs-revealjs.qmd
moved docs for github pages

---
format:
  revealjs:
    theme: [default, src/notebooks/custom.scss]
    include-in-header: [text, <link rel="shortcut icon" href="Cookbook.svg" />]
    navigation-mode: vertical
    transition: slide
    background-transition: fade
    incremental: true
    output-file: notebooks.exploring_commit_logs-revealjs.html
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.exploring_commit_logs-revealjs_files/md-default0.js" type="text/javascript"></script><script src="notebooks.exploring_commit_logs-revealjs_files/md-default1.js" type="text/javascript"></script>
# Exploring commit logs

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk/projects/london-clojurians-dec-2023-talk/src/notebooks/exploring_commit_logs.clj">projects/london-clojurians-dec-2023-talk/src/notebooks/exploring_commit_logs.clj</a></small></small></pre></div>

### 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/notebooks.exploring_commit_logs.qmd
moved docs for github pages

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: notebooks.exploring_commit_logs.html}
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.exploring_commit_logs_files/md-default0.js" type="text/javascript"></script><script src="notebooks.exploring_commit_logs_files/md-default1.js" type="text/javascript"></script>
AA

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk/projects/london-clojurians-dec-2023-talk/src/notebooks/exploring_commit_logs.clj">projects/london-clojurians-dec-2023-talk/src/notebooks/exploring_commit_logs.clj</a></small></small></pre></div>

### 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/visualization.qmd
moved docs for github pages

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: visualization.html}
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="visualization_files/md-default0.js" type="text/javascript"></script><script src="visualization_files/md-default1.js" type="text/javascript"></script><script src="visualization_files/vega2.js" type="text/javascript"></script><script src="visualization_files/vega3.js" type="text/javascript"></script><script src="visualization_files/vega4.js" type="text/javascript"></script>

# Visualization

<div class="sourceClojure">
```clojure
(ns visualization
  (:require [tablecloth.api :as tc]
            [aerial.hanami.common :as hc]
            [aerial.hanami.templates :as ht]
            [scicloj.noj.v1.vis.hanami.templates :as vht]
            [scicloj.noj.v1.vis :as vis]
            [scicloj.noj.v1.stats :as stats]
            [scicloj.noj.v1.datasets :as datasets]
            [tech.v3.datatype :as dtype]
            [tech.v3.datatype.functional :as fun]
            [scicloj.kindly.v4.api :as kindly]
            [scicloj.kindly.v4.kind :as kind]
            [hiccup.core :as hiccup]
            [clojure2d.color :as color]))
```
</div>

## Visualizing datases with Hanami
Noj offers a few convenience functions to make [Hanami](https://github.com/jsa-aerial/hanami) plotting work smoothly with [Tablecloth](https://scicloj.github.io/tablecloth/) and [Kindly](https://scicloj.github.io/kindly/).

<div class="sourceClojure">
```clojure
(def random-walk
  (let [n 20]
    (-> {:x (range n)
         :y (->> (repeatedly n #(- (rand) 0.5))
                 (reductions +))}
        tc/dataset)))
```
</div>

### A simple plot
We can plot a Tablecloth datasete using a Hanami template:

<div class="sourceClojure">
```clojure
(-> random-walk
    (vis/hanami-plot ht/point-chart
                     {:MSIZE 200}))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"y","type":"quantitative"},"x":{"field":"x","type":"quantitative"}},"mark":{"type":"circle","size":200,"tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"values":"x,y\n0,-0.10891746407198855\n1,-0.17746785165549706\n2,0.010481929682169322\n3,-0.30373971592778526\n4,-0.47604808081984973\n5,-0.892613043086356\n6,-1.1415894660576191\n7,-1.3022333469107266\n8,-1.648762135975216\n9,-1.3201114922367414\n10,-1.7176056054413757\n11,-1.3492575022010356\n12,-0.8540467998730537\n13,-0.9979245662928977\n14,-1.0470624845665784\n15,-0.7440189393874057\n16,-0.3609645768215545\n17,-0.6690171277438733\n18,-0.2370752883476035\n19,-0.3441999031150036\n","format":{"type":"csv"}}});</script></div>

Let us look inside the resulting vega-lite space. We can see the dataset is included as CSV:

<div class="sourceClojure">
```clojure
(-> random-walk
    (vis/hanami-plot ht/point-chart
                     {:MSIZE 200})
    kind/pprint)
```
</div>

<div class="printedClojure">
```clojure
{:encoding
 {:y {:field "y", :type "quantitative"},
  :x {:field "x", :type "quantitative"}},
 :mark {:type "circle", :size 200, :tooltip true},
 :width 400,
 :background "floralwhite",
 :height 300,
 :data
 {:values
  "x,y\n0,-0.10891746407198855\n1,-0.17746785165549706\n2,0.010481929682169322\n3,-0.30373971592778526\n4,-0.47604808081984973\n5,-0.892613043086356\n6,-1.1415894660576191\n7,-1.3022333469107266\n8,-1.648762135975216\n9,-1.3201114922367414\n10,-1.7176056054413757\n11,-1.3492575022010356\n12,-0.8540467998730537\n13,-0.9979245662928977\n14,-1.0470624845665784\n15,-0.7440189393874057\n16,-0.3609645768215545\n17,-0.6690171277438733\n18,-0.2370752883476035\n19,-0.3441999031150036\n",
  :format {:type "csv"}}}

```
</div>

We can used Hanami temples from the namespace `[aerial.hanami.templates :as ht]'
as well as the additional templates at Noj's `[scicloj.noj.v1.vis.hanami.templates :as vht]`.

<div class="sourceClojure">
```clojure
(-> datasets/iris
    (vis/hanami-plot vht/rule-chart
                     {:X :sepal-width
                      :Y :sepal-length
                      :X2 :petal-width
                      :Y2 :petal-length
                      :OPACITY 0.2
                      :SIZE 3
                      :COLOR "species"}))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"sepal-length","type":"quantitative"},"color":{"field":"species","type":"nominal"},"size":{"value":3},"opacity":{"value":0.2},"x":{"field":"sepal-width","type":"quantitative"},"y2":{"field":"petal-length","type":"quantitative"},"x2":{"field":"petal-width","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","height":300,"data":{"values":"sepal-length,sepal-width,petal-length,petal-width,species\n5.1,3.5,1.4,0.2,setosa\n4.9,3.0,1.4,0.2,setosa\n4.7,3.2,1.3,0.2,setosa\n4.6,3.1,1.5,0.2,setosa\n5.0,3.6,1.4,0.2,setosa\n5.4,3.9,1.7,0.4,setosa\n4.6,3.4,1.4,0.3,setosa\n5.0,3.4,1.5,0.2,setosa\n4.4,2.9,1.4,0.2,setosa\n4.9,3.1,1.5,0.1,setosa\n5.4,3.7,1.5,0.2,setosa\n4.8,3.4,1.6,0.2,setosa\n4.8,3.0,1.4,0.1,setosa\n4.3,3.0,1.1,0.1,setosa\n5.8,4.0,1.2,0.2,setosa\n5.7,4.4,1.5,0.4,setosa\n5.4,3.9,1.3,0.4,setosa\n5.1,3.5,1.4,0.3,setosa\n5.7,3.8,1.7,0.3,setosa\n5.1,3.8,1.5,0.3,setosa\n5.4,3.4,1.7,0.2,setosa\n5.1,3.7,1.5,0.4,setosa\n4.6,3.6,1.0,0.2,setosa\n5.1,3.3,1.7,0.5,setosa\n4.8,3.4,1.9,0.2,setosa\n5.0,3.0,1.6,0.2,setosa\n5.0,3.4,1.6,0.4,setosa\n5.2,3.5,1.5,0.2,setosa\n5.2,3.4,1.4,0.2,setosa\n4.7,3.2,1.6,0.2,setosa\n4.8,3.1,1.6,0.2,setosa\n5.4,3.4,1.5,0.4,setosa\n5.2,4.1,1.5,0.1,setosa\n5.5,4.2,1.4,0.2,setosa\n4.9,3.1,1.5,0.2,setosa\n5.0,3.2,1.2,0.2,setosa\n5.5,3.5,1.3,0.2,setosa\n4.9,3.6,1.4,0.1,setosa\n4.4,3.0,1.3,0.2,setosa\n5.1,3.4,1.5,0.2,setosa\n5.0,3.5,1.3,0.3,setosa\n4.5,2.3,1.3,0.3,setosa\n4.4,3.2,1.3,0.2,setosa\n5.0,3.5,1.6,0.6,setosa\n5.1,3.8,1.9,0.4,setosa\n4.8,3.0,1.4,0.3,setosa\n5.1,3.8,1.6,0.2,setosa\n4.6,3.2,1.4,0.2,setosa\n5.3,3.7,1.5,0.2,setosa\n5.0,3.3,1.4,0.2,setosa\n7.0,3.2,4.7,1.4,versicolor\n6.4,3.2,4.5,1.5,versicolor\n6.9,3.1,4.9,1.5,versicolor\n5.5,2.3,4.0,1.3,versicolor\n6.5,2.8,4.6,1.5,versicolor\n5.7,2.8,4.5,1.3,versicolor\n6.3,3.3,4.7,1.6,versicolor\n4.9,2.4,3.3,1.0,versicolor\n6.6,2.9,4.6,1.3,versicolor\n5.2,2.7,3.9,1.4,versicolor\n5.0,2.0,3.5,1.0,versicolor\n5.9,3.0,4.2,1.5,versicolor\n6.0,2.2,4.0,1.0,versicolor\n6.1,2.9,4.7,1.4,versicolor\n5.6,2.9,3.6,1.3,versicolor\n6.7,3.1,4.4,1.4,versicolor\n5.6,3.0,4.5,1.5,versicolor\n5.8,2.7,4.1,1.0,versicolor\n6.2,2.2,4.5,1.5,versicolor\n5.6,2.5,3.9,1.1,versicolor\n5.9,3.2,4.8,1.8,versicolor\n6.1,2.8,4.0,1.3,versicolor\n6.3,2.5,4.9,1.5,versicolor\n6.1,2.8,4.7,1.2,versicolor\n6.4,2.9,4.3,1.3,versicolor\n6.6,3.0,4.4,1.4,versicolor\n6.8,2.8,4.8,1.4,versicolor\n6.7,3.0,5.0,1.7,versicolor\n6.0,2.9,4.5,1.5,versicolor\n5.7,2.6,3.5,1.0,versicolor\n5.5,2.4,3.8,1.1,versicolor\n5.5,2.4,3.7,1.0,versicolor\n5.8,2.7,3.9,1.2,versicolor\n6.0,2.7,5.1,1.6,versicolor\n5.4,3.0,4.5,1.5,versicolor\n6.0,3.4,4.5,1.6,versicolor\n6.7,3.1,4.7,1.5,versicolor\n6.3,2.3,4.4,1.3,versicolor\n5.6,3.0,4.1,1.3,versicolor\n5.5,2.5,4.0,1.3,versicolor\n5.5,2.6,4.4,1.2,versicolor\n6.1,3.0,4.6,1.4,versicolor\n5.8,2.6,4.0,1.2,versicolor\n5.0,2.3,3.3,1.0,versicolor\n5.6,2.7,4.2,1.3,versicolor\n5.7,3.0,4.2,1.2,versicolor\n5.7,2.9,4.2,1.3,versicolor\n6.2,2.9,4.3,1.3,versicolor\n5.1,2.5,3.0,1.1,versicolor\n5.7,2.8,4.1,1.3,versicolor\n6.3,3.3,6.0,2.5,virginica\n5.8,2.7,5.1,1.9,virginica\n7.1,3.0,5.9,2.1,virginica\n6.3,2.9,5.6,1.8,virginica\n6.5,3.0,5.8,2.2,virginica\n7.6,3.0,6.6,2.1,virginica\n4.9,2.5,4.5,1.7,virginica\n7.3,2.9,6.3,1.8,virginica\n6.7,2.5,5.8,1.8,virginica\n7.2,3.6,6.1,2.5,virginica\n6.5,3.2,5.1,2.0,virginica\n6.4,2.7,5.3,1.9,virginica\n6.8,3.0,5.5,2.1,virginica\n5.7,2.5,5.0,2.0,virginica\n5.8,2.8,5.1,2.4,virginica\n6.4,3.2,5.3,2.3,virginica\n6.5,3.0,5.5,1.8,virginica\n7.7,3.8,6.7,2.2,virginica\n7.7,2.6,6.9,2.3,virginica\n6.0,2.2,5.0,1.5,virginica\n6.9,3.2,5.7,2.3,virginica\n5.6,2.8,4.9,2.0,virginica\n7.7,2.8,6.7,2.0,virginica\n6.3,2.7,4.9,1.8,virginica\n6.7,3.3,5.7,2.1,virginica\n7.2,3.2,6.0,1.8,virginica\n6.2,2.8,4.8,1.8,virginica\n6.1,3.0,4.9,1.8,virginica\n6.4,2.8,5.6,2.1,virginica\n7.2,3.0,5.8,1.6,virginica\n7.4,2.8,6.1,1.9,virginica\n7.9,3.8,6.4,2.0,virginica\n6.4,2.8,5.6,2.2,virginica\n6.3,2.8,5.1,1.5,virginica\n6.1,2.6,5.6,1.4,virginica\n7.7,3.0,6.1,2.3,virginica\n6.3,3.4,5.6,2.4,virginica\n6.4,3.1,5.5,1.8,virginica\n6.0,3.0,4.8,1.8,virginica\n6.9,3.1,5.4,2.1,virginica\n6.7,3.1,5.6,2.4,virginica\n6.9,3.1,5.1,2.3,virginica\n5.8,2.7,5.1,1.9,virginica\n6.8,3.2,5.9,2.3,virginica\n6.7,3.3,5.7,2.5,virginica\n6.7,3.0,5.2,2.3,virginica\n6.3,2.5,5.0,1.9,virginica\n6.5,3.0,5.2,2.0,virginica\n6.2,3.4,5.4,2.3,virginica\n5.9,3.0,5.1,1.8,virginica\n","format":{"type":"csv"}}});</script></div>

### Grouped datasets
Grouped datasets are handled automatically with a table view.

<div class="sourceClojure">
```clojure
(-> datasets/iris
    (tc/group-by [:species])
    (vis/hanami-plot vht/rule-chart
                     {:X :sepal-width
                      :Y :sepal-length
                      :X2 :petal-width
                      :Y2 :petal-length
                      :OPACITY 0.2
                      :SIZE 3}))
```
</div>

<table class="table"><thead><tr><th>species</th><th>plot-0</th></tr></thead><tbody><tr><td><div><p>setosa</p></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"sepal-length","type":"quantitative"},"size":{"value":3},"opacity":{"value":0.2},"x":{"field":"sepal-width","type":"quantitative"},"y2":{"field":"petal-length","type":"quantitative"},"x2":{"field":"petal-width","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","height":300,"data":{"values":"sepal-length,sepal-width,petal-length,petal-width,species\n5.1,3.5,1.4,0.2,setosa\n4.9,3.0,1.4,0.2,setosa\n4.7,3.2,1.3,0.2,setosa\n4.6,3.1,1.5,0.2,setosa\n5.0,3.6,1.4,0.2,setosa\n5.4,3.9,1.7,0.4,setosa\n4.6,3.4,1.4,0.3,setosa\n5.0,3.4,1.5,0.2,setosa\n4.4,2.9,1.4,0.2,setosa\n4.9,3.1,1.5,0.1,setosa\n5.4,3.7,1.5,0.2,setosa\n4.8,3.4,1.6,0.2,setosa\n4.8,3.0,1.4,0.1,setosa\n4.3,3.0,1.1,0.1,setosa\n5.8,4.0,1.2,0.2,setosa\n5.7,4.4,1.5,0.4,setosa\n5.4,3.9,1.3,0.4,setosa\n5.1,3.5,1.4,0.3,setosa\n5.7,3.8,1.7,0.3,setosa\n5.1,3.8,1.5,0.3,setosa\n5.4,3.4,1.7,0.2,setosa\n5.1,3.7,1.5,0.4,setosa\n4.6,3.6,1.0,0.2,setosa\n5.1,3.3,1.7,0.5,setosa\n4.8,3.4,1.9,0.2,setosa\n5.0,3.0,1.6,0.2,setosa\n5.0,3.4,1.6,0.4,setosa\n5.2,3.5,1.5,0.2,setosa\n5.2,3.4,1.4,0.2,setosa\n4.7,3.2,1.6,0.2,setosa\n4.8,3.1,1.6,0.2,setosa\n5.4,3.4,1.5,0.4,setosa\n5.2,4.1,1.5,0.1,setosa\n5.5,4.2,1.4,0.2,setosa\n4.9,3.1,1.5,0.2,setosa\n5.0,3.2,1.2,0.2,setosa\n5.5,3.5,1.3,0.2,setosa\n4.9,3.6,1.4,0.1,setosa\n4.4,3.0,1.3,0.2,setosa\n5.1,3.4,1.5,0.2,setosa\n5.0,3.5,1.3,0.3,setosa\n4.5,2.3,1.3,0.3,setosa\n4.4,3.2,1.3,0.2,setosa\n5.0,3.5,1.6,0.6,setosa\n5.1,3.8,1.9,0.4,setosa\n4.8,3.0,1.4,0.3,setosa\n5.1,3.8,1.6,0.2,setosa\n4.6,3.2,1.4,0.2,setosa\n5.3,3.7,1.5,0.2,setosa\n5.0,3.3,1.4,0.2,setosa\n","format":{"type":"csv"}}});</script></div></td></tr><tr><td><div><p>versicolor</p></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"sepal-length","type":"quantitative"},"size":{"value":3},"opacity":{"value":0.2},"x":{"field":"sepal-width","type":"quantitative"},"y2":{"field":"petal-length","type":"quantitative"},"x2":{"field":"petal-width","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","height":300,"data":{"values":"sepal-length,sepal-width,petal-length,petal-width,species\n7.0,3.2,4.7,1.4,versicolor\n6.4,3.2,4.5,1.5,versicolor\n6.9,3.1,4.9,1.5,versicolor\n5.5,2.3,4.0,1.3,versicolor\n6.5,2.8,4.6,1.5,versicolor\n5.7,2.8,4.5,1.3,versicolor\n6.3,3.3,4.7,1.6,versicolor\n4.9,2.4,3.3,1.0,versicolor\n6.6,2.9,4.6,1.3,versicolor\n5.2,2.7,3.9,1.4,versicolor\n5.0,2.0,3.5,1.0,versicolor\n5.9,3.0,4.2,1.5,versicolor\n6.0,2.2,4.0,1.0,versicolor\n6.1,2.9,4.7,1.4,versicolor\n5.6,2.9,3.6,1.3,versicolor\n6.7,3.1,4.4,1.4,versicolor\n5.6,3.0,4.5,1.5,versicolor\n5.8,2.7,4.1,1.0,versicolor\n6.2,2.2,4.5,1.5,versicolor\n5.6,2.5,3.9,1.1,versicolor\n5.9,3.2,4.8,1.8,versicolor\n6.1,2.8,4.0,1.3,versicolor\n6.3,2.5,4.9,1.5,versicolor\n6.1,2.8,4.7,1.2,versicolor\n6.4,2.9,4.3,1.3,versicolor\n6.6,3.0,4.4,1.4,versicolor\n6.8,2.8,4.8,1.4,versicolor\n6.7,3.0,5.0,1.7,versicolor\n6.0,2.9,4.5,1.5,versicolor\n5.7,2.6,3.5,1.0,versicolor\n5.5,2.4,3.8,1.1,versicolor\n5.5,2.4,3.7,1.0,versicolor\n5.8,2.7,3.9,1.2,versicolor\n6.0,2.7,5.1,1.6,versicolor\n5.4,3.0,4.5,1.5,versicolor\n6.0,3.4,4.5,1.6,versicolor\n6.7,3.1,4.7,1.5,versicolor\n6.3,2.3,4.4,1.3,versicolor\n5.6,3.0,4.1,1.3,versicolor\n5.5,2.5,4.0,1.3,versicolor\n5.5,2.6,4.4,1.2,versicolor\n6.1,3.0,4.6,1.4,versicolor\n5.8,2.6,4.0,1.2,versicolor\n5.0,2.3,3.3,1.0,versicolor\n5.6,2.7,4.2,1.3,versicolor\n5.7,3.0,4.2,1.2,versicolor\n5.7,2.9,4.2,1.3,versicolor\n6.2,2.9,4.3,1.3,versicolor\n5.1,2.5,3.0,1.1,versicolor\n5.7,2.8,4.1,1.3,versicolor\n","format":{"type":"csv"}}});</script></div></td></tr><tr><td><div><p>virginica</p></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"sepal-length","type":"quantitative"},"size":{"value":3},"opacity":{"value":0.2},"x":{"field":"sepal-width","type":"quantitative"},"y2":{"field":"petal-length","type":"quantitative"},"x2":{"field":"petal-width","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","height":300,"data":{"values":"sepal-length,sepal-width,petal-length,petal-width,species\n6.3,3.3,6.0,2.5,virginica\n5.8,2.7,5.1,1.9,virginica\n7.1,3.0,5.9,2.1,virginica\n6.3,2.9,5.6,1.8,virginica\n6.5,3.0,5.8,2.2,virginica\n7.6,3.0,6.6,2.1,virginica\n4.9,2.5,4.5,1.7,virginica\n7.3,2.9,6.3,1.8,virginica\n6.7,2.5,5.8,1.8,virginica\n7.2,3.6,6.1,2.5,virginica\n6.5,3.2,5.1,2.0,virginica\n6.4,2.7,5.3,1.9,virginica\n6.8,3.0,5.5,2.1,virginica\n5.7,2.5,5.0,2.0,virginica\n5.8,2.8,5.1,2.4,virginica\n6.4,3.2,5.3,2.3,virginica\n6.5,3.0,5.5,1.8,virginica\n7.7,3.8,6.7,2.2,virginica\n7.7,2.6,6.9,2.3,virginica\n6.0,2.2,5.0,1.5,virginica\n6.9,3.2,5.7,2.3,virginica\n5.6,2.8,4.9,2.0,virginica\n7.7,2.8,6.7,2.0,virginica\n6.3,2.7,4.9,1.8,virginica\n6.7,3.3,5.7,2.1,virginica\n7.2,3.2,6.0,1.8,virginica\n6.2,2.8,4.8,1.8,virginica\n6.1,3.0,4.9,1.8,virginica\n6.4,2.8,5.6,2.1,virginica\n7.2,3.0,5.8,1.6,virginica\n7.4,2.8,6.1,1.9,virginica\n7.9,3.8,6.4,2.0,virginica\n6.4,2.8,5.6,2.2,virginica\n6.3,2.8,5.1,1.5,virginica\n6.1,2.6,5.6,1.4,virginica\n7.7,3.0,6.1,2.3,virginica\n6.3,3.4,5.6,2.4,virginica\n6.4,3.1,5.5,1.8,virginica\n6.0,3.0,4.8,1.8,virginica\n6.9,3.1,5.4,2.1,virginica\n6.7,3.1,5.6,2.4,virginica\n6.9,3.1,5.1,2.3,virginica\n5.8,2.7,5.1,1.9,virginica\n6.8,3.2,5.9,2.3,virginica\n6.7,3.3,5.7,2.5,virginica\n6.7,3.0,5.2,2.3,virginica\n6.3,2.5,5.0,1.9,virginica\n6.5,3.0,5.2,2.0,virginica\n6.2,3.4,5.4,2.3,virginica\n5.9,3.0,5.1,1.8,virginica\n","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>

### Additional Hanami templates
The `scicloj.noj.v1.vis.hanami.templates` namespace add Hanami templates to Hanami's own collection.

<div class="sourceClojure">
```clojure
(-> datasets/mtcars
    (vis/hanami-plot vht/boxplot-chart
                     {:X :gear
                      :XTYPE :nominal
                      :Y :mpg}))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"mpg","type":"quantitative"},"x":{"field":"gear","type":"nominal"}},"mark":{"type":"boxplot","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"values":"name,mpg,cyl,disp,hp,drat,wt,qsec,vs,am,gear,carb\nMazda RX4,21.0,6,160.0,110,3.9,2.62,16.46,0,1,4,4\nMazda RX4 Wag,21.0,6,160.0,110,3.9,2.875,17.02,0,1,4,4\nDatsun 710,22.8,4,108.0,93,3.85,2.32,18.61,1,1,4,1\nHornet 4 Drive,21.4,6,258.0,110,3.08,3.215,19.44,1,0,3,1\nHornet Sportabout,18.7,8,360.0,175,3.15,3.44,17.02,0,0,3,2\nValiant,18.1,6,225.0,105,2.76,3.46,20.22,1,0,3,1\nDuster 360,14.3,8,360.0,245,3.21,3.57,15.84,0,0,3,4\nMerc 240D,24.4,4,146.7,62,3.69,3.19,20.0,1,0,4,2\nMerc 230,22.8,4,140.8,95,3.92,3.15,22.9,1,0,4,2\nMerc 280,19.2,6,167.6,123,3.92,3.44,18.3,1,0,4,4\nMerc 280C,17.8,6,167.6,123,3.92,3.44,18.9,1,0,4,4\nMerc 450SE,16.4,8,275.8,180,3.07,4.07,17.4,0,0,3,3\nMerc 450SL,17.3,8,275.8,180,3.07,3.73,17.6,0,0,3,3\nMerc 450SLC,15.2,8,275.8,180,3.07,3.78,18.0,0,0,3,3\nCadillac Fleetwood,10.4,8,472.0,205,2.93,5.25,17.98,0,0,3,4\nLincoln Continental,10.4,8,460.0,215,3.0,5.424,17.82,0,0,3,4\nChrysler Imperial,14.7,8,440.0,230,3.23,5.345,17.42,0,0,3,4\nFiat 128,32.4,4,78.7,66,4.08,2.2,19.47,1,1,4,1\nHonda Civic,30.4,4,75.7,52,4.93,1.615,18.52,1,1,4,2\nToyota Corolla,33.9,4,71.1,65,4.22,1.835,19.9,1,1,4,1\nToyota Corona,21.5,4,120.1,97,3.7,2.465,20.01,1,0,3,1\nDodge Challenger,15.5,8,318.0,150,2.76,3.52,16.87,0,0,3,2\nAMC Javelin,15.2,8,304.0,150,3.15,3.435,17.3,0,0,3,2\nCamaro Z28,13.3,8,350.0,245,3.73,3.84,15.41,0,0,3,4\nPontiac Firebird,19.2,8,400.0,175,3.08,3.845,17.05,0,0,3,2\nFiat X1-9,27.3,4,79.0,66,4.08,1.935,18.9,1,1,4,1\nPorsche 914-2,26.0,4,120.3,91,4.43,2.14,16.7,0,1,5,2\nLotus Europa,30.4,4,95.1,113,3.77,1.513,16.9,1,1,5,2\nFord Pantera L,15.8,8,351.0,264,4.22,3.17,14.5,0,1,5,4\nFerrari Dino,19.7,6,145.0,175,3.62,2.77,15.5,0,1,5,6\nMaserati Bora,15.0,8,301.0,335,3.54,3.57,14.6,0,1,5,8\nVolvo 142E,21.4,4,121.0,109,4.11,2.78,18.6,1,1,4,2\n","format":{"type":"csv"}}});</script></div>

### Layers

<div class="sourceClojure">
```clojure
(-> random-walk
    (vis/hanami-layers
     {:TITLE "points and a line"}
     [(vis/hanami-plot nil
                       ht/point-chart
                       {:MSIZE 400})
      (vis/hanami-plot nil
                       ht/line-chart
                       {:MSIZE 4
                        :MCOLOR "brown"})]))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"points and a line"},"layer":[{"encoding":{"y":{"field":"y","type":"quantitative"},"x":{"field":"x","type":"quantitative"}},"mark":{"type":"circle","size":400,"tooltip":true},"width":400,"background":"floralwhite","height":300},{"encoding":{"y":{"field":"y","type":"quantitative"},"x":{"field":"x","type":"quantitative"}},"mark":{"type":"line","size":4,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300,"data":{"values":"x,y\n0,-0.10891746407198855\n1,-0.17746785165549706\n2,0.010481929682169322\n3,-0.30373971592778526\n4,-0.47604808081984973\n5,-0.892613043086356\n6,-1.1415894660576191\n7,-1.3022333469107266\n8,-1.648762135975216\n9,-1.3201114922367414\n10,-1.7176056054413757\n11,-1.3492575022010356\n12,-0.8540467998730537\n13,-0.9979245662928977\n14,-1.0470624845665784\n15,-0.7440189393874057\n16,-0.3609645768215545\n17,-0.6690171277438733\n18,-0.2370752883476035\n19,-0.3441999031150036\n","format":{"type":"csv"}}});</script></div>

### Concatenation

<div class="sourceClojure">
```clojure
(-> random-walk
    (vis/hanami-vconcat
     {}
     [(vis/hanami-plot nil
                       ht/point-chart
                       {:MSIZE 400
                        :HEIGHT 100
                        :WIDTH 100})
      (vis/hanami-plot nil
                       ht/line-chart
                       {:MSIZE 4
                        :MCOLOR "brown"
                        :HEIGHT 100
                        :WIDTH 100})]))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","vconcat":[{"encoding":{"y":{"field":"y","type":"quantitative"},"x":{"field":"x","type":"quantitative"}},"mark":{"type":"circle","size":400,"tooltip":true},"width":100,"background":"floralwhite","height":100},{"encoding":{"y":{"field":"y","type":"quantitative"},"x":{"field":"x","type":"quantitative"}},"mark":{"type":"line","size":4,"color":"brown","tooltip":true},"width":100,"background":"floralwhite","height":100}],"height":300,"data":{"values":"x,y\n0,-0.10891746407198855\n1,-0.17746785165549706\n2,0.010481929682169322\n3,-0.30373971592778526\n4,-0.47604808081984973\n5,-0.892613043086356\n6,-1.1415894660576191\n7,-1.3022333469107266\n8,-1.648762135975216\n9,-1.3201114922367414\n10,-1.7176056054413757\n11,-1.3492575022010356\n12,-0.8540467998730537\n13,-0.9979245662928977\n14,-1.0470624845665784\n15,-0.7440189393874057\n16,-0.3609645768215545\n17,-0.6690171277438733\n18,-0.2370752883476035\n19,-0.3441999031150036\n","format":{"type":"csv"}}});</script></div>

<div class="sourceClojure">
```clojure
(-> random-walk
    (vis/hanami-hconcat
     {}
     [(vis/hanami-plot nil
                       ht/point-chart
                       {:MSIZE 400
                        :HEIGHT 100
                        :WIDTH 100})
      (vis/hanami-plot nil
                       ht/line-chart
                       {:MSIZE 4
                        :MCOLOR "brown"
                        :HEIGHT 100
                        :WIDTH 100})]))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"hconcat":[{"encoding":{"y":{"field":"y","type":"quantitative"},"x":{"field":"x","type":"quantitative"}},"mark":{"type":"circle","size":400,"tooltip":true},"width":100,"background":"floralwhite","height":100},{"encoding":{"y":{"field":"y","type":"quantitative"},"x":{"field":"x","type":"quantitative"}},"mark":{"type":"line","size":4,"color":"brown","tooltip":true},"width":100,"background":"floralwhite","height":100}],"width":400,"background":"floralwhite","height":300,"data":{"values":"x,y\n0,-0.10891746407198855\n1,-0.17746785165549706\n2,0.010481929682169322\n3,-0.30373971592778526\n4,-0.47604808081984973\n5,-0.892613043086356\n6,-1.1415894660576191\n7,-1.3022333469107266\n8,-1.648762135975216\n9,-1.3201114922367414\n10,-1.7176056054413757\n11,-1.3492575022010356\n12,-0.8540467998730537\n13,-0.9979245662928977\n14,-1.0470624845665784\n15,-0.7440189393874057\n16,-0.3609645768215545\n17,-0.6690171277438733\n18,-0.2370752883476035\n19,-0.3441999031150036\n","format":{"type":"csv"}}});</script></div>

### Linear regression

<div class="sourceClojure">
```clojure
(-> datasets/mtcars
    (stats/add-predictions :mpg [:wt]
                           {:model-type :smile.regression/ordinary-least-square})
    (vis/hanami-layers {}
                       [(vis/hanami-plot nil
                                         ht/point-chart
                                         {:X :wt
                                          :Y :mpg
                                          :MSIZE 200
                                          :HEIGHT 200
                                          :WIDTH 200})
                        (vis/hanami-plot nil
                                         ht/line-chart
                                         {:X :wt
                                          :Y :mpg-prediction
                                          :MSIZE 5
                                          :MCOLOR "purple"
                                          :YTITLE :mpg})]))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","layer":[{"encoding":{"y":{"field":"mpg","type":"quantitative"},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"circle","size":200,"tooltip":true},"width":200,"background":"floralwhite","height":200},{"encoding":{"y":{"field":"mpg-prediction","type":"quantitative","axis":{"title":"mpg"}},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"line","size":5,"color":"purple","tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300,"data":{"values":"name,mpg,cyl,disp,hp,drat,wt,qsec,vs,am,gear,carb,mpg-prediction\nMazda RX4,21.0,6,160.0,110,3.9,2.62,16.46,0,1,4,4,23.28261064680863\nMazda RX4 Wag,21.0,6,160.0,110,3.9,2.875,17.02,0,1,4,4,21.91977039576435\nDatsun 710,22.8,4,108.0,93,3.85,2.32,18.61,1,1,4,1,24.885952118625436\nHornet 4 Drive,21.4,6,258.0,110,3.08,3.215,19.44,1,0,3,1,20.102650061038638\nHornet Sportabout,18.7,8,360.0,175,3.15,3.44,17.02,0,0,3,2,18.900143957176034\nValiant,18.1,6,225.0,105,2.76,3.46,20.22,1,0,3,1,18.793254525721583\nDuster 360,14.3,8,360.0,245,3.21,3.57,15.84,0,0,3,4,18.205362652722087\nMerc 240D,24.4,4,146.7,62,3.69,3.19,20.0,1,0,4,2,20.236261850356705\nMerc 230,22.8,4,140.8,95,3.92,3.15,22.9,1,0,4,2,20.45004071326561\nMerc 280,19.2,6,167.6,123,3.92,3.44,18.3,1,0,4,4,18.900143957176034\nMerc 280C,17.8,6,167.6,123,3.92,3.44,18.9,1,0,4,4,18.900143957176034\nMerc 450SE,16.4,8,275.8,180,3.07,4.07,17.4,0,0,3,3,15.533126866360746\nMerc 450SL,17.3,8,275.8,180,3.07,3.73,17.6,0,0,3,3,17.350247201086457\nMerc 450SLC,15.2,8,275.8,180,3.07,3.78,18.0,0,0,3,3,17.083023622450327\nCadillac Fleetwood,10.4,8,472.0,205,2.93,5.25,17.98,0,0,3,4,9.226650410547986\nLincoln Continental,10.4,8,460.0,215,3.0,5.424,17.82,0,0,3,4,8.29671235689424\nChrysler Imperial,14.7,8,440.0,230,3.23,5.345,17.42,0,0,3,4,8.718925611139333\nFiat 128,32.4,4,78.7,66,4.08,2.2,19.47,1,1,4,1,25.527288707352156\nHonda Civic,30.4,4,75.7,52,4.93,1.615,18.52,1,1,4,2,28.653804577394922\nToyota Corolla,33.9,4,71.1,65,4.22,1.835,19.9,1,1,4,1,27.478020831395934\nToyota Corona,21.5,4,120.1,97,3.7,2.465,20.01,1,0,3,1,24.11100374058065\nDodge Challenger,15.5,8,318.0,150,2.76,3.52,16.87,0,0,3,2,18.47258623135822\nAMC Javelin,15.2,8,304.0,150,3.15,3.435,17.3,0,0,3,2,18.92686631503965\nCamaro Z28,13.3,8,350.0,245,3.73,3.84,15.41,0,0,3,4,16.762355328086965\nPontiac Firebird,19.2,8,400.0,175,3.08,3.845,17.05,0,0,3,2,16.73563297022335\nFiat X1-9,27.3,4,79.0,66,4.08,1.935,18.9,1,1,4,1,26.943573674123666\nPorsche 914-2,26.0,4,120.3,91,4.43,2.14,16.7,0,1,5,2,25.847957001715518\nLotus Europa,30.4,4,95.1,113,3.77,1.513,16.9,1,1,5,2,29.198940677812637\nFord Pantera L,15.8,8,351.0,264,4.22,3.17,14.5,0,1,5,4,20.34315128181116\nFerrari Dino,19.7,6,145.0,175,3.62,2.77,15.5,0,1,5,6,22.48093991090023\nMaserati Bora,15.0,8,301.0,335,3.54,3.57,14.6,0,1,5,8,18.205362652722087\nVolvo 142E,21.4,4,121.0,109,4.11,2.78,18.6,1,1,4,2,22.427495195173\n","format":{"type":"csv"}}});</script></div>

### Histogram

<div class="sourceClojure">
```clojure
(-> datasets/iris
    (vis/hanami-histogram :sepal-width
                          {:nbins 10}))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"count","type":"quantitative"},"x":{"scale":{"zero":false},"field":"left","type":"quantitative"},"y2":{"field":0,"type":"quantitative"},"x2":{"scale":{"zero":false},"field":"right","type":"quantitative"}},"mark":"rect","width":400,"background":"floralwhite","height":300,"data":{"values":"count,left,right\n4,2.0,2.24\n7,2.24,2.48\n22,2.48,2.72\n24,2.72,2.96\n37,2.96,3.2\n31,3.2,3.4400000000000004\n10,3.4400000000000004,3.6800000000000006\n11,3.6800000000000006,3.9200000000000004\n2,3.9200000000000004,4.16\n2,4.16,4.4\n","format":{"type":"csv"}}});</script></div>

### Combining a few things together

The following is inspired by the example at Plotnine's [main page](https://plotnine.readthedocs.io/en/stable/).
Note how we add regression lines here. We take care of layout and colouring on our side, not using Vega-Lite for that.

<div class="sourceClojure">
```clojure
(let [pallete (->> :accent
                   color/palette
                   (mapv color/format-hex))]
  (-> datasets/mtcars
      (tc/group-by :gear {:result-type :as-map})
      (->> (sort-by key)
           (map-indexed
            (fn [i [group-name ds]]
              (-> ds
                  (stats/add-predictions :mpg [:wt]
                                         {:model-type :smile.regression/ordinary-least-square})
                  (tc/select-columns [:gear :wt :mpg :mpg-prediction])
                  (vis/hanami-layers {:TITLE (str "grear=" group-name)}
                                     [(vis/hanami-plot nil
                                                       ht/point-chart
                                                       {:X :wt
                                                        :Y :mpg
                                                        :MSIZE 200
                                                        :MCOLOR (pallete i)
                                                        :HEIGHT 200
                                                        :WIDTH 200})
                                      (vis/hanami-plot nil
                                                       ht/line-chart
                                                       {:X :wt
                                                        :Y :mpg-prediction
                                                        :MSIZE 5
                                                        :MCOLOR (pallete i)
                                                        :YTITLE :mpg})]
                                     ))))
           (vis/hanami-vconcat nil {}))))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","vconcat":[{"width":400,"background":"floralwhite","title":{"text":"grear=3"},"layer":[{"encoding":{"y":{"field":"mpg","type":"quantitative"},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"circle","size":200,"color":"#7fc97f","tooltip":true},"width":200,"background":"floralwhite","height":200},{"encoding":{"y":{"field":"mpg-prediction","type":"quantitative","axis":{"title":"mpg"}},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"line","size":5,"color":"#7fc97f","tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300,"data":{"values":"gear,wt,mpg,mpg-prediction\n3,3.215,21.4,18.24575076879608\n3,3.44,18.7,17.535458674671055\n3,3.46,18.1,17.472321599637716\n3,3.57,14.3,17.125067686954374\n3,4.07,16.4,15.546640811120986\n3,3.73,17.3,16.61997108668769\n3,3.78,15.2,16.46212839910435\n3,5.25,10.4,11.821553384154196\n3,5.424,10.4,11.272260831364175\n3,5.345,14.7,11.521652277745854\n3,2.465,21.5,20.613391082546155\n3,3.52,15.5,17.282910374537714\n3,3.435,15.2,17.551242943429386\n3,3.84,13.3,16.272717174004345\n3,3.845,19.2,16.25693290524601\n","format":{"type":"csv"}}},{"width":400,"background":"floralwhite","title":{"text":"grear=4"},"layer":[{"encoding":{"y":{"field":"mpg","type":"quantitative"},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"circle","size":200,"color":"#beaed4","tooltip":true},"width":200,"background":"floralwhite","height":200},{"encoding":{"y":{"field":"mpg-prediction","type":"quantitative","axis":{"title":"mpg"}},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"line","size":5,"color":"#beaed4","tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300,"data":{"values":"gear,wt,mpg,mpg-prediction\n4,2.62,21.0,24.510455071959058\n4,2.875,21.0,22.76026807682699\n4,2.32,22.8,26.569498595643847\n4,3.19,24.4,20.59827237695796\n4,3.15,22.8,20.872811513449268\n4,3.44,19.2,18.882402773887303\n4,3.44,17.8,18.882402773887303\n4,2.2,32.4,27.39311600511776\n4,1.615,30.4,31.4082508763031\n4,1.835,33.9,29.89828562560092\n4,1.935,27.3,29.211937784372658\n4,2.78,21.4,23.41229852599384\n","format":{"type":"csv"}}},{"width":400,"background":"floralwhite","title":{"text":"grear=5"},"layer":[{"encoding":{"y":{"field":"mpg","type":"quantitative"},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"circle","size":200,"color":"#fdc086","tooltip":true},"width":200,"background":"floralwhite","height":200},{"encoding":{"y":{"field":"mpg-prediction","type":"quantitative","axis":{"title":"mpg"}},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"line","size":5,"color":"#fdc086","tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300,"data":{"values":"gear,wt,mpg,mpg-prediction\n5,2.14,26.0,25.34362502587085\n5,1.513,30.4,30.38867758620586\n5,3.17,15.8,17.055899129307758\n5,2.77,19.7,20.274433458070124\n5,3.57,15.0,13.83736480054539\n","format":{"type":"csv"}}}],"height":300});</script></div>

A similar example with histograms:

<div class="sourceClojure">
```clojure
(let [pallete (->> :accent
                   color/palette
                   (mapv color/format-hex))]
  (-> datasets/iris
      (tc/group-by :species {:result-type :as-map})
      (->> (sort-by key)
           (map-indexed
            (fn [i [group-name ds]]
              (-> ds
                  (vis/hanami-histogram :sepal-width
                                        {:nbins 10}))))
           (vis/hanami-vconcat nil {}))))
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","vconcat":[{"encoding":{"y":{"field":"count","type":"quantitative"},"x":{"scale":{"zero":false},"field":"left","type":"quantitative"},"y2":{"field":0,"type":"quantitative"},"x2":{"scale":{"zero":false},"field":"right","type":"quantitative"}},"mark":"rect","width":400,"background":"floralwhite","height":300,"data":{"values":"count,left,right\n1,2.3,2.51\n0,2.51,2.7199999999999998\n1,2.7199999999999998,2.9299999999999997\n10,2.9299999999999997,3.14\n7,3.14,3.35\n15,3.35,3.56\n6,3.56,3.7700000000000005\n6,3.7700000000000005,3.9800000000000004\n2,3.9800000000000004,4.19\n2,4.19,4.4\n","format":{"type":"csv"}}},{"encoding":{"y":{"field":"count","type":"quantitative"},"x":{"scale":{"zero":false},"field":"left","type":"quantitative"},"y2":{"field":0,"type":"quantitative"},"x2":{"scale":{"zero":false},"field":"right","type":"quantitative"}},"mark":"rect","width":400,"background":"floralwhite","height":300,"data":{"values":"count,left,right\n1,2.0,2.14\n2,2.14,2.28\n6,2.28,2.42\n4,2.42,2.56\n3,2.56,2.7\n11,2.7,2.84\n7,2.84,2.98\n11,2.98,3.12\n3,3.12,3.26\n2,3.26,3.4\n","format":{"type":"csv"}}},{"encoding":{"y":{"field":"count","type":"quantitative"},"x":{"scale":{"zero":false},"field":"left","type":"quantitative"},"y2":{"field":0,"type":"quantitative"},"x2":{"scale":{"zero":false},"field":"right","type":"quantitative"}},"mark":"rect","width":400,"background":"floralwhite","height":300,"data":{"values":"count,left,right\n1,2.2,2.3600000000000003\n4,2.3600000000000003,2.52\n2,2.52,2.68\n12,2.68,2.84\n2,2.84,3.0\n16,3.0,3.16\n8,3.16,3.3200000000000003\n2,3.3200000000000003,3.48\n1,3.48,3.6399999999999997\n2,3.6399999999999997,3.8\n","format":{"type":"csv"}}}],"height":300});</script></div>

Scatterplots and regression lines again, this time using Vega-Lite for layout and coloring (using its "facet" option).

<div class="sourceClojure">
```clojure
(-> datasets/mtcars
    (tc/group-by [:gear])
    (stats/add-predictions :mpg [:wt]
                           {:model-type :smile.regression/ordinary-least-square})
    (tc/ungroup)
    (tc/select-columns [:gear :wt :mpg :mpg-prediction])
    (vis/hanami-layers {}
                       [(vis/hanami-plot nil
                                         ht/point-chart
                                         {:X :wt
                                          :Y :mpg
                                          :MSIZE 200
                                          :COLOR "gear"
                                          :HEIGHT 100
                                          :WIDTH 200})
                        (vis/hanami-plot nil
                                         ht/line-chart
                                         {:X :wt
                                          :Y :mpg-prediction
                                          :MSIZE 5
                                          :COLOR "gear"
                                          :YTITLE :mpg})])
    ((fn [spec]
       {:facet {:row {:field "gear"}}
        :spec (dissoc spec :data)
        :data (:data spec)}))
    kind/vega-lite)
```
</div>

<div><script>vegaEmbed(document.currentScript.parentElement, {"facet":{"row":{"field":"gear"}},"spec":{"width":400,"background":"floralwhite","layer":[{"encoding":{"y":{"field":"mpg","type":"quantitative"},"color":{"field":"gear","type":"nominal"},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"circle","size":200,"tooltip":true},"width":200,"background":"floralwhite","height":100},{"encoding":{"y":{"field":"mpg-prediction","type":"quantitative","axis":{"title":"mpg"}},"color":{"field":"gear","type":"nominal"},"x":{"field":"wt","type":"quantitative"}},"mark":{"type":"line","size":5,"tooltip":true},"width":400,"background":"floralwhite","height":300}],"height":300},"data":{"values":"gear,wt,mpg,mpg-prediction\n4,2.62,21.0,24.510455071959058\n4,2.875,21.0,22.76026807682699\n4,2.32,22.8,26.569498595643847\n4,3.19,24.4,20.59827237695796\n4,3.15,22.8,20.872811513449268\n4,3.44,19.2,18.882402773887303\n4,3.44,17.8,18.882402773887303\n4,2.2,32.4,27.39311600511776\n4,1.615,30.4,31.4082508763031\n4,1.835,33.9,29.89828562560092\n4,1.935,27.3,29.211937784372658\n4,2.78,21.4,23.41229852599384\n3,3.215,21.4,18.24575076879608\n3,3.44,18.7,17.535458674671055\n3,3.46,18.1,17.472321599637716\n3,3.57,14.3,17.125067686954374\n3,4.07,16.4,15.546640811120986\n3,3.73,17.3,16.61997108668769\n3,3.78,15.2,16.46212839910435\n3,5.25,10.4,11.821553384154196\n3,5.424,10.4,11.272260831364175\n3,5.345,14.7,11.521652277745854\n3,2.465,21.5,20.613391082546155\n3,3.52,15.5,17.282910374537714\n3,3.435,15.2,17.551242943429386\n3,3.84,13.3,16.272717174004345\n3,3.845,19.2,16.25693290524601\n5,2.14,26.0,25.34362502587085\n5,1.513,30.4,30.38867758620586\n5,3.17,15.8,17.055899129307758\n5,2.77,19.7,20.274433458070124\n5,3.57,15.0,13.83736480054539\n","format":{"type":"csv"}}});</script></div>

<div class="sourceClojure">
```clojure
:bye
```
</div>

<div class="printedClojure">
```clojure
:bye

```
</div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/london-clojurians-talk/notebooks/visualization.clj">notebooks/visualization.clj</a></small></small></pre></div>

### 2023-12-22 docs/projects/visual-tools/clay-calva-demo-20231216/scratch.qmd
moved docs for github pages

--- 2023-12-21 projects/visual-tools/clay-calva-demo-20231216/docs/scratch-revealjs.qmd
@@
 format:
-  revealjs: {theme: solarized, navigation-mode: vertical, transition: slide, background-transition: fade, incremental: true, output-file: scratch-revealjs.html}
+  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scratch.html}
 highlight-style: solarized
@@
 </style>
-<script src="scratch-revealjs_files/md-default1.js" type="text/javascript"></script><script src="scratch-revealjs_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega3.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega4.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
+<script src="scratch_files/md-default1.js" type="text/javascript"></script><script src="scratch_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="scratch_files/vega3.js" type="text/javascript"></script><script src="scratch_files/vega4.js" type="text/javascript"></script><script src="scratch_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
 
@@
 
-<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"scratch-revealjs_files\/0.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"scratch_files\/0.csv","format":{"type":"csv"}}});</script></div>
 

### 2023-12-22 docs/projects/visual-tools/clay-cider-demo-20231217/scratch-revealjs.qmd
moved docs for github pages

--- 2023-12-21 projects/visual-tools/clay-cider-demo-20231217/docs/scratch.qmd
@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scratch.html}
+  revealjs: {theme: solarized, navigation-mode: vertical, transition: slide, background-transition: fade, incremental: true, output-file: scratch-revealjs.html}
 highlight-style: solarized
@@
 </style>
-<script src="scratch_files/md-default13.js" type="text/javascript"></script><script src="scratch_files/md-default14.js" type="text/javascript"></script>
+<script src="scratch-revealjs_files/md-default13.js" type="text/javascript"></script><script src="scratch-revealjs_files/md-default14.js" type="text/javascript"></script>
 
@@
 
-<img src="scratch_files/0.png" style="width:100%;" />
+<img src="scratch-revealjs_files/0.png" style="width:100%;" />
 
@@
 
-<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="scratch_files/0.png" style="width:100%;" /><img src="scratch_files/1.png" style="width:100%;" /></div><p>\]</p></div>
+<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="scratch-revealjs_files/0.png" style="width:100%;" /><img src="scratch-revealjs_files/1.png" style="width:100%;" /></div><p>\]</p></div>
 
@@
 
-<div><h3>raw image</h3><img src="scratch_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="scratch_files/2.png" style="width:100%;" /></div>
+<div><h3>raw image</h3><img src="scratch-revealjs_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="scratch-revealjs_files/2.png" style="width:100%;" /></div>
 
@@
 
-<img src="scratch_files/3.png" style="width:100%;" />
+<img src="scratch-revealjs_files/3.png" style="width:100%;" />
 
@@
 
-<img src="scratch_files/4.png" style="width:100%;" />
+<img src="scratch-revealjs_files/4.png" style="width:100%;" />
 
@@
 
-<img src="scratch_files/5.png" style="width:100%;" />
+<img src="scratch-revealjs_files/5.png" style="width:100%;" />
 
@@
 <div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.7
-</code></pre></div><img src="scratch_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
-</code></pre></div><img src="scratch_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
-</code></pre></div><img src="scratch_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
-</code></pre></div><img src="scratch_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
-</code></pre></div><img src="scratch_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
-</code></pre></div><img src="scratch_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
-</code></pre></div><img src="scratch_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>
+</code></pre></div><img src="scratch-revealjs_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
+</code></pre></div><img src="scratch-revealjs_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
+</code></pre></div><img src="scratch-revealjs_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
+</code></pre></div><img src="scratch-revealjs_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
+</code></pre></div><img src="scratch-revealjs_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
+</code></pre></div><img src="scratch-revealjs_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
+</code></pre></div><img src="scratch-revealjs_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>
 

### 2023-12-22 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
rerendering docs

--- 2023-12-22 docs/projects/visual-tools/clay-calva-demo-20231216/scratch.qmd
@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scratch.html}
+  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
 highlight-style: solarized
@@
 </style>
-<script src="scratch_files/md-default1.js" type="text/javascript"></script><script src="scratch_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="scratch_files/vega3.js" type="text/javascript"></script><script src="scratch_files/vega4.js" type="text/javascript"></script><script src="scratch_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
+<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+
+# Clay & Noj demo: data visualization
 
@@
 ```clojure
-(ns scratch
+(ns index
   (:require [scicloj.noj.v1.datasets
@@
 </div>
-
-# Intro
 
@@
 
-<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"scratch_files\/0.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>
 
@@
 
-<div><pre><small><small>source: projects/visual-tools/clay-calva-demo-20231216/notebooks/scratch.clj</small></small></pre></div>
+<div><pre><small><small>source: projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj</small></small></pre></div>

### 2023-12-22 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
rerendering

--- 2023-12-21 projects/visual-tools/clay-cider-demo-20231217/docs/scratch.qmd
@@
 </style>
-<script src="scratch_files/md-default13.js" type="text/javascript"></script><script src="scratch_files/md-default14.js" type="text/javascript"></script>
+<script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/md-default14.js" type="text/javascript"></script>
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
 
-# Image processing
+# Clay & Noj demo: image processing
 
@@
 ```clojure
-(ns scratch
+(ns index
   (:require [tech.v3.libs.buffered-image :as bufimg]
@@
 
-<img src="scratch_files/0.png" style="width:100%;" />
+<img src="index_files/0.png" style="width:100%;" />
 
@@
 
-<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="scratch_files/0.png" style="width:100%;" /><img src="scratch_files/1.png" style="width:100%;" /></div><p>\]</p></div>
+<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="index_files/0.png" style="width:100%;" /><img src="index_files/1.png" style="width:100%;" /></div><p>\]</p></div>
 
@@
 
-<div><h3>raw image</h3><img src="scratch_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="scratch_files/2.png" style="width:100%;" /></div>
+<div><h3>raw image</h3><img src="index_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="index_files/2.png" style="width:100%;" /></div>
 
@@
 
-<img src="scratch_files/3.png" style="width:100%;" />
+<img src="index_files/3.png" style="width:100%;" />
 
@@
 
-<img src="scratch_files/4.png" style="width:100%;" />
+<img src="index_files/4.png" style="width:100%;" />
 
@@
 
-<img src="scratch_files/5.png" style="width:100%;" />
+<img src="index_files/5.png" style="width:100%;" />
 
@@
 <div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.7
-</code></pre></div><img src="scratch_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
-</code></pre></div><img src="scratch_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
-</code></pre></div><img src="scratch_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
-</code></pre></div><img src="scratch_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
-</code></pre></div><img src="scratch_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
-</code></pre></div><img src="scratch_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
-</code></pre></div><img src="scratch_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>
+</code></pre></div><img src="index_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
+</code></pre></div><img src="index_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
+</code></pre></div><img src="index_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
+</code></pre></div><img src="index_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
+</code></pre></div><img src="index_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
+</code></pre></div><img src="index_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
+</code></pre></div><img src="index_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>
 
@@
 
-<div><pre><small><small>source: projects/visual-tools/clay-cider-demo-20231217/notebooks/scratch.clj</small></small></pre></div>
+<div><pre><small><small>source: projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj</small></small></pre></div>

### 2023-12-22 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
added clay configurations, rerendered

@@
 
-<div><pre><small><small>source: projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj</small></small></pre></div>
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj">projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj</a></small></small></pre></div>

### 2023-12-22 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
added clay configurations, rerendered

@@
 
-<div><pre><small><small>source: projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj</small></small></pre></div>
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj">projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj</a></small></small></pre></div>

### 2023-12-31 docs/projects/data-sources/hdf/scicloj.scrapbook.hdf.qmd
rendered HDF tutorial

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scicloj.scrapbook.hdf.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scicloj.scrapbook.hdf_files/md-default3.js" type="text/javascript"></script><script src="scicloj.scrapbook.hdf_files/md-default4.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

# Reading HDF files
Original discussion at the Clojurians Zulip [chat](https://scicloj.github.io/docs/community/chat/): [#data-science > import hdf files](https://clojurians.zulipchat.com/#narrow/stream/151924-data-science/topic/import.20hdf.20files).

<div class="sourceClojure">
```clojure
(ns scicloj.scrapbook.hdf
  (:require [babashka.fs :as fs]
            [tech.v3.tensor :as tensor]
            [clojure.java.io :as io]
            [clojure.string :as string]
            [scicloj.noj.v1.vis.image :as vis.image]
            [tech.v3.datatype.functional :as fun])
  (:import io.jhdf.HdfFile
           java.io.File))
```
</div>

<div class="sourceClojure">
```clojure
(set! *warn-on-reflection* true)
```
</div>

<div class="printedClojure">
```clojure
true

```
</div>

We will use the followig function
to read an [HDF](https://en.wikipedia.org/wiki/Hierarchical_Data_Format) file
using [jHDF](https://github.com/jamesmudd/jhdf/),
and convert it to [dtype-next](https://github.com/cnuernber/dtype-next) tensors.

<div class="sourceClojure">
```clojure
(defn hdf5->tensors [path]
  (let [file ^File (io/file path)
        hdf-file ^HdfFile (HdfFile. file)
        children ^java.util.Map (.getChildren hdf-file)]
    (->> children
         keys
         (mapv (fn [key]
                 (let [child ^io.jhdf.dataset.ContiguousDatasetImpl (.get children key)
                       knew (keyword (first (string/split key
                                                          #" ")))]
                   {:key key
                    :data (-> child
                              .getData
                              tensor/->tensor)}))))))
```
</div>

Let us apply the function to a test file:

<div class="sourceClojure">
```clojure
(def tensors
  (hdf5->tensors "data/test.h5"))
```
</div>

<div class="sourceClojure">
```clojure
(count tensors)
```
</div>

<div class="printedClojure">
```clojure
20

```
</div>

<div class="sourceClojure">
```clojure
(take 3 tensors)
```
</div>

<div class="printedClojure">
```clojure
({:key "0", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[112 110 111 ... 114 118 124]
 [105 112 106 ... 115 120 119]
 [107 109 108 ... 117 123 115]
 ...
 [132 138 134 ... 109 107 109]
 [130 129 129 ... 115 111 103]
 [134 135 134 ... 110 111 110]]}
 {:key "1", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[124 120 121 ... 117 121 124]
 [118 123 117 ... 118 122 121]
 [120 123 117 ... 119 123 118]
 ...
 [133 139 136 ... 111 106 108]
 [133 132 131 ... 116 111 103]
 [136 137 135 ... 114 111 108]]}
 {:key "10", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[125 120 120 ... 116 121 127]
 [116 122 116 ... 117 121 119]
 [120 121 115 ... 120 123 118]
 ...
 [132 139 133 ... 112 107 108]
 [135 132 132 ... 115 112 104]
 [134 135 135 ... 114 112 108]]})

```
</div>

Let us visualize a few of the tensors as images:

<div class="sourceClojure">
```clojure
(->> tensors
     (take 3)
     (mapcat (fn [row]
               [row
                (-> row
                    :data
                    (fun/* 200)
                    (vis.image/tensor->image
                     :ushort-gray))])))
```
</div>

<div><p>(</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">{:key "0", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[112 110 111 ... 114 118 124]
 [105 112 106 ... 115 120 119]
 [107 109 108 ... 117 123 115]
 ...
 [132 138 134 ... 109 107 109]
 [130 129 129 ... 115 111 103]
 [134 135 134 ... 110 111 110]]}
</code></pre></div><img src="scicloj.scrapbook.hdf_files/0.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "1", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[124 120 121 ... 117 121 124]
 [118 123 117 ... 118 122 121]
 [120 123 117 ... 119 123 118]
 ...
 [133 139 136 ... 111 106 108]
 [133 132 131 ... 116 111 103]
 [136 137 135 ... 114 111 108]]}
</code></pre></div><img src="scicloj.scrapbook.hdf_files/1.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "10", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[125 120 120 ... 116 121 127]
 [116 122 116 ... 117 121 119]
 [120 121 115 ... 120 123 118]
 ...
 [132 139 133 ... 112 107 108]
 [135 132 132 ... 115 112 104]
 [134 135 135 ... 114 112 108]]}
</code></pre></div><img src="scicloj.scrapbook.hdf_files/2.png" style="width:100%;" /></div><p>)</p></div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-sources/hdf/notebooks/scicloj/scrapbook/hdf.clj</small></small></pre></div>

### 2023-12-31 docs/projects/data-formats/hdf/index.qmd
rerendered HDF tutorial under the new position

--- 2023-12-31 docs/projects/data-sources/hdf/scicloj.scrapbook.hdf.qmd
@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scicloj.scrapbook.hdf.html}
+  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
 highlight-style: solarized
@@
 </style>
-<script src="scicloj.scrapbook.hdf_files/md-default3.js" type="text/javascript"></script><script src="scicloj.scrapbook.hdf_files/md-default4.js" type="text/javascript"></script>
+<script src="index_files/md-default3.js" type="text/javascript"></script><script src="index_files/md-default4.js" type="text/javascript"></script>
 <table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
@@
 ```clojure
-(ns scicloj.scrapbook.hdf
+(ns index
   (:require [babashka.fs :as fs]
@@
  [134 135 134 ... 110 111 110]]}
-</code></pre></div><img src="scicloj.scrapbook.hdf_files/0.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "1", :data #tech.v3.tensor&lt;int32&gt;[600 800]
+</code></pre></div><img src="index_files/0.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "1", :data #tech.v3.tensor&lt;int32&gt;[600 800]
 [[124 120 121 ... 117 121 124]
@@
  [136 137 135 ... 114 111 108]]}
-</code></pre></div><img src="scicloj.scrapbook.hdf_files/1.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "10", :data #tech.v3.tensor&lt;int32&gt;[600 800]
+</code></pre></div><img src="index_files/1.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "10", :data #tech.v3.tensor&lt;int32&gt;[600 800]
 [[125 120 120 ... 116 121 127]
@@
  [134 135 135 ... 114 112 108]]}
-</code></pre></div><img src="scicloj.scrapbook.hdf_files/2.png" style="width:100%;" /></div><p>)</p></div>
+</code></pre></div><img src="index_files/2.png" style="width:100%;" /></div><p>)</p></div>
 
@@
 
-<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-sources/hdf/notebooks/scicloj/scrapbook/hdf.clj</small></small></pre></div>
+<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj</small></small></pre></div>

### 2023-12-31 docs/projects/data-formats/hdf/index.qmd
rerendered hdf project

@@
 
-<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj</small></small></pre></div>
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main//home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj">/home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj</a></small></small></pre></div>

### 2024-01-01 docs/projects/data-formats/hdf/index.qmd
rerendered documents in new Clay version (corrected source links, changed table styling)

--- 2023-12-31 docs/projects/data-formats/hdf/index.qmd
@@
 ---
-<style>table {
-  border-style: thin;
-}
-th, td {
-  padding: 6px;
-}
-td {
-  text-align: left;
-}
-th {
-  text-align: center;
-  background-color: #ddd;
-}
-tr:nth-child(even) {
-  background-color: #f6f6f6;
-}
-</style><style>.printedClojure .sourceCode {
+<style>.printedClojure .sourceCode {
   background-color: transparent;
@@
 
-<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj</small></small></pre></div>
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/data-formats/hdf/notebooks/index.clj">projects/data-formats/hdf/notebooks/index.clj</a></small></small></pre></div>

### 2024-01-01 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
rerendered documents in new Clay version (corrected source links, changed table styling)

@@
 
-<table class="table"><thead><tr><th>sepal-length</th><th>sepal-width</th><th>petal-length</th><th>petal-width</th><th>species</th></tr></thead><tbody><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.3</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.0</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.5</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.6</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.3</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>7.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.7</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>6.0</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.7</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>6.3</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.6</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.3</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>6.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.9</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.2</p></div></td><td><div><p>6.0</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.9</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.4</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.6</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr></tbody><script>new DataTable(document.currentScript.parentElement,
- {"sPaginationType": "full_numbers", "order": []});</script>datatables</table>
+<table class="table"><thead><tr><th>sepal-length</th><th>sepal-width</th><th>petal-length</th><th>petal-width</th><th>species</th></tr></thead><tbody><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.3</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.0</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.5</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.6</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.3</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>7.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.7</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>6.0</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.7</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>6.3</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.6</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.3</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>6.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.9</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.2</p></div></td><td><div><p>6.0</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.9</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.4</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.6</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr></tbody><script>new DataTable(document.currentScript.parentElement, {"sPagunationType":"full_numbers","order":[]});</script></table>
 

### 2024-01-11 docs/projects/main/noj/ml.qmd
rendered draft ml tutorial

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: ml.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>.table {
    overflow-y: scroll;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ml_files/md-default0.js" type="text/javascript"></script><script src="ml_files/md-default1.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

<div class="sourceClojure">
```clojure
(ns ml
  (:require [scicloj.ml.core :as ml]
            [scicloj.ml.metamorph :as mm]
            [scicloj.ml.dataset :refer [dataset add-column]]
            [scicloj.ml.dataset :as ds]
            [fastmath.stats]
            [tablecloth.api :as tc]
            [scicloj.noj.v1.datasets :as datasets]
            [scicloj.kindly.v4.kind :as kind]))
```
</div>

# Machine learning - DRAFT

## Linear regression
We will explore the Iris dataset:

<div class="sourceClojure">
```clojure
(tc/head datasets/iris)
```
</div>

_unnamed [5 5]:

| :sepal-length | :sepal-width | :petal-length | :petal-width | :species |
|--------------:|-------------:|--------------:|-------------:|----------|
|           5.1 |          3.5 |           1.4 |          0.2 |   setosa |
|           4.9 |          3.0 |           1.4 |          0.2 |   setosa |
|           4.7 |          3.2 |           1.3 |          0.2 |   setosa |
|           4.6 |          3.1 |           1.5 |          0.2 |   setosa |
|           5.0 |          3.6 |           1.4 |          0.2 |   setosa |

A Metamorph pipeline for linear regression:

<div class="sourceClojure">
```clojure
(def additive-pipeline
  (ml/pipeline
   (mm/set-inference-target :sepal-length)
   (mm/drop-columns [:species])
   {:metamorph/id :model}
   (mm/model {:model-type :smile.regression/ordinary-least-square})))
```
</div>

Training and evaluating the pipeline on various subsets:

<div class="sourceClojure">
```clojure
(def evaluations
  (ml/evaluate-pipelines
   [additive-pipeline]
   (ds/split->seq datasets/iris :holdout)
   ml/rmse
   :loss
   {:other-metrices [{:name :r2
                      :metric-fn fastmath.stats/r2-determination}]}))
```
</div>

Printing one of the trained models (note that the Smile regression model is recognized by Kindly and printed correctly):

<div class="sourceClojure">
```clojure
(-> evaluations
    flatten
    first
    :fit-ctx
    :model
    ml/thaw-model)
```
</div>

<div class="printedClojure">
```clojure
Linear Model:

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7887     -0.2280      0.0231      0.2356      0.8178

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.2647     0.3103     7.2981     0.0000 ***
sepal-width         0.5371     0.0811     6.6238     0.0000 ***
petal-length        0.6748     0.0740     9.1169     0.0000 ***
petal-width        -0.4828     0.1607    -3.0046     0.0034 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3126 on 96 degrees of freedom
Multiple R-squared: 0.8617,    Adjusted R-squared: 0.8574
F-statistic: 199.4075 on 4 and 96 DF,  p-value: 4.187e-41

```
</div>

Equivalently, we may turn the model to a string and display that string as code:

<div class="sourceClojure">
```clojure
^kind/code
(-> evaluations
    flatten
    first
    :fit-ctx
    :model
    ml/thaw-model
    str)
```
</div>

<div class="sourceClojure">
```clojure
Linear Model:

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7887     -0.2280      0.0231      0.2356      0.8178

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.2647     0.3103     7.2981     0.0000 ***
sepal-width         0.5371     0.0811     6.6238     0.0000 ***
petal-length        0.6748     0.0740     9.1169     0.0000 ***
petal-width        -0.4828     0.1607    -3.0046     0.0034 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3126 on 96 degrees of freedom
Multiple R-squared: 0.8617,    Adjusted R-squared: 0.8574
F-statistic: 199.4075 on 4 and 96 DF,  p-value: 4.187e-41

```
</div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/main/noj/notebooks/ml.clj">projects/main/noj/notebooks/ml.clj</a></small></small></pre></div>

### 2024-01-11 docs/projects/noj/ml.qmd
moved the noj docs

--- 2024-01-11 docs/projects/main/noj/ml.qmd
@@
        Min          1Q      Median          3Q         Max
-   -0.7887     -0.2280      0.0231      0.2356      0.8178
+   -0.7698     -0.2528      0.0188      0.2103      0.5987
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           2.2647     0.3103     7.2981     0.0000 ***
-sepal-width         0.5371     0.0811     6.6238     0.0000 ***
-petal-length        0.6748     0.0740     9.1169     0.0000 ***
-petal-width        -0.4828     0.1607    -3.0046     0.0034 **
+Intercept           1.8690     0.2997     6.2352     0.0000 ***
+sepal-width         0.6645     0.0791     8.3956     0.0000 ***
+petal-length        0.7226     0.0722    10.0028     0.0000 ***
+petal-width        -0.6541     0.1594    -4.1043     0.0001 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3126 on 96 degrees of freedom
-Multiple R-squared: 0.8617,    Adjusted R-squared: 0.8574
-F-statistic: 199.4075 on 4 and 96 DF,  p-value: 4.187e-41
-
-```
-</div>
-
-Equivalently, we may turn the model to a string and display that string as code:
-
-<div class="sourceClojure">
-```clojure
-^kind/code
-(-> evaluations
-    flatten
-    first
-    :fit-ctx
-    :model
-    ml/thaw-model
-    str)
-```
-</div>
-
-<div class="sourceClojure">
-```clojure
-Linear Model:
-
-Residuals:
-       Min          1Q      Median          3Q         Max
-   -0.7887     -0.2280      0.0231      0.2356      0.8178
-
-Coefficients:
-                  Estimate Std. Error    t value   Pr(>|t|)
-Intercept           2.2647     0.3103     7.2981     0.0000 ***
-sepal-width         0.5371     0.0811     6.6238     0.0000 ***
-petal-length        0.6748     0.0740     9.1169     0.0000 ***
-petal-width        -0.4828     0.1607    -3.0046     0.0034 **
----------------------------------------------------------------------
-Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-
-Residual standard error: 0.3126 on 96 degrees of freedom
-Multiple R-squared: 0.8617,    Adjusted R-squared: 0.8574
-F-statistic: 199.4075 on 4 and 96 DF,  p-value: 4.187e-41
+Residual standard error: 0.3154 on 96 degrees of freedom
+Multiple R-squared: 0.8466,    Adjusted R-squared: 0.8418
+F-statistic: 176.6175 on 4 and 96 DF,  p-value: 6.018e-39
 
@@
 
-<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/main/noj/notebooks/ml.clj">projects/main/noj/notebooks/ml.clj</a></small></small></pre></div>
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ml.clj">projects/noj/notebooks/ml.clj</a></small></small></pre></div>

### 2024-01-11 docs/projects/noj/ml.qmd
rerendered noj ml doc

@@
 
+# Machine learning - DRAFT
+
 <div class="sourceClojure">
@@
 </div>
-
-# Machine learning - DRAFT
 
@@
        Min          1Q      Median          3Q         Max
-   -0.7698     -0.2528      0.0188      0.2103      0.5987
+   -0.7900     -0.2237      0.0394      0.2235      0.8037
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.8690     0.2997     6.2352     0.0000 ***
-sepal-width         0.6645     0.0791     8.3956     0.0000 ***
-petal-length        0.7226     0.0722    10.0028     0.0000 ***
-petal-width        -0.6541     0.1594    -4.1043     0.0001 ***
+Intercept           1.7690     0.3120     5.6689     0.0000 ***
+sepal-width         0.6801     0.0844     8.0599     0.0000 ***
+petal-length        0.7043     0.0664    10.6014     0.0000 ***
+petal-width        -0.5256     0.1508    -3.4858     0.0007 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3154 on 96 degrees of freedom
-Multiple R-squared: 0.8466,    Adjusted R-squared: 0.8418
-F-statistic: 176.6175 on 4 and 96 DF,  p-value: 6.018e-39
+Residual standard error: 0.3057 on 96 degrees of freedom
+Multiple R-squared: 0.8690,    Adjusted R-squared: 0.8649
+F-statistic: 212.1968 on 4 and 96 DF,  p-value: 3.179e-42
 

### 2024-01-17 docs/projects/noj/ml.qmd
rerendered

@@
             [scicloj.kindly.v4.kind :as kind]))
+```
+</div>
+
+<div class="sourceClojure">
+```clojure
+(+ 2 3)
+```
+</div>
+
+<div class="printedClojure">
+```clojure
+5
+
 ```
@@
        Min          1Q      Median          3Q         Max
-   -0.7900     -0.2237      0.0394      0.2235      0.8037
+   -0.7792     -0.2471      0.0207      0.2372      0.8531
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.7690     0.3120     5.6689     0.0000 ***
-sepal-width         0.6801     0.0844     8.0599     0.0000 ***
-petal-length        0.7043     0.0664    10.6014     0.0000 ***
-petal-width        -0.5256     0.1508    -3.4858     0.0007 ***
+Intercept           1.6869     0.2922     5.7726     0.0000 ***
+sepal-width         0.6573     0.0790     8.3247     0.0000 ***
+petal-length        0.8419     0.0696    12.0977     0.0000 ***
+petal-width        -0.8468     0.1618    -5.2346     0.0000 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3057 on 96 degrees of freedom
-Multiple R-squared: 0.8690,    Adjusted R-squared: 0.8649
-F-statistic: 212.1968 on 4 and 96 DF,  p-value: 3.179e-42
+Residual standard error: 0.3135 on 96 degrees of freedom
+Multiple R-squared: 0.8817,    Adjusted R-squared: 0.8780
+F-statistic: 238.3941 on 4 and 96 DF,  p-value: 2.404e-44
 

### 2024-01-17 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
rerendered

@@
 ---
-<style>.printedClojure .sourceCode {
+<style></style><style>.printedClojure .sourceCode {
   background-color: transparent;
@@
 </style>
-<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
-<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script>
+<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
 
@@
 
-<div class="sourceClojure">
+::: {.sourceClojure}
 ```clojure
@@
 ```
-</div>
+:::
+
+::: {.sourceClojure}
+```clojure
+(kind/video {:youtube-id "X_SsjhmG5Ok"})
+```
+:::
+
+<div style="max-height:600px;overflow-y:auto;"><iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/X_SsjhmG5Ok"></iframe></div>
 
@@
 ```
-</div>
+:::
 
-<div class="printedClojure">
+::: {.printedClojure}
 ```clojure
@@
 ```
-</div>
+:::
 
@@
 ```
-</div>
+:::
 
-<table class="table"><thead><tr><th>sepal-length</th><th>sepal-width</th><th>petal-length</th><th>petal-width</th><th>species</th></tr></thead><tbody><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.3</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.0</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.5</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.6</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.3</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>7.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.7</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>6.0</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.7</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>6.3</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.6</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.3</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>6.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.9</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.2</p></div></td><td><div><p>6.0</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.9</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.4</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.6</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr></tbody><script>new DataTable(document.currentScript.parentElement, {"sPagunationType":"full_numbers","order":[]});</script></table>
+<div style="max-height:600px;overflow-y:auto;"><table class="table"><thead><tr><th>sepal-length</th><th>sepal-width</th><th>petal-length</th><th>petal-width</th><th>species</th></tr></thead><tbody><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.3</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.0</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.5</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.6</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.3</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>7.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.7</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>6.0</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.7</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>6.3</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.6</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.3</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>6.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.9</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.2</p></div></td><td><div><p>6.0</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.9</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.4</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.6</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr></tbody></table></div>
 
@@
 ```
-</div>
+:::
 
-<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>
+<div style="max-height:600px;overflow-y:auto;"><div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div></div>
 

### 2024-01-17 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
rerendered

@@
 <script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/md-default14.js" type="text/javascript"></script>
-<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
 
@@
 ```
-</div>
+:::
+
+::: {.sourceClojure}
+```clojure
+(kind/video {:youtube-id "fd4kjlws6Ts"})
+```
+:::
+
+<div style="max-height:600px;overflow-y:auto;"><iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/fd4kjlws6Ts"></iframe></div>
 
@@
 ```
-</div>
+:::
 
-<div class="sourceClojure">
+::: {.sourceClojure}
 ```clojure
@@
 ```
-</div>
+:::
 
-<img src="index_files/0.png" style="width:100%;" />
+<div style="max-height:600px;overflow-y:auto;"><img src="index_files/0.png" style="width:100%;" /></div>
 
@@
 ```
-</div>
+:::
 
-<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="index_files/0.png" style="width:100%;" /><img src="index_files/1.png" style="width:100%;" /></div><p>\]</p></div>
+<div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><img src="index_files/0.png" style="width:100%;" /></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/1.png" style="width:100%;" /></div></div><p>\]</p></div></div>
 
@@
 ```
-</div>
+:::
 
-<div><h3>raw image</h3><img src="index_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="index_files/2.png" style="width:100%;" /></div>
+<div style="max-height:600px;overflow-y:auto;"><div><h3>raw image</h3><div style="max-height:600px;overflow-y:auto;"><img src="index_files/0.png" style="width:100%;" /></div><h3>darkened image</h3><div style="max-height:600px;overflow-y:auto;"><img src="index_files/2.png" style="width:100%;" /></div></div></div>
 
@@
 ```
-</div>
+:::
 
-<img src="index_files/3.png" style="width:100%;" />
+<div style="max-height:600px;overflow-y:auto;"><img src="index_files/3.png" style="width:100%;" /></div>
 
@@
 ```
-</div>
+:::
 
-<img src="index_files/4.png" style="width:100%;" />
+<div style="max-height:600px;overflow-y:auto;"><img src="index_files/4.png" style="width:100%;" /></div>
 
-<div class="sourceClojure">
+::: {.sourceClojure}
 ```clojure
@@
 ```
-</div>
+:::
 
-<img src="index_files/5.png" style="width:100%;" />
+<div style="max-height:600px;overflow-y:auto;"><img src="index_files/5.png" style="width:100%;" /></div>
 
-<div class="sourceClojure">
+::: {.sourceClojure}
 ```clojure
@@
 ```
-</div>
+:::
 
-<div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.7
-</code></pre></div><img src="index_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
-</code></pre></div><img src="index_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
-</code></pre></div><img src="index_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
-</code></pre></div><img src="index_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
-</code></pre></div><img src="index_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
-</code></pre></div><img src="index_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
-</code></pre></div><img src="index_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>
+<div style="max-height:600px;overflow-y:auto;"><div><p>(</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.7
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/6.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.8
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/7.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.9
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/8.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/9.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.1
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/10.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.2
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/11.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.3
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/12.png" style="width:100%;" /></div></div><p>\]</p></div></div></div><p>)</p></div></div>
 

### 2024-01-20 projects/geography/seattle-parks/docs/index.qmd
Ranking Seattle neighborhoods by the proportion of area covered by parks. WIP

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default0.js" type="text/javascript"></script><script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/portal2.js" type="text/javascript"></script>

# Seattle Parks & Neighborhoods

::: {.sourceClojure}
```clojure
(ns index
  (:require [geo
             [geohash :as geohash]
             [jts :as jts]
             [spatial :as spatial]
             [io :as geoio]
             [crs :as crs]]
            [tech.v3.datatype.functional :as fun]
            [tablecloth.api :as tc]
            [scicloj.kindly.v4.kind :as kind]
            [scicloj.kindly.v4.api :as kindly])
  (:import (org.locationtech.jts.index.strtree STRtree)
           (org.locationtech.jts.geom Geometry Point Polygon)
           (org.locationtech.jts.geom.prep PreparedGeometry
                                           PreparedLineString
                                           PreparedPolygon
                                           PreparedGeometryFactory)
           (java.util TreeMap)))
```
:::

In this analysis we rank Seattle neighborhoods
by the presence of of Parks in them
(in terms of area proportion).

## Raw geo data

::: {.sourceClojure}
```clojure
(defn read-geogson-gz
  "Read a gzipped GeoJSON file."
  [path]
  ;; See [Reading and Writing Compressed Files](Reading and Writing Compressed Files) by John Cromartie.
  (with-open [in (java.util.zip.GZIPInputStream.
                  (clojure.java.io/input-stream
                   path))]
    (-> in
        slurp
        geoio/read-geojson)))
```
:::

::: {.sourceClojure}
```clojure
(def neighborhoods-geojson
  (read-geogson-gz
   "data/Seattle/Neighborhood_Map_Atlas_Neighborhoods.geojson.gz"))
```
:::

::: {.sourceClojure}
```clojure
(count neighborhoods-geojson)
```
:::

::: {.printedClojure}
```clojure
94

```
:::

::: {.sourceClojure}
```clojure
(->> neighborhoods-geojson
     (take 5)
     kind/portal)
```
:::

<div style="max-height:600px;overflow-y:auto;"><div><script>portal_api.embed().renderOutputItem(
                {'mime': 'x-application/edn',
                 'text': (() => "({^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 27]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :L_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Ballard\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Loyal Heights\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD_ALT_NAMES]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 2.13206555455933E7]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 18831.00959637]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.Polygon 0x1f3c397d \"POLYGON ((-122.376336564723 47.6759176989664, -122.376707907517 47.6759982290459, -122.377903057631 47.6759978849021, -122.379988625303 47.6759893429385, -122.38182788443 47.675992079457, -122.383602752477 47.675979810424, -122.385435721425 47.6759587956618, -122.387087434206 47.6759521343769, -122.387702391216 47.6759476875929, -122.388955759168 47.6759424488678, -122.390449346263 47.6759259868868, -122.391773109273 47.6759158131504, -122.392827172066 47.6759153143353, -122.392956550545 47.6759141859541, -122.392956303464 47.6763287099834, -122.392959618409 47.676929558447, -122.392961263359 47.6775085790216, -122.392971502986 47.6781034200237, -122.392975009807 47.6792517755972, -122.392983771129 47.6798142464259, -122.39300195772 47.6811303942788, -122.393014530791 47.6824285808909, -122.393016158048 47.6837341155494, -122.393022827056 47.685021586284, -122.393030577589 47.6863450742964, -122.393032746621 47.687668638629, -122.393046187318 47.6889956475812, -122.393010665051 47.6902980913372, -122.393002415356 47.6905813205566, -122.392432373275 47.6905826938111, -122.390347910813 47.6905631204492, -122.388192979124 47.6905805029145, -122.385832831602 47.6905766041982, -122.383275316007 47.690593164597, -122.383201215024 47.6905936585447, -122.381453020656 47.6905978829044, -122.379876313408 47.6905988541749, -122.379103841332 47.6906041929746, -122.377117910432 47.6906029639028, -122.376810344766 47.6906051591463, -122.376810264834 47.6905341242701, -122.376810989127 47.6900117143006, -122.376803067488 47.688976146724, -122.376794751014 47.6879443550321, -122.376800402808 47.6870068457338, -122.376784403749 47.6860923366759, -122.376785260609 47.6851813698577, -122.376780535885 47.6842704786057, -122.376787310842 47.6833707854178, -122.376777423242 47.6822860591882, -122.376767820487 47.6811938310584, -122.376770442503 47.680154307228, -122.376770065639 47.6792017979916, -122.376769882216 47.6780678404081, -122.376759750881 47.6775387646826, -122.376761985459 47.676862137338, -122.376772171763 47.6764361697665, -122.376772451106 47.6764114022001, -122.376770700102 47.6763866189683, -122.37676692258 47.6763619488292, -122.376761120573 47.6763374777451, -122.376753802121 47.6763131984825, -122.376744969247 47.6762891966531, -122.376733608705 47.6762655291531, -122.376721246367 47.6762423037704, -122.376706358898 47.6762194979699, -122.376690473449 47.6761972626929, -122.376672575492 47.6761756116819, -122.376653693551 47.6761550023704, -122.376620811506 47.6761243856628, -122.37659791092 47.6761051588887, -122.376573006221 47.6760868163511, -122.376547112434 47.6760693435982, -122.376519722058 47.6760527482053, -122.376336564723 47.6759176989664))\"]]]} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 28]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :L_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Ballard\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Ballard\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD_ALT_NAMES]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Adams\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 2.25521329700012E7]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 29926.3393002841]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.Polygon 0x7ee462dc \"POLYGON ((-122.376218981706 47.6681795106282, -122.376214914328 47.6671023311431, -122.376222341407 47.6660363069762, -122.376218608455 47.6649703907559, -122.376224015951 47.6638363569551, -122.376213335479 47.6628953406738, -122.376215127819 47.6622035949171, -122.376226087158 47.6616326743118, -122.376232028288 47.6610807160121, -122.376228293294 47.6609890799218, -122.376311034007 47.6610075816866, -122.376347589125 47.6610084573967, -122.376398615454 47.6610011680257, -122.376399768145 47.6609545379595, -122.376409994362 47.6608888474507, -122.376480021595 47.6608892699844, -122.376649883965 47.6608858972706, -122.376802044838 47.6608843923845, -122.376904962586 47.6608818836445, -122.377020085186 47.6608803234087, -122.377118045713 47.6608817375375, -122.377232905674 47.6608884069341, -122.377236922833 47.66093826616, -122.377241607037 47.6610105668296, -122.377247426981 47.6611040169469, -122.377305369317 47.6611246108013, -122.377431782777 47.6611615428936, -122.377533178917 47.661176106273, -122.377584412861 47.6611416500979, -122.377614865595 47.6610908096894, -122.377654375344 47.6610203519417, -122.377677258636 47.6609879511404, -122.377715398852 47.6609397055094, -122.377726544603 47.6609050217262, -122.377743040356 47.6608625536466, -122.377758604553 47.6608228828779, -122.377777465054 47.6607746413824, -122.37779127635 47.6607442918602, -122.377820881952 47.6607161699336, -122.377887950662 47.6607024071657, -122.377930778536 47.6607094956517, -122.377982464813 47.6607244326554, -122.378037380882 47.6607456241841, -122.378088199365 47.6607655003304, -122.378144441121 47.6607800757394, -122.378223937077 47.6608089028157, -122.378285257703 47.6608236665358, -122.378343627844 47.6608415550177, -122.378411485271 47.6608543445299, -122.378488168664 47.6608738696264, -122.378572163043 47.6609004074106, -122.378624823197 47.6609139603348, -122.378697367829 47.6609307992309, -122.378751686634 47.6609489565742, -122.378820681289 47.6609658435608, -122.378862952393 47.6609883202932, -122.378922441567 47.6610097066181, -122.379081035255 47.6610539119557, -122.379265109385 47.6611018840283, -122.379389299035 47.6611322460587, -122.379421555758 47.661107986769, -122.379478983191 47.6611282867812, -122.379642682521 47.6611735357023, -122.379800016148 47.6612264976409, -122.379946110899 47.6612768697639, -122.380065852996 47.6613111901579, -122.380130945811 47.6613333136908, -122.380153431187 47.6613558013855, -122.380174148089 47.6613870535744, -122.380188835134 47.6614202727708, -122.380211038217 47.6614844088921, -122.380243167414 47.6615070228645, -122.380303354114 47.6615177305899, -122.380350754978 47.6615250129872, -122.380395375702 47.6615411592479, -122.380479446062 47.6615701795669, -122.380560130101 47.6616047302561, -122.380614654221 47.6616297389514, -122.380663593942 47.6616546093877, -122.380701872643 47.6616792817304, -122.380715579541 47.6617306802593, -122.380690732307 47.6617822596553, -122.380664357784 47.6618166364496, -122.380648035454 47.6618648436206, -122.38068448469 47.6618791728427, -122.380717946765 47.6618954274041, -122.380752187784 47.6619037455183, -122.3807905011 47.6619125221318, -122.380829216037 47.6619347892012, -122.380866227641 47.6619680050916, -122.380895420488 47.6619942145727, -122.380932407944 47.6620266164946, -122.380968643252 47.6620508026807, -122.381020641587 47.6620761452478, -122.381098871967 47.6621134707754, -122.381167450224 47.6621503707618, -122.381238114463 47.6621891699481, -122.381288223574 47.6622192082262, -122.381338421512 47.6622522447606, -122.3813897159 47.6622880078852, -122.381432789931 47.6623203269265, -122.381503551814 47.6623794330982, -122.381572734045 47.6624365895899, -122.38161407395 47.6624788294554, -122.381656280718 47.6625160872786, -122.381699821145 47.6625470286, -122.381806787089 47.662629206954, -122.381897197478 47.6627006417839, -122.38202451515 47.6628017373534, -122.382159570742 47.6629070976345, -122.382234956653 47.6629680680843, -122.382331552118 47.6630427176998, -122.382358242278 47.6630700320529, -122.382342968803 47.6631023303298, -122.382300682104 47.6631816104811, -122.382248627965 47.663256610552, -122.382205916571 47.663321629404, -122.38216549549 47.6633783907977, -122.382130138578 47.6634348263973, -122.382111305681 47.6634668729497, -122.382088660645 47.6635071976301, -122.382072994312 47.6635433570874, -122.382079921409 47.6635714972306, -122.382102317187 47.6636079530782, -122.382132615196 47.6636371467198, -122.382152009826 47.6636580053991, -122.382179632041 47.6636995745085, -122.382226640061 47.6637617023103, -122.382265013459 47.6637894576431, -122.382287032988 47.6638132797402, -122.382294565904 47.6638447105061, -122.382324691125 47.6638851315305, -122.382351104041 47.6639201617707, -122.382392788521 47.6639568697887, -122.38242584513 47.6639764710789, -122.38247158058 47.6639788482028, -122.382526667558 47.6639545348073, -122.382589068071 47.6639202245904, -122.382688434965 47.6638664743225, -122.382803320873 47.6638057006604, -122.382905199031 47.663751101759, -122.382941717148 47.6637336385167, -122.382966133764 47.6637527577184, -122.383031165255 47.6638067137846, -122.383132900026 47.6639004872976, -122.383239585043 47.663990079865, -122.383357582155 47.664084702746, -122.383387571069 47.6640694706022, -122.383426541835 47.6640661980484, -122.383483321407 47.6641156388281, -122.383559518957 47.6641867091696, -122.383607936888 47.6642279949219, -122.38366498611 47.6642694629143, -122.383705216851 47.6642573901608, -122.38374678886 47.6642902858182, -122.383815084444 47.6643515662311, -122.383891529058 47.6644138925092, -122.383928986632 47.6644449161712, -122.383947792141 47.6644800067992, -122.383881817267 47.6645135521425, -122.383814999715 47.6645528502698, -122.38387902594 47.664607076829, -122.3839775665 47.6646786995044, -122.384135832697 47.6645923552987, -122.384242145277 47.664533325113, -122.384331352798 47.6644791975459, -122.384412812772 47.6644375145094, -122.384489691936 47.6643953371378, -122.384583062228 47.6643447088215, -122.384661052548 47.6643057722524, -122.384713096475 47.6642814988847, -122.384746725629 47.6642692587552, -122.384788936095 47.6643065154152, -122.384849380778 47.6643597190268, -122.384916058885 47.6644177644245, -122.384963881728 47.6644560585874, -122.385017250443 47.66451017243, -122.38495372199 47.6645406434711, -122.38488642209 47.6645807627338, -122.384922310085 47.6646101792558, -122.385012204179 47.6646810620896, -122.385091014123 47.664737571192, -122.385159582752 47.6647909208934, -122.385201908298 47.6648150228112, -122.385244683332 47.6647862053257, -122.385303491814 47.6647505716182, -122.385335942888 47.664766838992, -122.385364999663 47.6647883794225, -122.385420652472 47.6648339787411, -122.385451231037 47.6648554984145, -122.385494792308 47.6648869950637, -122.385533657102 47.6648631581812, -122.385581912972 47.6648309670042, -122.385653628924 47.6647858172476, -122.385701427821 47.6648232971616, -122.385777171524 47.6648790340154, -122.385893932504 47.6649660019066, -122.385994659925 47.6650427770733, -122.386107642287 47.6651221273146, -122.386185644498 47.6651855020668, -122.386271942321 47.6652548044143, -122.386383902301 47.6653338685933, -122.386499667119 47.6654214064798, -122.386605559289 47.6655011526632, -122.386735763139 47.6655964196413, -122.386825130185 47.665666494009, -122.386949062028 47.6657555910979, -122.387060182093 47.6658404499214, -122.387166631533 47.6659218162079, -122.387306671535 47.666023546488, -122.387401610193 47.6660932446749, -122.387475179069 47.6661439966965, -122.387516634605 47.6661728654544, -122.387661780928 47.6662756396602, -122.387757343215 47.6663491849378, -122.387916210759 47.6664695947904, -122.387977069777 47.6665364583886, -122.387952685858 47.6665694384435, -122.387879792562 47.6666430976967, -122.387801925444 47.6667201233013, -122.387757098252 47.6667651647428, -122.387756642093 47.6668008177192, -122.387783862165 47.666845689913, -122.387817905054 47.6668981382935, -122.387853754042 47.6669261407119, -122.387899028582 47.6669639114684, -122.387925044609 47.6669854927731, -122.387989093289 47.6670062977376, -122.388036952435 47.6670286949155, -122.388068309967 47.6670422342458, -122.388102023645 47.6670667095868, -122.388061205643 47.6671100682211, -122.388074746639 47.6671386747837, -122.38812121483 47.6671654609862, -122.388179258012 47.6671720807621, -122.388207496189 47.667149202303, -122.388257608331 47.6670942340291, -122.388295448462 47.6670531011843, -122.388323114251 47.6670280449451, -122.388366114046 47.6670406541589, -122.38840365641 47.667057407844, -122.388461732815 47.6670821074944, -122.388539763869 47.6671123185078, -122.388634327555 47.6671524151722, -122.388685173013 47.6671728433664, -122.38881245377 47.6672210192078, -122.388873688193 47.6672494885957, -122.38891982302 47.6672820632114, -122.388953218756 47.6673128406666, -122.388986123599 47.6673272153655, -122.389022855146 47.6673338260221, -122.389090731696 47.66732989987, -122.389113865738 47.6672212730366, -122.389136699377 47.6671365149558, -122.389173242354 47.6671368297695, -122.389173484642 47.6672805268316, -122.389171263858 47.6674266996656, -122.389202123689 47.6674575116872, -122.389281412655 47.6674619127757, -122.389330063777 47.6674598772914, -122.389379189758 47.6674567641031, -122.389482438853 47.6674479412747, -122.389543221697 47.6674443690314, -122.389608953719 47.6674366159831, -122.389712620413 47.6674247884508, -122.3897598728 47.6674268846986, -122.389807306022 47.6674350195555, -122.389904659175 47.6674495849077, -122.390051923575 47.6674703227754, -122.390137799552 47.6674913424451, -122.390203337111 47.6674940457067, -122.390247520863 47.6674953269465, -122.390283174704 47.6674998095369, -122.390300447147 47.6675343634824, -122.390353770916 47.6675358623119, -122.390433026738 47.6675391490383, -122.390475250473 47.6675596943012, -122.390473342253 47.6676145613099, -122.390477772294 47.6676608156235, -122.390514276394 47.6676598024281, -122.390635008225 47.6676586661427, -122.390746079771 47.6676568906986, -122.390827781605 47.6676571445704, -122.39089434969 47.6676603475363, -122.390898510793 47.6676298710342, -122.39090934373 47.6675849930683, -122.390949953969 47.6675855517923, -122.390993547426 47.6675671324767, -122.39099884901 47.6675069918754, -122.391040432475 47.6675061663225, -122.391084025833 47.6674877469723, -122.391108680302 47.6674638452388, -122.391143028365 47.6674416960582, -122.391201627742 47.6673821978372, -122.391240126961 47.667380043104, -122.391290771825 47.6673598990265, -122.391335198315 47.6673354270804, -122.391379477649 47.6673060300438, -122.391412940626 47.6672712968426, -122.391423768106 47.6672431712659, -122.391428443478 47.6672129446238, -122.391447849834 47.6671663214747, -122.391436925275 47.6671404217219, -122.391413510072 47.6671210333067, -122.391450270666 47.6670947382224, -122.39150153965 47.6670954078681, -122.391596984383 47.6670971013938, -122.391693353066 47.667095783058, -122.391784275357 47.6670989520519, -122.391847118954 47.6670964215749, -122.391887213677 47.6670967297431, -122.39192374287 47.6671134961467, -122.392030845721 47.667114772877, -122.392088872647 47.6671208338811, -122.392091136672 47.6671624904442, -122.392096235224 47.6672309720358, -122.392099602433 47.6673263407844, -122.392123114103 47.6673827879395, -122.392134561906 47.6674091946602, -122.392171081212 47.6674086949117, -122.392252243641 47.667407884292, -122.392389680333 47.6674054463277, -122.392477951447 47.6674047951721, -122.392540287934 47.6674022709074, -122.392632321467 47.6673917139587, -122.392675287915 47.6674031651836, -122.392708553001 47.6674126068037, -122.392806337896 47.6674077119961, -122.392873990148 47.6673963317975, -122.392919826064 47.667385035803, -122.392979481849 47.6673946302089, -122.393020401485 47.6673885858434, -122.393097774332 47.6673798574582, -122.393167294004 47.667379976715, -122.393225074576 47.6673778141995, -122.393221955442 47.6674091336357, -122.393222832524 47.6674721885578, -122.393238436297 47.6675355991731, -122.39329750546 47.6675594685231, -122.39335375596 47.6675570271599, -122.393399964841 47.6675243468383, -122.393444656135 47.6675256198886, -122.393447697804 47.6675593395581, -122.393489845271 47.667560390512, -122.393527436354 47.6675618035958, -122.393566974398 47.6675604481272, -122.393614160218 47.6675603160078, -122.393645262763 47.6675484076, -122.393680391047 47.6675015686923, -122.393720254174 47.6674434394496, -122.393758752289 47.6673905560685, -122.393757692749 47.6673214625349, -122.393758475899 47.6672123268719, -122.393761223881 47.6671179455581, -122.393761680877 47.667014855468, -122.393760758474 47.6669334205727, -122.393761456334 47.6668552627146, -122.393760920936 47.6667867186574, -122.393765722004 47.6666931234954, -122.393763843119 47.6666136296473, -122.393767269073 47.6665587417421, -122.393796709599 47.6665421862331, -122.393833203324 47.6665408720148, -122.393910313456 47.6665403298084, -122.394029980183 47.6665376194448, -122.394117717169 47.6665361172178, -122.394193764847 47.6665340039903, -122.394245997497 47.6665329885134, -122.394307860673 47.6665316265894, -122.394382484335 47.6665327891635, -122.394451454801 47.6665315438599, -122.394526529294 47.6665308150352, -122.394590436569 47.6665299391312, -122.3945952516 47.6665551084125, -122.394635468656 47.6665594842731, -122.394716744218 47.6665624834001, -122.394813536912 47.6665584143733, -122.394843759846 47.6665341357291, -122.394841147025 47.6664809587645, -122.394834886514 47.6664245753894, -122.394832801734 47.6663889575007, -122.394849524551 47.6663544523763, -122.394885346531 47.6663476632794, -122.394935394624 47.6663414930711, -122.395069633444 47.6663171592766, -122.395206433201 47.6662936044866, -122.395308991403 47.6662787878676, -122.395398394388 47.6662652224049, -122.395458038067 47.6662575494403, -122.395482297078 47.6662374655706, -122.395511564436 47.6661814089142, -122.395580500711 47.6660608844761, -122.395639755034 47.6659558738869, -122.395696400198 47.6658484569148, -122.395770194014 47.6657207534141, -122.395814140519 47.6656466724319, -122.395837925516 47.6655939472982, -122.395801046284 47.6655824137779, -122.395729887252 47.665561453444, -122.395570832898 47.6655197621848, -122.395426186168 47.6654847281626, -122.395205449697 47.6654334710868, -122.395101200575 47.6654088509248, -122.394958059481 47.6653732390149, -122.394867536756 47.6653495016551, -122.394823231201 47.665344110738, -122.394783768728 47.6653479077655, -122.394711747893 47.6653488950151, -122.394649838534 47.6653486724238, -122.394611634832 47.6653437119756, -122.394571254065 47.6653338542645, -122.394512428063 47.6653349178054, -122.394489224569 47.6653563579404, -122.394421250033 47.6653400233256, -122.394273061951 47.6653052936606, -122.394154612135 47.6652808672428, -122.394109115682 47.6652526992279, -122.394142815643 47.6651921692967, -122.394150283421 47.6651367117978, -122.394063403634 47.665115965855, -122.393934023035 47.6650823489977, -122.393773467102 47.6650412328498, -122.393637085721 47.6650110104485, -122.393577692627 47.664993186853, -122.393446811582 47.6649771563125, -122.393294488555 47.6649567491072, -122.393088231659 47.6649313388824, -122.39292273862 47.6649116685336, -122.392737956194 47.6648917050166, -122.392595402171 47.6648755763921, -122.392420804653 47.6648568438781, -122.392196290103 47.6648316823013, -122.392034348038 47.6648119620737, -122.391865820573 47.6647925886425, -122.391679468479 47.6647710170423, -122.391507873986 47.664750871118, -122.391337343463 47.6647323810584, -122.391230366599 47.6647182062387, -122.391190126095 47.6647129724218, -122.391156789332 47.6647010892321, -122.391116662995 47.6646827435971, -122.391090137256 47.6646441606977, -122.391132274605 47.6646449553595, -122.391252961814 47.6646595001083, -122.391423533134 47.6646793603173, -122.391584933773 47.6646979751453, -122.39174836492 47.6647166044343, -122.391919967094 47.66473700681, -122.392068598633 47.6647527961854, -122.392237607771 47.6647713059764, -122.392384277691 47.6647893494728, -122.392543119103 47.6648071837026, -122.392703498522 47.6648255536658, -122.392838967999 47.6648423365095, -122.393000910464 47.6648620555932, -122.393189301041 47.6648838972179, -122.393332362163 47.6649000181571, -122.393533391983 47.6649203151783, -122.393601740175 47.6649322322938, -122.393684023226 47.6649519707042, -122.393836414988 47.6649915706156, -122.393974481457 47.6650272109698, -122.39413602018 47.6650672421714, -122.39427651762 47.6650993355217, -122.394383548187 47.6651321442783, -122.394521615404 47.6651677839692, -122.394626878068 47.6651923904079, -122.394748535505 47.6652222564645, -122.394858520011 47.6652520251458, -122.394941932347 47.665275560252, -122.395007135528 47.6653009728056, -122.395042412106 47.6653098291457, -122.395098606394 47.6653225118381, -122.395187899967 47.6653391110931, -122.395185307563 47.6653034998161, -122.395182532559 47.6652786879627, -122.395179178089 47.6652514850901, -122.395162586765 47.6652059118399, -122.395194553866 47.6651890640388, -122.395224023521 47.6651735357711, -122.395290858212 47.6651350445393, -122.395204106523 47.6651017012969, -122.395119909873 47.6650858468054, -122.395046830492 47.6650684681901, -122.39491744166 47.6650345956364, -122.394787129257 47.6650037343916, -122.394669611865 47.6649765538592, -122.394623315925 47.6649555521337, -122.394630722072 47.664931843196, -122.39466863731 47.6649272103267, -122.394781561663 47.6649366305867, -122.394908810353 47.6649499675211, -122.395034604815 47.6649655519374, -122.395104542044 47.6649796744066, -122.395233389999 47.6650124404972, -122.395414408425 47.6650590578252, -122.395551871431 47.6650914481458, -122.395691469559 47.6651273655221, -122.395839806131 47.6651670184029, -122.396042201092 47.6652157840011, -122.396171549386 47.6652482849121, -122.396296251292 47.6652781075585, -122.396459688551 47.6653136965464, -122.396570246818 47.6653456409346, -122.396718427527 47.6653800676452, -122.396855483979 47.665415761231, -122.396963980581 47.6654466195237, -122.397073450918 47.6654760934093, -122.397141178563 47.6654842038667, -122.397149422473 47.6654377757309, -122.397177066384 47.6654121605609, -122.397138272521 47.6654044671828, -122.397102876745 47.6653747903804, -122.397134701875 47.6653195124396, -122.397163384799 47.6652609787434, -122.397222202334 47.6651584582248, -122.397276785874 47.665050125973, -122.397423157647 47.665075022853, -122.397399749934 47.6651233727284, -122.39737971908 47.6651658927397, -122.397359414468 47.6651993330766, -122.397339259321 47.6652377416216, -122.397319095638 47.6652758501897, -122.397296012182 47.6653181120077, -122.397274685418 47.6653513094429, -122.397295673685 47.6653743286203, -122.397342829988 47.6653901334534, -122.397400122238 47.6654055421706, -122.397475746638 47.6654231409141, -122.397556484426 47.6654420406776, -122.397623962211 47.665458680349, -122.397699669262 47.665479020038, -122.397774279557 47.6654966325135, -122.397832552849 47.6655109135237, -122.397880558751 47.6655212223654, -122.397927550357 47.6655315451191, -122.397966319421 47.6655384246432, -122.397999728422 47.6655694994146, -122.39802676278 47.6655910644734, -122.398084211448 47.6656116547174, -122.398134246127 47.6656219355846, -122.398174556359 47.6656294365165, -122.398212799301 47.6656356808877, -122.398278140071 47.6656487502093, -122.398360834154 47.665665180397, -122.398431287859 47.665679550672, -122.398513964754 47.6656954239765, -122.398583380244 47.6657089944956, -122.398645670001 47.6657218489658, -122.398687293904 47.6657561095398, -122.398612765463 47.665741238405, -122.398356595061 47.6656929164311, -122.398235140748 47.6656699064362, -122.398104491423 47.6656448377607, -122.3980167349 47.6656287770187, -122.397948259732 47.6656127082847, -122.397885804754 47.6655943716031, -122.39782650029 47.6655795481232, -122.397781530071 47.6655689402946, -122.397723263948 47.6655549164294, -122.397678260268 47.6655431953524, -122.397616894538 47.6655273285234, -122.397555520348 47.6655111620389, -122.397495259751 47.6654982794665, -122.397433836139 47.6654804853879, -122.397378589189 47.6654656059629, -122.397333561173 47.6654530708063, -122.397278355512 47.6654395617044, -122.397239495894 47.6654296840457, -122.397190129026 47.6654415869513, -122.397181717127 47.665499285341, -122.397245120336 47.6655154241672, -122.397316687075 47.6655330790791, -122.397409730533 47.6655562228905, -122.397492513889 47.6655756516231, -122.397578422737 47.6655977792514, -122.397664290935 47.665618536436, -122.39772258882 47.6656336310949, -122.39777682947 47.6656487814479, -122.397851432305 47.6656661370596, -122.397910720126 47.6656804040982, -122.397981183276 47.6656950746105, -122.39804053691 47.6657115255453, -122.398085524056 47.6657226896999, -122.398160185648 47.6657419726038, -122.398198014074 47.6657513071111, -122.398264560144 47.6657707010876, -122.398336103604 47.6657875417595, -122.398407605837 47.6658030116642, -122.398480171431 47.6658200947712, -122.398531336782 47.6658342161785, -122.398603977261 47.6658537831363, -122.398692287664 47.6658882164346, -122.39877946725 47.66591880896, -122.398835952565 47.6659410831018, -122.398867753365 47.6659524281792, -122.398911932974 47.6659704585057, -122.399006965293 47.6659922027588, -122.399079482332 47.6660076582998, -122.399163281345 47.6660270715246, -122.399245966763 47.6660432014615, -122.39934098258 47.6660643886569, -122.399419676086 47.6660827578667, -122.399488136071 47.6660982689299, -122.399581040329 47.6661167430826, -122.399672938066 47.6661354879204, -122.399775013722 47.6661552063895, -122.399864882943 47.66617397897, -122.399947619147 47.6661917783836, -122.400028293199 47.6662084924321, -122.400089635415 47.6662235440262, -122.40013665262 47.6662346794603, -122.400172438128 47.6662435272319, -122.400203530533 47.6662650359713, -122.400199574332 47.6663021081989, -122.400159847648 47.6662971705439, -122.400125135044 47.666290235959, -122.400029162253 47.6662709905185, -122.399946434937 47.6662534911302, -122.399868770265 47.6662356216171, -122.39976559026 47.6662129192681, -122.39966444622 47.6661904457502, -122.399572531612 47.6661711441265, -122.399477549058 47.6661510706823, -122.399381494707 47.6661290839471, -122.399274256775 47.6661064365975, -122.399172099348 47.6660839765795, -122.399061843144 47.666062184803, -122.399020912783 47.6660509649151, -122.398963990868 47.6660478914062, -122.398916850764 47.6660326440166, -122.39882696536 47.666013313909, -122.398762522226 47.6659963763111, -122.398690961584 47.6659789794789, -122.398613307306 47.6659614090685, -122.398548839807 47.6659436577576, -122.398501814173 47.665932221702, -122.398459845214 47.6659202019576, -122.398420572908 47.6659303388334, -122.398360483097 47.6659568711198, -122.398348008176 47.6659806927817, -122.398288513526 47.6659932923167, -122.398303533746 47.6660371300684, -122.398320785868 47.6660877069077, -122.398361478046 47.6661247222789, -122.398396248342 47.6661335849026, -122.398431092144 47.6661448882923, -122.398493440936 47.6661596699889, -122.39856190796 47.6661754384288, -122.398684601054 47.666205843122, -122.398793076407 47.6662358860725, -122.398907679134 47.6662672156447, -122.399026356089 47.6662990461122, -122.399149222623 47.6663351889532, -122.39924339749 47.6663621288211, -122.39932849276 47.666390864466, -122.399431921207 47.666421790131, -122.399521931429 47.6664452312246, -122.399587472287 47.6664648951874, -122.399670365025 47.6664878770214, -122.399712450875 47.6665037506191, -122.399744244471 47.6665148386387, -122.399740807532 47.6665691699517, -122.399739268132 47.6666191050841, -122.399739055292 47.6666457146117, -122.399792844176 47.6666795074254, -122.399849372052 47.6667031514349, -122.399940892961 47.6667430237498, -122.400033394773 47.6667817681315, -122.400128141528 47.6668276370482, -122.400275810269 47.6668785189333, -122.400401302962 47.6669343755368, -122.400542819837 47.6669831564955, -122.400688345804 47.6670302542602, -122.400786334216 47.6670826329956, -122.400912759638 47.6671357343367, -122.400982205724 47.667183878683, -122.401043987268 47.6672134481104, -122.40117032336 47.6672635512539, -122.401287627703 47.6673170346491, -122.401420841206 47.6673596307978, -122.401540018899 47.6674079041331, -122.401615187632 47.6674438870858, -122.401685123866 47.667440996262, -122.401763005473 47.6674659731992, -122.401847320935 47.6675023870714, -122.401937968462 47.6675636492733, -122.402004341665 47.6678461950895, -122.401941481828 47.6680499727374, -122.401012947588 47.6676816094831, -122.3983273256 47.6674845638036, -122.398337852112 47.6681206608513, -122.398327335285 47.668563432689, -122.398305959458 47.6694545076039, -122.398302731334 47.6695663760642, -122.398337579049 47.671094419885, -122.398343274343 47.6720250537468, -122.398373497892 47.6740903885558, -122.39836900529 47.6758286109207, -122.398264017499 47.6758644570828, -122.395673683783 47.6758796144233, -122.392956550545 47.6759141859541, -122.392827172066 47.6759153143353, -122.391773109273 47.6759158131504, -122.390449346263 47.6759259868868, -122.388955759168 47.6759424488678, -122.387702391216 47.6759476875929, -122.387087434206 47.6759521343769, -122.385435721425 47.6759587956618, -122.383602752477 47.675979810424, -122.38182788443 47.675992079457, -122.379988625303 47.6759893429385, -122.377903057631 47.6759978849021, -122.376707907517 47.6759982290459, -122.376336564723 47.6759176989664, -122.376214150095 47.6757431382831, -122.376206970115 47.6747491618888, -122.376206910876 47.6736189728118, -122.376208757484 47.6725529816933, -122.376215401015 47.6714605332274, -122.376216126032 47.6703567685299, -122.376212003553 47.6692606527246, -122.376218981706 47.6681795106282))\"]]]} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 29]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :L_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Ballard\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Whittier Heights\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD_ALT_NAMES]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.41956874919434E7]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 15934.4392663199]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.Polygon 0x11cff25b \"POLYGON ((-122.376336564723 47.6759176989664, -122.376519722058 47.6760527482053, -122.376547112434 47.6760693435982, -122.376573006221 47.6760868163511, -122.37659791092 47.6761051588887, -122.376620811506 47.6761243856628, -122.376653693551 47.6761550023704, -122.376672575492 47.6761756116819, -122.376690473449 47.6761972626929, -122.376706358898 47.6762194979699, -122.376721246367 47.6762423037704, -122.376733608705 47.6762655291531, -122.376744969247 47.6762891966531, -122.376753802121 47.6763131984825, -122.376761120573 47.6763374777451, -122.37676692258 47.6763619488292, -122.376770700102 47.6763866189683, -122.376772451106 47.6764114022001, -122.376772171763 47.6764361697665, -122.376761985459 47.676862137338, -122.376759750881 47.6775387646826, -122.376769882216 47.6780678404081, -122.376770065639 47.6792017979916, -122.376770442503 47.680154307228, -122.376767820487 47.6811938310584, -122.376777423242 47.6822860591882, -122.376787310842 47.6833707854178, -122.376780535885 47.6842704786057, -122.376785260609 47.6851813698577, -122.376784403749 47.6860923366759, -122.376800402808 47.6870068457338, -122.376794751014 47.6879443550321, -122.376803067488 47.688976146724, -122.376810989127 47.6900117143006, -122.376810264834 47.6905341242701, -122.376810344766 47.6906051591463, -122.375110107987 47.6906173771311, -122.373230534841 47.6906248812211, -122.37140439251 47.6906367315375, -122.369524666912 47.6906390778747, -122.367607389199 47.6906418559576, -122.366004446548 47.6906481724782, -122.366003399739 47.6904922338054, -122.36599385014 47.6887402933599, -122.366005835095 47.6862900886837, -122.36599586678 47.6845239294054, -122.366032959089 47.6832519011367, -122.366038176946 47.6830846527711, -122.366006789592 47.6805923152563, -122.366049650322 47.6763326418883, -122.366053675503 47.6760045296047, -122.366299114137 47.6760152803027, -122.367446257021 47.6759532251209, -122.368513687945 47.6759415886584, -122.369529736837 47.6759772497078, -122.370612103444 47.6759215200542, -122.371140989063 47.6759582978223, -122.371714110737 47.6759807230408, -122.373288186248 47.6759402633333, -122.375585947496 47.6759338606538, -122.376080171672 47.6758970068068, -122.376336564723 47.6759176989664))\"]]]} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 30]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :L_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Ballard\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"West Woodland\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD_ALT_NAMES]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 2.21993668730164E7]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 21789.6510873493]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.Polygon 0x41b6d8d1 \"POLYGON ((-122.376336564723 47.6759176989664, -122.376080171672 47.6758970068068, -122.375585947496 47.6759338606538, -122.373288186248 47.6759402633333, -122.371714110737 47.6759807230408, -122.371140989063 47.6759582978223, -122.370612103444 47.6759215200542, -122.369529736837 47.6759772497078, -122.368513687945 47.6759415886584, -122.367446257021 47.6759532251209, -122.366299114137 47.6760152803027, -122.366053675503 47.6760045296047, -122.365227601151 47.6759917757154, -122.364351081075 47.6759893337515, -122.363647800755 47.6759930842157, -122.36271708327 47.6759941851371, -122.362245131082 47.6759948642237, -122.36094806215 47.6759980385768, -122.360691453297 47.6760043068067, -122.36077646407 47.6758922436911, -122.360771594157 47.6752948902842, -122.360775562234 47.6745665726628, -122.360777556465 47.6739264976242, -122.360786418032 47.673226562611, -122.360788381154 47.6724300211048, -122.360793230899 47.671593595961, -122.360789714591 47.6707487566245, -122.360797202559 47.66986396762, -122.36080519647 47.6689791289769, -122.360803810493 47.6680859329074, -122.360802846427 47.6671898180224, -122.360802670245 47.6669075629066, -122.360801382733 47.6662767003006, -122.360803809514 47.6653578322292, -122.360802011097 47.6644333226362, -122.360799877982 47.6634974208525, -122.360790125255 47.6626647898188, -122.360789123417 47.6625616346537, -122.360789702508 47.662374140783, -122.36079141909 47.6614656503796, -122.36214579117 47.6614566051262, -122.363439573738 47.661457526372, -122.364137181521 47.6614573212743, -122.366155922999 47.6614736585099, -122.366120224218 47.6593510369868, -122.365384555672 47.6584891840664, -122.36504049713 47.6581417180235, -122.365039920817 47.6577605839202, -122.365898909139 47.6571615480529, -122.36609426973 47.6570254164477, -122.366796991946 47.6565298464815, -122.366826844662 47.6565443969658, -122.366857901565 47.6565653580207, -122.366891472649 47.6565855569296, -122.366931099591 47.6566046887304, -122.366984914141 47.6566404245544, -122.36696633103 47.6566639819699, -122.366941865149 47.6566944739385, -122.366945853884 47.6567265106697, -122.366920737647 47.656769350089, -122.366914591904 47.6568017802057, -122.366910524252 47.6568358533544, -122.366929434489 47.6568577922272, -122.366954358163 47.6568772076512, -122.366989609651 47.6569027823278, -122.3670234701 47.6568812040272, -122.367058714568 47.6569065218601, -122.367084805348 47.6569311055126, -122.367136503061 47.6569638706548, -122.367176745134 47.6569866362092, -122.367208199216 47.657021044885, -122.367256821766 47.6570527373811, -122.367316047732 47.6570999253012, -122.36736372904 47.657134115369, -122.367407280992 47.6571658761019, -122.367396828116 47.6571898810789, -122.367342953188 47.6571864936152, -122.367260663289 47.6571829321847, -122.36712573072 47.6571833781758, -122.367123844393 47.6572226062806, -122.367068701234 47.657245027876, -122.367084706917 47.6572716756283, -122.367124722507 47.6572867749918, -122.367208951699 47.6572872688121, -122.367317651982 47.657291845841, -122.367357287779 47.6572940538329, -122.367410165606 47.6572980117273, -122.367491586888 47.6573065121605, -122.367593130693 47.6573092570451, -122.36765110338 47.6573139601153, -122.367750869179 47.6573252123496, -122.367747961565 47.6573641969622, -122.367744851179 47.6573963293169, -122.367735882061 47.6574362095165, -122.367731058077 47.6574790329932, -122.367936013957 47.6574790133695, -122.36811967029 47.6574792807636, -122.368143685487 47.657502264309, -122.368179766803 47.6575215294621, -122.368221128874 47.6575478353438, -122.368257128799 47.6575643593633, -122.368282158263 47.6575873292113, -122.368331017204 47.6576269870795, -122.368369279504 47.6576514067545, -122.36839535663 47.6576754764687, -122.368436678466 47.6577004118894, -122.368470690691 47.6577183335634, -122.368499655604 47.6577371375356, -122.368533877812 47.6577621682691, -122.368560912329 47.6577842971086, -122.368597146509 47.6578087440486, -122.368627142653 47.6578280910938, -122.368654079328 47.6578469220186, -122.368707076446 47.6578892661541, -122.368734199128 47.6579143928902, -122.368793128141 47.6579514298714, -122.36882312391 47.657970776521, -122.36885318474 47.6579923074877, -122.368876064888 47.6580111934047, -122.368919610383 47.6580426963992, -122.368944478452 47.6580601845718, -122.36898805566 47.6580927583049, -122.369025330251 47.6581180478279, -122.36905969088 47.6581477470354, -122.369033975504 47.6581702869537, -122.36900709337 47.6581876586224, -122.368999691683 47.65821187988, -122.369018464588 47.6582634682636, -122.369043721192 47.6582941041555, -122.36907469147 47.6583120666742, -122.369109790614 47.6583324156284, -122.369156891474 47.6583468617493, -122.369212098743 47.6583609412648, -122.369318009446 47.6583740372247, -122.369358310498 47.6583987288221, -122.369406708617 47.6584227545456, -122.369440827205 47.6584442306362, -122.369473898213 47.6584646068355, -122.369514255849 47.6584912259011, -122.369572211863 47.658529646547, -122.36960323056 47.6585492364699, -122.369632132312 47.658565855815, -122.369664043734 47.6585813205437, -122.369695987565 47.6585978988375, -122.369736191513 47.6586192927535, -122.369776192963 47.6586338340435, -122.369816583052 47.6586615237593, -122.369826797328 47.6586981462173, -122.369867901674 47.6587156720736, -122.369905201188 47.6587417749067, -122.369942483773 47.6587673213019, -122.369968447737 47.6587875363313, -122.36999861459 47.6588126217082, -122.370029609556 47.6588313975654, -122.370067898867 47.6588566734205, -122.370117927743 47.6589014987462, -122.370168841769 47.658941942404, -122.370195999136 47.658968182, -122.370216908268 47.6589890221901, -122.370246158652 47.6590174187339, -122.370277517982 47.6590485290195, -122.370311839933 47.6590768571086, -122.370336830517 47.659098456122, -122.370367021263 47.6591243550065, -122.37039624775 47.6591519379133, -122.370416312519 47.6591785304467, -122.37044639117 47.6592006177754, -122.370473353282 47.6592202622183, -122.370502724993 47.6592527701992, -122.370517288468 47.6592991883743, -122.370540243237 47.6593205575537, -122.370541017091 47.6594496797416, -122.370642889997 47.6594633860064, -122.370668935633 47.6594863416389, -122.370703095449 47.6595091877392, -122.370724046049 47.6595313982104, -122.370741182515 47.6595618864373, -122.370756054473 47.659584435873, -122.370772022238 47.6596097127233, -122.370788980152 47.6596341619315, -122.370825412255 47.6596652035978, -122.370858696122 47.6596927316213, -122.370910463566 47.659727679378, -122.370957379969 47.6597358289275, -122.370966433314 47.6598017724136, -122.370995075217 47.6598438873314, -122.37109454691 47.6598793049694, -122.371137413708 47.6598877660403, -122.371168305238 47.6598687118902, -122.371211132648 47.6598415272093, -122.37124000278 47.6598227572507, -122.371275908778 47.6598017070751, -122.371311854781 47.6597820276275, -122.371350762806 47.6597595659607, -122.37142619989 47.6598057186435, -122.371463427483 47.6598293373683, -122.371491518562 47.6598528222021, -122.371540422629 47.6598938490718, -122.37156744254 47.6599154204198, -122.371596499027 47.6599372215243, -122.371639131162 47.6599720350715, -122.371672301585 47.6599957081771, -122.371750903628 47.6600459313941, -122.371792245425 47.6600714220276, -122.371820280267 47.6600929796089, -122.371851340784 47.6601139393066, -122.371913698707 47.6601638248364, -122.371986215918 47.660214129744, -122.372040239984 47.6602567154385, -122.372114688276 47.6603036953151, -122.372164590997 47.6603441514304, -122.372243445585 47.6604028537521, -122.372274482371 47.6604229997362, -122.372276324586 47.660485227525, -122.37227074266 47.6605365874913, -122.37225504101 47.6605888984651, -122.372252063055 47.6606253992408, -122.372300935393 47.660631036882, -122.372337587815 47.660635211775, -122.37240070095 47.6606420278766, -122.372440477734 47.6606489023762, -122.372484156738 47.6606504973298, -122.372563572134 47.6606595783311, -122.372624730427 47.6606689056685, -122.37273364879 47.6606805869493, -122.372806816049 47.6606842681617, -122.372842543097 47.6606914541774, -122.37289961108 47.660699722995, -122.37296059064 47.6607030118459, -122.373007484147 47.6607103469529, -122.373209839634 47.660724877436, -122.373245437373 47.6607276953685, -122.373330945994 47.6607369503739, -122.373385815625 47.6607395073355, -122.373419895432 47.6607253365243, -122.373466983151 47.660739223728, -122.373496885087 47.6607552715937, -122.373551113066 47.6607704334901, -122.373591847227 47.6607753667089, -122.373628337943 47.6607740593064, -122.373632702775 47.660750136064, -122.373666450031 47.6607247442675, -122.373705682622 47.6607132455431, -122.373771253658 47.6607002765727, -122.373804034818 47.6606765259987, -122.373804998654 47.6606063340659, -122.373874968362 47.6606048306868, -122.374082995739 47.6606053156307, -122.374297091976 47.6606051614314, -122.374502100296 47.6606065007312, -122.374690879977 47.6606080589335, -122.374897876649 47.6606079996829, -122.375106909387 47.6606081694125, -122.375206342681 47.6606079373933, -122.375281407609 47.6606071780974, -122.375395605626 47.6606086739619, -122.37542406779 47.6606274826827, -122.375423424091 47.6606570969644, -122.375407829398 47.6606786873881, -122.375378139928 47.6607040247744, -122.375332531732 47.6607400316276, -122.375302401399 47.6607676029867, -122.375283362005 47.6607927961628, -122.3752817205 47.660822980606, -122.375298776239 47.6608677362913, -122.375322319322 47.6609088480108, -122.375367789142 47.6609536903689, -122.375414915253 47.6609859567612, -122.375480757744 47.6610163415218, -122.375549698916 47.661048569405, -122.375616507521 47.6610773131594, -122.37567132516 47.6610952082863, -122.375713866021 47.6611097131508, -122.375766573924 47.6611248945907, -122.375816044728 47.6611335649309, -122.375873685334 47.6611440093711, -122.375928012797 47.6611624680215, -122.375974541099 47.6611574674372, -122.375994709938 47.6611190630255, -122.376028531523 47.6610791024086, -122.376045764347 47.6610443363587, -122.376053339804 47.6609918779637, -122.376029447109 47.6609389890523, -122.376000962688 47.6609023572787, -122.376035494866 47.6608692423874, -122.376094954205 47.6608554981113, -122.376142250917 47.6608593131576, -122.376170357689 47.660900320073, -122.37622552108 47.6609298638619, -122.376227046633 47.6609641613863, -122.376228293294 47.6609890799218, -122.376232028288 47.6610807160121, -122.376226087158 47.6616326743118, -122.376215127819 47.6622035949171, -122.376213335479 47.6628953406738, -122.376224015951 47.6638363569551, -122.376218608455 47.6649703907559, -122.376222341407 47.6660363069762, -122.376214914328 47.6671023311431, -122.376218981706 47.6681795106282, -122.376212003553 47.6692606527246, -122.376216126032 47.6703567685299, -122.376215401015 47.6714605332274, -122.376208757484 47.6725529816933, -122.376206910876 47.6736189728118, -122.376206970115 47.6747491618888, -122.376214150095 47.6757431382831, -122.376336564723 47.6759176989664))\"]]]} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 31]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :L_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"North Central\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Phinney Ridge\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :S_HOOD_ALT_NAMES]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"Woodland Park\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 3.21231178777466E7]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :Shape__Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 27120.7859379681]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.Polygon 0x3fbfe64b \"POLYGON ((-122.347307566662 47.6650052913031, -122.348867895321 47.6650090912859, -122.349792869513 47.6649918965054, -122.349989420364 47.6650332375445, -122.350304163556 47.6650388147716, -122.351421221038 47.6650141642968, -122.352495514378 47.6650193785027, -122.353450405799 47.6650188929375, -122.354365227588 47.6650188912667, -122.355056521311 47.6650267528834, -122.355414376827 47.6650317400371, -122.355416519216 47.6643598303278, -122.355424977054 47.6636610158142, -122.355424140879 47.6630086831036, -122.355427805224 47.6625273664197, -122.355436677765 47.662206602761, -122.355438314261 47.6621412005632, -122.355573420679 47.6621809112223, -122.355864863892 47.6622576482863, -122.356113413965 47.6623422844097, -122.356200383141 47.6623840944536, -122.356311534565 47.6624373631027, -122.356476832915 47.6625377642513, -122.356569133827 47.6625883712575, -122.357013669094 47.6628335347683, -122.357378460614 47.6630582987986, -122.357703834377 47.6633056110634, -122.358267789163 47.6637988671757, -122.359051229737 47.664492005053, -122.359500905186 47.6648939854014, -122.359642871567 47.6650460222814, -122.3598308178 47.6652951273317, -122.360257228516 47.6660101362634, -122.360375131079 47.6662064525472, -122.360743692216 47.666817181635, -122.360802670245 47.6669075629066, -122.360802846427 47.6671898180224, -122.360803810493 47.6680859329074, -122.36080519647 47.6689791289769, -122.360797202559 47.66986396762, -122.360789714591 47.6707487566245, -122.360793230899 47.671593595961, -122.360788381154 47.6724300211048, -122.360786418032 47.673226562611, -122.360777556465 47.6739264976242, -122.360775562234 47.6745665726628, -122.360771594157 47.6752948902842, -122.36077646407 47.6758922436911, -122.360691453297 47.6760043068067, -122.36094806215 47.6759980385768, -122.362245131082 47.6759948642237, -122.36271708327 47.6759941851371, -122.363647800755 47.6759930842157, -122.364351081075 47.6759893337515, -122.365227601151 47.6759917757154, -122.366053675503 47.6760045296047, -122.366049650322 47.6763326418883, -122.366006789592 47.6805923152563, -122.366038176946 47.6830846527711, -122.366032959089 47.6832519011367, -122.365072292044 47.6832400978159, -122.360853796868 47.6832540116804, -122.356720447386 47.6832808551648, -122.352902763328 47.6833062957672, -122.350224039798 47.6832962725287, -122.346173568009 47.683293139086, -122.344486258114 47.6833050746089, -122.34448184051 47.682507422038, -122.344493201644 47.6813797044772, -122.344498539691 47.6813538417466, -122.344504896624 47.6813280939604, -122.344511764863 47.6813024678503, -122.344520157279 47.6812769071635, -122.34452906298 47.6812515541157, -122.344538988795 47.6812263584634, -122.34454993299 47.6812012784631, -122.344561392211 47.6811764481954, -122.344574379345 47.6811518121086, -122.344587880268 47.6811273833018, -122.344613552414 47.6810851841658, -122.344629611324 47.6810614500549, -122.344646692321 47.6810379593003, -122.344664290317 47.6810148042395, -122.344682911652 47.6809919356879, -122.344702049261 47.6809693600197, -122.344982950426 47.6806457607991, -122.345002598574 47.6806233071122, -122.345021223875 47.6806005669062, -122.34503984117 47.6805775698876, -122.345057435099 47.6805542863574, -122.345074008684 47.6805308022656, -122.345090066683 47.6805070677453, -122.345105103095 47.6804830898613, -122.345119626422 47.6804589475059, -122.345132679663 47.6804365809458, -122.345145671323 47.6804121160041, -122.345159168049 47.6803875587207, -122.345171645889 47.6803628864969, -122.345183615423 47.680338178197, -122.345195581199 47.6803133411366, -122.345207037435 47.6802884255483, -122.34521798359 47.6802634307376, -122.345228927245 47.6802383503202, -122.345239360831 47.6802131910313, -122.345249286114 47.6801879956669, -122.345258700074 47.6801626782776, -122.345267605743 47.6801373251639, -122.345276510157 47.6801119292468, -122.345284904496 47.6800864541079, -122.34529278877 47.6800609000981, -122.345300164744 47.6800353100135, -122.345307539466 47.6800096771256, -122.345314404644 47.6799839653602, -122.34532076225 47.6799582603297, -122.345326609795 47.6799324764289, -122.345331949043 47.6799066564535, -122.345337286522 47.679880793682, -122.345342116214 47.6798548944784, -122.345346436583 47.6798289595651, -122.345350249894 47.6798030310293, -122.345388766947 47.6794348332565, -122.345489574102 47.678591097451, -122.34550729821 47.6783281431494, -122.345510616247 47.6783026497212, -122.345521037373 47.6782770623701, -122.345527907924 47.6782515646106, -122.345534778989 47.6782260668437, -122.345542157085 47.6782005626977, -122.345549536409 47.6781751010031, -122.345556915727 47.678149639308, -122.345564296292 47.6781242207661, -122.345572183868 47.678098795143, -122.345580071965 47.6780733698634, -122.345587960771 47.678047987042, -122.345595850098 47.678022604564, -122.345603740134 47.6779972645442, -122.345612138237 47.6779719181311, -122.345620537059 47.6779466145269, -122.345628935861 47.6779213105713, -122.345637334666 47.6778960069659, -122.345646242253 47.6778707394257, -122.345654642277 47.6778454782708, -122.345663550572 47.6778202535388, -122.345672966923 47.6777950220623, -122.345681876447 47.6777698401315, -122.345691294025 47.6777446514562, -122.34570071232 47.6777195055896, -122.345710130596 47.6776943593714, -122.345719550118 47.677669256306, -122.345729477184 47.6776441468533, -122.345738897934 47.677619086589, -122.345748826217 47.6775940195866, -122.345759262031 47.6775689458458, -122.345769192266 47.6775439644539, -122.345779629306 47.677518933514, -122.34590637354 47.6773574430743, -122.346596886857 47.6764789695799, -122.346617048988 47.6764568084887, -122.346636187836 47.6764343612505, -122.346654809675 47.6764115779707, -122.346672408949 47.6763885510035, -122.3466889862 47.6763652810441, -122.346705555936 47.6763417535642, -122.346720594874 47.6763179470316, -122.346735120546 47.6762939328673, -122.346749132953 47.6762697110715, -122.346761616528 47.6762452954857, -122.346774094379 47.676220665878, -122.346785043921 47.6761958424742, -122.346795482175 47.6761708970522, -122.346804899651 47.6761457510927, -122.34681380637 47.6761204834594, -122.346821694796 47.6760951005437, -122.346828564421 47.6760696027034, -122.346834923303 47.6760439835405, -122.346840265133 47.6760182915476, -122.346844589422 47.6759925277843, -122.346848405454 47.6759667279532, -122.346850697451 47.6759408627296, -122.346852986424 47.6759149115564, -122.34685325133 47.6758891589, -122.346853447502 47.6758436130604, -122.346851677106 47.6758176729946, -122.346849400445 47.6757917828246, -122.346846618018 47.6757659418417, -122.346842313553 47.6757401214293, -122.346837504581 47.6757143933574, -122.346831683051 47.6756887640242, -122.346824849504 47.6756632341244, -122.346817510208 47.675637753762, -122.34680916087 47.675612458445, -122.346800307021 47.675587255117, -122.346789935404 47.6755622007595, -122.346779060742 47.6755373243608, -122.346767684594 47.6755126259001, -122.34675479089 47.6754881192253, -122.346741395172 47.6754637901441, -122.346731081703 47.6754407485692, -122.346719703106 47.675415964498, -122.346707818984 47.6753912731306, -122.346695937874 47.6753666670096, -122.346683549257 47.6753420676288, -122.346671164401 47.6753175970057, -122.346658273283 47.6752931759253, -122.346644876414 47.6752688040298, -122.346631482061 47.675244518089, -122.346617583215 47.6752203244863, -122.346603685108 47.6751961736916, -122.346589282508 47.6751721152348, -122.34657437366 47.6751481066708, -122.346559468555 47.6751242261621, -122.346544565239 47.6751003887981, -122.346528649385 47.6750766501685, -122.346513243046 47.675052990759, -122.34649682522 47.6750294304204, -122.346480916897 47.6750059489513, -122.346463996579 47.6749825669103, -122.346447078758 47.6749592701215, -122.346430163445 47.6749360589356, -122.346412743654 47.6749129404369, -122.346394818336 47.6748899142881, -122.346376896045 47.674866973735, -122.346358977509 47.6748441615873, -122.346340046971 47.6748214485152, -122.3463216247 47.6747987718606, -122.346302700426 47.6747762727961, -122.34628326991 47.6747538236216, -122.346263336154 47.6747315095848, -122.346243913149 47.67470931722, -122.346223478154 47.6746872242802, -122.346203045659 47.6746652165915, -122.34618261693 47.6746433376581, -122.346161683706 47.6746215507078, -122.346140753729 47.6745998925198, -122.346119319278 47.6745783270162, -122.34609738158 47.674556896298, -122.346075954121 47.6745355876097, -122.346053516422 47.6745144204382, -122.346031081244 47.6744933392187, -122.346008649822 47.6744723864029, -122.345985713408 47.6744515262775, -122.345962274995 47.6744308437389, -122.345939346093 47.6744102404205, -122.345915407691 47.6743898217777, -122.345891471799 47.6743694887354, -122.345867539664 47.6743492840963, -122.345843104304 47.6743292149421, -122.345818672689 47.6743092738401, -122.345793737331 47.6742894682293, -122.345768806985 47.674269834175, -122.34574337163 47.6742502921071, -122.345717940041 47.6742308787927, -122.345692006464 47.6742116434137, -122.345666076642 47.674192536437, -122.345640150577 47.6741735578627, -122.344897905857 47.6736916881744, -122.344393544584 47.6731878075112, -122.344369438002 47.673161563858, -122.344350015147 47.6731393283662, -122.344330081596 47.6731169711869, -122.344311160051 47.6730945149437, -122.344292234788 47.6730719302889, -122.344273812777 47.673049210148, -122.344255388293 47.6730264043986, -122.344237468833 47.67300350631, -122.344219545657 47.6729804798103, -122.34420212574 47.6729573181759, -122.344185212081 47.6729341066548, -122.344168294704 47.6729107667229, -122.34415188236 47.6728873348036, -122.344135974508 47.6728638102023, -122.344120062938 47.6728401571904, -122.344104148884 47.6728164182198, -122.3440892486 47.6727926233352, -122.344074344068 47.6727686996965, -122.344059438315 47.6727447336037, -122.344045543303 47.6727206252973, -122.344031647579 47.6726964741796, -122.344017747616 47.6726721946586, -122.344004353905 47.6726478652528, -122.343991465222 47.6726234438612, -122.343979082281 47.6725989729427, -122.343966696853 47.6725744160666, -122.343954308948 47.6725497735835, -122.343942934287 47.6725250751955, -122.343931557139 47.6725002908499, -122.343920177513 47.6724754208975, -122.343909812881 47.6724505374858, -122.343899443997 47.6724255253209, -122.343889075134 47.6724005135058, -122.343879718775 47.6723754026261, -122.343870360651 47.672350248599, -122.343861001821 47.6723250521123, -122.343852655688 47.6722997990272, -122.343843800105 47.6722744670578, -122.34383595899 47.672249121637, -122.343828115396 47.6722236906101, -122.343820779308 47.6721982532048, -122.343813947688 47.6721727227699, -122.343807116606 47.6721471926785, -122.343800790735 47.672121613069, -122.343794464146 47.6720959906495, -122.34378915202 47.6720703547793, -122.343783837412 47.6720446333033, -122.343778524042 47.672018954279, -122.343773715688 47.6719931832711, -122.343769414305 47.6719674055414, -122.343765619884 47.6719416207391, -122.343761824753 47.6719157934778, -122.343758536582 47.6718899591439, -122.343755754667 47.6718640756295, -122.343752972744 47.6718381917642, -122.343751739629 47.67181323009, -122.343751492865 47.6717872701443, -122.343749724879 47.6717613728357, -122.343746942965 47.6717354889702, -122.343743147858 47.671709661708, -122.343738847758 47.6716839267797, -122.343733028208 47.6716582972839, -122.343725689748 47.6716327739155, -122.343717847554 47.671607386034, -122.343708994642 47.671582139659, -122.343699133522 47.6715571210975, -122.343688261696 47.6715322443929, -122.343676381135 47.6715075951573, -122.343663492889 47.6714831737275, -122.34364959591 47.671458979766, -122.343634693207 47.6714350988712, -122.34361877909 47.6714113173727, -122.343603376406 47.6713877003691, -122.343586963543 47.6713642252133, -122.343570046946 47.6713408851911, -122.343552627868 47.6713177234559, -122.343535211803 47.6712946469658, -122.343517294501 47.6712717915651, -122.343498364753 47.6712490355727, -122.343479441749 47.6712264932332, -122.343460522503 47.6712040796497, -122.343440593288 47.6711818507283, -122.343420162116 47.6711598000854, -122.343399736445 47.6711379202922, -122.343378807777 47.671116218791, -122.343357377142 47.6710946952168, -122.343335445275 47.6710733927298, -122.343313010197 47.6710522253667, -122.343290582599 47.6710313148156, -122.343267144313 47.6710105461142, -122.343243712997 47.6709900345824, -122.343219778473 47.6709696581733, -122.343195851958 47.6709495389198, -122.343171423671 47.6709296400571, -122.343145986483 47.6709099265396, -122.343121062478 47.6708904199607, -122.343095131009 47.670871183995, -122.343069205052 47.6708521192276, -122.343042779628 47.6708333183402, -122.343015852443 47.6708147381926, -122.342988425058 47.6707963787639, -122.342961004632 47.6707782761521, -122.342933590462 47.6707603882493, -122.342905169328 47.6707427702483, -122.342876754441 47.6707253666049, -122.342847840075 47.6707082264886, -122.342818932678 47.6706913435395, -122.342789017086 47.6706746880384, -122.342759617689 47.6706583254248, -122.342729210107 47.6706421906094, -122.342698811245 47.6706263554054, -122.342668418626 47.670610734558, -122.342637527254 47.6705954200455, -122.342606136412 47.6705803694086, -122.342574245574 47.670565582303, -122.342542870937 47.6705510884359, -122.342510488818 47.6705368644717, -122.341536132237 47.6702371791038, -122.340924268323 47.6700484103442, -122.340890520367 47.6700395599196, -122.34085726302 47.6700301031724, -122.340824497725 47.6700201257224, -122.340792222002 47.6700095419644, -122.340759930663 47.669998401403, -122.340728637606 47.669986690622, -122.340697329137 47.6699744658547, -122.340666513773 47.6699617207234, -122.340636697406 47.669948447833, -122.340606864917 47.6699346184983, -122.340578033715 47.6699203045453, -122.340549187104 47.6699054766074, -122.34052134178 47.6698901640522, -122.340493989757 47.6698743736014, -122.340467132805 47.669858148402, -122.340440769155 47.6698414453077, -122.340415406792 47.6698242575984, -122.340390540223 47.6698066779514, -122.340366170679 47.6697887488192, -122.340340290972 47.6697712253839, -122.340315919499 47.6697532106285, -122.340288929275 47.6697324026858, -122.340264500721 47.6697124179372, -122.340241075418 47.6696920341884, -122.340217639676 47.6696713076683, -122.340195210196 47.6696502680984, -122.340173785216 47.6696288726834, -122.340152857771 47.6696071274278, -122.340132428613 47.669585076194, -122.340113006425 47.6695627543711, -122.340094083021 47.6695401258623, -122.340076164836 47.6695171843201, -122.340058747205 47.6694939792394, -122.340017468094 47.6694703611258, -122.340018094829 47.669439462271, -122.340018846127 47.6693953660748, -122.340021771514 47.669198716564, -122.340026409396 47.6687810557474, -122.340032268235 47.668755614529, -122.340037618902 47.6687301375634, -122.340042462098 47.6687046669585, -122.340047304048 47.6686791535506, -122.340051637817 47.6686536040447, -122.340055971591 47.6686280548895, -122.340059796656 47.6686024692924, -122.340063114263 47.6685768904071, -122.340066431144 47.668551268712, -122.340069747504 47.6685256470237, -122.340072555684 47.6684999892376, -122.340074856928 47.6684743381566, -122.34007715641 47.6684486442795, -122.340082471836 47.667914353136, -122.340086900669 47.6670869356763, -122.340087969201 47.6664061318327, -122.340099824506 47.6657298978586, -122.340202545541 47.6650376379612, -122.340449279385 47.6650425998776, -122.342697946464 47.6650225937497, -122.343218691111 47.6650108080465, -122.344520287628 47.6649984316009, -122.345091959432 47.6650105968045, -122.346067549327 47.6650414741391, -122.346093435108 47.6650243357179, -122.346125026488 47.66501149119, -122.346159298506 47.6650035812492, -122.346230329133 47.6650034517696, -122.346449839817 47.664996980288, -122.347307566662 47.6650052913031))\"]]]})")}
                , document.currentScript.parentElement);</script></div></div>

::: {.sourceClojure}
```clojure
(def parks-geojson
  (read-geogson-gz
   "data/Seattle/Park_Boundary_(details).geojson.gz"))
```
:::

::: {.sourceClojure}
```clojure
(count parks-geojson)
```
:::

::: {.printedClojure}
```clojure
2809

```
:::

::: {.sourceClojure}
```clojure
(->> parks-geojson
     (take 5)
     kind/portal)
```
:::

<div style="max-height:600px;overflow-y:auto;"><div><script>portal_api.embed().renderOutputItem(
                {'mime': 'x-application/edn',
                 'text': (() => "({^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 442]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SE_ANNO_CAD_DATA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SDQL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"QL-D1\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 207882]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_CRT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PIN]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"4006000485\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ADDRESS]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \" \"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.4691943312522366E-6]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA_NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"East Duwamish GS: S Chicago St\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAMEFLAG]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 9]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_EDT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SUBPARCEL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 9851]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OWNER]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"EAST DUWAMISH GREENBELT\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :USE_]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GlobalID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"{D4B7025E-1135-4232-88AB-CBF72932E6AE}\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :AMWOID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"PROPERTY-EDUWSC\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :MAINT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :REVIEW_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2004-04-08T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :LEASE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"N\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ACQ_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"1997-10-21T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.005215887160444538]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.MultiPolygon 0x40d3f919 \"MULTIPOLYGON (((-122.28235899499998 47.525165833000074, -122.28168484899999 47.525164389000054, -122.28168307199996 47.52516438600003, -122.28145050399996 47.52516388600003, -122.281450582 47.525147437000044, -122.28092621899998 47.525146310000025, -122.28092721899998 47.52433074500004, -122.28129411599997 47.52433142700005, -122.28247185299995 47.52433360800006, -122.28270306299999 47.52433403400005, -122.28270162899997 47.52516656600005, -122.28235899499998 47.525165833000074)))\"]]]} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 443]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SE_ANNO_CAD_DATA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SDQL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"QL-D1\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 207883]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_CRT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PIN]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"0603001220\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ADDRESS]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \" \"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.460570191594512E-7]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA_NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"East Duwamish GS: S Chicago St\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAMEFLAG]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 9]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_EDT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SUBPARCEL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 4779]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OWNER]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"EAST DUWAMISH GREENBELT\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :USE_]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GlobalID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"{26B4F4BC-F9AE-42D4-B062-51387C6D9FFF}\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :AMWOID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"PROPERTY-EDUWC\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :MAINT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :REVIEW_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2004-04-08T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :LEASE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"N\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ACQ_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"1994-10-06T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.0015461198840460832]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.MultiPolygon 0x58cfc71a \"MULTIPOLYGON (((-122.28304862799996 47.52231724600006, -122.28304832999999 47.52242690400004, -122.28304803199995 47.52253656500005, -122.28304773399998 47.52264622200005, -122.28260370699996 47.52264502600008, -122.28260405999998 47.522588839000036, -122.28260414399995 47.52253536900008, -122.28260449199996 47.522316051000075, -122.28304862799996 47.52231724600006)))\"]]]} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 443]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SE_ANNO_CAD_DATA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SDQL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"QL-D1\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 207884]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_CRT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PIN]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"0603001220\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ADDRESS]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \" \"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 9.743577447048599E-8]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA_NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"East Duwamish GS: S Chicago St\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAMEFLAG]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 9]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_EDT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SUBPARCEL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 4711]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OWNER]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"EAST DUWAMISH GREENBELT\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :USE_]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GlobalID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"{E97D7F7F-2666-4008-A905-2F416A66C2A1}\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :AMWOID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"PROPERTY-EDUWC\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :MAINT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :REVIEW_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2004-04-08T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :LEASE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"N\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ACQ_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"1994-10-06T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.0013271653095071236]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.MultiPolygon 0x8cfa074 \"MULTIPOLYGON (((-122.28304922499996 47.52209792800005, -122.28304892699998 47.52220758500005, -122.28304862799996 47.52231724600006, -122.28260449199996 47.522316051000075, -122.28260466499995 47.522206389000075, -122.28260483899999 47.522096730000044, -122.28304922499996 47.52209792800005)))\"]]]} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 443]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SE_ANNO_CAD_DATA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SDQL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"QL-D1\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 207885]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_CRT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PIN]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"0603001220\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ADDRESS]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \" \"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 4.87386722719263E-8]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA_NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"East Duwamish GS: S Chicago St\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAMEFLAG]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 9]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_EDT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SUBPARCEL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 4779]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OWNER]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"EAST DUWAMISH GREENBELT\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :USE_]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GlobalID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"{C28A4700-BB4F-4C25-928E-57022F6D001B}\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :AMWOID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"PROPERTY-EDUWC\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :MAINT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :REVIEW_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2004-04-08T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :LEASE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"N\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ACQ_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"1994-10-06T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.0011082207640129814]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.MultiPolygon 0x640bf559 \"MULTIPOLYGON (((-122.28304952299999 47.52198826600005, -122.28304922499996 47.52209792800005, -122.28260483899999 47.522096730000044, -122.28260501299997 47.52198707100007, -122.28304952299999 47.52198826600005)))\"]]]} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :properties]] {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 443]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SE_ANNO_CAD_DATA]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SDQL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"QL-D1\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OBJECTID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 207886]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_CRT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PIN]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"0603001220\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ADDRESS]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \" \"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Area]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 9.757207624044397E-8]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :PMA_NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"East Duwamish GS: S Chicago St\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAMEFLAG]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 9]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GIS_EDT_DT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2024-01-19T14:07:23Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SUBPARCEL]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 4712]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :OWNER]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :NAME]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"EAST DUWAMISH GREENBELT\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :USE_]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :GlobalID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"{4DB6A932-327A-4E2E-AC8A-C068D114AA61}\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :AMWOID]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"PROPERTY-EDUWC\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :MAINT]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"DPR\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :REVIEW_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"2004-04-08T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :LEASE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"N\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ACQ_DATE]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"1994-10-06T00:00:00Z\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :SHAPE_Length]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.0013284113092379031]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geometry]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector #object[org.locationtech.jts.geom.MultiPolygon 0x3b4fd3f0 \"MULTIPOLYGON (((-122.28305071699998 47.52154962900005, -122.28305041899995 47.52165928900007, -122.28305012099997 47.521768948000044, -122.28260536 47.52176775000004, -122.28260570799995 47.52154843200003, -122.28305071699998 47.52154962900005)))\"]]]})")}
                , document.currentScript.parentElement);</script></div></div>

## Coordinate conversions

Both datasets use the [WGS84](https://en.wikipedia.org/wiki/World_Geodetic_System)
coordinate system.
For area computations, etc., we need to convert them to a coordinate system
which is locally correct in terms of distances in a region around Seattle.

[EPSG:4326](https://epsg.io/4326)

::: {.sourceClojure}
```clojure
(def wgs84-crs (crs/create-crs 4326))
```
:::

[EPSG:2285](https://epsg.io/2285)

United States (USA) - Oregon and Washington. [1 3]:

|      Center coordinates |                                Projected bounds |                      WGS84 bounds |
|-------------------------|-------------------------------------------------|-----------------------------------|
| [1692592.39 -541752.55] | [[559165.71 -1834123.81] [2832684.98 777497.1]] | [[-124.79 41.98] [-116.47 49.05]] |

::: {.sourceClojure}
```clojure
(def Seattle-crs (crs/create-crs 2285))
```
:::

::: {.sourceClojure}
```clojure
(def crs-transform
  (crs/create-transform wgs84-crs Seattle-crs))
```
:::

::: {.sourceClojure}
```clojure
(defn wgs84->Seattle
  "Transforming latitude-longitude coordinates
  to local Eucledian coordinates around Seattle."
  [geometry]
  (jts/transform-geom geometry crs-transform))
```
:::

## Some geometrical functions

::: {.sourceClojure}
```clojure
(defn area [^Geometry geometry]
  (.getArea geometry))
```
:::

::: {.sourceClojure}
```clojure
(defn buffer [^Geometry geometry radius]
  (.buffer geometry radius))
```
:::

::: {.sourceClojure}
```clojure
(defn intersection [^Geometry geometry1
                    ^Geometry geometry2]
  (.intersection geometry1
                 geometry2))
```
:::

## Preproessed datasets

::: {.sourceClojure}
```clojure
(defn geojson->dataset [geojson dataset-name]
  (-> geojson
      (->> (map (fn [{:keys [geometry properties]}]
                  (assoc properties :geometry geometry))))
      tc/dataset
      (tc/map-columns :geometry [:geometry]
                      wgs84->Seattle)
      (tc/set-dataset-name dataset-name)))
```
:::

::: {.sourceClojure}
```clojure
(def neighborhoods
  (-> neighborhoods-geojson
      (geojson->dataset "Seattle neighborhoods")))
```
:::

::: {.sourceClojure}
```clojure
(-> neighborhoods
    (tc/drop-columns [:geometry])
    kind/table)
```
:::

<div style="max-height:600px;overflow-y:auto;"><table class="table"><thead><tr><th>OBJECTID</th><th>L_HOOD</th><th>S_HOOD</th><th>S_HOOD_ALT_NAMES</th><th>Shape__Area</th><th>Shape__Length</th></tr></thead><tbody><tr><td><div><p>27</p></div></td><td><div><p>Ballard</p></div></td><td><div><p>Loyal Heights</p></div></td><td><div></div></td><td><div><p>2.13206555455933E7</p></div></td><td><div><p>18831.00959637</p></div></td></tr><tr><td><div><p>28</p></div></td><td><div><p>Ballard</p></div></td><td><div><p>Ballard</p></div></td><td><div><p>Adams</p></div></td><td><div><p>2.25521329700012E7</p></div></td><td><div><p>29926.3393002841</p></div></td></tr><tr><td><div><p>29</p></div></td><td><div><p>Ballard</p></div></td><td><div><p>Whittier Heights</p></div></td><td><div></div></td><td><div><p>1.41956874919434E7</p></div></td><td><div><p>15934.4392663199</p></div></td></tr><tr><td><div><p>30</p></div></td><td><div><p>Ballard</p></div></td><td><div><p>West Woodland</p></div></td><td><div></div></td><td><div><p>2.21993668730164E7</p></div></td><td><div><p>21789.6510873493</p></div></td></tr><tr><td><div><p>31</p></div></td><td><div><p>North Central</p></div></td><td><div><p>Phinney Ridge</p></div></td><td><div><p>Woodland Park</p></div></td><td><div><p>3.21231178777466E7</p></div></td><td><div><p>27120.7859379681</p></div></td></tr><tr><td><div><p>32</p></div></td><td><div><p>North Central</p></div></td><td><div><p>Wallingford</p></div></td><td><div><p>Meridian, Tangle Town, Northlake</p></div></td><td><div><p>4.20683426137695E7</p></div></td><td><div><p>33040.2469861198</p></div></td></tr><tr><td><div><p>33</p></div></td><td><div><p>North Central</p></div></td><td><div><p>Fremont</p></div></td><td><div></div></td><td><div><p>2.65037565718689E7</p></div></td><td><div><p>25999.2849357187</p></div></td></tr><tr><td><div><p>34</p></div></td><td><div><p>North Central</p></div></td><td><div><p>Green Lake</p></div></td><td><div></div></td><td><div><p>3.73146297898865E7</p></div></td><td><div><p>25387.7074962486</p></div></td></tr><tr><td><div><p>35</p></div></td><td><div><p>Northeast</p></div></td><td><div><p>View Ridge</p></div></td><td><div></div></td><td><div><p>2.56129799440918E7</p></div></td><td><div><p>22657.0394732799</p></div></td></tr><tr><td><div><p>36</p></div></td><td><div><p>Northeast</p></div></td><td><div><p>Ravenna</p></div></td><td><div><p>University Village</p></div></td><td><div><p>3.67833915366516E7</p></div></td><td><div><p>31163.6208763331</p></div></td></tr><tr><td><div><p>37</p></div></td><td><div><p>Northeast</p></div></td><td><div><p>Sand Point</p></div></td><td><div></div></td><td><div><p>1.92498571397095E7</p></div></td><td><div><p>21396.6958008648</p></div></td></tr><tr><td><div><p>38</p></div></td><td><div><p>Northeast</p></div></td><td><div><p>Bryant</p></div></td><td><div></div></td><td><div><p>1.54850780333252E7</p></div></td><td><div><p>20928.0017243062</p></div></td></tr><tr><td><div><p>39</p></div></td><td><div><p>Northeast</p></div></td><td><div><p>Windermere</p></div></td><td><div><p>Hawthorne Hills</p></div></td><td><div><p>2.23639666230164E7</p></div></td><td><div><p>33332.8291968304</p></div></td></tr><tr><td><div><p>40</p></div></td><td><div><p>Northeast</p></div></td><td><div><p>Laurelhurst</p></div></td><td><div></div></td><td><div><p>1.90517768183594E7</p></div></td><td><div><p>26489.2422321737</p></div></td></tr><tr><td><div><p>41</p></div></td><td><div><p>Northeast</p></div></td><td><div><p>Roosevelt</p></div></td><td><div><p>Fairview</p></div></td><td><div><p>2.1491594324707E7</p></div></td><td><div><p>22866.0797374364</p></div></td></tr><tr><td><div><p>42</p></div></td><td><div><p>University District</p></div></td><td><div><p>University of Washington</p></div></td><td><div></div></td><td><div><p>2.55236751180115E7</p></div></td><td><div><p>30983.2126641678</p></div></td></tr><tr><td><div><p>43</p></div></td><td><div><p>Queen Anne</p></div></td><td><div><p>East Queen Anne</p></div></td><td><div></div></td><td><div><p>1.93546995965576E7</p></div></td><td><div><p>21488.397378299</p></div></td></tr><tr><td><div><p>44</p></div></td><td><div><p>Queen Anne</p></div></td><td><div><p>West Queen Anne</p></div></td><td><div></div></td><td><div><p>1.79749859528503E7</p></div></td><td><div><p>20631.7057292923</p></div></td></tr><tr><td><div><p>45</p></div></td><td><div><p>Queen Anne</p></div></td><td><div><p>Lower Queen Anne</p></div></td><td><div><p>Uptown, Seattle Center</p></div></td><td><div><p>1.75156244566956E7</p></div></td><td><div><p>20496.7289222394</p></div></td></tr><tr><td><div><p>46</p></div></td><td><div><p>Queen Anne</p></div></td><td><div><p>North Queen Anne</p></div></td><td><div></div></td><td><div><p>2.9604288333252E7</p></div></td><td><div><p>26753.5542817429</p></div></td></tr><tr><td><div><p>47</p></div></td><td><div><p>Cascade</p></div></td><td><div><p>Westlake</p></div></td><td><div></div></td><td><div><p>3645184.07894897</p></div></td><td><div><p>11017.3231739615</p></div></td></tr><tr><td><div><p>48</p></div></td><td><div><p>Cascade</p></div></td><td><div><p>Eastlake</p></div></td><td><div></div></td><td><div><p>7426907.96139526</p></div></td><td><div><p>16672.5117837403</p></div></td></tr><tr><td><div><p>49</p></div></td><td><div><p>Cascade</p></div></td><td><div><p>South Lake Union</p></div></td><td><div></div></td><td><div><p>1.6107105419342E7</p></div></td><td><div><p>29323.5462843847</p></div></td></tr><tr><td><div><p>50</p></div></td><td><div><p>Magnolia</p></div></td><td><div><p>Lawton Park</p></div></td><td><div></div></td><td><div><p>5.5091525290863E7</p></div></td><td><div><p>38766.0673349107</p></div></td></tr><tr><td><div><p>51</p></div></td><td><div><p>Magnolia</p></div></td><td><div><p>Briarcliff</p></div></td><td><div><p>Carleton Park</p></div></td><td><div><p>2.65509365782471E7</p></div></td><td><div><p>26609.7912261135</p></div></td></tr><tr><td><div><p>52</p></div></td><td><div><p>Magnolia</p></div></td><td><div><p>Southeast Magnolia</p></div></td><td><div></div></td><td><div><p>1.84692638882751E7</p></div></td><td><div><p>20223.1801501522</p></div></td></tr><tr><td><div><p>53</p></div></td><td><div><p>Central Area</p></div></td><td><div><p>Madrona</p></div></td><td><div></div></td><td><div><p>1.38454828085938E7</p></div></td><td><div><p>17052.9427067693</p></div></td></tr><tr><td><div><p>54</p></div></td><td><div><p>Central Area</p></div></td><td><div><p>Harrison/Denny-Blaine</p></div></td><td><div></div></td><td><div><p>1.36033956731873E7</p></div></td><td><div><p>17241.2743191595</p></div></td></tr><tr><td><div><p>55</p></div></td><td><div><p>Central Area</p></div></td><td><div><p>Minor</p></div></td><td><div><p>Central District, Squire Park</p></div></td><td><div><p>1.7933144708252E7</p></div></td><td><div><p>18241.5487859812</p></div></td></tr><tr><td><div><p>56</p></div></td><td><div><p>Central Area</p></div></td><td><div><p>Leschi</p></div></td><td><div></div></td><td><div><p>1.80917413764954E7</p></div></td><td><div><p>20413.0560516882</p></div></td></tr><tr><td><div><p>57</p></div></td><td><div><p>Central Area</p></div></td><td><div><p>Mann</p></div></td><td><div><p>Central District, Garfield</p></div></td><td><div><p>1.11338288620605E7</p></div></td><td><div><p>17843.105758736</p></div></td></tr><tr><td><div><p>58</p></div></td><td><div><p>Central Area</p></div></td><td><div><p>Atlantic</p></div></td><td><div><p>Judkins Park, Jackson Place, Coleman</p></div></td><td><div><p>2.06649862726135E7</p></div></td><td><div><p>25426.2311626675</p></div></td></tr><tr><td><div><p>59</p></div></td><td><div><p>Downtown</p></div></td><td><div><p>Pike-Market</p></div></td><td><div><p>Pike Place Market</p></div></td><td><div><p>2343359.32580566</p></div></td><td><div><p>7326.58173024624</p></div></td></tr><tr><td><div><p>60</p></div></td><td><div><p>Downtown</p></div></td><td><div><p>Belltown</p></div></td><td><div><p>Denny Regrade</p></div></td><td><div><p>9845864.78594971</p></div></td><td><div><p>17836.7271544608</p></div></td></tr><tr><td><div><p>61</p></div></td><td><div><p>Downtown</p></div></td><td><div><p>International District</p></div></td><td><div><p>Chinatown, ID, Little Saigon</p></div></td><td><div><p>6169375.81655884</p></div></td><td><div><p>11772.3871410021</p></div></td></tr><tr><td><div><p>62</p></div></td><td><div><p>Downtown</p></div></td><td><div><p>Central Business District</p></div></td><td><div><p>Commercial Core, West Edge</p></div></td><td><div><p>9477398.61834717</p></div></td><td><div><p>18209.4628624588</p></div></td></tr><tr><td><div><p>63</p></div></td><td><div><p>Downtown</p></div></td><td><div><p>First Hill</p></div></td><td><div></div></td><td><div><p>9517568.47363281</p></div></td><td><div><p>13225.2335159542</p></div></td></tr><tr><td><div><p>64</p></div></td><td><div><p>Downtown</p></div></td><td><div><p>Yesler Terrace</p></div></td><td><div></div></td><td><div><p>5348937.24771118</p></div></td><td><div><p>9611.35354641661</p></div></td></tr><tr><td><div><p>65</p></div></td><td><div><p>Downtown</p></div></td><td><div><p>Pioneer Square</p></div></td><td><div></div></td><td><div><p>7545979.0869751</p></div></td><td><div><p>17297.5867148564</p></div></td></tr><tr><td><div><p>66</p></div></td><td><div><p>Interbay</p></div></td><td><div><p>Interbay</p></div></td><td><div></div></td><td><div><p>3.35039410921631E7</p></div></td><td><div><p>64207.5867611718</p></div></td></tr><tr><td><div><p>67</p></div></td><td><div><p>Greater Duwamish</p></div></td><td><div><p>SODO</p></div></td><td><div></div></td><td><div><p>4.96031675905914E7</p></div></td><td><div><p>38520.9885110863</p></div></td></tr><tr><td><div><p>68</p></div></td><td><div><p>Greater Duwamish</p></div></td><td><div><p>Georgetown</p></div></td><td><div></div></td><td><div><p>5.13050726461182E7</p></div></td><td><div><p>45963.6656769607</p></div></td></tr><tr><td><div><p>69</p></div></td><td><div><p>Greater Duwamish</p></div></td><td><div><p>South Park</p></div></td><td><div></div></td><td><div><p>2.94234521522369E7</p></div></td><td><div><p>30433.4048686311</p></div></td></tr><tr><td><div><p>70</p></div></td><td><div><p>Greater Duwamish</p></div></td><td><div><p>Harbor Island</p></div></td><td><div></div></td><td><div><p>1.78323007354431E7</p></div></td><td><div><p>24381.2966280601</p></div></td></tr><tr><td><div><p>71</p></div></td><td><div><p>West Seattle</p></div></td><td><div><p>Seaview</p></div></td><td><div></div></td><td><div><p>1.8463061797821E7</p></div></td><td><div><p>23122.2640032568</p></div></td></tr><tr><td><div><p>72</p></div></td><td><div><p>West Seattle</p></div></td><td><div><p>Gatewood</p></div></td><td><div><p>Morgan Junction</p></div></td><td><div><p>2.28217074689484E7</p></div></td><td><div><p>23801.2647005122</p></div></td></tr><tr><td><div><p>73</p></div></td><td><div><p>West Seattle</p></div></td><td><div><p>Arbor Heights</p></div></td><td><div></div></td><td><div><p>2.61973140573883E7</p></div></td><td><div><p>28162.4351386166</p></div></td></tr><tr><td><div><p>74</p></div></td><td><div><p>West Seattle</p></div></td><td><div><p>Alki</p></div></td><td><div></div></td><td><div><p>2.45834691841736E7</p></div></td><td><div><p>45568.1378536906</p></div></td></tr><tr><td><div><p>75</p></div></td><td><div><p>West Seattle</p></div></td><td><div><p>North Admiral</p></div></td><td><div><p>Belvidere</p></div></td><td><div><p>4.85814163202972E7</p></div></td><td><div><p>30687.7844700837</p></div></td></tr><tr><td><div><p>76</p></div></td><td><div><p>West Seattle</p></div></td><td><div><p>Fairmount Park</p></div></td><td><div></div></td><td><div><p>1.61539000976257E7</p></div></td><td><div><p>24955.7128414259</p></div></td></tr><tr><td><div><p>77</p></div></td><td><div><p>West Seattle</p></div></td><td><div><p>Genesee</p></div></td><td><div><p>Alaska Junction, West Seattle Junction</p></div></td><td><div><p>2.11649765813446E7</p></div></td><td><div><p>19870.8696089241</p></div></td></tr><tr><td><div><p>78</p></div></td><td><div><p>West Seattle</p></div></td><td><div><p>Fauntleroy</p></div></td><td><div><p>Endolyne, Arroyo Heights, Brace Point</p></div></td><td><div><p>3.38818638706665E7</p></div></td><td><div><p>42276.5317877774</p></div></td></tr><tr><td><div><p>79</p></div></td><td><div><p>Beacon Hill</p></div></td><td><div><p>North Beacon Hill</p></div></td><td><div><p>Jefferson Park</p></div></td><td><div><p>4.84759144557953E7</p></div></td><td><div><p>33865.4891739901</p></div></td></tr><tr><td><div><p>80</p></div></td><td><div><p>Beacon Hill</p></div></td><td><div><p>Mid-Beacon Hill</p></div></td><td><div></div></td><td><div><p>5.26204707883301E7</p></div></td><td><div><p>40522.1829275323</p></div></td></tr><tr><td><div><p>81</p></div></td><td><div><p>Beacon Hill</p></div></td><td><div><p>South Beacon Hill</p></div></td><td><div></div></td><td><div><p>3.84488268989563E7</p></div></td><td><div><p>38996.7151070849</p></div></td></tr><tr><td><div><p>82</p></div></td><td><div><p>Beacon Hill</p></div></td><td><div><p>Holly Park</p></div></td><td><div><p>New Holly</p></div></td><td><div><p>8444235.97859192</p></div></td><td><div><p>15848.3624185113</p></div></td></tr><tr><td><div><p>83</p></div></td><td><div><p>Rainier Valley</p></div></td><td><div><p>Brighton</p></div></td><td><div></div></td><td><div><p>1.8366938275177E7</p></div></td><td><div><p>18911.3293490837</p></div></td></tr><tr><td><div><p>84</p></div></td><td><div><p>Rainier Valley</p></div></td><td><div><p>Dunlap</p></div></td><td><div></div></td><td><div><p>1.96016012150879E7</p></div></td><td><div><p>20847.6531922997</p></div></td></tr><tr><td><div><p>85</p></div></td><td><div><p>Rainier Valley</p></div></td><td><div><p>Rainier Beach</p></div></td><td><div></div></td><td><div><p>3.31282361414948E7</p></div></td><td><div><p>34965.6132100475</p></div></td></tr><tr><td><div><p>86</p></div></td><td><div><p>Rainier Valley</p></div></td><td><div><p>Rainier View</p></div></td><td><div><p>Lake Ridge</p></div></td><td><div><p>1.82485661794434E7</p></div></td><td><div><p>34791.8218147105</p></div></td></tr><tr><td><div><p>87</p></div></td><td><div><p>Rainier Valley</p></div></td><td><div><p>Mount Baker</p></div></td><td><div><p>North Rainier</p></div></td><td><div><p>2.89869952343292E7</p></div></td><td><div><p>26318.9819054871</p></div></td></tr><tr><td><div><p>88</p></div></td><td><div><p>Rainier Valley</p></div></td><td><div><p>Columbia City</p></div></td><td><div><p>Columbia Heights</p></div></td><td><div><p>3.74065764927979E7</p></div></td><td><div><p>35177.0608039675</p></div></td></tr><tr><td><div><p>89</p></div></td><td><div><p>Delridge</p></div></td><td><div><p>Highland Park</p></div></td><td><div></div></td><td><div><p>3.98103334158325E7</p></div></td><td><div><p>31111.0630837714</p></div></td></tr><tr><td><div><p>90</p></div></td><td><div><p>Delridge</p></div></td><td><div><p>North Delridge</p></div></td><td><div><p>Avalon, Luna Park, Pigeon Point</p></div></td><td><div><p>2.94546565672607E7</p></div></td><td><div><p>23549.9313666304</p></div></td></tr><tr><td><div><p>91</p></div></td><td><div><p>Delridge</p></div></td><td><div><p>Riverview</p></div></td><td><div></div></td><td><div><p>3.30382671929626E7</p></div></td><td><div><p>25917.1176391015</p></div></td></tr><tr><td><div><p>92</p></div></td><td><div><p>Delridge</p></div></td><td><div><p>High Point</p></div></td><td><div></div></td><td><div><p>2.33430083368683E7</p></div></td><td><div><p>23180.3963596714</p></div></td></tr><tr><td><div><p>93</p></div></td><td><div><p>Delridge</p></div></td><td><div><p>South Delridge</p></div></td><td><div><p>White Center</p></div></td><td><div><p>1.79233162238464E7</p></div></td><td><div><p>23416.3405359794</p></div></td></tr><tr><td><div><p>94</p></div></td><td><div><p>Delridge</p></div></td><td><div><p>Roxhill</p></div></td><td><div><p>Westwood Village</p></div></td><td><div><p>1.87810598441162E7</p></div></td><td><div><p>22360.0472289145</p></div></td></tr><tr><td><div><p>95</p></div></td><td><div><p>Seward Park</p></div></td><td><div><p>Seward Park</p></div></td><td><div><p>Lakewood, Hillman City</p></div></td><td><div><p>4.38352790059662E7</p></div></td><td><div><p>52212.7868103531</p></div></td></tr><tr><td><div><p>96</p></div></td><td><div><p>Northeast</p></div></td><td><div><p>Wedgwood</p></div></td><td><div></div></td><td><div><p>3.05997136261597E7</p></div></td><td><div><p>23840.2187274324</p></div></td></tr><tr><td><div><p>97</p></div></td><td><div><p>Capitol Hill</p></div></td><td><div><p>Portage Bay</p></div></td><td><div><p>Roanoke Park</p></div></td><td><div><p>4421635.26721191</p></div></td><td><div><p>10013.2739563989</p></div></td></tr><tr><td><div><p>98</p></div></td><td><div><p>Capitol Hill</p></div></td><td><div><p>Montlake</p></div></td><td><div><p>North Capitol Hill</p></div></td><td><div><p>2.1474786741394E7</p></div></td><td><div><p>46165.83098345</p></div></td></tr><tr><td><div><p>99</p></div></td><td><div><p>Capitol Hill</p></div></td><td><div><p>Madison Park</p></div></td><td><div><p>Broadmoor, Washington Park</p></div></td><td><div><p>2.46809502223511E7</p></div></td><td><div><p>26230.4347480002</p></div></td></tr><tr><td><div><p>100</p></div></td><td><div><p>Capitol Hill</p></div></td><td><div><p>Broadway</p></div></td><td><div><p>Pike/Pine</p></div></td><td><div><p>3.02392405212402E7</p></div></td><td><div><p>26851.9474418256</p></div></td></tr><tr><td><div><p>101</p></div></td><td><div><p>Capitol Hill</p></div></td><td><div><p>Stevens</p></div></td><td><div><p>Interlaken Park, Miller Park, Madison-Miller</p></div></td><td><div><p>2.60395920790405E7</p></div></td><td><div><p>25522.3456368768</p></div></td></tr><tr><td><div><p>102</p></div></td><td><div><p>Lake City</p></div></td><td><div><p>Victory Heights</p></div></td><td><div></div></td><td><div><p>2.15127314890137E7</p></div></td><td><div><p>20753.0018992847</p></div></td></tr><tr><td><div><p>103</p></div></td><td><div><p>Lake City</p></div></td><td><div><p>Matthews Beach</p></div></td><td><div></div></td><td><div><p>3.09809783014832E7</p></div></td><td><div><p>31369.8925404597</p></div></td></tr><tr><td><div><p>104</p></div></td><td><div><p>Lake City</p></div></td><td><div><p>Meadowbrook</p></div></td><td><div></div></td><td><div><p>1.70348487789307E7</p></div></td><td><div><p>18770.2820324215</p></div></td></tr><tr><td><div><p>105</p></div></td><td><div><p>Lake City</p></div></td><td><div><p>Olympic Hills</p></div></td><td><div></div></td><td><div><p>2.58367421641541E7</p></div></td><td><div><p>19993.8160570763</p></div></td></tr><tr><td><div><p>106</p></div></td><td><div><p>Lake City</p></div></td><td><div><p>Cedar Park</p></div></td><td><div></div></td><td><div><p>2.04414858487244E7</p></div></td><td><div><p>22788.760382662</p></div></td></tr><tr><td><div><p>110</p></div></td><td><div><p>Northwest</p></div></td><td><div><p>Broadview</p></div></td><td><div></div></td><td><div><p>4.81134497303162E7</p></div></td><td><div><p>34640.309665739</p></div></td></tr><tr><td><div><p>111</p></div></td><td><div><p>Northwest</p></div></td><td><div><p>Bitter Lake</p></div></td><td><div></div></td><td><div><p>2.76903364438171E7</p></div></td><td><div><p>26446.2030540938</p></div></td></tr><tr><td><div><p>112</p></div></td><td><div><p>Northgate</p></div></td><td><div><p>Haller Lake</p></div></td><td><div></div></td><td><div><p>4.72030810796204E7</p></div></td><td><div><p>29413.5534484151</p></div></td></tr><tr><td><div><p>113</p></div></td><td><div><p>Northgate</p></div></td><td><div><p>Pinehurst</p></div></td><td><div><p>Jackson Park</p></div></td><td><div><p>2.94388508770142E7</p></div></td><td><div><p>26171.2717608103</p></div></td></tr><tr><td><div><p>114</p></div></td><td><div><p>Northwest</p></div></td><td><div><p>North Beach/Blue Ridge</p></div></td><td><div></div></td><td><div><p>3.10622649915771E7</p></div></td><td><div><p>32947.8059119899</p></div></td></tr><tr><td><div><p>115</p></div></td><td><div><p>Northgate</p></div></td><td><div><p>Licton Springs</p></div></td><td><div><p>North College Park</p></div></td><td><div><p>2.17047062611389E7</p></div></td><td><div><p>20132.8982458333</p></div></td></tr><tr><td><div><p>116</p></div></td><td><div><p>Northgate</p></div></td><td><div><p>Maple Leaf</p></div></td><td><div><p>Olympic View</p></div></td><td><div><p>3.43804707826233E7</p></div></td><td><div><p>25503.0574082691</p></div></td></tr><tr><td><div><p>117</p></div></td><td><div><p>Northwest</p></div></td><td><div><p>Crown Hill</p></div></td><td><div></div></td><td><div><p>1.58657504196777E7</p></div></td><td><div><p>18997.8080379411</p></div></td></tr><tr><td><div><p>118</p></div></td><td><div><p>Northwest</p></div></td><td><div><p>Greenwood</p></div></td><td><div></div></td><td><div><p>4.20445636731262E7</p></div></td><td><div><p>26501.5265911049</p></div></td></tr><tr><td><div><p>119</p></div></td><td><div><p>Ballard</p></div></td><td><div><p>Sunset Hill</p></div></td><td><div><p>Golden Gardens, Shilshole</p></div></td><td><div><p>2.43356204689941E7</p></div></td><td><div><p>29416.7300633571</p></div></td></tr><tr><td><div><p>121</p></div></td><td><div><p>University District</p></div></td><td><div><p>University District</p></div></td><td><div></div></td><td><div><p>1.36862548569946E7</p></div></td><td><div><p>21581.6459789299</p></div></td></tr><tr><td><div><p>123</p></div></td><td><div><p>University District</p></div></td><td><div><p>University Heights</p></div></td><td><div><p>Cowen Park</p></div></td><td><div><p>1.03757480522461E7</p></div></td><td><div><p>15163.9069096811</p></div></td></tr><tr><td><div><p>124</p></div></td><td><div><p>Downtown</p></div></td><td><div><p>Denny Triangle</p></div></td><td><div><p>Denny Regrade</p></div></td><td><div><p>5128172.31045532</p></div></td><td><div><p>10574.1779826691</p></div></td></tr><tr><td><div><p>126</p></div></td><td><div><p>Greater Duwamish</p></div></td><td><div><p>Industrial District</p></div></td><td><div></div></td><td><div><p>6.24341310114746E7</p></div></td><td><div><p>88995.7569839975</p></div></td></tr></tbody></table></div>

::: {.sourceClojure}
```clojure
(def parks
  (-> parks-geojson
      (geojson->dataset "Seattle parks")
      (tc/map-columns :geometry
                      [:geometry]
                      ;; avoiding some [linestring pathologies](https://gis.stackexchange.com/questions/50399/fixing-non-noded-intersection-problem-using-postgis)
                      #(buffer % 1))))
```
:::

::: {.sourceClojure}
```clojure
(delay
  (-> parks
      (tc/drop-columns [:geometry])
      (tc/head 20)
      kind/table))
```
:::

<div style="max-height:600px;overflow-y:auto;"><table class="table"><thead><tr><th>SE_ANNO_CAD_DATA</th><th>NAMEFLAG</th><th>ADDRESS</th><th>MAINT</th><th>LEASE</th><th>PMA_NAME</th><th>SUBPARCEL</th><th>PMA</th><th>REVIEW_DATE</th><th>GlobalID</th><th>OBJECTID</th><th>AMWOID</th><th>SDQL</th><th>USE_</th><th>PIN</th><th>GIS_EDT_DT</th><th>SHAPE_Area</th><th>SHAPE_Length</th><th>GIS_CRT_DT</th><th>NAME</th><th>OWNER</th><th>ACQ_DATE</th></tr></thead><tbody><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>East Duwamish GS: S Chicago St</p></div></td><td><div><p>9851</p></div></td><td><div><p>442</p></div></td><td><div><p>2004-04-08T00:00:00Z</p></div></td><td><div><p>{D4B7025E-1135-4232-88AB-CBF72932E6AE}</p></div></td><td><div><p>207882</p></div></td><td><div><p>PROPERTY-EDUWSC</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>4006000485</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>1.4691943312522366E-6</p></div></td><td><div><p>0.005215887160444538</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>EAST DUWAMISH GREENBELT</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1997-10-21T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>East Duwamish GS: S Chicago St</p></div></td><td><div><p>4779</p></div></td><td><div><p>443</p></div></td><td><div><p>2004-04-08T00:00:00Z</p></div></td><td><div><p>{26B4F4BC-F9AE-42D4-B062-51387C6D9FFF}</p></div></td><td><div><p>207883</p></div></td><td><div><p>PROPERTY-EDUWC</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>0603001220</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>1.460570191594512E-7</p></div></td><td><div><p>0.0015461198840460832</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>EAST DUWAMISH GREENBELT</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1994-10-06T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>East Duwamish GS: S Chicago St</p></div></td><td><div><p>4711</p></div></td><td><div><p>443</p></div></td><td><div><p>2004-04-08T00:00:00Z</p></div></td><td><div><p>{E97D7F7F-2666-4008-A905-2F416A66C2A1}</p></div></td><td><div><p>207884</p></div></td><td><div><p>PROPERTY-EDUWC</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>0603001220</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>9.743577447048599E-8</p></div></td><td><div><p>0.0013271653095071236</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>EAST DUWAMISH GREENBELT</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1994-10-06T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>East Duwamish GS: S Chicago St</p></div></td><td><div><p>4779</p></div></td><td><div><p>443</p></div></td><td><div><p>2004-04-08T00:00:00Z</p></div></td><td><div><p>{C28A4700-BB4F-4C25-928E-57022F6D001B}</p></div></td><td><div><p>207885</p></div></td><td><div><p>PROPERTY-EDUWC</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>0603001220</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>4.87386722719263E-8</p></div></td><td><div><p>0.0011082207640129814</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>EAST DUWAMISH GREENBELT</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1994-10-06T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>East Duwamish GS: S Chicago St</p></div></td><td><div><p>4712</p></div></td><td><div><p>443</p></div></td><td><div><p>2004-04-08T00:00:00Z</p></div></td><td><div><p>{4DB6A932-327A-4E2E-AC8A-C068D114AA61}</p></div></td><td><div><p>207886</p></div></td><td><div><p>PROPERTY-EDUWC</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>0603001220</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>9.757207624044397E-8</p></div></td><td><div><p>0.0013284113092379031</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>EAST DUWAMISH GREENBELT</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1994-10-06T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Genesee Park and Playfield</p></div></td><td><div><p>4618</p></div></td><td><div><p>409</p></div></td><td><div><p>1899-12-30T00:00:01Z</p></div></td><td><div><p>{AD2E47C9-323B-4DDE-8186-98A4FC79C3F8}</p></div></td><td><div><p>207887</p></div></td><td><div><p>PROPERTY-GENPK</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>4154300585</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>2.892289652506793E-6</p></div></td><td><div><p>0.007000440212562059</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>GENESEE PARK AND PLAYFIELD</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1996-06-03T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div><p>5244 SW JACOBSEN ROAD</p></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Wolf Creek Ravine Natural Area</p></div></td><td><div><p>16397</p></div></td><td><div><p>278</p></div></td><td><div><p>2004-04-19T00:00:00Z</p></div></td><td><div><p>{A7E54352-0DC3-47E4-B562-DAA0F18B78E2}</p></div></td><td><div><p>207888</p></div></td><td><div><p>PROPERTY-WLFCRAV</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>5344200125</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>6.25557675764001E-8</p></div></td><td><div><p>0.0010504796990982068</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>WOLF CREEK RAVINE NATURAL AREA</p></div></td><td><div><p>DPR</p></div></td><td><div><p>2004-04-07T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Jefferson Park</p></div></td><td><div><p>15550</p></div></td><td><div><p>114</p></div></td><td><div><p>2004-04-08T00:00:00Z</p></div></td><td><div><p>{B82B7BD2-DCD9-49A2-BE5D-30C1D9BF4392}</p></div></td><td><div><p>207889</p></div></td><td><div><p>PROPERTY-JEFFPK</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>1624049270</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>3.2670040661028276E-6</p></div></td><td><div><p>0.018380332716286137</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>JEFFERSON PARK</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1988-07-25T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Queen Anne Boulevard</p></div></td><td><div><p>753</p></div></td><td><div><p>328</p></div></td><td><div><p>2004-04-09T00:00:00Z</p></div></td><td><div><p>{3DA31C7B-C33D-4DD9-9092-71B1DA135BC8}</p></div></td><td><div><p>207890</p></div></td><td><div><p>PROPERTY-QABL</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>2533300180</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>5.790553187521671E-9</p></div></td><td><div><p>4.111515370853996E-4</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>QUEEN ANNE BOULEVARD</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1910-07-25T00:00:01Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Queen Anne Boulevard</p></div></td><td><div><p>4688</p></div></td><td><div><p>328</p></div></td><td><div><p>2004-04-09T00:00:00Z</p></div></td><td><div><p>{D3DA12EE-31E0-4476-95CE-1739E8FF8550}</p></div></td><td><div><p>207891</p></div></td><td><div><p>PROPERTY-QABL</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>2533300180</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>5.139665582905777E-9</p></div></td><td><div><p>3.9228813174494234E-4</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>QUEEN ANNE BOULEVARD</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1910-07-25T00:00:01Z</p></div></td></tr><tr><td><div></div></td><td><div><p>7</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Ravenna Woods</p></div></td><td><div><p>15807</p></div></td><td><div><p>4411</p></div></td><td><div><p>2004-05-05T00:00:00Z</p></div></td><td><div><p>{B1A2F3C6-C43A-4600-8064-A3DEFAE61DDC}</p></div></td><td><div><p>207892</p></div></td><td><div><p>PROPERTY-RAVWOOD</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>0925049168</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>5.585829095854119E-7</p></div></td><td><div><p>0.0030915009702507513</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>RAVENNA WOODS</p></div></td><td><div><p>DPR</p></div></td><td><div><p>2002-07-02T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Montlake Playfield</p></div></td><td><div><p>1507</p></div></td><td><div><p>376</p></div></td><td><div><p>1998-10-15T00:00:00Z</p></div></td><td><div><p>{BF38EE1A-DBAB-400C-B083-B3F8B6A1EB39}</p></div></td><td><div><p>207893</p></div></td><td><div><p>PROPERTY-MTLKPF</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>4089400080</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>3.917576385699785E-7</p></div></td><td><div><p>0.0026768636765498316</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>MONTLAKE PLAYFIELD</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1933-12-31T00:00:01Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Montlake Playfield</p></div></td><td><div><p>1507</p></div></td><td><div><p>376</p></div></td><td><div><p>2004-03-30T00:00:00Z</p></div></td><td><div><p>{4CC47610-4927-465F-A346-04F66008D480}</p></div></td><td><div><p>207894</p></div></td><td><div><p>PROPERTY-MTLKPF</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>6788202280</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>1.1273410584671711E-6</p></div></td><td><div><p>0.004459900867682873</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>MONTLAKE PLAYFIELD</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1933-12-31T00:00:01Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Montlake Playfield</p></div></td><td><div><p>1507</p></div></td><td><div><p>376</p></div></td><td><div><p>2004-03-30T00:00:00Z</p></div></td><td><div><p>{10310B09-822A-4344-95CC-2D5D90C2466C}</p></div></td><td><div><p>207895</p></div></td><td><div><p>PROPERTY-MTLKPF</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>6788202280</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>1.4591960880701082E-6</p></div></td><td><div><p>0.006312257575513224</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>MONTLAKE PLAYFIELD</p></div></td><td><div><p>DPR</p></div></td><td><div><p>1933-12-31T00:00:01Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div><p>4357 PALATINE AVE N</p></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Fremont Peak Park</p></div></td><td><div><p>16454</p></div></td><td><div><p>4424</p></div></td><td><div><p>2004-10-06T00:00:00Z</p></div></td><td><div><p>{A13D75B6-B355-4BDF-84CF-4D2838170201}</p></div></td><td><div><p>207896</p></div></td><td><div><p>PROPERTY-FRMPKPK</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>6610000810</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>6.118914081332531E-8</p></div></td><td><div><p>0.0011669443524576426</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>FREMONT PEAK PARK</p></div></td><td><div><p>DPR</p></div></td><td><div><p>2004-09-30T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>SW Queen Anne Greenbelt</p></div></td><td><div><p>16459</p></div></td><td><div><p>234</p></div></td><td><div><p>2005-01-06T00:00:00Z</p></div></td><td><div><p>{A13C70F6-F0AE-4E55-A12C-990BBC545F8D}</p></div></td><td><div><p>207897</p></div></td><td><div><p>PROPERTY-SWQAGRB</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>7705100037</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>5.565195258199712E-9</p></div></td><td><div><p>3.556012201607765E-4</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>SW QUEEN ANNE GREENBELT</p></div></td><td><div><p>DPR</p></div></td><td><div><p>2004-11-04T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>3</p></div></td><td><div><p>9026 4TH AVE S</p></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Marra-Desimone Park</p></div></td><td><div><p>16455</p></div></td><td><div><p>4447</p></div></td><td><div><p>2007-02-21T00:00:00Z</p></div></td><td><div><p>{E641A30D-FE4B-4B1D-9358-7F0F71324691}</p></div></td><td><div><p>207898</p></div></td><td><div><p>PROPERTY-MARDESPK</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>3224049044</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>2.211413981358282E-6</p></div></td><td><div><p>0.006388002898489655</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>MARRA-DESIMONE PARK</p></div></td><td><div><p>DPR</p></div></td><td><div><p>2004-12-28T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div><p>9026 4TH AVE S</p></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Marra-Desimone Park</p></div></td><td><div><p>16455</p></div></td><td><div><p>4447</p></div></td><td><div><p>2007-02-21T00:00:00Z</p></div></td><td><div><p>{6A440787-F078-4DB9-9187-DA0E029A8E18}</p></div></td><td><div><p>207899</p></div></td><td><div><p>PROPERTY-MARDESPK</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div><p>3224049035</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>1.981420659558925E-6</p></div></td><td><div><p>0.009774073825241834</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>MARRA-DESIMONE PARK</p></div></td><td><div><p>DPR</p></div></td><td><div><p>2004-12-28T00:00:00Z</p></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>Y</p></div></td><td><div><p>Meadowbrook Playfield</p></div></td><td><div><p>803</p></div></td><td><div><p>352</p></div></td><td><div></div></td><td><div><p>{49C14F14-94FF-4080-9DE8-56EDF006145A}</p></div></td><td><div><p>207900</p></div></td><td><div><p>PROPERTY-MBPF</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>5.268695375108406E-7</p></div></td><td><div><p>0.00550990095454217</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>MEADOWBROOK PLAYFIELD</p></div></td><td><div><p>SSD1</p></div></td><td><div></div></td></tr><tr><td><div></div></td><td><div><p>9</p></div></td><td><div></div></td><td><div><p>DPR</p></div></td><td><div><p>N</p></div></td><td><div><p>Meadowbrook Teen Life Center</p></div></td><td><div></div></td><td><div><p>352</p></div></td><td><div></div></td><td><div><p>{D099D793-CFEA-44E9-A57B-D8A1BA4525AF}</p></div></td><td><div><p>207901</p></div></td><td><div><p>PROPERTY-MBPF</p></div></td><td><div><p>QL-D1</p></div></td><td><div></div></td><td><div></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>8.504523207167994E-8</p></div></td><td><div><p>0.0011865488770908574</p></div></td><td><div><p>2024-01-19T14:07:23Z</p></div></td><td><div><p>MEADOWBROOK TEEN LIFE CENTER</p></div></td><td><div><p>SSD1</p></div></td><td><div></div></td></tr></tbody></table></div>

## A Spatial index structure

We need an index structure to quickly match between the two sets of geometries.

See the JTS [SearchUsingPreparedGeometryIndex tutorial](https://github.com/locationtech/jts/blob/master/modules/example/src/main/java/org/locationtech/jtsexample/technique/SearchUsingPreparedGeometryIndex.java).

::: {.sourceClojure}
```clojure
(defn make-spatial-index [dataset & {:keys [geometry-column]
                                     :or   {geometry-column :geometry}}]
  (let [tree ^STRtree (STRtree.)]
    (doseq [row (tc/rows dataset :as-maps)]
      (let [geometry ^Geometry (row geometry-column)]
        (.insert tree
                 (.getEnvelopeInternal geometry)
                 (assoc row
                        :prepared-geometry
                        (PreparedGeometryFactory/prepare geometry)))))
    tree))
```
:::

::: {.sourceClojure}
```clojure
(def parks-index
  (make-spatial-index parks))
```
:::

::: {.sourceClojure}
```clojure
(defn intersecting-places [^Geometry region spatial-index]
  (->> (.query ^STRtree spatial-index
               ^Envelope (.getEnvelopeInternal ^Geometry region))
       (filter (fn [row]
                 (.intersects ^PreparedGeometry (:prepared-geometry row)
                              region)))
       tc/dataset))
```
:::

For example, let us find the parks intersecting with the first neighborhood:

::: {.sourceClojure}
```clojure
(delay
  (-> neighborhoods
      :geometry
      first
      (intersecting-places parks-index)
      (tc/select-columns [:PMA_NAME :NAME])))
```
:::

_unnamed [2 2]:

|               :PMA_NAME |                   :NAME |
|-------------------------|-------------------------|
|         Salmon Bay Park |         SALMON BAY PARK |
| Loyal Heights Playfield | LOYAL HEIGHTS PLAYFIELD |

## A Joined dataset

We compute [a spatial join](https://en.wikipedia.org/wiki/Spatial_join)
of the two datasets.

Note that even though many parks will appear as intersecting many neighbourhoods, this is not too memory-heavy, since they are references to the same map.

::: {.sourceClojure}
```clojure
(def neighborhoods-with-parks
  (-> neighborhoods
      (tc/map-columns :parks
                      [:geometry]
                      #(intersecting-places % parks-index))))
```
:::

::: {.sourceClojure}
```clojure
(delay
  (-> neighborhoods-with-parks
      (tc/map-columns :n-parks
                      [:parks]
                      tc/row-count)
      (tc/select-columns [:L_HOOD :S_HOOD :S_HOOD_ALT_NAMES
                          :n-parks])))
```
:::

Seattle neighborhoods [94 4]:

|             :L_HOOD |                :S_HOOD |                :S_HOOD_ALT_NAMES | :n-parks |
|---------------------|------------------------|----------------------------------|---------:|
|             Ballard |          Loyal Heights |                                  |        2 |
|             Ballard |                Ballard |                            Adams |        7 |
|             Ballard |       Whittier Heights |                                  |        4 |
|             Ballard |          West Woodland |                                  |        5 |
|       North Central |          Phinney Ridge |                    Woodland Park |       11 |
|       North Central |            Wallingford | Meridian, Tangle Town, Northlake |       27 |
|       North Central |                Fremont |                                  |       15 |
|       North Central |             Green Lake |                                  |       19 |
|           Northeast |             View Ridge |                                  |       15 |
|           Northeast |                Ravenna |               University Village |       12 |
|                 ... |                    ... |                              ... |      ... |
|           Northgate |              Pinehurst |                     Jackson Park |        8 |
|           Northwest | North Beach/Blue Ridge |                                  |       32 |
|           Northgate |         Licton Springs |               North College Park |        6 |
|           Northgate |             Maple Leaf |                     Olympic View |       18 |
|           Northwest |             Crown Hill |                                  |        5 |
|           Northwest |              Greenwood |                                  |       36 |
|             Ballard |            Sunset Hill |        Golden Gardens, Shilshole |        9 |
| University District |    University District |                                  |       11 |
| University District |     University Heights |                       Cowen Park |       21 |
|            Downtown |         Denny Triangle |                    Denny Regrade |        3 |
|    Greater Duwamish |    Industrial District |                                  |        5 |

## Computing areas
For evey neigbourhood, we will compute the proportion of its area covered by parks.

::: {.sourceClojure}
```clojure
(delay
  (-> neighborhoods-with-parks
      (tc/map-columns :neighborhood-area
                      [:geometry]
                      area)
      (tc/map-columns :intersection-area
                      [:geometry :parks]
                      (fn [^Geometry neigh-geometry parks]
                        (->> parks
                             :geometry
                             (map (fn [^Geometry park-geometry]
                                    (area
                                     (.intersection (.buffer park-geometry 1)
                                                    neigh-geometry))))
                             fun/sum)))
      (tc/map-columns :park-names
                      [:parks]
                      (fn [parks]
                        (->> parks
                             :PMA_NAME
                             distinct
                             vec)))
      (tc/add-column :area-proportion
                     #(fun// (:intersection-area %)
                             (:neighborhood-area %)))
      (tc/select-columns [:L_HOOD :S_HOOD :S_HOOD_ALT_NAMES
                          :park-names
                          :neighborhood-area
                          :intersection-area
                          :area-proportion])
      (tc/order-by [:area-proportion] :desc)
      kind/table))
```
:::

<div style="max-height:600px;overflow-y:auto;"><table class="table"><thead><tr><th>L_HOOD</th><th>S_HOOD</th><th>S_HOOD_ALT_NAMES</th><th>park-names</th><th>neighborhood-area</th><th>intersection-area</th><th>area-proportion</th></tr></thead><tbody><tr><td><div><p>Northeast</p></div></td><td><div><p>Sand Point</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Warren G. Magnuson Park"]
</code></pre></div></div></td><td><div><p>1.924985714007309E7</p></div></td><td><div><p>1.2694407322392896E7</p></div></td><td><div><p>0.6594546250406457</p></div></td></tr><tr><td><div><p>Magnolia</p></div></td><td><div><p>Lawton Park</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Magnolia Manor Park"
 "Lawton Park"
 "Discovery Park"
 "Kiwanis Memorial Preserve Park"
 "Discovery Park Boulevard"
 "Discovery Park Tidelands"
 "Kiwanis Ravine Overlook"
 "Daybreak Star"
 "Commodore Park"]
</code></pre></div></div></td><td><div><p>5.5091525292193405E7</p></div></td><td><div><p>2.5768911594667178E7</p></div></td><td><div><p>0.46774728886148104</p></div></td></tr><tr><td><div><p>Delridge</p></div></td><td><div><p>North Delridge</p></div></td><td><div><p>Avalon, Luna Park, Pigeon Point</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Greg Davis Park"
 "Cottage Grove Park"
 "Rotary Viewpoint"
 "Camp Long"
 "West Seattle Golf Course"
 "West Seattle Stadium"
 "Longfellow Creek GS: North"
 "Puget Boulevard"
 "West Duwamish Greenbelt"
 "Pigeon Point"
 "Delridge Playfield"
 "Westbridge Shops"
 "WEST DUWAMISH GREENBELT"]
</code></pre></div></div></td><td><div><p>2.945465656812994E7</p></div></td><td><div><p>1.3245569878227614E7</p></div></td><td><div><p>0.44969357723081976</p></div></td></tr><tr><td><div><p>North Central</p></div></td><td><div><p>Green Lake</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Ravenna Boulevard"
 "Green Lake Park"
 "Green Lake"
 "Crescent Place"
 "North Park Shops"]
</code></pre></div></div></td><td><div><p>3.731462978987473E7</p></div></td><td><div><p>1.5314645167249074E7</p></div></td><td><div><p>0.41041932489987293</p></div></td></tr><tr><td><div><p>Seward Park</p></div></td><td><div><p>Seward Park</p></div></td><td><div><p>Lakewood, Hillman City</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Martha Washington Park"
 "Seward Park"
 "Lake Washington Boulevard"
 "Lakewood Playground"
 "Lakewood Moorage"
 "Genesee Park and Playfield"
 "Stan Sayres Memorial Park"]
</code></pre></div></div></td><td><div><p>4.3835279006813824E7</p></div></td><td><div><p>1.3252664479684925E7</p></div></td><td><div><p>0.30232873566573876</p></div></td></tr><tr><td><div><p>Delridge</p></div></td><td><div><p>Riverview</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Delridge and Myrtle"
 "West Duwamish GS: Riverview"
 "Riverview Playfield"
 "West Duwamish GS: Puget Park"
 "Puget Creek Edible Park"
 "Puget Creek Greenspace"
 "Puget Ridge Playground"
 "Delridge Wetland"
 "Puget Park"
 "Puget Boulevard"
 "Pigeon Point"]
</code></pre></div></div></td><td><div><p>3.303826719332341E7</p></div></td><td><div><p>8769575.924383609</p></div></td><td><div><p>0.2654369211638261</p></div></td></tr><tr><td><div><p>North Central</p></div></td><td><div><p>Phinney Ridge</p></div></td><td><div><p>Woodland Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Cascade Place"
 "Sunset Place"
 "Rainier Place"
 "Woodland Park Zoo"
 "Woodland Park"
 "Linden Orchard Park"
 "Green Lake Park"]
</code></pre></div></div></td><td><div><p>3.2123117878649313E7</p></div></td><td><div><p>8349752.958056866</p></div></td><td><div><p>0.25992971758219474</p></div></td></tr><tr><td><div><p>Northgate</p></div></td><td><div><p>Pinehurst</p></div></td><td><div><p>Jackson Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Hubbard Homestead Park"
 "Victory Creek Park"
 "Pinehurst Playground"
 "Flicker Haven Natural Area on Thornton Creek"
 "Licorice Fern Natural Area on Thornton Creek"
 "Jackson Park Golf Course"]
</code></pre></div></div></td><td><div><p>2.9438850877818238E7</p></div></td><td><div><p>7646861.188494857</p></div></td><td><div><p>0.2597540651376668</p></div></td></tr><tr><td><div><p>Capitol Hill</p></div></td><td><div><p>Montlake</p></div></td><td><div><p>North Capitol Hill</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Washington Park and Arboretum"
 "Interlaken Park"
 "Montlake Boulevard"
 "Lake Washington Boulevard"
 "East Montlake Park"
 "Grand Army Cemetery"
 "Montlake Playfield"
 "Harvard-Miller/Roanoke Annex"
 "West Montlake Park"]
</code></pre></div></div></td><td><div><p>2.14747867418963E7</p></div></td><td><div><p>5452986.107546446</p></div></td><td><div><p>0.25392504116969533</p></div></td></tr><tr><td><div><p>West Seattle</p></div></td><td><div><p>Fauntleroy</p></div></td><td><div><p>Endolyne, Arroyo Heights, Brace Point</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Fauntleroy Park"
 "Arroyos Natural Area"
 "Stim Bullitt Natural Area"
 "Endolyne Park"
 "Fauntleroy Creek Ravine"
 "Lincoln Park"
 "Kilbourne Park"
 "Solstice Park"]
</code></pre></div></div></td><td><div><p>3.3881863871407755E7</p></div></td><td><div><p>7399817.180664994</p></div></td><td><div><p>0.2184005345381709</p></div></td></tr><tr><td><div><p>Beacon Hill</p></div></td><td><div><p>North Beacon Hill</p></div></td><td><div><p>Jefferson Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Cheasty GS: Cheasty Blvd"
 "Jefferson Park Golf Course"
 "Cheasty Boulevard"
 "Jefferson Park"
 "East Duwamish GS: Beacon Ave S"
 "Twelfth Avenue South Viewpoint"
 "Stevens Place"
 "Cheasty Greenspace: McClellan"
 "East Duwamish GS: I-90"
 "Beacon Hill Playground"
 "Future Sister City Park"
 "Katie Black's Garden"
 "Daejeon Park"
 "Lewis Park"
 "Dr. Jose Rizal Park"
 "Sturgus Park"]
</code></pre></div></div></td><td><div><p>4.847591445665426E7</p></div></td><td><div><p>1.046069634381901E7</p></div></td><td><div><p>0.2157916247907537</p></div></td></tr><tr><td><div><p>Delridge</p></div></td><td><div><p>Highland Park</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["West Duwamish GS: Othello St."
 "Westcrest Park"
 "Highland Park Playground"]
</code></pre></div></div></td><td><div><p>3.981033341691431E7</p></div></td><td><div><p>8327022.199101201</p></div></td><td><div><p>0.20916735642217155</p></div></td></tr><tr><td><div><p>Capitol Hill</p></div></td><td><div><p>Madison Park</p></div></td><td><div><p>Broadmoor, Washington Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Lambert Place"
 "Hyde Place"
 "Madison Park"
 "Madison Park North Beach"
 "Washington Park and Arboretum"
 "Lake Washington Boulevard"
 " Lake Washington Boulevard"]
</code></pre></div></div></td><td><div><p>2.4680950222860403E7</p></div></td><td><div><p>4675806.696395554</p></div></td><td><div><p>0.18945002741688</p></div></td></tr><tr><td><div><p>Rainier Valley</p></div></td><td><div><p>Mount Baker</p></div></td><td><div><p>North Rainier</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["S Charlestown & 35th Ave S"
 "Stan Sayres Memorial Park"
 "Hunter Boulevard"
 "Horton Hil Corridor"
 "Lakewood Triangle"
 "Trudys Triangle"
 "Mount Baker Park"
 "Lake Washington Boulevard"
 "Landing Parkway"
 "Sierra Place"
 "Mount Claire Park"
 "Colman Park"
 "East Portal Viewpoint"
 "South Day Street Park"
 "York Playground"
 "Mount Baker Boulevard"
 "Martin Luther King JR Memorial"
 "College Street Park"
 "Amy Yee Tennis Center"
 "Bradner Gardens Park"
 "Mt Baker Ridge Viewpoint"
 "Sam Smith Park"]
</code></pre></div></div></td><td><div><p>2.8986995235084333E7</p></div></td><td><div><p>4682493.1951638255</p></div></td><td><div><p>0.16153772259555838</p></div></td></tr><tr><td><div><p>Delridge</p></div></td><td><div><p>High Point</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Walt Hundley Playfield"
 "Longfellow Creek GS: South"
 "Longfellow Creek GS: Central"
 "Camp Long"]
</code></pre></div></div></td><td><div><p>2.3343008337069765E7</p></div></td><td><div><p>3379054.5025715176</p></div></td><td><div><p>0.14475659922570583</p></div></td></tr><tr><td><div><p>Northwest</p></div></td><td><div><p>Broadview</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Carkeek Park"
 "Pipers Creek Natural Area"
 "Llandover Woods Greenspace"]
</code></pre></div></div></td><td><div><p>4.8113449731243916E7</p></div></td><td><div><p>6789015.469879707</p></div></td><td><div><p>0.14110431714629385</p></div></td></tr><tr><td><div><p>Central Area</p></div></td><td><div><p>Leschi</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Lake Washington Boulevard"
 "Frink Park"
 "Flo Ware Park"
 "Leschi Park"
 "Peppi's Playground"
 "Leschi-Lake Dell Natural Area"
 "Leschi Park and South Moorage"
 "North Leschi Moorage"
 "Madrona Park"
 "Powell Barnett Park"]
</code></pre></div></div></td><td><div><p>1.8091741377063915E7</p></div></td><td><div><p>2488664.0659542754</p></div></td><td><div><p>0.13755801689213387</p></div></td></tr><tr><td><div><p>West Seattle</p></div></td><td><div><p>Alki</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Me-Kwa-Mooks Natural Area"
 "Me-Kwa-Mooks Park"
 "Emma Schmitz Memorial Overlook"
 "Andover Place"
 "Cormorant Cove"
 "Charles Richey Sr Viewpoint"
 "Schmitz Preserve Park"
 "Schmitz Boulevard"
 "Duwamish Head Greenbelt"
 "Alki Beach Park"
 "Bar-S Playground"
 "Alki Playground"
 "Hamilton Viewpoint Park"]
</code></pre></div></div></td><td><div><p>2.45834691846126E7</p></div></td><td><div><p>3368610.236147073</p></div></td><td><div><p>0.13702745576102698</p></div></td></tr><tr><td><div><p>Capitol Hill</p></div></td><td><div><p>Stevens</p></div></td><td><div><p>Interlaken Park, Miller Park, Madison-Miller</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Miller Triangle"
 "Seven Hills Park"
 "Washington Park - Japanese Gdn"
 " Lake Washington Boulevard"
 "Washington Park and Arboretum"
 "Washington Park"
 "Lake Washington Boulevard"
 "Pendleton Miller Playfield"
 "Prentis I. Frazier Park"
 "Interlaken Park"
 "Boren Park"]
</code></pre></div></div></td><td><div><p>2.6039592079779927E7</p></div></td><td><div><p>3257296.7380544366</p></div></td><td><div><p>0.12509015994086056</p></div></td></tr><tr><td><div><p>Ballard</p></div></td><td><div><p>Sunset Hill</p></div></td><td><div><p>Golden Gardens, Shilshole</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["NW 60th Street Viewpoint"
 "Webster Park"
 "Sunset Hill Park"
 "Golden Gardens Park"]
</code></pre></div></div></td><td><div><p>2.4335620469794728E7</p></div></td><td><div><p>2999062.204514957</p></div></td><td><div><p>0.12323754835991878</p></div></td></tr><tr><td><div><p>West Seattle</p></div></td><td><div><p>North Admiral</p></div></td><td><div><p>Belvidere</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Hiawatha Playfield"
 "Schmitz Preserve Park"
 "Schmitz Boulevard"
 "Duwamish Head Greenbelt"
 "Fairmount Park"
 "Belvedere Park"
 "Nantes Park"
 "College Street Ravine"
 "California Place"
 "Hamilton Viewpoint Park"]
</code></pre></div></div></td><td><div><p>4.858141632113909E7</p></div></td><td><div><p>5960598.691665671</p></div></td><td><div><p>0.12269297898324247</p></div></td></tr><tr><td><div><p>Rainier Valley</p></div></td><td><div><p>Columbia City</p></div></td><td><div><p>Columbia Heights</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Hitt's Hill Park"
 "Brighton Playfield"
 "Hillman P-Patch"
 "Genesee Park and Playfield"
 "Lake People Park (Xacua'bs)"
 "Cheasty GS: Cheasty Blvd"
 "Cheasty Boulevard"
 "York Park"
 "Columbia Park"
 "Rainier Playfield"]
</code></pre></div></div></td><td><div><p>3.7406576493219726E7</p></div></td><td><div><p>4344458.806638756</p></div></td><td><div><p>0.11614157760270384</p></div></td></tr><tr><td><div><p>Central Area</p></div></td><td><div><p>Atlantic</p></div></td><td><div><p>Judkins Park, Jackson Place, Coleman</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Colman Playground"
 "Martin Luther King JR Memorial"
 "Amy Yee Tennis Center"
 "Jimi Hendrix Park"
 "Atlantic Street Park"
 "Sam Smith Park"
 "Benvenuto Viewpoint"
 "Judkins Park and Playfield"
 "Judge Charles M. Stokes Overlook"
 "Pratt Park"
 "Blue Dog Pond"
 "Dr. Blanche Lavizzo Park"
 "Langston Hughes Cultural Arts"]
</code></pre></div></div></td><td><div><p>2.0664986273336366E7</p></div></td><td><div><p>2395983.464898887</p></div></td><td><div><p>0.11594411112628604</p></div></td></tr><tr><td><div><p>Queen Anne</p></div></td><td><div><p>West Queen Anne</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Kinnear Park"
 "Marshall Park"
 "Parsons Gardens"
 "Queen Anne Boulevard"
 "SW Queen Anne Greenbelt"
 "West Queen Anne Playfield"
 "Queen Anne Swimming Pool"
 "West Central Grounds Maintenance"
 "12th West & West Howe Park"]
</code></pre></div></div></td><td><div><p>1.797498595288394E7</p></div></td><td><div><p>1964455.447449051</p></div></td><td><div><p>0.10928828832457976</p></div></td></tr><tr><td><div><p>Capitol Hill</p></div></td><td><div><p>Broadway</p></div></td><td><div><p>Pike/Pine</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Plymouth Pillars Park"
 "Bellevue Place"
 "Lakeview Place"
 "Cal Anderson Park"
 "Thomas Street Gardens"
 "Tashkent Park"
 "Williams Place"
 "Broadway Hill Park"
 "Volunteer Parkway"
 "Summit Slope Park"
 "Thomas Street Mini Park"
 "Belmont Place"
 "Summit Place"
 "Bullitt Life Estate"
 "St. Marks Greenbelt"
 "Streissguth Gardens"
 "I-5 Colonnade"
 "Volunteer Park"]
</code></pre></div></div></td><td><div><p>3.0239240521690477E7</p></div></td><td><div><p>3304530.7655596808</p></div></td><td><div><p>0.10927955558901538</p></div></td></tr><tr><td><div><p>Downtown</p></div></td><td><div><p>Pike-Market</p></div></td><td><div><p>Pike Place Market</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Seattle Aquarium"
 "Piers 62 and 63"
 "Waterfront Park"
 "Victor Steinbrueck Park"]
</code></pre></div></div></td><td><div><p>2343359.3260714533</p></div></td><td><div><p>255005.04346191516</p></div></td><td><div><p>0.10882029086397978</p></div></td></tr><tr><td><div><p>Magnolia</p></div></td><td><div><p>Briarcliff</p></div></td><td><div><p>Carleton Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Magnolia Tidelands Park"
 "Magnolia Park"
 "Magnolia Boulevard"
 "Parkmont Place"
 "Eastmont Place"
 "Carleton Center"
 "Carleton Highlands"
 "ARAPAHOE TRIANGLE"
 "Discovery Park"]
</code></pre></div></div></td><td><div><p>2.6550936578728132E7</p></div></td><td><div><p>2713294.302010858</p></div></td><td><div><p>0.10219203733041468</p></div></td></tr><tr><td><div><p>Interbay</p></div></td><td><div><p>Interbay</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Myrtle Edwards Park"
 "Ursula Judkins Viewpoint"
 "Smith Cove Park"
 "Magnolia Boulevard"
 "Magnolia Greenbelt"
 "Thorndyke Park"
 "Open Water Park"
 "Interbay P-patch"
 "Interbay Golf"
 "Interbay Athletic Field"
 "Commodore Park"]
</code></pre></div></div></td><td><div><p>3.350394109364654E7</p></div></td><td><div><p>3234156.7950585634</p></div></td><td><div><p>0.09653063757540652</p></div></td></tr><tr><td><div><p>Rainier Valley</p></div></td><td><div><p>Dunlap</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Chinook Beach Park"
 "Atlantic City Boat Ramp"
 "Rainier Beach Urban Farm and Wetlands"
 "Beer Sheva Park"
 "Rainier Beach Community Center"
 "Pritchard Island Beach"
 "East Duwamish GS: MLK Way"
 "Rainier Beach Playfield"]
</code></pre></div></div></td><td><div><p>1.9601601215604942E7</p></div></td><td><div><p>1782788.7703944917</p></div></td><td><div><p>0.0909511805073967</p></div></td></tr><tr><td><div><p>Central Area</p></div></td><td><div><p>Madrona</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Nora's Woods"
 "Madrona Playground"
 "Madrona Park"
 "Lake Washington Boulevard"
 "Madrona Ravine"
 "Alvin Larkins Park"
 "Madrona Briar Patch"
 "Howell Park"
 "William Grose Park"
 "Harrison Ridge Greenbelt"]
</code></pre></div></div></td><td><div><p>1.3845482808694465E7</p></div></td><td><div><p>1211682.0145605851</p></div></td><td><div><p>0.08751460901021757</p></div></td></tr><tr><td><div><p>Magnolia</p></div></td><td><div><p>Southeast Magnolia</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Magnolia Boulevard"
 "Condon Way Centerstrip"
 "Magnolia Park"
 "West Magnolia Playfield"
 " "
 "Lowery C. \"Pop\" Mounger Pool"
 "Ella Bailey Park"
 "Bayview Playground"]
</code></pre></div></div></td><td><div><p>1.8469263888735063E7</p></div></td><td><div><p>1466342.6454210556</p></div></td><td><div><p>0.07939367016762483</p></div></td></tr><tr><td><div><p>Beacon Hill</p></div></td><td><div><p>Holly Park</p></div></td><td><div><p>New Holly</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["John C. Little, Sr. Park" "Van Asselt Playground"]
</code></pre></div></div></td><td><div><p>8444235.979074124</p></div></td><td><div><p>656778.4801970643</p></div></td><td><div><p>0.07777831905984671</p></div></td></tr><tr><td><div><p>Beacon Hill</p></div></td><td><div><p>South Beacon Hill</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["East Duwamish GS: S Chicago St" "Benefit Playground"]
</code></pre></div></div></td><td><div><p>3.844882690015128E7</p></div></td><td><div><p>2989598.1245943466</p></div></td><td><div><p>0.07775524939572562</p></div></td></tr><tr><td><div><p>Rainier Valley</p></div></td><td><div><p>Rainier View</p></div></td><td><div><p>Lake Ridge</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Lakeridge Park"
 "Taylor Creek Headwaters"
 "Lakeridge Playground"
 "Thayer Place"]
</code></pre></div></div></td><td><div><p>1.8248566179783218E7</p></div></td><td><div><p>1398373.180214077</p></div></td><td><div><p>0.07662920836834146</p></div></td></tr><tr><td><div><p>Queen Anne</p></div></td><td><div><p>East Queen Anne</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Queen Anne Boulevard"
 "Bhy Kracke Park"
 "Northeast Queen Anne Greenbelt"
 "Highland Place"
 "Highland Drive Parkway"
 "Observatory Courts"
 "East Queen Anne Playground"
 "Wolf Creek Ravine Natural Area"
 "Trolley Hill Park"
 "MacLean Park"
 "Westlake Greenbelt"
 "Thomas C. Wales Park"]
</code></pre></div></div></td><td><div><p>1.9354699596494563E7</p></div></td><td><div><p>1448114.7496615453</p></div></td><td><div><p>0.07481979983423878</p></div></td></tr><tr><td><div><p>Rainier Valley</p></div></td><td><div><p>Rainier Beach</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Kubota Gardens Natural Area"
 "Lakeridge Park"
 "Lakeridge Playground"
 "Thayer Place"
 "Kubota Gardens"
 "Fred Hutchinson Playground"
 "Sturtevant Ravine"
 "East Duwamish GS: MLK Way"
 "Fletcher Place"
 "Chinook Beach Park"]
</code></pre></div></div></td><td><div><p>3.312823614223316E7</p></div></td><td><div><p>2442620.8848146023</p></div></td><td><div><p>0.07373229514325559</p></div></td></tr><tr><td><div><p>Central Area</p></div></td><td><div><p>Harrison/Denny-Blaine</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Denny Blaine Lake Park"
 "Harrison Ridge Greenbelt"
 "Viretta Park"
 "Stevens Triangle"
 "Denny Blaine Park"
 "Lakeview Park"
 "McGilvra Boulevard"
 "Lake Washington Boulevard"
 "3001 E Madison"]
</code></pre></div></div></td><td><div><p>1.360339567318952E7</p></div></td><td><div><p>946560.209820138</p></div></td><td><div><p>0.06958264190504156</p></div></td></tr><tr><td><div><p>Northeast</p></div></td><td><div><p>Ravenna</p></div></td><td><div><p>University Village</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Blakeley Crescent Park"
 "Ravenna Ravine"
 "Burke-Gilman Trail"
 "Ravenna Park"
 "Ravenna-Eckstein Park"]
</code></pre></div></div></td><td><div><p>3.678339153768188E7</p></div></td><td><div><p>2537736.5238547004</p></div></td><td><div><p>0.06899136859783514</p></div></td></tr><tr><td><div><p>Lake City</p></div></td><td><div><p>Meadowbrook</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Thornton Creek Natural Area: 25th/95th"
 "Meadowbrook Playfield"
 "Meadowbrook Teen Life Center"
 "LaVilla Meadows Natural Area on Thornton Creek"]
</code></pre></div></div></td><td><div><p>1.703484877942584E7</p></div></td><td><div><p>1162909.7193452865</p></div></td><td><div><p>0.06826651262967551</p></div></td></tr><tr><td><div><p>Northwest</p></div></td><td><div><p>North Beach/Blue Ridge</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Soundview Playfield"
 "Blue Ridge Places"
 "Carkeek Park"
 "Blue Ridge Circle"
 "North Beach Park"
 "North Beach Ravine: 30th NW Natural Area"
 "Golden Gardens Park"]
</code></pre></div></div></td><td><div><p>3.1062264992039643E7</p></div></td><td><div><p>1942086.5722656162</p></div></td><td><div><p>0.06252237474515514</p></div></td></tr><tr><td><div><p>Northeast</p></div></td><td><div><p>Roosevelt</p></div></td><td><div><p>Fairview</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Ravenna Boulevard"
 "Ravenna Park"
 "Cowen Park"
 "Roosevelt Land-Bank Site"
 "Banner Way Triangles"
 "Froula Playground"
 "Rainbow Point"
 "Maple Leaf Reservoir Park"]
</code></pre></div></div></td><td><div><p>2.1491594324983705E7</p></div></td><td><div><p>1309062.5613024468</p></div></td><td><div><p>0.06091044440480054</p></div></td></tr><tr><td><div><p>Lake City</p></div></td><td><div><p>Matthews Beach</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Mock Creek Ravine"
 "Little Brook Creek Natural Area"
 "Chinook Passage Natural Area on Thornton Creek"
 "Burke-Gilman Trail"
 "Matthews Beach Park"]
</code></pre></div></div></td><td><div><p>3.0980978301755752E7</p></div></td><td><div><p>1770241.0308238121</p></div></td><td><div><p>0.05713961042745668</p></div></td></tr><tr><td><div><p>Northeast</p></div></td><td><div><p>Bryant</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Burke-Gilman Trail"
 "Burke-Gilman Playground Park"
 "Bryant Playground"]
</code></pre></div></div></td><td><div><p>1.5485078033882016E7</p></div></td><td><div><p>829201.5932133237</p></div></td><td><div><p>0.053548428454735265</p></div></td></tr><tr><td><div><p>Delridge</p></div></td><td><div><p>Roxhill</p></div></td><td><div><p>Westwood Village</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Roxhill Park"
 "S.W. Community Center and Pool"
 "E.C. Hughes Playground"]
</code></pre></div></div></td><td><div><p>1.87810598448122E7</p></div></td><td><div><p>995987.7545642204</p></div></td><td><div><p>0.053031498903366586</p></div></td></tr><tr><td><div><p>Northeast</p></div></td><td><div><p>View Ridge</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Burke-Gilman Trail" "View Ridge Playfield" "Inverness Ravine Park"]
</code></pre></div></div></td><td><div><p>2.561297994427941E7</p></div></td><td><div><p>1288763.708935325</p></div></td><td><div><p>0.05031682028951758</p></div></td></tr><tr><td><div><p>Cascade</p></div></td><td><div><p>South Lake Union</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Denny Park"
 "Lake Union Park"
 "Fairview Walkway"
 "Cascade Playground"
 "I-5 Colonnade"
 "Terry Pettus Park"
 "Lynn Street Mini Park"]
</code></pre></div></div></td><td><div><p>1.6107105419750454E7</p></div></td><td><div><p>800866.192857775</p></div></td><td><div><p>0.04972129827099516</p></div></td></tr><tr><td><div><p>Queen Anne</p></div></td><td><div><p>North Queen Anne</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Queen Anne Boulevard"
 "Coe Play Park"
 "Queen Anne Bowl Playfield"
 "Mayfair Park"
 "David Rodgers Park"
 "West Ewing Mini Park"
 "Soundview Terrace"]
</code></pre></div></div></td><td><div><p>2.960428833366627E7</p></div></td><td><div><p>1355843.879844315</p></div></td><td><div><p>0.04579890131330861</p></div></td></tr><tr><td><div><p>North Central</p></div></td><td><div><p>Wallingford</p></div></td><td><div><p>Meridian, Tangle Town, Northlake</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Gas Works Park"
 "Harbor Patrol Office and Shop"
 "Waterway 19"
 "Wallingford Steps"
 "Burke-Gilman Trail"
 "Sunnyside Ave N Boat Ramp"
 "Wallingford Playfield"
 "Demonstration Garden"
 "North Passage Point Park"
 "NE 60th Street Park"
 "Meridian Playground"
 "Corliss Place"
 "Keystone Place"
 "Green Lake Park"]
</code></pre></div></div></td><td><div><p>4.2068342614797205E7</p></div></td><td><div><p>1777393.4021316427</p></div></td><td><div><p>0.04225014088162481</p></div></td></tr><tr><td><div><p>Lake City</p></div></td><td><div><p>Victory Heights</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Homewood Natural Area on Thornton Creek"
 "Kingfisher Natural Area on Thornton Creek"
 "Virgil Flaim Park"
 "Lake City Park"
 "Victory Heights Playground"
 "Pinehurst Pocket Park"]
</code></pre></div></div></td><td><div><p>2.151273148967749E7</p></div></td><td><div><p>900485.900698212</p></div></td><td><div><p>0.04185827825398623</p></div></td></tr><tr><td><div><p>Beacon Hill</p></div></td><td><div><p>Mid-Beacon Hill</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Dearborn Park"
 "Cheasty Greenspace: Mt View"
 "Maple School Ravine"
 "Maple Wood Playfield"
 "Cleveland Playfield"
 "East Duwamish GS: S Spokane St"]
</code></pre></div></div></td><td><div><p>5.262047078955701E7</p></div></td><td><div><p>2161142.3873948674</p></div></td><td><div><p>0.041070373468109767</p></div></td></tr><tr><td><div><p>Central Area</p></div></td><td><div><p>Mann</p></div></td><td><div><p>Central District, Garfield</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Garfield Teen Life Center"
 "Garfield Playfield"
 "Homer Harris Park"
 "Gerber Park"
 "Plum Tree Park"
 "Julia Lee's Park"]
</code></pre></div></div></td><td><div><p>1.113382886245558E7</p></div></td><td><div><p>443902.819098556</p></div></td><td><div><p>0.03986973615118534</p></div></td></tr><tr><td><div><p>Cascade</p></div></td><td><div><p>Eastlake</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["I-5 Colonnade"
 "Fairview Park"
 "South Passage Point Park"
 "Rogers Playground"
 "Roanoke Street Mini Park"
 "Terry Pettus Park"
 "Lynn Street Mini Park"]
</code></pre></div></div></td><td><div><p>7426907.961769626</p></div></td><td><div><p>293104.7959594849</p></div></td><td><div><p>0.039465252224513386</p></div></td></tr><tr><td><div><p>Northgate</p></div></td><td><div><p>Maple Leaf</p></div></td><td><div><p>Olympic View</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Sacajawea Playground"
 "Maple Leaf Community Garden"
 "Beaver Pond Natural Area on Thornton Creek"
 "Maple Leaf Reservoir Park"
 "Kingfisher Natural Area on Thornton Creek"
 "Victory Creek Confluence Natural Area on TC"
 "Northgate Park"
 "Northgate Community Center"]
</code></pre></div></div></td><td><div><p>3.4380470783073254E7</p></div></td><td><div><p>1130968.2364097128</p></div></td><td><div><p>0.03289565880425725</p></div></td></tr><tr><td><div><p>Northeast</p></div></td><td><div><p>Laurelhurst</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Union Bay Boglands #2"
 "Union Bay Boglands #1"
 "LAURELHURST TRIANGLE"
 "Belvoir Place"
 "Laurelhurst Playfield"
 "Laurelhurst Recreation Center"
 "Sun Park"]
</code></pre></div></div></td><td><div><p>1.905177681936156E7</p></div></td><td><div><p>622689.0135556267</p></div></td><td><div><p>0.03268403884108136</p></div></td></tr><tr><td><div><p>Northeast</p></div></td><td><div><p>Wedgwood</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Dahl (Waldo J.) Playfield"
 "Picardo (Rainie) P-Patch"
 "Thornton Creek Natural Area: 25th/95th"
 "Wedgwood Square"
 "8605 35th Ave NE"
 "Inverness Ravine Park"
 "Maple Springs Natural Area"]
</code></pre></div></div></td><td><div><p>3.059971362703256E7</p></div></td><td><div><p>968985.0098010622</p></div></td><td><div><p>0.031666473144540686</p></div></td></tr><tr><td><div><p>Downtown</p></div></td><td><div><p>Yesler Terrace</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Yesler Terrace Park" "Horiuchi Park" "Boren Place"]
</code></pre></div></div></td><td><div><p>5348937.247801803</p></div></td><td><div><p>159300.53646585828</p></div></td><td><div><p>0.02978171720584764</p></div></td></tr><tr><td><div><p>Downtown</p></div></td><td><div><p>Belltown</p></div></td><td><div><p>Denny Regrade</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Myrtle Edwards Park"
 "Bell Street Park Boulevard"
 "Belltown Cottage Park"
 "Belltown P-patch"
 "Regrade Park"
 "Alaskan Way Boulevard"
 "Tilikum Place"]
</code></pre></div></div></td><td><div><p>9845864.786277873</p></div></td><td><div><p>279689.8893769705</p></div></td><td><div><p>0.028406838347686095</p></div></td></tr><tr><td><div><p>Capitol Hill</p></div></td><td><div><p>Portage Bay</p></div></td><td><div><p>Roanoke Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Roanoke Park" "Bagley Viewpoint"]
</code></pre></div></div></td><td><div><p>4421635.267367266</p></div></td><td><div><p>121026.6277003076</p></div></td><td><div><p>0.027371463357349548</p></div></td></tr><tr><td><div><p>Greater Duwamish</p></div></td><td><div><p>South Park</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["South Park Meadow"
 "Marra-Desimone Park"
 "Cesar Chavez Park"
 "South Park Playground"
 "Duwamish Waterway Park"]
</code></pre></div></div></td><td><div><p>2.9423452152724065E7</p></div></td><td><div><p>788757.1095861244</p></div></td><td><div><p>0.0268070893072654</p></div></td></tr><tr><td><div><p>West Seattle</p></div></td><td><div><p>Arbor Heights</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Seola Park" "Seola Beach Greenbelt" "Fauntleroy Park"]
</code></pre></div></div></td><td><div><p>2.619731405785146E7</p></div></td><td><div><p>661354.2410716552</p></div></td><td><div><p>0.0252451163356361</p></div></td></tr><tr><td><div><p>Lake City</p></div></td><td><div><p>Cedar Park</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Lake City Memorial Triangle"
 "Burke-Gilman Trail"
 "Lake City Urban Hub Village"
 "Cedar Park"
 "University Lake Shore Place"
 "NE 130th Street End"]
</code></pre></div></div></td><td><div><p>2.04414858490784E7</p></div></td><td><div><p>500421.66464288835</p></div></td><td><div><p>0.02448068933626221</p></div></td></tr><tr><td><div><p>University District</p></div></td><td><div><p>University District</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Burke-Gilman Trail"
 "Ravenna Woods"
 "Christie Park"
 "17th Avenue NE Centerstrip"
 "North Passage Point Park"
 "Northlake Park"
 "University Playground"]
</code></pre></div></div></td><td><div><p>1.3686254858800735E7</p></div></td><td><div><p>324977.58184178185</p></div></td><td><div><p>0.023744814428383235</p></div></td></tr><tr><td><div><p>Northgate</p></div></td><td><div><p>Licton Springs</p></div></td><td><div><p>North College Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Mineral Springs Park" "Licton Springs Park"]
</code></pre></div></div></td><td><div><p>2.1704706262052845E7</p></div></td><td><div><p>513945.6292462934</p></div></td><td><div><p>0.023678994916639065</p></div></td></tr><tr><td><div><p>Northgate</p></div></td><td><div><p>Haller Lake</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Haller Lake Community St End" "Northacres Park" "Helene Madison Pool"]
</code></pre></div></div></td><td><div><p>4.720308108008111E7</p></div></td><td><div><p>1112625.044392759</p></div></td><td><div><p>0.023571025851155034</p></div></td></tr><tr><td><div><p>Northeast</p></div></td><td><div><p>Windermere</p></div></td><td><div><p>Hawthorne Hills</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Burke-Gilman Trail" "University Circle" "Warren G. Magnuson Park"]
</code></pre></div></div></td><td><div><p>2.2363966623912185E7</p></div></td><td><div><p>500567.5192937572</p></div></td><td><div><p>0.022382769913389885</p></div></td></tr><tr><td><div><p>Ballard</p></div></td><td><div><p>Loyal Heights</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Salmon Bay Park" "Loyal Heights Playfield"]
</code></pre></div></div></td><td><div><p>2.1320655545884836E7</p></div></td><td><div><p>421263.7501266854</p></div></td><td><div><p>0.019758480184629914</p></div></td></tr><tr><td><div><p>Downtown</p></div></td><td><div><p>International District</p></div></td><td><div><p>Chinatown, ID, Little Saigon</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Donnie Chin International Children's Park"
 "Hing Hay Park Addition"
 "ID/Chinatown Community Center"
 "Beacon Place"
 "Chinatown/ID Hub Urban Village"
 "Hing Hay Park"
 "Kobe Terrace"]
</code></pre></div></div></td><td><div><p>6169375.816795917</p></div></td><td><div><p>121130.99413208748</p></div></td><td><div><p>0.019634238167548886</p></div></td></tr><tr><td><div><p>Rainier Valley</p></div></td><td><div><p>Brighton</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Othello Park"]
</code></pre></div></div></td><td><div><p>1.8366938275487844E7</p></div></td><td><div><p>342712.9789050467</p></div></td><td><div><p>0.01865923289797433</p></div></td></tr><tr><td><div><p>Downtown</p></div></td><td><div><p>Central Business District</p></div></td><td><div><p>Commercial Core, West Edge</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Waterfront Park" "Jim Ellis Freeway Park" "Westlake Park"]
</code></pre></div></div></td><td><div><p>9477398.618861396</p></div></td><td><div><p>176559.42602316735</p></div></td><td><div><p>0.018629524105041706</p></div></td></tr><tr><td><div><p>North Central</p></div></td><td><div><p>Fremont</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["A. B. Ernst Park"
 "Fremont Canal Park"
 "Burke-Gilman Trail"
 "Fremont Peak Park"
 "Troll's Knoll Park"
 "B.F. Day Playground"
 "Ross Playground"]
</code></pre></div></div></td><td><div><p>2.650375657209128E7</p></div></td><td><div><p>443605.6587439842</p></div></td><td><div><p>0.016737463519081116</p></div></td></tr><tr><td><div><p>Northwest</p></div></td><td><div><p>Bitter Lake</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Bitter Lake Playfield" "Bitter Lake Open Space Park"]
</code></pre></div></div></td><td><div><p>2.769033644488096E7</p></div></td><td><div><p>463326.8142235621</p></div></td><td><div><p>0.016732437149900217</p></div></td></tr><tr><td><div><p>Northwest</p></div></td><td><div><p>Greenwood</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Alice Ball Park"
 "Greenwood Park"
 "6th Avenue NW Pocket Park"
 "Sandel Playground"
 "Carkeek Park"]
</code></pre></div></div></td><td><div><p>4.204456367454267E7</p></div></td><td><div><p>689596.1664853458</p></div></td><td><div><p>0.01640155364254346</p></div></td></tr><tr><td><div><p>University District</p></div></td><td><div><p>University Heights</p></div></td><td><div><p>Cowen Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["17th Avenue NE Centerstrip"
 "Ravenna Boulevard"
 "Park Home Circle"
 "University Heights"
 "Ravenna Park"]
</code></pre></div></div></td><td><div><p>1.037574805292391E7</p></div></td><td><div><p>166849.97798407465</p></div></td><td><div><p>0.016080766141681316</p></div></td></tr><tr><td><div><p>West Seattle</p></div></td><td><div><p>Gatewood</p></div></td><td><div><p>Morgan Junction</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Orchard Street Ravine"
 "Myrtle Reservoir Park"
 "Lincoln Park"
 "Lowman Beach Park"
 "Pelly Place Natural Area"
 "Watton Life Estate"
 nil]
</code></pre></div></div></td><td><div><p>2.2821707469523415E7</p></div></td><td><div><p>355085.68614532915</p></div></td><td><div><p>0.015559120044787095</p></div></td></tr><tr><td><div><p>West Seattle</p></div></td><td><div><p>Fairmount Park</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Fairmount Playground"]
</code></pre></div></div></td><td><div><p>1.6153900097573552E7</p></div></td><td><div><p>237376.26008061314</p></div></td><td><div><p>0.014694671791134142</p></div></td></tr><tr><td><div><p>Downtown</p></div></td><td><div><p>First Hill</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Jim Ellis Freeway Park" "First Hill Park" "Boylston Place"]
</code></pre></div></div></td><td><div><p>9517568.473671103</p></div></td><td><div><p>126769.23408250557</p></div></td><td><div><p>0.0133194979824094</p></div></td></tr><tr><td><div><p>Downtown</p></div></td><td><div><p>Pioneer Square</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Union Station Square"
 "Occidental Square"
 "City Hall Park"
 "Prefontaine Place"
 "Pioneer Square"]
</code></pre></div></div></td><td><div><p>7545979.087288558</p></div></td><td><div><p>95347.44250189843</p></div></td><td><div><p>0.0126355296508195</p></div></td></tr><tr><td><div><p>Ballard</p></div></td><td><div><p>Ballard</p></div></td><td><div><p>Adams</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Bergen Place"
 "Ballard Corners Park"
 "Marvins Garden"
 "Ballard Commons Park"
 "Thyme Patch Park"
 "Ballard Playground"]
</code></pre></div></div></td><td><div><p>2.255213297047855E7</p></div></td><td><div><p>244344.9612760165</p></div></td><td><div><p>0.01083467189537556</p></div></td></tr><tr><td><div><p>Cascade</p></div></td><td><div><p>Westlake</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Lake Union Park"]
</code></pre></div></div></td><td><div><p>3645184.079110308</p></div></td><td><div><p>37961.61985636592</p></div></td><td><div><p>0.010414184587800388</p></div></td></tr><tr><td><div><p>Ballard</p></div></td><td><div><p>West Woodland</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Greenwood Triangle"
 "14th Avenue NW Boat Ramp"
 "Gilman Playground"
 "Gemenskap Park"]
</code></pre></div></div></td><td><div><p>2.2199366873893585E7</p></div></td><td><div><p>226099.72709449235</p></div></td><td><div><p>0.010184962858575269</p></div></td></tr><tr><td><div><p>Central Area</p></div></td><td><div><p>Minor</p></div></td><td><div><p>Central District, Squire Park</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Spruce Street Mini Park"
 "Garfield Playfield"
 "Cayton Corner Park"
 "Langston Hughes Annex"
 "12th Ave Square Park"
 "Firehouse Mini Park"
 "Spring Street Mini Park"
 "T.T. Minor Playground"
 "McGilvra Place"]
</code></pre></div></div></td><td><div><p>1.7933144708720244E7</p></div></td><td><div><p>172158.54773067622</p></div></td><td><div><p>0.009600019992420052</p></div></td></tr><tr><td><div><p>Greater Duwamish</p></div></td><td><div><p>Industrial District</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Herrings House Park (Tulaltx)"
 "Alki Beach Park"
 "Seacrest Park"
 "Don Armeni Boat Ramp"]
</code></pre></div></div></td><td><div><p>6.243413101303743E7</p></div></td><td><div><p>559378.0064992205</p></div></td><td><div><p>0.00895949054504197</p></div></td></tr><tr><td><div><p>Ballard</p></div></td><td><div><p>Whittier Heights</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Kirke Park" "Ballard Swimming Pool" "Baker Park on Crown Hill"]
</code></pre></div></div></td><td><div><p>1.4195687492422596E7</p></div></td><td><div><p>108946.50009691996</p></div></td><td><div><p>0.007674619503639655</p></div></td></tr><tr><td><div><p>Delridge</p></div></td><td><div><p>South Delridge</p></div></td><td><div><p>White Center</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Longfellow Creek GS: South"]
</code></pre></div></div></td><td><div><p>1.792331622408078E7</p></div></td><td><div><p>132742.1724476857</p></div></td><td><div><p>0.007406116746929937</p></div></td></tr><tr><td><div><p>Queen Anne</p></div></td><td><div><p>Lower Queen Anne</p></div></td><td><div><p>Uptown, Seattle Center</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Blaine Place"
 "Counterbalance Park"
 "Kinnear Place"
 "Kerry Park (Franklin Place)"
 "Kerry Park and Viewpoint"
 "Ward Springs Park"]
</code></pre></div></div></td><td><div><p>1.7515624457317874E7</p></div></td><td><div><p>106952.95177903834</p></div></td><td><div><p>0.006106145518229259</p></div></td></tr><tr><td><div><p>Northwest</p></div></td><td><div><p>Crown Hill</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Crown Hill Glen" "Crown Hill Park"]
</code></pre></div></div></td><td><div><p>1.586575041985613E7</p></div></td><td><div><p>94943.40486711139</p></div></td><td><div><p>0.005984173603808166</p></div></td></tr><tr><td><div><p>University District</p></div></td><td><div><p>University of Washington</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Union Bay Boglands #2"
 "Union Bay Boglands #1"
 "Fritz Hedges Waterway Park"]
</code></pre></div></div></td><td><div><p>2.5523675124439575E7</p></div></td><td><div><p>142125.03524102044</p></div></td><td><div><p>0.005568360925614982</p></div></td></tr><tr><td><div><p>Greater Duwamish</p></div></td><td><div><p>Georgetown</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Georgetown Pump Station" "Oxbow Park" "Georgetown Playfield"]
</code></pre></div></div></td><td><div><p>5.130507264703818E7</p></div></td><td><div><p>281438.2271119965</p></div></td><td><div><p>0.005485582859383083</p></div></td></tr><tr><td><div><p>Lake City</p></div></td><td><div><p>Olympic Hills</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Thornton Creek Addition: North Branch"
 "Albert Davis Park"
 "Little Brook Park"]
</code></pre></div></div></td><td><div><p>2.5836742164596498E7</p></div></td><td><div><p>141195.81351923634</p></div></td><td><div><p>0.005464923271662082</p></div></td></tr><tr><td><div><p>West Seattle</p></div></td><td><div><p>Genesee</p></div></td><td><div><p>Alaska Junction, West Seattle Junction</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["West Seattle Junction"
 "Junction Plaza Park"
 "Ercolini Park"
 "Dakota Place Park"
 "48th Ave SW/SW Charlestown St"
 "Fauntleroy Place"]
</code></pre></div></div></td><td><div><p>2.1164976581792817E7</p></div></td><td><div><p>91891.1780685815</p></div></td><td><div><p>0.00434166216595916</p></div></td></tr><tr><td><div><p>West Seattle</p></div></td><td><div><p>Seaview</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["Lowman Beach Park" "Morgan Junction Park"]
</code></pre></div></div></td><td><div><p>1.846306179837895E7</p></div></td><td><div><p>51860.33722001134</p></div></td><td><div><p>0.002808869828110777</p></div></td></tr><tr><td><div><p>Downtown</p></div></td><td><div><p>Denny Triangle</p></div></td><td><div><p>Denny Regrade</p></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">["McGraw Square" "Westlake Square" "Urban Triangle Park"]
</code></pre></div></div></td><td><div><p>5128172.310711999</p></div></td><td><div><p>11668.172603196248</p></div></td><td><div><p>0.002275308218256073</p></div></td></tr><tr><td><div><p>Greater Duwamish</p></div></td><td><div><p>Harbor Island</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">[]
</code></pre></div></div></td><td><div><p>1.7832300735864956E7</p></div></td><td><div><p>0.0</p></div></td><td><div><p>0.0</p></div></td></tr><tr><td><div><p>Greater Duwamish</p></div></td><td><div><p>SODO</p></div></td><td><div></div></td><td><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">[]
</code></pre></div></div></td><td><div><p>4.9603167591402024E7</p></div></td><td><div><p>0.0</p></div></td><td><div><p>0.0</p></div></td></tr></tbody></table></div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: projects/geography/seattle-parks/notebooks/index.clj</small></small></pre></div>

### 2024-01-22 docs/projects/data-formats/hdf/index.qmd
hdf - rerendered

@@
   html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
-highlight-style: solarized
 code-block-background: true
@@
 <script src="index_files/md-default3.js" type="text/javascript"></script><script src="index_files/md-default4.js" type="text/javascript"></script>
-<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
 
@@
 ```
-</div>
+:::
 
-<div><p>(</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">{:key "0", :data #tech.v3.tensor&lt;int32&gt;[600 800]
+<div style="max-height:600px;overflow-y:auto;"><div><p>(</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">{:key "0", :data #tech.v3.tensor&lt;int32&gt;[600 800]
 [[112 110 111 ... 114 118 124]
@@
  [134 135 134 ... 110 111 110]]}
-</code></pre></div><img src="index_files/0.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "1", :data #tech.v3.tensor&lt;int32&gt;[600 800]
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/0.png" style="width:100%;" /></div><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">{:key "1", :data #tech.v3.tensor&lt;int32&gt;[600 800]
 [[124 120 121 ... 117 121 124]
@@
  [136 137 135 ... 114 111 108]]}
-</code></pre></div><img src="index_files/1.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "10", :data #tech.v3.tensor&lt;int32&gt;[600 800]
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/1.png" style="width:100%;" /></div><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">{:key "10", :data #tech.v3.tensor&lt;int32&gt;[600 800]
 [[125 120 120 ... 116 121 127]
@@
  [134 135 135 ... 114 112 108]]}
-</code></pre></div><img src="index_files/2.png" style="width:100%;" /></div><p>)</p></div>
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/2.png" style="width:100%;" /></div></div><p>)</p></div></div>
 

### 2024-01-23 docs/projects/noj/ml.qmd
various notebooks - rerendered

--- 2024-01-11 docs/projects/noj/ml.qmd
@@
   html: {toc: true, toc-depth: 4, theme: spacelab, output-file: ml.html}
-highlight-style: solarized
 code-block-background: true
@@
 ---
-<style>.table {
-    overflow-y: scroll;
-}
-</style><style>.printedClojure .sourceCode {
+<style></style><style>.printedClojure .sourceCode {
   background-color: transparent;
@@
 <script src="ml_files/md-default0.js" type="text/javascript"></script><script src="ml_files/md-default1.js" type="text/javascript"></script>
-<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
 
@@
        Min          1Q      Median          3Q         Max
-   -0.7900     -0.2237      0.0394      0.2235      0.8037
+   -0.8225     -0.2071      0.0197      0.1946      0.8181
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.7690     0.3120     5.6689     0.0000 ***
-sepal-width         0.6801     0.0844     8.0599     0.0000 ***
-petal-length        0.7043     0.0664    10.6014     0.0000 ***
-petal-width        -0.5256     0.1508    -3.4858     0.0007 ***
+Intercept           1.7397     0.2949     5.8997     0.0000 ***
+sepal-width         0.6671     0.0809     8.2462     0.0000 ***
+petal-length        0.7522     0.0638    11.7822     0.0000 ***
+petal-width        -0.6293     0.1438    -4.3776     0.0000 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3057 on 96 degrees of freedom
-Multiple R-squared: 0.8690,    Adjusted R-squared: 0.8649
-F-statistic: 212.1968 on 4 and 96 DF,  p-value: 3.179e-42
+Residual standard error: 0.3188 on 96 degrees of freedom
+Multiple R-squared: 0.8758,    Adjusted R-squared: 0.8719
+F-statistic: 225.6278 on 4 and 96 DF,  p-value: 2.442e-43
 
 ```
-</div>
+:::
 

### 2024-01-23 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
various notebooks - rerendered

@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><p>(</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.7
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/6.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.8
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/7.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.9
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/8.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/9.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.1
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/10.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.2
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/11.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.3
+<div style="max-height:600px;overflow-y:auto;"><div><p>(</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">0.7
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/6.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">0.8
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/7.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">0.9
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/8.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">1
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/9.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">1.1
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/10.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">1.2
+</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/11.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">1.3
 </code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/12.png" style="width:100%;" /></div></div><p>\]</p></div></div></div><p>)</p></div></div>

### 2024-01-25 docs/projects/math/wolframite/index.qmd
Wolframite - rendered doc

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default0.js" type="text/javascript"></script><script src="index_files/md-default1.js" type="text/javascript"></script>
<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>

::: {.sourceClojure}
```clojure
(ns index
  (:refer-clojure
   ;; Exclude symbols also used by Wolfram:
   :exclude [Byte Character Integer Number Short String Thread])
  (:require
   [wolframite.core :as wl :refer [wl]]
   [wolframite.tools.hiccup]
   [wolframite.base.parse :as parse]
   [wolframite.jlink]
   [scicloj.kindly.v4.kind :as kind]
   [scicloj.kindly.v4.api :as kindly])
  (:import (com.wolfram.jlink MathCanvas KernelLink)
           (java.awt Color Frame)
           (java.awt.event WindowAdapter ActionEvent)))
```
:::

::: {.sourceClojure}
```clojure
(def md
  (comp kindly/hide-code kind/md))
```
:::

# Wolframite

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/),

It is mostly copied and adpated from [the official demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).

## Init (base example)

::: {.sourceClojure}
```clojure
(wl/eval '(Dot [1 2 3] [4 5 6]))
```
:::

::: {.printedClojure}
```clojure
32

```
:::

## Strings of WL code

::: {.sourceClojure}
```clojure
(wl/eval "{1 , 2, 3} . {4, 5, 6}")
```
:::

::: {.printedClojure}
```clojure
32

```
:::

## Def // intern WL fns, i.e. effectively define WL fns as clojure fns:

::: {.sourceClojure}
```clojure
(def W:Plus (parse/parse-fn 'Plus {:kernel/link @wl/kernel-link-atom}))
```
:::

::: {.sourceClojure}
```clojure
(W:Plus 1 2 3)
```
:::

::: {.printedClojure}
```clojure
6

```
:::

... and call it

::: {.sourceClojure}
```clojure
(wl/clj-intern 'Plus {})
```
:::

::: {.printedClojure}
```clojure
#'index/Plus

```
:::

a simpler way to do the same -> fn Plus in this ns

::: {.sourceClojure}
```clojure
(map wl/clj-intern ['Dot 'Plus])
```
:::

::: {.printedClojure}
```clojure
(#'index/Dot #'index/Plus)

```
:::

 Call interned Wl functions:

::: {.sourceClojure}
```clojure
(Dot [1 2 3] [4 5 6])
```
:::

::: {.printedClojure}
```clojure
32

```
:::

::: {.sourceClojure}
```clojure
(Plus 1 2 3)
```
:::

::: {.printedClojure}
```clojure
6

```
:::

::: {.sourceClojure}
```clojure
(Plus [1 2] [3 4])
```
:::

::: {.printedClojure}
```clojure
[4 6]

```
:::

::: {.sourceClojure}
```clojure
(def greetings
  (wl/eval
   '(Function [x] (StringJoin "Hello, " x "! This is a Mathematica function's output."))))
```
:::

::: {.sourceClojure}
```clojure
(greetings "Stephen")
```
:::

::: {.printedClojure}
```clojure
"Hello, Stephen! This is a Mathematica function's output."

```
:::

 ## Bidirectional translation
(Somewhat experimental, especially in the wl->clj direction)

::: {.sourceClojure}
```clojure
(wl/->clj! "GridGraph[{5, 5}]")
```
:::

::: {.printedClojure}
```clojure
(GridGraph [5 5])

```
:::

::: {.sourceClojure}
```clojure
(wl/->wl! '(GridGraph [5 5]) {:output-fn str})
```
:::

::: {.printedClojure}
```clojure
"GridGraph[{5, 5}]"

```
:::

## Graphics

### A helper function to view things in tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly)

::: {.sourceClojure}
```clojure
(defn view
  ([form]
   (view form nil))
  ([form {:keys [folded?]}]
   (-> form
       (wolframite.tools.hiccup/view* folded?)
       kind/hiccup)))
```
:::

 ### Draw Something!

::: {.sourceClojure}
```clojure
(view
 '(GridGraph [5 5]))
```
:::

<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlh4AHgAff4ADI2PjU5Pzc7QDY8Rjg7QTo9Qjw/Qzo+RTw/RDtART5BRT5DSDpDUDpEUj1GUj1GVDpHWj1HWj1IWT9LXD1MY0BDRkJER0BDSUFESkVHSUJGTUZIS0NIT0ZJTUlLTUpMT0VKUUdNVUtNUU5PUkhOVkBLW0lPWE5QUktRWkxSW0xTXE5VX1FSVVJVV1VXWVZYWldaXVhZW1pbXVtcXkJQZk9WYEVWb1BXYVBYYlJaZFRbZlRcZ1peY11fYFVdaUtbc0pcd0pceF5gY1dgbFliblpjcVtkcl1mc15ndV9odmFiY2FjZGNkZmJlaWZnaWlqa2tsbWxtbm1ucWtvdmBqeGJtemNtfGRvfmZwf3Bxc3NzdXN0dnV2d3Z3eHN3fHd4eXV4fXl5enp7fHt8fX1+f1Flg1dngF9wi1lvkGZxgGhygml0g2x3h2RziWZ0im56ind9hH9/gHl+hnJ+jm5+lmF4nGh7mXN/kXB/l2V9on6BhHSAknWClHiFlnmGmHuImn2KnX+Mn2eApmuDpm6GqnGGpn2LoHqLpXeNr4CAgYCChYOEhIaHh4eHiIOHjYeIiISIjomJioqLjIuMjo2NjoaMlo+PkIONnoSPno+QkIWQn5KSk5CTlpOUlJWWlpGUmJKXnpqamp2enoGOoYKQo4ORpIWTpoaUp4eVqYmXq4qZro2brpWdp56foJOcqZSdqpGdroKVsoSWso2bsY6dsomdupCftJGhtpOiuJSjuZWkupOjvJenvpqnu5movp+rvqGhoaOjpKampqOlqqenqKmpqa2traOosaKqtKGrurGxsbKytLa2trS3vLq6ur29vZipw5uswpysw5urxJ6uxp+wx6GyyqWzyKO0zKi2yam3za+6yqy6zrG5xLnE1bzH2MLCwsXFxcXGyMnJyc7OzsDI1cXP3cbQ3sjR3tLS0tXV1dnZ2d7e3srT4NTb5eHh4ebm5urq6u3t7eXp8PHx8fX19fb3+vr6+v///////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAA4AHgAQAI/wDxCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtWa9VlFexBHX1eE9YllciHFW1qGyLi66KGvb0JkYF1mI3aO7UFycF1GA1aMIT0YINXOMKNjEFyE9JxyuzEmyIFHjg/W0YKgypwoGLYMvF4yzIMmcKxyc0BNdcJMCI3PUhJgBb2KUHdSw6Va14BnrgYlURNONDZcGYr8FegrBizivEJ6S4yOGARdxaSriSH+mQBVxajuiSP8kh6A5cWxqlCR/p2DVeWx3TiSvZyHQ+1EWQrM+cef9KgXvJLfEGu/xYgA5ERFDwnvYlBKALLVEKOGEFFZo4YUYZqjhhhxq6IYC1rxHiwCHdGjiiSimqKKEeAggzXvRCIDHijTWaOOJhwhAC4MKuHHjj0AGKUsApTBIAnIQKcMBg4EgcI02UEYp5ZRUVmnllVhmqeWWWQYCon8G9MLlmGSWaeaZUa5igHnOGbAKmnDGKSeZvRjg3XnWHHDJnHz26ec1Btj3HghzQbSOAra8l4R4v8VjwSjvrRFDcvd40N95d3hgT3IyqHGfBfEkF0USIiqwjkSLoGAdNtbcYUE60oX/wsGOuo2iADjSKYMBKsShgkGhv4GjAKS60cJBK9KlowAfIRZnwiIT0UOaDkaQ0AFb0t0jiQU4GKGCBUjGqkANRtSgQCjSCUSdCkbcYEEke0nHTAcmGKGDAnGsRhE4cJRATIDpCjQOJBK0wk7AAqnDSQScqIMwPuy0EoEj4zwMDzESwEHWRegQ8vBA7giy6cfzCDLPx/jYI4g7KONDCDoZmeMxyiGP/HDJJ3+sMssov5xRxy3XjDLOKO/css8YyRy0yEObXPTKR8OMEdA0M02y0zpD3bPUFyldtc0IE501zx8jzfHMHwt9dc4PG711zGg/rPbNWLetddlcW0R12lbT/802wm7jDffSYAcstt1kP2y23nEjPHfYdQN+t+J5V+Q134Wne7jkiSO8eEV7y9035H8HHDjlg3/ddOnpnu555RSF7vjohkdu+uSvp4756k93HvDnsTce8OO1sy6d67/DPtHlomcu3ea3+54u8BPJPjztmtveOu7J694872NH/bPw6RKfvfHJIT+98hIxP7vzyUG/vfTSUS+R9eVj/7z2x3O/vvfvAx/ixDc18knHfPtD32/UVz/2RcR914Pfb+TXP/olx34Rwd8B9Rc//qXPfw0EYAQFyDkCno1wJIyeCS0CwfxJkDUU/KAFf4NBiGgwOQjsoAJZw8ALOhAiLdzgC/9FE8MFgtCH40Ph2nq3QssZEIccnKAHjThD1tTwITf8TQ6luEPR9JCGP3xIEKE4xMsUkYdHBGMSVbfE8L0taU/UYhRhOEU0VlE0V3RIFlmzRTp28TJftGIYHTJGOZaxMWf0YhoFucbdtXGAb+xaHPk4RyLWUZF3vEweG7JH0fTRkn9sTCDxOMiGFJKSh+RLIgG5SFI28nuPLGEkWThJT1bSjJdkZSYbs0mGdPIyn8RlKPkySk2WkiGntGUq6bJKUbbSmK8MYCxVOEsnKtFvTKxm8K5JumwKDo7cLJ43UVfAcJ5vnLkDJxux6cZvnnCd3WwnOSVpzgSis3vlhKc45Zn/Tnrq85z8xOc7HclOSLqTlvXU4T3/l0+CxtOg80ToP+0ZUIYOFJYFleVBrTlRhVY0hA3F6EM1GlGOOnSfEO0n4xLKxYWC1J8nBWhKBbrSjrb0o0hUZ0wpOlOL1nSnHu3pSyUK1JsKNacXlWZGqblRiiQTmLdEZC6duUu+9HIhv2xMMKU6TLoUk5fHXMhTtRpVVU6VmM8EazRHOM35NdGptYTqMtvSTLRWlS5XVUhW+bJVs3a1LV+1algVMla+lpWZZ/VqWgW7Vhem0K3aXF5cyTrXstRVsXdtS14Tsle69BWxfy1LYPE62IQU1rOHpWtiAbtY0jZWiI+t4Fsly1I//7oUqT8VKUpJqlKT6lamvKUp6CZr2Mp25bKszWxZNouQ07bls6oNbVdGq9nSIqSzz02tZVcr2tZWV4SObatsI3s/4qLWuFxBbneV2xXmHsS5ZYHudqXLFeou17oHwW58tXtc7k7Xu/cFL2zFK8PZlre2oLytGnX6W54G16fDRbAwFcxIBit1pEwt6TZtalucLhimDQ7qg4caYQ4n2MMVrsg9lDGFB3jiVAh7BhgaIAkEIUwciWiAIjYWMHJIogFg8A3C1uGJBkxBGfGSiDygoAEjXAEH4EpXPb6AASJcwQcKiE62FqGAIahhCBZYRJJ/4wkF+OAKRFhAGPTzG2Jw6/8KRtBAFOQxkTCsYDi68VLFkmOJEOiCOKq4ADOkQwwN0AobtOhAMOSFgVQQRxchsIR0xjEs4kSjBmGQSDoMsCriWMEJyYGHAnh1nje0YD4Z+MN7/pAB9FKlBW94DyoUUJvfOMEK78GFARwGEWOEgEGlWNM0hk3sYhv72MhOtrKXzexmO5vZfFAAg2hBgFk8+9rYzra2tz1sagRiTTASwCi4Te5ym/va0ZgFAQ5NnGWd+93wjjcvCECs84DAGBHxNYNGIQBcQOPf0YBGwAcu8IIT/OAGTzjCF67whjP84Q6P+MPp8KXzUDsVAJe4xiHO8Y17vOMgb7ghBIBnSwvAEBn/D7nKP87ylbu84apY93usYQA6tPzmL885zj++CwEU6T0hwDdENt1p3Xw61KN+j6lRrerz/AEDbL4MC2J9HlRYoNasufV7cmEAWEXkCzUoeSkUsOffUMIEbFrFAgadHGBoYFXWwAUHgMFo9+hGFyighHTEoYCfY+PSmZZIPJ7QZDXca9HSqQcXMGAENWCZMVtWABHUQAQFiDldrvGBGoyAAS5EXTTBsIAO4KyBJ9B5IiueggM2weuAOcMLDKjxw8ChBwboAVcI83EDvICtgKljEw448pirZ97sulor6v0ve7niXoPotyvy7S99t2Lf9uLX+cXf7/Gzkvz6Atj6AiZj/2wLTN4MZh/6/E2vf72//K00vyDwRf/2sdJ96n+f+dcvyPO5En31T18r1Yd/4WdI40dFBmZ+EsZVFOZKFsZWSwVZTUV8CehXCwhNDRheDzheEXhgJjZhKMaAIHZhu5VhvbVhRdVhR/VhRBViRjViuFViJ3hiKZhiKyiCwEWCwmWCLIiCLqiCvmWDDoaDEKaDQChiQkhicDWBoFWBahVSRdiCR/iCSdiBCviBFphUDohhEKhhtEWFFGiFTYiFGKiFGsiF7XN+/Jd+W1F/AHh/7pd/BLF/W9F/a7h+9td+WvF+BBF/aTh/V8GGWRGAb/ha4kdgBlh+QISGc6iGyGeHbf+Ih1mhhwMhh1pBh434f4HohnkIhwPBh4voh1YBiFghiJtIiARoiHZ0gImohNHFhIzlhFk4gltYgl0Ygx44gyCYW0/Ig1Hog1Noi1WIi1eoi7F4g7OYg7W4gzLYgzQIg8p4i8yYiz9YjEF4jEMogV64hGD4iiFIjUZojUiIjcD4hcIYhjXojVAIjlIojs8YjNE4jNM4hrJYhrTIgeOojeXIjecoj8ZIj8hoj+1Iju9ojvE4YBlIfhuIgNnYitvoWhdokGSIkGaokPfIkPnokN3Ij9Xoj9cIkLu4jL3YjL8YkPg4kProjB8JjSEpjSOZku64kvBIhOjIi+roi8nokgL/CZMEKZMa+Y0cGY5nyIrz5YoYSYw9mY4/uY5BuZBD2ZDfBYtHSZNJaZNLWZFNeZFPKYYQOY8SWY8PpIiVyIjc54iZCIlYIYkCQYlZYYljiYmjqImRyIkC4YlhCYpVIYpXQYpxaYqoVICpiIhiBJZrKZb0R5ZvaZZXgZb4oJZYwZaF6ZZ5CZdnKZf4QJeDaZdUgZdWoZeTyZfK5JeYpIqBKZTSR5RZaZRb2Y9d+Y9fSZr+Z5oBBpWpuZGr2ZGtyZSl6ZSxqZWFeJCHmJCriJuvqZvgJ5u9GZG/OZHBaZW5iZW7iZrHyZXJ6ZXLSZIWaZJFiZIzCZI1KZI3uZ0q2Z0s/8mOOFmSOnmSLQmeLymeMUme6pmT7LmT3xmV3DmV3umR72me8Yme8zmbPlmbQEmR1nmV2HmaBRmdqjmdrGlDgtmYhPmHhhmZiGkVimmZDoqZU6GZVcGZiUmZjHkVjgmhkLmZktmhGCEOcDABxYB16UIOkAABBvMw6/AJEPAJMBYwEQMBkGBjAXMxE6AxFVEPcaAAOjAEIeABvfcb90AJCrACRYACGBAuyREK40IE5oIs6UIdKUAEN6AAkzB8ouEMHkACRHAvcfB5DfEIIdBpd6AArccardABd4INgWABPMYaumIKxGEKvyIdwiIo2DALHYClv5EOFnApxRECkSARh/8yC4rCKKzhKH7HKmogA5RiKe+RKWDKF53yHoGAAaHyG1GABKVyo26xJJ5qANjADazaqq76qrAaq7I6q7Raq7Z6q7X6bc0CaAbwC7j6q8AarMI6rK2qJr5QIAYAC8S6rMzarMD6C3YycwegCc5ardZ6rdmAAPVGHBwALA5BDCgAbAIQC0FSruaaIm2QALtaLCRyru76rhiCBwHwIucRDQEwI/Car/maI4mCJwrQBvoasO4aC0RiJFLaEORgAMd6HmugHr/BHuwGHyKQHPRQaedRp2hKFyKwB6UCMKwhBARyHrygADxqFlHgA7tKCwqQpKIRB2H3aMchHZ0QAguLDb7/EAKdQGgakAuWVgPakRzOoACHVg0+AAWbuhDwMAMhsAZ0gAQKkAnpIg9M0AFXcAdVsABxcLRelQUaYAV3YAUYkAUZSxf3MKRVcAdqwAFMcHp8ZgFGQAdrQAIywKIQUQ+iMAMHEAe4ly5n0QQDwAUsmxzGIAUDIAXeKi9cMABNoBcIEw5kcAA80Ar6op30GZ72OZ74WbnrebmaZA6eKVegqUuiSUgNCqIPGooRSqITWhWE4LnGeYq++ZfAOZrCWYcjuqElSqGuy5uwi5yyq5y0y5zD6ZzttbvQ2bvS+bvUGbwD2pwFulzGS7n+iZQAqpS3Kby2C5vF+7mUFbpUNbqm/1S6VhGiqHu7VMGhusu9xeW9dgW+yCS+VUG+d5m6uLu6VNG66nte7ItZ7itW8EsV8puZ9Hu+ucu60cuT0yuV1UuV19u8w/u82/u6fYmKoQmYpOua2UuczHfA7qm58Mm58lmVDpzBxLvB+Wt8+5tc/UtY/zsVAZyhAzwV6GvAJ6x9KbxeK2xaLSwVLywVGkrA9jsV+CvBn0nBomvB4YvBl6i9JkzEoGvE34vE76vEbcnE7sfBmZvA9bnA99nA5Xmd54lXWCygX0ygYWyg6enB+gnCVjXGDErFj2nFpfiQCEqbCjo9boxFOxwVPRwVPyzDBXy/lGmhpouhPhzDUjHD9/+bx3q0x1DRx1Dxx4kcyEI8yI78FJD8FJIcFYosxIzMSZfsFJnsFJsMFZ0sFRUayk0xyk1Ryk9xylExxLw7wbFbwbN7wbW7xBp8xTUsfzesfDncXKrMFKzMFK7sFLAMFbJ8vLTsu7YMvLiMvbpcwrzsxN0Lxe0rxf4LxyIqx5H4yb40zEtRzEtxzE2RzE+Rytxcvt58luCMVeKsFOSsFObMFOjsFOqcy1W8y3n4znoVz0kxz0lRz0txz02Rz9K8z9Tcz73ch7/MfsH8XgCNFAKNFAStFAbNFMssvXX8n3ccoNVZxs57xtDb0J/40HcY0QZByON7uvNrvoAcxKjsz5z/NdFHUdFHcdFJkdFLgdAjPM0Q3MSzXMS1fMS3nMT6HMf8/M0mXZco/YgqDX82bRQ4bRQ6jRQ8rRQbjcAdTb0fbb0hnZ9gvJ9i3NSX+dRlGdV7ONVFUdVFcdVHkdVJsdUdrMWWy8WY68VibcZkrVk0fV1sTRRuTRRwbRRyjRQ+LdIPTNIRPNRPXNRRfNRTnNTdvNTubNYXitaHqdadGNhDMdhDUdhFcdhHQddZ3NUK/NUMHNZqPNZsXNbWvL7YzL/azMLr/NLtnJh/nV+eLRSgLRSiTRSkbRSJvdcj3dclHdv6O9sqXNs6fNsCDNOTLNOxvNvYB90wLN2cTMmobMnY/33I2m3K3F3dmF3Imi2hnD2XvR0Uvx0UwT0Uw10Upk3Gxr3YyF2cGWnXm4vXnVveLW3IfozI203dyuzdlM3Olq3b/h2/Lh3duU2hBp7QSr3QTK3cKMzcOOzcwvzdAR7erzzeymzd+rfeQNHeQPHeQhHfRIGW61AJNPAMk5su7AAKFKAModqjw0ABw0C3yREPy0ABoHAwCEMPzkADlWCqEXEPrkECK7AALVB2bWcBIIADGiACQpYrG8ABOMABHSB02yECWs4BGAAMWksX48ACF3ADJLAYZZ4QngACjkapGSDkbaYBfjcHCuB1v/EMFvAHzfIHtyId5GABc0AcpaABXv/OGuyQAWrQLKnAAegSEexBarphDUTQBckhD6n2HlWwBJQiAlRX6W9wAm3OFUtQBe/RBxvAtqLBBUQgawASEcyAqhdrAd7wDbie67q+67ze677+68Ae7MI+7MHuCgdQDbJmANtA7Mze7M7+7NCe68lgAH92HrpgAMkQ7dq+7dze7NtgAJSuG9VwAK7Q7eZ+7ujuDfWxrtjAAWz3EOAKbABQCIhQ7/Z+7/ie7/q+7/ze7/7+7wDv72awAOxuCwJgBwGf8Aq/8Azf8PZ+BgGQG+dBDQFwBg5/8Rif8QpvBwBQdLqxAGag8SI/8iRfCAX7HkcSEZRWcrrxBjOQHOygAB7/3wcdUOpaUbF6eh6lYAGs3hiV0ge5ZgB0LhoyEOq6IQ1kFxH2oARGYO0YkOiikQU6gOy6EQ2QLh2pIvHYQA0qAC1TygElZw06kAXSYQwaUO26YQRKYPMFsQ4ncAN3EAhrgAFjkC7w8AIoMAeBwAYcEAVsf/NKAAJvEAhvEAJKEOOicQ9RoAGDPwco4AI87vOksQaBcAc4cAJI/hDx8AgiAABOcLi/QQ+ZwAIAIATB8PfUFwowAAAyEApjyxf3EAxCAAAssAmI/xvK4AQAIAKRcOOxMwhBkwcAHsl54OHInAcE/hSDIOJxSOI/YeI/geJBoeJDoZgf+t/nrbrpvZjO/+8T0O8T0g8U1C8U1t/9PfH9PRH+PzH+QVH+HB7JAi7eyY/PHmr+PIH+PKH+PsH+QOH+Bw4Q+AQOJFjQ4EGECRUuZHhwnqB5DSVOpFjRYkV7gtxd5NjR40eDhNCBxIeOEEmUKVUWdCfI3kqYMTk+jCjT5k2FGTfi5NlToEiSJn0OvdnyJVGkKmkmZUpSZ1OoHoGCFBrVakWjV7U2XLrVK8KnX8UWnPqx6li0WdGO7br2a1i3X8t6PBt3q1q7WtvmtQqXr9W5Hev+hYqXcNO9h5P6VZw0MMfBjYkaljw0ceWejDH3fHwx8maclEHfvDxapmbTMjtb/JwapmjXK0vHTv+JmnbK1RVb3yYJmzfI2b892hYudSTVk8VV+lZ+MXhzjBqho8xNcfd0isyxS3y+nSFx7w2rT7wefqF28wm7pz8Inj3C8RLLvzeInj7B9fcFutc/MH7D+frDx77+8tOPPwH/YyjA/gjUz8D7EOxPwYUY1M/B+yCkT0L9KFTIwvswpE/D9zi8z8OEQKRPxPdIZM9E+lBESMX3WGTPxfRgfE/Gg2hkz8b0cDRPR/Z4NMjH9IA0T8jwiEzPyIKQNE/J8Jj0zknzoCRIyvCo9M7K7bAMT8uBuPTOy+3AxE5M78gUyMzt0MROzenY3M7NkpITUCE5p6MTOjuxwxNO7PqE7s//5gKdblA990TI0OYQVU5R6Bh1lE+XLkVI0uIobc5STQ+CVDlOhfNUOVBDZSlTVfGDqFWCTi0uVVgHZLXWUn+TVThaYR21uFx52/W3Xlv9VbhgbxuWt2JVPfa3ZGlb9rZmQ32Wt2hjm5a2ajW99rZsXds2tm4v/Za2cFMb17VyHT03tnRNWze1dvd817V4R5vXtHoFvDe1fEHbd7R+G7wV1oA3Gxi0gi88uNWEMVt4s4ZDfFjViCubGLOKV7w41Iwl27iyjmv8WNOQGxtZspJ/PPnSlBVbubGWk3zZ0ZgPm1mxmqe8ec+cCdv5sJ67/FnAoP8amrCizzy6wFdrxWfp/7+ajvPpB6OulWq+rC4U6wy1hpXrvLye7l/TkuaLbLvMhg7t0dTOi+243G4ObtDktotut+xWDu/N9I6L77X8Lg5wzAR3i3C0DBcO8coUX4vxsRz/DXLJJEeLcrEs5w3zxjQfi3O5jjOrUV/BHlHsVkn3yvPbQFdMdLFc3wp22mQ/jPa3pJMaH9xj050w3r2yXavgXRv+r+K3Ov6q5FNbnq/mtXoeMNPpQt1Y1VtkXdXro4retOnzqv6q8KEaf7Ty7Tq/L9+lXh+09uN6P6r0m5p/s/rduh+q/DFlf5jp31r+15QAOiZ7gtmes7p3o++FKoFIGWBlCoiWAzJlgkSpoP9kLsiWCGpqg0PpYGM+KJYMLiZ+tSqhYk74lRQiZYQ+aeFhXuiVGBJlhpxZIGQaaK0HBimEl9ohT2pImBtuJYdDKSJOjviXJOpliI5q4k2eyJcoXmWJPqmiTa6YlyxaZYuZWSGsvmiXMEZljDzpomp66JkfeiuIS5rintoYkzPGJY1QWSNO7giTPLplj4ipo4D+uJJArmWQTOnjTQ6pkkSmZY5VKmR/HombN7Imjuaa5JcqeaAytiqSY1lkUhppk0tSJ5O62aS7OpmmT0YolKoapVhKiZRTnmaWoXJTPFjxA3Lco1byOIYNxFGPWtGjGTZoBj1qVQ9x2OAY8qjVPcj/8QNWxMMjxMDAAjhgACGso1XM8IACOKCAF5CjVeBgAQJCgAAWgKNV5IiBAc7pAWa0ah1LsOcCMEAMjnATENjARjSM4AFtasoZFriDNbBBjStkQJyaGocF3uDQarxBAerU1DoycAVqEPQOGHBGqODhASNEAxvWCMQ/LQIPCwSCoDPVQRw0RQ8P0GGmBDVCFELlgivsFBtXiEGoomAEoc7BA8i8VBx04NCZBsIC8KiIMzQA1Zn+AQPo4GpXvfpVsIZVrGMla1nNelazHsMA1RCqKRRQDrTGVa5zpWtdu9oNA+RCqLgwQDfs+lfABlau5TAAKoRKDQMgQ7CLZWxj0YGB/z8I1RoaKClFgJECoWLDFAGogyA8+1nQhla0oyVtaU17WtSm9rRAWEBmcREANKhWtrOlbW1t+9kyBCCkO6VGAMpwW+AGV7izRUMAcCHZBQRhuMtlLnMHUQcAmCKzKAhGRcShALbudA4v6KgCdCHUQGxAmI6ShwJUIdRUKICajrpHBga6U10oYKKOcsEchFoNBYijIvV4QVBnGg0OtEJT93BCEXZaDRJQIlRfwAFWrYGDMISKEiTILkGJ4ITxOqoVHFDpTInKVIqQIwNDGIUq7sCBKGTYUewQAQ4CsYo+kKAHIHZUPFqQAkCo4g81aEFCL0WPHoSgD6oIhA48wI5Q3YIjChzYgypGQYQMcNQi7OBCBizAglao+FLxiMMGLCCCTdD4x4vwgAU8wAhnqqoemziBATYQBx8PuBUsUEAGtPCOj9QjzrC6B1V/h494aLlVgf7dPeJxlD8nWtGLZnSjHf1oSEda0pOmdKUtfWlMZ1rTm+Z0pz39aVCHWtSjJnWpoRMQADs=" style="margin-top:1rem;" /></div></details></div></div>

::: {.sourceClojure}
```clojure
(view
 '(GridGraph [5 5])
 {:folded? true})
```
:::

<div style="max-height:600px;overflow-y:auto;"><div><details><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlh4AHgAff4ADI2PjU5Pzc7QDY8Rjg7QTo9Qjw/Qzo+RTw/RDtART5BRT5DSDpDUDpEUj1GUj1GVDpHWj1HWj1IWT9LXD1MY0BDRkJER0BDSUFESkVHSUJGTUZIS0NIT0ZJTUlLTUpMT0VKUUdNVUtNUU5PUkhOVkBLW0lPWE5QUktRWkxSW0xTXE5VX1FSVVJVV1VXWVZYWldaXVhZW1pbXVtcXkJQZk9WYEVWb1BXYVBYYlJaZFRbZlRcZ1peY11fYFVdaUtbc0pcd0pceF5gY1dgbFliblpjcVtkcl1mc15ndV9odmFiY2FjZGNkZmJlaWZnaWlqa2tsbWxtbm1ucWtvdmBqeGJtemNtfGRvfmZwf3Bxc3NzdXN0dnV2d3Z3eHN3fHd4eXV4fXl5enp7fHt8fX1+f1Flg1dngF9wi1lvkGZxgGhygml0g2x3h2RziWZ0im56ind9hH9/gHl+hnJ+jm5+lmF4nGh7mXN/kXB/l2V9on6BhHSAknWClHiFlnmGmHuImn2KnX+Mn2eApmuDpm6GqnGGpn2LoHqLpXeNr4CAgYCChYOEhIaHh4eHiIOHjYeIiISIjomJioqLjIuMjo2NjoaMlo+PkIONnoSPno+QkIWQn5KSk5CTlpOUlJWWlpGUmJKXnpqamp2enoGOoYKQo4ORpIWTpoaUp4eVqYmXq4qZro2brpWdp56foJOcqZSdqpGdroKVsoSWso2bsY6dsomdupCftJGhtpOiuJSjuZWkupOjvJenvpqnu5movp+rvqGhoaOjpKampqOlqqenqKmpqa2traOosaKqtKGrurGxsbKytLa2trS3vLq6ur29vZipw5uswpysw5urxJ6uxp+wx6GyyqWzyKO0zKi2yam3za+6yqy6zrG5xLnE1bzH2MLCwsXFxcXGyMnJyc7OzsDI1cXP3cbQ3sjR3tLS0tXV1dnZ2d7e3srT4NTb5eHh4ebm5urq6u3t7eXp8PHx8fX19fb3+vr6+v///////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAA4AHgAQAI/wDxCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtWa9VlFexBHX1eE9YllciHFW1qGyLi66KGvb0JkYF1mI3aO7UFycF1GA1aMIT0YINXOMKNjEFyE9JxyuzEmyIFHjg/W0YKgypwoGLYMvF4yzIMmcKxyc0BNdcJMCI3PUhJgBb2KUHdSw6Va14BnrgYlURNONDZcGYr8FegrBizivEJ6S4yOGARdxaSriSH+mQBVxajuiSP8kh6A5cWxqlCR/p2DVeWx3TiSvZyHQ+1EWQrM+cef9KgXvJLfEGu/xYgA5ERFDwnvYlBKALLVEKOGEFFZo4YUYZqjhhhxq6IYC1rxHiwCHdGjiiSimqKKEeAggzXvRCIDHijTWaOOJhwhAC4MKuHHjj0AGKUsApTBIAnIQKcMBg4EgcI02UEYp5ZRUVmnllVhmqeWWWQYCon8G9MLlmGSWaeaZUa5igHnOGbAKmnDGKSeZvRjg3XnWHHDJnHz26ec1Btj3HghzQbSOAra8l4R4v8VjwSjvrRFDcvd40N95d3hgT3IyqHGfBfEkF0USIiqwjkSLoGAdNtbcYUE60oX/wsGOuo2iADjSKYMBKsShgkGhv4GjAKS60cJBK9KlowAfIRZnwiIT0UOaDkaQ0AFb0t0jiQU4GKGCBUjGqkANRtSgQCjSCUSdCkbcYEEke0nHTAcmGKGDAnGsRhE4cJRATIDpCjQOJBK0wk7AAqnDSQScqIMwPuy0EoEj4zwMDzESwEHWRegQ8vBA7giy6cfzCDLPx/jYI4g7KONDCDoZmeMxyiGP/HDJJ3+sMssov5xRxy3XjDLOKO/css8YyRy0yEObXPTKR8OMEdA0M02y0zpD3bPUFyldtc0IE501zx8jzfHMHwt9dc4PG711zGg/rPbNWLetddlcW0R12lbT/802wm7jDffSYAcstt1kP2y23nEjPHfYdQN+t+J5V+Q134Wne7jkiSO8eEV7y9035H8HHDjlg3/ddOnpnu555RSF7vjohkdu+uSvp4756k93HvDnsTce8OO1sy6d67/DPtHlomcu3ea3+54u8BPJPjztmtveOu7J694872NH/bPw6RKfvfHJIT+98hIxP7vzyUG/vfTSUS+R9eVj/7z2x3O/vvfvAx/ixDc18knHfPtD32/UVz/2RcR914Pfb+TXP/olx34Rwd8B9Rc//qXPfw0EYAQFyDkCno1wJIyeCS0CwfxJkDUU/KAFf4NBiGgwOQjsoAJZw8ALOhAiLdzgC/9FE8MFgtCH40Ph2nq3QssZEIccnKAHjThD1tTwITf8TQ6luEPR9JCGP3xIEKE4xMsUkYdHBGMSVbfE8L0taU/UYhRhOEU0VlE0V3RIFlmzRTp28TJftGIYHTJGOZaxMWf0YhoFucbdtXGAb+xaHPk4RyLWUZF3vEweG7JH0fTRkn9sTCDxOMiGFJKSh+RLIgG5SFI28nuPLGEkWThJT1bSjJdkZSYbs0mGdPIyn8RlKPkySk2WkiGntGUq6bJKUbbSmK8MYCxVOEsnKtFvTKxm8K5JumwKDo7cLJ43UVfAcJ5vnLkDJxux6cZvnnCd3WwnOSVpzgSis3vlhKc45Zn/Tnrq85z8xOc7HclOSLqTlvXU4T3/l0+CxtOg80ToP+0ZUIYOFJYFleVBrTlRhVY0hA3F6EM1GlGOOnSfEO0n4xLKxYWC1J8nBWhKBbrSjrb0o0hUZ0wpOlOL1nSnHu3pSyUK1JsKNacXlWZGqblRiiQTmLdEZC6duUu+9HIhv2xMMKU6TLoUk5fHXMhTtRpVVU6VmM8EazRHOM35NdGptYTqMtvSTLRWlS5XVUhW+bJVs3a1LV+1algVMla+lpWZZ/VqWgW7Vhem0K3aXF5cyTrXstRVsXdtS14Tsle69BWxfy1LYPE62IQU1rOHpWtiAbtY0jZWiI+t4Fsly1I//7oUqT8VKUpJqlKT6lamvKUp6CZr2Mp25bKszWxZNouQ07bls6oNbVdGq9nSIqSzz02tZVcr2tZWV4SObatsI3s/4qLWuFxBbneV2xXmHsS5ZYHudqXLFeou17oHwW58tXtc7k7Xu/cFL2zFK8PZlre2oLytGnX6W54G16fDRbAwFcxIBit1pEwt6TZtalucLhimDQ7qg4caYQ4n2MMVrsg9lDGFB3jiVAh7BhgaIAkEIUwciWiAIjYWMHJIogFg8A3C1uGJBkxBGfGSiDygoAEjXAEH4EpXPb6AASJcwQcKiE62FqGAIahhCBZYRJJ/4wkF+OAKRFhAGPTzG2Jw6/8KRtBAFOQxkTCsYDi68VLFkmOJEOiCOKq4ADOkQwwN0AobtOhAMOSFgVQQRxchsIR0xjEs4kSjBmGQSDoMsCriWMEJyYGHAnh1nje0YD4Z+MN7/pAB9FKlBW94DyoUUJvfOMEK78GFARwGEWOEgEGlWNM0hk3sYhv72MhOtrKXzexmO5vZfFAAg2hBgFk8+9rYzra2tz1sagRiTTASwCi4Te5ym/va0ZgFAQ5NnGWd+93wjjcvCECs84DAGBHxNYNGIQBcQOPf0YBGwAcu8IIT/OAGTzjCF67whjP84Q6P+MPp8KXzUDsVAJe4xiHO8Y17vOMgb7ghBIBnSwvAEBn/D7nKP87ylbu84apY93usYQA6tPzmL885zj++CwEU6T0hwDdENt1p3Xw61KN+j6lRrerz/AEDbL4MC2J9HlRYoNasufV7cmEAWEXkCzUoeSkUsOffUMIEbFrFAgadHGBoYFXWwAUHgMFo9+hGFyighHTEoYCfY+PSmZZIPJ7QZDXca9HSqQcXMGAENWCZMVtWABHUQAQFiDldrvGBGoyAAS5EXTTBsIAO4KyBJ9B5IiueggM2weuAOcMLDKjxw8ChBwboAVcI83EDvICtgKljEw448pirZ97sulor6v0ve7niXoPotyvy7S99t2Lf9uLX+cXf7/Gzkvz6Atj6AiZj/2wLTN4MZh/6/E2vf72//K00vyDwRf/2sdJ96n+f+dcvyPO5En31T18r1Yd/4WdI40dFBmZ+EsZVFOZKFsZWSwVZTUV8CehXCwhNDRheDzheEXhgJjZhKMaAIHZhu5VhvbVhRdVhR/VhRBViRjViuFViJ3hiKZhiKyiCwEWCwmWCLIiCLqiCvmWDDoaDEKaDQChiQkhicDWBoFWBahVSRdiCR/iCSdiBCviBFphUDohhEKhhtEWFFGiFTYiFGKiFGsiF7XN+/Jd+W1F/AHh/7pd/BLF/W9F/a7h+9td+WvF+BBF/aTh/V8GGWRGAb/ha4kdgBlh+QISGc6iGyGeHbf+Ih1mhhwMhh1pBh434f4HohnkIhwPBh4voh1YBiFghiJtIiARoiHZ0gImohNHFhIzlhFk4gltYgl0Ygx44gyCYW0/Ig1Hog1Noi1WIi1eoi7F4g7OYg7W4gzLYgzQIg8p4i8yYiz9YjEF4jEMogV64hGD4iiFIjUZojUiIjcD4hcIYhjXojVAIjlIojs8YjNE4jNM4hrJYhrTIgeOojeXIjecoj8ZIj8hoj+1Iju9ojvE4YBlIfhuIgNnYitvoWhdokGSIkGaokPfIkPnokN3Ij9Xoj9cIkLu4jL3YjL8YkPg4kProjB8JjSEpjSOZku64kvBIhOjIi+roi8nokgL/CZMEKZMa+Y0cGY5nyIrz5YoYSYw9mY4/uY5BuZBD2ZDfBYtHSZNJaZNLWZFNeZFPKYYQOY8SWY8PpIiVyIjc54iZCIlYIYkCQYlZYYljiYmjqImRyIkC4YlhCYpVIYpXQYpxaYqoVICpiIhiBJZrKZb0R5ZvaZZXgZb4oJZYwZaF6ZZ5CZdnKZf4QJeDaZdUgZdWoZeTyZfK5JeYpIqBKZTSR5RZaZRb2Y9d+Y9fSZr+Z5oBBpWpuZGr2ZGtyZSl6ZSxqZWFeJCHmJCriJuvqZvgJ5u9GZG/OZHBaZW5iZW7iZrHyZXJ6ZXLSZIWaZJFiZIzCZI1KZI3uZ0q2Z0s/8mOOFmSOnmSLQmeLymeMUme6pmT7LmT3xmV3DmV3umR72me8Yme8zmbPlmbQEmR1nmV2HmaBRmdqjmdrGlDgtmYhPmHhhmZiGkVimmZDoqZU6GZVcGZiUmZjHkVjgmhkLmZktmhGCEOcDABxYB16UIOkAABBvMw6/AJEPAJMBYwEQMBkGBjAXMxE6AxFVEPcaAAOjAEIeABvfcb90AJCrACRYACGBAuyREK40IE5oIs6UIdKUAEN6AAkzB8ouEMHkACRHAvcfB5DfEIIdBpd6AArccardABd4INgWABPMYaumIKxGEKvyIdwiIo2DALHYClv5EOFnApxRECkSARh/8yC4rCKKzhKH7HKmogA5RiKe+RKWDKF53yHoGAAaHyG1GABKVyo26xJJ5qANjADazaqq76qrAaq7I6q7Raq7Z6q7X6bc0CaAbwC7j6q8AarMI6rK2qJr5QIAYAC8S6rMzarMD6C3YycwegCc5ardZ6rdmAAPVGHBwALA5BDCgAbAIQC0FSruaaIm2QALtaLCRyru76rhiCBwHwIucRDQEwI/Car/maI4mCJwrQBvoasO4aC0RiJFLaEORgAMd6HmugHr/BHuwGHyKQHPRQaedRp2hKFyKwB6UCMKwhBARyHrygADxqFlHgA7tKCwqQpKIRB2H3aMchHZ0QAguLDb7/EAKdQGgakAuWVgPakRzOoACHVg0+AAWbuhDwMAMhsAZ0gAQKkAnpIg9M0AFXcAdVsABxcLRelQUaYAV3YAUYkAUZSxf3MKRVcAdqwAFMcHp8ZgFGQAdrQAIywKIQUQ+iMAMHEAe4ly5n0QQDwAUsmxzGIAUDIAXeKi9cMABNoBcIEw5kcAA80Ar6op30GZ72OZ74WbnrebmaZA6eKVegqUuiSUgNCqIPGooRSqITWhWE4LnGeYq++ZfAOZrCWYcjuqElSqGuy5uwi5yyq5y0y5zD6ZzttbvQ2bvS+bvUGbwD2pwFulzGS7n+iZQAqpS3Kby2C5vF+7mUFbpUNbqm/1S6VhGiqHu7VMGhusu9xeW9dgW+yCS+VUG+d5m6uLu6VNG66nte7ItZ7itW8EsV8puZ9Hu+ucu60cuT0yuV1UuV19u8w/u82/u6fYmKoQmYpOua2UuczHfA7qm58Mm58lmVDpzBxLvB+Wt8+5tc/UtY/zsVAZyhAzwV6GvAJ6x9KbxeK2xaLSwVLywVGkrA9jsV+CvBn0nBomvB4YvBl6i9JkzEoGvE34vE76vEbcnE7sfBmZvA9bnA99nA5Xmd54lXWCygX0ygYWyg6enB+gnCVjXGDErFj2nFpfiQCEqbCjo9boxFOxwVPRwVPyzDBXy/lGmhpouhPhzDUjHD9/+bx3q0x1DRx1Dxx4kcyEI8yI78FJD8FJIcFYosxIzMSZfsFJnsFJsMFZ0sFRUayk0xyk1Ryk9xylExxLw7wbFbwbN7wbW7xBp8xTUsfzesfDncXKrMFKzMFK7sFLAMFbJ8vLTsu7YMvLiMvbpcwrzsxN0Lxe0rxf4LxyIqx5H4yb40zEtRzEtxzE2RzE+Rytxcvt58luCMVeKsFOSsFObMFOjsFOqcy1W8y3n4znoVz0kxz0lRz0txz02Rz9K8z9Tcz73ch7/MfsH8XgCNFAKNFAStFAbNFMssvXX8n3ccoNVZxs57xtDb0J/40HcY0QZByON7uvNrvoAcxKjsz5z/NdFHUdFHcdFJkdFLgdAjPM0Q3MSzXMS1fMS3nMT6HMf8/M0mXZco/YgqDX82bRQ4bRQ6jRQ8rRQbjcAdTb0fbb0hnZ9gvJ9i3NSX+dRlGdV7ONVFUdVFcdVHkdVJsdUdrMWWy8WY68VibcZkrVk0fV1sTRRuTRRwbRRyjRQ+LdIPTNIRPNRPXNRRfNRTnNTdvNTubNYXitaHqdadGNhDMdhDUdhFcdhHQddZ3NUK/NUMHNZqPNZsXNbWvL7YzL/azMLr/NLtnJh/nV+eLRSgLRSiTRSkbRSJvdcj3dclHdv6O9sqXNs6fNsCDNOTLNOxvNvYB90wLN2cTMmobMnY/33I2m3K3F3dmF3Imi2hnD2XvR0Uvx0UwT0Uw10Upk3Gxr3YyF2cGWnXm4vXnVveLW3IfozI203dyuzdlM3Olq3b/h2/Lh3duU2hBp7QSr3QTK3cKMzcOOzcwvzdAR7erzzeymzd+rfeQNHeQPHeQhHfRIGW61AJNPAMk5su7AAKFKAModqjw0ABw0C3yREPy0ABoHAwCEMPzkADlWCqEXEPrkECK7AALVB2bWcBIIADGiACQpYrG8ABOMABHSB02yECWs4BGAAMWksX48ACF3ADJLAYZZ4QngACjkapGSDkbaYBfjcHCuB1v/EMFvAHzfIHtyId5GABc0AcpaABXv/OGuyQAWrQLKnAAegSEexBarphDUTQBckhD6n2HlWwBJQiAlRX6W9wAm3OFUtQBe/RBxvAtqLBBUQgawASEcyAqhdrAd7wDbie67q+67ze677+68Ae7MI+7MHuCgdQDbJmANtA7Mze7M7+7NCe68lgAH92HrpgAMkQ7dq+7dze7NtgAJSuG9VwAK7Q7eZ+7ujuDfWxrtjAAWz3EOAKbABQCIhQ7/Z+7/ie7/q+7/ze7/7+7wDv72awAOxuCwJgBwGf8Aq/8Azf8PZ+BgGQG+dBDQFwBg5/8Rif8QpvBwBQdLqxAGag8SI/8iRfCAX7HkcSEZRWcrrxBjOQHOygAB7/3wcdUOpaUbF6eh6lYAGs3hiV0ge5ZgB0LhoyEOq6IQ1kFxH2oARGYO0YkOiikQU6gOy6EQ2QLh2pIvHYQA0qAC1TygElZw06kAXSYQwaUO26YQRKYPMFsQ4ncAN3EAhrgAFjkC7w8AIoMAeBwAYcEAVsf/NKAAJvEAhvEAJKEOOicQ9RoAGDPwco4AI87vOksQaBcAc4cAJI/hDx8AgiAABOcLi/QQ+ZwAIAIATB8PfUFwowAAAyEApjyxf3EAxCAAAssAmI/xvK4AQAIAKRcOOxMwhBkwcAHsl54OHInAcE/hSDIOJxSOI/YeI/geJBoeJDoZgf+t/nrbrpvZjO/+8T0O8T0g8U1C8U1t/9PfH9PRH+PzH+QVH+HB7JAi7eyY/PHmr+PIH+PKH+PsH+QOH+Bw4Q+AQOJFjQ4EGECRUuZHhwnqB5DSVOpFjRYkV7gtxd5NjR40eDhNCBxIeOEEmUKVUWdCfI3kqYMTk+jCjT5k2FGTfi5NlToEiSJn0OvdnyJVGkKmkmZUpSZ1OoHoGCFBrVakWjV7U2XLrVK8KnX8UWnPqx6li0WdGO7br2a1i3X8t6PBt3q1q7WtvmtQqXr9W5Hev+hYqXcNO9h5P6VZw0MMfBjYkaljw0ceWejDH3fHwx8maclEHfvDxapmbTMjtb/JwapmjXK0vHTv+JmnbK1RVb3yYJmzfI2b892hYudSTVk8VV+lZ+MXhzjBqho8xNcfd0isyxS3y+nSFx7w2rT7wefqF28wm7pz8Inj3C8RLLvzeInj7B9fcFutc/MH7D+frDx77+8tOPPwH/YyjA/gjUz8D7EOxPwYUY1M/B+yCkT0L9KFTIwvswpE/D9zi8z8OEQKRPxPdIZM9E+lBESMX3WGTPxfRgfE/Gg2hkz8b0cDRPR/Z4NMjH9IA0T8jwiEzPyIKQNE/J8Jj0zknzoCRIyvCo9M7K7bAMT8uBuPTOy+3AxE5M78gUyMzt0MROzenY3M7NkpITUCE5p6MTOjuxwxNO7PqE7s//5gKdblA990TI0OYQVU5R6Bh1lE+XLkVI0uIobc5STQ+CVDlOhfNUOVBDZSlTVfGDqFWCTi0uVVgHZLXWUn+TVThaYR21uFx52/W3Xlv9VbhgbxuWt2JVPfa3ZGlb9rZmQ32Wt2hjm5a2ajW99rZsXds2tm4v/Za2cFMb17VyHT03tnRNWze1dvd817V4R5vXtHoFvDe1fEHbd7R+G7wV1oA3Gxi0gi88uNWEMVt4s4ZDfFjViCubGLOKV7w41Iwl27iyjmv8WNOQGxtZspJ/PPnSlBVbubGWk3zZ0ZgPm1mxmqe8ec+cCdv5sJ67/FnAoP8amrCizzy6wFdrxWfp/7+ajvPpB6OulWq+rC4U6wy1hpXrvLye7l/TkuaLbLvMhg7t0dTOi+243G4ObtDktotut+xWDu/N9I6L77X8Lg5wzAR3i3C0DBcO8coUX4vxsRz/DXLJJEeLcrEs5w3zxjQfi3O5jjOrUV/BHlHsVkn3yvPbQFdMdLFc3wp22mQ/jPa3pJMaH9xj050w3r2yXavgXRv+r+K3Ov6q5FNbnq/mtXoeMNPpQt1Y1VtkXdXro4retOnzqv6q8KEaf7Ty7Tq/L9+lXh+09uN6P6r0m5p/s/rduh+q/DFlf5jp31r+15QAOiZ7gtmes7p3o++FKoFIGWBlCoiWAzJlgkSpoP9kLsiWCGpqg0PpYGM+KJYMLiZ+tSqhYk74lRQiZYQ+aeFhXuiVGBJlhpxZIGQaaK0HBimEl9ohT2pImBtuJYdDKSJOjviXJOpliI5q4k2eyJcoXmWJPqmiTa6YlyxaZYuZWSGsvmiXMEZljDzpomp66JkfeiuIS5rintoYkzPGJY1QWSNO7giTPLplj4ipo4D+uJJArmWQTOnjTQ6pkkSmZY5VKmR/HombN7Imjuaa5JcqeaAytiqSY1lkUhppk0tSJ5O62aS7OpmmT0YolKoapVhKiZRTnmaWoXJTPFjxA3Lco1byOIYNxFGPWtGjGTZoBj1qVQ9x2OAY8qjVPcj/8QNWxMMjxMDAAjhgACGso1XM8IACOKCAF5CjVeBgAQJCgAAWgKNV5IiBAc7pAWa0ah1LsOcCMEAMjnATENjARjSM4AFtasoZFriDNbBBjStkQJyaGocF3uDQarxBAerU1DoycAVqEPQOGHBGqODhASNEAxvWCMQ/LQIPCwSCoDPVQRw0RQ8P0GGmBDVCFELlgivsFBtXiEGoomAEoc7BA8i8VBx04NCZBsIC8KiIMzQA1Zn+AQPo4GpXvfpVsIZVrGMla1nNelazHsMA1RCqKRRQDrTGVa5zpWtdu9oNA+RCqLgwQDfs+lfABlau5TAAKoRKDQMgQ7CLZWxj0YGB/z8I1RoaKClFgJECoWLDFAGogyA8+1nQhla0oyVtaU17WtSm9rRAWEBmcREANKhWtrOlbW1t+9kyBCCkO6VGAMpwW+AGV7izRUMAcCHZBQRhuMtlLnMHUQcAmCKzKAhGRcShALbudA4v6KgCdCHUQGxAmI6ShwJUIdRUKICajrpHBga6U10oYKKOcsEchFoNBYijIvV4QVBnGg0OtEJT93BCEXZaDRJQIlRfwAFWrYGDMISKEiTILkGJ4ITxOqoVHFDpTInKVIqQIwNDGIUq7sCBKGTYUewQAQ4CsYo+kKAHIHZUPFqQAkCo4g81aEFCL0WPHoSgD6oIhA48wI5Q3YIjChzYgypGQYQMcNQi7OBCBizAglao+FLxiMMGLCCCTdD4x4vwgAU8wAhnqqoemziBATYQBx8PuBUsUEAGtPCOj9QjzrC6B1V/h494aLlVgf7dPeJxlD8nWtGLZnSjHf1oSEda0pOmdKUtfWlMZ1rTm+Z0pz39aVCHWtSjJnWpoRMQADs=" style="margin-top:1rem;" /></div></details></div></div>

::: {.sourceClojure}
```clojure
(view
 '(ChemicalData "Ethanol" "StructureDiagram"))
```
:::

<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">ChemicalData["Ethanol", "StructureDiagram"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhgwArAPdXABUVFTc3N4CAgAMDAxAQEFVVVZCQkK2trRwcHJeXl3p6ekZGRggICAcHB/X19URERC8vL4+Pj/39/ZKSkllZWcrKypycnP7+/vb29lhYWIyMjE5OTlJSUtvb246Ojri4uJSUlKenp5OTk29vb8XFxYiIiGtra8jIyKqqqtfX14qKiu7u7vT09LKysh0dHVZWVqOjoz4+PuDg4OHh4b6+vry8vGlpaezs7EVFRcTExL29vfLy8rq6uoSEhF1dXaioqJqamjU1NXh4eDQ0NJ+fn19fX5aWlqWlpfr6+tXV1W1tbd/f36urq5ubm7W1tYmJifj4+H9/f6GhoVRUVJ2dndnZ2R4eHv///8vLywAAAMfHx2RkZPv7+9DQ0JmZmbS0tNTU1OLi4kdHR+vr683NzXNzc6ysrElJSYKCgsPDw7GxsaamplBQUHx8fDExMXl5eUhISK6urujo6N3d3Q8PD3R0dOXl5dPT02FhYVxcXOPj49zc3H5+fjIyMufn58DAwGJiYvz8/DY2NsbGxpGRkXFxcZiYmLCwsHd3dwQEBEpKSrOzs9HR0cLCwp6eng4ODubm5s7OzlFRUfDw8IGBgfPz82VlZYeHh4aGhjg4OAEBAUxMTAYGBmdnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAgwArAAAI/wCvCBxIsKDBgwgTKlzI0CCShhAjSpxIsaLEFTFyWNzIsaPHiUReMCnUY9LHkyhTTqzB5sjAP1OkqJxJc2YVJSVYGITBgUbNiGCyHCrIZsjPkxhUmEiRcAemER2OLgw6lGBRqR1DbODRMIkNDVCwHqRK1KhYimkyUJn4YdOPswTJWjULt6GMOpRuWLRAgURduQOv1l0oYcKWLh3HREEU5mzQLJAjZ6E7+GAcMS1QkgEkQmzQMmZChw5CufJALEWM0FSDo+rPoGbKmiYop80bO0dB4CHzOkvsubMFeslzQqweRHz20IQt23QgQUwGD3LzZCZz4JXvWCI029CmDymvB/+mrGiR1Ek9Cs0JfgWKBhtJ6l4gZIlRTSlT/rAn2GEEph11LVEGGjOkRAMHMOx30IEJ1tWIFY581N9/CiaEn351wSCJDhu5B1+FC6GnXl2VXDJCJQRBkskjmnDiQgQHofAdiBDd0UkEXNSVRCQDrZGIJhAU8QAdWQhSUBRA0DiRE2f8NpgDDTCgxUASLJCFEAStoGRFhvhQXF0vZGGIQY8ksqVHfrShAG5nWcHAQZ1kUcGZHlVQRAJnMYDAQY5kgQmdHx0AxxdY6XnQEVmUAehHgRgA3lFuHmRDFg0u6pFJRxWQRRMGETCABJaGKhCUDMw5kCJZCCDqqj5q0scWihAmkEUAq9aqIouJAOBBrbz26uuvwAYr7LDEFmvsscgmq+yyzDYLYkAAOw==" style="margin-top:1rem;" /></div></details></div></div>

## More Working Examples

::: {.sourceClojure}
```clojure
(wl/eval '(GeoNearest (Entity "Ocean") Here))
```
:::

::: {.printedClojure}
```clojure
[:entity.ocean/mediterranean-sea-eastern-basin
 :entity.ocean/mediterranean-sea]

```
:::

 TODO: Make this work with `view` as well.

::: {.sourceClojure}
```clojure
(view '(TextStructure "The cat sat on the mat."))
```
:::

<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">TextStructure["The cat sat on the mat."]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhpAGaAPd8ANzc3Kenp8zMzNLS0peXl/Hx8fT09M/Pz9PT0xwcHC0tLePj44+PjxkZGZqamjU1NcHBwbq6upubm7W1tYmJidHR0ba2tpmZmampqTY2Nl5eXlhYWBISEqCgoBEREW1tbcPDw7GxseDg4GlpaaWlpdbW1v7+/urq6gwMDO7u7ltbW/X19fr6+pGRkSwsLD8/P52dnVRUVJiYmHFxcTw8PKqqqnl5eUNDQ0JCQkRERBAQEIqKivn5+djY2KKiokdHR42NjdDQ0GNjY+bm5s7OzikpKQ4ODgkJCeXl5XR0dA8PD/Dw8PPz8woKCoaGhjg4OKSkpB0dHbKysjk5OWZmZsrKypycnC4uLoeHh2VlZZKSkllZWYuLiw0NDf39/RsbGxoaGtvb27i4uI6OjpSUlC8vLwAAAIKCgklJSRMTE5OTk3t7e25uboODg0hISN3d3a6urujo6HV1dRYWFqampnBwcGtra/f398jIyMXFxaioqPb29v///8vLy9fX11NTU7u7u7e3twcHB9/f3wgICNXV1QYGBu/v76GhoX9/f/j4+BUVFSsrK7CwsHd3dwQEBEtLS8LCwoiIiAsLCwMDA0ZGRiAgIH19fR8fH2FhYbm5uXx8fFBQUEVFRSMjI+zs7N7e3oyMjD09PZWVlaysrJ+fnzQ0NHh4eIWFhQUFBYCAgGRkZPv7+8fHx8bGxlZWVqurqzExMcnJyenp6SQkJK2trbOzswEBAcTExCYmJjo6OqOjoyoqKrS0tNTU1OLi4hQUFDAwMJ6enuTk5DMzM2pqaq+vr+3t7RcXF9nZ2dra2pCQkOHh4b6+vr29vfLy8sDAwGJiYvz8/Ofn5yUlJWhoaM3Nzevr6wICAr+/v19fX5aWlry8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vCH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAApAGaAAAI/wD5CBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKhRomoEHV3KVGLSplAtBjJDtSrVNnyeBmWV6JhKrl6jjgwDxKBWoGDFZvwEqC0aT20BDcqqNGgcM2FU3s2rNqSeL2brAt3bd6OQMgXVEBJaCK/KxnwLexwFOPHioJAlZzycWIkiNmkWZdlDENEVQ1E2sfII5ckRI39+DQwSLUqTMnAG2rFatU9EWT8WETKlhcfs2rdzC9zN24zvksy26GiSQ9ZANVMOZdIhmrRMRs0nCf9U4xl099KnU6/eSAmKpTSa6kziJE0gbdu4dTd3rpkiZ4JqGCEKFaScgg0qA11iiCqu7AJGHR3JYYY2sEgBSSUCzULIFrXY8sotz8XhByJmaOLHiXdA9IkSr0TSChm5PKchhx6CKJCIJJqIYklxfMGLD6TkIAge4wETjDDDGHMEgjKB4ocdyJzoRzLjCUiggUzyoSCDDkLIXi5+aNPFMnncEggfM3b4YYgjlihliv1J9N91t+wyECS6CKQMJVoM1EwqcWzUhxlOEPTMQNMM5AU11RCUjWMT5WGGdQclKtCijQ70aGQmFaNEWNIEk2dW2BAp0BajzpRIZQDWeeeoe/b/KdCfgWpEyTZ80JGLQHPIaikfmDoKaZz+IQagYHycYolAOxDiHbCGcLORDYYYl5AyNUiSC4aaDhsRDzSAscMbCGGrLbcCbZoSJpkQNIoZn9BF0BrL0rRqYAQpy6yzikbLnp2wECPQF1wQZO62wnJKbERzjofsvXzMgI0SFFN8CxQbZUJNQoh4gkwMaxDzQsIVsWIFDo+40AILA3X8ccgjd6swSYQkQpAUZhQi70AQq8rqdQ9XJnHFFmNsK8AC80GwQC6DLDLJC0/U8M4CQYwFIW8MorXWK2zkyBH1GUQKNsJ4IZAKMQskqR8YpdACCkIINHbZZ6fNx9opRRH3QNuY/3EC1Xz0LBMqyODLc2VXZ731IF0fzUfAAxc8t9l8oE0Q3i6ZEPZNU58VeGUlpEJCSLiYMQZBlo4QC0Gc2C2CGSFQlMIhBCWBiUCqs+467Cl94EEKlxJDg8MECR5TB5QAf2zxoIseEiVIR85H7gO1TtDrsbf0TC4c+IJT50EPhIogcgCSzQ4bdCTELavA0Ys2yCjCBwyTRGJCGBpMYjcfGdCCQTYXqABEHAEMCriiAiRAxggEQj/74U9/Benf/wJYkkN8gRG7qEUnBCFAwBkPJp9oghssEAEskMZzPRtf+c6Xvn89LmlLa+D98rc/CQKwgyiBAFVOxzljAY15BLHFA/8I0YVKQKMjJthGMAThgRh4jw8m2EQDmvCEGjBgfwtwwxGUoAtnQEQaHcCBDo5QhDNYK4pTrOIVC5LFLXbRJCLYwHRuYCoP/kwmkVCAIZABiQXYMYhDLOIRXQg5pRUMjVS0Iha1yEUvpoQJsUhAD6JGyUpa8pKYzKQmN8nJTnryk6AMpShHScpSmvKUqEylKlfZnwm48pWwjKUsZ0nLWtoSln9LCBFuyUtZSqsh0uilMF9JpYaIYJjITOYtddaQBSjzmdCcwC8REsxo0rKYCBmENbeZTEAgBAHgDKc4x0nOcprznOgUJxMU8ot0upOcbGuIF95Jz3DWiiHHqKc+95n/zl8tJAX8DKhAETDJhMxzoOa850E+gdCG7jOerIyoRCdK0Ypa9KIYzahGN8rRjnr0oyANqUhHStKSmvSkKE2pSlfK0pKqAQhjWAYJZIOQSFzDIstgGUdWEIoDDCQMsDiJLGpBEDFkYyFWoJ1FRgHTMTgAhxwZgp38UAI+SNUjL43pTBNiU5zqdCM89alAgCoSpo7BqVCNSFcdQlQ+5PQiaogXC0qghlkgBBZ+rMjmwAoEMhhgrEE1SQEYACcTjAIJSFVqRUYRKGmUAAjx8kh98OAKgexVI3Hlw1zrete8UuSyGVlBX//KB7KGhLF8cCxkKYLXh/AQtE6JLB9AYAs+/7ACEATwgc5a0QIJDOO2uWWmHsJAgBVgYABWkAAoGkEAW5iADyvrgTV6cQFjHAq4uhXIcIu7kBW0IBu1LW1Q72CLUcAgnmN4rltNcAhN4EECW50IHQYgkAU4oL4+2IYtUpSNHpQiGVaoAgy2gQuKoFYgEvBDCjSBCzstIL/75YMxSiAMApjqGnRQAwnsaoIIjGIUBY7DLgaxjW0IQMR8IK9544mBN/jACmJ9SGYFQlvb4ja7vPUtdoVLXOMiV7nMdS50WSBd6lrXxsHVbo+7+93wklXF5xVIegWyDPa6F740ZciB+ZDgYQRAIEP4MjSSoQcZAOK5JyABGUjxjBwPA/8WzJBbnJmBiBZYIS/GCEUHpLEyPiQDBqMIAWnGXOYzK2TGfFgADGbbCFakgABDeJwfQdDoR0daDY2g3SiaYYJshGIaipCAbFZ2gBbEgRW1KDClHQ3prGSaId5lwQXmQtZABEIasxiFV6a83k8sQwB8aMWXJ3KAwDbjiHtQwzC8kA1j8KERMJiGNKwQAEUswQHYhAhqvZCMUMziBC2AxgqSvexm88EKerC2A97gBStUwASFcAC3fXCHAmghBSimLB9QbGtc65oPo5iAFxYwBtgmBNGKZjSrI93aVVva1ZrmtKdBLeohl/rUqVb4wzGt2ITEetbi5UO/c71r9VbZ18D/FrZDtt3tWXgZzF+WQgf2sIJtMMMLDlAGK7iRm9bCWc58cAACvFAIYUhZICs7BBmkHYEJ8EHmNLf5oWV7jBYEHbF8cMYRW+sArGs9K5EG+E0HgQiBWMB7pDbaAbzYdYF8XQ1hZzIflCEBVpBVC4fiAyCsw+uTj8E4n+gARVbAANI4IFEICOwK/t4ISlkBFAIRgNMlMgoGLGMM2yACH8D93MQLZPE8eHzkAxEHKwxEGEP4hQMWoN58VxbFeBfI3gEOeYA/qyGIrvrV3b51P7Y960eEu0BGMfay8+HsFlc7270e/LgrxLtzr/vd8z77vpvgE3/nQ+BXbnnMa/7lVo05/wQEIgVlLMBOKVaGpB8XZz6QIs7rZEUhCHD0IfdBE59fxtPH/3T1H1y2CQcEpdABBFhgrSWABNgBBaYGjTMKXcMMgRUIaMcCBxABAlEBXoSABZgVjSN3EgYCQMUCZSEQsuBFvMYA17dofHAMgkcRpFABcSABAuEKo5CAHWAAjVBQVhBZphURWyYQJ2B0fECDNmgAOwhYb4ABA0EK6vdeZOAM0uB6+7YLIjgQJQhwpEUAt8cQCLdoGqiA6/eFC9iADxiBE1iBF5iBA7iBDNgQ0PeBITiCfHCFJ5iCAsGCK6dQfAB+YfZ08dQLylAC2TMQPtd+78cHCAADpRAC9McHPP+0MtBQWVS2B1Lwh/6HEIiGC7W1DevEB0twKK3FiQLxiVnhHQ7IBxAoEBJocd7EBxjIB6LoiYeiBluIEG9YAGSAB0GlBZ3IDUQyBmZzDKFwfUKIhxThCzUAApFgHxYILIjVCP5nBXPBB9ZwJpSnhyfQgkHQjF6AWKJHjRNQegNRCkjwDH91DIiQDFIIe71IJKfIB1oIEZm4iZ1IiqFYj7NoimWoimfYiq8Yi6RIi25odXyAi7rIB7woEL7oiME4jJ9QjC2oZXo4DHRwgTFXUIAoAqPDB3vgGz4nAgJBAMxgAMsQLwXQiI/IAvcnEHuAglKAkZd4EJnFCj3AWdwQCKz/cAgE4EewMBc3mZM7WYrDt48i149pyAc/qZN+JJCwRpB80ActEFSBoAlecA2jEC9kQCXQAATEeIcRKRE80AIXYFd88AzbMATSgAtKCI0CgW48UAASMI0+iI0taJZoqZbnpgdvKQHK0G4IwAcl4ADS0AewwAR3AAW+kG/LyG9UaZXx8o7xKGPxQpM2iZNK+Tg+aZlByZSnmIpFyYpHmZSbWYsH8YZPGZUi15hXyQdZyQdb2ZUr+JUK8YN8cA3L8AysgAEXKRCAyAIEAArSYG49yQchwGlvAATMcA1qcAcm4AxkIGX1kXRkMAteAAi19ZK8GZNmYXktEF88YAHbIAPW/yAQVUAAw/Cd4TmeQglwRLmKpOaPXoSe4jkepGkQpukFPjBeUjAKVlBVfOALpSAMuwSbxkgRIWB6A/EGpaAGsFAAzxaNuOAAMlAFBkaXCbqgDXpuuGAFBJAHQEgHZLBhfMADxqAF2wAIXoBiv0AAfYBid7Cf/TmUIVmfmMid3gme88kH5XmeOKqenNmeRumK8dmj9DmQipKfKQaj/gmgAjoBBCqbCUGbrnkBu5AMR4WdfACIVrULaoABDrqj06AHDuBedtUMo4AICLALRxQCF8BnLNMDgCZoTweTLQUTSVWneFpSd5qnfApSb/BVfRqogjqohFqohsoRv5CoirqojP/aqI76qJAaqZI6qZRKqVgXUgZQqZq6qZzaqZ7KqEugFnQwqqRaqqZ6qqiaqqq6qqzaqq7qqs4mUm/wqrRaq7Z6q7hqqmnFFCbQq776q8AarMI6rMRarMZ6rMiarCSVrMzarM76rNAKrIc6rdRardZ6rdiardq6rdzard76reAaruI6ruRaruYaEmH1U4F1EWaFVtoHpef6EOkKWBnRrk/1ri0lWn5FrxiBWqr1CdsXrxOhr6TVg0vVWI8FsPBqUt4FXvQKZehlclb2XvE1EFuWYJ9QChAAX3HWX/9VAKRABqMgiUFwAZjGMs9ACqNQA/7UrQ3rZONVXlHmiBLbXhT/m2XDd08Yq7EcywcemwwgK7Ika7KNgLIqy7IS9XG0JpW3RnI0S2XX92vBNmwWGyjc5m2fEApBMIRfBm3SFggRwArHsAwG4F3HwAN0IEB0IAv3cwHy861KG3Ij92/Wh3JTWxAsh7Vay7XPFm3SALZiS7Zmi7Zqy7Zh4LYRBX10Z3e7SH18J7HYB3iyWXmXl3naxwAsk43PRil7wAomMAtacAwsoAYlsB5LoAXr0QHkArdWt7jTJ3uPC7WRi6/u0n2W+wmYu3mC13gs6bmgK7qka7qoKxCqm7gEaQwgCAtVSIImqF4o+AkqWKA5WxAZKxDbl4MCMQ1QIAHGQAZeoQxQ/7AMjfAMC7AMNggA4PqGyBuHVti8AvG80Tu5eli9+Iq9fKC93Ou9cxe+41u+52u8AmGQu9iODLmCDgmReDu/LXi9/gcDf8llx6AIwLMH0nQMKogm1uKtt5iLA6yQv9iQT5rA1LvAu9vADywBETzBFXzBs5DBqmSaUCmVqomVWsmVD+mVIkwQAcvAwxdnPRAK1xAHBHAC0nCTJtAB7/YGagCo3ArDqDmVVbmarfmaNxybOTwQO1zCPcwHPxzEQ1zEgXDESbzEAHwpSPqi/LmkATqgVSy9AKfA1qvFfDB/wgABEYAxIDAKakAK65QCekAGHdB+rHuk+pnGAsGkbIzA7v8Cx/Xrf3Rsx3isx3zMB34MyIIssJicyZq8yZzcyZ78yaAcyqI8yqRcyh4hAraWyqq8yqzcyq78yrAcy7I8y7Rcy7Z8y7j8ytppyitxDRXwy8AczMI8zMRczMZ8zMiczMq8zMzczM78zMXcsrw8zdRczdZ8zdiczdq8zdzczd78zeAczuI8zuRczgbWVPfqEVdFVVtaEY3AKfYqQAFrzh3lrwn7EZMliQbXEO+8yKmVsPNMzxt1sQrGYA4GYSkyYRV2YRkmoh32YSE2YiV2YnYCsQLRYi8mVtbgAFpAAl7Rz1U7EDu7sSTQsf4FtCE7svZBtEa7stIs0JiUt98WbuP/pmzM5mzopm7s5m7wJm/JQG/2hm92om/81rT/FnADV3AFsAzXIA2AYIEgPb1XOwtZu7Wu0LV+C7hjW7YtcLZpmyuGi7gwvUmU632b1wKdp3h/940CQHoIygeop3qsdyND/Xp2Ent6Zx2jUHujsAfS0DV34Ay98GzwbLuah7uZu7uc67uhO7qlO4rDywfFO9aaRJtBOIM1mIBGyIOwkIRL2IQS8IRRWNdTuLxz6EWjkIV74AXQcAFQgAGDHdVvTL2lEMfPVlD4273fy7/ka74JiL6UnUmWrY3c6I21Zw3h+NbkaI4rmI7reNcEDJl74Ac+QBqFENvwzMg8PD8nnMIc/7nCA9HCwS3cFlqWZ5mWSuiWcNmXVvCXgTmYhXmYiTnUi2knUOyY7DmjRFADXqAIdBA7sk2bWfygW9zFQkzERozEJqDETDzeUTPcF8qgDmoFG9qhHxqidkWiJoqiKsqiLqqkMgqPe6AIsLANAVACBKAMAa7dcvzIdzxbktzHfxzIDq5Ke1rj1XzjOD7Nf7rjPv7jQB7kIWECw1DkRn7kSJ7kSr7kTN7kTv7kUB7lUj7lVF7lVn7lUu6gvMwKudrlXv7lYB7mYj7mZK6quzrKXpDmar7mbN7mbv7mcB7ncj7ndF7ndn7neJ7ner7ndq5eQv7ngB7ogj7ohF7ohn7oiP+e6Iq+6IxuSkNVVEelEDqOt+gszwvb6CI1WIV1WIkVpQgLWQGN6SY1X/V1X4mG0D570gE2YAV2xSPdsz8btCrNByV7smV5tC8t6qNUbLOCbDZtbl47bdV2bdk221Nd1Xwb7FotuF1NuGDdtm+r66ZEeIaHeGrNA7x7brUneXhr2Jeb2Jvbu5/b2MEL2am7utJuSi8Yg5hdhPZ7hCHnzzpc2/WL29ur2/srvr39v+luSsiojMx4Kc8YjdNYjVds243MQN0twd/NDRYc3i7c76IUlmMpEHaJ3gSel3spl9OrwySc8aPgw0B84GAsxgtOxhJfSgdKEAoq4RlP4RJKoQf/T7vb7eKRvMcybskpv/M83/M+//NAH/RCP/QYpQlGf/RIn/RKv/RM3/RO//RQH/VSP/VUX/VWf/VYn/Vav/Vc3/Ve//VgH/XZcABkX/Zmf/Zon/Zqv/Zs3/Zu//ZwH/dyP/d0X/d2f/d4n/d6v/d83/d+//YPTPSCP/iEX/iGf/iIn/iKv/iM3/iOH9yfoLLb0Aih6hBr9fgXZQIOIAB3IA14YHwN0VqYf1FMEApnJAUs82D6lSKEZmYm4GY7dtEuBmMC4QcDFranvvqjr0kdoAfKEO3kdtNPN3M1F2cNV2mthtQEJw3HQADHsAIk0AfBb267j0ksgAckwAB6MAyI/3jtUsB/5bd+v/d1ez18e+AKkf4JSOB5fAB61a9JitAHY1AARKjZlZidYbiGYJjaM6oJ6gkQfPi4GtXBYAcDAhUuZNjQ4UOIESVOpFjR4kWMGTVu5NjR40eQITX6qrUwQKEgEQR6QcJHSg+BvZTxgbWAzzYmApc84zNqhUACe0BEEhgnWcqVLUUuZdrU6VOoUaVOpYrRAJkgPLyAGlXg2bYh0nBhcAmTj0yag/hwC8TqEAGbPoHuiSPj0J4AAr6GHVvV71/AgQUPJuw3BZxtagKIEPimlBpYBcrGnFmFwDAeFrbJsCZQLp+gfBBIGCVGGh/HkCUXZt3a9WvYsWXPpitd2/Zt3Ll17+bd2/dv4MGFDyde3Phx5MmVL2fe3Plz6NGlT6de3fp13wEBADs=" style="margin-top:1rem;" /></div></details></div></div>

## Wolfram Alpha

::: {.sourceClojure}
```clojure
(wl/eval '(WolframAlpha "number of moons of Saturn" "Result"))
```
:::

::: {.printedClojure}
```clojure
(Quantity 145 (IndependentUnit "moons"))

```
:::

::: {.sourceClojure}
```clojure
(view '(WolframAlpha "number of moons of Saturn" "Result"))
```
:::

<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">WolframAlpha["number of moons of Saturn", "Result"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhYwAqAPdeAPHx8dvb29/f3+7u7tra2rqvoquej+bi3ZuLebuwpOjk4JWEcfDu7N/a1ZiHdZ2OfKudjrGklo58Z8zEu+np6d3Y0dnTzM3FvINwWdPMxNDIwPf29O7r6M/Iv8O5r+rn4/X08srBuLCjlY99adXOx66hkqCRgIJuV9bPyIVxW8/Hv/7+/oFtVuTg29zW0LWqnKyfkJqKeN/a1OTk5NvVz5uMeoVyXPr5+MG4rZF/a417Ztzc3L+1qZB+aq+ilNPNxY9+afX19Yt5ZIZzXePe2fn5+fr6+tnZ2eXl5YRxW6eZiresn/Lw7pmJdrarnvLy8ol3YYh1X8K4rdHKwtDJwce+tLyypvT09O3t7dTNxbKmmOPf2ritoIl2Yf////b29vv7+6WXhuDb1YFtV+fn59bQyfz8/O3q55+QfuHc1+Le2aqdjt3d3ejo6PDw8PPz8760qPTz8fDu68jAturn5O3r6Obm5vr6+aGSgbSpm/j4+H9rVJmJd4d0X4JuWIp4Y6GSgrWpnP39/fv6+svDuo17Z5aGc6KUg6OVhPb19JaFcoRwWunl4d7Z0/f399jSy9XPx4d0XpKAbevo5Ovr69zX0eLd2LmuofPy8Me/tefk38W8sYNvWaKTgufj3/39/NnTzbqvo+Dg4LSomqaYiJKBbaeZifn496+jlMC2q97e3uXh3IBsVZWFcpyNe9LLw5SDcPj39tHKwZOCbrernuPj48rCueHd1+/t6u7s6baqnfb185eHdJyMetTOxuzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5iH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAYwAqAAAI/wC9CBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxZsMibJyhTqlzJsqXLlyivgCGpMIiqIzhz6tzJs6fPnzxrGaFpMMgRMkVWEE244ouoHWaWDlRlRypDQaraWDVyRI9VhlhUWb1yRNDXhW+OKF1Kdu1ZhG2lxn0LV+1BJlQO7TmDUAyrQAS17Bk8GHDBuXQNIibIQweUvQdv5LBhWOAaNDQy06Cj2G7izm4NyoBs0EmMMJW9HHqxcPFnga4JjuZbMM2YFnhSx8DR2i6LKUC6uFiSQolZL3Jg9EkCqAXBQaEK+TE0haDwMooWGWpE8BWfIUMQPf8iGHvg7IJ3JF3ygia1pF6SosR4dTAui1KTfAzJZIkVDS+Y6AALFZAAwskWAq3QSSRVgDLKHpkM1EUMpGhShylRnCJQJaykskojcLQSy0DlCXQeQVzMMgh7qaFCSyO36LLHJqB5wYItXrxSikB/zOFFHpHsIpAgvLgikC97cCeQLikkIlAXpKz1yx6VCCTFEJ/UFVpBJwqkxglECNReQiVAsaV9snhBQhMC6UDjCCIQFMIeIHjhQw8EfbAHCk96MNAne3QgEAdCNKGBkId5dlCXg8wSykBjIpTBHpgkqhQLaa7ZJo0Y8EDQI3t84AUiaBAUyx4h9EnQHhcMlEgqhoz/YYIF5CkqGmlqEqbrHhUcNMEeG1hqY6ZseuGmFxJEQJAte8ThRQk5EETHHiSoOhCrBuUiY5qw2colrht4Iq64TUDgiYaM1DHQCg84UCOmahZ7rC5ROOnFCk08IBAKezQwEBdBWisQtl4wcJxAfPhAordegJBGGnPs8UMalhwUqRcJDGEFDVmYcNu7xG7qxQY6LCALCp1wosBAYfSRCSiB7EGIhH5e26oXCCiiwgEHeMDCDwtvmeuunFhc2QpU9DLEIodoUp9vIRtLoxe4GLAcHggOdEcBOkxHhXU1D3zzBjg4kEQkNdAXtFwMf1YiSG+/FbdHc39VN0d3sy20SI4cVTHUawS5sYNVKxAwAOAEzTDDV1gQ8AbiK1ByhCNfrUDBEQIgofnmnHfu+eegh775DGwEAABdjmBhh+ist+46EmQMMBPitNdu++2456777rz37jtIAQEAOw==" style="margin-top:1rem;" /></div></details></div></div>

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/math/wolframite/notebooks/index.clj">projects/math/wolframite/notebooks/index.clj</a></small></small></pre></div>

### 2024-01-25 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

@@
 
-This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/),
+This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
 
-It is mostly copied and adpated from [the official demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).
+It is mostly copied and adpated from [the official Wolframite demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).
 

### 2024-01-25 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

@@
 <div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
+
+# Wolframite
+This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
+It is mostly copied and adpated from [the official Wolframite demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).
 
@@
 :::
-
-::: {.sourceClojure}
-```clojure
-(def md
-  (comp kindly/hide-code kind/md))
-```
-:::
-
-# Wolframite
-
-This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
-
-It is mostly copied and adpated from [the official Wolframite demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).
 

### 2024-01-25 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

--- 2024-01-25 docs/projects/math/wolframite/index.qmd
@@
 include-in-header: {text: '<link rel = "icon" href = "data:," />'}
+title: Wolfram Lanauge interop with Wolframite - DRAFT
+author: Daniel Slutsky
 
@@
 <div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
+
+This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
+It is mostly copied and adpated from [the official Wolframite demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).
 

### 2024-01-28 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

@@
 This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
-It is mostly copied and adpated from [the official Wolframite demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).
+It is also appears at the Wolrfamite repo as [dev/kindly-demo.clj](https://github.com/scicloj/wolframite/blob/main/dev/kindly_demo.clj).
+Note that to use Wolframite, you need Wolfamite in the dependencies,
+as well as the `WOLFRAM_INSTALL_PATH`
+set up in your system, as explained in
+[Wolframite's README](https://github.com/scicloj/wolframite/).
 
@@
   (:require
-   [wolframite.core :as wl :refer [wl]]
-   [wolframite.tools.hiccup]
+   [wolframite.core :as wl]
+   [wolframite.tools.hiccup :refer [view]]
    [wolframite.base.parse :as parse]
@@
 
+## Make sure Wo
+
 ## Init (base example)
@@
 ```clojure
+^:note-to-test/skip
+
 (wl/eval '(Dot [1 2 3] [4 5 6]))
@@
 ... and call it
-
-::: {.sourceClojure}
-```clojure
-(wl/clj-intern 'Plus {})
-```
-:::
-
-::: {.printedClojure}
-```clojure
-#'index/Plus
-
-```
-:::
-
-a simpler way to do the same -> fn Plus in this ns
-
-::: {.sourceClojure}
-```clojure
-(map wl/clj-intern ['Dot 'Plus])
-```
-:::
-
-::: {.printedClojure}
-```clojure
-(#'index/Dot #'index/Plus)
-
-```
-:::
-
- Call interned Wl functions:
-
-::: {.sourceClojure}
-```clojure
-(Dot [1 2 3] [4 5 6])
-```
-:::
-
-::: {.printedClojure}
-```clojure
-32
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(Plus 1 2 3)
-```
-:::
-
-::: {.printedClojure}
-```clojure
-6
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(Plus [1 2] [3 4])
-```
-:::
-
-::: {.printedClojure}
-```clojure
-[4 6]
-
-```
-:::
 
@@
 
-### A helper function to view things in tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly)
-
-::: {.sourceClojure}
-```clojure
-(defn view
-  ([form]
-   (view form nil))
-  ([form {:keys [folded?]}]
-   (-> form
-       (wolframite.tools.hiccup/view* folded?)
-       kind/hiccup)))
-```
-:::
-
- ### Draw Something!
-
 ::: {.sourceClojure}
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlh4AHgAff4ADI2PjU5Pzc7QDY8Rjg7QTo9Qjw/Qzo+RTw/RDtART5BRT5DSDpDUDpEUj1GUj1GVDpHWj1HWj1IWT9LXD1MY0BDRkJER0BDSUFESkVHSUJGTUZIS0NIT0ZJTUlLTUpMT0VKUUdNVUtNUU5PUkhOVkBLW0lPWE5QUktRWkxSW0xTXE5VX1FSVVJVV1VXWVZYWldaXVhZW1pbXVtcXkJQZk9WYEVWb1BXYVBYYlJaZFRbZlRcZ1peY11fYFVdaUtbc0pcd0pceF5gY1dgbFliblpjcVtkcl1mc15ndV9odmFiY2FjZGNkZmJlaWZnaWlqa2tsbWxtbm1ucWtvdmBqeGJtemNtfGRvfmZwf3Bxc3NzdXN0dnV2d3Z3eHN3fHd4eXV4fXl5enp7fHt8fX1+f1Flg1dngF9wi1lvkGZxgGhygml0g2x3h2RziWZ0im56ind9hH9/gHl+hnJ+jm5+lmF4nGh7mXN/kXB/l2V9on6BhHSAknWClHiFlnmGmHuImn2KnX+Mn2eApmuDpm6GqnGGpn2LoHqLpXeNr4CAgYCChYOEhIaHh4eHiIOHjYeIiISIjomJioqLjIuMjo2NjoaMlo+PkIONnoSPno+QkIWQn5KSk5CTlpOUlJWWlpGUmJKXnpqamp2enoGOoYKQo4ORpIWTpoaUp4eVqYmXq4qZro2brpWdp56foJOcqZSdqpGdroKVsoSWso2bsY6dsomdupCftJGhtpOiuJSjuZWkupOjvJenvpqnu5movp+rvqGhoaOjpKampqOlqqenqKmpqa2traOosaKqtKGrurGxsbKytLa2trS3vLq6ur29vZipw5uswpysw5urxJ6uxp+wx6GyyqWzyKO0zKi2yam3za+6yqy6zrG5xLnE1bzH2MLCwsXFxcXGyMnJyc7OzsDI1cXP3cbQ3sjR3tLS0tXV1dnZ2d7e3srT4NTb5eHh4ebm5urq6u3t7eXp8PHx8fX19fb3+vr6+v///////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAA4AHgAQAI/wDxCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtWa9VlFexBHX1eE9YllciHFW1qGyLi66KGvb0JkYF1mI3aO7UFycF1GA1aMIT0YINXOMKNjEFyE9JxyuzEmyIFHjg/W0YKgypwoGLYMvF4yzIMmcKxyc0BNdcJMCI3PUhJgBb2KUHdSw6Va14BnrgYlURNONDZcGYr8FegrBizivEJ6S4yOGARdxaSriSH+mQBVxajuiSP8kh6A5cWxqlCR/p2DVeWx3TiSvZyHQ+1EWQrM+cef9KgXvJLfEGu/xYgA5ERFDwnvYlBKALLVEKOGEFFZo4YUYZqjhhhxq6IYC1rxHiwCHdGjiiSimqKKEeAggzXvRCIDHijTWaOOJhwhAC4MKuHHjj0AGKUsApTBIAnIQKcMBg4EgcI02UEYp5ZRUVmnllVhmqeWWWQYCon8G9MLlmGSWaeaZUa5igHnOGbAKmnDGKSeZvRjg3XnWHHDJnHz26ec1Btj3HghzQbSOAra8l4R4v8VjwSjvrRFDcvd40N95d3hgT3IyqHGfBfEkF0USIiqwjkSLoGAdNtbcYUE60oX/wsGOuo2iADjSKYMBKsShgkGhv4GjAKS60cJBK9KlowAfIRZnwiIT0UOaDkaQ0AFb0t0jiQU4GKGCBUjGqkANRtSgQCjSCUSdCkbcYEEke0nHTAcmGKGDAnGsRhE4cJRATIDpCjQOJBK0wk7AAqnDSQScqIMwPuy0EoEj4zwMDzESwEHWRegQ8vBA7giy6cfzCDLPx/jYI4g7KONDCDoZmeMxyiGP/HDJJ3+sMssov5xRxy3XjDLOKO/css8YyRy0yEObXPTKR8OMEdA0M02y0zpD3bPUFyldtc0IE501zx8jzfHMHwt9dc4PG711zGg/rPbNWLetddlcW0R12lbT/802wm7jDffSYAcstt1kP2y23nEjPHfYdQN+t+J5V+Q134Wne7jkiSO8eEV7y9035H8HHDjlg3/ddOnpnu555RSF7vjohkdu+uSvp4756k93HvDnsTce8OO1sy6d67/DPtHlomcu3ea3+54u8BPJPjztmtveOu7J694872NH/bPw6RKfvfHJIT+98hIxP7vzyUG/vfTSUS+R9eVj/7z2x3O/vvfvAx/ixDc18knHfPtD32/UVz/2RcR914Pfb+TXP/olx34Rwd8B9Rc//qXPfw0EYAQFyDkCno1wJIyeCS0CwfxJkDUU/KAFf4NBiGgwOQjsoAJZw8ALOhAiLdzgC/9FE8MFgtCH40Ph2nq3QssZEIccnKAHjThD1tTwITf8TQ6luEPR9JCGP3xIEKE4xMsUkYdHBGMSVbfE8L0taU/UYhRhOEU0VlE0V3RIFlmzRTp28TJftGIYHTJGOZaxMWf0YhoFucbdtXGAb+xaHPk4RyLWUZF3vEweG7JH0fTRkn9sTCDxOMiGFJKSh+RLIgG5SFI28nuPLGEkWThJT1bSjJdkZSYbs0mGdPIyn8RlKPkySk2WkiGntGUq6bJKUbbSmK8MYCxVOEsnKtFvTKxm8K5JumwKDo7cLJ43UVfAcJ5vnLkDJxux6cZvnnCd3WwnOSVpzgSis3vlhKc45Zn/Tnrq85z8xOc7HclOSLqTlvXU4T3/l0+CxtOg80ToP+0ZUIYOFJYFleVBrTlRhVY0hA3F6EM1GlGOOnSfEO0n4xLKxYWC1J8nBWhKBbrSjrb0o0hUZ0wpOlOL1nSnHu3pSyUK1JsKNacXlWZGqblRiiQTmLdEZC6duUu+9HIhv2xMMKU6TLoUk5fHXMhTtRpVVU6VmM8EazRHOM35NdGptYTqMtvSTLRWlS5XVUhW+bJVs3a1LV+1algVMla+lpWZZ/VqWgW7Vhem0K3aXF5cyTrXstRVsXdtS14Tsle69BWxfy1LYPE62IQU1rOHpWtiAbtY0jZWiI+t4Fsly1I//7oUqT8VKUpJqlKT6lamvKUp6CZr2Mp25bKszWxZNouQ07bls6oNbVdGq9nSIqSzz02tZVcr2tZWV4SObatsI3s/4qLWuFxBbneV2xXmHsS5ZYHudqXLFeou17oHwW58tXtc7k7Xu/cFL2zFK8PZlre2oLytGnX6W54G16fDRbAwFcxIBit1pEwt6TZtalucLhimDQ7qg4caYQ4n2MMVrsg9lDGFB3jiVAh7BhgaIAkEIUwciWiAIjYWMHJIogFg8A3C1uGJBkxBGfGSiDygoAEjXAEH4EpXPb6AASJcwQcKiE62FqGAIahhCBZYRJJ/4wkF+OAKRFhAGPTzG2Jw6/8KRtBAFOQxkTCsYDi68VLFkmOJEOiCOKq4ADOkQwwN0AobtOhAMOSFgVQQRxchsIR0xjEs4kSjBmGQSDoMsCriWMEJyYGHAnh1nje0YD4Z+MN7/pAB9FKlBW94DyoUUJvfOMEK78GFARwGEWOEgEGlWNM0hk3sYhv72MhOtrKXzexmO5vZfFAAg2hBgFk8+9rYzra2tz1sagRiTTASwCi4Te5ym/va0ZgFAQ5NnGWd+93wjjcvCECs84DAGBHxNYNGIQBcQOPf0YBGwAcu8IIT/OAGTzjCF67whjP84Q6P+MPp8KXzUDsVAJe4xiHO8Y17vOMgb7ghBIBnSwvAEBn/D7nKP87ylbu84apY93usYQA6tPzmL885zj++CwEU6T0hwDdENt1p3Xw61KN+j6lRrerz/AEDbL4MC2J9HlRYoNasufV7cmEAWEXkCzUoeSkUsOffUMIEbFrFAgadHGBoYFXWwAUHgMFo9+hGFyighHTEoYCfY+PSmZZIPJ7QZDXca9HSqQcXMGAENWCZMVtWABHUQAQFiDldrvGBGoyAAS5EXTTBsIAO4KyBJ9B5IiueggM2weuAOcMLDKjxw8ChBwboAVcI83EDvICtgKljEw448pirZ97sulor6v0ve7niXoPotyvy7S99t2Lf9uLX+cXf7/Gzkvz6Atj6AiZj/2wLTN4MZh/6/E2vf72//K00vyDwRf/2sdJ96n+f+dcvyPO5En31T18r1Yd/4WdI40dFBmZ+EsZVFOZKFsZWSwVZTUV8CehXCwhNDRheDzheEXhgJjZhKMaAIHZhu5VhvbVhRdVhR/VhRBViRjViuFViJ3hiKZhiKyiCwEWCwmWCLIiCLqiCvmWDDoaDEKaDQChiQkhicDWBoFWBahVSRdiCR/iCSdiBCviBFphUDohhEKhhtEWFFGiFTYiFGKiFGsiF7XN+/Jd+W1F/AHh/7pd/BLF/W9F/a7h+9td+WvF+BBF/aTh/V8GGWRGAb/ha4kdgBlh+QISGc6iGyGeHbf+Ih1mhhwMhh1pBh434f4HohnkIhwPBh4voh1YBiFghiJtIiARoiHZ0gImohNHFhIzlhFk4gltYgl0Ygx44gyCYW0/Ig1Hog1Noi1WIi1eoi7F4g7OYg7W4gzLYgzQIg8p4i8yYiz9YjEF4jEMogV64hGD4iiFIjUZojUiIjcD4hcIYhjXojVAIjlIojs8YjNE4jNM4hrJYhrTIgeOojeXIjecoj8ZIj8hoj+1Iju9ojvE4YBlIfhuIgNnYitvoWhdokGSIkGaokPfIkPnokN3Ij9Xoj9cIkLu4jL3YjL8YkPg4kProjB8JjSEpjSOZku64kvBIhOjIi+roi8nokgL/CZMEKZMa+Y0cGY5nyIrz5YoYSYw9mY4/uY5BuZBD2ZDfBYtHSZNJaZNLWZFNeZFPKYYQOY8SWY8PpIiVyIjc54iZCIlYIYkCQYlZYYljiYmjqImRyIkC4YlhCYpVIYpXQYpxaYqoVICpiIhiBJZrKZb0R5ZvaZZXgZb4oJZYwZaF6ZZ5CZdnKZf4QJeDaZdUgZdWoZeTyZfK5JeYpIqBKZTSR5RZaZRb2Y9d+Y9fSZr+Z5oBBpWpuZGr2ZGtyZSl6ZSxqZWFeJCHmJCriJuvqZvgJ5u9GZG/OZHBaZW5iZW7iZrHyZXJ6ZXLSZIWaZJFiZIzCZI1KZI3uZ0q2Z0s/8mOOFmSOnmSLQmeLymeMUme6pmT7LmT3xmV3DmV3umR72me8Yme8zmbPlmbQEmR1nmV2HmaBRmdqjmdrGlDgtmYhPmHhhmZiGkVimmZDoqZU6GZVcGZiUmZjHkVjgmhkLmZktmhGCEOcDABxYB16UIOkAABBvMw6/AJEPAJMBYwEQMBkGBjAXMxE6AxFVEPcaAAOjAEIeABvfcb90AJCrACRYACGBAuyREK40IE5oIs6UIdKUAEN6AAkzB8ouEMHkACRHAvcfB5DfEIIdBpd6AArccardABd4INgWABPMYaumIKxGEKvyIdwiIo2DALHYClv5EOFnApxRECkSARh/8yC4rCKKzhKH7HKmogA5RiKe+RKWDKF53yHoGAAaHyG1GABKVyo26xJJ5qANjADazaqq76qrAaq7I6q7Raq7Z6q7X6bc0CaAbwC7j6q8AarMI6rK2qJr5QIAYAC8S6rMzarMD6C3YycwegCc5ardZ6rdmAAPVGHBwALA5BDCgAbAIQC0FSruaaIm2QALtaLCRyru76rhiCBwHwIucRDQEwI/Car/maI4mCJwrQBvoasO4aC0RiJFLaEORgAMd6HmugHr/BHuwGHyKQHPRQaedRp2hKFyKwB6UCMKwhBARyHrygADxqFlHgA7tKCwqQpKIRB2H3aMchHZ0QAguLDb7/EAKdQGgakAuWVgPakRzOoACHVg0+AAWbuhDwMAMhsAZ0gAQKkAnpIg9M0AFXcAdVsABxcLRelQUaYAV3YAUYkAUZSxf3MKRVcAdqwAFMcHp8ZgFGQAdrQAIywKIQUQ+iMAMHEAe4ly5n0QQDwAUsmxzGIAUDIAXeKi9cMABNoBcIEw5kcAA80Ar6op30GZ72OZ74WbnrebmaZA6eKVegqUuiSUgNCqIPGooRSqITWhWE4LnGeYq++ZfAOZrCWYcjuqElSqGuy5uwi5yyq5y0y5zD6ZzttbvQ2bvS+bvUGbwD2pwFulzGS7n+iZQAqpS3Kby2C5vF+7mUFbpUNbqm/1S6VhGiqHu7VMGhusu9xeW9dgW+yCS+VUG+d5m6uLu6VNG66nte7ItZ7itW8EsV8puZ9Hu+ucu60cuT0yuV1UuV19u8w/u82/u6fYmKoQmYpOua2UuczHfA7qm58Mm58lmVDpzBxLvB+Wt8+5tc/UtY/zsVAZyhAzwV6GvAJ6x9KbxeK2xaLSwVLywVGkrA9jsV+CvBn0nBomvB4YvBl6i9JkzEoGvE34vE76vEbcnE7sfBmZvA9bnA99nA5Xmd54lXWCygX0ygYWyg6enB+gnCVjXGDErFj2nFpfiQCEqbCjo9boxFOxwVPRwVPyzDBXy/lGmhpouhPhzDUjHD9/+bx3q0x1DRx1Dxx4kcyEI8yI78FJD8FJIcFYosxIzMSZfsFJnsFJsMFZ0sFRUayk0xyk1Ryk9xylExxLw7wbFbwbN7wbW7xBp8xTUsfzesfDncXKrMFKzMFK7sFLAMFbJ8vLTsu7YMvLiMvbpcwrzsxN0Lxe0rxf4LxyIqx5H4yb40zEtRzEtxzE2RzE+Rytxcvt58luCMVeKsFOSsFObMFOjsFOqcy1W8y3n4znoVz0kxz0lRz0txz02Rz9K8z9Tcz73ch7/MfsH8XgCNFAKNFAStFAbNFMssvXX8n3ccoNVZxs57xtDb0J/40HcY0QZByON7uvNrvoAcxKjsz5z/NdFHUdFHcdFJkdFLgdAjPM0Q3MSzXMS1fMS3nMT6HMf8/M0mXZco/YgqDX82bRQ4bRQ6jRQ8rRQbjcAdTb0fbb0hnZ9gvJ9i3NSX+dRlGdV7ONVFUdVFcdVHkdVJsdUdrMWWy8WY68VibcZkrVk0fV1sTRRuTRRwbRRyjRQ+LdIPTNIRPNRPXNRRfNRTnNTdvNTubNYXitaHqdadGNhDMdhDUdhFcdhHQddZ3NUK/NUMHNZqPNZsXNbWvL7YzL/azMLr/NLtnJh/nV+eLRSgLRSiTRSkbRSJvdcj3dclHdv6O9sqXNs6fNsCDNOTLNOxvNvYB90wLN2cTMmobMnY/33I2m3K3F3dmF3Imi2hnD2XvR0Uvx0UwT0Uw10Upk3Gxr3YyF2cGWnXm4vXnVveLW3IfozI203dyuzdlM3Olq3b/h2/Lh3duU2hBp7QSr3QTK3cKMzcOOzcwvzdAR7erzzeymzd+rfeQNHeQPHeQhHfRIGW61AJNPAMk5su7AAKFKAModqjw0ABw0C3yREPy0ABoHAwCEMPzkADlWCqEXEPrkECK7AALVB2bWcBIIADGiACQpYrG8ABOMABHSB02yECWs4BGAAMWksX48ACF3ADJLAYZZ4QngACjkapGSDkbaYBfjcHCuB1v/EMFvAHzfIHtyId5GABc0AcpaABXv/OGuyQAWrQLKnAAegSEexBarphDUTQBckhD6n2HlWwBJQiAlRX6W9wAm3OFUtQBe/RBxvAtqLBBUQgawASEcyAqhdrAd7wDbie67q+67ze677+68Ae7MI+7MHuCgdQDbJmANtA7Mze7M7+7NCe68lgAH92HrpgAMkQ7dq+7dze7NtgAJSuG9VwAK7Q7eZ+7ujuDfWxrtjAAWz3EOAKbABQCIhQ7/Z+7/ie7/q+7/ze7/7+7wDv72awAOxuCwJgBwGf8Aq/8Azf8PZ+BgGQG+dBDQFwBg5/8Rif8QpvBwBQdLqxAGag8SI/8iRfCAX7HkcSEZRWcrrxBjOQHOygAB7/3wcdUOpaUbF6eh6lYAGs3hiV0ge5ZgB0LhoyEOq6IQ1kFxH2oARGYO0YkOiikQU6gOy6EQ2QLh2pIvHYQA0qAC1TygElZw06kAXSYQwaUO26YQRKYPMFsQ4ncAN3EAhrgAFjkC7w8AIoMAeBwAYcEAVsf/NKAAJvEAhvEAJKEOOicQ9RoAGDPwco4AI87vOksQaBcAc4cAJI/hDx8AgiAABOcLi/QQ+ZwAIAIATB8PfUFwowAAAyEApjyxf3EAxCAAAssAmI/xvK4AQAIAKRcOOxMwhBkwcAHsl54OHInAcE/hSDIOJxSOI/YeI/geJBoeJDoZgf+t/nrbrpvZjO/+8T0O8T0g8U1C8U1t/9PfH9PRH+PzH+QVH+HB7JAi7eyY/PHmr+PIH+PKH+PsH+QOH+Bw4Q+AQOJFjQ4EGECRUuZHhwnqB5DSVOpFjRYkV7gtxd5NjR40eDhNCBxIeOEEmUKVUWdCfI3kqYMTk+jCjT5k2FGTfi5NlToEiSJn0OvdnyJVGkKmkmZUpSZ1OoHoGCFBrVakWjV7U2XLrVK8KnX8UWnPqx6li0WdGO7br2a1i3X8t6PBt3q1q7WtvmtQqXr9W5Hev+hYqXcNO9h5P6VZw0MMfBjYkaljw0ceWejDH3fHwx8maclEHfvDxapmbTMjtb/JwapmjXK0vHTv+JmnbK1RVb3yYJmzfI2b892hYudSTVk8VV+lZ+MXhzjBqho8xNcfd0isyxS3y+nSFx7w2rT7wefqF28wm7pz8Inj3C8RLLvzeInj7B9fcFutc/MH7D+frDx77+8tOPPwH/YyjA/gjUz8D7EOxPwYUY1M/B+yCkT0L9KFTIwvswpE/D9zi8z8OEQKRPxPdIZM9E+lBESMX3WGTPxfRgfE/Gg2hkz8b0cDRPR/Z4NMjH9IA0T8jwiEzPyIKQNE/J8Jj0zknzoCRIyvCo9M7K7bAMT8uBuPTOy+3AxE5M78gUyMzt0MROzenY3M7NkpITUCE5p6MTOjuxwxNO7PqE7s//5gKdblA990TI0OYQVU5R6Bh1lE+XLkVI0uIobc5STQ+CVDlOhfNUOVBDZSlTVfGDqFWCTi0uVVgHZLXWUn+TVThaYR21uFx52/W3Xlv9VbhgbxuWt2JVPfa3ZGlb9rZmQ32Wt2hjm5a2ajW99rZsXds2tm4v/Za2cFMb17VyHT03tnRNWze1dvd817V4R5vXtHoFvDe1fEHbd7R+G7wV1oA3Gxi0gi88uNWEMVt4s4ZDfFjViCubGLOKV7w41Iwl27iyjmv8WNOQGxtZspJ/PPnSlBVbubGWk3zZ0ZgPm1mxmqe8ec+cCdv5sJ67/FnAoP8amrCizzy6wFdrxWfp/7+ajvPpB6OulWq+rC4U6wy1hpXrvLye7l/TkuaLbLvMhg7t0dTOi+243G4ObtDktotut+xWDu/N9I6L77X8Lg5wzAR3i3C0DBcO8coUX4vxsRz/DXLJJEeLcrEs5w3zxjQfi3O5jjOrUV/BHlHsVkn3yvPbQFdMdLFc3wp22mQ/jPa3pJMaH9xj050w3r2yXavgXRv+r+K3Ov6q5FNbnq/mtXoeMNPpQt1Y1VtkXdXro4retOnzqv6q8KEaf7Ty7Tq/L9+lXh+09uN6P6r0m5p/s/rduh+q/DFlf5jp31r+15QAOiZ7gtmes7p3o++FKoFIGWBlCoiWAzJlgkSpoP9kLsiWCGpqg0PpYGM+KJYMLiZ+tSqhYk74lRQiZYQ+aeFhXuiVGBJlhpxZIGQaaK0HBimEl9ohT2pImBtuJYdDKSJOjviXJOpliI5q4k2eyJcoXmWJPqmiTa6YlyxaZYuZWSGsvmiXMEZljDzpomp66JkfeiuIS5rintoYkzPGJY1QWSNO7giTPLplj4ipo4D+uJJArmWQTOnjTQ6pkkSmZY5VKmR/HombN7Imjuaa5JcqeaAytiqSY1lkUhppk0tSJ5O62aS7OpmmT0YolKoapVhKiZRTnmaWoXJTPFjxA3Lco1byOIYNxFGPWtGjGTZoBj1qVQ9x2OAY8qjVPcj/8QNWxMMjxMDAAjhgACGso1XM8IACOKCAF5CjVeBgAQJCgAAWgKNV5IiBAc7pAWa0ah1LsOcCMEAMjnATENjARjSM4AFtasoZFriDNbBBjStkQJyaGocF3uDQarxBAerU1DoycAVqEPQOGHBGqODhASNEAxvWCMQ/LQIPCwSCoDPVQRw0RQ8P0GGmBDVCFELlgivsFBtXiEGoomAEoc7BA8i8VBx04NCZBsIC8KiIMzQA1Zn+AQPo4GpXvfpVsIZVrGMla1nNelazHsMA1RCqKRRQDrTGVa5zpWtdu9oNA+RCqLgwQDfs+lfABlau5TAAKoRKDQMgQ7CLZWxj0YGB/z8I1RoaKClFgJECoWLDFAGogyA8+1nQhla0oyVtaU17WtSm9rRAWEBmcREANKhWtrOlbW1t+9kyBCCkO6VGAMpwW+AGV7izRUMAcCHZBQRhuMtlLnMHUQcAmCKzKAhGRcShALbudA4v6KgCdCHUQGxAmI6ShwJUIdRUKICajrpHBga6U10oYKKOcsEchFoNBYijIvV4QVBnGg0OtEJT93BCEXZaDRJQIlRfwAFWrYGDMISKEiTILkGJ4ITxOqoVHFDpTInKVIqQIwNDGIUq7sCBKGTYUewQAQ4CsYo+kKAHIHZUPFqQAkCo4g81aEFCL0WPHoSgD6oIhA48wI5Q3YIjChzYgypGQYQMcNQi7OBCBizAglao+FLxiMMGLCCCTdD4x4vwgAU8wAhnqqoemziBATYQBx8PuBUsUEAGtPCOj9QjzrC6B1V/h494aLlVgf7dPeJxlD8nWtGLZnSjHf1oSEda0pOmdKUtfWlMZ1rTm+Z0pz39aVCHWtSjJnWpoRMQADs=" style="margin-top:1rem;" /></div></details></div></div>
+<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhwAO/A/frAB8mMSIpMyIpNSQrNSYsNikvNyMrOCMsOSQtOyYvPSkvOCYwPiswOC4zOi80OzA0OzE2PTM4PjU5Py83QzM4QDY6QTI5RTY8RDo9Qjw/Qzk+Rz0/RDA8TjI+UT1AQz5BRTtBSTxCSz1DTD5FTjNAUzVCVTlHXDtJXjxKYD1MY0FDRkJER0RFR0VGSEdISUpKS0tLTEtMTExNTUFHUUJJUkNKVERLVUVMVklOVkZOWEJNXkhPWkhQWk5SWEtSXUxUX1FRUVVVVVFUW1JWXVpaWl1dXUVPYEVRYk5WYU9YY0FRakNUbUVWb05bb1FaZlpdYVNcaFVdalZfbEpbdkpcd0tdeExeek1ffF1gZVdgbVlibk5hfVljcFtkclxmc11mdF9odlhmfGFhYWVlZWRlaGpqam1tbWJpc2NqdG5ucGFreWJsemNtfGRvfmZwf21ye290fXJycnV1dXp6en19fVlvkFpwklxzlV50l191mGZxgGhzgml0g2t2hmx3h2JyimZ2jm56inl9gnF9jnN/kH6CiHyDjXWBknaDlHiFlnqHmXuImnyJm36Lnn+Mn2eApnaJp3mMqn6Ts4KCgoWFhYWHi4mJiY6Ojo2SmIuSnZGRkZKSlJaWlpmZmZ2dnYGOoYKQo4ORpISSpoaUp4aUqImXq4+ZqIqZrYybr5CaqYGWtY2bsI6dspCftJ2iqZqir5Ggtp+ms5OiuJSjuZWkupemvZiovqGhoaWlpamqqq6urq6zvLGxsbW1tbq6ur29vZqqwZyqwJuswpysw52txp+wx6Cwx6GyyqSzyqO0zKu3ybO/0r7CyLjB0b3G1cHBwcXFxcnJyc7OzsHL28TN3M/Q0s7V39LS0tDR1NXV1dnZ2d7e3tLZ4tTb5dbd5+Li4uXl5eDk6urq6u7u7uXp8PHx8fLz9vb29vb3+vj5+/r7/P///////////////////////////////////////////////////////////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAwAO/AwAI/wDXCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS55MubLly5gza97MubPnz6BDix5NurTp06hTq17NurXr17Bjy55N+2a6bM9+XTNXG6U2aL6kiet98ls0X9G+ETcpTpovaNqWlzR37dezbOlegrsEREYMGDGATP+KLt1juU5FZMiAoV4OtPIe0+kqAx58jDG8ssPnCE1O/e9FeFLOfhxpMwkQ38UQQxCXgMMSLjK0gIEEEEAQAQYtxKCJfgRa9EwQMHxAYYUVqADDHMN1aNE2YsCgwogQSGCiGNuoaJE4/qmAQYUxZgBDEM/YWFE6msAgIY8SZNCCDLeoZAkMOyYRSCOfDBJFBBLAIAdvQkakiwwZQHADH4yAgkgXF0jgghgOdglRNECsAIEIbCgCiiJriBDBCkBI4yZE4ojRggQXeIEIKIzwcQMEH8igy58PneOfBBFEMQgojQSCBAQYxGAJSp7AIIENqyRj6qmyIBEBDJRA2tAzMmD/AIIjp54qDBgQtFAGl64mtE0QKlAQCDK1IoNMIBF8EESNvSZkzhhygiFMrckg4wgIGMgQZLMJUSIqErOcSmwyq9yQpScmZQNDBTwQQ624UGT5C7cHlRNEBiDI8u6pfEAAAyf0HmTGChGEsq+poUCwghkBG8QJDBD4cXAysoCg7IAND/SLqFCM+y4xPFQQQzYlybFCBbRMnAwxIXwgBocNdwLDA6ConEwS2baZ8TOi8mHzHhJom7FA4MSKhMfvIgMKBC6gO7Q6RXwAgrsT01LBCnKQVLQEYNicTCASxODn0ERgcAPS+5biLy5Dr0PHyVRPTMzVk7SNC8SlqGxsDhgQ/9G2NDFEEIjXagStM0i9QCyK17Tkyok6kEcu+eSUV2755ZhnrvnmnHfu+eegh+65uhJIbDMyFsch+uqst+7667DHDvo5QGAQhdfJQIEBEObI7vvvwAcvfOtxqAAC7nyEjd3wzDfv/POvc9ICBCnbHMoDMPQykifT2+I1MhVAUMIj5Jdv/vnop6/++uy37/778Mcv//z01y//FgFA0AjuSEiQgP0ADKAAB0jAAhqQfngAQAXagLs2SAAAeTigBCdIwQpaUIAJkAAScNcICARgCxcMoQhHSMICkgACFcBd41rgtJBoYnrT8poGIMCBEtrwhjjM4SOokL+aec0JFQiADv+HSMQiDtAOCvSZ15IHADsY8YlQjKL6AiABJ+AuYQGwghS3yMUicgACGsDdMCLQAk2MBBcugIC+bFYMTkWBGHCMoxznSMc62vGOeMyjHvfIxz768Y+ADKQfG/EACCgCdzzAgAgEychGOvKRkIykJAEpCwdUQA24W4MEHFCLSXryk6AMpSgdOQIM8AB3iahQI0bJyla68pWRjMKO0LYvWTCNbSKBBsQS4TVS+CsXQxPHurpmM2JQYAWtGlrUcoC7G3ygCG2jBAsoELeJgaECMEhRw3IBMVJ4LZUweI9IzBEEDPjAa10I2+ECFocPaKCa+0KEv+Y1NOlBoFQqWwXTADb/tI1BABE2G4YGVBCHtn1DBhXowul8sLtzkKQTaVyEytTWgrq1bWMSWIPKagGCDLzMoLHyQTEmhgyGykA5QzuHGKRWC5WpYVXbGtokppe3iS3CATDoREnKQYQVUMCH71oFtoCA0rbFYXqD25ctdoDNmA5NZhHgwkg/xoVV6bRt63hGDNjlvaQFIlcFxeo3gIAvfL4LFBV4JsZIkg0gfCACYKieqWzBhwp0yqnBLIKcoHCKWhEDESHI0lWxmg45uCACN3CEx6x1g1XJAWZPXRcIEBE3ZJwCCg5gQRG0edEYYKACfABGrWihBkYBgWQniUYQWEAhGjjBCYuSwApk4Aus/xIEHGNwwY5EgIQohIxROVWHbQVSjjlAyQEXQAIUfjBDDJxorVhVRydi8AEU+gAKSBABBC7ggjGss22+kMEKKHSD19IgRi0IQjRU8o05REhESVqSGVA7XOJq4jvwxRAMxIBX26YjF0CAwQrSdIEP/AgXkLXtM8QQgxVMKK3s0QR0h5sNMxhpQhL4QIbmUFSVXIMTRThAAHqgifXW1yDfuIUZEBCAEEzCFw49MUHEwQs5UCAAE5iDLsYhY4Kc4xeTCEEADmCGW3S4x9G4RA8MYIAicIK+LvEG+abRY4Skg3zGqDJCVPEIVWj5IMUgn3C/TJBpkM8bM5HyI6hM5oFc+f8RWW7zQLjsZTkLxBjkS7CWzfwINMtEzWyW85vjbGc62/nOeT40n/0cE0AfetCHXgeXJRFpPD9Cz1VedJqn/GgsR1oSXa50ou2s6T9z2s6QPrShD21pTPe41I0+taA9repHUJrVo5YzrGHiaFTTutChxvWlFX3mTa+503D+dLDt3Gpi99nYgW5zqoF9a2bnus27fkmvZ53sWtfZ2sMmdbFNfWxfd9vOoP62nJst7meTO9pknracVw1uV8s421GWtbR/PW9bizrcuh53rMvNbULLOd3/tveJ8d2Sbe/73P1Wd5vZHXB3DxzeX5Z3myedcGczmtf6jje/N77sdV+bzAz/Z4nDRQ7xNiNc2Aqvb8pXsvKMj5zMHIe5x6GNbIOTXOJkpji2BQ5ygj/c52R+eb13/u6eR5reJgf40C1edIxrWeM497fO2/1xbYfc5i1PesknfvIvz1wlNb/6zb8MdbJLHeVE97rRWY50tmt96VznubnrruW2B73se457vucOdr5XWelRj/lwz56StFcZ63avduKZfnGne7vjeW/63pUN9C8LHe5Ul7vVH7/2vo/97283u+Ab/nW1hz3ymK941wc/+h5DXsuId7vibct4lDje9qWvst89D/hMr17lrSf9600ved1TvuqWB3bntfx51Yee9tE/+OmJn/rAX5/1hHe9/+F7nHO8y17vBX/69qlf/Fcfn+bJB/7yD7/+Klff+7MHf+1lfHvh17/H92d834d84ad84ydj5Td5mVd5m3douYd6u4dVvXcSv8d/wUd+/ydjAeh+Awh/BSh/B3hiCeh8Cwh9DSh9sTd1+UeA+3di/ddjD8h9Edg2E2gSFeiCF4iAd6eA56d56Xd5W9eDDPiD6JaBJ7aB9/Z+aBd/Fjh/GDh99td+SdiBS/iBTRiC9TWCEPh8opd9LmeE9YWEC6eEjceEOOiEOgiFACiFY0iFZWiFZ4iFw6WFMsiF2HeCEZeCoLeCHtiC9fWCMhaD7Nd9AsiHVeiHwwWIIriDJCiEJv9IhHkYhCqIfkfHeXpofYb4hojoXzm4iGqogWwoc2Toe2b4h52YhYy4hSXYhXj4hZ94hKG4eKNIgaWYiKc4h2A4XGIoim5IinBoimi4iM2nio7IipD4c5eIf5RId5YoiXu4jIWnfsNYh6t4h8eYda8YhrHIe7Nog7XIicFYX4IYhYTIgZnoi5tIWLdoW8M3iDM4NDVYEjcIjHLIjqlIjcVojZXogLloW7soi71Ii79oi+GIi9moi9sogd0oj9+ojgVpj9Pojnaof16IjclYiNAofs1ofpPog/tIbRdpjhlpgOp3kP6YkDS4kCQxjwRZj1g1jmtYjlN4jgKZjm2jiKj/aJJY9Y/cGJDeOJDg6JJtQ4cSWY0U2Ypip5Ntw5MK6ZMMCZQOKZRD047k+I4ZE48r2ZA3uY5YRZRVOZEsWJF2p5RDw5Qp6ZRZCZVb+ZAv2Y87iZLwqJIjwZJBKY0hOZMjCYIleZdtSJM/aZNDg5PDBZOgKJN9mZdXuJfOiImIGYd2uZjK6JHMyI9kmTFmGZdoOZdaGZhcOZRuuZRweZVyKRJ0GZWPyZHPKJnRCISoyZiqqZGUyZe86JdPCZgZI5gQKZsASZtpaZsNg5td+ZllGZoNg5WaqZacyZZtQ5iwaJiz2Zj0qJitGZlD+JH9FpFfaZRhiZRfxpza6Jy7CZ0t/ymdPNiR1TmZIAmZGPmaJMma5Zma57maRViZDXOZopmZpLmZt9mZU3mPRZmPR3mNY6mbPcmbx+mbAQOcyymclkmcAWOc+Ymc+6mc/UmfAWOfxTmaIVGaaymVGeOVMWmVGYqfG6qfv8mfGeOdCAmeBSqedemejWiej2idJIedIQqWfSiWpmeh9IKhD6qhIMGhyemhDaOiJ8miTWmgEYqg9KKg/WmjhSmiP0qiQWqiCYqiDUOVN6qdOcqduMeg9emg9AKhJSqhJ0qhHwqmFyqm3EKmVWqmV4qmWeqf2Qmg2ymgX8qj3OKjYwqkHyGkE0qkAaOlUYqjh6ij/gelzSmlff9KpX9qpU2KpYOqpj3Kps3ipo8Kp5EqpwFjpG+JpGeppGXKpNzipGmqqN/JqG3qpx4BqGcqqPRCqItqqJqIqDBIqXtqqb2Cqa0KqaUqqbGKq83Cp6vqqL2qqb/KqcGKqiuqqpfKqh3hqnEKq9ziqaAJqpgpqm9Kqs1iqnOqp8Oqq67Cq9Hqq90KrNwCooXKpYfqpf4Hrr1CrM9qrOWKrOeqrNUqrPEqrpBCrhwhrZtKrc2irrPKrrXqrk9IoEnqoqYZm+opkuyplzBKjDJqjDSadcx6pM66q9D6r+baK97aqfrqKvLKsfTqsfYKsug6sCMLKSU7rh27EQCbrALbKwT/m6q0io62moYKG6oM26Eb+Z6uGZ+wmZ7TuZ5E254o+LB4GbGJ6bBHC7FJK7FLG7VNO7VPa7RCS50zip7aB68ky69/4q8y+7GuErLBCrYuK7ZuQrYaMbP3WrOucrPNmrM1ubOe2LPZ+rNDGrQxCp9dK5/Xqbf3qa2Zyq0qi68sq7Z/8rL9GrNva7aQgrb5yrhu4rhjC7kZAbeJK7eQIqs4a7A6i7A6mLGfurEwe7Jlm7Jnu7K9Yq3Dia2Fy7eBSp5/O7SBW7SDy7SH6bSOObH4WLH66LWuSLgjarjHiritq7g2S6dbaqddiqfvarxTirz1qryT67quArsNKrvHS7uv/2q7FAu4Fku8GEu9jWq9KIu9f0K5zcK9Yeq91Qu+0yq+wUu+wyu4NYq+xaq+q8u+buK+zWu5XYK5bau5GMG5y+u5fwK/ayq/6Uu/AXuaW4u0uau0kWi1vYu1vzuf/Duv/hu5rJu9zDu3Ldu4bNslbru5ktu+2vu5zruu0Nuu0nurBCwkBqzCCHwRCkzCDOwmoFu3onu3pCuMH2yyIczCI+zCJQzDN2wjOSwkK5zALRzAL9zAJ3y5KSzFO2wRPczEP9wldKuxdvuXeJuTR5y6SUzFS2zFTYzFT6wiUWwjU8zDVdwlAmzCcdwhc6widezFdywkeQzDpnutqPu4qivCAP+Mx1fsJg5cqRDcvxJMs/b7n8IboBcLe7z7nL4bncBryfiLyebbnVlcwFtMx11cEV/sxmEsJGN8umVcm2dskGmMyGtsx23MyG/syKWMw6fsx6lMEausy61sI0FMxkNsxkWMioUcu4ecuYmsxIssyI3cJY+cq5EMwpMct5Vcp5fMEtyAB3jgDId2DnlgB7YQaZBwB5AQabZwB3gQY3LmDOLMDTCRDr1gMgAAABhgBrkwYSf2DAeyzw8gBp3AWTKWDZdABAMAAANABJcAZTIGDp0gBg+wz+LRX/VVDrlgBhiwzyogB73wzBERDS3yARMSARBGBLUlY9sQBzDAAhiWJDD/AASeQNLSUQ6UECGfJQESoAEsIAOUANA3eQvr8QEVoNIYYGBxcGS21QtEECJJLQFLvV8mhhK6QF0RoAFaoAd60AUhAAE+wk/DJQ1AME0UAAVtsAdqcF7ONQdE3TDfkFvh4wNrwAdr4AMotCbflTHFBSUPcANgoAdtAEQKEwRjM1wPEyYi4AVerQUz1CiPchIbgwEaQAho4wgikCW4hFXa4FYQoAfVZFk84C90MFzlIAZykgVyZSq0kAW5IgZxTS90ICo80Fd+pQemRR5YdTcVIAL7UyvFgAgX0Cn0pDW1ky8HYws34FzXQFiqTQGhQEvJYAxRkCXAhFXeAgHDsi/I/+AHTJNMbcNNEBAF1J0MobAnH9U21+BZNtBV71IxGQAEfe0RlJBGNXUwVrMwWKULEDMIKlMMzR0Es+0q1yADEpAFxjIxWlABMvDcQ2MvGUADU3Uwg+Avkz00A1MB4XIwyEBRnzIS5RArt2MzDhQDvN0wY6ACInDep+II/sILbWMJLRABrb0vK3QJbcMLEEMreiMCHzAGbaMNMSABDGQzsiQDBZ4R/hTc+YQ9TZIxByUBbHA64KMCpz00QaABG+Q1SKABQdA2dKACF1DhE8MGQePUzRIq9+Q1hAQDxw0StzA9N34wMWIEqpDner7nfN7nfv7ngB7ogj7ohF7ohn7oiP+e6Ip+6IDAABAgUV7jAxVgAYte6ZZ+6Zie6Zq+6YkeCQVA5biD5gQQCZxe6qZ+6qie6pduAeaEO4sAAQwACKo+67Re67au6UZAKbgzC0wT5S40PfB0MCBAQ11U7MZOQlQwABBgMD8URMf+7NAuQUgkAUpkM8kTAE4U7dq+7fVDRVBwRR5UBdw+7uTePl90PF4jDLliRiJxC2lU5/uCJTogCapA7/Ze7/h+7/qe7/y+7/7e7wD/7wIf8AQ/8AZf8Ah/8Aqf8Ay/8AIvCX/g6JBuM5JO6Q7f8Bh/8Rqf8Ry/8R7f8SDv8ZIgCZBAAKDuNZpEAJDw8Swf8i7f8jD/8jL/H/MDPwEVcE5e8+oM8Ac0P/M+3/NA//NCT/OSYAQREAG73usj4Qs97jX65AK+HjDbsFVHHuAXsAJz0Db30uU2gwQYEOZDMwdkbuYH40AywCwN4wlpZFYT00Ex0NIhIQ6xkgVeowcRMDJts1ItbjNLAwMyPjQ0TgEttVF7EuIZw+MQ4OMkBeRCPjTZgFB64DVScAFKThKUMD24rd8XoAIMM94wEAGEEOADjtD0AjgSoFAqk04xAOEZIw7ldANkTy0XDgPZreFkDu+ncgq5It4iAQ61EwId/i7CkAMik9i3KQbBsjjenQXYbVszBQEAbuG5YlGeDwFaEPumIgolst5D/yMNsZIDMRTfIrA79e0RiWPZh1QsoEADWRL1Q/PZb+UH8LQKPhABLjAHOE0bgSInXTD4pwIQtbpAWCFG3DqECRUuZNjQ4UOIESVOpFjR4kWMGTOmm9MiApJVyUSKJMYnwgcg2TSuZNnS5UuYMVl6giFhBqiRIpEp0oABhi+ZEnHF+PAgRBc+gcCMgJABhqagUaVOpVq1JbQgKyJciLIn0BoeEHzKKWfV7Fm0aWF+K+JCAgUkbQK1SVJBggsx39Tu5dvX77pycmBcgMBjTaA9WS5EYAEk2l/IkSXD1AQDAwQaYPzw6QICwocYufhCKwJDBYYIEiR8gBGE12TYsWVL3P9WBsYKDKorZHAho1O62cGFxxY3SQZuuxIyrIgx6eBw6NH3pusUo0WG5BhUwDCzTfp38FV5BYHxITtrItD8mtNlZgUAABjG3Cob3v79mL7myIAPocgmvfATcECMpLEkCAIAICAIS6Qh8EEIIfqGEyIegE+GOX6JcEMO1xnnljIwgE+FNHQxRzJr7LCjmQ5b5NCcO+qgxUUaH1QHkjogUadGHvGjpY47TuxxyO+aUdGa2Lx55JFpiHQSunSWNOZJKoNT5RFVqtQSNmOWBG5LMP2aZklvklyyyTDTVCvKR6ZU882zrswSTjqp6vKRL+vUM6YxHykTNiWZ3HPQl9h0k1D/RDWSM1FGMbozz0YjhajPPycLFE1JM23IUE07ZUgSLD0VFaFHR/WUUjMFNVVTTlfV9EpJXNW0VFkjRRXQM2uNtFVdGV20V0ZpBZbQWy3NdVhCeUV2T1DnXHZPYZ+ls1jJLpVWT2WvffNXbeGMttswqY3MWnDVzLbcLWFFV81v16VSXMjIdVfLc+d1sll7t2w33x7h/UtefomsN+AauSV4yH0PbtFfvwBWmMaBH+ZQXYl5TLhiCBnuy2GMN4y4YwINBnnDi0fGT2O+ODZ5wI9Xtg9flyMsOebvUN5LZZrDaznn6CjmWcCZfxbOZrVwFhpKKY/GT2SlpQu6adiITsto/6hl27nqyWDGOrqnt/5LarSo9jqyq8f2i2mzufQy7eDAPktstvkqO+60fKZ7sq7vNstts+DW+6y5/65Ka8H/yrtwqfi2ym/Epwq88aDQhvyswyeHSfGqGLc8psc3d8luz82qPPSVMKdKc9JZ6jz1jCRnXabRX7fI9KlQl/2i1W+niHDdYV+796Bol8p24CXKvfiHQEe+pdiXb0j4qIh3ftOkp/88VOuZ/z17jaAPSnruETo+fN7Dt6j58L2XCfzwx+fedfMjQp979WNin3v3s1c+/onmz75+mNwve/mzXvn4JxH/WQ+ALxGg9Qg4PfgdsCEJnN4CXdLA6T3QefuT4P9DKOg8C7YEg87T4PIi2EGFfHB5IWTJCJdXQuQZEIUT3N4MH8LClbgQeTAsHgdtmMIa/pAhONSIDovHQ+Cd0IYqRB4RM2JE4CGxdzIUIqmCWMWEOBEjUOydFHWnxBkysXhavAgXdefF2/mwimIEHhktYsbboVF2VFzjFbG4DjdWBI6yk+PrwIhCNvYujxTZ4+v6yDo1CjGQuhvkRArJukOm7o8dXOTtGimRR6YukqSjoyLtiMVLRiSTpNtk6BL5w0rKLpQQGWXoSum5SUowla9b5UNa6blXbq6TqPxkFWvpkFtuLpeWi+UBZ8m6XzYkmJYb5uROucReCjGZDFnm5Jr/CbldQhNPdxwimVKFKW6Kr3rhTEgx+XfM1E1zIdWE3DUb98wwRvOH6lQIOxvnTsSZM37oJB09E2JPxOGzcNmM5zbJiRB/IgSghROo4OAJSHnaMKHrWKjgGvo3fZqPn6GbaEX/dlG9ERSiBj1oR491UJDeLaPh26jnTKoqlI7zoA+lZERn+FJwhjOldBNpTUlKTpweVJxtEipCVsq9lm4uqELdadxoKkubonCpMSVqUY+avaRabqrkbCrbegrVn4ZzqzqVKTmfasyodnCs3Oxq2q5qvaxObq13bKvZvorWsHJzrlis69jeOr24Qm6vVeyr1856zrRKcLBCLOzW7orY/7zecbE/bCzW/uq8wDZusjasbNUOu8/EHnCzM+ws1C67vMwibrQoLG3THgvayILSm7iCKVfLGs7PajS0/FttB1urtNMiL7WF660Ef3u01+o2tr6crbFqS9aqCjW4xRuu4Ip7wOMKLbcs3W38rsu/7P4sudxdrjSbW62T2ja6M8WeUKv7t+/GL7w82y5Su2u++JpvvjmbLvDeq7f8tu+23Byvfcs7z/OOK73QPRR7Y1XU/94twPgb8B3727sI023CA6wwFguM1fumL8HxWjBbO1zFC+suw3HbsANPLMT6gvjAEh3xv0pM1xf/8MNwDTH9atywG/M1xzZM8e1WzLYWZ/9wyDOMMY9nfNMfbyzIhF0yCossuyOnLckkrHIHdwzYHv8vyimbMmO7LMEmg/nJUh3zzcpM2TMf8Mqvy7LZtvzCOPPvy5gNswLbXLQ3czbP8Zsz6+o8tjvvcNDmSzOf16zWP08t0KRdNPnae9BDey3RR6z0+y5NzkxvbdNR7LT+HvFg9/a5gpEO26RZW2rrFTp1ocbaqLsI6+ntGbWqBiGr3+Zq3+J6g6cu6jpoXTVbn1HYJvx0OI8NtWTHcdkxbDY3n920aPNx2j2s9h2vrbRsG3LbSSQ2hHm9Ql/3DdjGHfcUu43Fbx8t3JBs9xffXcdHKzbdi1s3duudxnKnOt//ot135voN3n/LTtaki7fQ5q3JhL9O18I9dxMLfrqDyzfiiAw4pis+xovXLuP63bgk7+3JgfM25MMbuYDXS86JU/fjbVx59FpO4Zfj9uS8TLl3a/69m3M459xs9K57jt+fry/oLh76HWPu35kLMun2W7qSm47FhYeu4T97OClLTrqiU/zoIvbTN4u6X5pl3XNb51nXXfn10D0dw1Fn5NQDWHUuXx3FHQc13S1pdwbiHc96h/HOtQkpsQL+goJXNOF1bPiCIl6vihch4znteCJDfqSSlyzlW2h5UmOeyXx3tt9V6fkcgv7Wokeh3FVselqivoiqVzbrO6j2zbE9Z27H/yXcYUl6a8MembJ/Iu2lbXs0a96nnJdt2WmbUxMj/4CuN7Lw00n8LRpf29LnX9hlPnYfO9+50Mcx9wmtfLAyn7niR+9zo99gmKMfr+o3L/sV7P7yw1/nzvI4+MVsfxLDPyEzP0YDPm+zvn7CvjLSPnEjQEvjv77zPz8DQBsTQCpzQE+DwNKTwFWjQCCzQDPDQFNDtf6jPwTzQCkDQTgTwViTP8gyQRpDQTJTQUFjwVxzQdiCQSiTQTejQUqzwWEjwQjUQTbjQUDzwVcDQmbTwODjwF4zQklDwmBTQmpjwgN0QnSDwlaTQnajQm6zQnhDQI5SwDdiQHrzQnITwg0kQv9I08Jf40J/Q0N3A0N8Y0N9c0N1g0OEk0N7o0OUs0OCw0N+00ON40OAU8MmBESVE0SDI0SSM0SFw0HlUkSfY0SMc0SX0z8Ck0TyokSks0SRw0Sc00QLM8AwxEKLA0WWE0WhI0Ws40QD80Syq5T2I78BdMUqoj4sE0OXIkM9MkOIg0Q/gkUZk8Xwo8X7s8ULxMXCQ8QrNMb/Q8YAVMYQZMbH80Oeg8YJlMYKpMYVtMbMw8bDKyreEybf2xzvgzpUBDlVtDlWZDpwHD1xjDxy9EVCAkavE0bW0UU640WlskdHwse300eTc8ZT1MYO5MYP9MYajEcrI0YnQ8gnVMgUZMj/H3RIL4NINZPILKTIGbTIJMTI5JvHzavHdgS6d7Q6kZQzU6xDk/TIHgTJKVxJPdNIR+PIVITJI5TJLqTJ8yPJ5XtJs2OqcySmlvxDoXy+sytKZ7JJo8NJdtTJKOTJOPRJ8+FHQ/NHrQJITBLI3iNIsDvKbEzK8VtKsDQlpxQ7qKS5k1S6lMw7q3zAYtM9milHZmJKyME9y6HLmLFLa8LLdxLLcRQqv2wnwEQcrJw1rZQrrhQlrzTHs/w9oEw/sqxFs4xLTzNIlyTMxmSlx7zLyETHtPy+tZS6tqS6txw8zMyexGS4xRSszrSlz/zL0DRKzURKzjzNu0vNxlvNFpzM//mrzGS8zGJrTa17Tc2KTWCaTcOszaYEzhcUzmkkTqsSTHrMTancQqrcQ9+8QejMQensRuqUrtFUx9KsO90MPN68vO4MwrlETtVSTmVizns6zMLRy8nhS5cpzPp0Tmwqz7lbR7bMzjfczkJsT2a7zbHEzqGkKgRFHvyEHP1cGf4MKPsUHONcO/gkLvmkJvq0UP8MzO+cxPBcyPF0sPcUUNMk0Dw00Ed80OLJ0NzbUOvq0HX6UIa6UIwC0NdTUfRk0UF00UwstnQM0PP8u/RcvPUMPRgltxHtxBKtyBONvyeNxSj9yCnVOQUdzJKy0XrCUYvSUb2J0MaZUJPxJ23wBP8sQAAEGAJOcBBuAgdckIMEMIAZsIRnONLQKYdeoAMLMAALoINeqA++egZLmIEBWIA4wAVwCCdp4IQhYFMs8ARt+AtwmIQYcIEMUA0MaIEYiINKFSJz4AQZMA1OXQEYEAP1qCJdII8VqIAIqABUDQJdwCJoEIPbyI3VgAEg4AQh+SFtiAPr0NUPcAEYmIRG3QtpCIIWkAAImAEkSAIagAAJWAEg0BAbAocycAEMeAAQ8AEnuIEIgAAViAFP+KFyoAMYyAAIqAAecAIeqACxgAE6IFQUookPgAAIuAEnQAINeACfGINknaFfAIJmxYwkQAIRoNYWCAI4RQttAAIVgAD/L5CFnKiFNtgNGXiGGRIHMWgBCEgCUkCGkRiGQQCBCoCBc2WtOYCBCqgBRiBZkSiGRqgBCWiBObAhmqgADSCEYRgJZCiFJHiAFjCIGXoGGcCONqCFnJAFMCBXIAhVsyiHIlCBCnCEnMiJU9CADACCgT0gOQBZP8jakaCFG5AAGFhVCfIEF4gAKSgGsk0GYsgCCFBZFIKGmriBWojbZPADCHCBnO0gcACCDNCAU8haZCBZR4gAFSgCe6UKmoCAROBbkSAFCGgBSuigZ6gJMKDcZKgFEFABMdBTvQEHGcAAH4BbvjUGH8AAGfha/RKDDwABW/BcMEBbjpWgSQBZUvBc/0RwALu1inQAAgzgAZmlXC2ogBiA3fCJgxXQAGHw3GQYhAiAAWzln04A2cP13FP4206QoF+AAQgYBOkVBg1QgTiQINPFAC6Q3mTYAQwIgnOwCryFAERwX1GoW9HgH3GQAQno3PKNAMyVoCL4gBtw32S4gQ8oAgmihBWQgJ+VXi+oABl4jvjJBfEVBfdFBAiQAbWdClyAgQeQhePlW2QQCy1IXBVeYRZuYRd+YRiOYRmeYRquYRu+YRzOYR3GYVDQV0UoYb7NAQyggR0uYiM+YiROYiVe4hwOhnZVAwRWAwl4gGBgYiu+YizOYi024mSYgeJFYEV4AAkAhS0uYzM+Y/80VmItuAwgjltZ+FtcsApNAFlgQGANgAAOWBI93mM+7mM//mNADmRBHmRCLmRDPmRETmRFRuQqCAAIIGP3dYIKCIBFrmRLvmRMzmRN3uREtgMAqAA+QGA+kAAAsANOPmVUTmVVXuVLDgAJgAIE7uEAmAJWrmVbvmVc1mQOgAANQGBguFyoqIpOcAEI2FvpRQYKgIASyGVmbmZnfuZH2AJHbgQERoIKSABozmZt3mZMxgMAkAA9QGA9IGU84GZzPmd0/uMEkAAkQOBGgIAA2IJ0nmd63mYSaFcEroXLXVmq4AXxDQX3pYXL3QR0OIeCPmiDTmiEXmiFbmiGfmiHjmj/iJ5oia5oir5oi85ojN5oje5ojqboanDZUHZfEPiANPhoj05plF5plW5pln5pl45pmC5oczjdKEDgKHBdc0iHmZZpn+5poP5poQ5qok7odEiD2UVgv4UBbChqpx5qqH5qqY5qn55jCGBa6Q2Fun2NqjDdCoBi6R2EDn4M8CKCDDBe6e1eGLgFCaKDFbgAYpBeYpBVOpCgEIaA7fVcHsgAIpCgaJCBCCBf6VUDCmbeqHDeCjBmviUGEVhg0r2bYYYAgPZcJ3DdAOGfX4iBCBhpyjUJ65Wgb4iBC3CCNs4JUADe78WuAhaBuKbcWpDV9DWLa4gBCfCB1o5bLZCAGAAK/wkShyDIABBQbLINhL8NZgkqAxagAA3mW1KIgBUwAxTSBGIOBMqlBRDoWgvmH1+oiSygXGLwAd2+BrTghLxtBbKtBSe43EkgWNEGgcnOCWJYAwhggTF43PjZBiD4AAogBCBGBkKgAJTwjg4qhzFogQdgg9seCVAAAQyIgett67aFAqzOiVbIgepN7bNQB0qwDAiAAkQAhVBQhORNWTP41Q7CBRnIVx8IBBBnhDUAAQEugsvuIGgAghV4Vj1wBFFwBD2gAecGgg8G7SJoVg1YA0YQhU8IBCR4ANCI4xkyhzhwiwrgAkUABVAghCiAgAs41h1RC08YVgh4gDDHgBWQAf9LmN8f+oUg4FZn1dcKYA05yG4UygYxcAHz0Nd2LVYxUIkfEgdh/YDLiAAxxgAXCALe5ixLiAHcwHOxaAEZ4Oe92AZLsPEAIIAMkAE64PMqEodOIAIYqPQIiAEzyF3CygUxkAEGMAAGiAExyIXHnpxfMAPNJoABaI1OkHMbugY6SNoBGAAVAAJLEPC/MIddsIIqeAX7JqxqsIIpYARcx6Jt+AMq+ANhDydxYAQqsIJq6PJwKodXsAIr2AUTn06ifARiKE4erT4fRVIgbUQhHUUiTfddXPfTS9LKW9LVa9LeIVPEMdORqdAcDdF8kvd+pPfYs/fPw/fa03d729Lr7FL/hE89hT8+hr8dGd1LGoUvL/0nMP0oMVUpgs9Kgx++iJ+9id++io9Ehy9JBlXKck/5YazSYrzSmMzSTZT5iKT5nbT5Ulz5oGz5snz5eMf5jdT5qeR5Dwt5xRz56yv54jv5BoR5jiP6mzR67UT6vfN5ygR6yxT6orr4/Mx4ANt4hep4vUG7mOH3wvF3kAH4MBX4+7ROlof4dr/Ed2/FoU/RV09Ap88+qD9DqU8dsJdQsZcwsqcos78btHeZIu3RvR/Dvl/Avw/GwA9Lqn9Kqy9QrBeiwS/Twteww/eos/94ulF7wWH7jnF7j4d7h5L7n6f7BlWvyo87pXdNpuf7ug/F/7uHx7w3t9uH/Nxfxd1XyXjX+uDk+uH0evK8fLXM/Bbd/GvUe+cPUujPPOOPTuQndwftfYF7/F6M/DKc/Hycfc/p/H7/fBYL/cSnm8VfGdP/G9THGNUffdbf0esHz+wXT+U/KPNfe/QHiHUCBxIsaPAgwoQKFzJs6PAhxIgQpz165E0iRofeKk7L6PEjyJAiR5IsaTBdRWMmV7Js6fLlS1WPVMGsafMmzpvGKqbL6fMn0KAMKVoUanDjo45GlzJtyhLlI5VOp1KtClGmJKtat3Jdt/NRz65ixwYletEpUqVk17J9CVVq27hyR8qkOfcuXolfw+bt6/eg2alp/xIu/P+2MGK/kmYmbnx3r+PIbAOj5Sj5stjDmDdrxcr5M1XIoEcbpdx0MOnUPzWrbn2zruvYNUXLrm3SNFPUtneLZM37t8fFdoET18uzOPKHuJfqTu4coe/n0gnCnm59IO3r0pcbba7defTvyT2Ll569fHHuQr2jBx6+/W/h8JOfn79bfVD29mu/3y+7un+81Rega/gBpR+BqvWXYGrkMSjbgA+OZuBPCEr42YIXcgaghqlF2CFmFPpkIYiSZVhiZPKhONqHKzYmYk4kuojYiTMW5qCNl7WY418w4iQjj33VGGReHBKZ2I5H3uXjTUAqKdeQT8alopSFJVnlZBWddZplWP7/FaWXYxkZ5mPHkZkXkzY5eSZXYLLZ2SNZvVkmWHPOlWZNa9pJlZt7OkWln2tdGahTeMKkJ6FL9ZmoUGMyqtWgjwpl6EuISrpaSpd2haOmVUXaaU6UumQpqDYtWmpNjqJq1KerwiRqS6S62tKps7IEqK1CtZrrSrCyJCuvJNUaLF1xEqurmcf65OtKwCr70bDPeqSqtC7tWq1HzJrkLLYRRdstRLiC29K1406kpWBdmktrpuu6RK27IZUb70LalsQtvdC1m29JnPIrb7L/hmQvSfgKPNC3Bw8krsIYzduwQASPZLDCCTcML8QNPQyxxCJRfLDFCvubMUQbN9xxSB8L/xzywRiTrJDJCqMMksr/siwwwy9rHLDODs38Uc383vzvyD0vFPPBP3sUdL5D8+uy0QUhLbDSGTFNr9P55hw1QlP/WzVGV8ebNb1Qcy2Q1/yCLZHY7pIdb9FnG5R2vmtH1Pa6b7u7tdwE0U2v3RDhba7e65p99t/xBv7Q4OMWbm7cfWPHs+QFLa6RupWftK/mBh3OdeLuXt5Q4+A+Pi7flYe+7ugMld7t6eBGrjrlna/T+kKvYxt7t59Hvbq5uCuke7W8Y5u65MCPK3xCxEtrfLW+G608uMwj5Pyz0Es7e/K1d279Qdgrq/2zyPdNfbfgH5W57QKRr6z0PaOPrfoFif9/7PvHcn++95rXT9D9iJU/YsVPZ/Or1v8GEsBgDTBY5pPbAaWVQIEskFcN5NX+INi/yk1wHRXM1QVzVcCXRfBZHfygrUJoqwciboOSOyH72qfCWY2QZCVUFgyT0r6CzNBVGWxhnXY4kByqRYg9XBULQefCvhFRiAjjnBBrmLEbHquJTlzHEVH1QyUG0YlWdGIWSyVFiFGRWF80IhR3mMTfLVFuZ9xhGEG1RTZ2UYhvlGEa2zfGhpUxWHe0XRw7tcbptfFsf+xcIDW1R4X1kVeH1FwiLzVHQtZxh4+sXCQlNUj5FZJrl5RcJh+1yIM1Mlef7FsoGTVJTlayfaeUWyr/EzVKgZXSVq88WywJtUkDdjJqt+RaLgO1Sl620na/jFow/TTLf9VyVsc0WjL3tEsS9tJoz+xZNO20TH4101XX1Fk25zRMahbze+iqjA6vGM43TdOG1ezZN1+2TjZtM1/dXFU8STbPM43TneX03zm5lE4w5tF29aTXPVGVz4ztk0ztnOI7dbZQiDU0TP2E6D85GNDcxBCQBe3cQeOV0FJNtGEV9dJDyRjRl5W0Yh/VXEjdNVJQtRRkL63cRVWa0RdulDkdReRNJZdSPq6UZDVdWVD7FtN1zbRTR7VZUuWWU6LulIk97c5PIRnVsy3VXE3V1FOFtlWuDZWRRc1YWJs2/9aoTdWsVXXjVdeTVUyu1WhdHddXL5VWrNW1Z2Ul5Vk5Ftf8zBWUfdXZXcGVV0ntdWyHfVlbAftWQw72QIVF5WNJ9ldaBvZkla3QZWGZ2YwltluLfVRj3TZaiEWWs5P15GdHFFpcrvZijLmiVzors9jGaLbArK3CNstM3SaNtz/yLTKB2zJj4fa0jEpt3pQrsNJiy7mJgi7hpPsv4XKTuFQzbpOQC03tPu22V7QuobDrOPLmq7XDfa0vwasm8WKTvfTirj29+zX55om+4LQv3MzrRPQGSr2mA7C73Ntd+FqTv4fyrzwRbDgBC5HAfjIw7CRsLvwiVL9qc3ClIKxPDf+PS8H5ZTA8QTwqETOUxLKj8A4tvCcM787F3eKwSD1cNxXHisUUtTG2qFstGduJxsUDcvSYe14dA47Hv/KxSZEsLRzLlMmKc3KzoOzSqOB2HUKWFpHnZOTnSflZJu4wiiWK5W1p2aZcxu2XnxXmN405e2VWFpWZamXRrflebUbqm6945hynmaV9LtifoRpoJ8ZZWXNmU53Hd+dj5dmre2bdoSeWaLEuOoowbt+jzxRp/E2agEoe8KWDl2mPbVqtnVbjp20XajKNWoClDlajjzXrMNWagbfG4KkrnOrlrTplrebrq/UY687t2ku9tuCvc1VpvA67esWm2bEdm2yDBjv/xtVO37WBlm3Vbhuky9Zcs7H0bBBGe4Xnpl2hjRrupY07uuWG6bu7F2+0zttq9c7uvXHabVB/m379Dtu/1xtwoeabf/sWbFHQWUQ4tpuGDdfgwz0bcYFOHI8LV+rAZV1wBB6cbQk/8MelenEg8sWOJb/byTOc8rNNW7Ejl+DLBRfzGs+ca4OucsZ3u3GODhSNPWfryrnYckvmnHE7P/LRjVZz097chE3HXNEpHvWe5ZpY6a7SulNYcR+GnNlVx+HVSfd0Mm9dZ1Ov7tmrmHbXrd3ObYds0um4dFfOPXd1l/TdSfZzPQe9uEP3adY9DhdG552Sezdm34f3d1IHPmNv/x9y3M0Y+eZN3taVZ23Z0Z15P27+ep339edtOxxUF/67h8dq4j2a+uA2npWPN+fr5Rp7oM5+uasXduv3m3vC7l6rvZ9u6OF9e4AO37LFp+vxt1t7Yi5fo80H7fMNG/3y/t7bwf/w9WWbfcxuv73J13f1eRr+3o5ftOUv2/TJmX6rrv+47aft++N1eTCP3pGlD9/pQVv+Jdj5Odz8wVX9hdf9/dYATlj3Edz37VgCztcCJlcDblj8+dMBUtYE9lcFjtcFllgGYtQGwlYHPtgH1lcIvpicLFkENtkJhlgK/tcK3tgI6lQJxlcMsoQ5QEMhkAAJwIEvlAMcSUMnlEAHaP+BLoiDEGkDLhwBBxwBLmiDEImDLmgBB5RAJ0hDDpJMOfgCHJBACRTCM3RhSZxDLgRBDHwABEBABsAAEHQCEWrOL4iBDLRAG2IADMQAJYBD51xDHMQADFAABFCAC8RAHFxD54ADJcAADGAABERAC8iAGPxC55RDJwABDLAhBKgADARBLpzDT4hDGcBABkTAA1xABeQhDIjBNkiOOTSiCrQhBVxAG0pACwABNFTOLciACkhAG14AIUrACsQALlTOMwBBC0jAA0SAKkKABHwADFCCOUjONhTBIz4ABFTAKj6ANJoBE+KEOBRBC0RADSiCLSRDMgxDIyABBKwAELwiLsn/AQxIQAgEgiyoIzKEghZAwAfIgCXKDSc8YgW0wSkggzqeQhtQgB5yQt/8whpCABeIQjGooywEAghIAAzIgTrIzTYEwSwiQSMMQzIggy0owg1AQAsUQTjWRDqkAR7ugTGoI02WJCK8oxjMYdRoAgw8QBQQQ03SJCloQAYAARVyTS/EgATYwCwEpTrOgg1oZC+cjTYAQQZogCg4ZTIQQxRAAAxowtmUQxHMIiIgpFO2gSSaQUfWBC/EQAS0gVbSJCF4ZSdwjTYoJRKYpVaeAjHGAdeUQxB8gAgAQ1wmAzCIwAcEgU72TBysQAScQmEiAxJUAAwcpdF0Qk8iQknGJVrG/wAv2AQRCKZeaiUy/AAGyMBivswkOGZTFmYytIFGSkPU4AIMQIAjuGYyOEIEwMAxGo00yIAE6AFuykIErMAkRE05yAAG5KVrIgNiFkFNXEM9BgJu5qZX+oLRlAMQYIAUVKctqCRYGk0ZiGZ1ImYZ7CQe1kJ1SgEGAEFqZkwv1KYjjKZTIkMgSIAMKOJL5EJPrkJ1EoMbvgE1DCiBFqiBHiiCJqiCLiiDNqiDPiiERqiETiiFRmgsYEAEEEJ1JsMNYIAQVCiIhqiIjiiJlqiJTqgzYMAFgAF9auUXYAAGOMOJziiN1qiN3qiICgEG1MCG3uQHxAKOBqmQDimRlugbfP/AAwAlbq6CV/amS3ACHgrDhmoABHBARVwplmaplm4pl3apl34pmIapmI4pmZapmZ5pmVpBADwAKGyoE0jAAaCpnM4pndapnd4pnprpHQCABOzBhvKBBACAHeQpoRaqoR4qotLpAUiAE2woKDxAAFhBok4qpVaqpd5pB0DABWwoMLyjQ74ElEIAYVanLZLApZ4qqqaqqj6CmkJAm1bnZCLAqs4qrdZqne5pcG7oHgQqHtiqr/4qsHIpAjDqhn4CBATAFQSrsi5rrWaqBnCqStblftYmZOJmp6qAIHSDtm4rt3art34ruIaruI4ruZaruZ4ruqaruq7ruXrDLqhABAz/wobOQAY8AbveK77mq77uK7/2q7pawwdcQBdsaBdgwAdYg78mrMIuLMM2bL4+QQbMwIYOQifugsNeLMZmrMbyqyDM4qi65ik4AAzkAkxkA3DyQXUqglcGpM6YQxBgQKPi5ixEa9TEwQeAwIaCwAf45WXiIS1UpxO0ZzX2DERCwCJUJx9QgAxYpkuIwc1WZGTmAAYoZtRYAh76p2uCAX5mQ9ToQm0qAm4mwgPAgC5ETTYopRosqUpaQtSYg1XmQIvWJDHorBjYxC/U48AWJh/sppP2zDYo5w1ArVaGgkrSAdeYQxF8gAa0plbOggZ8QBGIYtTQwQq4amEWg9TKwDdw/w1tQgDKxiUydAFlsixMzEFtdoGS1iQy6IFKlsHQRs0t1KMPpKNTKkIFJObmcg00xAAGiEC1BuUpiMBp7iLXfENgVsDROmUt+IBGesLZmEMZVC4fCC5NEkMXQIALzAFOlEMZuIAEgIAfnIIwDMMqDAINqCQR+OHZqEMjSkAFrIEo2AIxyIIi+IA/AoFsyg1/QmIWOEItEEMtOEIWQAAGxADJyk00AMEHRAASKIIsEIMtiMIacOM09g04EIELRMAMDMIqDAMwnEIfgEAEuEAZvOdLlAM9fgAwtiE0viE4So46dEIMrMAqsjABuwARcK3k9IIyYoADRIADBGMuYqfkZP8DETwiKrJwBayADHSCGfILKcKABlDAD/9wNMIAHZhwTfiCGMxwAzRABsgAEejCEwuMNAQiDDSAA1wAHMrhIk6CDMQABARxDMjAJORu5YxDJsZABTiAyCJi/mKSLhCBDHyAH6tADFTiUmQDJqDACRgCFwrRN+SCI7PBM7yu7YhDLzTBCTRBL7Sk7ZjDM7SBCaRALuCx7aiDNBjCCaAAJugw0XWc7C2epz2gyL3gle1gj81ghNVgkN0gVZWxvOnyk/HyiPlyktmy2eEynxFzlhlziyHzlAGzWwkzvzkzm0Hzj0mzmRUgxlkzxG1JLOPWSWFJ1wXL10lJ2M1KOVfJ/sn/Wf+Z0v+tjzZHGTfDDzVLFjhrnDgjnizzHi3v0OBZGjNjGjb7WT1vWUC3zzs7Wjzb0jzbTwCy2z3rTz671j4LXT/D3j8b30JzWwuyXkYb3kbrXkdD30ebmzKLXkGr2kEjWkK7WUprTkPr2kM7U0QD0ESLXUWbWkgD30i7XkkT30lr30wL3EorH26ts6u0s5TUtNfdtDfltALtNDuP3aqcM6+k85Mw9ao49ZMMNLW1NLG9tKbFNKAdNcMlNfotNVVTkFU3NVZr0UW/V1AL31A7X1GTn1qD3E97312DX15j3167X1+rHFsboFubNauhtaIdNs3V9YIFtgQOtvgVNv5B/7bPeTPLLbZlsx9mM6BmI11if7Nnp4tjc9poS51knxhlw+Bn219oW+Bqc11ro9lr53JsK+Bsg2BtIxZnK91pSxw5z3WpQDU6SzU+vbUHxfVXG7cc3Tah5XYz7zYF9rYK/jbe/TUEUrdBW7cHYjcNarfgSTfQebdLgzcKincvk7flmTfhoXdZq7cMsvcxuzfocfcty7e1Mbaxpbar4bfqdRlXK4lXowpYKwlyb7VyKxRzo9BV9zSuwTdB8ze4+Te2ATiyCbjIBLfeDTfHFbeE88qC50qBH8mBl0qCH4lWm3iDk9SDOzeCQ3eniLXNkXV/0/eKabi2cbjvEfiL01SM8/84ufk4zlD4WFu4wWG4uBG5vRk50Xi444H4OKsTjSsSkt+4kpMck9ObkwMclPNLidvKiRNJioPKihNJi5N5kDvVkNt3NIe5+en3Mm85znW5v325wsn5fWU51eH4hev4LsP5NvN5gJV2Z1/RmXdKmgeJjf+5nVsdniOcnqOcoRMgogu3or+5iF/6uoz5rJR5kCy6pjQ6jzw63AH6kgt6MRO6PXs65Ph5qkc62k26yVW6zME66sg65qk6l7P6M7u6QnfZmod6m4MVp1v5iIuQlNselftzp3cZqLuKqPMIqV+KqedIsVP7setVshPUstsKqvc6rcudrcMcrvOcrr9Ypn//+Kafu86lO9Stuw22+5S/O7Bns7DLNLE3O/U9O0dHO5zxOv/5+p3nO0Lve1pLO8HDs8FLOsLDtMI/dr/bu7PjO2pPvGr3O52zdLlrHrw7nbyzHb0fT8M79MPXesSftcYHeMUDecqb+8o3dstvOMfD/MeTXshjXc33+Ms3V7cz1rcbXclXy7SvSrXnyLVLSrbbyLgXfM77386r3cjbXdFvz8nbdMyD/Mz/d88XOcNb/L9jPHEr+9V3s9jLH8CbtMALmr+rPdmHuNmHPc6vPVG3PeOlvQbavV7jvad1vFLHfZWD+9njs96TIN8Ttt/D2uHjYOJf9uIrG+C3teBD+9wP/3zjB/Pjg3bk287Ro0rS28jSP0rTz8i2I33Qo9bQa13hW/TkK3blB/zlX9Hnl0roz8joM0rpu8jpg37qP9fqK97NA/3W63zXZ/jXP/nPu2DUy/PU013VA17rE0vtg8rtu0juJ8rur8jTO3zzQ/Tz+130U970T3jmV/Pmy3bnd071d8r1r0j2E8r2o0jv2/7vX1fwz/LwM3/68/b6A8Q6gQMJFjR4EGFChQsZNnT4EGJEiRMpEpT0SFVFjRs5dvT4EeRHY48epQt5EmVKlStVTiPpjSVEbySnxbR5E2fOlOlIGtP5E2hQoQhVYRx6FGlSlSNLKnX6FCpEl49gKp35qP9mVK1bt/J85JNrWLFIi0oaexZtTqYm07Z1G3Jq1aRXs761e3eiV7B4+fZdWDSjX8GDB64lfLhvXKd0ETe2q9dx5LYXA0u2HNbwZc1RFVuluRm0U8ihSR8tWxp10MypWdvsPPdza9krR8+2fRLwbd0gV+/2TfE1Usa/iUusXRx5Q8rJmTPs3Rz6wOBHh0e3vu74dei5tVt/3h359KHVwSfPXr74afTMv6/fLV4oefe+z8/Xvdw+8fb5ZcMPKp+/2eoLsDXuCLxtvwNL8w8oABVEbcAHSVNPwtYSrFAzBn9yEMPNIuzwMgNBJO3CER3TUCcOTYzswxUbw8/FzUqMcTD/FHNSkUbCWsxRMAp5jGzGH/GyESccheRrxyPvElFJwoJssi0ibzISSreSrDItGLH068ktxZLSJiq9HOvKMcNi0sy3ukyTs5cWi43Nt8qMEyof6UxrzTuTAjMmMfUUrac/JzNKULTyLDQoPlnyE9Gh5mw0KDQhherQSXFSdCVGLdXp0U1xstNTpSoNdSVMVdKU1Jg6TXUlSVlVjSS2Xj3K1JRQnRWlVXENSctdgRrV145qRenWYD3S1ViOQE3WJmCZBc5Nz7B6NidkqZ3I1WtRclbbh4Y9qdhuI7JWXId6LfckbtFV6NuQwl2XIXLhTSjbeTVS196C2gXp3XwPktdf/4KWDZgifAne96N+CR4I4IXPXXgigwNG2COFIW6Y4HohdkhifynuyOKFMQ544I0f6jjfjzkKmeCR/dXY5IVQtlfljVgO2OV8H46Z41h5nqhmjW72N2d7S/5ZoZnnDbqiofMtel6YkTZIaXiZpshpe6GGd+epE6p63asnynrerdeV2uvCfE67IbElIhtes9E9mm2CwEbX7YjgXlfucruu2+61AU8ob5ngHPzfQBGnl9DFD7q73MIf2hvdvsWle3DIxZXcIcrLtbxbtNnWvFvOG/JcXNC1/Rtx0rU1nSHUu1X9WswBd/1a2BeSXVvaqRU9bdyp1V0h3q/1/VnWMxfccf+CiE/IeGqRZxZ4r4V/9nmEon92+mRtr/t6ZrM/aHtmuzdW+duZb16g8Q0qP9nzg61+6vCTdb8g+I2V39fvR1+fffgjiP6Cxb9d0Q9p9jOWAAdCQF8ZEFfpAx8Am8dAgThwVxCclf+CR0HHWXAdGMSVBl+FwJ8pMFggFOGsSMgqCf6vKexzXrRgMy0ZMkxxNxSICXmGQl+p8HAybGGqOGg9Dy4OiDbU4RBJ9cIOxlCHSazLDZkYKh7GzIe7kqIOBVJFTxWxfkdE3Ba56MVNXdFkWcQVGZeYQx060YhQvCEbqejGG4IxgWIcHB2FaEcZonFjapwVH9lnRkvBMYxylCH/IZtnyEkBEmKCfBUjHedISOHxhHoEHCUXZ8lGITKPigwgDYUTxEL6kX2QXJgkWcVJxHkSUZjsoSbr5srBwbJQqiQYK1NlS8DhUlCgzKQoK0hK6piykahsniyxSEu2+bJuwPyTLgPGS1JBk23S1JMwZ0nMDxpzPMispDIdR01/WTNU2EybNu/EzDQ6M23q9Bo76cTNZnoTieCMjzg7Sc7FmTNf6PSUPKdGzzi5M5Dw9BpBkWZQNgHUXgLdFEN/5tA02fOd+ByjPv/Dz1f6E3EIjaRCp0ZRnlnUTBCdl0QtZdKYoXRMGE2oRvfI0QZ59JYgHZxK4cXSSbnUZDD1kkhX/0lSpAF1Y0LdkkxHStNN2nRDOP2lTgHH03X5FFJIvRhV60bUXRr1Z1oVGVfZZlV0YbVRYm0ZWdPG1KI6tZZQTZFUo8lWr3m1mmDlmVpxZtepmbVcaEUUX4nmV6S59atwfaZcb0TXbBr2Z4AVl2ALRdinQZZneD2nXmNmWa1hNmaIzati48nYIjl2naA1mWS7RVlBebZsqt2YZgPKWZPBNm6yhRhrteXaP+GWb7p1WON06Fs9Abdyws3YI8zCxXUY907I/ZxySUbcG0KXThYUhyuWoIRMfEOH5fgFE5QQiGwsMRphUEIYoiGr5qkjG4FQAhN+UQ4dbiMTSliCK8RxFP9pxAEGKigAAzIAgzL8onnfmIQMYFCAAkhABkXIhXsBJw5OBEEGDWBAA2AQhE70t5O5KEIMJMAABsBABpTYRvOeUYYYZMDEKohBHKQBlHRYQgYrkAAEeAwBCagABnOw7+ByIYMWYKDHPv4ADMQA3sFFIwguQHKSMdDhaCBuG2OAwQck8IAH8BgDLZBBLhBXDjlsecc9rsAKZGAJCrMkHQCugATU8IlVtAIUbdCABFwwBhCzjRMwQHIUFHEKWYjCDzSAgAqCoA3A+UIGH4CADwhRClmcYhBIeMAHZOALwGkjCC2AAA38IApZoGIRUYBAlTlR4TG4QAIaaAMoZLEKR4D/Yc4wkMObVWIJGEAgCbZARjKITWxieCECuuZ1zHQBAwnQgBXFLjYyArFoIvx5ateQQQY0AIphSxsZjtAABmRwDbaJowiSDsS3pb0KGkgABrpgmzrk0IIHfGEY0ia2LZAAARhY4ibQcLYT2K3vZKjB3/L2mjiAgIEZBMPgxEaGIiDQAoDPcwwquMAqklHwYq9izWNY9sYsIWpFRJzYwaABBoCA7Z81GwJrQHnHoQBvaNikDB/QADBm3nEaZCAII1+YJkR9ip4nQwsVgMGKp9aLXw/i6ISIQAx64bVtxKACWjh6KR7QAk3MMwgfoIExeg4MDaigDDHZhgwk0IajIwMR/xCQwc0bGgQMIOHoyViFA2DgCa/JQeMeNzgyLqCCOXjNE7+O9tGRAHShB0zgEUBE3tsggRgwXSUwL0Xea7HoSpAD9KEX/ehJX3rTnx71qVf96lnfete/Hvaxdz0zWhCBQOQ9GSL4ABlk33vf/x74wRf+8GEfjiNnAfdZCHM4iN985z8f+tH/PRkyMAPBGzwQEmgBM6Tffe9/H/zCr4QKHmCLvJfC37xgSSdEbf68VwACJCDJ/Olff/vfH//51//++d9///8fAANQAAcwAK0gAB7gE3APCSoAAQjQAR8QAiNQAieQAgUQDwBAAvQA9/RAAgAADyoQBENQBEeQBCEQAf8kAAmuT98cAQICYAtKEAZjUAZncAJJ4AEuAPdsoeI6gSU4QdSEAfc0AAI4gAaL0AiPEAkfwQAhABRwzwkkwACSUAqnkAoj0A4AoAL4APf4IAIAwA6qEAzDUAzxLwAqwAlwDxRasArGkA3bkAo5IAI0APeCoeJabSVwQdQ47uiIYdXQYBn+EBADURAHkRAL0RAPERETUREXkREb0REfERIb0RTgb/Ly7gYwAAciURM3kRM70RM/ERQfURkkoALAAPdwTQKUIRRXkRVb0RVfkRNxAANuAPfirgJSARZzURd3kRc/8QwyAALI7uhWwd/IbCWkgcSg7ujSEAbUD2nKIQb/MEDrjg4YKu4SvGYMxA73aOADxsBrLmEFIIDnjk4LyG3IfoYXYOABmvDoBsHfrmwl1CEIMsAGVLDYoIDcXC5m5GAFKsD9UI7apo7ukCbxIIAUji4U/M3vpkbgIOD2eq4WKsDwFi4ao+DtbuADgkAdYiIXfu0hUY4FvS5tpIHtLHLmWqHw0m7hGq4GiGHmiKEGWE4fTUYdykAFKqAVei4KKkAGauwbRc0Req7aYMAYWcIcxiAcCeH6PuECPuDa2IYSXCACwOD6VkEEyM3c0iYXSAwJxlHfgAEJLK8op4YkMWAE9FDfkAEMIMAFKOHciOADKoAd05IQIGAFxuAcbuIb/4IgHJMgFNjtFLQAAj4ACLIybcyhDKSyBhjBJYlNFtrgAqpM4aDS2UBgEGqh2GphEEAA3tyybnQhGiugDWTh24ZhEWwgAlygDMyhbq4BCCRNC07h25AhFJLALoMAHHJiG8RAyiLAAkaABi7Ax1wgCHyybsoBwCQNAmbgBoRQAtjMGaPpEraMAhwgBGwgBHjsA2JAEx7PZHghxyggAi7ABkQgAiCgwOTgHNlGGqIM/i6ABmigOjHABcQA83BiHDiBwVbgAz5gBWAgBixhJucpF4IABvjTP11gxhxtcZ5BDGCgBfpTBcRMDJ7BcbIhDmTABfhTBVYgBoJgwhYHHCwhBq0CrD9Z4AVkgBMG1CbEgRcmIQ7MYBJy4T4XR7wsIQ7KgA464bwKKRo0YQ7KQA40ob1kKBs6gQ7KIA4sob5kaBtygQ7MIA4mgRdY1LmuFEuzVEu3lEu71Eu/FEzDVEzHlEzL1EzPFE3TVE3XlE3b1E3fFE7jVE7nlE7r1E7vFE/zVE/3lE/71E//FFADVVAHlVAL1VAPFVETVVEXlVEb1VEfFVIjVVInlVIr1ToCAgA7" style="margin-top:1rem;" /></div></details></div></div>
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlh4AHgAff4ADI2PjU5Pzc7QDY8Rjg7QTo9Qjw/Qzo+RTw/RDtART5BRT5DSDpDUDpEUj1GUj1GVDpHWj1HWj1IWT9LXD1MY0BDRkJER0BDSUFESkVHSUJGTUZIS0NIT0ZJTUlLTUpMT0VKUUdNVUtNUU5PUkhOVkBLW0lPWE5QUktRWkxSW0xTXE5VX1FSVVJVV1VXWVZYWldaXVhZW1pbXVtcXkJQZk9WYEVWb1BXYVBYYlJaZFRbZlRcZ1peY11fYFVdaUtbc0pcd0pceF5gY1dgbFliblpjcVtkcl1mc15ndV9odmFiY2FjZGNkZmJlaWZnaWlqa2tsbWxtbm1ucWtvdmBqeGJtemNtfGRvfmZwf3Bxc3NzdXN0dnV2d3Z3eHN3fHd4eXV4fXl5enp7fHt8fX1+f1Flg1dngF9wi1lvkGZxgGhygml0g2x3h2RziWZ0im56ind9hH9/gHl+hnJ+jm5+lmF4nGh7mXN/kXB/l2V9on6BhHSAknWClHiFlnmGmHuImn2KnX+Mn2eApmuDpm6GqnGGpn2LoHqLpXeNr4CAgYCChYOEhIaHh4eHiIOHjYeIiISIjomJioqLjIuMjo2NjoaMlo+PkIONnoSPno+QkIWQn5KSk5CTlpOUlJWWlpGUmJKXnpqamp2enoGOoYKQo4ORpIWTpoaUp4eVqYmXq4qZro2brpWdp56foJOcqZSdqpGdroKVsoSWso2bsY6dsomdupCftJGhtpOiuJSjuZWkupOjvJenvpqnu5movp+rvqGhoaOjpKampqOlqqenqKmpqa2traOosaKqtKGrurGxsbKytLa2trS3vLq6ur29vZipw5uswpysw5urxJ6uxp+wx6GyyqWzyKO0zKi2yam3za+6yqy6zrG5xLnE1bzH2MLCwsXFxcXGyMnJyc7OzsDI1cXP3cbQ3sjR3tLS0tXV1dnZ2d7e3srT4NTb5eHh4ebm5urq6u3t7eXp8PHx8fX19fb3+vr6+v///////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAA4AHgAQAI/wDxCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtWa9VlFexBHX1eE9YllciHFW1qGyLi66KGvb0JkYF1mI3aO7UFycF1GA1aMIT0YINXOMKNjEFyE9JxyuzEmyIFHjg/W0YKgypwoGLYMvF4yzIMmcKxyc0BNdcJMCI3PUhJgBb2KUHdSw6Va14BnrgYlURNONDZcGYr8FegrBizivEJ6S4yOGARdxaSriSH+mQBVxajuiSP8kh6A5cWxqlCR/p2DVeWx3TiSvZyHQ+1EWQrM+cef9KgXvJLfEGu/xYgA5ERFDwnvYlBKALLVEKOGEFFZo4YUYZqjhhhxq6IYC1rxHiwCHdGjiiSimqKKEeAggzXvRCIDHijTWaOOJhwhAC4MKuHHjj0AGKUsApTBIAnIQKcMBg4EgcI02UEYp5ZRUVmnllVhmqeWWWQYCon8G9MLlmGSWaeaZUa5igHnOGbAKmnDGKSeZvRjg3XnWHHDJnHz26ec1Btj3HghzQbSOAra8l4R4v8VjwSjvrRFDcvd40N95d3hgT3IyqHGfBfEkF0USIiqwjkSLoGAdNtbcYUE60oX/wsGOuo2iADjSKYMBKsShgkGhv4GjAKS60cJBK9KlowAfIRZnwiIT0UOaDkaQ0AFb0t0jiQU4GKGCBUjGqkANRtSgQCjSCUSdCkbcYEEke0nHTAcmGKGDAnGsRhE4cJRATIDpCjQOJBK0wk7AAqnDSQScqIMwPuy0EoEj4zwMDzESwEHWRegQ8vBA7giy6cfzCDLPx/jYI4g7KONDCDoZmeMxyiGP/HDJJ3+sMssov5xRxy3XjDLOKO/css8YyRy0yEObXPTKR8OMEdA0M02y0zpD3bPUFyldtc0IE501zx8jzfHMHwt9dc4PG711zGg/rPbNWLetddlcW0R12lbT/802wm7jDffSYAcstt1kP2y23nEjPHfYdQN+t+J5V+Q134Wne7jkiSO8eEV7y9035H8HHDjlg3/ddOnpnu555RSF7vjohkdu+uSvp4756k93HvDnsTce8OO1sy6d67/DPtHlomcu3ea3+54u8BPJPjztmtveOu7J694872NH/bPw6RKfvfHJIT+98hIxP7vzyUG/vfTSUS+R9eVj/7z2x3O/vvfvAx/ixDc18knHfPtD32/UVz/2RcR914Pfb+TXP/olx34Rwd8B9Rc//qXPfw0EYAQFyDkCno1wJIyeCS0CwfxJkDUU/KAFf4NBiGgwOQjsoAJZw8ALOhAiLdzgC/9FE8MFgtCH40Ph2nq3QssZEIccnKAHjThD1tTwITf8TQ6luEPR9JCGP3xIEKE4xMsUkYdHBGMSVbfE8L0taU/UYhRhOEU0VlE0V3RIFlmzRTp28TJftGIYHTJGOZaxMWf0YhoFucbdtXGAb+xaHPk4RyLWUZF3vEweG7JH0fTRkn9sTCDxOMiGFJKSh+RLIgG5SFI28nuPLGEkWThJT1bSjJdkZSYbs0mGdPIyn8RlKPkySk2WkiGntGUq6bJKUbbSmK8MYCxVOEsnKtFvTKxm8K5JumwKDo7cLJ43UVfAcJ5vnLkDJxux6cZvnnCd3WwnOSVpzgSis3vlhKc45Zn/Tnrq85z8xOc7HclOSLqTlvXU4T3/l0+CxtOg80ToP+0ZUIYOFJYFleVBrTlRhVY0hA3F6EM1GlGOOnSfEO0n4xLKxYWC1J8nBWhKBbrSjrb0o0hUZ0wpOlOL1nSnHu3pSyUK1JsKNacXlWZGqblRiiQTmLdEZC6duUu+9HIhv2xMMKU6TLoUk5fHXMhTtRpVVU6VmM8EazRHOM35NdGptYTqMtvSTLRWlS5XVUhW+bJVs3a1LV+1algVMla+lpWZZ/VqWgW7Vhem0K3aXF5cyTrXstRVsXdtS14Tsle69BWxfy1LYPE62IQU1rOHpWtiAbtY0jZWiI+t4Fsly1I//7oUqT8VKUpJqlKT6lamvKUp6CZr2Mp25bKszWxZNouQ07bls6oNbVdGq9nSIqSzz02tZVcr2tZWV4SObatsI3s/4qLWuFxBbneV2xXmHsS5ZYHudqXLFeou17oHwW58tXtc7k7Xu/cFL2zFK8PZlre2oLytGnX6W54G16fDRbAwFcxIBit1pEwt6TZtalucLhimDQ7qg4caYQ4n2MMVrsg9lDGFB3jiVAh7BhgaIAkEIUwciWiAIjYWMHJIogFg8A3C1uGJBkxBGfGSiDygoAEjXAEH4EpXPb6AASJcwQcKiE62FqGAIahhCBZYRJJ/4wkF+OAKRFhAGPTzG2Jw6/8KRtBAFOQxkTCsYDi68VLFkmOJEOiCOKq4ADOkQwwN0AobtOhAMOSFgVQQRxchsIR0xjEs4kSjBmGQSDoMsCriWMEJyYGHAnh1nje0YD4Z+MN7/pAB9FKlBW94DyoUUJvfOMEK78GFARwGEWOEgEGlWNM0hk3sYhv72MhOtrKXzexmO5vZfFAAg2hBgFk8+9rYzra2tz1sagRiTTASwCi4Te5ym/va0ZgFAQ5NnGWd+93wjjcvCECs84DAGBHxNYNGIQBcQOPf0YBGwAcu8IIT/OAGTzjCF67whjP84Q6P+MPp8KXzUDsVAJe4xiHO8Y17vOMgb7ghBIBnSwvAEBn/D7nKP87ylbu84apY93usYQA6tPzmL885zj++CwEU6T0hwDdENt1p3Xw61KN+j6lRrerz/AEDbL4MC2J9HlRYoNasufV7cmEAWEXkCzUoeSkUsOffUMIEbFrFAgadHGBoYFXWwAUHgMFo9+hGFyighHTEoYCfY+PSmZZIPJ7QZDXca9HSqQcXMGAENWCZMVtWABHUQAQFiDldrvGBGoyAAS5EXTTBsIAO4KyBJ9B5IiueggM2weuAOcMLDKjxw8ChBwboAVcI83EDvICtgKljEw448pirZ97sulor6v0ve7niXoPotyvy7S99t2Lf9uLX+cXf7/Gzkvz6Atj6AiZj/2wLTN4MZh/6/E2vf72//K00vyDwRf/2sdJ96n+f+dcvyPO5En31T18r1Yd/4WdI40dFBmZ+EsZVFOZKFsZWSwVZTUV8CehXCwhNDRheDzheEXhgJjZhKMaAIHZhu5VhvbVhRdVhR/VhRBViRjViuFViJ3hiKZhiKyiCwEWCwmWCLIiCLqiCvmWDDoaDEKaDQChiQkhicDWBoFWBahVSRdiCR/iCSdiBCviBFphUDohhEKhhtEWFFGiFTYiFGKiFGsiF7XN+/Jd+W1F/AHh/7pd/BLF/W9F/a7h+9td+WvF+BBF/aTh/V8GGWRGAb/ha4kdgBlh+QISGc6iGyGeHbf+Ih1mhhwMhh1pBh434f4HohnkIhwPBh4voh1YBiFghiJtIiARoiHZ0gImohNHFhIzlhFk4gltYgl0Ygx44gyCYW0/Ig1Hog1Noi1WIi1eoi7F4g7OYg7W4gzLYgzQIg8p4i8yYiz9YjEF4jEMogV64hGD4iiFIjUZojUiIjcD4hcIYhjXojVAIjlIojs8YjNE4jNM4hrJYhrTIgeOojeXIjecoj8ZIj8hoj+1Iju9ojvE4YBlIfhuIgNnYitvoWhdokGSIkGaokPfIkPnokN3Ij9Xoj9cIkLu4jL3YjL8YkPg4kProjB8JjSEpjSOZku64kvBIhOjIi+roi8nokgL/CZMEKZMa+Y0cGY5nyIrz5YoYSYw9mY4/uY5BuZBD2ZDfBYtHSZNJaZNLWZFNeZFPKYYQOY8SWY8PpIiVyIjc54iZCIlYIYkCQYlZYYljiYmjqImRyIkC4YlhCYpVIYpXQYpxaYqoVICpiIhiBJZrKZb0R5ZvaZZXgZb4oJZYwZaF6ZZ5CZdnKZf4QJeDaZdUgZdWoZeTyZfK5JeYpIqBKZTSR5RZaZRb2Y9d+Y9fSZr+Z5oBBpWpuZGr2ZGtyZSl6ZSxqZWFeJCHmJCriJuvqZvgJ5u9GZG/OZHBaZW5iZW7iZrHyZXJ6ZXLSZIWaZJFiZIzCZI1KZI3uZ0q2Z0s/8mOOFmSOnmSLQmeLymeMUme6pmT7LmT3xmV3DmV3umR72me8Yme8zmbPlmbQEmR1nmV2HmaBRmdqjmdrGlDgtmYhPmHhhmZiGkVimmZDoqZU6GZVcGZiUmZjHkVjgmhkLmZktmhGCEOcDABxYB16UIOkAABBvMw6/AJEPAJMBYwEQMBkGBjAXMxE6AxFVEPcaAAOjAEIeABvfcb90AJCrACRYACGBAuyREK40IE5oIs6UIdKUAEN6AAkzB8ouEMHkACRHAvcfB5DfEIIdBpd6AArccardABd4INgWABPMYaumIKxGEKvyIdwiIo2DALHYClv5EOFnApxRECkSARh/8yC4rCKKzhKH7HKmogA5RiKe+RKWDKF53yHoGAAaHyG1GABKVyo26xJJ5qANjADazaqq76qrAaq7I6q7Raq7Z6q7X6bc0CaAbwC7j6q8AarMI6rK2qJr5QIAYAC8S6rMzarMD6C3YycwegCc5ardZ6rdmAAPVGHBwALA5BDCgAbAIQC0FSruaaIm2QALtaLCRyru76rhiCBwHwIucRDQEwI/Car/maI4mCJwrQBvoasO4aC0RiJFLaEORgAMd6HmugHr/BHuwGHyKQHPRQaedRp2hKFyKwB6UCMKwhBARyHrygADxqFlHgA7tKCwqQpKIRB2H3aMchHZ0QAguLDb7/EAKdQGgakAuWVgPakRzOoACHVg0+AAWbuhDwMAMhsAZ0gAQKkAnpIg9M0AFXcAdVsABxcLRelQUaYAV3YAUYkAUZSxf3MKRVcAdqwAFMcHp8ZgFGQAdrQAIywKIQUQ+iMAMHEAe4ly5n0QQDwAUsmxzGIAUDIAXeKi9cMABNoBcIEw5kcAA80Ar6op30GZ72OZ74WbnrebmaZA6eKVegqUuiSUgNCqIPGooRSqITWhWE4LnGeYq++ZfAOZrCWYcjuqElSqGuy5uwi5yyq5y0y5zD6ZzttbvQ2bvS+bvUGbwD2pwFulzGS7n+iZQAqpS3Kby2C5vF+7mUFbpUNbqm/1S6VhGiqHu7VMGhusu9xeW9dgW+yCS+VUG+d5m6uLu6VNG66nte7ItZ7itW8EsV8puZ9Hu+ucu60cuT0yuV1UuV19u8w/u82/u6fYmKoQmYpOua2UuczHfA7qm58Mm58lmVDpzBxLvB+Wt8+5tc/UtY/zsVAZyhAzwV6GvAJ6x9KbxeK2xaLSwVLywVGkrA9jsV+CvBn0nBomvB4YvBl6i9JkzEoGvE34vE76vEbcnE7sfBmZvA9bnA99nA5Xmd54lXWCygX0ygYWyg6enB+gnCVjXGDErFj2nFpfiQCEqbCjo9boxFOxwVPRwVPyzDBXy/lGmhpouhPhzDUjHD9/+bx3q0x1DRx1Dxx4kcyEI8yI78FJD8FJIcFYosxIzMSZfsFJnsFJsMFZ0sFRUayk0xyk1Ryk9xylExxLw7wbFbwbN7wbW7xBp8xTUsfzesfDncXKrMFKzMFK7sFLAMFbJ8vLTsu7YMvLiMvbpcwrzsxN0Lxe0rxf4LxyIqx5H4yb40zEtRzEtxzE2RzE+Rytxcvt58luCMVeKsFOSsFObMFOjsFOqcy1W8y3n4znoVz0kxz0lRz0txz02Rz9K8z9Tcz73ch7/MfsH8XgCNFAKNFAStFAbNFMssvXX8n3ccoNVZxs57xtDb0J/40HcY0QZByON7uvNrvoAcxKjsz5z/NdFHUdFHcdFJkdFLgdAjPM0Q3MSzXMS1fMS3nMT6HMf8/M0mXZco/YgqDX82bRQ4bRQ6jRQ8rRQbjcAdTb0fbb0hnZ9gvJ9i3NSX+dRlGdV7ONVFUdVFcdVHkdVJsdUdrMWWy8WY68VibcZkrVk0fV1sTRRuTRRwbRRyjRQ+LdIPTNIRPNRPXNRRfNRTnNTdvNTubNYXitaHqdadGNhDMdhDUdhFcdhHQddZ3NUK/NUMHNZqPNZsXNbWvL7YzL/azMLr/NLtnJh/nV+eLRSgLRSiTRSkbRSJvdcj3dclHdv6O9sqXNs6fNsCDNOTLNOxvNvYB90wLN2cTMmobMnY/33I2m3K3F3dmF3Imi2hnD2XvR0Uvx0UwT0Uw10Upk3Gxr3YyF2cGWnXm4vXnVveLW3IfozI203dyuzdlM3Olq3b/h2/Lh3duU2hBp7QSr3QTK3cKMzcOOzcwvzdAR7erzzeymzd+rfeQNHeQPHeQhHfRIGW61AJNPAMk5su7AAKFKAModqjw0ABw0C3yREPy0ABoHAwCEMPzkADlWCqEXEPrkECK7AALVB2bWcBIIADGiACQpYrG8ABOMABHSB02yECWs4BGAAMWksX48ACF3ADJLAYZZ4QngACjkapGSDkbaYBfjcHCuB1v/EMFvAHzfIHtyId5GABc0AcpaABXv/OGuyQAWrQLKnAAegSEexBarphDUTQBckhD6n2HlWwBJQiAlRX6W9wAm3OFUtQBe/RBxvAtqLBBUQgawASEcyAqhdrAd7wDbie67q+67ze677+68Ae7MI+7MHuCgdQDbJmANtA7Mze7M7+7NCe68lgAH92HrpgAMkQ7dq+7dze7NtgAJSuG9VwAK7Q7eZ+7ujuDfWxrtjAAWz3EOAKbABQCIhQ7/Z+7/ie7/q+7/ze7/7+7wDv72awAOxuCwJgBwGf8Aq/8Azf8PZ+BgGQG+dBDQFwBg5/8Rif8QpvBwBQdLqxAGag8SI/8iRfCAX7HkcSEZRWcrrxBjOQHOygAB7/3wcdUOpaUbF6eh6lYAGs3hiV0ge5ZgB0LhoyEOq6IQ1kFxH2oARGYO0YkOiikQU6gOy6EQ2QLh2pIvHYQA0qAC1TygElZw06kAXSYQwaUO26YQRKYPMFsQ4ncAN3EAhrgAFjkC7w8AIoMAeBwAYcEAVsf/NKAAJvEAhvEAJKEOOicQ9RoAGDPwco4AI87vOksQaBcAc4cAJI/hDx8AgiAABOcLi/QQ+ZwAIAIATB8PfUFwowAAAyEApjyxf3EAxCAAAssAmI/xvK4AQAIAKRcOOxMwhBkwcAHsl54OHInAcE/hSDIOJxSOI/YeI/geJBoeJDoZgf+t/nrbrpvZjO/+8T0O8T0g8U1C8U1t/9PfH9PRH+PzH+QVH+HB7JAi7eyY/PHmr+PIH+PKH+PsH+QOH+Bw4Q+AQOJFjQ4EGECRUuZHhwnqB5DSVOpFjRYkV7gtxd5NjR40eDhNCBxIeOEEmUKVUWdCfI3kqYMTk+jCjT5k2FGTfi5NlToEiSJn0OvdnyJVGkKmkmZUpSZ1OoHoGCFBrVakWjV7U2XLrVK8KnX8UWnPqx6li0WdGO7br2a1i3X8t6PBt3q1q7WtvmtQqXr9W5Hev+hYqXcNO9h5P6VZw0MMfBjYkaljw0ceWejDH3fHwx8maclEHfvDxapmbTMjtb/JwapmjXK0vHTv+JmnbK1RVb3yYJmzfI2b892hYudSTVk8VV+lZ+MXhzjBqho8xNcfd0isyxS3y+nSFx7w2rT7wefqF28wm7pz8Inj3C8RLLvzeInj7B9fcFutc/MH7D+frDx77+8tOPPwH/YyjA/gjUz8D7EOxPwYUY1M/B+yCkT0L9KFTIwvswpE/D9zi8z8OEQKRPxPdIZM9E+lBESMX3WGTPxfRgfE/Gg2hkz8b0cDRPR/Z4NMjH9IA0T8jwiEzPyIKQNE/J8Jj0zknzoCRIyvCo9M7K7bAMT8uBuPTOy+3AxE5M78gUyMzt0MROzenY3M7NkpITUCE5p6MTOjuxwxNO7PqE7s//5gKdblA990TI0OYQVU5R6Bh1lE+XLkVI0uIobc5STQ+CVDlOhfNUOVBDZSlTVfGDqFWCTi0uVVgHZLXWUn+TVThaYR21uFx52/W3Xlv9VbhgbxuWt2JVPfa3ZGlb9rZmQ32Wt2hjm5a2ajW99rZsXds2tm4v/Za2cFMb17VyHT03tnRNWze1dvd817V4R5vXtHoFvDe1fEHbd7R+G7wV1oA3Gxi0gi88uNWEMVt4s4ZDfFjViCubGLOKV7w41Iwl27iyjmv8WNOQGxtZspJ/PPnSlBVbubGWk3zZ0ZgPm1mxmqe8ec+cCdv5sJ67/FnAoP8amrCizzy6wFdrxWfp/7+ajvPpB6OulWq+rC4U6wy1hpXrvLye7l/TkuaLbLvMhg7t0dTOi+243G4ObtDktotut+xWDu/N9I6L77X8Lg5wzAR3i3C0DBcO8coUX4vxsRz/DXLJJEeLcrEs5w3zxjQfi3O5jjOrUV/BHlHsVkn3yvPbQFdMdLFc3wp22mQ/jPa3pJMaH9xj050w3r2yXavgXRv+r+K3Ov6q5FNbnq/mtXoeMNPpQt1Y1VtkXdXro4retOnzqv6q8KEaf7Ty7Tq/L9+lXh+09uN6P6r0m5p/s/rduh+q/DFlf5jp31r+15QAOiZ7gtmes7p3o++FKoFIGWBlCoiWAzJlgkSpoP9kLsiWCGpqg0PpYGM+KJYMLiZ+tSqhYk74lRQiZYQ+aeFhXuiVGBJlhpxZIGQaaK0HBimEl9ohT2pImBtuJYdDKSJOjviXJOpliI5q4k2eyJcoXmWJPqmiTa6YlyxaZYuZWSGsvmiXMEZljDzpomp66JkfeiuIS5rintoYkzPGJY1QWSNO7giTPLplj4ipo4D+uJJArmWQTOnjTQ6pkkSmZY5VKmR/HombN7Imjuaa5JcqeaAytiqSY1lkUhppk0tSJ5O62aS7OpmmT0YolKoapVhKiZRTnmaWoXJTPFjxA3Lco1byOIYNxFGPWtGjGTZoBj1qVQ9x2OAY8qjVPcj/8QNWxMMjxMDAAjhgACGso1XM8IACOKCAF5CjVeBgAQJCgAAWgKNV5IiBAc7pAWa0ah1LsOcCMEAMjnATENjARjSM4AFtasoZFriDNbBBjStkQJyaGocF3uDQarxBAerU1DoycAVqEPQOGHBGqODhASNEAxvWCMQ/LQIPCwSCoDPVQRw0RQ8P0GGmBDVCFELlgivsFBtXiEGoomAEoc7BA8i8VBx04NCZBsIC8KiIMzQA1Zn+AQPo4GpXvfpVsIZVrGMla1nNelazHsMA1RCqKRRQDrTGVa5zpWtdu9oNA+RCqLgwQDfs+lfABlau5TAAKoRKDQMgQ7CLZWxj0YGB/z8I1RoaKClFgJECoWLDFAGogyA8+1nQhla0oyVtaU17WtSm9rRAWEBmcREANKhWtrOlbW1t+9kyBCCkO6VGAMpwW+AGV7izRUMAcCHZBQRhuMtlLnMHUQcAmCKzKAhGRcShALbudA4v6KgCdCHUQGxAmI6ShwJUIdRUKICajrpHBga6U10oYKKOcsEchFoNBYijIvV4QVBnGg0OtEJT93BCEXZaDRJQIlRfwAFWrYGDMISKEiTILkGJ4ITxOqoVHFDpTInKVIqQIwNDGIUq7sCBKGTYUewQAQ4CsYo+kKAHIHZUPFqQAkCo4g81aEFCL0WPHoSgD6oIhA48wI5Q3YIjChzYgypGQYQMcNQi7OBCBizAglao+FLxiMMGLCCCTdD4x4vwgAU8wAhnqqoemziBATYQBx8PuBUsUEAGtPCOj9QjzrC6B1V/h494aLlVgf7dPeJxlD8nWtGLZnSjHf1oSEda0pOmdKUtfWlMZ1rTm+Z0pz39aVCHWtSjJnWpoRMQADs=" style="margin-top:1rem;" /></div></details></div></div>
+<div style="max-height:600px;overflow-y:auto;"><div><details><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhwAO/A/frAB8mMSIpMyIpNSQrNSYsNikvNyMrOCMsOSQtOyYvPSkvOCYwPiswOC4zOi80OzA0OzE2PTM4PjU5Py83QzM4QDY6QTI5RTY8RDo9Qjw/Qzk+Rz0/RDA8TjI+UT1AQz5BRTtBSTxCSz1DTD5FTjNAUzVCVTlHXDtJXjxKYD1MY0FDRkJER0RFR0VGSEdISUpKS0tLTEtMTExNTUFHUUJJUkNKVERLVUVMVklOVkZOWEJNXkhPWkhQWk5SWEtSXUxUX1FRUVVVVVFUW1JWXVpaWl1dXUVPYEVRYk5WYU9YY0FRakNUbUVWb05bb1FaZlpdYVNcaFVdalZfbEpbdkpcd0tdeExeek1ffF1gZVdgbVlibk5hfVljcFtkclxmc11mdF9odlhmfGFhYWVlZWRlaGpqam1tbWJpc2NqdG5ucGFreWJsemNtfGRvfmZwf21ye290fXJycnV1dXp6en19fVlvkFpwklxzlV50l191mGZxgGhzgml0g2t2hmx3h2JyimZ2jm56inl9gnF9jnN/kH6CiHyDjXWBknaDlHiFlnqHmXuImnyJm36Lnn+Mn2eApnaJp3mMqn6Ts4KCgoWFhYWHi4mJiY6Ojo2SmIuSnZGRkZKSlJaWlpmZmZ2dnYGOoYKQo4ORpISSpoaUp4aUqImXq4+ZqIqZrYybr5CaqYGWtY2bsI6dspCftJ2iqZqir5Ggtp+ms5OiuJSjuZWkupemvZiovqGhoaWlpamqqq6urq6zvLGxsbW1tbq6ur29vZqqwZyqwJuswpysw52txp+wx6Cwx6GyyqSzyqO0zKu3ybO/0r7CyLjB0b3G1cHBwcXFxcnJyc7OzsHL28TN3M/Q0s7V39LS0tDR1NXV1dnZ2d7e3tLZ4tTb5dbd5+Li4uXl5eDk6urq6u7u7uXp8PHx8fLz9vb29vb3+vj5+/r7/P///////////////////////////////////////////////////////////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAwAO/AwAI/wDXCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS55MubLly5gza97MubPnz6BDix5NurTp06hTq17NurXr17Bjy55N+2a6bM9+XTNXG6U2aL6kiet98ls0X9G+ETcpTpovaNqWlzR37dezbOlegrsEREYMGDGATP+KLt1juU5FZMiAoV4OtPIe0+kqAx58jDG8ssPnCE1O/e9FeFLOfhxpMwkQ38UQQxCXgMMSLjK0gIEEEEAQAQYtxKCJfgRa9EwQMHxAYYUVqADDHMN1aNE2YsCgwogQSGCiGNuoaJE4/qmAQYUxZgBDEM/YWFE6msAgIY8SZNCCDLeoZAkMOyYRSCOfDBJFBBLAIAdvQkakiwwZQHADH4yAgkgXF0jgghgOdglRNECsAIEIbCgCiiJriBDBCkBI4yZE4ojRggQXeIEIKIzwcQMEH8igy58PneOfBBFEMQgojQSCBAQYxGAJSp7AIIENqyRj6qmyIBEBDJRA2tAzMmD/AIIjp54qDBgQtFAGl64mtE0QKlAQCDK1IoNMIBF8EESNvSZkzhhygiFMrckg4wgIGMgQZLMJUSIqErOcSmwyq9yQpScmZQNDBTwQQ624UGT5C7cHlRNEBiDI8u6pfEAAAyf0HmTGChGEsq+poUCwghkBG8QJDBD4cXAysoCg7IAND/SLqFCM+y4xPFQQQzYlybFCBbRMnAwxIXwgBocNdwLDA6ConEwS2baZ8TOi8mHzHhJom7FA4MSKhMfvIgMKBC6gO7Q6RXwAgrsT01LBCnKQVLQEYNicTCASxODn0ERgcAPS+5biLy5Dr0PHyVRPTMzVk7SNC8SlqGxsDhgQ/9G2NDFEEIjXagStM0i9QCyK17Tkyok6kEcu+eSUV2755ZhnrvnmnHfu+eegh+65uhJIbDMyFsch+uqst+7667DHDvo5QGAQhdfJQIEBEObI7vvvwAcvfOtxqAAC7nyEjd3wzDfv/POvc9ICBCnbHMoDMPQykifT2+I1MhVAUMIj5Jdv/vnop6/++uy37/778Mcv//z01y//FgFA0AjuSEiQgP0ADKAAB0jAAhqQfngAQAXagLs2SAAAeTigBCdIwQpaUIAJkAAScNcICARgCxcMoQhHSMICkgACFcBd41rgtJBoYnrT8poGIMCBEtrwhjjM4SOokL+aec0JFQiADv+HSMQiDtAOCvSZ15IHADsY8YlQjKL6AiABJ+AuYQGwghS3yMUicgACGsDdMCLQAk2MBBcugIC+bFYMTkWBGHCMoxznSMc62vGOeMyjHvfIxz768Y+ADKQfG/EACCgCdzzAgAgEychGOvKRkIykJAEpCwdUQA24W4MEHFCLSXryk6AMpSgdOQIM8AB3iahQI0bJyla68pWRjMKO0LYvWTCNbSKBBsQS4TVS+CsXQxPHurpmM2JQYAWtGlrUcoC7G3ygCG2jBAsoELeJgaECMEhRw3IBMVJ4LZUweI9IzBEEDPjAa10I2+ECFocPaKCa+0KEv+Y1NOlBoFQqWwXTADb/tI1BABE2G4YGVBCHtn1DBhXowul8sLtzkKQTaVyEytTWgrq1bWMSWIPKagGCDLzMoLHyQTEmhgyGykA5QzuHGKRWC5WpYVXbGtokppe3iS3CATDoREnKQYQVUMCH71oFtoCA0rbFYXqD25ctdoDNmA5NZhHgwkg/xoVV6bRt63hGDNjlvaQFIlcFxeo3gIAvfL4LFBV4JsZIkg0gfCACYKieqWzBhwp0yqnBLIKcoHCKWhEDESHI0lWxmg45uCACN3CEx6x1g1XJAWZPXRcIEBE3ZJwCCg5gQRG0edEYYKACfABGrWihBkYBgWQniUYQWEAhGjjBCYuSwApk4Aus/xIEHGNwwY5EgIQohIxROVWHbQVSjjlAyQEXQAIUfjBDDJxorVhVRydi8AEU+gAKSBABBC7ggjGss22+kMEKKHSD19IgRi0IQjRU8o05REhESVqSGVA7XOJq4jvwxRAMxIBX26YjF0CAwQrSdIEP/AgXkLXtM8QQgxVMKK3s0QR0h5sNMxhpQhL4QIbmUFSVXIMTRThAAHqgifXW1yDfuIUZEBCAEEzCFw49MUHEwQs5UCAAE5iDLsYhY4Kc4xeTCEEADmCGW3S4x9G4RA8MYIAicIK+LvEG+abRY4Skg3zGqDJCVPEIVWj5IMUgn3C/TJBpkM8bM5HyI6hM5oFc+f8RWW7zQLjsZTkLxBjkS7CWzfwINMtEzWyW85vjbGc62/nOeT40n/0cE0AfetCHXgeXJRFpPD9Cz1VedJqn/GgsR1oSXa50ou2s6T9z2s6QPrShD21pTPe41I0+taA9repHUJrVo5YzrGHiaFTTutChxvWlFX3mTa+503D+dLDt3Gpi99nYgW5zqoF9a2bnus27fkmvZ53sWtfZ2sMmdbFNfWxfd9vOoP62nJst7meTO9pknracVw1uV8s421GWtbR/PW9bizrcuh53rMvNbULLOd3/tveJ8d2Sbe/73P1Wd5vZHXB3DxzeX5Z3myedcGczmtf6jje/N77sdV+bzAz/Z4nDRQ7xNiNc2Aqvb8pXsvKMj5zMHIe5x6GNbIOTXOJkpji2BQ5ygj/c52R+eb13/u6eR5reJgf40C1edIxrWeM497fO2/1xbYfc5i1PesknfvIvz1wlNb/6zb8MdbJLHeVE97rRWY50tmt96VznubnrruW2B73se457vucOdr5XWelRj/lwz56StFcZ63avduKZfnGne7vjeW/63pUN9C8LHe5Ul7vVH7/2vo/97283u+Ab/nW1hz3ymK941wc/+h5DXsuId7vibct4lDje9qWvst89D/hMr17lrSf9600ved1TvuqWB3bntfx51Yee9tE/+OmJn/rAX5/1hHe9/+F7nHO8y17vBX/69qlf/Fcfn+bJB/7yD7/+Klff+7MHf+1lfHvh17/H92d834d84ad84ydj5Td5mVd5m3douYd6u4dVvXcSv8d/wUd+/ydjAeh+Awh/BSh/B3hiCeh8Cwh9DSh9sTd1+UeA+3di/ddjD8h9Edg2E2gSFeiCF4iAd6eA56d56Xd5W9eDDPiD6JaBJ7aB9/Z+aBd/Fjh/GDh99td+SdiBS/iBTRiC9TWCEPh8opd9LmeE9YWEC6eEjceEOOiEOgiFACiFY0iFZWiFZ4iFw6WFMsiF2HeCEZeCoLeCHtiC9fWCMhaD7Nd9AsiHVeiHwwWIIriDJCiEJv9IhHkYhCqIfkfHeXpofYb4hojoXzm4iGqogWwoc2Toe2b4h52YhYy4hSXYhXj4hZ94hKG4eKNIgaWYiKc4h2A4XGIoim5IinBoimi4iM2nio7IipD4c5eIf5RId5YoiXu4jIWnfsNYh6t4h8eYda8YhrHIe7Nog7XIicFYX4IYhYTIgZnoi5tIWLdoW8M3iDM4NDVYEjcIjHLIjqlIjcVojZXogLloW7soi71Ii79oi+GIi9moi9sogd0oj9+ojgVpj9Pojnaof16IjclYiNAofs1ofpPog/tIbRdpjhlpgOp3kP6YkDS4kCQxjwRZj1g1jmtYjlN4jgKZjm2jiKj/aJJY9Y/cGJDeOJDg6JJtQ4cSWY0U2Ypip5Ntw5MK6ZMMCZQOKZRD047k+I4ZE48r2ZA3uY5YRZRVOZEsWJF2p5RDw5Qp6ZRZCZVb+ZAv2Y87iZLwqJIjwZJBKY0hOZMjCYIleZdtSJM/aZNDg5PDBZOgKJN9mZdXuJfOiImIGYd2uZjK6JHMyI9kmTFmGZdoOZdaGZhcOZRuuZRweZVyKRJ0GZWPyZHPKJnRCISoyZiqqZGUyZe86JdPCZgZI5gQKZsASZtpaZsNg5td+ZllGZoNg5WaqZacyZZtQ5iwaJiz2Zj0qJitGZlD+JH9FpFfaZRhiZRfxpza6Jy7CZ0t/ymdPNiR1TmZIAmZGPmaJMma5Zma57maRViZDXOZopmZpLmZt9mZU3mPRZmPR3mNY6mbPcmbx+mbAQOcyymclkmcAWOc+Ymc+6mc/UmfAWOfxTmaIVGaaymVGeOVMWmVGYqfG6qfv8mfGeOdCAmeBSqedemejWiej2idJIedIQqWfSiWpmeh9IKhD6qhIMGhyemhDaOiJ8miTWmgEYqg9KKg/WmjhSmiP0qiQWqiCYqiDUOVN6qdOcqduMeg9emg9AKhJSqhJ0qhHwqmFyqm3EKmVWqmV4qmWeqf2Qmg2ymgX8qj3OKjYwqkHyGkE0qkAaOlUYqjh6ij/gelzSmlff9KpX9qpU2KpYOqpj3Kps3ipo8Kp5EqpwFjpG+JpGeppGXKpNzipGmqqN/JqG3qpx4BqGcqqPRCqItqqJqIqDBIqXtqqb2Cqa0KqaUqqbGKq83Cp6vqqL2qqb/KqcGKqiuqqpfKqh3hqnEKq9ziqaAJqpgpqm9Kqs1iqnOqp8Oqq67Cq9Hqq90KrNwCooXKpYfqpf4Hrr1CrM9qrOWKrOeqrNUqrPEqrpBCrhwhrZtKrc2irrPKrrXqrk9IoEnqoqYZm+opkuyplzBKjDJqjDSadcx6pM66q9D6r+baK97aqfrqKvLKsfTqsfYKsug6sCMLKSU7rh27EQCbrALbKwT/m6q0io62moYKG6oM26Eb+Z6uGZ+wmZ7TuZ5E254o+LB4GbGJ6bBHC7FJK7FLG7VNO7VPa7RCS50zip7aB68ky69/4q8y+7GuErLBCrYuK7ZuQrYaMbP3WrOucrPNmrM1ubOe2LPZ+rNDGrQxCp9dK5/Xqbf3qa2Zyq0qi68sq7Z/8rL9GrNva7aQgrb5yrhu4rhjC7kZAbeJK7eQIqs4a7A6i7A6mLGfurEwe7Jlm7Jnu7K9Yq3Dia2Fy7eBSp5/O7SBW7SDy7SH6bSOObH4WLH66LWuSLgjarjHiritq7g2S6dbaqddiqfvarxTirz1qryT67quArsNKrvHS7uv/2q7FAu4Fku8GEu9jWq9KIu9f0K5zcK9Yeq91Qu+0yq+wUu+wyu4NYq+xaq+q8u+buK+zWu5XYK5bau5GMG5y+u5fwK/ayq/6Uu/AXuaW4u0uau0kWi1vYu1vzuf/Duv/hu5rJu9zDu3Ldu4bNslbru5ktu+2vu5zruu0Nuu0nurBCwkBqzCCHwRCkzCDOwmoFu3onu3pCuMH2yyIczCI+zCJQzDN2wjOSwkK5zALRzAL9zAJ3y5KSzFO2wRPczEP9wldKuxdvuXeJuTR5y6SUzFS2zFTYzFT6wiUWwjU8zDVdwlAmzCcdwhc6widezFdywkeQzDpnutqPu4qivCAP+Mx1fsJg5cqRDcvxJMs/b7n8IboBcLe7z7nL4bncBryfiLyebbnVlcwFtMx11cEV/sxmEsJGN8umVcm2dskGmMyGtsx23MyG/syKWMw6fsx6lMEausy61sI0FMxkNsxkWMioUcu4ecuYmsxIssyI3cJY+cq5EMwpMct5Vcp5fMEtyAB3jgDId2DnlgB7YQaZBwB5AQabZwB3gQY3LmDOLMDTCRDr1gMgAAABhgBrkwYSf2DAeyzw8gBp3AWTKWDZdABAMAAANABJcAZTIGDp0gBg+wz+LRX/VVDrlgBhiwzyogB73wzBERDS3yARMSARBGBLUlY9sQBzDAAhiWJDD/AASeQNLSUQ6UECGfJQESoAEsIAOUANA3eQvr8QEVoNIYYGBxcGS21QtEECJJLQFLvV8mhhK6QF0RoAFaoAd60AUhAAE+wk/DJQ1AME0UAAVtsAdqcF7ONQdE3TDfkFvh4wNrwAdr4AMotCbflTHFBSUPcANgoAdtAEQKEwRjM1wPEyYi4AVerQUz1CiPchIbgwEaQAho4wgikCW4hFXa4FYQoAfVZFk84C90MFzlIAZykgVyZSq0kAW5IgZxTS90ICo80Fd+pQemRR5YdTcVIAL7UyvFgAgX0Cn0pDW1ky8HYws34FzXQFiqTQGhQEvJYAxRkCXAhFXeAgHDsi/I/+AHTJNMbcNNEBAF1J0MobAnH9U21+BZNtBV71IxGQAEfe0RlJBGNXUwVrMwWKULEDMIKlMMzR0Es+0q1yADEpAFxjIxWlABMvDcQ2MvGUADU3Uwg+Avkz00A1MB4XIwyEBRnzIS5RArt2MzDhQDvN0wY6ACInDep+II/sILbWMJLRABrb0vK3QJbcMLEEMreiMCHzAGbaMNMSABDGQzsiQDBZ4R/hTc+YQ9TZIxByUBbHA64KMCpz00QaABG+Q1SKABQdA2dKACF1DhE8MGQePUzRIq9+Q1hAQDxw0StzA9N34wMWIEqpDner7nfN7nfv7ngB7ogj7ohF7ohn7oiP+e6Ip+6IDAABAgUV7jAxVgAYte6ZZ+6Zie6Zq+6YkeCQVA5biD5gQQCZxe6qZ+6qie6pduAeaEO4sAAQwACKo+67Re67au6UZAKbgzC0wT5S40PfB0MCBAQ11U7MZOQlQwABBgMD8URMf+7NAuQUgkAUpkM8kTAE4U7dq+7fVDRVBwRR5UBdw+7uTePl90PF4jDLliRiJxC2lU5/uCJTogCapA7/Ze7/h+7/qe7/y+7/7e7wD/7wIf8AQ/8AZf8Ah/8Aqf8Ay/8AIvCX/g6JBuM5JO6Q7f8Bh/8Rqf8Ry/8R7f8SDv8ZIgCZBAAKDuNZpEAJDw8Swf8i7f8jD/8jL/H/MDPwEVcE5e8+oM8Ac0P/M+3/NA//NCT/OSYAQREAG73usj4Qs97jX65AK+HjDbsFVHHuAXsAJz0Db30uU2gwQYEOZDMwdkbuYH40AywCwN4wlpZFYT00Ex0NIhIQ6xkgVeowcRMDJts1ItbjNLAwMyPjQ0TgEttVF7EuIZw+MQ4OMkBeRCPjTZgFB64DVScAFKThKUMD24rd8XoAIMM94wEAGEEOADjtD0AjgSoFAqk04xAOEZIw7ldANkTy0XDgPZreFkDu+ncgq5It4iAQ61EwId/i7CkAMik9i3KQbBsjjenQXYbVszBQEAbuG5YlGeDwFaEPumIgolst5D/yMNsZIDMRTfIrA79e0RiWPZh1QsoEADWRL1Q/PZb+UH8LQKPhABLjAHOE0bgSInXTD4pwIQtbpAWCFG3DqECRUuZNjQ4UOIESVOpFjR4kWMGTOmm9MiApJVyUSKJMYnwgcg2TSuZNnS5UuYMVl6giFhBqiRIpEp0oABhi+ZEnHF+PAgRBc+gcCMgJABhqagUaVOpVq1JbQgKyJciLIn0BoeEHzKKWfV7Fm0aWF+K+JCAgUkbQK1SVJBggsx39Tu5dvX77pycmBcgMBjTaA9WS5EYAEk2l/IkSXD1AQDAwQaYPzw6QICwocYufhCKwJDBYYIEiR8gBGE12TYsWVL3P9WBsYKDKorZHAho1O62cGFxxY3SQZuuxIyrIgx6eBw6NH3pusUo0WG5BhUwDCzTfp38FV5BYHxITtrItD8mtNlZgUAABjG3Cob3v79mL7myIAPocgmvfATcECMpLEkCAIAICAIS6Qh8EEIIfqGEyIegE+GOX6JcEMO1xnnljIwgE+FNHQxRzJr7LCjmQ5b5NCcO+qgxUUaH1QHkjogUadGHvGjpY47TuxxyO+aUdGa2Lx55JFpiHQSunSWNOZJKoNT5RFVqtQSNmOWBG5LMP2aZklvklyyyTDTVCvKR6ZU882zrswSTjqp6vKRL+vUM6YxHykTNiWZ3HPQl9h0k1D/RDWSM1FGMbozz0YjhajPPycLFE1JM23IUE07ZUgSLD0VFaFHR/WUUjMFNVVTTlfV9EpJXNW0VFkjRRXQM2uNtFVdGV20V0ZpBZbQWy3NdVhCeUV2T1DnXHZPYZ+ls1jJLpVWT2WvffNXbeGMttswqY3MWnDVzLbcLWFFV81v16VSXMjIdVfLc+d1sll7t2w33x7h/UtefomsN+AauSV4yH0PbtFfvwBWmMaBH+ZQXYl5TLhiCBnuy2GMN4y4YwINBnnDi0fGT2O+ODZ5wI9Xtg9flyMsOebvUN5LZZrDaznn6CjmWcCZfxbOZrVwFhpKKY/GT2SlpQu6adiITsto/6hl27nqyWDGOrqnt/5LarSo9jqyq8f2i2mzufQy7eDAPktstvkqO+60fKZ7sq7vNstts+DW+6y5/65Ka8H/yrtwqfi2ym/Epwq88aDQhvyswyeHSfGqGLc8psc3d8luz82qPPSVMKdKc9JZ6jz1jCRnXabRX7fI9KlQl/2i1W+niHDdYV+796Bol8p24CXKvfiHQEe+pdiXb0j4qIh3ftOkp/88VOuZ/z17jaAPSnruETo+fN7Dt6j58L2XCfzwx+fedfMjQp979WNin3v3s1c+/onmz75+mNwve/mzXvn4JxH/WQ+ALxGg9Qg4PfgdsCEJnN4CXdLA6T3QefuT4P9DKOg8C7YEg87T4PIi2EGFfHB5IWTJCJdXQuQZEIUT3N4MH8LClbgQeTAsHgdtmMIa/pAhONSIDovHQ+Cd0IYqRB4RM2JE4CGxdzIUIqmCWMWEOBEjUOydFHWnxBkysXhavAgXdefF2/mwimIEHhktYsbboVF2VFzjFbG4DjdWBI6yk+PrwIhCNvYujxTZ4+v6yDo1CjGQuhvkRArJukOm7o8dXOTtGimRR6YukqSjoyLtiMVLRiSTpNtk6BL5w0rKLpQQGWXoSum5SUowla9b5UNa6blXbq6TqPxkFWvpkFtuLpeWi+UBZ8m6XzYkmJYb5uROucReCjGZDFnm5Jr/CbldQhNPdxwimVKFKW6Kr3rhTEgx+XfM1E1zIdWE3DUb98wwRvOH6lQIOxvnTsSZM37oJB09E2JPxOGzcNmM5zbJiRB/IgSghROo4OAJSHnaMKHrWKjgGvo3fZqPn6GbaEX/dlG9ERSiBj1oR491UJDeLaPh26jnTKoqlI7zoA+lZERn+FJwhjOldBNpTUlKTpweVJxtEipCVsq9lm4uqELdadxoKkubonCpMSVqUY+avaRabqrkbCrbegrVn4ZzqzqVKTmfasyodnCs3Oxq2q5qvaxObq13bKvZvorWsHJzrlis69jeOr24Qm6vVeyr1856zrRKcLBCLOzW7orY/7zecbE/bCzW/uq8wDZusjasbNUOu8/EHnCzM+ws1C67vMwibrQoLG3THgvayILSm7iCKVfLGs7PajS0/FttB1urtNMiL7WF660Ef3u01+o2tr6crbFqS9aqCjW4xRuu4Ip7wOMKLbcs3W38rsu/7P4sudxdrjSbW62T2ja6M8WeUKv7t+/GL7w82y5Su2u++JpvvjmbLvDeq7f8tu+23Byvfcs7z/OOK73QPRR7Y1XU/94twPgb8B3727sI023CA6wwFguM1fumL8HxWjBbO1zFC+suw3HbsANPLMT6gvjAEh3xv0pM1xf/8MNwDTH9atywG/M1xzZM8e1WzLYWZ/9wyDOMMY9nfNMfbyzIhF0yCossuyOnLckkrHIHdwzYHv8vyimbMmO7LMEmg/nJUh3zzcpM2TMf8Mqvy7LZtvzCOPPvy5gNswLbXLQ3czbP8Zsz6+o8tjvvcNDmSzOf16zWP08t0KRdNPnae9BDey3RR6z0+y5NzkxvbdNR7LT+HvFg9/a5gpEO26RZW2rrFTp1ocbaqLsI6+ntGbWqBiGr3+Zq3+J6g6cu6jpoXTVbn1HYJvx0OI8NtWTHcdkxbDY3n920aPNx2j2s9h2vrbRsG3LbSSQ2hHm9Ql/3DdjGHfcUu43Fbx8t3JBs9xffXcdHKzbdi1s3duudxnKnOt//ot135voN3n/LTtaki7fQ5q3JhL9O18I9dxMLfrqDyzfiiAw4pis+xovXLuP63bgk7+3JgfM25MMbuYDXS86JU/fjbVx59FpO4Zfj9uS8TLl3a/69m3M459xs9K57jt+fry/oLh76HWPu35kLMun2W7qSm47FhYeu4T97OClLTrqiU/zoIvbTN4u6X5pl3XNb51nXXfn10D0dw1Fn5NQDWHUuXx3FHQc13S1pdwbiHc96h/HOtQkpsQL+goJXNOF1bPiCIl6vihch4znteCJDfqSSlyzlW2h5UmOeyXx3tt9V6fkcgv7Wokeh3FVselqivoiqVzbrO6j2zbE9Z27H/yXcYUl6a8MembJ/Iu2lbXs0a96nnJdt2WmbUxMj/4CuN7Lw00n8LRpf29LnX9hlPnYfO9+50Mcx9wmtfLAyn7niR+9zo99gmKMfr+o3L/sV7P7yw1/nzvI4+MVsfxLDPyEzP0YDPm+zvn7CvjLSPnEjQEvjv77zPz8DQBsTQCpzQE+DwNKTwFWjQCCzQDPDQFNDtf6jPwTzQCkDQTgTwViTP8gyQRpDQTJTQUFjwVxzQdiCQSiTQTejQUqzwWEjwQjUQTbjQUDzwVcDQmbTwODjwF4zQklDwmBTQmpjwgN0QnSDwlaTQnajQm6zQnhDQI5SwDdiQHrzQnITwg0kQv9I08Jf40J/Q0N3A0N8Y0N9c0N1g0OEk0N7o0OUs0OCw0N+00ON40OAU8MmBESVE0SDI0SSM0SFw0HlUkSfY0SMc0SX0z8Ck0TyokSks0SRw0Sc00QLM8AwxEKLA0WWE0WhI0Ws40QD80Syq5T2I78BdMUqoj4sE0OXIkM9MkOIg0Q/gkUZk8Xwo8X7s8ULxMXCQ8QrNMb/Q8YAVMYQZMbH80Oeg8YJlMYKpMYVtMbMw8bDKyreEybf2xzvgzpUBDlVtDlWZDpwHD1xjDxy9EVCAkavE0bW0UU640WlskdHwse300eTc8ZT1MYO5MYP9MYajEcrI0YnQ8gnVMgUZMj/H3RIL4NINZPILKTIGbTIJMTI5JvHzavHdgS6d7Q6kZQzU6xDk/TIHgTJKVxJPdNIR+PIVITJI5TJLqTJ8yPJ5XtJs2OqcySmlvxDoXy+sytKZ7JJo8NJdtTJKOTJOPRJ8+FHQ/NHrQJITBLI3iNIsDvKbEzK8VtKsDQlpxQ7qKS5k1S6lMw7q3zAYtM9milHZmJKyME9y6HLmLFLa8LLdxLLcRQqv2wnwEQcrJw1rZQrrhQlrzTHs/w9oEw/sqxFs4xLTzNIlyTMxmSlx7zLyETHtPy+tZS6tqS6txw8zMyexGS4xRSszrSlz/zL0DRKzURKzjzNu0vNxlvNFpzM//mrzGS8zGJrTa17Tc2KTWCaTcOszaYEzhcUzmkkTqsSTHrMTancQqrcQ9+8QejMQensRuqUrtFUx9KsO90MPN68vO4MwrlETtVSTmVizns6zMLRy8nhS5cpzPp0Tmwqz7lbR7bMzjfczkJsT2a7zbHEzqGkKgRFHvyEHP1cGf4MKPsUHONcO/gkLvmkJvq0UP8MzO+cxPBcyPF0sPcUUNMk0Dw00Ed80OLJ0NzbUOvq0HX6UIa6UIwC0NdTUfRk0UF00UwstnQM0PP8u/RcvPUMPRgltxHtxBKtyBONvyeNxSj9yCnVOQUdzJKy0XrCUYvSUb2J0MaZUJPxJ23wBP8sQAAEGAJOcBBuAgdckIMEMIAZsIRnONLQKYdeoAMLMAALoINeqA++egZLmIEBWIA4wAVwCCdp4IQhYFMs8ARt+AtwmIQYcIEMUA0MaIEYiINKFSJz4AQZMA1OXQEYEAP1qCJdII8VqIAIqABUDQJdwCJoEIPbyI3VgAEg4AQh+SFtiAPr0NUPcAEYmIRG3QtpCIIWkAAImAEkSAIagAAJWAEg0BAbAocycAEMeAAQ8AEnuIEIgAAViAFP+KFyoAMYyAAIqAAecAIeqACxgAE6IFQUookPgAAIuAEnQAINeACfGINknaFfAIJmxYwkQAIRoNYWCAI4RQttAAIVgAD/L5CFnKiFNtgNGXiGGRIHMWgBCEgCUkCGkRiGQQCBCoCBc2WtOYCBCqgBRiBZkSiGRqgBCWiBObAhmqgADSCEYRgJZCiFJHiAFjCIGXoGGcCONqCFnJAFMCBXIAhVsyiHIlCBCnCEnMiJU9CADACCgT0gOQBZP8jakaCFG5AAGFhVCfIEF4gAKSgGsk0GYsgCCFBZFIKGmriBWojbZPADCHCBnO0gcACCDNCAU8haZCBZR4gAFSgCe6UKmoCAROBbkSAFCGgBSuigZ6gJMKDcZKgFEFABMdBTvQEHGcAAH4BbvjUGH8AAGfha/RKDDwABW/BcMEBbjpWgSQBZUvBc/0RwALu1inQAAgzgAZmlXC2ogBiA3fCJgxXQAGHw3GQYhAiAAWzln04A2cP13FP4206QoF+AAQgYBOkVBg1QgTiQINPFAC6Q3mTYAQwIgnOwCryFAERwX1GoW9HgH3GQAQno3PKNAMyVoCL4gBtw32S4gQ8oAgmihBWQgJ+VXi+oABl4jvjJBfEVBfdFBAiQAbWdClyAgQeQhePlW2QQCy1IXBVeYRZuYRd+YRiOYRmeYRquYRu+YRzOYR3GYVDQV0UoYb7NAQyggR0uYiM+YiROYiVe4hwOhnZVAwRWAwl4gGBgYiu+YizOYi024mSYgeJFYEV4AAkAhS0uYzM+Y/80VmItuAwgjltZ+FtcsApNAFlgQGANgAAOWBI93mM+7mM//mNADmRBHmRCLmRDPmRETmRFRuQqCAAIIGP3dYIKCIBFrmRLvmRMzmRN3uREtgMAqAA+QGA+kAAAsANOPmVUTmVVXuVLDgAJgAIE7uEAmAJWrmVbvmVc1mQOgAANQGBguFyoqIpOcAEI2FvpRQYKgIASyGVmbmZnfuZH2AJHbgQERoIKSABozmZt3mZMxgMAkAA9QGA9IGU84GZzPmd0/uMEkAAkQOBGgIAA2IJ0nmd63mYSaFcEroXLXVmq4AXxDQX3pYXL3QR0OIeCPmiDTmiEXmiFbmiGfmiHjmj/iJ5oia5oir5oi85ojN5oje5ojqboanDZUHZfEPiANPhoj05plF5plW5pln5pl45pmC5oczjdKEDgKHBdc0iHmZZpn+5poP5poQ5qok7odEiD2UVgv4UBbChqpx5qqH5qqY5qn55jCGBa6Q2Fun2NqjDdCoBi6R2EDn4M8CKCDDBe6e1eGLgFCaKDFbgAYpBeYpBVOpCgEIaA7fVcHsgAIpCgaJCBCCBf6VUDCmbeqHDeCjBmviUGEVhg0r2bYYYAgPZcJ3DdAOGfX4iBCBhpyjUJ65Wgb4iBC3CCNs4JUADe78WuAhaBuKbcWpDV9DWLa4gBCfCB1o5bLZCAGAAK/wkShyDIABBQbLINhL8NZgkqAxagAA3mW1KIgBUwAxTSBGIOBMqlBRDoWgvmH1+oiSygXGLwAd2+BrTghLxtBbKtBSe43EkgWNEGgcnOCWJYAwhggTF43PjZBiD4AAogBCBGBkKgAJTwjg4qhzFogQdgg9seCVAAAQyIgett67aFAqzOiVbIgepN7bNQB0qwDAiAAkQAhVBQhORNWTP41Q7CBRnIVx8IBBBnhDUAAQEugsvuIGgAghV4Vj1wBFFwBD2gAecGgg8G7SJoVg1YA0YQhU8IBCR4ANCI4xkyhzhwiwrgAkUABVAghCiAgAs41h1RC08YVgh4gDDHgBWQAf9LmN8f+oUg4FZn1dcKYA05yG4UygYxcAHz0Nd2LVYxUIkfEgdh/YDLiAAxxgAXCALe5ixLiAHcwHOxaAEZ4Oe92AZLsPEAIIAMkAE64PMqEodOIAIYqPQIiAEzyF3CygUxkAEGMAAGiAExyIXHnpxfMAPNJoABaI1OkHMbugY6SNoBGAAVAAJLEPC/MIddsIIqeAX7JqxqsIIpYARcx6Jt+AMq+ANhDydxYAQqsIJq6PJwKodXsAIr2AUTn06ifARiKE4erT4fRVIgbUQhHUUiTfddXPfTS9LKW9LVa9LeIVPEMdORqdAcDdF8kvd+pPfYs/fPw/fa03d729Lr7FL/hE89hT8+hr8dGd1LGoUvL/0nMP0oMVUpgs9Kgx++iJ+9id++io9Ehy9JBlXKck/5YazSYrzSmMzSTZT5iKT5nbT5Ulz5oGz5snz5eMf5jdT5qeR5Dwt5xRz56yv54jv5BoR5jiP6mzR67UT6vfN5ygR6yxT6orr4/Mx4ANt4hep4vUG7mOH3wvF3kAH4MBX4+7ROlof4dr/Ed2/FoU/RV09Ap88+qD9DqU8dsJdQsZcwsqcos78btHeZIu3RvR/Dvl/Avw/GwA9Lqn9Kqy9QrBeiwS/Twteww/eos/94ulF7wWH7jnF7j4d7h5L7n6f7BlWvyo87pXdNpuf7ug/F/7uHx7w3t9uH/Nxfxd1XyXjX+uDk+uH0evK8fLXM/Bbd/GvUe+cPUujPPOOPTuQndwftfYF7/F6M/DKc/Hycfc/p/H7/fBYL/cSnm8VfGdP/G9THGNUffdbf0esHz+wXT+U/KPNfe/QHiHUCBxIsaPAgwoQKFzJs6PAhxIgQpz165E0iRofeKk7L6PEjyJAiR5IsaTBdRWMmV7Js6fLlS1WPVMGsafMmzpvGKqbL6fMn0KAMKVoUanDjo45GlzJtyhLlI5VOp1KtClGmJKtat3Jdt/NRz65ixwYletEpUqVk17J9CVVq27hyR8qkOfcuXolfw+bt6/eg2alp/xIu/P+2MGK/kmYmbnx3r+PIbAOj5Sj5stjDmDdrxcr5M1XIoEcbpdx0MOnUPzWrbn2zruvYNUXLrm3SNFPUtneLZM37t8fFdoET18uzOPKHuJfqTu4coe/n0gnCnm59IO3r0pcbba7defTvyT2Ll569fHHuQr2jBx6+/W/h8JOfn79bfVD29mu/3y+7un+81Rega/gBpR+BqvWXYGrkMSjbgA+OZuBPCEr42YIXcgaghqlF2CFmFPpkIYiSZVhiZPKhONqHKzYmYk4kuojYiTMW5qCNl7WY418w4iQjj33VGGReHBKZ2I5H3uXjTUAqKdeQT8alopSFJVnlZBWddZplWP7/FaWXYxkZ5mPHkZkXkzY5eSZXYLLZ2SNZvVkmWHPOlWZNa9pJlZt7OkWln2tdGahTeMKkJ6FL9ZmoUGMyqtWgjwpl6EuISrpaSpd2haOmVUXaaU6UumQpqDYtWmpNjqJq1KerwiRqS6S62tKps7IEqK1CtZrrSrCyJCuvJNUaLF1xEqurmcf65OtKwCr70bDPeqSqtC7tWq1HzJrkLLYRRdstRLiC29K1406kpWBdmktrpuu6RK27IZUb70LalsQtvdC1m29JnPIrb7L/hmQvSfgKPNC3Bw8krsIYzduwQASPZLDCCTcML8QNPQyxxCJRfLDFCvubMUQbN9xxSB8L/xzywRiTrJDJCqMMksr/siwwwy9rHLDODs38Uc383vzvyD0vFPPBP3sUdL5D8+uy0QUhLbDSGTFNr9P55hw1QlP/WzVGV8ebNb1Qcy2Q1/yCLZHY7pIdb9FnG5R2vmtH1Pa6b7u7tdwE0U2v3RDhba7e65p99t/xBv7Q4OMWbm7cfWPHs+QFLa6RupWftK/mBh3OdeLuXt5Q4+A+Pi7flYe+7ugMld7t6eBGrjrlna/T+kKvYxt7t59Hvbq5uCuke7W8Y5u65MCPK3xCxEtrfLW+G608uMwj5Pyz0Es7e/K1d279Qdgrq/2zyPdNfbfgH5W57QKRr6z0PaOPrfoFif9/7PvHcn++95rXT9D9iJU/YsVPZ/Or1v8GEsBgDTBY5pPbAaWVQIEskFcN5NX+INi/yk1wHRXM1QVzVcCXRfBZHfygrUJoqwciboOSOyH72qfCWY2QZCVUFgyT0r6CzNBVGWxhnXY4kByqRYg9XBULQefCvhFRiAjjnBBrmLEbHquJTlzHEVH1QyUG0YlWdGIWSyVFiFGRWF80IhR3mMTfLVFuZ9xhGEG1RTZ2UYhvlGEa2zfGhpUxWHe0XRw7tcbptfFsf+xcIDW1R4X1kVeH1FwiLzVHQtZxh4+sXCQlNUj5FZJrl5RcJh+1yIM1Mlef7FsoGTVJTlayfaeUWyr/EzVKgZXSVq88WywJtUkDdjJqt+RaLgO1Sl620na/jFow/TTLf9VyVsc0WjL3tEsS9tJoz+xZNO20TH4101XX1Fk25zRMahbze+iqjA6vGM43TdOG1ezZN1+2TjZtM1/dXFU8STbPM43TneX03zm5lE4w5tF29aTXPVGVz4ztk0ztnOI7dbZQiDU0TP2E6D85GNDcxBCQBe3cQeOV0FJNtGEV9dJDyRjRl5W0Yh/VXEjdNVJQtRRkL63cRVWa0RdulDkdReRNJZdSPq6UZDVdWVD7FtN1zbRTR7VZUuWWU6LulIk97c5PIRnVsy3VXE3V1FOFtlWuDZWRRc1YWJs2/9aoTdWsVXXjVdeTVUyu1WhdHddXL5VWrNW1Z2Ul5Vk5Ftf8zBWUfdXZXcGVV0ntdWyHfVlbAftWQw72QIVF5WNJ9ldaBvZkla3QZWGZ2YwltluLfVRj3TZaiEWWs5P15GdHFFpcrvZijLmiVzors9jGaLbArK3CNstM3SaNtz/yLTKB2zJj4fa0jEpt3pQrsNJiy7mJgi7hpPsv4XKTuFQzbpOQC03tPu22V7QuobDrOPLmq7XDfa0vwasm8WKTvfTirj29+zX55om+4LQv3MzrRPQGSr2mA7C73Ntd+FqTv4fyrzwRbDgBC5HAfjIw7CRsLvwiVL9qc3ClIKxPDf+PS8H5ZTA8QTwqETOUxLKj8A4tvCcM787F3eKwSD1cNxXHisUUtTG2qFstGduJxsUDcvSYe14dA47Hv/KxSZEsLRzLlMmKc3KzoOzSqOB2HUKWFpHnZOTnSflZJu4wiiWK5W1p2aZcxu2XnxXmN405e2VWFpWZamXRrflebUbqm6945hynmaV9LtifoRpoJ8ZZWXNmU53Hd+dj5dmre2bdoSeWaLEuOoowbt+jzxRp/E2agEoe8KWDl2mPbVqtnVbjp20XajKNWoClDlajjzXrMNWagbfG4KkrnOrlrTplrebrq/UY687t2ku9tuCvc1VpvA67esWm2bEdm2yDBjv/xtVO37WBlm3Vbhuky9Zcs7H0bBBGe4Xnpl2hjRrupY07uuWG6bu7F2+0zttq9c7uvXHabVB/m379Dtu/1xtwoeabf/sWbFHQWUQ4tpuGDdfgwz0bcYFOHI8LV+rAZV1wBB6cbQk/8MelenEg8sWOJb/byTOc8rNNW7Ejl+DLBRfzGs+ca4OucsZ3u3GODhSNPWfryrnYckvmnHE7P/LRjVZz097chE3HXNEpHvWe5ZpY6a7SulNYcR+GnNlVx+HVSfd0Mm9dZ1Ov7tmrmHbXrd3ObYds0um4dFfOPXd1l/TdSfZzPQe9uEP3adY9DhdG552Sezdm34f3d1IHPmNv/x9y3M0Y+eZN3taVZ23Z0Z15P27+ep339edtOxxUF/67h8dq4j2a+uA2npWPN+fr5Rp7oM5+uasXduv3m3vC7l6rvZ9u6OF9e4AO37LFp+vxt1t7Yi5fo80H7fMNG/3y/t7bwf/w9WWbfcxuv73J13f1eRr+3o5ftOUv2/TJmX6rrv+47aft++N1eTCP3pGlD9/pQVv+Jdj5Odz8wVX9hdf9/dYATlj3Edz37VgCztcCJlcDblj8+dMBUtYE9lcFjtcFllgGYtQGwlYHPtgH1lcIvpicLFkENtkJhlgK/tcK3tgI6lQJxlcMsoQ5QEMhkAAJwIEvlAMcSUMnlEAHaP+BLoiDEGkDLhwBBxwBLmiDEImDLmgBB5RAJ0hDDpJMOfgCHJBACRTCM3RhSZxDLgRBDHwABEBABsAAEHQCEWrOL4iBDLRAG2IADMQAJYBD51xDHMQADFAABFCAC8RAHFxD54ADJcAADGAABERAC8iAGPxC55RDJwABDLAhBKgADARBLpzDT4hDGcBABkTAA1xABeQhDIjBNkiOOTSiCrQhBVxAG0pACwABNFTOLciACkhAG14AIUrACsQALlTOMwBBC0jAA0SAKkKABHwADFCCOUjONhTBIz4ABFTAKj6ANJoBE+KEOBRBC0RADSiCLSRDMgxDIyABBKwAELwiLsn/AQxIQAgEgiyoIzKEghZAwAfIgCXKDSc8YgW0wSkggzqeQhtQgB5yQt/8whpCABeIQjGooywEAghIAAzIgTrIzTYEwSwiQSMMQzIggy0owg1AQAsUQTjWRDqkAR7ugTGoI02WJCK8oxjMYdRoAgw8QBQQQ03SJCloQAYAARVyTS/EgATYwCwEpTrOgg1oZC+cjTYAQQZogCg4ZTIQQxRAAAxowtmUQxHMIiIgpFO2gSSaQUfWBC/EQAS0gVbSJCF4ZSdwjTYoJRKYpVaeAjHGAdeUQxB8gAgAQ1wmAzCIwAcEgU72TBysQAScQmEiAxJUAAwcpdF0Qk8iQknGJVrG/wAv2AQRCKZeaiUy/AAGyMBivswkOGZTFmYytIFGSkPU4AIMQIAjuGYyOEIEwMAxGo00yIAE6AFuykIErMAkRE05yAAG5KVrIgNiFkFNXEM9BgJu5qZX+oLRlAMQYIAUVKctqCRYGk0ZiGZ1ImYZ7CQe1kJ1SgEGAEFqZkwv1KYjjKZTIkMgSIAMKOJL5EJPrkJ1EoMbvgE1DCiBFqiBHiiCJqiCLiiDNqiDPiiERqiETiiFRmgsYEAEEEJ1JsMNYIAQVCiIhqiIjiiJlqiJTqgzYMAFgAF9auUXYAAGOMOJziiN1qiN3qiICgEG1MCG3uQHxAKOBqmQDimRlugbfP/AAwAlbq6CV/amS3ACHgrDhmoABHBARVwplmaplm4pl3apl34pmIapmI4pmZapmZ5pmVpBADwAKGyoE0jAAaCpnM4pndapnd4pnprpHQCABOzBhvKBBACAHeQpoRaqoR4qotLpAUiAE2woKDxAAFhBok4qpVaqpd5pB0DABWwoMLyjQ74ElEIAYVanLZLApZ4qqqaqqj6CmkJAm1bnZCLAqs4qrdZqne5pcG7oHgQqHtiqr/4qsHIpAjDqhn4CBATAFQSrsi5rrWaqBnCqStblftYmZOJmp6qAIHSDtm4rt3art34ruIaruI4ruZaruZ4ruqaruq7ruXrDLqhABAz/wobOQAY8AbveK77mq77uK7/2q7pawwdcQBdsaBdgwAdYg78mrMIuLMM2bL4+QQbMwIYOQifugsNeLMZmrMbyqyDM4qi65ik4AAzkAkxkA3DyQXUqglcGpM6YQxBgQKPi5ixEa9TEwQeAwIaCwAf45WXiIS1UpxO0ZzX2DERCwCJUJx9QgAxYpkuIwc1WZGTmAAYoZtRYAh76p2uCAX5mQ9ToQm0qAm4mwgPAgC5ETTYopRosqUpaQtSYg1XmQIvWJDHorBjYxC/U48AWJh/sppP2zDYo5w1ArVaGgkrSAdeYQxF8gAa0plbOggZ8QBGIYtTQwQq4amEWg9TKwDdw/w1tQgDKxiUydAFlsixMzEFtdoGS1iQy6IFKlsHQRs0t1KMPpKNTKkIFJObmcg00xAAGiEC1BuUpiMBp7iLXfENgVsDROmUt+IBGesLZmEMZVC4fCC5NEkMXQIALzAFOlEMZuIAEgIAfnIIwDMMqDAINqCQR+OHZqEMjSkAFrIEo2AIxyIIi+IA/AoFsyg1/QmIWOEItEEMtOEIWQAAGxADJyk00AMEHRAASKIIsEIMtiMIacOM09g04EIELRMAMDMIqDAMwnEIfgEAEuEAZvOdLlAM9fgAwtiE0viE4So46dEIMrMAqsjABuwARcK3k9IIyYoADRIADBGMuYqfkZP8DETwiKrJwBayADHSCGfILKcKABlDAD/9wNMIAHZhwTfiCGMxwAzRABsgAEejCEwuMNAQiDDSAA1wAHMrhIk6CDMQABARxDMjAJORu5YxDJsZABTiAyCJi/mKSLhCBDHyAH6tADFTiUmQDJqDACRgCFwrRN+SCI7PBM7yu7YhDLzTBCTRBL7Sk7ZjDM7SBCaRALuCx7aiDNBjCCaAAJugw0XWc7C2epz2gyL3gle1gj81ghNVgkN0gVZWxvOnyk/HyiPlyktmy2eEynxFzlhlziyHzlAGzWwkzvzkzm0Hzj0mzmRUgxlkzxG1JLOPWSWFJ1wXL10lJ2M1KOVfJ/sn/Wf+Z0v+tjzZHGTfDDzVLFjhrnDgjnizzHi3v0OBZGjNjGjb7WT1vWUC3zzs7Wjzb0jzbTwCy2z3rTz671j4LXT/D3j8b30JzWwuyXkYb3kbrXkdD30ebmzKLXkGr2kEjWkK7WUprTkPr2kM7U0QD0ESLXUWbWkgD30i7XkkT30lr30wL3EorH26ts6u0s5TUtNfdtDfltALtNDuP3aqcM6+k85Mw9ao49ZMMNLW1NLG9tKbFNKAdNcMlNfotNVVTkFU3NVZr0UW/V1AL31A7X1GTn1qD3E97312DX15j3167X1+rHFsboFubNauhtaIdNs3V9YIFtgQOtvgVNv5B/7bPeTPLLbZlsx9mM6BmI11if7Nnp4tjc9poS51knxhlw+Bn219oW+Bqc11ro9lr53JsK+Bsg2BtIxZnK91pSxw5z3WpQDU6SzU+vbUHxfVXG7cc3Tah5XYz7zYF9rYK/jbe/TUEUrdBW7cHYjcNarfgSTfQebdLgzcKincvk7flmTfhoXdZq7cMsvcxuzfocfcty7e1Mbaxpbar4bfqdRlXK4lXowpYKwlyb7VyKxRzo9BV9zSuwTdB8ze4+Te2ATiyCbjIBLfeDTfHFbeE88qC50qBH8mBl0qCH4lWm3iDk9SDOzeCQ3eniLXNkXV/0/eKabi2cbjvEfiL01SM8/84ufk4zlD4WFu4wWG4uBG5vRk50Xi444H4OKsTjSsSkt+4kpMck9ObkwMclPNLidvKiRNJioPKihNJi5N5kDvVkNt3NIe5+en3Mm85znW5v325wsn5fWU51eH4hev4LsP5NvN5gJV2Z1/RmXdKmgeJjf+5nVsdniOcnqOcoRMgogu3or+5iF/6uoz5rJR5kCy6pjQ6jzw63AH6kgt6MRO6PXs65Ph5qkc62k26yVW6zME66sg65qk6l7P6M7u6QnfZmod6m4MVp1v5iIuQlNselftzp3cZqLuKqPMIqV+KqedIsVP7setVshPUstsKqvc6rcudrcMcrvOcrr9Ypn//+Kafu86lO9Stuw22+5S/O7Bns7DLNLE3O/U9O0dHO5zxOv/5+p3nO0Lve1pLO8HDs8FLOsLDtMI/dr/bu7PjO2pPvGr3O52zdLlrHrw7nbyzHb0fT8M79MPXesSftcYHeMUDecqb+8o3dstvOMfD/MeTXshjXc33+Ms3V7cz1rcbXclXy7SvSrXnyLVLSrbbyLgXfM77386r3cjbXdFvz8nbdMyD/Mz/d88XOcNb/L9jPHEr+9V3s9jLH8CbtMALmr+rPdmHuNmHPc6vPVG3PeOlvQbavV7jvad1vFLHfZWD+9njs96TIN8Ttt/D2uHjYOJf9uIrG+C3teBD+9wP/3zjB/Pjg3bk287Ro0rS28jSP0rTz8i2I33Qo9bQa13hW/TkK3blB/zlX9Hnl0roz8joM0rpu8jpg37qP9fqK97NA/3W63zXZ/jXP/nPu2DUy/PU013VA17rE0vtg8rtu0juJ8rur8jTO3zzQ/Tz+130U970T3jmV/Pmy3bnd071d8r1r0j2E8r2o0jv2/7vX1fwz/LwM3/68/b6A8Q6gQMJFjR4EGFChQsZNnT4EGJEiRMpEpT0SFVFjRs5dvT4EeRHY48epQt5EmVKlStVTiPpjSVEbySnxbR5E2fOlOlIGtP5E2hQoQhVYRx6FGlSlSNLKnX6FCpEl49gKp35qP9mVK1bt/J85JNrWLFIi0oaexZtTqYm07Z1G3Jq1aRXs761e3eiV7B4+fZdWDSjX8GDB64lfLhvXKd0ETe2q9dx5LYXA0u2HNbwZc1RFVuluRm0U8ihSR8tWxp10MypWdvsPPdza9krR8+2fRLwbd0gV+/2TfE1Usa/iUusXRx5Q8rJmTPs3Rz6wOBHh0e3vu74dei5tVt/3h359KHVwSfPXr74afTMv6/fLV4oefe+z8/Xvdw+8fb5ZcMPKp+/2eoLsDXuCLxtvwNL8w8oABVEbcAHSVNPwtYSrFAzBn9yEMPNIuzwMgNBJO3CER3TUCcOTYzswxUbw8/FzUqMcTD/FHNSkUbCWsxRMAp5jGzGH/GyESccheRrxyPvElFJwoJssi0ibzISSreSrDItGLH068ktxZLSJiq9HOvKMcNi0sy3ukyTs5cWi43Nt8qMEyof6UxrzTuTAjMmMfUUrac/JzNKULTyLDQoPlnyE9Gh5mw0KDQhherQSXFSdCVGLdXp0U1xstNTpSoNdSVMVdKU1Jg6TXUlSVlVjSS2Xj3K1JRQnRWlVXENSctdgRrV145qRenWYD3S1ViOQE3WJmCZBc5Nz7B6NidkqZ3I1WtRclbbh4Y9qdhuI7JWXId6LfckbtFV6NuQwl2XIXLhTSjbeTVS196C2gXp3XwPktdf/4KWDZgifAne96N+CR4I4IXPXXgigwNG2COFIW6Y4HohdkhifynuyOKFMQ544I0f6jjfjzkKmeCR/dXY5IVQtlfljVgO2OV8H46Z41h5nqhmjW72N2d7S/5ZoZnnDbqiofMtel6YkTZIaXiZpshpe6GGd+epE6p63asnynrerdeV2uvCfE67IbElIhtes9E9mm2CwEbX7YjgXlfucruu2+61AU8ob5ngHPzfQBGnl9DFD7q73MIf2hvdvsWle3DIxZXcIcrLtbxbtNnWvFvOG/JcXNC1/Rtx0rU1nSHUu1X9WswBd/1a2BeSXVvaqRU9bdyp1V0h3q/1/VnWMxfccf+CiE/IeGqRZxZ4r4V/9nmEon92+mRtr/t6ZrM/aHtmuzdW+duZb16g8Q0qP9nzg61+6vCTdb8g+I2V39fvR1+fffgjiP6Cxb9d0Q9p9jOWAAdCQF8ZEFfpAx8Am8dAgThwVxCclf+CR0HHWXAdGMSVBl+FwJ8pMFggFOGsSMgqCf6vKexzXrRgMy0ZMkxxNxSICXmGQl+p8HAybGGqOGg9Dy4OiDbU4RBJ9cIOxlCHSazLDZkYKh7GzIe7kqIOBVJFTxWxfkdE3Ba56MVNXdFkWcQVGZeYQx060YhQvCEbqejGG4IxgWIcHB2FaEcZonFjapwVH9lnRkvBMYxylCH/IZtnyEkBEmKCfBUjHedISOHxhHoEHCUXZ8lGITKPigwgDYUTxEL6kX2QXJgkWcVJxHkSUZjsoSbr5srBwbJQqiQYK1NlS8DhUlCgzKQoK0hK6piykahsniyxSEu2+bJuwPyTLgPGS1JBk23S1JMwZ0nMDxpzPMispDIdR01/WTNU2EybNu/EzDQ6M23q9Bo76cTNZnoTieCMjzg7Sc7FmTNf6PSUPKdGzzi5M5Dw9BpBkWZQNgHUXgLdFEN/5tA02fOd+ByjPv/Dz1f6E3EIjaRCp0ZRnlnUTBCdl0QtZdKYoXRMGE2oRvfI0QZ59JYgHZxK4cXSSbnUZDD1kkhX/0lSpAF1Y0LdkkxHStNN2nRDOP2lTgHH03X5FFJIvRhV60bUXRr1Z1oVGVfZZlV0YbVRYm0ZWdPG1KI6tZZQTZFUo8lWr3m1mmDlmVpxZtepmbVcaEUUX4nmV6S59atwfaZcb0TXbBr2Z4AVl2ALRdinQZZneD2nXmNmWa1hNmaIzati48nYIjl2naA1mWS7RVlBebZsqt2YZgPKWZPBNm6yhRhrteXaP+GWb7p1WON06Fs9Abdyws3YI8zCxXUY907I/ZxySUbcG0KXThYUhyuWoIRMfEOH5fgFE5QQiGwsMRphUEIYoiGr5qkjG4FQAhN+UQ4dbiMTSliCK8RxFP9pxAEGKigAAzIAgzL8onnfmIQMYFCAAkhABkXIhXsBJw5OBEEGDWBAA2AQhE70t5O5KEIMJMAABsBABpTYRvOeUYYYZMDEKohBHKQBlHRYQgYrkAAEeAwBCagABnOw7+ByIYMWYKDHPv4ADMQA3sFFIwguQHKSMdDhaCBuG2OAwQck8IAH8BgDLZBBLhBXDjlsecc9rsAKZGAJCrMkHQCugATU8IlVtAIUbdCABFwwBhCzjRMwQHIUFHEKWYjCDzSAgAqCoA3A+UIGH4CADwhRClmcYhBIeMAHZOALwGkjCC2AAA38IApZoGIRUYBAlTlR4TG4QAIaaAMoZLEKR4D/Yc4wkMObVWIJGEAgCbZARjKITWxieCECuuZ1zHQBAwnQgBXFLjYyArFoIvx5ateQQQY0AIphSxsZjtAABmRwDbaJowiSDsS3pb0KGkgABrpgmzrk0IIHfGEY0ia2LZAAARhY4ibQcLYT2K3vZKjB3/L2mjiAgIEZBMPgxEaGIiDQAoDPcwwquMAqklHwYq9izWNY9sYsIWpFRJzYwaABBoCA7Z81GwJrQHnHoQBvaNikDB/QADBm3nEaZCAII1+YJkR9ip4nQwsVgMGKp9aLXw/i6ISIQAx64bVtxKACWjh6KR7QAk3MMwgfoIExeg4MDaigDDHZhgwk0IajIwMR/xCQwc0bGgQMIOHoyViFA2DgCa/JQeMeNzgyLqCCOXjNE7+O9tGRAHShB0zgEUBE3tsggRgwXSUwL0Xea7HoSpAD9KEX/ehJX3rTnx71qVf96lnfete/Hvaxdz0zWhCBQOQ9GSL4ABlk33vf/x74wRf+8GEfjiNnAfdZCHM4iN985z8f+tH/PRkyMAPBGzwQEmgBM6Tffe9/H/zCr4QKHmCLvJfC37xgSSdEbf68VwACJCDJ/Olff/vfH//51//++d9///8fAANQAAcwAK0gAB7gE3APCSoAAQjQAR8QAiNQAieQAgUQDwBAAvQA9/RAAgAADyoQBENQBEeQBCEQAf8kAAmuT98cAQICYAtKEAZjUAZncAJJ4AEuAPdsoeI6gSU4QdSEAfc0AAI4gAaL0AiPEAkfwQAhABRwzwkkwACSUAqnkAoj0A4AoAL4APf4IAIAwA6qEAzDUAzxLwAqwAlwDxRasArGkA3bkAo5IAI0APeCoeJabSVwQdQ47uiIYdXQYBn+EBADURAHkRAL0RAPERETUREXkREb0REfERIb0RTgb/Ly7gYwAAciURM3kRM70RM/ERQfURkkoALAAPdwTQKUIRRXkRVb0RVfkRNxAANuAPfirgJSARZzURd3kRc/8QwyAALI7uhWwd/IbCWkgcSg7ujSEAbUD2nKIQb/MEDrjg4YKu4SvGYMxA73aOADxsBrLmEFIIDnjk4LyG3IfoYXYOABmvDoBsHfrmwl1CEIMsAGVLDYoIDcXC5m5GAFKsD9UI7apo7ukCbxIIAUji4U/M3vpkbgIOD2eq4WKsDwFi4ao+DtbuADgkAdYiIXfu0hUY4FvS5tpIHtLHLmWqHw0m7hGq4GiGHmiKEGWE4fTUYdykAFKqAVei4KKkAGauwbRc0Req7aYMAYWcIcxiAcCeH6PuECPuDa2IYSXCACwOD6VkEEyM3c0iYXSAwJxlHfgAEJLK8op4YkMWAE9FDfkAEMIMAFKOHciOADKoAd05IQIGAFxuAcbuIb/4IgHJMgFNjtFLQAAj4ACLIybcyhDKSyBhjBJYlNFtrgAqpM4aDS2UBgEGqh2GphEEAA3tyybnQhGiugDWTh24ZhEWwgAlygDMyhbq4BCCRNC07h25AhFJLALoMAHHJiG8RAyiLAAkaABi7Ax1wgCHyybsoBwCQNAmbgBoRQAtjMGaPpEraMAhwgBGwgBHjsA2JAEx7PZHghxyggAi7ABkQgAiCgwOTgHNlGGqIM/i6ABmigOjHABcQA83BiHDiBwVbgAz5gBWAgBixhJucpF4IABvjTP11gxhxtcZ5BDGCgBfpTBcRMDJ7BcbIhDmTABfhTBVYgBoJgwhYHHCwhBq0CrD9Z4AVkgBMG1CbEgRcmIQ7MYBJy4T4XR7wsIQ7KgA464bwKKRo0YQ7KQA40ob1kKBs6gQ7KIA4sob5kaBtygQ7MIA4mgRdY1LmuFEuzVEu3lEu71Eu/FEzDVEzHlEzL1EzPFE3TVE3XlE3b1E3fFE7jVE7nlE7r1E7vFE/zVE/3lE/71E//FFADVVAHlVAL1VAPFVETVVEXlVEb1VEfFVIjVVInlVIr1ToCAgA7" style="margin-top:1rem;" /></div></details></div></div>
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">ChemicalData["Ethanol", "StructureDiagram"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhgwArAPdXABUVFTc3N4CAgAMDAxAQEFVVVZCQkK2trRwcHJeXl3p6ekZGRggICAcHB/X19URERC8vL4+Pj/39/ZKSkllZWcrKypycnP7+/vb29lhYWIyMjE5OTlJSUtvb246Ojri4uJSUlKenp5OTk29vb8XFxYiIiGtra8jIyKqqqtfX14qKiu7u7vT09LKysh0dHVZWVqOjoz4+PuDg4OHh4b6+vry8vGlpaezs7EVFRcTExL29vfLy8rq6uoSEhF1dXaioqJqamjU1NXh4eDQ0NJ+fn19fX5aWlqWlpfr6+tXV1W1tbd/f36urq5ubm7W1tYmJifj4+H9/f6GhoVRUVJ2dndnZ2R4eHv///8vLywAAAMfHx2RkZPv7+9DQ0JmZmbS0tNTU1OLi4kdHR+vr683NzXNzc6ysrElJSYKCgsPDw7GxsaamplBQUHx8fDExMXl5eUhISK6urujo6N3d3Q8PD3R0dOXl5dPT02FhYVxcXOPj49zc3H5+fjIyMufn58DAwGJiYvz8/DY2NsbGxpGRkXFxcZiYmLCwsHd3dwQEBEpKSrOzs9HR0cLCwp6eng4ODubm5s7OzlFRUfDw8IGBgfPz82VlZYeHh4aGhjg4OAEBAUxMTAYGBmdnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZ2dnZyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAgwArAAAI/wCvCBxIsKDBgwgTKlzI0CCShhAjSpxIsaLEFTFyWNzIsaPHiUReMCnUY9LHkyhTTqzB5sjAP1OkqJxJc2YVJSVYGITBgUbNiGCyHCrIZsjPkxhUmEiRcAemER2OLgw6lGBRqR1DbODRMIkNDVCwHqRK1KhYimkyUJn4YdOPswTJWjULt6GMOpRuWLRAgURduQOv1l0oYcKWLh3HREEU5mzQLJAjZ6E7+GAcMS1QkgEkQmzQMmZChw5CufJALEWM0FSDo+rPoGbKmiYop80bO0dB4CHzOkvsubMFeslzQqweRHz20IQt23QgQUwGD3LzZCZz4JXvWCI029CmDymvB/+mrGiR1Ek9Cs0JfgWKBhtJ6l4gZIlRTSlT/rAn2GEEph11LVEGGjOkRAMHMOx30IEJ1tWIFY581N9/CiaEn351wSCJDhu5B1+FC6GnXl2VXDJCJQRBkskjmnDiQgQHofAdiBDd0UkEXNSVRCQDrZGIJhAU8QAdWQhSUBRA0DiRE2f8NpgDDTCgxUASLJCFEAStoGRFhvhQXF0vZGGIQY8ksqVHfrShAG5nWcHAQZ1kUcGZHlVQRAJnMYDAQY5kgQmdHx0AxxdY6XnQEVmUAehHgRgA3lFuHmRDFg0u6pFJRxWQRRMGETCABJaGKhCUDMw5kCJZCCDqqj5q0scWihAmkEUAq9aqIouJAOBBrbz26uuvwAYr7LDEFmvsscgmq+yyzDYLYkAAOw==" style="margin-top:1rem;" /></div></details></div></div>
+<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">ChemicalData["Ethanol", "StructureDiagram"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhBgFVAPdkADAwMLq6uiwsLNPT0x4eHo+Pj9/f31VVVYyMjICAgFtbW0pKSi8vL3l5eZmZmba2ticnJ3FxcZiYmNfX18jIyLOzs2dnZ+rq6j8/P3x8fHp6eo2Njfn5+aurqyYmJoODgz4+Ps/Pz0dHR9bW1uTk5FxcXKqqqsbGxkFBQdHR0WVlZYeHh0lJSYKCgu7u7m9vbxMTE6+vr/b29lpaWsXFxVFRUZqamjU1NSgoKLy8vNnZ2U9PTwkJCVJSUiEhIV5eXqenp+Dg4MzMzFdXV3t7e5aWll9fXxUVFf39/Q0NDVZWVtra2qysrIqKir6+vuHh4RAQEPT09BcXF+3t7R0dHbKysjo6OhsbG8LCwisrK9LS0gAAAAwMDKOjoyoqKjs7Ow8PD+Xl5XR0dMvLy/////X19UREREJCQkNDQ6SkpFNTU+np6TExMcnJyYaGhjg4OP7+/qGhoX9/f/j4+Pf393BwcGtrawsLC4iIiOPj4wEBAWxsbLe3twcHBxoaGi0tLRwcHAMDAwgICMPDw7GxsRYWFqampnV1dejo6N3d3a6urkhISDMzM2pqar+/v+vr6wICAjIyMsDAwGJiYufn5/z8/FhYWAoKCvPz8/Dw8F1dXaioqCUlJWBgYKCgoMfHx/v7+2RkZGZmZjk5Ofr6+qWlpZGRkQUFBc7Ozg4ODubm5ikpKVRUVJ2dnWlpae/v7wYGBkxMTCAgIEZGRvHx8VlZWZKSkk5OTq2trSQkJBERESIiIh8fH7m5uWFhYTQ0NJ+fn3h4eLW1tZubm4mJiU1NTX5+fi4uLpycnMrKyqKiotjY2BgYGDc3N97e3uzs7EVFRSMjI+Li4hQUFLS0tNTU1I6Ojri4uJSUlBISEtXV1bu7u21tbfLy8ktLSwQEBLCwsHd3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3dyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAABgFVAAAI/wDJCBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJEmOvKSVTqlzJsmXFKGK2FHLksqbNmzg9wklzZQsaWVvUOMtJtKjRowLbvNliZQyZOU2S9CGCCanVq1g9qjKyBZAhOAQpTdLjpwuSrGjTqlVIxw0XQXKiIBTyZcubNmvz6r0KR5GPLUOCLIQDBNCWH2H2Kl7sUsuZLWywPCwjh8cdN3QYc8zDhIlThUE6C9F89FEjSIWQVZL4xNIWH4rAkr64acuWTgs92Q41OycpU1BOiclkEUukLWe09K5Y+3bu3cttXlu1pdiSjJVaFYLk6lH0iM1xK//UvYX395VLYm3x0qsjrUOnoJgidb5h+Ofl65fMJCa+LfofLXHLFqtco59C940H3YEgVYLMdnY8Q1IvXmwRy3UMFpRgQuSZlyFHgxyHhnIpkWKLLsIR9yEZGyLU4YoaPTHEFruAI9tKz9iBmmoftnjQizBaRJkgXOAxx01aoLFFJINk6KNBQAYpERyGGOaLKkTBAc4ugD1xYHOLSCLmmGRKEsyCUkJEF1OfGTUHHlzwIEcZ9TVn25145plfmg5R4oseXt2IlCq+bEEFEILOZqeejO7Jp0JzEJOEIMbIlVYyo2zxxWjLNdeMJ6CGKqonoaD5qEFwEBINYILlBUcpgOj/MQklvTVnCX4enkpQNdBAJtliURgjSBJNHKmZrbjqStAUewSS2mqkBaHEFrlUkWheyCro6KmgYJNNit9hwcYWs2izWLYcmsrnNllUh+F5lQxzRCDcoKQXui6qG6QkXBb4IX+nJDGEsWrh+6O+H3YTzjd6hAPgijoAlUUOaxkMJcIHIgEMM5A0MhSfuOCwRQ2JpGVxQVF+SMMvyJF46m9QwBJMN1mdTFDKA2Giibm95THDazFc++gjrkDCjCdnWWXzQDgnBUMgL7igmQwtXHLHCpkpa1AKKGxxwwkfuvDCNzAUAcpecJjAyxZGJKY1Qn39VQIJH44gwhZ/OJFXCCDY/4XX2wu1dcclH8iQIRzUeLBFDx9jtYYKZKWRNOAMhfHDFrx0IHR0HGwARh8a0GJV56n0kUFVlEPURjNbYBDChxdYoMc3GkyekzCKs9J46hAh0YUfkIhywYcV6LJFMxTkNAELWxxDE+8VYZJBH2BYw8HhHayNWE2v1PHNNBJAC71FzrCyBQQPfCjDB1Zj9hAih7wRDTOcvNHAGhBVIsE030TwyvgbkQQDtrCAZXwoDwp4TWwWIgRONGoLHkBFQxwxwEVMAIAdqYQD+Oc/lbEMDVk7iCj0pAc9uUIhcKgFBIWBQZC8IgLfc4D49KMxOySEebYJxAL4cD06gMMMkLhTMf8UkgAEXK+FIVneFhggCV0Z4044wJ9BpPEX2+ABiTgRBgS2cAAD8MkZJVySQpAgsi1AAhFYvAkHrAEGQWTAUjBS0hbuEEKE0KIPttlBGnESOz1cIQ2b+w4HgriFAjTkTFv4hu326JIQYGALo0jGh1phmz44BBSBsE0VGIkTOGTvNlg60Cxsw4aHrGoLt+IkTtZ3CS5gTT+5sM0eHuIavKmSKCQoAY2Cdh4p2MYaDwmHbQhwy6Kc4AY+GcB3UmEbZTzEGraBQTGLgoQ4cCxCyymEbRDwkAzYBhDTNEo3GgALXXyiN7HcwiwdwpUlhvMoiQgFnWZjBttE4iEV2sIt3smsT4XYoJIOQcIpNNnPghqEDmG0RUMSYJtTGPShBOnbFrhwxIRggge28QZEN6qDMN5gIe1KpOg2ClFh2kYA9iqIKk65hQyQlKSPsc03biGJsyAhACwgJGBe+tLL5UmndyoBT3lKgyoyahcBGKpSpfECRsjiCAQAwAsuqNSqWvWqWM2qVrfK1a569atgDatYx0rWspr1rGhNq1rXyta2uvWtcI2rXOdK17ra1a0BAQA7" style="margin-top:1rem;" /></div></details></div></div>
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">TextStructure["The cat sat on the mat."]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhpAGaAPd8ANzc3Kenp8zMzNLS0peXl/Hx8fT09M/Pz9PT0xwcHC0tLePj44+PjxkZGZqamjU1NcHBwbq6upubm7W1tYmJidHR0ba2tpmZmampqTY2Nl5eXlhYWBISEqCgoBEREW1tbcPDw7GxseDg4GlpaaWlpdbW1v7+/urq6gwMDO7u7ltbW/X19fr6+pGRkSwsLD8/P52dnVRUVJiYmHFxcTw8PKqqqnl5eUNDQ0JCQkRERBAQEIqKivn5+djY2KKiokdHR42NjdDQ0GNjY+bm5s7OzikpKQ4ODgkJCeXl5XR0dA8PD/Dw8PPz8woKCoaGhjg4OKSkpB0dHbKysjk5OWZmZsrKypycnC4uLoeHh2VlZZKSkllZWYuLiw0NDf39/RsbGxoaGtvb27i4uI6OjpSUlC8vLwAAAIKCgklJSRMTE5OTk3t7e25uboODg0hISN3d3a6urujo6HV1dRYWFqampnBwcGtra/f398jIyMXFxaioqPb29v///8vLy9fX11NTU7u7u7e3twcHB9/f3wgICNXV1QYGBu/v76GhoX9/f/j4+BUVFSsrK7CwsHd3dwQEBEtLS8LCwoiIiAsLCwMDA0ZGRiAgIH19fR8fH2FhYbm5uXx8fFBQUEVFRSMjI+zs7N7e3oyMjD09PZWVlaysrJ+fnzQ0NHh4eIWFhQUFBYCAgGRkZPv7+8fHx8bGxlZWVqurqzExMcnJyenp6SQkJK2trbOzswEBAcTExCYmJjo6OqOjoyoqKrS0tNTU1OLi4hQUFDAwMJ6enuTk5DMzM2pqaq+vr+3t7RcXF9nZ2dra2pCQkOHh4b6+vr29vfLy8sDAwGJiYvz8/Ofn5yUlJWhoaM3Nzevr6wICAr+/v19fX5aWlry8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vLy8vCH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAApAGaAAAI/wD5CBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKhRomoEHV3KVGLSplAtBjJDtSrVNnyeBmWV6JhKrl6jjgwDxKBWoGDFZvwEqC0aT20BDcqqNGgcM2FU3s2rNqSeL2brAt3bd6OQMgXVEBJaCK/KxnwLexwFOPHioJAlZzycWIkiNmkWZdlDENEVQ1E2sfII5ckRI39+DQwSLUqTMnAG2rFatU9EWT8WETKlhcfs2rdzC9zN24zvksy26GiSQ9ZANVMOZdIhmrRMRs0nCf9U4xl099KnU6/eSAmKpTSa6kziJE0gbdu4dTd3rpkiZ4JqGCEKFaScgg0qA11iiCqu7AJGHR3JYYY2sEgBSSUCzULIFrXY8sotz8XhByJmaOLHiXdA9IkSr0TSChm5PKchhx6CKJCIJJqIYklxfMGLD6TkIAge4wETjDDDGHMEgjKB4ocdyJzoRzLjCUiggUzyoSCDDkLIXi5+aNPFMnncEggfM3b4YYgjlihliv1J9N91t+wyECS6CKQMJVoM1EwqcWzUhxlOEPTMQNMM5AU11RCUjWMT5WGGdQclKtCijQ70aGQmFaNEWNIEk2dW2BAp0BajzpRIZQDWeeeoe/b/KdCfgWpEyTZ80JGLQHPIaikfmDoKaZz+IQagYHycYolAOxDiHbCGcLORDYYYl5AyNUiSC4aaDhsRDzSAscMbCGGrLbcCbZoSJpkQNIoZn9BF0BrL0rRqYAQpy6yzikbLnp2wECPQF1wQZO62wnJKbERzjofsvXzMgI0SFFN8CxQbZUJNQoh4gkwMaxDzQsIVsWIFDo+40AILA3X8ccgjd6swSYQkQpAUZhQi70AQq8rqdQ9XJnHFFmNsK8AC80GwQC6DLDLJC0/U8M4CQYwFIW8MorXWK2zkyBH1GUQKNsJ4IZAKMQskqR8YpdACCkIINHbZZ6fNx9opRRH3QNuY/3EC1Xz0LBMqyODLc2VXZ731IF0fzUfAAxc8t9l8oE0Q3i6ZEPZNU58VeGUlpEJCSLiYMQZBlo4QC0Gc2C2CGSFQlMIhBCWBiUCqs+467Cl94EEKlxJDg8MECR5TB5QAf2zxoIseEiVIR85H7gO1TtDrsbf0TC4c+IJT50EPhIogcgCSzQ4bdCTELavA0Ys2yCjCBwyTRGJCGBpMYjcfGdCCQTYXqABEHAEMCriiAiRAxggEQj/74U9/Benf/wJYkkN8gRG7qEUnBCFAwBkPJp9oghssEAEskMZzPRtf+c6Xvn89LmlLa+D98rc/CQKwgyiBAFVOxzljAY15BLHFA/8I0YVKQKMjJthGMAThgRh4jw8m2EQDmvCEGjBgfwtwwxGUoAtnQEQaHcCBDo5QhDNYK4pTrOIVC5LFLXbRJCLYwHRuYCoP/kwmkVCAIZABiQXYMYhDLOIRXQg5pRUMjVS0Iha1yEUvpoQJsUhAD6JGyUpa8pKYzKQmN8nJTnryk6AMpShHScpSmvKUqEylKlfZnwm48pWwjKUsZ0nLWtoSln9LCBFuyUtZSqsh0uilMF9JpYaIYJjITOYtddaQBSjzmdCcwC8REsxo0rKYCBmENbeZTEAgBAHgDKc4x0nOcprznOgUJxMU8ot0upOcbGuIF95Jz3DWiiHHqKc+95n/zl8tJAX8DKhAETDJhMxzoOa850E+gdCG7jOerIyoRCdK0Ypa9KIYzahGN8rRjnr0oyANqUhHStKSmvSkKE2pSlfK0pKqAQhjWAYJZIOQSFzDIstgGUdWEIoDDCQMsDiJLGpBEDFkYyFWoJ1FRgHTMTgAhxwZgp38UAI+SNUjL43pTBNiU5zqdCM89alAgCoSpo7BqVCNSFcdQlQ+5PQiaogXC0qghlkgBBZ+rMjmwAoEMhhgrEE1SQEYACcTjAIJSFVqRUYRKGmUAAjx8kh98OAKgexVI3Hlw1zrete8UuSyGVlBX//KB7KGhLF8cCxkKYLXh/AQtE6JLB9AYAs+/7ACEATwgc5a0QIJDOO2uWWmHsJAgBVgYABWkAAoGkEAW5iADyvrgTV6cQFjHAq4uhXIcIu7kBW0IBu1LW1Q72CLUcAgnmN4rltNcAhN4EECW50IHQYgkAU4oL4+2IYtUpSNHpQiGVaoAgy2gQuKoFYgEvBDCjSBCzstIL/75YMxSiAMApjqGnRQAwnsaoIIjGIUBY7DLgaxjW0IQMR8IK9544mBN/jACmJ9SGYFQlvb4ja7vPUtdoVLXOMiV7nMdS50WSBd6lrXxsHVbo+7+93wklXF5xVIegWyDPa6F740ZciB+ZDgYQRAIEP4MjSSoQcZAOK5JyABGUjxjBwPA/8WzJBbnJmBiBZYIS/GCEUHpLEyPiQDBqMIAWnGXOYzK2TGfFgADGbbCFakgABDeJwfQdDoR0daDY2g3SiaYYJshGIaipCAbFZ2gBbEgRW1KDClHQ3prGSaId5lwQXmQtZABEIasxiFV6a83k8sQwB8aMWXJ3KAwDbjiHtQwzC8kA1j8KERMJiGNKwQAEUswQHYhAhqvZCMUMziBC2AxgqSvexm88EKerC2A97gBStUwASFcAC3fXCHAmghBSimLB9QbGtc65oPo5iAFxYwBtgmBNGKZjSrI93aVVva1ZrmtKdBLeohl/rUqVb4wzGt2ITEetbi5UO/c71r9VbZ18D/FrZDtt3tWXgZzF+WQgf2sIJtMMMLDlAGK7iRm9bCWc58cAACvFAIYUhZICs7BBmkHYEJ8EHmNLf5oWV7jBYEHbF8cMYRW+sArGs9K5EG+E0HgQiBWMB7pDbaAbzYdYF8XQ1hZzIflCEBVpBVC4fiAyCsw+uTj8E4n+gARVbAANI4IFEICOwK/t4ISlkBFAIRgNMlMgoGLGMM2yACH8D93MQLZPE8eHzkAxEHKwxEGEP4hQMWoN58VxbFeBfI3gEOeYA/qyGIrvrV3b51P7Y960eEu0BGMfay8+HsFlc7270e/LgrxLtzr/vd8z77vpvgE3/nQ+BXbnnMa/7lVo05/wQEIgVlLMBOKVaGpB8XZz6QIs7rZEUhCHD0IfdBE59fxtPH/3T1H1y2CQcEpdABBFhgrSWABNgBBaYGjTMKXcMMgRUIaMcCBxABAlEBXoSABZgVjSN3EgYCQMUCZSEQsuBFvMYA17dofHAMgkcRpFABcSABAuEKo5CAHWAAjVBQVhBZphURWyYQJ2B0fECDNmgAOwhYb4ABA0EK6vdeZOAM0uB6+7YLIjgQJQhwpEUAt8cQCLdoGqiA6/eFC9iADxiBE1iBF5iBA7iBDNgQ0PeBITiCfHCFJ5iCAsGCK6dQfAB+YfZ08dQLylAC2TMQPtd+78cHCAADpRAC9McHPP+0MtBQWVS2B1Lwh/6HEIiGC7W1DevEB0twKK3FiQLxiVnhHQ7IBxAoEBJocd7EBxjIB6LoiYeiBluIEG9YAGSAB0GlBZ3IDUQyBmZzDKFwfUKIhxThCzUAApFgHxYILIjVCP5nBXPBB9ZwJpSnhyfQgkHQjF6AWKJHjRNQegNRCkjwDH91DIiQDFIIe71IJKfIB1oIEZm4iZ1IiqFYj7NoimWoimfYiq8Yi6RIi25odXyAi7rIB7woEL7oiME4jJ9QjC2oZXo4DHRwgTFXUIAoAqPDB3vgGz4nAgJBAMxgAMsQLwXQiI/IAvcnEHuAglKAkZd4EJnFCj3AWdwQCKz/cAgE4EewMBc3mZM7WYrDt48i149pyAc/qZN+JJCwRpB80ActEFSBoAlecA2jEC9kQCXQAATEeIcRKRE80AIXYFd88AzbMATSgAtKCI0CgW48UAASMI0+iI0taJZoqZbnpgdvKQHK0G4IwAcl4ADS0AewwAR3AAW+kG/LyG9UaZXx8o7xKGPxQpM2iZNK+Tg+aZlByZSnmIpFyYpHmZSbWYsH8YZPGZUi15hXyQdZyQdb2ZUr+JUK8YN8cA3L8AysgAEXKRCAyAIEAArSYG49yQchwGlvAATMcA1qcAcm4AxkIGX1kXRkMAteAAi19ZK8GZNmYXktEF88YAHbIAPW/yAQVUAAw/Cd4TmeQglwRLmKpOaPXoSe4jkepGkQpukFPjBeUjAKVlBVfOALpSAMuwSbxkgRIWB6A/EGpaAGsFAAzxaNuOAAMlAFBkaXCbqgDXpuuGAFBJAHQEgHZLBhfMADxqAF2wAIXoBiv0AAfYBid7Cf/TmUIVmfmMid3gme88kH5XmeOKqenNmeRumK8dmj9DmQipKfKQaj/gmgAjoBBCqbCUGbrnkBu5AMR4WdfACIVrULaoABDrqj06AHDuBedtUMo4AICLALRxQCF8BnLNMDgCZoTweTLQUTSVWneFpSd5qnfApSb/BVfRqogjqohFqohsoRv5CoirqojP/aqI76qJAaqZI6qZRKqVgXUgZQqZq6qZzaqZ7KqEugFnQwqqRaqqZ6qqiaqqq6qqzaqq7qqs4mUm/wqrRaq7Z6q7hqqmnFFCbQq776q8AarMI6rMRarMZ6rMiarCSVrMzarM76rNAKrIc6rdRardZ6rdiardq6rdzard76reAaruI6ruRaruYaEmH1U4F1EWaFVtoHpef6EOkKWBnRrk/1ri0lWn5FrxiBWqr1CdsXrxOhr6TVg0vVWI8FsPBqUt4FXvQKZehlclb2XvE1EFuWYJ9QChAAX3HWX/9VAKRABqMgiUFwAZjGMs9ACqNQA/7UrQ3rZONVXlHmiBLbXhT/m2XDd08Yq7EcywcemwwgK7Ika7KNgLIqy7IS9XG0JpW3RnI0S2XX92vBNmwWGyjc5m2fEApBMIRfBm3SFggRwArHsAwG4F3HwAN0IEB0IAv3cwHy861KG3Ij92/Wh3JTWxAsh7Vay7XPFm3SALZiS7Zmi7Zqy7Zh4LYRBX10Z3e7SH18J7HYB3iyWXmXl3naxwAsk43PRil7wAomMAtacAwsoAYlsB5LoAXr0QHkArdWt7jTJ3uPC7WRi6/u0n2W+wmYu3mC13gs6bmgK7qka7qoKxCqm7gEaQwgCAtVSIImqF4o+AkqWKA5WxAZKxDbl4MCMQ1QIAHGQAZeoQxQ/7AMjfAMC7AMNggA4PqGyBuHVti8AvG80Tu5eli9+Iq9fKC93Ou9cxe+41u+52u8AmGQu9iODLmCDgmReDu/LXi9/gcDf8llx6AIwLMH0nQMKogm1uKtt5iLA6yQv9iQT5rA1LvAu9vADywBETzBFXzBs5DBqmSaUCmVqomVWsmVD+mVIkwQAcvAwxdnPRAK1xAHBHAC0nCTJtAB7/YGagCo3ArDqDmVVbmarfmaNxybOTwQO1zCPcwHPxzEQ1zEgXDESbzEAHwpSPqi/LmkATqgVSy9AKfA1qvFfDB/wgABEYAxIDAKakAK65QCekAGHdB+rHuk+pnGAsGkbIzA7v8Cx/Xrf3Rsx3isx3zMB34MyIIssJicyZq8yZzcyZ78yaAcyqI8yqRcyh4hAraWyqq8yqzcyq78yrAcy7I8y7Rcy7Z8y7j8ytppyitxDRXwy8AczMI8zMRczMZ8zMiczMq8zMzczM78zMXcsrw8zdRczdZ8zdiczdq8zdzczd78zeAczuI8zuRczgbWVPfqEVdFVVtaEY3AKfYqQAFrzh3lrwn7EZMliQbXEO+8yKmVsPNMzxt1sQrGYA4GYSkyYRV2YRkmoh32YSE2YiV2YnYCsQLRYi8mVtbgAFpAAl7Rz1U7EDu7sSTQsf4FtCE7svZBtEa7stIs0JiUt98WbuP/pmzM5mzopm7s5m7wJm/JQG/2hm92om/81rT/FnADV3AFsAzXIA2AYIEgPb1XOwtZu7Wu0LV+C7hjW7YtcLZpmyuGi7gwvUmU632b1wKdp3h/940CQHoIygeop3qsdyND/Xp2Ent6Zx2jUHujsAfS0DV34Ay98GzwbLuah7uZu7uc67uhO7qlO4rDywfFO9aaRJtBOIM1mIBGyIOwkIRL2IQS8IRRWNdTuLxz6EWjkIV74AXQcAFQgAGDHdVvTL2lEMfPVlD4273fy7/ka74JiL6UnUmWrY3c6I21Zw3h+NbkaI4rmI7reNcEDJl74Ac+QBqFENvwzMg8PD8nnMIc/7nCA9HCwS3cFlqWZ5mWSuiWcNmXVvCXgTmYhXmYiTnUi2knUOyY7DmjRFADXqAIdBA7sk2bWfygW9zFQkzERozEJqDETDzeUTPcF8qgDmoFG9qhHxqidkWiJoqiKsqiLqqkMgqPe6AIsLANAVACBKAMAa7dcvzIdzxbktzHfxzIDq5Ke1rj1XzjOD7Nf7rjPv7jQB7kIWECw1DkRn7kSJ7kSr7kTN7kTv7kUB7lUj7lVF7lVn7lUu6gvMwKudrlXv7lYB7mYj7mZK6quzrKXpDmar7mbN7mbv7mcB7ncj7ndF7ndn7neJ7ner7ndq5eQv7ngB7ogj7ohF7ohn7oiP+e6Iq+6IxuSkNVVEelEDqOt+gszwvb6CI1WIV1WIkVpQgLWQGN6SY1X/V1X4mG0D570gE2YAV2xSPdsz8btCrNByV7smV5tC8t6qNUbLOCbDZtbl47bdV2bdk221Nd1Xwb7FotuF1NuGDdtm+r66ZEeIaHeGrNA7x7brUneXhr2Jeb2Jvbu5/b2MEL2am7utJuSi8Yg5hdhPZ7hCHnzzpc2/WL29ur2/srvr39v+luSsiojMx4Kc8YjdNYjVds243MQN0twd/NDRYc3i7c76IUlmMpEHaJ3gSel3spl9OrwySc8aPgw0B84GAsxgtOxhJfSgdKEAoq4RlP4RJKoQf/T7vb7eKRvMcybskpv/M83/M+//NAH/RCP/QYpQlGf/RIn/RKv/RM3/RO//RQH/VSP/VUX/VWf/VYn/Vav/Vc3/Ve//VgH/XZcABkX/Zmf/Zon/Zqv/Zs3/Zu//ZwH/dyP/d0X/d2f/d4n/d6v/d83/d+//YPTPSCP/iEX/iGf/iIn/iKv/iM3/iOH9yfoLLb0Aih6hBr9fgXZQIOIAB3IA14YHwN0VqYf1FMEApnJAUs82D6lSKEZmYm4GY7dtEuBmMC4QcDFranvvqjr0kdoAfKEO3kdtNPN3M1F2cNV2mthtQEJw3HQADHsAIk0AfBb267j0ksgAckwAB6MAyI/3jtUsB/5bd+v/d1ez18e+AKkf4JSOB5fAB61a9JitAHY1AARKjZlZidYbiGYJjaM6oJ6gkQfPi4GtXBYAcDAhUuZNjQ4UOIESVOpFjR4kWMGTVu5NjR40eQITX6qrUwQKEgEQR6QcJHSg+BvZTxgbWAzzYmApc84zNqhUACe0BEEhgnWcqVLUUuZdrU6VOoUaVOpYrRAJkgPLyAGlXg2bYh0nBhcAmTj0yag/hwC8TqEAGbPoHuiSPj0J4AAr6GHVvV71/AgQUPJuw3BZxtagKIEPimlBpYBcrGnFmFwDAeFrbJsCZQLp+gfBBIGCVGGh/HkCUXZt3a9WvYsWXPpitd2/Zt3Ll17+bd2/dv4MGFDyde3Phx5MmVL2fe3Plz6NGlT6de3fp13wEBADs=" style="margin-top:1rem;" /></div></details></div></div>
+<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">TextStructure["The cat sat on the mat."]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhSAM0AfeJAKqqqtnZ2dzc3MjIyKWlpa2trRAQEI+Pj6mpqcbGxsLCwj4+PicnJx4eHoCAgODg4Kurq15eXtDQ0MXFxaenp0dHR6Ghofj4+EFBQdLS0hEREY2Njerq6ouLiw0NDSwsLNHR0fLy8r29vTo6OggICLy8vPHx8RISEm1tbdfX18zMzDw8PPn5+XV1dU5OTgwMDNXV1RoaGm9vbz09PYyMjLq6unZ2dpGRkT8/P1FRUQEBAUpKSoqKioODg3JyciEhIVJSUgMDAzY2NtjY2Dc3N6KiohgYGCIiItvb2x0dHfT09LKyslxcXPX19ff393BwcGtra3FxcZiYmCUlJRUVFbGxscPDw5aWll9fX5OTk1dXV9PT01ZWVhYWFqamprm5uWFhYR8fH8HBwd3d3a6urujo6EhISMfHx/v7+wAAAM/Pz6OjoyoqKlNTU9bW1rCwsAQEBEtLS3d3dzU1NZqamigoKC8vL6CgoFhYWLOzsxMTE87Ozg4ODubm5ikpKZmZmba2tgYGBkxMTO/v72pqajMzM+Tk5AUFBcvLy/////7+/nt7e25ubmdnZ5ycnMrKyi4uLuPj47e3twcHB3Nzc9ra2pCQkBkZGSsrK5KSkllZWf39/WlpaZ6enjs7O4eHh2VlZSYmJsTExOXl5Q8PD09PTwkJCV1dXaioqJeXl2xsbEZGRiAgIH19faSkpJSUlI6Ojri4uDk5OWZmZi0tLRwcHHx8fFBQUEJCQkRERENDQ8DAwDIyMvz8/GJiYufn54SEhK+vr4mJibW1tZubm01NTYWFhX5+fvb29lpaWklJSYKCgpWVlaysrPr6+lVVVbS0tBQUFNTU1OLi4t/f3+vr683Nzb+/vwICAlRUVJ2dnXp6euHh4b6+vuzs7N7e3iMjI0BAQBsbG2NjY/Dw8AoKCoGBgfPz8+7u7u3t7RcXF4aGhjg4ODAwMAsLC8nJyenp6TExMbu7uzQ0NJ+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fnyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAASAM0AQAI/wATCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS57clhsiRE0oa95s0TJmzqB5NkqTBlHo06gPji6dujVHaXliy55NOw8ggqtNu97NOTfv3xShkB5OvDjpSbhJ6x5sCIk3rM2fA/+ZDkmkhr4JR5+uUrjx78eTs/8mDCkNJazlz3PvyShNIezKC6dfj1JJtfv4oZHGgx+/dIHZDXaJeVgNqB59OmniHnzjCUgggixZQRoWCwUo2CEPWoXhgRDelMuCDFkY2IYdriRhGhQqtJo1hA1CGodTuZhhiTXZAWKFpLE4mIww0kjSiSkmtJobiSgiSRtsdOGHL2oshIYXXNRBxRSCSOHET03cwQQtRiQhhBxbKOTEEpx4EoYRkIAiCkKopAILMKqQ9qUcdNbpSkmKxDLLPLVQ4cctr/yy0Jhlnpnmmge1+WacacxZJ513NvWLMeGwYoQdnFyTUDByECOQkUgqyWRaYvxhySfHkJKGEY/WuUxBQxb/eWSSSzap0JNRTlnllTkdI8c3zpiDSS3PTJPIJpbYYYQZYR5EqJloqsmmm3DK2SqkPoIEJI5pUDOKLsZho01C3YDznThi9PRKNN9hM845BqGzjR7ggYKGQeqAZ1wbJEXCDniHJPPNQfLS+529+OpbHL9MfWLKd7kIatBo7STybbjjnqWFwsTpAStp3oJbnLjkmmscujm5k0YzCg4XzyacdAxPQQXXe29B+XJMGsPZdrStiqTJY0Qal/jSCihDpzFJJQfRE0QaQQBBxxJ3+DJJGoGkm1MvXAznhw9ZZMFJF6TFUVAZBptSSg9/8LCDDqRtY1AOONRtYxq11K133ceM/+SEH6R5csMwNXgRxRGk3WIQ2qSpzbbbcKchd0F0201a3nvzzZQvpAVRCg1XyJB0LcZ+HAMMMRBtNNLHMW2WOXuT9kLmdbvwcRpCq3500ks3/XTUU1d9ddY4qexJGrLYwAZp7eHSwg+ktUIQ42k43vbbcc+t992YZ953zz5PyK07cKzDwkDnrEBaFAaJAQfeKhSUQi1piMPrTSiQdkIzBTVhizs6IkgOqMADExSkBCRIwyEMkZBrvGglRRBfQTbRjBFU4yADLOABE7jABj5QKlkgjTgCmIhzJIM0hejFx4JwgvKdTyDpWx9bUMgg8pkPfepLA/sK4j74yY9+9ruJyv/SAARFJAId5SCNDARSCbjNgHIENCBBEKhABiLEgTMCX0h+JiTSuEMEBgEBaSpGkF58oHpEMkg3SCMFnLwDbh6QBkI4cJBfSNEg5iDNBjyYRZNEgTRLiIgdEZLHNOzxih+ECjk0gLUMGGQT4SBNJ273xTCOcYY3AloaKlkQMaaBjAMxIxoPssY0tNEmKiMFHQWCgTQc4QIDQdwPCjLIgxTykAfBYo+06BEuImQ1ZEDIgMpRkCpkDyF1SIMycAIE0txgI4ggjSb4uEuS8IA044CmNKkplSuQBgoIUQNpeHG7YB5kmJh8T4hIY06DoJMgxpRcQpK5TFSmoQIEeUYaGkH/kDms6iHRTMM0EdlHXoYPRdxaTkGIQJqbCQQMpElBQk6ojps4IYnuuF9FyKGCN1wzDbrgpkrSEQbSsIMCsKQIRz1KmpAStJpKKQZpJpCQ5emgD+JRKEEYmgaHooWG62zQQhtKEIimQaIIoagQ70mQjfFzIAyt6EJW+lGX5jKRBv2IL1UTn4PggDQa9acOGkHWspp1eUG4CQxIk4uKSIAHcaBfcTwhUpVQYx7DeUEOiFE6hrw1rsah60ulEgqwJiQCpNHUQEQ0kK+mQaNnAWpCEeLYsKZhrGbNLFqXis+BOHWnaZCqQf4qV+II9qoFzapGtjqxrhqksgQpqc6gdhMs/55iImQoxHA8wA4wtCITgaurSjZRBHZEjjRzYIYSEpLb3fb2t8EdbFROsEmF+IA0EMgpZQ2rFslqUqeN5a5AZKuztNqzswL5LFRDa5Dmkoa3vgVuGk5rEF2qVlsS7KJQCQLbgSQzDTcIm4AHHDZP2eQMpMmGRGZBGnVs4xGbGIgTootamJ7kF8Rog6pIY4RgHITBoX1whAUy4fkK1yniSAMcFEII0kBDu14V708zqV/wCqS/AvlvgAlMYAPXRGXoTYR6BRLVgoDYwRCWMIXri9X7boS1t7NxInCciFamoa9AeQBpPhARZpAGCHdUsokRIoYmu4QFVYjkZb9QEC8TMf/MJF4yD83MFN2mwYoH2QFp4rdY1xaEymeBmzonG+PHEsTKWP4JkJu6T9CKNhFuBrNBSkzfOafWyRaBMoxfK2MHkOYPRGkAaYYAkfJEA7JxHvNBVECap9JkGWwtiKlRnQhKJ4TVjY6KDEhjAYQgQ1Wk8Cljbyzjs7wgDQxgkJSp7Ok0gFooi/ZsronM3oHM2llyJgiuXc0VRMSCHHLRdJ/3G15DD8QN2EgDK5YrlOumoRgQeRgO5pjtgXCANAuwySYCkQZwFETe9Fa1Qe6dhnxHRQGkiYcKDXID0kQgyts1d1qWNwlaQ7zQGkW3utkNlGind9qJKPJAAH4QgleaIAT/N/hWFNEGDoMgLuIGkJ/5W+xxkMYM8DLIBaiRk2psWAYjJggLbJCJglAhDVTIOUESAD2BGwRxQSB1Sp6AghAgZAukWYXRka70gTC93rGEmtShYuUdEuQdKoOD68a97GKbhXNp8HGNIw5Zm6cB5wfZefGYKm1ui1wgR0+6Qb7u9IJAfexZgQBxrOqWmCdi2FMudgjaQZof0OGCAhmDMBpQCCPiBBpPcw8CBiGQXzCDFWkoB5axgO+XF0kBeNABHPhQeIIAgzRH+MLNlCCPLIikBvpbhBo8f6xYoD4NVSgI6wvuekXAXva0P7ntca97gfDe90r5hsGK8QgjwkMYQzxA/2vJTWyJo+VE5ZBCzlmwhx5oFPKAnnzlLz8QzXOe+DTxuJBB/vdELH8Bzfd8s1d7A3F7rlR9iXB9VXEMxPFobeF48Od2HGAGw6ED6nAEBjAc4vAAOpEHBkMafJBEpHEIHVAQo5BipKEBrJBAaeAH79By0idhlEcaJCAOHjCCcMYRzrABjASCDEAE7bBhaeAABnGCw6GCLOiCMCgmM5gGNXiDCpSDRWENSTAckyCE2AAMXEV+kWd+aLEaUGMEH3gbbEd3A0eBpGGBGKiBHHhejOZ31SYQRpiCK0gaSkiAJNaET4iDVBFBwzECMJdfvzRz5UZrigABRHBcpAEJWZAZO/8BD9uQNMPBB74wMAYRCTmQbsNBC8SgQu0RgwMxCOPwPsRxAnjADSPRBFewAqQ4HEFQAVpziZlIHJzoiXgoEKLYivpzikyBDnLQg52zCmcwiFwIaGehCMKQgcRBAqvQDZv2Z25XJIioiGnAiI7ohn3naAWBiZpIGrWYCJ+4ELlYHKaIilPhDI7FB4gCGtUgCRZgAYCAU0HhBm/QCaiQAM6wEH3wBtrwBmsXESFQA0WgDQWwBUFXEudgBQXgCARwDeCmj/zojxQRkANZkAfJFL1wBhRAD5KQDoiBBglAAcRAAQOADCDRju8Yj1Oxj/34jxBBkQRpkFexCV9AARKDaTj/mZM6uZM82ZM++ZNAGZRCOZREWZRGeZRImZRKuZRM2ZRO+ZRQGZVSOZVUWZVWeZVYmZVauZVc2ZVe+ZVgGZZiOZZbYQVmeZZomZZquZZs2ZZu+ZZwGZdyGZdjUBHeMJd4mZdwKQEd4Qx6+ZeAiZYXiREqEJiGeZiImZhomVIbAQKK+ZiQGZlryZcUwQKSeZmD+RCFeZmc2ZmQSUIM4QWiOZqkWZqmeZqomZqquZqs2Zqu2ZqgCRHT8Jq0WZusGQsd4QS2uZu8SZoLtxHQ0JvCOZzEWZykeY0aIQ/GuZzM2ZyniZsUoZvO6ZyZ6RB5MJ3YmZ3NOQwQQQHe+Z3gGZ7i/zme5Fme5nme6Jme6pmesfkQ07Ce8Bmf6AmdG+EE8nmf+Amev6kR0JCf/vmfABqg4ImcGSEPAnqgCJqg48lm0amgDlqdDZEHDjqhFJqgZEiWGJqhGrqhHNqhHvqhIBqiIjqiJFqiJnqiKJqiKrqiLNqiLvqiMBqjMjqjNFqjNnqjOJqjOrqjPNqjPvqjQBqkQjqkRFqkRnqkSJqkSrqkTNqkTvqkUBqlUjqlIboHCXClWGoNApCPQ/EI+MgTyHClZYAQApAA1+EUSnClXVcQA5AAY1oRo5AA5tgSIIClWDoAAfAfPvELCVCXCMGnfqoTVmqnCaClXCoUXnqoORGmbv9KpmZKFHVKqHiqp1CRqC7hCDSQqZqaqZYgCvvpEIrQCxBKEsxAAwR6E96QqdrgUwPxBTSQAE+hCFdAA++AEH2QqaRXEYhAAwrwEkWwqcD6BlKIE2pAA/IwEJvQC8RXrMe6E5gKrJzqqRIRqqM6EqV6qjaRqjSwqgfhqrA6FL8KrZkqrCpBrR/RC/t5rZdKA0vwDu6aAHnwrM3wqQyxq73KEuq6E9pKA1bQra8KFddAA712ELtAA5Giq7zqqzQQDO7qrgoAAZlaBNU6E8w6EGRAAzwnEBXrrOzasPAqr/S6EPbaEvmqE/varwbhrUTxqwzbsA8bsRPbESPrETdAA7//WbIrgalyVBCPsAE0wGcAlbAsga49kao+CwurRBAq+xRlkKkeaRB08LMXMbMt8au2QhCVkKmUyRPmKhAXm7FFIqo8obMG0bNSCxFUqxJEyxNGSwNIm7L/Cq40cLUDkbU0sLUmkbYbUbO/ubYtQbYGYQ00wAyKWq9CqxapmgWSYLD4lwhL+xSdQAM0dTY0sAFrKhF6qxJWexDNQAOSQBRfKxSAWxCCS7hoe7hpkbiL6wqN+7hBsbkG0bmfixKZmxF8SxOjSxBoMKtAKxBDAAid4AhkUAme1wQiQAE0sAYigHi/G7zDi39nAEbwAAGpcEHvIAKbMA0FIAXKCy8cUANr/0AHBYBniSAKIvBClSAC6cACCkAPqeAF78CqidC8wku8BBG9iTC91YsRiesEvFsQrrsJiPAGdLAGX5BoYiACn6oAInAzHCACApAIEkAAqWABJcBxJzEA22oQCkADCFAQvTDAdHAHgPCmAsECIsAiAVAEjpAI9noBYkAPUlAAAxCyIQG7BdENNEABAlEGIvANipAAxHChIUzAJGzCicANIjAKlnkHf0AGiDCYATAM9NAJ0NAsZbQHAEAHjgABbkB8o7C8iWAIIhC1wSACYxrGiCfABGzAiXa9m4AOgOAIfwAAATASuTsQu3u2A0G/zysQxou8ysu8wFu/0Cu91Gu92P+rvdwrAt4LvuJLvuaLvurLvu4Lv/Lrx/Y7EPirv5hnEf37v0obtwLBxgV8wDykwAXBwA4MwRJMwRaMwRmBwwShwzycCNMgAkiwjSLgOmggAqbxAAXwB9qwBEgsEG4ADY6wBvIwCoB8vMkrxucgAo9QEEogArWKrNZQj1JAALtwR1sgArBgrOdbvuU8EE0gBgDwB6jgkLoLzIkgzMRszBWRxwMRsNwpEGiwuDRwAONMA1WgQukArM26z5nqz5ka0AMRuRyQCZk6pr8KAhuQCVFLA3QwBP7sCOMMCzMjEH9gqgIRsClADzQgBaVKA/yjx/yM0AD9mwzt0DRwzBORuIn/kAI0cANh9rghQACcmqkbsI6JkAU0ULilmlJIwKvDQANZUNFSYJIoYQIPXRCY6noCYQKukKk1m6nVDMgeLA1Y7cI08AXP6rPJa3UmQcsDEQw0kAe+K7n8bE5WjdWautVg/Q7a4NOZigpOnQhoEAs+fQCZGgyM6QwWgNWA7bkDkQHGmgggAKykptjNmgg73dOVC9S/GglCTQxZnc0gYc8hTQP5zNcr/c8KPdCbWtCjndAuTQMNHdURPdEVfdEZvdEdnQgf7YgiTdImnakprc+p3dILzdowLdMSQdM2jdOj/K2SzdM0YAk+DdRCTdQ0YNRIrdRMvdezPLcHodZsnQiC/7sLBVGsinUBNEAAEtDPGl25eIYGSd3cR8sipq2px8oByVsQqVoE6FPYzZ3VWYAOAgENwJoZtz0QkZAKlJ0Fa0fe5o3e47wB5AsRnp0Ie1DeAyEGFv0Am4AGbvAKNADeinABZ0AD13ABN2PhdIDhGs7h4C0QkUsPxCABkXAvvwoLiGBEkUDasHQOkcugtg3SiRCwUkAP0gEDmYpnJo7iG97hwe3iMC6/xa3UAlEAKJ3cA9G52jAKm+AEKuCzaxfdbTbdAnHUUpAFEZwIZTCrA6ASyLviAkHfsIDdV40Az4EMouCzftoENKDZqDAEgrKrbmsNyMACASDUHnbW2r2NPv+b5vNLAyQdC9/g34kQ53Ne5zTgp7tqCRugAoE+6KA9EBp8A27gDGjwDaUKRgJRsBZwQYowBOMsj5CdCL1wAZ1bCRcQYa8uEFaO5VrO5QPxq1JQBVfSCyXQ3DFLERE+4QRQ4Ree4Unu4SAu4iQuEEfO7Cq+5C8e44kw4zWeCDee0Dm+4wMx4D9e0kIuEEROA0a+7Cmu5CzO6Nfu5BFB04kg5b3tuKSc61m+5TTQ5UP95dQ95mV+5jSg6BqB1tye6ALx3eEt4gJB3sxwAGegQk2AvNklEFZQ0tOQrNbgs4bw4SE+4vdC32tg3zSA3wLhqnfQ0emACjQAnc5wATXbBCn/Je4sUKpk4N8msLiWkHMOD/EST/HGTgM7axACADoCEQKWcACQLhDc4LaOSLVIr/QE0fSw4IiRmwVh9qsXmghLYNEO5dWoEO4+HrCw8JBee7dHn/RLn8RO3+5YvxHybgI1m0b2/q3TcNPIqQKM7nleThBFHeaZSvdg3d0o0djPJhCiQAPtlAgBQAOdsJ+JP7B4brC/6ed4+wuZepMj8avDkAGenwGIMAw+qw1cOgSZqlgC0fiPTxCRLxB+TkJNuwH+7QRCHahm3s9mfdW2PwzM4EiJcOuJELoCcet3fwN5v/cC8avaQHybINRP+xERXvRXkPZSPxBU//SHG/Vrf/1u/5/1NLD1XU8HX08DYe/RY++2Zh/8aC/Zaj/1bZ8IVz+sMw3liSD3NED3S1v8x08PfN/vfg8QNC4kSoSEBg03BAkiopFH4UOIESUqLEJjWAaMGRAN20BDmzOC1mjsgqiGxjWCFw5+eViGxhWCTW7QSPdQHo0aC2koUMiBxhqI3mgUUdiJxrSHo34+nNlL4R8aTQhOoOFK0cNgNOSlXNny5USwCh3RkDZxGo0DOiVFdEWjkk6eatm6JWj0DMSKSB6K0fowEg0CT6MSvEbjDcTC1uRCbPs2kd2wkSUKzaJQJDNkBL/QSEBQBI0SEJ1loeGNIGmQD5kJJGjw1VWFAgxLpv9dW6GTAzQMFUX4kAxZ0R0zNzkY6SHDVE4fFqAxwfZziRUPTp9uwTTBITQsKSf4u+xDZ8ITMWSGBiLzAYkq0aAXEQINNQQJ0Eg/MUPf7jSoKby/NdHn0MAj7bqKVIBoDRo4gO65sb6L6Ky0xqNhLcbokjAuCSl8qLG6aLjrobz2wo+gvwIjCCqpEinssIcSW2xDCyFbECzKLKMBM8048ww00QY8jYbUFFptoIJoeO0h2VicMTrqmrTORpIeMgmlRFSiAZ6HWKChskQkoIEMiMoYpj6GMPQJqIeEIoogcgaBjaBfaLiDKRq4Q5GgO2gIACKlmOHqyiy3XLLBidygoRP/gmqgoZtIGnW0GfrgUkhRRh1tFNL6jHKMIhrKeEgBDx8yBDDBUiwMQ4J2oUGxRCi19NJIH7NwyYhqJEiRtgDJsbNEmEsIIlRoGOPHIAkasjVSHxpjNlpprYLHRISypFhtaNji1Uiu0C0R4mhw4jhmH3rEomafqwgVEdJNdwAB3kwkOwsgqvbaV7XdjaFmIhqXpX0joirKcWkAQIKaIOpPod/2I+jgXnsDVliCKlJYIQQVLBcsQiUyFNFWF8UWU0kT9fhVkGXdNOJOPw1VoVFNTOROFXeCSFVWXSU5Vk0vTlPQW3PdlSBfIwp22ERQg+jYIl0maFkldT5X3XXbfUik/ygVmvJP8xRyhufC6puozJ6W2nnNhxQxgRtrjJpToaZKJWimcyDapCOQrMyaoK25XDDjiAb4kiAAmmxSjJATCVzw6QiXFUsQU1YIVK8TadntmBGZeVXAEU+8Q8Z1jpZngjiARb9ENuPVKOMgGoaGPYg9mrUiwVQ2XM9rW4+ZqxJoqOzRNafhG25B10mEiAKgAZXaI6sovsiya1qR3jUHnqGcIDIegI55fei+Km5NwJLprpAHHf5GTLh8/1CPaPXWE6nI04cqTh4iviHyW/bDNVcc7Mx9V9yozqEMfgSBnKiS9bLBVO5yrMof4v4HqNrZKnSj24/pOpS6h7DPdaqBnf9BZKcQpiVveZKhWklOwpUbiIZnWXGQRPiXiDMFZSgKUUQGUAG+g7xCTnSy02CUQANYuIsgUqBBNapEgxSCR3gMAo5EmEO8hskjI1PMQB8KxxwpUhEjVpTVdTg1wEQUkGUHhFlhLPcQmgFNK1rcYoe8qDMJEsQKNCCGMyyYCARNTCHPAsEGFUIaInkQIiGcH216QZr95EkvdFIBGzNgguD5CVwsgQgMaNC9QjKJeWHJzhIgMpNGshGSDBlGRCxZgESoClUE2QO5FMKCIUiCGAexBDcWZj7S3dI/eYwIHwV4oARlkiD1Ww4NoIhFR3LxhchkIxeN8kb3OY6AsSLI5E7/lEAzLlCNWdSiM0uTvDgmYo51vCMvIeLLogEJIoBE1geXRruLjTAyJZzaCY+YRK3xbAk0yEBYXhjDh/iEbPukAQKs4AYOpGOHbKuT27ZGg7sJiQbkUwk+8bZE2xAzdAfhYjfgE5kXenSTE3kmXqQZRmpKjozYpMEZFZLGRIg0MiWN4BLRUK1d3DEPNJBARBCElHQWS0sd/NvsmibMiSgqFgrNAncIYoFvgoU4klQIQxAQEVHQQHFI5dRIJ9JJiEAVmhBhiBewaswu7Q4xzZlIOgIXr0QwLBHn0yVBdtpTYAL1fcC0WCY1CkOOEkSm/pSZYD8aFpp+UWWRsyYCTdVS/23G9LBgSSwcbYpTnfLUp0fxYyKGGsiighCe5ZJnWOipkMJQqaIq5BKoRAERNCABeBcKG5piM8NE/CUTYFTo2t7W0GumSFsFeyUNNrCJe7J2UE18CDK8QINgKAQENEBl2SBQBEjSliDTrS4Nr5vdykYTjGKs5kof69JUYS4R3IWIIr7rRnBi9CwbQBCvqIK9h6CjI0r4UYoI8o2DgNadiSAkVyfylyxkNRYRgQYNHgERchQBAjG5EVmBGIKHbGKWvzJwNL0qEbA+pMEPfkiEJyyhDZCjbGPp6VmywIIM04EGKeAWAgCAXIW4xBJ1zc/EGHZfiOiXBvwVL1+RqlHnQv9XutRt73u1u14mWxe78G3ceFPa2DJCFo3qZa+UwRtVz4UzEfOt71QEFuT99vchACbqgAvstMmCRST+UUhbVItE5SbCkr4liGyQ92SfcEwhfFmTCtSqkLPwuW3BJUiwPlQ+jq1WiXqDDt8UkQ43yPgAfXVGKlgnLvZUdSRa83T7CDKu9lBZsY+7snkJo+WXqrfTn1YIqnkz1maJuXTT4ZUSZrIngqCBOaUcpsMSgQYEtXmQo+2wQmQMvgdExCVZGAUNsxKgqVr4kjhORFbpwG0DlxYsIc7xlqp9q2vrBLrcoQozYIxHtCrkDDSgg3IyQYNFEsRQaJLrb4gWV/z4Wk//ChG2K4scv2AK09KY1jSnSw3qVEuoarM2dSJsrepfspqxrlbglllFcYjfOr6UVshmDtLrXxN82GIxNrID3M5lH5W0cS7UobhtPHtKOp9cQgNU8JoIRTzXORJXSAiAmN1EkGMmazKUWW/TlognYiZBgplsmEHcEMi4j8md9HJhYQmwR+8VekzEFg5SBQnAYKewiHZIaGABbhTM7JdM+9rb3kWTWnnjLssyelOp3rKfve5AvHt4y6VrJ2hLR2bewBdggAgE3UDFOcoEIiKxBQswwygCjnmzJzLHlwiRIIBAYg1gIIG2SCFukbRwtQigAjVAytgdFvdXaeBJiJD+BqZH/z0NVK+TmbhCBRL4Da0T8YCONEMNIHjDQYagkM/AQh4wcIMIwNdPgNO5+cOIBH/lSpXGPz7ykz84xRLuVyCC3RJiJ/vc0a52wtsI7nIXPPzZLvIqL9aAfGep32EaeLqzv8IDM8siOYJIvJNTCPBzPMhDIvLbjMq7vMzbPJgzKhGiOYkgh9xoBgGghl3YAArIOTzrOoKwJIuQBhCYDzogEpGYv2LTBhiYBhVgBi/YgDUJgZmQBGqghndgBh1iu3cjjUeIBKeAmUQIllewghSYAE+7AxzTuYsywNoYiybJgiIQhcwoHtKYDikANoIog44YkQDYwoPowocIr73SuP2jnP9s8riHGEPqMEP8CzOMIgic055E2IPcqA7iqpJkO4g/+IX34DwL9LxaOQgoighFEIUwPIg16KtsAxc3iAXquIGToT0MjAhyoyFGpI5HFDUR8KjpOICtU4hIIKLpYAYBeAg0eBbqyAQSyz4bcT5ZVAg9pA4L6MM0NL++KiQqpA4rxEKJgEMu9MJEAMODoDNiLENjRMOTIi+V4r/ziiw7JEPfa0YCvBhdS4Q7fIhb5MOHuIA/pIFAHMQKFC2Za5basw8cSsa/uDOLSoS8ecN7m44i6CtkxI9f8LTpQAVkgAWySYGZmA4ACIFgoYHnSwRXHAwjRAOTm44lIBKu2zlDdAL/HnwEJIioLzyDBMCgRLDId8BIjTTEsABJkSTJ51ACARgACegDp1KIb3iHCUiBYkHJTDKBSkiAPQAq24CHR0iAMchCmywXnNRJntQJlCAHN0iASiAy0ZDBR3gAiQyoDJiARwiAbwkLARCFARgEsFBJlnTJodQZk8xIaeNIjyzLkRzLh1BLtowMsGzJl/wvmaTJt3yOEMgAUUAEI6IVJ/iGAbCGBxCiMkBLrUmBBBiAwZQIJZCGCZCGvmwCEEiAyUODDLACFVhLgkAHxIQBXLtL0AxN0RxN0ixNz2MIKjFN1VxN1mxN13xN2IxN2ZxN2qxN1URN28xN3dxN3uxN3/xN/+AMTuFkS9wcTuM8TuRMTuVcTuZsTucEKXt6TumcTuqsTuu8TuzMTok4B0MgP+38TvAMT/EcT/IsT/M8T/RMT/VcT/ZsT/d8T/iMT/mcT/qsT/u8T/zMT/3cT/7sT//8TwANUAEdUAItUIiYAARNUAVdUAZtUAd9UAiNUAmdUAqtUAu9UAzN0AwtRQPFzy3QUBANUREdURItURMFUXDr0NrwAhZtURd9URiNURmdURqtURu9URzNUR3dUR7t0R5dMBXFT3nwUSItUiM9UiRNUiUl0hQN0shYUiiNUimdUipNUiB10voc0irdUi7tUi9d0ibF0olQBDItUzM9UzRNU/81XVM2bVM3fVM4jVM5nVM6rVM7FdP6tFM93VM+7VM//VNA3VM8HVRCLVRDPVRETVRFXVRGbVRHfVRIjVRJnVRKrVRLvVRMzVRN3VRO7VRP/VRQDVVRHVVSLVVTPVVUTVVVXVVWbVVXfVVYjVVZnVVarVVbvVVczVVd3VVe7VVf/VVgDVZhHVZiLVZjPVZkTVZlXVZmbVZnfVZojVZpndZURYYESAAwQpKOFM3JvFZvHYAAgKZ0SABjpNZJtVZsnQgB2NbQ7FZvTcxwhYhxLVdzHU2h8Ii1vCPQlA7EeQOkMwjcq9dJvVdtyNfF21ff8VeFAFiBNc17pQErkAh9vcv/igiGd7jYd1CA9xgKHGPYhpXUh43YiJjYt6xYjM3YjS2Cjr29jyVNoegIWOjFnwnNdVwPzSqSgG1ZR31ZIJLZXcPDksVAm8Urj9VZ0KQMSagKISJZtlzHRIAUCilao2VUpFVaiGDasXRaqEWWnJ3asaQMBDSQh5jYTUCEN6CDNfiCo0wEMRCBl1QAEcgaDhCBVZQAAkgFCygBp5wIp/UoCuBaRVCBNbgCC5CH1fMsEVCMACgCR1AIZFCAZqADR0AFFXg3hagGSViDVFgDeUA6hfiFEnCFP0AFa6hJr9VOsNUWsS25g02Esj3btF3btn3buA0duu2Su83bvdUkifBb/8AVXMI13FdKXG5kXMeFXMmlXMslCMzVXM71XDgJ3dEt3YatkRRAIs/V1xCYD+04iA14rT9SJw4CLQVYnSyQMd8TSt6NiKxwiCIJBubIAqhIXwpDAGk4iCSahtWggUzYwzW4m/s1ri28gTdSgd7BoU7AsNMFT+vF3rE92O2lJe8F385KBKQxiPLdEvSVAvWNCKdtX2SB3y2ZXw6u3wDO3/3tX0cEYO8d4AI+4INIYIG1FebIF9bVHkjRhlHYBCdQgY7YFKMZX2SRgixYxWPUlsjxYAyMhI6oD4PYgFeYrT5YDRIjDmK4AVQYgl8otiVYvWnwNBggCGQAn0cwj3N4D/8bTgQAuwEJYAFFGAV6qIoFZmCeqeEHxmGP2OEe/uHwrckL9r0i/kIkDot1ZOJYeeIoJogpdjAKu+Is3uJEGIsuJogvpoEwToQxdjAzRmOYRKI2fuM4doUZ5hkTmAkOu6OzuAH/SgRDowfYCGKJAq3ZYwj35VuLmKKN6IiPQJaBU4h3oAFdCZ6q4A7imJaH8BsqATDbgiFm0IZbyZNLFmMdyrc5vk5bKWVjQ2UkWuVWfmXxjWVe5jAJqWUmuYiMyGWPSA2D6GWC+OVg7hZXIGbtKBZk/i+xCZ1mfmZLbq5prlcJuowsvCMA6ZGogmVjIaojua105BTNeRJkSQXroQH/aKAwGvDIXhgE6B0XKKIGGkiFDi43OogIvkjEarbOf76RgF68gRaQgv7mgwathO4zZmNoxHHoIoHoN5RoirZojIYIjSYIjvboiXCJkIaIkfZn0MEVYJ7ZoHkYojFoCyYqpSGwmUYZdIEadnEXg7iqh1iPiRbmrIwINEiHMZgAHYKiCyAiZrgGaljeRLheVMAWUDmxkjbppPaZn1UjcW40iAmq1wGtqX4zJb5qdcnqh9hqiPBqig5r2CJrs463tL4RtnZruJZrGqDraY0j0SGdO1If1aE1qP5jN6tqD5MMg8AkhVDs4DHACxCFO2jEs+6JtvBeVMgA2Jg33xHlurZr/0rb7ApaPM/OINB26agmRHQk5EyEiNNObJ1e7Yho7deejtgOndk2rtq+bd+RY3MNp3Gyo8Uzp4dAJ6hmp9jpPLBwWuVm2a5u7ki8jWq5gSp4h0owgekiaRg6AwTAoWa4inFBAEei5t2WTu6mI+/mFfDeIxrYuvFWtkK05Q+LCKlVD/ausLZ87/ie7/qGCA7Ab/3m74L6b6QmuZsaicz6OfMDKoP+rHN8p4VGmQdP765V7fYmCN2xAPXNcIlAA2kYHb1Yj64N8OwMpxHPqcW7q81CcZdW8fJu8PUNiwiXcQpXiBq/8XgT6x3HNwn/8Y8VMzJbPCDLrzRLp1VmM+Nmcf/kfvHDVu/UnnCqIojmM/FEoAooegT7hYjfeIdEUKjyMOoiuEQgb04uN64yi/MzA/MhU7NOZvDjPu/kTvMYZ3OIePMDjTc6b6G5ogE813ONFIM+D3GJ5TWCEDgvLDhii+SWS7Yyp+oWL+3IeHJIf2CRZV4dChCGcAVu64U8MeLfgAZuGwVY2IDd/XPm1LWHRDl2JnWW4zCXU3QzZ3Q0X1g1Jwgob/Ndi/VEqIZZ1wlbVwhcpwFdl+he//Vgh1bEUzztWUDxc0DWjUDM0zxmV/UzN+1ol/CvnnEJP4ABiIRKuAZYWA16KAOzubc7UIEA2IOK6ITU8AbwIYABGIJdmAn/oBX2Ya9DBDxYdG9AyVt3y2t3ClzyRXdweX/0eo9yaUeLfN/3fmcPgDcBgSd4gz+UhF/4hn/41s3sOuTGBLTFPTyIXAzHcSzHdxdsk3p2rmXukaf2mJmODSiBJqhHqRAAfpwOCvDKyzWK6bAECpZ459zGbtR5XOxDcaQOoE91oW8cosdZo6cwpC8MpWd6p08EqG+SqX+IarB6Wsr6P49LsYyImJxJ03XNalCDCQgABfaGkMwaNKgEFRCFDIBkiOiFUVCDBEiBcdd68tT7uVTjuvz71gz8wS/8ww82xWd8x38IyJd8yrd81V991m9913992I992Z992q9927993M99/93ffd7vfd//feAPfuEffuIvfuM/fuRPfieVgAFofud/fuiPfumffuqvfuu/fuzPfu3ffu7vfu//fvAPf/Eff/Iv/+kXPeWHVWj4UvZvf/d/f/iPf/nv0TBNf1dd//nPf/3ff/7vf/8HCC8CBwrclOggwoQKFzJs6PAhxIgSJ1KsaPEixowaN3Ls6PEjyJAiR07sZfIkypQqV7Js6fIlzJgyZ9KsafMmzpw6d/Ls6bMlyaBChxItavQo0qRKlzJt6vQp1KhSp1KtavUq1qxat3Lt6vUr2LBix5Ita/Ys2rRq17Jt6/Yt3Lhy59Kta/cu3rx69/Lt6/cv4MCCBxMubP/4MOLEihczbuz4MeTIkidTrmz5MubMmjdz7uz5M+jQokeTLm36NOrUqlezbu36NezYsmfTrm37Nu7cunfz7u37N/DgwocTL278OPLkypczb+78OfTo0qdT/wgiAfbsAwJ4E/srwRiH38MrvZBAxcPr2bFv754wXYIA1efTP12EBv78+d+YAKuGhjwIbdKLIgj9F6BSJtDwx0P36acffwghQcMS9Vl4oWf3BfMOh+8oAAF+RRjk1YEIkUEDNQYCuJSCDDqkYYcegkiDiAdNWCGGOepI2X1qLFQJfhJ8pUgvIyZyYooHEWkkUi02SIOPCgFJg5CJ3Lgjllky1iNDzdD/IElZSEbl5ItQdvmljRRquSabg3G5UDc0UHBQGSJ8o0gCxACCUC+IvEHHHYCUkRA3IozCghV3/EEGIkweFMAw9HQCzRYL9bIHAHQ4AoEbBR40ighDJGKICHTQEIwIg4IqqoB+0rHGF9Mo9I4Im6ADiCN/ACCfQt7UQEEq9JARgKeJkNnQmwrFOaeVFCqiwhpXWCDPOQixIII1iQRQhCMIIaNAM5qiogILClUjyRqprCFPfwr9UoIrf6BijTNt2ntvUckmFAwNeRw0BA0TSIIfGQeZ4Ap+N+T3CEKI0PCONvhtgB8qyCCERiwSH4BfMBcg5IwFCW+M5kEZrAjCg6Ka/4xgIiEQgJ8lEouS0H2RZEEDMQo/nJAKsOCXxcQ0lIDQsQzpixC//jYbTAE0ZPEHflJYnEgTNCAgTcIHTcMMfpmMvAYaCGFNwwY303CDewf1DDN+nYSAL9xxf3R0IpFMPMC/NNBDQyzfoHMQwgh0h4woE5PnsCUbqIAMCwHcPAxCA5zthjNofMO1CAjtQoMF1SSiyBA+91Hyir1c4GUlFxi0MkJeajPKJk6oMHElCN0nRRVOJNJLCTRYMiI5Pg9Qby8gTNxu0QvRbTcNeDe7wSvfHNQH1wxTjfMNqAzxy0GOUFhtItOkQgMMByET8yNhnwNiMwh9c7YELCgyyt6uyP99P/4W3TdMBv1ngMgwJqaNeiUCYDS4RkICQINO9CIhouDcQRxGg2whpAxk+5sTbkYeOtHgAG9LBMI2mIhhMCMDpGOZmE6otbM1gWd689R9tFGsTdwsHXlDhUJAJACDLehJ/PMfAAVIwAnRgFcHeQcN9nQ9GriigQepmiUIeBDJITAR71tDQjjADG0o6Q7kSwgyXkEDJOSvjGY02oP0Y4G0AcwSTjzIiaShEGdMzGIOY0bYEtI0vAGJHgsBUZRe5jyGsA6OKEJIIUUgtDnezD33QU9C1kADDhzkAoOYGkKaVjtj9bBMacTPGiVEg1QoRIHQeCJ+IpGQXgyiXQh5BA3/MpcIaowSkwqxIB0WIoZYnrGXZ7wPKkQgTGEOQADFKiAEExKxLUSimc68Ag0MkQiHtU8hsPxCIq65kAnQYBcHgSUNACABGyqkkEc6pAoT0TQ3LAQVNCDPfZKEEElSUiEXgMcQ5IGfTSZPIcAcJjGNmZAJIUBKNDjlEnXHEDSkYwwTEKMsLyAFGjDjGtQoV0JSQANUONOZCqABBHwpUvzRbSEAe0NCFOGzT+JHeg6rwUIUCIBE1IAGCViIyaqgpATEDD9XkMff0nlOeRayEzRQpUKGQYM9HOQ+g4rkJBEyiC9ADT+wyAQN+NlJZJkJIhPSaUKAhNCqZWEhFxDFHYJG/wOIIoQDCJMYKjLgqTOwFD/2Gyle8VVShQAMRwhRmAr8J9gM9MdhkFMIDGhQgERsTgEL2QMNDnsQFgxBEsSAGTeEmsJEFFKS8kRIFWgAgqbS4KnzjGoifqEwKUjCGtRwAjSyykMXcTVKD7lSWA+KSmYoxAkRu0EV3lEJE6BMlm09AwJ62owCwRIBg/UfGfMqXTbtNSF9VUjI0sYQh3lhIQ/MnAT6tZBrBKwh6QBAMs252ULmgUoLkaSsEuFUhdDzIAj40hsTEVut0haNtnUIbhEi1t0qJAGcs2VxG4IGafiMjEDy63QjfK/qIuS6CYmt9RBCjiKEdJpkI0dKvSekaf84DaMH2YSpUkA1BACASRa0hGbRydkVJYKbM00IOiamBNKa9iD1TUQNFeJO/j7pvw0J8EEGfD3eJuQN7k0IN2X5iKsp5ETvSEQ6KJpHhIihCJuUMJgvROG8QTgRFszCKBCiCH4NzcOneiM3mYFRSRo3EXSlgxOxGt2DuIEGWJwxCt+JSBorQWFGREPTJDtfqNbTew9ISJ+LONsiRwTJiVBy1ZiMkC/QwAoJqYYY2+wwVxipF17c4TmhYaRRwGIDOw4zrOkzZmSWORGAOFsNYCABhEkBfA5TmCtUIIETLRUhD5hYM9QAAifTgFWJUCQs5AEDN4ggZiYENEKcPIxI7Nj/nNzcwBdggAhJ3gDEPKYvahX5hwxEwg2h5VoeBsHJ/iqvq7dVU27HSlGDHmAAkajENWDBNXqUQREmwOodVBCAPdynEwT0RswIMIAh7EJhN401xqkzawuntHD6WUM9PSyCOOXnAKNNSCQmmh9moPogaAitfjKRYXNaIz8qo/FB9jAyUJLz3Iw+iDPcmZ8sSIDEC5w3pb2KbwHrdsnj1c8GStAErNKghQIYn34oIG+EVMOo+bHEzDIu9vuZoBIJ2EN8G3bARJDDDQmoxKvnOA0VPOIBHlsIBzIwgUcEQKEOEYAoBrB1hihBAAOQQB/yWxFuIGIA1Lj7NCbATqpUQw0T/wjAB73xjvS5vBIqEEUGuGepUaghASmI+9hTf0aHVVH1rn89blgP+9nTPjayrz3uc3+a2+u+977vzDkMYe7fE7/4xj8+8pOv/OUzv/nOfz70oy/96VO/+p1xRoyyr/3tc7/73v8++MMv/vGTv/zmPz/606/+9bO//e5/P/zjr/5jWt8zTiAI/vOv//3zv//+/z8ABqAADiABFqABHiACJqACLiADNqADPiAEJqCj1B9n3F8EXiAGZqAGbiAHdqAHfiAIhuACTiAFboYznCAKpqAKriALtqALviAMxqAMziAN1qAN3iAO5qAO7iAP9qAP/iAQBqEQ1mAJFqERHiESJv+hEi4hEzahEz4hFEahFE4hFVahFV4hFmahFm4hF3ahF34hGIahGI4hGZahGZ4hGqahGq4hG7ahG74hHMahHM4hHdahHd4hHubhaygBdoAPQwxAAvTYRYxCAmTWRajHerSHQsCHEemhI4aGIkDTlTFEH+DH4GGEwzjWRTjIJ0VImtTaI4biZpCXBTTE5tyVRmQiRsBIh3xIiIyIpYmiLGKGBdFAzyWEqUBSKtKAJuqPvTHdk8XiLA4jZRjVBCyEBW2AH2aEKm7iL7YOyQgjMU7jY0gOFynERxXUKrlKoPTYtWTLtnRLJl6AGNCDFBTAACiefzHEsnzis0TLtPjhN2r/C7d4C7iIC7mYC7qoC7ssxLvEy7xIETUOpFYoSGkphPecnMG8lc7QQIZVzdVkjcN8gfeQDX6swQeViZEdRNKkCdM4TVVJDSpF5NloDdfQgNdc5JaNTdkkjHatje+0TUYSJE1aBQV0UxbRACzYUuAMjseRR9XkjPZwjwTBgjUwjuOcCkQsz92kCfRITyJQj0OiklBuT/d8j9aMT/kkwvk4pPqwj/vAj/zQDxPVpFlWBcr01wMVDEIoEAM5UDJVDRO9kQRVyUH8An6IHlf9UP8EEQ0MUJpIGkIgkRLJZRMhBBQJJBUdxBVl0RZ10Rd5ixjt2VlWZlM4wcZI00EY1eQZ/5IcJQQd0YDFyCVSRdAoKV7THKMnfVIopQkpJVDTkeYqtZI18dIs1VJD4JIu2aZl9uZShFabeYPvCOQydVQzQZM0yaXfeRhK1aZkoVEwAVQxHRNBGZS+0cByJgRDORRbJYJEUZRFmdhBaBRHGedHdZhvpudRAAkzFIiBKY2SrBRLSQ9ZKYTD1NmjbFTS3RtYMZ2+lZU9oZVadWciuFV+bEBczVVdlaV6NihR9MLNpIgXUWYiANZz9U9/ZJp90gA2IRYN9Oc6Kl2ZYdq+JYRvnU1wDVeCZRFyKRdzWc2FZgCFOiiNhkRNxUKWZYHiZddDaGhCOIw2wqUY7CeALV2Sxf9miSKEgVkAgvGmQixYg12akdYolQ5FJDjNA8XCQmCYQmxYh/mo2sHCTG7CZXVmiN7biCKpph2Ek9nlQUTZN1FZQlgZlmmZQnTZl1WpnnKEqcTMo92S06SZkrAZgf0oflSBkTwQHZCg7TwjQ1gaia5pInCap3FdqJkmqfHJqRmSqiEEq7nanobqRliBT9HfQdzaDeTartFArxWq2kUMAaiAGngJDZjpmRZpmuqbpAJJv/1bwA1cwR0cDSTcwjXcw0XcxFWcTYkqs2KEcDppx6mVn4UcmJqmG2RMftxAntZWpU1ppD7dgUod1Vkd1uWH1n2a18FM2DUru4ZE2Z1d2k3/BDw8AnjYElRU3uVl3ublERp4Hujp5SqRnumhXrsWrMEeLMImrMIuLMM2rMM+LMRGrMROLMVWrMVeLMZmrMZubEMggsd+LMiGrMiOLMmWrMmeLMqmrMquLMu2rMu+LMzGrMzOLM3WrM3eLM7mrM7uLM/2rM/+LNAGrdAOLdG+rDSIINImrdIuLdM2rdM+LdRGrdROLdVWrdUy7TBcrdZuLdd2rdd+LdiGrdiOLdmWrf4NwwWkrdquLdu2rdu+LdzGrdzOLd3Wrd3eLd7mrd7uLd/2rd/+LeAGruAOLuEWruEeLuImruIuLuM2ruM+rt6KJ8dOLuVWruVeLuZmruZu/y7ndq7nfi7ohq7oji7plq7pni7qpq7qri7rtq7rvi7sxq7szi7t1q7t3i7ucsYFWEMJNEMwXEMGbFnu5u4emI1+SIGtfsSSDO/lGhA0UMMgVEMloNcGlCZINCPzUi7XDBJC6NM1hgT2Zu/GDgLZCCTQ1ZFIhK/4ZuwDdJCpJsI1DENQHUSf/Ek3aqcIIEIiPEAB/IE2LMFTNYEI3OQahIp1AUInOAIZVMIx0Yqt4IquNOJBhMAuoAIdbIjw7g43Csr6TiP5dtr7KsTBJMzCIMQF0AABhNcBOILPbIA0ZZl+IAgaDEwHrVQVvFHN3EzO4MckHgQ3nKTOYCTRMGQJd//wMNIqPQxAyDFET3LlT1YSRR3AGTRQE9xkSCnCBdDVNVxAHu0SHTzAJqCBG4iRN5EW7ugO7/jOiCADVnXDjnkDwtwYCFmNTxqOEc8iMtCqTw0DDNirW+bXA5Wid+JHh3LQFahdL4aAJRzA/CYCN+hkC8nXX85QkDFW0x3EOfjMjv0xXAryHctiGYjBGqjVAQCC38XRHKHvCdMAPCQECzgNIqsdmCgEwmzSI6FbPUGTIFrBMNgQKoMm+n7yMCJDANTASWoDRhWncSLnINOA8DoDLJtmL9ZUNxhnJHiJ88QTLifCK8PCQyhzRzGzME/jJrzDxHiaSi2o9JzwDcxRNHv/WC+iV10NqSQLYn3BAw3kUkOkc11B5TjjISJcg3YlRO/clYVeaH+wszsDKDxnEoDE6OjU8zYLpxQ8xEE/lyv9sx02jZsmhMkQw0HwqEMoNGi+M/bGyUb600H+HBqQjeLBAxKAmEhrtCzu0hq8b8YEw0FwaUJ4KRS3c0kzNPaizGKlFAQUQbss2mnV02VJMHzp11T2NIfRNB6GwMbkQXYiwcRA5ZkJ6ucQ6iAD9ceYNE4C3fgw1SvpTaPaM2r9Bz1g0vtEkZkFqpqBNVXbocnQwBUsgRUgwi68DC8mBKqqKq+BD0mPNUPXnAVwAzltwaFKAAy0Fyz8qUT/XCJsglERlMPEiUHM6OJg61ph3zUeUkO65scfWMMxKYLH5QfImXBJBnUFBQ3LJGV+SEEjKrWPoVYiOAG/lFylKslqX+QSi7YdcoAETEACSEMkqKPBmB3aZUQZnEECWK8TUMPmIUEGVwQHbIHkZTTROHe8Erd4jzd5l7d5nzd6p7d6rzd7t7d7vzd8x7d8zzd917d93zd+5zeWBAQAOw==" style="margin-top:1rem;" /></div></details></div></div>
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">WolframAlpha["number of moons of Saturn", "Result"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhYwAqAPdeAPHx8dvb29/f3+7u7tra2rqvoquej+bi3ZuLebuwpOjk4JWEcfDu7N/a1ZiHdZ2OfKudjrGklo58Z8zEu+np6d3Y0dnTzM3FvINwWdPMxNDIwPf29O7r6M/Iv8O5r+rn4/X08srBuLCjlY99adXOx66hkqCRgIJuV9bPyIVxW8/Hv/7+/oFtVuTg29zW0LWqnKyfkJqKeN/a1OTk5NvVz5uMeoVyXPr5+MG4rZF/a417Ztzc3L+1qZB+aq+ilNPNxY9+afX19Yt5ZIZzXePe2fn5+fr6+tnZ2eXl5YRxW6eZiresn/Lw7pmJdrarnvLy8ol3YYh1X8K4rdHKwtDJwce+tLyypvT09O3t7dTNxbKmmOPf2ritoIl2Yf////b29vv7+6WXhuDb1YFtV+fn59bQyfz8/O3q55+QfuHc1+Le2aqdjt3d3ejo6PDw8PPz8760qPTz8fDu68jAturn5O3r6Obm5vr6+aGSgbSpm/j4+H9rVJmJd4d0X4JuWIp4Y6GSgrWpnP39/fv6+svDuo17Z5aGc6KUg6OVhPb19JaFcoRwWunl4d7Z0/f399jSy9XPx4d0XpKAbevo5Ovr69zX0eLd2LmuofPy8Me/tefk38W8sYNvWaKTgufj3/39/NnTzbqvo+Dg4LSomqaYiJKBbaeZifn496+jlMC2q97e3uXh3IBsVZWFcpyNe9LLw5SDcPj39tHKwZOCbrernuPj48rCueHd1+/t6u7s6baqnfb185eHdJyMetTOxuzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5uzp5iH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAYwAqAAAI/wC9CBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxZsMibJyhTqlzJsqXLlyivgCGpMIiqIzhz6tzJs6fPnzxrGaFpMMgRMkVWEE244ouoHWaWDlRlRypDQaraWDVyRI9VhlhUWb1yRNDXhW+OKF1Kdu1ZhG2lxn0LV+1BJlQO7TmDUAyrQAS17Bk8GHDBuXQNIibIQweUvQdv5LBhWOAaNDQy06Cj2G7izm4NyoBs0EmMMJW9HHqxcPFnga4JjuZbMM2YFnhSx8DR2i6LKUC6uFiSQolZL3Jg9EkCqAXBQaEK+TE0haDwMooWGWpE8BWfIUMQPf8iGHvg7IJ3JF3ygia1pF6SosR4dTAui1KTfAzJZIkVDS+Y6AALFZAAwskWAq3QSSRVgDLKHpkM1EUMpGhShylRnCJQJaykskojcLQSy0DlCXQeQVzMMgh7qaFCSyO36LLHJqB5wYItXrxSikB/zOFFHpHsIpAgvLgikC97cCeQLikkIlAXpKz1yx6VCCTFEJ/UFVpBJwqkxglECNReQiVAsaV9snhBQhMC6UDjCCIQFMIeIHjhQw8EfbAHCk96MNAne3QgEAdCNKGBkId5dlCXg8wSykBjIpTBHpgkqhQLaa7ZJo0Y8EDQI3t84AUiaBAUyx4h9EnQHhcMlEgqhoz/YYIF5CkqGmlqEqbrHhUcNMEeG1hqY6ZseuGmFxJEQJAte8ThRQk5EETHHiSoOhCrBuUiY5qw2colrht4Iq64TUDgiYaM1DHQCg84UCOmahZ7rC5ROOnFCk08IBAKezQwEBdBWisQtl4wcJxAfPhAordegJBGGnPs8UMalhwUqRcJDGEFDVmYcNu7xG7qxQY6LCALCp1wosBAYfSRCSiB7EGIhH5e26oXCCiiwgEHeMDCDwtvmeuunFhc2QpU9DLEIodoUp9vIRtLoxe4GLAcHggOdEcBOkxHhXU1D3zzBjg4kEQkNdAXtFwMf1YiSG+/FbdHc39VN0d3sy20SI4cVTHUawS5sYNVKxAwAOAEzTDDV1gQ8AbiK1ByhCNfrUDBEQIgofnmnHfu+eegh775DGwEAABdjmBhh+ist+46EmQMMBPitNdu++2456777rz37jtIAQEAOw==" style="margin-top:1rem;" /></div></details></div></div>
+<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">WolframAlpha["number of moons of Saturn", "Result"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhxgBTAPeXAPHx8fb185F/a6iaivHv7O/v7/Hv7eLd2KKTgt/a1YVyXMW8scW8ssrBuPf29O7r6OPj4+Hd18rCuYh1X9/a1L+1qYt4Y7Gkluvo5Orn5LOnmaSWhtzX0d3Y0tXOx5iIdol3Yfn5+JKAbeDc1uHh4Z2OfO/s6se+tPv7+p6Offb19KWXh5eHdIFtV7muoqaYiNPMxLerntDIwINwWaudjpaGc5SDb7KmmNTNxYRwWrCklq6hksK4rcnAt4d0XoNvWbqvoqCRgIJuV+Hc187Gvd/f36OUhNnTzI9+adPNxcvDue3q58/Iv6yfkN7e3uXh3Ozs7Id0X4JuWMzEu72zp5GAbOTg26ibi6GSgpuLeZ+Qfsa9s+Db1aWXhuLi4tvb25+Qf/T09IRxW+Xl5ZWFcoBsVfDu68G3rPTz8cjAtubm5unm4vr6+eTk5NvVz9zc3I17ZuLe2ambjKqdjpmJd+rq6u/t6raqne7s6djSy/f39+Xh3aOVhIp3Ytra2tnZ2Y99abCjlfPx7/v7+7qvo7SomuDg4O7u7tbPyIVxW/X19cO6r/r6+vLy8rOnmpeGdPj4+Ih1YNfRyc/Hv/7+/rGll4l2Yf////b29ujo6N3d3ePe2dbQyefn5/z8/Ip4Y6qcjfDw8L60qPPz89DJwc7HvtfRytHKwvr5+PXz8paFcpiHdezp5sS7sMe/tdvWz+fk37uwpMC2q9TOxpyMesvDuo17Z+jk4JWEcfDu7IZzXYt5ZNHKwZOCbrWpnPz8+/39/fv6+sS7sc3FvK6ik6eZiZKBbZOCb/j39pSDcNLLw/39/Ofj3/Py8LmuodrVzpqKePf29Y58Z+bj3uzq5unl4d7Z07Spm6GSgZB/a7arnpmJdu3t7Y58aOvo5enp6d3Y0ejl4Z2NfMi/tdrUzdXPx39rVPTy8K2gkritoIx6Zfn4962gkb2ypoFtVqeZivLw7resn6+ilJB+aubi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3SH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAxgBTAAAI/wAvCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0g3AmtUR82Yp1CjSp1KtarVq1izapWaiRukpBQHffPzp6zZs2jTql3Ltq3bt3DdGgoDFqKiN3Hz6t3Lt6/aTpTqMsRE9o+mUIwCC57oSVEns2MWJ/SE908nYJIxjqp8KLPBOmU7ec6oh+wXT6MFUvpiGHXqi1DKdk4dRvZrjKv/eHnNrezX2xfb/Pny+ltZ18ArPv6DeXSmss2TU3zOPDX16NIlXrcOPfv07s7Be/+PuD189fHkxWcuj/4h+/Xq2zN8L5m+fIX2Hf46daXYNImU3FFMMa8kVMmACCY4YIEL5XffQQ4iBIwVUzQRhTkYuiERFRiao0RCunQooogfNhjfgwhFeNASI2YY0RFldFiiQcDECIcROOaYIznznYiiQSoaBE8XRHZRhYsPLXHhHBjOWBAaGKZjUZA/UplQO0g2hIoq5iSzRpMIsYJhK1P6+CNBViKEpTkaOtSEOVLAAguYB22CIRNlnneJKLHg4YksuNgCSi6XUOLKI7vwUQ1CwQxTjDGfHDOHMsswxIwz0MAhDS3tUJPQFrFYIxAbw2CRzS7bxCKIQvAIY2Qf3WT/kQ44iqVoZkNrtsnQOBimcYmdHiL0TJYTsZeIOeW82eEqlBQioiXnGESOOi2aU8UmCa3DTowjunMHcgT1Yk48v87TYiT0IJSGGNVaS0StBaV5UK4NDSGEOegINASdBp2C4X8VGWuOOObQQkgyGGpjThBAmGuOKAVNwi00Z9QiCpfm/PDMQcg8gqEPlfTgyg45YIgNuAKJ2wQO99bgCxU0zIChMShfIgOGusQAAzh5jPNCC+a4s4etekpE70LwUMsCG/ryW1AaGHrDyw1drBBIGna4J96x5lwRmArsmhODQNTEmAJBe0hhjhC8EETJCTH6YIJBcmAIRjMEmeCx2AaJ/2uJO32YQhArn2CYh0HZwOmNkDoskpC8Bh09WQnmRDJ308EeJAuGP7RYxg4qNCSwD2gMFIQ52aAwUOLzEHS6OVMcJAqGxBQ0AoYihGBQMyCY04Kn4c5MaEGuYEguQchg+EGxtzIkOUIKl8EBQftmbtDs5nxSiStT8LABt6qEbqKexxpBECjmaEAQNObsMlAGGJKB0C+FuyO+QEya4wFCJ0RZkLhSwJtBxGSODRQEGCESAwa007yFPM8gysCQ46jnNLeNoxa/KEg1xGWOC/SIfOYw30BokD6CZMEcFhjIFjDEg4RcA0MwGAglLiSGSh3kHBjqxf/MkQhGYagEBlkhD/+dsTitFS0iDyRIONglB4NUz0kOMcOx3JGK8UWnfAQhofoGcsIUCuQGxCpIKTBUgYHAA0NZUEg3zFEGeImrhwhB40G20DkM4SIWFKgZkBqokCQKJBpHmoAbhkDIQkoAQy4g5C0g4ggMJcGKA8HiCEvIRRQO5AoYekJC8oAhXwwkHBjqgkI+gKEqDuSNCZHjQR5QCEuIyAc6SNfj+HilMA6kAe1qVxofQgQMMQCSApGkQLRoQksKhB0YikBCZoHIgbDIHFhQCMLMobtT8jCV5tilhLhACBaIaA7RIBp2kGhLgfQgl9XSZkNIgaEFAPMSwrwEMSvpxUs4A0OnSIgwfDn/kORZKyEINIcCdgjHg6iSISYQhQ9+CK+BQK4gfizUMiZK0YomAEMNmOg4F0IIGL4znvMUSBcHIgkMBSIhCMCQFQiyt6wd5AAYMmDwCmqQgzYkF4BIJoRoqaZyMuSJB0GFAbJFrRaYcpYgFOEwKSlSY15iHQkkwEGYESMkwGtz5rgDQgaAoVIQFJvqbMgZMNS2PR4RIhFdCFANIo9dgOMgKHgH7T54xRBmkamXGOlAsFqCag4kFdP0KkGiMQE2csIguDSHAGxoTZoWxKaXwAMdRIWQupkjDjs9a0KsIInOdhZ9D/OsJI7gkLXmjWsv8IApHaAMG2AIEKX7qF0nucWm/9bzEr+gBYaSkYcMsgEGSMDQOxp6CVPEqAXOuBwGbhCjH2Drq3HMZkEItjAPBIAg57gDhrZB3EvIy7LovGa9KiiQW3izQz+IArfMgYsHiG5rs11qbfPqVIGkQgsdcscE1nsFvxaEFDLDkALCZo4obKxv4jWodAmyhpRiqAzSYEEWBMCtbLg3sxtNCHjR6diEmLYglFAGFoAmImm0QnXvTepd56tXgixDCYkTERmU0d2BeIMGauuQGG4wPAR3eCCQFcg0KkGtEcFBFOtAaoZp4gBr8GIYHshAejRrEQwgggiSwMNDQtABUpyCCygOiTfcQIpSSMIbNXYoT4nyUPS0Gdkob/ZOnH0yZ+nUmSd3Bk6edbLn1/QZJ382z5LBApo/DOJMClFDWdKclEOURRGITggJDPMaSJTlG5E+yCDKoobbOKEsesh0QYTzh0bcBgBlKcKgH1SAshgiORAoiyYgHWlPLMcPmEiOJ4pgFghwAwCNCLawh03sYhv72MhOtrKXzWxih+IblflDKLIDDEX75drYzjZf3kCX8WBiDIXRtrjHne0icGPVtwGGHsLQ7Ha7+93wbvcoMMEIUdv73vjOt773ze9++/vfAA+4wAdO8IIb/OAIT7jCAx4QADs=" style="margin-top:1rem;" /></div></details></div></div>
 

### 2024-01-28 docs/projects/math/wolframite/index.qmd
wolframite - rerendered

@@
 include-in-header: {text: '<link rel = "icon" href = "data:," />'}
-title: Wolfram Lanauge interop with Wolframite - DRAFT
+title: Wolfram Langauge interop with Wolframite
 author: Daniel Slutsky

### 2024-01-28 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

@@
 Note that to use Wolframite, you need Wolfamite in the dependencies,
-as well as the `WOLFRAM_INSTALL_PATH`
+and if Wolfraimte fails to find the correct install path automatically,
+you may need to have the `WOLFRAM_INSTALL_PATH` environment variable
 set up in your system, as explained in
@@
 :::
-
-## Make sure Wo
 
@@
 
-## Def // intern WL fns, i.e. effectively define WL fns as clojure fns:
+## Def / intern WL fns, i.e. effectively define WL fns as clojure fns:
 

### 2024-01-28 docs/projects/noj/ml.qmd
Noj - rendered book

@@
        Min          1Q      Median          3Q         Max
-   -0.8225     -0.2071      0.0197      0.1946      0.8181
+   -0.8363     -0.2220      0.0278      0.2168      0.6757
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.7397     0.2949     5.8997     0.0000 ***
-sepal-width         0.6671     0.0809     8.2462     0.0000 ***
-petal-length        0.7522     0.0638    11.7822     0.0000 ***
-petal-width        -0.6293     0.1438    -4.3776     0.0000 ***
+Intercept           1.8228     0.2974     6.1291     0.0000 ***
+sepal-width         0.6696     0.0822     8.1451     0.0000 ***
+petal-length        0.7126     0.0684    10.4175     0.0000 ***
+petal-width        -0.5688     0.1563    -3.6381     0.0004 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3188 on 96 degrees of freedom
-Multiple R-squared: 0.8758,    Adjusted R-squared: 0.8719
-F-statistic: 225.6278 on 4 and 96 DF,  p-value: 2.442e-43
+Residual standard error: 0.3192 on 96 degrees of freedom
+Multiple R-squared: 0.8711,    Adjusted R-squared: 0.8671
+F-statistic: 216.3502 on 4 and 96 DF,  p-value: 1.417e-42
 

### 2024-01-28 docs/projects/noj/index.qmd
Noj - rerendered book

--- 2024-01-28 docs/projects/math/wolframite/index.qmd
@@
 include-in-header: {text: '<link rel = "icon" href = "data:," />'}
-title: Wolfram Langauge interop with Wolframite
-author: Daniel Slutsky
 
@@
 
-This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
-It is also appears at the Wolrfamite repo as [dev/kindly-demo.clj](https://github.com/scicloj/wolframite/blob/main/dev/kindly_demo.clj).
-Note that to use Wolframite, you need Wolfamite in the dependencies,
-as well as the `WOLFRAM_INSTALL_PATH`
-set up in your system, as explained in
-[Wolframite's README](https://github.com/scicloj/wolframite/).
-
-::: {.sourceClojure}
-```clojure
-(ns index
-  (:refer-clojure
-   ;; Exclude symbols also used by Wolfram:
-   :exclude [Byte Character Integer Number Short String Thread])
-  (:require
-   [wolframite.core :as wl]
-   [wolframite.tools.hiccup :refer [view]]
-   [wolframite.base.parse :as parse]
-   [wolframite.jlink]
-   [scicloj.kindly.v4.kind :as kind]
-   [scicloj.kindly.v4.api :as kindly])
-  (:import (com.wolfram.jlink MathCanvas KernelLink)
-           (java.awt Color Frame)
-           (java.awt.event WindowAdapter ActionEvent)))
-```
-:::
-
-## Make sure Wo
-
-## Init (base example)
-
-::: {.sourceClojure}
-```clojure
-^:note-to-test/skip
-
-(wl/eval '(Dot [1 2 3] [4 5 6]))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-32
-
-```
-:::
-
-## Strings of WL code
-
-::: {.sourceClojure}
-```clojure
-(wl/eval "{1 , 2, 3} . {4, 5, 6}")
-```
-:::
-
-::: {.printedClojure}
-```clojure
-32
-
-```
-:::
-
-## Def // intern WL fns, i.e. effectively define WL fns as clojure fns:
-
-::: {.sourceClojure}
-```clojure
-(def W:Plus (parse/parse-fn 'Plus {:kernel/link @wl/kernel-link-atom}))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(W:Plus 1 2 3)
-```
-:::
-
-::: {.printedClojure}
-```clojure
-6
-
-```
-:::
-
-... and call it
-
-::: {.sourceClojure}
-```clojure
-(def greetings
-  (wl/eval
-   '(Function [x] (StringJoin "Hello, " x "! This is a Mathematica function's output."))))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(greetings "Stephen")
-```
-:::
-
-::: {.printedClojure}
-```clojure
-"Hello, Stephen! This is a Mathematica function's output."
-
-```
-:::
-
- ## Bidirectional translation
-(Somewhat experimental, especially in the wl->clj direction)
-
-::: {.sourceClojure}
-```clojure
-(wl/->clj! "GridGraph[{5, 5}]")
-```
-:::
-
-::: {.printedClojure}
-```clojure
-(GridGraph [5 5])
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(wl/->wl! '(GridGraph [5 5]) {:output-fn str})
-```
-:::
-
-::: {.printedClojure}
-```clojure
-"GridGraph[{5, 5}]"
-
-```
-:::
-
-## Graphics
-
-::: {.sourceClojure}
-```clojure
-(view
- '(GridGraph [5 5]))
-```
-:::
-
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhwAO/A/frAB8mMSIpMyIpNSQrNSYsNikvNyMrOCMsOSQtOyYvPSkvOCYwPiswOC4zOi80OzA0OzE2PTM4PjU5Py83QzM4QDY6QTI5RTY8RDo9Qjw/Qzk+Rz0/RDA8TjI+UT1AQz5BRTtBSTxCSz1DTD5FTjNAUzVCVTlHXDtJXjxKYD1MY0FDRkJER0RFR0VGSEdISUpKS0tLTEtMTExNTUFHUUJJUkNKVERLVUVMVklOVkZOWEJNXkhPWkhQWk5SWEtSXUxUX1FRUVVVVVFUW1JWXVpaWl1dXUVPYEVRYk5WYU9YY0FRakNUbUVWb05bb1FaZlpdYVNcaFVdalZfbEpbdkpcd0tdeExeek1ffF1gZVdgbVlibk5hfVljcFtkclxmc11mdF9odlhmfGFhYWVlZWRlaGpqam1tbWJpc2NqdG5ucGFreWJsemNtfGRvfmZwf21ye290fXJycnV1dXp6en19fVlvkFpwklxzlV50l191mGZxgGhzgml0g2t2hmx3h2JyimZ2jm56inl9gnF9jnN/kH6CiHyDjXWBknaDlHiFlnqHmXuImnyJm36Lnn+Mn2eApnaJp3mMqn6Ts4KCgoWFhYWHi4mJiY6Ojo2SmIuSnZGRkZKSlJaWlpmZmZ2dnYGOoYKQo4ORpISSpoaUp4aUqImXq4+ZqIqZrYybr5CaqYGWtY2bsI6dspCftJ2iqZqir5Ggtp+ms5OiuJSjuZWkupemvZiovqGhoaWlpamqqq6urq6zvLGxsbW1tbq6ur29vZqqwZyqwJuswpysw52txp+wx6Cwx6GyyqSzyqO0zKu3ybO/0r7CyLjB0b3G1cHBwcXFxcnJyc7OzsHL28TN3M/Q0s7V39LS0tDR1NXV1dnZ2d7e3tLZ4tTb5dbd5+Li4uXl5eDk6urq6u7u7uXp8PHx8fLz9vb29vb3+vj5+/r7/P///////////////////////////////////////////////////////////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAwAO/AwAI/wDXCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS55MubLly5gza97MubPnz6BDix5NurTp06hTq17NurXr17Bjy55N+2a6bM9+XTNXG6U2aL6kiet98ls0X9G+ETcpTpovaNqWlzR37dezbOlegrsEREYMGDGATP+KLt1juU5FZMiAoV4OtPIe0+kqAx58jDG8ssPnCE1O/e9FeFLOfhxpMwkQ38UQQxCXgMMSLjK0gIEEEEAQAQYtxKCJfgRa9EwQMHxAYYUVqADDHMN1aNE2YsCgwogQSGCiGNuoaJE4/qmAQYUxZgBDEM/YWFE6msAgIY8SZNCCDLeoZAkMOyYRSCOfDBJFBBLAIAdvQkakiwwZQHADH4yAgkgXF0jgghgOdglRNECsAIEIbCgCiiJriBDBCkBI4yZE4ojRggQXeIEIKIzwcQMEH8igy58PneOfBBFEMQgojQSCBAQYxGAJSp7AIIENqyRj6qmyIBEBDJRA2tAzMmD/AIIjp54qDBgQtFAGl64mtE0QKlAQCDK1IoNMIBF8EESNvSZkzhhygiFMrckg4wgIGMgQZLMJUSIqErOcSmwyq9yQpScmZQNDBTwQQ624UGT5C7cHlRNEBiDI8u6pfEAAAyf0HmTGChGEsq+poUCwghkBG8QJDBD4cXAysoCg7IAND/SLqFCM+y4xPFQQQzYlybFCBbRMnAwxIXwgBocNdwLDA6ConEwS2baZ8TOi8mHzHhJom7FA4MSKhMfvIgMKBC6gO7Q6RXwAgrsT01LBCnKQVLQEYNicTCASxODn0ERgcAPS+5biLy5Dr0PHyVRPTMzVk7SNC8SlqGxsDhgQ/9G2NDFEEIjXagStM0i9QCyK17Tkyok6kEcu+eSUV2755ZhnrvnmnHfu+eegh+65uhJIbDMyFsch+uqst+7667DHDvo5QGAQhdfJQIEBEObI7vvvwAcvfOtxqAAC7nyEjd3wzDfv/POvc9ICBCnbHMoDMPQykifT2+I1MhVAUMIj5Jdv/vnop6/++uy37/778Mcv//z01y//FgFA0AjuSEiQgP0ADKAAB0jAAhqQfngAQAXagLs2SAAAeTigBCdIwQpaUIAJkAAScNcICARgCxcMoQhHSMICkgACFcBd41rgtJBoYnrT8poGIMCBEtrwhjjM4SOokL+aec0JFQiADv+HSMQiDtAOCvSZ15IHADsY8YlQjKL6AiABJ+AuYQGwghS3yMUicgACGsDdMCLQAk2MBBcugIC+bFYMTkWBGHCMoxznSMc62vGOeMyjHvfIxz768Y+ADKQfG/EACCgCdzzAgAgEychGOvKRkIykJAEpCwdUQA24W4MEHFCLSXryk6AMpSgdOQIM8AB3iahQI0bJyla68pWRjMKO0LYvWTCNbSKBBsQS4TVS+CsXQxPHurpmM2JQYAWtGlrUcoC7G3ygCG2jBAsoELeJgaECMEhRw3IBMVJ4LZUweI9IzBEEDPjAa10I2+ECFocPaKCa+0KEv+Y1NOlBoFQqWwXTADb/tI1BABE2G4YGVBCHtn1DBhXowul8sLtzkKQTaVyEytTWgrq1bWMSWIPKagGCDLzMoLHyQTEmhgyGykA5QzuHGKRWC5WpYVXbGtokppe3iS3CATDoREnKQYQVUMCH71oFtoCA0rbFYXqD25ctdoDNmA5NZhHgwkg/xoVV6bRt63hGDNjlvaQFIlcFxeo3gIAvfL4LFBV4JsZIkg0gfCACYKieqWzBhwp0yqnBLIKcoHCKWhEDESHI0lWxmg45uCACN3CEx6x1g1XJAWZPXRcIEBE3ZJwCCg5gQRG0edEYYKACfABGrWihBkYBgWQniUYQWEAhGjjBCYuSwApk4Aus/xIEHGNwwY5EgIQohIxROVWHbQVSjjlAyQEXQAIUfjBDDJxorVhVRydi8AEU+gAKSBABBC7ggjGss22+kMEKKHSD19IgRi0IQjRU8o05REhESVqSGVA7XOJq4jvwxRAMxIBX26YjF0CAwQrSdIEP/AgXkLXtM8QQgxVMKK3s0QR0h5sNMxhpQhL4QIbmUFSVXIMTRThAAHqgifXW1yDfuIUZEBCAEEzCFw49MUHEwQs5UCAAE5iDLsYhY4Kc4xeTCEEADmCGW3S4x9G4RA8MYIAicIK+LvEG+abRY4Skg3zGqDJCVPEIVWj5IMUgn3C/TJBpkM8bM5HyI6hM5oFc+f8RWW7zQLjsZTkLxBjkS7CWzfwINMtEzWyW85vjbGc62/nOeT40n/0cE0AfetCHXgeXJRFpPD9Cz1VedJqn/GgsR1oSXa50ou2s6T9z2s6QPrShD21pTPe41I0+taA9repHUJrVo5YzrGHiaFTTutChxvWlFX3mTa+503D+dLDt3Gpi99nYgW5zqoF9a2bnus27fkmvZ53sWtfZ2sMmdbFNfWxfd9vOoP62nJst7meTO9pknracVw1uV8s421GWtbR/PW9bizrcuh53rMvNbULLOd3/tveJ8d2Sbe/73P1Wd5vZHXB3DxzeX5Z3myedcGczmtf6jje/N77sdV+bzAz/Z4nDRQ7xNiNc2Aqvb8pXsvKMj5zMHIe5x6GNbIOTXOJkpji2BQ5ygj/c52R+eb13/u6eR5reJgf40C1edIxrWeM497fO2/1xbYfc5i1PesknfvIvz1wlNb/6zb8MdbJLHeVE97rRWY50tmt96VznubnrruW2B73se457vucOdr5XWelRj/lwz56StFcZ63avduKZfnGne7vjeW/63pUN9C8LHe5Ul7vVH7/2vo/97283u+Ab/nW1hz3ymK941wc/+h5DXsuId7vibct4lDje9qWvst89D/hMr17lrSf9600ved1TvuqWB3bntfx51Yee9tE/+OmJn/rAX5/1hHe9/+F7nHO8y17vBX/69qlf/Fcfn+bJB/7yD7/+Klff+7MHf+1lfHvh17/H92d834d84ad84ydj5Td5mVd5m3douYd6u4dVvXcSv8d/wUd+/ydjAeh+Awh/BSh/B3hiCeh8Cwh9DSh9sTd1+UeA+3di/ddjD8h9Edg2E2gSFeiCF4iAd6eA56d56Xd5W9eDDPiD6JaBJ7aB9/Z+aBd/Fjh/GDh99td+SdiBS/iBTRiC9TWCEPh8opd9LmeE9YWEC6eEjceEOOiEOgiFACiFY0iFZWiFZ4iFw6WFMsiF2HeCEZeCoLeCHtiC9fWCMhaD7Nd9AsiHVeiHwwWIIriDJCiEJv9IhHkYhCqIfkfHeXpofYb4hojoXzm4iGqogWwoc2Toe2b4h52YhYy4hSXYhXj4hZ94hKG4eKNIgaWYiKc4h2A4XGIoim5IinBoimi4iM2nio7IipD4c5eIf5RId5YoiXu4jIWnfsNYh6t4h8eYda8YhrHIe7Nog7XIicFYX4IYhYTIgZnoi5tIWLdoW8M3iDM4NDVYEjcIjHLIjqlIjcVojZXogLloW7soi71Ii79oi+GIi9moi9sogd0oj9+ojgVpj9Pojnaof16IjclYiNAofs1ofpPog/tIbRdpjhlpgOp3kP6YkDS4kCQxjwRZj1g1jmtYjlN4jgKZjm2jiKj/aJJY9Y/cGJDeOJDg6JJtQ4cSWY0U2Ypip5Ntw5MK6ZMMCZQOKZRD047k+I4ZE48r2ZA3uY5YRZRVOZEsWJF2p5RDw5Qp6ZRZCZVb+ZAv2Y87iZLwqJIjwZJBKY0hOZMjCYIleZdtSJM/aZNDg5PDBZOgKJN9mZdXuJfOiImIGYd2uZjK6JHMyI9kmTFmGZdoOZdaGZhcOZRuuZRweZVyKRJ0GZWPyZHPKJnRCISoyZiqqZGUyZe86JdPCZgZI5gQKZsASZtpaZsNg5td+ZllGZoNg5WaqZacyZZtQ5iwaJiz2Zj0qJitGZlD+JH9FpFfaZRhiZRfxpza6Jy7CZ0t/ymdPNiR1TmZIAmZGPmaJMma5Zma57maRViZDXOZopmZpLmZt9mZU3mPRZmPR3mNY6mbPcmbx+mbAQOcyymclkmcAWOc+Ymc+6mc/UmfAWOfxTmaIVGaaymVGeOVMWmVGYqfG6qfv8mfGeOdCAmeBSqedemejWiej2idJIedIQqWfSiWpmeh9IKhD6qhIMGhyemhDaOiJ8miTWmgEYqg9KKg/WmjhSmiP0qiQWqiCYqiDUOVN6qdOcqduMeg9emg9AKhJSqhJ0qhHwqmFyqm3EKmVWqmV4qmWeqf2Qmg2ymgX8qj3OKjYwqkHyGkE0qkAaOlUYqjh6ij/gelzSmlff9KpX9qpU2KpYOqpj3Kps3ipo8Kp5EqpwFjpG+JpGeppGXKpNzipGmqqN/JqG3qpx4BqGcqqPRCqItqqJqIqDBIqXtqqb2Cqa0KqaUqqbGKq83Cp6vqqL2qqb/KqcGKqiuqqpfKqh3hqnEKq9ziqaAJqpgpqm9Kqs1iqnOqp8Oqq67Cq9Hqq90KrNwCooXKpYfqpf4Hrr1CrM9qrOWKrOeqrNUqrPEqrpBCrhwhrZtKrc2irrPKrrXqrk9IoEnqoqYZm+opkuyplzBKjDJqjDSadcx6pM66q9D6r+baK97aqfrqKvLKsfTqsfYKsug6sCMLKSU7rh27EQCbrALbKwT/m6q0io62moYKG6oM26Eb+Z6uGZ+wmZ7TuZ5E254o+LB4GbGJ6bBHC7FJK7FLG7VNO7VPa7RCS50zip7aB68ky69/4q8y+7GuErLBCrYuK7ZuQrYaMbP3WrOucrPNmrM1ubOe2LPZ+rNDGrQxCp9dK5/Xqbf3qa2Zyq0qi68sq7Z/8rL9GrNva7aQgrb5yrhu4rhjC7kZAbeJK7eQIqs4a7A6i7A6mLGfurEwe7Jlm7Jnu7K9Yq3Dia2Fy7eBSp5/O7SBW7SDy7SH6bSOObH4WLH66LWuSLgjarjHiritq7g2S6dbaqddiqfvarxTirz1qryT67quArsNKrvHS7uv/2q7FAu4Fku8GEu9jWq9KIu9f0K5zcK9Yeq91Qu+0yq+wUu+wyu4NYq+xaq+q8u+buK+zWu5XYK5bau5GMG5y+u5fwK/ayq/6Uu/AXuaW4u0uau0kWi1vYu1vzuf/Duv/hu5rJu9zDu3Ldu4bNslbru5ktu+2vu5zruu0Nuu0nurBCwkBqzCCHwRCkzCDOwmoFu3onu3pCuMH2yyIczCI+zCJQzDN2wjOSwkK5zALRzAL9zAJ3y5KSzFO2wRPczEP9wldKuxdvuXeJuTR5y6SUzFS2zFTYzFT6wiUWwjU8zDVdwlAmzCcdwhc6widezFdywkeQzDpnutqPu4qivCAP+Mx1fsJg5cqRDcvxJMs/b7n8IboBcLe7z7nL4bncBryfiLyebbnVlcwFtMx11cEV/sxmEsJGN8umVcm2dskGmMyGtsx23MyG/syKWMw6fsx6lMEausy61sI0FMxkNsxkWMioUcu4ecuYmsxIssyI3cJY+cq5EMwpMct5Vcp5fMEtyAB3jgDId2DnlgB7YQaZBwB5AQabZwB3gQY3LmDOLMDTCRDr1gMgAAABhgBrkwYSf2DAeyzw8gBp3AWTKWDZdABAMAAANABJcAZTIGDp0gBg+wz+LRX/VVDrlgBhiwzyogB73wzBERDS3yARMSARBGBLUlY9sQBzDAAhiWJDD/AASeQNLSUQ6UECGfJQESoAEsIAOUANA3eQvr8QEVoNIYYGBxcGS21QtEECJJLQFLvV8mhhK6QF0RoAFaoAd60AUhAAE+wk/DJQ1AME0UAAVtsAdqcF7ONQdE3TDfkFvh4wNrwAdr4AMotCbflTHFBSUPcANgoAdtAEQKEwRjM1wPEyYi4AVerQUz1CiPchIbgwEaQAho4wgikCW4hFXa4FYQoAfVZFk84C90MFzlIAZykgVyZSq0kAW5IgZxTS90ICo80Fd+pQemRR5YdTcVIAL7UyvFgAgX0Cn0pDW1ky8HYws34FzXQFiqTQGhQEvJYAxRkCXAhFXeAgHDsi/I/+AHTJNMbcNNEBAF1J0MobAnH9U21+BZNtBV71IxGQAEfe0RlJBGNXUwVrMwWKULEDMIKlMMzR0Es+0q1yADEpAFxjIxWlABMvDcQ2MvGUADU3Uwg+Avkz00A1MB4XIwyEBRnzIS5RArt2MzDhQDvN0wY6ACInDep+II/sILbWMJLRABrb0vK3QJbcMLEEMreiMCHzAGbaMNMSABDGQzsiQDBZ4R/hTc+YQ9TZIxByUBbHA64KMCpz00QaABG+Q1SKABQdA2dKACF1DhE8MGQePUzRIq9+Q1hAQDxw0StzA9N34wMWIEqpDner7nfN7nfv7ngB7ogj7ohF7ohn7oiP+e6Ip+6IDAABAgUV7jAxVgAYte6ZZ+6Zie6Zq+6YkeCQVA5biD5gQQCZxe6qZ+6qie6pduAeaEO4sAAQwACKo+67Re67au6UZAKbgzC0wT5S40PfB0MCBAQ11U7MZOQlQwABBgMD8URMf+7NAuQUgkAUpkM8kTAE4U7dq+7fVDRVBwRR5UBdw+7uTePl90PF4jDLliRiJxC2lU5/uCJTogCapA7/Ze7/h+7/qe7/y+7/7e7wD/7wIf8AQ/8AZf8Ah/8Aqf8Ay/8AIvCX/g6JBuM5JO6Q7f8Bh/8Rqf8Ry/8R7f8SDv8ZIgCZBAAKDuNZpEAJDw8Swf8i7f8jD/8jL/H/MDPwEVcE5e8+oM8Ac0P/M+3/NA//NCT/OSYAQREAG73usj4Qs97jX65AK+HjDbsFVHHuAXsAJz0Db30uU2gwQYEOZDMwdkbuYH40AywCwN4wlpZFYT00Ex0NIhIQ6xkgVeowcRMDJts1ItbjNLAwMyPjQ0TgEttVF7EuIZw+MQ4OMkBeRCPjTZgFB64DVScAFKThKUMD24rd8XoAIMM94wEAGEEOADjtD0AjgSoFAqk04xAOEZIw7ldANkTy0XDgPZreFkDu+ncgq5It4iAQ61EwId/i7CkAMik9i3KQbBsjjenQXYbVszBQEAbuG5YlGeDwFaEPumIgolst5D/yMNsZIDMRTfIrA79e0RiWPZh1QsoEADWRL1Q/PZb+UH8LQKPhABLjAHOE0bgSInXTD4pwIQtbpAWCFG3DqECRUuZNjQ4UOIESVOpFjR4kWMGTOmm9MiApJVyUSKJMYnwgcg2TSuZNnS5UuYMVl6giFhBqiRIpEp0oABhi+ZEnHF+PAgRBc+gcCMgJABhqagUaVOpVq1JbQgKyJciLIn0BoeEHzKKWfV7Fm0aWF+K+JCAgUkbQK1SVJBggsx39Tu5dvX77pycmBcgMBjTaA9WS5EYAEk2l/IkSXD1AQDAwQaYPzw6QICwocYufhCKwJDBYYIEiR8gBGE12TYsWVL3P9WBsYKDKorZHAho1O62cGFxxY3SQZuuxIyrIgx6eBw6NH3pusUo0WG5BhUwDCzTfp38FV5BYHxITtrItD8mtNlZgUAABjG3Cob3v79mL7myIAPocgmvfATcECMpLEkCAIAICAIS6Qh8EEIIfqGEyIegE+GOX6JcEMO1xnnljIwgE+FNHQxRzJr7LCjmQ5b5NCcO+qgxUUaH1QHkjogUadGHvGjpY47TuxxyO+aUdGa2Lx55JFpiHQSunSWNOZJKoNT5RFVqtQSNmOWBG5LMP2aZklvklyyyTDTVCvKR6ZU882zrswSTjqp6vKRL+vUM6YxHykTNiWZ3HPQl9h0k1D/RDWSM1FGMbozz0YjhajPPycLFE1JM23IUE07ZUgSLD0VFaFHR/WUUjMFNVVTTlfV9EpJXNW0VFkjRRXQM2uNtFVdGV20V0ZpBZbQWy3NdVhCeUV2T1DnXHZPYZ+ls1jJLpVWT2WvffNXbeGMttswqY3MWnDVzLbcLWFFV81v16VSXMjIdVfLc+d1sll7t2w33x7h/UtefomsN+AauSV4yH0PbtFfvwBWmMaBH+ZQXYl5TLhiCBnuy2GMN4y4YwINBnnDi0fGT2O+ODZ5wI9Xtg9flyMsOebvUN5LZZrDaznn6CjmWcCZfxbOZrVwFhpKKY/GT2SlpQu6adiITsto/6hl27nqyWDGOrqnt/5LarSo9jqyq8f2i2mzufQy7eDAPktstvkqO+60fKZ7sq7vNstts+DW+6y5/65Ka8H/yrtwqfi2ym/Epwq88aDQhvyswyeHSfGqGLc8psc3d8luz82qPPSVMKdKc9JZ6jz1jCRnXabRX7fI9KlQl/2i1W+niHDdYV+796Bol8p24CXKvfiHQEe+pdiXb0j4qIh3ftOkp/88VOuZ/z17jaAPSnruETo+fN7Dt6j58L2XCfzwx+fedfMjQp979WNin3v3s1c+/onmz75+mNwve/mzXvn4JxH/WQ+ALxGg9Qg4PfgdsCEJnN4CXdLA6T3QefuT4P9DKOg8C7YEg87T4PIi2EGFfHB5IWTJCJdXQuQZEIUT3N4MH8LClbgQeTAsHgdtmMIa/pAhONSIDovHQ+Cd0IYqRB4RM2JE4CGxdzIUIqmCWMWEOBEjUOydFHWnxBkysXhavAgXdefF2/mwimIEHhktYsbboVF2VFzjFbG4DjdWBI6yk+PrwIhCNvYujxTZ4+v6yDo1CjGQuhvkRArJukOm7o8dXOTtGimRR6YukqSjoyLtiMVLRiSTpNtk6BL5w0rKLpQQGWXoSum5SUowla9b5UNa6blXbq6TqPxkFWvpkFtuLpeWi+UBZ8m6XzYkmJYb5uROucReCjGZDFnm5Jr/CbldQhNPdxwimVKFKW6Kr3rhTEgx+XfM1E1zIdWE3DUb98wwRvOH6lQIOxvnTsSZM37oJB09E2JPxOGzcNmM5zbJiRB/IgSghROo4OAJSHnaMKHrWKjgGvo3fZqPn6GbaEX/dlG9ERSiBj1oR491UJDeLaPh26jnTKoqlI7zoA+lZERn+FJwhjOldBNpTUlKTpweVJxtEipCVsq9lm4uqELdadxoKkubonCpMSVqUY+avaRabqrkbCrbegrVn4ZzqzqVKTmfasyodnCs3Oxq2q5qvaxObq13bKvZvorWsHJzrlis69jeOr24Qm6vVeyr1856zrRKcLBCLOzW7orY/7zecbE/bCzW/uq8wDZusjasbNUOu8/EHnCzM+ws1C67vMwibrQoLG3THgvayILSm7iCKVfLGs7PajS0/FttB1urtNMiL7WF660Ef3u01+o2tr6crbFqS9aqCjW4xRuu4Ip7wOMKLbcs3W38rsu/7P4sudxdrjSbW62T2ja6M8WeUKv7t+/GL7w82y5Su2u++JpvvjmbLvDeq7f8tu+23Byvfcs7z/OOK73QPRR7Y1XU/94twPgb8B3727sI023CA6wwFguM1fumL8HxWjBbO1zFC+suw3HbsANPLMT6gvjAEh3xv0pM1xf/8MNwDTH9atywG/M1xzZM8e1WzLYWZ/9wyDOMMY9nfNMfbyzIhF0yCossuyOnLckkrHIHdwzYHv8vyimbMmO7LMEmg/nJUh3zzcpM2TMf8Mqvy7LZtvzCOPPvy5gNswLbXLQ3czbP8Zsz6+o8tjvvcNDmSzOf16zWP08t0KRdNPnae9BDey3RR6z0+y5NzkxvbdNR7LT+HvFg9/a5gpEO26RZW2rrFTp1ocbaqLsI6+ntGbWqBiGr3+Zq3+J6g6cu6jpoXTVbn1HYJvx0OI8NtWTHcdkxbDY3n920aPNx2j2s9h2vrbRsG3LbSSQ2hHm9Ql/3DdjGHfcUu43Fbx8t3JBs9xffXcdHKzbdi1s3duudxnKnOt//ot135voN3n/LTtaki7fQ5q3JhL9O18I9dxMLfrqDyzfiiAw4pis+xovXLuP63bgk7+3JgfM25MMbuYDXS86JU/fjbVx59FpO4Zfj9uS8TLl3a/69m3M459xs9K57jt+fry/oLh76HWPu35kLMun2W7qSm47FhYeu4T97OClLTrqiU/zoIvbTN4u6X5pl3XNb51nXXfn10D0dw1Fn5NQDWHUuXx3FHQc13S1pdwbiHc96h/HOtQkpsQL+goJXNOF1bPiCIl6vihch4znteCJDfqSSlyzlW2h5UmOeyXx3tt9V6fkcgv7Wokeh3FVselqivoiqVzbrO6j2zbE9Z27H/yXcYUl6a8MembJ/Iu2lbXs0a96nnJdt2WmbUxMj/4CuN7Lw00n8LRpf29LnX9hlPnYfO9+50Mcx9wmtfLAyn7niR+9zo99gmKMfr+o3L/sV7P7yw1/nzvI4+MVsfxLDPyEzP0YDPm+zvn7CvjLSPnEjQEvjv77zPz8DQBsTQCpzQE+DwNKTwFWjQCCzQDPDQFNDtf6jPwTzQCkDQTgTwViTP8gyQRpDQTJTQUFjwVxzQdiCQSiTQTejQUqzwWEjwQjUQTbjQUDzwVcDQmbTwODjwF4zQklDwmBTQmpjwgN0QnSDwlaTQnajQm6zQnhDQI5SwDdiQHrzQnITwg0kQv9I08Jf40J/Q0N3A0N8Y0N9c0N1g0OEk0N7o0OUs0OCw0N+00ON40OAU8MmBESVE0SDI0SSM0SFw0HlUkSfY0SMc0SX0z8Ck0TyokSks0SRw0Sc00QLM8AwxEKLA0WWE0WhI0Ws40QD80Syq5T2I78BdMUqoj4sE0OXIkM9MkOIg0Q/gkUZk8Xwo8X7s8ULxMXCQ8QrNMb/Q8YAVMYQZMbH80Oeg8YJlMYKpMYVtMbMw8bDKyreEybf2xzvgzpUBDlVtDlWZDpwHD1xjDxy9EVCAkavE0bW0UU640WlskdHwse300eTc8ZT1MYO5MYP9MYajEcrI0YnQ8gnVMgUZMj/H3RIL4NINZPILKTIGbTIJMTI5JvHzavHdgS6d7Q6kZQzU6xDk/TIHgTJKVxJPdNIR+PIVITJI5TJLqTJ8yPJ5XtJs2OqcySmlvxDoXy+sytKZ7JJo8NJdtTJKOTJOPRJ8+FHQ/NHrQJITBLI3iNIsDvKbEzK8VtKsDQlpxQ7qKS5k1S6lMw7q3zAYtM9milHZmJKyME9y6HLmLFLa8LLdxLLcRQqv2wnwEQcrJw1rZQrrhQlrzTHs/w9oEw/sqxFs4xLTzNIlyTMxmSlx7zLyETHtPy+tZS6tqS6txw8zMyexGS4xRSszrSlz/zL0DRKzURKzjzNu0vNxlvNFpzM//mrzGS8zGJrTa17Tc2KTWCaTcOszaYEzhcUzmkkTqsSTHrMTancQqrcQ9+8QejMQensRuqUrtFUx9KsO90MPN68vO4MwrlETtVSTmVizns6zMLRy8nhS5cpzPp0Tmwqz7lbR7bMzjfczkJsT2a7zbHEzqGkKgRFHvyEHP1cGf4MKPsUHONcO/gkLvmkJvq0UP8MzO+cxPBcyPF0sPcUUNMk0Dw00Ed80OLJ0NzbUOvq0HX6UIa6UIwC0NdTUfRk0UF00UwstnQM0PP8u/RcvPUMPRgltxHtxBKtyBONvyeNxSj9yCnVOQUdzJKy0XrCUYvSUb2J0MaZUJPxJ23wBP8sQAAEGAJOcBBuAgdckIMEMIAZsIRnONLQKYdeoAMLMAALoINeqA++egZLmIEBWIA4wAVwCCdp4IQhYFMs8ARt+AtwmIQYcIEMUA0MaIEYiINKFSJz4AQZMA1OXQEYEAP1qCJdII8VqIAIqABUDQJdwCJoEIPbyI3VgAEg4AQh+SFtiAPr0NUPcAEYmIRG3QtpCIIWkAAImAEkSAIagAAJWAEg0BAbAocycAEMeAAQ8AEnuIEIgAAViAFP+KFyoAMYyAAIqAAecAIeqACxgAE6IFQUookPgAAIuAEnQAINeACfGINknaFfAIJmxYwkQAIRoNYWCAI4RQttAAIVgAD/L5CFnKiFNtgNGXiGGRIHMWgBCEgCUkCGkRiGQQCBCoCBc2WtOYCBCqgBRiBZkSiGRqgBCWiBObAhmqgADSCEYRgJZCiFJHiAFjCIGXoGGcCONqCFnJAFMCBXIAhVsyiHIlCBCnCEnMiJU9CADACCgT0gOQBZP8jakaCFG5AAGFhVCfIEF4gAKSgGsk0GYsgCCFBZFIKGmriBWojbZPADCHCBnO0gcACCDNCAU8haZCBZR4gAFSgCe6UKmoCAROBbkSAFCGgBSuigZ6gJMKDcZKgFEFABMdBTvQEHGcAAH4BbvjUGH8AAGfha/RKDDwABW/BcMEBbjpWgSQBZUvBc/0RwALu1inQAAgzgAZmlXC2ogBiA3fCJgxXQAGHw3GQYhAiAAWzln04A2cP13FP4206QoF+AAQgYBOkVBg1QgTiQINPFAC6Q3mTYAQwIgnOwCryFAERwX1GoW9HgH3GQAQno3PKNAMyVoCL4gBtw32S4gQ8oAgmihBWQgJ+VXi+oABl4jvjJBfEVBfdFBAiQAbWdClyAgQeQhePlW2QQCy1IXBVeYRZuYRd+YRiOYRmeYRquYRu+YRzOYR3GYVDQV0UoYb7NAQyggR0uYiM+YiROYiVe4hwOhnZVAwRWAwl4gGBgYiu+YizOYi024mSYgeJFYEV4AAkAhS0uYzM+Y/80VmItuAwgjltZ+FtcsApNAFlgQGANgAAOWBI93mM+7mM//mNADmRBHmRCLmRDPmRETmRFRuQqCAAIIGP3dYIKCIBFrmRLvmRMzmRN3uREtgMAqAA+QGA+kAAAsANOPmVUTmVVXuVLDgAJgAIE7uEAmAJWrmVbvmVc1mQOgAANQGBguFyoqIpOcAEI2FvpRQYKgIASyGVmbmZnfuZH2AJHbgQERoIKSABozmZt3mZMxgMAkAA9QGA9IGU84GZzPmd0/uMEkAAkQOBGgIAA2IJ0nmd63mYSaFcEroXLXVmq4AXxDQX3pYXL3QR0OIeCPmiDTmiEXmiFbmiGfmiHjmj/iJ5oia5oir5oi85ojN5oje5ojqboanDZUHZfEPiANPhoj05plF5plW5pln5pl45pmC5oczjdKEDgKHBdc0iHmZZpn+5poP5poQ5qok7odEiD2UVgv4UBbChqpx5qqH5qqY5qn55jCGBa6Q2Fun2NqjDdCoBi6R2EDn4M8CKCDDBe6e1eGLgFCaKDFbgAYpBeYpBVOpCgEIaA7fVcHsgAIpCgaJCBCCBf6VUDCmbeqHDeCjBmviUGEVhg0r2bYYYAgPZcJ3DdAOGfX4iBCBhpyjUJ65Wgb4iBC3CCNs4JUADe78WuAhaBuKbcWpDV9DWLa4gBCfCB1o5bLZCAGAAK/wkShyDIABBQbLINhL8NZgkqAxagAA3mW1KIgBUwAxTSBGIOBMqlBRDoWgvmH1+oiSygXGLwAd2+BrTghLxtBbKtBSe43EkgWNEGgcnOCWJYAwhggTF43PjZBiD4AAogBCBGBkKgAJTwjg4qhzFogQdgg9seCVAAAQyIgett67aFAqzOiVbIgepN7bNQB0qwDAiAAkQAhVBQhORNWTP41Q7CBRnIVx8IBBBnhDUAAQEugsvuIGgAghV4Vj1wBFFwBD2gAecGgg8G7SJoVg1YA0YQhU8IBCR4ANCI4xkyhzhwiwrgAkUABVAghCiAgAs41h1RC08YVgh4gDDHgBWQAf9LmN8f+oUg4FZn1dcKYA05yG4UygYxcAHz0Nd2LVYxUIkfEgdh/YDLiAAxxgAXCALe5ixLiAHcwHOxaAEZ4Oe92AZLsPEAIIAMkAE64PMqEodOIAIYqPQIiAEzyF3CygUxkAEGMAAGiAExyIXHnpxfMAPNJoABaI1OkHMbugY6SNoBGAAVAAJLEPC/MIddsIIqeAX7JqxqsIIpYARcx6Jt+AMq+ANhDydxYAQqsIJq6PJwKodXsAIr2AUTn06ifARiKE4erT4fRVIgbUQhHUUiTfddXPfTS9LKW9LVa9LeIVPEMdORqdAcDdF8kvd+pPfYs/fPw/fa03d729Lr7FL/hE89hT8+hr8dGd1LGoUvL/0nMP0oMVUpgs9Kgx++iJ+9id++io9Ehy9JBlXKck/5YazSYrzSmMzSTZT5iKT5nbT5Ulz5oGz5snz5eMf5jdT5qeR5Dwt5xRz56yv54jv5BoR5jiP6mzR67UT6vfN5ygR6yxT6orr4/Mx4ANt4hep4vUG7mOH3wvF3kAH4MBX4+7ROlof4dr/Ed2/FoU/RV09Ap88+qD9DqU8dsJdQsZcwsqcos78btHeZIu3RvR/Dvl/Avw/GwA9Lqn9Kqy9QrBeiwS/Twteww/eos/94ulF7wWH7jnF7j4d7h5L7n6f7BlWvyo87pXdNpuf7ug/F/7uHx7w3t9uH/Nxfxd1XyXjX+uDk+uH0evK8fLXM/Bbd/GvUe+cPUujPPOOPTuQndwftfYF7/F6M/DKc/Hycfc/p/H7/fBYL/cSnm8VfGdP/G9THGNUffdbf0esHz+wXT+U/KPNfe/QHiHUCBxIsaPAgwoQKFzJs6PAhxIgQpz165E0iRofeKk7L6PEjyJAiR5IsaTBdRWMmV7Js6fLlS1WPVMGsafMmzpvGKqbL6fMn0KAMKVoUanDjo45GlzJtyhLlI5VOp1KtClGmJKtat3Jdt/NRz65ixwYletEpUqVk17J9CVVq27hyR8qkOfcuXolfw+bt6/eg2alp/xIu/P+2MGK/kmYmbnx3r+PIbAOj5Sj5stjDmDdrxcr5M1XIoEcbpdx0MOnUPzWrbn2zruvYNUXLrm3SNFPUtneLZM37t8fFdoET18uzOPKHuJfqTu4coe/n0gnCnm59IO3r0pcbba7defTvyT2Ll569fHHuQr2jBx6+/W/h8JOfn79bfVD29mu/3y+7un+81Rega/gBpR+BqvWXYGrkMSjbgA+OZuBPCEr42YIXcgaghqlF2CFmFPpkIYiSZVhiZPKhONqHKzYmYk4kuojYiTMW5qCNl7WY418w4iQjj33VGGReHBKZ2I5H3uXjTUAqKdeQT8alopSFJVnlZBWddZplWP7/FaWXYxkZ5mPHkZkXkzY5eSZXYLLZ2SNZvVkmWHPOlWZNa9pJlZt7OkWln2tdGahTeMKkJ6FL9ZmoUGMyqtWgjwpl6EuISrpaSpd2haOmVUXaaU6UumQpqDYtWmpNjqJq1KerwiRqS6S62tKps7IEqK1CtZrrSrCyJCuvJNUaLF1xEqurmcf65OtKwCr70bDPeqSqtC7tWq1HzJrkLLYRRdstRLiC29K1406kpWBdmktrpuu6RK27IZUb70LalsQtvdC1m29JnPIrb7L/hmQvSfgKPNC3Bw8krsIYzduwQASPZLDCCTcML8QNPQyxxCJRfLDFCvubMUQbN9xxSB8L/xzywRiTrJDJCqMMksr/siwwwy9rHLDODs38Uc383vzvyD0vFPPBP3sUdL5D8+uy0QUhLbDSGTFNr9P55hw1QlP/WzVGV8ebNb1Qcy2Q1/yCLZHY7pIdb9FnG5R2vmtH1Pa6b7u7tdwE0U2v3RDhba7e65p99t/xBv7Q4OMWbm7cfWPHs+QFLa6RupWftK/mBh3OdeLuXt5Q4+A+Pi7flYe+7ugMld7t6eBGrjrlna/T+kKvYxt7t59Hvbq5uCuke7W8Y5u65MCPK3xCxEtrfLW+G608uMwj5Pyz0Es7e/K1d279Qdgrq/2zyPdNfbfgH5W57QKRr6z0PaOPrfoFif9/7PvHcn++95rXT9D9iJU/YsVPZ/Or1v8GEsBgDTBY5pPbAaWVQIEskFcN5NX+INi/yk1wHRXM1QVzVcCXRfBZHfygrUJoqwciboOSOyH72qfCWY2QZCVUFgyT0r6CzNBVGWxhnXY4kByqRYg9XBULQefCvhFRiAjjnBBrmLEbHquJTlzHEVH1QyUG0YlWdGIWSyVFiFGRWF80IhR3mMTfLVFuZ9xhGEG1RTZ2UYhvlGEa2zfGhpUxWHe0XRw7tcbptfFsf+xcIDW1R4X1kVeH1FwiLzVHQtZxh4+sXCQlNUj5FZJrl5RcJh+1yIM1Mlef7FsoGTVJTlayfaeUWyr/EzVKgZXSVq88WywJtUkDdjJqt+RaLgO1Sl620na/jFow/TTLf9VyVsc0WjL3tEsS9tJoz+xZNO20TH4101XX1Fk25zRMahbze+iqjA6vGM43TdOG1ezZN1+2TjZtM1/dXFU8STbPM43TneX03zm5lE4w5tF29aTXPVGVz4ztk0ztnOI7dbZQiDU0TP2E6D85GNDcxBCQBe3cQeOV0FJNtGEV9dJDyRjRl5W0Yh/VXEjdNVJQtRRkL63cRVWa0RdulDkdReRNJZdSPq6UZDVdWVD7FtN1zbRTR7VZUuWWU6LulIk97c5PIRnVsy3VXE3V1FOFtlWuDZWRRc1YWJs2/9aoTdWsVXXjVdeTVUyu1WhdHddXL5VWrNW1Z2Ul5Vk5Ftf8zBWUfdXZXcGVV0ntdWyHfVlbAftWQw72QIVF5WNJ9ldaBvZkla3QZWGZ2YwltluLfVRj3TZaiEWWs5P15GdHFFpcrvZijLmiVzors9jGaLbArK3CNstM3SaNtz/yLTKB2zJj4fa0jEpt3pQrsNJiy7mJgi7hpPsv4XKTuFQzbpOQC03tPu22V7QuobDrOPLmq7XDfa0vwasm8WKTvfTirj29+zX55om+4LQv3MzrRPQGSr2mA7C73Ntd+FqTv4fyrzwRbDgBC5HAfjIw7CRsLvwiVL9qc3ClIKxPDf+PS8H5ZTA8QTwqETOUxLKj8A4tvCcM787F3eKwSD1cNxXHisUUtTG2qFstGduJxsUDcvSYe14dA47Hv/KxSZEsLRzLlMmKc3KzoOzSqOB2HUKWFpHnZOTnSflZJu4wiiWK5W1p2aZcxu2XnxXmN405e2VWFpWZamXRrflebUbqm6945hynmaV9LtifoRpoJ8ZZWXNmU53Hd+dj5dmre2bdoSeWaLEuOoowbt+jzxRp/E2agEoe8KWDl2mPbVqtnVbjp20XajKNWoClDlajjzXrMNWagbfG4KkrnOrlrTplrebrq/UY687t2ku9tuCvc1VpvA67esWm2bEdm2yDBjv/xtVO37WBlm3Vbhuky9Zcs7H0bBBGe4Xnpl2hjRrupY07uuWG6bu7F2+0zttq9c7uvXHabVB/m379Dtu/1xtwoeabf/sWbFHQWUQ4tpuGDdfgwz0bcYFOHI8LV+rAZV1wBB6cbQk/8MelenEg8sWOJb/byTOc8rNNW7Ejl+DLBRfzGs+ca4OucsZ3u3GODhSNPWfryrnYckvmnHE7P/LRjVZz097chE3HXNEpHvWe5ZpY6a7SulNYcR+GnNlVx+HVSfd0Mm9dZ1Ov7tmrmHbXrd3ObYds0um4dFfOPXd1l/TdSfZzPQe9uEP3adY9DhdG552Sezdm34f3d1IHPmNv/x9y3M0Y+eZN3taVZ23Z0Z15P27+ep339edtOxxUF/67h8dq4j2a+uA2npWPN+fr5Rp7oM5+uasXduv3m3vC7l6rvZ9u6OF9e4AO37LFp+vxt1t7Yi5fo80H7fMNG/3y/t7bwf/w9WWbfcxuv73J13f1eRr+3o5ftOUv2/TJmX6rrv+47aft++N1eTCP3pGlD9/pQVv+Jdj5Odz8wVX9hdf9/dYATlj3Edz37VgCztcCJlcDblj8+dMBUtYE9lcFjtcFllgGYtQGwlYHPtgH1lcIvpicLFkENtkJhlgK/tcK3tgI6lQJxlcMsoQ5QEMhkAAJwIEvlAMcSUMnlEAHaP+BLoiDEGkDLhwBBxwBLmiDEImDLmgBB5RAJ0hDDpJMOfgCHJBACRTCM3RhSZxDLgRBDHwABEBABsAAEHQCEWrOL4iBDLRAG2IADMQAJYBD51xDHMQADFAABFCAC8RAHFxD54ADJcAADGAABERAC8iAGPxC55RDJwABDLAhBKgADARBLpzDT4hDGcBABkTAA1xABeQhDIjBNkiOOTSiCrQhBVxAG0pACwABNFTOLciACkhAG14AIUrACsQALlTOMwBBC0jAA0SAKkKABHwADFCCOUjONhTBIz4ABFTAKj6ANJoBE+KEOBRBC0RADSiCLSRDMgxDIyABBKwAELwiLsn/AQxIQAgEgiyoIzKEghZAwAfIgCXKDSc8YgW0wSkggzqeQhtQgB5yQt/8whpCABeIQjGooywEAghIAAzIgTrIzTYEwSwiQSMMQzIggy0owg1AQAsUQTjWRDqkAR7ugTGoI02WJCK8oxjMYdRoAgw8QBQQQ03SJCloQAYAARVyTS/EgATYwCwEpTrOgg1oZC+cjTYAQQZogCg4ZTIQQxRAAAxowtmUQxHMIiIgpFO2gSSaQUfWBC/EQAS0gVbSJCF4ZSdwjTYoJRKYpVaeAjHGAdeUQxB8gAgAQ1wmAzCIwAcEgU72TBysQAScQmEiAxJUAAwcpdF0Qk8iQknGJVrG/wAv2AQRCKZeaiUy/AAGyMBivswkOGZTFmYytIFGSkPU4AIMQIAjuGYyOEIEwMAxGo00yIAE6AFuykIErMAkRE05yAAG5KVrIgNiFkFNXEM9BgJu5qZX+oLRlAMQYIAUVKctqCRYGk0ZiGZ1ImYZ7CQe1kJ1SgEGAEFqZkwv1KYjjKZTIkMgSIAMKOJL5EJPrkJ1EoMbvgE1DCiBFqiBHiiCJqiCLiiDNqiDPiiERqiETiiFRmgsYEAEEEJ1JsMNYIAQVCiIhqiIjiiJlqiJTqgzYMAFgAF9auUXYAAGOMOJziiN1qiN3qiICgEG1MCG3uQHxAKOBqmQDimRlugbfP/AAwAlbq6CV/amS3ACHgrDhmoABHBARVwplmaplm4pl3apl34pmIapmI4pmZapmZ5pmVpBADwAKGyoE0jAAaCpnM4pndapnd4pnprpHQCABOzBhvKBBACAHeQpoRaqoR4qotLpAUiAE2woKDxAAFhBok4qpVaqpd5pB0DABWwoMLyjQ74ElEIAYVanLZLApZ4qqqaqqj6CmkJAm1bnZCLAqs4qrdZqne5pcG7oHgQqHtiqr/4qsHIpAjDqhn4CBATAFQSrsi5rrWaqBnCqStblftYmZOJmp6qAIHSDtm4rt3art34ruIaruI4ruZaruZ4ruqaruq7ruXrDLqhABAz/wobOQAY8AbveK77mq77uK7/2q7pawwdcQBdsaBdgwAdYg78mrMIuLMM2bL4+QQbMwIYOQifugsNeLMZmrMbyqyDM4qi65ik4AAzkAkxkA3DyQXUqglcGpM6YQxBgQKPi5ixEa9TEwQeAwIaCwAf45WXiIS1UpxO0ZzX2DERCwCJUJx9QgAxYpkuIwc1WZGTmAAYoZtRYAh76p2uCAX5mQ9ToQm0qAm4mwgPAgC5ETTYopRosqUpaQtSYg1XmQIvWJDHorBjYxC/U48AWJh/sppP2zDYo5w1ArVaGgkrSAdeYQxF8gAa0plbOggZ8QBGIYtTQwQq4amEWg9TKwDdw/w1tQgDKxiUydAFlsixMzEFtdoGS1iQy6IFKlsHQRs0t1KMPpKNTKkIFJObmcg00xAAGiEC1BuUpiMBp7iLXfENgVsDROmUt+IBGesLZmEMZVC4fCC5NEkMXQIALzAFOlEMZuIAEgIAfnIIwDMMqDAINqCQR+OHZqEMjSkAFrIEo2AIxyIIi+IA/AoFsyg1/QmIWOEItEEMtOEIWQAAGxADJyk00AMEHRAASKIIsEIMtiMIacOM09g04EIELRMAMDMIqDAMwnEIfgEAEuEAZvOdLlAM9fgAwtiE0viE4So46dEIMrMAqsjABuwARcK3k9IIyYoADRIADBGMuYqfkZP8DETwiKrJwBayADHSCGfILKcKABlDAD/9wNMIAHZhwTfiCGMxwAzRABsgAEejCEwuMNAQiDDSAA1wAHMrhIk6CDMQABARxDMjAJORu5YxDJsZABTiAyCJi/mKSLhCBDHyAH6tADFTiUmQDJqDACRgCFwrRN+SCI7PBM7yu7YhDLzTBCTRBL7Sk7ZjDM7SBCaRALuCx7aiDNBjCCaAAJugw0XWc7C2epz2gyL3gle1gj81ghNVgkN0gVZWxvOnyk/HyiPlyktmy2eEynxFzlhlziyHzlAGzWwkzvzkzm0Hzj0mzmRUgxlkzxG1JLOPWSWFJ1wXL10lJ2M1KOVfJ/sn/Wf+Z0v+tjzZHGTfDDzVLFjhrnDgjnizzHi3v0OBZGjNjGjb7WT1vWUC3zzs7Wjzb0jzbTwCy2z3rTz671j4LXT/D3j8b30JzWwuyXkYb3kbrXkdD30ebmzKLXkGr2kEjWkK7WUprTkPr2kM7U0QD0ESLXUWbWkgD30i7XkkT30lr30wL3EorH26ts6u0s5TUtNfdtDfltALtNDuP3aqcM6+k85Mw9ao49ZMMNLW1NLG9tKbFNKAdNcMlNfotNVVTkFU3NVZr0UW/V1AL31A7X1GTn1qD3E97312DX15j3167X1+rHFsboFubNauhtaIdNs3V9YIFtgQOtvgVNv5B/7bPeTPLLbZlsx9mM6BmI11if7Nnp4tjc9poS51knxhlw+Bn219oW+Bqc11ro9lr53JsK+Bsg2BtIxZnK91pSxw5z3WpQDU6SzU+vbUHxfVXG7cc3Tah5XYz7zYF9rYK/jbe/TUEUrdBW7cHYjcNarfgSTfQebdLgzcKincvk7flmTfhoXdZq7cMsvcxuzfocfcty7e1Mbaxpbar4bfqdRlXK4lXowpYKwlyb7VyKxRzo9BV9zSuwTdB8ze4+Te2ATiyCbjIBLfeDTfHFbeE88qC50qBH8mBl0qCH4lWm3iDk9SDOzeCQ3eniLXNkXV/0/eKabi2cbjvEfiL01SM8/84ufk4zlD4WFu4wWG4uBG5vRk50Xi444H4OKsTjSsSkt+4kpMck9ObkwMclPNLidvKiRNJioPKihNJi5N5kDvVkNt3NIe5+en3Mm85znW5v325wsn5fWU51eH4hev4LsP5NvN5gJV2Z1/RmXdKmgeJjf+5nVsdniOcnqOcoRMgogu3or+5iF/6uoz5rJR5kCy6pjQ6jzw63AH6kgt6MRO6PXs65Ph5qkc62k26yVW6zME66sg65qk6l7P6M7u6QnfZmod6m4MVp1v5iIuQlNselftzp3cZqLuKqPMIqV+KqedIsVP7setVshPUstsKqvc6rcudrcMcrvOcrr9Ypn//+Kafu86lO9Stuw22+5S/O7Bns7DLNLE3O/U9O0dHO5zxOv/5+p3nO0Lve1pLO8HDs8FLOsLDtMI/dr/bu7PjO2pPvGr3O52zdLlrHrw7nbyzHb0fT8M79MPXesSftcYHeMUDecqb+8o3dstvOMfD/MeTXshjXc33+Ms3V7cz1rcbXclXy7SvSrXnyLVLSrbbyLgXfM77386r3cjbXdFvz8nbdMyD/Mz/d88XOcNb/L9jPHEr+9V3s9jLH8CbtMALmr+rPdmHuNmHPc6vPVG3PeOlvQbavV7jvad1vFLHfZWD+9njs96TIN8Ttt/D2uHjYOJf9uIrG+C3teBD+9wP/3zjB/Pjg3bk287Ro0rS28jSP0rTz8i2I33Qo9bQa13hW/TkK3blB/zlX9Hnl0roz8joM0rpu8jpg37qP9fqK97NA/3W63zXZ/jXP/nPu2DUy/PU013VA17rE0vtg8rtu0juJ8rur8jTO3zzQ/Tz+130U970T3jmV/Pmy3bnd071d8r1r0j2E8r2o0jv2/7vX1fwz/LwM3/68/b6A8Q6gQMJFjR4EGFChQsZNnT4EGJEiRMpEpT0SFVFjRs5dvT4EeRHY48epQt5EmVKlStVTiPpjSVEbySnxbR5E2fOlOlIGtP5E2hQoQhVYRx6FGlSlSNLKnX6FCpEl49gKp35qP9mVK1bt/J85JNrWLFIi0oaexZtTqYm07Z1G3Jq1aRXs761e3eiV7B4+fZdWDSjX8GDB64lfLhvXKd0ETe2q9dx5LYXA0u2HNbwZc1RFVuluRm0U8ihSR8tWxp10MypWdvsPPdza9krR8+2fRLwbd0gV+/2TfE1Usa/iUusXRx5Q8rJmTPs3Rz6wOBHh0e3vu74dei5tVt/3h359KHVwSfPXr74afTMv6/fLV4oefe+z8/Xvdw+8fb5ZcMPKp+/2eoLsDXuCLxtvwNL8w8oABVEbcAHSVNPwtYSrFAzBn9yEMPNIuzwMgNBJO3CER3TUCcOTYzswxUbw8/FzUqMcTD/FHNSkUbCWsxRMAp5jGzGH/GyESccheRrxyPvElFJwoJssi0ibzISSreSrDItGLH068ktxZLSJiq9HOvKMcNi0sy3ukyTs5cWi43Nt8qMEyof6UxrzTuTAjMmMfUUrac/JzNKULTyLDQoPlnyE9Gh5mw0KDQhherQSXFSdCVGLdXp0U1xstNTpSoNdSVMVdKU1Jg6TXUlSVlVjSS2Xj3K1JRQnRWlVXENSctdgRrV145qRenWYD3S1ViOQE3WJmCZBc5Nz7B6NidkqZ3I1WtRclbbh4Y9qdhuI7JWXId6LfckbtFV6NuQwl2XIXLhTSjbeTVS196C2gXp3XwPktdf/4KWDZgifAne96N+CR4I4IXPXXgigwNG2COFIW6Y4HohdkhifynuyOKFMQ544I0f6jjfjzkKmeCR/dXY5IVQtlfljVgO2OV8H46Z41h5nqhmjW72N2d7S/5ZoZnnDbqiofMtel6YkTZIaXiZpshpe6GGd+epE6p63asnynrerdeV2uvCfE67IbElIhtes9E9mm2CwEbX7YjgXlfucruu2+61AU8ob5ngHPzfQBGnl9DFD7q73MIf2hvdvsWle3DIxZXcIcrLtbxbtNnWvFvOG/JcXNC1/Rtx0rU1nSHUu1X9WswBd/1a2BeSXVvaqRU9bdyp1V0h3q/1/VnWMxfccf+CiE/IeGqRZxZ4r4V/9nmEon92+mRtr/t6ZrM/aHtmuzdW+duZb16g8Q0qP9nzg61+6vCTdb8g+I2V39fvR1+fffgjiP6Cxb9d0Q9p9jOWAAdCQF8ZEFfpAx8Am8dAgThwVxCclf+CR0HHWXAdGMSVBl+FwJ8pMFggFOGsSMgqCf6vKexzXrRgMy0ZMkxxNxSICXmGQl+p8HAybGGqOGg9Dy4OiDbU4RBJ9cIOxlCHSazLDZkYKh7GzIe7kqIOBVJFTxWxfkdE3Ba56MVNXdFkWcQVGZeYQx060YhQvCEbqejGG4IxgWIcHB2FaEcZonFjapwVH9lnRkvBMYxylCH/IZtnyEkBEmKCfBUjHedISOHxhHoEHCUXZ8lGITKPigwgDYUTxEL6kX2QXJgkWcVJxHkSUZjsoSbr5srBwbJQqiQYK1NlS8DhUlCgzKQoK0hK6piykahsniyxSEu2+bJuwPyTLgPGS1JBk23S1JMwZ0nMDxpzPMispDIdR01/WTNU2EybNu/EzDQ6M23q9Bo76cTNZnoTieCMjzg7Sc7FmTNf6PSUPKdGzzi5M5Dw9BpBkWZQNgHUXgLdFEN/5tA02fOd+ByjPv/Dz1f6E3EIjaRCp0ZRnlnUTBCdl0QtZdKYoXRMGE2oRvfI0QZ59JYgHZxK4cXSSbnUZDD1kkhX/0lSpAF1Y0LdkkxHStNN2nRDOP2lTgHH03X5FFJIvRhV60bUXRr1Z1oVGVfZZlV0YbVRYm0ZWdPG1KI6tZZQTZFUo8lWr3m1mmDlmVpxZtepmbVcaEUUX4nmV6S59atwfaZcb0TXbBr2Z4AVl2ALRdinQZZneD2nXmNmWa1hNmaIzati48nYIjl2naA1mWS7RVlBebZsqt2YZgPKWZPBNm6yhRhrteXaP+GWb7p1WON06Fs9Abdyws3YI8zCxXUY907I/ZxySUbcG0KXThYUhyuWoIRMfEOH5fgFE5QQiGwsMRphUEIYoiGr5qkjG4FQAhN+UQ4dbiMTSliCK8RxFP9pxAEGKigAAzIAgzL8onnfmIQMYFCAAkhABkXIhXsBJw5OBEEGDWBAA2AQhE70t5O5KEIMJMAABsBABpTYRvOeUYYYZMDEKohBHKQBlHRYQgYrkAAEeAwBCagABnOw7+ByIYMWYKDHPv4ADMQA3sFFIwguQHKSMdDhaCBuG2OAwQck8IAH8BgDLZBBLhBXDjlsecc9rsAKZGAJCrMkHQCugATU8IlVtAIUbdCABFwwBhCzjRMwQHIUFHEKWYjCDzSAgAqCoA3A+UIGH4CADwhRClmcYhBIeMAHZOALwGkjCC2AAA38IApZoGIRUYBAlTlR4TG4QAIaaAMoZLEKR4D/Yc4wkMObVWIJGEAgCbZARjKITWxieCECuuZ1zHQBAwnQgBXFLjYyArFoIvx5ateQQQY0AIphSxsZjtAABmRwDbaJowiSDsS3pb0KGkgABrpgmzrk0IIHfGEY0ia2LZAAARhY4ibQcLYT2K3vZKjB3/L2mjiAgIEZBMPgxEaGIiDQAoDPcwwquMAqklHwYq9izWNY9sYsIWpFRJzYwaABBoCA7Z81GwJrQHnHoQBvaNikDB/QADBm3nEaZCAII1+YJkR9ip4nQwsVgMGKp9aLXw/i6ISIQAx64bVtxKACWjh6KR7QAk3MMwgfoIExeg4MDaigDDHZhgwk0IajIwMR/xCQwc0bGgQMIOHoyViFA2DgCa/JQeMeNzgyLqCCOXjNE7+O9tGRAHShB0zgEUBE3tsggRgwXSUwL0Xea7HoSpAD9KEX/ehJX3rTnx71qVf96lnfete/Hvaxdz0zWhCBQOQ9GSL4ABlk33vf/x74wRf+8GEfjiNnAfdZCHM4iN985z8f+tH/PRkyMAPBGzwQEmgBM6Tffe9/H/zCr4QKHmCLvJfC37xgSSdEbf68VwACJCDJ/Olff/vfH//51//++d9///8fAANQAAcwAK0gAB7gE3APCSoAAQjQAR8QAiNQAieQAgUQDwBAAvQA9/RAAgAADyoQBENQBEeQBCEQAf8kAAmuT98cAQICYAtKEAZjUAZncAJJ4AEuAPdsoeI6gSU4QdSEAfc0AAI4gAaL0AiPEAkfwQAhABRwzwkkwACSUAqnkAoj0A4AoAL4APf4IAIAwA6qEAzDUAzxLwAqwAlwDxRasArGkA3bkAo5IAI0APeCoeJabSVwQdQ47uiIYdXQYBn+EBADURAHkRAL0RAPERETUREXkREb0REfERIb0RTgb/Ly7gYwAAciURM3kRM70RM/ERQfURkkoALAAPdwTQKUIRRXkRVb0RVfkRNxAANuAPfirgJSARZzURd3kRc/8QwyAALI7uhWwd/IbCWkgcSg7ujSEAbUD2nKIQb/MEDrjg4YKu4SvGYMxA73aOADxsBrLmEFIIDnjk4LyG3IfoYXYOABmvDoBsHfrmwl1CEIMsAGVLDYoIDcXC5m5GAFKsD9UI7apo7ukCbxIIAUji4U/M3vpkbgIOD2eq4WKsDwFi4ao+DtbuADgkAdYiIXfu0hUY4FvS5tpIHtLHLmWqHw0m7hGq4GiGHmiKEGWE4fTUYdykAFKqAVei4KKkAGauwbRc0Req7aYMAYWcIcxiAcCeH6PuECPuDa2IYSXCACwOD6VkEEyM3c0iYXSAwJxlHfgAEJLK8op4YkMWAE9FDfkAEMIMAFKOHciOADKoAd05IQIGAFxuAcbuIb/4IgHJMgFNjtFLQAAj4ACLIybcyhDKSyBhjBJYlNFtrgAqpM4aDS2UBgEGqh2GphEEAA3tyybnQhGiugDWTh24ZhEWwgAlygDMyhbq4BCCRNC07h25AhFJLALoMAHHJiG8RAyiLAAkaABi7Ax1wgCHyybsoBwCQNAmbgBoRQAtjMGaPpEraMAhwgBGwgBHjsA2JAEx7PZHghxyggAi7ABkQgAiCgwOTgHNlGGqIM/i6ABmigOjHABcQA83BiHDiBwVbgAz5gBWAgBixhJucpF4IABvjTP11gxhxtcZ5BDGCgBfpTBcRMDJ7BcbIhDmTABfhTBVYgBoJgwhYHHCwhBq0CrD9Z4AVkgBMG1CbEgRcmIQ7MYBJy4T4XR7wsIQ7KgA464bwKKRo0YQ7KQA40ob1kKBs6gQ7KIA4sob5kaBtygQ7MIA4mgRdY1LmuFEuzVEu3lEu71Eu/FEzDVEzHlEzL1EzPFE3TVE3XlE3b1E3fFE7jVE7nlE7r1E7vFE/zVE/3lE/71E//FFADVVAHlVAL1VAPFVETVVEXlVEb1VEfFVIjVVInlVIr1ToCAgA7" style="margin-top:1rem;" /></div></details></div></div>
-
-::: {.sourceClojure}
-```clojure
-(view
- '(GridGraph [5 5])
- {:folded? true})
-```
-:::
-
-<div style="max-height:600px;overflow-y:auto;"><div><details><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhwAO/A/frAB8mMSIpMyIpNSQrNSYsNikvNyMrOCMsOSQtOyYvPSkvOCYwPiswOC4zOi80OzA0OzE2PTM4PjU5Py83QzM4QDY6QTI5RTY8RDo9Qjw/Qzk+Rz0/RDA8TjI+UT1AQz5BRTtBSTxCSz1DTD5FTjNAUzVCVTlHXDtJXjxKYD1MY0FDRkJER0RFR0VGSEdISUpKS0tLTEtMTExNTUFHUUJJUkNKVERLVUVMVklOVkZOWEJNXkhPWkhQWk5SWEtSXUxUX1FRUVVVVVFUW1JWXVpaWl1dXUVPYEVRYk5WYU9YY0FRakNUbUVWb05bb1FaZlpdYVNcaFVdalZfbEpbdkpcd0tdeExeek1ffF1gZVdgbVlibk5hfVljcFtkclxmc11mdF9odlhmfGFhYWVlZWRlaGpqam1tbWJpc2NqdG5ucGFreWJsemNtfGRvfmZwf21ye290fXJycnV1dXp6en19fVlvkFpwklxzlV50l191mGZxgGhzgml0g2t2hmx3h2JyimZ2jm56inl9gnF9jnN/kH6CiHyDjXWBknaDlHiFlnqHmXuImnyJm36Lnn+Mn2eApnaJp3mMqn6Ts4KCgoWFhYWHi4mJiY6Ojo2SmIuSnZGRkZKSlJaWlpmZmZ2dnYGOoYKQo4ORpISSpoaUp4aUqImXq4+ZqIqZrYybr5CaqYGWtY2bsI6dspCftJ2iqZqir5Ggtp+ms5OiuJSjuZWkupemvZiovqGhoaWlpamqqq6urq6zvLGxsbW1tbq6ur29vZqqwZyqwJuswpysw52txp+wx6Cwx6GyyqSzyqO0zKu3ybO/0r7CyLjB0b3G1cHBwcXFxcnJyc7OzsHL28TN3M/Q0s7V39LS0tDR1NXV1dnZ2d7e3tLZ4tTb5dbd5+Li4uXl5eDk6urq6u7u7uXp8PHx8fLz9vb29vb3+vj5+/r7/P///////////////////////////////////////////////////////////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAwAO/AwAI/wDXCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS55MubLly5gza97MubPnz6BDix5NurTp06hTq17NurXr17Bjy55N+2a6bM9+XTNXG6U2aL6kiet98ls0X9G+ETcpTpovaNqWlzR37dezbOlegrsEREYMGDGATP+KLt1juU5FZMiAoV4OtPIe0+kqAx58jDG8ssPnCE1O/e9FeFLOfhxpMwkQ38UQQxCXgMMSLjK0gIEEEEAQAQYtxKCJfgRa9EwQMHxAYYUVqADDHMN1aNE2YsCgwogQSGCiGNuoaJE4/qmAQYUxZgBDEM/YWFE6msAgIY8SZNCCDLeoZAkMOyYRSCOfDBJFBBLAIAdvQkakiwwZQHADH4yAgkgXF0jgghgOdglRNECsAIEIbCgCiiJriBDBCkBI4yZE4ojRggQXeIEIKIzwcQMEH8igy58PneOfBBFEMQgojQSCBAQYxGAJSp7AIIENqyRj6qmyIBEBDJRA2tAzMmD/AIIjp54qDBgQtFAGl64mtE0QKlAQCDK1IoNMIBF8EESNvSZkzhhygiFMrckg4wgIGMgQZLMJUSIqErOcSmwyq9yQpScmZQNDBTwQQ624UGT5C7cHlRNEBiDI8u6pfEAAAyf0HmTGChGEsq+poUCwghkBG8QJDBD4cXAysoCg7IAND/SLqFCM+y4xPFQQQzYlybFCBbRMnAwxIXwgBocNdwLDA6ConEwS2baZ8TOi8mHzHhJom7FA4MSKhMfvIgMKBC6gO7Q6RXwAgrsT01LBCnKQVLQEYNicTCASxODn0ERgcAPS+5biLy5Dr0PHyVRPTMzVk7SNC8SlqGxsDhgQ/9G2NDFEEIjXagStM0i9QCyK17Tkyok6kEcu+eSUV2755ZhnrvnmnHfu+eegh+65uhJIbDMyFsch+uqst+7667DHDvo5QGAQhdfJQIEBEObI7vvvwAcvfOtxqAAC7nyEjd3wzDfv/POvc9ICBCnbHMoDMPQykifT2+I1MhVAUMIj5Jdv/vnop6/++uy37/778Mcv//z01y//FgFA0AjuSEiQgP0ADKAAB0jAAhqQfngAQAXagLs2SAAAeTigBCdIwQpaUIAJkAAScNcICARgCxcMoQhHSMICkgACFcBd41rgtJBoYnrT8poGIMCBEtrwhjjM4SOokL+aec0JFQiADv+HSMQiDtAOCvSZ15IHADsY8YlQjKL6AiABJ+AuYQGwghS3yMUicgACGsDdMCLQAk2MBBcugIC+bFYMTkWBGHCMoxznSMc62vGOeMyjHvfIxz768Y+ADKQfG/EACCgCdzzAgAgEychGOvKRkIykJAEpCwdUQA24W4MEHFCLSXryk6AMpSgdOQIM8AB3iahQI0bJyla68pWRjMKO0LYvWTCNbSKBBsQS4TVS+CsXQxPHurpmM2JQYAWtGlrUcoC7G3ygCG2jBAsoELeJgaECMEhRw3IBMVJ4LZUweI9IzBEEDPjAa10I2+ECFocPaKCa+0KEv+Y1NOlBoFQqWwXTADb/tI1BABE2G4YGVBCHtn1DBhXowul8sLtzkKQTaVyEytTWgrq1bWMSWIPKagGCDLzMoLHyQTEmhgyGykA5QzuHGKRWC5WpYVXbGtokppe3iS3CATDoREnKQYQVUMCH71oFtoCA0rbFYXqD25ctdoDNmA5NZhHgwkg/xoVV6bRt63hGDNjlvaQFIlcFxeo3gIAvfL4LFBV4JsZIkg0gfCACYKieqWzBhwp0yqnBLIKcoHCKWhEDESHI0lWxmg45uCACN3CEx6x1g1XJAWZPXRcIEBE3ZJwCCg5gQRG0edEYYKACfABGrWihBkYBgWQniUYQWEAhGjjBCYuSwApk4Aus/xIEHGNwwY5EgIQohIxROVWHbQVSjjlAyQEXQAIUfjBDDJxorVhVRydi8AEU+gAKSBABBC7ggjGss22+kMEKKHSD19IgRi0IQjRU8o05REhESVqSGVA7XOJq4jvwxRAMxIBX26YjF0CAwQrSdIEP/AgXkLXtM8QQgxVMKK3s0QR0h5sNMxhpQhL4QIbmUFSVXIMTRThAAHqgifXW1yDfuIUZEBCAEEzCFw49MUHEwQs5UCAAE5iDLsYhY4Kc4xeTCEEADmCGW3S4x9G4RA8MYIAicIK+LvEG+abRY4Skg3zGqDJCVPEIVWj5IMUgn3C/TJBpkM8bM5HyI6hM5oFc+f8RWW7zQLjsZTkLxBjkS7CWzfwINMtEzWyW85vjbGc62/nOeT40n/0cE0AfetCHXgeXJRFpPD9Cz1VedJqn/GgsR1oSXa50ou2s6T9z2s6QPrShD21pTPe41I0+taA9repHUJrVo5YzrGHiaFTTutChxvWlFX3mTa+503D+dLDt3Gpi99nYgW5zqoF9a2bnus27fkmvZ53sWtfZ2sMmdbFNfWxfd9vOoP62nJst7meTO9pknracVw1uV8s421GWtbR/PW9bizrcuh53rMvNbULLOd3/tveJ8d2Sbe/73P1Wd5vZHXB3DxzeX5Z3myedcGczmtf6jje/N77sdV+bzAz/Z4nDRQ7xNiNc2Aqvb8pXsvKMj5zMHIe5x6GNbIOTXOJkpji2BQ5ygj/c52R+eb13/u6eR5reJgf40C1edIxrWeM497fO2/1xbYfc5i1PesknfvIvz1wlNb/6zb8MdbJLHeVE97rRWY50tmt96VznubnrruW2B73se457vucOdr5XWelRj/lwz56StFcZ63avduKZfnGne7vjeW/63pUN9C8LHe5Ul7vVH7/2vo/97283u+Ab/nW1hz3ymK941wc/+h5DXsuId7vibct4lDje9qWvst89D/hMr17lrSf9600ved1TvuqWB3bntfx51Yee9tE/+OmJn/rAX5/1hHe9/+F7nHO8y17vBX/69qlf/Fcfn+bJB/7yD7/+Klff+7MHf+1lfHvh17/H92d834d84ad84ydj5Td5mVd5m3douYd6u4dVvXcSv8d/wUd+/ydjAeh+Awh/BSh/B3hiCeh8Cwh9DSh9sTd1+UeA+3di/ddjD8h9Edg2E2gSFeiCF4iAd6eA56d56Xd5W9eDDPiD6JaBJ7aB9/Z+aBd/Fjh/GDh99td+SdiBS/iBTRiC9TWCEPh8opd9LmeE9YWEC6eEjceEOOiEOgiFACiFY0iFZWiFZ4iFw6WFMsiF2HeCEZeCoLeCHtiC9fWCMhaD7Nd9AsiHVeiHwwWIIriDJCiEJv9IhHkYhCqIfkfHeXpofYb4hojoXzm4iGqogWwoc2Toe2b4h52YhYy4hSXYhXj4hZ94hKG4eKNIgaWYiKc4h2A4XGIoim5IinBoimi4iM2nio7IipD4c5eIf5RId5YoiXu4jIWnfsNYh6t4h8eYda8YhrHIe7Nog7XIicFYX4IYhYTIgZnoi5tIWLdoW8M3iDM4NDVYEjcIjHLIjqlIjcVojZXogLloW7soi71Ii79oi+GIi9moi9sogd0oj9+ojgVpj9Pojnaof16IjclYiNAofs1ofpPog/tIbRdpjhlpgOp3kP6YkDS4kCQxjwRZj1g1jmtYjlN4jgKZjm2jiKj/aJJY9Y/cGJDeOJDg6JJtQ4cSWY0U2Ypip5Ntw5MK6ZMMCZQOKZRD047k+I4ZE48r2ZA3uY5YRZRVOZEsWJF2p5RDw5Qp6ZRZCZVb+ZAv2Y87iZLwqJIjwZJBKY0hOZMjCYIleZdtSJM/aZNDg5PDBZOgKJN9mZdXuJfOiImIGYd2uZjK6JHMyI9kmTFmGZdoOZdaGZhcOZRuuZRweZVyKRJ0GZWPyZHPKJnRCISoyZiqqZGUyZe86JdPCZgZI5gQKZsASZtpaZsNg5td+ZllGZoNg5WaqZacyZZtQ5iwaJiz2Zj0qJitGZlD+JH9FpFfaZRhiZRfxpza6Jy7CZ0t/ymdPNiR1TmZIAmZGPmaJMma5Zma57maRViZDXOZopmZpLmZt9mZU3mPRZmPR3mNY6mbPcmbx+mbAQOcyymclkmcAWOc+Ymc+6mc/UmfAWOfxTmaIVGaaymVGeOVMWmVGYqfG6qfv8mfGeOdCAmeBSqedemejWiej2idJIedIQqWfSiWpmeh9IKhD6qhIMGhyemhDaOiJ8miTWmgEYqg9KKg/WmjhSmiP0qiQWqiCYqiDUOVN6qdOcqduMeg9emg9AKhJSqhJ0qhHwqmFyqm3EKmVWqmV4qmWeqf2Qmg2ymgX8qj3OKjYwqkHyGkE0qkAaOlUYqjh6ij/gelzSmlff9KpX9qpU2KpYOqpj3Kps3ipo8Kp5EqpwFjpG+JpGeppGXKpNzipGmqqN/JqG3qpx4BqGcqqPRCqItqqJqIqDBIqXtqqb2Cqa0KqaUqqbGKq83Cp6vqqL2qqb/KqcGKqiuqqpfKqh3hqnEKq9ziqaAJqpgpqm9Kqs1iqnOqp8Oqq67Cq9Hqq90KrNwCooXKpYfqpf4Hrr1CrM9qrOWKrOeqrNUqrPEqrpBCrhwhrZtKrc2irrPKrrXqrk9IoEnqoqYZm+opkuyplzBKjDJqjDSadcx6pM66q9D6r+baK97aqfrqKvLKsfTqsfYKsug6sCMLKSU7rh27EQCbrALbKwT/m6q0io62moYKG6oM26Eb+Z6uGZ+wmZ7TuZ5E254o+LB4GbGJ6bBHC7FJK7FLG7VNO7VPa7RCS50zip7aB68ky69/4q8y+7GuErLBCrYuK7ZuQrYaMbP3WrOucrPNmrM1ubOe2LPZ+rNDGrQxCp9dK5/Xqbf3qa2Zyq0qi68sq7Z/8rL9GrNva7aQgrb5yrhu4rhjC7kZAbeJK7eQIqs4a7A6i7A6mLGfurEwe7Jlm7Jnu7K9Yq3Dia2Fy7eBSp5/O7SBW7SDy7SH6bSOObH4WLH66LWuSLgjarjHiritq7g2S6dbaqddiqfvarxTirz1qryT67quArsNKrvHS7uv/2q7FAu4Fku8GEu9jWq9KIu9f0K5zcK9Yeq91Qu+0yq+wUu+wyu4NYq+xaq+q8u+buK+zWu5XYK5bau5GMG5y+u5fwK/ayq/6Uu/AXuaW4u0uau0kWi1vYu1vzuf/Duv/hu5rJu9zDu3Ldu4bNslbru5ktu+2vu5zruu0Nuu0nurBCwkBqzCCHwRCkzCDOwmoFu3onu3pCuMH2yyIczCI+zCJQzDN2wjOSwkK5zALRzAL9zAJ3y5KSzFO2wRPczEP9wldKuxdvuXeJuTR5y6SUzFS2zFTYzFT6wiUWwjU8zDVdwlAmzCcdwhc6widezFdywkeQzDpnutqPu4qivCAP+Mx1fsJg5cqRDcvxJMs/b7n8IboBcLe7z7nL4bncBryfiLyebbnVlcwFtMx11cEV/sxmEsJGN8umVcm2dskGmMyGtsx23MyG/syKWMw6fsx6lMEausy61sI0FMxkNsxkWMioUcu4ecuYmsxIssyI3cJY+cq5EMwpMct5Vcp5fMEtyAB3jgDId2DnlgB7YQaZBwB5AQabZwB3gQY3LmDOLMDTCRDr1gMgAAABhgBrkwYSf2DAeyzw8gBp3AWTKWDZdABAMAAANABJcAZTIGDp0gBg+wz+LRX/VVDrlgBhiwzyogB73wzBERDS3yARMSARBGBLUlY9sQBzDAAhiWJDD/AASeQNLSUQ6UECGfJQESoAEsIAOUANA3eQvr8QEVoNIYYGBxcGS21QtEECJJLQFLvV8mhhK6QF0RoAFaoAd60AUhAAE+wk/DJQ1AME0UAAVtsAdqcF7ONQdE3TDfkFvh4wNrwAdr4AMotCbflTHFBSUPcANgoAdtAEQKEwRjM1wPEyYi4AVerQUz1CiPchIbgwEaQAho4wgikCW4hFXa4FYQoAfVZFk84C90MFzlIAZykgVyZSq0kAW5IgZxTS90ICo80Fd+pQemRR5YdTcVIAL7UyvFgAgX0Cn0pDW1ky8HYws34FzXQFiqTQGhQEvJYAxRkCXAhFXeAgHDsi/I/+AHTJNMbcNNEBAF1J0MobAnH9U21+BZNtBV71IxGQAEfe0RlJBGNXUwVrMwWKULEDMIKlMMzR0Es+0q1yADEpAFxjIxWlABMvDcQ2MvGUADU3Uwg+Avkz00A1MB4XIwyEBRnzIS5RArt2MzDhQDvN0wY6ACInDep+II/sILbWMJLRABrb0vK3QJbcMLEEMreiMCHzAGbaMNMSABDGQzsiQDBZ4R/hTc+YQ9TZIxByUBbHA64KMCpz00QaABG+Q1SKABQdA2dKACF1DhE8MGQePUzRIq9+Q1hAQDxw0StzA9N34wMWIEqpDner7nfN7nfv7ngB7ogj7ohF7ohn7oiP+e6Ip+6IDAABAgUV7jAxVgAYte6ZZ+6Zie6Zq+6YkeCQVA5biD5gQQCZxe6qZ+6qie6pduAeaEO4sAAQwACKo+67Re67au6UZAKbgzC0wT5S40PfB0MCBAQ11U7MZOQlQwABBgMD8URMf+7NAuQUgkAUpkM8kTAE4U7dq+7fVDRVBwRR5UBdw+7uTePl90PF4jDLliRiJxC2lU5/uCJTogCapA7/Ze7/h+7/qe7/y+7/7e7wD/7wIf8AQ/8AZf8Ah/8Aqf8Ay/8AIvCX/g6JBuM5JO6Q7f8Bh/8Rqf8Ry/8R7f8SDv8ZIgCZBAAKDuNZpEAJDw8Swf8i7f8jD/8jL/H/MDPwEVcE5e8+oM8Ac0P/M+3/NA//NCT/OSYAQREAG73usj4Qs97jX65AK+HjDbsFVHHuAXsAJz0Db30uU2gwQYEOZDMwdkbuYH40AywCwN4wlpZFYT00Ex0NIhIQ6xkgVeowcRMDJts1ItbjNLAwMyPjQ0TgEttVF7EuIZw+MQ4OMkBeRCPjTZgFB64DVScAFKThKUMD24rd8XoAIMM94wEAGEEOADjtD0AjgSoFAqk04xAOEZIw7ldANkTy0XDgPZreFkDu+ncgq5It4iAQ61EwId/i7CkAMik9i3KQbBsjjenQXYbVszBQEAbuG5YlGeDwFaEPumIgolst5D/yMNsZIDMRTfIrA79e0RiWPZh1QsoEADWRL1Q/PZb+UH8LQKPhABLjAHOE0bgSInXTD4pwIQtbpAWCFG3DqECRUuZNjQ4UOIESVOpFjR4kWMGTOmm9MiApJVyUSKJMYnwgcg2TSuZNnS5UuYMVl6giFhBqiRIpEp0oABhi+ZEnHF+PAgRBc+gcCMgJABhqagUaVOpVq1JbQgKyJciLIn0BoeEHzKKWfV7Fm0aWF+K+JCAgUkbQK1SVJBggsx39Tu5dvX77pycmBcgMBjTaA9WS5EYAEk2l/IkSXD1AQDAwQaYPzw6QICwocYufhCKwJDBYYIEiR8gBGE12TYsWVL3P9WBsYKDKorZHAho1O62cGFxxY3SQZuuxIyrIgx6eBw6NH3pusUo0WG5BhUwDCzTfp38FV5BYHxITtrItD8mtNlZgUAABjG3Cob3v79mL7myIAPocgmvfATcECMpLEkCAIAICAIS6Qh8EEIIfqGEyIegE+GOX6JcEMO1xnnljIwgE+FNHQxRzJr7LCjmQ5b5NCcO+qgxUUaH1QHkjogUadGHvGjpY47TuxxyO+aUdGa2Lx55JFpiHQSunSWNOZJKoNT5RFVqtQSNmOWBG5LMP2aZklvklyyyTDTVCvKR6ZU882zrswSTjqp6vKRL+vUM6YxHykTNiWZ3HPQl9h0k1D/RDWSM1FGMbozz0YjhajPPycLFE1JM23IUE07ZUgSLD0VFaFHR/WUUjMFNVVTTlfV9EpJXNW0VFkjRRXQM2uNtFVdGV20V0ZpBZbQWy3NdVhCeUV2T1DnXHZPYZ+ls1jJLpVWT2WvffNXbeGMttswqY3MWnDVzLbcLWFFV81v16VSXMjIdVfLc+d1sll7t2w33x7h/UtefomsN+AauSV4yH0PbtFfvwBWmMaBH+ZQXYl5TLhiCBnuy2GMN4y4YwINBnnDi0fGT2O+ODZ5wI9Xtg9flyMsOebvUN5LZZrDaznn6CjmWcCZfxbOZrVwFhpKKY/GT2SlpQu6adiITsto/6hl27nqyWDGOrqnt/5LarSo9jqyq8f2i2mzufQy7eDAPktstvkqO+60fKZ7sq7vNstts+DW+6y5/65Ka8H/yrtwqfi2ym/Epwq88aDQhvyswyeHSfGqGLc8psc3d8luz82qPPSVMKdKc9JZ6jz1jCRnXabRX7fI9KlQl/2i1W+niHDdYV+796Bol8p24CXKvfiHQEe+pdiXb0j4qIh3ftOkp/88VOuZ/z17jaAPSnruETo+fN7Dt6j58L2XCfzwx+fedfMjQp979WNin3v3s1c+/onmz75+mNwve/mzXvn4JxH/WQ+ALxGg9Qg4PfgdsCEJnN4CXdLA6T3QefuT4P9DKOg8C7YEg87T4PIi2EGFfHB5IWTJCJdXQuQZEIUT3N4MH8LClbgQeTAsHgdtmMIa/pAhONSIDovHQ+Cd0IYqRB4RM2JE4CGxdzIUIqmCWMWEOBEjUOydFHWnxBkysXhavAgXdefF2/mwimIEHhktYsbboVF2VFzjFbG4DjdWBI6yk+PrwIhCNvYujxTZ4+v6yDo1CjGQuhvkRArJukOm7o8dXOTtGimRR6YukqSjoyLtiMVLRiSTpNtk6BL5w0rKLpQQGWXoSum5SUowla9b5UNa6blXbq6TqPxkFWvpkFtuLpeWi+UBZ8m6XzYkmJYb5uROucReCjGZDFnm5Jr/CbldQhNPdxwimVKFKW6Kr3rhTEgx+XfM1E1zIdWE3DUb98wwRvOH6lQIOxvnTsSZM37oJB09E2JPxOGzcNmM5zbJiRB/IgSghROo4OAJSHnaMKHrWKjgGvo3fZqPn6GbaEX/dlG9ERSiBj1oR491UJDeLaPh26jnTKoqlI7zoA+lZERn+FJwhjOldBNpTUlKTpweVJxtEipCVsq9lm4uqELdadxoKkubonCpMSVqUY+avaRabqrkbCrbegrVn4ZzqzqVKTmfasyodnCs3Oxq2q5qvaxObq13bKvZvorWsHJzrlis69jeOr24Qm6vVeyr1856zrRKcLBCLOzW7orY/7zecbE/bCzW/uq8wDZusjasbNUOu8/EHnCzM+ws1C67vMwibrQoLG3THgvayILSm7iCKVfLGs7PajS0/FttB1urtNMiL7WF660Ef3u01+o2tr6crbFqS9aqCjW4xRuu4Ip7wOMKLbcs3W38rsu/7P4sudxdrjSbW62T2ja6M8WeUKv7t+/GL7w82y5Su2u++JpvvjmbLvDeq7f8tu+23Byvfcs7z/OOK73QPRR7Y1XU/94twPgb8B3727sI023CA6wwFguM1fumL8HxWjBbO1zFC+suw3HbsANPLMT6gvjAEh3xv0pM1xf/8MNwDTH9atywG/M1xzZM8e1WzLYWZ/9wyDOMMY9nfNMfbyzIhF0yCossuyOnLckkrHIHdwzYHv8vyimbMmO7LMEmg/nJUh3zzcpM2TMf8Mqvy7LZtvzCOPPvy5gNswLbXLQ3czbP8Zsz6+o8tjvvcNDmSzOf16zWP08t0KRdNPnae9BDey3RR6z0+y5NzkxvbdNR7LT+HvFg9/a5gpEO26RZW2rrFTp1ocbaqLsI6+ntGbWqBiGr3+Zq3+J6g6cu6jpoXTVbn1HYJvx0OI8NtWTHcdkxbDY3n920aPNx2j2s9h2vrbRsG3LbSSQ2hHm9Ql/3DdjGHfcUu43Fbx8t3JBs9xffXcdHKzbdi1s3duudxnKnOt//ot135voN3n/LTtaki7fQ5q3JhL9O18I9dxMLfrqDyzfiiAw4pis+xovXLuP63bgk7+3JgfM25MMbuYDXS86JU/fjbVx59FpO4Zfj9uS8TLl3a/69m3M459xs9K57jt+fry/oLh76HWPu35kLMun2W7qSm47FhYeu4T97OClLTrqiU/zoIvbTN4u6X5pl3XNb51nXXfn10D0dw1Fn5NQDWHUuXx3FHQc13S1pdwbiHc96h/HOtQkpsQL+goJXNOF1bPiCIl6vihch4znteCJDfqSSlyzlW2h5UmOeyXx3tt9V6fkcgv7Wokeh3FVselqivoiqVzbrO6j2zbE9Z27H/yXcYUl6a8MembJ/Iu2lbXs0a96nnJdt2WmbUxMj/4CuN7Lw00n8LRpf29LnX9hlPnYfO9+50Mcx9wmtfLAyn7niR+9zo99gmKMfr+o3L/sV7P7yw1/nzvI4+MVsfxLDPyEzP0YDPm+zvn7CvjLSPnEjQEvjv77zPz8DQBsTQCpzQE+DwNKTwFWjQCCzQDPDQFNDtf6jPwTzQCkDQTgTwViTP8gyQRpDQTJTQUFjwVxzQdiCQSiTQTejQUqzwWEjwQjUQTbjQUDzwVcDQmbTwODjwF4zQklDwmBTQmpjwgN0QnSDwlaTQnajQm6zQnhDQI5SwDdiQHrzQnITwg0kQv9I08Jf40J/Q0N3A0N8Y0N9c0N1g0OEk0N7o0OUs0OCw0N+00ON40OAU8MmBESVE0SDI0SSM0SFw0HlUkSfY0SMc0SX0z8Ck0TyokSks0SRw0Sc00QLM8AwxEKLA0WWE0WhI0Ws40QD80Syq5T2I78BdMUqoj4sE0OXIkM9MkOIg0Q/gkUZk8Xwo8X7s8ULxMXCQ8QrNMb/Q8YAVMYQZMbH80Oeg8YJlMYKpMYVtMbMw8bDKyreEybf2xzvgzpUBDlVtDlWZDpwHD1xjDxy9EVCAkavE0bW0UU640WlskdHwse300eTc8ZT1MYO5MYP9MYajEcrI0YnQ8gnVMgUZMj/H3RIL4NINZPILKTIGbTIJMTI5JvHzavHdgS6d7Q6kZQzU6xDk/TIHgTJKVxJPdNIR+PIVITJI5TJLqTJ8yPJ5XtJs2OqcySmlvxDoXy+sytKZ7JJo8NJdtTJKOTJOPRJ8+FHQ/NHrQJITBLI3iNIsDvKbEzK8VtKsDQlpxQ7qKS5k1S6lMw7q3zAYtM9milHZmJKyME9y6HLmLFLa8LLdxLLcRQqv2wnwEQcrJw1rZQrrhQlrzTHs/w9oEw/sqxFs4xLTzNIlyTMxmSlx7zLyETHtPy+tZS6tqS6txw8zMyexGS4xRSszrSlz/zL0DRKzURKzjzNu0vNxlvNFpzM//mrzGS8zGJrTa17Tc2KTWCaTcOszaYEzhcUzmkkTqsSTHrMTancQqrcQ9+8QejMQensRuqUrtFUx9KsO90MPN68vO4MwrlETtVSTmVizns6zMLRy8nhS5cpzPp0Tmwqz7lbR7bMzjfczkJsT2a7zbHEzqGkKgRFHvyEHP1cGf4MKPsUHONcO/gkLvmkJvq0UP8MzO+cxPBcyPF0sPcUUNMk0Dw00Ed80OLJ0NzbUOvq0HX6UIa6UIwC0NdTUfRk0UF00UwstnQM0PP8u/RcvPUMPRgltxHtxBKtyBONvyeNxSj9yCnVOQUdzJKy0XrCUYvSUb2J0MaZUJPxJ23wBP8sQAAEGAJOcBBuAgdckIMEMIAZsIRnONLQKYdeoAMLMAALoINeqA++egZLmIEBWIA4wAVwCCdp4IQhYFMs8ARt+AtwmIQYcIEMUA0MaIEYiINKFSJz4AQZMA1OXQEYEAP1qCJdII8VqIAIqABUDQJdwCJoEIPbyI3VgAEg4AQh+SFtiAPr0NUPcAEYmIRG3QtpCIIWkAAImAEkSAIagAAJWAEg0BAbAocycAEMeAAQ8AEnuIEIgAAViAFP+KFyoAMYyAAIqAAecAIeqACxgAE6IFQUookPgAAIuAEnQAINeACfGINknaFfAIJmxYwkQAIRoNYWCAI4RQttAAIVgAD/L5CFnKiFNtgNGXiGGRIHMWgBCEgCUkCGkRiGQQCBCoCBc2WtOYCBCqgBRiBZkSiGRqgBCWiBObAhmqgADSCEYRgJZCiFJHiAFjCIGXoGGcCONqCFnJAFMCBXIAhVsyiHIlCBCnCEnMiJU9CADACCgT0gOQBZP8jakaCFG5AAGFhVCfIEF4gAKSgGsk0GYsgCCFBZFIKGmriBWojbZPADCHCBnO0gcACCDNCAU8haZCBZR4gAFSgCe6UKmoCAROBbkSAFCGgBSuigZ6gJMKDcZKgFEFABMdBTvQEHGcAAH4BbvjUGH8AAGfha/RKDDwABW/BcMEBbjpWgSQBZUvBc/0RwALu1inQAAgzgAZmlXC2ogBiA3fCJgxXQAGHw3GQYhAiAAWzln04A2cP13FP4206QoF+AAQgYBOkVBg1QgTiQINPFAC6Q3mTYAQwIgnOwCryFAERwX1GoW9HgH3GQAQno3PKNAMyVoCL4gBtw32S4gQ8oAgmihBWQgJ+VXi+oABl4jvjJBfEVBfdFBAiQAbWdClyAgQeQhePlW2QQCy1IXBVeYRZuYRd+YRiOYRmeYRquYRu+YRzOYR3GYVDQV0UoYb7NAQyggR0uYiM+YiROYiVe4hwOhnZVAwRWAwl4gGBgYiu+YizOYi024mSYgeJFYEV4AAkAhS0uYzM+Y/80VmItuAwgjltZ+FtcsApNAFlgQGANgAAOWBI93mM+7mM//mNADmRBHmRCLmRDPmRETmRFRuQqCAAIIGP3dYIKCIBFrmRLvmRMzmRN3uREtgMAqAA+QGA+kAAAsANOPmVUTmVVXuVLDgAJgAIE7uEAmAJWrmVbvmVc1mQOgAANQGBguFyoqIpOcAEI2FvpRQYKgIASyGVmbmZnfuZH2AJHbgQERoIKSABozmZt3mZMxgMAkAA9QGA9IGU84GZzPmd0/uMEkAAkQOBGgIAA2IJ0nmd63mYSaFcEroXLXVmq4AXxDQX3pYXL3QR0OIeCPmiDTmiEXmiFbmiGfmiHjmj/iJ5oia5oir5oi85ojN5oje5ojqboanDZUHZfEPiANPhoj05plF5plW5pln5pl45pmC5oczjdKEDgKHBdc0iHmZZpn+5poP5poQ5qok7odEiD2UVgv4UBbChqpx5qqH5qqY5qn55jCGBa6Q2Fun2NqjDdCoBi6R2EDn4M8CKCDDBe6e1eGLgFCaKDFbgAYpBeYpBVOpCgEIaA7fVcHsgAIpCgaJCBCCBf6VUDCmbeqHDeCjBmviUGEVhg0r2bYYYAgPZcJ3DdAOGfX4iBCBhpyjUJ65Wgb4iBC3CCNs4JUADe78WuAhaBuKbcWpDV9DWLa4gBCfCB1o5bLZCAGAAK/wkShyDIABBQbLINhL8NZgkqAxagAA3mW1KIgBUwAxTSBGIOBMqlBRDoWgvmH1+oiSygXGLwAd2+BrTghLxtBbKtBSe43EkgWNEGgcnOCWJYAwhggTF43PjZBiD4AAogBCBGBkKgAJTwjg4qhzFogQdgg9seCVAAAQyIgett67aFAqzOiVbIgepN7bNQB0qwDAiAAkQAhVBQhORNWTP41Q7CBRnIVx8IBBBnhDUAAQEugsvuIGgAghV4Vj1wBFFwBD2gAecGgg8G7SJoVg1YA0YQhU8IBCR4ANCI4xkyhzhwiwrgAkUABVAghCiAgAs41h1RC08YVgh4gDDHgBWQAf9LmN8f+oUg4FZn1dcKYA05yG4UygYxcAHz0Nd2LVYxUIkfEgdh/YDLiAAxxgAXCALe5ixLiAHcwHOxaAEZ4Oe92AZLsPEAIIAMkAE64PMqEodOIAIYqPQIiAEzyF3CygUxkAEGMAAGiAExyIXHnpxfMAPNJoABaI1OkHMbugY6SNoBGAAVAAJLEPC/MIddsIIqeAX7JqxqsIIpYARcx6Jt+AMq+ANhDydxYAQqsIJq6PJwKodXsAIr2AUTn06ifARiKE4erT4fRVIgbUQhHUUiTfddXPfTS9LKW9LVa9LeIVPEMdORqdAcDdF8kvd+pPfYs/fPw/fa03d729Lr7FL/hE89hT8+hr8dGd1LGoUvL/0nMP0oMVUpgs9Kgx++iJ+9id++io9Ehy9JBlXKck/5YazSYrzSmMzSTZT5iKT5nbT5Ulz5oGz5snz5eMf5jdT5qeR5Dwt5xRz56yv54jv5BoR5jiP6mzR67UT6vfN5ygR6yxT6orr4/Mx4ANt4hep4vUG7mOH3wvF3kAH4MBX4+7ROlof4dr/Ed2/FoU/RV09Ap88+qD9DqU8dsJdQsZcwsqcos78btHeZIu3RvR/Dvl/Avw/GwA9Lqn9Kqy9QrBeiwS/Twteww/eos/94ulF7wWH7jnF7j4d7h5L7n6f7BlWvyo87pXdNpuf7ug/F/7uHx7w3t9uH/Nxfxd1XyXjX+uDk+uH0evK8fLXM/Bbd/GvUe+cPUujPPOOPTuQndwftfYF7/F6M/DKc/Hycfc/p/H7/fBYL/cSnm8VfGdP/G9THGNUffdbf0esHz+wXT+U/KPNfe/QHiHUCBxIsaPAgwoQKFzJs6PAhxIgQpz165E0iRofeKk7L6PEjyJAiR5IsaTBdRWMmV7Js6fLlS1WPVMGsafMmzpvGKqbL6fMn0KAMKVoUanDjo45GlzJtyhLlI5VOp1KtClGmJKtat3Jdt/NRz65ixwYletEpUqVk17J9CVVq27hyR8qkOfcuXolfw+bt6/eg2alp/xIu/P+2MGK/kmYmbnx3r+PIbAOj5Sj5stjDmDdrxcr5M1XIoEcbpdx0MOnUPzWrbn2zruvYNUXLrm3SNFPUtneLZM37t8fFdoET18uzOPKHuJfqTu4coe/n0gnCnm59IO3r0pcbba7defTvyT2Ll569fHHuQr2jBx6+/W/h8JOfn79bfVD29mu/3y+7un+81Rega/gBpR+BqvWXYGrkMSjbgA+OZuBPCEr42YIXcgaghqlF2CFmFPpkIYiSZVhiZPKhONqHKzYmYk4kuojYiTMW5qCNl7WY418w4iQjj33VGGReHBKZ2I5H3uXjTUAqKdeQT8alopSFJVnlZBWddZplWP7/FaWXYxkZ5mPHkZkXkzY5eSZXYLLZ2SNZvVkmWHPOlWZNa9pJlZt7OkWln2tdGahTeMKkJ6FL9ZmoUGMyqtWgjwpl6EuISrpaSpd2haOmVUXaaU6UumQpqDYtWmpNjqJq1KerwiRqS6S62tKps7IEqK1CtZrrSrCyJCuvJNUaLF1xEqurmcf65OtKwCr70bDPeqSqtC7tWq1HzJrkLLYRRdstRLiC29K1406kpWBdmktrpuu6RK27IZUb70LalsQtvdC1m29JnPIrb7L/hmQvSfgKPNC3Bw8krsIYzduwQASPZLDCCTcML8QNPQyxxCJRfLDFCvubMUQbN9xxSB8L/xzywRiTrJDJCqMMksr/siwwwy9rHLDODs38Uc383vzvyD0vFPPBP3sUdL5D8+uy0QUhLbDSGTFNr9P55hw1QlP/WzVGV8ebNb1Qcy2Q1/yCLZHY7pIdb9FnG5R2vmtH1Pa6b7u7tdwE0U2v3RDhba7e65p99t/xBv7Q4OMWbm7cfWPHs+QFLa6RupWftK/mBh3OdeLuXt5Q4+A+Pi7flYe+7ugMld7t6eBGrjrlna/T+kKvYxt7t59Hvbq5uCuke7W8Y5u65MCPK3xCxEtrfLW+G608uMwj5Pyz0Es7e/K1d279Qdgrq/2zyPdNfbfgH5W57QKRr6z0PaOPrfoFif9/7PvHcn++95rXT9D9iJU/YsVPZ/Or1v8GEsBgDTBY5pPbAaWVQIEskFcN5NX+INi/yk1wHRXM1QVzVcCXRfBZHfygrUJoqwciboOSOyH72qfCWY2QZCVUFgyT0r6CzNBVGWxhnXY4kByqRYg9XBULQefCvhFRiAjjnBBrmLEbHquJTlzHEVH1QyUG0YlWdGIWSyVFiFGRWF80IhR3mMTfLVFuZ9xhGEG1RTZ2UYhvlGEa2zfGhpUxWHe0XRw7tcbptfFsf+xcIDW1R4X1kVeH1FwiLzVHQtZxh4+sXCQlNUj5FZJrl5RcJh+1yIM1Mlef7FsoGTVJTlayfaeUWyr/EzVKgZXSVq88WywJtUkDdjJqt+RaLgO1Sl620na/jFow/TTLf9VyVsc0WjL3tEsS9tJoz+xZNO20TH4101XX1Fk25zRMahbze+iqjA6vGM43TdOG1ezZN1+2TjZtM1/dXFU8STbPM43TneX03zm5lE4w5tF29aTXPVGVz4ztk0ztnOI7dbZQiDU0TP2E6D85GNDcxBCQBe3cQeOV0FJNtGEV9dJDyRjRl5W0Yh/VXEjdNVJQtRRkL63cRVWa0RdulDkdReRNJZdSPq6UZDVdWVD7FtN1zbRTR7VZUuWWU6LulIk97c5PIRnVsy3VXE3V1FOFtlWuDZWRRc1YWJs2/9aoTdWsVXXjVdeTVUyu1WhdHddXL5VWrNW1Z2Ul5Vk5Ftf8zBWUfdXZXcGVV0ntdWyHfVlbAftWQw72QIVF5WNJ9ldaBvZkla3QZWGZ2YwltluLfVRj3TZaiEWWs5P15GdHFFpcrvZijLmiVzors9jGaLbArK3CNstM3SaNtz/yLTKB2zJj4fa0jEpt3pQrsNJiy7mJgi7hpPsv4XKTuFQzbpOQC03tPu22V7QuobDrOPLmq7XDfa0vwasm8WKTvfTirj29+zX55om+4LQv3MzrRPQGSr2mA7C73Ntd+FqTv4fyrzwRbDgBC5HAfjIw7CRsLvwiVL9qc3ClIKxPDf+PS8H5ZTA8QTwqETOUxLKj8A4tvCcM787F3eKwSD1cNxXHisUUtTG2qFstGduJxsUDcvSYe14dA47Hv/KxSZEsLRzLlMmKc3KzoOzSqOB2HUKWFpHnZOTnSflZJu4wiiWK5W1p2aZcxu2XnxXmN405e2VWFpWZamXRrflebUbqm6945hynmaV9LtifoRpoJ8ZZWXNmU53Hd+dj5dmre2bdoSeWaLEuOoowbt+jzxRp/E2agEoe8KWDl2mPbVqtnVbjp20XajKNWoClDlajjzXrMNWagbfG4KkrnOrlrTplrebrq/UY687t2ku9tuCvc1VpvA67esWm2bEdm2yDBjv/xtVO37WBlm3Vbhuky9Zcs7H0bBBGe4Xnpl2hjRrupY07uuWG6bu7F2+0zttq9c7uvXHabVB/m379Dtu/1xtwoeabf/sWbFHQWUQ4tpuGDdfgwz0bcYFOHI8LV+rAZV1wBB6cbQk/8MelenEg8sWOJb/byTOc8rNNW7Ejl+DLBRfzGs+ca4OucsZ3u3GODhSNPWfryrnYckvmnHE7P/LRjVZz097chE3HXNEpHvWe5ZpY6a7SulNYcR+GnNlVx+HVSfd0Mm9dZ1Ov7tmrmHbXrd3ObYds0um4dFfOPXd1l/TdSfZzPQe9uEP3adY9DhdG552Sezdm34f3d1IHPmNv/x9y3M0Y+eZN3taVZ23Z0Z15P27+ep339edtOxxUF/67h8dq4j2a+uA2npWPN+fr5Rp7oM5+uasXduv3m3vC7l6rvZ9u6OF9e4AO37LFp+vxt1t7Yi5fo80H7fMNG/3y/t7bwf/w9WWbfcxuv73J13f1eRr+3o5ftOUv2/TJmX6rrv+47aft++N1eTCP3pGlD9/pQVv+Jdj5Odz8wVX9hdf9/dYATlj3Edz37VgCztcCJlcDblj8+dMBUtYE9lcFjtcFllgGYtQGwlYHPtgH1lcIvpicLFkENtkJhlgK/tcK3tgI6lQJxlcMsoQ5QEMhkAAJwIEvlAMcSUMnlEAHaP+BLoiDEGkDLhwBBxwBLmiDEImDLmgBB5RAJ0hDDpJMOfgCHJBACRTCM3RhSZxDLgRBDHwABEBABsAAEHQCEWrOL4iBDLRAG2IADMQAJYBD51xDHMQADFAABFCAC8RAHFxD54ADJcAADGAABERAC8iAGPxC55RDJwABDLAhBKgADARBLpzDT4hDGcBABkTAA1xABeQhDIjBNkiOOTSiCrQhBVxAG0pACwABNFTOLciACkhAG14AIUrACsQALlTOMwBBC0jAA0SAKkKABHwADFCCOUjONhTBIz4ABFTAKj6ANJoBE+KEOBRBC0RADSiCLSRDMgxDIyABBKwAELwiLsn/AQxIQAgEgiyoIzKEghZAwAfIgCXKDSc8YgW0wSkggzqeQhtQgB5yQt/8whpCABeIQjGooywEAghIAAzIgTrIzTYEwSwiQSMMQzIggy0owg1AQAsUQTjWRDqkAR7ugTGoI02WJCK8oxjMYdRoAgw8QBQQQ03SJCloQAYAARVyTS/EgATYwCwEpTrOgg1oZC+cjTYAQQZogCg4ZTIQQxRAAAxowtmUQxHMIiIgpFO2gSSaQUfWBC/EQAS0gVbSJCF4ZSdwjTYoJRKYpVaeAjHGAdeUQxB8gAgAQ1wmAzCIwAcEgU72TBysQAScQmEiAxJUAAwcpdF0Qk8iQknGJVrG/wAv2AQRCKZeaiUy/AAGyMBivswkOGZTFmYytIFGSkPU4AIMQIAjuGYyOEIEwMAxGo00yIAE6AFuykIErMAkRE05yAAG5KVrIgNiFkFNXEM9BgJu5qZX+oLRlAMQYIAUVKctqCRYGk0ZiGZ1ImYZ7CQe1kJ1SgEGAEFqZkwv1KYjjKZTIkMgSIAMKOJL5EJPrkJ1EoMbvgE1DCiBFqiBHiiCJqiCLiiDNqiDPiiERqiETiiFRmgsYEAEEEJ1JsMNYIAQVCiIhqiIjiiJlqiJTqgzYMAFgAF9auUXYAAGOMOJziiN1qiN3qiICgEG1MCG3uQHxAKOBqmQDimRlugbfP/AAwAlbq6CV/amS3ACHgrDhmoABHBARVwplmaplm4pl3apl34pmIapmI4pmZapmZ5pmVpBADwAKGyoE0jAAaCpnM4pndapnd4pnprpHQCABOzBhvKBBACAHeQpoRaqoR4qotLpAUiAE2woKDxAAFhBok4qpVaqpd5pB0DABWwoMLyjQ74ElEIAYVanLZLApZ4qqqaqqj6CmkJAm1bnZCLAqs4qrdZqne5pcG7oHgQqHtiqr/4qsHIpAjDqhn4CBATAFQSrsi5rrWaqBnCqStblftYmZOJmp6qAIHSDtm4rt3art34ruIaruI4ruZaruZ4ruqaruq7ruXrDLqhABAz/wobOQAY8AbveK77mq77uK7/2q7pawwdcQBdsaBdgwAdYg78mrMIuLMM2bL4+QQbMwIYOQifugsNeLMZmrMbyqyDM4qi65ik4AAzkAkxkA3DyQXUqglcGpM6YQxBgQKPi5ixEa9TEwQeAwIaCwAf45WXiIS1UpxO0ZzX2DERCwCJUJx9QgAxYpkuIwc1WZGTmAAYoZtRYAh76p2uCAX5mQ9ToQm0qAm4mwgPAgC5ETTYopRosqUpaQtSYg1XmQIvWJDHorBjYxC/U48AWJh/sppP2zDYo5w1ArVaGgkrSAdeYQxF8gAa0plbOggZ8QBGIYtTQwQq4amEWg9TKwDdw/w1tQgDKxiUydAFlsixMzEFtdoGS1iQy6IFKlsHQRs0t1KMPpKNTKkIFJObmcg00xAAGiEC1BuUpiMBp7iLXfENgVsDROmUt+IBGesLZmEMZVC4fCC5NEkMXQIALzAFOlEMZuIAEgIAfnIIwDMMqDAINqCQR+OHZqEMjSkAFrIEo2AIxyIIi+IA/AoFsyg1/QmIWOEItEEMtOEIWQAAGxADJyk00AMEHRAASKIIsEIMtiMIacOM09g04EIELRMAMDMIqDAMwnEIfgEAEuEAZvOdLlAM9fgAwtiE0viE4So46dEIMrMAqsjABuwARcK3k9IIyYoADRIADBGMuYqfkZP8DETwiKrJwBayADHSCGfILKcKABlDAD/9wNMIAHZhwTfiCGMxwAzRABsgAEejCEwuMNAQiDDSAA1wAHMrhIk6CDMQABARxDMjAJORu5YxDJsZABTiAyCJi/mKSLhCBDHyAH6tADFTiUmQDJqDACRgCFwrRN+SCI7PBM7yu7YhDLzTBCTRBL7Sk7ZjDM7SBCaRALuCx7aiDNBjCCaAAJugw0XWc7C2epz2gyL3gle1gj81ghNVgkN0gVZWxvOnyk/HyiPlyktmy2eEynxFzlhlziyHzlAGzWwkzvzkzm0Hzj0mzmRUgxlkzxG1JLOPWSWFJ1wXL10lJ2M1KOVfJ/sn/Wf+Z0v+tjzZHGTfDDzVLFjhrnDgjnizzHi3v0OBZGjNjGjb7WT1vWUC3zzs7Wjzb0jzbTwCy2z3rTz671j4LXT/D3j8b30JzWwuyXkYb3kbrXkdD30ebmzKLXkGr2kEjWkK7WUprTkPr2kM7U0QD0ESLXUWbWkgD30i7XkkT30lr30wL3EorH26ts6u0s5TUtNfdtDfltALtNDuP3aqcM6+k85Mw9ao49ZMMNLW1NLG9tKbFNKAdNcMlNfotNVVTkFU3NVZr0UW/V1AL31A7X1GTn1qD3E97312DX15j3167X1+rHFsboFubNauhtaIdNs3V9YIFtgQOtvgVNv5B/7bPeTPLLbZlsx9mM6BmI11if7Nnp4tjc9poS51knxhlw+Bn219oW+Bqc11ro9lr53JsK+Bsg2BtIxZnK91pSxw5z3WpQDU6SzU+vbUHxfVXG7cc3Tah5XYz7zYF9rYK/jbe/TUEUrdBW7cHYjcNarfgSTfQebdLgzcKincvk7flmTfhoXdZq7cMsvcxuzfocfcty7e1Mbaxpbar4bfqdRlXK4lXowpYKwlyb7VyKxRzo9BV9zSuwTdB8ze4+Te2ATiyCbjIBLfeDTfHFbeE88qC50qBH8mBl0qCH4lWm3iDk9SDOzeCQ3eniLXNkXV/0/eKabi2cbjvEfiL01SM8/84ufk4zlD4WFu4wWG4uBG5vRk50Xi444H4OKsTjSsSkt+4kpMck9ObkwMclPNLidvKiRNJioPKihNJi5N5kDvVkNt3NIe5+en3Mm85znW5v325wsn5fWU51eH4hev4LsP5NvN5gJV2Z1/RmXdKmgeJjf+5nVsdniOcnqOcoRMgogu3or+5iF/6uoz5rJR5kCy6pjQ6jzw63AH6kgt6MRO6PXs65Ph5qkc62k26yVW6zME66sg65qk6l7P6M7u6QnfZmod6m4MVp1v5iIuQlNselftzp3cZqLuKqPMIqV+KqedIsVP7setVshPUstsKqvc6rcudrcMcrvOcrr9Ypn//+Kafu86lO9Stuw22+5S/O7Bns7DLNLE3O/U9O0dHO5zxOv/5+p3nO0Lve1pLO8HDs8FLOsLDtMI/dr/bu7PjO2pPvGr3O52zdLlrHrw7nbyzHb0fT8M79MPXesSftcYHeMUDecqb+8o3dstvOMfD/MeTXshjXc33+Ms3V7cz1rcbXclXy7SvSrXnyLVLSrbbyLgXfM77386r3cjbXdFvz8nbdMyD/Mz/d88XOcNb/L9jPHEr+9V3s9jLH8CbtMALmr+rPdmHuNmHPc6vPVG3PeOlvQbavV7jvad1vFLHfZWD+9njs96TIN8Ttt/D2uHjYOJf9uIrG+C3teBD+9wP/3zjB/Pjg3bk287Ro0rS28jSP0rTz8i2I33Qo9bQa13hW/TkK3blB/zlX9Hnl0roz8joM0rpu8jpg37qP9fqK97NA/3W63zXZ/jXP/nPu2DUy/PU013VA17rE0vtg8rtu0juJ8rur8jTO3zzQ/Tz+130U970T3jmV/Pmy3bnd071d8r1r0j2E8r2o0jv2/7vX1fwz/LwM3/68/b6A8Q6gQMJFjR4EGFChQsZNnT4EGJEiRMpEpT0SFVFjRs5dvT4EeRHY48epQt5EmVKlStVTiPpjSVEbySnxbR5E2fOlOlIGtP5E2hQoQhVYRx6FGlSlSNLKnX6FCpEl49gKp35qP9mVK1bt/J85JNrWLFIi0oaexZtTqYm07Z1G3Jq1aRXs761e3eiV7B4+fZdWDSjX8GDB64lfLhvXKd0ETe2q9dx5LYXA0u2HNbwZc1RFVuluRm0U8ihSR8tWxp10MypWdvsPPdza9krR8+2fRLwbd0gV+/2TfE1Usa/iUusXRx5Q8rJmTPs3Rz6wOBHh0e3vu74dei5tVt/3h359KHVwSfPXr74afTMv6/fLV4oefe+z8/Xvdw+8fb5ZcMPKp+/2eoLsDXuCLxtvwNL8w8oABVEbcAHSVNPwtYSrFAzBn9yEMPNIuzwMgNBJO3CER3TUCcOTYzswxUbw8/FzUqMcTD/FHNSkUbCWsxRMAp5jGzGH/GyESccheRrxyPvElFJwoJssi0ibzISSreSrDItGLH068ktxZLSJiq9HOvKMcNi0sy3ukyTs5cWi43Nt8qMEyof6UxrzTuTAjMmMfUUrac/JzNKULTyLDQoPlnyE9Gh5mw0KDQhherQSXFSdCVGLdXp0U1xstNTpSoNdSVMVdKU1Jg6TXUlSVlVjSS2Xj3K1JRQnRWlVXENSctdgRrV145qRenWYD3S1ViOQE3WJmCZBc5Nz7B6NidkqZ3I1WtRclbbh4Y9qdhuI7JWXId6LfckbtFV6NuQwl2XIXLhTSjbeTVS196C2gXp3XwPktdf/4KWDZgifAne96N+CR4I4IXPXXgigwNG2COFIW6Y4HohdkhifynuyOKFMQ544I0f6jjfjzkKmeCR/dXY5IVQtlfljVgO2OV8H46Z41h5nqhmjW72N2d7S/5ZoZnnDbqiofMtel6YkTZIaXiZpshpe6GGd+epE6p63asnynrerdeV2uvCfE67IbElIhtes9E9mm2CwEbX7YjgXlfucruu2+61AU8ob5ngHPzfQBGnl9DFD7q73MIf2hvdvsWle3DIxZXcIcrLtbxbtNnWvFvOG/JcXNC1/Rtx0rU1nSHUu1X9WswBd/1a2BeSXVvaqRU9bdyp1V0h3q/1/VnWMxfccf+CiE/IeGqRZxZ4r4V/9nmEon92+mRtr/t6ZrM/aHtmuzdW+duZb16g8Q0qP9nzg61+6vCTdb8g+I2V39fvR1+fffgjiP6Cxb9d0Q9p9jOWAAdCQF8ZEFfpAx8Am8dAgThwVxCclf+CR0HHWXAdGMSVBl+FwJ8pMFggFOGsSMgqCf6vKexzXrRgMy0ZMkxxNxSICXmGQl+p8HAybGGqOGg9Dy4OiDbU4RBJ9cIOxlCHSazLDZkYKh7GzIe7kqIOBVJFTxWxfkdE3Ba56MVNXdFkWcQVGZeYQx060YhQvCEbqejGG4IxgWIcHB2FaEcZonFjapwVH9lnRkvBMYxylCH/IZtnyEkBEmKCfBUjHedISOHxhHoEHCUXZ8lGITKPigwgDYUTxEL6kX2QXJgkWcVJxHkSUZjsoSbr5srBwbJQqiQYK1NlS8DhUlCgzKQoK0hK6piykahsniyxSEu2+bJuwPyTLgPGS1JBk23S1JMwZ0nMDxpzPMispDIdR01/WTNU2EybNu/EzDQ6M23q9Bo76cTNZnoTieCMjzg7Sc7FmTNf6PSUPKdGzzi5M5Dw9BpBkWZQNgHUXgLdFEN/5tA02fOd+ByjPv/Dz1f6E3EIjaRCp0ZRnlnUTBCdl0QtZdKYoXRMGE2oRvfI0QZ59JYgHZxK4cXSSbnUZDD1kkhX/0lSpAF1Y0LdkkxHStNN2nRDOP2lTgHH03X5FFJIvRhV60bUXRr1Z1oVGVfZZlV0YbVRYm0ZWdPG1KI6tZZQTZFUo8lWr3m1mmDlmVpxZtepmbVcaEUUX4nmV6S59atwfaZcb0TXbBr2Z4AVl2ALRdinQZZneD2nXmNmWa1hNmaIzati48nYIjl2naA1mWS7RVlBebZsqt2YZgPKWZPBNm6yhRhrteXaP+GWb7p1WON06Fs9Abdyws3YI8zCxXUY907I/ZxySUbcG0KXThYUhyuWoIRMfEOH5fgFE5QQiGwsMRphUEIYoiGr5qkjG4FQAhN+UQ4dbiMTSliCK8RxFP9pxAEGKigAAzIAgzL8onnfmIQMYFCAAkhABkXIhXsBJw5OBEEGDWBAA2AQhE70t5O5KEIMJMAABsBABpTYRvOeUYYYZMDEKohBHKQBlHRYQgYrkAAEeAwBCagABnOw7+ByIYMWYKDHPv4ADMQA3sFFIwguQHKSMdDhaCBuG2OAwQck8IAH8BgDLZBBLhBXDjlsecc9rsAKZGAJCrMkHQCugATU8IlVtAIUbdCABFwwBhCzjRMwQHIUFHEKWYjCDzSAgAqCoA3A+UIGH4CADwhRClmcYhBIeMAHZOALwGkjCC2AAA38IApZoGIRUYBAlTlR4TG4QAIaaAMoZLEKR4D/Yc4wkMObVWIJGEAgCbZARjKITWxieCECuuZ1zHQBAwnQgBXFLjYyArFoIvx5ateQQQY0AIphSxsZjtAABmRwDbaJowiSDsS3pb0KGkgABrpgmzrk0IIHfGEY0ia2LZAAARhY4ibQcLYT2K3vZKjB3/L2mjiAgIEZBMPgxEaGIiDQAoDPcwwquMAqklHwYq9izWNY9sYsIWpFRJzYwaABBoCA7Z81GwJrQHnHoQBvaNikDB/QADBm3nEaZCAII1+YJkR9ip4nQwsVgMGKp9aLXw/i6ISIQAx64bVtxKACWjh6KR7QAk3MMwgfoIExeg4MDaigDDHZhgwk0IajIwMR/xCQwc0bGgQMIOHoyViFA2DgCa/JQeMeNzgyLqCCOXjNE7+O9tGRAHShB0zgEUBE3tsggRgwXSUwL0Xea7HoSpAD9KEX/ehJX3rTnx71qVf96lnfete/Hvaxdz0zWhCBQOQ9GSL4ABlk33vf/x74wRf+8GEfjiNnAfdZCHM4iN985z8f+tH/PRkyMAPBGzwQEmgBM6Tffe9/H/zCr4QKHmCLvJfC37xgSSdEbf68VwACJCDJ/Olff/vfH//51//++d9///8fAANQAAcwAK0gAB7gE3APCSoAAQjQAR8QAiNQAieQAgUQDwBAAvQA9/RAAgAADyoQBENQBEeQBCEQAf8kAAmuT98cAQICYAtKEAZjUAZncAJJ4AEuAPdsoeI6gSU4QdSEAfc0AAI4gAaL0AiPEAkfwQAhABRwzwkkwACSUAqnkAoj0A4AoAL4APf4IAIAwA6qEAzDUAzxLwAqwAlwDxRasArGkA3bkAo5IAI0APeCoeJabSVwQdQ47uiIYdXQYBn+EBADURAHkRAL0RAPERETUREXkREb0REfERIb0RTgb/Ly7gYwAAciURM3kRM70RM/ERQfURkkoALAAPdwTQKUIRRXkRVb0RVfkRNxAANuAPfirgJSARZzURd3kRc/8QwyAALI7uhWwd/IbCWkgcSg7ujSEAbUD2nKIQb/MEDrjg4YKu4SvGYMxA73aOADxsBrLmEFIIDnjk4LyG3IfoYXYOABmvDoBsHfrmwl1CEIMsAGVLDYoIDcXC5m5GAFKsD9UI7apo7ukCbxIIAUji4U/M3vpkbgIOD2eq4WKsDwFi4ao+DtbuADgkAdYiIXfu0hUY4FvS5tpIHtLHLmWqHw0m7hGq4GiGHmiKEGWE4fTUYdykAFKqAVei4KKkAGauwbRc0Req7aYMAYWcIcxiAcCeH6PuECPuDa2IYSXCACwOD6VkEEyM3c0iYXSAwJxlHfgAEJLK8op4YkMWAE9FDfkAEMIMAFKOHciOADKoAd05IQIGAFxuAcbuIb/4IgHJMgFNjtFLQAAj4ACLIybcyhDKSyBhjBJYlNFtrgAqpM4aDS2UBgEGqh2GphEEAA3tyybnQhGiugDWTh24ZhEWwgAlygDMyhbq4BCCRNC07h25AhFJLALoMAHHJiG8RAyiLAAkaABi7Ax1wgCHyybsoBwCQNAmbgBoRQAtjMGaPpEraMAhwgBGwgBHjsA2JAEx7PZHghxyggAi7ABkQgAiCgwOTgHNlGGqIM/i6ABmigOjHABcQA83BiHDiBwVbgAz5gBWAgBixhJucpF4IABvjTP11gxhxtcZ5BDGCgBfpTBcRMDJ7BcbIhDmTABfhTBVYgBoJgwhYHHCwhBq0CrD9Z4AVkgBMG1CbEgRcmIQ7MYBJy4T4XR7wsIQ7KgA464bwKKRo0YQ7KQA40ob1kKBs6gQ7KIA4sob5kaBtygQ7MIA4mgRdY1LmuFEuzVEu3lEu71Eu/FEzDVEzHlEzL1EzPFE3TVE3XlE3b1E3fFE7jVE7nlE7r1E7vFE/zVE/3lE/71E//FFADVVAHlVAL1VAPFVETVVEXlVEb1VEfFVIjVVInlVIr1ToCAgA7" style="margin-top:1rem;" /></div></details></div></div>
-
-::: {.sourceClojure}
-```clojure
-(view
- '(ChemicalData "Ethanol" "StructureDiagram"))
-```
-:::
-
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">ChemicalData["Ethanol", "StructureDiagram"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhBgFVAPdkADAwMLq6uiwsLNPT0x4eHo+Pj9/f31VVVYyMjICAgFtbW0pKSi8vL3l5eZmZmba2ticnJ3FxcZiYmNfX18jIyLOzs2dnZ+rq6j8/P3x8fHp6eo2Njfn5+aurqyYmJoODgz4+Ps/Pz0dHR9bW1uTk5FxcXKqqqsbGxkFBQdHR0WVlZYeHh0lJSYKCgu7u7m9vbxMTE6+vr/b29lpaWsXFxVFRUZqamjU1NSgoKLy8vNnZ2U9PTwkJCVJSUiEhIV5eXqenp+Dg4MzMzFdXV3t7e5aWll9fXxUVFf39/Q0NDVZWVtra2qysrIqKir6+vuHh4RAQEPT09BcXF+3t7R0dHbKysjo6OhsbG8LCwisrK9LS0gAAAAwMDKOjoyoqKjs7Ow8PD+Xl5XR0dMvLy/////X19UREREJCQkNDQ6SkpFNTU+np6TExMcnJyYaGhjg4OP7+/qGhoX9/f/j4+Pf393BwcGtrawsLC4iIiOPj4wEBAWxsbLe3twcHBxoaGi0tLRwcHAMDAwgICMPDw7GxsRYWFqampnV1dejo6N3d3a6urkhISDMzM2pqar+/v+vr6wICAjIyMsDAwGJiYufn5/z8/FhYWAoKCvPz8/Dw8F1dXaioqCUlJWBgYKCgoMfHx/v7+2RkZGZmZjk5Ofr6+qWlpZGRkQUFBc7Ozg4ODubm5ikpKVRUVJ2dnWlpae/v7wYGBkxMTCAgIEZGRvHx8VlZWZKSkk5OTq2trSQkJBERESIiIh8fH7m5uWFhYTQ0NJ+fn3h4eLW1tZubm4mJiU1NTX5+fi4uLpycnMrKyqKiotjY2BgYGDc3N97e3uzs7EVFRSMjI+Li4hQUFLS0tNTU1I6Ojri4uJSUlBISEtXV1bu7u21tbfLy8ktLSwQEBLCwsHd3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3dyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAABgFVAAAI/wDJCBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJEmOvKSVTqlzJsmXFKGK2FHLksqbNmzg9wklzZQsaWVvUOMtJtKjRowLbvNliZQyZOU2S9CGCCanVq1g9qjKyBZAhOAQpTdLjpwuSrGjTqlVIxw0XQXKiIBTyZcubNmvz6r0KR5GPLUOCLIQDBNCWH2H2Kl7sUsuZLWywPCwjh8cdN3QYc8zDhIlThUE6C9F89FEjSIWQVZL4xNIWH4rAkr64acuWTgs92Q41OycpU1BOiclkEUukLWe09K5Y+3bu3cttXlu1pdiSjJVaFYLk6lH0iM1xK//UvYX395VLYm3x0qsjrUOnoJgidb5h+Ofl65fMJCa+LfofLXHLFqtco59C940H3YEgVYLMdnY8Q1IvXmwRy3UMFpRgQuSZlyFHgxyHhnIpkWKLLsIR9yEZGyLU4YoaPTHEFruAI9tKz9iBmmoftnjQizBaRJkgXOAxx01aoLFFJINk6KNBQAYpERyGGOaLKkTBAc4ugD1xYHOLSCLmmGRKEsyCUkJEF1OfGTUHHlzwIEcZ9TVn25145plfmg5R4oseXt2IlCq+bEEFEILOZqeejO7Jp0JzEJOEIMbIlVYyo2zxxWjLNdeMJ6CGKqonoaD5qEFwEBINYILlBUcpgOj/MQklvTVnCX4enkpQNdBAJtliURgjSBJNHKmZrbjqStAUewSS2mqkBaHEFrlUkWheyCro6KmgYJNNit9hwcYWs2izWLYcmsrnNllUh+F5lQxzRCDcoKQXui6qG6QkXBb4IX+nJDGEsWrh+6O+H3YTzjd6hAPgijoAlUUOaxkMJcIHIgEMM5A0MhSfuOCwRQ2JpGVxQVF+SMMvyJF46m9QwBJMN1mdTFDKA2Giibm95THDazFc++gjrkDCjCdnWWXzQDgnBUMgL7igmQwtXHLHCpkpa1AKKGxxwwkfuvDCNzAUAcpecJjAyxZGJKY1Qn39VQIJH44gwhZ/OJFXCCDY/4XX2wu1dcclH8iQIRzUeLBFDx9jtYYKZKWRNOAMhfHDFrx0IHR0HGwARh8a0GJV56n0kUFVlEPURjNbYBDChxdYoMc3GkyekzCKs9J46hAh0YUfkIhywYcV6LJFMxTkNAELWxxDE+8VYZJBH2BYw8HhHayNWE2v1PHNNBJAC71FzrCyBQQPfCjDB1Zj9hAih7wRDTOcvNHAGhBVIsE030TwyvgbkQQDtrCAZXwoDwp4TWwWIgRONGoLHkBFQxwxwEVMAIAdqYQD+Oc/lbEMDVk7iCj0pAc9uUIhcKgFBIWBQZC8IgLfc4D49KMxOySEebYJxAL4cD06gMMMkLhTMf8UkgAEXK+FIVneFhggCV0Z4044wJ9BpPEX2+ABiTgRBgS2cAAD8MkZJVySQpAgsi1AAhFYvAkHrAEGQWTAUjBS0hbuEEKE0KIPttlBGnESOz1cIQ2b+w4HgriFAjTkTFv4hu326JIQYGALo0jGh1phmz44BBSBsE0VGIkTOGTvNlg60Cxsw4aHrGoLt+IkTtZ3CS5gTT+5sM0eHuIavKmSKCQoAY2Cdh4p2MYaDwmHbQhwy6Kc4AY+GcB3UmEbZTzEGraBQTGLgoQ4cCxCyymEbRDwkAzYBhDTNEo3GgALXXyiN7HcwiwdwpUlhvMoiQgFnWZjBttE4iEV2sIt3smsT4XYoJIOQcIpNNnPghqEDmG0RUMSYJtTGPShBOnbFrhwxIRggge28QZEN6qDMN5gIe1KpOg2ClFh2kYA9iqIKk65hQyQlKSPsc03biGJsyAhACwgJGBe+tLL5UmndyoBT3lKgyoyahcBGKpSpfECRsjiCAQAwAsuqNSqWvWqWM2qVrfK1a569atgDatYx0rWspr1rGhNq1rXyta2uvWtcI2rXOdK17ra1a0BAQA7" style="margin-top:1rem;" /></div></details></div></div>
-
-## More Working Examples
-
-::: {.sourceClojure}
-```clojure
-(wl/eval '(GeoNearest (Entity "Ocean") Here))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-[:entity.ocean/mediterranean-sea-eastern-basin
- :entity.ocean/mediterranean-sea]
-
-```
-:::
-
- TODO: Make this work with `view` as well.
-
-::: {.sourceClojure}
-```clojure
-(view '(TextStructure "The cat sat on the mat."))
-```
-:::
-
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">TextStructure["The cat sat on the mat."]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhSAM0AfeJAKqqqtnZ2dzc3MjIyKWlpa2trRAQEI+Pj6mpqcbGxsLCwj4+PicnJx4eHoCAgODg4Kurq15eXtDQ0MXFxaenp0dHR6Ghofj4+EFBQdLS0hEREY2Njerq6ouLiw0NDSwsLNHR0fLy8r29vTo6OggICLy8vPHx8RISEm1tbdfX18zMzDw8PPn5+XV1dU5OTgwMDNXV1RoaGm9vbz09PYyMjLq6unZ2dpGRkT8/P1FRUQEBAUpKSoqKioODg3JyciEhIVJSUgMDAzY2NtjY2Dc3N6KiohgYGCIiItvb2x0dHfT09LKyslxcXPX19ff393BwcGtra3FxcZiYmCUlJRUVFbGxscPDw5aWll9fX5OTk1dXV9PT01ZWVhYWFqamprm5uWFhYR8fH8HBwd3d3a6urujo6EhISMfHx/v7+wAAAM/Pz6OjoyoqKlNTU9bW1rCwsAQEBEtLS3d3dzU1NZqamigoKC8vL6CgoFhYWLOzsxMTE87Ozg4ODubm5ikpKZmZmba2tgYGBkxMTO/v72pqajMzM+Tk5AUFBcvLy/////7+/nt7e25ubmdnZ5ycnMrKyi4uLuPj47e3twcHB3Nzc9ra2pCQkBkZGSsrK5KSkllZWf39/WlpaZ6enjs7O4eHh2VlZSYmJsTExOXl5Q8PD09PTwkJCV1dXaioqJeXl2xsbEZGRiAgIH19faSkpJSUlI6Ojri4uDk5OWZmZi0tLRwcHHx8fFBQUEJCQkRERENDQ8DAwDIyMvz8/GJiYufn54SEhK+vr4mJibW1tZubm01NTYWFhX5+fvb29lpaWklJSYKCgpWVlaysrPr6+lVVVbS0tBQUFNTU1OLi4t/f3+vr683Nzb+/vwICAlRUVJ2dnXp6euHh4b6+vuzs7N7e3iMjI0BAQBsbG2NjY/Dw8AoKCoGBgfPz8+7u7u3t7RcXF4aGhjg4ODAwMAsLC8nJyenp6TExMbu7uzQ0NJ+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fnyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAASAM0AQAI/wATCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS57clhsiRE0oa95s0TJmzqB5NkqTBlHo06gPji6dujVHaXliy55NOw8ggqtNu97NOTfv3xShkB5OvDjpSbhJ6x5sCIk3rM2fA/+ZDkmkhr4JR5+uUrjx78eTs/8mDCkNJazlz3PvyShNIezKC6dfj1JJtfv4oZHGgx+/dIHZDXaJeVgNqB59OmniHnzjCUgggixZQRoWCwUo2CEPWoXhgRDelMuCDFkY2IYdriRhGhQqtJo1hA1CGodTuZhhiTXZAWKFpLE4mIww0kjSiSkmtJobiSgiSRtsdOGHL2oshIYXXNRBxRSCSOHET03cwQQtRiQhhBxbKOTEEpx4EoYRkIAiCkKopAILMKqQ9qUcdNbpSkmKxDLLPLVQ4cctr/yy0Jhlnpnmmge1+WacacxZJ513NvWLMeGwYoQdnFyTUDByECOQkUgqyWRaYvxhySfHkJKGEY/WuUxBQxb/eWSSSzap0JNRTlnllTkdI8c3zpiDSS3PTJPIJpbYYYQZYR5EqJloqsmmm3DK2SqkPoIEJI5pUDOKLsZho01C3YDznThi9PRKNN9hM845BqGzjR7ggYKGQeqAZ1wbJEXCDniHJPPNQfLS+529+OpbHL9MfWLKd7kIatBo7STybbjjnqWFwsTpAStp3oJbnLjkmmscujm5k0YzCg4XzyacdAxPQQXXe29B+XJMGsPZdrStiqTJY0Qal/jSCihDpzFJJQfRE0QaQQBBxxJ3+DJJGoGkm1MvXAznhw9ZZMFJF6TFUVAZBptSSg9/8LCDDqRtY1AOONRtYxq11K133ceM/+SEH6R5csMwNXgRxRGk3WIQ2qSpzbbbcKchd0F0201a3nvzzZQvpAVRCg1XyJB0LcZ+HAMMMRBtNNLHMW2WOXuT9kLmdbvwcRpCq3500ks3/XTUU1d9ddY4qexJGrLYwAZp7eHSwg+ktUIQ42k43vbbcc+t992YZ953zz5PyK07cKzDwkDnrEBaFAaJAQfeKhSUQi1piMPrTSiQdkIzBTVhizs6IkgOqMADExSkBCRIwyEMkZBrvGglRRBfQTbRjBFU4yADLOABE7jABj5QKlkgjTgCmIhzJIM0hejFx4JwgvKdTyDpWx9bUMgg8pkPfepLA/sK4j74yY9+9ruJyv/SAARFJAId5SCNDARSCbjNgHIENCBBEKhABiLEgTMCX0h+JiTSuEMEBgEBaSpGkF58oHpEMkg3SCMFnLwDbh6QBkI4cJBfSNEg5iDNBjyYRZNEgTRLiIgdEZLHNOzxih+ECjk0gLUMGGQT4SBNJ273xTCOcYY3AloaKlkQMaaBjAMxIxoPssY0tNEmKiMFHQWCgTQc4QIDQdwPCjLIgxTykAfBYo+06BEuImQ1ZEDIgMpRkCpkDyF1SIMycAIE0txgI4ggjSb4uEuS8IA044CmNKkplSuQBgoIUQNpeHG7YB5kmJh8T4hIY06DoJMgxpRcQpK5TFSmoQIEeUYaGkH/kDms6iHRTMM0EdlHXoYPRdxaTkGIQJqbCQQMpElBQk6ojps4IYnuuF9FyKGCN1wzDbrgpkrSEQbSsIMCsKQIRz1KmpAStJpKKQZpJpCQ5emgD+JRKEEYmgaHooWG62zQQhtKEIimQaIIoagQ70mQjfFzIAyt6EJW+lGX5jKRBv2IL1UTn4PggDQa9acOGkHWspp1eUG4CQxIk4uKSIAHcaBfcTwhUpVQYx7DeUEOiFE6hrw1rsah60ulEgqwJiQCpNHUQEQ0kK+mQaNnAWpCEeLYsKZhrGbNLFqXis+BOHWnaZCqQf4qV+II9qoFzapGtjqxrhqksgQpqc6gdhMs/55iImQoxHA8wA4wtCITgaurSjZRBHZEjjRzYIYSEpLb3fb2t8EdbFROsEmF+IA0EMgpZQ2rFslqUqeN5a5AZKuztNqzswL5LFRDa5Dmkoa3vgVuGk5rEF2qVlsS7KJQCQLbgSQzDTcIm4AHHDZP2eQMpMmGRGZBGnVs4xGbGIgTootamJ7kF8Rog6pIY4RgHITBoX1whAUy4fkK1yniSAMcFEII0kBDu14V708zqV/wCqS/AvlvgAlMYAPXRGXoTYR6BRLVgoDYwRCWMIXri9X7boS1t7NxInCciFamoa9AeQBpPhARZpAGCHdUsokRIoYmu4QFVYjkZb9QEC8TMf/MJF4yD83MFN2mwYoH2QFp4rdY1xaEymeBmzonG+PHEsTKWP4JkJu6T9CKNhFuBrNBSkzfOafWyRaBMoxfK2MHkOYPRGkAaYYAkfJEA7JxHvNBVECap9JkGWwtiKlRnQhKJ4TVjY6KDEhjAYQgQ1Wk8Cljbyzjs7wgDQxgkJSp7Ok0gFooi/ZsronM3oHM2llyJgiuXc0VRMSCHHLRdJ/3G15DD8QN2EgDK5YrlOumoRgQeRgO5pjtgXCANAuwySYCkQZwFETe9Fa1Qe6dhnxHRQGkiYcKDXID0kQgyts1d1qWNwlaQ7zQGkW3utkNlGind9qJKPJAAH4QgleaIAT/N/hWFNEGDoMgLuIGkJ/5W+xxkMYM8DLIBaiRk2psWAYjJggLbJCJglAhDVTIOUESAD2BGwRxQSB1Sp6AghAgZAukWYXRka70gTC93rGEmtShYuUdEuQdKoOD68a97GKbhXNp8HGNIw5Zm6cB5wfZefGYKm1ui1wgR0+6Qb7u9IJAfexZgQBxrOqWmCdi2FMudgjaQZof0OGCAhmDMBpQCCPiBBpPcw8CBiGQXzCDFWkoB5axgO+XF0kBeNABHPhQeIIAgzRH+MLNlCCPLIikBvpbhBo8f6xYoD4NVSgI6wvuekXAXva0P7ntca97gfDe90r5hsGK8QgjwkMYQzxA/2vJTWyJo+VE5ZBCzlmwhx5oFPKAnnzlLz8QzXOe+DTxuJBB/vdELH8Bzfd8s1d7A3F7rlR9iXB9VXEMxPFobeF48Od2HGAGw6ED6nAEBjAc4vAAOpEHBkMafJBEpHEIHVAQo5BipKEBrJBAaeAH79By0idhlEcaJCAOHjCCcMYRzrABjASCDEAE7bBhaeAABnGCw6GCLOiCMCgmM5gGNXiDCpSDRWENSTAckyCE2AAMXEV+kWd+aLEaUGMEH3gbbEd3A0eBpGGBGKiBHHhejOZ31SYQRpiCK0gaSkiAJNaET4iDVBFBwzECMJdfvzRz5UZrigABRHBcpAEJWZAZO/8BD9uQNMPBB74wMAYRCTmQbsNBC8SgQu0RgwMxCOPwPsRxAnjADSPRBFewAqQ4HEFQAVpziZlIHJzoiXgoEKLYivpzikyBDnLQg52zCmcwiFwIaGehCMKQgcRBAqvQDZv2Z25XJIioiGnAiI7ohn3naAWBiZpIGrWYCJ+4ELlYHKaIilPhDI7FB4gCGtUgCRZgAYCAU0HhBm/QCaiQAM6wEH3wBtrwBmsXESFQA0WgDQWwBUFXEudgBQXgCARwDeCmj/zojxQRkANZkAfJFL1wBhRAD5KQDoiBBglAAcRAAQOADCDRju8Yj1Oxj/34jxBBkQRpkFexCV9AARKDaTj/mZM6uZM82ZM++ZNAGZRCOZREWZRGeZRImZRKuZRM2ZRO+ZRQGZVSOZVUWZVWeZVYmZVauZVc2ZVe+ZVgGZZiOZZbYQVmeZZomZZquZZs2ZZu+ZZwGZdyGZdjUBHeMJd4mZdwKQEd4Qx6+ZeAiZYXiREqEJiGeZiImZhomVIbAQKK+ZiQGZlryZcUwQKSeZmD+RCFeZmc2ZmQSUIM4QWiOZqkWZqmeZqomZqquZqs2Zqu2ZqgCRHT8Jq0WZusGQsd4QS2uZu8SZoLtxHQ0JvCOZzEWZykeY0aIQ/GuZzM2ZyniZsUoZvO6ZyZ6RB5MJ3YmZ3NOQwQQQHe+Z3gGZ7i/zme5Fme5nme6Jme6pmesfkQ07Ce8Bmf6AmdG+EE8nmf+Amev6kR0JCf/vmfABqg4ImcGSEPAnqgCJqg48lm0amgDlqdDZEHDjqhFJqgZEiWGJqhGrqhHNqhHvqhIBqiIjqiJFqiJnqiKJqiKrqiLNqiLvqiMBqjMjqjNFqjNnqjOJqjOrqjPNqjPvqjQBqkQjqkRFqkRnqkSJqkSrqkTNqkTvqkUBqlUjqlIboHCXClWGoNApCPQ/EI+MgTyHClZYAQApAA1+EUSnClXVcQA5AAY1oRo5AA5tgSIIClWDoAAfAfPvELCVCXCMGnfqoTVmqnCaClXCoUXnqoORGmbv9KpmZKFHVKqHiqp1CRqC7hCDSQqZqaqZYgCvvpEIrQCxBKEsxAAwR6E96QqdrgUwPxBTSQAE+hCFdAA++AEH2QqaRXEYhAAwrwEkWwqcD6BlKIE2pAA/IwEJvQC8RXrMe6E5gKrJzqqRIRqqM6EqV6qjaRqjSwqgfhqrA6FL8KrZkqrCpBrR/RC/t5rZdKA0vwDu6aAHnwrM3wqQyxq73KEuq6E9pKA1bQra8KFddAA712ELtAA5Giq7zqqzQQDO7qrgoAAZlaBNU6E8w6EGRAAzwnEBXrrOzasPAqr/S6EPbaEvmqE/varwbhrUTxqwzbsA8bsRPbESPrETdAA7//WbIrgalyVBCPsAE0wGcAlbAsga49kao+CwurRBAq+xRlkKkeaRB08LMXMbMt8au2QhCVkKmUyRPmKhAXm7FFIqo8obMG0bNSCxFUqxJEyxNGSwNIm7L/Cq40cLUDkbU0sLUmkbYbUbO/ubYtQbYGYQ00wAyKWq9CqxapmgWSYLD4lwhL+xSdQAM0dTY0sAFrKhF6qxJWexDNQAOSQBRfKxSAWxCCS7hoe7hpkbiL6wqN+7hBsbkG0bmfixKZmxF8SxOjSxBoMKtAKxBDAAid4AhkUAme1wQiQAE0sAYigHi/G7zDi39nAEbwAAGpcEHvIAKbMA0FIAXKCy8cUANr/0AHBYBniSAKIvBClSAC6cACCkAPqeAF78CqidC8wku8BBG9iTC91YsRiesEvFsQrrsJiPAGdLAGX5BoYiACn6oAInAzHCACApAIEkAAqWABJcBxJzEA22oQCkADCFAQvTDAdHAHgPCmAsECIsAiAVAEjpAI9noBYkAPUlAAAxCyIQG7BdENNEABAlEGIvANipAAxHChIUzAJGzCicANIjAKlnkHf0AGiDCYATAM9NAJ0NAsZbQHAEAHjgABbkB8o7C8iWAIIhC1wSACYxrGiCfABGzAiXa9m4AOgOAIfwAAATASuTsQu3u2A0G/zysQxou8ysu8wFu/0Cu91Gu92P+rvdwrAt4LvuJLvuaLvurLvu4Lv/Lrx/Y7EPirv5hnEf37v0obtwLBxgV8wDykwAXBwA4MwRJMwRaMwRmBwwShwzycCNMgAkiwjSLgOmggAqbxAAXwB9qwBEgsEG4ADY6wBvIwCoB8vMkrxucgAo9QEEogArWKrNZQj1JAALtwR1sgArBgrOdbvuU8EE0gBgDwB6jgkLoLzIkgzMRszBWRxwMRsNwpEGiwuDRwAONMA1WgQukArM26z5nqz5ka0AMRuRyQCZk6pr8KAhuQCVFLA3QwBP7sCOMMCzMjEH9gqgIRsClADzQgBaVKA/yjx/yM0AD9mwzt0DRwzBORuIn/kAI0cANh9rghQACcmqkbsI6JkAU0ULilmlJIwKvDQANZUNFSYJIoYQIPXRCY6noCYQKukKk1m6nVDMgeLA1Y7cI08AXP6rPJa3UmQcsDEQw0kAe+K7n8bE5WjdWautVg/Q7a4NOZigpOnQhoEAs+fQCZGgyM6QwWgNWA7bkDkQHGmgggAKykptjNmgg73dOVC9S/GglCTQxZnc0gYc8hTQP5zNcr/c8KPdCbWtCjndAuTQMNHdURPdEVfdEZvdEdnQgf7YgiTdImnakprc+p3dILzdowLdMSQdM2jdOj/K2SzdM0YAk+DdRCTdQ0YNRIrdRMvdezPLcHodZsnQiC/7sLBVGsinUBNEAAEtDPGl25eIYGSd3cR8sipq2px8oByVsQqVoE6FPYzZ3VWYAOAgENwJoZtz0QkZAKlJ0Fa0fe5o3e47wB5AsRnp0Ie1DeAyEGFv0Am4AGbvAKNADeinABZ0AD13ABN2PhdIDhGs7h4C0QkUsPxCABkXAvvwoLiGBEkUDasHQOkcugtg3SiRCwUkAP0gEDmYpnJo7iG97hwe3iMC6/xa3UAlEAKJ3cA9G52jAKm+AEKuCzaxfdbTbdAnHUUpAFEZwIZTCrA6ASyLviAkHfsIDdV40Az4EMouCzftoENKDZqDAEgrKrbmsNyMACASDUHnbW2r2NPv+b5vNLAyQdC9/g34kQ53Ne5zTgp7tqCRugAoE+6KA9EBp8A27gDGjwDaUKRgJRsBZwQYowBOMsj5CdCL1wAZ1bCRcQYa8uEFaO5VrO5QPxq1JQBVfSCyXQ3DFLERE+4QRQ4Ree4Unu4SAu4iQuEEfO7Cq+5C8e44kw4zWeCDee0Dm+4wMx4D9e0kIuEEROA0a+7Cmu5CzO6Nfu5BFB04kg5b3tuKSc61m+5TTQ5UP95dQ95mV+5jSg6BqB1tye6ALx3eEt4gJB3sxwAGegQk2AvNklEFZQ0tOQrNbgs4bw4SE+4vdC32tg3zSA3wLhqnfQ0emACjQAnc5wATXbBCn/Je4sUKpk4N8msLiWkHMOD/EST/HGTgM7axACADoCEQKWcACQLhDc4LaOSLVIr/QE0fSw4IiRmwVh9qsXmghLYNEO5dWoEO4+HrCw8JBee7dHn/RLn8RO3+5YvxHybgI1m0b2/q3TcNPIqQKM7nleThBFHeaZSvdg3d0o0djPJhCiQAPtlAgBQAOdsJ+JP7B4brC/6ed4+wuZepMj8avDkAGenwGIMAw+qw1cOgSZqlgC0fiPTxCRLxB+TkJNuwH+7QRCHahm3s9mfdW2PwzM4EiJcOuJELoCcet3fwN5v/cC8avaQHybINRP+xERXvRXkPZSPxBU//SHG/Vrf/1u/5/1NLD1XU8HX08DYe/RY++2Zh/8aC/Zaj/1bZ8IVz+sMw3liSD3NED3S1v8x08PfN/vfg8QNC4kSoSEBg03BAkiopFH4UOIESUqLEJjWAaMGRAN20BDmzOC1mjsgqiGxjWCFw5+eViGxhWCTW7QSPdQHo0aC2koUMiBxhqI3mgUUdiJxrSHo34+nNlL4R8aTQhOoOFK0cNgNOSlXNny5USwCh3RkDZxGo0DOiVFdEWjkk6eatm6JWj0DMSKSB6K0fowEg0CT6MSvEbjDcTC1uRCbPs2kd2wkSUKzaJQJDNkBL/QSEBQBI0SEJ1loeGNIGmQD5kJJGjw1VWFAgxLpv9dW6GTAzQMFUX4kAxZ0R0zNzkY6SHDVE4fFqAxwfZziRUPTp9uwTTBITQsKSf4u+xDZ8ITMWSGBiLzAYkq0aAXEQINNQQJ0Eg/MUPf7jSoKby/NdHn0MAj7bqKVIBoDRo4gO65sb6L6Ky0xqNhLcbokjAuCSl8qLG6aLjrobz2wo+gvwIjCCqpEinssIcSW2xDCyFbECzKLKMBM8048ww00QY8jYbUFFptoIJoeO0h2VicMTrqmrTORpIeMgmlRFSiAZ6HWKChskQkoIEMiMoYpj6GMPQJqIeEIoogcgaBjaBfaLiDKRq4Q5GgO2gIACKlmOHqyiy3XLLBidygoRP/gmqgoZtIGnW0GfrgUkhRRh1tFNL6jHKMIhrKeEgBDx8yBDDBUiwMQ4J2oUGxRCi19NJIH7NwyYhqJEiRtgDJsbNEmEsIIlRoGOPHIAkasjVSHxpjNlpprYLHRISypFhtaNji1Uiu0C0R4mhw4jhmH3rEomafqwgVEdJNdwAB3kwkOwsgqvbaV7XdjaFmIhqXpX0joirKcWkAQIKaIOpPod/2I+jgXnsDVliCKlJYIQQVLBcsQiUyFNFWF8UWU0kT9fhVkGXdNOJOPw1VoVFNTOROFXeCSFVWXSU5Vk0vTlPQW3PdlSBfIwp22ERQg+jYIl0maFkldT5X3XXbfUik/ygVmvJP8xRyhufC6puozJ6W2nnNhxQxgRtrjJpToaZKJWimcyDapCOQrMyaoK25XDDjiAb4kiAAmmxSjJATCVzw6QiXFUsQU1YIVK8TadntmBGZeVXAEU+8Q8Z1jpZngjiARb9ENuPVKOMgGoaGPYg9mrUiwVQ2XM9rW4+ZqxJoqOzRNafhG25B10mEiAKgAZXaI6sovsiya1qR3jUHnqGcIDIegI55fei+Km5NwJLprpAHHf5GTLh8/1CPaPXWE6nI04cqTh4iviHyW/bDNVcc7Mx9V9yozqEMfgSBnKiS9bLBVO5yrMof4v4HqNrZKnSj24/pOpS6h7DPdaqBnf9BZKcQpiVveZKhWklOwpUbiIZnWXGQRPiXiDMFZSgKUUQGUAG+g7xCTnSy02CUQANYuIsgUqBBNapEgxSCR3gMAo5EmEO8hskjI1PMQB8KxxwpUhEjVpTVdTg1wEQUkGUHhFlhLPcQmgFNK1rcYoe8qDMJEsQKNCCGMyyYCARNTCHPAsEGFUIaInkQIiGcH216QZr95EkvdFIBGzNgguD5CVwsgQgMaNC9QjKJeWHJzhIgMpNGshGSDBlGRCxZgESoClUE2QO5FMKCIUiCGAexBDcWZj7S3dI/eYwIHwV4oARlkiD1Ww4NoIhFR3LxhchkIxeN8kb3OY6AsSLI5E7/lEAzLlCNWdSiM0uTvDgmYo51vCMvIeLLogEJIoBE1geXRruLjTAyJZzaCY+YRK3xbAk0yEBYXhjDh/iEbPukAQKs4AYOpGOHbKuT27ZGg7sJiQbkUwk+8bZE2xAzdAfhYjfgE5kXenSTE3kmXqQZRmpKjozYpMEZFZLGRIg0MiWN4BLRUK1d3DEPNJBARBCElHQWS0sd/NvsmibMiSgqFgrNAncIYoFvgoU4klQIQxAQEVHQQHFI5dRIJ9JJiEAVmhBhiBewaswu7Q4xzZlIOgIXr0QwLBHn0yVBdtpTYAL1fcC0WCY1CkOOEkSm/pSZYD8aFpp+UWWRsyYCTdVS/23G9LBgSSwcbYpTnfLUp0fxYyKGGsiighCe5ZJnWOipkMJQqaIq5BKoRAERNCABeBcKG5piM8NE/CUTYFTo2t7W0GumSFsFeyUNNrCJe7J2UE18CDK8QINgKAQENEBl2SBQBEjSliDTrS4Nr5vdykYTjGKs5kof69JUYS4R3IWIIr7rRnBi9CwbQBCvqIK9h6CjI0r4UYoI8o2DgNadiSAkVyfylyxkNRYRgQYNHgERchQBAjG5EVmBGIKHbGKWvzJwNL0qEbA+pMEPfkiEJyyhDZCjbGPp6VmywIIM04EGKeAWAgCAXIW4xBJ1zc/EGHZfiOiXBvwVL1+RqlHnQv9XutRt73u1u14mWxe78G3ceFPa2DJCFo3qZa+UwRtVz4UzEfOt71QEFuT99vchACbqgAvstMmCRST+UUhbVItE5SbCkr4liGyQ92SfcEwhfFmTCtSqkLPwuW3BJUiwPlQ+jq1WiXqDDt8UkQ43yPgAfXVGKlgnLvZUdSRa83T7CDKu9lBZsY+7snkJo+WXqrfTn1YIqnkz1maJuXTT4ZUSZrIngqCBOaUcpsMSgQYEtXmQo+2wQmQMvgdExCVZGAUNsxKgqVr4kjhORFbpwG0DlxYsIc7xlqp9q2vrBLrcoQozYIxHtCrkDDSgg3IyQYNFEsRQaJLrb4gWV/z4Wk//ChG2K4scv2AK09KY1jSnSw3qVEuoarM2dSJsrepfspqxrlbglllFcYjfOr6UVshmDtLrXxN82GIxNrID3M5lH5W0cS7UobhtPHtKOp9cQgNU8JoIRTzXORJXSAiAmN1EkGMmazKUWW/TlognYiZBgplsmEHcEMi4j8md9HJhYQmwR+8VekzEFg5SBQnAYKewiHZIaGABbhTM7JdM+9rb3kWTWnnjLssyelOp3rKfve5AvHt4y6VrJ2hLR2bewBdggAgE3UDFOcoEIiKxBQswwygCjnmzJzLHlwiRIIBAYg1gIIG2SCFukbRwtQigAjVAytgdFvdXaeBJiJD+BqZH/z0NVK+TmbhCBRL4Da0T8YCONEMNIHjDQYagkM/AQh4wcIMIwNdPgNO5+cOIBH/lSpXGPz7ykz84xRLuVyCC3RJiJ/vc0a52wtsI7nIXPPzZLvIqL9aAfGep32EaeLqzv8IDM8siOYJIvJNTCPBzPMhDIvLbjMq7vMzbPJgzKhGiOYkgh9xoBgGghl3YAArIOTzrOoKwJIuQBhCYDzogEpGYv2LTBhiYBhVgBi/YgDUJgZmQBGqghndgBh1iu3cjjUeIBKeAmUQIllewghSYAE+7AxzTuYsywNoYiybJgiIQhcwoHtKYDikANoIog44YkQDYwoPowocIr73SuP2jnP9s8riHGEPqMEP8CzOMIgic055E2IPcqA7iqpJkO4g/+IX34DwL9LxaOQgoighFEIUwPIg16KtsAxc3iAXquIGToT0MjAhyoyFGpI5HFDUR8KjpOICtU4hIIKLpYAYBeAg0eBbqyAQSyz4bcT5ZVAg9pA4L6MM0NL++KiQqpA4rxEKJgEMu9MJEAMODoDNiLENjRMOTIi+V4r/ziiw7JEPfa0YCvBhdS4Q7fIhb5MOHuIA/pIFAHMQKFC2Za5basw8cSsa/uDOLSoS8ecN7m44i6CtkxI9f8LTpQAVkgAWySYGZmA4ACIFgoYHnSwRXHAwjRAOTm44lIBKu2zlDdAL/HnwEJIioLzyDBMCgRLDId8BIjTTEsABJkSTJ51ACARgACegDp1KIb3iHCUiBYkHJTDKBSkiAPQAq24CHR0iAMchCmywXnNRJntQJlCAHN0iASiAy0ZDBR3gAiQyoDJiARwiAbwkLARCFARgEsFBJlnTJodQZk8xIaeNIjyzLkRzLh1BLtowMsGzJl/wvmaTJt3yOEMgAUUAEI6IVJ/iGAbCGBxCiMkBLrUmBBBiAwZQIJZCGCZCGvmwCEEiAyUODDLACFVhLgkAHxIQBXLtL0AxN0RxN0ixNz2MIKjFN1VxN1mxN13xN2IxN2ZxN2qxN1URN28xN3dxN3uxN3/xN/+AMTuFkS9wcTuM8TuRMTuVcTuZsTucEKXt6TumcTuqsTuu8TuzMTok4B0MgP+38TvAMT/EcT/IsT/M8T/RMT/VcT/ZsT/d8T/iMT/mcT/qsT/u8T/zMT/3cT/7sT//8TwANUAEdUAItUIiYAARNUAVdUAZtUAd9UAiNUAmdUAqtUAu9UAzN0AwtRQPFzy3QUBANUREdURItURMFUXDr0NrwAhZtURd9URiNURmdURqtURu9URzNUR3dUR7t0R5dMBXFT3nwUSItUiM9UiRNUiUl0hQN0shYUiiNUimdUipNUiB10voc0irdUi7tUi9d0ibF0olQBDItUzM9UzRNU/81XVM2bVM3fVM4jVM5nVM6rVM7FdP6tFM93VM+7VM//VNA3VM8HVRCLVRDPVRETVRFXVRGbVRHfVRIjVRJnVRKrVRLvVRMzVRN3VRO7VRP/VRQDVVRHVVSLVVTPVVUTVVVXVVWbVVXfVVYjVVZnVVarVVbvVVczVVd3VVe7VVf/VVgDVZhHVZiLVZjPVZkTVZlXVZmbVZnfVZojVZpndZURYYESAAwQpKOFM3JvFZvHYAAgKZ0SABjpNZJtVZsnQgB2NbQ7FZvTcxwhYhxLVdzHU2h8Ii1vCPQlA7EeQOkMwjcq9dJvVdtyNfF21ff8VeFAFiBNc17pQErkAh9vcv/igiGd7jYd1CA9xgKHGPYhpXUh43YiJjYt6xYjM3YjS2Cjr29jyVNoegIWOjFnwnNdVwPzSqSgG1ZR31ZIJLZXcPDksVAm8Urj9VZ0KQMSagKISJZtlzHRIAUCilao2VUpFVaiGDasXRaqEWWnJ3asaQMBDSQh5jYTUCEN6CDNfiCo0wEMRCBl1QAEcgaDhCBVZQAAkgFCygBp5wIp/UoCuBaRVCBNbgCC5CH1fMsEVCMACgCR1AIZFCAZqADR0AFFXg3hagGSViDVFgDeUA6hfiFEnCFP0AFa6hJr9VOsNUWsS25g02Esj3btF3btn3buA0duu2Su83bvdUkifBb/8AVXMI13FdKXG5kXMeFXMmlXMslCMzVXM71XDgJ3dEt3YatkRRAIs/V1xCYD+04iA14rT9SJw4CLQVYnSyQMd8TSt6NiKxwiCIJBubIAqhIXwpDAGk4iCSahtWggUzYwzW4m/s1ri28gTdSgd7BoU7AsNMFT+vF3rE92O2lJe8F385KBKQxiPLdEvSVAvWNCKdtX2SB3y2ZXw6u3wDO3/3tX0cEYO8d4AI+4INIYIG1FebIF9bVHkjRhlHYBCdQgY7YFKMZX2SRgixYxWPUlsjxYAyMhI6oD4PYgFeYrT5YDRIjDmK4AVQYgl8otiVYvWnwNBggCGQAn0cwj3N4D/8bTgQAuwEJYAFFGAV6qIoFZmCeqeEHxmGP2OEe/uHwrckL9r0i/kIkDot1ZOJYeeIoJogpdjAKu+Is3uJEGIsuJogvpoEwToQxdjAzRmOYRKI2fuM4doUZ5hkTmAkOu6OzuAH/SgRDowfYCGKJAq3ZYwj35VuLmKKN6IiPQJaBU4h3oAFdCZ6q4A7imJaH8BsqATDbgiFm0IZbyZNLFmMdyrc5vk5bKWVjQ2UkWuVWfmXxjWVe5jAJqWUmuYiMyGWPSA2D6GWC+OVg7hZXIGbtKBZk/i+xCZ1mfmZLbq5prlcJuowsvCMA6ZGogmVjIaojua105BTNeRJkSQXroQH/aKAwGvDIXhgE6B0XKKIGGkiFDi43OogIvkjEarbOf76RgF68gRaQgv7mgwathO4zZmNoxHHoIoHoN5RoirZojIYIjSYIjvboiXCJkIaIkfZn0MEVYJ7ZoHkYojFoCyYqpSGwmUYZdIEadnEXg7iqh1iPiRbmrIwINEiHMZgAHYKiCyAiZrgGaljeRLheVMAWUDmxkjbppPaZn1UjcW40iAmq1wGtqX4zJb5qdcnqh9hqiPBqig5r2CJrs463tL4RtnZruJZrGqDraY0j0SGdO1If1aE1qP5jN6tqD5MMg8AkhVDs4DHACxCFO2jEs+6JtvBeVMgA2Jg33xHlurZr/0rb7ApaPM/OINB26agmRHQk5EyEiNNObJ1e7Yho7deejtgOndk2rtq+bd+RY3MNp3Gyo8Uzp4dAJ6hmp9jpPLBwWuVm2a5u7ki8jWq5gSp4h0owgekiaRg6AwTAoWa4inFBAEei5t2WTu6mI+/mFfDeIxrYuvFWtkK05Q+LCKlVD/ausLZ87/ie7/qGCA7Ab/3m74L6b6QmuZsaicz6OfMDKoP+rHN8p4VGmQdP765V7fYmCN2xAPXNcIlAA2kYHb1Yj64N8OwMpxHPqcW7q81CcZdW8fJu8PUNiwiXcQpXiBq/8XgT6x3HNwn/8Y8VMzJbPCDLrzRLp1VmM+Nmcf/kfvHDVu/UnnCqIojmM/FEoAooegT7hYjfeIdEUKjyMOoiuEQgb04uN64yi/MzA/MhU7NOZvDjPu/kTvMYZ3OIePMDjTc6b6G5ogE813ONFIM+D3GJ5TWCEDgvLDhii+SWS7Yyp+oWL+3IeHJIf2CRZV4dChCGcAVu64U8MeLfgAZuGwVY2IDd/XPm1LWHRDl2JnWW4zCXU3QzZ3Q0X1g1Jwgob/Ndi/VEqIZZ1wlbVwhcpwFdl+he//Vgh1bEUzztWUDxc0DWjUDM0zxmV/UzN+1ol/CvnnEJP4ABiIRKuAZYWA16KAOzubc7UIEA2IOK6ITU8AbwIYABGIJdmAn/oBX2Ya9DBDxYdG9AyVt3y2t3ClzyRXdweX/0eo9yaUeLfN/3fmcPgDcBgSd4gz+UhF/4hn/41s3sOuTGBLTFPTyIXAzHcSzHdxdsk3p2rmXukaf2mJmODSiBJqhHqRAAfpwOCvDKyzWK6bAECpZ459zGbtR5XOxDcaQOoE91oW8cosdZo6cwpC8MpWd6p08EqG+SqX+IarB6Wsr6P49LsYyImJxJ03XNalCDCQgABfaGkMwaNKgEFRCFDIBkiOiFUVCDBEiBcdd68tT7uVTjuvz71gz8wS/8ww82xWd8x38IyJd8yrd81V991m9913992I992Z992q9927993M99/93ffd7vfd//feAPfuEffuIvfuM/fuRPfieVgAFofud/fuiPfumffuqvfuu/fuzPfu3ffu7vfu//fvAPf/Eff/Iv/+kXPeWHVWj4UvZvf/d/f/iPf/nv0TBNf1dd//nPf/3ff/7vf/8HCC8CBwrclOggwoQKFzJs6PAhxIgSJ1KsaPEixowaN3Ls6PEjyJAiR07sZfIkypQqV7Js6fIlzJgyZ9KsafMmzpw6d/Ls6bMlyaBChxItavQo0qRKlzJt6vQp1KhSp1KtavUq1qxat3Lt6vUr2LBix5Ita/Ys2rRq17Jt6/Yt3Lhy59Kta/cu3rx69/Lt6/cv4MCCBxMubP/4MOLEihczbuz4MeTIkidTrmz5MubMmjdz7uz5M+jQokeTLm36NOrUqlezbu36NezYsmfTrm37Nu7cunfz7u37N/DgwocTL278OPLkypczb+78OfTo0qdT/wgiAfbsAwJ4E/srwRiH38MrvZBAxcPr2bFv754wXYIA1efTP12EBv78+d+YAKuGhjwIbdKLIgj9F6BSJtDwx0P36acffwghQcMS9Vl4oWf3BfMOh+8oAAF+RRjk1YEIkUEDNQYCuJSCDDqkYYcegkiDiAdNWCGGOepI2X1qLFQJfhJ8pUgvIyZyYooHEWkkUi02SIOPCgFJg5CJ3Lgjllky1iNDzdD/IElZSEbl5ItQdvmljRRquSabg3G5UDc0UHBQGSJ8o0gCxACCUC+IvEHHHYCUkRA3IozCghV3/EEGIkweFMAw9HQCzRYL9bIHAHQ4AoEbBR40ighDJGKICHTQEIwIg4IqqoB+0rHGF9Mo9I4Im6ADiCN/ACCfQt7UQEEq9JARgKeJkNnQmwrFOaeVFCqiwhpXWCDPOQixIII1iQRQhCMIIaNAM5qiogILClUjyRqprCFPfwr9UoIrf6BijTNt2ntvUckmFAwNeRw0BA0TSIIfGQeZ4Ap+N+T3CEKI0PCONvhtgB8qyCCERiwSH4BfMBcg5IwFCW+M5kEZrAjCg6Ka/4xgIiEQgJ8lEouS0H2RZEEDMQo/nJAKsOCXxcQ0lIDQsQzpixC//jYbTAE0ZPEHflJYnEgTNCAgTcIHTcMMfpmMvAYaCGFNwwY303CDewf1DDN+nYSAL9xxf3R0IpFMPMC/NNBDQyzfoHMQwgh0h4woE5PnsCUbqIAMCwHcPAxCA5zthjNofMO1CAjtQoMF1SSiyBA+91Hyir1c4GUlFxi0MkJeajPKJk6oMHElCN0nRRVOJNJLCTRYMiI5Pg9Qby8gTNxu0QvRbTcNeDe7wSvfHNQH1wxTjfMNqAzxy0GOUFhtItOkQgMMByET8yNhnwNiMwh9c7YELCgyyt6uyP99P/4W3TdMBv1ngMgwJqaNeiUCYDS4RkICQINO9CIhouDcQRxGg2whpAxk+5sTbkYeOtHgAG9LBMI2mIhhMCMDpGOZmE6otbM1gWd689R9tFGsTdwsHXlDhUJAJACDLehJ/PMfAAVIwAnRgFcHeQcN9nQ9GriigQepmiUIeBDJITAR71tDQjjADG0o6Q7kSwgyXkEDJOSvjGY02oP0Y4G0AcwSTjzIiaShEGdMzGIOY0bYEtI0vAGJHgsBUZRe5jyGsA6OKEJIIUUgtDnezD33QU9C1kADDhzkAoOYGkKaVjtj9bBMacTPGiVEg1QoRIHQeCJ+IpGQXgyiXQh5BA3/MpcIaowSkwqxIB0WIoZYnrGXZ7wPKkQgTGEOQADFKiAEExKxLUSimc68Ag0MkQiHtU8hsPxCIq65kAnQYBcHgSUNACABGyqkkEc6pAoT0TQ3LAQVNCDPfZKEEElSUiEXgMcQ5IGfTSZPIcAcJjGNmZAJIUBKNDjlEnXHEDSkYwwTEKMsLyAFGjDjGtQoV0JSQANUONOZCqABBHwpUvzRbSEAe0NCFOGzT+JHeg6rwUIUCIBE1IAGCViIyaqgpATEDD9XkMff0nlOeRayEzRQpUKGQYM9HOQ+g4rkJBEyiC9ADT+wyAQN+NlJZJkJIhPSaUKAhNCqZWEhFxDFHYJG/wOIIoQDCJMYKjLgqTOwFD/2Gyle8VVShQAMRwhRmAr8J9gM9MdhkFMIDGhQgERsTgEL2QMNDnsQFgxBEsSAGTeEmsJEFFKS8kRIFWgAgqbS4KnzjGoifqEwKUjCGtRwAjSyykMXcTVKD7lSWA+KSmYoxAkRu0EV3lEJE6BMlm09AwJ62owCwRIBg/UfGfMqXTbtNSF9VUjI0sYQh3lhIQ/MnAT6tZBrBKwh6QBAMs252ULmgUoLkaSsEuFUhdDzIAj40hsTEVut0haNtnUIbhEi1t0qJAGcs2VxG4IGafiMjEDy63QjfK/qIuS6CYmt9RBCjiKEdJpkI0dKvSekaf84DaMH2YSpUkA1BACASRa0hGbRydkVJYKbM00IOiamBNKa9iD1TUQNFeJO/j7pvw0J8EEGfD3eJuQN7k0IN2X5iKsp5ETvSEQ6KJpHhIihCJuUMJgvROG8QTgRFszCKBCiCH4NzcOneiM3mYFRSRo3EXSlgxOxGt2DuIEGWJwxCt+JSBorQWFGREPTJDtfqNbTew9ISJ+LONsiRwTJiVBy1ZiMkC/QwAoJqYYY2+wwVxipF17c4TmhYaRRwGIDOw4zrOkzZmSWORGAOFsNYCABhEkBfA5TmCtUIIETLRUhD5hYM9QAAifTgFWJUCQs5AEDN4ggZiYENEKcPIxI7Nj/nNzcwBdggAhJ3gDEPKYvahX5hwxEwg2h5VoeBsHJ/iqvq7dVU27HSlGDHmAAkajENWDBNXqUQREmwOodVBCAPdynEwT0RswIMIAh7EJhN401xqkzawuntHD6WUM9PSyCOOXnAKNNSCQmmh9moPogaAitfjKRYXNaIz8qo/FB9jAyUJLz3Iw+iDPcmZ8sSIDEC5w3pb2KbwHrdsnj1c8GStAErNKghQIYn34oIG+EVMOo+bHEzDIu9vuZoBIJ2EN8G3bARJDDDQmoxKvnOA0VPOIBHlsIBzIwgUcEQKEOEYAoBrB1hihBAAOQQB/yWxFuIGIA1Lj7NCbATqpUQw0T/wjAB73xjvS5vBIqEEUGuGepUaghASmI+9hTf0aHVVH1rn89blgP+9nTPjayrz3uc3+a2+u+977vzDkMYe7fE7/4xj8+8pOv/OUzv/nOfz70oy/96VO/+p1xRoyyr/3tc7/73v8++MMv/vGTv/zmPz/606/+9bO//e5/P/zjr/5jWt8zTiAI/vOv//3zv//+/z8ABqAADiABFqABHiACJqACLiADNqADPiAEJqCj1B9n3F8EXiAGZqAGbiAHdqAHfiAIhuACTiAFboYznCAKpqAKriALtqALviAMxqAMziAN1qAN3iAO5qAO7iAP9qAP/iAQBqEQ1mAJFqERHiESJv+hEi4hEzahEz4hFEahFE4hFVahFV4hFmahFm4hF3ahF34hGIahGI4hGZahGZ4hGqahGq4hG7ahG74hHMahHM4hHdahHd4hHubhaygBdoAPQwxAAvTYRYxCAmTWRajHerSHQsCHEemhI4aGIkDTlTFEH+DH4GGEwzjWRTjIJ0VImtTaI4biZpCXBTTE5tyVRmQiRsBIh3xIiIyIpYmiLGKGBdFAzyWEqUBSKtKAJuqPvTHdk8XiLA4jZRjVBCyEBW2AH2aEKm7iL7YOyQgjMU7jY0gOFynERxXUKrlKoPTYtWTLtnRLJl6AGNCDFBTAACiefzHEsnzis0TLtPjhN2r/C7d4C7iIC7mYC7qoC7ssxLvEy7xIETUOpFYoSGkphPecnMG8lc7QQIZVzdVkjcN8gfeQDX6swQeViZEdRNKkCdM4TVVJDSpF5NloDdfQgNdc5JaNTdkkjHatje+0TUYSJE1aBQV0UxbRACzYUuAMjseRR9XkjPZwjwTBgjUwjuOcCkQsz92kCfRITyJQj0OiklBuT/d8j9aMT/kkwvk4pPqwj/vAj/zQDxPVpFlWBcr01wMVDEIoEAM5UDJVDRO9kQRVyUH8An6IHlf9UP8EEQ0MUJpIGkIgkRLJZRMhBBQJJBUdxBVl0RZ10Rd5ixjt2VlWZlM4wcZI00EY1eQZ/5IcJQQd0YDFyCVSRdAoKV7THKMnfVIopQkpJVDTkeYqtZI18dIs1VJD4JIu2aZl9uZShFabeYPvCOQydVQzQZM0yaXfeRhK1aZkoVEwAVQxHRNBGZS+0cByJgRDORRbJYJEUZRFmdhBaBRHGedHdZhvpudRAAkzFIiBKY2SrBRLSQ9ZKYTD1NmjbFTS3RtYMZ2+lZU9oZVadWciuFV+bEBczVVdlaV6NihR9MLNpIgXUWYiANZz9U9/ZJp90gA2IRYN9Oc6Kl2ZYdq+JYRvnU1wDVeCZRFyKRdzWc2FZgCFOiiNhkRNxUKWZYHiZddDaGhCOIw2wqUY7CeALV2Sxf9miSKEgVkAgvGmQixYg12akdYolQ5FJDjNA8XCQmCYQmxYh/mo2sHCTG7CZXVmiN7biCKpph2Ek9nlQUTZN1FZQlgZlmmZQnTZl1WpnnKEqcTMo92S06SZkrAZgf0oflSBkTwQHZCg7TwjQ1gaia5pInCap3FdqJkmqfHJqRmSqiEEq7nanobqRliBT9HfQdzaDeTartFArxWq2kUMAaiAGngJDZjpmRZpmuqbpAJJv/1bwA1cwR0cDSTcwjXcw0XcxFWcTYkqs2KEcDppx6mVn4UcmJqmG2RMftxAntZWpU1ppD7dgUod1Vkd1uWH1n2a18FM2DUru4ZE2Z1d2k3/BDw8AnjYElRU3uVl3ublERp4Hujp5SqRnumhXrsWrMEeLMImrMIuLMM2rMM+LMRGrMROLMVWrMVeLMZmrMZubEMggsd+LMiGrMiOLMmWrMmeLMqmrMquLMu2rMu+LMzGrMzOLM3WrM3eLM7mrM7uLM/2rM/+LNAGrdAOLdG+rDSIINImrdIuLdM2rdM+LdRGrdROLdVWrdUy7TBcrdZuLdd2rdd+LdiGrdiOLdmWrf4NwwWkrdquLdu2rdu+LdzGrdzOLd3Wrd3eLd7mrd7uLd/2rd/+LeAGruAOLuEWruEeLuImruIuLuM2ruM+rt6KJ8dOLuVWruVeLuZmruZu/y7ndq7nfi7ohq7oji7plq7pni7qpq7qri7rtq7rvi7sxq7szi7t1q7t3i7ucsYFWEMJNEMwXEMGbFnu5u4emI1+SIGtfsSSDO/lGhA0UMMgVEMloNcGlCZINCPzUi7XDBJC6NM1hgT2Zu/GDgLZCCTQ1ZFIhK/4ZuwDdJCpJsI1DENQHUSf/Ek3aqcIIEIiPEAB/IE2LMFTNYEI3OQahIp1AUInOAIZVMIx0Yqt4IquNOJBhMAuoAIdbIjw7g43Csr6TiP5dtr7KsTBJMzCIMQF0AABhNcBOILPbIA0ZZl+IAgaDEwHrVQVvFHN3EzO4MckHgQ3nKTOYCTRMGQJd//wMNIqPQxAyDFET3LlT1YSRR3AGTRQE9xkSCnCBdDVNVxAHu0SHTzAJqCBG4iRN5EW7ugO7/jOiCADVnXDjnkDwtwYCFmNTxqOEc8iMtCqTw0DDNirW+bXA5Wid+JHh3LQFahdL4aAJRzA/CYCN+hkC8nXX85QkDFW0x3EOfjMjv0xXAryHctiGYjBGqjVAQCC38XRHKHvCdMAPCQECzgNIqsdmCgEwmzSI6FbPUGTIFrBMNgQKoMm+n7yMCJDANTASWoDRhWncSLnINOA8DoDLJtmL9ZUNxhnJHiJ88QTLifCK8PCQyhzRzGzME/jJrzDxHiaSi2o9JzwDcxRNHv/WC+iV10NqSQLYn3BAw3kUkOkc11B5TjjISJcg3YlRO/clYVeaH+wszsDKDxnEoDE6OjU8zYLpxQ8xEE/lyv9sx02jZsmhMkQw0HwqEMoNGi+M/bGyUb600H+HBqQjeLBAxKAmEhrtCzu0hq8b8YEw0FwaUJ4KRS3c0kzNPaizGKlFAQUQbss2mnV02VJMHzp11T2NIfRNB6GwMbkQXYiwcRA5ZkJ6ucQ6iAD9ceYNE4C3fgw1SvpTaPaM2r9Bz1g0vtEkZkFqpqBNVXbocnQwBUsgRUgwi68DC8mBKqqKq+BD0mPNUPXnAVwAzltwaFKAAy0Fyz8qUT/XCJsglERlMPEiUHM6OJg61ph3zUeUkO65scfWMMxKYLH5QfImXBJBnUFBQ3LJGV+SEEjKrWPoVYiOAG/lFylKslqX+QSi7YdcoAETEACSEMkqKPBmB3aZUQZnEECWK8TUMPmIUEGVwQHbIHkZTTROHe8Erd4jzd5l7d5nzd6p7d6rzd7t7d7vzd8x7d8zzd917d93zd+5zeWBAQAOw==" style="margin-top:1rem;" /></div></details></div></div>
-
-## Wolfram Alpha
-
-::: {.sourceClojure}
-```clojure
-(wl/eval '(WolframAlpha "number of moons of Saturn" "Result"))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-(Quantity 145 (IndependentUnit "moons"))
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(view '(WolframAlpha "number of moons of Saturn" "Result"))
-```
-:::
-
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">WolframAlpha["number of moons of Saturn", "Result"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhxgBTAPeXAPHx8fb185F/a6iaivHv7O/v7/Hv7eLd2KKTgt/a1YVyXMW8scW8ssrBuPf29O7r6OPj4+Hd18rCuYh1X9/a1L+1qYt4Y7Gkluvo5Orn5LOnmaSWhtzX0d3Y0tXOx5iIdol3Yfn5+JKAbeDc1uHh4Z2OfO/s6se+tPv7+p6Offb19KWXh5eHdIFtV7muoqaYiNPMxLerntDIwINwWaudjpaGc5SDb7KmmNTNxYRwWrCklq6hksK4rcnAt4d0XoNvWbqvoqCRgIJuV+Hc187Gvd/f36OUhNnTzI9+adPNxcvDue3q58/Iv6yfkN7e3uXh3Ozs7Id0X4JuWMzEu72zp5GAbOTg26ibi6GSgpuLeZ+Qfsa9s+Db1aWXhuLi4tvb25+Qf/T09IRxW+Xl5ZWFcoBsVfDu68G3rPTz8cjAtubm5unm4vr6+eTk5NvVz9zc3I17ZuLe2ambjKqdjpmJd+rq6u/t6raqne7s6djSy/f39+Xh3aOVhIp3Ytra2tnZ2Y99abCjlfPx7/v7+7qvo7SomuDg4O7u7tbPyIVxW/X19cO6r/r6+vLy8rOnmpeGdPj4+Ih1YNfRyc/Hv/7+/rGll4l2Yf////b29ujo6N3d3ePe2dbQyefn5/z8/Ip4Y6qcjfDw8L60qPPz89DJwc7HvtfRytHKwvr5+PXz8paFcpiHdezp5sS7sMe/tdvWz+fk37uwpMC2q9TOxpyMesvDuo17Z+jk4JWEcfDu7IZzXYt5ZNHKwZOCbrWpnPz8+/39/fv6+sS7sc3FvK6ik6eZiZKBbZOCb/j39pSDcNLLw/39/Ofj3/Py8LmuodrVzpqKePf29Y58Z+bj3uzq5unl4d7Z07Spm6GSgZB/a7arnpmJdu3t7Y58aOvo5enp6d3Y0ejl4Z2NfMi/tdrUzdXPx39rVPTy8K2gkritoIx6Zfn4962gkb2ypoFtVqeZivLw7resn6+ilJB+aubi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3SH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAxgBTAAAI/wAvCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0g3AmtUR82Yp1CjSp1KtarVq1izapWaiRukpBQHffPzp6zZs2jTql3Ltq3bt3DdGgoDFqKiN3Hz6t3Lt6/aTpTqMsRE9o+mUIwCC57oSVEns2MWJ/SE908nYJIxjqp8KLPBOmU7ec6oh+wXT6MFUvpiGHXqi1DKdk4dRvZrjKv/eHnNrezX2xfb/Pny+ltZ18ArPv6DeXSmss2TU3zOPDX16NIlXrcOPfv07s7Be/+PuD189fHkxWcuj/4h+/Xq2zN8L5m+fIX2Hf46daXYNImU3FFMMa8kVMmACCY4YIEL5XffQQ4iBIwVUzQRhTkYuiERFRiao0RCunQooogfNhjfgwhFeNASI2YY0RFldFiiQcDECIcROOaYIznznYiiQSoaBE8XRHZRhYsPLXHhHBjOWBAaGKZjUZA/UplQO0g2hIoq5iSzRpMIsYJhK1P6+CNBViKEpTkaOtSEOVLAAguYB22CIRNlnneJKLHg4YksuNgCSi6XUOLKI7vwUQ1CwQxTjDGfHDOHMsswxIwz0MAhDS3tUJPQFrFYIxAbw2CRzS7bxCKIQvAIY2Qf3WT/kQ44iqVoZkNrtsnQOBimcYmdHiL0TJYTsZeIOeW82eEqlBQioiXnGESOOi2aU8UmCa3DTowjunMHcgT1Yk48v87TYiT0IJSGGNVaS0StBaV5UK4NDSGEOegINASdBp2C4X8VGWuOOObQQkgyGGpjThBAmGuOKAVNwi00Z9QiCpfm/PDMQcg8gqEPlfTgyg45YIgNuAKJ2wQO99bgCxU0zIChMShfIgOGusQAAzh5jPNCC+a4s4etekpE70LwUMsCG/ryW1AaGHrDyw1drBBIGna4J96x5lwRmArsmhODQNTEmAJBe0hhjhC8EETJCTH6YIJBcmAIRjMEmeCx2AaJ/2uJO32YQhArn2CYh0HZwOmNkDoskpC8Bh09WQnmRDJ308EeJAuGP7RYxg4qNCSwD2gMFIQ52aAwUOLzEHS6OVMcJAqGxBQ0AoYihGBQMyCY04Kn4c5MaEGuYEguQchg+EGxtzIkOUIKl8EBQftmbtDs5nxSiStT8LABt6qEbqKexxpBECjmaEAQNObsMlAGGJKB0C+FuyO+QEya4wFCJ0RZkLhSwJtBxGSODRQEGCESAwa007yFPM8gysCQ46jnNLeNoxa/KEg1xGWOC/SIfOYw30BokD6CZMEcFhjIFjDEg4RcA0MwGAglLiSGSh3kHBjqxf/MkQhGYagEBlkhD/+dsTitFS0iDyRIONglB4NUz0kOMcOx3JGK8UWnfAQhofoGcsIUCuQGxCpIKTBUgYHAA0NZUEg3zFEGeImrhwhB40G20DkM4SIWFKgZkBqokCQKJBpHmoAbhkDIQkoAQy4g5C0g4ggMJcGKA8HiCEvIRRQO5AoYekJC8oAhXwwkHBjqgkI+gKEqDuSNCZHjQR5QCEuIyAc6SNfj+HilMA6kAe1qVxofQgQMMQCSApGkQLRoQksKhB0YikBCZoHIgbDIHFhQCMLMobtT8jCV5tilhLhACBaIaA7RIBp2kGhLgfQgl9XSZkNIgaEFAPMSwrwEMSvpxUs4A0OnSIgwfDn/kORZKyEINIcCdgjHg6iSISYQhQ9+CK+BQK4gfizUMiZK0YomAEMNmOg4F0IIGL4znvMUSBcHIgkMBSIhCMCQFQiyt6wd5AAYMmDwCmqQgzYkF4BIJoRoqaZyMuSJB0GFAbJFrRaYcpYgFOEwKSlSY15iHQkkwEGYESMkwGtz5rgDQgaAoVIQFJvqbMgZMNS2PR4RIhFdCFANIo9dgOMgKHgH7T54xRBmkamXGOlAsFqCag4kFdP0KkGiMQE2csIguDSHAGxoTZoWxKaXwAMdRIWQupkjDjs9a0KsIInOdhZ9D/OsJI7gkLXmjWsv8IApHaAMG2AIEKX7qF0nucWm/9bzEr+gBYaSkYcMsgEGSMDQOxp6CVPEqAXOuBwGbhCjH2Drq3HMZkEItjAPBIAg57gDhrZB3EvIy7LovGa9KiiQW3izQz+IArfMgYsHiG5rs11qbfPqVIGkQgsdcscE1nsFvxaEFDLDkALCZo4obKxv4jWodAmyhpRiqAzSYEEWBMCtbLg3sxtNCHjR6diEmLYglFAGFoAmImm0QnXvTepd56tXgixDCYkTERmU0d2BeIMGauuQGG4wPAR3eCCQFcg0KkGtEcFBFOtAaoZp4gBr8GIYHshAejRrEQwgggiSwMNDQtABUpyCCygOiTfcQIpSSMIbNXYoT4nyUPS0Gdkob/ZOnH0yZ+nUmSd3Bk6edbLn1/QZJ382z5LBApo/DOJMClFDWdKclEOURRGITggJDPMaSJTlG5E+yCDKoobbOKEsesh0QYTzh0bcBgBlKcKgH1SAshgiORAoiyYgHWlPLMcPmEiOJ4pgFghwAwCNCLawh03sYhv72MhOtrKXzWxih+IblflDKLIDDEX75drYzjZf3kCX8WBiDIXRtrjHne0icGPVtwGGHsLQ7Ha7+93wbvcoMMEIUdv73vjOt773ze9++/vfAA+4wAdO8IIb/OAIT7jCAx4QADs=" style="margin-top:1rem;" /></div></details></div></div>
+# Preface
+[Noj](https://scicloj.github.io/noj/) (short for Scinojure)
+is an opinionated way to use the emerging Clojure data stack.
+It collects a few of the relevant libraries together
+and addes some layers of composition on top of them.
 
@@
 
-<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/math/wolframite/notebooks/index.clj">projects/math/wolframite/notebooks/index.clj</a></small></small></pre></div>
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/index.clj">projects/noj/notebooks/index.clj</a></small></small></pre></div>

### 2024-01-28 docs/projects/noj/ml.qmd
Noj - rerendered book

@@
        Min          1Q      Median          3Q         Max
-   -0.8363     -0.2220      0.0278      0.2168      0.6757
+   -0.7943     -0.2312      0.0256      0.2059      0.8735
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.8228     0.2974     6.1291     0.0000 ***
-sepal-width         0.6696     0.0822     8.1451     0.0000 ***
-petal-length        0.7126     0.0684    10.4175     0.0000 ***
-petal-width        -0.5688     0.1563    -3.6381     0.0004 ***
+Intercept           1.7726     0.3098     5.7220     0.0000 ***
+sepal-width         0.6807     0.0824     8.2622     0.0000 ***
+petal-length        0.7112     0.0700    10.1639     0.0000 ***
+petal-width        -0.5768     0.1582    -3.6467     0.0004 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3192 on 96 degrees of freedom
-Multiple R-squared: 0.8711,    Adjusted R-squared: 0.8671
-F-statistic: 216.3502 on 4 and 96 DF,  p-value: 1.417e-42
+Residual standard error: 0.3230 on 96 degrees of freedom
+Multiple R-squared: 0.8500,    Adjusted R-squared: 0.8453
+F-statistic: 181.3338 on 4 and 96 DF,  p-value: 2.062e-39
 

### 2024-02-01 docs/projects/noj/ggplot.qmd
noj - rerendered book

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: ggplot.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ggplot_files/md-default0.js" type="text/javascript"></script><script src="ggplot_files/md-default1.js" type="text/javascript"></script>
<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>

# Exploring ggplot

::: {.sourceClojure}
```clojure
(ns ggplot
  (:require [clojisr.v1.r :as r :refer [r]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]))
```
:::

::: {.sourceClojure}
```clojure
(r/library "ggplot2")
```
:::

::: {.printedClojure}
```clojure
[1] "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices" "utils"    
[7] "datasets"  "methods"   "base"

```
:::

::: {.sourceClojure}
```clojure
(def plot
  (r "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point()
         + stat_smooth(method=\"lm\")
         + facet_wrap(~cyl))"))
```
:::

::: {.sourceClojure}
```clojure
(-> plot
    plotting/plot->svg
    kind/html)
```
:::

<?xml version="1.0" encoding="UTF-8"?>
<svg xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink" width="504pt" height="504pt" viewBox="0 0 504 504" version="1.1">
<defs>
<g>
<symbol overflow="visible" id="glyph0-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph0-1">
<path style="stroke:none;" d="M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-2">
<path style="stroke:none;" d="M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 "/>
</symbol>
<symbol overflow="visible" id="glyph0-3">
<path style="stroke:none;" d="M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-4">
<path style="stroke:none;" d="M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-5">
<path style="stroke:none;" d="M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 "/>
</symbol>
<symbol overflow="visible" id="glyph0-6">
<path style="stroke:none;" d="M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 "/>
</symbol>
<symbol overflow="visible" id="glyph0-7">
<path style="stroke:none;" d="M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph0-8">
<path style="stroke:none;" d="M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 "/>
</symbol>
<symbol overflow="visible" id="glyph1-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph1-1">
<path style="stroke:none;" d="M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-2">
<path style="stroke:none;" d="M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-3">
<path style="stroke:none;" d="M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-4">
<path style="stroke:none;" d="M 2.84375 -5.765625 L 1.875 -5.765625 L 1.875 -6.671875 C 1.875 -7.046875 2.09375 -7.25 2.515625 -7.25 C 2.59375 -7.25 2.625 -7.25 2.84375 -7.234375 L 2.84375 -8 C 2.625 -8.046875 2.515625 -8.046875 2.328125 -8.046875 C 1.46875 -8.046875 0.96875 -7.5625 0.96875 -6.75 L 0.96875 -5.765625 L 0.203125 -5.765625 L 0.203125 -5.015625 L 0.96875 -5.015625 L 0.96875 0 L 1.875 0 L 1.875 -5.015625 L 2.84375 -5.015625 Z M 2.84375 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-5">
<path style="stroke:none;" d="M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-6">
<path style="stroke:none;" d="M 2.984375 -5.921875 C 1.359375 -5.921875 0.390625 -4.78125 0.390625 -2.84375 C 0.390625 -0.890625 1.359375 0.25 3 0.25 C 4.625 0.25 5.609375 -0.90625 5.609375 -2.796875 C 5.609375 -4.796875 4.65625 -5.921875 2.984375 -5.921875 Z M 3 -5.078125 C 4.03125 -5.078125 4.65625 -4.234375 4.65625 -2.8125 C 4.65625 -1.4375 4.015625 -0.59375 3 -0.59375 C 1.984375 -0.59375 1.359375 -1.4375 1.359375 -2.84375 C 1.359375 -4.234375 1.984375 -5.078125 3 -5.078125 Z M 3 -5.078125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-7">
<path style="stroke:none;" d="M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-8">
<path style="stroke:none;" d="M 2.59375 -8.015625 C 1.5 -6.578125 0.796875 -4.578125 0.796875 -2.84375 C 0.796875 -1.109375 1.5 0.890625 2.59375 2.328125 L 3.203125 2.328125 C 2.234375 0.765625 1.6875 -1.09375 1.6875 -2.84375 C 1.6875 -4.59375 2.234375 -6.453125 3.203125 -8.015625 Z M 2.59375 -8.015625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-9">
<path style="stroke:none;" d="M 1.671875 -8.015625 L 0.75 -8.015625 L 0.75 0 L 1.671875 0 Z M 1.671875 -8.015625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-10">
<path style="stroke:none;" d="M 1.015625 2.328125 C 2.125 0.890625 2.8125 -1.109375 2.8125 -2.84375 C 2.8125 -4.578125 2.125 -6.578125 1.015625 -8.015625 L 0.421875 -8.015625 C 1.390625 -6.453125 1.921875 -4.59375 1.921875 -2.84375 C 1.921875 -1.09375 1.390625 0.765625 0.421875 2.328125 Z M 1.015625 2.328125 "/>
</symbol>
<symbol overflow="visible" id="glyph2-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph2-1">
<path style="stroke:none;" d="M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph2-2">
<path style="stroke:none;" d="M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 "/>
</symbol>
<symbol overflow="visible" id="glyph2-3">
<path style="stroke:none;" d="M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 "/>
</symbol>
</g>
<clipPath id="clip1">
  <path d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 234.925781 L 35.152344 234.925781 Z M 35.152344 23.246094 "/>
</clipPath>
<clipPath id="clip2">
  <path d="M 35.152344 203 L 229.136719 203 L 229.136719 205 L 35.152344 205 Z M 35.152344 203 "/>
</clipPath>
<clipPath id="clip3">
  <path d="M 35.152344 150 L 229.136719 150 L 229.136719 152 L 35.152344 152 Z M 35.152344 150 "/>
</clipPath>
<clipPath id="clip4">
  <path d="M 35.152344 97 L 229.136719 97 L 229.136719 98 L 35.152344 98 Z M 35.152344 97 "/>
</clipPath>
<clipPath id="clip5">
  <path d="M 35.152344 44 L 229.136719 44 L 229.136719 45 L 35.152344 45 Z M 35.152344 44 "/>
</clipPath>
<clipPath id="clip6">
  <path d="M 67 23.246094 L 68 23.246094 L 68 234.925781 L 67 234.925781 Z M 67 23.246094 "/>
</clipPath>
<clipPath id="clip7">
  <path d="M 101 23.246094 L 102 23.246094 L 102 234.925781 L 101 234.925781 Z M 101 23.246094 "/>
</clipPath>
<clipPath id="clip8">
  <path d="M 135 23.246094 L 136 23.246094 L 136 234.925781 L 135 234.925781 Z M 135 23.246094 "/>
</clipPath>
<clipPath id="clip9">
  <path d="M 169 23.246094 L 170 23.246094 L 170 234.925781 L 169 234.925781 Z M 169 23.246094 "/>
</clipPath>
<clipPath id="clip10">
  <path d="M 203 23.246094 L 204 23.246094 L 204 234.925781 L 203 234.925781 Z M 203 23.246094 "/>
</clipPath>
<clipPath id="clip11">
  <path d="M 35.152344 230 L 229.136719 230 L 229.136719 232 L 35.152344 232 Z M 35.152344 230 "/>
</clipPath>
<clipPath id="clip12">
  <path d="M 35.152344 177 L 229.136719 177 L 229.136719 179 L 35.152344 179 Z M 35.152344 177 "/>
</clipPath>
<clipPath id="clip13">
  <path d="M 35.152344 123 L 229.136719 123 L 229.136719 125 L 35.152344 125 Z M 35.152344 123 "/>
</clipPath>
<clipPath id="clip14">
  <path d="M 35.152344 70 L 229.136719 70 L 229.136719 72 L 35.152344 72 Z M 35.152344 70 "/>
</clipPath>
<clipPath id="clip15">
  <path d="M 50 23.246094 L 52 23.246094 L 52 234.925781 L 50 234.925781 Z M 50 23.246094 "/>
</clipPath>
<clipPath id="clip16">
  <path d="M 84 23.246094 L 86 23.246094 L 86 234.925781 L 84 234.925781 Z M 84 23.246094 "/>
</clipPath>
<clipPath id="clip17">
  <path d="M 118 23.246094 L 120 23.246094 L 120 234.925781 L 118 234.925781 Z M 118 23.246094 "/>
</clipPath>
<clipPath id="clip18">
  <path d="M 151 23.246094 L 154 23.246094 L 154 234.925781 L 151 234.925781 Z M 151 23.246094 "/>
</clipPath>
<clipPath id="clip19">
  <path d="M 185 23.246094 L 187 23.246094 L 187 234.925781 L 185 234.925781 Z M 185 23.246094 "/>
</clipPath>
<clipPath id="clip20">
  <path d="M 219 23.246094 L 221 23.246094 L 221 234.925781 L 219 234.925781 Z M 219 23.246094 "/>
</clipPath>
<clipPath id="clip21">
  <path d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 469.851562 L 35.152344 469.851562 Z M 35.152344 258.171875 "/>
</clipPath>
<clipPath id="clip22">
  <path d="M 35.152344 438 L 229.136719 438 L 229.136719 440 L 35.152344 440 Z M 35.152344 438 "/>
</clipPath>
<clipPath id="clip23">
  <path d="M 35.152344 385 L 229.136719 385 L 229.136719 387 L 35.152344 387 Z M 35.152344 385 "/>
</clipPath>
<clipPath id="clip24">
  <path d="M 35.152344 332 L 229.136719 332 L 229.136719 333 L 35.152344 333 Z M 35.152344 332 "/>
</clipPath>
<clipPath id="clip25">
  <path d="M 35.152344 278 L 229.136719 278 L 229.136719 280 L 35.152344 280 Z M 35.152344 278 "/>
</clipPath>
<clipPath id="clip26">
  <path d="M 67 258.171875 L 68 258.171875 L 68 469.851562 L 67 469.851562 Z M 67 258.171875 "/>
</clipPath>
<clipPath id="clip27">
  <path d="M 101 258.171875 L 102 258.171875 L 102 469.851562 L 101 469.851562 Z M 101 258.171875 "/>
</clipPath>
<clipPath id="clip28">
  <path d="M 135 258.171875 L 136 258.171875 L 136 469.851562 L 135 469.851562 Z M 135 258.171875 "/>
</clipPath>
<clipPath id="clip29">
  <path d="M 169 258.171875 L 170 258.171875 L 170 469.851562 L 169 469.851562 Z M 169 258.171875 "/>
</clipPath>
<clipPath id="clip30">
  <path d="M 203 258.171875 L 204 258.171875 L 204 469.851562 L 203 469.851562 Z M 203 258.171875 "/>
</clipPath>
<clipPath id="clip31">
  <path d="M 35.152344 465 L 229.136719 465 L 229.136719 467 L 35.152344 467 Z M 35.152344 465 "/>
</clipPath>
<clipPath id="clip32">
  <path d="M 35.152344 411 L 229.136719 411 L 229.136719 414 L 35.152344 414 Z M 35.152344 411 "/>
</clipPath>
<clipPath id="clip33">
  <path d="M 35.152344 358 L 229.136719 358 L 229.136719 360 L 35.152344 360 Z M 35.152344 358 "/>
</clipPath>
<clipPath id="clip34">
  <path d="M 35.152344 305 L 229.136719 305 L 229.136719 307 L 35.152344 307 Z M 35.152344 305 "/>
</clipPath>
<clipPath id="clip35">
  <path d="M 50 258.171875 L 52 258.171875 L 52 469.851562 L 50 469.851562 Z M 50 258.171875 "/>
</clipPath>
<clipPath id="clip36">
  <path d="M 84 258.171875 L 86 258.171875 L 86 469.851562 L 84 469.851562 Z M 84 258.171875 "/>
</clipPath>
<clipPath id="clip37">
  <path d="M 118 258.171875 L 120 258.171875 L 120 469.851562 L 118 469.851562 Z M 118 258.171875 "/>
</clipPath>
<clipPath id="clip38">
  <path d="M 151 258.171875 L 154 258.171875 L 154 469.851562 L 151 469.851562 Z M 151 258.171875 "/>
</clipPath>
<clipPath id="clip39">
  <path d="M 185 258.171875 L 187 258.171875 L 187 469.851562 L 185 469.851562 Z M 185 258.171875 "/>
</clipPath>
<clipPath id="clip40">
  <path d="M 219 258.171875 L 221 258.171875 L 221 469.851562 L 219 469.851562 Z M 219 258.171875 "/>
</clipPath>
<clipPath id="clip41">
  <path d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 234.925781 L 234.617188 234.925781 Z M 234.617188 23.246094 "/>
</clipPath>
<clipPath id="clip42">
  <path d="M 234.617188 203 L 428.601562 203 L 428.601562 205 L 234.617188 205 Z M 234.617188 203 "/>
</clipPath>
<clipPath id="clip43">
  <path d="M 234.617188 150 L 428.601562 150 L 428.601562 152 L 234.617188 152 Z M 234.617188 150 "/>
</clipPath>
<clipPath id="clip44">
  <path d="M 234.617188 97 L 428.601562 97 L 428.601562 98 L 234.617188 98 Z M 234.617188 97 "/>
</clipPath>
<clipPath id="clip45">
  <path d="M 234.617188 44 L 428.601562 44 L 428.601562 45 L 234.617188 45 Z M 234.617188 44 "/>
</clipPath>
<clipPath id="clip46">
  <path d="M 266 23.246094 L 268 23.246094 L 268 234.925781 L 266 234.925781 Z M 266 23.246094 "/>
</clipPath>
<clipPath id="clip47">
  <path d="M 300 23.246094 L 302 23.246094 L 302 234.925781 L 300 234.925781 Z M 300 23.246094 "/>
</clipPath>
<clipPath id="clip48">
  <path d="M 334 23.246094 L 336 23.246094 L 336 234.925781 L 334 234.925781 Z M 334 23.246094 "/>
</clipPath>
<clipPath id="clip49">
  <path d="M 368 23.246094 L 370 23.246094 L 370 234.925781 L 368 234.925781 Z M 368 23.246094 "/>
</clipPath>
<clipPath id="clip50">
  <path d="M 402 23.246094 L 404 23.246094 L 404 234.925781 L 402 234.925781 Z M 402 23.246094 "/>
</clipPath>
<clipPath id="clip51">
  <path d="M 234.617188 230 L 428.601562 230 L 428.601562 232 L 234.617188 232 Z M 234.617188 230 "/>
</clipPath>
<clipPath id="clip52">
  <path d="M 234.617188 177 L 428.601562 177 L 428.601562 179 L 234.617188 179 Z M 234.617188 177 "/>
</clipPath>
<clipPath id="clip53">
  <path d="M 234.617188 123 L 428.601562 123 L 428.601562 125 L 234.617188 125 Z M 234.617188 123 "/>
</clipPath>
<clipPath id="clip54">
  <path d="M 234.617188 70 L 428.601562 70 L 428.601562 72 L 234.617188 72 Z M 234.617188 70 "/>
</clipPath>
<clipPath id="clip55">
  <path d="M 249 23.246094 L 251 23.246094 L 251 234.925781 L 249 234.925781 Z M 249 23.246094 "/>
</clipPath>
<clipPath id="clip56">
  <path d="M 283 23.246094 L 285 23.246094 L 285 234.925781 L 283 234.925781 Z M 283 23.246094 "/>
</clipPath>
<clipPath id="clip57">
  <path d="M 317 23.246094 L 319 23.246094 L 319 234.925781 L 317 234.925781 Z M 317 23.246094 "/>
</clipPath>
<clipPath id="clip58">
  <path d="M 351 23.246094 L 353 23.246094 L 353 234.925781 L 351 234.925781 Z M 351 23.246094 "/>
</clipPath>
<clipPath id="clip59">
  <path d="M 385 23.246094 L 387 23.246094 L 387 234.925781 L 385 234.925781 Z M 385 23.246094 "/>
</clipPath>
<clipPath id="clip60">
  <path d="M 419 23.246094 L 421 23.246094 L 421 234.925781 L 419 234.925781 Z M 419 23.246094 "/>
</clipPath>
<clipPath id="clip61">
  <path d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 469.851562 L 234.617188 469.851562 Z M 234.617188 258.171875 "/>
</clipPath>
<clipPath id="clip62">
  <path d="M 234.617188 438 L 428.601562 438 L 428.601562 440 L 234.617188 440 Z M 234.617188 438 "/>
</clipPath>
<clipPath id="clip63">
  <path d="M 234.617188 385 L 428.601562 385 L 428.601562 387 L 234.617188 387 Z M 234.617188 385 "/>
</clipPath>
<clipPath id="clip64">
  <path d="M 234.617188 332 L 428.601562 332 L 428.601562 333 L 234.617188 333 Z M 234.617188 332 "/>
</clipPath>
<clipPath id="clip65">
  <path d="M 234.617188 278 L 428.601562 278 L 428.601562 280 L 234.617188 280 Z M 234.617188 278 "/>
</clipPath>
<clipPath id="clip66">
  <path d="M 266 258.171875 L 268 258.171875 L 268 469.851562 L 266 469.851562 Z M 266 258.171875 "/>
</clipPath>
<clipPath id="clip67">
  <path d="M 300 258.171875 L 302 258.171875 L 302 469.851562 L 300 469.851562 Z M 300 258.171875 "/>
</clipPath>
<clipPath id="clip68">
  <path d="M 334 258.171875 L 336 258.171875 L 336 469.851562 L 334 469.851562 Z M 334 258.171875 "/>
</clipPath>
<clipPath id="clip69">
  <path d="M 368 258.171875 L 370 258.171875 L 370 469.851562 L 368 469.851562 Z M 368 258.171875 "/>
</clipPath>
<clipPath id="clip70">
  <path d="M 402 258.171875 L 404 258.171875 L 404 469.851562 L 402 469.851562 Z M 402 258.171875 "/>
</clipPath>
<clipPath id="clip71">
  <path d="M 234.617188 465 L 428.601562 465 L 428.601562 467 L 234.617188 467 Z M 234.617188 465 "/>
</clipPath>
<clipPath id="clip72">
  <path d="M 234.617188 411 L 428.601562 411 L 428.601562 414 L 234.617188 414 Z M 234.617188 411 "/>
</clipPath>
<clipPath id="clip73">
  <path d="M 234.617188 358 L 428.601562 358 L 428.601562 360 L 234.617188 360 Z M 234.617188 358 "/>
</clipPath>
<clipPath id="clip74">
  <path d="M 234.617188 305 L 428.601562 305 L 428.601562 307 L 234.617188 307 Z M 234.617188 305 "/>
</clipPath>
<clipPath id="clip75">
  <path d="M 249 258.171875 L 251 258.171875 L 251 469.851562 L 249 469.851562 Z M 249 258.171875 "/>
</clipPath>
<clipPath id="clip76">
  <path d="M 283 258.171875 L 285 258.171875 L 285 469.851562 L 283 469.851562 Z M 283 258.171875 "/>
</clipPath>
<clipPath id="clip77">
  <path d="M 317 258.171875 L 319 258.171875 L 319 469.851562 L 317 469.851562 Z M 317 258.171875 "/>
</clipPath>
<clipPath id="clip78">
  <path d="M 351 258.171875 L 353 258.171875 L 353 469.851562 L 351 469.851562 Z M 351 258.171875 "/>
</clipPath>
<clipPath id="clip79">
  <path d="M 385 258.171875 L 387 258.171875 L 387 469.851562 L 385 469.851562 Z M 385 258.171875 "/>
</clipPath>
<clipPath id="clip80">
  <path d="M 419 258.171875 L 421 258.171875 L 421 469.851562 L 419 469.851562 Z M 419 258.171875 "/>
</clipPath>
<clipPath id="clip81">
  <path d="M 35.152344 240.402344 L 229.136719 240.402344 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 240.402344 "/>
</clipPath>
<clipPath id="clip82">
  <path d="M 234.617188 240.402344 L 428.601562 240.402344 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 240.402344 "/>
</clipPath>
<clipPath id="clip83">
  <path d="M 35.152344 5.480469 L 229.136719 5.480469 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 5.480469 "/>
</clipPath>
<clipPath id="clip84">
  <path d="M 234.617188 5.480469 L 428.601562 5.480469 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 5.480469 "/>
</clipPath>
</defs>
<g id="surface36">
<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 "/>
<g clip-path="url(#clip1)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 234.925781 L 229.136719 234.925781 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 234.925781 "/>
</g>
<g clip-path="url(#clip2)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 204.210938 L 229.136719 204.210938 "/>
</g>
<g clip-path="url(#clip3)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 150.910156 L 229.136719 150.910156 "/>
</g>
<g clip-path="url(#clip4)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 97.613281 L 229.136719 97.613281 "/>
</g>
<g clip-path="url(#clip5)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 44.3125 L 229.136719 44.3125 "/>
</g>
<g clip-path="url(#clip6)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 234.925781 L 67.707031 23.246094 "/>
</g>
<g clip-path="url(#clip7)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 234.925781 L 101.621094 23.246094 "/>
</g>
<g clip-path="url(#clip8)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 234.925781 L 135.535156 23.246094 "/>
</g>
<g clip-path="url(#clip9)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 234.925781 L 169.449219 23.246094 "/>
</g>
<g clip-path="url(#clip10)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 234.925781 L 203.363281 23.246094 "/>
</g>
<g clip-path="url(#clip11)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 230.859375 L 229.136719 230.859375 "/>
</g>
<g clip-path="url(#clip12)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 177.558594 L 229.136719 177.558594 "/>
</g>
<g clip-path="url(#clip13)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 124.261719 L 229.136719 124.261719 "/>
</g>
<g clip-path="url(#clip14)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 70.960938 L 229.136719 70.960938 "/>
</g>
<g clip-path="url(#clip15)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 234.925781 L 50.75 23.246094 "/>
</g>
<g clip-path="url(#clip16)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 234.925781 L 84.664062 23.246094 "/>
</g>
<g clip-path="url(#clip17)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 234.925781 L 118.578125 23.246094 "/>
</g>
<g clip-path="url(#clip18)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 234.925781 L 152.492188 23.246094 "/>
</g>
<g clip-path="url(#clip19)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 234.925781 L 186.40625 23.246094 "/>
</g>
<g clip-path="url(#clip20)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 234.925781 L 220.320312 23.246094 "/>
</g>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 118.933594 C 120.53125 121.539062 116.625 121.539062 116.625 118.933594 C 116.625 116.324219 120.53125 116.324219 120.53125 118.933594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 150.910156 C 93.402344 153.515625 89.492188 153.515625 89.492188 150.910156 C 89.492188 148.304688 93.402344 148.304688 93.402344 150.910156 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 124.261719 C 134.097656 126.867188 130.1875 126.867188 130.1875 124.261719 C 130.1875 121.65625 134.097656 121.65625 134.097656 124.261719 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 108.273438 C 174.796875 110.878906 170.886719 110.878906 170.886719 108.273438 C 170.886719 105.664062 174.796875 105.664062 174.796875 108.273438 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 113.601562 C 154.445312 116.207031 150.539062 116.207031 150.539062 113.601562 C 150.539062 110.996094 154.445312 110.996094 154.445312 113.601562 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 129.589844 C 140.882812 132.199219 136.972656 132.199219 136.972656 129.589844 C 136.972656 126.984375 140.882812 126.984375 140.882812 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 102.941406 C 161.230469 105.546875 157.320312 105.546875 157.320312 102.941406 C 157.320312 100.335938 161.230469 100.335938 161.230469 102.941406 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 92.28125 C 154.445312 94.890625 150.539062 94.890625 150.539062 92.28125 C 150.539062 89.675781 154.445312 89.675781 154.445312 92.28125 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 92.28125 C 147.664062 94.890625 143.753906 94.890625 143.753906 92.28125 C 143.753906 89.675781 147.664062 89.675781 147.664062 92.28125 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 140.25 C 106.96875 142.859375 103.058594 142.859375 103.058594 140.25 C 103.058594 137.644531 106.96875 137.644531 106.96875 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 129.589844 C 113.75 132.199219 109.839844 132.199219 109.839844 129.589844 C 109.839844 126.984375 113.75 126.984375 113.75 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 118.933594 C 140.882812 121.539062 136.972656 121.539062 136.972656 118.933594 C 136.972656 116.324219 140.882812 116.324219 140.882812 118.933594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 113.601562 C 140.882812 116.207031 136.972656 116.207031 136.972656 113.601562 C 136.972656 110.996094 140.882812 110.996094 140.882812 113.601562 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 150.910156 C 106.96875 153.515625 103.058594 153.515625 103.058594 150.910156 C 103.058594 148.304688 106.96875 148.304688 106.96875 150.910156 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 145.582031 C 120.53125 148.1875 116.625 148.1875 116.625 145.582031 C 116.625 142.976562 120.53125 142.976562 120.53125 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 161.570312 C 106.96875 164.175781 103.058594 164.175781 103.058594 161.570312 C 103.058594 158.964844 106.96875 158.964844 106.96875 161.570312 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 145.582031 C 127.316406 148.1875 123.40625 148.1875 123.40625 145.582031 C 123.40625 142.976562 127.316406 142.976562 127.316406 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 150.910156 C 120.53125 153.515625 116.625 153.515625 116.625 150.910156 C 116.625 148.304688 120.53125 148.304688 120.53125 150.910156 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 118.933594 C 134.097656 121.539062 130.1875 121.539062 130.1875 118.933594 C 130.1875 116.324219 134.097656 116.324219 134.097656 118.933594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 124.261719 C 147.664062 126.867188 143.753906 126.867188 143.753906 124.261719 C 143.753906 121.65625 147.664062 121.65625 147.664062 124.261719 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 108.273438 C 147.664062 110.878906 143.753906 110.878906 143.753906 108.273438 C 143.753906 105.664062 147.664062 105.664062 147.664062 108.273438 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 86.953125 C 174.796875 89.558594 170.886719 89.558594 170.886719 86.953125 C 170.886719 84.347656 174.796875 84.347656 174.796875 86.953125 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 166.902344 C 100.183594 169.507812 96.273438 169.507812 96.273438 166.902344 C 96.273438 164.292969 100.183594 164.292969 100.183594 166.902344 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 208.707031 49.644531 C 208.707031 52.25 204.800781 52.25 204.800781 49.644531 C 204.800781 47.035156 208.707031 47.035156 208.707031 49.644531 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 222.273438 49.644531 C 222.273438 52.25 218.363281 52.25 218.363281 49.644531 C 218.363281 47.035156 222.273438 47.035156 222.273438 49.644531 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 181.578125 65.632812 C 181.578125 68.238281 177.667969 68.238281 177.667969 65.632812 C 177.667969 63.027344 181.578125 63.027344 181.578125 65.632812 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 134.921875 C 113.75 137.527344 109.839844 137.527344 109.839844 134.921875 C 109.839844 132.316406 113.75 132.316406 113.75 134.921875 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 84.664062 165.398438 L 86.382812 163.894531 L 88.097656 162.386719 L 91.535156 159.371094 L 93.25 157.859375 L 94.96875 156.347656 L 96.683594 154.832031 L 98.402344 153.3125 L 100.117188 151.792969 L 103.554688 148.738281 L 105.269531 147.207031 L 106.988281 145.671875 L 108.703125 144.128906 L 110.421875 142.582031 L 112.140625 141.027344 L 113.855469 139.46875 L 115.574219 137.902344 L 117.289062 136.328125 L 119.007812 134.742188 L 120.726562 133.148438 L 122.441406 131.546875 L 124.160156 129.933594 L 125.875 128.3125 L 127.59375 126.679688 L 129.308594 125.035156 L 131.027344 123.382812 L 132.746094 121.71875 L 134.460938 120.050781 L 136.179688 118.371094 L 137.894531 116.683594 L 139.613281 114.988281 L 141.332031 113.289062 L 143.046875 111.582031 L 144.765625 109.871094 L 146.480469 108.152344 L 148.199219 106.433594 L 149.917969 104.710938 L 151.632812 102.980469 L 153.351562 101.25 L 155.066406 99.515625 L 156.785156 97.78125 L 158.503906 96.042969 L 160.21875 94.300781 L 161.9375 92.558594 L 163.652344 90.816406 L 165.371094 89.070312 L 167.085938 87.324219 L 168.804688 85.578125 L 170.523438 83.828125 L 172.238281 82.078125 L 173.957031 80.328125 L 175.671875 78.574219 L 177.390625 76.824219 L 179.109375 75.070312 L 180.824219 73.316406 L 182.542969 71.5625 L 184.257812 69.804688 L 185.976562 68.050781 L 187.695312 66.292969 L 189.410156 64.539062 L 191.128906 62.78125 L 192.84375 61.023438 L 196.28125 57.507812 L 197.996094 55.75 L 199.714844 53.992188 L 201.429688 52.230469 L 203.148438 50.472656 L 204.863281 48.710938 L 206.582031 46.953125 L 208.300781 45.191406 L 210.015625 43.433594 L 211.734375 41.671875 L 213.449219 39.914062 L 216.886719 36.390625 L 218.601562 34.628906 L 220.320312 32.867188 L 220.320312 48.824219 L 218.601562 50.3125 L 216.886719 51.800781 L 215.167969 53.289062 L 213.449219 54.78125 L 211.734375 56.269531 L 210.015625 57.761719 L 208.300781 59.25 L 204.863281 62.234375 L 203.148438 63.722656 L 201.429688 65.214844 L 199.714844 66.707031 L 197.996094 68.199219 L 196.28125 69.691406 L 192.84375 72.675781 L 191.128906 74.167969 L 189.410156 75.664062 L 187.695312 77.15625 L 184.257812 80.148438 L 182.542969 81.640625 L 180.824219 83.136719 L 179.109375 84.636719 L 175.671875 87.628906 L 173.957031 89.128906 L 172.238281 90.628906 L 170.523438 92.128906 L 168.804688 93.632812 L 167.085938 95.132812 L 165.371094 96.636719 L 163.652344 98.144531 L 161.9375 99.648438 L 160.21875 101.160156 L 158.503906 102.667969 L 156.785156 104.179688 L 155.066406 105.695312 L 153.351562 107.210938 L 151.632812 108.730469 L 149.917969 110.253906 L 148.199219 111.78125 L 146.480469 113.3125 L 144.765625 114.84375 L 143.046875 116.382812 L 141.332031 117.929688 L 139.613281 119.476562 L 137.894531 121.035156 L 136.179688 122.597656 L 134.460938 124.167969 L 132.746094 125.75 L 131.027344 127.335938 L 129.308594 128.933594 L 127.59375 130.542969 L 125.875 132.160156 L 124.160156 133.789062 L 122.441406 135.425781 L 120.726562 137.074219 L 119.007812 138.730469 L 117.289062 140.398438 L 115.574219 142.074219 L 113.855469 143.757812 L 112.140625 145.449219 L 110.421875 147.144531 L 108.703125 148.847656 L 106.988281 150.558594 L 105.269531 152.273438 L 103.554688 153.988281 L 101.835938 155.710938 L 100.117188 157.4375 L 98.402344 159.167969 L 96.683594 160.902344 L 94.96875 162.636719 L 93.25 164.371094 L 91.535156 166.113281 L 89.816406 167.851562 L 88.097656 169.597656 L 86.382812 171.339844 L 84.664062 173.085938 Z M 84.664062 165.398438 "/>
<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 169.242188 L 86.382812 167.617188 L 88.097656 165.992188 L 91.535156 162.742188 L 93.25 161.117188 L 94.96875 159.492188 L 96.683594 157.867188 L 98.402344 156.242188 L 100.117188 154.613281 L 103.554688 151.363281 L 105.269531 149.738281 L 106.988281 148.113281 L 108.703125 146.488281 L 112.140625 143.238281 L 113.855469 141.613281 L 115.574219 139.988281 L 117.289062 138.363281 L 120.726562 135.113281 L 122.441406 133.488281 L 124.160156 131.859375 L 125.875 130.234375 L 127.59375 128.609375 L 129.308594 126.984375 L 132.746094 123.734375 L 134.460938 122.109375 L 136.179688 120.484375 L 137.894531 118.859375 L 141.332031 115.609375 L 143.046875 113.984375 L 144.765625 112.359375 L 146.480469 110.734375 L 148.199219 109.105469 L 149.917969 107.480469 L 151.632812 105.855469 L 153.351562 104.230469 L 155.066406 102.605469 L 158.503906 99.355469 L 160.21875 97.730469 L 161.9375 96.105469 L 163.652344 94.480469 L 165.371094 92.855469 L 167.085938 91.230469 L 170.523438 87.980469 L 172.238281 86.351562 L 173.957031 84.726562 L 175.671875 83.101562 L 179.109375 79.851562 L 180.824219 78.226562 L 182.542969 76.601562 L 184.257812 74.976562 L 187.695312 71.726562 L 189.410156 70.101562 L 191.128906 68.476562 L 192.84375 66.851562 L 194.5625 65.222656 L 196.28125 63.597656 L 197.996094 61.972656 L 199.714844 60.347656 L 201.429688 58.722656 L 203.148438 57.097656 L 204.863281 55.472656 L 208.300781 52.222656 L 210.015625 50.597656 L 211.734375 48.972656 L 213.449219 47.347656 L 216.886719 44.097656 L 218.601562 42.46875 L 220.320312 40.84375 "/>
<g clip-path="url(#clip21)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 469.847656 L 229.136719 469.847656 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 469.847656 "/>
</g>
<g clip-path="url(#clip22)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 439.132812 L 229.136719 439.132812 "/>
</g>
<g clip-path="url(#clip23)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 385.835938 L 229.136719 385.835938 "/>
</g>
<g clip-path="url(#clip24)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 332.535156 L 229.136719 332.535156 "/>
</g>
<g clip-path="url(#clip25)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 279.238281 L 229.136719 279.238281 "/>
</g>
<g clip-path="url(#clip26)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 469.847656 L 67.707031 258.171875 "/>
</g>
<g clip-path="url(#clip27)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 469.847656 L 101.621094 258.171875 "/>
</g>
<g clip-path="url(#clip28)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 469.847656 L 135.535156 258.171875 "/>
</g>
<g clip-path="url(#clip29)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 469.847656 L 169.449219 258.171875 "/>
</g>
<g clip-path="url(#clip30)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 469.847656 L 203.363281 258.171875 "/>
</g>
<g clip-path="url(#clip31)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 465.785156 L 229.136719 465.785156 "/>
</g>
<g clip-path="url(#clip32)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 412.484375 L 229.136719 412.484375 "/>
</g>
<g clip-path="url(#clip33)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 359.1875 L 229.136719 359.1875 "/>
</g>
<g clip-path="url(#clip34)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 305.886719 L 229.136719 305.886719 "/>
</g>
<g clip-path="url(#clip35)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 469.847656 L 50.75 258.171875 "/>
</g>
<g clip-path="url(#clip36)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 469.847656 L 84.664062 258.171875 "/>
</g>
<g clip-path="url(#clip37)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 469.847656 L 118.578125 258.171875 "/>
</g>
<g clip-path="url(#clip38)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 469.847656 L 152.492188 258.171875 "/>
</g>
<g clip-path="url(#clip39)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 469.847656 L 186.40625 258.171875 "/>
</g>
<g clip-path="url(#clip40)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 469.847656 L 220.320312 258.171875 "/>
</g>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 391.164062 C 86.621094 393.773438 82.710938 393.773438 82.710938 391.164062 C 82.710938 388.558594 86.621094 388.558594 86.621094 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 364.515625 C 106.96875 367.121094 103.058594 367.121094 103.058594 364.515625 C 103.058594 361.910156 106.96875 361.910156 106.96875 364.515625 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 59.488281 428.472656 C 59.488281 431.082031 55.578125 431.082031 55.578125 428.472656 C 55.578125 425.867188 59.488281 425.867188 59.488281 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 401.824219 C 86.621094 404.429688 82.710938 404.429688 82.710938 401.824219 C 82.710938 399.21875 86.621094 399.21875 86.621094 401.824219 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 407.15625 C 86.621094 409.761719 82.710938 409.761719 82.710938 407.15625 C 82.710938 404.546875 86.621094 404.546875 86.621094 407.15625 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 423.144531 C 79.835938 425.75 75.925781 425.75 75.925781 423.144531 C 75.925781 420.539062 79.835938 420.539062 79.835938 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 385.835938 C 106.96875 388.441406 103.058594 388.441406 103.058594 385.835938 C 103.058594 383.230469 106.96875 383.230469 106.96875 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 401.824219 C 100.183594 404.429688 96.273438 404.429688 96.273438 401.824219 C 96.273438 399.21875 100.183594 399.21875 100.183594 401.824219 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 412.484375 C 86.621094 415.089844 82.710938 415.089844 82.710938 412.484375 C 82.710938 409.878906 86.621094 409.878906 86.621094 412.484375 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 375.175781 C 113.75 377.78125 109.839844 377.78125 109.839844 375.175781 C 109.839844 372.570312 113.75 372.570312 113.75 375.175781 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 380.503906 C 113.75 383.113281 109.839844 383.113281 109.839844 380.503906 C 109.839844 377.898438 113.75 377.898438 113.75 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 412.484375 C 79.835938 415.089844 75.925781 415.089844 75.925781 412.484375 C 75.925781 409.878906 79.835938 409.878906 79.835938 412.484375 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 375.175781 C 100.183594 377.78125 96.273438 377.78125 96.273438 375.175781 C 96.273438 372.570312 100.183594 372.570312 100.183594 375.175781 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 369.847656 C 106.96875 372.453125 103.058594 372.453125 103.058594 369.847656 C 103.058594 367.238281 106.96875 367.238281 106.96875 369.847656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 423.144531 C 86.621094 425.75 82.710938 425.75 82.710938 423.144531 C 82.710938 420.539062 86.621094 420.539062 86.621094 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 57.535156 440.144531 L 58.21875 439.300781 L 60.28125 436.769531 L 60.96875 435.921875 L 61.65625 435.078125 L 62.339844 434.234375 L 63.027344 433.386719 L 63.714844 432.542969 L 65.089844 430.847656 L 65.777344 430.003906 L 66.464844 429.15625 L 67.148438 428.308594 L 67.835938 427.457031 L 68.523438 426.609375 L 69.210938 425.757812 L 69.898438 424.910156 L 70.585938 424.058594 L 71.269531 423.203125 L 72.644531 421.5 L 74.019531 419.789062 L 74.707031 418.929688 L 75.390625 418.070312 L 76.765625 416.351562 L 78.140625 414.625 L 78.828125 413.757812 L 79.511719 412.890625 L 80.886719 411.148438 L 81.574219 410.273438 L 82.261719 409.394531 L 82.949219 408.511719 L 83.632812 407.628906 L 85.007812 405.847656 L 86.382812 404.050781 L 87.070312 403.140625 L 87.753906 402.230469 L 88.441406 401.3125 L 89.128906 400.390625 L 89.816406 399.460938 L 90.503906 398.523438 L 91.191406 397.578125 L 91.875 396.628906 L 92.5625 395.667969 L 93.25 394.703125 L 93.9375 393.730469 L 94.625 392.75 L 95.3125 391.761719 L 95.996094 390.765625 L 96.683594 389.765625 L 97.371094 388.757812 L 98.058594 387.742188 L 98.746094 386.722656 L 99.433594 385.699219 L 100.117188 384.667969 L 100.804688 383.632812 L 101.492188 382.59375 L 102.179688 381.550781 L 102.867188 380.503906 L 103.554688 379.453125 L 104.238281 378.402344 L 105.613281 376.285156 L 106.988281 374.160156 L 107.675781 373.09375 L 108.359375 372.027344 L 109.046875 370.960938 L 109.734375 369.886719 L 110.421875 368.816406 L 111.796875 366.667969 L 111.796875 375.09375 L 111.109375 375.949219 L 109.046875 378.527344 L 108.359375 379.390625 L 107.675781 380.253906 L 106.300781 381.988281 L 105.613281 382.859375 L 104.238281 384.609375 L 103.554688 385.484375 L 102.867188 386.367188 L 101.492188 388.140625 L 100.804688 389.03125 L 100.117188 389.929688 L 99.433594 390.832031 L 98.746094 391.738281 L 98.058594 392.648438 L 97.371094 393.566406 L 96.683594 394.488281 L 95.996094 395.421875 L 95.3125 396.355469 L 94.625 397.300781 L 93.9375 398.25 L 93.25 399.210938 L 92.5625 400.175781 L 91.875 401.148438 L 91.191406 402.128906 L 90.503906 403.117188 L 89.816406 404.113281 L 89.128906 405.113281 L 88.441406 406.121094 L 87.753906 407.136719 L 87.070312 408.15625 L 86.382812 409.179688 L 85.695312 410.210938 L 85.007812 411.246094 L 84.320312 412.285156 L 83.632812 413.328125 L 82.949219 414.375 L 82.261719 415.425781 L 80.886719 417.535156 L 80.199219 418.59375 L 79.511719 419.65625 L 78.828125 420.71875 L 77.453125 422.851562 L 75.390625 426.0625 L 74.707031 427.136719 L 73.332031 429.285156 L 71.269531 432.519531 L 70.585938 433.597656 L 67.148438 439.007812 L 66.464844 440.089844 L 65.777344 441.175781 L 65.089844 442.257812 L 62.339844 446.601562 L 61.65625 447.6875 L 60.96875 448.773438 L 60.28125 449.863281 L 59.59375 450.949219 L 58.90625 452.039062 L 58.21875 453.125 L 57.535156 454.214844 Z M 57.535156 440.144531 "/>
<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 57.535156 447.179688 L 58.21875 446.210938 L 60.28125 443.316406 L 60.96875 442.347656 L 61.65625 441.382812 L 62.339844 440.417969 L 63.027344 439.453125 L 63.714844 438.484375 L 65.777344 435.589844 L 66.464844 434.621094 L 67.148438 433.65625 L 69.210938 430.761719 L 69.898438 429.792969 L 70.585938 428.828125 L 71.269531 427.863281 L 71.957031 426.898438 L 72.644531 425.929688 L 74.707031 423.035156 L 75.390625 422.066406 L 77.453125 419.171875 L 78.140625 418.203125 L 78.828125 417.238281 L 79.511719 416.273438 L 80.199219 415.308594 L 80.886719 414.339844 L 82.949219 411.445312 L 83.632812 410.476562 L 85.695312 407.582031 L 86.382812 406.613281 L 87.070312 405.648438 L 87.753906 404.683594 L 88.441406 403.71875 L 89.128906 402.75 L 91.191406 399.855469 L 91.875 398.886719 L 94.625 395.027344 L 95.3125 394.058594 L 95.996094 393.09375 L 97.371094 391.164062 L 98.058594 390.195312 L 99.433594 388.265625 L 100.117188 387.300781 L 100.804688 386.332031 L 102.867188 383.4375 L 103.554688 382.46875 L 104.238281 381.503906 L 105.613281 379.574219 L 106.300781 378.605469 L 107.675781 376.675781 L 108.359375 375.710938 L 109.046875 374.742188 L 111.109375 371.847656 L 111.796875 370.878906 "/>
<g clip-path="url(#clip41)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 234.925781 L 428.601562 234.925781 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 234.925781 "/>
</g>
<g clip-path="url(#clip42)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 204.210938 L 428.601562 204.210938 "/>
</g>
<g clip-path="url(#clip43)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 150.910156 L 428.601562 150.910156 "/>
</g>
<g clip-path="url(#clip44)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 97.613281 L 428.601562 97.613281 "/>
</g>
<g clip-path="url(#clip45)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 44.3125 L 428.601562 44.3125 "/>
</g>
<g clip-path="url(#clip46)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 234.925781 L 267.171875 23.246094 "/>
</g>
<g clip-path="url(#clip47)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 234.925781 L 301.085938 23.246094 "/>
</g>
<g clip-path="url(#clip48)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 234.925781 L 335 23.246094 "/>
</g>
<g clip-path="url(#clip49)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 234.925781 L 368.914062 23.246094 "/>
</g>
<g clip-path="url(#clip50)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 234.925781 L 402.828125 23.246094 "/>
</g>
<g clip-path="url(#clip51)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 230.859375 L 428.601562 230.859375 "/>
</g>
<g clip-path="url(#clip52)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 177.558594 L 428.601562 177.558594 "/>
</g>
<g clip-path="url(#clip53)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 124.261719 L 428.601562 124.261719 "/>
</g>
<g clip-path="url(#clip54)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 70.960938 L 428.601562 70.960938 "/>
</g>
<g clip-path="url(#clip55)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 234.925781 L 250.214844 23.246094 "/>
</g>
<g clip-path="url(#clip56)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 234.925781 L 284.128906 23.246094 "/>
</g>
<g clip-path="url(#clip57)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 234.925781 L 318.042969 23.246094 "/>
</g>
<g clip-path="url(#clip58)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 234.925781 L 351.957031 23.246094 "/>
</g>
<g clip-path="url(#clip59)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 234.925781 L 385.871094 23.246094 "/>
</g>
<g clip-path="url(#clip60)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 234.925781 L 419.785156 23.246094 "/>
</g>
<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 134.921875 C 320 137.527344 316.089844 137.527344 316.089844 134.921875 C 316.089844 132.316406 320 132.316406 320 134.921875 "/>
<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 129.589844 C 320 132.199219 316.089844 132.199219 316.089844 129.589844 C 316.089844 126.984375 320 126.984375 320 129.589844 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 318.042969 124.148438 L 318.128906 124.214844 L 318.214844 124.285156 L 318.300781 124.347656 L 318.386719 124.414062 L 318.472656 124.476562 L 318.558594 124.535156 L 318.644531 124.597656 L 318.730469 124.652344 L 318.816406 124.710938 L 318.902344 124.761719 L 318.988281 124.816406 L 319.074219 124.867188 L 319.246094 124.960938 L 319.417969 125.046875 L 319.503906 125.085938 L 319.675781 125.15625 L 319.847656 125.21875 L 320.105469 125.289062 L 320.277344 125.320312 L 320.363281 125.332031 L 320.535156 125.347656 L 320.707031 125.347656 L 320.878906 125.332031 L 320.964844 125.320312 L 321.050781 125.304688 L 321.136719 125.285156 L 321.308594 125.238281 L 321.390625 125.207031 L 321.5625 125.136719 L 321.734375 125.050781 L 321.90625 124.949219 L 321.992188 124.894531 L 322.078125 124.835938 L 322.164062 124.773438 L 322.25 124.707031 L 322.421875 124.566406 L 322.59375 124.410156 L 322.679688 124.328125 L 322.765625 124.242188 L 322.9375 124.0625 L 323.023438 123.96875 L 323.195312 123.773438 L 323.28125 123.671875 L 323.453125 123.460938 L 323.539062 123.351562 L 323.796875 123.011719 L 323.882812 122.894531 L 324.054688 122.652344 L 324.3125 122.277344 L 324.484375 122.019531 L 324.742188 121.621094 L 324.828125 121.484375 L 324.828125 137.699219 L 324.742188 137.632812 L 324.65625 137.5625 L 324.570312 137.5 L 324.484375 137.433594 L 324.398438 137.371094 L 324.3125 137.3125 L 324.226562 137.25 L 324.140625 137.195312 L 324.054688 137.136719 L 323.96875 137.085938 L 323.882812 137.03125 L 323.796875 136.980469 L 323.625 136.886719 L 323.453125 136.800781 L 323.367188 136.761719 L 323.195312 136.691406 L 323.023438 136.628906 L 322.765625 136.558594 L 322.59375 136.527344 L 322.507812 136.515625 L 322.421875 136.507812 L 322.25 136.5 L 322.164062 136.5 L 321.992188 136.515625 L 321.90625 136.527344 L 321.820312 136.542969 L 321.734375 136.5625 L 321.5625 136.609375 L 321.476562 136.640625 L 321.390625 136.675781 L 321.308594 136.710938 L 321.136719 136.796875 L 320.964844 136.898438 L 320.878906 136.953125 L 320.792969 137.011719 L 320.707031 137.074219 L 320.621094 137.140625 L 320.449219 137.28125 L 320.277344 137.4375 L 320.191406 137.519531 L 320.105469 137.605469 L 319.933594 137.785156 L 319.847656 137.878906 L 319.675781 138.074219 L 319.589844 138.175781 L 319.417969 138.386719 L 319.332031 138.496094 L 319.074219 138.835938 L 318.988281 138.953125 L 318.816406 139.195312 L 318.558594 139.570312 L 318.386719 139.828125 L 318.214844 140.09375 L 318.128906 140.230469 L 318.042969 140.363281 Z M 318.042969 124.148438 "/>
<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 132.257812 L 318.214844 132.1875 L 318.300781 132.15625 L 318.472656 132.085938 L 318.558594 132.054688 L 318.644531 132.019531 L 318.730469 131.988281 L 318.902344 131.917969 L 318.988281 131.886719 L 319.160156 131.816406 L 319.246094 131.785156 L 319.417969 131.714844 L 319.503906 131.683594 L 319.589844 131.648438 L 319.675781 131.617188 L 319.847656 131.546875 L 319.933594 131.515625 L 320.105469 131.445312 L 320.191406 131.414062 L 320.363281 131.34375 L 320.449219 131.3125 L 320.535156 131.277344 L 320.621094 131.246094 L 320.792969 131.175781 L 320.878906 131.144531 L 321.050781 131.074219 L 321.136719 131.042969 L 321.308594 130.972656 L 321.390625 130.941406 L 321.476562 130.90625 L 321.5625 130.875 L 321.734375 130.804688 L 321.820312 130.773438 L 321.992188 130.703125 L 322.078125 130.671875 L 322.25 130.601562 L 322.335938 130.570312 L 322.421875 130.535156 L 322.507812 130.503906 L 322.679688 130.433594 L 322.765625 130.402344 L 322.9375 130.332031 L 323.023438 130.300781 L 323.195312 130.230469 L 323.28125 130.199219 L 323.367188 130.164062 L 323.453125 130.132812 L 323.625 130.0625 L 323.710938 130.03125 L 323.882812 129.960938 L 323.96875 129.929688 L 324.140625 129.859375 L 324.226562 129.828125 L 324.3125 129.792969 L 324.398438 129.761719 L 324.570312 129.691406 L 324.65625 129.660156 L 324.828125 129.589844 "/>
<g clip-path="url(#clip61)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 469.847656 L 428.601562 469.847656 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 469.847656 "/>
</g>
<g clip-path="url(#clip62)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 439.132812 L 428.601562 439.132812 "/>
</g>
<g clip-path="url(#clip63)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 385.835938 L 428.601562 385.835938 "/>
</g>
<g clip-path="url(#clip64)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 332.535156 L 428.601562 332.535156 "/>
</g>
<g clip-path="url(#clip65)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 279.238281 L 428.601562 279.238281 "/>
</g>
<g clip-path="url(#clip66)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 469.847656 L 267.171875 258.171875 "/>
</g>
<g clip-path="url(#clip67)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 469.847656 L 301.085938 258.171875 "/>
</g>
<g clip-path="url(#clip68)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 469.847656 L 335 258.171875 "/>
</g>
<g clip-path="url(#clip69)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 469.847656 L 368.914062 258.171875 "/>
</g>
<g clip-path="url(#clip70)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 469.847656 L 402.828125 258.171875 "/>
</g>
<g clip-path="url(#clip71)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 465.785156 L 428.601562 465.785156 "/>
</g>
<g clip-path="url(#clip72)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 412.484375 L 428.601562 412.484375 "/>
</g>
<g clip-path="url(#clip73)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 359.1875 L 428.601562 359.1875 "/>
</g>
<g clip-path="url(#clip74)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 305.886719 L 428.601562 305.886719 "/>
</g>
<g clip-path="url(#clip75)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 469.847656 L 250.214844 258.171875 "/>
</g>
<g clip-path="url(#clip76)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 469.847656 L 284.128906 258.171875 "/>
</g>
<g clip-path="url(#clip77)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 469.847656 L 318.042969 258.171875 "/>
</g>
<g clip-path="url(#clip78)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 469.847656 L 351.957031 258.171875 "/>
</g>
<g clip-path="url(#clip79)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 469.847656 L 385.871094 258.171875 "/>
</g>
<g clip-path="url(#clip80)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 469.847656 L 419.785156 258.171875 "/>
</g>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 396.496094 C 292.867188 399.101562 288.957031 399.101562 288.957031 396.496094 C 288.957031 393.890625 292.867188 393.890625 292.867188 396.496094 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 428.472656 C 265.738281 431.082031 261.828125 431.082031 261.828125 428.472656 C 261.828125 425.867188 265.738281 425.867188 265.738281 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 385.835938 C 286.085938 388.441406 282.175781 388.441406 282.175781 385.835938 C 282.175781 383.230469 286.085938 383.230469 286.085938 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 391.164062 C 286.085938 393.773438 282.175781 393.773438 282.175781 391.164062 C 282.175781 388.558594 286.085938 388.558594 286.085938 391.164062 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 407.15625 C 286.085938 409.761719 282.175781 409.761719 282.175781 407.15625 C 282.175781 404.546875 286.085938 404.546875 286.085938 407.15625 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 385.835938 C 292.867188 388.441406 288.957031 388.441406 288.957031 385.835938 C 288.957031 383.230469 292.867188 383.230469 292.867188 385.835938 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 243.433594 452.394531 L 244.035156 451.695312 L 245.238281 450.304688 L 245.839844 449.605469 L 246.4375 448.90625 L 248.84375 446.109375 L 249.445312 445.40625 L 250.046875 444.707031 L 250.644531 444.003906 L 251.246094 443.300781 L 251.847656 442.59375 L 252.449219 441.890625 L 253.652344 440.476562 L 254.253906 439.765625 L 254.851562 439.058594 L 255.453125 438.347656 L 257.257812 436.203125 L 257.859375 435.484375 L 258.460938 434.761719 L 259.058594 434.039062 L 259.660156 433.316406 L 260.261719 432.589844 L 260.863281 431.859375 L 262.066406 430.390625 L 262.667969 429.652344 L 263.265625 428.910156 L 263.867188 428.164062 L 264.46875 427.414062 L 265.070312 426.660156 L 265.671875 425.902344 L 266.273438 425.140625 L 266.875 424.375 L 267.472656 423.601562 L 268.074219 422.828125 L 268.675781 422.050781 L 269.878906 420.480469 L 271.082031 418.894531 L 271.679688 418.09375 L 272.882812 416.484375 L 273.484375 415.675781 L 274.085938 414.863281 L 274.6875 414.046875 L 275.285156 413.226562 L 275.886719 412.40625 L 277.089844 410.757812 L 277.691406 409.929688 L 278.894531 408.265625 L 279.492188 407.433594 L 281.296875 404.925781 L 282.5 403.246094 L 283.101562 402.402344 L 283.699219 401.5625 L 284.902344 399.875 L 285.503906 399.027344 L 286.105469 398.183594 L 287.308594 396.488281 L 287.90625 395.640625 L 288.507812 394.792969 L 289.109375 393.941406 L 289.710938 393.09375 L 290.3125 392.242188 L 290.914062 391.394531 L 290.914062 398.976562 L 290.3125 399.675781 L 289.710938 400.371094 L 287.90625 402.46875 L 287.308594 403.167969 L 286.707031 403.867188 L 286.105469 404.570312 L 285.503906 405.269531 L 283.699219 407.378906 L 283.101562 408.085938 L 281.296875 410.207031 L 279.492188 412.339844 L 278.894531 413.054688 L 278.292969 413.769531 L 276.488281 415.925781 L 275.285156 417.378906 L 274.6875 418.105469 L 273.484375 419.574219 L 272.28125 421.050781 L 271.679688 421.796875 L 271.082031 422.546875 L 270.480469 423.296875 L 269.277344 424.8125 L 268.675781 425.578125 L 268.074219 426.347656 L 267.472656 427.121094 L 266.875 427.898438 L 266.273438 428.679688 L 265.671875 429.464844 L 265.070312 430.253906 L 264.46875 431.046875 L 263.867188 431.84375 L 263.265625 432.644531 L 262.667969 433.453125 L 262.066406 434.257812 L 261.464844 435.070312 L 260.261719 436.703125 L 259.660156 437.523438 L 259.058594 438.347656 L 258.460938 439.171875 L 257.257812 440.828125 L 255.453125 443.324219 L 254.851562 444.160156 L 254.253906 445 L 251.847656 448.359375 L 250.644531 450.046875 L 250.046875 450.894531 L 249.445312 451.738281 L 248.84375 452.585938 L 248.242188 453.429688 L 247.640625 454.277344 L 247.039062 455.128906 L 246.4375 455.976562 L 245.839844 456.824219 L 244.636719 458.527344 L 244.035156 459.375 L 243.433594 460.226562 Z M 243.433594 452.394531 "/>
<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 243.433594 456.308594 L 245.839844 453.214844 L 246.4375 452.441406 L 250.046875 447.800781 L 250.644531 447.027344 L 251.246094 446.25 L 254.253906 442.382812 L 254.851562 441.609375 L 258.460938 436.96875 L 259.058594 436.195312 L 259.660156 435.417969 L 262.667969 431.550781 L 263.265625 430.777344 L 266.875 426.136719 L 267.472656 425.359375 L 271.082031 420.71875 L 271.679688 419.945312 L 274.6875 416.078125 L 275.285156 415.304688 L 275.886719 414.527344 L 278.894531 410.660156 L 279.492188 409.886719 L 283.101562 405.246094 L 283.699219 404.46875 L 287.308594 399.828125 L 287.90625 399.054688 L 290.914062 395.1875 "/>
<g clip-path="url(#clip81)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 240.40625 L 35.152344 240.40625 Z M 35.152344 258.171875 "/>
</g>
<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-1" x="129.644531" y="252.204102"/>
</g>
<g clip-path="url(#clip82)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 240.40625 L 234.617188 240.40625 Z M 234.617188 258.171875 "/>
</g>
<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-2" x="329.109375" y="252.204102"/>
</g>
<g clip-path="url(#clip83)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 5.480469 L 35.152344 5.480469 Z M 35.152344 23.246094 "/>
</g>
<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-3" x="129.644531" y="17.27832"/>
</g>
<g clip-path="url(#clip84)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 5.480469 L 234.617188 5.480469 Z M 234.617188 23.246094 "/>
</g>
<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-4" x="329.109375" y="17.27832"/>
</g>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 472.589844 L 50.75 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 472.589844 L 84.664062 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 472.589844 L 118.578125 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 472.589844 L 152.492188 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 472.589844 L 186.40625 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 472.589844 L 220.320312 469.847656 "/>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-5" x="45.75" y="481.196289"/>
  <use xlink:href="#glyph0-6" x="50.75" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-5" x="79.664062" y="481.196289"/>
  <use xlink:href="#glyph0-4" x="84.664062" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-7" x="113.578125" y="481.196289"/>
  <use xlink:href="#glyph0-6" x="118.578125" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-7" x="147.492188" y="481.196289"/>
  <use xlink:href="#glyph0-4" x="152.492188" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-8" x="181.40625" y="481.196289"/>
  <use xlink:href="#glyph0-6" x="186.40625" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-8" x="215.320312" y="481.196289"/>
  <use xlink:href="#glyph0-4" x="220.320312" y="481.196289"/>
</g>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 472.589844 L 250.214844 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 472.589844 L 284.128906 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 472.589844 L 318.042969 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 472.589844 L 351.957031 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 472.589844 L 385.871094 469.847656 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 472.589844 L 419.785156 469.847656 "/>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-5" x="245.214844" y="481.196289"/>
  <use xlink:href="#glyph0-6" x="250.214844" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-5" x="279.128906" y="481.196289"/>
  <use xlink:href="#glyph0-4" x="284.128906" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-7" x="313.042969" y="481.196289"/>
  <use xlink:href="#glyph0-6" x="318.042969" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-7" x="346.957031" y="481.196289"/>
  <use xlink:href="#glyph0-4" x="351.957031" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-8" x="380.871094" y="481.196289"/>
  <use xlink:href="#glyph0-6" x="385.871094" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-8" x="414.785156" y="481.196289"/>
  <use xlink:href="#glyph0-4" x="419.785156" y="481.196289"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-5" x="20.21875" y="233.774414"/>
  <use xlink:href="#glyph0-6" x="25.21875" y="233.774414"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-7" x="20.21875" y="180.473633"/>
  <use xlink:href="#glyph0-6" x="25.21875" y="180.473633"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-8" x="20.21875" y="127.176758"/>
  <use xlink:href="#glyph0-6" x="25.21875" y="127.176758"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-3" x="20.21875" y="73.875977"/>
  <use xlink:href="#glyph0-6" x="25.21875" y="73.875977"/>
</g>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 230.859375 L 35.152344 230.859375 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 177.558594 L 35.152344 177.558594 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 124.261719 L 35.152344 124.261719 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 70.960938 L 35.152344 70.960938 "/>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-5" x="20.21875" y="468.700195"/>
  <use xlink:href="#glyph0-6" x="25.21875" y="468.700195"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-7" x="20.21875" y="415.399414"/>
  <use xlink:href="#glyph0-6" x="25.21875" y="415.399414"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-8" x="20.21875" y="362.102539"/>
  <use xlink:href="#glyph0-6" x="25.21875" y="362.102539"/>
</g>
<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
  <use xlink:href="#glyph0-3" x="20.21875" y="308.801758"/>
  <use xlink:href="#glyph0-6" x="25.21875" y="308.801758"/>
</g>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 465.785156 L 35.152344 465.785156 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 412.484375 L 35.152344 412.484375 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 359.1875 L 35.152344 359.1875 "/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 305.886719 L 35.152344 305.886719 "/>
<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
  <use xlink:href="#glyph1-1" x="224.875" y="494.538086"/>
  <use xlink:href="#glyph1-2" x="230.875" y="494.538086"/>
  <use xlink:href="#glyph1-3" x="233.875" y="494.538086"/>
</g>
<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
  <use xlink:href="#glyph2-1" x="13.499023" y="256.046875"/>
  <use xlink:href="#glyph2-2" x="13.499023" y="250.046875"/>
  <use xlink:href="#glyph2-3" x="13.499023" y="242.046875"/>
</g>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;" d="M 439.5625 295.328125 L 498.519531 295.328125 L 498.519531 197.769531 L 439.5625 197.769531 Z M 439.5625 295.328125 "/>
<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
  <use xlink:href="#glyph1-4" x="445.042969" y="212.768555"/>
  <use xlink:href="#glyph1-5" x="448.042969" y="212.768555"/>
  <use xlink:href="#glyph1-1" x="454.042969" y="212.768555"/>
  <use xlink:href="#glyph1-2" x="460.042969" y="212.768555"/>
  <use xlink:href="#glyph1-6" x="463.042969" y="212.768555"/>
  <use xlink:href="#glyph1-7" x="469.042969" y="212.768555"/>
  <use xlink:href="#glyph1-8" x="473.042969" y="212.768555"/>
  <use xlink:href="#glyph1-1" x="477.042969" y="212.768555"/>
  <use xlink:href="#glyph1-3" x="482.042969" y="212.768555"/>
  <use xlink:href="#glyph1-9" x="487.042969" y="212.768555"/>
  <use xlink:href="#glyph1-10" x="489.042969" y="212.768555"/>
</g>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 229.367188 C 455.636719 231.972656 451.726562 231.972656 451.726562 229.367188 C 451.726562 226.761719 455.636719 226.761719 455.636719 229.367188 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 229.367188 L 460.59375 229.367188 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 246.648438 C 455.636719 249.253906 451.726562 249.253906 451.726562 246.648438 C 451.726562 244.042969 455.636719 244.042969 455.636719 246.648438 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 246.648438 L 460.59375 246.648438 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 263.925781 C 455.636719 266.535156 451.726562 266.535156 451.726562 263.925781 C 451.726562 261.320312 455.636719 261.320312 455.636719 263.925781 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 263.925781 L 460.59375 263.925781 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 281.207031 C 455.636719 283.8125 451.726562 283.8125 451.726562 281.207031 C 451.726562 278.601562 455.636719 278.601562 455.636719 281.207031 "/>
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 281.207031 L 460.59375 281.207031 "/>
<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
  <use xlink:href="#glyph0-3" x="467.800781" y="232.282227"/>
</g>
<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
  <use xlink:href="#glyph0-4" x="467.800781" y="249.563477"/>
</g>
<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
  <use xlink:href="#glyph0-1" x="467.800781" y="266.84082"/>
</g>
<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
  <use xlink:href="#glyph0-2" x="467.800781" y="284.12207"/>
</g>
</g>
</svg>

::: {.sourceClojure}
```clojure
(-> plot
    r/r->clj)
```
:::

::: {.printedClojure}
```clojure
{:data
 {:manufacturer
  ["audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "audi"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "chevrolet"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "dodge"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "ford"
   "honda"
   "honda"
   "honda"
   "honda"
   "honda"
   "honda"
   "honda"
   "honda"
   "honda"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "hyundai"
   "jeep"
   "jeep"
   "jeep"
   "jeep"
   "jeep"
   "jeep"
   "jeep"
   "jeep"
   "land rover"
   "land rover"
   "land rover"
   "land rover"
   "lincoln"
   "lincoln"
   "lincoln"
   "mercury"
   "mercury"
   "mercury"
   "mercury"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "nissan"
   "pontiac"
   "pontiac"
   "pontiac"
   "pontiac"
   "pontiac"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "subaru"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "toyota"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"
   "volkswagen"],
  :model
  ["a4"
   "a4"
   "a4"
   "a4"
   "a4"
   "a4"
   "a4"
   "a4 quattro"
   "a4 quattro"
   "a4 quattro"
   "a4 quattro"
   "a4 quattro"
   "a4 quattro"
   "a4 quattro"
   "a4 quattro"
   "a6 quattro"
   "a6 quattro"
   "a6 quattro"
   "c1500 suburban 2wd"
   "c1500 suburban 2wd"
   "c1500 suburban 2wd"
   "c1500 suburban 2wd"
   "c1500 suburban 2wd"
   "corvette"
   "corvette"
   "corvette"
   "corvette"
   "corvette"
   "k1500 tahoe 4wd"
   "k1500 tahoe 4wd"
   "k1500 tahoe 4wd"
   "k1500 tahoe 4wd"
   "malibu"
   "malibu"
   "malibu"
   "malibu"
   "malibu"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "caravan 2wd"
   "dakota pickup 4wd"
   "dakota pickup 4wd"
   "dakota pickup 4wd"
   "dakota pickup 4wd"
   "dakota pickup 4wd"
   "dakota pickup 4wd"
   "dakota pickup 4wd"
   "dakota pickup 4wd"
   "dakota pickup 4wd"
   "durango 4wd"
   "durango 4wd"
   "durango 4wd"
   "durango 4wd"
   "durango 4wd"
   "durango 4wd"
   "durango 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "ram 1500 pickup 4wd"
   "expedition 2wd"
   "expedition 2wd"
   "expedition 2wd"
   "explorer 4wd"
   "explorer 4wd"
   "explorer 4wd"
   "explorer 4wd"
   "explorer 4wd"
   "explorer 4wd"
   "f150 pickup 4wd"
   "f150 pickup 4wd"
   "f150 pickup 4wd"
   "f150 pickup 4wd"
   "f150 pickup 4wd"
   "f150 pickup 4wd"
   "f150 pickup 4wd"
   "mustang"
   "mustang"
   "mustang"
   "mustang"
   "mustang"
   "mustang"
   "mustang"
   "mustang"
   "mustang"
   "civic"
   "civic"
   "civic"
   "civic"
   "civic"
   "civic"
   "civic"
   "civic"
   "civic"
   "sonata"
   "sonata"
   "sonata"
   "sonata"
   "sonata"
   "sonata"
   "sonata"
   "tiburon"
   "tiburon"
   "tiburon"
   "tiburon"
   "tiburon"
   "tiburon"
   "tiburon"
   "grand cherokee 4wd"
   "grand cherokee 4wd"
   "grand cherokee 4wd"
   "grand cherokee 4wd"
   "grand cherokee 4wd"
   "grand cherokee 4wd"
   "grand cherokee 4wd"
   "grand cherokee 4wd"
   "range rover"
   "range rover"
   "range rover"
   "range rover"
   "navigator 2wd"
   "navigator 2wd"
   "navigator 2wd"
   "mountaineer 4wd"
   "mountaineer 4wd"
   "mountaineer 4wd"
   "mountaineer 4wd"
   "altima"
   "altima"
   "altima"
   "altima"
   "altima"
   "altima"
   "maxima"
   "maxima"
   "maxima"
   "pathfinder 4wd"
   "pathfinder 4wd"
   "pathfinder 4wd"
   "pathfinder 4wd"
   "grand prix"
   "grand prix"
   "grand prix"
   "grand prix"
   "grand prix"
   "forester awd"
   "forester awd"
   "forester awd"
   "forester awd"
   "forester awd"
   "forester awd"
   "impreza awd"
   "impreza awd"
   "impreza awd"
   "impreza awd"
   "impreza awd"
   "impreza awd"
   "impreza awd"
   "impreza awd"
   "4runner 4wd"
   "4runner 4wd"
   "4runner 4wd"
   "4runner 4wd"
   "4runner 4wd"
   "4runner 4wd"
   "camry"
   "camry"
   "camry"
   "camry"
   "camry"
   "camry"
   "camry"
   "camry solara"
   "camry solara"
   "camry solara"
   "camry solara"
   "camry solara"
   "camry solara"
   "camry solara"
   "corolla"
   "corolla"
   "corolla"
   "corolla"
   "corolla"
   "land cruiser wagon 4wd"
   "land cruiser wagon 4wd"
   "toyota tacoma 4wd"
   "toyota tacoma 4wd"
   "toyota tacoma 4wd"
   "toyota tacoma 4wd"
   "toyota tacoma 4wd"
   "toyota tacoma 4wd"
   "toyota tacoma 4wd"
   "gti"
   "gti"
   "gti"
   "gti"
   "gti"
   "jetta"
   "jetta"
   "jetta"
   "jetta"
   "jetta"
   "jetta"
   "jetta"
   "jetta"
   "jetta"
   "new beetle"
   "new beetle"
   "new beetle"
   "new beetle"
   "new beetle"
   "new beetle"
   "passat"
   "passat"
   "passat"
   "passat"
   "passat"
   "passat"
   "passat"],
  :displ
  [1.8
   1.8
   2.0
   2.0
   2.8
   2.8
   3.1
   1.8
   1.8
   2.0
   2.0
   2.8
   2.8
   3.1
   3.1
   2.8
   3.1
   4.2
   5.3
   5.3
   5.3
   5.7
   6.0
   5.7
   5.7
   6.2
   6.2
   7.0
   5.3
   5.3
   5.7
   6.5
   2.4
   2.4
   3.1
   3.5
   3.6
   2.4
   3.0
   3.3
   3.3
   3.3
   3.3
   3.3
   3.8
   3.8
   3.8
   4.0
   3.7
   3.7
   3.9
   3.9
   4.7
   4.7
   4.7
   5.2
   5.2
   3.9
   4.7
   4.7
   4.7
   5.2
   5.7
   5.9
   4.7
   4.7
   4.7
   4.7
   4.7
   4.7
   5.2
   5.2
   5.7
   5.9
   4.6
   5.4
   5.4
   4.0
   4.0
   4.0
   4.0
   4.6
   5.0
   4.2
   4.2
   4.6
   4.6
   4.6
   5.4
   5.4
   3.8
   3.8
   4.0
   4.0
   4.6
   4.6
   4.6
   4.6
   5.4
   1.6
   1.6
   1.6
   1.6
   1.6
   1.8
   1.8
   1.8
   2.0
   2.4
   2.4
   2.4
   2.4
   2.5
   2.5
   3.3
   2.0
   2.0
   2.0
   2.0
   2.7
   2.7
   2.7
   3.0
   3.7
   4.0
   4.7
   4.7
   4.7
   5.7
   6.1
   4.0
   4.2
   4.4
   4.6
   5.4
   5.4
   5.4
   4.0
   4.0
   4.6
   5.0
   2.4
   2.4
   2.5
   2.5
   3.5
   3.5
   3.0
   3.0
   3.5
   3.3
   3.3
   4.0
   5.6
   3.1
   3.8
   3.8
   3.8
   5.3
   2.5
   2.5
   2.5
   2.5
   2.5
   2.5
   2.2
   2.2
   2.5
   2.5
   2.5
   2.5
   2.5
   2.5
   2.7
   2.7
   3.4
   3.4
   4.0
   4.7
   2.2
   2.2
   2.4
   2.4
   3.0
   3.0
   3.5
   2.2
   2.2
   2.4
   2.4
   3.0
   3.0
   3.3
   1.8
   1.8
   1.8
   1.8
   1.8
   4.7
   5.7
   2.7
   2.7
   2.7
   3.4
   3.4
   4.0
   4.0
   2.0
   2.0
   2.0
   2.0
   2.8
   1.9
   2.0
   2.0
   2.0
   2.0
   2.5
   2.5
   2.8
   2.8
   1.9
   1.9
   2.0
   2.0
   2.5
   2.5
   1.8
   1.8
   2.0
   2.0
   2.8
   2.8
   3.6],
  :year
  [1999
   1999
   2008
   2008
   1999
   1999
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   2008
   1999
   2008
   2008
   2008
   2008
   2008
   1999
   2008
   1999
   1999
   2008
   2008
   2008
   2008
   2008
   1999
   1999
   1999
   2008
   1999
   2008
   2008
   1999
   1999
   1999
   1999
   2008
   2008
   2008
   1999
   1999
   2008
   2008
   2008
   2008
   1999
   1999
   2008
   2008
   2008
   1999
   1999
   1999
   2008
   2008
   2008
   1999
   2008
   1999
   2008
   2008
   2008
   2008
   2008
   2008
   1999
   1999
   2008
   1999
   1999
   1999
   2008
   1999
   1999
   1999
   2008
   2008
   1999
   1999
   1999
   1999
   1999
   2008
   1999
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   2008
   2008
   1999
   1999
   1999
   1999
   1999
   2008
   2008
   2008
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   1999
   1999
   2008
   2008
   2008
   2008
   2008
   2008
   2008
   1999
   1999
   2008
   2008
   2008
   2008
   1999
   2008
   2008
   1999
   1999
   1999
   2008
   1999
   2008
   2008
   1999
   1999
   1999
   2008
   2008
   2008
   2008
   1999
   1999
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   2008
   2008
   2008
   1999
   1999
   1999
   1999
   2008
   2008
   2008
   2008
   1999
   1999
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   1999
   1999
   1999
   2008
   2008
   1999
   2008
   1999
   1999
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   1999
   1999
   2008
   2008
   2008
   2008
   1999
   1999
   1999
   1999
   1999
   1999
   2008
   2008
   1999
   1999
   2008
   2008
   1999
   1999
   2008],
  :cyl
  [4
   4
   4
   4
   6
   6
   6
   4
   4
   4
   4
   6
   6
   6
   6
   6
   6
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   4
   4
   6
   6
   6
   4
   6
   6
   6
   6
   6
   6
   6
   6
   6
   6
   6
   6
   6
   6
   8
   8
   8
   8
   8
   6
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   6
   6
   6
   6
   8
   8
   6
   6
   8
   8
   8
   8
   8
   6
   6
   6
   6
   8
   8
   8
   8
   8
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   6
   6
   6
   4
   4
   4
   4
   6
   6
   6
   6
   6
   6
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   8
   6
   6
   8
   8
   4
   4
   4
   4
   6
   6
   6
   6
   6
   6
   6
   6
   8
   6
   6
   6
   6
   8
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   4
   6
   6
   6
   8
   4
   4
   4
   4
   6
   6
   6
   4
   4
   4
   4
   6
   6
   6
   4
   4
   4
   4
   4
   8
   8
   4
   4
   4
   6
   6
   6
   6
   4
   4
   4
   4
   6
   4
   4
   4
   4
   4
   5
   5
   6
   6
   4
   4
   4
   4
   5
   5
   4
   4
   4
   4
   6
   6
   6],
  :trans
  ["auto(l5)"
   "manual(m5)"
   "manual(m6)"
   "auto(av)"
   "auto(l5)"
   "manual(m5)"
   "auto(av)"
   "manual(m5)"
   "auto(l5)"
   "manual(m6)"
   "auto(s6)"
   "auto(l5)"
   "manual(m5)"
   "auto(s6)"
   "manual(m6)"
   "auto(l5)"
   "auto(s6)"
   "auto(s6)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "manual(m6)"
   "auto(l4)"
   "manual(m6)"
   "auto(s6)"
   "manual(m6)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(s6)"
   "auto(l3)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l6)"
   "auto(l6)"
   "manual(m6)"
   "auto(l4)"
   "auto(l4)"
   "manual(m5)"
   "auto(l5)"
   "auto(l5)"
   "auto(l5)"
   "manual(m5)"
   "auto(l4)"
   "auto(l4)"
   "auto(l5)"
   "auto(l5)"
   "auto(l5)"
   "auto(l4)"
   "auto(l5)"
   "auto(l4)"
   "manual(m6)"
   "auto(l5)"
   "auto(l5)"
   "auto(l5)"
   "manual(m6)"
   "manual(m6)"
   "auto(l4)"
   "manual(m5)"
   "auto(l5)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l6)"
   "auto(l5)"
   "manual(m5)"
   "auto(l5)"
   "auto(l5)"
   "auto(l6)"
   "auto(l4)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "auto(l5)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l5)"
   "manual(m6)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "auto(l5)"
   "auto(l5)"
   "manual(m6)"
   "auto(l4)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "auto(l5)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "auto(l4)"
   "manual(m6)"
   "manual(m5)"
   "auto(l5)"
   "auto(l5)"
   "auto(l4)"
   "auto(l4)"
   "auto(l5)"
   "auto(l5)"
   "auto(l5)"
   "auto(l5)"
   "auto(l4)"
   "auto(s6)"
   "auto(s6)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l6)"
   "auto(l5)"
   "auto(l5)"
   "auto(l6)"
   "auto(l4)"
   "manual(m5)"
   "auto(l4)"
   "auto(av)"
   "manual(m6)"
   "manual(m6)"
   "auto(av)"
   "auto(l4)"
   "manual(m5)"
   "auto(av)"
   "auto(l4)"
   "manual(m5)"
   "auto(l5)"
   "auto(s5)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "auto(s4)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "auto(l4)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "auto(s4)"
   "auto(s4)"
   "manual(m5)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "auto(l4)"
   "manual(m5)"
   "auto(l5)"
   "auto(l5)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "auto(l5)"
   "auto(l4)"
   "manual(m5)"
   "auto(s6)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(s5)"
   "auto(l4)"
   "manual(m5)"
   "auto(s5)"
   "auto(l3)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "auto(l4)"
   "auto(s6)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "manual(m6)"
   "auto(l5)"
   "manual(m5)"
   "auto(l4)"
   "manual(m6)"
   "auto(s6)"
   "manual(m5)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "auto(s6)"
   "manual(m6)"
   "auto(s6)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "auto(l4)"
   "manual(m5)"
   "auto(s6)"
   "manual(m5)"
   "auto(l5)"
   "auto(s6)"
   "manual(m6)"
   "auto(l5)"
   "manual(m5)"
   "auto(s6)"],
  :drv
  ["f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "4"
   "4"
   "4"
   "4"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "r"
   "r"
   "r"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "r"
   "r"
   "r"
   "4"
   "4"
   "4"
   "4"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "4"
   "4"
   "4"
   "4"
   "f"
   "f"
   "f"
   "f"
   "f"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "4"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"
   "f"],
  :cty
  [18
   21
   20
   21
   16
   18
   18
   18
   16
   20
   19
   15
   17
   17
   15
   15
   17
   16
   14
   11
   14
   13
   12
   16
   15
   16
   15
   15
   14
   11
   11
   14
   19
   22
   18
   18
   17
   18
   17
   16
   16
   17
   17
   11
   15
   15
   16
   16
   15
   14
   13
   14
   14
   14
   9
   11
   11
   13
   13
   9
   13
   11
   13
   11
   12
   9
   13
   13
   12
   9
   11
   11
   13
   11
   11
   11
   12
   14
   15
   14
   13
   13
   13
   14
   14
   13
   13
   13
   11
   13
   18
   18
   17
   16
   15
   15
   15
   15
   14
   28
   24
   25
   23
   24
   26
   25
   24
   21
   18
   18
   21
   21
   18
   18
   19
   19
   19
   20
   20
   17
   16
   17
   17
   15
   15
   14
   9
   14
   13
   11
   11
   12
   12
   11
   11
   11
   12
   14
   13
   13
   13
   21
   19
   23
   23
   19
   19
   18
   19
   19
   14
   15
   14
   12
   18
   16
   17
   18
   16
   18
   18
   20
   19
   20
   18
   21
   19
   19
   19
   20
   20
   19
   20
   15
   16
   15
   15
   16
   14
   21
   21
   21
   21
   18
   18
   19
   21
   21
   21
   22
   18
   18
   18
   24
   24
   26
   28
   26
   11
   13
   15
   16
   17
   15
   15
   15
   16
   21
   19
   21
   22
   17
   33
   21
   19
   22
   21
   21
   21
   16
   17
   35
   29
   21
   19
   20
   20
   21
   18
   19
   21
   16
   18
   17],
  :hwy
  [29
   29
   31
   30
   26
   26
   27
   26
   25
   28
   27
   25
   25
   25
   25
   24
   25
   23
   20
   15
   20
   17
   17
   26
   23
   26
   25
   24
   19
   14
   15
   17
   27
   30
   26
   29
   26
   24
   24
   22
   22
   24
   24
   17
   22
   21
   23
   23
   19
   18
   17
   17
   19
   19
   12
   17
   15
   17
   17
   12
   17
   16
   18
   15
   16
   12
   17
   17
   16
   12
   15
   16
   17
   15
   17
   17
   18
   17
   19
   17
   19
   19
   17
   17
   17
   16
   16
   17
   15
   17
   26
   25
   26
   24
   21
   22
   23
   22
   20
   33
   32
   32
   29
   32
   34
   36
   36
   29
   26
   27
   30
   31
   26
   26
   28
   26
   29
   28
   27
   24
   24
   24
   22
   19
   20
   17
   12
   19
   18
   14
   15
   18
   18
   15
   17
   16
   18
   17
   19
   19
   17
   29
   27
   31
   32
   27
   26
   26
   25
   25
   17
   17
   20
   18
   26
   26
   27
   28
   25
   25
   24
   27
   25
   26
   23
   26
   26
   26
   26
   25
   27
   25
   27
   20
   20
   19
   17
   20
   17
   29
   27
   31
   31
   26
   26
   28
   27
   29
   31
   31
   26
   26
   27
   30
   33
   35
   37
   35
   15
   18
   20
   20
   22
   17
   19
   18
   20
   29
   26
   29
   29
   24
   44
   29
   26
   29
   29
   29
   29
   23
   24
   44
   41
   29
   26
   28
   29
   29
   29
   28
   29
   26
   26
   26],
  :fl
  ["p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "r"
   "e"
   "r"
   "r"
   "r"
   "p"
   "p"
   "p"
   "p"
   "p"
   "r"
   "e"
   "r"
   "d"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "e"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "e"
   "r"
   "r"
   "r"
   "r"
   "e"
   "r"
   "r"
   "r"
   "r"
   "r"
   "e"
   "r"
   "r"
   "r"
   "e"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "p"
   "r"
   "r"
   "r"
   "p"
   "r"
   "r"
   "r"
   "c"
   "p"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "d"
   "r"
   "r"
   "r"
   "e"
   "r"
   "r"
   "p"
   "p"
   "r"
   "r"
   "p"
   "r"
   "p"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "p"
   "p"
   "r"
   "r"
   "p"
   "r"
   "r"
   "p"
   "p"
   "r"
   "p"
   "r"
   "r"
   "p"
   "r"
   "r"
   "r"
   "p"
   "r"
   "p"
   "r"
   "r"
   "r"
   "r"
   "p"
   "r"
   "p"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "r"
   "p"
   "p"
   "r"
   "d"
   "r"
   "r"
   "p"
   "p"
   "r"
   "r"
   "r"
   "r"
   "d"
   "d"
   "r"
   "r"
   "r"
   "r"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"
   "p"],
  :class
  ["compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "midsize"
   "midsize"
   "midsize"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "2seater"
   "2seater"
   "2seater"
   "2seater"
   "2seater"
   "suv"
   "suv"
   "suv"
   "suv"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "minivan"
   "minivan"
   "minivan"
   "minivan"
   "minivan"
   "minivan"
   "minivan"
   "minivan"
   "minivan"
   "minivan"
   "minivan"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "compact"
   "compact"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "suv"
   "suv"
   "suv"
   "suv"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "compact"
   "compact"
   "compact"
   "compact"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "suv"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "suv"
   "suv"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "pickup"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "compact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "subcompact"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"
   "midsize"]},
 :layers [nil nil],
 :scales nil,
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
 :theme [],
 :coordinates nil,
 :facet nil,
 :plot_env nil,
 :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}

```
:::

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ggplot.clj">projects/noj/notebooks/ggplot.clj</a></small></small></pre></div>

### 2024-02-01 docs/projects/noj/ml.qmd
noj - rerendered book

@@
        Min          1Q      Median          3Q         Max
-   -0.7943     -0.2312      0.0256      0.2059      0.8735
+   -0.8908     -0.2103      0.0371      0.2256      0.8160
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.7726     0.3098     5.7220     0.0000 ***
-sepal-width         0.6807     0.0824     8.2622     0.0000 ***
-petal-length        0.7112     0.0700    10.1639     0.0000 ***
-petal-width        -0.5768     0.1582    -3.6467     0.0004 ***
+Intercept           2.0708     0.3356     6.1706     0.0000 ***
+sepal-width         0.5954     0.0889     6.6968     0.0000 ***
+petal-length        0.6671     0.0715     9.3273     0.0000 ***
+petal-width        -0.4532     0.1618    -2.8002     0.0062 **
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3230 on 96 degrees of freedom
-Multiple R-squared: 0.8500,    Adjusted R-squared: 0.8453
-F-statistic: 181.3338 on 4 and 96 DF,  p-value: 2.062e-39
+Residual standard error: 0.3363 on 96 degrees of freedom
+Multiple R-squared: 0.8299,    Adjusted R-squared: 0.8246
+F-statistic: 156.1599 on 4 and 96 DF,  p-value: 8.448e-37
 

### 2024-02-03 docs/projects/noj/ggplot.qmd
Noj - rerendered

@@
 (ns ggplot
-  (:require [clojisr.v1.r :as r :refer [r]]
+  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
             [clojisr.v1.applications.plotting :as plotting]
@@
 </defs>
-<g id="surface36">
+<g id="surface6">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 (-> plot
-    r/r->clj)
+    r->clj
+    (dissoc :data))
 ```
@@
 ```clojure
-{:data
- {:manufacturer
-  ["audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "audi"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "chevrolet"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "dodge"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "ford"
-   "honda"
-   "honda"
-   "honda"
-   "honda"
-   "honda"
-   "honda"
-   "honda"
-   "honda"
-   "honda"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "hyundai"
-   "jeep"
-   "jeep"
-   "jeep"
-   "jeep"
-   "jeep"
-   "jeep"
-   "jeep"
-   "jeep"
-   "land rover"
-   "land rover"
-   "land rover"
-   "land rover"
-   "lincoln"
-   "lincoln"
-   "lincoln"
-   "mercury"
-   "mercury"
-   "mercury"
-   "mercury"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "nissan"
-   "pontiac"
-   "pontiac"
-   "pontiac"
-   "pontiac"
-   "pontiac"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "subaru"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "toyota"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"
-   "volkswagen"],
-  :model
-  ["a4"
-   "a4"
-   "a4"
-   "a4"
-   "a4"
-   "a4"
-   "a4"
-   "a4 quattro"
-   "a4 quattro"
-   "a4 quattro"
-   "a4 quattro"
-   "a4 quattro"
-   "a4 quattro"
-   "a4 quattro"
-   "a4 quattro"
-   "a6 quattro"
-   "a6 quattro"
-   "a6 quattro"
-   "c1500 suburban 2wd"
-   "c1500 suburban 2wd"
-   "c1500 suburban 2wd"
-   "c1500 suburban 2wd"
-   "c1500 suburban 2wd"
-   "corvette"
-   "corvette"
-   "corvette"
-   "corvette"
-   "corvette"
-   "k1500 tahoe 4wd"
-   "k1500 tahoe 4wd"
-   "k1500 tahoe 4wd"
-   "k1500 tahoe 4wd"
-   "malibu"
-   "malibu"
-   "malibu"
-   "malibu"
-   "malibu"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "caravan 2wd"
-   "dakota pickup 4wd"
-   "dakota pickup 4wd"
-   "dakota pickup 4wd"
-   "dakota pickup 4wd"
-   "dakota pickup 4wd"
-   "dakota pickup 4wd"
-   "dakota pickup 4wd"
-   "dakota pickup 4wd"
-   "dakota pickup 4wd"
-   "durango 4wd"
-   "durango 4wd"
-   "durango 4wd"
-   "durango 4wd"
-   "durango 4wd"
-   "durango 4wd"
-   "durango 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "ram 1500 pickup 4wd"
-   "expedition 2wd"
-   "expedition 2wd"
-   "expedition 2wd"
-   "explorer 4wd"
-   "explorer 4wd"
-   "explorer 4wd"
-   "explorer 4wd"
-   "explorer 4wd"
-   "explorer 4wd"
-   "f150 pickup 4wd"
-   "f150 pickup 4wd"
-   "f150 pickup 4wd"
-   "f150 pickup 4wd"
-   "f150 pickup 4wd"
-   "f150 pickup 4wd"
-   "f150 pickup 4wd"
-   "mustang"
-   "mustang"
-   "mustang"
-   "mustang"
-   "mustang"
-   "mustang"
-   "mustang"
-   "mustang"
-   "mustang"
-   "civic"
-   "civic"
-   "civic"
-   "civic"
-   "civic"
-   "civic"
-   "civic"
-   "civic"
-   "civic"
-   "sonata"
-   "sonata"
-   "sonata"
-   "sonata"
-   "sonata"
-   "sonata"
-   "sonata"
-   "tiburon"
-   "tiburon"
-   "tiburon"
-   "tiburon"
-   "tiburon"
-   "tiburon"
-   "tiburon"
-   "grand cherokee 4wd"
-   "grand cherokee 4wd"
-   "grand cherokee 4wd"
-   "grand cherokee 4wd"
-   "grand cherokee 4wd"
-   "grand cherokee 4wd"
-   "grand cherokee 4wd"
-   "grand cherokee 4wd"
-   "range rover"
-   "range rover"
-   "range rover"
-   "range rover"
-   "navigator 2wd"
-   "navigator 2wd"
-   "navigator 2wd"
-   "mountaineer 4wd"
-   "mountaineer 4wd"
-   "mountaineer 4wd"
-   "mountaineer 4wd"
-   "altima"
-   "altima"
-   "altima"
-   "altima"
-   "altima"
-   "altima"
-   "maxima"
-   "maxima"
-   "maxima"
-   "pathfinder 4wd"
-   "pathfinder 4wd"
-   "pathfinder 4wd"
-   "pathfinder 4wd"
-   "grand prix"
-   "grand prix"
-   "grand prix"
-   "grand prix"
-   "grand prix"
-   "forester awd"
-   "forester awd"
-   "forester awd"
-   "forester awd"
-   "forester awd"
-   "forester awd"
-   "impreza awd"
-   "impreza awd"
-   "impreza awd"
-   "impreza awd"
-   "impreza awd"
-   "impreza awd"
-   "impreza awd"
-   "impreza awd"
-   "4runner 4wd"
-   "4runner 4wd"
-   "4runner 4wd"
-   "4runner 4wd"
-   "4runner 4wd"
-   "4runner 4wd"
-   "camry"
-   "camry"
-   "camry"
-   "camry"
-   "camry"
-   "camry"
-   "camry"
-   "camry solara"
-   "camry solara"
-   "camry solara"
-   "camry solara"
-   "camry solara"
-   "camry solara"
-   "camry solara"
-   "corolla"
-   "corolla"
-   "corolla"
-   "corolla"
-   "corolla"
-   "land cruiser wagon 4wd"
-   "land cruiser wagon 4wd"
-   "toyota tacoma 4wd"
-   "toyota tacoma 4wd"
-   "toyota tacoma 4wd"
-   "toyota tacoma 4wd"
-   "toyota tacoma 4wd"
-   "toyota tacoma 4wd"
-   "toyota tacoma 4wd"
-   "gti"
-   "gti"
-   "gti"
-   "gti"
-   "gti"
-   "jetta"
-   "jetta"
-   "jetta"
-   "jetta"
-   "jetta"
-   "jetta"
-   "jetta"
-   "jetta"
-   "jetta"
-   "new beetle"
-   "new beetle"
-   "new beetle"
-   "new beetle"
-   "new beetle"
-   "new beetle"
-   "passat"
-   "passat"
-   "passat"
-   "passat"
-   "passat"
-   "passat"
-   "passat"],
-  :displ
-  [1.8
-   1.8
-   2.0
-   2.0
-   2.8
-   2.8
-   3.1
-   1.8
-   1.8
-   2.0
-   2.0
-   2.8
-   2.8
-   3.1
-   3.1
-   2.8
-   3.1
-   4.2
-   5.3
-   5.3
-   5.3
-   5.7
-   6.0
-   5.7
-   5.7
-   6.2
-   6.2
-   7.0
-   5.3
-   5.3
-   5.7
-   6.5
-   2.4
-   2.4
-   3.1
-   3.5
-   3.6
-   2.4
-   3.0
-   3.3
-   3.3
-   3.3
-   3.3
-   3.3
-   3.8
-   3.8
-   3.8
-   4.0
-   3.7
-   3.7
-   3.9
-   3.9
-   4.7
-   4.7
-   4.7
-   5.2
-   5.2
-   3.9
-   4.7
-   4.7
-   4.7
-   5.2
-   5.7
-   5.9
-   4.7
-   4.7
-   4.7
-   4.7
-   4.7
-   4.7
-   5.2
-   5.2
-   5.7
-   5.9
-   4.6
-   5.4
-   5.4
-   4.0
-   4.0
-   4.0
-   4.0
-   4.6
-   5.0
-   4.2
-   4.2
-   4.6
-   4.6
-   4.6
-   5.4
-   5.4
-   3.8
-   3.8
-   4.0
-   4.0
-   4.6
-   4.6
-   4.6
-   4.6
-   5.4
-   1.6
-   1.6
-   1.6
-   1.6
-   1.6
-   1.8
-   1.8
-   1.8
-   2.0
-   2.4
-   2.4
-   2.4
-   2.4
-   2.5
-   2.5
-   3.3
-   2.0
-   2.0
-   2.0
-   2.0
-   2.7
-   2.7
-   2.7
-   3.0
-   3.7
-   4.0
-   4.7
-   4.7
-   4.7
-   5.7
-   6.1
-   4.0
-   4.2
-   4.4
-   4.6
-   5.4
-   5.4
-   5.4
-   4.0
-   4.0
-   4.6
-   5.0
-   2.4
-   2.4
-   2.5
-   2.5
-   3.5
-   3.5
-   3.0
-   3.0
-   3.5
-   3.3
-   3.3
-   4.0
-   5.6
-   3.1
-   3.8
-   3.8
-   3.8
-   5.3
-   2.5
-   2.5
-   2.5
-   2.5
-   2.5
-   2.5
-   2.2
-   2.2
-   2.5
-   2.5
-   2.5
-   2.5
-   2.5
-   2.5
-   2.7
-   2.7
-   3.4
-   3.4
-   4.0
-   4.7
-   2.2
-   2.2
-   2.4
-   2.4
-   3.0
-   3.0
-   3.5
-   2.2
-   2.2
-   2.4
-   2.4
-   3.0
-   3.0
-   3.3
-   1.8
-   1.8
-   1.8
-   1.8
-   1.8
-   4.7
-   5.7
-   2.7
-   2.7
-   2.7
-   3.4
-   3.4
-   4.0
-   4.0
-   2.0
-   2.0
-   2.0
-   2.0
-   2.8
-   1.9
-   2.0
-   2.0
-   2.0
-   2.0
-   2.5
-   2.5
-   2.8
-   2.8
-   1.9
-   1.9
-   2.0
-   2.0
-   2.5
-   2.5
-   1.8
-   1.8
-   2.0
-   2.0
-   2.8
-   2.8
-   3.6],
-  :year
-  [1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   2008
-   2008
-   2008
-   2008
-   2008
-   1999
-   2008
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   1999
-   2008
-   1999
-   2008
-   2008
-   1999
-   1999
-   1999
-   1999
-   2008
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   2008
-   1999
-   1999
-   1999
-   2008
-   2008
-   2008
-   1999
-   2008
-   1999
-   2008
-   2008
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   2008
-   1999
-   1999
-   1999
-   2008
-   1999
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   1999
-   1999
-   1999
-   2008
-   1999
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   2008
-   1999
-   1999
-   1999
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   1999
-   2008
-   2008
-   1999
-   1999
-   1999
-   2008
-   1999
-   2008
-   2008
-   1999
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   1999
-   1999
-   1999
-   2008
-   2008
-   1999
-   2008
-   1999
-   1999
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   1999
-   1999
-   2008
-   2008
-   2008
-   2008
-   1999
-   1999
-   1999
-   1999
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008
-   2008
-   1999
-   1999
-   2008],
-  :cyl
-  [4
-   4
-   4
-   4
-   6
-   6
-   6
-   4
-   4
-   4
-   4
-   6
-   6
-   6
-   6
-   6
-   6
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   4
-   4
-   6
-   6
-   6
-   4
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   8
-   8
-   8
-   8
-   8
-   6
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   6
-   6
-   6
-   6
-   8
-   8
-   6
-   6
-   8
-   8
-   8
-   8
-   8
-   6
-   6
-   6
-   6
-   8
-   8
-   8
-   8
-   8
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   6
-   6
-   6
-   4
-   4
-   4
-   4
-   6
-   6
-   6
-   6
-   6
-   6
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   8
-   6
-   6
-   8
-   8
-   4
-   4
-   4
-   4
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   6
-   8
-   6
-   6
-   6
-   6
-   8
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   4
-   6
-   6
-   6
-   8
-   4
-   4
-   4
-   4
-   6
-   6
-   6
-   4
-   4
-   4
-   4
-   6
-   6
-   6
-   4
-   4
-   4
-   4
-   4
-   8
-   8
-   4
-   4
-   4
-   6
-   6
-   6
-   6
-   4
-   4
-   4
-   4
-   6
-   4
-   4
-   4
-   4
-   4
-   5
-   5
-   6
-   6
-   4
-   4
-   4
-   4
-   5
-   5
-   4
-   4
-   4
-   4
-   6
-   6
-   6],
-  :trans
-  ["auto(l5)"
-   "manual(m5)"
-   "manual(m6)"
-   "auto(av)"
-   "auto(l5)"
-   "manual(m5)"
-   "auto(av)"
-   "manual(m5)"
-   "auto(l5)"
-   "manual(m6)"
-   "auto(s6)"
-   "auto(l5)"
-   "manual(m5)"
-   "auto(s6)"
-   "manual(m6)"
-   "auto(l5)"
-   "auto(s6)"
-   "auto(s6)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "manual(m6)"
-   "auto(l4)"
-   "manual(m6)"
-   "auto(s6)"
-   "manual(m6)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(s6)"
-   "auto(l3)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l6)"
-   "auto(l6)"
-   "manual(m6)"
-   "auto(l4)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l5)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l4)"
-   "auto(l5)"
-   "auto(l4)"
-   "manual(m6)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l5)"
-   "manual(m6)"
-   "manual(m6)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l6)"
-   "auto(l5)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l6)"
-   "auto(l4)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l5)"
-   "manual(m6)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l5)"
-   "manual(m6)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(l4)"
-   "manual(m6)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l4)"
-   "auto(s6)"
-   "auto(s6)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l6)"
-   "auto(l5)"
-   "auto(l5)"
-   "auto(l6)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(av)"
-   "manual(m6)"
-   "manual(m6)"
-   "auto(av)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(av)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(s5)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(s4)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(s4)"
-   "auto(s4)"
-   "manual(m5)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l5)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(s6)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(s5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(s5)"
-   "auto(l3)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(l4)"
-   "auto(s6)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m6)"
-   "auto(l5)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m6)"
-   "auto(s6)"
-   "manual(m5)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "auto(s6)"
-   "manual(m6)"
-   "auto(s6)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(l4)"
-   "manual(m5)"
-   "auto(s6)"
-   "manual(m5)"
-   "auto(l5)"
-   "auto(s6)"
-   "manual(m6)"
-   "auto(l5)"
-   "manual(m5)"
-   "auto(s6)"],
-  :drv
-  ["f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "4"
-   "4"
-   "4"
-   "4"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "r"
-   "r"
-   "r"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "r"
-   "r"
-   "r"
-   "4"
-   "4"
-   "4"
-   "4"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "4"
-   "4"
-   "4"
-   "4"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "4"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"
-   "f"],
-  :cty
-  [18
-   21
-   20
-   21
-   16
-   18
-   18
-   18
-   16
-   20
-   19
-   15
-   17
-   17
-   15
-   15
-   17
-   16
-   14
-   11
-   14
-   13
-   12
-   16
-   15
-   16
-   15
-   15
-   14
-   11
-   11
-   14
-   19
-   22
-   18
-   18
-   17
-   18
-   17
-   16
-   16
-   17
-   17
-   11
-   15
-   15
-   16
-   16
-   15
-   14
-   13
-   14
-   14
-   14
-   9
-   11
-   11
-   13
-   13
-   9
-   13
-   11
-   13
-   11
-   12
-   9
-   13
-   13
-   12
-   9
-   11
-   11
-   13
-   11
-   11
-   11
-   12
-   14
-   15
-   14
-   13
-   13
-   13
-   14
-   14
-   13
-   13
-   13
-   11
-   13
-   18
-   18
-   17
-   16
-   15
-   15
-   15
-   15
-   14
-   28
-   24
-   25
-   23
-   24
-   26
-   25
-   24
-   21
-   18
-   18
-   21
-   21
-   18
-   18
-   19
-   19
-   19
-   20
-   20
-   17
-   16
-   17
-   17
-   15
-   15
-   14
-   9
-   14
-   13
-   11
-   11
-   12
-   12
-   11
-   11
-   11
-   12
-   14
-   13
-   13
-   13
-   21
-   19
-   23
-   23
-   19
-   19
-   18
-   19
-   19
-   14
-   15
-   14
-   12
-   18
-   16
-   17
-   18
-   16
-   18
-   18
-   20
-   19
-   20
-   18
-   21
-   19
-   19
-   19
-   20
-   20
-   19
-   20
-   15
-   16
-   15
-   15
-   16
-   14
-   21
-   21
-   21
-   21
-   18
-   18
-   19
-   21
-   21
-   21
-   22
-   18
-   18
-   18
-   24
-   24
-   26
-   28
-   26
-   11
-   13
-   15
-   16
-   17
-   15
-   15
-   15
-   16
-   21
-   19
-   21
-   22
-   17
-   33
-   21
-   19
-   22
-   21
-   21
-   21
-   16
-   17
-   35
-   29
-   21
-   19
-   20
-   20
-   21
-   18
-   19
-   21
-   16
-   18
-   17],
-  :hwy
-  [29
-   29
-   31
-   30
-   26
-   26
-   27
-   26
-   25
-   28
-   27
-   25
-   25
-   25
-   25
-   24
-   25
-   23
-   20
-   15
-   20
-   17
-   17
-   26
-   23
-   26
-   25
-   24
-   19
-   14
-   15
-   17
-   27
-   30
-   26
-   29
-   26
-   24
-   24
-   22
-   22
-   24
-   24
-   17
-   22
-   21
-   23
-   23
-   19
-   18
-   17
-   17
-   19
-   19
-   12
-   17
-   15
-   17
-   17
-   12
-   17
-   16
-   18
-   15
-   16
-   12
-   17
-   17
-   16
-   12
-   15
-   16
-   17
-   15
-   17
-   17
-   18
-   17
-   19
-   17
-   19
-   19
-   17
-   17
-   17
-   16
-   16
-   17
-   15
-   17
-   26
-   25
-   26
-   24
-   21
-   22
-   23
-   22
-   20
-   33
-   32
-   32
-   29
-   32
-   34
-   36
-   36
-   29
-   26
-   27
-   30
-   31
-   26
-   26
-   28
-   26
-   29
-   28
-   27
-   24
-   24
-   24
-   22
-   19
-   20
-   17
-   12
-   19
-   18
-   14
-   15
-   18
-   18
-   15
-   17
-   16
-   18
-   17
-   19
-   19
-   17
-   29
-   27
-   31
-   32
-   27
-   26
-   26
-   25
-   25
-   17
-   17
-   20
-   18
-   26
-   26
-   27
-   28
-   25
-   25
-   24
-   27
-   25
-   26
-   23
-   26
-   26
-   26
-   26
-   25
-   27
-   25
-   27
-   20
-   20
-   19
-   17
-   20
-   17
-   29
-   27
-   31
-   31
-   26
-   26
-   28
-   27
-   29
-   31
-   31
-   26
-   26
-   27
-   30
-   33
-   35
-   37
-   35
-   15
-   18
-   20
-   20
-   22
-   17
-   19
-   18
-   20
-   29
-   26
-   29
-   29
-   24
-   44
-   29
-   26
-   29
-   29
-   29
-   29
-   23
-   24
-   44
-   41
-   29
-   26
-   28
-   29
-   29
-   29
-   28
-   29
-   26
-   26
-   26],
-  :fl
-  ["p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "r"
-   "e"
-   "r"
-   "r"
-   "r"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "r"
-   "e"
-   "r"
-   "d"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "e"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "e"
-   "r"
-   "r"
-   "r"
-   "r"
-   "e"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "e"
-   "r"
-   "r"
-   "r"
-   "e"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "p"
-   "r"
-   "r"
-   "r"
-   "p"
-   "r"
-   "r"
-   "r"
-   "c"
-   "p"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "d"
-   "r"
-   "r"
-   "r"
-   "e"
-   "r"
-   "r"
-   "p"
-   "p"
-   "r"
-   "r"
-   "p"
-   "r"
-   "p"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "p"
-   "p"
-   "r"
-   "r"
-   "p"
-   "r"
-   "r"
-   "p"
-   "p"
-   "r"
-   "p"
-   "r"
-   "r"
-   "p"
-   "r"
-   "r"
-   "r"
-   "p"
-   "r"
-   "p"
-   "r"
-   "r"
-   "r"
-   "r"
-   "p"
-   "r"
-   "p"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "r"
-   "p"
-   "p"
-   "r"
-   "d"
-   "r"
-   "r"
-   "p"
-   "p"
-   "r"
-   "r"
-   "r"
-   "r"
-   "d"
-   "d"
-   "r"
-   "r"
-   "r"
-   "r"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"
-   "p"],
-  :class
-  ["compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "midsize"
-   "midsize"
-   "midsize"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "2seater"
-   "2seater"
-   "2seater"
-   "2seater"
-   "2seater"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "minivan"
-   "minivan"
-   "minivan"
-   "minivan"
-   "minivan"
-   "minivan"
-   "minivan"
-   "minivan"
-   "minivan"
-   "minivan"
-   "minivan"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "compact"
-   "compact"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "suv"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "suv"
-   "suv"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "pickup"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "compact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "subcompact"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"
-   "midsize"]},
- :layers [nil nil],
+{:layers [nil nil],
  :scales nil,
@@
 
+Trying to mimic [cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list (WIP):
+
+::: {.sourceClojure}
+```clojure
+(let [f (-> plot
+            (r$ 'facet)
+            (r$ 'params)
+            (r$ 'facets))]
+  (when (-> `(is.null ~f)
+            r
+            r->clj)
+    (let [facet (-> `(ls ~f)
+                    r
+                    (r->clj)
+                    first)]
+      {:facet facet
+       :facet-levels (-> plot
+                         (r$ 'data)
+                         (r/bra facet))})))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:facet "cyl", :facet-levels # A tibble: 234 × 1
+     cyl
+   &lt;int&gt;
+ 1     4
+ 2     4
+ 3     4
+ 4     4
+ 5     6
+ 6     6
+ 7     6
+ 8     4
+ 9     4
+10     4
+# ℹ 224 more rows
+}
+
+```
+:::
+
 <div style="background-color:grey;height:2px;width:100%;"></div>

### 2024-02-03 docs/projects/noj/ml.qmd
Noj - rerendered

@@
        Min          1Q      Median          3Q         Max
-   -0.8908     -0.2103      0.0371      0.2256      0.8160
+   -0.8557     -0.1977      0.0083      0.1911      0.8454
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           2.0708     0.3356     6.1706     0.0000 ***
-sepal-width         0.5954     0.0889     6.6968     0.0000 ***
-petal-length        0.6671     0.0715     9.3273     0.0000 ***
-petal-width        -0.4532     0.1618    -2.8002     0.0062 **
+Intercept           2.0204     0.3078     6.5649     0.0000 ***
+sepal-width         0.5955     0.0814     7.3147     0.0000 ***
+petal-length        0.7028     0.0686    10.2518     0.0000 ***
+petal-width        -0.5389     0.1507    -3.5765     0.0005 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3363 on 96 degrees of freedom
-Multiple R-squared: 0.8299,    Adjusted R-squared: 0.8246
-F-statistic: 156.1599 on 4 and 96 DF,  p-value: 8.448e-37
+Residual standard error: 0.3055 on 96 degrees of freedom
+Multiple R-squared: 0.8637,    Adjusted R-squared: 0.8594
+F-statistic: 202.7159 on 4 and 96 DF,  p-value: 2.121e-41
 

### 2024-02-04 docs/projects/noj/ggplot.qmd
Noj -rerendered

@@
 # Exploring ggplot
+following
+[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list
+in representing a plot as a data structure.
 
@@
 </defs>
-<g id="surface6">
+<g id="surface11">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 
-Trying to mimic [cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list (WIP):
-
 ::: {.sourceClojure}
 ```clojure
-(let [f (-> plot
+(defn gg-facet [ggplot]
+  (let [f (-> ggplot
               (r$ 'facet)
@@
               r->clj)
-    (let [facet (-> `(ls ~f)
-                    r
-                    (r->clj)
-                    first)]
+      (let [facet (r `(ls ~f))]
         {:facet facet
@@
                            (r$ 'data)
-                         (r/bra facet))})))
+                           (r/bra facet))}))))
 ```
@@
 
+::: {.sourceClojure}
+```clojure
+(-> plot
+    gg-facet
+    (update-vals r->clj))
+```
+:::
+
+<div style="max-height:600px;overflow-y:auto;"><div><p>{</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet ["cyl"]</code></pre></div><table><tr><td valign="top"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet-levels
+</code></pre></div></div></td><td><div style="margin-left:10px;"><div><p>_unnamed \[234 1\]:</p><table class="table"><thead><tr><th style="text-align:right;">:cyl</th></tr></thead><tbody><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">...</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">5</td></tr><tr><td style="text-align:right;">5</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">6</td></tr></tbody></table></div></div></td></tr></table></div><p>}</p></div></div>
+
+::: {.sourceClojure}
+```clojure
+(r/require-r '[base])
+```
+:::
+
 ::: {.printedClojure}
 ```clojure
-{:facet "cyl", :facet-levels # A tibble: 234 × 1
-     cyl
-   &lt;int&gt;
- 1     4
- 2     4
- 3     4
- 4     4
- 5     6
- 6     6
- 7     6
- 8     4
- 9     4
-10     4
-# ℹ 224 more rows
-}
+nil
 
@@
 
+::: {.sourceClojure}
+```clojure
+(defn ->clj
+  ([r-obj avoid]
+   (->clj r-obj avoid []))
+  ([r-obj avoid path]
+   (prn path)
+   (let [relevant-names (some->> r-obj
+                                 r.base/names
+                                 r->clj
+                                 (filter (complement avoid)))]
+     (cond
+       ;;
+       ;; a named list or a ggproto object
+       (seq relevant-names) (->> relevant-names
+                                 (map (fn [nam]
+                                        [(keyword nam) (-> r-obj
+                                                           (r$ nam)
+                                                           (->clj avoid
+                                                                  (conj path nam)))]))
+                                 (into {}))
+       ;;
+       ;; a ggproto method
+       (-> r-obj
+           r.base/class
+           r->clj
+           first
+           (= "ggproto_method"))
+       :ggproto-method
+       ;;
+       ;; an unnamed list
+       (-> r-obj
+           r.base/is-list
+           r->clj
+           first)
+       (-> r-obj
+           r.base/length
+           r->clj
+           first
+           range
+           (->> (mapv (fn [i]
+                        (prn [path (inc i)])
+                        (-> r-obj
+                            (r/brabra (inc i))
+                            (->clj avoid
+                                   (conj path [i])))))))
+       ;;
+       (r.base/is-function r-obj) :function
+       (r.base/is-atomic r-obj) (r->clj r-obj)
+       :else r-obj))))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> plot
+    (->clj #{"data" "plot_env"}))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend :function,
+   :mapping :function,
+   :super :ggproto-method,
+   :computed_stat_params {:na.rm :function},
+   :inherit.aes :function,
+   :geom_params {:na.rm :function},
+   :geom
+   {:non_missing_aes :function,
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape :function,
+     :colour :function,
+     :size :function,
+     :fill :function,
+     :alpha :function,
+     :stroke :function},
+    :super :ggproto-method,
+    :required_aes :function,
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm :function},
+   :constructor :function,
+   :computed_mapping {:x :function, :y :function, :colour :function},
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :computed_geom_params {:na.rm :function}}
+  {:aes_params [],
+   :stat
+   {:extra_params :function,
+    :super :ggproto-method,
+    :compute_group :ggproto-method,
+    :required_aes :function,
+    :setup_params :ggproto-method,
+    :dropped_aes :function},
+   :show.legend :function,
+   :mapping :function,
+   :super :ggproto-method,
+   :computed_stat_params
+   {:na.rm :function,
+    :method :function,
+    :n :function,
+    :orientation :function,
+    :level :function,
+    :fullrange :function,
+    :flipped_aes :function,
+    :se :function,
+    :formula :function,
+    :method.args [],
+    :span :function},
+   :inherit.aes :function,
+   :geom_params
+   {:se :function, :na.rm :function, :orientation :function},
+   :geom
+   {:setup_params :ggproto-method,
+    :super :ggproto-method,
+    :draw_key :ggproto-method,
+    :extra_params :function,
+    :required_aes :function,
+    :draw_group :ggproto-method,
+    :optional_aes :function,
+    :rename_size :function,
+    :setup_data :ggproto-method,
+    :default_aes
+    {:colour :function,
+     :fill :function,
+     :linewidth :function,
+     :linetype :function,
+     :weight :function,
+     :alpha :function}},
+   :stat_params
+   {:na.rm :function,
+    :method :function,
+    :n :function,
+    :orientation :function,
+    :level :function,
+    :fullrange :function,
+    :se :function,
+    :formula :function,
+    :method.args [],
+    :span :function},
+   :constructor {: :function, :method :function},
+   :computed_mapping {:x :function, :y :function, :colour :function},
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :computed_geom_params
+   {:se :function,
+    :na.rm :function,
+    :orientation :function,
+    :flipped_aes :function}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x :function, :y :function, :colour :function},
+ :theme [],
+ :coordinates
+ {:expand :function,
+  :clip :function,
+  :limits {:x :function, :y :function},
+  :super :ggproto-method,
+  :default :function},
+ :facet
+ {:params
+  {:dir :function,
+   :nrow :function,
+   :as.table :function,
+   :free {:x :function, :y :function},
+   :drop :function,
+   :strip.position :function,
+   :ncol :function,
+   :facets {:cyl :function},
+   :labeller :function},
+  :shrink :function,
+  :super :ggproto-method},
+ :labels {:x :function, :y :function, :colour :function}}
+
+```
+:::
+
 <div style="background-color:grey;height:2px;width:100%;"></div>

### 2024-02-04 docs/projects/noj/ml.qmd
Noj -rerendered

--- 2024-02-01 docs/projects/noj/ml.qmd
@@
        Min          1Q      Median          3Q         Max
-   -0.8908     -0.2103      0.0371      0.2256      0.8160
+   -0.7870     -0.2330      0.0191      0.1918      0.8921
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           2.0708     0.3356     6.1706     0.0000 ***
-sepal-width         0.5954     0.0889     6.6968     0.0000 ***
-petal-length        0.6671     0.0715     9.3273     0.0000 ***
-petal-width        -0.4532     0.1618    -2.8002     0.0062 **
+Intercept           1.8173     0.3337     5.4454     0.0000 ***
+sepal-width         0.6625     0.0869     7.6273     0.0000 ***
+petal-length        0.7158     0.0749     9.5532     0.0000 ***
+petal-width        -0.5929     0.1640    -3.6144     0.0005 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3363 on 96 degrees of freedom
-Multiple R-squared: 0.8299,    Adjusted R-squared: 0.8246
-F-statistic: 156.1599 on 4 and 96 DF,  p-value: 8.448e-37
+Residual standard error: 0.3308 on 96 degrees of freedom
+Multiple R-squared: 0.8280,    Adjusted R-squared: 0.8227
+F-statistic: 154.0902 on 4 and 96 DF,  p-value: 1.435e-36
 

### 2024-02-05 docs/projects/noj/ggplot.qmd
Noj - rerendered

--- 2024-02-03 docs/projects/noj/ggplot.qmd
@@
 </style>
-<script src="ggplot_files/md-default0.js" type="text/javascript"></script><script src="ggplot_files/md-default1.js" type="text/javascript"></script>
-<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
+<script src="ggplot_files/md-default5.js" type="text/javascript"></script><script src="ggplot_files/md-default6.js" type="text/javascript"></script>
+
+```{=html}
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+```
 
 # Exploring ggplot
+following
+[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list
+in representing a plot as a data structure.
 
@@
             [clojisr.v1.applications.plotting :as plotting]
-            [scicloj.kindly.v4.kind :as kind]))
+            [scicloj.kindly.v4.kind :as kind]
+            [clojure.walk :as walk]
+            [tablecloth.api :as tc]))
 ```
@@
 
+```{=html}
 <?xml version="1.0" encoding="UTF-8"?>
@@
 </defs>
-<g id="surface6">
+<g id="surface428">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 
+```
+
 ::: {.sourceClojure}
@@
                            (r$ 'data)
-                         (r/bra facet))})))
+                           (r/bra facet))}))))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> plot
+    gg-facet
+    (update-vals r->clj))
+```
+:::
+
+```{=html}
+<div><p>{</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet ["cyl"]</code></pre></div><table><tr><td valign="top"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet-levels
+</code></pre></div></td><td><div style="margin-left:10px;"><span data-qmd="_unnamed [234 1]:
+
+| :cyl |
+|-----:|
+|    4 |
+|    4 |
+|    4 |
+|    4 |
+|    6 |
+|    6 |
+|    6 |
+|    4 |
+|    4 |
+|    4 |
+|  ... |
+|    4 |
+|    4 |
+|    5 |
+|    5 |
+|    4 |
+|    4 |
+|    4 |
+|    4 |
+|    6 |
+|    6 |
+|    6 |
+
+"></span></div></td></tr></table></div><p>}</p></div>
+```
+
+::: {.sourceClojure}
+```clojure
+(r/require-r '[base])
 ```
@@
 ```clojure
-{:facet "cyl", :facet-levels # A tibble: 234 × 1
-     cyl
-   &lt;int&gt;
- 1     4
- 2     4
- 3     4
- 4     4
- 5     6
- 6     6
- 7     6
- 8     4
- 9     4
-10     4
-# ℹ 224 more rows
-}
-
-```
-:::
-
+nil
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn ggolot->clj
+  ([r-obj
+    options]
+   (ggolot->clj r-obj options []))
+  ([r-obj
+    {:as options
+     :keys [avoid]}
+    path]
+   #_(prn path)
+   (let [relevant-names (some->> r-obj
+                                 r.base/names
+                                 r->clj
+                                 (filter (complement avoid)))]
+     (cond
+       ;;
+       ;; a named list or a ggproto object
+       (seq relevant-names) (->> relevant-names
+                                 (map (fn [nam]
+                                        [(keyword nam) (-> r-obj
+                                                           (r$ nam)
+                                                           (ggolot->clj options
+                                                                        (conj path nam)))]))
+                                 (into {}))
+       ;;
+       ;; a ggproto method
+       (-> r-obj
+           r.base/class
+           r->clj
+           first
+           (= "ggproto_method"))
+       :ggproto-method
+       ;;
+       ;; an unnamed list
+       (-> r-obj
+           r.base/is-list
+           r->clj
+           first)
+       (-> r-obj
+           r.base/length
+           r->clj
+           first
+           range
+           (->> (mapv (fn [i]
+                        (prn [path (inc i)])
+                        (-> r-obj
+                            (r/brabra (inc i))
+                            (ggolot->clj options
+                                         (conj path [i])))))))
+       ;;
+       (r.base/is-atomic r-obj) (try (r->clj r-obj)
+                                     (catch Exception e
+                                       (-> r-obj println with-out-str)))
+       :else r-obj))))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, aes(cty, hwy))
+         + geom_point())"
+    r
+    (ggolot->clj {:avoid #{"data" "plot_env"}}))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"]}}
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn h4 [title]
+  (kind/hiccup [:h3 title]))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn ggplot-summary [r-code]
+  (let [plot (r r-code)
+        clj (-> plot
+                (ggolot->clj {:avoid #{"data" "plot_env"}})
+                (->> (walk/postwalk (fn [form]
+                                      (if (and (symbol? form)
+                                               (-> form str (= "~")))
+                                        (str form)
+                                        form)))))]
+    (kind/fragment
+     [(h4 "code")
+      (kind/md
+       (format "\n```{r eval=FALSE}\n%s\n```\n"
+               r-code))
+      (h4 "image")
+      (plotting/plot->buffered-image plot)
+      (h4 "clj")
+      (kind/pprint clj)])))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy))
+         + geom_point())")
+```
+:::
+
+```{=html}
+<h3>code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy))
+         + geom_point())
+```
+
+```{=html}
+<h3>image</h3>
+```
+
+```{=html}
+<img src="ggplot_files/0.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj</h3>
+```
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x ["~" cty], :y ["~" hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"]}}
+
+```
+:::
+
+## Exlploring a few plots
+
+### A scatterplot
+
+::: {.sourceClojure}
+```clojure
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy))
+         + geom_point())")
+```
+:::
+
+```{=html}
+<h3>code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy))
+         + geom_point())
+```
+
+```{=html}
+<h3>image</h3>
+```
+
+```{=html}
+<img src="ggplot_files/1.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj</h3>
+```
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x ["~" cty], :y ["~" hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"]}}
+
+```
+:::
+
+### A scatterplot with colours
+
+::: {.sourceClojure}
+```clojure
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point())")
+```
+:::
+
+```{=html}
+<h3>code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point())
+```
+
+```{=html}
+<h3>image</h3>
+```
+
+```{=html}
+<img src="ggplot_files/2.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj</h3>
+```
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x ["~" cty], :y ["~" hwy], :colour ["~" [factor cyl]]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
+
+```
+:::
+
+### A scatterplot with colours and smoothing
+
+::: {.sourceClojure}
+```clojure
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method=\"lm\"))")
+```
+:::
+
+```{=html}
+<h3>code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method="lm"))
+```
+
+```{=html}
+<h3>image</h3>
+```
+
+```{=html}
+<img src="ggplot_files/3.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj</h3>
+```
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position {:compute_layer :ggproto-method, :super :ggproto-method}}
+  {:aes_params [],
+   :stat
+   {:extra_params ["na.rm" "orientation"],
+    :super :ggproto-method,
+    :compute_group :ggproto-method,
+    :required_aes ["x" "y"],
+    :setup_params :ggproto-method,
+    :dropped_aes ["weight"]},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
+   :geom
+   {:setup_params :ggproto-method,
+    :super :ggproto-method,
+    :draw_key :ggproto-method,
+    :extra_params ["na.rm" "orientation"],
+    :required_aes ["x" "y"],
+    :draw_group :ggproto-method,
+    :optional_aes ["ymin" "ymax"],
+    :rename_size [true],
+    :setup_data :ggproto-method,
+    :default_aes
+    {:colour ["#3366FF"],
+     :fill ["grey60"],
+     :linewidth [1.0],
+     :linetype [1.0],
+     :weight [1.0],
+     :alpha [0.4]}},
+   :stat_params
+   {:na.rm [false],
+    :method ["lm"],
+    :n [80.0],
+    :orientation [nil],
+    :level [0.95],
+    :fullrange [false],
+    :se [true],
+    :formula nil,
+    :method.args [],
+    :span [0.75]},
+   :constructor {: nil, :method ["lm"]},
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x ["~" cty], :y ["~" hwy], :colour ["~" [factor cyl]]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
+
+```
+:::
+
+### A scatterplot with colours, smoothing, and facets
+
+::: {.sourceClojure}
+```clojure
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method=\"lm\")
+         + facet_wrap(~cyl))")
+```
+:::
+
+```{=html}
+<h3>code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method="lm")
+         + facet_wrap(~cyl))
+```
+
+```{=html}
+<h3>image</h3>
+```
+
+```{=html}
+<img src="ggplot_files/4.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj</h3>
+```
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position {:compute_layer :ggproto-method, :super :ggproto-method}}
+  {:aes_params [],
+   :stat
+   {:extra_params ["na.rm" "orientation"],
+    :super :ggproto-method,
+    :compute_group :ggproto-method,
+    :required_aes ["x" "y"],
+    :setup_params :ggproto-method,
+    :dropped_aes ["weight"]},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
+   :geom
+   {:setup_params :ggproto-method,
+    :super :ggproto-method,
+    :draw_key :ggproto-method,
+    :extra_params ["na.rm" "orientation"],
+    :required_aes ["x" "y"],
+    :draw_group :ggproto-method,
+    :optional_aes ["ymin" "ymax"],
+    :rename_size [true],
+    :setup_data :ggproto-method,
+    :default_aes
+    {:colour ["#3366FF"],
+     :fill ["grey60"],
+     :linewidth [1.0],
+     :linetype [1.0],
+     :weight [1.0],
+     :alpha [0.4]}},
+   :stat_params
+   {:na.rm [false],
+    :method ["lm"],
+    :n [80.0],
+    :orientation [nil],
+    :level [0.95],
+    :fullrange [false],
+    :se [true],
+    :formula nil,
+    :method.args [],
+    :span [0.75]},
+   :constructor {: nil, :method ["lm"]},
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x ["~" cty], :y ["~" hwy], :colour ["~" [factor cyl]]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet
+ {:params
+  {:dir ["h"],
+   :nrow nil,
+   :as.table [true],
+   :free {:x [false], :y [false]},
+   :drop [true],
+   :strip.position ["top"],
+   :ncol nil,
+   :facets {:cyl ["~" cyl]},
+   :labeller
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55eafa698ac0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+  :shrink [true],
+  :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
+
+```
+:::
+
+```{=html}
 <div style="background-color:grey;height:2px;width:100%;"></div>
-
+```
+
+```{=html}
 <div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ggplot.clj">projects/noj/notebooks/ggplot.clj</a></small></small></pre></div>
+```

### 2024-02-05 docs/projects/noj/index.qmd
Noj - rerendered

@@
 <script src="index_files/md-default0.js" type="text/javascript"></script><script src="index_files/md-default1.js" type="text/javascript"></script>
-<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
+
+```{=html}
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+```
 
@@
 
+```{=html}
 <div style="background-color:grey;height:2px;width:100%;"></div>
+```
 
+```{=html}
 <div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/index.clj">projects/noj/notebooks/index.clj</a></small></small></pre></div>
+```

### 2024-02-05 docs/projects/noj/ml.qmd
Noj - rerendered

--- 2024-02-01 docs/projects/noj/ml.qmd
@@
 <script src="ml_files/md-default0.js" type="text/javascript"></script><script src="ml_files/md-default1.js" type="text/javascript"></script>
-<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
+
+```{=html}
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+```
 
@@
        Min          1Q      Median          3Q         Max
-   -0.8908     -0.2103      0.0371      0.2256      0.8160
+   -0.7904     -0.2163      0.0132      0.1774      0.8282
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           2.0708     0.3356     6.1706     0.0000 ***
-sepal-width         0.5954     0.0889     6.6968     0.0000 ***
-petal-length        0.6671     0.0715     9.3273     0.0000 ***
-petal-width        -0.4532     0.1618    -2.8002     0.0062 **
+Intercept           2.1092     0.2799     7.5344     0.0000 ***
+sepal-width         0.5826     0.0743     7.8394     0.0000 ***
+petal-length        0.7037     0.0624    11.2696     0.0000 ***
+petal-width        -0.5557     0.1425    -3.8986     0.0002 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3363 on 96 degrees of freedom
-Multiple R-squared: 0.8299,    Adjusted R-squared: 0.8246
-F-statistic: 156.1599 on 4 and 96 DF,  p-value: 8.448e-37
+Residual standard error: 0.3015 on 96 degrees of freedom
+Multiple R-squared: 0.8707,    Adjusted R-squared: 0.8667
+F-statistic: 215.5039 on 4 and 96 DF,  p-value: 1.668e-42
 
@@
 
+```{=html}
 <div style="background-color:grey;height:2px;width:100%;"></div>
+```
 
+```{=html}
 <div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ml.clj">projects/noj/notebooks/ml.clj</a></small></small></pre></div>
+```

### 2024-02-05 docs/projects/noj/ggplot.qmd
Noj - rerendered

--- 2024-02-03 docs/projects/noj/ggplot.qmd
@@
 </style>
-<script src="ggplot_files/md-default0.js" type="text/javascript"></script><script src="ggplot_files/md-default1.js" type="text/javascript"></script>
-<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
+<script src="ggplot_files/md-default4.js" type="text/javascript"></script><script src="ggplot_files/md-default5.js" type="text/javascript"></script><script src="ggplot_files/portal6.js" type="text/javascript"></script>
+
+```{=html}
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+```
 
 # Exploring ggplot
+Here we explore [ggplot2](https://ggplot2.tidyverse.org/) from Clojure. The goal is to eventually implement a similar grammar in Clojure.
+
+## Setup
+We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.
 
@@
 ```clojure
-(def plot
-  (r "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+(r/require-r '[base])
+```
+:::
+
+::: {.printedClojure}
+```clojure
+nil
+
+```
+:::
+
+the base R library
+
+## An example plot
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
          + geom_point()
          + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))"))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> plot
+         + facet_wrap(~cyl))"
+    r
     plotting/plot->svg
@@
 </defs>
-<g id="surface6">
+<g id="surface929">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 
+```
+
+## Representing plots as Clojure data
+Inspired by
+[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list finction, let us represent ggplot objects as R data structures.
+
 ::: {.sourceClojure}
 ```clojure
+(defn ggolot->clj
+  ([r-obj
+    options]
+   (ggolot->clj r-obj options []))
+  ([r-obj
+    {:as options
+     :keys [avoid]}
+    path]
+   #_(prn path)
+   (let [relevant-names (some->> r-obj
+                                 r.base/names
+                                 r->clj
+                                 (filter (complement avoid)))]
+     (cond
+       ;;
+       ;; a named list or a ggproto object
+       (seq relevant-names) (->> relevant-names
+                                 (map (fn [nam]
+                                        [(keyword nam) (-> r-obj
+                                                           (r$ nam)
+                                                           (ggolot->clj options
+                                                                        (conj path nam)))]))
+                                 (into {}))
+       ;;
+       ;; a ggproto method
+       (-> r-obj
+           r.base/class
+           r->clj
+           first
+           (= "ggproto_method"))
+       :ggproto-method
+       ;;
+       ;; an unnamed list
+       (-> r-obj
+           r.base/is-list
+           r->clj
+           first)
+       (-> r-obj
+           r.base/length
+           r->clj
+           first
+           range
+           (->> (mapv (fn [i]
+                        (prn [path (inc i)])
+                        (-> r-obj
+                            (r/brabra (inc i))
+                            (ggolot->clj options
+                                         (conj path [i])))))))
+       ;;
+       (r.base/is-atomic r-obj) (try (r->clj r-obj)
+                                     (catch Exception e
+                                       (-> r-obj println with-out-str)))
+       :else r-obj))))
+```
+:::
+
+For example:
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, aes(cty, hwy))
+         + geom_point())"
+    r
+    (ggolot->clj {:avoid #{"data" "plot_env"}}))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"]}}
+
+```
+:::
+
+## Exlploring a few plots
+Let us explore and compare a few plots this way:
+
+::: {.sourceClojure}
+```clojure
+(defn h4 [title]
+  (kind/hiccup [:h3 title]))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn ggplot-summary [r-code]
+  (let [plot (r r-code)
+        clj (-> plot
+                (ggolot->clj {:avoid #{"data" "plot_env"}}))]
+    (kind/fragment
+     [(h4 "R code")
+      (kind/md
+       (format "\n```{r eval=FALSE}\n%s\n```\n"
+               r-code))
+      (h4 "plot")
       (-> plot
-    r->clj
-    (dissoc :data))
-```
-:::
+          plotting/plot->buffered-image)
+      (h4 "clj data")
+      (kind/pprint clj)
+      (h4 "portal view")
+      (->> clj
+           (walk/postwalk (fn [form]
+                            ;; Avoiding symbols that
+                            (if (or (and (symbol? form)
+                                         (-> form str (= "~")))
+                                    (and (keyword? form)
+                                         (-> form str (= "."))))
+                              (str form)
+                              form)))
+           kind/portal)])))
+```
+:::
+
+### A scatterplot
+
+::: {.sourceClojure}
+```clojure
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy))
+         + geom_point())")
+```
+:::
+
+```{=html}
+<h3>R code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy))
+         + geom_point())
+```
+
+```{=html}
+<h3>plot</h3>
+```
+
+```{=html}
+<img src="ggplot_files/0.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj data</h3>
+```
 
@@
 ```clojure
-{:layers [nil nil],
- :scales nil,
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"]}}
+
+```
+:::
+
+```{=html}
+<h3>portal view</h3>
+```
+
+```{=html}
+<div><script>portal_api.embed().renderOutputItem(
+                {'mime': 'x-application/edn',
+                 'text': (() => "^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :layers]] [^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :constructor]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector geom_point]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :position]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :inherit.aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :show.legend]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :aes_params]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :non_missing_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"size\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"shape\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"colour\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_key]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default_aes]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shape]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 19.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"black\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :size]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.5]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fill]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :alpha]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stroke]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.5]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_panel]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}}], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cty]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector hwy]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :theme]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :coordinates]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :expand]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :clip]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"on\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :limits]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :facet]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shrink]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :labels]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"cty\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"hwy\"]]]}}")}
+                , document.currentScript.parentElement);</script></div>
+```
+
+### A scatterplot with colours
+
+::: {.sourceClojure}
+```clojure
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point())")
+```
+:::
+
+```{=html}
+<h3>R code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point())
+```
+
+```{=html}
+<h3>plot</h3>
+```
+
+```{=html}
+<img src="ggplot_files/1.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj data</h3>
+```
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
  :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
  :theme [],
- :coordinates nil,
- :facet nil,
- :plot_env nil,
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
  :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
@@
 
-Trying to mimic [cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list (WIP):
+```{=html}
+<h3>portal view</h3>
+```
+
+```{=html}
+<div><script>portal_api.embed().renderOutputItem(
+                {'mime': 'x-application/edn',
+                 'text': (() => "^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :layers]] [^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :constructor]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector geom_point]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :position]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :inherit.aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :show.legend]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :aes_params]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :non_missing_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"size\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"shape\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"colour\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_key]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default_aes]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shape]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 19.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"black\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :size]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.5]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fill]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :alpha]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stroke]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.5]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_panel]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}}], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cty]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector hwy]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector factor]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cyl]]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :theme]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :coordinates]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :expand]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :clip]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"on\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :limits]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :facet]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shrink]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :labels]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"cty\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"hwy\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"factor(cyl)\"]]]}}")}
+                , document.currentScript.parentElement);</script></div>
+```
+
+### A scatterplot with colours and smoothing
 
@@
 ```clojure
-(let [f (-> plot
-            (r$ 'facet)
-            (r$ 'params)
-            (r$ 'facets))]
-  (when (-> `(is.null ~f)
-            r
-            r->clj)
-    (let [facet (-> `(ls ~f)
-                    r
-                    (r->clj)
-                    first)]
-      {:facet facet
-       :facet-levels (-> plot
-                         (r$ 'data)
-                         (r/bra facet))})))
-```
-:::
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method=\"lm\"))")
+```
+:::
+
+```{=html}
+<h3>R code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method="lm"))
+```
+
+```{=html}
+<h3>plot</h3>
+```
+
+```{=html}
+<img src="ggplot_files/2.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj data</h3>
+```
 
@@
 ```clojure
-{:facet "cyl", :facet-levels # A tibble: 234 × 1
-     cyl
-   &lt;int&gt;
- 1     4
- 2     4
- 3     4
- 4     4
- 5     6
- 6     6
- 7     6
- 8     4
- 9     4
-10     4
-# ℹ 224 more rows
-}
-
-```
-:::
-
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position {:compute_layer :ggproto-method, :super :ggproto-method}}
+  {:aes_params [],
+   :stat
+   {:extra_params ["na.rm" "orientation"],
+    :super :ggproto-method,
+    :compute_group :ggproto-method,
+    :required_aes ["x" "y"],
+    :setup_params :ggproto-method,
+    :dropped_aes ["weight"]},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
+   :geom
+   {:setup_params :ggproto-method,
+    :super :ggproto-method,
+    :draw_key :ggproto-method,
+    :extra_params ["na.rm" "orientation"],
+    :required_aes ["x" "y"],
+    :draw_group :ggproto-method,
+    :optional_aes ["ymin" "ymax"],
+    :rename_size [true],
+    :setup_data :ggproto-method,
+    :default_aes
+    {:colour ["#3366FF"],
+     :fill ["grey60"],
+     :linewidth [1.0],
+     :linetype [1.0],
+     :weight [1.0],
+     :alpha [0.4]}},
+   :stat_params
+   {:na.rm [false],
+    :method ["lm"],
+    :n [80.0],
+    :orientation [nil],
+    :level [0.95],
+    :fullrange [false],
+    :se [true],
+    :formula nil,
+    :method.args [],
+    :span [0.75]},
+   :constructor {: nil, :method ["lm"]},
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
+
+```
+:::
+
+```{=html}
+<h3>portal view</h3>
+```
+
+```{=html}
+<div><script>portal_api.embed().renderOutputItem(
+                {'mime': 'x-application/edn',
+                 'text': (() => "^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :layers]] [^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :constructor]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector geom_point]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :position]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :inherit.aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :show.legend]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :aes_params]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :non_missing_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"size\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"shape\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"colour\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_key]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default_aes]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shape]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 19.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"black\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :size]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.5]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fill]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :alpha]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stroke]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.5]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_panel]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}} ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :constructor]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :method]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"lm\"]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :method.args]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :span]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.75]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :formula]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :level]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.95]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :orientation]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :n]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 80.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :se]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :method]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"lm\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fullrange]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :position]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :inherit.aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :show.legend]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :se]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :orientation]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :aes_params]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :extra_params]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"na.rm\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"orientation\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_group]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :setup_params]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :dropped_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"weight\"]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_group]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_key]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default_aes]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"#3366FF\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fill]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"grey60\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :linewidth]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :linetype]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :weight]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :alpha]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.4]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :rename_size]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :setup_data]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :optional_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"ymin\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"ymax\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :setup_params]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :extra_params]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"na.rm\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"orientation\"]]]}}], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cty]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector hwy]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector factor]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cyl]]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :theme]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :coordinates]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :expand]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :clip]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"on\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :limits]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :facet]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shrink]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :labels]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"cty\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"hwy\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"factor(cyl)\"]]]}}")}
+                , document.currentScript.parentElement);</script></div>
+```
+
+### A scatterplot with colours, smoothing, and facets
+
+::: {.sourceClojure}
+```clojure
+(ggplot-summary
+ "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method=\"lm\")
+         + facet_wrap(~cyl))")
+```
+:::
+
+```{=html}
+<h3>R code</h3>
+```
+
+```{r eval=FALSE}
+(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method="lm")
+         + facet_wrap(~cyl))
+```
+
+```{=html}
+<h3>plot</h3>
+```
+
+```{=html}
+<img src="ggplot_files/3.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj data</h3>
+```
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor [geom_point],
+   :position {:compute_layer :ggproto-method, :super :ggproto-method}}
+  {:aes_params [],
+   :stat
+   {:extra_params ["na.rm" "orientation"],
+    :super :ggproto-method,
+    :compute_group :ggproto-method,
+    :required_aes ["x" "y"],
+    :setup_params :ggproto-method,
+    :dropped_aes ["weight"]},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
+   :geom
+   {:setup_params :ggproto-method,
+    :super :ggproto-method,
+    :draw_key :ggproto-method,
+    :extra_params ["na.rm" "orientation"],
+    :required_aes ["x" "y"],
+    :draw_group :ggproto-method,
+    :optional_aes ["ymin" "ymax"],
+    :rename_size [true],
+    :setup_data :ggproto-method,
+    :default_aes
+    {:colour ["#3366FF"],
+     :fill ["grey60"],
+     :linewidth [1.0],
+     :linetype [1.0],
+     :weight [1.0],
+     :alpha [0.4]}},
+   :stat_params
+   {:na.rm [false],
+    :method ["lm"],
+    :n [80.0],
+    :orientation [nil],
+    :level [0.95],
+    :fullrange [false],
+    :se [true],
+    :formula nil,
+    :method.args [],
+    :span [0.75]},
+   :constructor {: nil, :method ["lm"]},
+   :position
+   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet
+ {:params
+  {:dir ["h"],
+   :nrow nil,
+   :as.table [true],
+   :free {:x [false], :y [false]},
+   :drop [true],
+   :strip.position ["top"],
+   :ncol nil,
+   :facets {:cyl [~ cyl]},
+   :labeller
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55eafa698ac0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+  :shrink [true],
+  :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
+
+```
+:::
+
+```{=html}
+<h3>portal view</h3>
+```
+
+```{=html}
+<div><script>portal_api.embed().renderOutputItem(
+                {'mime': 'x-application/edn',
+                 'text': (() => "^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :layers]] [^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :constructor]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector geom_point]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :position]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :inherit.aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :show.legend]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :aes_params]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :non_missing_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"size\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"shape\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"colour\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_key]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default_aes]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shape]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 19.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"black\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :size]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.5]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fill]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :alpha]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stroke]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.5]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_panel]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}} ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :constructor]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :method]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"lm\"]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :method.args]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :span]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.75]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :formula]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :level]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.95]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :orientation]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :n]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 80.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :se]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :method]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"lm\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fullrange]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :position]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :inherit.aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :show.legend]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :se]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :orientation]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :aes_params]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :extra_params]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"na.rm\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"orientation\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_group]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :setup_params]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :dropped_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"weight\"]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_group]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_key]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default_aes]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"#3366FF\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fill]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"grey60\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :linewidth]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :linetype]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :weight]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :alpha]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.4]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :rename_size]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :setup_data]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :optional_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"ymin\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"ymax\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :setup_params]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :extra_params]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"na.rm\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"orientation\"]]]}}], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cty]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector hwy]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector factor]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cyl]]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :theme]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :coordinates]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :expand]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :clip]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"on\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :limits]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :facet]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :free]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :drop]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :nrow]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :labeller]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"function (labels, multi_line = TRUE) \\n{\\n    labels <- lapply(labels, as.character)\\n    if (multi_line) {\\n        labels\\n    }\\n    else {\\n        collapse_labels_lines(labels)\\n    }\\n}\\n<bytecode: 0x55eafa698ac0>\\n<environment: namespace:ggplot2>\\nattr(,\\\"class\\\")\\n[1] \\\"function\\\" \\\"labeller\\\"\\n\"]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ncol]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :as.table]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :dir]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"h\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :strip.position]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"top\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :facets]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :cyl]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cyl]]]}}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shrink]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :labels]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"cty\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"hwy\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"factor(cyl)\"]]]}}")}
+                , document.currentScript.parentElement);</script></div>
+```
+
+```{=html}
 <div style="background-color:grey;height:2px;width:100%;"></div>
-
+```
+
+```{=html}
 <div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ggplot.clj">projects/noj/notebooks/ggplot.clj</a></small></small></pre></div>
+```

### 2024-02-05 docs/projects/noj/ml.qmd
Noj - rerendered

@@
        Min          1Q      Median          3Q         Max
-   -0.7904     -0.2163      0.0132      0.1774      0.8282
+   -0.8799     -0.2284      0.0138      0.2569      0.6354
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           2.1092     0.2799     7.5344     0.0000 ***
-sepal-width         0.5826     0.0743     7.8394     0.0000 ***
-petal-length        0.7037     0.0624    11.2696     0.0000 ***
-petal-width        -0.5557     0.1425    -3.8986     0.0002 ***
+Intercept           1.9687     0.3043     6.4705     0.0000 ***
+sepal-width         0.6222     0.0800     7.7748     0.0000 ***
+petal-length        0.6929     0.0713     9.7167     0.0000 ***
+petal-width        -0.5072     0.1639    -3.0944     0.0026 **
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3015 on 96 degrees of freedom
-Multiple R-squared: 0.8707,    Adjusted R-squared: 0.8667
-F-statistic: 215.5039 on 4 and 96 DF,  p-value: 1.668e-42
+Residual standard error: 0.3196 on 96 degrees of freedom
+Multiple R-squared: 0.8577,    Adjusted R-squared: 0.8533
+F-statistic: 192.9066 on 4 and 96 DF,  p-value: 1.640e-40
 

### 2024-02-05 docs/projects/noj/ggplot.qmd
Noj - rerendered

--- 2024-02-05 docs/projects/noj/ggplot.qmd
@@
 </style>
-<script src="ggplot_files/md-default5.js" type="text/javascript"></script><script src="ggplot_files/md-default6.js" type="text/javascript"></script>
+<script src="ggplot_files/md-default4.js" type="text/javascript"></script><script src="ggplot_files/md-default5.js" type="text/javascript"></script>
 
@@
 
-# Exploring ggplot
-following
-[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list
-in representing a plot as a data structure.
+# Exploring ggplot - DRAFT
+Here we explore [ggplot2](https://ggplot2.tidyverse.org/) from Clojure. The goal is to eventually implement a similar grammar in Clojure.
+
+## Setup
+We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.
 
@@
 
+Loading ggplot2:
+
 ::: {.sourceClojure}
@@
 
+The base R library:
+
 ::: {.sourceClojure}
 ```clojure
-(def plot
-  (r "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+(r/require-r '[base])
+```
+:::
+
+::: {.printedClojure}
+```clojure
+nil
+
+```
+:::
+
+## An example plot
+Here is how we may generate and display a plot:
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
          + geom_point()
          + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))"))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> plot
+         + facet_wrap(~cyl))"
+    r
     plotting/plot->svg
@@
 </defs>
-<g id="surface428">
+<g id="surface679">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 
+We may also [generate](https://scicloj.github.io/clojisr/doc/clojisr/v1/codegen-test/) the R code from a Clojure form and pass Clojure data to R, but for now, we are simply using R code using an R dataset.
+We are using the `mpg` dataset, which is part of the `ggplot` package.
+
 ::: {.sourceClojure}
 ```clojure
-(-> plot
-    r->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers [nil nil],
- :scales nil,
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates nil,
- :facet nil,
- :plot_env nil,
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn gg-facet [ggplot]
-  (let [f (-> ggplot
-              (r$ 'facet)
-              (r$ 'params)
-              (r$ 'facets))]
-    (when (-> `(is.null ~f)
+(-> "mpg"
     r
     r->clj)
-      (let [facet (r `(ls ~f))]
-        {:facet facet
-         :facet-levels (-> plot
-                           (r$ 'data)
-                           (r/bra facet))}))))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> plot
-    gg-facet
-    (update-vals r->clj))
-```
-:::
-
-```{=html}
-<div><p>{</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet ["cyl"]</code></pre></div><table><tr><td valign="top"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet-levels
-</code></pre></div></td><td><div style="margin-left:10px;"><span data-qmd="_unnamed [234 1]:
-
-| :cyl |
-|-----:|
-|    4 |
-|    4 |
-|    4 |
-|    4 |
-|    6 |
-|    6 |
-|    6 |
-|    4 |
-|    4 |
-|    4 |
-|  ... |
-|    4 |
-|    4 |
-|    5 |
-|    5 |
-|    4 |
-|    4 |
-|    4 |
-|    4 |
-|    6 |
-|    6 |
-|    6 |
-
-"></span></div></td></tr></table></div><p>}</p></div>
-```
-
-::: {.sourceClojure}
-```clojure
-(r/require-r '[base])
-```
-:::
-
-::: {.printedClojure}
-```clojure
-nil
-
-```
-:::
+```
+:::
+
+_unnamed [234 11]:
+
+| :manufacturer |     :model | :displ | :year | :cyl |     :trans | :drv | :cty | :hwy | :fl |     :class |
+|---------------|------------|-------:|------:|-----:|------------|------|-----:|-----:|-----|------------|
+|          audi |         a4 |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    compact |
+|          audi |         a4 |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    compact |
+|          audi |         a4 |    2.0 |  2008 |    4 | manual(m6) |    f |   20 |   31 |   p |    compact |
+|          audi |         a4 |    2.0 |  2008 |    4 |   auto(av) |    f |   21 |   30 |   p |    compact |
+|          audi |         a4 |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    compact |
+|          audi |         a4 |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    compact |
+|          audi |         a4 |    3.1 |  2008 |    6 |   auto(av) |    f |   18 |   27 |   p |    compact |
+|          audi | a4 quattro |    1.8 |  1999 |    4 | manual(m5) |    4 |   18 |   26 |   p |    compact |
+|          audi | a4 quattro |    1.8 |  1999 |    4 |   auto(l5) |    4 |   16 |   25 |   p |    compact |
+|          audi | a4 quattro |    2.0 |  2008 |    4 | manual(m6) |    4 |   20 |   28 |   p |    compact |
+|           ... |        ... |    ... |   ... |  ... |        ... |  ... |  ... |  ... | ... |        ... |
+|    volkswagen | new beetle |    2.0 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   r | subcompact |
+|    volkswagen | new beetle |    2.0 |  1999 |    4 |   auto(l4) |    f |   19 |   26 |   r | subcompact |
+|    volkswagen | new beetle |    2.5 |  2008 |    5 | manual(m5) |    f |   20 |   28 |   r | subcompact |
+|    volkswagen | new beetle |    2.5 |  2008 |    5 |   auto(s6) |    f |   20 |   29 |   r | subcompact |
+|    volkswagen |     passat |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    midsize |
+|    volkswagen |     passat |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    midsize |
+|    volkswagen |     passat |    2.0 |  2008 |    4 |   auto(s6) |    f |   19 |   28 |   p |    midsize |
+|    volkswagen |     passat |    2.0 |  2008 |    4 | manual(m6) |    f |   21 |   29 |   p |    midsize |
+|    volkswagen |     passat |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    midsize |
+|    volkswagen |     passat |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    midsize |
+|    volkswagen |     passat |    3.6 |  2008 |    6 |   auto(s6) |    f |   17 |   26 |   p |    midsize |
+
+## Representing plots as Clojure data
+Inspired by
+[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list finction, let us represent ggplot objects as R data structures.
+A ggplot object is an R list of [ggproto](https://bookdown.dongzhuoer.com/hadley/ggplot2-book/introducing-ggproto) objects. We recursively unwrap this structure and convert it to Clojure.
 
@@
 
+In the conversion, we avoid some big parts of the structure, e.g., the `"plot_env"` member. We also do no report the toplevel `"data"` member, which is simply the dataset.
+For example:
+
 ::: {.sourceClojure}
@@
     r
-    (ggolot->clj {:avoid #{"data" "plot_env"}}))
+    (ggolot->clj {:avoid #{"plot_env"}})
+    (dissoc :data))
 ```
@@
    :constructor [geom_point],
-   :position
-   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}],
  :scales {:scales [], :super :ggproto-method},
@@
 
+## Exlploring a few plots
+Let us explore and compare a few plots this way:
+
 ::: {.sourceClojure}
@@
         clj (-> plot
-                (ggolot->clj {:avoid #{"data" "plot_env"}})
-                (->> (walk/postwalk (fn [form]
-                                      (if (and (symbol? form)
-                                               (-> form str (= "~")))
-                                        (str form)
-                                        form)))))]
+                (ggolot->clj {:avoid #{"plot_env"}})
+                (dissoc :data))]
     (kind/fragment
-     [(h4 "code")
+     [(h4 "R code")
       (kind/md
-       (format "\n```{r eval=FALSE}\n%s\n```\n"
+       (format "\n```\n%s\n```\n"
                r-code))
-      (h4 "image")
-      (plotting/plot->buffered-image plot)
-      (h4 "clj")
+      (h4 "plot")
+      (-> plot
+          plotting/plot->buffered-image)
+      (h4 "clj data")
       (kind/pprint clj)])))
@@
 :::
+
+### A scatterplot
 
@@
 ```{=html}
-<h3>code</h3>
-```
-
-```{r eval=FALSE}
+<h3>R code</h3>
+```
+
+```
 (ggplot(mpg, aes(cty, hwy))
@@
 ```{=html}
-<h3>image</h3>
+<h3>plot</h3>
 ```
@@
 ```{=html}
-<h3>clj</h3>
+<h3>clj data</h3>
 ```
@@
    :constructor [geom_point],
-   :position
-   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}],
  :scales {:scales [], :super :ggproto-method},
- :mapping {:x ["~" cty], :y ["~" hwy]},
+ :mapping {:x [~ cty], :y [~ hwy]},
  :theme [],
@@
 
-## Exlploring a few plots
-
-### A scatterplot
+### A scatterplot with colours
 
@@
 (ggplot-summary
- "(ggplot(mpg, aes(cty, hwy))
+ "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
          + geom_point())")
@@
 ```{=html}
-<h3>code</h3>
-```
-
-```{r eval=FALSE}
-(ggplot(mpg, aes(cty, hwy))
+<h3>R code</h3>
+```
+
+```
+(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
          + geom_point())
@@
    :constructor [geom_point],
-   :position
-   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}],
  :scales {:scales [], :super :ggproto-method},
- :mapping {:x ["~" cty], :y ["~" hwy]},
+ :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
  :theme [],
@@
  :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-### A scatterplot with colours
+ :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
+
+```
+:::
+
+### A scatterplot with colours and smoothing
 
@@
  "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())")
-```
-:::
-
-```{=html}
-<h3>code</h3>
-```
-
-```{r eval=FALSE}
+         + geom_point()
+         + stat_smooth(method=\"lm\"))")
+```
+:::
+
+```{=html}
+<h3>R code</h3>
+```
+
+```
 (ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())
-```
-
-```{=html}
-<h3>image</h3>
+         + geom_point()
+         + stat_smooth(method="lm"))
+```
+
+```{=html}
+<h3>plot</h3>
 ```
@@
    :constructor [geom_point],
-   :position
-   {:compute_layer :ggproto-method, :super :ggproto-method}}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x ["~" cty], :y ["~" hwy], :colour ["~" [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-### A scatterplot with colours and smoothing
-
-::: {.sourceClojure}
-```clojure
-(ggplot-summary
- "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\"))")
-```
-:::
-
-```{=html}
-<h3>code</h3>
-```
-
-```{r eval=FALSE}
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method="lm"))
-```
-
-```{=html}
-<h3>image</h3>
-```
-
-```{=html}
-<img src="ggplot_files/3.png" style="width:100%;" />
-```
-
-```{=html}
-<h3>clj</h3>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method}}
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}
   {:aes_params [],
@@
    :constructor {: nil, :method ["lm"]},
-   :position
-   {:compute_layer :ggproto-method, :super :ggproto-method}}],
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}],
  :scales {:scales [], :super :ggproto-method},
- :mapping {:x ["~" cty], :y ["~" hwy], :colour ["~" [factor cyl]]},
+ :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
  :theme [],
@@
 ```{=html}
-<h3>code</h3>
-```
-
-```{r eval=FALSE}
+<h3>R code</h3>
+```
+
+```
 (ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
@@
 ```{=html}
-<h3>image</h3>
-```
-
-```{=html}
-<img src="ggplot_files/4.png" style="width:100%;" />
-```
-
-```{=html}
-<h3>clj</h3>
+<h3>plot</h3>
+```
+
+```{=html}
+<img src="ggplot_files/3.png" style="width:100%;" />
+```
+
+```{=html}
+<h3>clj data</h3>
 ```
@@
    :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method}}
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}
   {:aes_params [],
@@
    :ncol nil,
-   :facets {:cyl ["~" cyl]},
+   :facets {:cyl [~ cyl]},
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55eafa698ac0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x559b84332b20&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],

### 2024-02-05 docs/projects/noj/ml.qmd
Noj - rerendered

@@
        Min          1Q      Median          3Q         Max
-   -0.8799     -0.2284      0.0138      0.2569      0.6354
+   -0.7420     -0.2582      0.0213      0.2341      0.8930
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.9687     0.3043     6.4705     0.0000 ***
-sepal-width         0.6222     0.0800     7.7748     0.0000 ***
-petal-length        0.6929     0.0713     9.7167     0.0000 ***
-petal-width        -0.5072     0.1639    -3.0944     0.0026 **
+Intercept           1.8651     0.3225     5.7825     0.0000 ***
+sepal-width         0.6599     0.0863     7.6500     0.0000 ***
+petal-length        0.7003     0.0701     9.9877     0.0000 ***
+petal-width        -0.5694     0.1585    -3.5924     0.0005 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3196 on 96 degrees of freedom
-Multiple R-squared: 0.8577,    Adjusted R-squared: 0.8533
-F-statistic: 192.9066 on 4 and 96 DF,  p-value: 1.640e-40
+Residual standard error: 0.3268 on 96 degrees of freedom
+Multiple R-squared: 0.8465,    Adjusted R-squared: 0.8418
+F-statistic: 176.5359 on 4 and 96 DF,  p-value: 6.132e-39
 

### 2024-02-06 docs/projects/noj/ggplot.qmd
Noj - rerendered

@@
 </defs>
-<g id="surface679">
+<g id="surface931">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 ## Representing plots as Clojure data
-Inspired by
-[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list finction, let us represent ggplot objects as R data structures.
 A ggplot object is an R list of [ggproto](https://bookdown.dongzhuoer.com/hadley/ggplot2-book/introducing-ggproto) objects. We recursively unwrap this structure and convert it to Clojure.

### 2024-02-06 docs/projects/noj/ml.qmd
Noj - rerendered

--- 2024-02-05 docs/projects/noj/ml.qmd
@@
        Min          1Q      Median          3Q         Max
-   -0.8799     -0.2284      0.0138      0.2569      0.6354
+   -0.7855     -0.2024      0.0281      0.2007      0.6159
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.9687     0.3043     6.4705     0.0000 ***
-sepal-width         0.6222     0.0800     7.7748     0.0000 ***
-petal-length        0.6929     0.0713     9.7167     0.0000 ***
-petal-width        -0.5072     0.1639    -3.0944     0.0026 **
+Intercept           1.8316     0.3045     6.0143     0.0000 ***
+sepal-width         0.6567     0.0798     8.2255     0.0000 ***
+petal-length        0.6798     0.0680     9.9990     0.0000 ***
+petal-width        -0.4501     0.1530    -2.9415     0.0041 **
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3196 on 96 degrees of freedom
-Multiple R-squared: 0.8577,    Adjusted R-squared: 0.8533
-F-statistic: 192.9066 on 4 and 96 DF,  p-value: 1.640e-40
+Residual standard error: 0.2950 on 96 degrees of freedom
+Multiple R-squared: 0.8767,    Adjusted R-squared: 0.8728
+F-statistic: 227.5000 on 4 and 96 DF,  p-value: 1.726e-43
 

### 2024-02-06 docs/projects/noj/ggplot.qmd
Noj - rerendered

@@
             [clojure.walk :as walk]
-            [tablecloth.api :as tc]))
+            [tablecloth.api :as tc]
+            [editscript.core :as editscript]
+            [clojure.pprint :as pp]
+            [clojure.string :as str]))
 ```
@@
 </defs>
-<g id="surface931">
+<g id="surface3322">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 ```clojure
-(defn ggolot->clj
+(defn ggplot->clj
   ([r-obj
     options]
-   (ggolot->clj r-obj options []))
+   (ggplot->clj r-obj options []))
   ([r-obj
@@
                                                            (r$ nam)
-                                                           (ggolot->clj options
+                                                           (ggplot->clj options
                                                                         (conj path nam)))]))
@@
            (->> (mapv (fn [i]
-                        (prn [path (inc i)])
                         (-> r-obj
                             (r/brabra (inc i))
-                            (ggolot->clj options
+                            (ggplot->clj options
                                          (conj path [i])))))))
@@
     r
-    (ggolot->clj {:avoid #{"plot_env"}})
+    (ggplot->clj {:avoid #{"plot_env"}})
     (dissoc :data))
@@
 ```clojure
-(defn h4 [title]
-  (kind/hiccup [:h3 title]))
+(defn h3 [title] (kind/hiccup [:h3 title]))
 ```
@@
 ```clojure
-(defn ggplot-summary [r-code]
+(defn h4 [title] (kind/hiccup [:h4 title]))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn ggplot-summary
+  ([title r-code]
+   (ggplot-summary r-code))
+  ([title r-code prev-clj-to-compare]
    (let [plot (r r-code)
          clj (-> plot
-                (ggolot->clj {:avoid #{"plot_env"}})
+                 (ggplot->clj {:avoid #{"plot_env"}})
                  (dissoc :data))]
+     {:title title
+      :r-code r-code
+      :image (plotting/plot->buffered-image plot)
+      :clj clj
+      :diff (when prev-clj-to-compare
+              (-> prev-clj-to-compare
+                  (editscript/diff clj)
+                  pp/pprint
+                  with-out-str
+                  (str/replace #": " ":_ ")
+                  read-string))})))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn view-summary [{:keys [title r-code image clj diff]}]
   (kind/fragment
-     [(h4 "R code")
+   [(h3 title)
+    (h4 "R code")
     (kind/md
@@
     (h4 "plot")
-      (-> plot
-          plotting/plot->buffered-image)
+    image
     (h4 "clj data")
-      (kind/pprint clj)])))
-```
-:::
-
-### A scatterplot
+    clj
+    (when diff
+      (kind/fragment
+       [(h4 "clj diff with previous")
+        diff]))]))
+```
+:::
 
@@
 ```clojure
-(ggplot-summary
+(->> [;;
+      ["A scatterplot"
        "(ggplot(mpg, aes(cty, hwy))
-         + geom_point())")
-```
-:::
-
-```{=html}
-<h3>R code</h3>
+         + geom_point())"]
+      ;;
+      ["A scatterplot with colours"
+       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point())"]
+      ;;
+      ["A scatterplot with colours and smoothing"
+       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method=\"lm\"))"]
+      ;;
+      ["A scatterplot with colours, smoothing, and facets"
+       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
+         + geom_point()
+         + stat_smooth(method=\"lm\")
+         + facet_wrap(~cyl))"]]
+     (reductions (fn [prev-summary [title r-code]]
+                   (ggplot-summary title
+                                   r-code
+                                   (:clj prev-summary)))
+                 nil)
+     rest
+     (map view-summary)
+     kind/fragment)
+```
+:::
+
+```{=html}
+<h3>A scatterplot</h3>
+```
+
+```{=html}
+<h4>R code</h4>
 ```
@@
 ```{=html}
-<h3>plot</h3>
+<h4>plot</h4>
 ```
@@
 ```{=html}
-<h3>clj data</h3>
+<h4>clj data</h4>
 ```
@@
 
-### A scatterplot with colours
-
-::: {.sourceClojure}
-```clojure
-(ggplot-summary
- "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())")
-```
-:::
-
-```{=html}
-<h3>R code</h3>
+```{=html}
+<h3>A scatterplot with colours</h3>
+```
+
+```{=html}
+<h4>R code</h4>
 ```
@@
 
-### A scatterplot with colours and smoothing
-
-::: {.sourceClojure}
-```clojure
-(ggplot-summary
- "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\"))")
-```
-:::
-
-```{=html}
-<h3>R code</h3>
+```{=html}
+<h4>clj diff with previous</h4>
+```
+
+::: {.printedClojure}
+```clojure
+[[[:mapping :colour] :+ [~[factor cyl]]]
+ [[:labels :colour] :+ ["factor(cyl)"]]]
+
+```
+:::
+
+```{=html}
+<h3>A scatterplot with colours and smoothing</h3>
+```
+
+```{=html}
+<h4>R code</h4>
 ```
@@
 
-### A scatterplot with colours, smoothing, and facets
-
-::: {.sourceClojure}
-```clojure
-(ggplot-summary
- "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))")
-```
-:::
-
-```{=html}
-<h3>R code</h3>
+```{=html}
+<h4>clj diff with previous</h4>
+```
+
+::: {.printedClojure}
+```clojure
+[[[:layers 1]
+  :+
+  {:aes_params [],
+   :stat
+   {:extra_params ["na.rm" "orientation"],
+    :super :ggproto-method,
+    :compute_group :ggproto-method,
+    :required_aes ["x" "y"],
+    :setup_params :ggproto-method,
+    :dropped_aes ["weight"]},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
+   :geom
+   {:setup_params :ggproto-method,
+    :super :ggproto-method,
+    :draw_key :ggproto-method,
+    :extra_params ["na.rm" "orientation"],
+    :required_aes ["x" "y"],
+    :draw_group :ggproto-method,
+    :optional_aes ["ymin" "ymax"],
+    :rename_size [true],
+    :setup_data :ggproto-method,
+    :default_aes
+    {:colour ["#3366FF"],
+     :fill ["grey60"],
+     :linewidth [1.0],
+     :linetype [1.0],
+     :weight [1.0],
+     :alpha [0.4]}},
+   :stat_params
+   {:na.rm [false],
+    :method ["lm"],
+    :n [80.0],
+    :orientation [nil],
+    :level [0.95],
+    :fullrange [false],
+    :se [true],
+    :formula nil,
+    :method.args [],
+    :span [0.75]},
+   :constructor {:_ nil, :method ["lm"]},
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}]]
+
+```
+:::
+
+```{=html}
+<h3>A scatterplot with colours, smoothing, and facets</h3>
+```
+
+```{=html}
+<h4>R code</h4>
 ```
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x559b84332b20&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x557f413a3978&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
 ```{=html}
+<h4>clj diff with previous</h4>
+```
+
+::: {.printedClojure}
+```clojure
+[[[:facet :params]
+  :+
+  {:dir ["h"],
+   :nrow nil,
+   :as.table [true],
+   :free {:x [false], :y [false]},
+   :drop [true],
+   :strip.position ["top"],
+   :ncol nil,
+   :facets {:cyl [~cyl]},
+   :labeller
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x557f413a3978&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+
+```
+:::
+
+```{=html}
 <div style="background-color:grey;height:2px;width:100%;"></div>

### 2024-02-06 docs/projects/noj/ml.qmd
Noj - rerendered

@@
        Min          1Q      Median          3Q         Max
-   -0.7855     -0.2024      0.0281      0.2007      0.6159
+   -0.8076     -0.2157      0.0177      0.2335      0.7341
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.8316     0.3045     6.0143     0.0000 ***
-sepal-width         0.6567     0.0798     8.2255     0.0000 ***
-petal-length        0.6798     0.0680     9.9990     0.0000 ***
-petal-width        -0.4501     0.1530    -2.9415     0.0041 **
+Intercept           1.8682     0.2970     6.2904     0.0000 ***
+sepal-width         0.6388     0.0786     8.1279     0.0000 ***
+petal-length        0.7250     0.0713    10.1635     0.0000 ***
+petal-width        -0.5999     0.1646    -3.6449     0.0004 ***
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.2950 on 96 degrees of freedom
-Multiple R-squared: 0.8767,    Adjusted R-squared: 0.8728
-F-statistic: 227.5000 on 4 and 96 DF,  p-value: 1.726e-43
+Residual standard error: 0.3197 on 96 degrees of freedom
+Multiple R-squared: 0.8499,    Adjusted R-squared: 0.8452
+F-statistic: 181.1746 on 4 and 96 DF,  p-value: 2.137e-39
 

### 2024-02-08 docs/projects/noj/ggplot.qmd
Noj -rerendered

@@
 </style>
-<script src="ggplot_files/md-default4.js" type="text/javascript"></script><script src="ggplot_files/md-default5.js" type="text/javascript"></script>
+<script src="ggplot_files/md-default6.js" type="text/javascript"></script><script src="ggplot_files/md-default7.js" type="text/javascript"></script>
 
@@
 </defs>
-<g id="surface3322">
+<g id="surface445">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 (defn ggplot->clj
-  ([r-obj
-    options]
-   (ggplot->clj r-obj options []))
+  ([r-obj]
+   (ggplot->clj r-obj {} []))
   ([r-obj
     {:as options
-     :keys [avoid]}
+     :keys [avoid]
+     :or {avoid #{"plot_env"}}}
     path]
@@
     r
-    (ggplot->clj {:avoid #{"plot_env"}})
+    ggplot->clj
     (dissoc :data))
@@
          clj (-> plot
-                 (ggplot->clj {:avoid #{"plot_env"}})
+                 ggplot->clj
                  (dissoc :data))]
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x557f413a3978&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55801151ed28&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x557f413a3978&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55801151ed28&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+
+```
+:::
+
+## Exploring
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, aes(cty, hwy)))"
+    r
+    ggplot->clj
+    (dissoc :data))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers [],
+ :scales {:super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"]}}
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, aes(cty, hwy)))"
+    r
+    ggplot->clj
+    (dissoc :data))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers [],
+ :scales {:super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"]}}
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy)))"
+    r
+    ggplot->clj
+    (dissoc :data))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers [],
+ :scales {:super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"]}}
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
+      + geom_point(mapping=aes(color=cyl), size=5)
+      + ylim(c(20,30)))"
+    r
+    ggplot->clj
+    (dissoc :data))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params {:size [5.0]},
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping {:colour [~ cyl]},
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}],
+ :scales
+ {:scales
+  [{:labels [],
+    :scale_name ["position_c"],
+    :breaks [],
+    :call
+    {:labels labels,
+     :scale_name ["position_c"],
+     :breaks breaks,
+     :name name,
+     :palette identity,
+     :super ScaleContinuousPosition,
+     :guide guide,
+     :minor_breaks minor_breaks,
+     :n.breaks n.breaks,
+     : nil,
+     :aesthetics [$ ggplot_global y_aes],
+     :na.value na.value,
+     :trans trans,
+     :oob oob,
+     :position position,
+     :limits limits,
+     :expand expand},
+    :rescaler :ggproto-method,
+    :name [],
+    :palette :ggproto-method,
+    :super :ggproto-method,
+    :guide [],
+    :minor_breaks [],
+    :n.breaks nil,
+    :aesthetics
+    ["y"
+     "ymin"
+     "ymax"
+     "yend"
+     "yintercept"
+     "ymin_final"
+     "ymax_final"
+     "lower"
+     "middle"
+     "upper"
+     "y0"],
+    :na.value [nil],
+    :trans
+    {:name ["identity"],
+     :transform
+     "function (x) \nx\n&lt;bytecode: 0x55800c808140&gt;\n&lt;environment: namespace:base&gt;\n",
+     :inverse
+     "function (x) \nx\n&lt;bytecode: 0x55800c808140&gt;\n&lt;environment: namespace:base&gt;\n",
+     :breaks
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x558011cf7cd0&gt;\n&lt;environment: 0x5580173bcb00&gt;\n",
+     :minor_breaks
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558011cff4b8&gt;\n&lt;environment: 0x5580173bcc88&gt;\n",
+     :format
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558011d098e0&gt;\n&lt;environment: 0x5580173bcdd8&gt;\n",
+     :domain [##-Inf ##Inf]},
+    :oob :ggproto-method,
+    :position ["left"],
+    :limits [20.0 30.0],
+    :expand [],
+    :range {:super :ggproto-method}}],
+  :super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
+      + geom_point(mapping=aes(color=factor(cyl)), size=20))"
+    r
+    plotting/plot->buffered-image)
+```
+:::
+
+```{=html}
+<img src="ggplot_files/4.png" style="width:100%;" />
+```
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
+      + geom_point(mapping=aes(color=cyl), size=5)
+      + ylim(c(20,30))
+      + scale_x_log10())"
+    r
+    ggplot->clj
+    (dissoc :data))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params {:size [5.0]},
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping {:colour [~ cyl]},
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}],
+ :scales
+ {:scales
+  [{:range {:super :ggproto-method}, :super :ggproto-method}
+   {:labels [],
+    :scale_name ["position_c"],
+    :breaks [],
+    :call
+    {:labels labels,
+     :scale_name ["position_c"],
+     :breaks breaks,
+     :name name,
+     :palette identity,
+     :super ScaleContinuousPosition,
+     :guide guide,
+     :minor_breaks minor_breaks,
+     :n.breaks n.breaks,
+     : nil,
+     :aesthetics [$ ggplot_global x_aes],
+     :na.value na.value,
+     :trans trans,
+     :oob oob,
+     :position position,
+     :limits limits,
+     :expand expand},
+    :rescaler :ggproto-method,
+    :name [],
+    :palette :ggproto-method,
+    :super :ggproto-method,
+    :guide [],
+    :minor_breaks [],
+    :n.breaks nil,
+    :aesthetics
+    ["x"
+     "xmin"
+     "xmax"
+     "xend"
+     "xintercept"
+     "xmin_final"
+     "xmax_final"
+     "xlower"
+     "xmiddle"
+     "xupper"
+     "x0"],
+    :na.value [nil],
+    :trans
+    {:name ["log-10"],
+     :transform
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55801c8071a8&gt;\n&lt;environment: 0x55801c3836c8&gt;\n",
+     :inverse
+     "function (x) \nbase^x\n&lt;bytecode: 0x55801c807058&gt;\n&lt;environment: 0x55801c3836c8&gt;\n",
+     :breaks
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55801c8159d0&gt;\n&lt;environment: 0x55801c386a88&gt;\n",
+     :minor_breaks
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558011cff4b8&gt;\n&lt;environment: 0x55801c38a500&gt;\n",
+     :format
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558011d098e0&gt;\n&lt;environment: 0x55801c38a3b0&gt;\n",
+     :domain [1.0E-100 ##Inf]},
+    :oob :ggproto-method,
+    :position ["bottom"],
+    :limits nil,
+    :expand [],
+    :range {:super :ggproto-method}}],
+  :super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
+      + geom_point(mapping=aes(color=cyl), size=5)
+      + ylim(c(20,30))
+      + scale_x_log10()
+      + theme_linedraw())"
+    r
+    ggplot->clj
+    (dissoc :data))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params {:size [5.0]},
+   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
+   :show.legend [nil],
+   :mapping {:colour [~ cyl]},
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false]},
+   :geom
+   {:non_missing_aes ["size" "shape" "colour"],
+    :draw_key :ggproto-method,
+    :default_aes
+    {:shape [19.0],
+     :colour ["black"],
+     :size [1.5],
+     :fill [nil],
+     :alpha [nil],
+     :stroke [0.5]},
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method},
+   :stat_params {:na.rm [false]},
+   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}],
+ :scales
+ {:scales
+  [{:range {:super :ggproto-method}, :super :ggproto-method}
+   {:range {:super :ggproto-method}, :super :ggproto-method}],
+  :super :ggproto-method},
+ :mapping {:x [~ cty], :y [~ hwy]},
+ :theme
+ {:axis.ticks
+  {:colour ["black"],
+   :linewidth [0.5],
+   :linetype nil,
+   :lineend nil,
+   :arrow [false],
+   :inherit.blank [true]},
+  :legend.justification ["center"],
+  :panel.grid.minor
+  {:colour nil,
+   :linewidth [0.05],
+   :linetype nil,
+   :lineend nil,
+   :arrow [false],
+   :inherit.blank [true]},
+  :strip.text.x.bottom nil,
+  :legend.key.width nil,
+  :panel.spacing.x nil,
+  :axis.text.y
+  {:hjust [1.0],
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust nil,
+   :margin [0.0 2.2 0.0 0.0]},
+  :panel.ontop [false],
+  :axis.ticks.x.top nil,
+  :panel.border
+  {:fill [nil],
+   :colour ["black"],
+   :linewidth [1.0],
+   :linetype nil,
+   :inherit.blank [true]},
+  :legend.key.height nil,
+  :plot.caption
+  {:hjust [1.0],
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size [0.8],
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [1.0],
+   :margin [5.5 0.0 0.0 0.0]},
+  :panel.grid.major.y nil,
+  :panel.grid
+  {:colour ["black"],
+   :linewidth nil,
+   :linetype nil,
+   :lineend nil,
+   :arrow [false],
+   :inherit.blank [true]},
+  :axis.ticks.x.bottom nil,
+  :panel.grid.major.x nil,
+  :plot.tag
+  {:hjust [0.5],
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size [1.2],
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [0.5],
+   :margin nil},
+  :axis.text
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size [0.8],
+   :face nil,
+   :lineheight nil,
+   :colour ["black"],
+   :vjust nil,
+   :margin nil},
+  :axis.line.x nil,
+  :panel.spacing.y nil,
+  :legend.spacing.x nil,
+  :axis.text.x
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [1.0],
+   :margin [2.2 0.0 0.0 0.0]},
+  :axis.line.y.left nil,
+  :plot.caption.position ["panel"],
+  :plot.subtitle
+  {:hjust [0.0],
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [1.0],
+   :margin [0.0 0.0 5.5 0.0]},
+  :axis.ticks.y.right nil,
+  :legend.box nil,
+  :strip.text.y
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle [-90.0],
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust nil,
+   :margin nil},
+  :panel.spacing [5.5],
+  :legend.background
+  {:fill nil,
+   :colour [nil],
+   :linewidth nil,
+   :linetype nil,
+   :inherit.blank [true]},
+  :strip.switch.pad.grid [2.75],
+  :axis.ticks.length.y.left nil,
+  :legend.direction nil,
+  :strip.text
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size [0.8],
+   :face nil,
+   :lineheight nil,
+   :colour ["white"],
+   :vjust nil,
+   :margin [4.4 4.4 4.4 4.4]},
+  :axis.line.x.bottom nil,
+  :axis.ticks.length.x.bottom nil,
+  :axis.text.y.left nil,
+  :axis.ticks.length.x nil,
+  :plot.margin [5.5 5.5 5.5 5.5],
+  :axis.ticks.length [2.75],
+  :plot.title
+  {:hjust [0.0],
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size [1.2],
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [1.0],
+   :margin [0.0 0.0 5.5 0.0]},
+  :axis.ticks.y nil,
+  :legend.text.align nil,
+  :legend.text
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size [0.8],
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust nil,
+   :margin nil},
+  :legend.key
+  {:fill ["white"],
+   :colour [nil],
+   :linewidth nil,
+   :linetype nil,
+   :inherit.blank [true]},
+  :axis.line.y nil,
+  :axis.title.y.left nil,
+  :axis.ticks.length.x.top nil,
+  :legend.box.margin [0.0 0.0 0.0 0.0],
+  :axis.title.y.right
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle [-90.0],
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [0.0],
+   :margin [0.0 0.0 0.0 2.75]},
+  :title nil,
+  :strip.clip ["inherit"],
+  :strip.background.x nil,
+  :strip.text.x nil,
+  :strip.placement ["inside"],
+  :axis.ticks.x nil,
+  :axis.line.y.right nil,
+  :axis.title.x.bottom nil,
+  :legend.key.size [1.2],
+  :axis.text.x.top
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [0.0],
+   :margin [0.0 0.0 2.2 0.0]},
+  :panel.background
+  {:fill ["white"],
+   :colour [nil],
+   :linewidth nil,
+   :linetype nil,
+   :inherit.blank [true]},
+  :plot.tag.position ["topleft"],
+  :legend.margin [5.5 5.5 5.5 5.5],
+  :plot.title.position ["panel"],
+  :line
+  {:colour ["black"],
+   :linewidth [0.5],
+   :linetype [1.0],
+   :lineend ["butt"],
+   :arrow [false],
+   :inherit.blank [true]},
+  :strip.text.y.left
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle [90.0],
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust nil,
+   :margin nil},
+  :strip.background
+  {:fill ["black"],
+   :colour nil,
+   :linewidth nil,
+   :linetype nil,
+   :inherit.blank [true]},
+  :axis.title.y
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle [90.0],
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [1.0],
+   :margin [0.0 2.75 0.0 0.0]},
+  :legend.box.background [],
+  :panel.grid.major
+  {:colour nil,
+   :linewidth [0.1],
+   :linetype nil,
+   :lineend nil,
+   :arrow [false],
+   :inherit.blank [true]},
+  :axis.title nil,
+  :strip.text.y.right nil,
+  :legend.title.align nil,
+  :plot.background
+  {:fill nil,
+   :colour ["white"],
+   :linewidth nil,
+   :linetype nil,
+   :inherit.blank [true]},
+  :aspect.ratio nil,
+  :legend.spacing [11.0],
+  :axis.title.x
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [1.0],
+   :margin [2.75 0.0 0.0 0.0]},
+  :axis.line.x.top nil,
+  :legend.position ["right"],
+  :axis.ticks.length.y nil,
+  :axis.ticks.y.left nil,
+  :axis.ticks.length.y.right nil,
+  :legend.box.just nil,
+  :legend.title
+  {:hjust [0.0],
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust nil,
+   :margin nil},
+  :axis.text.y.right
+  {:hjust [0.0],
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust nil,
+   :margin [0.0 0.0 0.0 2.2]},
+  :axis.text.x.bottom nil,
+  :strip.background.y nil,
+  :axis.line [],
+  :rect
+  {:fill ["white"],
+   :colour ["black"],
+   :linewidth [0.5],
+   :linetype [1.0],
+   :inherit.blank [true]},
+  :legend.box.spacing [11.0],
+  :panel.grid.minor.y nil,
+  :panel.grid.minor.x nil,
+  :strip.switch.pad.wrap [2.75],
+  :axis.title.x.top
+  {:hjust nil,
+   :family nil,
+   :inherit.blank [true],
+   :debug nil,
+   :angle nil,
+   :size nil,
+   :face nil,
+   :lineheight nil,
+   :colour nil,
+   :vjust [0.0],
+   :margin [0.0 0.0 2.75 0.0]},
+  :strip.text.x.top nil,
+  :legend.spacing.y nil,
+  :text
+  {:hjust [0.5],
+   :family [""],
+   :inherit.blank [true],
+   :debug [false],
+   :angle [0.0],
+   :size [11.0],
+   :face ["plain"],
+   :lineheight [0.9],
+   :colour ["black"],
+   :vjust [0.5],
+   :margin [0.0 0.0 0.0 0.0]}},
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(data.frame(x = rnorm(1000, 2, 2)), aes(x)) +
+      geom_histogram(aes(y=..density..)) +  # scale histogram y
+      geom_density(col = 'red', size=5))"
+    r
+    plotting/plot->buffered-image)
+```
+:::
+
+```{=html}
+<img src="ggplot_files/5.png" style="width:100%;" />
+```
+
+::: {.sourceClojure}
+```clojure
+(-> "(ggplot(data.frame(x = rnorm(1000, 2, 2)), aes(x)) +
+      geom_histogram(aes(y=..density..)) +  # scale histogram y
+      geom_density(col = 'red'))"
+    r
+    ggplot->clj
+    (dissoc :data))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+{:layers
+ [{:aes_params [],
+   :stat
+   {:default_aes
+    {:x [~ [after_stat count]],
+     :y [~ [after_stat count]],
+     :weight [1.0]},
+    :extra_params ["na.rm" "orientation"],
+    :super :ggproto-method,
+    :compute_group :ggproto-method,
+    :required_aes ["x|y"],
+    :setup_params :ggproto-method,
+    :dropped_aes ["weight"]},
+   :show.legend [nil],
+   :mapping {:y [~ ..density..]},
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params {:na.rm [false], :orientation [nil]},
+   :geom
+   {:setup_data :ggproto-method,
+    :rename_size [true],
+    :non_missing_aes ["xmin" "xmax" "ymin" "ymax"],
+    :extra_params ["just" "na.rm" "orientation"],
+    :super :ggproto-method,
+    :required_aes ["x" "y"],
+    :draw_panel :ggproto-method,
+    :setup_params :ggproto-method},
+   :stat_params
+   {:binwidth nil,
+    :bins nil,
+    :na.rm [false],
+    :orientation [nil],
+    :pad [false]},
+   :constructor [geom_histogram {0 aes, :y ..density..}],
+   :position
+   {:setup_data :ggproto-method,
+    :type nil,
+    :compute_panel :ggproto-method,
+    :vjust [1.0],
+    :reverse [false],
+    :super :ggproto-method,
+    :fill [false],
+    :setup_params :ggproto-method},
+   :data []}
+  {:aes_params {:colour ["red"]},
+   :stat
+   {:default_aes
+    {:x [~ [after_stat density]],
+     :y [~ [after_stat density]],
+     :fill [nil],
+     :weight nil},
+    :extra_params ["na.rm" "orientation"],
+    :super :ggproto-method,
+    :compute_group :ggproto-method,
+    :required_aes ["x|y"],
+    :setup_params :ggproto-method,
+    :dropped_aes ["weight"]},
+   :show.legend [nil],
+   :mapping nil,
+   :super :ggproto-method,
+   :inherit.aes [true],
+   :geom_params
+   {:na.rm [false], :orientation [nil], :outline.type ["upper"]},
+   :geom
+   {:default_aes
+    {:fill [nil],
+     :weight [1.0],
+     :colour ["black"],
+     :alpha [nil],
+     :linewidth [0.5],
+     :linetype [1.0]},
+    :super :ggproto-method},
+   :stat_params {:na.rm [false], :orientation [nil]},
+   :constructor {: nil, :col ["red"]},
+   :position {:compute_layer :ggproto-method, :super :ggproto-method},
+   :data []}],
+ :scales {:scales [], :super :ggproto-method},
+ :mapping {:x [~ x]},
+ :theme [],
+ :coordinates
+ {:expand [true],
+  :clip ["on"],
+  :limits {:x nil, :y nil},
+  :super :ggproto-method,
+  :default [true]},
+ :facet {:shrink [true], :super :ggproto-method},
+ :labels {:x ["x"], :y ["density"], :fill ["fill"], :weight ["weight"]}}
 

### 2024-02-08 docs/projects/noj/ml.qmd
Noj -rerendered

--- 2024-02-06 docs/projects/noj/ml.qmd
@@
        Min          1Q      Median          3Q         Max
-   -0.7855     -0.2024      0.0281      0.2007      0.6159
+   -0.8148     -0.2402      0.0173      0.1886      0.7180
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           1.8316     0.3045     6.0143     0.0000 ***
-sepal-width         0.6567     0.0798     8.2255     0.0000 ***
-petal-length        0.6798     0.0680     9.9990     0.0000 ***
-petal-width        -0.4501     0.1530    -2.9415     0.0041 **
+Intercept           2.0188     0.3171     6.3667     0.0000 ***
+sepal-width         0.6187     0.0852     7.2590     0.0000 ***
+petal-length        0.6704     0.0716     9.3627     0.0000 ***
+petal-width        -0.5103     0.1616    -3.1572     0.0021 **
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.2950 on 96 degrees of freedom
-Multiple R-squared: 0.8767,    Adjusted R-squared: 0.8728
-F-statistic: 227.5000 on 4 and 96 DF,  p-value: 1.726e-43
+Residual standard error: 0.3191 on 96 degrees of freedom
+Multiple R-squared: 0.8440,    Adjusted R-squared: 0.8391
+F-statistic: 173.0879 on 4 and 96 DF,  p-value: 1.363e-38
 

### 2024-02-15 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

@@
 ```clojure
-^:note-to-test/skip
-
 (wl/eval '(Dot [1 2 3] [4 5 6]))
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhwAO/A/frAB8mMSIpMyIpNSQrNSYsNikvNyMrOCMsOSQtOyYvPSkvOCYwPiswOC4zOi80OzA0OzE2PTM4PjU5Py83QzM4QDY6QTI5RTY8RDo9Qjw/Qzk+Rz0/RDA8TjI+UT1AQz5BRTtBSTxCSz1DTD5FTjNAUzVCVTlHXDtJXjxKYD1MY0FDRkJER0RFR0VGSEdISUpKS0tLTEtMTExNTUFHUUJJUkNKVERLVUVMVklOVkZOWEJNXkhPWkhQWk5SWEtSXUxUX1FRUVVVVVFUW1JWXVpaWl1dXUVPYEVRYk5WYU9YY0FRakNUbUVWb05bb1FaZlpdYVNcaFVdalZfbEpbdkpcd0tdeExeek1ffF1gZVdgbVlibk5hfVljcFtkclxmc11mdF9odlhmfGFhYWVlZWRlaGpqam1tbWJpc2NqdG5ucGFreWJsemNtfGRvfmZwf21ye290fXJycnV1dXp6en19fVlvkFpwklxzlV50l191mGZxgGhzgml0g2t2hmx3h2JyimZ2jm56inl9gnF9jnN/kH6CiHyDjXWBknaDlHiFlnqHmXuImnyJm36Lnn+Mn2eApnaJp3mMqn6Ts4KCgoWFhYWHi4mJiY6Ojo2SmIuSnZGRkZKSlJaWlpmZmZ2dnYGOoYKQo4ORpISSpoaUp4aUqImXq4+ZqIqZrYybr5CaqYGWtY2bsI6dspCftJ2iqZqir5Ggtp+ms5OiuJSjuZWkupemvZiovqGhoaWlpamqqq6urq6zvLGxsbW1tbq6ur29vZqqwZyqwJuswpysw52txp+wx6Cwx6GyyqSzyqO0zKu3ybO/0r7CyLjB0b3G1cHBwcXFxcnJyc7OzsHL28TN3M/Q0s7V39LS0tDR1NXV1dnZ2d7e3tLZ4tTb5dbd5+Li4uXl5eDk6urq6u7u7uXp8PHx8fLz9vb29vb3+vj5+/r7/P///////////////////////////////////////////////////////////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAwAO/AwAI/wDXCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS55MubLly5gza97MubPnz6BDix5NurTp06hTq17NurXr17Bjy55N+2a6bM9+XTNXG6U2aL6kiet98ls0X9G+ETcpTpovaNqWlzR37dezbOlegrsEREYMGDGATP+KLt1juU5FZMiAoV4OtPIe0+kqAx58jDG8ssPnCE1O/e9FeFLOfhxpMwkQ38UQQxCXgMMSLjK0gIEEEEAQAQYtxKCJfgRa9EwQMHxAYYUVqADDHMN1aNE2YsCgwogQSGCiGNuoaJE4/qmAQYUxZgBDEM/YWFE6msAgIY8SZNCCDLeoZAkMOyYRSCOfDBJFBBLAIAdvQkakiwwZQHADH4yAgkgXF0jgghgOdglRNECsAIEIbCgCiiJriBDBCkBI4yZE4ojRggQXeIEIKIzwcQMEH8igy58PneOfBBFEMQgojQSCBAQYxGAJSp7AIIENqyRj6qmyIBEBDJRA2tAzMmD/AIIjp54qDBgQtFAGl64mtE0QKlAQCDK1IoNMIBF8EESNvSZkzhhygiFMrckg4wgIGMgQZLMJUSIqErOcSmwyq9yQpScmZQNDBTwQQ624UGT5C7cHlRNEBiDI8u6pfEAAAyf0HmTGChGEsq+poUCwghkBG8QJDBD4cXAysoCg7IAND/SLqFCM+y4xPFQQQzYlybFCBbRMnAwxIXwgBocNdwLDA6ConEwS2baZ8TOi8mHzHhJom7FA4MSKhMfvIgMKBC6gO7Q6RXwAgrsT01LBCnKQVLQEYNicTCASxODn0ERgcAPS+5biLy5Dr0PHyVRPTMzVk7SNC8SlqGxsDhgQ/9G2NDFEEIjXagStM0i9QCyK17Tkyok6kEcu+eSUV2755ZhnrvnmnHfu+eegh+65uhJIbDMyFsch+uqst+7667DHDvo5QGAQhdfJQIEBEObI7vvvwAcvfOtxqAAC7nyEjd3wzDfv/POvc9ICBCnbHMoDMPQykifT2+I1MhVAUMIj5Jdv/vnop6/++uy37/778Mcv//z01y//FgFA0AjuSEiQgP0ADKAAB0jAAhqQfngAQAXagLs2SAAAeTigBCdIwQpaUIAJkAAScNcICARgCxcMoQhHSMICkgACFcBd41rgtJBoYnrT8poGIMCBEtrwhjjM4SOokL+aec0JFQiADv+HSMQiDtAOCvSZ15IHADsY8YlQjKL6AiABJ+AuYQGwghS3yMUicgACGsDdMCLQAk2MBBcugIC+bFYMTkWBGHCMoxznSMc62vGOeMyjHvfIxz768Y+ADKQfG/EACCgCdzzAgAgEychGOvKRkIykJAEpCwdUQA24W4MEHFCLSXryk6AMpSgdOQIM8AB3iahQI0bJyla68pWRjMKO0LYvWTCNbSKBBsQS4TVS+CsXQxPHurpmM2JQYAWtGlrUcoC7G3ygCG2jBAsoELeJgaECMEhRw3IBMVJ4LZUweI9IzBEEDPjAa10I2+ECFocPaKCa+0KEv+Y1NOlBoFQqWwXTADb/tI1BABE2G4YGVBCHtn1DBhXowul8sLtzkKQTaVyEytTWgrq1bWMSWIPKagGCDLzMoLHyQTEmhgyGykA5QzuHGKRWC5WpYVXbGtokppe3iS3CATDoREnKQYQVUMCH71oFtoCA0rbFYXqD25ctdoDNmA5NZhHgwkg/xoVV6bRt63hGDNjlvaQFIlcFxeo3gIAvfL4LFBV4JsZIkg0gfCACYKieqWzBhwp0yqnBLIKcoHCKWhEDESHI0lWxmg45uCACN3CEx6x1g1XJAWZPXRcIEBE3ZJwCCg5gQRG0edEYYKACfABGrWihBkYBgWQniUYQWEAhGjjBCYuSwApk4Aus/xIEHGNwwY5EgIQohIxROVWHbQVSjjlAyQEXQAIUfjBDDJxorVhVRydi8AEU+gAKSBABBC7ggjGss22+kMEKKHSD19IgRi0IQjRU8o05REhESVqSGVA7XOJq4jvwxRAMxIBX26YjF0CAwQrSdIEP/AgXkLXtM8QQgxVMKK3s0QR0h5sNMxhpQhL4QIbmUFSVXIMTRThAAHqgifXW1yDfuIUZEBCAEEzCFw49MUHEwQs5UCAAE5iDLsYhY4Kc4xeTCEEADmCGW3S4x9G4RA8MYIAicIK+LvEG+abRY4Skg3zGqDJCVPEIVWj5IMUgn3C/TJBpkM8bM5HyI6hM5oFc+f8RWW7zQLjsZTkLxBjkS7CWzfwINMtEzWyW85vjbGc62/nOeT40n/0cE0AfetCHXgeXJRFpPD9Cz1VedJqn/GgsR1oSXa50ou2s6T9z2s6QPrShD21pTPe41I0+taA9repHUJrVo5YzrGHiaFTTutChxvWlFX3mTa+503D+dLDt3Gpi99nYgW5zqoF9a2bnus27fkmvZ53sWtfZ2sMmdbFNfWxfd9vOoP62nJst7meTO9pknracVw1uV8s421GWtbR/PW9bizrcuh53rMvNbULLOd3/tveJ8d2Sbe/73P1Wd5vZHXB3DxzeX5Z3myedcGczmtf6jje/N77sdV+bzAz/Z4nDRQ7xNiNc2Aqvb8pXsvKMj5zMHIe5x6GNbIOTXOJkpji2BQ5ygj/c52R+eb13/u6eR5reJgf40C1edIxrWeM497fO2/1xbYfc5i1PesknfvIvz1wlNb/6zb8MdbJLHeVE97rRWY50tmt96VznubnrruW2B73se457vucOdr5XWelRj/lwz56StFcZ63avduKZfnGne7vjeW/63pUN9C8LHe5Ul7vVH7/2vo/97283u+Ab/nW1hz3ymK941wc/+h5DXsuId7vibct4lDje9qWvst89D/hMr17lrSf9600ved1TvuqWB3bntfx51Yee9tE/+OmJn/rAX5/1hHe9/+F7nHO8y17vBX/69qlf/Fcfn+bJB/7yD7/+Klff+7MHf+1lfHvh17/H92d834d84ad84ydj5Td5mVd5m3douYd6u4dVvXcSv8d/wUd+/ydjAeh+Awh/BSh/B3hiCeh8Cwh9DSh9sTd1+UeA+3di/ddjD8h9Edg2E2gSFeiCF4iAd6eA56d56Xd5W9eDDPiD6JaBJ7aB9/Z+aBd/Fjh/GDh99td+SdiBS/iBTRiC9TWCEPh8opd9LmeE9YWEC6eEjceEOOiEOgiFACiFY0iFZWiFZ4iFw6WFMsiF2HeCEZeCoLeCHtiC9fWCMhaD7Nd9AsiHVeiHwwWIIriDJCiEJv9IhHkYhCqIfkfHeXpofYb4hojoXzm4iGqogWwoc2Toe2b4h52YhYy4hSXYhXj4hZ94hKG4eKNIgaWYiKc4h2A4XGIoim5IinBoimi4iM2nio7IipD4c5eIf5RId5YoiXu4jIWnfsNYh6t4h8eYda8YhrHIe7Nog7XIicFYX4IYhYTIgZnoi5tIWLdoW8M3iDM4NDVYEjcIjHLIjqlIjcVojZXogLloW7soi71Ii79oi+GIi9moi9sogd0oj9+ojgVpj9Pojnaof16IjclYiNAofs1ofpPog/tIbRdpjhlpgOp3kP6YkDS4kCQxjwRZj1g1jmtYjlN4jgKZjm2jiKj/aJJY9Y/cGJDeOJDg6JJtQ4cSWY0U2Ypip5Ntw5MK6ZMMCZQOKZRD047k+I4ZE48r2ZA3uY5YRZRVOZEsWJF2p5RDw5Qp6ZRZCZVb+ZAv2Y87iZLwqJIjwZJBKY0hOZMjCYIleZdtSJM/aZNDg5PDBZOgKJN9mZdXuJfOiImIGYd2uZjK6JHMyI9kmTFmGZdoOZdaGZhcOZRuuZRweZVyKRJ0GZWPyZHPKJnRCISoyZiqqZGUyZe86JdPCZgZI5gQKZsASZtpaZsNg5td+ZllGZoNg5WaqZacyZZtQ5iwaJiz2Zj0qJitGZlD+JH9FpFfaZRhiZRfxpza6Jy7CZ0t/ymdPNiR1TmZIAmZGPmaJMma5Zma57maRViZDXOZopmZpLmZt9mZU3mPRZmPR3mNY6mbPcmbx+mbAQOcyymclkmcAWOc+Ymc+6mc/UmfAWOfxTmaIVGaaymVGeOVMWmVGYqfG6qfv8mfGeOdCAmeBSqedemejWiej2idJIedIQqWfSiWpmeh9IKhD6qhIMGhyemhDaOiJ8miTWmgEYqg9KKg/WmjhSmiP0qiQWqiCYqiDUOVN6qdOcqduMeg9emg9AKhJSqhJ0qhHwqmFyqm3EKmVWqmV4qmWeqf2Qmg2ymgX8qj3OKjYwqkHyGkE0qkAaOlUYqjh6ij/gelzSmlff9KpX9qpU2KpYOqpj3Kps3ipo8Kp5EqpwFjpG+JpGeppGXKpNzipGmqqN/JqG3qpx4BqGcqqPRCqItqqJqIqDBIqXtqqb2Cqa0KqaUqqbGKq83Cp6vqqL2qqb/KqcGKqiuqqpfKqh3hqnEKq9ziqaAJqpgpqm9Kqs1iqnOqp8Oqq67Cq9Hqq90KrNwCooXKpYfqpf4Hrr1CrM9qrOWKrOeqrNUqrPEqrpBCrhwhrZtKrc2irrPKrrXqrk9IoEnqoqYZm+opkuyplzBKjDJqjDSadcx6pM66q9D6r+baK97aqfrqKvLKsfTqsfYKsug6sCMLKSU7rh27EQCbrALbKwT/m6q0io62moYKG6oM26Eb+Z6uGZ+wmZ7TuZ5E254o+LB4GbGJ6bBHC7FJK7FLG7VNO7VPa7RCS50zip7aB68ky69/4q8y+7GuErLBCrYuK7ZuQrYaMbP3WrOucrPNmrM1ubOe2LPZ+rNDGrQxCp9dK5/Xqbf3qa2Zyq0qi68sq7Z/8rL9GrNva7aQgrb5yrhu4rhjC7kZAbeJK7eQIqs4a7A6i7A6mLGfurEwe7Jlm7Jnu7K9Yq3Dia2Fy7eBSp5/O7SBW7SDy7SH6bSOObH4WLH66LWuSLgjarjHiritq7g2S6dbaqddiqfvarxTirz1qryT67quArsNKrvHS7uv/2q7FAu4Fku8GEu9jWq9KIu9f0K5zcK9Yeq91Qu+0yq+wUu+wyu4NYq+xaq+q8u+buK+zWu5XYK5bau5GMG5y+u5fwK/ayq/6Uu/AXuaW4u0uau0kWi1vYu1vzuf/Duv/hu5rJu9zDu3Ldu4bNslbru5ktu+2vu5zruu0Nuu0nurBCwkBqzCCHwRCkzCDOwmoFu3onu3pCuMH2yyIczCI+zCJQzDN2wjOSwkK5zALRzAL9zAJ3y5KSzFO2wRPczEP9wldKuxdvuXeJuTR5y6SUzFS2zFTYzFT6wiUWwjU8zDVdwlAmzCcdwhc6widezFdywkeQzDpnutqPu4qivCAP+Mx1fsJg5cqRDcvxJMs/b7n8IboBcLe7z7nL4bncBryfiLyebbnVlcwFtMx11cEV/sxmEsJGN8umVcm2dskGmMyGtsx23MyG/syKWMw6fsx6lMEausy61sI0FMxkNsxkWMioUcu4ecuYmsxIssyI3cJY+cq5EMwpMct5Vcp5fMEtyAB3jgDId2DnlgB7YQaZBwB5AQabZwB3gQY3LmDOLMDTCRDr1gMgAAABhgBrkwYSf2DAeyzw8gBp3AWTKWDZdABAMAAANABJcAZTIGDp0gBg+wz+LRX/VVDrlgBhiwzyogB73wzBERDS3yARMSARBGBLUlY9sQBzDAAhiWJDD/AASeQNLSUQ6UECGfJQESoAEsIAOUANA3eQvr8QEVoNIYYGBxcGS21QtEECJJLQFLvV8mhhK6QF0RoAFaoAd60AUhAAE+wk/DJQ1AME0UAAVtsAdqcF7ONQdE3TDfkFvh4wNrwAdr4AMotCbflTHFBSUPcANgoAdtAEQKEwRjM1wPEyYi4AVerQUz1CiPchIbgwEaQAho4wgikCW4hFXa4FYQoAfVZFk84C90MFzlIAZykgVyZSq0kAW5IgZxTS90ICo80Fd+pQemRR5YdTcVIAL7UyvFgAgX0Cn0pDW1ky8HYws34FzXQFiqTQGhQEvJYAxRkCXAhFXeAgHDsi/I/+AHTJNMbcNNEBAF1J0MobAnH9U21+BZNtBV71IxGQAEfe0RlJBGNXUwVrMwWKULEDMIKlMMzR0Es+0q1yADEpAFxjIxWlABMvDcQ2MvGUADU3Uwg+Avkz00A1MB4XIwyEBRnzIS5RArt2MzDhQDvN0wY6ACInDep+II/sILbWMJLRABrb0vK3QJbcMLEEMreiMCHzAGbaMNMSABDGQzsiQDBZ4R/hTc+YQ9TZIxByUBbHA64KMCpz00QaABG+Q1SKABQdA2dKACF1DhE8MGQePUzRIq9+Q1hAQDxw0StzA9N34wMWIEqpDner7nfN7nfv7ngB7ogj7ohF7ohn7oiP+e6Ip+6IDAABAgUV7jAxVgAYte6ZZ+6Zie6Zq+6YkeCQVA5biD5gQQCZxe6qZ+6qie6pduAeaEO4sAAQwACKo+67Re67au6UZAKbgzC0wT5S40PfB0MCBAQ11U7MZOQlQwABBgMD8URMf+7NAuQUgkAUpkM8kTAE4U7dq+7fVDRVBwRR5UBdw+7uTePl90PF4jDLliRiJxC2lU5/uCJTogCapA7/Ze7/h+7/qe7/y+7/7e7wD/7wIf8AQ/8AZf8Ah/8Aqf8Ay/8AIvCX/g6JBuM5JO6Q7f8Bh/8Rqf8Ry/8R7f8SDv8ZIgCZBAAKDuNZpEAJDw8Swf8i7f8jD/8jL/H/MDPwEVcE5e8+oM8Ac0P/M+3/NA//NCT/OSYAQREAG73usj4Qs97jX65AK+HjDbsFVHHuAXsAJz0Db30uU2gwQYEOZDMwdkbuYH40AywCwN4wlpZFYT00Ex0NIhIQ6xkgVeowcRMDJts1ItbjNLAwMyPjQ0TgEttVF7EuIZw+MQ4OMkBeRCPjTZgFB64DVScAFKThKUMD24rd8XoAIMM94wEAGEEOADjtD0AjgSoFAqk04xAOEZIw7ldANkTy0XDgPZreFkDu+ncgq5It4iAQ61EwId/i7CkAMik9i3KQbBsjjenQXYbVszBQEAbuG5YlGeDwFaEPumIgolst5D/yMNsZIDMRTfIrA79e0RiWPZh1QsoEADWRL1Q/PZb+UH8LQKPhABLjAHOE0bgSInXTD4pwIQtbpAWCFG3DqECRUuZNjQ4UOIESVOpFjR4kWMGTOmm9MiApJVyUSKJMYnwgcg2TSuZNnS5UuYMVl6giFhBqiRIpEp0oABhi+ZEnHF+PAgRBc+gcCMgJABhqagUaVOpVq1JbQgKyJciLIn0BoeEHzKKWfV7Fm0aWF+K+JCAgUkbQK1SVJBggsx39Tu5dvX77pycmBcgMBjTaA9WS5EYAEk2l/IkSXD1AQDAwQaYPzw6QICwocYufhCKwJDBYYIEiR8gBGE12TYsWVL3P9WBsYKDKorZHAho1O62cGFxxY3SQZuuxIyrIgx6eBw6NH3pusUo0WG5BhUwDCzTfp38FV5BYHxITtrItD8mtNlZgUAABjG3Cob3v79mL7myIAPocgmvfATcECMpLEkCAIAICAIS6Qh8EEIIfqGEyIegE+GOX6JcEMO1xnnljIwgE+FNHQxRzJr7LCjmQ5b5NCcO+qgxUUaH1QHkjogUadGHvGjpY47TuxxyO+aUdGa2Lx55JFpiHQSunSWNOZJKoNT5RFVqtQSNmOWBG5LMP2aZklvklyyyTDTVCvKR6ZU882zrswSTjqp6vKRL+vUM6YxHykTNiWZ3HPQl9h0k1D/RDWSM1FGMbozz0YjhajPPycLFE1JM23IUE07ZUgSLD0VFaFHR/WUUjMFNVVTTlfV9EpJXNW0VFkjRRXQM2uNtFVdGV20V0ZpBZbQWy3NdVhCeUV2T1DnXHZPYZ+ls1jJLpVWT2WvffNXbeGMttswqY3MWnDVzLbcLWFFV81v16VSXMjIdVfLc+d1sll7t2w33x7h/UtefomsN+AauSV4yH0PbtFfvwBWmMaBH+ZQXYl5TLhiCBnuy2GMN4y4YwINBnnDi0fGT2O+ODZ5wI9Xtg9flyMsOebvUN5LZZrDaznn6CjmWcCZfxbOZrVwFhpKKY/GT2SlpQu6adiITsto/6hl27nqyWDGOrqnt/5LarSo9jqyq8f2i2mzufQy7eDAPktstvkqO+60fKZ7sq7vNstts+DW+6y5/65Ka8H/yrtwqfi2ym/Epwq88aDQhvyswyeHSfGqGLc8psc3d8luz82qPPSVMKdKc9JZ6jz1jCRnXabRX7fI9KlQl/2i1W+niHDdYV+796Bol8p24CXKvfiHQEe+pdiXb0j4qIh3ftOkp/88VOuZ/z17jaAPSnruETo+fN7Dt6j58L2XCfzwx+fedfMjQp979WNin3v3s1c+/onmz75+mNwve/mzXvn4JxH/WQ+ALxGg9Qg4PfgdsCEJnN4CXdLA6T3QefuT4P9DKOg8C7YEg87T4PIi2EGFfHB5IWTJCJdXQuQZEIUT3N4MH8LClbgQeTAsHgdtmMIa/pAhONSIDovHQ+Cd0IYqRB4RM2JE4CGxdzIUIqmCWMWEOBEjUOydFHWnxBkysXhavAgXdefF2/mwimIEHhktYsbboVF2VFzjFbG4DjdWBI6yk+PrwIhCNvYujxTZ4+v6yDo1CjGQuhvkRArJukOm7o8dXOTtGimRR6YukqSjoyLtiMVLRiSTpNtk6BL5w0rKLpQQGWXoSum5SUowla9b5UNa6blXbq6TqPxkFWvpkFtuLpeWi+UBZ8m6XzYkmJYb5uROucReCjGZDFnm5Jr/CbldQhNPdxwimVKFKW6Kr3rhTEgx+XfM1E1zIdWE3DUb98wwRvOH6lQIOxvnTsSZM37oJB09E2JPxOGzcNmM5zbJiRB/IgSghROo4OAJSHnaMKHrWKjgGvo3fZqPn6GbaEX/dlG9ERSiBj1oR491UJDeLaPh26jnTKoqlI7zoA+lZERn+FJwhjOldBNpTUlKTpweVJxtEipCVsq9lm4uqELdadxoKkubonCpMSVqUY+avaRabqrkbCrbegrVn4ZzqzqVKTmfasyodnCs3Oxq2q5qvaxObq13bKvZvorWsHJzrlis69jeOr24Qm6vVeyr1856zrRKcLBCLOzW7orY/7zecbE/bCzW/uq8wDZusjasbNUOu8/EHnCzM+ws1C67vMwibrQoLG3THgvayILSm7iCKVfLGs7PajS0/FttB1urtNMiL7WF660Ef3u01+o2tr6crbFqS9aqCjW4xRuu4Ip7wOMKLbcs3W38rsu/7P4sudxdrjSbW62T2ja6M8WeUKv7t+/GL7w82y5Su2u++JpvvjmbLvDeq7f8tu+23Byvfcs7z/OOK73QPRR7Y1XU/94twPgb8B3727sI023CA6wwFguM1fumL8HxWjBbO1zFC+suw3HbsANPLMT6gvjAEh3xv0pM1xf/8MNwDTH9atywG/M1xzZM8e1WzLYWZ/9wyDOMMY9nfNMfbyzIhF0yCossuyOnLckkrHIHdwzYHv8vyimbMmO7LMEmg/nJUh3zzcpM2TMf8Mqvy7LZtvzCOPPvy5gNswLbXLQ3czbP8Zsz6+o8tjvvcNDmSzOf16zWP08t0KRdNPnae9BDey3RR6z0+y5NzkxvbdNR7LT+HvFg9/a5gpEO26RZW2rrFTp1ocbaqLsI6+ntGbWqBiGr3+Zq3+J6g6cu6jpoXTVbn1HYJvx0OI8NtWTHcdkxbDY3n920aPNx2j2s9h2vrbRsG3LbSSQ2hHm9Ql/3DdjGHfcUu43Fbx8t3JBs9xffXcdHKzbdi1s3duudxnKnOt//ot135voN3n/LTtaki7fQ5q3JhL9O18I9dxMLfrqDyzfiiAw4pis+xovXLuP63bgk7+3JgfM25MMbuYDXS86JU/fjbVx59FpO4Zfj9uS8TLl3a/69m3M459xs9K57jt+fry/oLh76HWPu35kLMun2W7qSm47FhYeu4T97OClLTrqiU/zoIvbTN4u6X5pl3XNb51nXXfn10D0dw1Fn5NQDWHUuXx3FHQc13S1pdwbiHc96h/HOtQkpsQL+goJXNOF1bPiCIl6vihch4znteCJDfqSSlyzlW2h5UmOeyXx3tt9V6fkcgv7Wokeh3FVselqivoiqVzbrO6j2zbE9Z27H/yXcYUl6a8MembJ/Iu2lbXs0a96nnJdt2WmbUxMj/4CuN7Lw00n8LRpf29LnX9hlPnYfO9+50Mcx9wmtfLAyn7niR+9zo99gmKMfr+o3L/sV7P7yw1/nzvI4+MVsfxLDPyEzP0YDPm+zvn7CvjLSPnEjQEvjv77zPz8DQBsTQCpzQE+DwNKTwFWjQCCzQDPDQFNDtf6jPwTzQCkDQTgTwViTP8gyQRpDQTJTQUFjwVxzQdiCQSiTQTejQUqzwWEjwQjUQTbjQUDzwVcDQmbTwODjwF4zQklDwmBTQmpjwgN0QnSDwlaTQnajQm6zQnhDQI5SwDdiQHrzQnITwg0kQv9I08Jf40J/Q0N3A0N8Y0N9c0N1g0OEk0N7o0OUs0OCw0N+00ON40OAU8MmBESVE0SDI0SSM0SFw0HlUkSfY0SMc0SX0z8Ck0TyokSks0SRw0Sc00QLM8AwxEKLA0WWE0WhI0Ws40QD80Syq5T2I78BdMUqoj4sE0OXIkM9MkOIg0Q/gkUZk8Xwo8X7s8ULxMXCQ8QrNMb/Q8YAVMYQZMbH80Oeg8YJlMYKpMYVtMbMw8bDKyreEybf2xzvgzpUBDlVtDlWZDpwHD1xjDxy9EVCAkavE0bW0UU640WlskdHwse300eTc8ZT1MYO5MYP9MYajEcrI0YnQ8gnVMgUZMj/H3RIL4NINZPILKTIGbTIJMTI5JvHzavHdgS6d7Q6kZQzU6xDk/TIHgTJKVxJPdNIR+PIVITJI5TJLqTJ8yPJ5XtJs2OqcySmlvxDoXy+sytKZ7JJo8NJdtTJKOTJOPRJ8+FHQ/NHrQJITBLI3iNIsDvKbEzK8VtKsDQlpxQ7qKS5k1S6lMw7q3zAYtM9milHZmJKyME9y6HLmLFLa8LLdxLLcRQqv2wnwEQcrJw1rZQrrhQlrzTHs/w9oEw/sqxFs4xLTzNIlyTMxmSlx7zLyETHtPy+tZS6tqS6txw8zMyexGS4xRSszrSlz/zL0DRKzURKzjzNu0vNxlvNFpzM//mrzGS8zGJrTa17Tc2KTWCaTcOszaYEzhcUzmkkTqsSTHrMTancQqrcQ9+8QejMQensRuqUrtFUx9KsO90MPN68vO4MwrlETtVSTmVizns6zMLRy8nhS5cpzPp0Tmwqz7lbR7bMzjfczkJsT2a7zbHEzqGkKgRFHvyEHP1cGf4MKPsUHONcO/gkLvmkJvq0UP8MzO+cxPBcyPF0sPcUUNMk0Dw00Ed80OLJ0NzbUOvq0HX6UIa6UIwC0NdTUfRk0UF00UwstnQM0PP8u/RcvPUMPRgltxHtxBKtyBONvyeNxSj9yCnVOQUdzJKy0XrCUYvSUb2J0MaZUJPxJ23wBP8sQAAEGAJOcBBuAgdckIMEMIAZsIRnONLQKYdeoAMLMAALoINeqA++egZLmIEBWIA4wAVwCCdp4IQhYFMs8ARt+AtwmIQYcIEMUA0MaIEYiINKFSJz4AQZMA1OXQEYEAP1qCJdII8VqIAIqABUDQJdwCJoEIPbyI3VgAEg4AQh+SFtiAPr0NUPcAEYmIRG3QtpCIIWkAAImAEkSAIagAAJWAEg0BAbAocycAEMeAAQ8AEnuIEIgAAViAFP+KFyoAMYyAAIqAAecAIeqACxgAE6IFQUookPgAAIuAEnQAINeACfGINknaFfAIJmxYwkQAIRoNYWCAI4RQttAAIVgAD/L5CFnKiFNtgNGXiGGRIHMWgBCEgCUkCGkRiGQQCBCoCBc2WtOYCBCqgBRiBZkSiGRqgBCWiBObAhmqgADSCEYRgJZCiFJHiAFjCIGXoGGcCONqCFnJAFMCBXIAhVsyiHIlCBCnCEnMiJU9CADACCgT0gOQBZP8jakaCFG5AAGFhVCfIEF4gAKSgGsk0GYsgCCFBZFIKGmriBWojbZPADCHCBnO0gcACCDNCAU8haZCBZR4gAFSgCe6UKmoCAROBbkSAFCGgBSuigZ6gJMKDcZKgFEFABMdBTvQEHGcAAH4BbvjUGH8AAGfha/RKDDwABW/BcMEBbjpWgSQBZUvBc/0RwALu1inQAAgzgAZmlXC2ogBiA3fCJgxXQAGHw3GQYhAiAAWzln04A2cP13FP4206QoF+AAQgYBOkVBg1QgTiQINPFAC6Q3mTYAQwIgnOwCryFAERwX1GoW9HgH3GQAQno3PKNAMyVoCL4gBtw32S4gQ8oAgmihBWQgJ+VXi+oABl4jvjJBfEVBfdFBAiQAbWdClyAgQeQhePlW2QQCy1IXBVeYRZuYRd+YRiOYRmeYRquYRu+YRzOYR3GYVDQV0UoYb7NAQyggR0uYiM+YiROYiVe4hwOhnZVAwRWAwl4gGBgYiu+YizOYi024mSYgeJFYEV4AAkAhS0uYzM+Y/80VmItuAwgjltZ+FtcsApNAFlgQGANgAAOWBI93mM+7mM//mNADmRBHmRCLmRDPmRETmRFRuQqCAAIIGP3dYIKCIBFrmRLvmRMzmRN3uREtgMAqAA+QGA+kAAAsANOPmVUTmVVXuVLDgAJgAIE7uEAmAJWrmVbvmVc1mQOgAANQGBguFyoqIpOcAEI2FvpRQYKgIASyGVmbmZnfuZH2AJHbgQERoIKSABozmZt3mZMxgMAkAA9QGA9IGU84GZzPmd0/uMEkAAkQOBGgIAA2IJ0nmd63mYSaFcEroXLXVmq4AXxDQX3pYXL3QR0OIeCPmiDTmiEXmiFbmiGfmiHjmj/iJ5oia5oir5oi85ojN5oje5ojqboanDZUHZfEPiANPhoj05plF5plW5pln5pl45pmC5oczjdKEDgKHBdc0iHmZZpn+5poP5poQ5qok7odEiD2UVgv4UBbChqpx5qqH5qqY5qn55jCGBa6Q2Fun2NqjDdCoBi6R2EDn4M8CKCDDBe6e1eGLgFCaKDFbgAYpBeYpBVOpCgEIaA7fVcHsgAIpCgaJCBCCBf6VUDCmbeqHDeCjBmviUGEVhg0r2bYYYAgPZcJ3DdAOGfX4iBCBhpyjUJ65Wgb4iBC3CCNs4JUADe78WuAhaBuKbcWpDV9DWLa4gBCfCB1o5bLZCAGAAK/wkShyDIABBQbLINhL8NZgkqAxagAA3mW1KIgBUwAxTSBGIOBMqlBRDoWgvmH1+oiSygXGLwAd2+BrTghLxtBbKtBSe43EkgWNEGgcnOCWJYAwhggTF43PjZBiD4AAogBCBGBkKgAJTwjg4qhzFogQdgg9seCVAAAQyIgett67aFAqzOiVbIgepN7bNQB0qwDAiAAkQAhVBQhORNWTP41Q7CBRnIVx8IBBBnhDUAAQEugsvuIGgAghV4Vj1wBFFwBD2gAecGgg8G7SJoVg1YA0YQhU8IBCR4ANCI4xkyhzhwiwrgAkUABVAghCiAgAs41h1RC08YVgh4gDDHgBWQAf9LmN8f+oUg4FZn1dcKYA05yG4UygYxcAHz0Nd2LVYxUIkfEgdh/YDLiAAxxgAXCALe5ixLiAHcwHOxaAEZ4Oe92AZLsPEAIIAMkAE64PMqEodOIAIYqPQIiAEzyF3CygUxkAEGMAAGiAExyIXHnpxfMAPNJoABaI1OkHMbugY6SNoBGAAVAAJLEPC/MIddsIIqeAX7JqxqsIIpYARcx6Jt+AMq+ANhDydxYAQqsIJq6PJwKodXsAIr2AUTn06ifARiKE4erT4fRVIgbUQhHUUiTfddXPfTS9LKW9LVa9LeIVPEMdORqdAcDdF8kvd+pPfYs/fPw/fa03d729Lr7FL/hE89hT8+hr8dGd1LGoUvL/0nMP0oMVUpgs9Kgx++iJ+9id++io9Ehy9JBlXKck/5YazSYrzSmMzSTZT5iKT5nbT5Ulz5oGz5snz5eMf5jdT5qeR5Dwt5xRz56yv54jv5BoR5jiP6mzR67UT6vfN5ygR6yxT6orr4/Mx4ANt4hep4vUG7mOH3wvF3kAH4MBX4+7ROlof4dr/Ed2/FoU/RV09Ap88+qD9DqU8dsJdQsZcwsqcos78btHeZIu3RvR/Dvl/Avw/GwA9Lqn9Kqy9QrBeiwS/Twteww/eos/94ulF7wWH7jnF7j4d7h5L7n6f7BlWvyo87pXdNpuf7ug/F/7uHx7w3t9uH/Nxfxd1XyXjX+uDk+uH0evK8fLXM/Bbd/GvUe+cPUujPPOOPTuQndwftfYF7/F6M/DKc/Hycfc/p/H7/fBYL/cSnm8VfGdP/G9THGNUffdbf0esHz+wXT+U/KPNfe/QHiHUCBxIsaPAgwoQKFzJs6PAhxIgQpz165E0iRofeKk7L6PEjyJAiR5IsaTBdRWMmV7Js6fLlS1WPVMGsafMmzpvGKqbL6fMn0KAMKVoUanDjo45GlzJtyhLlI5VOp1KtClGmJKtat3Jdt/NRz65ixwYletEpUqVk17J9CVVq27hyR8qkOfcuXolfw+bt6/eg2alp/xIu/P+2MGK/kmYmbnx3r+PIbAOj5Sj5stjDmDdrxcr5M1XIoEcbpdx0MOnUPzWrbn2zruvYNUXLrm3SNFPUtneLZM37t8fFdoET18uzOPKHuJfqTu4coe/n0gnCnm59IO3r0pcbba7defTvyT2Ll569fHHuQr2jBx6+/W/h8JOfn79bfVD29mu/3y+7un+81Rega/gBpR+BqvWXYGrkMSjbgA+OZuBPCEr42YIXcgaghqlF2CFmFPpkIYiSZVhiZPKhONqHKzYmYk4kuojYiTMW5qCNl7WY418w4iQjj33VGGReHBKZ2I5H3uXjTUAqKdeQT8alopSFJVnlZBWddZplWP7/FaWXYxkZ5mPHkZkXkzY5eSZXYLLZ2SNZvVkmWHPOlWZNa9pJlZt7OkWln2tdGahTeMKkJ6FL9ZmoUGMyqtWgjwpl6EuISrpaSpd2haOmVUXaaU6UumQpqDYtWmpNjqJq1KerwiRqS6S62tKps7IEqK1CtZrrSrCyJCuvJNUaLF1xEqurmcf65OtKwCr70bDPeqSqtC7tWq1HzJrkLLYRRdstRLiC29K1406kpWBdmktrpuu6RK27IZUb70LalsQtvdC1m29JnPIrb7L/hmQvSfgKPNC3Bw8krsIYzduwQASPZLDCCTcML8QNPQyxxCJRfLDFCvubMUQbN9xxSB8L/xzywRiTrJDJCqMMksr/siwwwy9rHLDODs38Uc383vzvyD0vFPPBP3sUdL5D8+uy0QUhLbDSGTFNr9P55hw1QlP/WzVGV8ebNb1Qcy2Q1/yCLZHY7pIdb9FnG5R2vmtH1Pa6b7u7tdwE0U2v3RDhba7e65p99t/xBv7Q4OMWbm7cfWPHs+QFLa6RupWftK/mBh3OdeLuXt5Q4+A+Pi7flYe+7ugMld7t6eBGrjrlna/T+kKvYxt7t59Hvbq5uCuke7W8Y5u65MCPK3xCxEtrfLW+G608uMwj5Pyz0Es7e/K1d279Qdgrq/2zyPdNfbfgH5W57QKRr6z0PaOPrfoFif9/7PvHcn++95rXT9D9iJU/YsVPZ/Or1v8GEsBgDTBY5pPbAaWVQIEskFcN5NX+INi/yk1wHRXM1QVzVcCXRfBZHfygrUJoqwciboOSOyH72qfCWY2QZCVUFgyT0r6CzNBVGWxhnXY4kByqRYg9XBULQefCvhFRiAjjnBBrmLEbHquJTlzHEVH1QyUG0YlWdGIWSyVFiFGRWF80IhR3mMTfLVFuZ9xhGEG1RTZ2UYhvlGEa2zfGhpUxWHe0XRw7tcbptfFsf+xcIDW1R4X1kVeH1FwiLzVHQtZxh4+sXCQlNUj5FZJrl5RcJh+1yIM1Mlef7FsoGTVJTlayfaeUWyr/EzVKgZXSVq88WywJtUkDdjJqt+RaLgO1Sl620na/jFow/TTLf9VyVsc0WjL3tEsS9tJoz+xZNO20TH4101XX1Fk25zRMahbze+iqjA6vGM43TdOG1ezZN1+2TjZtM1/dXFU8STbPM43TneX03zm5lE4w5tF29aTXPVGVz4ztk0ztnOI7dbZQiDU0TP2E6D85GNDcxBCQBe3cQeOV0FJNtGEV9dJDyRjRl5W0Yh/VXEjdNVJQtRRkL63cRVWa0RdulDkdReRNJZdSPq6UZDVdWVD7FtN1zbRTR7VZUuWWU6LulIk97c5PIRnVsy3VXE3V1FOFtlWuDZWRRc1YWJs2/9aoTdWsVXXjVdeTVUyu1WhdHddXL5VWrNW1Z2Ul5Vk5Ftf8zBWUfdXZXcGVV0ntdWyHfVlbAftWQw72QIVF5WNJ9ldaBvZkla3QZWGZ2YwltluLfVRj3TZaiEWWs5P15GdHFFpcrvZijLmiVzors9jGaLbArK3CNstM3SaNtz/yLTKB2zJj4fa0jEpt3pQrsNJiy7mJgi7hpPsv4XKTuFQzbpOQC03tPu22V7QuobDrOPLmq7XDfa0vwasm8WKTvfTirj29+zX55om+4LQv3MzrRPQGSr2mA7C73Ntd+FqTv4fyrzwRbDgBC5HAfjIw7CRsLvwiVL9qc3ClIKxPDf+PS8H5ZTA8QTwqETOUxLKj8A4tvCcM787F3eKwSD1cNxXHisUUtTG2qFstGduJxsUDcvSYe14dA47Hv/KxSZEsLRzLlMmKc3KzoOzSqOB2HUKWFpHnZOTnSflZJu4wiiWK5W1p2aZcxu2XnxXmN405e2VWFpWZamXRrflebUbqm6945hynmaV9LtifoRpoJ8ZZWXNmU53Hd+dj5dmre2bdoSeWaLEuOoowbt+jzxRp/E2agEoe8KWDl2mPbVqtnVbjp20XajKNWoClDlajjzXrMNWagbfG4KkrnOrlrTplrebrq/UY687t2ku9tuCvc1VpvA67esWm2bEdm2yDBjv/xtVO37WBlm3Vbhuky9Zcs7H0bBBGe4Xnpl2hjRrupY07uuWG6bu7F2+0zttq9c7uvXHabVB/m379Dtu/1xtwoeabf/sWbFHQWUQ4tpuGDdfgwz0bcYFOHI8LV+rAZV1wBB6cbQk/8MelenEg8sWOJb/byTOc8rNNW7Ejl+DLBRfzGs+ca4OucsZ3u3GODhSNPWfryrnYckvmnHE7P/LRjVZz097chE3HXNEpHvWe5ZpY6a7SulNYcR+GnNlVx+HVSfd0Mm9dZ1Ov7tmrmHbXrd3ObYds0um4dFfOPXd1l/TdSfZzPQe9uEP3adY9DhdG552Sezdm34f3d1IHPmNv/x9y3M0Y+eZN3taVZ23Z0Z15P27+ep339edtOxxUF/67h8dq4j2a+uA2npWPN+fr5Rp7oM5+uasXduv3m3vC7l6rvZ9u6OF9e4AO37LFp+vxt1t7Yi5fo80H7fMNG/3y/t7bwf/w9WWbfcxuv73J13f1eRr+3o5ftOUv2/TJmX6rrv+47aft++N1eTCP3pGlD9/pQVv+Jdj5Odz8wVX9hdf9/dYATlj3Edz37VgCztcCJlcDblj8+dMBUtYE9lcFjtcFllgGYtQGwlYHPtgH1lcIvpicLFkENtkJhlgK/tcK3tgI6lQJxlcMsoQ5QEMhkAAJwIEvlAMcSUMnlEAHaP+BLoiDEGkDLhwBBxwBLmiDEImDLmgBB5RAJ0hDDpJMOfgCHJBACRTCM3RhSZxDLgRBDHwABEBABsAAEHQCEWrOL4iBDLRAG2IADMQAJYBD51xDHMQADFAABFCAC8RAHFxD54ADJcAADGAABERAC8iAGPxC55RDJwABDLAhBKgADARBLpzDT4hDGcBABkTAA1xABeQhDIjBNkiOOTSiCrQhBVxAG0pACwABNFTOLciACkhAG14AIUrACsQALlTOMwBBC0jAA0SAKkKABHwADFCCOUjONhTBIz4ABFTAKj6ANJoBE+KEOBRBC0RADSiCLSRDMgxDIyABBKwAELwiLsn/AQxIQAgEgiyoIzKEghZAwAfIgCXKDSc8YgW0wSkggzqeQhtQgB5yQt/8whpCABeIQjGooywEAghIAAzIgTrIzTYEwSwiQSMMQzIggy0owg1AQAsUQTjWRDqkAR7ugTGoI02WJCK8oxjMYdRoAgw8QBQQQ03SJCloQAYAARVyTS/EgATYwCwEpTrOgg1oZC+cjTYAQQZogCg4ZTIQQxRAAAxowtmUQxHMIiIgpFO2gSSaQUfWBC/EQAS0gVbSJCF4ZSdwjTYoJRKYpVaeAjHGAdeUQxB8gAgAQ1wmAzCIwAcEgU72TBysQAScQmEiAxJUAAwcpdF0Qk8iQknGJVrG/wAv2AQRCKZeaiUy/AAGyMBivswkOGZTFmYytIFGSkPU4AIMQIAjuGYyOEIEwMAxGo00yIAE6AFuykIErMAkRE05yAAG5KVrIgNiFkFNXEM9BgJu5qZX+oLRlAMQYIAUVKctqCRYGk0ZiGZ1ImYZ7CQe1kJ1SgEGAEFqZkwv1KYjjKZTIkMgSIAMKOJL5EJPrkJ1EoMbvgE1DCiBFqiBHiiCJqiCLiiDNqiDPiiERqiETiiFRmgsYEAEEEJ1JsMNYIAQVCiIhqiIjiiJlqiJTqgzYMAFgAF9auUXYAAGOMOJziiN1qiN3qiICgEG1MCG3uQHxAKOBqmQDimRlugbfP/AAwAlbq6CV/amS3ACHgrDhmoABHBARVwplmaplm4pl3apl34pmIapmI4pmZapmZ5pmVpBADwAKGyoE0jAAaCpnM4pndapnd4pnprpHQCABOzBhvKBBACAHeQpoRaqoR4qotLpAUiAE2woKDxAAFhBok4qpVaqpd5pB0DABWwoMLyjQ74ElEIAYVanLZLApZ4qqqaqqj6CmkJAm1bnZCLAqs4qrdZqne5pcG7oHgQqHtiqr/4qsHIpAjDqhn4CBATAFQSrsi5rrWaqBnCqStblftYmZOJmp6qAIHSDtm4rt3art34ruIaruI4ruZaruZ4ruqaruq7ruXrDLqhABAz/wobOQAY8AbveK77mq77uK7/2q7pawwdcQBdsaBdgwAdYg78mrMIuLMM2bL4+QQbMwIYOQifugsNeLMZmrMbyqyDM4qi65ik4AAzkAkxkA3DyQXUqglcGpM6YQxBgQKPi5ixEa9TEwQeAwIaCwAf45WXiIS1UpxO0ZzX2DERCwCJUJx9QgAxYpkuIwc1WZGTmAAYoZtRYAh76p2uCAX5mQ9ToQm0qAm4mwgPAgC5ETTYopRosqUpaQtSYg1XmQIvWJDHorBjYxC/U48AWJh/sppP2zDYo5w1ArVaGgkrSAdeYQxF8gAa0plbOggZ8QBGIYtTQwQq4amEWg9TKwDdw/w1tQgDKxiUydAFlsixMzEFtdoGS1iQy6IFKlsHQRs0t1KMPpKNTKkIFJObmcg00xAAGiEC1BuUpiMBp7iLXfENgVsDROmUt+IBGesLZmEMZVC4fCC5NEkMXQIALzAFOlEMZuIAEgIAfnIIwDMMqDAINqCQR+OHZqEMjSkAFrIEo2AIxyIIi+IA/AoFsyg1/QmIWOEItEEMtOEIWQAAGxADJyk00AMEHRAASKIIsEIMtiMIacOM09g04EIELRMAMDMIqDAMwnEIfgEAEuEAZvOdLlAM9fgAwtiE0viE4So46dEIMrMAqsjABuwARcK3k9IIyYoADRIADBGMuYqfkZP8DETwiKrJwBayADHSCGfILKcKABlDAD/9wNMIAHZhwTfiCGMxwAzRABsgAEejCEwuMNAQiDDSAA1wAHMrhIk6CDMQABARxDMjAJORu5YxDJsZABTiAyCJi/mKSLhCBDHyAH6tADFTiUmQDJqDACRgCFwrRN+SCI7PBM7yu7YhDLzTBCTRBL7Sk7ZjDM7SBCaRALuCx7aiDNBjCCaAAJugw0XWc7C2epz2gyL3gle1gj81ghNVgkN0gVZWxvOnyk/HyiPlyktmy2eEynxFzlhlziyHzlAGzWwkzvzkzm0Hzj0mzmRUgxlkzxG1JLOPWSWFJ1wXL10lJ2M1KOVfJ/sn/Wf+Z0v+tjzZHGTfDDzVLFjhrnDgjnizzHi3v0OBZGjNjGjb7WT1vWUC3zzs7Wjzb0jzbTwCy2z3rTz671j4LXT/D3j8b30JzWwuyXkYb3kbrXkdD30ebmzKLXkGr2kEjWkK7WUprTkPr2kM7U0QD0ESLXUWbWkgD30i7XkkT30lr30wL3EorH26ts6u0s5TUtNfdtDfltALtNDuP3aqcM6+k85Mw9ao49ZMMNLW1NLG9tKbFNKAdNcMlNfotNVVTkFU3NVZr0UW/V1AL31A7X1GTn1qD3E97312DX15j3167X1+rHFsboFubNauhtaIdNs3V9YIFtgQOtvgVNv5B/7bPeTPLLbZlsx9mM6BmI11if7Nnp4tjc9poS51knxhlw+Bn219oW+Bqc11ro9lr53JsK+Bsg2BtIxZnK91pSxw5z3WpQDU6SzU+vbUHxfVXG7cc3Tah5XYz7zYF9rYK/jbe/TUEUrdBW7cHYjcNarfgSTfQebdLgzcKincvk7flmTfhoXdZq7cMsvcxuzfocfcty7e1Mbaxpbar4bfqdRlXK4lXowpYKwlyb7VyKxRzo9BV9zSuwTdB8ze4+Te2ATiyCbjIBLfeDTfHFbeE88qC50qBH8mBl0qCH4lWm3iDk9SDOzeCQ3eniLXNkXV/0/eKabi2cbjvEfiL01SM8/84ufk4zlD4WFu4wWG4uBG5vRk50Xi444H4OKsTjSsSkt+4kpMck9ObkwMclPNLidvKiRNJioPKihNJi5N5kDvVkNt3NIe5+en3Mm85znW5v325wsn5fWU51eH4hev4LsP5NvN5gJV2Z1/RmXdKmgeJjf+5nVsdniOcnqOcoRMgogu3or+5iF/6uoz5rJR5kCy6pjQ6jzw63AH6kgt6MRO6PXs65Ph5qkc62k26yVW6zME66sg65qk6l7P6M7u6QnfZmod6m4MVp1v5iIuQlNselftzp3cZqLuKqPMIqV+KqedIsVP7setVshPUstsKqvc6rcudrcMcrvOcrr9Ypn//+Kafu86lO9Stuw22+5S/O7Bns7DLNLE3O/U9O0dHO5zxOv/5+p3nO0Lve1pLO8HDs8FLOsLDtMI/dr/bu7PjO2pPvGr3O52zdLlrHrw7nbyzHb0fT8M79MPXesSftcYHeMUDecqb+8o3dstvOMfD/MeTXshjXc33+Ms3V7cz1rcbXclXy7SvSrXnyLVLSrbbyLgXfM77386r3cjbXdFvz8nbdMyD/Mz/d88XOcNb/L9jPHEr+9V3s9jLH8CbtMALmr+rPdmHuNmHPc6vPVG3PeOlvQbavV7jvad1vFLHfZWD+9njs96TIN8Ttt/D2uHjYOJf9uIrG+C3teBD+9wP/3zjB/Pjg3bk287Ro0rS28jSP0rTz8i2I33Qo9bQa13hW/TkK3blB/zlX9Hnl0roz8joM0rpu8jpg37qP9fqK97NA/3W63zXZ/jXP/nPu2DUy/PU013VA17rE0vtg8rtu0juJ8rur8jTO3zzQ/Tz+130U970T3jmV/Pmy3bnd071d8r1r0j2E8r2o0jv2/7vX1fwz/LwM3/68/b6A8Q6gQMJFjR4EGFChQsZNnT4EGJEiRMpEpT0SFVFjRs5dvT4EeRHY48epQt5EmVKlStVTiPpjSVEbySnxbR5E2fOlOlIGtP5E2hQoQhVYRx6FGlSlSNLKnX6FCpEl49gKp35qP9mVK1bt/J85JNrWLFIi0oaexZtTqYm07Z1G3Jq1aRXs761e3eiV7B4+fZdWDSjX8GDB64lfLhvXKd0ETe2q9dx5LYXA0u2HNbwZc1RFVuluRm0U8ihSR8tWxp10MypWdvsPPdza9krR8+2fRLwbd0gV+/2TfE1Usa/iUusXRx5Q8rJmTPs3Rz6wOBHh0e3vu74dei5tVt/3h359KHVwSfPXr74afTMv6/fLV4oefe+z8/Xvdw+8fb5ZcMPKp+/2eoLsDXuCLxtvwNL8w8oABVEbcAHSVNPwtYSrFAzBn9yEMPNIuzwMgNBJO3CER3TUCcOTYzswxUbw8/FzUqMcTD/FHNSkUbCWsxRMAp5jGzGH/GyESccheRrxyPvElFJwoJssi0ibzISSreSrDItGLH068ktxZLSJiq9HOvKMcNi0sy3ukyTs5cWi43Nt8qMEyof6UxrzTuTAjMmMfUUrac/JzNKULTyLDQoPlnyE9Gh5mw0KDQhherQSXFSdCVGLdXp0U1xstNTpSoNdSVMVdKU1Jg6TXUlSVlVjSS2Xj3K1JRQnRWlVXENSctdgRrV145qRenWYD3S1ViOQE3WJmCZBc5Nz7B6NidkqZ3I1WtRclbbh4Y9qdhuI7JWXId6LfckbtFV6NuQwl2XIXLhTSjbeTVS196C2gXp3XwPktdf/4KWDZgifAne96N+CR4I4IXPXXgigwNG2COFIW6Y4HohdkhifynuyOKFMQ544I0f6jjfjzkKmeCR/dXY5IVQtlfljVgO2OV8H46Z41h5nqhmjW72N2d7S/5ZoZnnDbqiofMtel6YkTZIaXiZpshpe6GGd+epE6p63asnynrerdeV2uvCfE67IbElIhtes9E9mm2CwEbX7YjgXlfucruu2+61AU8ob5ngHPzfQBGnl9DFD7q73MIf2hvdvsWle3DIxZXcIcrLtbxbtNnWvFvOG/JcXNC1/Rtx0rU1nSHUu1X9WswBd/1a2BeSXVvaqRU9bdyp1V0h3q/1/VnWMxfccf+CiE/IeGqRZxZ4r4V/9nmEon92+mRtr/t6ZrM/aHtmuzdW+duZb16g8Q0qP9nzg61+6vCTdb8g+I2V39fvR1+fffgjiP6Cxb9d0Q9p9jOWAAdCQF8ZEFfpAx8Am8dAgThwVxCclf+CR0HHWXAdGMSVBl+FwJ8pMFggFOGsSMgqCf6vKexzXrRgMy0ZMkxxNxSICXmGQl+p8HAybGGqOGg9Dy4OiDbU4RBJ9cIOxlCHSazLDZkYKh7GzIe7kqIOBVJFTxWxfkdE3Ba56MVNXdFkWcQVGZeYQx060YhQvCEbqejGG4IxgWIcHB2FaEcZonFjapwVH9lnRkvBMYxylCH/IZtnyEkBEmKCfBUjHedISOHxhHoEHCUXZ8lGITKPigwgDYUTxEL6kX2QXJgkWcVJxHkSUZjsoSbr5srBwbJQqiQYK1NlS8DhUlCgzKQoK0hK6piykahsniyxSEu2+bJuwPyTLgPGS1JBk23S1JMwZ0nMDxpzPMispDIdR01/WTNU2EybNu/EzDQ6M23q9Bo76cTNZnoTieCMjzg7Sc7FmTNf6PSUPKdGzzi5M5Dw9BpBkWZQNgHUXgLdFEN/5tA02fOd+ByjPv/Dz1f6E3EIjaRCp0ZRnlnUTBCdl0QtZdKYoXRMGE2oRvfI0QZ59JYgHZxK4cXSSbnUZDD1kkhX/0lSpAF1Y0LdkkxHStNN2nRDOP2lTgHH03X5FFJIvRhV60bUXRr1Z1oVGVfZZlV0YbVRYm0ZWdPG1KI6tZZQTZFUo8lWr3m1mmDlmVpxZtepmbVcaEUUX4nmV6S59atwfaZcb0TXbBr2Z4AVl2ALRdinQZZneD2nXmNmWa1hNmaIzati48nYIjl2naA1mWS7RVlBebZsqt2YZgPKWZPBNm6yhRhrteXaP+GWb7p1WON06Fs9Abdyws3YI8zCxXUY907I/ZxySUbcG0KXThYUhyuWoIRMfEOH5fgFE5QQiGwsMRphUEIYoiGr5qkjG4FQAhN+UQ4dbiMTSliCK8RxFP9pxAEGKigAAzIAgzL8onnfmIQMYFCAAkhABkXIhXsBJw5OBEEGDWBAA2AQhE70t5O5KEIMJMAABsBABpTYRvOeUYYYZMDEKohBHKQBlHRYQgYrkAAEeAwBCagABnOw7+ByIYMWYKDHPv4ADMQA3sFFIwguQHKSMdDhaCBuG2OAwQck8IAH8BgDLZBBLhBXDjlsecc9rsAKZGAJCrMkHQCugATU8IlVtAIUbdCABFwwBhCzjRMwQHIUFHEKWYjCDzSAgAqCoA3A+UIGH4CADwhRClmcYhBIeMAHZOALwGkjCC2AAA38IApZoGIRUYBAlTlR4TG4QAIaaAMoZLEKR4D/Yc4wkMObVWIJGEAgCbZARjKITWxieCECuuZ1zHQBAwnQgBXFLjYyArFoIvx5ateQQQY0AIphSxsZjtAABmRwDbaJowiSDsS3pb0KGkgABrpgmzrk0IIHfGEY0ia2LZAAARhY4ibQcLYT2K3vZKjB3/L2mjiAgIEZBMPgxEaGIiDQAoDPcwwquMAqklHwYq9izWNY9sYsIWpFRJzYwaABBoCA7Z81GwJrQHnHoQBvaNikDB/QADBm3nEaZCAII1+YJkR9ip4nQwsVgMGKp9aLXw/i6ISIQAx64bVtxKACWjh6KR7QAk3MMwgfoIExeg4MDaigDDHZhgwk0IajIwMR/xCQwc0bGgQMIOHoyViFA2DgCa/JQeMeNzgyLqCCOXjNE7+O9tGRAHShB0zgEUBE3tsggRgwXSUwL0Xea7HoSpAD9KEX/ehJX3rTnx71qVf96lnfete/Hvaxdz0zWhCBQOQ9GSL4ABlk33vf/x74wRf+8GEfjiNnAfdZCHM4iN985z8f+tH/PRkyMAPBGzwQEmgBM6Tffe9/H/zCr4QKHmCLvJfC37xgSSdEbf68VwACJCDJ/Olff/vfH//51//++d9///8fAANQAAcwAK0gAB7gE3APCSoAAQjQAR8QAiNQAieQAgUQDwBAAvQA9/RAAgAADyoQBENQBEeQBCEQAf8kAAmuT98cAQICYAtKEAZjUAZncAJJ4AEuAPdsoeI6gSU4QdSEAfc0AAI4gAaL0AiPEAkfwQAhABRwzwkkwACSUAqnkAoj0A4AoAL4APf4IAIAwA6qEAzDUAzxLwAqwAlwDxRasArGkA3bkAo5IAI0APeCoeJabSVwQdQ47uiIYdXQYBn+EBADURAHkRAL0RAPERETUREXkREb0REfERIb0RTgb/Ly7gYwAAciURM3kRM70RM/ERQfURkkoALAAPdwTQKUIRRXkRVb0RVfkRNxAANuAPfirgJSARZzURd3kRc/8QwyAALI7uhWwd/IbCWkgcSg7ujSEAbUD2nKIQb/MEDrjg4YKu4SvGYMxA73aOADxsBrLmEFIIDnjk4LyG3IfoYXYOABmvDoBsHfrmwl1CEIMsAGVLDYoIDcXC5m5GAFKsD9UI7apo7ukCbxIIAUji4U/M3vpkbgIOD2eq4WKsDwFi4ao+DtbuADgkAdYiIXfu0hUY4FvS5tpIHtLHLmWqHw0m7hGq4GiGHmiKEGWE4fTUYdykAFKqAVei4KKkAGauwbRc0Req7aYMAYWcIcxiAcCeH6PuECPuDa2IYSXCACwOD6VkEEyM3c0iYXSAwJxlHfgAEJLK8op4YkMWAE9FDfkAEMIMAFKOHciOADKoAd05IQIGAFxuAcbuIb/4IgHJMgFNjtFLQAAj4ACLIybcyhDKSyBhjBJYlNFtrgAqpM4aDS2UBgEGqh2GphEEAA3tyybnQhGiugDWTh24ZhEWwgAlygDMyhbq4BCCRNC07h25AhFJLALoMAHHJiG8RAyiLAAkaABi7Ax1wgCHyybsoBwCQNAmbgBoRQAtjMGaPpEraMAhwgBGwgBHjsA2JAEx7PZHghxyggAi7ABkQgAiCgwOTgHNlGGqIM/i6ABmigOjHABcQA83BiHDiBwVbgAz5gBWAgBixhJucpF4IABvjTP11gxhxtcZ5BDGCgBfpTBcRMDJ7BcbIhDmTABfhTBVYgBoJgwhYHHCwhBq0CrD9Z4AVkgBMG1CbEgRcmIQ7MYBJy4T4XR7wsIQ7KgA464bwKKRo0YQ7KQA40ob1kKBs6gQ7KIA4sob5kaBtygQ7MIA4mgRdY1LmuFEuzVEu3lEu71Eu/FEzDVEzHlEzL1EzPFE3TVE3XlE3b1E3fFE7jVE7nlE7r1E7vFE/zVE/3lE/71E//FFADVVAHlVAL1VAPFVETVVEXlVEb1VEfFVIjVVInlVIr1ToCAgA7" style="margin-top:1rem;" /></div></details></div></div>
+```{=html}
+<div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhwAO/A/frAB8mMSIpMyIpNSQrNSYsNikvNyMrOCMsOSQtOyYvPSkvOCYwPiswOC4zOi80OzA0OzE2PTM4PjU5Py83QzM4QDY6QTI5RTY8RDo9Qjw/Qzk+Rz0/RDA8TjI+UT1AQz5BRTtBSTxCSz1DTD5FTjNAUzVCVTlHXDtJXjxKYD1MY0FDRkJER0RFR0VGSEdISUpKS0tLTEtMTExNTUFHUUJJUkNKVERLVUVMVklOVkZOWEJNXkhPWkhQWk5SWEtSXUxUX1FRUVVVVVFUW1JWXVpaWl1dXUVPYEVRYk5WYU9YY0FRakNUbUVWb05bb1FaZlpdYVNcaFVdalZfbEpbdkpcd0tdeExeek1ffF1gZVdgbVlibk5hfVljcFtkclxmc11mdF9odlhmfGFhYWVlZWRlaGpqam1tbWJpc2NqdG5ucGFreWJsemNtfGRvfmZwf21ye290fXJycnV1dXp6en19fVlvkFpwklxzlV50l191mGZxgGhzgml0g2t2hmx3h2JyimZ2jm56inl9gnF9jnN/kH6CiHyDjXWBknaDlHiFlnqHmXuImnyJm36Lnn+Mn2eApnaJp3mMqn6Ts4KCgoWFhYWHi4mJiY6Ojo2SmIuSnZGRkZKSlJaWlpmZmZ2dnYGOoYKQo4ORpISSpoaUp4aUqImXq4+ZqIqZrYybr5CaqYGWtY2bsI6dspCftJ2iqZqir5Ggtp+ms5OiuJSjuZWkupemvZiovqGhoaWlpamqqq6urq6zvLGxsbW1tbq6ur29vZqqwZyqwJuswpysw52txp+wx6Cwx6GyyqSzyqO0zKu3ybO/0r7CyLjB0b3G1cHBwcXFxcnJyc7OzsHL28TN3M/Q0s7V39LS0tDR1NXV1dnZ2d7e3tLZ4tTb5dbd5+Li4uXl5eDk6urq6u7u7uXp8PHx8fLz9vb29vb3+vj5+/r7/P///////////////////////////////////////////////////////////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAwAO/AwAI/wDXCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS55MubLly5gza97MubPnz6BDix5NurTp06hTq17NurXr17Bjy55N+2a6bM9+XTNXG6U2aL6kiet98ls0X9G+ETcpTpovaNqWlzR37dezbOlegrsEREYMGDGATP+KLt1juU5FZMiAoV4OtPIe0+kqAx58jDG8ssPnCE1O/e9FeFLOfhxpMwkQ38UQQxCXgMMSLjK0gIEEEEAQAQYtxKCJfgRa9EwQMHxAYYUVqADDHMN1aNE2YsCgwogQSGCiGNuoaJE4/qmAQYUxZgBDEM/YWFE6msAgIY8SZNCCDLeoZAkMOyYRSCOfDBJFBBLAIAdvQkakiwwZQHADH4yAgkgXF0jgghgOdglRNECsAIEIbCgCiiJriBDBCkBI4yZE4ojRggQXeIEIKIzwcQMEH8igy58PneOfBBFEMQgojQSCBAQYxGAJSp7AIIENqyRj6qmyIBEBDJRA2tAzMmD/AIIjp54qDBgQtFAGl64mtE0QKlAQCDK1IoNMIBF8EESNvSZkzhhygiFMrckg4wgIGMgQZLMJUSIqErOcSmwyq9yQpScmZQNDBTwQQ624UGT5C7cHlRNEBiDI8u6pfEAAAyf0HmTGChGEsq+poUCwghkBG8QJDBD4cXAysoCg7IAND/SLqFCM+y4xPFQQQzYlybFCBbRMnAwxIXwgBocNdwLDA6ConEwS2baZ8TOi8mHzHhJom7FA4MSKhMfvIgMKBC6gO7Q6RXwAgrsT01LBCnKQVLQEYNicTCASxODn0ERgcAPS+5biLy5Dr0PHyVRPTMzVk7SNC8SlqGxsDhgQ/9G2NDFEEIjXagStM0i9QCyK17Tkyok6kEcu+eSUV2755ZhnrvnmnHfu+eegh+65uhJIbDMyFsch+uqst+7667DHDvo5QGAQhdfJQIEBEObI7vvvwAcvfOtxqAAC7nyEjd3wzDfv/POvc9ICBCnbHMoDMPQykifT2+I1MhVAUMIj5Jdv/vnop6/++uy37/778Mcv//z01y//FgFA0AjuSEiQgP0ADKAAB0jAAhqQfngAQAXagLs2SAAAeTigBCdIwQpaUIAJkAAScNcICARgCxcMoQhHSMICkgACFcBd41rgtJBoYnrT8poGIMCBEtrwhjjM4SOokL+aec0JFQiADv+HSMQiDtAOCvSZ15IHADsY8YlQjKL6AiABJ+AuYQGwghS3yMUicgACGsDdMCLQAk2MBBcugIC+bFYMTkWBGHCMoxznSMc62vGOeMyjHvfIxz768Y+ADKQfG/EACCgCdzzAgAgEychGOvKRkIykJAEpCwdUQA24W4MEHFCLSXryk6AMpSgdOQIM8AB3iahQI0bJyla68pWRjMKO0LYvWTCNbSKBBsQS4TVS+CsXQxPHurpmM2JQYAWtGlrUcoC7G3ygCG2jBAsoELeJgaECMEhRw3IBMVJ4LZUweI9IzBEEDPjAa10I2+ECFocPaKCa+0KEv+Y1NOlBoFQqWwXTADb/tI1BABE2G4YGVBCHtn1DBhXowul8sLtzkKQTaVyEytTWgrq1bWMSWIPKagGCDLzMoLHyQTEmhgyGykA5QzuHGKRWC5WpYVXbGtokppe3iS3CATDoREnKQYQVUMCH71oFtoCA0rbFYXqD25ctdoDNmA5NZhHgwkg/xoVV6bRt63hGDNjlvaQFIlcFxeo3gIAvfL4LFBV4JsZIkg0gfCACYKieqWzBhwp0yqnBLIKcoHCKWhEDESHI0lWxmg45uCACN3CEx6x1g1XJAWZPXRcIEBE3ZJwCCg5gQRG0edEYYKACfABGrWihBkYBgWQniUYQWEAhGjjBCYuSwApk4Aus/xIEHGNwwY5EgIQohIxROVWHbQVSjjlAyQEXQAIUfjBDDJxorVhVRydi8AEU+gAKSBABBC7ggjGss22+kMEKKHSD19IgRi0IQjRU8o05REhESVqSGVA7XOJq4jvwxRAMxIBX26YjF0CAwQrSdIEP/AgXkLXtM8QQgxVMKK3s0QR0h5sNMxhpQhL4QIbmUFSVXIMTRThAAHqgifXW1yDfuIUZEBCAEEzCFw49MUHEwQs5UCAAE5iDLsYhY4Kc4xeTCEEADmCGW3S4x9G4RA8MYIAicIK+LvEG+abRY4Skg3zGqDJCVPEIVWj5IMUgn3C/TJBpkM8bM5HyI6hM5oFc+f8RWW7zQLjsZTkLxBjkS7CWzfwINMtEzWyW85vjbGc62/nOeT40n/0cE0AfetCHXgeXJRFpPD9Cz1VedJqn/GgsR1oSXa50ou2s6T9z2s6QPrShD21pTPe41I0+taA9repHUJrVo5YzrGHiaFTTutChxvWlFX3mTa+503D+dLDt3Gpi99nYgW5zqoF9a2bnus27fkmvZ53sWtfZ2sMmdbFNfWxfd9vOoP62nJst7meTO9pknracVw1uV8s421GWtbR/PW9bizrcuh53rMvNbULLOd3/tveJ8d2Sbe/73P1Wd5vZHXB3DxzeX5Z3myedcGczmtf6jje/N77sdV+bzAz/Z4nDRQ7xNiNc2Aqvb8pXsvKMj5zMHIe5x6GNbIOTXOJkpji2BQ5ygj/c52R+eb13/u6eR5reJgf40C1edIxrWeM497fO2/1xbYfc5i1PesknfvIvz1wlNb/6zb8MdbJLHeVE97rRWY50tmt96VznubnrruW2B73se457vucOdr5XWelRj/lwz56StFcZ63avduKZfnGne7vjeW/63pUN9C8LHe5Ul7vVH7/2vo/97283u+Ab/nW1hz3ymK941wc/+h5DXsuId7vibct4lDje9qWvst89D/hMr17lrSf9600ved1TvuqWB3bntfx51Yee9tE/+OmJn/rAX5/1hHe9/+F7nHO8y17vBX/69qlf/Fcfn+bJB/7yD7/+Klff+7MHf+1lfHvh17/H92d834d84ad84ydj5Td5mVd5m3douYd6u4dVvXcSv8d/wUd+/ydjAeh+Awh/BSh/B3hiCeh8Cwh9DSh9sTd1+UeA+3di/ddjD8h9Edg2E2gSFeiCF4iAd6eA56d56Xd5W9eDDPiD6JaBJ7aB9/Z+aBd/Fjh/GDh99td+SdiBS/iBTRiC9TWCEPh8opd9LmeE9YWEC6eEjceEOOiEOgiFACiFY0iFZWiFZ4iFw6WFMsiF2HeCEZeCoLeCHtiC9fWCMhaD7Nd9AsiHVeiHwwWIIriDJCiEJv9IhHkYhCqIfkfHeXpofYb4hojoXzm4iGqogWwoc2Toe2b4h52YhYy4hSXYhXj4hZ94hKG4eKNIgaWYiKc4h2A4XGIoim5IinBoimi4iM2nio7IipD4c5eIf5RId5YoiXu4jIWnfsNYh6t4h8eYda8YhrHIe7Nog7XIicFYX4IYhYTIgZnoi5tIWLdoW8M3iDM4NDVYEjcIjHLIjqlIjcVojZXogLloW7soi71Ii79oi+GIi9moi9sogd0oj9+ojgVpj9Pojnaof16IjclYiNAofs1ofpPog/tIbRdpjhlpgOp3kP6YkDS4kCQxjwRZj1g1jmtYjlN4jgKZjm2jiKj/aJJY9Y/cGJDeOJDg6JJtQ4cSWY0U2Ypip5Ntw5MK6ZMMCZQOKZRD047k+I4ZE48r2ZA3uY5YRZRVOZEsWJF2p5RDw5Qp6ZRZCZVb+ZAv2Y87iZLwqJIjwZJBKY0hOZMjCYIleZdtSJM/aZNDg5PDBZOgKJN9mZdXuJfOiImIGYd2uZjK6JHMyI9kmTFmGZdoOZdaGZhcOZRuuZRweZVyKRJ0GZWPyZHPKJnRCISoyZiqqZGUyZe86JdPCZgZI5gQKZsASZtpaZsNg5td+ZllGZoNg5WaqZacyZZtQ5iwaJiz2Zj0qJitGZlD+JH9FpFfaZRhiZRfxpza6Jy7CZ0t/ymdPNiR1TmZIAmZGPmaJMma5Zma57maRViZDXOZopmZpLmZt9mZU3mPRZmPR3mNY6mbPcmbx+mbAQOcyymclkmcAWOc+Ymc+6mc/UmfAWOfxTmaIVGaaymVGeOVMWmVGYqfG6qfv8mfGeOdCAmeBSqedemejWiej2idJIedIQqWfSiWpmeh9IKhD6qhIMGhyemhDaOiJ8miTWmgEYqg9KKg/WmjhSmiP0qiQWqiCYqiDUOVN6qdOcqduMeg9emg9AKhJSqhJ0qhHwqmFyqm3EKmVWqmV4qmWeqf2Qmg2ymgX8qj3OKjYwqkHyGkE0qkAaOlUYqjh6ij/gelzSmlff9KpX9qpU2KpYOqpj3Kps3ipo8Kp5EqpwFjpG+JpGeppGXKpNzipGmqqN/JqG3qpx4BqGcqqPRCqItqqJqIqDBIqXtqqb2Cqa0KqaUqqbGKq83Cp6vqqL2qqb/KqcGKqiuqqpfKqh3hqnEKq9ziqaAJqpgpqm9Kqs1iqnOqp8Oqq67Cq9Hqq90KrNwCooXKpYfqpf4Hrr1CrM9qrOWKrOeqrNUqrPEqrpBCrhwhrZtKrc2irrPKrrXqrk9IoEnqoqYZm+opkuyplzBKjDJqjDSadcx6pM66q9D6r+baK97aqfrqKvLKsfTqsfYKsug6sCMLKSU7rh27EQCbrALbKwT/m6q0io62moYKG6oM26Eb+Z6uGZ+wmZ7TuZ5E254o+LB4GbGJ6bBHC7FJK7FLG7VNO7VPa7RCS50zip7aB68ky69/4q8y+7GuErLBCrYuK7ZuQrYaMbP3WrOucrPNmrM1ubOe2LPZ+rNDGrQxCp9dK5/Xqbf3qa2Zyq0qi68sq7Z/8rL9GrNva7aQgrb5yrhu4rhjC7kZAbeJK7eQIqs4a7A6i7A6mLGfurEwe7Jlm7Jnu7K9Yq3Dia2Fy7eBSp5/O7SBW7SDy7SH6bSOObH4WLH66LWuSLgjarjHiritq7g2S6dbaqddiqfvarxTirz1qryT67quArsNKrvHS7uv/2q7FAu4Fku8GEu9jWq9KIu9f0K5zcK9Yeq91Qu+0yq+wUu+wyu4NYq+xaq+q8u+buK+zWu5XYK5bau5GMG5y+u5fwK/ayq/6Uu/AXuaW4u0uau0kWi1vYu1vzuf/Duv/hu5rJu9zDu3Ldu4bNslbru5ktu+2vu5zruu0Nuu0nurBCwkBqzCCHwRCkzCDOwmoFu3onu3pCuMH2yyIczCI+zCJQzDN2wjOSwkK5zALRzAL9zAJ3y5KSzFO2wRPczEP9wldKuxdvuXeJuTR5y6SUzFS2zFTYzFT6wiUWwjU8zDVdwlAmzCcdwhc6widezFdywkeQzDpnutqPu4qivCAP+Mx1fsJg5cqRDcvxJMs/b7n8IboBcLe7z7nL4bncBryfiLyebbnVlcwFtMx11cEV/sxmEsJGN8umVcm2dskGmMyGtsx23MyG/syKWMw6fsx6lMEausy61sI0FMxkNsxkWMioUcu4ecuYmsxIssyI3cJY+cq5EMwpMct5Vcp5fMEtyAB3jgDId2DnlgB7YQaZBwB5AQabZwB3gQY3LmDOLMDTCRDr1gMgAAABhgBrkwYSf2DAeyzw8gBp3AWTKWDZdABAMAAANABJcAZTIGDp0gBg+wz+LRX/VVDrlgBhiwzyogB73wzBERDS3yARMSARBGBLUlY9sQBzDAAhiWJDD/AASeQNLSUQ6UECGfJQESoAEsIAOUANA3eQvr8QEVoNIYYGBxcGS21QtEECJJLQFLvV8mhhK6QF0RoAFaoAd60AUhAAE+wk/DJQ1AME0UAAVtsAdqcF7ONQdE3TDfkFvh4wNrwAdr4AMotCbflTHFBSUPcANgoAdtAEQKEwRjM1wPEyYi4AVerQUz1CiPchIbgwEaQAho4wgikCW4hFXa4FYQoAfVZFk84C90MFzlIAZykgVyZSq0kAW5IgZxTS90ICo80Fd+pQemRR5YdTcVIAL7UyvFgAgX0Cn0pDW1ky8HYws34FzXQFiqTQGhQEvJYAxRkCXAhFXeAgHDsi/I/+AHTJNMbcNNEBAF1J0MobAnH9U21+BZNtBV71IxGQAEfe0RlJBGNXUwVrMwWKULEDMIKlMMzR0Es+0q1yADEpAFxjIxWlABMvDcQ2MvGUADU3Uwg+Avkz00A1MB4XIwyEBRnzIS5RArt2MzDhQDvN0wY6ACInDep+II/sILbWMJLRABrb0vK3QJbcMLEEMreiMCHzAGbaMNMSABDGQzsiQDBZ4R/hTc+YQ9TZIxByUBbHA64KMCpz00QaABG+Q1SKABQdA2dKACF1DhE8MGQePUzRIq9+Q1hAQDxw0StzA9N34wMWIEqpDner7nfN7nfv7ngB7ogj7ohF7ohn7oiP+e6Ip+6IDAABAgUV7jAxVgAYte6ZZ+6Zie6Zq+6YkeCQVA5biD5gQQCZxe6qZ+6qie6pduAeaEO4sAAQwACKo+67Re67au6UZAKbgzC0wT5S40PfB0MCBAQ11U7MZOQlQwABBgMD8URMf+7NAuQUgkAUpkM8kTAE4U7dq+7fVDRVBwRR5UBdw+7uTePl90PF4jDLliRiJxC2lU5/uCJTogCapA7/Ze7/h+7/qe7/y+7/7e7wD/7wIf8AQ/8AZf8Ah/8Aqf8Ay/8AIvCX/g6JBuM5JO6Q7f8Bh/8Rqf8Ry/8R7f8SDv8ZIgCZBAAKDuNZpEAJDw8Swf8i7f8jD/8jL/H/MDPwEVcE5e8+oM8Ac0P/M+3/NA//NCT/OSYAQREAG73usj4Qs97jX65AK+HjDbsFVHHuAXsAJz0Db30uU2gwQYEOZDMwdkbuYH40AywCwN4wlpZFYT00Ex0NIhIQ6xkgVeowcRMDJts1ItbjNLAwMyPjQ0TgEttVF7EuIZw+MQ4OMkBeRCPjTZgFB64DVScAFKThKUMD24rd8XoAIMM94wEAGEEOADjtD0AjgSoFAqk04xAOEZIw7ldANkTy0XDgPZreFkDu+ncgq5It4iAQ61EwId/i7CkAMik9i3KQbBsjjenQXYbVszBQEAbuG5YlGeDwFaEPumIgolst5D/yMNsZIDMRTfIrA79e0RiWPZh1QsoEADWRL1Q/PZb+UH8LQKPhABLjAHOE0bgSInXTD4pwIQtbpAWCFG3DqECRUuZNjQ4UOIESVOpFjR4kWMGTOmm9MiApJVyUSKJMYnwgcg2TSuZNnS5UuYMVl6giFhBqiRIpEp0oABhi+ZEnHF+PAgRBc+gcCMgJABhqagUaVOpVq1JbQgKyJciLIn0BoeEHzKKWfV7Fm0aWF+K+JCAgUkbQK1SVJBggsx39Tu5dvX77pycmBcgMBjTaA9WS5EYAEk2l/IkSXD1AQDAwQaYPzw6QICwocYufhCKwJDBYYIEiR8gBGE12TYsWVL3P9WBsYKDKorZHAho1O62cGFxxY3SQZuuxIyrIgx6eBw6NH3pusUo0WG5BhUwDCzTfp38FV5BYHxITtrItD8mtNlZgUAABjG3Cob3v79mL7myIAPocgmvfATcECMpLEkCAIAICAIS6Qh8EEIIfqGEyIegE+GOX6JcEMO1xnnljIwgE+FNHQxRzJr7LCjmQ5b5NCcO+qgxUUaH1QHkjogUadGHvGjpY47TuxxyO+aUdGa2Lx55JFpiHQSunSWNOZJKoNT5RFVqtQSNmOWBG5LMP2aZklvklyyyTDTVCvKR6ZU882zrswSTjqp6vKRL+vUM6YxHykTNiWZ3HPQl9h0k1D/RDWSM1FGMbozz0YjhajPPycLFE1JM23IUE07ZUgSLD0VFaFHR/WUUjMFNVVTTlfV9EpJXNW0VFkjRRXQM2uNtFVdGV20V0ZpBZbQWy3NdVhCeUV2T1DnXHZPYZ+ls1jJLpVWT2WvffNXbeGMttswqY3MWnDVzLbcLWFFV81v16VSXMjIdVfLc+d1sll7t2w33x7h/UtefomsN+AauSV4yH0PbtFfvwBWmMaBH+ZQXYl5TLhiCBnuy2GMN4y4YwINBnnDi0fGT2O+ODZ5wI9Xtg9flyMsOebvUN5LZZrDaznn6CjmWcCZfxbOZrVwFhpKKY/GT2SlpQu6adiITsto/6hl27nqyWDGOrqnt/5LarSo9jqyq8f2i2mzufQy7eDAPktstvkqO+60fKZ7sq7vNstts+DW+6y5/65Ka8H/yrtwqfi2ym/Epwq88aDQhvyswyeHSfGqGLc8psc3d8luz82qPPSVMKdKc9JZ6jz1jCRnXabRX7fI9KlQl/2i1W+niHDdYV+796Bol8p24CXKvfiHQEe+pdiXb0j4qIh3ftOkp/88VOuZ/z17jaAPSnruETo+fN7Dt6j58L2XCfzwx+fedfMjQp979WNin3v3s1c+/onmz75+mNwve/mzXvn4JxH/WQ+ALxGg9Qg4PfgdsCEJnN4CXdLA6T3QefuT4P9DKOg8C7YEg87T4PIi2EGFfHB5IWTJCJdXQuQZEIUT3N4MH8LClbgQeTAsHgdtmMIa/pAhONSIDovHQ+Cd0IYqRB4RM2JE4CGxdzIUIqmCWMWEOBEjUOydFHWnxBkysXhavAgXdefF2/mwimIEHhktYsbboVF2VFzjFbG4DjdWBI6yk+PrwIhCNvYujxTZ4+v6yDo1CjGQuhvkRArJukOm7o8dXOTtGimRR6YukqSjoyLtiMVLRiSTpNtk6BL5w0rKLpQQGWXoSum5SUowla9b5UNa6blXbq6TqPxkFWvpkFtuLpeWi+UBZ8m6XzYkmJYb5uROucReCjGZDFnm5Jr/CbldQhNPdxwimVKFKW6Kr3rhTEgx+XfM1E1zIdWE3DUb98wwRvOH6lQIOxvnTsSZM37oJB09E2JPxOGzcNmM5zbJiRB/IgSghROo4OAJSHnaMKHrWKjgGvo3fZqPn6GbaEX/dlG9ERSiBj1oR491UJDeLaPh26jnTKoqlI7zoA+lZERn+FJwhjOldBNpTUlKTpweVJxtEipCVsq9lm4uqELdadxoKkubonCpMSVqUY+avaRabqrkbCrbegrVn4ZzqzqVKTmfasyodnCs3Oxq2q5qvaxObq13bKvZvorWsHJzrlis69jeOr24Qm6vVeyr1856zrRKcLBCLOzW7orY/7zecbE/bCzW/uq8wDZusjasbNUOu8/EHnCzM+ws1C67vMwibrQoLG3THgvayILSm7iCKVfLGs7PajS0/FttB1urtNMiL7WF660Ef3u01+o2tr6crbFqS9aqCjW4xRuu4Ip7wOMKLbcs3W38rsu/7P4sudxdrjSbW62T2ja6M8WeUKv7t+/GL7w82y5Su2u++JpvvjmbLvDeq7f8tu+23Byvfcs7z/OOK73QPRR7Y1XU/94twPgb8B3727sI023CA6wwFguM1fumL8HxWjBbO1zFC+suw3HbsANPLMT6gvjAEh3xv0pM1xf/8MNwDTH9atywG/M1xzZM8e1WzLYWZ/9wyDOMMY9nfNMfbyzIhF0yCossuyOnLckkrHIHdwzYHv8vyimbMmO7LMEmg/nJUh3zzcpM2TMf8Mqvy7LZtvzCOPPvy5gNswLbXLQ3czbP8Zsz6+o8tjvvcNDmSzOf16zWP08t0KRdNPnae9BDey3RR6z0+y5NzkxvbdNR7LT+HvFg9/a5gpEO26RZW2rrFTp1ocbaqLsI6+ntGbWqBiGr3+Zq3+J6g6cu6jpoXTVbn1HYJvx0OI8NtWTHcdkxbDY3n920aPNx2j2s9h2vrbRsG3LbSSQ2hHm9Ql/3DdjGHfcUu43Fbx8t3JBs9xffXcdHKzbdi1s3duudxnKnOt//ot135voN3n/LTtaki7fQ5q3JhL9O18I9dxMLfrqDyzfiiAw4pis+xovXLuP63bgk7+3JgfM25MMbuYDXS86JU/fjbVx59FpO4Zfj9uS8TLl3a/69m3M459xs9K57jt+fry/oLh76HWPu35kLMun2W7qSm47FhYeu4T97OClLTrqiU/zoIvbTN4u6X5pl3XNb51nXXfn10D0dw1Fn5NQDWHUuXx3FHQc13S1pdwbiHc96h/HOtQkpsQL+goJXNOF1bPiCIl6vihch4znteCJDfqSSlyzlW2h5UmOeyXx3tt9V6fkcgv7Wokeh3FVselqivoiqVzbrO6j2zbE9Z27H/yXcYUl6a8MembJ/Iu2lbXs0a96nnJdt2WmbUxMj/4CuN7Lw00n8LRpf29LnX9hlPnYfO9+50Mcx9wmtfLAyn7niR+9zo99gmKMfr+o3L/sV7P7yw1/nzvI4+MVsfxLDPyEzP0YDPm+zvn7CvjLSPnEjQEvjv77zPz8DQBsTQCpzQE+DwNKTwFWjQCCzQDPDQFNDtf6jPwTzQCkDQTgTwViTP8gyQRpDQTJTQUFjwVxzQdiCQSiTQTejQUqzwWEjwQjUQTbjQUDzwVcDQmbTwODjwF4zQklDwmBTQmpjwgN0QnSDwlaTQnajQm6zQnhDQI5SwDdiQHrzQnITwg0kQv9I08Jf40J/Q0N3A0N8Y0N9c0N1g0OEk0N7o0OUs0OCw0N+00ON40OAU8MmBESVE0SDI0SSM0SFw0HlUkSfY0SMc0SX0z8Ck0TyokSks0SRw0Sc00QLM8AwxEKLA0WWE0WhI0Ws40QD80Syq5T2I78BdMUqoj4sE0OXIkM9MkOIg0Q/gkUZk8Xwo8X7s8ULxMXCQ8QrNMb/Q8YAVMYQZMbH80Oeg8YJlMYKpMYVtMbMw8bDKyreEybf2xzvgzpUBDlVtDlWZDpwHD1xjDxy9EVCAkavE0bW0UU640WlskdHwse300eTc8ZT1MYO5MYP9MYajEcrI0YnQ8gnVMgUZMj/H3RIL4NINZPILKTIGbTIJMTI5JvHzavHdgS6d7Q6kZQzU6xDk/TIHgTJKVxJPdNIR+PIVITJI5TJLqTJ8yPJ5XtJs2OqcySmlvxDoXy+sytKZ7JJo8NJdtTJKOTJOPRJ8+FHQ/NHrQJITBLI3iNIsDvKbEzK8VtKsDQlpxQ7qKS5k1S6lMw7q3zAYtM9milHZmJKyME9y6HLmLFLa8LLdxLLcRQqv2wnwEQcrJw1rZQrrhQlrzTHs/w9oEw/sqxFs4xLTzNIlyTMxmSlx7zLyETHtPy+tZS6tqS6txw8zMyexGS4xRSszrSlz/zL0DRKzURKzjzNu0vNxlvNFpzM//mrzGS8zGJrTa17Tc2KTWCaTcOszaYEzhcUzmkkTqsSTHrMTancQqrcQ9+8QejMQensRuqUrtFUx9KsO90MPN68vO4MwrlETtVSTmVizns6zMLRy8nhS5cpzPp0Tmwqz7lbR7bMzjfczkJsT2a7zbHEzqGkKgRFHvyEHP1cGf4MKPsUHONcO/gkLvmkJvq0UP8MzO+cxPBcyPF0sPcUUNMk0Dw00Ed80OLJ0NzbUOvq0HX6UIa6UIwC0NdTUfRk0UF00UwstnQM0PP8u/RcvPUMPRgltxHtxBKtyBONvyeNxSj9yCnVOQUdzJKy0XrCUYvSUb2J0MaZUJPxJ23wBP8sQAAEGAJOcBBuAgdckIMEMIAZsIRnONLQKYdeoAMLMAALoINeqA++egZLmIEBWIA4wAVwCCdp4IQhYFMs8ARt+AtwmIQYcIEMUA0MaIEYiINKFSJz4AQZMA1OXQEYEAP1qCJdII8VqIAIqABUDQJdwCJoEIPbyI3VgAEg4AQh+SFtiAPr0NUPcAEYmIRG3QtpCIIWkAAImAEkSAIagAAJWAEg0BAbAocycAEMeAAQ8AEnuIEIgAAViAFP+KFyoAMYyAAIqAAecAIeqACxgAE6IFQUookPgAAIuAEnQAINeACfGINknaFfAIJmxYwkQAIRoNYWCAI4RQttAAIVgAD/L5CFnKiFNtgNGXiGGRIHMWgBCEgCUkCGkRiGQQCBCoCBc2WtOYCBCqgBRiBZkSiGRqgBCWiBObAhmqgADSCEYRgJZCiFJHiAFjCIGXoGGcCONqCFnJAFMCBXIAhVsyiHIlCBCnCEnMiJU9CADACCgT0gOQBZP8jakaCFG5AAGFhVCfIEF4gAKSgGsk0GYsgCCFBZFIKGmriBWojbZPADCHCBnO0gcACCDNCAU8haZCBZR4gAFSgCe6UKmoCAROBbkSAFCGgBSuigZ6gJMKDcZKgFEFABMdBTvQEHGcAAH4BbvjUGH8AAGfha/RKDDwABW/BcMEBbjpWgSQBZUvBc/0RwALu1inQAAgzgAZmlXC2ogBiA3fCJgxXQAGHw3GQYhAiAAWzln04A2cP13FP4206QoF+AAQgYBOkVBg1QgTiQINPFAC6Q3mTYAQwIgnOwCryFAERwX1GoW9HgH3GQAQno3PKNAMyVoCL4gBtw32S4gQ8oAgmihBWQgJ+VXi+oABl4jvjJBfEVBfdFBAiQAbWdClyAgQeQhePlW2QQCy1IXBVeYRZuYRd+YRiOYRmeYRquYRu+YRzOYR3GYVDQV0UoYb7NAQyggR0uYiM+YiROYiVe4hwOhnZVAwRWAwl4gGBgYiu+YizOYi024mSYgeJFYEV4AAkAhS0uYzM+Y/80VmItuAwgjltZ+FtcsApNAFlgQGANgAAOWBI93mM+7mM//mNADmRBHmRCLmRDPmRETmRFRuQqCAAIIGP3dYIKCIBFrmRLvmRMzmRN3uREtgMAqAA+QGA+kAAAsANOPmVUTmVVXuVLDgAJgAIE7uEAmAJWrmVbvmVc1mQOgAANQGBguFyoqIpOcAEI2FvpRQYKgIASyGVmbmZnfuZH2AJHbgQERoIKSABozmZt3mZMxgMAkAA9QGA9IGU84GZzPmd0/uMEkAAkQOBGgIAA2IJ0nmd63mYSaFcEroXLXVmq4AXxDQX3pYXL3QR0OIeCPmiDTmiEXmiFbmiGfmiHjmj/iJ5oia5oir5oi85ojN5oje5ojqboanDZUHZfEPiANPhoj05plF5plW5pln5pl45pmC5oczjdKEDgKHBdc0iHmZZpn+5poP5poQ5qok7odEiD2UVgv4UBbChqpx5qqH5qqY5qn55jCGBa6Q2Fun2NqjDdCoBi6R2EDn4M8CKCDDBe6e1eGLgFCaKDFbgAYpBeYpBVOpCgEIaA7fVcHsgAIpCgaJCBCCBf6VUDCmbeqHDeCjBmviUGEVhg0r2bYYYAgPZcJ3DdAOGfX4iBCBhpyjUJ65Wgb4iBC3CCNs4JUADe78WuAhaBuKbcWpDV9DWLa4gBCfCB1o5bLZCAGAAK/wkShyDIABBQbLINhL8NZgkqAxagAA3mW1KIgBUwAxTSBGIOBMqlBRDoWgvmH1+oiSygXGLwAd2+BrTghLxtBbKtBSe43EkgWNEGgcnOCWJYAwhggTF43PjZBiD4AAogBCBGBkKgAJTwjg4qhzFogQdgg9seCVAAAQyIgett67aFAqzOiVbIgepN7bNQB0qwDAiAAkQAhVBQhORNWTP41Q7CBRnIVx8IBBBnhDUAAQEugsvuIGgAghV4Vj1wBFFwBD2gAecGgg8G7SJoVg1YA0YQhU8IBCR4ANCI4xkyhzhwiwrgAkUABVAghCiAgAs41h1RC08YVgh4gDDHgBWQAf9LmN8f+oUg4FZn1dcKYA05yG4UygYxcAHz0Nd2LVYxUIkfEgdh/YDLiAAxxgAXCALe5ixLiAHcwHOxaAEZ4Oe92AZLsPEAIIAMkAE64PMqEodOIAIYqPQIiAEzyF3CygUxkAEGMAAGiAExyIXHnpxfMAPNJoABaI1OkHMbugY6SNoBGAAVAAJLEPC/MIddsIIqeAX7JqxqsIIpYARcx6Jt+AMq+ANhDydxYAQqsIJq6PJwKodXsAIr2AUTn06ifARiKE4erT4fRVIgbUQhHUUiTfddXPfTS9LKW9LVa9LeIVPEMdORqdAcDdF8kvd+pPfYs/fPw/fa03d729Lr7FL/hE89hT8+hr8dGd1LGoUvL/0nMP0oMVUpgs9Kgx++iJ+9id++io9Ehy9JBlXKck/5YazSYrzSmMzSTZT5iKT5nbT5Ulz5oGz5snz5eMf5jdT5qeR5Dwt5xRz56yv54jv5BoR5jiP6mzR67UT6vfN5ygR6yxT6orr4/Mx4ANt4hep4vUG7mOH3wvF3kAH4MBX4+7ROlof4dr/Ed2/FoU/RV09Ap88+qD9DqU8dsJdQsZcwsqcos78btHeZIu3RvR/Dvl/Avw/GwA9Lqn9Kqy9QrBeiwS/Twteww/eos/94ulF7wWH7jnF7j4d7h5L7n6f7BlWvyo87pXdNpuf7ug/F/7uHx7w3t9uH/Nxfxd1XyXjX+uDk+uH0evK8fLXM/Bbd/GvUe+cPUujPPOOPTuQndwftfYF7/F6M/DKc/Hycfc/p/H7/fBYL/cSnm8VfGdP/G9THGNUffdbf0esHz+wXT+U/KPNfe/QHiHUCBxIsaPAgwoQKFzJs6PAhxIgQpz165E0iRofeKk7L6PEjyJAiR5IsaTBdRWMmV7Js6fLlS1WPVMGsafMmzpvGKqbL6fMn0KAMKVoUanDjo45GlzJtyhLlI5VOp1KtClGmJKtat3Jdt/NRz65ixwYletEpUqVk17J9CVVq27hyR8qkOfcuXolfw+bt6/eg2alp/xIu/P+2MGK/kmYmbnx3r+PIbAOj5Sj5stjDmDdrxcr5M1XIoEcbpdx0MOnUPzWrbn2zruvYNUXLrm3SNFPUtneLZM37t8fFdoET18uzOPKHuJfqTu4coe/n0gnCnm59IO3r0pcbba7defTvyT2Ll569fHHuQr2jBx6+/W/h8JOfn79bfVD29mu/3y+7un+81Rega/gBpR+BqvWXYGrkMSjbgA+OZuBPCEr42YIXcgaghqlF2CFmFPpkIYiSZVhiZPKhONqHKzYmYk4kuojYiTMW5qCNl7WY418w4iQjj33VGGReHBKZ2I5H3uXjTUAqKdeQT8alopSFJVnlZBWddZplWP7/FaWXYxkZ5mPHkZkXkzY5eSZXYLLZ2SNZvVkmWHPOlWZNa9pJlZt7OkWln2tdGahTeMKkJ6FL9ZmoUGMyqtWgjwpl6EuISrpaSpd2haOmVUXaaU6UumQpqDYtWmpNjqJq1KerwiRqS6S62tKps7IEqK1CtZrrSrCyJCuvJNUaLF1xEqurmcf65OtKwCr70bDPeqSqtC7tWq1HzJrkLLYRRdstRLiC29K1406kpWBdmktrpuu6RK27IZUb70LalsQtvdC1m29JnPIrb7L/hmQvSfgKPNC3Bw8krsIYzduwQASPZLDCCTcML8QNPQyxxCJRfLDFCvubMUQbN9xxSB8L/xzywRiTrJDJCqMMksr/siwwwy9rHLDODs38Uc383vzvyD0vFPPBP3sUdL5D8+uy0QUhLbDSGTFNr9P55hw1QlP/WzVGV8ebNb1Qcy2Q1/yCLZHY7pIdb9FnG5R2vmtH1Pa6b7u7tdwE0U2v3RDhba7e65p99t/xBv7Q4OMWbm7cfWPHs+QFLa6RupWftK/mBh3OdeLuXt5Q4+A+Pi7flYe+7ugMld7t6eBGrjrlna/T+kKvYxt7t59Hvbq5uCuke7W8Y5u65MCPK3xCxEtrfLW+G608uMwj5Pyz0Es7e/K1d279Qdgrq/2zyPdNfbfgH5W57QKRr6z0PaOPrfoFif9/7PvHcn++95rXT9D9iJU/YsVPZ/Or1v8GEsBgDTBY5pPbAaWVQIEskFcN5NX+INi/yk1wHRXM1QVzVcCXRfBZHfygrUJoqwciboOSOyH72qfCWY2QZCVUFgyT0r6CzNBVGWxhnXY4kByqRYg9XBULQefCvhFRiAjjnBBrmLEbHquJTlzHEVH1QyUG0YlWdGIWSyVFiFGRWF80IhR3mMTfLVFuZ9xhGEG1RTZ2UYhvlGEa2zfGhpUxWHe0XRw7tcbptfFsf+xcIDW1R4X1kVeH1FwiLzVHQtZxh4+sXCQlNUj5FZJrl5RcJh+1yIM1Mlef7FsoGTVJTlayfaeUWyr/EzVKgZXSVq88WywJtUkDdjJqt+RaLgO1Sl620na/jFow/TTLf9VyVsc0WjL3tEsS9tJoz+xZNO20TH4101XX1Fk25zRMahbze+iqjA6vGM43TdOG1ezZN1+2TjZtM1/dXFU8STbPM43TneX03zm5lE4w5tF29aTXPVGVz4ztk0ztnOI7dbZQiDU0TP2E6D85GNDcxBCQBe3cQeOV0FJNtGEV9dJDyRjRl5W0Yh/VXEjdNVJQtRRkL63cRVWa0RdulDkdReRNJZdSPq6UZDVdWVD7FtN1zbRTR7VZUuWWU6LulIk97c5PIRnVsy3VXE3V1FOFtlWuDZWRRc1YWJs2/9aoTdWsVXXjVdeTVUyu1WhdHddXL5VWrNW1Z2Ul5Vk5Ftf8zBWUfdXZXcGVV0ntdWyHfVlbAftWQw72QIVF5WNJ9ldaBvZkla3QZWGZ2YwltluLfVRj3TZaiEWWs5P15GdHFFpcrvZijLmiVzors9jGaLbArK3CNstM3SaNtz/yLTKB2zJj4fa0jEpt3pQrsNJiy7mJgi7hpPsv4XKTuFQzbpOQC03tPu22V7QuobDrOPLmq7XDfa0vwasm8WKTvfTirj29+zX55om+4LQv3MzrRPQGSr2mA7C73Ntd+FqTv4fyrzwRbDgBC5HAfjIw7CRsLvwiVL9qc3ClIKxPDf+PS8H5ZTA8QTwqETOUxLKj8A4tvCcM787F3eKwSD1cNxXHisUUtTG2qFstGduJxsUDcvSYe14dA47Hv/KxSZEsLRzLlMmKc3KzoOzSqOB2HUKWFpHnZOTnSflZJu4wiiWK5W1p2aZcxu2XnxXmN405e2VWFpWZamXRrflebUbqm6945hynmaV9LtifoRpoJ8ZZWXNmU53Hd+dj5dmre2bdoSeWaLEuOoowbt+jzxRp/E2agEoe8KWDl2mPbVqtnVbjp20XajKNWoClDlajjzXrMNWagbfG4KkrnOrlrTplrebrq/UY687t2ku9tuCvc1VpvA67esWm2bEdm2yDBjv/xtVO37WBlm3Vbhuky9Zcs7H0bBBGe4Xnpl2hjRrupY07uuWG6bu7F2+0zttq9c7uvXHabVB/m379Dtu/1xtwoeabf/sWbFHQWUQ4tpuGDdfgwz0bcYFOHI8LV+rAZV1wBB6cbQk/8MelenEg8sWOJb/byTOc8rNNW7Ejl+DLBRfzGs+ca4OucsZ3u3GODhSNPWfryrnYckvmnHE7P/LRjVZz097chE3HXNEpHvWe5ZpY6a7SulNYcR+GnNlVx+HVSfd0Mm9dZ1Ov7tmrmHbXrd3ObYds0um4dFfOPXd1l/TdSfZzPQe9uEP3adY9DhdG552Sezdm34f3d1IHPmNv/x9y3M0Y+eZN3taVZ23Z0Z15P27+ep339edtOxxUF/67h8dq4j2a+uA2npWPN+fr5Rp7oM5+uasXduv3m3vC7l6rvZ9u6OF9e4AO37LFp+vxt1t7Yi5fo80H7fMNG/3y/t7bwf/w9WWbfcxuv73J13f1eRr+3o5ftOUv2/TJmX6rrv+47aft++N1eTCP3pGlD9/pQVv+Jdj5Odz8wVX9hdf9/dYATlj3Edz37VgCztcCJlcDblj8+dMBUtYE9lcFjtcFllgGYtQGwlYHPtgH1lcIvpicLFkENtkJhlgK/tcK3tgI6lQJxlcMsoQ5QEMhkAAJwIEvlAMcSUMnlEAHaP+BLoiDEGkDLhwBBxwBLmiDEImDLmgBB5RAJ0hDDpJMOfgCHJBACRTCM3RhSZxDLgRBDHwABEBABsAAEHQCEWrOL4iBDLRAG2IADMQAJYBD51xDHMQADFAABFCAC8RAHFxD54ADJcAADGAABERAC8iAGPxC55RDJwABDLAhBKgADARBLpzDT4hDGcBABkTAA1xABeQhDIjBNkiOOTSiCrQhBVxAG0pACwABNFTOLciACkhAG14AIUrACsQALlTOMwBBC0jAA0SAKkKABHwADFCCOUjONhTBIz4ABFTAKj6ANJoBE+KEOBRBC0RADSiCLSRDMgxDIyABBKwAELwiLsn/AQxIQAgEgiyoIzKEghZAwAfIgCXKDSc8YgW0wSkggzqeQhtQgB5yQt/8whpCABeIQjGooywEAghIAAzIgTrIzTYEwSwiQSMMQzIggy0owg1AQAsUQTjWRDqkAR7ugTGoI02WJCK8oxjMYdRoAgw8QBQQQ03SJCloQAYAARVyTS/EgATYwCwEpTrOgg1oZC+cjTYAQQZogCg4ZTIQQxRAAAxowtmUQxHMIiIgpFO2gSSaQUfWBC/EQAS0gVbSJCF4ZSdwjTYoJRKYpVaeAjHGAdeUQxB8gAgAQ1wmAzCIwAcEgU72TBysQAScQmEiAxJUAAwcpdF0Qk8iQknGJVrG/wAv2AQRCKZeaiUy/AAGyMBivswkOGZTFmYytIFGSkPU4AIMQIAjuGYyOEIEwMAxGo00yIAE6AFuykIErMAkRE05yAAG5KVrIgNiFkFNXEM9BgJu5qZX+oLRlAMQYIAUVKctqCRYGk0ZiGZ1ImYZ7CQe1kJ1SgEGAEFqZkwv1KYjjKZTIkMgSIAMKOJL5EJPrkJ1EoMbvgE1DCiBFqiBHiiCJqiCLiiDNqiDPiiERqiETiiFRmgsYEAEEEJ1JsMNYIAQVCiIhqiIjiiJlqiJTqgzYMAFgAF9auUXYAAGOMOJziiN1qiN3qiICgEG1MCG3uQHxAKOBqmQDimRlugbfP/AAwAlbq6CV/amS3ACHgrDhmoABHBARVwplmaplm4pl3apl34pmIapmI4pmZapmZ5pmVpBADwAKGyoE0jAAaCpnM4pndapnd4pnprpHQCABOzBhvKBBACAHeQpoRaqoR4qotLpAUiAE2woKDxAAFhBok4qpVaqpd5pB0DABWwoMLyjQ74ElEIAYVanLZLApZ4qqqaqqj6CmkJAm1bnZCLAqs4qrdZqne5pcG7oHgQqHtiqr/4qsHIpAjDqhn4CBATAFQSrsi5rrWaqBnCqStblftYmZOJmp6qAIHSDtm4rt3art34ruIaruI4ruZaruZ4ruqaruq7ruXrDLqhABAz/wobOQAY8AbveK77mq77uK7/2q7pawwdcQBdsaBdgwAdYg78mrMIuLMM2bL4+QQbMwIYOQifugsNeLMZmrMbyqyDM4qi65ik4AAzkAkxkA3DyQXUqglcGpM6YQxBgQKPi5ixEa9TEwQeAwIaCwAf45WXiIS1UpxO0ZzX2DERCwCJUJx9QgAxYpkuIwc1WZGTmAAYoZtRYAh76p2uCAX5mQ9ToQm0qAm4mwgPAgC5ETTYopRosqUpaQtSYg1XmQIvWJDHorBjYxC/U48AWJh/sppP2zDYo5w1ArVaGgkrSAdeYQxF8gAa0plbOggZ8QBGIYtTQwQq4amEWg9TKwDdw/w1tQgDKxiUydAFlsixMzEFtdoGS1iQy6IFKlsHQRs0t1KMPpKNTKkIFJObmcg00xAAGiEC1BuUpiMBp7iLXfENgVsDROmUt+IBGesLZmEMZVC4fCC5NEkMXQIALzAFOlEMZuIAEgIAfnIIwDMMqDAINqCQR+OHZqEMjSkAFrIEo2AIxyIIi+IA/AoFsyg1/QmIWOEItEEMtOEIWQAAGxADJyk00AMEHRAASKIIsEIMtiMIacOM09g04EIELRMAMDMIqDAMwnEIfgEAEuEAZvOdLlAM9fgAwtiE0viE4So46dEIMrMAqsjABuwARcK3k9IIyYoADRIADBGMuYqfkZP8DETwiKrJwBayADHSCGfILKcKABlDAD/9wNMIAHZhwTfiCGMxwAzRABsgAEejCEwuMNAQiDDSAA1wAHMrhIk6CDMQABARxDMjAJORu5YxDJsZABTiAyCJi/mKSLhCBDHyAH6tADFTiUmQDJqDACRgCFwrRN+SCI7PBM7yu7YhDLzTBCTRBL7Sk7ZjDM7SBCaRALuCx7aiDNBjCCaAAJugw0XWc7C2epz2gyL3gle1gj81ghNVgkN0gVZWxvOnyk/HyiPlyktmy2eEynxFzlhlziyHzlAGzWwkzvzkzm0Hzj0mzmRUgxlkzxG1JLOPWSWFJ1wXL10lJ2M1KOVfJ/sn/Wf+Z0v+tjzZHGTfDDzVLFjhrnDgjnizzHi3v0OBZGjNjGjb7WT1vWUC3zzs7Wjzb0jzbTwCy2z3rTz671j4LXT/D3j8b30JzWwuyXkYb3kbrXkdD30ebmzKLXkGr2kEjWkK7WUprTkPr2kM7U0QD0ESLXUWbWkgD30i7XkkT30lr30wL3EorH26ts6u0s5TUtNfdtDfltALtNDuP3aqcM6+k85Mw9ao49ZMMNLW1NLG9tKbFNKAdNcMlNfotNVVTkFU3NVZr0UW/V1AL31A7X1GTn1qD3E97312DX15j3167X1+rHFsboFubNauhtaIdNs3V9YIFtgQOtvgVNv5B/7bPeTPLLbZlsx9mM6BmI11if7Nnp4tjc9poS51knxhlw+Bn219oW+Bqc11ro9lr53JsK+Bsg2BtIxZnK91pSxw5z3WpQDU6SzU+vbUHxfVXG7cc3Tah5XYz7zYF9rYK/jbe/TUEUrdBW7cHYjcNarfgSTfQebdLgzcKincvk7flmTfhoXdZq7cMsvcxuzfocfcty7e1Mbaxpbar4bfqdRlXK4lXowpYKwlyb7VyKxRzo9BV9zSuwTdB8ze4+Te2ATiyCbjIBLfeDTfHFbeE88qC50qBH8mBl0qCH4lWm3iDk9SDOzeCQ3eniLXNkXV/0/eKabi2cbjvEfiL01SM8/84ufk4zlD4WFu4wWG4uBG5vRk50Xi444H4OKsTjSsSkt+4kpMck9ObkwMclPNLidvKiRNJioPKihNJi5N5kDvVkNt3NIe5+en3Mm85znW5v325wsn5fWU51eH4hev4LsP5NvN5gJV2Z1/RmXdKmgeJjf+5nVsdniOcnqOcoRMgogu3or+5iF/6uoz5rJR5kCy6pjQ6jzw63AH6kgt6MRO6PXs65Ph5qkc62k26yVW6zME66sg65qk6l7P6M7u6QnfZmod6m4MVp1v5iIuQlNselftzp3cZqLuKqPMIqV+KqedIsVP7setVshPUstsKqvc6rcudrcMcrvOcrr9Ypn//+Kafu86lO9Stuw22+5S/O7Bns7DLNLE3O/U9O0dHO5zxOv/5+p3nO0Lve1pLO8HDs8FLOsLDtMI/dr/bu7PjO2pPvGr3O52zdLlrHrw7nbyzHb0fT8M79MPXesSftcYHeMUDecqb+8o3dstvOMfD/MeTXshjXc33+Ms3V7cz1rcbXclXy7SvSrXnyLVLSrbbyLgXfM77386r3cjbXdFvz8nbdMyD/Mz/d88XOcNb/L9jPHEr+9V3s9jLH8CbtMALmr+rPdmHuNmHPc6vPVG3PeOlvQbavV7jvad1vFLHfZWD+9njs96TIN8Ttt/D2uHjYOJf9uIrG+C3teBD+9wP/3zjB/Pjg3bk287Ro0rS28jSP0rTz8i2I33Qo9bQa13hW/TkK3blB/zlX9Hnl0roz8joM0rpu8jpg37qP9fqK97NA/3W63zXZ/jXP/nPu2DUy/PU013VA17rE0vtg8rtu0juJ8rur8jTO3zzQ/Tz+130U970T3jmV/Pmy3bnd071d8r1r0j2E8r2o0jv2/7vX1fwz/LwM3/68/b6A8Q6gQMJFjR4EGFChQsZNnT4EGJEiRMpEpT0SFVFjRs5dvT4EeRHY48epQt5EmVKlStVTiPpjSVEbySnxbR5E2fOlOlIGtP5E2hQoQhVYRx6FGlSlSNLKnX6FCpEl49gKp35qP9mVK1bt/J85JNrWLFIi0oaexZtTqYm07Z1G3Jq1aRXs761e3eiV7B4+fZdWDSjX8GDB64lfLhvXKd0ETe2q9dx5LYXA0u2HNbwZc1RFVuluRm0U8ihSR8tWxp10MypWdvsPPdza9krR8+2fRLwbd0gV+/2TfE1Usa/iUusXRx5Q8rJmTPs3Rz6wOBHh0e3vu74dei5tVt/3h359KHVwSfPXr74afTMv6/fLV4oefe+z8/Xvdw+8fb5ZcMPKp+/2eoLsDXuCLxtvwNL8w8oABVEbcAHSVNPwtYSrFAzBn9yEMPNIuzwMgNBJO3CER3TUCcOTYzswxUbw8/FzUqMcTD/FHNSkUbCWsxRMAp5jGzGH/GyESccheRrxyPvElFJwoJssi0ibzISSreSrDItGLH068ktxZLSJiq9HOvKMcNi0sy3ukyTs5cWi43Nt8qMEyof6UxrzTuTAjMmMfUUrac/JzNKULTyLDQoPlnyE9Gh5mw0KDQhherQSXFSdCVGLdXp0U1xstNTpSoNdSVMVdKU1Jg6TXUlSVlVjSS2Xj3K1JRQnRWlVXENSctdgRrV145qRenWYD3S1ViOQE3WJmCZBc5Nz7B6NidkqZ3I1WtRclbbh4Y9qdhuI7JWXId6LfckbtFV6NuQwl2XIXLhTSjbeTVS196C2gXp3XwPktdf/4KWDZgifAne96N+CR4I4IXPXXgigwNG2COFIW6Y4HohdkhifynuyOKFMQ544I0f6jjfjzkKmeCR/dXY5IVQtlfljVgO2OV8H46Z41h5nqhmjW72N2d7S/5ZoZnnDbqiofMtel6YkTZIaXiZpshpe6GGd+epE6p63asnynrerdeV2uvCfE67IbElIhtes9E9mm2CwEbX7YjgXlfucruu2+61AU8ob5ngHPzfQBGnl9DFD7q73MIf2hvdvsWle3DIxZXcIcrLtbxbtNnWvFvOG/JcXNC1/Rtx0rU1nSHUu1X9WswBd/1a2BeSXVvaqRU9bdyp1V0h3q/1/VnWMxfccf+CiE/IeGqRZxZ4r4V/9nmEon92+mRtr/t6ZrM/aHtmuzdW+duZb16g8Q0qP9nzg61+6vCTdb8g+I2V39fvR1+fffgjiP6Cxb9d0Q9p9jOWAAdCQF8ZEFfpAx8Am8dAgThwVxCclf+CR0HHWXAdGMSVBl+FwJ8pMFggFOGsSMgqCf6vKexzXrRgMy0ZMkxxNxSICXmGQl+p8HAybGGqOGg9Dy4OiDbU4RBJ9cIOxlCHSazLDZkYKh7GzIe7kqIOBVJFTxWxfkdE3Ba56MVNXdFkWcQVGZeYQx060YhQvCEbqejGG4IxgWIcHB2FaEcZonFjapwVH9lnRkvBMYxylCH/IZtnyEkBEmKCfBUjHedISOHxhHoEHCUXZ8lGITKPigwgDYUTxEL6kX2QXJgkWcVJxHkSUZjsoSbr5srBwbJQqiQYK1NlS8DhUlCgzKQoK0hK6piykahsniyxSEu2+bJuwPyTLgPGS1JBk23S1JMwZ0nMDxpzPMispDIdR01/WTNU2EybNu/EzDQ6M23q9Bo76cTNZnoTieCMjzg7Sc7FmTNf6PSUPKdGzzi5M5Dw9BpBkWZQNgHUXgLdFEN/5tA02fOd+ByjPv/Dz1f6E3EIjaRCp0ZRnlnUTBCdl0QtZdKYoXRMGE2oRvfI0QZ59JYgHZxK4cXSSbnUZDD1kkhX/0lSpAF1Y0LdkkxHStNN2nRDOP2lTgHH03X5FFJIvRhV60bUXRr1Z1oVGVfZZlV0YbVRYm0ZWdPG1KI6tZZQTZFUo8lWr3m1mmDlmVpxZtepmbVcaEUUX4nmV6S59atwfaZcb0TXbBr2Z4AVl2ALRdinQZZneD2nXmNmWa1hNmaIzati48nYIjl2naA1mWS7RVlBebZsqt2YZgPKWZPBNm6yhRhrteXaP+GWb7p1WON06Fs9Abdyws3YI8zCxXUY907I/ZxySUbcG0KXThYUhyuWoIRMfEOH5fgFE5QQiGwsMRphUEIYoiGr5qkjG4FQAhN+UQ4dbiMTSliCK8RxFP9pxAEGKigAAzIAgzL8onnfmIQMYFCAAkhABkXIhXsBJw5OBEEGDWBAA2AQhE70t5O5KEIMJMAABsBABpTYRvOeUYYYZMDEKohBHKQBlHRYQgYrkAAEeAwBCagABnOw7+ByIYMWYKDHPv4ADMQA3sFFIwguQHKSMdDhaCBuG2OAwQck8IAH8BgDLZBBLhBXDjlsecc9rsAKZGAJCrMkHQCugATU8IlVtAIUbdCABFwwBhCzjRMwQHIUFHEKWYjCDzSAgAqCoA3A+UIGH4CADwhRClmcYhBIeMAHZOALwGkjCC2AAA38IApZoGIRUYBAlTlR4TG4QAIaaAMoZLEKR4D/Yc4wkMObVWIJGEAgCbZARjKITWxieCECuuZ1zHQBAwnQgBXFLjYyArFoIvx5ateQQQY0AIphSxsZjtAABmRwDbaJowiSDsS3pb0KGkgABrpgmzrk0IIHfGEY0ia2LZAAARhY4ibQcLYT2K3vZKjB3/L2mjiAgIEZBMPgxEaGIiDQAoDPcwwquMAqklHwYq9izWNY9sYsIWpFRJzYwaABBoCA7Z81GwJrQHnHoQBvaNikDB/QADBm3nEaZCAII1+YJkR9ip4nQwsVgMGKp9aLXw/i6ISIQAx64bVtxKACWjh6KR7QAk3MMwgfoIExeg4MDaigDDHZhgwk0IajIwMR/xCQwc0bGgQMIOHoyViFA2DgCa/JQeMeNzgyLqCCOXjNE7+O9tGRAHShB0zgEUBE3tsggRgwXSUwL0Xea7HoSpAD9KEX/ehJX3rTnx71qVf96lnfete/Hvaxdz0zWhCBQOQ9GSL4ABlk33vf/x74wRf+8GEfjiNnAfdZCHM4iN985z8f+tH/PRkyMAPBGzwQEmgBM6Tffe9/H/zCr4QKHmCLvJfC37xgSSdEbf68VwACJCDJ/Olff/vfH//51//++d9///8fAANQAAcwAK0gAB7gE3APCSoAAQjQAR8QAiNQAieQAgUQDwBAAvQA9/RAAgAADyoQBENQBEeQBCEQAf8kAAmuT98cAQICYAtKEAZjUAZncAJJ4AEuAPdsoeI6gSU4QdSEAfc0AAI4gAaL0AiPEAkfwQAhABRwzwkkwACSUAqnkAoj0A4AoAL4APf4IAIAwA6qEAzDUAzxLwAqwAlwDxRasArGkA3bkAo5IAI0APeCoeJabSVwQdQ47uiIYdXQYBn+EBADURAHkRAL0RAPERETUREXkREb0REfERIb0RTgb/Ly7gYwAAciURM3kRM70RM/ERQfURkkoALAAPdwTQKUIRRXkRVb0RVfkRNxAANuAPfirgJSARZzURd3kRc/8QwyAALI7uhWwd/IbCWkgcSg7ujSEAbUD2nKIQb/MEDrjg4YKu4SvGYMxA73aOADxsBrLmEFIIDnjk4LyG3IfoYXYOABmvDoBsHfrmwl1CEIMsAGVLDYoIDcXC5m5GAFKsD9UI7apo7ukCbxIIAUji4U/M3vpkbgIOD2eq4WKsDwFi4ao+DtbuADgkAdYiIXfu0hUY4FvS5tpIHtLHLmWqHw0m7hGq4GiGHmiKEGWE4fTUYdykAFKqAVei4KKkAGauwbRc0Req7aYMAYWcIcxiAcCeH6PuECPuDa2IYSXCACwOD6VkEEyM3c0iYXSAwJxlHfgAEJLK8op4YkMWAE9FDfkAEMIMAFKOHciOADKoAd05IQIGAFxuAcbuIb/4IgHJMgFNjtFLQAAj4ACLIybcyhDKSyBhjBJYlNFtrgAqpM4aDS2UBgEGqh2GphEEAA3tyybnQhGiugDWTh24ZhEWwgAlygDMyhbq4BCCRNC07h25AhFJLALoMAHHJiG8RAyiLAAkaABi7Ax1wgCHyybsoBwCQNAmbgBoRQAtjMGaPpEraMAhwgBGwgBHjsA2JAEx7PZHghxyggAi7ABkQgAiCgwOTgHNlGGqIM/i6ABmigOjHABcQA83BiHDiBwVbgAz5gBWAgBixhJucpF4IABvjTP11gxhxtcZ5BDGCgBfpTBcRMDJ7BcbIhDmTABfhTBVYgBoJgwhYHHCwhBq0CrD9Z4AVkgBMG1CbEgRcmIQ7MYBJy4T4XR7wsIQ7KgA464bwKKRo0YQ7KQA40ob1kKBs6gQ7KIA4sob5kaBtygQ7MIA4mgRdY1LmuFEuzVEu3lEu71Eu/FEzDVEzHlEzL1EzPFE3TVE3XlE3b1E3fFE7jVE7nlE7r1E7vFE/zVE/3lE/71E//FFADVVAHlVAL1VAPFVETVVEXlVEb1VEfFVIjVVInlVIr1ToCAgA7" style="margin-top:1rem;" /></div></details></div>
+```
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhwAO/A/frAB8mMSIpMyIpNSQrNSYsNikvNyMrOCMsOSQtOyYvPSkvOCYwPiswOC4zOi80OzA0OzE2PTM4PjU5Py83QzM4QDY6QTI5RTY8RDo9Qjw/Qzk+Rz0/RDA8TjI+UT1AQz5BRTtBSTxCSz1DTD5FTjNAUzVCVTlHXDtJXjxKYD1MY0FDRkJER0RFR0VGSEdISUpKS0tLTEtMTExNTUFHUUJJUkNKVERLVUVMVklOVkZOWEJNXkhPWkhQWk5SWEtSXUxUX1FRUVVVVVFUW1JWXVpaWl1dXUVPYEVRYk5WYU9YY0FRakNUbUVWb05bb1FaZlpdYVNcaFVdalZfbEpbdkpcd0tdeExeek1ffF1gZVdgbVlibk5hfVljcFtkclxmc11mdF9odlhmfGFhYWVlZWRlaGpqam1tbWJpc2NqdG5ucGFreWJsemNtfGRvfmZwf21ye290fXJycnV1dXp6en19fVlvkFpwklxzlV50l191mGZxgGhzgml0g2t2hmx3h2JyimZ2jm56inl9gnF9jnN/kH6CiHyDjXWBknaDlHiFlnqHmXuImnyJm36Lnn+Mn2eApnaJp3mMqn6Ts4KCgoWFhYWHi4mJiY6Ojo2SmIuSnZGRkZKSlJaWlpmZmZ2dnYGOoYKQo4ORpISSpoaUp4aUqImXq4+ZqIqZrYybr5CaqYGWtY2bsI6dspCftJ2iqZqir5Ggtp+ms5OiuJSjuZWkupemvZiovqGhoaWlpamqqq6urq6zvLGxsbW1tbq6ur29vZqqwZyqwJuswpysw52txp+wx6Cwx6GyyqSzyqO0zKu3ybO/0r7CyLjB0b3G1cHBwcXFxcnJyc7OzsHL28TN3M/Q0s7V39LS0tDR1NXV1dnZ2d7e3tLZ4tTb5dbd5+Li4uXl5eDk6urq6u7u7uXp8PHx8fLz9vb29vb3+vj5+/r7/P///////////////////////////////////////////////////////////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAwAO/AwAI/wDXCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS55MubLly5gza97MubPnz6BDix5NurTp06hTq17NurXr17Bjy55N+2a6bM9+XTNXG6U2aL6kiet98ls0X9G+ETcpTpovaNqWlzR37dezbOlegrsEREYMGDGATP+KLt1juU5FZMiAoV4OtPIe0+kqAx58jDG8ssPnCE1O/e9FeFLOfhxpMwkQ38UQQxCXgMMSLjK0gIEEEEAQAQYtxKCJfgRa9EwQMHxAYYUVqADDHMN1aNE2YsCgwogQSGCiGNuoaJE4/qmAQYUxZgBDEM/YWFE6msAgIY8SZNCCDLeoZAkMOyYRSCOfDBJFBBLAIAdvQkakiwwZQHADH4yAgkgXF0jgghgOdglRNECsAIEIbCgCiiJriBDBCkBI4yZE4ojRggQXeIEIKIzwcQMEH8igy58PneOfBBFEMQgojQSCBAQYxGAJSp7AIIENqyRj6qmyIBEBDJRA2tAzMmD/AIIjp54qDBgQtFAGl64mtE0QKlAQCDK1IoNMIBF8EESNvSZkzhhygiFMrckg4wgIGMgQZLMJUSIqErOcSmwyq9yQpScmZQNDBTwQQ624UGT5C7cHlRNEBiDI8u6pfEAAAyf0HmTGChGEsq+poUCwghkBG8QJDBD4cXAysoCg7IAND/SLqFCM+y4xPFQQQzYlybFCBbRMnAwxIXwgBocNdwLDA6ConEwS2baZ8TOi8mHzHhJom7FA4MSKhMfvIgMKBC6gO7Q6RXwAgrsT01LBCnKQVLQEYNicTCASxODn0ERgcAPS+5biLy5Dr0PHyVRPTMzVk7SNC8SlqGxsDhgQ/9G2NDFEEIjXagStM0i9QCyK17Tkyok6kEcu+eSUV2755ZhnrvnmnHfu+eegh+65uhJIbDMyFsch+uqst+7667DHDvo5QGAQhdfJQIEBEObI7vvvwAcvfOtxqAAC7nyEjd3wzDfv/POvc9ICBCnbHMoDMPQykifT2+I1MhVAUMIj5Jdv/vnop6/++uy37/778Mcv//z01y//FgFA0AjuSEiQgP0ADKAAB0jAAhqQfngAQAXagLs2SAAAeTigBCdIwQpaUIAJkAAScNcICARgCxcMoQhHSMICkgACFcBd41rgtJBoYnrT8poGIMCBEtrwhjjM4SOokL+aec0JFQiADv+HSMQiDtAOCvSZ15IHADsY8YlQjKL6AiABJ+AuYQGwghS3yMUicgACGsDdMCLQAk2MBBcugIC+bFYMTkWBGHCMoxznSMc62vGOeMyjHvfIxz768Y+ADKQfG/EACCgCdzzAgAgEychGOvKRkIykJAEpCwdUQA24W4MEHFCLSXryk6AMpSgdOQIM8AB3iahQI0bJyla68pWRjMKO0LYvWTCNbSKBBsQS4TVS+CsXQxPHurpmM2JQYAWtGlrUcoC7G3ygCG2jBAsoELeJgaECMEhRw3IBMVJ4LZUweI9IzBEEDPjAa10I2+ECFocPaKCa+0KEv+Y1NOlBoFQqWwXTADb/tI1BABE2G4YGVBCHtn1DBhXowul8sLtzkKQTaVyEytTWgrq1bWMSWIPKagGCDLzMoLHyQTEmhgyGykA5QzuHGKRWC5WpYVXbGtokppe3iS3CATDoREnKQYQVUMCH71oFtoCA0rbFYXqD25ctdoDNmA5NZhHgwkg/xoVV6bRt63hGDNjlvaQFIlcFxeo3gIAvfL4LFBV4JsZIkg0gfCACYKieqWzBhwp0yqnBLIKcoHCKWhEDESHI0lWxmg45uCACN3CEx6x1g1XJAWZPXRcIEBE3ZJwCCg5gQRG0edEYYKACfABGrWihBkYBgWQniUYQWEAhGjjBCYuSwApk4Aus/xIEHGNwwY5EgIQohIxROVWHbQVSjjlAyQEXQAIUfjBDDJxorVhVRydi8AEU+gAKSBABBC7ggjGss22+kMEKKHSD19IgRi0IQjRU8o05REhESVqSGVA7XOJq4jvwxRAMxIBX26YjF0CAwQrSdIEP/AgXkLXtM8QQgxVMKK3s0QR0h5sNMxhpQhL4QIbmUFSVXIMTRThAAHqgifXW1yDfuIUZEBCAEEzCFw49MUHEwQs5UCAAE5iDLsYhY4Kc4xeTCEEADmCGW3S4x9G4RA8MYIAicIK+LvEG+abRY4Skg3zGqDJCVPEIVWj5IMUgn3C/TJBpkM8bM5HyI6hM5oFc+f8RWW7zQLjsZTkLxBjkS7CWzfwINMtEzWyW85vjbGc62/nOeT40n/0cE0AfetCHXgeXJRFpPD9Cz1VedJqn/GgsR1oSXa50ou2s6T9z2s6QPrShD21pTPe41I0+taA9repHUJrVo5YzrGHiaFTTutChxvWlFX3mTa+503D+dLDt3Gpi99nYgW5zqoF9a2bnus27fkmvZ53sWtfZ2sMmdbFNfWxfd9vOoP62nJst7meTO9pknracVw1uV8s421GWtbR/PW9bizrcuh53rMvNbULLOd3/tveJ8d2Sbe/73P1Wd5vZHXB3DxzeX5Z3myedcGczmtf6jje/N77sdV+bzAz/Z4nDRQ7xNiNc2Aqvb8pXsvKMj5zMHIe5x6GNbIOTXOJkpji2BQ5ygj/c52R+eb13/u6eR5reJgf40C1edIxrWeM497fO2/1xbYfc5i1PesknfvIvz1wlNb/6zb8MdbJLHeVE97rRWY50tmt96VznubnrruW2B73se457vucOdr5XWelRj/lwz56StFcZ63avduKZfnGne7vjeW/63pUN9C8LHe5Ul7vVH7/2vo/97283u+Ab/nW1hz3ymK941wc/+h5DXsuId7vibct4lDje9qWvst89D/hMr17lrSf9600ved1TvuqWB3bntfx51Yee9tE/+OmJn/rAX5/1hHe9/+F7nHO8y17vBX/69qlf/Fcfn+bJB/7yD7/+Klff+7MHf+1lfHvh17/H92d834d84ad84ydj5Td5mVd5m3douYd6u4dVvXcSv8d/wUd+/ydjAeh+Awh/BSh/B3hiCeh8Cwh9DSh9sTd1+UeA+3di/ddjD8h9Edg2E2gSFeiCF4iAd6eA56d56Xd5W9eDDPiD6JaBJ7aB9/Z+aBd/Fjh/GDh99td+SdiBS/iBTRiC9TWCEPh8opd9LmeE9YWEC6eEjceEOOiEOgiFACiFY0iFZWiFZ4iFw6WFMsiF2HeCEZeCoLeCHtiC9fWCMhaD7Nd9AsiHVeiHwwWIIriDJCiEJv9IhHkYhCqIfkfHeXpofYb4hojoXzm4iGqogWwoc2Toe2b4h52YhYy4hSXYhXj4hZ94hKG4eKNIgaWYiKc4h2A4XGIoim5IinBoimi4iM2nio7IipD4c5eIf5RId5YoiXu4jIWnfsNYh6t4h8eYda8YhrHIe7Nog7XIicFYX4IYhYTIgZnoi5tIWLdoW8M3iDM4NDVYEjcIjHLIjqlIjcVojZXogLloW7soi71Ii79oi+GIi9moi9sogd0oj9+ojgVpj9Pojnaof16IjclYiNAofs1ofpPog/tIbRdpjhlpgOp3kP6YkDS4kCQxjwRZj1g1jmtYjlN4jgKZjm2jiKj/aJJY9Y/cGJDeOJDg6JJtQ4cSWY0U2Ypip5Ntw5MK6ZMMCZQOKZRD047k+I4ZE48r2ZA3uY5YRZRVOZEsWJF2p5RDw5Qp6ZRZCZVb+ZAv2Y87iZLwqJIjwZJBKY0hOZMjCYIleZdtSJM/aZNDg5PDBZOgKJN9mZdXuJfOiImIGYd2uZjK6JHMyI9kmTFmGZdoOZdaGZhcOZRuuZRweZVyKRJ0GZWPyZHPKJnRCISoyZiqqZGUyZe86JdPCZgZI5gQKZsASZtpaZsNg5td+ZllGZoNg5WaqZacyZZtQ5iwaJiz2Zj0qJitGZlD+JH9FpFfaZRhiZRfxpza6Jy7CZ0t/ymdPNiR1TmZIAmZGPmaJMma5Zma57maRViZDXOZopmZpLmZt9mZU3mPRZmPR3mNY6mbPcmbx+mbAQOcyymclkmcAWOc+Ymc+6mc/UmfAWOfxTmaIVGaaymVGeOVMWmVGYqfG6qfv8mfGeOdCAmeBSqedemejWiej2idJIedIQqWfSiWpmeh9IKhD6qhIMGhyemhDaOiJ8miTWmgEYqg9KKg/WmjhSmiP0qiQWqiCYqiDUOVN6qdOcqduMeg9emg9AKhJSqhJ0qhHwqmFyqm3EKmVWqmV4qmWeqf2Qmg2ymgX8qj3OKjYwqkHyGkE0qkAaOlUYqjh6ij/gelzSmlff9KpX9qpU2KpYOqpj3Kps3ipo8Kp5EqpwFjpG+JpGeppGXKpNzipGmqqN/JqG3qpx4BqGcqqPRCqItqqJqIqDBIqXtqqb2Cqa0KqaUqqbGKq83Cp6vqqL2qqb/KqcGKqiuqqpfKqh3hqnEKq9ziqaAJqpgpqm9Kqs1iqnOqp8Oqq67Cq9Hqq90KrNwCooXKpYfqpf4Hrr1CrM9qrOWKrOeqrNUqrPEqrpBCrhwhrZtKrc2irrPKrrXqrk9IoEnqoqYZm+opkuyplzBKjDJqjDSadcx6pM66q9D6r+baK97aqfrqKvLKsfTqsfYKsug6sCMLKSU7rh27EQCbrALbKwT/m6q0io62moYKG6oM26Eb+Z6uGZ+wmZ7TuZ5E254o+LB4GbGJ6bBHC7FJK7FLG7VNO7VPa7RCS50zip7aB68ky69/4q8y+7GuErLBCrYuK7ZuQrYaMbP3WrOucrPNmrM1ubOe2LPZ+rNDGrQxCp9dK5/Xqbf3qa2Zyq0qi68sq7Z/8rL9GrNva7aQgrb5yrhu4rhjC7kZAbeJK7eQIqs4a7A6i7A6mLGfurEwe7Jlm7Jnu7K9Yq3Dia2Fy7eBSp5/O7SBW7SDy7SH6bSOObH4WLH66LWuSLgjarjHiritq7g2S6dbaqddiqfvarxTirz1qryT67quArsNKrvHS7uv/2q7FAu4Fku8GEu9jWq9KIu9f0K5zcK9Yeq91Qu+0yq+wUu+wyu4NYq+xaq+q8u+buK+zWu5XYK5bau5GMG5y+u5fwK/ayq/6Uu/AXuaW4u0uau0kWi1vYu1vzuf/Duv/hu5rJu9zDu3Ldu4bNslbru5ktu+2vu5zruu0Nuu0nurBCwkBqzCCHwRCkzCDOwmoFu3onu3pCuMH2yyIczCI+zCJQzDN2wjOSwkK5zALRzAL9zAJ3y5KSzFO2wRPczEP9wldKuxdvuXeJuTR5y6SUzFS2zFTYzFT6wiUWwjU8zDVdwlAmzCcdwhc6widezFdywkeQzDpnutqPu4qivCAP+Mx1fsJg5cqRDcvxJMs/b7n8IboBcLe7z7nL4bncBryfiLyebbnVlcwFtMx11cEV/sxmEsJGN8umVcm2dskGmMyGtsx23MyG/syKWMw6fsx6lMEausy61sI0FMxkNsxkWMioUcu4ecuYmsxIssyI3cJY+cq5EMwpMct5Vcp5fMEtyAB3jgDId2DnlgB7YQaZBwB5AQabZwB3gQY3LmDOLMDTCRDr1gMgAAABhgBrkwYSf2DAeyzw8gBp3AWTKWDZdABAMAAANABJcAZTIGDp0gBg+wz+LRX/VVDrlgBhiwzyogB73wzBERDS3yARMSARBGBLUlY9sQBzDAAhiWJDD/AASeQNLSUQ6UECGfJQESoAEsIAOUANA3eQvr8QEVoNIYYGBxcGS21QtEECJJLQFLvV8mhhK6QF0RoAFaoAd60AUhAAE+wk/DJQ1AME0UAAVtsAdqcF7ONQdE3TDfkFvh4wNrwAdr4AMotCbflTHFBSUPcANgoAdtAEQKEwRjM1wPEyYi4AVerQUz1CiPchIbgwEaQAho4wgikCW4hFXa4FYQoAfVZFk84C90MFzlIAZykgVyZSq0kAW5IgZxTS90ICo80Fd+pQemRR5YdTcVIAL7UyvFgAgX0Cn0pDW1ky8HYws34FzXQFiqTQGhQEvJYAxRkCXAhFXeAgHDsi/I/+AHTJNMbcNNEBAF1J0MobAnH9U21+BZNtBV71IxGQAEfe0RlJBGNXUwVrMwWKULEDMIKlMMzR0Es+0q1yADEpAFxjIxWlABMvDcQ2MvGUADU3Uwg+Avkz00A1MB4XIwyEBRnzIS5RArt2MzDhQDvN0wY6ACInDep+II/sILbWMJLRABrb0vK3QJbcMLEEMreiMCHzAGbaMNMSABDGQzsiQDBZ4R/hTc+YQ9TZIxByUBbHA64KMCpz00QaABG+Q1SKABQdA2dKACF1DhE8MGQePUzRIq9+Q1hAQDxw0StzA9N34wMWIEqpDner7nfN7nfv7ngB7ogj7ohF7ohn7oiP+e6Ip+6IDAABAgUV7jAxVgAYte6ZZ+6Zie6Zq+6YkeCQVA5biD5gQQCZxe6qZ+6qie6pduAeaEO4sAAQwACKo+67Re67au6UZAKbgzC0wT5S40PfB0MCBAQ11U7MZOQlQwABBgMD8URMf+7NAuQUgkAUpkM8kTAE4U7dq+7fVDRVBwRR5UBdw+7uTePl90PF4jDLliRiJxC2lU5/uCJTogCapA7/Ze7/h+7/qe7/y+7/7e7wD/7wIf8AQ/8AZf8Ah/8Aqf8Ay/8AIvCX/g6JBuM5JO6Q7f8Bh/8Rqf8Ry/8R7f8SDv8ZIgCZBAAKDuNZpEAJDw8Swf8i7f8jD/8jL/H/MDPwEVcE5e8+oM8Ac0P/M+3/NA//NCT/OSYAQREAG73usj4Qs97jX65AK+HjDbsFVHHuAXsAJz0Db30uU2gwQYEOZDMwdkbuYH40AywCwN4wlpZFYT00Ex0NIhIQ6xkgVeowcRMDJts1ItbjNLAwMyPjQ0TgEttVF7EuIZw+MQ4OMkBeRCPjTZgFB64DVScAFKThKUMD24rd8XoAIMM94wEAGEEOADjtD0AjgSoFAqk04xAOEZIw7ldANkTy0XDgPZreFkDu+ncgq5It4iAQ61EwId/i7CkAMik9i3KQbBsjjenQXYbVszBQEAbuG5YlGeDwFaEPumIgolst5D/yMNsZIDMRTfIrA79e0RiWPZh1QsoEADWRL1Q/PZb+UH8LQKPhABLjAHOE0bgSInXTD4pwIQtbpAWCFG3DqECRUuZNjQ4UOIESVOpFjR4kWMGTOmm9MiApJVyUSKJMYnwgcg2TSuZNnS5UuYMVl6giFhBqiRIpEp0oABhi+ZEnHF+PAgRBc+gcCMgJABhqagUaVOpVq1JbQgKyJciLIn0BoeEHzKKWfV7Fm0aWF+K+JCAgUkbQK1SVJBggsx39Tu5dvX77pycmBcgMBjTaA9WS5EYAEk2l/IkSXD1AQDAwQaYPzw6QICwocYufhCKwJDBYYIEiR8gBGE12TYsWVL3P9WBsYKDKorZHAho1O62cGFxxY3SQZuuxIyrIgx6eBw6NH3pusUo0WG5BhUwDCzTfp38FV5BYHxITtrItD8mtNlZgUAABjG3Cob3v79mL7myIAPocgmvfATcECMpLEkCAIAICAIS6Qh8EEIIfqGEyIegE+GOX6JcEMO1xnnljIwgE+FNHQxRzJr7LCjmQ5b5NCcO+qgxUUaH1QHkjogUadGHvGjpY47TuxxyO+aUdGa2Lx55JFpiHQSunSWNOZJKoNT5RFVqtQSNmOWBG5LMP2aZklvklyyyTDTVCvKR6ZU882zrswSTjqp6vKRL+vUM6YxHykTNiWZ3HPQl9h0k1D/RDWSM1FGMbozz0YjhajPPycLFE1JM23IUE07ZUgSLD0VFaFHR/WUUjMFNVVTTlfV9EpJXNW0VFkjRRXQM2uNtFVdGV20V0ZpBZbQWy3NdVhCeUV2T1DnXHZPYZ+ls1jJLpVWT2WvffNXbeGMttswqY3MWnDVzLbcLWFFV81v16VSXMjIdVfLc+d1sll7t2w33x7h/UtefomsN+AauSV4yH0PbtFfvwBWmMaBH+ZQXYl5TLhiCBnuy2GMN4y4YwINBnnDi0fGT2O+ODZ5wI9Xtg9flyMsOebvUN5LZZrDaznn6CjmWcCZfxbOZrVwFhpKKY/GT2SlpQu6adiITsto/6hl27nqyWDGOrqnt/5LarSo9jqyq8f2i2mzufQy7eDAPktstvkqO+60fKZ7sq7vNstts+DW+6y5/65Ka8H/yrtwqfi2ym/Epwq88aDQhvyswyeHSfGqGLc8psc3d8luz82qPPSVMKdKc9JZ6jz1jCRnXabRX7fI9KlQl/2i1W+niHDdYV+796Bol8p24CXKvfiHQEe+pdiXb0j4qIh3ftOkp/88VOuZ/z17jaAPSnruETo+fN7Dt6j58L2XCfzwx+fedfMjQp979WNin3v3s1c+/onmz75+mNwve/mzXvn4JxH/WQ+ALxGg9Qg4PfgdsCEJnN4CXdLA6T3QefuT4P9DKOg8C7YEg87T4PIi2EGFfHB5IWTJCJdXQuQZEIUT3N4MH8LClbgQeTAsHgdtmMIa/pAhONSIDovHQ+Cd0IYqRB4RM2JE4CGxdzIUIqmCWMWEOBEjUOydFHWnxBkysXhavAgXdefF2/mwimIEHhktYsbboVF2VFzjFbG4DjdWBI6yk+PrwIhCNvYujxTZ4+v6yDo1CjGQuhvkRArJukOm7o8dXOTtGimRR6YukqSjoyLtiMVLRiSTpNtk6BL5w0rKLpQQGWXoSum5SUowla9b5UNa6blXbq6TqPxkFWvpkFtuLpeWi+UBZ8m6XzYkmJYb5uROucReCjGZDFnm5Jr/CbldQhNPdxwimVKFKW6Kr3rhTEgx+XfM1E1zIdWE3DUb98wwRvOH6lQIOxvnTsSZM37oJB09E2JPxOGzcNmM5zbJiRB/IgSghROo4OAJSHnaMKHrWKjgGvo3fZqPn6GbaEX/dlG9ERSiBj1oR491UJDeLaPh26jnTKoqlI7zoA+lZERn+FJwhjOldBNpTUlKTpweVJxtEipCVsq9lm4uqELdadxoKkubonCpMSVqUY+avaRabqrkbCrbegrVn4ZzqzqVKTmfasyodnCs3Oxq2q5qvaxObq13bKvZvorWsHJzrlis69jeOr24Qm6vVeyr1856zrRKcLBCLOzW7orY/7zecbE/bCzW/uq8wDZusjasbNUOu8/EHnCzM+ws1C67vMwibrQoLG3THgvayILSm7iCKVfLGs7PajS0/FttB1urtNMiL7WF660Ef3u01+o2tr6crbFqS9aqCjW4xRuu4Ip7wOMKLbcs3W38rsu/7P4sudxdrjSbW62T2ja6M8WeUKv7t+/GL7w82y5Su2u++JpvvjmbLvDeq7f8tu+23Byvfcs7z/OOK73QPRR7Y1XU/94twPgb8B3727sI023CA6wwFguM1fumL8HxWjBbO1zFC+suw3HbsANPLMT6gvjAEh3xv0pM1xf/8MNwDTH9atywG/M1xzZM8e1WzLYWZ/9wyDOMMY9nfNMfbyzIhF0yCossuyOnLckkrHIHdwzYHv8vyimbMmO7LMEmg/nJUh3zzcpM2TMf8Mqvy7LZtvzCOPPvy5gNswLbXLQ3czbP8Zsz6+o8tjvvcNDmSzOf16zWP08t0KRdNPnae9BDey3RR6z0+y5NzkxvbdNR7LT+HvFg9/a5gpEO26RZW2rrFTp1ocbaqLsI6+ntGbWqBiGr3+Zq3+J6g6cu6jpoXTVbn1HYJvx0OI8NtWTHcdkxbDY3n920aPNx2j2s9h2vrbRsG3LbSSQ2hHm9Ql/3DdjGHfcUu43Fbx8t3JBs9xffXcdHKzbdi1s3duudxnKnOt//ot135voN3n/LTtaki7fQ5q3JhL9O18I9dxMLfrqDyzfiiAw4pis+xovXLuP63bgk7+3JgfM25MMbuYDXS86JU/fjbVx59FpO4Zfj9uS8TLl3a/69m3M459xs9K57jt+fry/oLh76HWPu35kLMun2W7qSm47FhYeu4T97OClLTrqiU/zoIvbTN4u6X5pl3XNb51nXXfn10D0dw1Fn5NQDWHUuXx3FHQc13S1pdwbiHc96h/HOtQkpsQL+goJXNOF1bPiCIl6vihch4znteCJDfqSSlyzlW2h5UmOeyXx3tt9V6fkcgv7Wokeh3FVselqivoiqVzbrO6j2zbE9Z27H/yXcYUl6a8MembJ/Iu2lbXs0a96nnJdt2WmbUxMj/4CuN7Lw00n8LRpf29LnX9hlPnYfO9+50Mcx9wmtfLAyn7niR+9zo99gmKMfr+o3L/sV7P7yw1/nzvI4+MVsfxLDPyEzP0YDPm+zvn7CvjLSPnEjQEvjv77zPz8DQBsTQCpzQE+DwNKTwFWjQCCzQDPDQFNDtf6jPwTzQCkDQTgTwViTP8gyQRpDQTJTQUFjwVxzQdiCQSiTQTejQUqzwWEjwQjUQTbjQUDzwVcDQmbTwODjwF4zQklDwmBTQmpjwgN0QnSDwlaTQnajQm6zQnhDQI5SwDdiQHrzQnITwg0kQv9I08Jf40J/Q0N3A0N8Y0N9c0N1g0OEk0N7o0OUs0OCw0N+00ON40OAU8MmBESVE0SDI0SSM0SFw0HlUkSfY0SMc0SX0z8Ck0TyokSks0SRw0Sc00QLM8AwxEKLA0WWE0WhI0Ws40QD80Syq5T2I78BdMUqoj4sE0OXIkM9MkOIg0Q/gkUZk8Xwo8X7s8ULxMXCQ8QrNMb/Q8YAVMYQZMbH80Oeg8YJlMYKpMYVtMbMw8bDKyreEybf2xzvgzpUBDlVtDlWZDpwHD1xjDxy9EVCAkavE0bW0UU640WlskdHwse300eTc8ZT1MYO5MYP9MYajEcrI0YnQ8gnVMgUZMj/H3RIL4NINZPILKTIGbTIJMTI5JvHzavHdgS6d7Q6kZQzU6xDk/TIHgTJKVxJPdNIR+PIVITJI5TJLqTJ8yPJ5XtJs2OqcySmlvxDoXy+sytKZ7JJo8NJdtTJKOTJOPRJ8+FHQ/NHrQJITBLI3iNIsDvKbEzK8VtKsDQlpxQ7qKS5k1S6lMw7q3zAYtM9milHZmJKyME9y6HLmLFLa8LLdxLLcRQqv2wnwEQcrJw1rZQrrhQlrzTHs/w9oEw/sqxFs4xLTzNIlyTMxmSlx7zLyETHtPy+tZS6tqS6txw8zMyexGS4xRSszrSlz/zL0DRKzURKzjzNu0vNxlvNFpzM//mrzGS8zGJrTa17Tc2KTWCaTcOszaYEzhcUzmkkTqsSTHrMTancQqrcQ9+8QejMQensRuqUrtFUx9KsO90MPN68vO4MwrlETtVSTmVizns6zMLRy8nhS5cpzPp0Tmwqz7lbR7bMzjfczkJsT2a7zbHEzqGkKgRFHvyEHP1cGf4MKPsUHONcO/gkLvmkJvq0UP8MzO+cxPBcyPF0sPcUUNMk0Dw00Ed80OLJ0NzbUOvq0HX6UIa6UIwC0NdTUfRk0UF00UwstnQM0PP8u/RcvPUMPRgltxHtxBKtyBONvyeNxSj9yCnVOQUdzJKy0XrCUYvSUb2J0MaZUJPxJ23wBP8sQAAEGAJOcBBuAgdckIMEMIAZsIRnONLQKYdeoAMLMAALoINeqA++egZLmIEBWIA4wAVwCCdp4IQhYFMs8ARt+AtwmIQYcIEMUA0MaIEYiINKFSJz4AQZMA1OXQEYEAP1qCJdII8VqIAIqABUDQJdwCJoEIPbyI3VgAEg4AQh+SFtiAPr0NUPcAEYmIRG3QtpCIIWkAAImAEkSAIagAAJWAEg0BAbAocycAEMeAAQ8AEnuIEIgAAViAFP+KFyoAMYyAAIqAAecAIeqACxgAE6IFQUookPgAAIuAEnQAINeACfGINknaFfAIJmxYwkQAIRoNYWCAI4RQttAAIVgAD/L5CFnKiFNtgNGXiGGRIHMWgBCEgCUkCGkRiGQQCBCoCBc2WtOYCBCqgBRiBZkSiGRqgBCWiBObAhmqgADSCEYRgJZCiFJHiAFjCIGXoGGcCONqCFnJAFMCBXIAhVsyiHIlCBCnCEnMiJU9CADACCgT0gOQBZP8jakaCFG5AAGFhVCfIEF4gAKSgGsk0GYsgCCFBZFIKGmriBWojbZPADCHCBnO0gcACCDNCAU8haZCBZR4gAFSgCe6UKmoCAROBbkSAFCGgBSuigZ6gJMKDcZKgFEFABMdBTvQEHGcAAH4BbvjUGH8AAGfha/RKDDwABW/BcMEBbjpWgSQBZUvBc/0RwALu1inQAAgzgAZmlXC2ogBiA3fCJgxXQAGHw3GQYhAiAAWzln04A2cP13FP4206QoF+AAQgYBOkVBg1QgTiQINPFAC6Q3mTYAQwIgnOwCryFAERwX1GoW9HgH3GQAQno3PKNAMyVoCL4gBtw32S4gQ8oAgmihBWQgJ+VXi+oABl4jvjJBfEVBfdFBAiQAbWdClyAgQeQhePlW2QQCy1IXBVeYRZuYRd+YRiOYRmeYRquYRu+YRzOYR3GYVDQV0UoYb7NAQyggR0uYiM+YiROYiVe4hwOhnZVAwRWAwl4gGBgYiu+YizOYi024mSYgeJFYEV4AAkAhS0uYzM+Y/80VmItuAwgjltZ+FtcsApNAFlgQGANgAAOWBI93mM+7mM//mNADmRBHmRCLmRDPmRETmRFRuQqCAAIIGP3dYIKCIBFrmRLvmRMzmRN3uREtgMAqAA+QGA+kAAAsANOPmVUTmVVXuVLDgAJgAIE7uEAmAJWrmVbvmVc1mQOgAANQGBguFyoqIpOcAEI2FvpRQYKgIASyGVmbmZnfuZH2AJHbgQERoIKSABozmZt3mZMxgMAkAA9QGA9IGU84GZzPmd0/uMEkAAkQOBGgIAA2IJ0nmd63mYSaFcEroXLXVmq4AXxDQX3pYXL3QR0OIeCPmiDTmiEXmiFbmiGfmiHjmj/iJ5oia5oir5oi85ojN5oje5ojqboanDZUHZfEPiANPhoj05plF5plW5pln5pl45pmC5oczjdKEDgKHBdc0iHmZZpn+5poP5poQ5qok7odEiD2UVgv4UBbChqpx5qqH5qqY5qn55jCGBa6Q2Fun2NqjDdCoBi6R2EDn4M8CKCDDBe6e1eGLgFCaKDFbgAYpBeYpBVOpCgEIaA7fVcHsgAIpCgaJCBCCBf6VUDCmbeqHDeCjBmviUGEVhg0r2bYYYAgPZcJ3DdAOGfX4iBCBhpyjUJ65Wgb4iBC3CCNs4JUADe78WuAhaBuKbcWpDV9DWLa4gBCfCB1o5bLZCAGAAK/wkShyDIABBQbLINhL8NZgkqAxagAA3mW1KIgBUwAxTSBGIOBMqlBRDoWgvmH1+oiSygXGLwAd2+BrTghLxtBbKtBSe43EkgWNEGgcnOCWJYAwhggTF43PjZBiD4AAogBCBGBkKgAJTwjg4qhzFogQdgg9seCVAAAQyIgett67aFAqzOiVbIgepN7bNQB0qwDAiAAkQAhVBQhORNWTP41Q7CBRnIVx8IBBBnhDUAAQEugsvuIGgAghV4Vj1wBFFwBD2gAecGgg8G7SJoVg1YA0YQhU8IBCR4ANCI4xkyhzhwiwrgAkUABVAghCiAgAs41h1RC08YVgh4gDDHgBWQAf9LmN8f+oUg4FZn1dcKYA05yG4UygYxcAHz0Nd2LVYxUIkfEgdh/YDLiAAxxgAXCALe5ixLiAHcwHOxaAEZ4Oe92AZLsPEAIIAMkAE64PMqEodOIAIYqPQIiAEzyF3CygUxkAEGMAAGiAExyIXHnpxfMAPNJoABaI1OkHMbugY6SNoBGAAVAAJLEPC/MIddsIIqeAX7JqxqsIIpYARcx6Jt+AMq+ANhDydxYAQqsIJq6PJwKodXsAIr2AUTn06ifARiKE4erT4fRVIgbUQhHUUiTfddXPfTS9LKW9LVa9LeIVPEMdORqdAcDdF8kvd+pPfYs/fPw/fa03d729Lr7FL/hE89hT8+hr8dGd1LGoUvL/0nMP0oMVUpgs9Kgx++iJ+9id++io9Ehy9JBlXKck/5YazSYrzSmMzSTZT5iKT5nbT5Ulz5oGz5snz5eMf5jdT5qeR5Dwt5xRz56yv54jv5BoR5jiP6mzR67UT6vfN5ygR6yxT6orr4/Mx4ANt4hep4vUG7mOH3wvF3kAH4MBX4+7ROlof4dr/Ed2/FoU/RV09Ap88+qD9DqU8dsJdQsZcwsqcos78btHeZIu3RvR/Dvl/Avw/GwA9Lqn9Kqy9QrBeiwS/Twteww/eos/94ulF7wWH7jnF7j4d7h5L7n6f7BlWvyo87pXdNpuf7ug/F/7uHx7w3t9uH/Nxfxd1XyXjX+uDk+uH0evK8fLXM/Bbd/GvUe+cPUujPPOOPTuQndwftfYF7/F6M/DKc/Hycfc/p/H7/fBYL/cSnm8VfGdP/G9THGNUffdbf0esHz+wXT+U/KPNfe/QHiHUCBxIsaPAgwoQKFzJs6PAhxIgQpz165E0iRofeKk7L6PEjyJAiR5IsaTBdRWMmV7Js6fLlS1WPVMGsafMmzpvGKqbL6fMn0KAMKVoUanDjo45GlzJtyhLlI5VOp1KtClGmJKtat3Jdt/NRz65ixwYletEpUqVk17J9CVVq27hyR8qkOfcuXolfw+bt6/eg2alp/xIu/P+2MGK/kmYmbnx3r+PIbAOj5Sj5stjDmDdrxcr5M1XIoEcbpdx0MOnUPzWrbn2zruvYNUXLrm3SNFPUtneLZM37t8fFdoET18uzOPKHuJfqTu4coe/n0gnCnm59IO3r0pcbba7defTvyT2Ll569fHHuQr2jBx6+/W/h8JOfn79bfVD29mu/3y+7un+81Rega/gBpR+BqvWXYGrkMSjbgA+OZuBPCEr42YIXcgaghqlF2CFmFPpkIYiSZVhiZPKhONqHKzYmYk4kuojYiTMW5qCNl7WY418w4iQjj33VGGReHBKZ2I5H3uXjTUAqKdeQT8alopSFJVnlZBWddZplWP7/FaWXYxkZ5mPHkZkXkzY5eSZXYLLZ2SNZvVkmWHPOlWZNa9pJlZt7OkWln2tdGahTeMKkJ6FL9ZmoUGMyqtWgjwpl6EuISrpaSpd2haOmVUXaaU6UumQpqDYtWmpNjqJq1KerwiRqS6S62tKps7IEqK1CtZrrSrCyJCuvJNUaLF1xEqurmcf65OtKwCr70bDPeqSqtC7tWq1HzJrkLLYRRdstRLiC29K1406kpWBdmktrpuu6RK27IZUb70LalsQtvdC1m29JnPIrb7L/hmQvSfgKPNC3Bw8krsIYzduwQASPZLDCCTcML8QNPQyxxCJRfLDFCvubMUQbN9xxSB8L/xzywRiTrJDJCqMMksr/siwwwy9rHLDODs38Uc383vzvyD0vFPPBP3sUdL5D8+uy0QUhLbDSGTFNr9P55hw1QlP/WzVGV8ebNb1Qcy2Q1/yCLZHY7pIdb9FnG5R2vmtH1Pa6b7u7tdwE0U2v3RDhba7e65p99t/xBv7Q4OMWbm7cfWPHs+QFLa6RupWftK/mBh3OdeLuXt5Q4+A+Pi7flYe+7ugMld7t6eBGrjrlna/T+kKvYxt7t59Hvbq5uCuke7W8Y5u65MCPK3xCxEtrfLW+G608uMwj5Pyz0Es7e/K1d279Qdgrq/2zyPdNfbfgH5W57QKRr6z0PaOPrfoFif9/7PvHcn++95rXT9D9iJU/YsVPZ/Or1v8GEsBgDTBY5pPbAaWVQIEskFcN5NX+INi/yk1wHRXM1QVzVcCXRfBZHfygrUJoqwciboOSOyH72qfCWY2QZCVUFgyT0r6CzNBVGWxhnXY4kByqRYg9XBULQefCvhFRiAjjnBBrmLEbHquJTlzHEVH1QyUG0YlWdGIWSyVFiFGRWF80IhR3mMTfLVFuZ9xhGEG1RTZ2UYhvlGEa2zfGhpUxWHe0XRw7tcbptfFsf+xcIDW1R4X1kVeH1FwiLzVHQtZxh4+sXCQlNUj5FZJrl5RcJh+1yIM1Mlef7FsoGTVJTlayfaeUWyr/EzVKgZXSVq88WywJtUkDdjJqt+RaLgO1Sl620na/jFow/TTLf9VyVsc0WjL3tEsS9tJoz+xZNO20TH4101XX1Fk25zRMahbze+iqjA6vGM43TdOG1ezZN1+2TjZtM1/dXFU8STbPM43TneX03zm5lE4w5tF29aTXPVGVz4ztk0ztnOI7dbZQiDU0TP2E6D85GNDcxBCQBe3cQeOV0FJNtGEV9dJDyRjRl5W0Yh/VXEjdNVJQtRRkL63cRVWa0RdulDkdReRNJZdSPq6UZDVdWVD7FtN1zbRTR7VZUuWWU6LulIk97c5PIRnVsy3VXE3V1FOFtlWuDZWRRc1YWJs2/9aoTdWsVXXjVdeTVUyu1WhdHddXL5VWrNW1Z2Ul5Vk5Ftf8zBWUfdXZXcGVV0ntdWyHfVlbAftWQw72QIVF5WNJ9ldaBvZkla3QZWGZ2YwltluLfVRj3TZaiEWWs5P15GdHFFpcrvZijLmiVzors9jGaLbArK3CNstM3SaNtz/yLTKB2zJj4fa0jEpt3pQrsNJiy7mJgi7hpPsv4XKTuFQzbpOQC03tPu22V7QuobDrOPLmq7XDfa0vwasm8WKTvfTirj29+zX55om+4LQv3MzrRPQGSr2mA7C73Ntd+FqTv4fyrzwRbDgBC5HAfjIw7CRsLvwiVL9qc3ClIKxPDf+PS8H5ZTA8QTwqETOUxLKj8A4tvCcM787F3eKwSD1cNxXHisUUtTG2qFstGduJxsUDcvSYe14dA47Hv/KxSZEsLRzLlMmKc3KzoOzSqOB2HUKWFpHnZOTnSflZJu4wiiWK5W1p2aZcxu2XnxXmN405e2VWFpWZamXRrflebUbqm6945hynmaV9LtifoRpoJ8ZZWXNmU53Hd+dj5dmre2bdoSeWaLEuOoowbt+jzxRp/E2agEoe8KWDl2mPbVqtnVbjp20XajKNWoClDlajjzXrMNWagbfG4KkrnOrlrTplrebrq/UY687t2ku9tuCvc1VpvA67esWm2bEdm2yDBjv/xtVO37WBlm3Vbhuky9Zcs7H0bBBGe4Xnpl2hjRrupY07uuWG6bu7F2+0zttq9c7uvXHabVB/m379Dtu/1xtwoeabf/sWbFHQWUQ4tpuGDdfgwz0bcYFOHI8LV+rAZV1wBB6cbQk/8MelenEg8sWOJb/byTOc8rNNW7Ejl+DLBRfzGs+ca4OucsZ3u3GODhSNPWfryrnYckvmnHE7P/LRjVZz097chE3HXNEpHvWe5ZpY6a7SulNYcR+GnNlVx+HVSfd0Mm9dZ1Ov7tmrmHbXrd3ObYds0um4dFfOPXd1l/TdSfZzPQe9uEP3adY9DhdG552Sezdm34f3d1IHPmNv/x9y3M0Y+eZN3taVZ23Z0Z15P27+ep339edtOxxUF/67h8dq4j2a+uA2npWPN+fr5Rp7oM5+uasXduv3m3vC7l6rvZ9u6OF9e4AO37LFp+vxt1t7Yi5fo80H7fMNG/3y/t7bwf/w9WWbfcxuv73J13f1eRr+3o5ftOUv2/TJmX6rrv+47aft++N1eTCP3pGlD9/pQVv+Jdj5Odz8wVX9hdf9/dYATlj3Edz37VgCztcCJlcDblj8+dMBUtYE9lcFjtcFllgGYtQGwlYHPtgH1lcIvpicLFkENtkJhlgK/tcK3tgI6lQJxlcMsoQ5QEMhkAAJwIEvlAMcSUMnlEAHaP+BLoiDEGkDLhwBBxwBLmiDEImDLmgBB5RAJ0hDDpJMOfgCHJBACRTCM3RhSZxDLgRBDHwABEBABsAAEHQCEWrOL4iBDLRAG2IADMQAJYBD51xDHMQADFAABFCAC8RAHFxD54ADJcAADGAABERAC8iAGPxC55RDJwABDLAhBKgADARBLpzDT4hDGcBABkTAA1xABeQhDIjBNkiOOTSiCrQhBVxAG0pACwABNFTOLciACkhAG14AIUrACsQALlTOMwBBC0jAA0SAKkKABHwADFCCOUjONhTBIz4ABFTAKj6ANJoBE+KEOBRBC0RADSiCLSRDMgxDIyABBKwAELwiLsn/AQxIQAgEgiyoIzKEghZAwAfIgCXKDSc8YgW0wSkggzqeQhtQgB5yQt/8whpCABeIQjGooywEAghIAAzIgTrIzTYEwSwiQSMMQzIggy0owg1AQAsUQTjWRDqkAR7ugTGoI02WJCK8oxjMYdRoAgw8QBQQQ03SJCloQAYAARVyTS/EgATYwCwEpTrOgg1oZC+cjTYAQQZogCg4ZTIQQxRAAAxowtmUQxHMIiIgpFO2gSSaQUfWBC/EQAS0gVbSJCF4ZSdwjTYoJRKYpVaeAjHGAdeUQxB8gAgAQ1wmAzCIwAcEgU72TBysQAScQmEiAxJUAAwcpdF0Qk8iQknGJVrG/wAv2AQRCKZeaiUy/AAGyMBivswkOGZTFmYytIFGSkPU4AIMQIAjuGYyOEIEwMAxGo00yIAE6AFuykIErMAkRE05yAAG5KVrIgNiFkFNXEM9BgJu5qZX+oLRlAMQYIAUVKctqCRYGk0ZiGZ1ImYZ7CQe1kJ1SgEGAEFqZkwv1KYjjKZTIkMgSIAMKOJL5EJPrkJ1EoMbvgE1DCiBFqiBHiiCJqiCLiiDNqiDPiiERqiETiiFRmgsYEAEEEJ1JsMNYIAQVCiIhqiIjiiJlqiJTqgzYMAFgAF9auUXYAAGOMOJziiN1qiN3qiICgEG1MCG3uQHxAKOBqmQDimRlugbfP/AAwAlbq6CV/amS3ACHgrDhmoABHBARVwplmaplm4pl3apl34pmIapmI4pmZapmZ5pmVpBADwAKGyoE0jAAaCpnM4pndapnd4pnprpHQCABOzBhvKBBACAHeQpoRaqoR4qotLpAUiAE2woKDxAAFhBok4qpVaqpd5pB0DABWwoMLyjQ74ElEIAYVanLZLApZ4qqqaqqj6CmkJAm1bnZCLAqs4qrdZqne5pcG7oHgQqHtiqr/4qsHIpAjDqhn4CBATAFQSrsi5rrWaqBnCqStblftYmZOJmp6qAIHSDtm4rt3art34ruIaruI4ruZaruZ4ruqaruq7ruXrDLqhABAz/wobOQAY8AbveK77mq77uK7/2q7pawwdcQBdsaBdgwAdYg78mrMIuLMM2bL4+QQbMwIYOQifugsNeLMZmrMbyqyDM4qi65ik4AAzkAkxkA3DyQXUqglcGpM6YQxBgQKPi5ixEa9TEwQeAwIaCwAf45WXiIS1UpxO0ZzX2DERCwCJUJx9QgAxYpkuIwc1WZGTmAAYoZtRYAh76p2uCAX5mQ9ToQm0qAm4mwgPAgC5ETTYopRosqUpaQtSYg1XmQIvWJDHorBjYxC/U48AWJh/sppP2zDYo5w1ArVaGgkrSAdeYQxF8gAa0plbOggZ8QBGIYtTQwQq4amEWg9TKwDdw/w1tQgDKxiUydAFlsixMzEFtdoGS1iQy6IFKlsHQRs0t1KMPpKNTKkIFJObmcg00xAAGiEC1BuUpiMBp7iLXfENgVsDROmUt+IBGesLZmEMZVC4fCC5NEkMXQIALzAFOlEMZuIAEgIAfnIIwDMMqDAINqCQR+OHZqEMjSkAFrIEo2AIxyIIi+IA/AoFsyg1/QmIWOEItEEMtOEIWQAAGxADJyk00AMEHRAASKIIsEIMtiMIacOM09g04EIELRMAMDMIqDAMwnEIfgEAEuEAZvOdLlAM9fgAwtiE0viE4So46dEIMrMAqsjABuwARcK3k9IIyYoADRIADBGMuYqfkZP8DETwiKrJwBayADHSCGfILKcKABlDAD/9wNMIAHZhwTfiCGMxwAzRABsgAEejCEwuMNAQiDDSAA1wAHMrhIk6CDMQABARxDMjAJORu5YxDJsZABTiAyCJi/mKSLhCBDHyAH6tADFTiUmQDJqDACRgCFwrRN+SCI7PBM7yu7YhDLzTBCTRBL7Sk7ZjDM7SBCaRALuCx7aiDNBjCCaAAJugw0XWc7C2epz2gyL3gle1gj81ghNVgkN0gVZWxvOnyk/HyiPlyktmy2eEynxFzlhlziyHzlAGzWwkzvzkzm0Hzj0mzmRUgxlkzxG1JLOPWSWFJ1wXL10lJ2M1KOVfJ/sn/Wf+Z0v+tjzZHGTfDDzVLFjhrnDgjnizzHi3v0OBZGjNjGjb7WT1vWUC3zzs7Wjzb0jzbTwCy2z3rTz671j4LXT/D3j8b30JzWwuyXkYb3kbrXkdD30ebmzKLXkGr2kEjWkK7WUprTkPr2kM7U0QD0ESLXUWbWkgD30i7XkkT30lr30wL3EorH26ts6u0s5TUtNfdtDfltALtNDuP3aqcM6+k85Mw9ao49ZMMNLW1NLG9tKbFNKAdNcMlNfotNVVTkFU3NVZr0UW/V1AL31A7X1GTn1qD3E97312DX15j3167X1+rHFsboFubNauhtaIdNs3V9YIFtgQOtvgVNv5B/7bPeTPLLbZlsx9mM6BmI11if7Nnp4tjc9poS51knxhlw+Bn219oW+Bqc11ro9lr53JsK+Bsg2BtIxZnK91pSxw5z3WpQDU6SzU+vbUHxfVXG7cc3Tah5XYz7zYF9rYK/jbe/TUEUrdBW7cHYjcNarfgSTfQebdLgzcKincvk7flmTfhoXdZq7cMsvcxuzfocfcty7e1Mbaxpbar4bfqdRlXK4lXowpYKwlyb7VyKxRzo9BV9zSuwTdB8ze4+Te2ATiyCbjIBLfeDTfHFbeE88qC50qBH8mBl0qCH4lWm3iDk9SDOzeCQ3eniLXNkXV/0/eKabi2cbjvEfiL01SM8/84ufk4zlD4WFu4wWG4uBG5vRk50Xi444H4OKsTjSsSkt+4kpMck9ObkwMclPNLidvKiRNJioPKihNJi5N5kDvVkNt3NIe5+en3Mm85znW5v325wsn5fWU51eH4hev4LsP5NvN5gJV2Z1/RmXdKmgeJjf+5nVsdniOcnqOcoRMgogu3or+5iF/6uoz5rJR5kCy6pjQ6jzw63AH6kgt6MRO6PXs65Ph5qkc62k26yVW6zME66sg65qk6l7P6M7u6QnfZmod6m4MVp1v5iIuQlNselftzp3cZqLuKqPMIqV+KqedIsVP7setVshPUstsKqvc6rcudrcMcrvOcrr9Ypn//+Kafu86lO9Stuw22+5S/O7Bns7DLNLE3O/U9O0dHO5zxOv/5+p3nO0Lve1pLO8HDs8FLOsLDtMI/dr/bu7PjO2pPvGr3O52zdLlrHrw7nbyzHb0fT8M79MPXesSftcYHeMUDecqb+8o3dstvOMfD/MeTXshjXc33+Ms3V7cz1rcbXclXy7SvSrXnyLVLSrbbyLgXfM77386r3cjbXdFvz8nbdMyD/Mz/d88XOcNb/L9jPHEr+9V3s9jLH8CbtMALmr+rPdmHuNmHPc6vPVG3PeOlvQbavV7jvad1vFLHfZWD+9njs96TIN8Ttt/D2uHjYOJf9uIrG+C3teBD+9wP/3zjB/Pjg3bk287Ro0rS28jSP0rTz8i2I33Qo9bQa13hW/TkK3blB/zlX9Hnl0roz8joM0rpu8jpg37qP9fqK97NA/3W63zXZ/jXP/nPu2DUy/PU013VA17rE0vtg8rtu0juJ8rur8jTO3zzQ/Tz+130U970T3jmV/Pmy3bnd071d8r1r0j2E8r2o0jv2/7vX1fwz/LwM3/68/b6A8Q6gQMJFjR4EGFChQsZNnT4EGJEiRMpEpT0SFVFjRs5dvT4EeRHY48epQt5EmVKlStVTiPpjSVEbySnxbR5E2fOlOlIGtP5E2hQoQhVYRx6FGlSlSNLKnX6FCpEl49gKp35qP9mVK1bt/J85JNrWLFIi0oaexZtTqYm07Z1G3Jq1aRXs761e3eiV7B4+fZdWDSjX8GDB64lfLhvXKd0ETe2q9dx5LYXA0u2HNbwZc1RFVuluRm0U8ihSR8tWxp10MypWdvsPPdza9krR8+2fRLwbd0gV+/2TfE1Usa/iUusXRx5Q8rJmTPs3Rz6wOBHh0e3vu74dei5tVt/3h359KHVwSfPXr74afTMv6/fLV4oefe+z8/Xvdw+8fb5ZcMPKp+/2eoLsDXuCLxtvwNL8w8oABVEbcAHSVNPwtYSrFAzBn9yEMPNIuzwMgNBJO3CER3TUCcOTYzswxUbw8/FzUqMcTD/FHNSkUbCWsxRMAp5jGzGH/GyESccheRrxyPvElFJwoJssi0ibzISSreSrDItGLH068ktxZLSJiq9HOvKMcNi0sy3ukyTs5cWi43Nt8qMEyof6UxrzTuTAjMmMfUUrac/JzNKULTyLDQoPlnyE9Gh5mw0KDQhherQSXFSdCVGLdXp0U1xstNTpSoNdSVMVdKU1Jg6TXUlSVlVjSS2Xj3K1JRQnRWlVXENSctdgRrV145qRenWYD3S1ViOQE3WJmCZBc5Nz7B6NidkqZ3I1WtRclbbh4Y9qdhuI7JWXId6LfckbtFV6NuQwl2XIXLhTSjbeTVS196C2gXp3XwPktdf/4KWDZgifAne96N+CR4I4IXPXXgigwNG2COFIW6Y4HohdkhifynuyOKFMQ544I0f6jjfjzkKmeCR/dXY5IVQtlfljVgO2OV8H46Z41h5nqhmjW72N2d7S/5ZoZnnDbqiofMtel6YkTZIaXiZpshpe6GGd+epE6p63asnynrerdeV2uvCfE67IbElIhtes9E9mm2CwEbX7YjgXlfucruu2+61AU8ob5ngHPzfQBGnl9DFD7q73MIf2hvdvsWle3DIxZXcIcrLtbxbtNnWvFvOG/JcXNC1/Rtx0rU1nSHUu1X9WswBd/1a2BeSXVvaqRU9bdyp1V0h3q/1/VnWMxfccf+CiE/IeGqRZxZ4r4V/9nmEon92+mRtr/t6ZrM/aHtmuzdW+duZb16g8Q0qP9nzg61+6vCTdb8g+I2V39fvR1+fffgjiP6Cxb9d0Q9p9jOWAAdCQF8ZEFfpAx8Am8dAgThwVxCclf+CR0HHWXAdGMSVBl+FwJ8pMFggFOGsSMgqCf6vKexzXrRgMy0ZMkxxNxSICXmGQl+p8HAybGGqOGg9Dy4OiDbU4RBJ9cIOxlCHSazLDZkYKh7GzIe7kqIOBVJFTxWxfkdE3Ba56MVNXdFkWcQVGZeYQx060YhQvCEbqejGG4IxgWIcHB2FaEcZonFjapwVH9lnRkvBMYxylCH/IZtnyEkBEmKCfBUjHedISOHxhHoEHCUXZ8lGITKPigwgDYUTxEL6kX2QXJgkWcVJxHkSUZjsoSbr5srBwbJQqiQYK1NlS8DhUlCgzKQoK0hK6piykahsniyxSEu2+bJuwPyTLgPGS1JBk23S1JMwZ0nMDxpzPMispDIdR01/WTNU2EybNu/EzDQ6M23q9Bo76cTNZnoTieCMjzg7Sc7FmTNf6PSUPKdGzzi5M5Dw9BpBkWZQNgHUXgLdFEN/5tA02fOd+ByjPv/Dz1f6E3EIjaRCp0ZRnlnUTBCdl0QtZdKYoXRMGE2oRvfI0QZ59JYgHZxK4cXSSbnUZDD1kkhX/0lSpAF1Y0LdkkxHStNN2nRDOP2lTgHH03X5FFJIvRhV60bUXRr1Z1oVGVfZZlV0YbVRYm0ZWdPG1KI6tZZQTZFUo8lWr3m1mmDlmVpxZtepmbVcaEUUX4nmV6S59atwfaZcb0TXbBr2Z4AVl2ALRdinQZZneD2nXmNmWa1hNmaIzati48nYIjl2naA1mWS7RVlBebZsqt2YZgPKWZPBNm6yhRhrteXaP+GWb7p1WON06Fs9Abdyws3YI8zCxXUY907I/ZxySUbcG0KXThYUhyuWoIRMfEOH5fgFE5QQiGwsMRphUEIYoiGr5qkjG4FQAhN+UQ4dbiMTSliCK8RxFP9pxAEGKigAAzIAgzL8onnfmIQMYFCAAkhABkXIhXsBJw5OBEEGDWBAA2AQhE70t5O5KEIMJMAABsBABpTYRvOeUYYYZMDEKohBHKQBlHRYQgYrkAAEeAwBCagABnOw7+ByIYMWYKDHPv4ADMQA3sFFIwguQHKSMdDhaCBuG2OAwQck8IAH8BgDLZBBLhBXDjlsecc9rsAKZGAJCrMkHQCugATU8IlVtAIUbdCABFwwBhCzjRMwQHIUFHEKWYjCDzSAgAqCoA3A+UIGH4CADwhRClmcYhBIeMAHZOALwGkjCC2AAA38IApZoGIRUYBAlTlR4TG4QAIaaAMoZLEKR4D/Yc4wkMObVWIJGEAgCbZARjKITWxieCECuuZ1zHQBAwnQgBXFLjYyArFoIvx5ateQQQY0AIphSxsZjtAABmRwDbaJowiSDsS3pb0KGkgABrpgmzrk0IIHfGEY0ia2LZAAARhY4ibQcLYT2K3vZKjB3/L2mjiAgIEZBMPgxEaGIiDQAoDPcwwquMAqklHwYq9izWNY9sYsIWpFRJzYwaABBoCA7Z81GwJrQHnHoQBvaNikDB/QADBm3nEaZCAII1+YJkR9ip4nQwsVgMGKp9aLXw/i6ISIQAx64bVtxKACWjh6KR7QAk3MMwgfoIExeg4MDaigDDHZhgwk0IajIwMR/xCQwc0bGgQMIOHoyViFA2DgCa/JQeMeNzgyLqCCOXjNE7+O9tGRAHShB0zgEUBE3tsggRgwXSUwL0Xea7HoSpAD9KEX/ehJX3rTnx71qVf96lnfete/Hvaxdz0zWhCBQOQ9GSL4ABlk33vf/x74wRf+8GEfjiNnAfdZCHM4iN985z8f+tH/PRkyMAPBGzwQEmgBM6Tffe9/H/zCr4QKHmCLvJfC37xgSSdEbf68VwACJCDJ/Olff/vfH//51//++d9///8fAANQAAcwAK0gAB7gE3APCSoAAQjQAR8QAiNQAieQAgUQDwBAAvQA9/RAAgAADyoQBENQBEeQBCEQAf8kAAmuT98cAQICYAtKEAZjUAZncAJJ4AEuAPdsoeI6gSU4QdSEAfc0AAI4gAaL0AiPEAkfwQAhABRwzwkkwACSUAqnkAoj0A4AoAL4APf4IAIAwA6qEAzDUAzxLwAqwAlwDxRasArGkA3bkAo5IAI0APeCoeJabSVwQdQ47uiIYdXQYBn+EBADURAHkRAL0RAPERETUREXkREb0REfERIb0RTgb/Ly7gYwAAciURM3kRM70RM/ERQfURkkoALAAPdwTQKUIRRXkRVb0RVfkRNxAANuAPfirgJSARZzURd3kRc/8QwyAALI7uhWwd/IbCWkgcSg7ujSEAbUD2nKIQb/MEDrjg4YKu4SvGYMxA73aOADxsBrLmEFIIDnjk4LyG3IfoYXYOABmvDoBsHfrmwl1CEIMsAGVLDYoIDcXC5m5GAFKsD9UI7apo7ukCbxIIAUji4U/M3vpkbgIOD2eq4WKsDwFi4ao+DtbuADgkAdYiIXfu0hUY4FvS5tpIHtLHLmWqHw0m7hGq4GiGHmiKEGWE4fTUYdykAFKqAVei4KKkAGauwbRc0Req7aYMAYWcIcxiAcCeH6PuECPuDa2IYSXCACwOD6VkEEyM3c0iYXSAwJxlHfgAEJLK8op4YkMWAE9FDfkAEMIMAFKOHciOADKoAd05IQIGAFxuAcbuIb/4IgHJMgFNjtFLQAAj4ACLIybcyhDKSyBhjBJYlNFtrgAqpM4aDS2UBgEGqh2GphEEAA3tyybnQhGiugDWTh24ZhEWwgAlygDMyhbq4BCCRNC07h25AhFJLALoMAHHJiG8RAyiLAAkaABi7Ax1wgCHyybsoBwCQNAmbgBoRQAtjMGaPpEraMAhwgBGwgBHjsA2JAEx7PZHghxyggAi7ABkQgAiCgwOTgHNlGGqIM/i6ABmigOjHABcQA83BiHDiBwVbgAz5gBWAgBixhJucpF4IABvjTP11gxhxtcZ5BDGCgBfpTBcRMDJ7BcbIhDmTABfhTBVYgBoJgwhYHHCwhBq0CrD9Z4AVkgBMG1CbEgRcmIQ7MYBJy4T4XR7wsIQ7KgA464bwKKRo0YQ7KQA40ob1kKBs6gQ7KIA4sob5kaBtygQ7MIA4mgRdY1LmuFEuzVEu3lEu71Eu/FEzDVEzHlEzL1EzPFE3TVE3XlE3b1E3fFE7jVE7nlE7r1E7vFE/zVE/3lE/71E//FFADVVAHlVAL1VAPFVETVVEXlVEb1VEfFVIjVVInlVIr1ToCAgA7" style="margin-top:1rem;" /></div></details></div></div>
+```{=html}
+<div><details><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">GridGraph[{5, 5}]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhwAO/A/frAB8mMSIpMyIpNSQrNSYsNikvNyMrOCMsOSQtOyYvPSkvOCYwPiswOC4zOi80OzA0OzE2PTM4PjU5Py83QzM4QDY6QTI5RTY8RDo9Qjw/Qzk+Rz0/RDA8TjI+UT1AQz5BRTtBSTxCSz1DTD5FTjNAUzVCVTlHXDtJXjxKYD1MY0FDRkJER0RFR0VGSEdISUpKS0tLTEtMTExNTUFHUUJJUkNKVERLVUVMVklOVkZOWEJNXkhPWkhQWk5SWEtSXUxUX1FRUVVVVVFUW1JWXVpaWl1dXUVPYEVRYk5WYU9YY0FRakNUbUVWb05bb1FaZlpdYVNcaFVdalZfbEpbdkpcd0tdeExeek1ffF1gZVdgbVlibk5hfVljcFtkclxmc11mdF9odlhmfGFhYWVlZWRlaGpqam1tbWJpc2NqdG5ucGFreWJsemNtfGRvfmZwf21ye290fXJycnV1dXp6en19fVlvkFpwklxzlV50l191mGZxgGhzgml0g2t2hmx3h2JyimZ2jm56inl9gnF9jnN/kH6CiHyDjXWBknaDlHiFlnqHmXuImnyJm36Lnn+Mn2eApnaJp3mMqn6Ts4KCgoWFhYWHi4mJiY6Ojo2SmIuSnZGRkZKSlJaWlpmZmZ2dnYGOoYKQo4ORpISSpoaUp4aUqImXq4+ZqIqZrYybr5CaqYGWtY2bsI6dspCftJ2iqZqir5Ggtp+ms5OiuJSjuZWkupemvZiovqGhoaWlpamqqq6urq6zvLGxsbW1tbq6ur29vZqqwZyqwJuswpysw52txp+wx6Cwx6GyyqSzyqO0zKu3ybO/0r7CyLjB0b3G1cHBwcXFxcnJyc7OzsHL28TN3M/Q0s7V39LS0tDR1NXV1dnZ2d7e3tLZ4tTb5dbd5+Li4uXl5eDk6urq6u7u7uXp8PHx8fLz9vb29vb3+vj5+/r7/P///////////////////////////////////////////////////////////////////////////////////yH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAwAO/AwAI/wDXCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS55MubLly5gza97MubPnz6BDix5NurTp06hTq17NurXr17Bjy55N+2a6bM9+XTNXG6U2aL6kiet98ls0X9G+ETcpTpovaNqWlzR37dezbOlegrsEREYMGDGATP+KLt1juU5FZMiAoV4OtPIe0+kqAx58jDG8ssPnCE1O/e9FeFLOfhxpMwkQ38UQQxCXgMMSLjK0gIEEEEAQAQYtxKCJfgRa9EwQMHxAYYUVqADDHMN1aNE2YsCgwogQSGCiGNuoaJE4/qmAQYUxZgBDEM/YWFE6msAgIY8SZNCCDLeoZAkMOyYRSCOfDBJFBBLAIAdvQkakiwwZQHADH4yAgkgXF0jgghgOdglRNECsAIEIbCgCiiJriBDBCkBI4yZE4ojRggQXeIEIKIzwcQMEH8igy58PneOfBBFEMQgojQSCBAQYxGAJSp7AIIENqyRj6qmyIBEBDJRA2tAzMmD/AIIjp54qDBgQtFAGl64mtE0QKlAQCDK1IoNMIBF8EESNvSZkzhhygiFMrckg4wgIGMgQZLMJUSIqErOcSmwyq9yQpScmZQNDBTwQQ624UGT5C7cHlRNEBiDI8u6pfEAAAyf0HmTGChGEsq+poUCwghkBG8QJDBD4cXAysoCg7IAND/SLqFCM+y4xPFQQQzYlybFCBbRMnAwxIXwgBocNdwLDA6ConEwS2baZ8TOi8mHzHhJom7FA4MSKhMfvIgMKBC6gO7Q6RXwAgrsT01LBCnKQVLQEYNicTCASxODn0ERgcAPS+5biLy5Dr0PHyVRPTMzVk7SNC8SlqGxsDhgQ/9G2NDFEEIjXagStM0i9QCyK17Tkyok6kEcu+eSUV2755ZhnrvnmnHfu+eegh+65uhJIbDMyFsch+uqst+7667DHDvo5QGAQhdfJQIEBEObI7vvvwAcvfOtxqAAC7nyEjd3wzDfv/POvc9ICBCnbHMoDMPQykifT2+I1MhVAUMIj5Jdv/vnop6/++uy37/778Mcv//z01y//FgFA0AjuSEiQgP0ADKAAB0jAAhqQfngAQAXagLs2SAAAeTigBCdIwQpaUIAJkAAScNcICARgCxcMoQhHSMICkgACFcBd41rgtJBoYnrT8poGIMCBEtrwhjjM4SOokL+aec0JFQiADv+HSMQiDtAOCvSZ15IHADsY8YlQjKL6AiABJ+AuYQGwghS3yMUicgACGsDdMCLQAk2MBBcugIC+bFYMTkWBGHCMoxznSMc62vGOeMyjHvfIxz768Y+ADKQfG/EACCgCdzzAgAgEychGOvKRkIykJAEpCwdUQA24W4MEHFCLSXryk6AMpSgdOQIM8AB3iahQI0bJyla68pWRjMKO0LYvWTCNbSKBBsQS4TVS+CsXQxPHurpmM2JQYAWtGlrUcoC7G3ygCG2jBAsoELeJgaECMEhRw3IBMVJ4LZUweI9IzBEEDPjAa10I2+ECFocPaKCa+0KEv+Y1NOlBoFQqWwXTADb/tI1BABE2G4YGVBCHtn1DBhXowul8sLtzkKQTaVyEytTWgrq1bWMSWIPKagGCDLzMoLHyQTEmhgyGykA5QzuHGKRWC5WpYVXbGtokppe3iS3CATDoREnKQYQVUMCH71oFtoCA0rbFYXqD25ctdoDNmA5NZhHgwkg/xoVV6bRt63hGDNjlvaQFIlcFxeo3gIAvfL4LFBV4JsZIkg0gfCACYKieqWzBhwp0yqnBLIKcoHCKWhEDESHI0lWxmg45uCACN3CEx6x1g1XJAWZPXRcIEBE3ZJwCCg5gQRG0edEYYKACfABGrWihBkYBgWQniUYQWEAhGjjBCYuSwApk4Aus/xIEHGNwwY5EgIQohIxROVWHbQVSjjlAyQEXQAIUfjBDDJxorVhVRydi8AEU+gAKSBABBC7ggjGss22+kMEKKHSD19IgRi0IQjRU8o05REhESVqSGVA7XOJq4jvwxRAMxIBX26YjF0CAwQrSdIEP/AgXkLXtM8QQgxVMKK3s0QR0h5sNMxhpQhL4QIbmUFSVXIMTRThAAHqgifXW1yDfuIUZEBCAEEzCFw49MUHEwQs5UCAAE5iDLsYhY4Kc4xeTCEEADmCGW3S4x9G4RA8MYIAicIK+LvEG+abRY4Skg3zGqDJCVPEIVWj5IMUgn3C/TJBpkM8bM5HyI6hM5oFc+f8RWW7zQLjsZTkLxBjkS7CWzfwINMtEzWyW85vjbGc62/nOeT40n/0cE0AfetCHXgeXJRFpPD9Cz1VedJqn/GgsR1oSXa50ou2s6T9z2s6QPrShD21pTPe41I0+taA9repHUJrVo5YzrGHiaFTTutChxvWlFX3mTa+503D+dLDt3Gpi99nYgW5zqoF9a2bnus27fkmvZ53sWtfZ2sMmdbFNfWxfd9vOoP62nJst7meTO9pknracVw1uV8s421GWtbR/PW9bizrcuh53rMvNbULLOd3/tveJ8d2Sbe/73P1Wd5vZHXB3DxzeX5Z3myedcGczmtf6jje/N77sdV+bzAz/Z4nDRQ7xNiNc2Aqvb8pXsvKMj5zMHIe5x6GNbIOTXOJkpji2BQ5ygj/c52R+eb13/u6eR5reJgf40C1edIxrWeM497fO2/1xbYfc5i1PesknfvIvz1wlNb/6zb8MdbJLHeVE97rRWY50tmt96VznubnrruW2B73se457vucOdr5XWelRj/lwz56StFcZ63avduKZfnGne7vjeW/63pUN9C8LHe5Ul7vVH7/2vo/97283u+Ab/nW1hz3ymK941wc/+h5DXsuId7vibct4lDje9qWvst89D/hMr17lrSf9600ved1TvuqWB3bntfx51Yee9tE/+OmJn/rAX5/1hHe9/+F7nHO8y17vBX/69qlf/Fcfn+bJB/7yD7/+Klff+7MHf+1lfHvh17/H92d834d84ad84ydj5Td5mVd5m3douYd6u4dVvXcSv8d/wUd+/ydjAeh+Awh/BSh/B3hiCeh8Cwh9DSh9sTd1+UeA+3di/ddjD8h9Edg2E2gSFeiCF4iAd6eA56d56Xd5W9eDDPiD6JaBJ7aB9/Z+aBd/Fjh/GDh99td+SdiBS/iBTRiC9TWCEPh8opd9LmeE9YWEC6eEjceEOOiEOgiFACiFY0iFZWiFZ4iFw6WFMsiF2HeCEZeCoLeCHtiC9fWCMhaD7Nd9AsiHVeiHwwWIIriDJCiEJv9IhHkYhCqIfkfHeXpofYb4hojoXzm4iGqogWwoc2Toe2b4h52YhYy4hSXYhXj4hZ94hKG4eKNIgaWYiKc4h2A4XGIoim5IinBoimi4iM2nio7IipD4c5eIf5RId5YoiXu4jIWnfsNYh6t4h8eYda8YhrHIe7Nog7XIicFYX4IYhYTIgZnoi5tIWLdoW8M3iDM4NDVYEjcIjHLIjqlIjcVojZXogLloW7soi71Ii79oi+GIi9moi9sogd0oj9+ojgVpj9Pojnaof16IjclYiNAofs1ofpPog/tIbRdpjhlpgOp3kP6YkDS4kCQxjwRZj1g1jmtYjlN4jgKZjm2jiKj/aJJY9Y/cGJDeOJDg6JJtQ4cSWY0U2Ypip5Ntw5MK6ZMMCZQOKZRD047k+I4ZE48r2ZA3uY5YRZRVOZEsWJF2p5RDw5Qp6ZRZCZVb+ZAv2Y87iZLwqJIjwZJBKY0hOZMjCYIleZdtSJM/aZNDg5PDBZOgKJN9mZdXuJfOiImIGYd2uZjK6JHMyI9kmTFmGZdoOZdaGZhcOZRuuZRweZVyKRJ0GZWPyZHPKJnRCISoyZiqqZGUyZe86JdPCZgZI5gQKZsASZtpaZsNg5td+ZllGZoNg5WaqZacyZZtQ5iwaJiz2Zj0qJitGZlD+JH9FpFfaZRhiZRfxpza6Jy7CZ0t/ymdPNiR1TmZIAmZGPmaJMma5Zma57maRViZDXOZopmZpLmZt9mZU3mPRZmPR3mNY6mbPcmbx+mbAQOcyymclkmcAWOc+Ymc+6mc/UmfAWOfxTmaIVGaaymVGeOVMWmVGYqfG6qfv8mfGeOdCAmeBSqedemejWiej2idJIedIQqWfSiWpmeh9IKhD6qhIMGhyemhDaOiJ8miTWmgEYqg9KKg/WmjhSmiP0qiQWqiCYqiDUOVN6qdOcqduMeg9emg9AKhJSqhJ0qhHwqmFyqm3EKmVWqmV4qmWeqf2Qmg2ymgX8qj3OKjYwqkHyGkE0qkAaOlUYqjh6ij/gelzSmlff9KpX9qpU2KpYOqpj3Kps3ipo8Kp5EqpwFjpG+JpGeppGXKpNzipGmqqN/JqG3qpx4BqGcqqPRCqItqqJqIqDBIqXtqqb2Cqa0KqaUqqbGKq83Cp6vqqL2qqb/KqcGKqiuqqpfKqh3hqnEKq9ziqaAJqpgpqm9Kqs1iqnOqp8Oqq67Cq9Hqq90KrNwCooXKpYfqpf4Hrr1CrM9qrOWKrOeqrNUqrPEqrpBCrhwhrZtKrc2irrPKrrXqrk9IoEnqoqYZm+opkuyplzBKjDJqjDSadcx6pM66q9D6r+baK97aqfrqKvLKsfTqsfYKsug6sCMLKSU7rh27EQCbrALbKwT/m6q0io62moYKG6oM26Eb+Z6uGZ+wmZ7TuZ5E254o+LB4GbGJ6bBHC7FJK7FLG7VNO7VPa7RCS50zip7aB68ky69/4q8y+7GuErLBCrYuK7ZuQrYaMbP3WrOucrPNmrM1ubOe2LPZ+rNDGrQxCp9dK5/Xqbf3qa2Zyq0qi68sq7Z/8rL9GrNva7aQgrb5yrhu4rhjC7kZAbeJK7eQIqs4a7A6i7A6mLGfurEwe7Jlm7Jnu7K9Yq3Dia2Fy7eBSp5/O7SBW7SDy7SH6bSOObH4WLH66LWuSLgjarjHiritq7g2S6dbaqddiqfvarxTirz1qryT67quArsNKrvHS7uv/2q7FAu4Fku8GEu9jWq9KIu9f0K5zcK9Yeq91Qu+0yq+wUu+wyu4NYq+xaq+q8u+buK+zWu5XYK5bau5GMG5y+u5fwK/ayq/6Uu/AXuaW4u0uau0kWi1vYu1vzuf/Duv/hu5rJu9zDu3Ldu4bNslbru5ktu+2vu5zruu0Nuu0nurBCwkBqzCCHwRCkzCDOwmoFu3onu3pCuMH2yyIczCI+zCJQzDN2wjOSwkK5zALRzAL9zAJ3y5KSzFO2wRPczEP9wldKuxdvuXeJuTR5y6SUzFS2zFTYzFT6wiUWwjU8zDVdwlAmzCcdwhc6widezFdywkeQzDpnutqPu4qivCAP+Mx1fsJg5cqRDcvxJMs/b7n8IboBcLe7z7nL4bncBryfiLyebbnVlcwFtMx11cEV/sxmEsJGN8umVcm2dskGmMyGtsx23MyG/syKWMw6fsx6lMEausy61sI0FMxkNsxkWMioUcu4ecuYmsxIssyI3cJY+cq5EMwpMct5Vcp5fMEtyAB3jgDId2DnlgB7YQaZBwB5AQabZwB3gQY3LmDOLMDTCRDr1gMgAAABhgBrkwYSf2DAeyzw8gBp3AWTKWDZdABAMAAANABJcAZTIGDp0gBg+wz+LRX/VVDrlgBhiwzyogB73wzBERDS3yARMSARBGBLUlY9sQBzDAAhiWJDD/AASeQNLSUQ6UECGfJQESoAEsIAOUANA3eQvr8QEVoNIYYGBxcGS21QtEECJJLQFLvV8mhhK6QF0RoAFaoAd60AUhAAE+wk/DJQ1AME0UAAVtsAdqcF7ONQdE3TDfkFvh4wNrwAdr4AMotCbflTHFBSUPcANgoAdtAEQKEwRjM1wPEyYi4AVerQUz1CiPchIbgwEaQAho4wgikCW4hFXa4FYQoAfVZFk84C90MFzlIAZykgVyZSq0kAW5IgZxTS90ICo80Fd+pQemRR5YdTcVIAL7UyvFgAgX0Cn0pDW1ky8HYws34FzXQFiqTQGhQEvJYAxRkCXAhFXeAgHDsi/I/+AHTJNMbcNNEBAF1J0MobAnH9U21+BZNtBV71IxGQAEfe0RlJBGNXUwVrMwWKULEDMIKlMMzR0Es+0q1yADEpAFxjIxWlABMvDcQ2MvGUADU3Uwg+Avkz00A1MB4XIwyEBRnzIS5RArt2MzDhQDvN0wY6ACInDep+II/sILbWMJLRABrb0vK3QJbcMLEEMreiMCHzAGbaMNMSABDGQzsiQDBZ4R/hTc+YQ9TZIxByUBbHA64KMCpz00QaABG+Q1SKABQdA2dKACF1DhE8MGQePUzRIq9+Q1hAQDxw0StzA9N34wMWIEqpDner7nfN7nfv7ngB7ogj7ohF7ohn7oiP+e6Ip+6IDAABAgUV7jAxVgAYte6ZZ+6Zie6Zq+6YkeCQVA5biD5gQQCZxe6qZ+6qie6pduAeaEO4sAAQwACKo+67Re67au6UZAKbgzC0wT5S40PfB0MCBAQ11U7MZOQlQwABBgMD8URMf+7NAuQUgkAUpkM8kTAE4U7dq+7fVDRVBwRR5UBdw+7uTePl90PF4jDLliRiJxC2lU5/uCJTogCapA7/Ze7/h+7/qe7/y+7/7e7wD/7wIf8AQ/8AZf8Ah/8Aqf8Ay/8AIvCX/g6JBuM5JO6Q7f8Bh/8Rqf8Ry/8R7f8SDv8ZIgCZBAAKDuNZpEAJDw8Swf8i7f8jD/8jL/H/MDPwEVcE5e8+oM8Ac0P/M+3/NA//NCT/OSYAQREAG73usj4Qs97jX65AK+HjDbsFVHHuAXsAJz0Db30uU2gwQYEOZDMwdkbuYH40AywCwN4wlpZFYT00Ex0NIhIQ6xkgVeowcRMDJts1ItbjNLAwMyPjQ0TgEttVF7EuIZw+MQ4OMkBeRCPjTZgFB64DVScAFKThKUMD24rd8XoAIMM94wEAGEEOADjtD0AjgSoFAqk04xAOEZIw7ldANkTy0XDgPZreFkDu+ncgq5It4iAQ61EwId/i7CkAMik9i3KQbBsjjenQXYbVszBQEAbuG5YlGeDwFaEPumIgolst5D/yMNsZIDMRTfIrA79e0RiWPZh1QsoEADWRL1Q/PZb+UH8LQKPhABLjAHOE0bgSInXTD4pwIQtbpAWCFG3DqECRUuZNjQ4UOIESVOpFjR4kWMGTOmm9MiApJVyUSKJMYnwgcg2TSuZNnS5UuYMVl6giFhBqiRIpEp0oABhi+ZEnHF+PAgRBc+gcCMgJABhqagUaVOpVq1JbQgKyJciLIn0BoeEHzKKWfV7Fm0aWF+K+JCAgUkbQK1SVJBggsx39Tu5dvX77pycmBcgMBjTaA9WS5EYAEk2l/IkSXD1AQDAwQaYPzw6QICwocYufhCKwJDBYYIEiR8gBGE12TYsWVL3P9WBsYKDKorZHAho1O62cGFxxY3SQZuuxIyrIgx6eBw6NH3pusUo0WG5BhUwDCzTfp38FV5BYHxITtrItD8mtNlZgUAABjG3Cob3v79mL7myIAPocgmvfATcECMpLEkCAIAICAIS6Qh8EEIIfqGEyIegE+GOX6JcEMO1xnnljIwgE+FNHQxRzJr7LCjmQ5b5NCcO+qgxUUaH1QHkjogUadGHvGjpY47TuxxyO+aUdGa2Lx55JFpiHQSunSWNOZJKoNT5RFVqtQSNmOWBG5LMP2aZklvklyyyTDTVCvKR6ZU882zrswSTjqp6vKRL+vUM6YxHykTNiWZ3HPQl9h0k1D/RDWSM1FGMbozz0YjhajPPycLFE1JM23IUE07ZUgSLD0VFaFHR/WUUjMFNVVTTlfV9EpJXNW0VFkjRRXQM2uNtFVdGV20V0ZpBZbQWy3NdVhCeUV2T1DnXHZPYZ+ls1jJLpVWT2WvffNXbeGMttswqY3MWnDVzLbcLWFFV81v16VSXMjIdVfLc+d1sll7t2w33x7h/UtefomsN+AauSV4yH0PbtFfvwBWmMaBH+ZQXYl5TLhiCBnuy2GMN4y4YwINBnnDi0fGT2O+ODZ5wI9Xtg9flyMsOebvUN5LZZrDaznn6CjmWcCZfxbOZrVwFhpKKY/GT2SlpQu6adiITsto/6hl27nqyWDGOrqnt/5LarSo9jqyq8f2i2mzufQy7eDAPktstvkqO+60fKZ7sq7vNstts+DW+6y5/65Ka8H/yrtwqfi2ym/Epwq88aDQhvyswyeHSfGqGLc8psc3d8luz82qPPSVMKdKc9JZ6jz1jCRnXabRX7fI9KlQl/2i1W+niHDdYV+796Bol8p24CXKvfiHQEe+pdiXb0j4qIh3ftOkp/88VOuZ/z17jaAPSnruETo+fN7Dt6j58L2XCfzwx+fedfMjQp979WNin3v3s1c+/onmz75+mNwve/mzXvn4JxH/WQ+ALxGg9Qg4PfgdsCEJnN4CXdLA6T3QefuT4P9DKOg8C7YEg87T4PIi2EGFfHB5IWTJCJdXQuQZEIUT3N4MH8LClbgQeTAsHgdtmMIa/pAhONSIDovHQ+Cd0IYqRB4RM2JE4CGxdzIUIqmCWMWEOBEjUOydFHWnxBkysXhavAgXdefF2/mwimIEHhktYsbboVF2VFzjFbG4DjdWBI6yk+PrwIhCNvYujxTZ4+v6yDo1CjGQuhvkRArJukOm7o8dXOTtGimRR6YukqSjoyLtiMVLRiSTpNtk6BL5w0rKLpQQGWXoSum5SUowla9b5UNa6blXbq6TqPxkFWvpkFtuLpeWi+UBZ8m6XzYkmJYb5uROucReCjGZDFnm5Jr/CbldQhNPdxwimVKFKW6Kr3rhTEgx+XfM1E1zIdWE3DUb98wwRvOH6lQIOxvnTsSZM37oJB09E2JPxOGzcNmM5zbJiRB/IgSghROo4OAJSHnaMKHrWKjgGvo3fZqPn6GbaEX/dlG9ERSiBj1oR491UJDeLaPh26jnTKoqlI7zoA+lZERn+FJwhjOldBNpTUlKTpweVJxtEipCVsq9lm4uqELdadxoKkubonCpMSVqUY+avaRabqrkbCrbegrVn4ZzqzqVKTmfasyodnCs3Oxq2q5qvaxObq13bKvZvorWsHJzrlis69jeOr24Qm6vVeyr1856zrRKcLBCLOzW7orY/7zecbE/bCzW/uq8wDZusjasbNUOu8/EHnCzM+ws1C67vMwibrQoLG3THgvayILSm7iCKVfLGs7PajS0/FttB1urtNMiL7WF660Ef3u01+o2tr6crbFqS9aqCjW4xRuu4Ip7wOMKLbcs3W38rsu/7P4sudxdrjSbW62T2ja6M8WeUKv7t+/GL7w82y5Su2u++JpvvjmbLvDeq7f8tu+23Byvfcs7z/OOK73QPRR7Y1XU/94twPgb8B3727sI023CA6wwFguM1fumL8HxWjBbO1zFC+suw3HbsANPLMT6gvjAEh3xv0pM1xf/8MNwDTH9atywG/M1xzZM8e1WzLYWZ/9wyDOMMY9nfNMfbyzIhF0yCossuyOnLckkrHIHdwzYHv8vyimbMmO7LMEmg/nJUh3zzcpM2TMf8Mqvy7LZtvzCOPPvy5gNswLbXLQ3czbP8Zsz6+o8tjvvcNDmSzOf16zWP08t0KRdNPnae9BDey3RR6z0+y5NzkxvbdNR7LT+HvFg9/a5gpEO26RZW2rrFTp1ocbaqLsI6+ntGbWqBiGr3+Zq3+J6g6cu6jpoXTVbn1HYJvx0OI8NtWTHcdkxbDY3n920aPNx2j2s9h2vrbRsG3LbSSQ2hHm9Ql/3DdjGHfcUu43Fbx8t3JBs9xffXcdHKzbdi1s3duudxnKnOt//ot135voN3n/LTtaki7fQ5q3JhL9O18I9dxMLfrqDyzfiiAw4pis+xovXLuP63bgk7+3JgfM25MMbuYDXS86JU/fjbVx59FpO4Zfj9uS8TLl3a/69m3M459xs9K57jt+fry/oLh76HWPu35kLMun2W7qSm47FhYeu4T97OClLTrqiU/zoIvbTN4u6X5pl3XNb51nXXfn10D0dw1Fn5NQDWHUuXx3FHQc13S1pdwbiHc96h/HOtQkpsQL+goJXNOF1bPiCIl6vihch4znteCJDfqSSlyzlW2h5UmOeyXx3tt9V6fkcgv7Wokeh3FVselqivoiqVzbrO6j2zbE9Z27H/yXcYUl6a8MembJ/Iu2lbXs0a96nnJdt2WmbUxMj/4CuN7Lw00n8LRpf29LnX9hlPnYfO9+50Mcx9wmtfLAyn7niR+9zo99gmKMfr+o3L/sV7P7yw1/nzvI4+MVsfxLDPyEzP0YDPm+zvn7CvjLSPnEjQEvjv77zPz8DQBsTQCpzQE+DwNKTwFWjQCCzQDPDQFNDtf6jPwTzQCkDQTgTwViTP8gyQRpDQTJTQUFjwVxzQdiCQSiTQTejQUqzwWEjwQjUQTbjQUDzwVcDQmbTwODjwF4zQklDwmBTQmpjwgN0QnSDwlaTQnajQm6zQnhDQI5SwDdiQHrzQnITwg0kQv9I08Jf40J/Q0N3A0N8Y0N9c0N1g0OEk0N7o0OUs0OCw0N+00ON40OAU8MmBESVE0SDI0SSM0SFw0HlUkSfY0SMc0SX0z8Ck0TyokSks0SRw0Sc00QLM8AwxEKLA0WWE0WhI0Ws40QD80Syq5T2I78BdMUqoj4sE0OXIkM9MkOIg0Q/gkUZk8Xwo8X7s8ULxMXCQ8QrNMb/Q8YAVMYQZMbH80Oeg8YJlMYKpMYVtMbMw8bDKyreEybf2xzvgzpUBDlVtDlWZDpwHD1xjDxy9EVCAkavE0bW0UU640WlskdHwse300eTc8ZT1MYO5MYP9MYajEcrI0YnQ8gnVMgUZMj/H3RIL4NINZPILKTIGbTIJMTI5JvHzavHdgS6d7Q6kZQzU6xDk/TIHgTJKVxJPdNIR+PIVITJI5TJLqTJ8yPJ5XtJs2OqcySmlvxDoXy+sytKZ7JJo8NJdtTJKOTJOPRJ8+FHQ/NHrQJITBLI3iNIsDvKbEzK8VtKsDQlpxQ7qKS5k1S6lMw7q3zAYtM9milHZmJKyME9y6HLmLFLa8LLdxLLcRQqv2wnwEQcrJw1rZQrrhQlrzTHs/w9oEw/sqxFs4xLTzNIlyTMxmSlx7zLyETHtPy+tZS6tqS6txw8zMyexGS4xRSszrSlz/zL0DRKzURKzjzNu0vNxlvNFpzM//mrzGS8zGJrTa17Tc2KTWCaTcOszaYEzhcUzmkkTqsSTHrMTancQqrcQ9+8QejMQensRuqUrtFUx9KsO90MPN68vO4MwrlETtVSTmVizns6zMLRy8nhS5cpzPp0Tmwqz7lbR7bMzjfczkJsT2a7zbHEzqGkKgRFHvyEHP1cGf4MKPsUHONcO/gkLvmkJvq0UP8MzO+cxPBcyPF0sPcUUNMk0Dw00Ed80OLJ0NzbUOvq0HX6UIa6UIwC0NdTUfRk0UF00UwstnQM0PP8u/RcvPUMPRgltxHtxBKtyBONvyeNxSj9yCnVOQUdzJKy0XrCUYvSUb2J0MaZUJPxJ23wBP8sQAAEGAJOcBBuAgdckIMEMIAZsIRnONLQKYdeoAMLMAALoINeqA++egZLmIEBWIA4wAVwCCdp4IQhYFMs8ARt+AtwmIQYcIEMUA0MaIEYiINKFSJz4AQZMA1OXQEYEAP1qCJdII8VqIAIqABUDQJdwCJoEIPbyI3VgAEg4AQh+SFtiAPr0NUPcAEYmIRG3QtpCIIWkAAImAEkSAIagAAJWAEg0BAbAocycAEMeAAQ8AEnuIEIgAAViAFP+KFyoAMYyAAIqAAecAIeqACxgAE6IFQUookPgAAIuAEnQAINeACfGINknaFfAIJmxYwkQAIRoNYWCAI4RQttAAIVgAD/L5CFnKiFNtgNGXiGGRIHMWgBCEgCUkCGkRiGQQCBCoCBc2WtOYCBCqgBRiBZkSiGRqgBCWiBObAhmqgADSCEYRgJZCiFJHiAFjCIGXoGGcCONqCFnJAFMCBXIAhVsyiHIlCBCnCEnMiJU9CADACCgT0gOQBZP8jakaCFG5AAGFhVCfIEF4gAKSgGsk0GYsgCCFBZFIKGmriBWojbZPADCHCBnO0gcACCDNCAU8haZCBZR4gAFSgCe6UKmoCAROBbkSAFCGgBSuigZ6gJMKDcZKgFEFABMdBTvQEHGcAAH4BbvjUGH8AAGfha/RKDDwABW/BcMEBbjpWgSQBZUvBc/0RwALu1inQAAgzgAZmlXC2ogBiA3fCJgxXQAGHw3GQYhAiAAWzln04A2cP13FP4206QoF+AAQgYBOkVBg1QgTiQINPFAC6Q3mTYAQwIgnOwCryFAERwX1GoW9HgH3GQAQno3PKNAMyVoCL4gBtw32S4gQ8oAgmihBWQgJ+VXi+oABl4jvjJBfEVBfdFBAiQAbWdClyAgQeQhePlW2QQCy1IXBVeYRZuYRd+YRiOYRmeYRquYRu+YRzOYR3GYVDQV0UoYb7NAQyggR0uYiM+YiROYiVe4hwOhnZVAwRWAwl4gGBgYiu+YizOYi024mSYgeJFYEV4AAkAhS0uYzM+Y/80VmItuAwgjltZ+FtcsApNAFlgQGANgAAOWBI93mM+7mM//mNADmRBHmRCLmRDPmRETmRFRuQqCAAIIGP3dYIKCIBFrmRLvmRMzmRN3uREtgMAqAA+QGA+kAAAsANOPmVUTmVVXuVLDgAJgAIE7uEAmAJWrmVbvmVc1mQOgAANQGBguFyoqIpOcAEI2FvpRQYKgIASyGVmbmZnfuZH2AJHbgQERoIKSABozmZt3mZMxgMAkAA9QGA9IGU84GZzPmd0/uMEkAAkQOBGgIAA2IJ0nmd63mYSaFcEroXLXVmq4AXxDQX3pYXL3QR0OIeCPmiDTmiEXmiFbmiGfmiHjmj/iJ5oia5oir5oi85ojN5oje5ojqboanDZUHZfEPiANPhoj05plF5plW5pln5pl45pmC5oczjdKEDgKHBdc0iHmZZpn+5poP5poQ5qok7odEiD2UVgv4UBbChqpx5qqH5qqY5qn55jCGBa6Q2Fun2NqjDdCoBi6R2EDn4M8CKCDDBe6e1eGLgFCaKDFbgAYpBeYpBVOpCgEIaA7fVcHsgAIpCgaJCBCCBf6VUDCmbeqHDeCjBmviUGEVhg0r2bYYYAgPZcJ3DdAOGfX4iBCBhpyjUJ65Wgb4iBC3CCNs4JUADe78WuAhaBuKbcWpDV9DWLa4gBCfCB1o5bLZCAGAAK/wkShyDIABBQbLINhL8NZgkqAxagAA3mW1KIgBUwAxTSBGIOBMqlBRDoWgvmH1+oiSygXGLwAd2+BrTghLxtBbKtBSe43EkgWNEGgcnOCWJYAwhggTF43PjZBiD4AAogBCBGBkKgAJTwjg4qhzFogQdgg9seCVAAAQyIgett67aFAqzOiVbIgepN7bNQB0qwDAiAAkQAhVBQhORNWTP41Q7CBRnIVx8IBBBnhDUAAQEugsvuIGgAghV4Vj1wBFFwBD2gAecGgg8G7SJoVg1YA0YQhU8IBCR4ANCI4xkyhzhwiwrgAkUABVAghCiAgAs41h1RC08YVgh4gDDHgBWQAf9LmN8f+oUg4FZn1dcKYA05yG4UygYxcAHz0Nd2LVYxUIkfEgdh/YDLiAAxxgAXCALe5ixLiAHcwHOxaAEZ4Oe92AZLsPEAIIAMkAE64PMqEodOIAIYqPQIiAEzyF3CygUxkAEGMAAGiAExyIXHnpxfMAPNJoABaI1OkHMbugY6SNoBGAAVAAJLEPC/MIddsIIqeAX7JqxqsIIpYARcx6Jt+AMq+ANhDydxYAQqsIJq6PJwKodXsAIr2AUTn06ifARiKE4erT4fRVIgbUQhHUUiTfddXPfTS9LKW9LVa9LeIVPEMdORqdAcDdF8kvd+pPfYs/fPw/fa03d729Lr7FL/hE89hT8+hr8dGd1LGoUvL/0nMP0oMVUpgs9Kgx++iJ+9id++io9Ehy9JBlXKck/5YazSYrzSmMzSTZT5iKT5nbT5Ulz5oGz5snz5eMf5jdT5qeR5Dwt5xRz56yv54jv5BoR5jiP6mzR67UT6vfN5ygR6yxT6orr4/Mx4ANt4hep4vUG7mOH3wvF3kAH4MBX4+7ROlof4dr/Ed2/FoU/RV09Ap88+qD9DqU8dsJdQsZcwsqcos78btHeZIu3RvR/Dvl/Avw/GwA9Lqn9Kqy9QrBeiwS/Twteww/eos/94ulF7wWH7jnF7j4d7h5L7n6f7BlWvyo87pXdNpuf7ug/F/7uHx7w3t9uH/Nxfxd1XyXjX+uDk+uH0evK8fLXM/Bbd/GvUe+cPUujPPOOPTuQndwftfYF7/F6M/DKc/Hycfc/p/H7/fBYL/cSnm8VfGdP/G9THGNUffdbf0esHz+wXT+U/KPNfe/QHiHUCBxIsaPAgwoQKFzJs6PAhxIgQpz165E0iRofeKk7L6PEjyJAiR5IsaTBdRWMmV7Js6fLlS1WPVMGsafMmzpvGKqbL6fMn0KAMKVoUanDjo45GlzJtyhLlI5VOp1KtClGmJKtat3Jdt/NRz65ixwYletEpUqVk17J9CVVq27hyR8qkOfcuXolfw+bt6/eg2alp/xIu/P+2MGK/kmYmbnx3r+PIbAOj5Sj5stjDmDdrxcr5M1XIoEcbpdx0MOnUPzWrbn2zruvYNUXLrm3SNFPUtneLZM37t8fFdoET18uzOPKHuJfqTu4coe/n0gnCnm59IO3r0pcbba7defTvyT2Ll569fHHuQr2jBx6+/W/h8JOfn79bfVD29mu/3y+7un+81Rega/gBpR+BqvWXYGrkMSjbgA+OZuBPCEr42YIXcgaghqlF2CFmFPpkIYiSZVhiZPKhONqHKzYmYk4kuojYiTMW5qCNl7WY418w4iQjj33VGGReHBKZ2I5H3uXjTUAqKdeQT8alopSFJVnlZBWddZplWP7/FaWXYxkZ5mPHkZkXkzY5eSZXYLLZ2SNZvVkmWHPOlWZNa9pJlZt7OkWln2tdGahTeMKkJ6FL9ZmoUGMyqtWgjwpl6EuISrpaSpd2haOmVUXaaU6UumQpqDYtWmpNjqJq1KerwiRqS6S62tKps7IEqK1CtZrrSrCyJCuvJNUaLF1xEqurmcf65OtKwCr70bDPeqSqtC7tWq1HzJrkLLYRRdstRLiC29K1406kpWBdmktrpuu6RK27IZUb70LalsQtvdC1m29JnPIrb7L/hmQvSfgKPNC3Bw8krsIYzduwQASPZLDCCTcML8QNPQyxxCJRfLDFCvubMUQbN9xxSB8L/xzywRiTrJDJCqMMksr/siwwwy9rHLDODs38Uc383vzvyD0vFPPBP3sUdL5D8+uy0QUhLbDSGTFNr9P55hw1QlP/WzVGV8ebNb1Qcy2Q1/yCLZHY7pIdb9FnG5R2vmtH1Pa6b7u7tdwE0U2v3RDhba7e65p99t/xBv7Q4OMWbm7cfWPHs+QFLa6RupWftK/mBh3OdeLuXt5Q4+A+Pi7flYe+7ugMld7t6eBGrjrlna/T+kKvYxt7t59Hvbq5uCuke7W8Y5u65MCPK3xCxEtrfLW+G608uMwj5Pyz0Es7e/K1d279Qdgrq/2zyPdNfbfgH5W57QKRr6z0PaOPrfoFif9/7PvHcn++95rXT9D9iJU/YsVPZ/Or1v8GEsBgDTBY5pPbAaWVQIEskFcN5NX+INi/yk1wHRXM1QVzVcCXRfBZHfygrUJoqwciboOSOyH72qfCWY2QZCVUFgyT0r6CzNBVGWxhnXY4kByqRYg9XBULQefCvhFRiAjjnBBrmLEbHquJTlzHEVH1QyUG0YlWdGIWSyVFiFGRWF80IhR3mMTfLVFuZ9xhGEG1RTZ2UYhvlGEa2zfGhpUxWHe0XRw7tcbptfFsf+xcIDW1R4X1kVeH1FwiLzVHQtZxh4+sXCQlNUj5FZJrl5RcJh+1yIM1Mlef7FsoGTVJTlayfaeUWyr/EzVKgZXSVq88WywJtUkDdjJqt+RaLgO1Sl620na/jFow/TTLf9VyVsc0WjL3tEsS9tJoz+xZNO20TH4101XX1Fk25zRMahbze+iqjA6vGM43TdOG1ezZN1+2TjZtM1/dXFU8STbPM43TneX03zm5lE4w5tF29aTXPVGVz4ztk0ztnOI7dbZQiDU0TP2E6D85GNDcxBCQBe3cQeOV0FJNtGEV9dJDyRjRl5W0Yh/VXEjdNVJQtRRkL63cRVWa0RdulDkdReRNJZdSPq6UZDVdWVD7FtN1zbRTR7VZUuWWU6LulIk97c5PIRnVsy3VXE3V1FOFtlWuDZWRRc1YWJs2/9aoTdWsVXXjVdeTVUyu1WhdHddXL5VWrNW1Z2Ul5Vk5Ftf8zBWUfdXZXcGVV0ntdWyHfVlbAftWQw72QIVF5WNJ9ldaBvZkla3QZWGZ2YwltluLfVRj3TZaiEWWs5P15GdHFFpcrvZijLmiVzors9jGaLbArK3CNstM3SaNtz/yLTKB2zJj4fa0jEpt3pQrsNJiy7mJgi7hpPsv4XKTuFQzbpOQC03tPu22V7QuobDrOPLmq7XDfa0vwasm8WKTvfTirj29+zX55om+4LQv3MzrRPQGSr2mA7C73Ntd+FqTv4fyrzwRbDgBC5HAfjIw7CRsLvwiVL9qc3ClIKxPDf+PS8H5ZTA8QTwqETOUxLKj8A4tvCcM787F3eKwSD1cNxXHisUUtTG2qFstGduJxsUDcvSYe14dA47Hv/KxSZEsLRzLlMmKc3KzoOzSqOB2HUKWFpHnZOTnSflZJu4wiiWK5W1p2aZcxu2XnxXmN405e2VWFpWZamXRrflebUbqm6945hynmaV9LtifoRpoJ8ZZWXNmU53Hd+dj5dmre2bdoSeWaLEuOoowbt+jzxRp/E2agEoe8KWDl2mPbVqtnVbjp20XajKNWoClDlajjzXrMNWagbfG4KkrnOrlrTplrebrq/UY687t2ku9tuCvc1VpvA67esWm2bEdm2yDBjv/xtVO37WBlm3Vbhuky9Zcs7H0bBBGe4Xnpl2hjRrupY07uuWG6bu7F2+0zttq9c7uvXHabVB/m379Dtu/1xtwoeabf/sWbFHQWUQ4tpuGDdfgwz0bcYFOHI8LV+rAZV1wBB6cbQk/8MelenEg8sWOJb/byTOc8rNNW7Ejl+DLBRfzGs+ca4OucsZ3u3GODhSNPWfryrnYckvmnHE7P/LRjVZz097chE3HXNEpHvWe5ZpY6a7SulNYcR+GnNlVx+HVSfd0Mm9dZ1Ov7tmrmHbXrd3ObYds0um4dFfOPXd1l/TdSfZzPQe9uEP3adY9DhdG552Sezdm34f3d1IHPmNv/x9y3M0Y+eZN3taVZ23Z0Z15P27+ep339edtOxxUF/67h8dq4j2a+uA2npWPN+fr5Rp7oM5+uasXduv3m3vC7l6rvZ9u6OF9e4AO37LFp+vxt1t7Yi5fo80H7fMNG/3y/t7bwf/w9WWbfcxuv73J13f1eRr+3o5ftOUv2/TJmX6rrv+47aft++N1eTCP3pGlD9/pQVv+Jdj5Odz8wVX9hdf9/dYATlj3Edz37VgCztcCJlcDblj8+dMBUtYE9lcFjtcFllgGYtQGwlYHPtgH1lcIvpicLFkENtkJhlgK/tcK3tgI6lQJxlcMsoQ5QEMhkAAJwIEvlAMcSUMnlEAHaP+BLoiDEGkDLhwBBxwBLmiDEImDLmgBB5RAJ0hDDpJMOfgCHJBACRTCM3RhSZxDLgRBDHwABEBABsAAEHQCEWrOL4iBDLRAG2IADMQAJYBD51xDHMQADFAABFCAC8RAHFxD54ADJcAADGAABERAC8iAGPxC55RDJwABDLAhBKgADARBLpzDT4hDGcBABkTAA1xABeQhDIjBNkiOOTSiCrQhBVxAG0pACwABNFTOLciACkhAG14AIUrACsQALlTOMwBBC0jAA0SAKkKABHwADFCCOUjONhTBIz4ABFTAKj6ANJoBE+KEOBRBC0RADSiCLSRDMgxDIyABBKwAELwiLsn/AQxIQAgEgiyoIzKEghZAwAfIgCXKDSc8YgW0wSkggzqeQhtQgB5yQt/8whpCABeIQjGooywEAghIAAzIgTrIzTYEwSwiQSMMQzIggy0owg1AQAsUQTjWRDqkAR7ugTGoI02WJCK8oxjMYdRoAgw8QBQQQ03SJCloQAYAARVyTS/EgATYwCwEpTrOgg1oZC+cjTYAQQZogCg4ZTIQQxRAAAxowtmUQxHMIiIgpFO2gSSaQUfWBC/EQAS0gVbSJCF4ZSdwjTYoJRKYpVaeAjHGAdeUQxB8gAgAQ1wmAzCIwAcEgU72TBysQAScQmEiAxJUAAwcpdF0Qk8iQknGJVrG/wAv2AQRCKZeaiUy/AAGyMBivswkOGZTFmYytIFGSkPU4AIMQIAjuGYyOEIEwMAxGo00yIAE6AFuykIErMAkRE05yAAG5KVrIgNiFkFNXEM9BgJu5qZX+oLRlAMQYIAUVKctqCRYGk0ZiGZ1ImYZ7CQe1kJ1SgEGAEFqZkwv1KYjjKZTIkMgSIAMKOJL5EJPrkJ1EoMbvgE1DCiBFqiBHiiCJqiCLiiDNqiDPiiERqiETiiFRmgsYEAEEEJ1JsMNYIAQVCiIhqiIjiiJlqiJTqgzYMAFgAF9auUXYAAGOMOJziiN1qiN3qiICgEG1MCG3uQHxAKOBqmQDimRlugbfP/AAwAlbq6CV/amS3ACHgrDhmoABHBARVwplmaplm4pl3apl34pmIapmI4pmZapmZ5pmVpBADwAKGyoE0jAAaCpnM4pndapnd4pnprpHQCABOzBhvKBBACAHeQpoRaqoR4qotLpAUiAE2woKDxAAFhBok4qpVaqpd5pB0DABWwoMLyjQ74ElEIAYVanLZLApZ4qqqaqqj6CmkJAm1bnZCLAqs4qrdZqne5pcG7oHgQqHtiqr/4qsHIpAjDqhn4CBATAFQSrsi5rrWaqBnCqStblftYmZOJmp6qAIHSDtm4rt3art34ruIaruI4ruZaruZ4ruqaruq7ruXrDLqhABAz/wobOQAY8AbveK77mq77uK7/2q7pawwdcQBdsaBdgwAdYg78mrMIuLMM2bL4+QQbMwIYOQifugsNeLMZmrMbyqyDM4qi65ik4AAzkAkxkA3DyQXUqglcGpM6YQxBgQKPi5ixEa9TEwQeAwIaCwAf45WXiIS1UpxO0ZzX2DERCwCJUJx9QgAxYpkuIwc1WZGTmAAYoZtRYAh76p2uCAX5mQ9ToQm0qAm4mwgPAgC5ETTYopRosqUpaQtSYg1XmQIvWJDHorBjYxC/U48AWJh/sppP2zDYo5w1ArVaGgkrSAdeYQxF8gAa0plbOggZ8QBGIYtTQwQq4amEWg9TKwDdw/w1tQgDKxiUydAFlsixMzEFtdoGS1iQy6IFKlsHQRs0t1KMPpKNTKkIFJObmcg00xAAGiEC1BuUpiMBp7iLXfENgVsDROmUt+IBGesLZmEMZVC4fCC5NEkMXQIALzAFOlEMZuIAEgIAfnIIwDMMqDAINqCQR+OHZqEMjSkAFrIEo2AIxyIIi+IA/AoFsyg1/QmIWOEItEEMtOEIWQAAGxADJyk00AMEHRAASKIIsEIMtiMIacOM09g04EIELRMAMDMIqDAMwnEIfgEAEuEAZvOdLlAM9fgAwtiE0viE4So46dEIMrMAqsjABuwARcK3k9IIyYoADRIADBGMuYqfkZP8DETwiKrJwBayADHSCGfILKcKABlDAD/9wNMIAHZhwTfiCGMxwAzRABsgAEejCEwuMNAQiDDSAA1wAHMrhIk6CDMQABARxDMjAJORu5YxDJsZABTiAyCJi/mKSLhCBDHyAH6tADFTiUmQDJqDACRgCFwrRN+SCI7PBM7yu7YhDLzTBCTRBL7Sk7ZjDM7SBCaRALuCx7aiDNBjCCaAAJugw0XWc7C2epz2gyL3gle1gj81ghNVgkN0gVZWxvOnyk/HyiPlyktmy2eEynxFzlhlziyHzlAGzWwkzvzkzm0Hzj0mzmRUgxlkzxG1JLOPWSWFJ1wXL10lJ2M1KOVfJ/sn/Wf+Z0v+tjzZHGTfDDzVLFjhrnDgjnizzHi3v0OBZGjNjGjb7WT1vWUC3zzs7Wjzb0jzbTwCy2z3rTz671j4LXT/D3j8b30JzWwuyXkYb3kbrXkdD30ebmzKLXkGr2kEjWkK7WUprTkPr2kM7U0QD0ESLXUWbWkgD30i7XkkT30lr30wL3EorH26ts6u0s5TUtNfdtDfltALtNDuP3aqcM6+k85Mw9ao49ZMMNLW1NLG9tKbFNKAdNcMlNfotNVVTkFU3NVZr0UW/V1AL31A7X1GTn1qD3E97312DX15j3167X1+rHFsboFubNauhtaIdNs3V9YIFtgQOtvgVNv5B/7bPeTPLLbZlsx9mM6BmI11if7Nnp4tjc9poS51knxhlw+Bn219oW+Bqc11ro9lr53JsK+Bsg2BtIxZnK91pSxw5z3WpQDU6SzU+vbUHxfVXG7cc3Tah5XYz7zYF9rYK/jbe/TUEUrdBW7cHYjcNarfgSTfQebdLgzcKincvk7flmTfhoXdZq7cMsvcxuzfocfcty7e1Mbaxpbar4bfqdRlXK4lXowpYKwlyb7VyKxRzo9BV9zSuwTdB8ze4+Te2ATiyCbjIBLfeDTfHFbeE88qC50qBH8mBl0qCH4lWm3iDk9SDOzeCQ3eniLXNkXV/0/eKabi2cbjvEfiL01SM8/84ufk4zlD4WFu4wWG4uBG5vRk50Xi444H4OKsTjSsSkt+4kpMck9ObkwMclPNLidvKiRNJioPKihNJi5N5kDvVkNt3NIe5+en3Mm85znW5v325wsn5fWU51eH4hev4LsP5NvN5gJV2Z1/RmXdKmgeJjf+5nVsdniOcnqOcoRMgogu3or+5iF/6uoz5rJR5kCy6pjQ6jzw63AH6kgt6MRO6PXs65Ph5qkc62k26yVW6zME66sg65qk6l7P6M7u6QnfZmod6m4MVp1v5iIuQlNselftzp3cZqLuKqPMIqV+KqedIsVP7setVshPUstsKqvc6rcudrcMcrvOcrr9Ypn//+Kafu86lO9Stuw22+5S/O7Bns7DLNLE3O/U9O0dHO5zxOv/5+p3nO0Lve1pLO8HDs8FLOsLDtMI/dr/bu7PjO2pPvGr3O52zdLlrHrw7nbyzHb0fT8M79MPXesSftcYHeMUDecqb+8o3dstvOMfD/MeTXshjXc33+Ms3V7cz1rcbXclXy7SvSrXnyLVLSrbbyLgXfM77386r3cjbXdFvz8nbdMyD/Mz/d88XOcNb/L9jPHEr+9V3s9jLH8CbtMALmr+rPdmHuNmHPc6vPVG3PeOlvQbavV7jvad1vFLHfZWD+9njs96TIN8Ttt/D2uHjYOJf9uIrG+C3teBD+9wP/3zjB/Pjg3bk287Ro0rS28jSP0rTz8i2I33Qo9bQa13hW/TkK3blB/zlX9Hnl0roz8joM0rpu8jpg37qP9fqK97NA/3W63zXZ/jXP/nPu2DUy/PU013VA17rE0vtg8rtu0juJ8rur8jTO3zzQ/Tz+130U970T3jmV/Pmy3bnd071d8r1r0j2E8r2o0jv2/7vX1fwz/LwM3/68/b6A8Q6gQMJFjR4EGFChQsZNnT4EGJEiRMpEpT0SFVFjRs5dvT4EeRHY48epQt5EmVKlStVTiPpjSVEbySnxbR5E2fOlOlIGtP5E2hQoQhVYRx6FGlSlSNLKnX6FCpEl49gKp35qP9mVK1bt/J85JNrWLFIi0oaexZtTqYm07Z1G3Jq1aRXs761e3eiV7B4+fZdWDSjX8GDB64lfLhvXKd0ETe2q9dx5LYXA0u2HNbwZc1RFVuluRm0U8ihSR8tWxp10MypWdvsPPdza9krR8+2fRLwbd0gV+/2TfE1Usa/iUusXRx5Q8rJmTPs3Rz6wOBHh0e3vu74dei5tVt/3h359KHVwSfPXr74afTMv6/fLV4oefe+z8/Xvdw+8fb5ZcMPKp+/2eoLsDXuCLxtvwNL8w8oABVEbcAHSVNPwtYSrFAzBn9yEMPNIuzwMgNBJO3CER3TUCcOTYzswxUbw8/FzUqMcTD/FHNSkUbCWsxRMAp5jGzGH/GyESccheRrxyPvElFJwoJssi0ibzISSreSrDItGLH068ktxZLSJiq9HOvKMcNi0sy3ukyTs5cWi43Nt8qMEyof6UxrzTuTAjMmMfUUrac/JzNKULTyLDQoPlnyE9Gh5mw0KDQhherQSXFSdCVGLdXp0U1xstNTpSoNdSVMVdKU1Jg6TXUlSVlVjSS2Xj3K1JRQnRWlVXENSctdgRrV145qRenWYD3S1ViOQE3WJmCZBc5Nz7B6NidkqZ3I1WtRclbbh4Y9qdhuI7JWXId6LfckbtFV6NuQwl2XIXLhTSjbeTVS196C2gXp3XwPktdf/4KWDZgifAne96N+CR4I4IXPXXgigwNG2COFIW6Y4HohdkhifynuyOKFMQ544I0f6jjfjzkKmeCR/dXY5IVQtlfljVgO2OV8H46Z41h5nqhmjW72N2d7S/5ZoZnnDbqiofMtel6YkTZIaXiZpshpe6GGd+epE6p63asnynrerdeV2uvCfE67IbElIhtes9E9mm2CwEbX7YjgXlfucruu2+61AU8ob5ngHPzfQBGnl9DFD7q73MIf2hvdvsWle3DIxZXcIcrLtbxbtNnWvFvOG/JcXNC1/Rtx0rU1nSHUu1X9WswBd/1a2BeSXVvaqRU9bdyp1V0h3q/1/VnWMxfccf+CiE/IeGqRZxZ4r4V/9nmEon92+mRtr/t6ZrM/aHtmuzdW+duZb16g8Q0qP9nzg61+6vCTdb8g+I2V39fvR1+fffgjiP6Cxb9d0Q9p9jOWAAdCQF8ZEFfpAx8Am8dAgThwVxCclf+CR0HHWXAdGMSVBl+FwJ8pMFggFOGsSMgqCf6vKexzXrRgMy0ZMkxxNxSICXmGQl+p8HAybGGqOGg9Dy4OiDbU4RBJ9cIOxlCHSazLDZkYKh7GzIe7kqIOBVJFTxWxfkdE3Ba56MVNXdFkWcQVGZeYQx060YhQvCEbqejGG4IxgWIcHB2FaEcZonFjapwVH9lnRkvBMYxylCH/IZtnyEkBEmKCfBUjHedISOHxhHoEHCUXZ8lGITKPigwgDYUTxEL6kX2QXJgkWcVJxHkSUZjsoSbr5srBwbJQqiQYK1NlS8DhUlCgzKQoK0hK6piykahsniyxSEu2+bJuwPyTLgPGS1JBk23S1JMwZ0nMDxpzPMispDIdR01/WTNU2EybNu/EzDQ6M23q9Bo76cTNZnoTieCMjzg7Sc7FmTNf6PSUPKdGzzi5M5Dw9BpBkWZQNgHUXgLdFEN/5tA02fOd+ByjPv/Dz1f6E3EIjaRCp0ZRnlnUTBCdl0QtZdKYoXRMGE2oRvfI0QZ59JYgHZxK4cXSSbnUZDD1kkhX/0lSpAF1Y0LdkkxHStNN2nRDOP2lTgHH03X5FFJIvRhV60bUXRr1Z1oVGVfZZlV0YbVRYm0ZWdPG1KI6tZZQTZFUo8lWr3m1mmDlmVpxZtepmbVcaEUUX4nmV6S59atwfaZcb0TXbBr2Z4AVl2ALRdinQZZneD2nXmNmWa1hNmaIzati48nYIjl2naA1mWS7RVlBebZsqt2YZgPKWZPBNm6yhRhrteXaP+GWb7p1WON06Fs9Abdyws3YI8zCxXUY907I/ZxySUbcG0KXThYUhyuWoIRMfEOH5fgFE5QQiGwsMRphUEIYoiGr5qkjG4FQAhN+UQ4dbiMTSliCK8RxFP9pxAEGKigAAzIAgzL8onnfmIQMYFCAAkhABkXIhXsBJw5OBEEGDWBAA2AQhE70t5O5KEIMJMAABsBABpTYRvOeUYYYZMDEKohBHKQBlHRYQgYrkAAEeAwBCagABnOw7+ByIYMWYKDHPv4ADMQA3sFFIwguQHKSMdDhaCBuG2OAwQck8IAH8BgDLZBBLhBXDjlsecc9rsAKZGAJCrMkHQCugATU8IlVtAIUbdCABFwwBhCzjRMwQHIUFHEKWYjCDzSAgAqCoA3A+UIGH4CADwhRClmcYhBIeMAHZOALwGkjCC2AAA38IApZoGIRUYBAlTlR4TG4QAIaaAMoZLEKR4D/Yc4wkMObVWIJGEAgCbZARjKITWxieCECuuZ1zHQBAwnQgBXFLjYyArFoIvx5ateQQQY0AIphSxsZjtAABmRwDbaJowiSDsS3pb0KGkgABrpgmzrk0IIHfGEY0ia2LZAAARhY4ibQcLYT2K3vZKjB3/L2mjiAgIEZBMPgxEaGIiDQAoDPcwwquMAqklHwYq9izWNY9sYsIWpFRJzYwaABBoCA7Z81GwJrQHnHoQBvaNikDB/QADBm3nEaZCAII1+YJkR9ip4nQwsVgMGKp9aLXw/i6ISIQAx64bVtxKACWjh6KR7QAk3MMwgfoIExeg4MDaigDDHZhgwk0IajIwMR/xCQwc0bGgQMIOHoyViFA2DgCa/JQeMeNzgyLqCCOXjNE7+O9tGRAHShB0zgEUBE3tsggRgwXSUwL0Xea7HoSpAD9KEX/ehJX3rTnx71qVf96lnfete/Hvaxdz0zWhCBQOQ9GSL4ABlk33vf/x74wRf+8GEfjiNnAfdZCHM4iN985z8f+tH/PRkyMAPBGzwQEmgBM6Tffe9/H/zCr4QKHmCLvJfC37xgSSdEbf68VwACJCDJ/Olff/vfH//51//++d9///8fAANQAAcwAK0gAB7gE3APCSoAAQjQAR8QAiNQAieQAgUQDwBAAvQA9/RAAgAADyoQBENQBEeQBCEQAf8kAAmuT98cAQICYAtKEAZjUAZncAJJ4AEuAPdsoeI6gSU4QdSEAfc0AAI4gAaL0AiPEAkfwQAhABRwzwkkwACSUAqnkAoj0A4AoAL4APf4IAIAwA6qEAzDUAzxLwAqwAlwDxRasArGkA3bkAo5IAI0APeCoeJabSVwQdQ47uiIYdXQYBn+EBADURAHkRAL0RAPERETUREXkREb0REfERIb0RTgb/Ly7gYwAAciURM3kRM70RM/ERQfURkkoALAAPdwTQKUIRRXkRVb0RVfkRNxAANuAPfirgJSARZzURd3kRc/8QwyAALI7uhWwd/IbCWkgcSg7ujSEAbUD2nKIQb/MEDrjg4YKu4SvGYMxA73aOADxsBrLmEFIIDnjk4LyG3IfoYXYOABmvDoBsHfrmwl1CEIMsAGVLDYoIDcXC5m5GAFKsD9UI7apo7ukCbxIIAUji4U/M3vpkbgIOD2eq4WKsDwFi4ao+DtbuADgkAdYiIXfu0hUY4FvS5tpIHtLHLmWqHw0m7hGq4GiGHmiKEGWE4fTUYdykAFKqAVei4KKkAGauwbRc0Req7aYMAYWcIcxiAcCeH6PuECPuDa2IYSXCACwOD6VkEEyM3c0iYXSAwJxlHfgAEJLK8op4YkMWAE9FDfkAEMIMAFKOHciOADKoAd05IQIGAFxuAcbuIb/4IgHJMgFNjtFLQAAj4ACLIybcyhDKSyBhjBJYlNFtrgAqpM4aDS2UBgEGqh2GphEEAA3tyybnQhGiugDWTh24ZhEWwgAlygDMyhbq4BCCRNC07h25AhFJLALoMAHHJiG8RAyiLAAkaABi7Ax1wgCHyybsoBwCQNAmbgBoRQAtjMGaPpEraMAhwgBGwgBHjsA2JAEx7PZHghxyggAi7ABkQgAiCgwOTgHNlGGqIM/i6ABmigOjHABcQA83BiHDiBwVbgAz5gBWAgBixhJucpF4IABvjTP11gxhxtcZ5BDGCgBfpTBcRMDJ7BcbIhDmTABfhTBVYgBoJgwhYHHCwhBq0CrD9Z4AVkgBMG1CbEgRcmIQ7MYBJy4T4XR7wsIQ7KgA464bwKKRo0YQ7KQA40ob1kKBs6gQ7KIA4sob5kaBtygQ7MIA4mgRdY1LmuFEuzVEu3lEu71Eu/FEzDVEzHlEzL1EzPFE3TVE3XlE3b1E3fFE7jVE7nlE7r1E7vFE/zVE/3lE/71E//FFADVVAHlVAL1VAPFVETVVEXlVEb1VEfFVIjVVInlVIr1ToCAgA7" style="margin-top:1rem;" /></div></details></div>
+```
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">ChemicalData["Ethanol", "StructureDiagram"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhBgFVAPdkADAwMLq6uiwsLNPT0x4eHo+Pj9/f31VVVYyMjICAgFtbW0pKSi8vL3l5eZmZmba2ticnJ3FxcZiYmNfX18jIyLOzs2dnZ+rq6j8/P3x8fHp6eo2Njfn5+aurqyYmJoODgz4+Ps/Pz0dHR9bW1uTk5FxcXKqqqsbGxkFBQdHR0WVlZYeHh0lJSYKCgu7u7m9vbxMTE6+vr/b29lpaWsXFxVFRUZqamjU1NSgoKLy8vNnZ2U9PTwkJCVJSUiEhIV5eXqenp+Dg4MzMzFdXV3t7e5aWll9fXxUVFf39/Q0NDVZWVtra2qysrIqKir6+vuHh4RAQEPT09BcXF+3t7R0dHbKysjo6OhsbG8LCwisrK9LS0gAAAAwMDKOjoyoqKjs7Ow8PD+Xl5XR0dMvLy/////X19UREREJCQkNDQ6SkpFNTU+np6TExMcnJyYaGhjg4OP7+/qGhoX9/f/j4+Pf393BwcGtrawsLC4iIiOPj4wEBAWxsbLe3twcHBxoaGi0tLRwcHAMDAwgICMPDw7GxsRYWFqampnV1dejo6N3d3a6urkhISDMzM2pqar+/v+vr6wICAjIyMsDAwGJiYufn5/z8/FhYWAoKCvPz8/Dw8F1dXaioqCUlJWBgYKCgoMfHx/v7+2RkZGZmZjk5Ofr6+qWlpZGRkQUFBc7Ozg4ODubm5ikpKVRUVJ2dnWlpae/v7wYGBkxMTCAgIEZGRvHx8VlZWZKSkk5OTq2trSQkJBERESIiIh8fH7m5uWFhYTQ0NJ+fn3h4eLW1tZubm4mJiU1NTX5+fi4uLpycnMrKyqKiotjY2BgYGDc3N97e3uzs7EVFRSMjI+Li4hQUFLS0tNTU1I6Ojri4uJSUlBISEtXV1bu7u21tbfLy8ktLSwQEBLCwsHd3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3dyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAABgFVAAAI/wDJCBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJEmOvKSVTqlzJsmXFKGK2FHLksqbNmzg9wklzZQsaWVvUOMtJtKjRowLbvNliZQyZOU2S9CGCCanVq1g9qjKyBZAhOAQpTdLjpwuSrGjTqlVIxw0XQXKiIBTyZcubNmvz6r0KR5GPLUOCLIQDBNCWH2H2Kl7sUsuZLWywPCwjh8cdN3QYc8zDhIlThUE6C9F89FEjSIWQVZL4xNIWH4rAkr64acuWTgs92Q41OycpU1BOiclkEUukLWe09K5Y+3bu3cttXlu1pdiSjJVaFYLk6lH0iM1xK//UvYX395VLYm3x0qsjrUOnoJgidb5h+Ofl65fMJCa+LfofLXHLFqtco59C940H3YEgVYLMdnY8Q1IvXmwRy3UMFpRgQuSZlyFHgxyHhnIpkWKLLsIR9yEZGyLU4YoaPTHEFruAI9tKz9iBmmoftnjQizBaRJkgXOAxx01aoLFFJINk6KNBQAYpERyGGOaLKkTBAc4ugD1xYHOLSCLmmGRKEsyCUkJEF1OfGTUHHlzwIEcZ9TVn25145plfmg5R4oseXt2IlCq+bEEFEILOZqeejO7Jp0JzEJOEIMbIlVYyo2zxxWjLNdeMJ6CGKqonoaD5qEFwEBINYILlBUcpgOj/MQklvTVnCX4enkpQNdBAJtliURgjSBJNHKmZrbjqStAUewSS2mqkBaHEFrlUkWheyCro6KmgYJNNit9hwcYWs2izWLYcmsrnNllUh+F5lQxzRCDcoKQXui6qG6QkXBb4IX+nJDGEsWrh+6O+H3YTzjd6hAPgijoAlUUOaxkMJcIHIgEMM5A0MhSfuOCwRQ2JpGVxQVF+SMMvyJF46m9QwBJMN1mdTFDKA2Giibm95THDazFc++gjrkDCjCdnWWXzQDgnBUMgL7igmQwtXHLHCpkpa1AKKGxxwwkfuvDCNzAUAcpecJjAyxZGJKY1Qn39VQIJH44gwhZ/OJFXCCDY/4XX2wu1dcclH8iQIRzUeLBFDx9jtYYKZKWRNOAMhfHDFrx0IHR0HGwARh8a0GJV56n0kUFVlEPURjNbYBDChxdYoMc3GkyekzCKs9J46hAh0YUfkIhywYcV6LJFMxTkNAELWxxDE+8VYZJBH2BYw8HhHayNWE2v1PHNNBJAC71FzrCyBQQPfCjDB1Zj9hAih7wRDTOcvNHAGhBVIsE030TwyvgbkQQDtrCAZXwoDwp4TWwWIgRONGoLHkBFQxwxwEVMAIAdqYQD+Oc/lbEMDVk7iCj0pAc9uUIhcKgFBIWBQZC8IgLfc4D49KMxOySEebYJxAL4cD06gMMMkLhTMf8UkgAEXK+FIVneFhggCV0Z4044wJ9BpPEX2+ABiTgRBgS2cAAD8MkZJVySQpAgsi1AAhFYvAkHrAEGQWTAUjBS0hbuEEKE0KIPttlBGnESOz1cIQ2b+w4HgriFAjTkTFv4hu326JIQYGALo0jGh1phmz44BBSBsE0VGIkTOGTvNlg60Cxsw4aHrGoLt+IkTtZ3CS5gTT+5sM0eHuIavKmSKCQoAY2Cdh4p2MYaDwmHbQhwy6Kc4AY+GcB3UmEbZTzEGraBQTGLgoQ4cCxCyymEbRDwkAzYBhDTNEo3GgALXXyiN7HcwiwdwpUlhvMoiQgFnWZjBttE4iEV2sIt3smsT4XYoJIOQcIpNNnPghqEDmG0RUMSYJtTGPShBOnbFrhwxIRggge28QZEN6qDMN5gIe1KpOg2ClFh2kYA9iqIKk65hQyQlKSPsc03biGJsyAhACwgJGBe+tLL5UmndyoBT3lKgyoyahcBGKpSpfECRsjiCAQAwAsuqNSqWvWqWM2qVrfK1a569atgDatYx0rWspr1rGhNq1rXyta2uvWtcI2rXOdK17ra1a0BAQA7" style="margin-top:1rem;" /></div></details></div></div>
+```{=html}
+<div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">ChemicalData["Ethanol", "StructureDiagram"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhBgFVAPdkADAwMLq6uiwsLNPT0x4eHo+Pj9/f31VVVYyMjICAgFtbW0pKSi8vL3l5eZmZmba2ticnJ3FxcZiYmNfX18jIyLOzs2dnZ+rq6j8/P3x8fHp6eo2Njfn5+aurqyYmJoODgz4+Ps/Pz0dHR9bW1uTk5FxcXKqqqsbGxkFBQdHR0WVlZYeHh0lJSYKCgu7u7m9vbxMTE6+vr/b29lpaWsXFxVFRUZqamjU1NSgoKLy8vNnZ2U9PTwkJCVJSUiEhIV5eXqenp+Dg4MzMzFdXV3t7e5aWll9fXxUVFf39/Q0NDVZWVtra2qysrIqKir6+vuHh4RAQEPT09BcXF+3t7R0dHbKysjo6OhsbG8LCwisrK9LS0gAAAAwMDKOjoyoqKjs7Ow8PD+Xl5XR0dMvLy/////X19UREREJCQkNDQ6SkpFNTU+np6TExMcnJyYaGhjg4OP7+/qGhoX9/f/j4+Pf393BwcGtrawsLC4iIiOPj4wEBAWxsbLe3twcHBxoaGi0tLRwcHAMDAwgICMPDw7GxsRYWFqampnV1dejo6N3d3a6urkhISDMzM2pqar+/v+vr6wICAjIyMsDAwGJiYufn5/z8/FhYWAoKCvPz8/Dw8F1dXaioqCUlJWBgYKCgoMfHx/v7+2RkZGZmZjk5Ofr6+qWlpZGRkQUFBc7Ozg4ODubm5ikpKVRUVJ2dnWlpae/v7wYGBkxMTCAgIEZGRvHx8VlZWZKSkk5OTq2trSQkJBERESIiIh8fH7m5uWFhYTQ0NJ+fn3h4eLW1tZubm4mJiU1NTX5+fi4uLpycnMrKyqKiotjY2BgYGDc3N97e3uzs7EVFRSMjI+Li4hQUFLS0tNTU1I6Ojri4uJSUlBISEtXV1bu7u21tbfLy8ktLSwQEBLCwsHd3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3d3dyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAABgFVAAAI/wDJCBxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJEmOvKSVTqlzJsmXFKGK2FHLksqbNmzg9wklzZQsaWVvUOMtJtKjRowLbvNliZQyZOU2S9CGCCanVq1g9qjKyBZAhOAQpTdLjpwuSrGjTqlVIxw0XQXKiIBTyZcubNmvz6r0KR5GPLUOCLIQDBNCWH2H2Kl7sUsuZLWywPCwjh8cdN3QYc8zDhIlThUE6C9F89FEjSIWQVZL4xNIWH4rAkr64acuWTgs92Q41OycpU1BOiclkEUukLWe09K5Y+3bu3cttXlu1pdiSjJVaFYLk6lH0iM1xK//UvYX395VLYm3x0qsjrUOnoJgidb5h+Ofl65fMJCa+LfofLXHLFqtco59C940H3YEgVYLMdnY8Q1IvXmwRy3UMFpRgQuSZlyFHgxyHhnIpkWKLLsIR9yEZGyLU4YoaPTHEFruAI9tKz9iBmmoftnjQizBaRJkgXOAxx01aoLFFJINk6KNBQAYpERyGGOaLKkTBAc4ugD1xYHOLSCLmmGRKEsyCUkJEF1OfGTUHHlzwIEcZ9TVn25145plfmg5R4oseXt2IlCq+bEEFEILOZqeejO7Jp0JzEJOEIMbIlVYyo2zxxWjLNdeMJ6CGKqonoaD5qEFwEBINYILlBUcpgOj/MQklvTVnCX4enkpQNdBAJtliURgjSBJNHKmZrbjqStAUewSS2mqkBaHEFrlUkWheyCro6KmgYJNNit9hwcYWs2izWLYcmsrnNllUh+F5lQxzRCDcoKQXui6qG6QkXBb4IX+nJDGEsWrh+6O+H3YTzjd6hAPgijoAlUUOaxkMJcIHIgEMM5A0MhSfuOCwRQ2JpGVxQVF+SMMvyJF46m9QwBJMN1mdTFDKA2Giibm95THDazFc++gjrkDCjCdnWWXzQDgnBUMgL7igmQwtXHLHCpkpa1AKKGxxwwkfuvDCNzAUAcpecJjAyxZGJKY1Qn39VQIJH44gwhZ/OJFXCCDY/4XX2wu1dcclH8iQIRzUeLBFDx9jtYYKZKWRNOAMhfHDFrx0IHR0HGwARh8a0GJV56n0kUFVlEPURjNbYBDChxdYoMc3GkyekzCKs9J46hAh0YUfkIhywYcV6LJFMxTkNAELWxxDE+8VYZJBH2BYw8HhHayNWE2v1PHNNBJAC71FzrCyBQQPfCjDB1Zj9hAih7wRDTOcvNHAGhBVIsE030TwyvgbkQQDtrCAZXwoDwp4TWwWIgRONGoLHkBFQxwxwEVMAIAdqYQD+Oc/lbEMDVk7iCj0pAc9uUIhcKgFBIWBQZC8IgLfc4D49KMxOySEebYJxAL4cD06gMMMkLhTMf8UkgAEXK+FIVneFhggCV0Z4044wJ9BpPEX2+ABiTgRBgS2cAAD8MkZJVySQpAgsi1AAhFYvAkHrAEGQWTAUjBS0hbuEEKE0KIPttlBGnESOz1cIQ2b+w4HgriFAjTkTFv4hu326JIQYGALo0jGh1phmz44BBSBsE0VGIkTOGTvNlg60Cxsw4aHrGoLt+IkTtZ3CS5gTT+5sM0eHuIavKmSKCQoAY2Cdh4p2MYaDwmHbQhwy6Kc4AY+GcB3UmEbZTzEGraBQTGLgoQ4cCxCyymEbRDwkAzYBhDTNEo3GgALXXyiN7HcwiwdwpUlhvMoiQgFnWZjBttE4iEV2sIt3smsT4XYoJIOQcIpNNnPghqEDmG0RUMSYJtTGPShBOnbFrhwxIRggge28QZEN6qDMN5gIe1KpOg2ClFh2kYA9iqIKk65hQyQlKSPsc03biGJsyAhACwgJGBe+tLL5UmndyoBT3lKgyoyahcBGKpSpfECRsjiCAQAwAsuqNSqWvWqWM2qVrfK1a569atgDatYx0rWspr1rGhNq1rXyta2uvWtcI2rXOdK17ra1a0BAQA7" style="margin-top:1rem;" /></div></details></div>
+```
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">TextStructure["The cat sat on the mat."]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhSAM0AfeJAKqqqtnZ2dzc3MjIyKWlpa2trRAQEI+Pj6mpqcbGxsLCwj4+PicnJx4eHoCAgODg4Kurq15eXtDQ0MXFxaenp0dHR6Ghofj4+EFBQdLS0hEREY2Njerq6ouLiw0NDSwsLNHR0fLy8r29vTo6OggICLy8vPHx8RISEm1tbdfX18zMzDw8PPn5+XV1dU5OTgwMDNXV1RoaGm9vbz09PYyMjLq6unZ2dpGRkT8/P1FRUQEBAUpKSoqKioODg3JyciEhIVJSUgMDAzY2NtjY2Dc3N6KiohgYGCIiItvb2x0dHfT09LKyslxcXPX19ff393BwcGtra3FxcZiYmCUlJRUVFbGxscPDw5aWll9fX5OTk1dXV9PT01ZWVhYWFqamprm5uWFhYR8fH8HBwd3d3a6urujo6EhISMfHx/v7+wAAAM/Pz6OjoyoqKlNTU9bW1rCwsAQEBEtLS3d3dzU1NZqamigoKC8vL6CgoFhYWLOzsxMTE87Ozg4ODubm5ikpKZmZmba2tgYGBkxMTO/v72pqajMzM+Tk5AUFBcvLy/////7+/nt7e25ubmdnZ5ycnMrKyi4uLuPj47e3twcHB3Nzc9ra2pCQkBkZGSsrK5KSkllZWf39/WlpaZ6enjs7O4eHh2VlZSYmJsTExOXl5Q8PD09PTwkJCV1dXaioqJeXl2xsbEZGRiAgIH19faSkpJSUlI6Ojri4uDk5OWZmZi0tLRwcHHx8fFBQUEJCQkRERENDQ8DAwDIyMvz8/GJiYufn54SEhK+vr4mJibW1tZubm01NTYWFhX5+fvb29lpaWklJSYKCgpWVlaysrPr6+lVVVbS0tBQUFNTU1OLi4t/f3+vr683Nzb+/vwICAlRUVJ2dnXp6euHh4b6+vuzs7N7e3iMjI0BAQBsbG2NjY/Dw8AoKCoGBgfPz8+7u7u3t7RcXF4aGhjg4ODAwMAsLC8nJyenp6TExMbu7uzQ0NJ+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fnyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAASAM0AQAI/wATCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS57clhsiRE0oa95s0TJmzqB5NkqTBlHo06gPji6dujVHaXliy55NOw8ggqtNu97NOTfv3xShkB5OvDjpSbhJ6x5sCIk3rM2fA/+ZDkmkhr4JR5+uUrjx78eTs/8mDCkNJazlz3PvyShNIezKC6dfj1JJtfv4oZHGgx+/dIHZDXaJeVgNqB59OmniHnzjCUgggixZQRoWCwUo2CEPWoXhgRDelMuCDFkY2IYdriRhGhQqtJo1hA1CGodTuZhhiTXZAWKFpLE4mIww0kjSiSkmtJobiSgiSRtsdOGHL2oshIYXXNRBxRSCSOHET03cwQQtRiQhhBxbKOTEEpx4EoYRkIAiCkKopAILMKqQ9qUcdNbpSkmKxDLLPLVQ4cctr/yy0Jhlnpnmmge1+WacacxZJ513NvWLMeGwYoQdnFyTUDByECOQkUgqyWRaYvxhySfHkJKGEY/WuUxBQxb/eWSSSzap0JNRTlnllTkdI8c3zpiDSS3PTJPIJpbYYYQZYR5EqJloqsmmm3DK2SqkPoIEJI5pUDOKLsZho01C3YDznThi9PRKNN9hM845BqGzjR7ggYKGQeqAZ1wbJEXCDniHJPPNQfLS+529+OpbHL9MfWLKd7kIatBo7STybbjjnqWFwsTpAStp3oJbnLjkmmscujm5k0YzCg4XzyacdAxPQQXXe29B+XJMGsPZdrStiqTJY0Qal/jSCihDpzFJJQfRE0QaQQBBxxJ3+DJJGoGkm1MvXAznhw9ZZMFJF6TFUVAZBptSSg9/8LCDDqRtY1AOONRtYxq11K133ceM/+SEH6R5csMwNXgRxRGk3WIQ2qSpzbbbcKchd0F0201a3nvzzZQvpAVRCg1XyJB0LcZ+HAMMMRBtNNLHMW2WOXuT9kLmdbvwcRpCq3500ks3/XTUU1d9ddY4qexJGrLYwAZp7eHSwg+ktUIQ42k43vbbcc+t992YZ953zz5PyK07cKzDwkDnrEBaFAaJAQfeKhSUQi1piMPrTSiQdkIzBTVhizs6IkgOqMADExSkBCRIwyEMkZBrvGglRRBfQTbRjBFU4yADLOABE7jABj5QKlkgjTgCmIhzJIM0hejFx4JwgvKdTyDpWx9bUMgg8pkPfepLA/sK4j74yY9+9ruJyv/SAARFJAId5SCNDARSCbjNgHIENCBBEKhABiLEgTMCX0h+JiTSuEMEBgEBaSpGkF58oHpEMkg3SCMFnLwDbh6QBkI4cJBfSNEg5iDNBjyYRZNEgTRLiIgdEZLHNOzxih+ECjk0gLUMGGQT4SBNJ273xTCOcYY3AloaKlkQMaaBjAMxIxoPssY0tNEmKiMFHQWCgTQc4QIDQdwPCjLIgxTykAfBYo+06BEuImQ1ZEDIgMpRkCpkDyF1SIMycAIE0txgI4ggjSb4uEuS8IA044CmNKkplSuQBgoIUQNpeHG7YB5kmJh8T4hIY06DoJMgxpRcQpK5TFSmoQIEeUYaGkH/kDms6iHRTMM0EdlHXoYPRdxaTkGIQJqbCQQMpElBQk6ojps4IYnuuF9FyKGCN1wzDbrgpkrSEQbSsIMCsKQIRz1KmpAStJpKKQZpJpCQ5emgD+JRKEEYmgaHooWG62zQQhtKEIimQaIIoagQ70mQjfFzIAyt6EJW+lGX5jKRBv2IL1UTn4PggDQa9acOGkHWspp1eUG4CQxIk4uKSIAHcaBfcTwhUpVQYx7DeUEOiFE6hrw1rsah60ulEgqwJiQCpNHUQEQ0kK+mQaNnAWpCEeLYsKZhrGbNLFqXis+BOHWnaZCqQf4qV+II9qoFzapGtjqxrhqksgQpqc6gdhMs/55iImQoxHA8wA4wtCITgaurSjZRBHZEjjRzYIYSEpLb3fb2t8EdbFROsEmF+IA0EMgpZQ2rFslqUqeN5a5AZKuztNqzswL5LFRDa5Dmkoa3vgVuGk5rEF2qVlsS7KJQCQLbgSQzDTcIm4AHHDZP2eQMpMmGRGZBGnVs4xGbGIgTootamJ7kF8Rog6pIY4RgHITBoX1whAUy4fkK1yniSAMcFEII0kBDu14V708zqV/wCqS/AvlvgAlMYAPXRGXoTYR6BRLVgoDYwRCWMIXri9X7boS1t7NxInCciFamoa9AeQBpPhARZpAGCHdUsokRIoYmu4QFVYjkZb9QEC8TMf/MJF4yD83MFN2mwYoH2QFp4rdY1xaEymeBmzonG+PHEsTKWP4JkJu6T9CKNhFuBrNBSkzfOafWyRaBMoxfK2MHkOYPRGkAaYYAkfJEA7JxHvNBVECap9JkGWwtiKlRnQhKJ4TVjY6KDEhjAYQgQ1Wk8Cljbyzjs7wgDQxgkJSp7Ok0gFooi/ZsronM3oHM2llyJgiuXc0VRMSCHHLRdJ/3G15DD8QN2EgDK5YrlOumoRgQeRgO5pjtgXCANAuwySYCkQZwFETe9Fa1Qe6dhnxHRQGkiYcKDXID0kQgyts1d1qWNwlaQ7zQGkW3utkNlGind9qJKPJAAH4QgleaIAT/N/hWFNEGDoMgLuIGkJ/5W+xxkMYM8DLIBaiRk2psWAYjJggLbJCJglAhDVTIOUESAD2BGwRxQSB1Sp6AghAgZAukWYXRka70gTC93rGEmtShYuUdEuQdKoOD68a97GKbhXNp8HGNIw5Zm6cB5wfZefGYKm1ui1wgR0+6Qb7u9IJAfexZgQBxrOqWmCdi2FMudgjaQZof0OGCAhmDMBpQCCPiBBpPcw8CBiGQXzCDFWkoB5axgO+XF0kBeNABHPhQeIIAgzRH+MLNlCCPLIikBvpbhBo8f6xYoD4NVSgI6wvuekXAXva0P7ntca97gfDe90r5hsGK8QgjwkMYQzxA/2vJTWyJo+VE5ZBCzlmwhx5oFPKAnnzlLz8QzXOe+DTxuJBB/vdELH8Bzfd8s1d7A3F7rlR9iXB9VXEMxPFobeF48Od2HGAGw6ED6nAEBjAc4vAAOpEHBkMafJBEpHEIHVAQo5BipKEBrJBAaeAH79By0idhlEcaJCAOHjCCcMYRzrABjASCDEAE7bBhaeAABnGCw6GCLOiCMCgmM5gGNXiDCpSDRWENSTAckyCE2AAMXEV+kWd+aLEaUGMEH3gbbEd3A0eBpGGBGKiBHHhejOZ31SYQRpiCK0gaSkiAJNaET4iDVBFBwzECMJdfvzRz5UZrigABRHBcpAEJWZAZO/8BD9uQNMPBB74wMAYRCTmQbsNBC8SgQu0RgwMxCOPwPsRxAnjADSPRBFewAqQ4HEFQAVpziZlIHJzoiXgoEKLYivpzikyBDnLQg52zCmcwiFwIaGehCMKQgcRBAqvQDZv2Z25XJIioiGnAiI7ohn3naAWBiZpIGrWYCJ+4ELlYHKaIilPhDI7FB4gCGtUgCRZgAYCAU0HhBm/QCaiQAM6wEH3wBtrwBmsXESFQA0WgDQWwBUFXEudgBQXgCARwDeCmj/zojxQRkANZkAfJFL1wBhRAD5KQDoiBBglAAcRAAQOADCDRju8Yj1Oxj/34jxBBkQRpkFexCV9AARKDaTj/mZM6uZM82ZM++ZNAGZRCOZREWZRGeZRImZRKuZRM2ZRO+ZRQGZVSOZVUWZVWeZVYmZVauZVc2ZVe+ZVgGZZiOZZbYQVmeZZomZZquZZs2ZZu+ZZwGZdyGZdjUBHeMJd4mZdwKQEd4Qx6+ZeAiZYXiREqEJiGeZiImZhomVIbAQKK+ZiQGZlryZcUwQKSeZmD+RCFeZmc2ZmQSUIM4QWiOZqkWZqmeZqomZqquZqs2Zqu2ZqgCRHT8Jq0WZusGQsd4QS2uZu8SZoLtxHQ0JvCOZzEWZykeY0aIQ/GuZzM2ZyniZsUoZvO6ZyZ6RB5MJ3YmZ3NOQwQQQHe+Z3gGZ7i/zme5Fme5nme6Jme6pmesfkQ07Ce8Bmf6AmdG+EE8nmf+Amev6kR0JCf/vmfABqg4ImcGSEPAnqgCJqg48lm0amgDlqdDZEHDjqhFJqgZEiWGJqhGrqhHNqhHvqhIBqiIjqiJFqiJnqiKJqiKrqiLNqiLvqiMBqjMjqjNFqjNnqjOJqjOrqjPNqjPvqjQBqkQjqkRFqkRnqkSJqkSrqkTNqkTvqkUBqlUjqlIboHCXClWGoNApCPQ/EI+MgTyHClZYAQApAA1+EUSnClXVcQA5AAY1oRo5AA5tgSIIClWDoAAfAfPvELCVCXCMGnfqoTVmqnCaClXCoUXnqoORGmbv9KpmZKFHVKqHiqp1CRqC7hCDSQqZqaqZYgCvvpEIrQCxBKEsxAAwR6E96QqdrgUwPxBTSQAE+hCFdAA++AEH2QqaRXEYhAAwrwEkWwqcD6BlKIE2pAA/IwEJvQC8RXrMe6E5gKrJzqqRIRqqM6EqV6qjaRqjSwqgfhqrA6FL8KrZkqrCpBrR/RC/t5rZdKA0vwDu6aAHnwrM3wqQyxq73KEuq6E9pKA1bQra8KFddAA712ELtAA5Giq7zqqzQQDO7qrgoAAZlaBNU6E8w6EGRAAzwnEBXrrOzasPAqr/S6EPbaEvmqE/varwbhrUTxqwzbsA8bsRPbESPrETdAA7//WbIrgalyVBCPsAE0wGcAlbAsga49kao+CwurRBAq+xRlkKkeaRB08LMXMbMt8au2QhCVkKmUyRPmKhAXm7FFIqo8obMG0bNSCxFUqxJEyxNGSwNIm7L/Cq40cLUDkbU0sLUmkbYbUbO/ubYtQbYGYQ00wAyKWq9CqxapmgWSYLD4lwhL+xSdQAM0dTY0sAFrKhF6qxJWexDNQAOSQBRfKxSAWxCCS7hoe7hpkbiL6wqN+7hBsbkG0bmfixKZmxF8SxOjSxBoMKtAKxBDAAid4AhkUAme1wQiQAE0sAYigHi/G7zDi39nAEbwAAGpcEHvIAKbMA0FIAXKCy8cUANr/0AHBYBniSAKIvBClSAC6cACCkAPqeAF78CqidC8wku8BBG9iTC91YsRiesEvFsQrrsJiPAGdLAGX5BoYiACn6oAInAzHCACApAIEkAAqWABJcBxJzEA22oQCkADCFAQvTDAdHAHgPCmAsECIsAiAVAEjpAI9noBYkAPUlAAAxCyIQG7BdENNEABAlEGIvANipAAxHChIUzAJGzCicANIjAKlnkHf0AGiDCYATAM9NAJ0NAsZbQHAEAHjgABbkB8o7C8iWAIIhC1wSACYxrGiCfABGzAiXa9m4AOgOAIfwAAATASuTsQu3u2A0G/zysQxou8ysu8wFu/0Cu91Gu92P+rvdwrAt4LvuJLvuaLvurLvu4Lv/Lrx/Y7EPirv5hnEf37v0obtwLBxgV8wDykwAXBwA4MwRJMwRaMwRmBwwShwzycCNMgAkiwjSLgOmggAqbxAAXwB9qwBEgsEG4ADY6wBvIwCoB8vMkrxucgAo9QEEogArWKrNZQj1JAALtwR1sgArBgrOdbvuU8EE0gBgDwB6jgkLoLzIkgzMRszBWRxwMRsNwpEGiwuDRwAONMA1WgQukArM26z5nqz5ka0AMRuRyQCZk6pr8KAhuQCVFLA3QwBP7sCOMMCzMjEH9gqgIRsClADzQgBaVKA/yjx/yM0AD9mwzt0DRwzBORuIn/kAI0cANh9rghQACcmqkbsI6JkAU0ULilmlJIwKvDQANZUNFSYJIoYQIPXRCY6noCYQKukKk1m6nVDMgeLA1Y7cI08AXP6rPJa3UmQcsDEQw0kAe+K7n8bE5WjdWautVg/Q7a4NOZigpOnQhoEAs+fQCZGgyM6QwWgNWA7bkDkQHGmgggAKykptjNmgg73dOVC9S/GglCTQxZnc0gYc8hTQP5zNcr/c8KPdCbWtCjndAuTQMNHdURPdEVfdEZvdEdnQgf7YgiTdImnakprc+p3dILzdowLdMSQdM2jdOj/K2SzdM0YAk+DdRCTdQ0YNRIrdRMvdezPLcHodZsnQiC/7sLBVGsinUBNEAAEtDPGl25eIYGSd3cR8sipq2px8oByVsQqVoE6FPYzZ3VWYAOAgENwJoZtz0QkZAKlJ0Fa0fe5o3e47wB5AsRnp0Ie1DeAyEGFv0Am4AGbvAKNADeinABZ0AD13ABN2PhdIDhGs7h4C0QkUsPxCABkXAvvwoLiGBEkUDasHQOkcugtg3SiRCwUkAP0gEDmYpnJo7iG97hwe3iMC6/xa3UAlEAKJ3cA9G52jAKm+AEKuCzaxfdbTbdAnHUUpAFEZwIZTCrA6ASyLviAkHfsIDdV40Az4EMouCzftoENKDZqDAEgrKrbmsNyMACASDUHnbW2r2NPv+b5vNLAyQdC9/g34kQ53Ne5zTgp7tqCRugAoE+6KA9EBp8A27gDGjwDaUKRgJRsBZwQYowBOMsj5CdCL1wAZ1bCRcQYa8uEFaO5VrO5QPxq1JQBVfSCyXQ3DFLERE+4QRQ4Ree4Unu4SAu4iQuEEfO7Cq+5C8e44kw4zWeCDee0Dm+4wMx4D9e0kIuEEROA0a+7Cmu5CzO6Nfu5BFB04kg5b3tuKSc61m+5TTQ5UP95dQ95mV+5jSg6BqB1tye6ALx3eEt4gJB3sxwAGegQk2AvNklEFZQ0tOQrNbgs4bw4SE+4vdC32tg3zSA3wLhqnfQ0emACjQAnc5wATXbBCn/Je4sUKpk4N8msLiWkHMOD/EST/HGTgM7axACADoCEQKWcACQLhDc4LaOSLVIr/QE0fSw4IiRmwVh9qsXmghLYNEO5dWoEO4+HrCw8JBee7dHn/RLn8RO3+5YvxHybgI1m0b2/q3TcNPIqQKM7nleThBFHeaZSvdg3d0o0djPJhCiQAPtlAgBQAOdsJ+JP7B4brC/6ed4+wuZepMj8avDkAGenwGIMAw+qw1cOgSZqlgC0fiPTxCRLxB+TkJNuwH+7QRCHahm3s9mfdW2PwzM4EiJcOuJELoCcet3fwN5v/cC8avaQHybINRP+xERXvRXkPZSPxBU//SHG/Vrf/1u/5/1NLD1XU8HX08DYe/RY++2Zh/8aC/Zaj/1bZ8IVz+sMw3liSD3NED3S1v8x08PfN/vfg8QNC4kSoSEBg03BAkiopFH4UOIESUqLEJjWAaMGRAN20BDmzOC1mjsgqiGxjWCFw5+eViGxhWCTW7QSPdQHo0aC2koUMiBxhqI3mgUUdiJxrSHo34+nNlL4R8aTQhOoOFK0cNgNOSlXNny5USwCh3RkDZxGo0DOiVFdEWjkk6eatm6JWj0DMSKSB6K0fowEg0CT6MSvEbjDcTC1uRCbPs2kd2wkSUKzaJQJDNkBL/QSEBQBI0SEJ1loeGNIGmQD5kJJGjw1VWFAgxLpv9dW6GTAzQMFUX4kAxZ0R0zNzkY6SHDVE4fFqAxwfZziRUPTp9uwTTBITQsKSf4u+xDZ8ITMWSGBiLzAYkq0aAXEQINNQQJ0Eg/MUPf7jSoKby/NdHn0MAj7bqKVIBoDRo4gO65sb6L6Ky0xqNhLcbokjAuCSl8qLG6aLjrobz2wo+gvwIjCCqpEinssIcSW2xDCyFbECzKLKMBM8048ww00QY8jYbUFFptoIJoeO0h2VicMTrqmrTORpIeMgmlRFSiAZ6HWKChskQkoIEMiMoYpj6GMPQJqIeEIoogcgaBjaBfaLiDKRq4Q5GgO2gIACKlmOHqyiy3XLLBidygoRP/gmqgoZtIGnW0GfrgUkhRRh1tFNL6jHKMIhrKeEgBDx8yBDDBUiwMQ4J2oUGxRCi19NJIH7NwyYhqJEiRtgDJsbNEmEsIIlRoGOPHIAkasjVSHxpjNlpprYLHRISypFhtaNji1Uiu0C0R4mhw4jhmH3rEomafqwgVEdJNdwAB3kwkOwsgqvbaV7XdjaFmIhqXpX0joirKcWkAQIKaIOpPod/2I+jgXnsDVliCKlJYIQQVLBcsQiUyFNFWF8UWU0kT9fhVkGXdNOJOPw1VoVFNTOROFXeCSFVWXSU5Vk0vTlPQW3PdlSBfIwp22ERQg+jYIl0maFkldT5X3XXbfUik/ygVmvJP8xRyhufC6puozJ6W2nnNhxQxgRtrjJpToaZKJWimcyDapCOQrMyaoK25XDDjiAb4kiAAmmxSjJATCVzw6QiXFUsQU1YIVK8TadntmBGZeVXAEU+8Q8Z1jpZngjiARb9ENuPVKOMgGoaGPYg9mrUiwVQ2XM9rW4+ZqxJoqOzRNafhG25B10mEiAKgAZXaI6sovsiya1qR3jUHnqGcIDIegI55fei+Km5NwJLprpAHHf5GTLh8/1CPaPXWE6nI04cqTh4iviHyW/bDNVcc7Mx9V9yozqEMfgSBnKiS9bLBVO5yrMof4v4HqNrZKnSj24/pOpS6h7DPdaqBnf9BZKcQpiVveZKhWklOwpUbiIZnWXGQRPiXiDMFZSgKUUQGUAG+g7xCTnSy02CUQANYuIsgUqBBNapEgxSCR3gMAo5EmEO8hskjI1PMQB8KxxwpUhEjVpTVdTg1wEQUkGUHhFlhLPcQmgFNK1rcYoe8qDMJEsQKNCCGMyyYCARNTCHPAsEGFUIaInkQIiGcH216QZr95EkvdFIBGzNgguD5CVwsgQgMaNC9QjKJeWHJzhIgMpNGshGSDBlGRCxZgESoClUE2QO5FMKCIUiCGAexBDcWZj7S3dI/eYwIHwV4oARlkiD1Ww4NoIhFR3LxhchkIxeN8kb3OY6AsSLI5E7/lEAzLlCNWdSiM0uTvDgmYo51vCMvIeLLogEJIoBE1geXRruLjTAyJZzaCY+YRK3xbAk0yEBYXhjDh/iEbPukAQKs4AYOpGOHbKuT27ZGg7sJiQbkUwk+8bZE2xAzdAfhYjfgE5kXenSTE3kmXqQZRmpKjozYpMEZFZLGRIg0MiWN4BLRUK1d3DEPNJBARBCElHQWS0sd/NvsmibMiSgqFgrNAncIYoFvgoU4klQIQxAQEVHQQHFI5dRIJ9JJiEAVmhBhiBewaswu7Q4xzZlIOgIXr0QwLBHn0yVBdtpTYAL1fcC0WCY1CkOOEkSm/pSZYD8aFpp+UWWRsyYCTdVS/23G9LBgSSwcbYpTnfLUp0fxYyKGGsiighCe5ZJnWOipkMJQqaIq5BKoRAERNCABeBcKG5piM8NE/CUTYFTo2t7W0GumSFsFeyUNNrCJe7J2UE18CDK8QINgKAQENEBl2SBQBEjSliDTrS4Nr5vdykYTjGKs5kof69JUYS4R3IWIIr7rRnBi9CwbQBCvqIK9h6CjI0r4UYoI8o2DgNadiSAkVyfylyxkNRYRgQYNHgERchQBAjG5EVmBGIKHbGKWvzJwNL0qEbA+pMEPfkiEJyyhDZCjbGPp6VmywIIM04EGKeAWAgCAXIW4xBJ1zc/EGHZfiOiXBvwVL1+RqlHnQv9XutRt73u1u14mWxe78G3ceFPa2DJCFo3qZa+UwRtVz4UzEfOt71QEFuT99vchACbqgAvstMmCRST+UUhbVItE5SbCkr4liGyQ92SfcEwhfFmTCtSqkLPwuW3BJUiwPlQ+jq1WiXqDDt8UkQ43yPgAfXVGKlgnLvZUdSRa83T7CDKu9lBZsY+7snkJo+WXqrfTn1YIqnkz1maJuXTT4ZUSZrIngqCBOaUcpsMSgQYEtXmQo+2wQmQMvgdExCVZGAUNsxKgqVr4kjhORFbpwG0DlxYsIc7xlqp9q2vrBLrcoQozYIxHtCrkDDSgg3IyQYNFEsRQaJLrb4gWV/z4Wk//ChG2K4scv2AK09KY1jSnSw3qVEuoarM2dSJsrepfspqxrlbglllFcYjfOr6UVshmDtLrXxN82GIxNrID3M5lH5W0cS7UobhtPHtKOp9cQgNU8JoIRTzXORJXSAiAmN1EkGMmazKUWW/TlognYiZBgplsmEHcEMi4j8md9HJhYQmwR+8VekzEFg5SBQnAYKewiHZIaGABbhTM7JdM+9rb3kWTWnnjLssyelOp3rKfve5AvHt4y6VrJ2hLR2bewBdggAgE3UDFOcoEIiKxBQswwygCjnmzJzLHlwiRIIBAYg1gIIG2SCFukbRwtQigAjVAytgdFvdXaeBJiJD+BqZH/z0NVK+TmbhCBRL4Da0T8YCONEMNIHjDQYagkM/AQh4wcIMIwNdPgNO5+cOIBH/lSpXGPz7ykz84xRLuVyCC3RJiJ/vc0a52wtsI7nIXPPzZLvIqL9aAfGep32EaeLqzv8IDM8siOYJIvJNTCPBzPMhDIvLbjMq7vMzbPJgzKhGiOYkgh9xoBgGghl3YAArIOTzrOoKwJIuQBhCYDzogEpGYv2LTBhiYBhVgBi/YgDUJgZmQBGqghndgBh1iu3cjjUeIBKeAmUQIllewghSYAE+7AxzTuYsywNoYiybJgiIQhcwoHtKYDikANoIog44YkQDYwoPowocIr73SuP2jnP9s8riHGEPqMEP8CzOMIgic055E2IPcqA7iqpJkO4g/+IX34DwL9LxaOQgoighFEIUwPIg16KtsAxc3iAXquIGToT0MjAhyoyFGpI5HFDUR8KjpOICtU4hIIKLpYAYBeAg0eBbqyAQSyz4bcT5ZVAg9pA4L6MM0NL++KiQqpA4rxEKJgEMu9MJEAMODoDNiLENjRMOTIi+V4r/ziiw7JEPfa0YCvBhdS4Q7fIhb5MOHuIA/pIFAHMQKFC2Za5basw8cSsa/uDOLSoS8ecN7m44i6CtkxI9f8LTpQAVkgAWySYGZmA4ACIFgoYHnSwRXHAwjRAOTm44lIBKu2zlDdAL/HnwEJIioLzyDBMCgRLDId8BIjTTEsABJkSTJ51ACARgACegDp1KIb3iHCUiBYkHJTDKBSkiAPQAq24CHR0iAMchCmywXnNRJntQJlCAHN0iASiAy0ZDBR3gAiQyoDJiARwiAbwkLARCFARgEsFBJlnTJodQZk8xIaeNIjyzLkRzLh1BLtowMsGzJl/wvmaTJt3yOEMgAUUAEI6IVJ/iGAbCGBxCiMkBLrUmBBBiAwZQIJZCGCZCGvmwCEEiAyUODDLACFVhLgkAHxIQBXLtL0AxN0RxN0ixNz2MIKjFN1VxN1mxN13xN2IxN2ZxN2qxN1URN28xN3dxN3uxN3/xN/+AMTuFkS9wcTuM8TuRMTuVcTuZsTucEKXt6TumcTuqsTuu8TuzMTok4B0MgP+38TvAMT/EcT/IsT/M8T/RMT/VcT/ZsT/d8T/iMT/mcT/qsT/u8T/zMT/3cT/7sT//8TwANUAEdUAItUIiYAARNUAVdUAZtUAd9UAiNUAmdUAqtUAu9UAzN0AwtRQPFzy3QUBANUREdURItURMFUXDr0NrwAhZtURd9URiNURmdURqtURu9URzNUR3dUR7t0R5dMBXFT3nwUSItUiM9UiRNUiUl0hQN0shYUiiNUimdUipNUiB10voc0irdUi7tUi9d0ibF0olQBDItUzM9UzRNU/81XVM2bVM3fVM4jVM5nVM6rVM7FdP6tFM93VM+7VM//VNA3VM8HVRCLVRDPVRETVRFXVRGbVRHfVRIjVRJnVRKrVRLvVRMzVRN3VRO7VRP/VRQDVVRHVVSLVVTPVVUTVVVXVVWbVVXfVVYjVVZnVVarVVbvVVczVVd3VVe7VVf/VVgDVZhHVZiLVZjPVZkTVZlXVZmbVZnfVZojVZpndZURYYESAAwQpKOFM3JvFZvHYAAgKZ0SABjpNZJtVZsnQgB2NbQ7FZvTcxwhYhxLVdzHU2h8Ii1vCPQlA7EeQOkMwjcq9dJvVdtyNfF21ff8VeFAFiBNc17pQErkAh9vcv/igiGd7jYd1CA9xgKHGPYhpXUh43YiJjYt6xYjM3YjS2Cjr29jyVNoegIWOjFnwnNdVwPzSqSgG1ZR31ZIJLZXcPDksVAm8Urj9VZ0KQMSagKISJZtlzHRIAUCilao2VUpFVaiGDasXRaqEWWnJ3asaQMBDSQh5jYTUCEN6CDNfiCo0wEMRCBl1QAEcgaDhCBVZQAAkgFCygBp5wIp/UoCuBaRVCBNbgCC5CH1fMsEVCMACgCR1AIZFCAZqADR0AFFXg3hagGSViDVFgDeUA6hfiFEnCFP0AFa6hJr9VOsNUWsS25g02Esj3btF3btn3buA0duu2Su83bvdUkifBb/8AVXMI13FdKXG5kXMeFXMmlXMslCMzVXM71XDgJ3dEt3YatkRRAIs/V1xCYD+04iA14rT9SJw4CLQVYnSyQMd8TSt6NiKxwiCIJBubIAqhIXwpDAGk4iCSahtWggUzYwzW4m/s1ri28gTdSgd7BoU7AsNMFT+vF3rE92O2lJe8F385KBKQxiPLdEvSVAvWNCKdtX2SB3y2ZXw6u3wDO3/3tX0cEYO8d4AI+4INIYIG1FebIF9bVHkjRhlHYBCdQgY7YFKMZX2SRgixYxWPUlsjxYAyMhI6oD4PYgFeYrT5YDRIjDmK4AVQYgl8otiVYvWnwNBggCGQAn0cwj3N4D/8bTgQAuwEJYAFFGAV6qIoFZmCeqeEHxmGP2OEe/uHwrckL9r0i/kIkDot1ZOJYeeIoJogpdjAKu+Is3uJEGIsuJogvpoEwToQxdjAzRmOYRKI2fuM4doUZ5hkTmAkOu6OzuAH/SgRDowfYCGKJAq3ZYwj35VuLmKKN6IiPQJaBU4h3oAFdCZ6q4A7imJaH8BsqATDbgiFm0IZbyZNLFmMdyrc5vk5bKWVjQ2UkWuVWfmXxjWVe5jAJqWUmuYiMyGWPSA2D6GWC+OVg7hZXIGbtKBZk/i+xCZ1mfmZLbq5prlcJuowsvCMA6ZGogmVjIaojua105BTNeRJkSQXroQH/aKAwGvDIXhgE6B0XKKIGGkiFDi43OogIvkjEarbOf76RgF68gRaQgv7mgwathO4zZmNoxHHoIoHoN5RoirZojIYIjSYIjvboiXCJkIaIkfZn0MEVYJ7ZoHkYojFoCyYqpSGwmUYZdIEadnEXg7iqh1iPiRbmrIwINEiHMZgAHYKiCyAiZrgGaljeRLheVMAWUDmxkjbppPaZn1UjcW40iAmq1wGtqX4zJb5qdcnqh9hqiPBqig5r2CJrs463tL4RtnZruJZrGqDraY0j0SGdO1If1aE1qP5jN6tqD5MMg8AkhVDs4DHACxCFO2jEs+6JtvBeVMgA2Jg33xHlurZr/0rb7ApaPM/OINB26agmRHQk5EyEiNNObJ1e7Yho7deejtgOndk2rtq+bd+RY3MNp3Gyo8Uzp4dAJ6hmp9jpPLBwWuVm2a5u7ki8jWq5gSp4h0owgekiaRg6AwTAoWa4inFBAEei5t2WTu6mI+/mFfDeIxrYuvFWtkK05Q+LCKlVD/ausLZ87/ie7/qGCA7Ab/3m74L6b6QmuZsaicz6OfMDKoP+rHN8p4VGmQdP765V7fYmCN2xAPXNcIlAA2kYHb1Yj64N8OwMpxHPqcW7q81CcZdW8fJu8PUNiwiXcQpXiBq/8XgT6x3HNwn/8Y8VMzJbPCDLrzRLp1VmM+Nmcf/kfvHDVu/UnnCqIojmM/FEoAooegT7hYjfeIdEUKjyMOoiuEQgb04uN64yi/MzA/MhU7NOZvDjPu/kTvMYZ3OIePMDjTc6b6G5ogE813ONFIM+D3GJ5TWCEDgvLDhii+SWS7Yyp+oWL+3IeHJIf2CRZV4dChCGcAVu64U8MeLfgAZuGwVY2IDd/XPm1LWHRDl2JnWW4zCXU3QzZ3Q0X1g1Jwgob/Ndi/VEqIZZ1wlbVwhcpwFdl+he//Vgh1bEUzztWUDxc0DWjUDM0zxmV/UzN+1ol/CvnnEJP4ABiIRKuAZYWA16KAOzubc7UIEA2IOK6ITU8AbwIYABGIJdmAn/oBX2Ya9DBDxYdG9AyVt3y2t3ClzyRXdweX/0eo9yaUeLfN/3fmcPgDcBgSd4gz+UhF/4hn/41s3sOuTGBLTFPTyIXAzHcSzHdxdsk3p2rmXukaf2mJmODSiBJqhHqRAAfpwOCvDKyzWK6bAECpZ459zGbtR5XOxDcaQOoE91oW8cosdZo6cwpC8MpWd6p08EqG+SqX+IarB6Wsr6P49LsYyImJxJ03XNalCDCQgABfaGkMwaNKgEFRCFDIBkiOiFUVCDBEiBcdd68tT7uVTjuvz71gz8wS/8ww82xWd8x38IyJd8yrd81V991m9913992I992Z992q9927993M99/93ffd7vfd//feAPfuEffuIvfuM/fuRPfieVgAFofud/fuiPfumffuqvfuu/fuzPfu3ffu7vfu//fvAPf/Eff/Iv/+kXPeWHVWj4UvZvf/d/f/iPf/nv0TBNf1dd//nPf/3ff/7vf/8HCC8CBwrclOggwoQKFzJs6PAhxIgSJ1KsaPEixowaN3Ls6PEjyJAiR07sZfIkypQqV7Js6fIlzJgyZ9KsafMmzpw6d/Ls6bMlyaBChxItavQo0qRKlzJt6vQp1KhSp1KtavUq1qxat3Lt6vUr2LBix5Ita/Ys2rRq17Jt6/Yt3Lhy59Kta/cu3rx69/Lt6/cv4MCCBxMubP/4MOLEihczbuz4MeTIkidTrmz5MubMmjdz7uz5M+jQokeTLm36NOrUqlezbu36NezYsmfTrm37Nu7cunfz7u37N/DgwocTL278OPLkypczb+78OfTo0qdT/wgiAfbsAwJ4E/srwRiH38MrvZBAxcPr2bFv754wXYIA1efTP12EBv78+d+YAKuGhjwIbdKLIgj9F6BSJtDwx0P36acffwghQcMS9Vl4oWf3BfMOh+8oAAF+RRjk1YEIkUEDNQYCuJSCDDqkYYcegkiDiAdNWCGGOepI2X1qLFQJfhJ8pUgvIyZyYooHEWkkUi02SIOPCgFJg5CJ3Lgjllky1iNDzdD/IElZSEbl5ItQdvmljRRquSabg3G5UDc0UHBQGSJ8o0gCxACCUC+IvEHHHYCUkRA3IozCghV3/EEGIkweFMAw9HQCzRYL9bIHAHQ4AoEbBR40ighDJGKICHTQEIwIg4IqqoB+0rHGF9Mo9I4Im6ADiCN/ACCfQt7UQEEq9JARgKeJkNnQmwrFOaeVFCqiwhpXWCDPOQixIII1iQRQhCMIIaNAM5qiogILClUjyRqprCFPfwr9UoIrf6BijTNt2ntvUckmFAwNeRw0BA0TSIIfGQeZ4Ap+N+T3CEKI0PCONvhtgB8qyCCERiwSH4BfMBcg5IwFCW+M5kEZrAjCg6Ka/4xgIiEQgJ8lEouS0H2RZEEDMQo/nJAKsOCXxcQ0lIDQsQzpixC//jYbTAE0ZPEHflJYnEgTNCAgTcIHTcMMfpmMvAYaCGFNwwY303CDewf1DDN+nYSAL9xxf3R0IpFMPMC/NNBDQyzfoHMQwgh0h4woE5PnsCUbqIAMCwHcPAxCA5zthjNofMO1CAjtQoMF1SSiyBA+91Hyir1c4GUlFxi0MkJeajPKJk6oMHElCN0nRRVOJNJLCTRYMiI5Pg9Qby8gTNxu0QvRbTcNeDe7wSvfHNQH1wxTjfMNqAzxy0GOUFhtItOkQgMMByET8yNhnwNiMwh9c7YELCgyyt6uyP99P/4W3TdMBv1ngMgwJqaNeiUCYDS4RkICQINO9CIhouDcQRxGg2whpAxk+5sTbkYeOtHgAG9LBMI2mIhhMCMDpGOZmE6otbM1gWd689R9tFGsTdwsHXlDhUJAJACDLehJ/PMfAAVIwAnRgFcHeQcN9nQ9GriigQepmiUIeBDJITAR71tDQjjADG0o6Q7kSwgyXkEDJOSvjGY02oP0Y4G0AcwSTjzIiaShEGdMzGIOY0bYEtI0vAGJHgsBUZRe5jyGsA6OKEJIIUUgtDnezD33QU9C1kADDhzkAoOYGkKaVjtj9bBMacTPGiVEg1QoRIHQeCJ+IpGQXgyiXQh5BA3/MpcIaowSkwqxIB0WIoZYnrGXZ7wPKkQgTGEOQADFKiAEExKxLUSimc68Ag0MkQiHtU8hsPxCIq65kAnQYBcHgSUNACABGyqkkEc6pAoT0TQ3LAQVNCDPfZKEEElSUiEXgMcQ5IGfTSZPIcAcJjGNmZAJIUBKNDjlEnXHEDSkYwwTEKMsLyAFGjDjGtQoV0JSQANUONOZCqABBHwpUvzRbSEAe0NCFOGzT+JHeg6rwUIUCIBE1IAGCViIyaqgpATEDD9XkMff0nlOeRayEzRQpUKGQYM9HOQ+g4rkJBEyiC9ADT+wyAQN+NlJZJkJIhPSaUKAhNCqZWEhFxDFHYJG/wOIIoQDCJMYKjLgqTOwFD/2Gyle8VVShQAMRwhRmAr8J9gM9MdhkFMIDGhQgERsTgEL2QMNDnsQFgxBEsSAGTeEmsJEFFKS8kRIFWgAgqbS4KnzjGoifqEwKUjCGtRwAjSyykMXcTVKD7lSWA+KSmYoxAkRu0EV3lEJE6BMlm09AwJ62owCwRIBg/UfGfMqXTbtNSF9VUjI0sYQh3lhIQ/MnAT6tZBrBKwh6QBAMs252ULmgUoLkaSsEuFUhdDzIAj40hsTEVut0haNtnUIbhEi1t0qJAGcs2VxG4IGafiMjEDy63QjfK/qIuS6CYmt9RBCjiKEdJpkI0dKvSekaf84DaMH2YSpUkA1BACASRa0hGbRydkVJYKbM00IOiamBNKa9iD1TUQNFeJO/j7pvw0J8EEGfD3eJuQN7k0IN2X5iKsp5ETvSEQ6KJpHhIihCJuUMJgvROG8QTgRFszCKBCiCH4NzcOneiM3mYFRSRo3EXSlgxOxGt2DuIEGWJwxCt+JSBorQWFGREPTJDtfqNbTew9ISJ+LONsiRwTJiVBy1ZiMkC/QwAoJqYYY2+wwVxipF17c4TmhYaRRwGIDOw4zrOkzZmSWORGAOFsNYCABhEkBfA5TmCtUIIETLRUhD5hYM9QAAifTgFWJUCQs5AEDN4ggZiYENEKcPIxI7Nj/nNzcwBdggAhJ3gDEPKYvahX5hwxEwg2h5VoeBsHJ/iqvq7dVU27HSlGDHmAAkajENWDBNXqUQREmwOodVBCAPdynEwT0RswIMIAh7EJhN401xqkzawuntHD6WUM9PSyCOOXnAKNNSCQmmh9moPogaAitfjKRYXNaIz8qo/FB9jAyUJLz3Iw+iDPcmZ8sSIDEC5w3pb2KbwHrdsnj1c8GStAErNKghQIYn34oIG+EVMOo+bHEzDIu9vuZoBIJ2EN8G3bARJDDDQmoxKvnOA0VPOIBHlsIBzIwgUcEQKEOEYAoBrB1hihBAAOQQB/yWxFuIGIA1Lj7NCbATqpUQw0T/wjAB73xjvS5vBIqEEUGuGepUaghASmI+9hTf0aHVVH1rn89blgP+9nTPjayrz3uc3+a2+u+977vzDkMYe7fE7/4xj8+8pOv/OUzv/nOfz70oy/96VO/+p1xRoyyr/3tc7/73v8++MMv/vGTv/zmPz/606/+9bO//e5/P/zjr/5jWt8zTiAI/vOv//3zv//+/z8ABqAADiABFqABHiACJqACLiADNqADPiAEJqCj1B9n3F8EXiAGZqAGbiAHdqAHfiAIhuACTiAFboYznCAKpqAKriALtqALviAMxqAMziAN1qAN3iAO5qAO7iAP9qAP/iAQBqEQ1mAJFqERHiESJv+hEi4hEzahEz4hFEahFE4hFVahFV4hFmahFm4hF3ahF34hGIahGI4hGZahGZ4hGqahGq4hG7ahG74hHMahHM4hHdahHd4hHubhaygBdoAPQwxAAvTYRYxCAmTWRajHerSHQsCHEemhI4aGIkDTlTFEH+DH4GGEwzjWRTjIJ0VImtTaI4biZpCXBTTE5tyVRmQiRsBIh3xIiIyIpYmiLGKGBdFAzyWEqUBSKtKAJuqPvTHdk8XiLA4jZRjVBCyEBW2AH2aEKm7iL7YOyQgjMU7jY0gOFynERxXUKrlKoPTYtWTLtnRLJl6AGNCDFBTAACiefzHEsnzis0TLtPjhN2r/C7d4C7iIC7mYC7qoC7ssxLvEy7xIETUOpFYoSGkphPecnMG8lc7QQIZVzdVkjcN8gfeQDX6swQeViZEdRNKkCdM4TVVJDSpF5NloDdfQgNdc5JaNTdkkjHatje+0TUYSJE1aBQV0UxbRACzYUuAMjseRR9XkjPZwjwTBgjUwjuOcCkQsz92kCfRITyJQj0OiklBuT/d8j9aMT/kkwvk4pPqwj/vAj/zQDxPVpFlWBcr01wMVDEIoEAM5UDJVDRO9kQRVyUH8An6IHlf9UP8EEQ0MUJpIGkIgkRLJZRMhBBQJJBUdxBVl0RZ10Rd5ixjt2VlWZlM4wcZI00EY1eQZ/5IcJQQd0YDFyCVSRdAoKV7THKMnfVIopQkpJVDTkeYqtZI18dIs1VJD4JIu2aZl9uZShFabeYPvCOQydVQzQZM0yaXfeRhK1aZkoVEwAVQxHRNBGZS+0cByJgRDORRbJYJEUZRFmdhBaBRHGedHdZhvpudRAAkzFIiBKY2SrBRLSQ9ZKYTD1NmjbFTS3RtYMZ2+lZU9oZVadWciuFV+bEBczVVdlaV6NihR9MLNpIgXUWYiANZz9U9/ZJp90gA2IRYN9Oc6Kl2ZYdq+JYRvnU1wDVeCZRFyKRdzWc2FZgCFOiiNhkRNxUKWZYHiZddDaGhCOIw2wqUY7CeALV2Sxf9miSKEgVkAgvGmQixYg12akdYolQ5FJDjNA8XCQmCYQmxYh/mo2sHCTG7CZXVmiN7biCKpph2Ek9nlQUTZN1FZQlgZlmmZQnTZl1WpnnKEqcTMo92S06SZkrAZgf0oflSBkTwQHZCg7TwjQ1gaia5pInCap3FdqJkmqfHJqRmSqiEEq7nanobqRliBT9HfQdzaDeTartFArxWq2kUMAaiAGngJDZjpmRZpmuqbpAJJv/1bwA1cwR0cDSTcwjXcw0XcxFWcTYkqs2KEcDppx6mVn4UcmJqmG2RMftxAntZWpU1ppD7dgUod1Vkd1uWH1n2a18FM2DUru4ZE2Z1d2k3/BDw8AnjYElRU3uVl3ublERp4Hujp5SqRnumhXrsWrMEeLMImrMIuLMM2rMM+LMRGrMROLMVWrMVeLMZmrMZubEMggsd+LMiGrMiOLMmWrMmeLMqmrMquLMu2rMu+LMzGrMzOLM3WrM3eLM7mrM7uLM/2rM/+LNAGrdAOLdG+rDSIINImrdIuLdM2rdM+LdRGrdROLdVWrdUy7TBcrdZuLdd2rdd+LdiGrdiOLdmWrf4NwwWkrdquLdu2rdu+LdzGrdzOLd3Wrd3eLd7mrd7uLd/2rd/+LeAGruAOLuEWruEeLuImruIuLuM2ruM+rt6KJ8dOLuVWruVeLuZmruZu/y7ndq7nfi7ohq7oji7plq7pni7qpq7qri7rtq7rvi7sxq7szi7t1q7t3i7ucsYFWEMJNEMwXEMGbFnu5u4emI1+SIGtfsSSDO/lGhA0UMMgVEMloNcGlCZINCPzUi7XDBJC6NM1hgT2Zu/GDgLZCCTQ1ZFIhK/4ZuwDdJCpJsI1DENQHUSf/Ek3aqcIIEIiPEAB/IE2LMFTNYEI3OQahIp1AUInOAIZVMIx0Yqt4IquNOJBhMAuoAIdbIjw7g43Csr6TiP5dtr7KsTBJMzCIMQF0AABhNcBOILPbIA0ZZl+IAgaDEwHrVQVvFHN3EzO4MckHgQ3nKTOYCTRMGQJd//wMNIqPQxAyDFET3LlT1YSRR3AGTRQE9xkSCnCBdDVNVxAHu0SHTzAJqCBG4iRN5EW7ugO7/jOiCADVnXDjnkDwtwYCFmNTxqOEc8iMtCqTw0DDNirW+bXA5Wid+JHh3LQFahdL4aAJRzA/CYCN+hkC8nXX85QkDFW0x3EOfjMjv0xXAryHctiGYjBGqjVAQCC38XRHKHvCdMAPCQECzgNIqsdmCgEwmzSI6FbPUGTIFrBMNgQKoMm+n7yMCJDANTASWoDRhWncSLnINOA8DoDLJtmL9ZUNxhnJHiJ88QTLifCK8PCQyhzRzGzME/jJrzDxHiaSi2o9JzwDcxRNHv/WC+iV10NqSQLYn3BAw3kUkOkc11B5TjjISJcg3YlRO/clYVeaH+wszsDKDxnEoDE6OjU8zYLpxQ8xEE/lyv9sx02jZsmhMkQw0HwqEMoNGi+M/bGyUb600H+HBqQjeLBAxKAmEhrtCzu0hq8b8YEw0FwaUJ4KRS3c0kzNPaizGKlFAQUQbss2mnV02VJMHzp11T2NIfRNB6GwMbkQXYiwcRA5ZkJ6ucQ6iAD9ceYNE4C3fgw1SvpTaPaM2r9Bz1g0vtEkZkFqpqBNVXbocnQwBUsgRUgwi68DC8mBKqqKq+BD0mPNUPXnAVwAzltwaFKAAy0Fyz8qUT/XCJsglERlMPEiUHM6OJg61ph3zUeUkO65scfWMMxKYLH5QfImXBJBnUFBQ3LJGV+SEEjKrWPoVYiOAG/lFylKslqX+QSi7YdcoAETEACSEMkqKPBmB3aZUQZnEECWK8TUMPmIUEGVwQHbIHkZTTROHe8Erd4jzd5l7d5nzd6p7d6rzd7t7d7vzd8x7d8zzd917d93zd+5zeWBAQAOw==" style="margin-top:1rem;" /></div></details></div></div>
+```{=html}
+<div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">TextStructure["The cat sat on the mat."]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhSAM0AfeJAKqqqtnZ2dzc3MjIyKWlpa2trRAQEI+Pj6mpqcbGxsLCwj4+PicnJx4eHoCAgODg4Kurq15eXtDQ0MXFxaenp0dHR6Ghofj4+EFBQdLS0hEREY2Njerq6ouLiw0NDSwsLNHR0fLy8r29vTo6OggICLy8vPHx8RISEm1tbdfX18zMzDw8PPn5+XV1dU5OTgwMDNXV1RoaGm9vbz09PYyMjLq6unZ2dpGRkT8/P1FRUQEBAUpKSoqKioODg3JyciEhIVJSUgMDAzY2NtjY2Dc3N6KiohgYGCIiItvb2x0dHfT09LKyslxcXPX19ff393BwcGtra3FxcZiYmCUlJRUVFbGxscPDw5aWll9fX5OTk1dXV9PT01ZWVhYWFqamprm5uWFhYR8fH8HBwd3d3a6urujo6EhISMfHx/v7+wAAAM/Pz6OjoyoqKlNTU9bW1rCwsAQEBEtLS3d3dzU1NZqamigoKC8vL6CgoFhYWLOzsxMTE87Ozg4ODubm5ikpKZmZmba2tgYGBkxMTO/v72pqajMzM+Tk5AUFBcvLy/////7+/nt7e25ubmdnZ5ycnMrKyi4uLuPj47e3twcHB3Nzc9ra2pCQkBkZGSsrK5KSkllZWf39/WlpaZ6enjs7O4eHh2VlZSYmJsTExOXl5Q8PD09PTwkJCV1dXaioqJeXl2xsbEZGRiAgIH19faSkpJSUlI6Ojri4uDk5OWZmZi0tLRwcHHx8fFBQUEJCQkRERENDQ8DAwDIyMvz8/GJiYufn54SEhK+vr4mJibW1tZubm01NTYWFhX5+fvb29lpaWklJSYKCgpWVlaysrPr6+lVVVbS0tBQUFNTU1OLi4t/f3+vr683Nzb+/vwICAlRUVJ2dnXp6euHh4b6+vuzs7N7e3iMjI0BAQBsbG2NjY/Dw8AoKCoGBgfPz8+7u7u3t7RcXF4aGhjg4ODAwMAsLC8nJyenp6TExMbu7uzQ0NJ+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fn5+fnyH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAASAM0AQAI/wATCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0iTKl3KtKnTp1CjSp1KtarVq1izat3KtavXr2DDih1LtqzZs2jTql3Ltq3bt3Djyp1Lt67du3jz6t3Lt6/fv4ADCx5MuLDhw4gTK17MuLHjx5AjS57clhsiRE0oa95s0TJmzqB5NkqTBlHo06gPji6dujVHaXliy55NOw8ggqtNu97NOTfv3xShkB5OvDjpSbhJ6x5sCIk3rM2fA/+ZDkmkhr4JR5+uUrjx78eTs/8mDCkNJazlz3PvyShNIezKC6dfj1JJtfv4oZHGgx+/dIHZDXaJeVgNqB59OmniHnzjCUgggixZQRoWCwUo2CEPWoXhgRDelMuCDFkY2IYdriRhGhQqtJo1hA1CGodTuZhhiTXZAWKFpLE4mIww0kjSiSkmtJobiSgiSRtsdOGHL2oshIYXXNRBxRSCSOHET03cwQQtRiQhhBxbKOTEEpx4EoYRkIAiCkKopAILMKqQ9qUcdNbpSkmKxDLLPLVQ4cctr/yy0Jhlnpnmmge1+WacacxZJ513NvWLMeGwYoQdnFyTUDByECOQkUgqyWRaYvxhySfHkJKGEY/WuUxBQxb/eWSSSzap0JNRTlnllTkdI8c3zpiDSS3PTJPIJpbYYYQZYR5EqJloqsmmm3DK2SqkPoIEJI5pUDOKLsZho01C3YDznThi9PRKNN9hM845BqGzjR7ggYKGQeqAZ1wbJEXCDniHJPPNQfLS+529+OpbHL9MfWLKd7kIatBo7STybbjjnqWFwsTpAStp3oJbnLjkmmscujm5k0YzCg4XzyacdAxPQQXXe29B+XJMGsPZdrStiqTJY0Qal/jSCihDpzFJJQfRE0QaQQBBxxJ3+DJJGoGkm1MvXAznhw9ZZMFJF6TFUVAZBptSSg9/8LCDDqRtY1AOONRtYxq11K133ceM/+SEH6R5csMwNXgRxRGk3WIQ2qSpzbbbcKchd0F0201a3nvzzZQvpAVRCg1XyJB0LcZ+HAMMMRBtNNLHMW2WOXuT9kLmdbvwcRpCq3500ks3/XTUU1d9ddY4qexJGrLYwAZp7eHSwg+ktUIQ42k43vbbcc+t992YZ953zz5PyK07cKzDwkDnrEBaFAaJAQfeKhSUQi1piMPrTSiQdkIzBTVhizs6IkgOqMADExSkBCRIwyEMkZBrvGglRRBfQTbRjBFU4yADLOABE7jABj5QKlkgjTgCmIhzJIM0hejFx4JwgvKdTyDpWx9bUMgg8pkPfepLA/sK4j74yY9+9ruJyv/SAARFJAId5SCNDARSCbjNgHIENCBBEKhABiLEgTMCX0h+JiTSuEMEBgEBaSpGkF58oHpEMkg3SCMFnLwDbh6QBkI4cJBfSNEg5iDNBjyYRZNEgTRLiIgdEZLHNOzxih+ECjk0gLUMGGQT4SBNJ273xTCOcYY3AloaKlkQMaaBjAMxIxoPssY0tNEmKiMFHQWCgTQc4QIDQdwPCjLIgxTykAfBYo+06BEuImQ1ZEDIgMpRkCpkDyF1SIMycAIE0txgI4ggjSb4uEuS8IA044CmNKkplSuQBgoIUQNpeHG7YB5kmJh8T4hIY06DoJMgxpRcQpK5TFSmoQIEeUYaGkH/kDms6iHRTMM0EdlHXoYPRdxaTkGIQJqbCQQMpElBQk6ojps4IYnuuF9FyKGCN1wzDbrgpkrSEQbSsIMCsKQIRz1KmpAStJpKKQZpJpCQ5emgD+JRKEEYmgaHooWG62zQQhtKEIimQaIIoagQ70mQjfFzIAyt6EJW+lGX5jKRBv2IL1UTn4PggDQa9acOGkHWspp1eUG4CQxIk4uKSIAHcaBfcTwhUpVQYx7DeUEOiFE6hrw1rsah60ulEgqwJiQCpNHUQEQ0kK+mQaNnAWpCEeLYsKZhrGbNLFqXis+BOHWnaZCqQf4qV+II9qoFzapGtjqxrhqksgQpqc6gdhMs/55iImQoxHA8wA4wtCITgaurSjZRBHZEjjRzYIYSEpLb3fb2t8EdbFROsEmF+IA0EMgpZQ2rFslqUqeN5a5AZKuztNqzswL5LFRDa5Dmkoa3vgVuGk5rEF2qVlsS7KJQCQLbgSQzDTcIm4AHHDZP2eQMpMmGRGZBGnVs4xGbGIgTootamJ7kF8Rog6pIY4RgHITBoX1whAUy4fkK1yniSAMcFEII0kBDu14V708zqV/wCqS/AvlvgAlMYAPXRGXoTYR6BRLVgoDYwRCWMIXri9X7boS1t7NxInCciFamoa9AeQBpPhARZpAGCHdUsokRIoYmu4QFVYjkZb9QEC8TMf/MJF4yD83MFN2mwYoH2QFp4rdY1xaEymeBmzonG+PHEsTKWP4JkJu6T9CKNhFuBrNBSkzfOafWyRaBMoxfK2MHkOYPRGkAaYYAkfJEA7JxHvNBVECap9JkGWwtiKlRnQhKJ4TVjY6KDEhjAYQgQ1Wk8Cljbyzjs7wgDQxgkJSp7Ok0gFooi/ZsronM3oHM2llyJgiuXc0VRMSCHHLRdJ/3G15DD8QN2EgDK5YrlOumoRgQeRgO5pjtgXCANAuwySYCkQZwFETe9Fa1Qe6dhnxHRQGkiYcKDXID0kQgyts1d1qWNwlaQ7zQGkW3utkNlGind9qJKPJAAH4QgleaIAT/N/hWFNEGDoMgLuIGkJ/5W+xxkMYM8DLIBaiRk2psWAYjJggLbJCJglAhDVTIOUESAD2BGwRxQSB1Sp6AghAgZAukWYXRka70gTC93rGEmtShYuUdEuQdKoOD68a97GKbhXNp8HGNIw5Zm6cB5wfZefGYKm1ui1wgR0+6Qb7u9IJAfexZgQBxrOqWmCdi2FMudgjaQZof0OGCAhmDMBpQCCPiBBpPcw8CBiGQXzCDFWkoB5axgO+XF0kBeNABHPhQeIIAgzRH+MLNlCCPLIikBvpbhBo8f6xYoD4NVSgI6wvuekXAXva0P7ntca97gfDe90r5hsGK8QgjwkMYQzxA/2vJTWyJo+VE5ZBCzlmwhx5oFPKAnnzlLz8QzXOe+DTxuJBB/vdELH8Bzfd8s1d7A3F7rlR9iXB9VXEMxPFobeF48Od2HGAGw6ED6nAEBjAc4vAAOpEHBkMafJBEpHEIHVAQo5BipKEBrJBAaeAH79By0idhlEcaJCAOHjCCcMYRzrABjASCDEAE7bBhaeAABnGCw6GCLOiCMCgmM5gGNXiDCpSDRWENSTAckyCE2AAMXEV+kWd+aLEaUGMEH3gbbEd3A0eBpGGBGKiBHHhejOZ31SYQRpiCK0gaSkiAJNaET4iDVBFBwzECMJdfvzRz5UZrigABRHBcpAEJWZAZO/8BD9uQNMPBB74wMAYRCTmQbsNBC8SgQu0RgwMxCOPwPsRxAnjADSPRBFewAqQ4HEFQAVpziZlIHJzoiXgoEKLYivpzikyBDnLQg52zCmcwiFwIaGehCMKQgcRBAqvQDZv2Z25XJIioiGnAiI7ohn3naAWBiZpIGrWYCJ+4ELlYHKaIilPhDI7FB4gCGtUgCRZgAYCAU0HhBm/QCaiQAM6wEH3wBtrwBmsXESFQA0WgDQWwBUFXEudgBQXgCARwDeCmj/zojxQRkANZkAfJFL1wBhRAD5KQDoiBBglAAcRAAQOADCDRju8Yj1Oxj/34jxBBkQRpkFexCV9AARKDaTj/mZM6uZM82ZM++ZNAGZRCOZREWZRGeZRImZRKuZRM2ZRO+ZRQGZVSOZVUWZVWeZVYmZVauZVc2ZVe+ZVgGZZiOZZbYQVmeZZomZZquZZs2ZZu+ZZwGZdyGZdjUBHeMJd4mZdwKQEd4Qx6+ZeAiZYXiREqEJiGeZiImZhomVIbAQKK+ZiQGZlryZcUwQKSeZmD+RCFeZmc2ZmQSUIM4QWiOZqkWZqmeZqomZqquZqs2Zqu2ZqgCRHT8Jq0WZusGQsd4QS2uZu8SZoLtxHQ0JvCOZzEWZykeY0aIQ/GuZzM2ZyniZsUoZvO6ZyZ6RB5MJ3YmZ3NOQwQQQHe+Z3gGZ7i/zme5Fme5nme6Jme6pmesfkQ07Ce8Bmf6AmdG+EE8nmf+Amev6kR0JCf/vmfABqg4ImcGSEPAnqgCJqg48lm0amgDlqdDZEHDjqhFJqgZEiWGJqhGrqhHNqhHvqhIBqiIjqiJFqiJnqiKJqiKrqiLNqiLvqiMBqjMjqjNFqjNnqjOJqjOrqjPNqjPvqjQBqkQjqkRFqkRnqkSJqkSrqkTNqkTvqkUBqlUjqlIboHCXClWGoNApCPQ/EI+MgTyHClZYAQApAA1+EUSnClXVcQA5AAY1oRo5AA5tgSIIClWDoAAfAfPvELCVCXCMGnfqoTVmqnCaClXCoUXnqoORGmbv9KpmZKFHVKqHiqp1CRqC7hCDSQqZqaqZYgCvvpEIrQCxBKEsxAAwR6E96QqdrgUwPxBTSQAE+hCFdAA++AEH2QqaRXEYhAAwrwEkWwqcD6BlKIE2pAA/IwEJvQC8RXrMe6E5gKrJzqqRIRqqM6EqV6qjaRqjSwqgfhqrA6FL8KrZkqrCpBrR/RC/t5rZdKA0vwDu6aAHnwrM3wqQyxq73KEuq6E9pKA1bQra8KFddAA712ELtAA5Giq7zqqzQQDO7qrgoAAZlaBNU6E8w6EGRAAzwnEBXrrOzasPAqr/S6EPbaEvmqE/varwbhrUTxqwzbsA8bsRPbESPrETdAA7//WbIrgalyVBCPsAE0wGcAlbAsga49kao+CwurRBAq+xRlkKkeaRB08LMXMbMt8au2QhCVkKmUyRPmKhAXm7FFIqo8obMG0bNSCxFUqxJEyxNGSwNIm7L/Cq40cLUDkbU0sLUmkbYbUbO/ubYtQbYGYQ00wAyKWq9CqxapmgWSYLD4lwhL+xSdQAM0dTY0sAFrKhF6qxJWexDNQAOSQBRfKxSAWxCCS7hoe7hpkbiL6wqN+7hBsbkG0bmfixKZmxF8SxOjSxBoMKtAKxBDAAid4AhkUAme1wQiQAE0sAYigHi/G7zDi39nAEbwAAGpcEHvIAKbMA0FIAXKCy8cUANr/0AHBYBniSAKIvBClSAC6cACCkAPqeAF78CqidC8wku8BBG9iTC91YsRiesEvFsQrrsJiPAGdLAGX5BoYiACn6oAInAzHCACApAIEkAAqWABJcBxJzEA22oQCkADCFAQvTDAdHAHgPCmAsECIsAiAVAEjpAI9noBYkAPUlAAAxCyIQG7BdENNEABAlEGIvANipAAxHChIUzAJGzCicANIjAKlnkHf0AGiDCYATAM9NAJ0NAsZbQHAEAHjgABbkB8o7C8iWAIIhC1wSACYxrGiCfABGzAiXa9m4AOgOAIfwAAATASuTsQu3u2A0G/zysQxou8ysu8wFu/0Cu91Gu92P+rvdwrAt4LvuJLvuaLvurLvu4Lv/Lrx/Y7EPirv5hnEf37v0obtwLBxgV8wDykwAXBwA4MwRJMwRaMwRmBwwShwzycCNMgAkiwjSLgOmggAqbxAAXwB9qwBEgsEG4ADY6wBvIwCoB8vMkrxucgAo9QEEogArWKrNZQj1JAALtwR1sgArBgrOdbvuU8EE0gBgDwB6jgkLoLzIkgzMRszBWRxwMRsNwpEGiwuDRwAONMA1WgQukArM26z5nqz5ka0AMRuRyQCZk6pr8KAhuQCVFLA3QwBP7sCOMMCzMjEH9gqgIRsClADzQgBaVKA/yjx/yM0AD9mwzt0DRwzBORuIn/kAI0cANh9rghQACcmqkbsI6JkAU0ULilmlJIwKvDQANZUNFSYJIoYQIPXRCY6noCYQKukKk1m6nVDMgeLA1Y7cI08AXP6rPJa3UmQcsDEQw0kAe+K7n8bE5WjdWautVg/Q7a4NOZigpOnQhoEAs+fQCZGgyM6QwWgNWA7bkDkQHGmgggAKykptjNmgg73dOVC9S/GglCTQxZnc0gYc8hTQP5zNcr/c8KPdCbWtCjndAuTQMNHdURPdEVfdEZvdEdnQgf7YgiTdImnakprc+p3dILzdowLdMSQdM2jdOj/K2SzdM0YAk+DdRCTdQ0YNRIrdRMvdezPLcHodZsnQiC/7sLBVGsinUBNEAAEtDPGl25eIYGSd3cR8sipq2px8oByVsQqVoE6FPYzZ3VWYAOAgENwJoZtz0QkZAKlJ0Fa0fe5o3e47wB5AsRnp0Ie1DeAyEGFv0Am4AGbvAKNADeinABZ0AD13ABN2PhdIDhGs7h4C0QkUsPxCABkXAvvwoLiGBEkUDasHQOkcugtg3SiRCwUkAP0gEDmYpnJo7iG97hwe3iMC6/xa3UAlEAKJ3cA9G52jAKm+AEKuCzaxfdbTbdAnHUUpAFEZwIZTCrA6ASyLviAkHfsIDdV40Az4EMouCzftoENKDZqDAEgrKrbmsNyMACASDUHnbW2r2NPv+b5vNLAyQdC9/g34kQ53Ne5zTgp7tqCRugAoE+6KA9EBp8A27gDGjwDaUKRgJRsBZwQYowBOMsj5CdCL1wAZ1bCRcQYa8uEFaO5VrO5QPxq1JQBVfSCyXQ3DFLERE+4QRQ4Ree4Unu4SAu4iQuEEfO7Cq+5C8e44kw4zWeCDee0Dm+4wMx4D9e0kIuEEROA0a+7Cmu5CzO6Nfu5BFB04kg5b3tuKSc61m+5TTQ5UP95dQ95mV+5jSg6BqB1tye6ALx3eEt4gJB3sxwAGegQk2AvNklEFZQ0tOQrNbgs4bw4SE+4vdC32tg3zSA3wLhqnfQ0emACjQAnc5wATXbBCn/Je4sUKpk4N8msLiWkHMOD/EST/HGTgM7axACADoCEQKWcACQLhDc4LaOSLVIr/QE0fSw4IiRmwVh9qsXmghLYNEO5dWoEO4+HrCw8JBee7dHn/RLn8RO3+5YvxHybgI1m0b2/q3TcNPIqQKM7nleThBFHeaZSvdg3d0o0djPJhCiQAPtlAgBQAOdsJ+JP7B4brC/6ed4+wuZepMj8avDkAGenwGIMAw+qw1cOgSZqlgC0fiPTxCRLxB+TkJNuwH+7QRCHahm3s9mfdW2PwzM4EiJcOuJELoCcet3fwN5v/cC8avaQHybINRP+xERXvRXkPZSPxBU//SHG/Vrf/1u/5/1NLD1XU8HX08DYe/RY++2Zh/8aC/Zaj/1bZ8IVz+sMw3liSD3NED3S1v8x08PfN/vfg8QNC4kSoSEBg03BAkiopFH4UOIESUqLEJjWAaMGRAN20BDmzOC1mjsgqiGxjWCFw5+eViGxhWCTW7QSPdQHo0aC2koUMiBxhqI3mgUUdiJxrSHo34+nNlL4R8aTQhOoOFK0cNgNOSlXNny5USwCh3RkDZxGo0DOiVFdEWjkk6eatm6JWj0DMSKSB6K0fowEg0CT6MSvEbjDcTC1uRCbPs2kd2wkSUKzaJQJDNkBL/QSEBQBI0SEJ1loeGNIGmQD5kJJGjw1VWFAgxLpv9dW6GTAzQMFUX4kAxZ0R0zNzkY6SHDVE4fFqAxwfZziRUPTp9uwTTBITQsKSf4u+xDZ8ITMWSGBiLzAYkq0aAXEQINNQQJ0Eg/MUPf7jSoKby/NdHn0MAj7bqKVIBoDRo4gO65sb6L6Ky0xqNhLcbokjAuCSl8qLG6aLjrobz2wo+gvwIjCCqpEinssIcSW2xDCyFbECzKLKMBM8048ww00QY8jYbUFFptoIJoeO0h2VicMTrqmrTORpIeMgmlRFSiAZ6HWKChskQkoIEMiMoYpj6GMPQJqIeEIoogcgaBjaBfaLiDKRq4Q5GgO2gIACKlmOHqyiy3XLLBidygoRP/gmqgoZtIGnW0GfrgUkhRRh1tFNL6jHKMIhrKeEgBDx8yBDDBUiwMQ4J2oUGxRCi19NJIH7NwyYhqJEiRtgDJsbNEmEsIIlRoGOPHIAkasjVSHxpjNlpprYLHRISypFhtaNji1Uiu0C0R4mhw4jhmH3rEomafqwgVEdJNdwAB3kwkOwsgqvbaV7XdjaFmIhqXpX0joirKcWkAQIKaIOpPod/2I+jgXnsDVliCKlJYIQQVLBcsQiUyFNFWF8UWU0kT9fhVkGXdNOJOPw1VoVFNTOROFXeCSFVWXSU5Vk0vTlPQW3PdlSBfIwp22ERQg+jYIl0maFkldT5X3XXbfUik/ygVmvJP8xRyhufC6puozJ6W2nnNhxQxgRtrjJpToaZKJWimcyDapCOQrMyaoK25XDDjiAb4kiAAmmxSjJATCVzw6QiXFUsQU1YIVK8TadntmBGZeVXAEU+8Q8Z1jpZngjiARb9ENuPVKOMgGoaGPYg9mrUiwVQ2XM9rW4+ZqxJoqOzRNafhG25B10mEiAKgAZXaI6sovsiya1qR3jUHnqGcIDIegI55fei+Km5NwJLprpAHHf5GTLh8/1CPaPXWE6nI04cqTh4iviHyW/bDNVcc7Mx9V9yozqEMfgSBnKiS9bLBVO5yrMof4v4HqNrZKnSj24/pOpS6h7DPdaqBnf9BZKcQpiVveZKhWklOwpUbiIZnWXGQRPiXiDMFZSgKUUQGUAG+g7xCTnSy02CUQANYuIsgUqBBNapEgxSCR3gMAo5EmEO8hskjI1PMQB8KxxwpUhEjVpTVdTg1wEQUkGUHhFlhLPcQmgFNK1rcYoe8qDMJEsQKNCCGMyyYCARNTCHPAsEGFUIaInkQIiGcH216QZr95EkvdFIBGzNgguD5CVwsgQgMaNC9QjKJeWHJzhIgMpNGshGSDBlGRCxZgESoClUE2QO5FMKCIUiCGAexBDcWZj7S3dI/eYwIHwV4oARlkiD1Ww4NoIhFR3LxhchkIxeN8kb3OY6AsSLI5E7/lEAzLlCNWdSiM0uTvDgmYo51vCMvIeLLogEJIoBE1geXRruLjTAyJZzaCY+YRK3xbAk0yEBYXhjDh/iEbPukAQKs4AYOpGOHbKuT27ZGg7sJiQbkUwk+8bZE2xAzdAfhYjfgE5kXenSTE3kmXqQZRmpKjozYpMEZFZLGRIg0MiWN4BLRUK1d3DEPNJBARBCElHQWS0sd/NvsmibMiSgqFgrNAncIYoFvgoU4klQIQxAQEVHQQHFI5dRIJ9JJiEAVmhBhiBewaswu7Q4xzZlIOgIXr0QwLBHn0yVBdtpTYAL1fcC0WCY1CkOOEkSm/pSZYD8aFpp+UWWRsyYCTdVS/23G9LBgSSwcbYpTnfLUp0fxYyKGGsiighCe5ZJnWOipkMJQqaIq5BKoRAERNCABeBcKG5piM8NE/CUTYFTo2t7W0GumSFsFeyUNNrCJe7J2UE18CDK8QINgKAQENEBl2SBQBEjSliDTrS4Nr5vdykYTjGKs5kof69JUYS4R3IWIIr7rRnBi9CwbQBCvqIK9h6CjI0r4UYoI8o2DgNadiSAkVyfylyxkNRYRgQYNHgERchQBAjG5EVmBGIKHbGKWvzJwNL0qEbA+pMEPfkiEJyyhDZCjbGPp6VmywIIM04EGKeAWAgCAXIW4xBJ1zc/EGHZfiOiXBvwVL1+RqlHnQv9XutRt73u1u14mWxe78G3ceFPa2DJCFo3qZa+UwRtVz4UzEfOt71QEFuT99vchACbqgAvstMmCRST+UUhbVItE5SbCkr4liGyQ92SfcEwhfFmTCtSqkLPwuW3BJUiwPlQ+jq1WiXqDDt8UkQ43yPgAfXVGKlgnLvZUdSRa83T7CDKu9lBZsY+7snkJo+WXqrfTn1YIqnkz1maJuXTT4ZUSZrIngqCBOaUcpsMSgQYEtXmQo+2wQmQMvgdExCVZGAUNsxKgqVr4kjhORFbpwG0DlxYsIc7xlqp9q2vrBLrcoQozYIxHtCrkDDSgg3IyQYNFEsRQaJLrb4gWV/z4Wk//ChG2K4scv2AK09KY1jSnSw3qVEuoarM2dSJsrepfspqxrlbglllFcYjfOr6UVshmDtLrXxN82GIxNrID3M5lH5W0cS7UobhtPHtKOp9cQgNU8JoIRTzXORJXSAiAmN1EkGMmazKUWW/TlognYiZBgplsmEHcEMi4j8md9HJhYQmwR+8VekzEFg5SBQnAYKewiHZIaGABbhTM7JdM+9rb3kWTWnnjLssyelOp3rKfve5AvHt4y6VrJ2hLR2bewBdggAgE3UDFOcoEIiKxBQswwygCjnmzJzLHlwiRIIBAYg1gIIG2SCFukbRwtQigAjVAytgdFvdXaeBJiJD+BqZH/z0NVK+TmbhCBRL4Da0T8YCONEMNIHjDQYagkM/AQh4wcIMIwNdPgNO5+cOIBH/lSpXGPz7ykz84xRLuVyCC3RJiJ/vc0a52wtsI7nIXPPzZLvIqL9aAfGep32EaeLqzv8IDM8siOYJIvJNTCPBzPMhDIvLbjMq7vMzbPJgzKhGiOYkgh9xoBgGghl3YAArIOTzrOoKwJIuQBhCYDzogEpGYv2LTBhiYBhVgBi/YgDUJgZmQBGqghndgBh1iu3cjjUeIBKeAmUQIllewghSYAE+7AxzTuYsywNoYiybJgiIQhcwoHtKYDikANoIog44YkQDYwoPowocIr73SuP2jnP9s8riHGEPqMEP8CzOMIgic055E2IPcqA7iqpJkO4g/+IX34DwL9LxaOQgoighFEIUwPIg16KtsAxc3iAXquIGToT0MjAhyoyFGpI5HFDUR8KjpOICtU4hIIKLpYAYBeAg0eBbqyAQSyz4bcT5ZVAg9pA4L6MM0NL++KiQqpA4rxEKJgEMu9MJEAMODoDNiLENjRMOTIi+V4r/ziiw7JEPfa0YCvBhdS4Q7fIhb5MOHuIA/pIFAHMQKFC2Za5basw8cSsa/uDOLSoS8ecN7m44i6CtkxI9f8LTpQAVkgAWySYGZmA4ACIFgoYHnSwRXHAwjRAOTm44lIBKu2zlDdAL/HnwEJIioLzyDBMCgRLDId8BIjTTEsABJkSTJ51ACARgACegDp1KIb3iHCUiBYkHJTDKBSkiAPQAq24CHR0iAMchCmywXnNRJntQJlCAHN0iASiAy0ZDBR3gAiQyoDJiARwiAbwkLARCFARgEsFBJlnTJodQZk8xIaeNIjyzLkRzLh1BLtowMsGzJl/wvmaTJt3yOEMgAUUAEI6IVJ/iGAbCGBxCiMkBLrUmBBBiAwZQIJZCGCZCGvmwCEEiAyUODDLACFVhLgkAHxIQBXLtL0AxN0RxN0ixNz2MIKjFN1VxN1mxN13xN2IxN2ZxN2qxN1URN28xN3dxN3uxN3/xN/+AMTuFkS9wcTuM8TuRMTuVcTuZsTucEKXt6TumcTuqsTuu8TuzMTok4B0MgP+38TvAMT/EcT/IsT/M8T/RMT/VcT/ZsT/d8T/iMT/mcT/qsT/u8T/zMT/3cT/7sT//8TwANUAEdUAItUIiYAARNUAVdUAZtUAd9UAiNUAmdUAqtUAu9UAzN0AwtRQPFzy3QUBANUREdURItURMFUXDr0NrwAhZtURd9URiNURmdURqtURu9URzNUR3dUR7t0R5dMBXFT3nwUSItUiM9UiRNUiUl0hQN0shYUiiNUimdUipNUiB10voc0irdUi7tUi9d0ibF0olQBDItUzM9UzRNU/81XVM2bVM3fVM4jVM5nVM6rVM7FdP6tFM93VM+7VM//VNA3VM8HVRCLVRDPVRETVRFXVRGbVRHfVRIjVRJnVRKrVRLvVRMzVRN3VRO7VRP/VRQDVVRHVVSLVVTPVVUTVVVXVVWbVVXfVVYjVVZnVVarVVbvVVczVVd3VVe7VVf/VVgDVZhHVZiLVZjPVZkTVZlXVZmbVZnfVZojVZpndZURYYESAAwQpKOFM3JvFZvHYAAgKZ0SABjpNZJtVZsnQgB2NbQ7FZvTcxwhYhxLVdzHU2h8Ii1vCPQlA7EeQOkMwjcq9dJvVdtyNfF21ff8VeFAFiBNc17pQErkAh9vcv/igiGd7jYd1CA9xgKHGPYhpXUh43YiJjYt6xYjM3YjS2Cjr29jyVNoegIWOjFnwnNdVwPzSqSgG1ZR31ZIJLZXcPDksVAm8Urj9VZ0KQMSagKISJZtlzHRIAUCilao2VUpFVaiGDasXRaqEWWnJ3asaQMBDSQh5jYTUCEN6CDNfiCo0wEMRCBl1QAEcgaDhCBVZQAAkgFCygBp5wIp/UoCuBaRVCBNbgCC5CH1fMsEVCMACgCR1AIZFCAZqADR0AFFXg3hagGSViDVFgDeUA6hfiFEnCFP0AFa6hJr9VOsNUWsS25g02Esj3btF3btn3buA0duu2Su83bvdUkifBb/8AVXMI13FdKXG5kXMeFXMmlXMslCMzVXM71XDgJ3dEt3YatkRRAIs/V1xCYD+04iA14rT9SJw4CLQVYnSyQMd8TSt6NiKxwiCIJBubIAqhIXwpDAGk4iCSahtWggUzYwzW4m/s1ri28gTdSgd7BoU7AsNMFT+vF3rE92O2lJe8F385KBKQxiPLdEvSVAvWNCKdtX2SB3y2ZXw6u3wDO3/3tX0cEYO8d4AI+4INIYIG1FebIF9bVHkjRhlHYBCdQgY7YFKMZX2SRgixYxWPUlsjxYAyMhI6oD4PYgFeYrT5YDRIjDmK4AVQYgl8otiVYvWnwNBggCGQAn0cwj3N4D/8bTgQAuwEJYAFFGAV6qIoFZmCeqeEHxmGP2OEe/uHwrckL9r0i/kIkDot1ZOJYeeIoJogpdjAKu+Is3uJEGIsuJogvpoEwToQxdjAzRmOYRKI2fuM4doUZ5hkTmAkOu6OzuAH/SgRDowfYCGKJAq3ZYwj35VuLmKKN6IiPQJaBU4h3oAFdCZ6q4A7imJaH8BsqATDbgiFm0IZbyZNLFmMdyrc5vk5bKWVjQ2UkWuVWfmXxjWVe5jAJqWUmuYiMyGWPSA2D6GWC+OVg7hZXIGbtKBZk/i+xCZ1mfmZLbq5prlcJuowsvCMA6ZGogmVjIaojua105BTNeRJkSQXroQH/aKAwGvDIXhgE6B0XKKIGGkiFDi43OogIvkjEarbOf76RgF68gRaQgv7mgwathO4zZmNoxHHoIoHoN5RoirZojIYIjSYIjvboiXCJkIaIkfZn0MEVYJ7ZoHkYojFoCyYqpSGwmUYZdIEadnEXg7iqh1iPiRbmrIwINEiHMZgAHYKiCyAiZrgGaljeRLheVMAWUDmxkjbppPaZn1UjcW40iAmq1wGtqX4zJb5qdcnqh9hqiPBqig5r2CJrs463tL4RtnZruJZrGqDraY0j0SGdO1If1aE1qP5jN6tqD5MMg8AkhVDs4DHACxCFO2jEs+6JtvBeVMgA2Jg33xHlurZr/0rb7ApaPM/OINB26agmRHQk5EyEiNNObJ1e7Yho7deejtgOndk2rtq+bd+RY3MNp3Gyo8Uzp4dAJ6hmp9jpPLBwWuVm2a5u7ki8jWq5gSp4h0owgekiaRg6AwTAoWa4inFBAEei5t2WTu6mI+/mFfDeIxrYuvFWtkK05Q+LCKlVD/ausLZ87/ie7/qGCA7Ab/3m74L6b6QmuZsaicz6OfMDKoP+rHN8p4VGmQdP765V7fYmCN2xAPXNcIlAA2kYHb1Yj64N8OwMpxHPqcW7q81CcZdW8fJu8PUNiwiXcQpXiBq/8XgT6x3HNwn/8Y8VMzJbPCDLrzRLp1VmM+Nmcf/kfvHDVu/UnnCqIojmM/FEoAooegT7hYjfeIdEUKjyMOoiuEQgb04uN64yi/MzA/MhU7NOZvDjPu/kTvMYZ3OIePMDjTc6b6G5ogE813ONFIM+D3GJ5TWCEDgvLDhii+SWS7Yyp+oWL+3IeHJIf2CRZV4dChCGcAVu64U8MeLfgAZuGwVY2IDd/XPm1LWHRDl2JnWW4zCXU3QzZ3Q0X1g1Jwgob/Ndi/VEqIZZ1wlbVwhcpwFdl+he//Vgh1bEUzztWUDxc0DWjUDM0zxmV/UzN+1ol/CvnnEJP4ABiIRKuAZYWA16KAOzubc7UIEA2IOK6ITU8AbwIYABGIJdmAn/oBX2Ya9DBDxYdG9AyVt3y2t3ClzyRXdweX/0eo9yaUeLfN/3fmcPgDcBgSd4gz+UhF/4hn/41s3sOuTGBLTFPTyIXAzHcSzHdxdsk3p2rmXukaf2mJmODSiBJqhHqRAAfpwOCvDKyzWK6bAECpZ459zGbtR5XOxDcaQOoE91oW8cosdZo6cwpC8MpWd6p08EqG+SqX+IarB6Wsr6P49LsYyImJxJ03XNalCDCQgABfaGkMwaNKgEFRCFDIBkiOiFUVCDBEiBcdd68tT7uVTjuvz71gz8wS/8ww82xWd8x38IyJd8yrd81V991m9913992I992Z992q9927993M99/93ffd7vfd//feAPfuEffuIvfuM/fuRPfieVgAFofud/fuiPfumffuqvfuu/fuzPfu3ffu7vfu//fvAPf/Eff/Iv/+kXPeWHVWj4UvZvf/d/f/iPf/nv0TBNf1dd//nPf/3ff/7vf/8HCC8CBwrclOggwoQKFzJs6PAhxIgSJ1KsaPEixowaN3Ls6PEjyJAiR07sZfIkypQqV7Js6fIlzJgyZ9KsafMmzpw6d/Ls6bMlyaBChxItavQo0qRKlzJt6vQp1KhSp1KtavUq1qxat3Lt6vUr2LBix5Ita/Ys2rRq17Jt6/Yt3Lhy59Kta/cu3rx69/Lt6/cv4MCCBxMubP/4MOLEihczbuz4MeTIkidTrmz5MubMmjdz7uz5M+jQokeTLm36NOrUqlezbu36NezYsmfTrm37Nu7cunfz7u37N/DgwocTL278OPLkypczb+78OfTo0qdT/wgiAfbsAwJ4E/srwRiH38MrvZBAxcPr2bFv754wXYIA1efTP12EBv78+d+YAKuGhjwIbdKLIgj9F6BSJtDwx0P36acffwghQcMS9Vl4oWf3BfMOh+8oAAF+RRjk1YEIkUEDNQYCuJSCDDqkYYcegkiDiAdNWCGGOepI2X1qLFQJfhJ8pUgvIyZyYooHEWkkUi02SIOPCgFJg5CJ3Lgjllky1iNDzdD/IElZSEbl5ItQdvmljRRquSabg3G5UDc0UHBQGSJ8o0gCxACCUC+IvEHHHYCUkRA3IozCghV3/EEGIkweFMAw9HQCzRYL9bIHAHQ4AoEbBR40ighDJGKICHTQEIwIg4IqqoB+0rHGF9Mo9I4Im6ADiCN/ACCfQt7UQEEq9JARgKeJkNnQmwrFOaeVFCqiwhpXWCDPOQixIII1iQRQhCMIIaNAM5qiogILClUjyRqprCFPfwr9UoIrf6BijTNt2ntvUckmFAwNeRw0BA0TSIIfGQeZ4Ap+N+T3CEKI0PCONvhtgB8qyCCERiwSH4BfMBcg5IwFCW+M5kEZrAjCg6Ka/4xgIiEQgJ8lEouS0H2RZEEDMQo/nJAKsOCXxcQ0lIDQsQzpixC//jYbTAE0ZPEHflJYnEgTNCAgTcIHTcMMfpmMvAYaCGFNwwY303CDewf1DDN+nYSAL9xxf3R0IpFMPMC/NNBDQyzfoHMQwgh0h4woE5PnsCUbqIAMCwHcPAxCA5zthjNofMO1CAjtQoMF1SSiyBA+91Hyir1c4GUlFxi0MkJeajPKJk6oMHElCN0nRRVOJNJLCTRYMiI5Pg9Qby8gTNxu0QvRbTcNeDe7wSvfHNQH1wxTjfMNqAzxy0GOUFhtItOkQgMMByET8yNhnwNiMwh9c7YELCgyyt6uyP99P/4W3TdMBv1ngMgwJqaNeiUCYDS4RkICQINO9CIhouDcQRxGg2whpAxk+5sTbkYeOtHgAG9LBMI2mIhhMCMDpGOZmE6otbM1gWd689R9tFGsTdwsHXlDhUJAJACDLehJ/PMfAAVIwAnRgFcHeQcN9nQ9GriigQepmiUIeBDJITAR71tDQjjADG0o6Q7kSwgyXkEDJOSvjGY02oP0Y4G0AcwSTjzIiaShEGdMzGIOY0bYEtI0vAGJHgsBUZRe5jyGsA6OKEJIIUUgtDnezD33QU9C1kADDhzkAoOYGkKaVjtj9bBMacTPGiVEg1QoRIHQeCJ+IpGQXgyiXQh5BA3/MpcIaowSkwqxIB0WIoZYnrGXZ7wPKkQgTGEOQADFKiAEExKxLUSimc68Ag0MkQiHtU8hsPxCIq65kAnQYBcHgSUNACABGyqkkEc6pAoT0TQ3LAQVNCDPfZKEEElSUiEXgMcQ5IGfTSZPIcAcJjGNmZAJIUBKNDjlEnXHEDSkYwwTEKMsLyAFGjDjGtQoV0JSQANUONOZCqABBHwpUvzRbSEAe0NCFOGzT+JHeg6rwUIUCIBE1IAGCViIyaqgpATEDD9XkMff0nlOeRayEzRQpUKGQYM9HOQ+g4rkJBEyiC9ADT+wyAQN+NlJZJkJIhPSaUKAhNCqZWEhFxDFHYJG/wOIIoQDCJMYKjLgqTOwFD/2Gyle8VVShQAMRwhRmAr8J9gM9MdhkFMIDGhQgERsTgEL2QMNDnsQFgxBEsSAGTeEmsJEFFKS8kRIFWgAgqbS4KnzjGoifqEwKUjCGtRwAjSyykMXcTVKD7lSWA+KSmYoxAkRu0EV3lEJE6BMlm09AwJ62owCwRIBg/UfGfMqXTbtNSF9VUjI0sYQh3lhIQ/MnAT6tZBrBKwh6QBAMs252ULmgUoLkaSsEuFUhdDzIAj40hsTEVut0haNtnUIbhEi1t0qJAGcs2VxG4IGafiMjEDy63QjfK/qIuS6CYmt9RBCjiKEdJpkI0dKvSekaf84DaMH2YSpUkA1BACASRa0hGbRydkVJYKbM00IOiamBNKa9iD1TUQNFeJO/j7pvw0J8EEGfD3eJuQN7k0IN2X5iKsp5ETvSEQ6KJpHhIihCJuUMJgvROG8QTgRFszCKBCiCH4NzcOneiM3mYFRSRo3EXSlgxOxGt2DuIEGWJwxCt+JSBorQWFGREPTJDtfqNbTew9ISJ+LONsiRwTJiVBy1ZiMkC/QwAoJqYYY2+wwVxipF17c4TmhYaRRwGIDOw4zrOkzZmSWORGAOFsNYCABhEkBfA5TmCtUIIETLRUhD5hYM9QAAifTgFWJUCQs5AEDN4ggZiYENEKcPIxI7Nj/nNzcwBdggAhJ3gDEPKYvahX5hwxEwg2h5VoeBsHJ/iqvq7dVU27HSlGDHmAAkajENWDBNXqUQREmwOodVBCAPdynEwT0RswIMIAh7EJhN401xqkzawuntHD6WUM9PSyCOOXnAKNNSCQmmh9moPogaAitfjKRYXNaIz8qo/FB9jAyUJLz3Iw+iDPcmZ8sSIDEC5w3pb2KbwHrdsnj1c8GStAErNKghQIYn34oIG+EVMOo+bHEzDIu9vuZoBIJ2EN8G3bARJDDDQmoxKvnOA0VPOIBHlsIBzIwgUcEQKEOEYAoBrB1hihBAAOQQB/yWxFuIGIA1Lj7NCbATqpUQw0T/wjAB73xjvS5vBIqEEUGuGepUaghASmI+9hTf0aHVVH1rn89blgP+9nTPjayrz3uc3+a2+u+977vzDkMYe7fE7/4xj8+8pOv/OUzv/nOfz70oy/96VO/+p1xRoyyr/3tc7/73v8++MMv/vGTv/zmPz/606/+9bO//e5/P/zjr/5jWt8zTiAI/vOv//3zv//+/z8ABqAADiABFqABHiACJqACLiADNqADPiAEJqCj1B9n3F8EXiAGZqAGbiAHdqAHfiAIhuACTiAFboYznCAKpqAKriALtqALviAMxqAMziAN1qAN3iAO5qAO7iAP9qAP/iAQBqEQ1mAJFqERHiESJv+hEi4hEzahEz4hFEahFE4hFVahFV4hFmahFm4hF3ahF34hGIahGI4hGZahGZ4hGqahGq4hG7ahG74hHMahHM4hHdahHd4hHubhaygBdoAPQwxAAvTYRYxCAmTWRajHerSHQsCHEemhI4aGIkDTlTFEH+DH4GGEwzjWRTjIJ0VImtTaI4biZpCXBTTE5tyVRmQiRsBIh3xIiIyIpYmiLGKGBdFAzyWEqUBSKtKAJuqPvTHdk8XiLA4jZRjVBCyEBW2AH2aEKm7iL7YOyQgjMU7jY0gOFynERxXUKrlKoPTYtWTLtnRLJl6AGNCDFBTAACiefzHEsnzis0TLtPjhN2r/C7d4C7iIC7mYC7qoC7ssxLvEy7xIETUOpFYoSGkphPecnMG8lc7QQIZVzdVkjcN8gfeQDX6swQeViZEdRNKkCdM4TVVJDSpF5NloDdfQgNdc5JaNTdkkjHatje+0TUYSJE1aBQV0UxbRACzYUuAMjseRR9XkjPZwjwTBgjUwjuOcCkQsz92kCfRITyJQj0OiklBuT/d8j9aMT/kkwvk4pPqwj/vAj/zQDxPVpFlWBcr01wMVDEIoEAM5UDJVDRO9kQRVyUH8An6IHlf9UP8EEQ0MUJpIGkIgkRLJZRMhBBQJJBUdxBVl0RZ10Rd5ixjt2VlWZlM4wcZI00EY1eQZ/5IcJQQd0YDFyCVSRdAoKV7THKMnfVIopQkpJVDTkeYqtZI18dIs1VJD4JIu2aZl9uZShFabeYPvCOQydVQzQZM0yaXfeRhK1aZkoVEwAVQxHRNBGZS+0cByJgRDORRbJYJEUZRFmdhBaBRHGedHdZhvpudRAAkzFIiBKY2SrBRLSQ9ZKYTD1NmjbFTS3RtYMZ2+lZU9oZVadWciuFV+bEBczVVdlaV6NihR9MLNpIgXUWYiANZz9U9/ZJp90gA2IRYN9Oc6Kl2ZYdq+JYRvnU1wDVeCZRFyKRdzWc2FZgCFOiiNhkRNxUKWZYHiZddDaGhCOIw2wqUY7CeALV2Sxf9miSKEgVkAgvGmQixYg12akdYolQ5FJDjNA8XCQmCYQmxYh/mo2sHCTG7CZXVmiN7biCKpph2Ek9nlQUTZN1FZQlgZlmmZQnTZl1WpnnKEqcTMo92S06SZkrAZgf0oflSBkTwQHZCg7TwjQ1gaia5pInCap3FdqJkmqfHJqRmSqiEEq7nanobqRliBT9HfQdzaDeTartFArxWq2kUMAaiAGngJDZjpmRZpmuqbpAJJv/1bwA1cwR0cDSTcwjXcw0XcxFWcTYkqs2KEcDppx6mVn4UcmJqmG2RMftxAntZWpU1ppD7dgUod1Vkd1uWH1n2a18FM2DUru4ZE2Z1d2k3/BDw8AnjYElRU3uVl3ublERp4Hujp5SqRnumhXrsWrMEeLMImrMIuLMM2rMM+LMRGrMROLMVWrMVeLMZmrMZubEMggsd+LMiGrMiOLMmWrMmeLMqmrMquLMu2rMu+LMzGrMzOLM3WrM3eLM7mrM7uLM/2rM/+LNAGrdAOLdG+rDSIINImrdIuLdM2rdM+LdRGrdROLdVWrdUy7TBcrdZuLdd2rdd+LdiGrdiOLdmWrf4NwwWkrdquLdu2rdu+LdzGrdzOLd3Wrd3eLd7mrd7uLd/2rd/+LeAGruAOLuEWruEeLuImruIuLuM2ruM+rt6KJ8dOLuVWruVeLuZmruZu/y7ndq7nfi7ohq7oji7plq7pni7qpq7qri7rtq7rvi7sxq7szi7t1q7t3i7ucsYFWEMJNEMwXEMGbFnu5u4emI1+SIGtfsSSDO/lGhA0UMMgVEMloNcGlCZINCPzUi7XDBJC6NM1hgT2Zu/GDgLZCCTQ1ZFIhK/4ZuwDdJCpJsI1DENQHUSf/Ek3aqcIIEIiPEAB/IE2LMFTNYEI3OQahIp1AUInOAIZVMIx0Yqt4IquNOJBhMAuoAIdbIjw7g43Csr6TiP5dtr7KsTBJMzCIMQF0AABhNcBOILPbIA0ZZl+IAgaDEwHrVQVvFHN3EzO4MckHgQ3nKTOYCTRMGQJd//wMNIqPQxAyDFET3LlT1YSRR3AGTRQE9xkSCnCBdDVNVxAHu0SHTzAJqCBG4iRN5EW7ugO7/jOiCADVnXDjnkDwtwYCFmNTxqOEc8iMtCqTw0DDNirW+bXA5Wid+JHh3LQFahdL4aAJRzA/CYCN+hkC8nXX85QkDFW0x3EOfjMjv0xXAryHctiGYjBGqjVAQCC38XRHKHvCdMAPCQECzgNIqsdmCgEwmzSI6FbPUGTIFrBMNgQKoMm+n7yMCJDANTASWoDRhWncSLnINOA8DoDLJtmL9ZUNxhnJHiJ88QTLifCK8PCQyhzRzGzME/jJrzDxHiaSi2o9JzwDcxRNHv/WC+iV10NqSQLYn3BAw3kUkOkc11B5TjjISJcg3YlRO/clYVeaH+wszsDKDxnEoDE6OjU8zYLpxQ8xEE/lyv9sx02jZsmhMkQw0HwqEMoNGi+M/bGyUb600H+HBqQjeLBAxKAmEhrtCzu0hq8b8YEw0FwaUJ4KRS3c0kzNPaizGKlFAQUQbss2mnV02VJMHzp11T2NIfRNB6GwMbkQXYiwcRA5ZkJ6ucQ6iAD9ceYNE4C3fgw1SvpTaPaM2r9Bz1g0vtEkZkFqpqBNVXbocnQwBUsgRUgwi68DC8mBKqqKq+BD0mPNUPXnAVwAzltwaFKAAy0Fyz8qUT/XCJsglERlMPEiUHM6OJg61ph3zUeUkO65scfWMMxKYLH5QfImXBJBnUFBQ3LJGV+SEEjKrWPoVYiOAG/lFylKslqX+QSi7YdcoAETEACSEMkqKPBmB3aZUQZnEECWK8TUMPmIUEGVwQHbIHkZTTROHe8Erd4jzd5l7d5nzd6p7d6rzd7t7d7vzd8x7d8zzd917d93zd+5zeWBAQAOw==" style="margin-top:1rem;" /></div></details></div>
+```
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">WolframAlpha["number of moons of Saturn", "Result"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhxgBTAPeXAPHx8fb185F/a6iaivHv7O/v7/Hv7eLd2KKTgt/a1YVyXMW8scW8ssrBuPf29O7r6OPj4+Hd18rCuYh1X9/a1L+1qYt4Y7Gkluvo5Orn5LOnmaSWhtzX0d3Y0tXOx5iIdol3Yfn5+JKAbeDc1uHh4Z2OfO/s6se+tPv7+p6Offb19KWXh5eHdIFtV7muoqaYiNPMxLerntDIwINwWaudjpaGc5SDb7KmmNTNxYRwWrCklq6hksK4rcnAt4d0XoNvWbqvoqCRgIJuV+Hc187Gvd/f36OUhNnTzI9+adPNxcvDue3q58/Iv6yfkN7e3uXh3Ozs7Id0X4JuWMzEu72zp5GAbOTg26ibi6GSgpuLeZ+Qfsa9s+Db1aWXhuLi4tvb25+Qf/T09IRxW+Xl5ZWFcoBsVfDu68G3rPTz8cjAtubm5unm4vr6+eTk5NvVz9zc3I17ZuLe2ambjKqdjpmJd+rq6u/t6raqne7s6djSy/f39+Xh3aOVhIp3Ytra2tnZ2Y99abCjlfPx7/v7+7qvo7SomuDg4O7u7tbPyIVxW/X19cO6r/r6+vLy8rOnmpeGdPj4+Ih1YNfRyc/Hv/7+/rGll4l2Yf////b29ujo6N3d3ePe2dbQyefn5/z8/Ip4Y6qcjfDw8L60qPPz89DJwc7HvtfRytHKwvr5+PXz8paFcpiHdezp5sS7sMe/tdvWz+fk37uwpMC2q9TOxpyMesvDuo17Z+jk4JWEcfDu7IZzXYt5ZNHKwZOCbrWpnPz8+/39/fv6+sS7sc3FvK6ik6eZiZKBbZOCb/j39pSDcNLLw/39/Ofj3/Py8LmuodrVzpqKePf29Y58Z+bj3uzq5unl4d7Z07Spm6GSgZB/a7arnpmJdu3t7Y58aOvo5enp6d3Y0ejl4Z2NfMi/tdrUzdXPx39rVPTy8K2gkritoIx6Zfn4962gkb2ypoFtVqeZivLw7resn6+ilJB+aubi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3SH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAxgBTAAAI/wAvCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0g3AmtUR82Yp1CjSp1KtarVq1izapWaiRukpBQHffPzp6zZs2jTql3Ltq3bt3DdGgoDFqKiN3Hz6t3Lt6/aTpTqMsRE9o+mUIwCC57oSVEns2MWJ/SE908nYJIxjqp8KLPBOmU7ec6oh+wXT6MFUvpiGHXqi1DKdk4dRvZrjKv/eHnNrezX2xfb/Pny+ltZ18ArPv6DeXSmss2TU3zOPDX16NIlXrcOPfv07s7Be/+PuD189fHkxWcuj/4h+/Xq2zN8L5m+fIX2Hf46daXYNImU3FFMMa8kVMmACCY4YIEL5XffQQ4iBIwVUzQRhTkYuiERFRiao0RCunQooogfNhjfgwhFeNASI2YY0RFldFiiQcDECIcROOaYIznznYiiQSoaBE8XRHZRhYsPLXHhHBjOWBAaGKZjUZA/UplQO0g2hIoq5iSzRpMIsYJhK1P6+CNBViKEpTkaOtSEOVLAAguYB22CIRNlnneJKLHg4YksuNgCSi6XUOLKI7vwUQ1CwQxTjDGfHDOHMsswxIwz0MAhDS3tUJPQFrFYIxAbw2CRzS7bxCKIQvAIY2Qf3WT/kQ44iqVoZkNrtsnQOBimcYmdHiL0TJYTsZeIOeW82eEqlBQioiXnGESOOi2aU8UmCa3DTowjunMHcgT1Yk48v87TYiT0IJSGGNVaS0StBaV5UK4NDSGEOegINASdBp2C4X8VGWuOOObQQkgyGGpjThBAmGuOKAVNwi00Z9QiCpfm/PDMQcg8gqEPlfTgyg45YIgNuAKJ2wQO99bgCxU0zIChMShfIgOGusQAAzh5jPNCC+a4s4etekpE70LwUMsCG/ryW1AaGHrDyw1drBBIGna4J96x5lwRmArsmhODQNTEmAJBe0hhjhC8EETJCTH6YIJBcmAIRjMEmeCx2AaJ/2uJO32YQhArn2CYh0HZwOmNkDoskpC8Bh09WQnmRDJ308EeJAuGP7RYxg4qNCSwD2gMFIQ52aAwUOLzEHS6OVMcJAqGxBQ0AoYihGBQMyCY04Kn4c5MaEGuYEguQchg+EGxtzIkOUIKl8EBQftmbtDs5nxSiStT8LABt6qEbqKexxpBECjmaEAQNObsMlAGGJKB0C+FuyO+QEya4wFCJ0RZkLhSwJtBxGSODRQEGCESAwa007yFPM8gysCQ46jnNLeNoxa/KEg1xGWOC/SIfOYw30BokD6CZMEcFhjIFjDEg4RcA0MwGAglLiSGSh3kHBjqxf/MkQhGYagEBlkhD/+dsTitFS0iDyRIONglB4NUz0kOMcOx3JGK8UWnfAQhofoGcsIUCuQGxCpIKTBUgYHAA0NZUEg3zFEGeImrhwhB40G20DkM4SIWFKgZkBqokCQKJBpHmoAbhkDIQkoAQy4g5C0g4ggMJcGKA8HiCEvIRRQO5AoYekJC8oAhXwwkHBjqgkI+gKEqDuSNCZHjQR5QCEuIyAc6SNfj+HilMA6kAe1qVxofQgQMMQCSApGkQLRoQksKhB0YikBCZoHIgbDIHFhQCMLMobtT8jCV5tilhLhACBaIaA7RIBp2kGhLgfQgl9XSZkNIgaEFAPMSwrwEMSvpxUs4A0OnSIgwfDn/kORZKyEINIcCdgjHg6iSISYQhQ9+CK+BQK4gfizUMiZK0YomAEMNmOg4F0IIGL4znvMUSBcHIgkMBSIhCMCQFQiyt6wd5AAYMmDwCmqQgzYkF4BIJoRoqaZyMuSJB0GFAbJFrRaYcpYgFOEwKSlSY15iHQkkwEGYESMkwGtz5rgDQgaAoVIQFJvqbMgZMNS2PR4RIhFdCFANIo9dgOMgKHgH7T54xRBmkamXGOlAsFqCag4kFdP0KkGiMQE2csIguDSHAGxoTZoWxKaXwAMdRIWQupkjDjs9a0KsIInOdhZ9D/OsJI7gkLXmjWsv8IApHaAMG2AIEKX7qF0nucWm/9bzEr+gBYaSkYcMsgEGSMDQOxp6CVPEqAXOuBwGbhCjH2Drq3HMZkEItjAPBIAg57gDhrZB3EvIy7LovGa9KiiQW3izQz+IArfMgYsHiG5rs11qbfPqVIGkQgsdcscE1nsFvxaEFDLDkALCZo4obKxv4jWodAmyhpRiqAzSYEEWBMCtbLg3sxtNCHjR6diEmLYglFAGFoAmImm0QnXvTepd56tXgixDCYkTERmU0d2BeIMGauuQGG4wPAR3eCCQFcg0KkGtEcFBFOtAaoZp4gBr8GIYHshAejRrEQwgggiSwMNDQtABUpyCCygOiTfcQIpSSMIbNXYoT4nyUPS0Gdkob/ZOnH0yZ+nUmSd3Bk6edbLn1/QZJ382z5LBApo/DOJMClFDWdKclEOURRGITggJDPMaSJTlG5E+yCDKoobbOKEsesh0QYTzh0bcBgBlKcKgH1SAshgiORAoiyYgHWlPLMcPmEiOJ4pgFghwAwCNCLawh03sYhv72MhOtrKXzWxih+IblflDKLIDDEX75drYzjZf3kCX8WBiDIXRtrjHne0icGPVtwGGHsLQ7Ha7+93wbvcoMMEIUdv73vjOt773ze9++/vfAA+4wAdO8IIb/OAIT7jCAx4QADs=" style="margin-top:1rem;" /></div></details></div></div>
+```{=html}
+<div><details open="open"><summary><h5 style="cursor:pointer;display:inline;padding:0.5rem 1rem 0 1rem;">WolframAlpha["number of moons of Saturn", "Result"]</h5></summary><div class="wl-results"><hr /><img src="data:image/jpeg;base64,R0lGODlhxgBTAPeXAPHx8fb185F/a6iaivHv7O/v7/Hv7eLd2KKTgt/a1YVyXMW8scW8ssrBuPf29O7r6OPj4+Hd18rCuYh1X9/a1L+1qYt4Y7Gkluvo5Orn5LOnmaSWhtzX0d3Y0tXOx5iIdol3Yfn5+JKAbeDc1uHh4Z2OfO/s6se+tPv7+p6Offb19KWXh5eHdIFtV7muoqaYiNPMxLerntDIwINwWaudjpaGc5SDb7KmmNTNxYRwWrCklq6hksK4rcnAt4d0XoNvWbqvoqCRgIJuV+Hc187Gvd/f36OUhNnTzI9+adPNxcvDue3q58/Iv6yfkN7e3uXh3Ozs7Id0X4JuWMzEu72zp5GAbOTg26ibi6GSgpuLeZ+Qfsa9s+Db1aWXhuLi4tvb25+Qf/T09IRxW+Xl5ZWFcoBsVfDu68G3rPTz8cjAtubm5unm4vr6+eTk5NvVz9zc3I17ZuLe2ambjKqdjpmJd+rq6u/t6raqne7s6djSy/f39+Xh3aOVhIp3Ytra2tnZ2Y99abCjlfPx7/v7+7qvo7SomuDg4O7u7tbPyIVxW/X19cO6r/r6+vLy8rOnmpeGdPj4+Ih1YNfRyc/Hv/7+/rGll4l2Yf////b29ujo6N3d3ePe2dbQyefn5/z8/Ip4Y6qcjfDw8L60qPPz89DJwc7HvtfRytHKwvr5+PXz8paFcpiHdezp5sS7sMe/tdvWz+fk37uwpMC2q9TOxpyMesvDuo17Z+jk4JWEcfDu7IZzXYt5ZNHKwZOCbrWpnPz8+/39/fv6+sS7sc3FvK6ik6eZiZKBbZOCb/j39pSDcNLLw/39/Ofj3/Py8LmuodrVzpqKePf29Y58Z+bj3uzq5unl4d7Z07Spm6GSgZB/a7arnpmJdu3t7Y58aOvo5enp6d3Y0ejl4Z2NfMi/tdrUzdXPx39rVPTy8K2gkritoIx6Zfn4962gkb2ypoFtVqeZivLw7resn6+ilJB+aubi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3ebi3SH/C05FVFNDQVBFMi4wAwEAAAAh+QQECgD/ACwAAAAAxgBTAAAI/wAvCRxIsKDBgwgTKlzIsKHDhxAjSpxIsaLFixgzatzIsaPHjyBDihxJsqTJkyhTqlzJsqXLlzBjypxJs6bNmzhz6tzJs6fPn0CDCh1KtKjRo0g3AmtUR82Yp1CjSp1KtarVq1izapWaiRukpBQHffPzp6zZs2jTql3Ltq3bt3DdGgoDFqKiN3Hz6t3Lt6/aTpTqMsRE9o+mUIwCC57oSVEns2MWJ/SE908nYJIxjqp8KLPBOmU7ec6oh+wXT6MFUvpiGHXqi1DKdk4dRvZrjKv/eHnNrezX2xfb/Pny+ltZ18ArPv6DeXSmss2TU3zOPDX16NIlXrcOPfv07s7Be/+PuD189fHkxWcuj/4h+/Xq2zN8L5m+fIX2Hf46daXYNImU3FFMMa8kVMmACCY4YIEL5XffQQ4iBIwVUzQRhTkYuiERFRiao0RCunQooogfNhjfgwhFeNASI2YY0RFldFiiQcDECIcROOaYIznznYiiQSoaBE8XRHZRhYsPLXHhHBjOWBAaGKZjUZA/UplQO0g2hIoq5iSzRpMIsYJhK1P6+CNBViKEpTkaOtSEOVLAAguYB22CIRNlnneJKLHg4YksuNgCSi6XUOLKI7vwUQ1CwQxTjDGfHDOHMsswxIwz0MAhDS3tUJPQFrFYIxAbw2CRzS7bxCKIQvAIY2Qf3WT/kQ44iqVoZkNrtsnQOBimcYmdHiL0TJYTsZeIOeW82eEqlBQioiXnGESOOi2aU8UmCa3DTowjunMHcgT1Yk48v87TYiT0IJSGGNVaS0StBaV5UK4NDSGEOegINASdBp2C4X8VGWuOOObQQkgyGGpjThBAmGuOKAVNwi00Z9QiCpfm/PDMQcg8gqEPlfTgyg45YIgNuAKJ2wQO99bgCxU0zIChMShfIgOGusQAAzh5jPNCC+a4s4etekpE70LwUMsCG/ryW1AaGHrDyw1drBBIGna4J96x5lwRmArsmhODQNTEmAJBe0hhjhC8EETJCTH6YIJBcmAIRjMEmeCx2AaJ/2uJO32YQhArn2CYh0HZwOmNkDoskpC8Bh09WQnmRDJ308EeJAuGP7RYxg4qNCSwD2gMFIQ52aAwUOLzEHS6OVMcJAqGxBQ0AoYihGBQMyCY04Kn4c5MaEGuYEguQchg+EGxtzIkOUIKl8EBQftmbtDs5nxSiStT8LABt6qEbqKexxpBECjmaEAQNObsMlAGGJKB0C+FuyO+QEya4wFCJ0RZkLhSwJtBxGSODRQEGCESAwa007yFPM8gysCQ46jnNLeNoxa/KEg1xGWOC/SIfOYw30BokD6CZMEcFhjIFjDEg4RcA0MwGAglLiSGSh3kHBjqxf/MkQhGYagEBlkhD/+dsTitFS0iDyRIONglB4NUz0kOMcOx3JGK8UWnfAQhofoGcsIUCuQGxCpIKTBUgYHAA0NZUEg3zFEGeImrhwhB40G20DkM4SIWFKgZkBqokCQKJBpHmoAbhkDIQkoAQy4g5C0g4ggMJcGKA8HiCEvIRRQO5AoYekJC8oAhXwwkHBjqgkI+gKEqDuSNCZHjQR5QCEuIyAc6SNfj+HilMA6kAe1qVxofQgQMMQCSApGkQLRoQksKhB0YikBCZoHIgbDIHFhQCMLMobtT8jCV5tilhLhACBaIaA7RIBp2kGhLgfQgl9XSZkNIgaEFAPMSwrwEMSvpxUs4A0OnSIgwfDn/kORZKyEINIcCdgjHg6iSISYQhQ9+CK+BQK4gfizUMiZK0YomAEMNmOg4F0IIGL4znvMUSBcHIgkMBSIhCMCQFQiyt6wd5AAYMmDwCmqQgzYkF4BIJoRoqaZyMuSJB0GFAbJFrRaYcpYgFOEwKSlSY15iHQkkwEGYESMkwGtz5rgDQgaAoVIQFJvqbMgZMNS2PR4RIhFdCFANIo9dgOMgKHgH7T54xRBmkamXGOlAsFqCag4kFdP0KkGiMQE2csIguDSHAGxoTZoWxKaXwAMdRIWQupkjDjs9a0KsIInOdhZ9D/OsJI7gkLXmjWsv8IApHaAMG2AIEKX7qF0nucWm/9bzEr+gBYaSkYcMsgEGSMDQOxp6CVPEqAXOuBwGbhCjH2Drq3HMZkEItjAPBIAg57gDhrZB3EvIy7LovGa9KiiQW3izQz+IArfMgYsHiG5rs11qbfPqVIGkQgsdcscE1nsFvxaEFDLDkALCZo4obKxv4jWodAmyhpRiqAzSYEEWBMCtbLg3sxtNCHjR6diEmLYglFAGFoAmImm0QnXvTepd56tXgixDCYkTERmU0d2BeIMGauuQGG4wPAR3eCCQFcg0KkGtEcFBFOtAaoZp4gBr8GIYHshAejRrEQwgggiSwMNDQtABUpyCCygOiTfcQIpSSMIbNXYoT4nyUPS0Gdkob/ZOnH0yZ+nUmSd3Bk6edbLn1/QZJ382z5LBApo/DOJMClFDWdKclEOURRGITggJDPMaSJTlG5E+yCDKoobbOKEsesh0QYTzh0bcBgBlKcKgH1SAshgiORAoiyYgHWlPLMcPmEiOJ4pgFghwAwCNCLawh03sYhv72MhOtrKXzWxih+IblflDKLIDDEX75drYzjZf3kCX8WBiDIXRtrjHne0icGPVtwGGHsLQ7Ha7+93wbvcoMMEIUdv73vjOt773ze9++/vfAA+4wAdO8IIb/OAIT7jCAx4QADs=" style="margin-top:1rem;" /></div></details></div>
+```
 
+```{=html}
 <div style="background-color:grey;height:2px;width:100%;"></div>
+```
 
+```{=html}
 <div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/math/wolframite/notebooks/index.clj">projects/math/wolframite/notebooks/index.clj</a></small></small></pre></div>
+```

### 2024-02-23 docs/projects/datavis/ggplot/repesenting.qmd
ggplot - rendered

--- 2024-02-08 docs/projects/noj/ggplot.qmd
@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: ggplot.html}
+  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: repesenting.html}
 code-block-background: true
@@
 </style>
-<script src="ggplot_files/md-default6.js" type="text/javascript"></script><script src="ggplot_files/md-default7.js" type="text/javascript"></script>
+<script src="repesenting_files/md-default6.js" type="text/javascript"></script><script src="repesenting_files/md-default7.js" type="text/javascript"></script>
 
@@
 
-# Exploring ggplot - DRAFT
-Here we explore [ggplot2](https://ggplot2.tidyverse.org/) from Clojure. The goal is to eventually implement a similar grammar in Clojure.
+# Using ggplot Clojure using ClojisR
 
@@
 ```clojure
-(ns ggplot
+(ns repesenting
   (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
@@
 
-The base R library:
+Requireing the base R library as a Clojure namespace:
 
@@
 </defs>
-<g id="surface445">
+<g id="surface266">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 ```{=html}
-<img src="ggplot_files/0.png" style="width:100%;" />
+<img src="repesenting_files/0.png" style="width:100%;" />
 ```
@@
 ```{=html}
-<img src="ggplot_files/1.png" style="width:100%;" />
+<img src="repesenting_files/1.png" style="width:100%;" />
 ```
@@
 ```{=html}
-<img src="ggplot_files/2.png" style="width:100%;" />
+<img src="repesenting_files/2.png" style="width:100%;" />
 ```
@@
 ```{=html}
-<img src="ggplot_files/3.png" style="width:100%;" />
+<img src="repesenting_files/3.png" style="width:100%;" />
 ```
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55801151ed28&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x556feb092c18&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55801151ed28&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x556feb092c18&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 
@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x55800c808140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x556fe5ccb140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x55800c808140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x556fe5ccb140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x558011cf7cd0&gt;\n&lt;environment: 0x5580173bcb00&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x556fe8978000&gt;\n&lt;environment: 0x556ff5d42868&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558011cff4b8&gt;\n&lt;environment: 0x5580173bcc88&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556fe8974af0&gt;\n&lt;environment: 0x556ff5d46510&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558011d098e0&gt;\n&lt;environment: 0x5580173bcdd8&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556fe89717a0&gt;\n&lt;environment: 0x556ff5d463c0&gt;\n",
      :domain [##-Inf ##Inf]},
@@
 ```{=html}
-<img src="ggplot_files/4.png" style="width:100%;" />
+<img src="repesenting_files/4.png" style="width:100%;" />
 ```
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55801c8071a8&gt;\n&lt;environment: 0x55801c3836c8&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x556feae855e8&gt;\n&lt;environment: 0x556ff3da9fc8&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x55801c807058&gt;\n&lt;environment: 0x55801c3836c8&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x556feae85738&gt;\n&lt;environment: 0x556ff3da9fc8&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55801c8159d0&gt;\n&lt;environment: 0x55801c386a88&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x556feae75a68&gt;\n&lt;environment: 0x556ff3dae4d0&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558011cff4b8&gt;\n&lt;environment: 0x55801c38a500&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556fe8974af0&gt;\n&lt;environment: 0x556ff3dae118&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558011d098e0&gt;\n&lt;environment: 0x55801c38a3b0&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556fe89717a0&gt;\n&lt;environment: 0x556ff3dadfc8&gt;\n",
      :domain [1.0E-100 ##Inf]},
@@
 ```{=html}
-<img src="ggplot_files/5.png" style="width:100%;" />
+<img src="repesenting_files/5.png" style="width:100%;" />
 ```
@@
 ```{=html}
-<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ggplot.clj">projects/noj/notebooks/ggplot.clj</a></small></small></pre></div>
-```
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/representing.clj">projects/datavis/ggplot/notebooks/representing.clj</a></small></small></pre></div>
+```

### 2024-02-23 docs/projects/noj/ggplot.qmd
Noj - rerendered

--- 2024-02-06 docs/projects/noj/ggplot.qmd
@@
 </style>
-<script src="ggplot_files/md-default4.js" type="text/javascript"></script><script src="ggplot_files/md-default5.js" type="text/javascript"></script>
+<script src="ggplot_files/md-default0.js" type="text/javascript"></script><script src="ggplot_files/md-default1.js" type="text/javascript"></script>
 
@@
 
-# Exploring ggplot - DRAFT
-Here we explore [ggplot2](https://ggplot2.tidyverse.org/) from Clojure. The goal is to eventually implement a similar grammar in Clojure.
-
-## Setup
-We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.
-
-::: {.sourceClojure}
-```clojure
-(ns ggplot
-  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
-            [clojisr.v1.applications.plotting :as plotting]
-            [scicloj.kindly.v4.kind :as kind]
-            [clojure.walk :as walk]
-            [tablecloth.api :as tc]))
-```
-:::
-
-Loading ggplot2:
-
-::: {.sourceClojure}
-```clojure
-(r/library "ggplot2")
-```
-:::
-
-::: {.printedClojure}
-```clojure
-[1] "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices" "utils"    
-[7] "datasets"  "methods"   "base"
-
-```
-:::
-
-The base R library:
-
-::: {.sourceClojure}
-```clojure
-(r/require-r '[base])
-```
-:::
-
-::: {.printedClojure}
-```clojure
-nil
-
-```
-:::
-
-## An example plot
-Here is how we may generate and display a plot:
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))"
-    r
-    plotting/plot->svg
-    kind/html)
-```
-:::
-
-```{=html}
-<?xml version="1.0" encoding="UTF-8"?>
-<svg xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink" width="504pt" height="504pt" viewBox="0 0 504 504" version="1.1">
-<defs>
-<g>
-<symbol overflow="visible" id="glyph0-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph0-1">
-<path style="stroke:none;" d="M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-2">
-<path style="stroke:none;" d="M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-3">
-<path style="stroke:none;" d="M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-4">
-<path style="stroke:none;" d="M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-5">
-<path style="stroke:none;" d="M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-6">
-<path style="stroke:none;" d="M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-7">
-<path style="stroke:none;" d="M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-8">
-<path style="stroke:none;" d="M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph1-1">
-<path style="stroke:none;" d="M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-2">
-<path style="stroke:none;" d="M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-3">
-<path style="stroke:none;" d="M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-4">
-<path style="stroke:none;" d="M 2.84375 -5.765625 L 1.875 -5.765625 L 1.875 -6.671875 C 1.875 -7.046875 2.09375 -7.25 2.515625 -7.25 C 2.59375 -7.25 2.625 -7.25 2.84375 -7.234375 L 2.84375 -8 C 2.625 -8.046875 2.515625 -8.046875 2.328125 -8.046875 C 1.46875 -8.046875 0.96875 -7.5625 0.96875 -6.75 L 0.96875 -5.765625 L 0.203125 -5.765625 L 0.203125 -5.015625 L 0.96875 -5.015625 L 0.96875 0 L 1.875 0 L 1.875 -5.015625 L 2.84375 -5.015625 Z M 2.84375 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-5">
-<path style="stroke:none;" d="M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-6">
-<path style="stroke:none;" d="M 2.984375 -5.921875 C 1.359375 -5.921875 0.390625 -4.78125 0.390625 -2.84375 C 0.390625 -0.890625 1.359375 0.25 3 0.25 C 4.625 0.25 5.609375 -0.90625 5.609375 -2.796875 C 5.609375 -4.796875 4.65625 -5.921875 2.984375 -5.921875 Z M 3 -5.078125 C 4.03125 -5.078125 4.65625 -4.234375 4.65625 -2.8125 C 4.65625 -1.4375 4.015625 -0.59375 3 -0.59375 C 1.984375 -0.59375 1.359375 -1.4375 1.359375 -2.84375 C 1.359375 -4.234375 1.984375 -5.078125 3 -5.078125 Z M 3 -5.078125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-7">
-<path style="stroke:none;" d="M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-8">
-<path style="stroke:none;" d="M 2.59375 -8.015625 C 1.5 -6.578125 0.796875 -4.578125 0.796875 -2.84375 C 0.796875 -1.109375 1.5 0.890625 2.59375 2.328125 L 3.203125 2.328125 C 2.234375 0.765625 1.6875 -1.09375 1.6875 -2.84375 C 1.6875 -4.59375 2.234375 -6.453125 3.203125 -8.015625 Z M 2.59375 -8.015625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-9">
-<path style="stroke:none;" d="M 1.671875 -8.015625 L 0.75 -8.015625 L 0.75 0 L 1.671875 0 Z M 1.671875 -8.015625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-10">
-<path style="stroke:none;" d="M 1.015625 2.328125 C 2.125 0.890625 2.8125 -1.109375 2.8125 -2.84375 C 2.8125 -4.578125 2.125 -6.578125 1.015625 -8.015625 L 0.421875 -8.015625 C 1.390625 -6.453125 1.921875 -4.59375 1.921875 -2.84375 C 1.921875 -1.09375 1.390625 0.765625 0.421875 2.328125 Z M 1.015625 2.328125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph2-1">
-<path style="stroke:none;" d="M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-2">
-<path style="stroke:none;" d="M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-3">
-<path style="stroke:none;" d="M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 "/>
-</symbol>
-</g>
-<clipPath id="clip1">
-  <path d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 234.925781 L 35.152344 234.925781 Z M 35.152344 23.246094 "/>
-</clipPath>
-<clipPath id="clip2">
-  <path d="M 35.152344 203 L 229.136719 203 L 229.136719 205 L 35.152344 205 Z M 35.152344 203 "/>
-</clipPath>
-<clipPath id="clip3">
-  <path d="M 35.152344 150 L 229.136719 150 L 229.136719 152 L 35.152344 152 Z M 35.152344 150 "/>
-</clipPath>
-<clipPath id="clip4">
-  <path d="M 35.152344 97 L 229.136719 97 L 229.136719 98 L 35.152344 98 Z M 35.152344 97 "/>
-</clipPath>
-<clipPath id="clip5">
-  <path d="M 35.152344 44 L 229.136719 44 L 229.136719 45 L 35.152344 45 Z M 35.152344 44 "/>
-</clipPath>
-<clipPath id="clip6">
-  <path d="M 67 23.246094 L 68 23.246094 L 68 234.925781 L 67 234.925781 Z M 67 23.246094 "/>
-</clipPath>
-<clipPath id="clip7">
-  <path d="M 101 23.246094 L 102 23.246094 L 102 234.925781 L 101 234.925781 Z M 101 23.246094 "/>
-</clipPath>
-<clipPath id="clip8">
-  <path d="M 135 23.246094 L 136 23.246094 L 136 234.925781 L 135 234.925781 Z M 135 23.246094 "/>
-</clipPath>
-<clipPath id="clip9">
-  <path d="M 169 23.246094 L 170 23.246094 L 170 234.925781 L 169 234.925781 Z M 169 23.246094 "/>
-</clipPath>
-<clipPath id="clip10">
-  <path d="M 203 23.246094 L 204 23.246094 L 204 234.925781 L 203 234.925781 Z M 203 23.246094 "/>
-</clipPath>
-<clipPath id="clip11">
-  <path d="M 35.152344 230 L 229.136719 230 L 229.136719 232 L 35.152344 232 Z M 35.152344 230 "/>
-</clipPath>
-<clipPath id="clip12">
-  <path d="M 35.152344 177 L 229.136719 177 L 229.136719 179 L 35.152344 179 Z M 35.152344 177 "/>
-</clipPath>
-<clipPath id="clip13">
-  <path d="M 35.152344 123 L 229.136719 123 L 229.136719 125 L 35.152344 125 Z M 35.152344 123 "/>
-</clipPath>
-<clipPath id="clip14">
-  <path d="M 35.152344 70 L 229.136719 70 L 229.136719 72 L 35.152344 72 Z M 35.152344 70 "/>
-</clipPath>
-<clipPath id="clip15">
-  <path d="M 50 23.246094 L 52 23.246094 L 52 234.925781 L 50 234.925781 Z M 50 23.246094 "/>
-</clipPath>
-<clipPath id="clip16">
-  <path d="M 84 23.246094 L 86 23.246094 L 86 234.925781 L 84 234.925781 Z M 84 23.246094 "/>
-</clipPath>
-<clipPath id="clip17">
-  <path d="M 118 23.246094 L 120 23.246094 L 120 234.925781 L 118 234.925781 Z M 118 23.246094 "/>
-</clipPath>
-<clipPath id="clip18">
-  <path d="M 151 23.246094 L 154 23.246094 L 154 234.925781 L 151 234.925781 Z M 151 23.246094 "/>
-</clipPath>
-<clipPath id="clip19">
-  <path d="M 185 23.246094 L 187 23.246094 L 187 234.925781 L 185 234.925781 Z M 185 23.246094 "/>
-</clipPath>
-<clipPath id="clip20">
-  <path d="M 219 23.246094 L 221 23.246094 L 221 234.925781 L 219 234.925781 Z M 219 23.246094 "/>
-</clipPath>
-<clipPath id="clip21">
-  <path d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 469.851562 L 35.152344 469.851562 Z M 35.152344 258.171875 "/>
-</clipPath>
-<clipPath id="clip22">
-  <path d="M 35.152344 438 L 229.136719 438 L 229.136719 440 L 35.152344 440 Z M 35.152344 438 "/>
-</clipPath>
-<clipPath id="clip23">
-  <path d="M 35.152344 385 L 229.136719 385 L 229.136719 387 L 35.152344 387 Z M 35.152344 385 "/>
-</clipPath>
-<clipPath id="clip24">
-  <path d="M 35.152344 332 L 229.136719 332 L 229.136719 333 L 35.152344 333 Z M 35.152344 332 "/>
-</clipPath>
-<clipPath id="clip25">
-  <path d="M 35.152344 278 L 229.136719 278 L 229.136719 280 L 35.152344 280 Z M 35.152344 278 "/>
-</clipPath>
-<clipPath id="clip26">
-  <path d="M 67 258.171875 L 68 258.171875 L 68 469.851562 L 67 469.851562 Z M 67 258.171875 "/>
-</clipPath>
-<clipPath id="clip27">
-  <path d="M 101 258.171875 L 102 258.171875 L 102 469.851562 L 101 469.851562 Z M 101 258.171875 "/>
-</clipPath>
-<clipPath id="clip28">
-  <path d="M 135 258.171875 L 136 258.171875 L 136 469.851562 L 135 469.851562 Z M 135 258.171875 "/>
-</clipPath>
-<clipPath id="clip29">
-  <path d="M 169 258.171875 L 170 258.171875 L 170 469.851562 L 169 469.851562 Z M 169 258.171875 "/>
-</clipPath>
-<clipPath id="clip30">
-  <path d="M 203 258.171875 L 204 258.171875 L 204 469.851562 L 203 469.851562 Z M 203 258.171875 "/>
-</clipPath>
-<clipPath id="clip31">
-  <path d="M 35.152344 465 L 229.136719 465 L 229.136719 467 L 35.152344 467 Z M 35.152344 465 "/>
-</clipPath>
-<clipPath id="clip32">
-  <path d="M 35.152344 411 L 229.136719 411 L 229.136719 414 L 35.152344 414 Z M 35.152344 411 "/>
-</clipPath>
-<clipPath id="clip33">
-  <path d="M 35.152344 358 L 229.136719 358 L 229.136719 360 L 35.152344 360 Z M 35.152344 358 "/>
-</clipPath>
-<clipPath id="clip34">
-  <path d="M 35.152344 305 L 229.136719 305 L 229.136719 307 L 35.152344 307 Z M 35.152344 305 "/>
-</clipPath>
-<clipPath id="clip35">
-  <path d="M 50 258.171875 L 52 258.171875 L 52 469.851562 L 50 469.851562 Z M 50 258.171875 "/>
-</clipPath>
-<clipPath id="clip36">
-  <path d="M 84 258.171875 L 86 258.171875 L 86 469.851562 L 84 469.851562 Z M 84 258.171875 "/>
-</clipPath>
-<clipPath id="clip37">
-  <path d="M 118 258.171875 L 120 258.171875 L 120 469.851562 L 118 469.851562 Z M 118 258.171875 "/>
-</clipPath>
-<clipPath id="clip38">
-  <path d="M 151 258.171875 L 154 258.171875 L 154 469.851562 L 151 469.851562 Z M 151 258.171875 "/>
-</clipPath>
-<clipPath id="clip39">
-  <path d="M 185 258.171875 L 187 258.171875 L 187 469.851562 L 185 469.851562 Z M 185 258.171875 "/>
-</clipPath>
-<clipPath id="clip40">
-  <path d="M 219 258.171875 L 221 258.171875 L 221 469.851562 L 219 469.851562 Z M 219 258.171875 "/>
-</clipPath>
-<clipPath id="clip41">
-  <path d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 234.925781 L 234.617188 234.925781 Z M 234.617188 23.246094 "/>
-</clipPath>
-<clipPath id="clip42">
-  <path d="M 234.617188 203 L 428.601562 203 L 428.601562 205 L 234.617188 205 Z M 234.617188 203 "/>
-</clipPath>
-<clipPath id="clip43">
-  <path d="M 234.617188 150 L 428.601562 150 L 428.601562 152 L 234.617188 152 Z M 234.617188 150 "/>
-</clipPath>
-<clipPath id="clip44">
-  <path d="M 234.617188 97 L 428.601562 97 L 428.601562 98 L 234.617188 98 Z M 234.617188 97 "/>
-</clipPath>
-<clipPath id="clip45">
-  <path d="M 234.617188 44 L 428.601562 44 L 428.601562 45 L 234.617188 45 Z M 234.617188 44 "/>
-</clipPath>
-<clipPath id="clip46">
-  <path d="M 266 23.246094 L 268 23.246094 L 268 234.925781 L 266 234.925781 Z M 266 23.246094 "/>
-</clipPath>
-<clipPath id="clip47">
-  <path d="M 300 23.246094 L 302 23.246094 L 302 234.925781 L 300 234.925781 Z M 300 23.246094 "/>
-</clipPath>
-<clipPath id="clip48">
-  <path d="M 334 23.246094 L 336 23.246094 L 336 234.925781 L 334 234.925781 Z M 334 23.246094 "/>
-</clipPath>
-<clipPath id="clip49">
-  <path d="M 368 23.246094 L 370 23.246094 L 370 234.925781 L 368 234.925781 Z M 368 23.246094 "/>
-</clipPath>
-<clipPath id="clip50">
-  <path d="M 402 23.246094 L 404 23.246094 L 404 234.925781 L 402 234.925781 Z M 402 23.246094 "/>
-</clipPath>
-<clipPath id="clip51">
-  <path d="M 234.617188 230 L 428.601562 230 L 428.601562 232 L 234.617188 232 Z M 234.617188 230 "/>
-</clipPath>
-<clipPath id="clip52">
-  <path d="M 234.617188 177 L 428.601562 177 L 428.601562 179 L 234.617188 179 Z M 234.617188 177 "/>
-</clipPath>
-<clipPath id="clip53">
-  <path d="M 234.617188 123 L 428.601562 123 L 428.601562 125 L 234.617188 125 Z M 234.617188 123 "/>
-</clipPath>
-<clipPath id="clip54">
-  <path d="M 234.617188 70 L 428.601562 70 L 428.601562 72 L 234.617188 72 Z M 234.617188 70 "/>
-</clipPath>
-<clipPath id="clip55">
-  <path d="M 249 23.246094 L 251 23.246094 L 251 234.925781 L 249 234.925781 Z M 249 23.246094 "/>
-</clipPath>
-<clipPath id="clip56">
-  <path d="M 283 23.246094 L 285 23.246094 L 285 234.925781 L 283 234.925781 Z M 283 23.246094 "/>
-</clipPath>
-<clipPath id="clip57">
-  <path d="M 317 23.246094 L 319 23.246094 L 319 234.925781 L 317 234.925781 Z M 317 23.246094 "/>
-</clipPath>
-<clipPath id="clip58">
-  <path d="M 351 23.246094 L 353 23.246094 L 353 234.925781 L 351 234.925781 Z M 351 23.246094 "/>
-</clipPath>
-<clipPath id="clip59">
-  <path d="M 385 23.246094 L 387 23.246094 L 387 234.925781 L 385 234.925781 Z M 385 23.246094 "/>
-</clipPath>
-<clipPath id="clip60">
-  <path d="M 419 23.246094 L 421 23.246094 L 421 234.925781 L 419 234.925781 Z M 419 23.246094 "/>
-</clipPath>
-<clipPath id="clip61">
-  <path d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 469.851562 L 234.617188 469.851562 Z M 234.617188 258.171875 "/>
-</clipPath>
-<clipPath id="clip62">
-  <path d="M 234.617188 438 L 428.601562 438 L 428.601562 440 L 234.617188 440 Z M 234.617188 438 "/>
-</clipPath>
-<clipPath id="clip63">
-  <path d="M 234.617188 385 L 428.601562 385 L 428.601562 387 L 234.617188 387 Z M 234.617188 385 "/>
-</clipPath>
-<clipPath id="clip64">
-  <path d="M 234.617188 332 L 428.601562 332 L 428.601562 333 L 234.617188 333 Z M 234.617188 332 "/>
-</clipPath>
-<clipPath id="clip65">
-  <path d="M 234.617188 278 L 428.601562 278 L 428.601562 280 L 234.617188 280 Z M 234.617188 278 "/>
-</clipPath>
-<clipPath id="clip66">
-  <path d="M 266 258.171875 L 268 258.171875 L 268 469.851562 L 266 469.851562 Z M 266 258.171875 "/>
-</clipPath>
-<clipPath id="clip67">
-  <path d="M 300 258.171875 L 302 258.171875 L 302 469.851562 L 300 469.851562 Z M 300 258.171875 "/>
-</clipPath>
-<clipPath id="clip68">
-  <path d="M 334 258.171875 L 336 258.171875 L 336 469.851562 L 334 469.851562 Z M 334 258.171875 "/>
-</clipPath>
-<clipPath id="clip69">
-  <path d="M 368 258.171875 L 370 258.171875 L 370 469.851562 L 368 469.851562 Z M 368 258.171875 "/>
-</clipPath>
-<clipPath id="clip70">
-  <path d="M 402 258.171875 L 404 258.171875 L 404 469.851562 L 402 469.851562 Z M 402 258.171875 "/>
-</clipPath>
-<clipPath id="clip71">
-  <path d="M 234.617188 465 L 428.601562 465 L 428.601562 467 L 234.617188 467 Z M 234.617188 465 "/>
-</clipPath>
-<clipPath id="clip72">
-  <path d="M 234.617188 411 L 428.601562 411 L 428.601562 414 L 234.617188 414 Z M 234.617188 411 "/>
-</clipPath>
-<clipPath id="clip73">
-  <path d="M 234.617188 358 L 428.601562 358 L 428.601562 360 L 234.617188 360 Z M 234.617188 358 "/>
-</clipPath>
-<clipPath id="clip74">
-  <path d="M 234.617188 305 L 428.601562 305 L 428.601562 307 L 234.617188 307 Z M 234.617188 305 "/>
-</clipPath>
-<clipPath id="clip75">
-  <path d="M 249 258.171875 L 251 258.171875 L 251 469.851562 L 249 469.851562 Z M 249 258.171875 "/>
-</clipPath>
-<clipPath id="clip76">
-  <path d="M 283 258.171875 L 285 258.171875 L 285 469.851562 L 283 469.851562 Z M 283 258.171875 "/>
-</clipPath>
-<clipPath id="clip77">
-  <path d="M 317 258.171875 L 319 258.171875 L 319 469.851562 L 317 469.851562 Z M 317 258.171875 "/>
-</clipPath>
-<clipPath id="clip78">
-  <path d="M 351 258.171875 L 353 258.171875 L 353 469.851562 L 351 469.851562 Z M 351 258.171875 "/>
-</clipPath>
-<clipPath id="clip79">
-  <path d="M 385 258.171875 L 387 258.171875 L 387 469.851562 L 385 469.851562 Z M 385 258.171875 "/>
-</clipPath>
-<clipPath id="clip80">
-  <path d="M 419 258.171875 L 421 258.171875 L 421 469.851562 L 419 469.851562 Z M 419 258.171875 "/>
-</clipPath>
-<clipPath id="clip81">
-  <path d="M 35.152344 240.402344 L 229.136719 240.402344 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 240.402344 "/>
-</clipPath>
-<clipPath id="clip82">
-  <path d="M 234.617188 240.402344 L 428.601562 240.402344 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 240.402344 "/>
-</clipPath>
-<clipPath id="clip83">
-  <path d="M 35.152344 5.480469 L 229.136719 5.480469 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 5.480469 "/>
-</clipPath>
-<clipPath id="clip84">
-  <path d="M 234.617188 5.480469 L 428.601562 5.480469 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 5.480469 "/>
-</clipPath>
-</defs>
-<g id="surface931">
-<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
-<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 "/>
-<g clip-path="url(#clip1)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 234.925781 L 229.136719 234.925781 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 234.925781 "/>
-</g>
-<g clip-path="url(#clip2)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 204.210938 L 229.136719 204.210938 "/>
-</g>
-<g clip-path="url(#clip3)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 150.910156 L 229.136719 150.910156 "/>
-</g>
-<g clip-path="url(#clip4)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 97.613281 L 229.136719 97.613281 "/>
-</g>
-<g clip-path="url(#clip5)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 44.3125 L 229.136719 44.3125 "/>
-</g>
-<g clip-path="url(#clip6)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 234.925781 L 67.707031 23.246094 "/>
-</g>
-<g clip-path="url(#clip7)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 234.925781 L 101.621094 23.246094 "/>
-</g>
-<g clip-path="url(#clip8)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 234.925781 L 135.535156 23.246094 "/>
-</g>
-<g clip-path="url(#clip9)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 234.925781 L 169.449219 23.246094 "/>
-</g>
-<g clip-path="url(#clip10)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 234.925781 L 203.363281 23.246094 "/>
-</g>
-<g clip-path="url(#clip11)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 230.859375 L 229.136719 230.859375 "/>
-</g>
-<g clip-path="url(#clip12)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 177.558594 L 229.136719 177.558594 "/>
-</g>
-<g clip-path="url(#clip13)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 124.261719 L 229.136719 124.261719 "/>
-</g>
-<g clip-path="url(#clip14)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 70.960938 L 229.136719 70.960938 "/>
-</g>
-<g clip-path="url(#clip15)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 234.925781 L 50.75 23.246094 "/>
-</g>
-<g clip-path="url(#clip16)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 234.925781 L 84.664062 23.246094 "/>
-</g>
-<g clip-path="url(#clip17)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 234.925781 L 118.578125 23.246094 "/>
-</g>
-<g clip-path="url(#clip18)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 234.925781 L 152.492188 23.246094 "/>
-</g>
-<g clip-path="url(#clip19)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 234.925781 L 186.40625 23.246094 "/>
-</g>
-<g clip-path="url(#clip20)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 234.925781 L 220.320312 23.246094 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 118.933594 C 120.53125 121.539062 116.625 121.539062 116.625 118.933594 C 116.625 116.324219 120.53125 116.324219 120.53125 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 150.910156 C 93.402344 153.515625 89.492188 153.515625 89.492188 150.910156 C 89.492188 148.304688 93.402344 148.304688 93.402344 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 124.261719 C 134.097656 126.867188 130.1875 126.867188 130.1875 124.261719 C 130.1875 121.65625 134.097656 121.65625 134.097656 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 108.273438 C 174.796875 110.878906 170.886719 110.878906 170.886719 108.273438 C 170.886719 105.664062 174.796875 105.664062 174.796875 108.273438 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 113.601562 C 154.445312 116.207031 150.539062 116.207031 150.539062 113.601562 C 150.539062 110.996094 154.445312 110.996094 154.445312 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 129.589844 C 140.882812 132.199219 136.972656 132.199219 136.972656 129.589844 C 136.972656 126.984375 140.882812 126.984375 140.882812 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 102.941406 C 161.230469 105.546875 157.320312 105.546875 157.320312 102.941406 C 157.320312 100.335938 161.230469 100.335938 161.230469 102.941406 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 92.28125 C 154.445312 94.890625 150.539062 94.890625 150.539062 92.28125 C 150.539062 89.675781 154.445312 89.675781 154.445312 92.28125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 92.28125 C 147.664062 94.890625 143.753906 94.890625 143.753906 92.28125 C 143.753906 89.675781 147.664062 89.675781 147.664062 92.28125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 140.25 C 106.96875 142.859375 103.058594 142.859375 103.058594 140.25 C 103.058594 137.644531 106.96875 137.644531 106.96875 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 129.589844 C 113.75 132.199219 109.839844 132.199219 109.839844 129.589844 C 109.839844 126.984375 113.75 126.984375 113.75 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 118.933594 C 140.882812 121.539062 136.972656 121.539062 136.972656 118.933594 C 136.972656 116.324219 140.882812 116.324219 140.882812 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 113.601562 C 140.882812 116.207031 136.972656 116.207031 136.972656 113.601562 C 136.972656 110.996094 140.882812 110.996094 140.882812 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 150.910156 C 106.96875 153.515625 103.058594 153.515625 103.058594 150.910156 C 103.058594 148.304688 106.96875 148.304688 106.96875 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 145.582031 C 120.53125 148.1875 116.625 148.1875 116.625 145.582031 C 116.625 142.976562 120.53125 142.976562 120.53125 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 161.570312 C 106.96875 164.175781 103.058594 164.175781 103.058594 161.570312 C 103.058594 158.964844 106.96875 158.964844 106.96875 161.570312 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 145.582031 C 127.316406 148.1875 123.40625 148.1875 123.40625 145.582031 C 123.40625 142.976562 127.316406 142.976562 127.316406 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 150.910156 C 120.53125 153.515625 116.625 153.515625 116.625 150.910156 C 116.625 148.304688 120.53125 148.304688 120.53125 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 118.933594 C 134.097656 121.539062 130.1875 121.539062 130.1875 118.933594 C 130.1875 116.324219 134.097656 116.324219 134.097656 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 124.261719 C 147.664062 126.867188 143.753906 126.867188 143.753906 124.261719 C 143.753906 121.65625 147.664062 121.65625 147.664062 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 108.273438 C 147.664062 110.878906 143.753906 110.878906 143.753906 108.273438 C 143.753906 105.664062 147.664062 105.664062 147.664062 108.273438 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 86.953125 C 174.796875 89.558594 170.886719 89.558594 170.886719 86.953125 C 170.886719 84.347656 174.796875 84.347656 174.796875 86.953125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 166.902344 C 100.183594 169.507812 96.273438 169.507812 96.273438 166.902344 C 96.273438 164.292969 100.183594 164.292969 100.183594 166.902344 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 208.707031 49.644531 C 208.707031 52.25 204.800781 52.25 204.800781 49.644531 C 204.800781 47.035156 208.707031 47.035156 208.707031 49.644531 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 222.273438 49.644531 C 222.273438 52.25 218.363281 52.25 218.363281 49.644531 C 218.363281 47.035156 222.273438 47.035156 222.273438 49.644531 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 181.578125 65.632812 C 181.578125 68.238281 177.667969 68.238281 177.667969 65.632812 C 177.667969 63.027344 181.578125 63.027344 181.578125 65.632812 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 134.921875 C 113.75 137.527344 109.839844 137.527344 109.839844 134.921875 C 109.839844 132.316406 113.75 132.316406 113.75 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 84.664062 165.398438 L 86.382812 163.894531 L 88.097656 162.386719 L 91.535156 159.371094 L 93.25 157.859375 L 94.96875 156.347656 L 96.683594 154.832031 L 98.402344 153.3125 L 100.117188 151.792969 L 103.554688 148.738281 L 105.269531 147.207031 L 106.988281 145.671875 L 108.703125 144.128906 L 110.421875 142.582031 L 112.140625 141.027344 L 113.855469 139.46875 L 115.574219 137.902344 L 117.289062 136.328125 L 119.007812 134.742188 L 120.726562 133.148438 L 122.441406 131.546875 L 124.160156 129.933594 L 125.875 128.3125 L 127.59375 126.679688 L 129.308594 125.035156 L 131.027344 123.382812 L 132.746094 121.71875 L 134.460938 120.050781 L 136.179688 118.371094 L 137.894531 116.683594 L 139.613281 114.988281 L 141.332031 113.289062 L 143.046875 111.582031 L 144.765625 109.871094 L 146.480469 108.152344 L 148.199219 106.433594 L 149.917969 104.710938 L 151.632812 102.980469 L 153.351562 101.25 L 155.066406 99.515625 L 156.785156 97.78125 L 158.503906 96.042969 L 160.21875 94.300781 L 161.9375 92.558594 L 163.652344 90.816406 L 165.371094 89.070312 L 167.085938 87.324219 L 168.804688 85.578125 L 170.523438 83.828125 L 172.238281 82.078125 L 173.957031 80.328125 L 175.671875 78.574219 L 177.390625 76.824219 L 179.109375 75.070312 L 180.824219 73.316406 L 182.542969 71.5625 L 184.257812 69.804688 L 185.976562 68.050781 L 187.695312 66.292969 L 189.410156 64.539062 L 191.128906 62.78125 L 192.84375 61.023438 L 196.28125 57.507812 L 197.996094 55.75 L 199.714844 53.992188 L 201.429688 52.230469 L 203.148438 50.472656 L 204.863281 48.710938 L 206.582031 46.953125 L 208.300781 45.191406 L 210.015625 43.433594 L 211.734375 41.671875 L 213.449219 39.914062 L 216.886719 36.390625 L 218.601562 34.628906 L 220.320312 32.867188 L 220.320312 48.824219 L 218.601562 50.3125 L 216.886719 51.800781 L 215.167969 53.289062 L 213.449219 54.78125 L 211.734375 56.269531 L 210.015625 57.761719 L 208.300781 59.25 L 204.863281 62.234375 L 203.148438 63.722656 L 201.429688 65.214844 L 199.714844 66.707031 L 197.996094 68.199219 L 196.28125 69.691406 L 192.84375 72.675781 L 191.128906 74.167969 L 189.410156 75.664062 L 187.695312 77.15625 L 184.257812 80.148438 L 182.542969 81.640625 L 180.824219 83.136719 L 179.109375 84.636719 L 175.671875 87.628906 L 173.957031 89.128906 L 172.238281 90.628906 L 170.523438 92.128906 L 168.804688 93.632812 L 167.085938 95.132812 L 165.371094 96.636719 L 163.652344 98.144531 L 161.9375 99.648438 L 160.21875 101.160156 L 158.503906 102.667969 L 156.785156 104.179688 L 155.066406 105.695312 L 153.351562 107.210938 L 151.632812 108.730469 L 149.917969 110.253906 L 148.199219 111.78125 L 146.480469 113.3125 L 144.765625 114.84375 L 143.046875 116.382812 L 141.332031 117.929688 L 139.613281 119.476562 L 137.894531 121.035156 L 136.179688 122.597656 L 134.460938 124.167969 L 132.746094 125.75 L 131.027344 127.335938 L 129.308594 128.933594 L 127.59375 130.542969 L 125.875 132.160156 L 124.160156 133.789062 L 122.441406 135.425781 L 120.726562 137.074219 L 119.007812 138.730469 L 117.289062 140.398438 L 115.574219 142.074219 L 113.855469 143.757812 L 112.140625 145.449219 L 110.421875 147.144531 L 108.703125 148.847656 L 106.988281 150.558594 L 105.269531 152.273438 L 103.554688 153.988281 L 101.835938 155.710938 L 100.117188 157.4375 L 98.402344 159.167969 L 96.683594 160.902344 L 94.96875 162.636719 L 93.25 164.371094 L 91.535156 166.113281 L 89.816406 167.851562 L 88.097656 169.597656 L 86.382812 171.339844 L 84.664062 173.085938 Z M 84.664062 165.398438 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 169.242188 L 86.382812 167.617188 L 88.097656 165.992188 L 91.535156 162.742188 L 93.25 161.117188 L 94.96875 159.492188 L 96.683594 157.867188 L 98.402344 156.242188 L 100.117188 154.613281 L 103.554688 151.363281 L 105.269531 149.738281 L 106.988281 148.113281 L 108.703125 146.488281 L 112.140625 143.238281 L 113.855469 141.613281 L 115.574219 139.988281 L 117.289062 138.363281 L 120.726562 135.113281 L 122.441406 133.488281 L 124.160156 131.859375 L 125.875 130.234375 L 127.59375 128.609375 L 129.308594 126.984375 L 132.746094 123.734375 L 134.460938 122.109375 L 136.179688 120.484375 L 137.894531 118.859375 L 141.332031 115.609375 L 143.046875 113.984375 L 144.765625 112.359375 L 146.480469 110.734375 L 148.199219 109.105469 L 149.917969 107.480469 L 151.632812 105.855469 L 153.351562 104.230469 L 155.066406 102.605469 L 158.503906 99.355469 L 160.21875 97.730469 L 161.9375 96.105469 L 163.652344 94.480469 L 165.371094 92.855469 L 167.085938 91.230469 L 170.523438 87.980469 L 172.238281 86.351562 L 173.957031 84.726562 L 175.671875 83.101562 L 179.109375 79.851562 L 180.824219 78.226562 L 182.542969 76.601562 L 184.257812 74.976562 L 187.695312 71.726562 L 189.410156 70.101562 L 191.128906 68.476562 L 192.84375 66.851562 L 194.5625 65.222656 L 196.28125 63.597656 L 197.996094 61.972656 L 199.714844 60.347656 L 201.429688 58.722656 L 203.148438 57.097656 L 204.863281 55.472656 L 208.300781 52.222656 L 210.015625 50.597656 L 211.734375 48.972656 L 213.449219 47.347656 L 216.886719 44.097656 L 218.601562 42.46875 L 220.320312 40.84375 "/>
-<g clip-path="url(#clip21)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 469.847656 L 229.136719 469.847656 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 469.847656 "/>
-</g>
-<g clip-path="url(#clip22)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 439.132812 L 229.136719 439.132812 "/>
-</g>
-<g clip-path="url(#clip23)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 385.835938 L 229.136719 385.835938 "/>
-</g>
-<g clip-path="url(#clip24)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 332.535156 L 229.136719 332.535156 "/>
-</g>
-<g clip-path="url(#clip25)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 279.238281 L 229.136719 279.238281 "/>
-</g>
-<g clip-path="url(#clip26)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 469.847656 L 67.707031 258.171875 "/>
-</g>
-<g clip-path="url(#clip27)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 469.847656 L 101.621094 258.171875 "/>
-</g>
-<g clip-path="url(#clip28)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 469.847656 L 135.535156 258.171875 "/>
-</g>
-<g clip-path="url(#clip29)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 469.847656 L 169.449219 258.171875 "/>
-</g>
-<g clip-path="url(#clip30)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 469.847656 L 203.363281 258.171875 "/>
-</g>
-<g clip-path="url(#clip31)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 465.785156 L 229.136719 465.785156 "/>
-</g>
-<g clip-path="url(#clip32)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 412.484375 L 229.136719 412.484375 "/>
-</g>
-<g clip-path="url(#clip33)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 359.1875 L 229.136719 359.1875 "/>
-</g>
-<g clip-path="url(#clip34)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 305.886719 L 229.136719 305.886719 "/>
-</g>
-<g clip-path="url(#clip35)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 469.847656 L 50.75 258.171875 "/>
-</g>
-<g clip-path="url(#clip36)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 469.847656 L 84.664062 258.171875 "/>
-</g>
-<g clip-path="url(#clip37)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 469.847656 L 118.578125 258.171875 "/>
-</g>
-<g clip-path="url(#clip38)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 469.847656 L 152.492188 258.171875 "/>
-</g>
-<g clip-path="url(#clip39)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 469.847656 L 186.40625 258.171875 "/>
-</g>
-<g clip-path="url(#clip40)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 469.847656 L 220.320312 258.171875 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 391.164062 C 86.621094 393.773438 82.710938 393.773438 82.710938 391.164062 C 82.710938 388.558594 86.621094 388.558594 86.621094 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 364.515625 C 106.96875 367.121094 103.058594 367.121094 103.058594 364.515625 C 103.058594 361.910156 106.96875 361.910156 106.96875 364.515625 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 59.488281 428.472656 C 59.488281 431.082031 55.578125 431.082031 55.578125 428.472656 C 55.578125 425.867188 59.488281 425.867188 59.488281 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 401.824219 C 86.621094 404.429688 82.710938 404.429688 82.710938 401.824219 C 82.710938 399.21875 86.621094 399.21875 86.621094 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 407.15625 C 86.621094 409.761719 82.710938 409.761719 82.710938 407.15625 C 82.710938 404.546875 86.621094 404.546875 86.621094 407.15625 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 423.144531 C 79.835938 425.75 75.925781 425.75 75.925781 423.144531 C 75.925781 420.539062 79.835938 420.539062 79.835938 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 385.835938 C 106.96875 388.441406 103.058594 388.441406 103.058594 385.835938 C 103.058594 383.230469 106.96875 383.230469 106.96875 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 401.824219 C 100.183594 404.429688 96.273438 404.429688 96.273438 401.824219 C 96.273438 399.21875 100.183594 399.21875 100.183594 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 412.484375 C 86.621094 415.089844 82.710938 415.089844 82.710938 412.484375 C 82.710938 409.878906 86.621094 409.878906 86.621094 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 375.175781 C 113.75 377.78125 109.839844 377.78125 109.839844 375.175781 C 109.839844 372.570312 113.75 372.570312 113.75 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 380.503906 C 113.75 383.113281 109.839844 383.113281 109.839844 380.503906 C 109.839844 377.898438 113.75 377.898438 113.75 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 412.484375 C 79.835938 415.089844 75.925781 415.089844 75.925781 412.484375 C 75.925781 409.878906 79.835938 409.878906 79.835938 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 375.175781 C 100.183594 377.78125 96.273438 377.78125 96.273438 375.175781 C 96.273438 372.570312 100.183594 372.570312 100.183594 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 369.847656 C 106.96875 372.453125 103.058594 372.453125 103.058594 369.847656 C 103.058594 367.238281 106.96875 367.238281 106.96875 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 423.144531 C 86.621094 425.75 82.710938 425.75 82.710938 423.144531 C 82.710938 420.539062 86.621094 420.539062 86.621094 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 57.535156 440.144531 L 58.21875 439.300781 L 60.28125 436.769531 L 60.96875 435.921875 L 61.65625 435.078125 L 62.339844 434.234375 L 63.027344 433.386719 L 63.714844 432.542969 L 65.089844 430.847656 L 65.777344 430.003906 L 66.464844 429.15625 L 67.148438 428.308594 L 67.835938 427.457031 L 68.523438 426.609375 L 69.210938 425.757812 L 69.898438 424.910156 L 70.585938 424.058594 L 71.269531 423.203125 L 72.644531 421.5 L 74.019531 419.789062 L 74.707031 418.929688 L 75.390625 418.070312 L 76.765625 416.351562 L 78.140625 414.625 L 78.828125 413.757812 L 79.511719 412.890625 L 80.886719 411.148438 L 81.574219 410.273438 L 82.261719 409.394531 L 82.949219 408.511719 L 83.632812 407.628906 L 85.007812 405.847656 L 86.382812 404.050781 L 87.070312 403.140625 L 87.753906 402.230469 L 88.441406 401.3125 L 89.128906 400.390625 L 89.816406 399.460938 L 90.503906 398.523438 L 91.191406 397.578125 L 91.875 396.628906 L 92.5625 395.667969 L 93.25 394.703125 L 93.9375 393.730469 L 94.625 392.75 L 95.3125 391.761719 L 95.996094 390.765625 L 96.683594 389.765625 L 97.371094 388.757812 L 98.058594 387.742188 L 98.746094 386.722656 L 99.433594 385.699219 L 100.117188 384.667969 L 100.804688 383.632812 L 101.492188 382.59375 L 102.179688 381.550781 L 102.867188 380.503906 L 103.554688 379.453125 L 104.238281 378.402344 L 105.613281 376.285156 L 106.988281 374.160156 L 107.675781 373.09375 L 108.359375 372.027344 L 109.046875 370.960938 L 109.734375 369.886719 L 110.421875 368.816406 L 111.796875 366.667969 L 111.796875 375.09375 L 111.109375 375.949219 L 109.046875 378.527344 L 108.359375 379.390625 L 107.675781 380.253906 L 106.300781 381.988281 L 105.613281 382.859375 L 104.238281 384.609375 L 103.554688 385.484375 L 102.867188 386.367188 L 101.492188 388.140625 L 100.804688 389.03125 L 100.117188 389.929688 L 99.433594 390.832031 L 98.746094 391.738281 L 98.058594 392.648438 L 97.371094 393.566406 L 96.683594 394.488281 L 95.996094 395.421875 L 95.3125 396.355469 L 94.625 397.300781 L 93.9375 398.25 L 93.25 399.210938 L 92.5625 400.175781 L 91.875 401.148438 L 91.191406 402.128906 L 90.503906 403.117188 L 89.816406 404.113281 L 89.128906 405.113281 L 88.441406 406.121094 L 87.753906 407.136719 L 87.070312 408.15625 L 86.382812 409.179688 L 85.695312 410.210938 L 85.007812 411.246094 L 84.320312 412.285156 L 83.632812 413.328125 L 82.949219 414.375 L 82.261719 415.425781 L 80.886719 417.535156 L 80.199219 418.59375 L 79.511719 419.65625 L 78.828125 420.71875 L 77.453125 422.851562 L 75.390625 426.0625 L 74.707031 427.136719 L 73.332031 429.285156 L 71.269531 432.519531 L 70.585938 433.597656 L 67.148438 439.007812 L 66.464844 440.089844 L 65.777344 441.175781 L 65.089844 442.257812 L 62.339844 446.601562 L 61.65625 447.6875 L 60.96875 448.773438 L 60.28125 449.863281 L 59.59375 450.949219 L 58.90625 452.039062 L 58.21875 453.125 L 57.535156 454.214844 Z M 57.535156 440.144531 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 57.535156 447.179688 L 58.21875 446.210938 L 60.28125 443.316406 L 60.96875 442.347656 L 61.65625 441.382812 L 62.339844 440.417969 L 63.027344 439.453125 L 63.714844 438.484375 L 65.777344 435.589844 L 66.464844 434.621094 L 67.148438 433.65625 L 69.210938 430.761719 L 69.898438 429.792969 L 70.585938 428.828125 L 71.269531 427.863281 L 71.957031 426.898438 L 72.644531 425.929688 L 74.707031 423.035156 L 75.390625 422.066406 L 77.453125 419.171875 L 78.140625 418.203125 L 78.828125 417.238281 L 79.511719 416.273438 L 80.199219 415.308594 L 80.886719 414.339844 L 82.949219 411.445312 L 83.632812 410.476562 L 85.695312 407.582031 L 86.382812 406.613281 L 87.070312 405.648438 L 87.753906 404.683594 L 88.441406 403.71875 L 89.128906 402.75 L 91.191406 399.855469 L 91.875 398.886719 L 94.625 395.027344 L 95.3125 394.058594 L 95.996094 393.09375 L 97.371094 391.164062 L 98.058594 390.195312 L 99.433594 388.265625 L 100.117188 387.300781 L 100.804688 386.332031 L 102.867188 383.4375 L 103.554688 382.46875 L 104.238281 381.503906 L 105.613281 379.574219 L 106.300781 378.605469 L 107.675781 376.675781 L 108.359375 375.710938 L 109.046875 374.742188 L 111.109375 371.847656 L 111.796875 370.878906 "/>
-<g clip-path="url(#clip41)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 234.925781 L 428.601562 234.925781 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 234.925781 "/>
-</g>
-<g clip-path="url(#clip42)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 204.210938 L 428.601562 204.210938 "/>
-</g>
-<g clip-path="url(#clip43)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 150.910156 L 428.601562 150.910156 "/>
-</g>
-<g clip-path="url(#clip44)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 97.613281 L 428.601562 97.613281 "/>
-</g>
-<g clip-path="url(#clip45)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 44.3125 L 428.601562 44.3125 "/>
-</g>
-<g clip-path="url(#clip46)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 234.925781 L 267.171875 23.246094 "/>
-</g>
-<g clip-path="url(#clip47)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 234.925781 L 301.085938 23.246094 "/>
-</g>
-<g clip-path="url(#clip48)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 234.925781 L 335 23.246094 "/>
-</g>
-<g clip-path="url(#clip49)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 234.925781 L 368.914062 23.246094 "/>
-</g>
-<g clip-path="url(#clip50)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 234.925781 L 402.828125 23.246094 "/>
-</g>
-<g clip-path="url(#clip51)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 230.859375 L 428.601562 230.859375 "/>
-</g>
-<g clip-path="url(#clip52)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 177.558594 L 428.601562 177.558594 "/>
-</g>
-<g clip-path="url(#clip53)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 124.261719 L 428.601562 124.261719 "/>
-</g>
-<g clip-path="url(#clip54)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 70.960938 L 428.601562 70.960938 "/>
-</g>
-<g clip-path="url(#clip55)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 234.925781 L 250.214844 23.246094 "/>
-</g>
-<g clip-path="url(#clip56)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 234.925781 L 284.128906 23.246094 "/>
-</g>
-<g clip-path="url(#clip57)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 234.925781 L 318.042969 23.246094 "/>
-</g>
-<g clip-path="url(#clip58)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 234.925781 L 351.957031 23.246094 "/>
-</g>
-<g clip-path="url(#clip59)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 234.925781 L 385.871094 23.246094 "/>
-</g>
-<g clip-path="url(#clip60)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 234.925781 L 419.785156 23.246094 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 134.921875 C 320 137.527344 316.089844 137.527344 316.089844 134.921875 C 316.089844 132.316406 320 132.316406 320 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 129.589844 C 320 132.199219 316.089844 132.199219 316.089844 129.589844 C 316.089844 126.984375 320 126.984375 320 129.589844 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 318.042969 124.148438 L 318.128906 124.214844 L 318.214844 124.285156 L 318.300781 124.347656 L 318.386719 124.414062 L 318.472656 124.476562 L 318.558594 124.535156 L 318.644531 124.597656 L 318.730469 124.652344 L 318.816406 124.710938 L 318.902344 124.761719 L 318.988281 124.816406 L 319.074219 124.867188 L 319.246094 124.960938 L 319.417969 125.046875 L 319.503906 125.085938 L 319.675781 125.15625 L 319.847656 125.21875 L 320.105469 125.289062 L 320.277344 125.320312 L 320.363281 125.332031 L 320.535156 125.347656 L 320.707031 125.347656 L 320.878906 125.332031 L 320.964844 125.320312 L 321.050781 125.304688 L 321.136719 125.285156 L 321.308594 125.238281 L 321.390625 125.207031 L 321.5625 125.136719 L 321.734375 125.050781 L 321.90625 124.949219 L 321.992188 124.894531 L 322.078125 124.835938 L 322.164062 124.773438 L 322.25 124.707031 L 322.421875 124.566406 L 322.59375 124.410156 L 322.679688 124.328125 L 322.765625 124.242188 L 322.9375 124.0625 L 323.023438 123.96875 L 323.195312 123.773438 L 323.28125 123.671875 L 323.453125 123.460938 L 323.539062 123.351562 L 323.796875 123.011719 L 323.882812 122.894531 L 324.054688 122.652344 L 324.3125 122.277344 L 324.484375 122.019531 L 324.742188 121.621094 L 324.828125 121.484375 L 324.828125 137.699219 L 324.742188 137.632812 L 324.65625 137.5625 L 324.570312 137.5 L 324.484375 137.433594 L 324.398438 137.371094 L 324.3125 137.3125 L 324.226562 137.25 L 324.140625 137.195312 L 324.054688 137.136719 L 323.96875 137.085938 L 323.882812 137.03125 L 323.796875 136.980469 L 323.625 136.886719 L 323.453125 136.800781 L 323.367188 136.761719 L 323.195312 136.691406 L 323.023438 136.628906 L 322.765625 136.558594 L 322.59375 136.527344 L 322.507812 136.515625 L 322.421875 136.507812 L 322.25 136.5 L 322.164062 136.5 L 321.992188 136.515625 L 321.90625 136.527344 L 321.820312 136.542969 L 321.734375 136.5625 L 321.5625 136.609375 L 321.476562 136.640625 L 321.390625 136.675781 L 321.308594 136.710938 L 321.136719 136.796875 L 320.964844 136.898438 L 320.878906 136.953125 L 320.792969 137.011719 L 320.707031 137.074219 L 320.621094 137.140625 L 320.449219 137.28125 L 320.277344 137.4375 L 320.191406 137.519531 L 320.105469 137.605469 L 319.933594 137.785156 L 319.847656 137.878906 L 319.675781 138.074219 L 319.589844 138.175781 L 319.417969 138.386719 L 319.332031 138.496094 L 319.074219 138.835938 L 318.988281 138.953125 L 318.816406 139.195312 L 318.558594 139.570312 L 318.386719 139.828125 L 318.214844 140.09375 L 318.128906 140.230469 L 318.042969 140.363281 Z M 318.042969 124.148438 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 132.257812 L 318.214844 132.1875 L 318.300781 132.15625 L 318.472656 132.085938 L 318.558594 132.054688 L 318.644531 132.019531 L 318.730469 131.988281 L 318.902344 131.917969 L 318.988281 131.886719 L 319.160156 131.816406 L 319.246094 131.785156 L 319.417969 131.714844 L 319.503906 131.683594 L 319.589844 131.648438 L 319.675781 131.617188 L 319.847656 131.546875 L 319.933594 131.515625 L 320.105469 131.445312 L 320.191406 131.414062 L 320.363281 131.34375 L 320.449219 131.3125 L 320.535156 131.277344 L 320.621094 131.246094 L 320.792969 131.175781 L 320.878906 131.144531 L 321.050781 131.074219 L 321.136719 131.042969 L 321.308594 130.972656 L 321.390625 130.941406 L 321.476562 130.90625 L 321.5625 130.875 L 321.734375 130.804688 L 321.820312 130.773438 L 321.992188 130.703125 L 322.078125 130.671875 L 322.25 130.601562 L 322.335938 130.570312 L 322.421875 130.535156 L 322.507812 130.503906 L 322.679688 130.433594 L 322.765625 130.402344 L 322.9375 130.332031 L 323.023438 130.300781 L 323.195312 130.230469 L 323.28125 130.199219 L 323.367188 130.164062 L 323.453125 130.132812 L 323.625 130.0625 L 323.710938 130.03125 L 323.882812 129.960938 L 323.96875 129.929688 L 324.140625 129.859375 L 324.226562 129.828125 L 324.3125 129.792969 L 324.398438 129.761719 L 324.570312 129.691406 L 324.65625 129.660156 L 324.828125 129.589844 "/>
-<g clip-path="url(#clip61)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 469.847656 L 428.601562 469.847656 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 469.847656 "/>
-</g>
-<g clip-path="url(#clip62)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 439.132812 L 428.601562 439.132812 "/>
-</g>
-<g clip-path="url(#clip63)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 385.835938 L 428.601562 385.835938 "/>
-</g>
-<g clip-path="url(#clip64)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 332.535156 L 428.601562 332.535156 "/>
-</g>
-<g clip-path="url(#clip65)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 279.238281 L 428.601562 279.238281 "/>
-</g>
-<g clip-path="url(#clip66)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 469.847656 L 267.171875 258.171875 "/>
-</g>
-<g clip-path="url(#clip67)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 469.847656 L 301.085938 258.171875 "/>
-</g>
-<g clip-path="url(#clip68)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 469.847656 L 335 258.171875 "/>
-</g>
-<g clip-path="url(#clip69)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 469.847656 L 368.914062 258.171875 "/>
-</g>
-<g clip-path="url(#clip70)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 469.847656 L 402.828125 258.171875 "/>
-</g>
-<g clip-path="url(#clip71)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 465.785156 L 428.601562 465.785156 "/>
-</g>
-<g clip-path="url(#clip72)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 412.484375 L 428.601562 412.484375 "/>
-</g>
-<g clip-path="url(#clip73)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 359.1875 L 428.601562 359.1875 "/>
-</g>
-<g clip-path="url(#clip74)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 305.886719 L 428.601562 305.886719 "/>
-</g>
-<g clip-path="url(#clip75)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 469.847656 L 250.214844 258.171875 "/>
-</g>
-<g clip-path="url(#clip76)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 469.847656 L 284.128906 258.171875 "/>
-</g>
-<g clip-path="url(#clip77)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 469.847656 L 318.042969 258.171875 "/>
-</g>
-<g clip-path="url(#clip78)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 469.847656 L 351.957031 258.171875 "/>
-</g>
-<g clip-path="url(#clip79)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 469.847656 L 385.871094 258.171875 "/>
-</g>
-<g clip-path="url(#clip80)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 469.847656 L 419.785156 258.171875 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 396.496094 C 292.867188 399.101562 288.957031 399.101562 288.957031 396.496094 C 288.957031 393.890625 292.867188 393.890625 292.867188 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 428.472656 C 265.738281 431.082031 261.828125 431.082031 261.828125 428.472656 C 261.828125 425.867188 265.738281 425.867188 265.738281 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 385.835938 C 286.085938 388.441406 282.175781 388.441406 282.175781 385.835938 C 282.175781 383.230469 286.085938 383.230469 286.085938 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 391.164062 C 286.085938 393.773438 282.175781 393.773438 282.175781 391.164062 C 282.175781 388.558594 286.085938 388.558594 286.085938 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 407.15625 C 286.085938 409.761719 282.175781 409.761719 282.175781 407.15625 C 282.175781 404.546875 286.085938 404.546875 286.085938 407.15625 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 385.835938 C 292.867188 388.441406 288.957031 388.441406 288.957031 385.835938 C 288.957031 383.230469 292.867188 383.230469 292.867188 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 243.433594 452.394531 L 244.035156 451.695312 L 245.238281 450.304688 L 245.839844 449.605469 L 246.4375 448.90625 L 248.84375 446.109375 L 249.445312 445.40625 L 250.046875 444.707031 L 250.644531 444.003906 L 251.246094 443.300781 L 251.847656 442.59375 L 252.449219 441.890625 L 253.652344 440.476562 L 254.253906 439.765625 L 254.851562 439.058594 L 255.453125 438.347656 L 257.257812 436.203125 L 257.859375 435.484375 L 258.460938 434.761719 L 259.058594 434.039062 L 259.660156 433.316406 L 260.261719 432.589844 L 260.863281 431.859375 L 262.066406 430.390625 L 262.667969 429.652344 L 263.265625 428.910156 L 263.867188 428.164062 L 264.46875 427.414062 L 265.070312 426.660156 L 265.671875 425.902344 L 266.273438 425.140625 L 266.875 424.375 L 267.472656 423.601562 L 268.074219 422.828125 L 268.675781 422.050781 L 269.878906 420.480469 L 271.082031 418.894531 L 271.679688 418.09375 L 272.882812 416.484375 L 273.484375 415.675781 L 274.085938 414.863281 L 274.6875 414.046875 L 275.285156 413.226562 L 275.886719 412.40625 L 277.089844 410.757812 L 277.691406 409.929688 L 278.894531 408.265625 L 279.492188 407.433594 L 281.296875 404.925781 L 282.5 403.246094 L 283.101562 402.402344 L 283.699219 401.5625 L 284.902344 399.875 L 285.503906 399.027344 L 286.105469 398.183594 L 287.308594 396.488281 L 287.90625 395.640625 L 288.507812 394.792969 L 289.109375 393.941406 L 289.710938 393.09375 L 290.3125 392.242188 L 290.914062 391.394531 L 290.914062 398.976562 L 290.3125 399.675781 L 289.710938 400.371094 L 287.90625 402.46875 L 287.308594 403.167969 L 286.707031 403.867188 L 286.105469 404.570312 L 285.503906 405.269531 L 283.699219 407.378906 L 283.101562 408.085938 L 281.296875 410.207031 L 279.492188 412.339844 L 278.894531 413.054688 L 278.292969 413.769531 L 276.488281 415.925781 L 275.285156 417.378906 L 274.6875 418.105469 L 273.484375 419.574219 L 272.28125 421.050781 L 271.679688 421.796875 L 271.082031 422.546875 L 270.480469 423.296875 L 269.277344 424.8125 L 268.675781 425.578125 L 268.074219 426.347656 L 267.472656 427.121094 L 266.875 427.898438 L 266.273438 428.679688 L 265.671875 429.464844 L 265.070312 430.253906 L 264.46875 431.046875 L 263.867188 431.84375 L 263.265625 432.644531 L 262.667969 433.453125 L 262.066406 434.257812 L 261.464844 435.070312 L 260.261719 436.703125 L 259.660156 437.523438 L 259.058594 438.347656 L 258.460938 439.171875 L 257.257812 440.828125 L 255.453125 443.324219 L 254.851562 444.160156 L 254.253906 445 L 251.847656 448.359375 L 250.644531 450.046875 L 250.046875 450.894531 L 249.445312 451.738281 L 248.84375 452.585938 L 248.242188 453.429688 L 247.640625 454.277344 L 247.039062 455.128906 L 246.4375 455.976562 L 245.839844 456.824219 L 244.636719 458.527344 L 244.035156 459.375 L 243.433594 460.226562 Z M 243.433594 452.394531 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 243.433594 456.308594 L 245.839844 453.214844 L 246.4375 452.441406 L 250.046875 447.800781 L 250.644531 447.027344 L 251.246094 446.25 L 254.253906 442.382812 L 254.851562 441.609375 L 258.460938 436.96875 L 259.058594 436.195312 L 259.660156 435.417969 L 262.667969 431.550781 L 263.265625 430.777344 L 266.875 426.136719 L 267.472656 425.359375 L 271.082031 420.71875 L 271.679688 419.945312 L 274.6875 416.078125 L 275.285156 415.304688 L 275.886719 414.527344 L 278.894531 410.660156 L 279.492188 409.886719 L 283.101562 405.246094 L 283.699219 404.46875 L 287.308594 399.828125 L 287.90625 399.054688 L 290.914062 395.1875 "/>
-<g clip-path="url(#clip81)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 240.40625 L 35.152344 240.40625 Z M 35.152344 258.171875 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-1" x="129.644531" y="252.204102"/>
-</g>
-<g clip-path="url(#clip82)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 240.40625 L 234.617188 240.40625 Z M 234.617188 258.171875 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-2" x="329.109375" y="252.204102"/>
-</g>
-<g clip-path="url(#clip83)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 5.480469 L 35.152344 5.480469 Z M 35.152344 23.246094 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="129.644531" y="17.27832"/>
-</g>
-<g clip-path="url(#clip84)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 5.480469 L 234.617188 5.480469 Z M 234.617188 23.246094 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-4" x="329.109375" y="17.27832"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 472.589844 L 50.75 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 472.589844 L 84.664062 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 472.589844 L 118.578125 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 472.589844 L 152.492188 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 472.589844 L 186.40625 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 472.589844 L 220.320312 469.847656 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="45.75" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="50.75" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="79.664062" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="84.664062" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="113.578125" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="118.578125" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="147.492188" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="152.492188" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="181.40625" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="186.40625" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="215.320312" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="220.320312" y="481.196289"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 472.589844 L 250.214844 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 472.589844 L 284.128906 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 472.589844 L 318.042969 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 472.589844 L 351.957031 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 472.589844 L 385.871094 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 472.589844 L 419.785156 469.847656 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="245.214844" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="250.214844" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="279.128906" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="284.128906" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="313.042969" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="318.042969" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="346.957031" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="351.957031" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="380.871094" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="385.871094" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="414.785156" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="419.785156" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="20.21875" y="233.774414"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="233.774414"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="20.21875" y="180.473633"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="180.473633"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="20.21875" y="127.176758"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="127.176758"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="20.21875" y="73.875977"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="73.875977"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 230.859375 L 35.152344 230.859375 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 177.558594 L 35.152344 177.558594 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 124.261719 L 35.152344 124.261719 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 70.960938 L 35.152344 70.960938 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="20.21875" y="468.700195"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="468.700195"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="20.21875" y="415.399414"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="415.399414"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="20.21875" y="362.102539"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="362.102539"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="20.21875" y="308.801758"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="308.801758"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 465.785156 L 35.152344 465.785156 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 412.484375 L 35.152344 412.484375 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 359.1875 L 35.152344 359.1875 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 305.886719 L 35.152344 305.886719 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph1-1" x="224.875" y="494.538086"/>
-  <use xlink:href="#glyph1-2" x="230.875" y="494.538086"/>
-  <use xlink:href="#glyph1-3" x="233.875" y="494.538086"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph2-1" x="13.499023" y="256.046875"/>
-  <use xlink:href="#glyph2-2" x="13.499023" y="250.046875"/>
-  <use xlink:href="#glyph2-3" x="13.499023" y="242.046875"/>
-</g>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;" d="M 439.5625 295.328125 L 498.519531 295.328125 L 498.519531 197.769531 L 439.5625 197.769531 Z M 439.5625 295.328125 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph1-4" x="445.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-5" x="448.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-1" x="454.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-2" x="460.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-6" x="463.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-7" x="469.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-8" x="473.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-1" x="477.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-3" x="482.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-9" x="487.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-10" x="489.042969" y="212.768555"/>
-</g>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 229.367188 C 455.636719 231.972656 451.726562 231.972656 451.726562 229.367188 C 451.726562 226.761719 455.636719 226.761719 455.636719 229.367188 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 229.367188 L 460.59375 229.367188 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 246.648438 C 455.636719 249.253906 451.726562 249.253906 451.726562 246.648438 C 451.726562 244.042969 455.636719 244.042969 455.636719 246.648438 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 246.648438 L 460.59375 246.648438 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 263.925781 C 455.636719 266.535156 451.726562 266.535156 451.726562 263.925781 C 451.726562 261.320312 455.636719 261.320312 455.636719 263.925781 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 263.925781 L 460.59375 263.925781 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 281.207031 C 455.636719 283.8125 451.726562 283.8125 451.726562 281.207031 C 451.726562 278.601562 455.636719 278.601562 455.636719 281.207031 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 281.207031 L 460.59375 281.207031 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="467.800781" y="232.282227"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-4" x="467.800781" y="249.563477"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-1" x="467.800781" y="266.84082"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-2" x="467.800781" y="284.12207"/>
-</g>
-</g>
-</svg>
-
-```
-
-We may also [generate](https://scicloj.github.io/clojisr/doc/clojisr/v1/codegen-test/) the R code from a Clojure form and pass Clojure data to R, but for now, we are simply using R code using an R dataset.
-We are using the `mpg` dataset, which is part of the `ggplot` package.
-
-::: {.sourceClojure}
-```clojure
-(-> "mpg"
-    r
-    r->clj)
-```
-:::
-
-_unnamed [234 11]:
-
-| :manufacturer |     :model | :displ | :year | :cyl |     :trans | :drv | :cty | :hwy | :fl |     :class |
-|---------------|------------|-------:|------:|-----:|------------|------|-----:|-----:|-----|------------|
-|          audi |         a4 |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    compact |
-|          audi |         a4 |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    compact |
-|          audi |         a4 |    2.0 |  2008 |    4 | manual(m6) |    f |   20 |   31 |   p |    compact |
-|          audi |         a4 |    2.0 |  2008 |    4 |   auto(av) |    f |   21 |   30 |   p |    compact |
-|          audi |         a4 |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    compact |
-|          audi |         a4 |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    compact |
-|          audi |         a4 |    3.1 |  2008 |    6 |   auto(av) |    f |   18 |   27 |   p |    compact |
-|          audi | a4 quattro |    1.8 |  1999 |    4 | manual(m5) |    4 |   18 |   26 |   p |    compact |
-|          audi | a4 quattro |    1.8 |  1999 |    4 |   auto(l5) |    4 |   16 |   25 |   p |    compact |
-|          audi | a4 quattro |    2.0 |  2008 |    4 | manual(m6) |    4 |   20 |   28 |   p |    compact |
-|           ... |        ... |    ... |   ... |  ... |        ... |  ... |  ... |  ... | ... |        ... |
-|    volkswagen | new beetle |    2.0 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   r | subcompact |
-|    volkswagen | new beetle |    2.0 |  1999 |    4 |   auto(l4) |    f |   19 |   26 |   r | subcompact |
-|    volkswagen | new beetle |    2.5 |  2008 |    5 | manual(m5) |    f |   20 |   28 |   r | subcompact |
-|    volkswagen | new beetle |    2.5 |  2008 |    5 |   auto(s6) |    f |   20 |   29 |   r | subcompact |
-|    volkswagen |     passat |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    midsize |
-|    volkswagen |     passat |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    midsize |
-|    volkswagen |     passat |    2.0 |  2008 |    4 |   auto(s6) |    f |   19 |   28 |   p |    midsize |
-|    volkswagen |     passat |    2.0 |  2008 |    4 | manual(m6) |    f |   21 |   29 |   p |    midsize |
-|    volkswagen |     passat |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    midsize |
-|    volkswagen |     passat |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    midsize |
-|    volkswagen |     passat |    3.6 |  2008 |    6 |   auto(s6) |    f |   17 |   26 |   p |    midsize |
-
-## Representing plots as Clojure data
-A ggplot object is an R list of [ggproto](https://bookdown.dongzhuoer.com/hadley/ggplot2-book/introducing-ggproto) objects. We recursively unwrap this structure and convert it to Clojure.
-
-::: {.sourceClojure}
-```clojure
-(defn ggolot->clj
-  ([r-obj
-    options]
-   (ggolot->clj r-obj options []))
-  ([r-obj
-    {:as options
-     :keys [avoid]}
-    path]
-   #_(prn path)
-   (let [relevant-names (some->> r-obj
-                                 r.base/names
-                                 r->clj
-                                 (filter (complement avoid)))]
-     (cond
-       ;;
-       ;; a named list or a ggproto object
-       (seq relevant-names) (->> relevant-names
-                                 (map (fn [nam]
-                                        [(keyword nam) (-> r-obj
-                                                           (r$ nam)
-                                                           (ggolot->clj options
-                                                                        (conj path nam)))]))
-                                 (into {}))
-       ;;
-       ;; a ggproto method
-       (-> r-obj
-           r.base/class
-           r->clj
-           first
-           (= "ggproto_method"))
-       :ggproto-method
-       ;;
-       ;; an unnamed list
-       (-> r-obj
-           r.base/is-list
-           r->clj
-           first)
-       (-> r-obj
-           r.base/length
-           r->clj
-           first
-           range
-           (->> (mapv (fn [i]
-                        (prn [path (inc i)])
-                        (-> r-obj
-                            (r/brabra (inc i))
-                            (ggolot->clj options
-                                         (conj path [i])))))))
-       ;;
-       (r.base/is-atomic r-obj) (try (r->clj r-obj)
-                                     (catch Exception e
-                                       (-> r-obj println with-out-str)))
-       :else r-obj))))
-```
-:::
-
-In the conversion, we avoid some big parts of the structure, e.g., the `"plot_env"` member. We also do no report the toplevel `"data"` member, which is simply the dataset.
-For example:
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy))
-         + geom_point())"
-    r
-    (ggolot->clj {:avoid #{"plot_env"}})
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-## Exlploring a few plots
-Let us explore and compare a few plots this way:
-
-::: {.sourceClojure}
-```clojure
-(defn h4 [title]
-  (kind/hiccup [:h3 title]))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn ggplot-summary [r-code]
-  (let [plot (r r-code)
-        clj (-> plot
-                (ggolot->clj {:avoid #{"plot_env"}})
-                (dissoc :data))]
-    (kind/fragment
-     [(h4 "R code")
-      (kind/md
-       (format "\n```\n%s\n```\n"
-               r-code))
-      (h4 "plot")
-      (-> plot
-          plotting/plot->buffered-image)
-      (h4 "clj data")
-      (kind/pprint clj)])))
-```
-:::
-
-### A scatterplot
-
-::: {.sourceClojure}
-```clojure
-(ggplot-summary
- "(ggplot(mpg, aes(cty, hwy))
-         + geom_point())")
-```
-:::
-
-```{=html}
-<h3>R code</h3>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy))
-         + geom_point())
-```
-
-```{=html}
-<h3>plot</h3>
-```
-
-```{=html}
-<img src="ggplot_files/0.png" style="width:100%;" />
-```
-
-```{=html}
-<h3>clj data</h3>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-### A scatterplot with colours
-
-::: {.sourceClojure}
-```clojure
-(ggplot-summary
- "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())")
-```
-:::
-
-```{=html}
-<h3>R code</h3>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())
-```
-
-```{=html}
-<h3>plot</h3>
-```
-
-```{=html}
-<img src="ggplot_files/1.png" style="width:100%;" />
-```
-
-```{=html}
-<h3>clj data</h3>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-### A scatterplot with colours and smoothing
-
-::: {.sourceClojure}
-```clojure
-(ggplot-summary
- "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\"))")
-```
-:::
-
-```{=html}
-<h3>R code</h3>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method="lm"))
-```
-
-```{=html}
-<h3>plot</h3>
-```
-
-```{=html}
-<img src="ggplot_files/2.png" style="width:100%;" />
-```
-
-```{=html}
-<h3>clj data</h3>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}
-  {:aes_params [],
-   :stat
-   {:extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x" "y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_params :ggproto-method,
-    :super :ggproto-method,
-    :draw_key :ggproto-method,
-    :extra_params ["na.rm" "orientation"],
-    :required_aes ["x" "y"],
-    :draw_group :ggproto-method,
-    :optional_aes ["ymin" "ymax"],
-    :rename_size [true],
-    :setup_data :ggproto-method,
-    :default_aes
-    {:colour ["#3366FF"],
-     :fill ["grey60"],
-     :linewidth [1.0],
-     :linetype [1.0],
-     :weight [1.0],
-     :alpha [0.4]}},
-   :stat_params
-   {:na.rm [false],
-    :method ["lm"],
-    :n [80.0],
-    :orientation [nil],
-    :level [0.95],
-    :fullrange [false],
-    :se [true],
-    :formula nil,
-    :method.args [],
-    :span [0.75]},
-   :constructor {: nil, :method ["lm"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-### A scatterplot with colours, smoothing, and facets
-
-::: {.sourceClojure}
-```clojure
-(ggplot-summary
- "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))")
-```
-:::
-
-```{=html}
-<h3>R code</h3>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method="lm")
-         + facet_wrap(~cyl))
-```
-
-```{=html}
-<h3>plot</h3>
-```
-
-```{=html}
-<img src="ggplot_files/3.png" style="width:100%;" />
-```
-
-```{=html}
-<h3>clj data</h3>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}
-  {:aes_params [],
-   :stat
-   {:extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x" "y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_params :ggproto-method,
-    :super :ggproto-method,
-    :draw_key :ggproto-method,
-    :extra_params ["na.rm" "orientation"],
-    :required_aes ["x" "y"],
-    :draw_group :ggproto-method,
-    :optional_aes ["ymin" "ymax"],
-    :rename_size [true],
-    :setup_data :ggproto-method,
-    :default_aes
-    {:colour ["#3366FF"],
-     :fill ["grey60"],
-     :linewidth [1.0],
-     :linetype [1.0],
-     :weight [1.0],
-     :alpha [0.4]}},
-   :stat_params
-   {:na.rm [false],
-    :method ["lm"],
-    :n [80.0],
-    :orientation [nil],
-    :level [0.95],
-    :fullrange [false],
-    :se [true],
-    :formula nil,
-    :method.args [],
-    :span [0.75]},
-   :constructor {: nil, :method ["lm"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet
- {:params
-  {:dir ["h"],
-   :nrow nil,
-   :as.table [true],
-   :free {:x [false], :y [false]},
-   :drop [true],
-   :strip.position ["top"],
-   :ncol nil,
-   :facets {:cyl [~ cyl]},
-   :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x559b84332b20&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
-  :shrink [true],
-  :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
+# Exploring ggplot (moved elsewhere)
+This notebook has moved to a dedicate set of notebooks [at this location](https://scicloj.github.io/clojure-data-scrapbook/projects/datavis/ggplot/).
 

### 2024-02-23 docs/projects/noj/ml.qmd
Noj - rerendered

@@
        Min          1Q      Median          3Q         Max
-   -0.8148     -0.2402      0.0173      0.1886      0.7180
+   -0.7326     -0.2096     -0.0182      0.1866      0.8517
 
@@
                   Estimate Std. Error    t value   Pr(>|t|)
-Intercept           2.0188     0.3171     6.3667     0.0000 ***
-sepal-width         0.6187     0.0852     7.2590     0.0000 ***
-petal-length        0.6704     0.0716     9.3627     0.0000 ***
-petal-width        -0.5103     0.1616    -3.1572     0.0021 **
+Intercept           1.7373     0.2932     5.9256     0.0000 ***
+sepal-width         0.6949     0.0767     9.0631     0.0000 ***
+petal-length        0.6458     0.0660     9.7786     0.0000 ***
+petal-width        -0.3970     0.1481    -2.6810     0.0086 **
 ---------------------------------------------------------------------
@@
 
-Residual standard error: 0.3191 on 96 degrees of freedom
-Multiple R-squared: 0.8440,    Adjusted R-squared: 0.8391
-F-statistic: 173.0879 on 4 and 96 DF,  p-value: 1.363e-38
+Residual standard error: 0.3194 on 96 degrees of freedom
+Multiple R-squared: 0.8511,    Adjusted R-squared: 0.8465
+F-statistic: 182.9573 on 4 and 96 DF,  p-value: 1.434e-39
 

### 2024-02-23 docs/projects/datavis/ggplot/repesenting.qmd
ggplot - missing rendered files

@@
 
-# Using ggplot Clojure using ClojisR
+# Representing ggplot plots as Clojure data
 
 ## Setup
+
 We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.
@@
 ## An example plot
+
 Here is how we may generate and display a plot:
@@
 </defs>
-<g id="surface266">
+<g id="surface309">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
 We may also [generate](https://scicloj.github.io/clojisr/doc/clojisr/v1/codegen-test/) the R code from a Clojure form and pass Clojure data to R, but for now, we are simply using R code using an R dataset.
+
 We are using the `mpg` dataset, which is part of the `ggplot` package.
@@
 ## Representing plots as Clojure data
+
 A ggplot object is an R list of [ggproto](https://bookdown.dongzhuoer.com/hadley/ggplot2-book/introducing-ggproto) objects. We recursively unwrap this structure and convert it to Clojure.
@@
 In the conversion, we avoid some big parts of the structure, e.g., the `"plot_env"` member. We also do no report the toplevel `"data"` member, which is simply the dataset.
+
 For example:
@@
 ## Exlploring a few plots
+
 Let us explore and compare a few plots this way:
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x556feb092c18&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55de132d0148&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x556feb092c18&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55de132d0148&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 
@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x556fe5ccb140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x55de0f7b0140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x556fe5ccb140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x55de0f7b0140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x556fe8978000&gt;\n&lt;environment: 0x556ff5d42868&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55de136ff278&gt;\n&lt;environment: 0x55de1aecfde8&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556fe8974af0&gt;\n&lt;environment: 0x556ff5d46510&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55de13704b78&gt;\n&lt;environment: 0x55de1aecff70&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556fe89717a0&gt;\n&lt;environment: 0x556ff5d463c0&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55de137081a0&gt;\n&lt;environment: 0x55de1aed00c0&gt;\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x556feae855e8&gt;\n&lt;environment: 0x556ff3da9fc8&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55de203785e0&gt;\n&lt;environment: 0x55de202c9318&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x556feae85738&gt;\n&lt;environment: 0x556ff3da9fc8&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x55de20378490&gt;\n&lt;environment: 0x55de202c9318&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x556feae75a68&gt;\n&lt;environment: 0x556ff3dae4d0&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55de20380260&gt;\n&lt;environment: 0x55de202cf2b8&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556fe8974af0&gt;\n&lt;environment: 0x556ff3dae118&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55de13704b78&gt;\n&lt;environment: 0x55de202cede8&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556fe89717a0&gt;\n&lt;environment: 0x556ff3dadfc8&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55de137081a0&gt;\n&lt;environment: 0x55de202cec98&gt;\n",
      :domain [1.0E-100 ##Inf]},

### 2024-02-24 docs/projects/datavis/ggplot/index.qmd
ggplot - rerendered

--- 2024-02-05 docs/projects/noj/index.qmd
@@
 # Preface
-[Noj](https://scicloj.github.io/noj/) (short for Scinojure)
-is an opinionated way to use the emerging Clojure data stack.
-It collects a few of the relevant libraries together
-and addes some layers of composition on top of them.
+In this series of notebooks, we explore [ggplot2](https://ggplot2.tidyverse.org/), a famous R package for grammar-of-graphics data visualization, from within Clojure.
 
@@
 ```{=html}
-<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/index.clj">projects/noj/notebooks/index.clj</a></small></small></pre></div>
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/index.clj">projects/datavis/ggplot/notebooks/index.clj</a></small></small></pre></div>
 ```

### 2024-02-24 docs/projects/datavis/ggplot/repesenting.qmd
ggplot - rerendered

--- 2024-02-23 docs/projects/datavis/ggplot/repesenting.qmd
@@
 
-# Using ggplot Clojure using ClojisR
+# Representing ggplot plots as Clojure data
 
@@
 </defs>
-<g id="surface266">
+<g id="surface69">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x556feb092c18&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x563a2d826c90&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x556feb092c18&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x563a2d826c90&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 
@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x556fe5ccb140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x563a29cf6140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x556fe5ccb140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x563a29cf6140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x556fe8978000&gt;\n&lt;environment: 0x556ff5d42868&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x563a2dc555a8&gt;\n&lt;environment: 0x563a37fcae88&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556fe8974af0&gt;\n&lt;environment: 0x556ff5d46510&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x563a2dc58f88&gt;\n&lt;environment: 0x563a37fcad00&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556fe89717a0&gt;\n&lt;environment: 0x556ff5d463c0&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x563a2dc62300&gt;\n&lt;environment: 0x563a37fcabb0&gt;\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x556feae855e8&gt;\n&lt;environment: 0x556ff3da9fc8&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x563a32799c88&gt;\n&lt;environment: 0x563a3279a318&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x556feae85738&gt;\n&lt;environment: 0x556ff3da9fc8&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x563a32799dd8&gt;\n&lt;environment: 0x563a3279a318&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x556feae75a68&gt;\n&lt;environment: 0x556ff3dae4d0&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x563a32792388&gt;\n&lt;environment: 0x563a3278d628&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556fe8974af0&gt;\n&lt;environment: 0x556ff3dae118&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x563a2dc58f88&gt;\n&lt;environment: 0x563a3278d9e0&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556fe89717a0&gt;\n&lt;environment: 0x556ff3dadfc8&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x563a2dc62300&gt;\n&lt;environment: 0x563a3278db30&gt;\n",
      :domain [1.0E-100 ##Inf]},

### 2024-02-24 docs/projects/datavis/ggplot/index.qmd
ggplot - rerendered

@@
 # Preface
+
 In this series of notebooks, we explore [ggplot2](https://ggplot2.tidyverse.org/), a famous R package for grammar-of-graphics data visualization, from within Clojure.

### 2024-02-24 docs/projects/datavis/ggplot/repesenting.qmd
ggplot - rerendered

--- 2024-02-23 docs/projects/datavis/ggplot/repesenting.qmd
@@
 </defs>
-<g id="surface309">
+<g id="surface69">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55de132d0148&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55b95a21db80&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55de132d0148&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55b95a21db80&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 
@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x55de0f7b0140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x55b9566f0140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x55de0f7b0140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x55b9566f0140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55de136ff278&gt;\n&lt;environment: 0x55de1aecfde8&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55b95a64c498&gt;\n&lt;environment: 0x55b9649d1458&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55de13704b78&gt;\n&lt;environment: 0x55de1aecff70&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55b95a64fe78&gt;\n&lt;environment: 0x55b9649d12d0&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55de137081a0&gt;\n&lt;environment: 0x55de1aed00c0&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55b95a6591f0&gt;\n&lt;environment: 0x55b9649d1180&gt;\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55de203785e0&gt;\n&lt;environment: 0x55de202c9318&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55b95f192f70&gt;\n&lt;environment: 0x55b95f193750&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x55de20378490&gt;\n&lt;environment: 0x55de202c9318&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x55b95f193130&gt;\n&lt;environment: 0x55b95f193750&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55de20380260&gt;\n&lt;environment: 0x55de202cf2b8&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55b95f18b830&gt;\n&lt;environment: 0x55b95f18ae80&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55de13704b78&gt;\n&lt;environment: 0x55de202cede8&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55b95a64fe78&gt;\n&lt;environment: 0x55b95f186e88&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55de137081a0&gt;\n&lt;environment: 0x55de202cec98&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55b95a6591f0&gt;\n&lt;environment: 0x55b95f186fd8&gt;\n",
      :domain [1.0E-100 ##Inf]},

### 2024-02-24 docs/projects/datavis/ggplot/comparing.qmd
ggplot - rerendered

--- 2024-02-24 docs/projects/datavis/ggplot/repesenting.qmd
@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: repesenting.html}
+  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: comparing.html}
 code-block-background: true
@@
 </style>
-<script src="repesenting_files/md-default6.js" type="text/javascript"></script><script src="repesenting_files/md-default7.js" type="text/javascript"></script>
+<script src="comparing_files/md-default4.js" type="text/javascript"></script><script src="comparing_files/md-default5.js" type="text/javascript"></script>
 
@@
 
-# Representing ggplot plots as Clojure data
-
-## Setup
-
-We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.
+# Comparing the data representations of ggplot plots
 
@@
 ```clojure
-(ns repesenting
+(ns comparing
   (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
@@
             [clojure.pprint :as pp]
-            [clojure.string :as str]))
-```
-:::
-
-Loading ggplot2:
-
-::: {.sourceClojure}
-```clojure
-(r/library "ggplot2")
-```
-:::
-
-::: {.printedClojure}
-```clojure
-[1] "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices" "utils"    
-[7] "datasets"  "methods"   "base"
-
-```
-:::
-
-Requireing the base R library as a Clojure namespace:
-
-::: {.sourceClojure}
-```clojure
-(r/require-r '[base])
-```
-:::
-
-::: {.printedClojure}
-```clojure
-nil
-
-```
-:::
-
-## An example plot
-
-Here is how we may generate and display a plot:
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))"
-    r
-    plotting/plot->svg
-    kind/html)
-```
-:::
-
-```{=html}
-<?xml version="1.0" encoding="UTF-8"?>
-<svg xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink" width="504pt" height="504pt" viewBox="0 0 504 504" version="1.1">
-<defs>
-<g>
-<symbol overflow="visible" id="glyph0-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph0-1">
-<path style="stroke:none;" d="M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-2">
-<path style="stroke:none;" d="M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-3">
-<path style="stroke:none;" d="M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-4">
-<path style="stroke:none;" d="M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-5">
-<path style="stroke:none;" d="M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-6">
-<path style="stroke:none;" d="M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-7">
-<path style="stroke:none;" d="M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-8">
-<path style="stroke:none;" d="M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph1-1">
-<path style="stroke:none;" d="M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-2">
-<path style="stroke:none;" d="M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-3">
-<path style="stroke:none;" d="M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-4">
-<path style="stroke:none;" d="M 2.84375 -5.765625 L 1.875 -5.765625 L 1.875 -6.671875 C 1.875 -7.046875 2.09375 -7.25 2.515625 -7.25 C 2.59375 -7.25 2.625 -7.25 2.84375 -7.234375 L 2.84375 -8 C 2.625 -8.046875 2.515625 -8.046875 2.328125 -8.046875 C 1.46875 -8.046875 0.96875 -7.5625 0.96875 -6.75 L 0.96875 -5.765625 L 0.203125 -5.765625 L 0.203125 -5.015625 L 0.96875 -5.015625 L 0.96875 0 L 1.875 0 L 1.875 -5.015625 L 2.84375 -5.015625 Z M 2.84375 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-5">
-<path style="stroke:none;" d="M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-6">
-<path style="stroke:none;" d="M 2.984375 -5.921875 C 1.359375 -5.921875 0.390625 -4.78125 0.390625 -2.84375 C 0.390625 -0.890625 1.359375 0.25 3 0.25 C 4.625 0.25 5.609375 -0.90625 5.609375 -2.796875 C 5.609375 -4.796875 4.65625 -5.921875 2.984375 -5.921875 Z M 3 -5.078125 C 4.03125 -5.078125 4.65625 -4.234375 4.65625 -2.8125 C 4.65625 -1.4375 4.015625 -0.59375 3 -0.59375 C 1.984375 -0.59375 1.359375 -1.4375 1.359375 -2.84375 C 1.359375 -4.234375 1.984375 -5.078125 3 -5.078125 Z M 3 -5.078125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-7">
-<path style="stroke:none;" d="M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-8">
-<path style="stroke:none;" d="M 2.59375 -8.015625 C 1.5 -6.578125 0.796875 -4.578125 0.796875 -2.84375 C 0.796875 -1.109375 1.5 0.890625 2.59375 2.328125 L 3.203125 2.328125 C 2.234375 0.765625 1.6875 -1.09375 1.6875 -2.84375 C 1.6875 -4.59375 2.234375 -6.453125 3.203125 -8.015625 Z M 2.59375 -8.015625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-9">
-<path style="stroke:none;" d="M 1.671875 -8.015625 L 0.75 -8.015625 L 0.75 0 L 1.671875 0 Z M 1.671875 -8.015625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-10">
-<path style="stroke:none;" d="M 1.015625 2.328125 C 2.125 0.890625 2.8125 -1.109375 2.8125 -2.84375 C 2.8125 -4.578125 2.125 -6.578125 1.015625 -8.015625 L 0.421875 -8.015625 C 1.390625 -6.453125 1.921875 -4.59375 1.921875 -2.84375 C 1.921875 -1.09375 1.390625 0.765625 0.421875 2.328125 Z M 1.015625 2.328125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph2-1">
-<path style="stroke:none;" d="M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-2">
-<path style="stroke:none;" d="M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-3">
-<path style="stroke:none;" d="M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 "/>
-</symbol>
-</g>
-<clipPath id="clip1">
-  <path d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 234.925781 L 35.152344 234.925781 Z M 35.152344 23.246094 "/>
-</clipPath>
-<clipPath id="clip2">
-  <path d="M 35.152344 203 L 229.136719 203 L 229.136719 205 L 35.152344 205 Z M 35.152344 203 "/>
-</clipPath>
-<clipPath id="clip3">
-  <path d="M 35.152344 150 L 229.136719 150 L 229.136719 152 L 35.152344 152 Z M 35.152344 150 "/>
-</clipPath>
-<clipPath id="clip4">
-  <path d="M 35.152344 97 L 229.136719 97 L 229.136719 98 L 35.152344 98 Z M 35.152344 97 "/>
-</clipPath>
-<clipPath id="clip5">
-  <path d="M 35.152344 44 L 229.136719 44 L 229.136719 45 L 35.152344 45 Z M 35.152344 44 "/>
-</clipPath>
-<clipPath id="clip6">
-  <path d="M 67 23.246094 L 68 23.246094 L 68 234.925781 L 67 234.925781 Z M 67 23.246094 "/>
-</clipPath>
-<clipPath id="clip7">
-  <path d="M 101 23.246094 L 102 23.246094 L 102 234.925781 L 101 234.925781 Z M 101 23.246094 "/>
-</clipPath>
-<clipPath id="clip8">
-  <path d="M 135 23.246094 L 136 23.246094 L 136 234.925781 L 135 234.925781 Z M 135 23.246094 "/>
-</clipPath>
-<clipPath id="clip9">
-  <path d="M 169 23.246094 L 170 23.246094 L 170 234.925781 L 169 234.925781 Z M 169 23.246094 "/>
-</clipPath>
-<clipPath id="clip10">
-  <path d="M 203 23.246094 L 204 23.246094 L 204 234.925781 L 203 234.925781 Z M 203 23.246094 "/>
-</clipPath>
-<clipPath id="clip11">
-  <path d="M 35.152344 230 L 229.136719 230 L 229.136719 232 L 35.152344 232 Z M 35.152344 230 "/>
-</clipPath>
-<clipPath id="clip12">
-  <path d="M 35.152344 177 L 229.136719 177 L 229.136719 179 L 35.152344 179 Z M 35.152344 177 "/>
-</clipPath>
-<clipPath id="clip13">
-  <path d="M 35.152344 123 L 229.136719 123 L 229.136719 125 L 35.152344 125 Z M 35.152344 123 "/>
-</clipPath>
-<clipPath id="clip14">
-  <path d="M 35.152344 70 L 229.136719 70 L 229.136719 72 L 35.152344 72 Z M 35.152344 70 "/>
-</clipPath>
-<clipPath id="clip15">
-  <path d="M 50 23.246094 L 52 23.246094 L 52 234.925781 L 50 234.925781 Z M 50 23.246094 "/>
-</clipPath>
-<clipPath id="clip16">
-  <path d="M 84 23.246094 L 86 23.246094 L 86 234.925781 L 84 234.925781 Z M 84 23.246094 "/>
-</clipPath>
-<clipPath id="clip17">
-  <path d="M 118 23.246094 L 120 23.246094 L 120 234.925781 L 118 234.925781 Z M 118 23.246094 "/>
-</clipPath>
-<clipPath id="clip18">
-  <path d="M 151 23.246094 L 154 23.246094 L 154 234.925781 L 151 234.925781 Z M 151 23.246094 "/>
-</clipPath>
-<clipPath id="clip19">
-  <path d="M 185 23.246094 L 187 23.246094 L 187 234.925781 L 185 234.925781 Z M 185 23.246094 "/>
-</clipPath>
-<clipPath id="clip20">
-  <path d="M 219 23.246094 L 221 23.246094 L 221 234.925781 L 219 234.925781 Z M 219 23.246094 "/>
-</clipPath>
-<clipPath id="clip21">
-  <path d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 469.851562 L 35.152344 469.851562 Z M 35.152344 258.171875 "/>
-</clipPath>
-<clipPath id="clip22">
-  <path d="M 35.152344 438 L 229.136719 438 L 229.136719 440 L 35.152344 440 Z M 35.152344 438 "/>
-</clipPath>
-<clipPath id="clip23">
-  <path d="M 35.152344 385 L 229.136719 385 L 229.136719 387 L 35.152344 387 Z M 35.152344 385 "/>
-</clipPath>
-<clipPath id="clip24">
-  <path d="M 35.152344 332 L 229.136719 332 L 229.136719 333 L 35.152344 333 Z M 35.152344 332 "/>
-</clipPath>
-<clipPath id="clip25">
-  <path d="M 35.152344 278 L 229.136719 278 L 229.136719 280 L 35.152344 280 Z M 35.152344 278 "/>
-</clipPath>
-<clipPath id="clip26">
-  <path d="M 67 258.171875 L 68 258.171875 L 68 469.851562 L 67 469.851562 Z M 67 258.171875 "/>
-</clipPath>
-<clipPath id="clip27">
-  <path d="M 101 258.171875 L 102 258.171875 L 102 469.851562 L 101 469.851562 Z M 101 258.171875 "/>
-</clipPath>
-<clipPath id="clip28">
-  <path d="M 135 258.171875 L 136 258.171875 L 136 469.851562 L 135 469.851562 Z M 135 258.171875 "/>
-</clipPath>
-<clipPath id="clip29">
-  <path d="M 169 258.171875 L 170 258.171875 L 170 469.851562 L 169 469.851562 Z M 169 258.171875 "/>
-</clipPath>
-<clipPath id="clip30">
-  <path d="M 203 258.171875 L 204 258.171875 L 204 469.851562 L 203 469.851562 Z M 203 258.171875 "/>
-</clipPath>
-<clipPath id="clip31">
-  <path d="M 35.152344 465 L 229.136719 465 L 229.136719 467 L 35.152344 467 Z M 35.152344 465 "/>
-</clipPath>
-<clipPath id="clip32">
-  <path d="M 35.152344 411 L 229.136719 411 L 229.136719 414 L 35.152344 414 Z M 35.152344 411 "/>
-</clipPath>
-<clipPath id="clip33">
-  <path d="M 35.152344 358 L 229.136719 358 L 229.136719 360 L 35.152344 360 Z M 35.152344 358 "/>
-</clipPath>
-<clipPath id="clip34">
-  <path d="M 35.152344 305 L 229.136719 305 L 229.136719 307 L 35.152344 307 Z M 35.152344 305 "/>
-</clipPath>
-<clipPath id="clip35">
-  <path d="M 50 258.171875 L 52 258.171875 L 52 469.851562 L 50 469.851562 Z M 50 258.171875 "/>
-</clipPath>
-<clipPath id="clip36">
-  <path d="M 84 258.171875 L 86 258.171875 L 86 469.851562 L 84 469.851562 Z M 84 258.171875 "/>
-</clipPath>
-<clipPath id="clip37">
-  <path d="M 118 258.171875 L 120 258.171875 L 120 469.851562 L 118 469.851562 Z M 118 258.171875 "/>
-</clipPath>
-<clipPath id="clip38">
-  <path d="M 151 258.171875 L 154 258.171875 L 154 469.851562 L 151 469.851562 Z M 151 258.171875 "/>
-</clipPath>
-<clipPath id="clip39">
-  <path d="M 185 258.171875 L 187 258.171875 L 187 469.851562 L 185 469.851562 Z M 185 258.171875 "/>
-</clipPath>
-<clipPath id="clip40">
-  <path d="M 219 258.171875 L 221 258.171875 L 221 469.851562 L 219 469.851562 Z M 219 258.171875 "/>
-</clipPath>
-<clipPath id="clip41">
-  <path d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 234.925781 L 234.617188 234.925781 Z M 234.617188 23.246094 "/>
-</clipPath>
-<clipPath id="clip42">
-  <path d="M 234.617188 203 L 428.601562 203 L 428.601562 205 L 234.617188 205 Z M 234.617188 203 "/>
-</clipPath>
-<clipPath id="clip43">
-  <path d="M 234.617188 150 L 428.601562 150 L 428.601562 152 L 234.617188 152 Z M 234.617188 150 "/>
-</clipPath>
-<clipPath id="clip44">
-  <path d="M 234.617188 97 L 428.601562 97 L 428.601562 98 L 234.617188 98 Z M 234.617188 97 "/>
-</clipPath>
-<clipPath id="clip45">
-  <path d="M 234.617188 44 L 428.601562 44 L 428.601562 45 L 234.617188 45 Z M 234.617188 44 "/>
-</clipPath>
-<clipPath id="clip46">
-  <path d="M 266 23.246094 L 268 23.246094 L 268 234.925781 L 266 234.925781 Z M 266 23.246094 "/>
-</clipPath>
-<clipPath id="clip47">
-  <path d="M 300 23.246094 L 302 23.246094 L 302 234.925781 L 300 234.925781 Z M 300 23.246094 "/>
-</clipPath>
-<clipPath id="clip48">
-  <path d="M 334 23.246094 L 336 23.246094 L 336 234.925781 L 334 234.925781 Z M 334 23.246094 "/>
-</clipPath>
-<clipPath id="clip49">
-  <path d="M 368 23.246094 L 370 23.246094 L 370 234.925781 L 368 234.925781 Z M 368 23.246094 "/>
-</clipPath>
-<clipPath id="clip50">
-  <path d="M 402 23.246094 L 404 23.246094 L 404 234.925781 L 402 234.925781 Z M 402 23.246094 "/>
-</clipPath>
-<clipPath id="clip51">
-  <path d="M 234.617188 230 L 428.601562 230 L 428.601562 232 L 234.617188 232 Z M 234.617188 230 "/>
-</clipPath>
-<clipPath id="clip52">
-  <path d="M 234.617188 177 L 428.601562 177 L 428.601562 179 L 234.617188 179 Z M 234.617188 177 "/>
-</clipPath>
-<clipPath id="clip53">
-  <path d="M 234.617188 123 L 428.601562 123 L 428.601562 125 L 234.617188 125 Z M 234.617188 123 "/>
-</clipPath>
-<clipPath id="clip54">
-  <path d="M 234.617188 70 L 428.601562 70 L 428.601562 72 L 234.617188 72 Z M 234.617188 70 "/>
-</clipPath>
-<clipPath id="clip55">
-  <path d="M 249 23.246094 L 251 23.246094 L 251 234.925781 L 249 234.925781 Z M 249 23.246094 "/>
-</clipPath>
-<clipPath id="clip56">
-  <path d="M 283 23.246094 L 285 23.246094 L 285 234.925781 L 283 234.925781 Z M 283 23.246094 "/>
-</clipPath>
-<clipPath id="clip57">
-  <path d="M 317 23.246094 L 319 23.246094 L 319 234.925781 L 317 234.925781 Z M 317 23.246094 "/>
-</clipPath>
-<clipPath id="clip58">
-  <path d="M 351 23.246094 L 353 23.246094 L 353 234.925781 L 351 234.925781 Z M 351 23.246094 "/>
-</clipPath>
-<clipPath id="clip59">
-  <path d="M 385 23.246094 L 387 23.246094 L 387 234.925781 L 385 234.925781 Z M 385 23.246094 "/>
-</clipPath>
-<clipPath id="clip60">
-  <path d="M 419 23.246094 L 421 23.246094 L 421 234.925781 L 419 234.925781 Z M 419 23.246094 "/>
-</clipPath>
-<clipPath id="clip61">
-  <path d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 469.851562 L 234.617188 469.851562 Z M 234.617188 258.171875 "/>
-</clipPath>
-<clipPath id="clip62">
-  <path d="M 234.617188 438 L 428.601562 438 L 428.601562 440 L 234.617188 440 Z M 234.617188 438 "/>
-</clipPath>
-<clipPath id="clip63">
-  <path d="M 234.617188 385 L 428.601562 385 L 428.601562 387 L 234.617188 387 Z M 234.617188 385 "/>
-</clipPath>
-<clipPath id="clip64">
-  <path d="M 234.617188 332 L 428.601562 332 L 428.601562 333 L 234.617188 333 Z M 234.617188 332 "/>
-</clipPath>
-<clipPath id="clip65">
-  <path d="M 234.617188 278 L 428.601562 278 L 428.601562 280 L 234.617188 280 Z M 234.617188 278 "/>
-</clipPath>
-<clipPath id="clip66">
-  <path d="M 266 258.171875 L 268 258.171875 L 268 469.851562 L 266 469.851562 Z M 266 258.171875 "/>
-</clipPath>
-<clipPath id="clip67">
-  <path d="M 300 258.171875 L 302 258.171875 L 302 469.851562 L 300 469.851562 Z M 300 258.171875 "/>
-</clipPath>
-<clipPath id="clip68">
-  <path d="M 334 258.171875 L 336 258.171875 L 336 469.851562 L 334 469.851562 Z M 334 258.171875 "/>
-</clipPath>
-<clipPath id="clip69">
-  <path d="M 368 258.171875 L 370 258.171875 L 370 469.851562 L 368 469.851562 Z M 368 258.171875 "/>
-</clipPath>
-<clipPath id="clip70">
-  <path d="M 402 258.171875 L 404 258.171875 L 404 469.851562 L 402 469.851562 Z M 402 258.171875 "/>
-</clipPath>
-<clipPath id="clip71">
-  <path d="M 234.617188 465 L 428.601562 465 L 428.601562 467 L 234.617188 467 Z M 234.617188 465 "/>
-</clipPath>
-<clipPath id="clip72">
-  <path d="M 234.617188 411 L 428.601562 411 L 428.601562 414 L 234.617188 414 Z M 234.617188 411 "/>
-</clipPath>
-<clipPath id="clip73">
-  <path d="M 234.617188 358 L 428.601562 358 L 428.601562 360 L 234.617188 360 Z M 234.617188 358 "/>
-</clipPath>
-<clipPath id="clip74">
-  <path d="M 234.617188 305 L 428.601562 305 L 428.601562 307 L 234.617188 307 Z M 234.617188 305 "/>
-</clipPath>
-<clipPath id="clip75">
-  <path d="M 249 258.171875 L 251 258.171875 L 251 469.851562 L 249 469.851562 Z M 249 258.171875 "/>
-</clipPath>
-<clipPath id="clip76">
-  <path d="M 283 258.171875 L 285 258.171875 L 285 469.851562 L 283 469.851562 Z M 283 258.171875 "/>
-</clipPath>
-<clipPath id="clip77">
-  <path d="M 317 258.171875 L 319 258.171875 L 319 469.851562 L 317 469.851562 Z M 317 258.171875 "/>
-</clipPath>
-<clipPath id="clip78">
-  <path d="M 351 258.171875 L 353 258.171875 L 353 469.851562 L 351 469.851562 Z M 351 258.171875 "/>
-</clipPath>
-<clipPath id="clip79">
-  <path d="M 385 258.171875 L 387 258.171875 L 387 469.851562 L 385 469.851562 Z M 385 258.171875 "/>
-</clipPath>
-<clipPath id="clip80">
-  <path d="M 419 258.171875 L 421 258.171875 L 421 469.851562 L 419 469.851562 Z M 419 258.171875 "/>
-</clipPath>
-<clipPath id="clip81">
-  <path d="M 35.152344 240.402344 L 229.136719 240.402344 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 240.402344 "/>
-</clipPath>
-<clipPath id="clip82">
-  <path d="M 234.617188 240.402344 L 428.601562 240.402344 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 240.402344 "/>
-</clipPath>
-<clipPath id="clip83">
-  <path d="M 35.152344 5.480469 L 229.136719 5.480469 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 5.480469 "/>
-</clipPath>
-<clipPath id="clip84">
-  <path d="M 234.617188 5.480469 L 428.601562 5.480469 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 5.480469 "/>
-</clipPath>
-</defs>
-<g id="surface69">
-<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
-<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 "/>
-<g clip-path="url(#clip1)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 234.925781 L 229.136719 234.925781 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 234.925781 "/>
-</g>
-<g clip-path="url(#clip2)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 204.210938 L 229.136719 204.210938 "/>
-</g>
-<g clip-path="url(#clip3)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 150.910156 L 229.136719 150.910156 "/>
-</g>
-<g clip-path="url(#clip4)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 97.613281 L 229.136719 97.613281 "/>
-</g>
-<g clip-path="url(#clip5)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 44.3125 L 229.136719 44.3125 "/>
-</g>
-<g clip-path="url(#clip6)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 234.925781 L 67.707031 23.246094 "/>
-</g>
-<g clip-path="url(#clip7)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 234.925781 L 101.621094 23.246094 "/>
-</g>
-<g clip-path="url(#clip8)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 234.925781 L 135.535156 23.246094 "/>
-</g>
-<g clip-path="url(#clip9)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 234.925781 L 169.449219 23.246094 "/>
-</g>
-<g clip-path="url(#clip10)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 234.925781 L 203.363281 23.246094 "/>
-</g>
-<g clip-path="url(#clip11)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 230.859375 L 229.136719 230.859375 "/>
-</g>
-<g clip-path="url(#clip12)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 177.558594 L 229.136719 177.558594 "/>
-</g>
-<g clip-path="url(#clip13)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 124.261719 L 229.136719 124.261719 "/>
-</g>
-<g clip-path="url(#clip14)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 70.960938 L 229.136719 70.960938 "/>
-</g>
-<g clip-path="url(#clip15)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 234.925781 L 50.75 23.246094 "/>
-</g>
-<g clip-path="url(#clip16)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 234.925781 L 84.664062 23.246094 "/>
-</g>
-<g clip-path="url(#clip17)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 234.925781 L 118.578125 23.246094 "/>
-</g>
-<g clip-path="url(#clip18)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 234.925781 L 152.492188 23.246094 "/>
-</g>
-<g clip-path="url(#clip19)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 234.925781 L 186.40625 23.246094 "/>
-</g>
-<g clip-path="url(#clip20)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 234.925781 L 220.320312 23.246094 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 118.933594 C 120.53125 121.539062 116.625 121.539062 116.625 118.933594 C 116.625 116.324219 120.53125 116.324219 120.53125 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 150.910156 C 93.402344 153.515625 89.492188 153.515625 89.492188 150.910156 C 89.492188 148.304688 93.402344 148.304688 93.402344 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 124.261719 C 134.097656 126.867188 130.1875 126.867188 130.1875 124.261719 C 130.1875 121.65625 134.097656 121.65625 134.097656 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 108.273438 C 174.796875 110.878906 170.886719 110.878906 170.886719 108.273438 C 170.886719 105.664062 174.796875 105.664062 174.796875 108.273438 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 113.601562 C 154.445312 116.207031 150.539062 116.207031 150.539062 113.601562 C 150.539062 110.996094 154.445312 110.996094 154.445312 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 129.589844 C 140.882812 132.199219 136.972656 132.199219 136.972656 129.589844 C 136.972656 126.984375 140.882812 126.984375 140.882812 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 102.941406 C 161.230469 105.546875 157.320312 105.546875 157.320312 102.941406 C 157.320312 100.335938 161.230469 100.335938 161.230469 102.941406 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 92.28125 C 154.445312 94.890625 150.539062 94.890625 150.539062 92.28125 C 150.539062 89.675781 154.445312 89.675781 154.445312 92.28125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 92.28125 C 147.664062 94.890625 143.753906 94.890625 143.753906 92.28125 C 143.753906 89.675781 147.664062 89.675781 147.664062 92.28125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 140.25 C 106.96875 142.859375 103.058594 142.859375 103.058594 140.25 C 103.058594 137.644531 106.96875 137.644531 106.96875 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 129.589844 C 113.75 132.199219 109.839844 132.199219 109.839844 129.589844 C 109.839844 126.984375 113.75 126.984375 113.75 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 118.933594 C 140.882812 121.539062 136.972656 121.539062 136.972656 118.933594 C 136.972656 116.324219 140.882812 116.324219 140.882812 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 113.601562 C 140.882812 116.207031 136.972656 116.207031 136.972656 113.601562 C 136.972656 110.996094 140.882812 110.996094 140.882812 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 150.910156 C 106.96875 153.515625 103.058594 153.515625 103.058594 150.910156 C 103.058594 148.304688 106.96875 148.304688 106.96875 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 145.582031 C 120.53125 148.1875 116.625 148.1875 116.625 145.582031 C 116.625 142.976562 120.53125 142.976562 120.53125 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 161.570312 C 106.96875 164.175781 103.058594 164.175781 103.058594 161.570312 C 103.058594 158.964844 106.96875 158.964844 106.96875 161.570312 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 145.582031 C 127.316406 148.1875 123.40625 148.1875 123.40625 145.582031 C 123.40625 142.976562 127.316406 142.976562 127.316406 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 150.910156 C 120.53125 153.515625 116.625 153.515625 116.625 150.910156 C 116.625 148.304688 120.53125 148.304688 120.53125 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 118.933594 C 134.097656 121.539062 130.1875 121.539062 130.1875 118.933594 C 130.1875 116.324219 134.097656 116.324219 134.097656 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 124.261719 C 147.664062 126.867188 143.753906 126.867188 143.753906 124.261719 C 143.753906 121.65625 147.664062 121.65625 147.664062 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 108.273438 C 147.664062 110.878906 143.753906 110.878906 143.753906 108.273438 C 143.753906 105.664062 147.664062 105.664062 147.664062 108.273438 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 86.953125 C 174.796875 89.558594 170.886719 89.558594 170.886719 86.953125 C 170.886719 84.347656 174.796875 84.347656 174.796875 86.953125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 166.902344 C 100.183594 169.507812 96.273438 169.507812 96.273438 166.902344 C 96.273438 164.292969 100.183594 164.292969 100.183594 166.902344 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 208.707031 49.644531 C 208.707031 52.25 204.800781 52.25 204.800781 49.644531 C 204.800781 47.035156 208.707031 47.035156 208.707031 49.644531 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 222.273438 49.644531 C 222.273438 52.25 218.363281 52.25 218.363281 49.644531 C 218.363281 47.035156 222.273438 47.035156 222.273438 49.644531 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 181.578125 65.632812 C 181.578125 68.238281 177.667969 68.238281 177.667969 65.632812 C 177.667969 63.027344 181.578125 63.027344 181.578125 65.632812 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 134.921875 C 113.75 137.527344 109.839844 137.527344 109.839844 134.921875 C 109.839844 132.316406 113.75 132.316406 113.75 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 84.664062 165.398438 L 86.382812 163.894531 L 88.097656 162.386719 L 91.535156 159.371094 L 93.25 157.859375 L 94.96875 156.347656 L 96.683594 154.832031 L 98.402344 153.3125 L 100.117188 151.792969 L 103.554688 148.738281 L 105.269531 147.207031 L 106.988281 145.671875 L 108.703125 144.128906 L 110.421875 142.582031 L 112.140625 141.027344 L 113.855469 139.46875 L 115.574219 137.902344 L 117.289062 136.328125 L 119.007812 134.742188 L 120.726562 133.148438 L 122.441406 131.546875 L 124.160156 129.933594 L 125.875 128.3125 L 127.59375 126.679688 L 129.308594 125.035156 L 131.027344 123.382812 L 132.746094 121.71875 L 134.460938 120.050781 L 136.179688 118.371094 L 137.894531 116.683594 L 139.613281 114.988281 L 141.332031 113.289062 L 143.046875 111.582031 L 144.765625 109.871094 L 146.480469 108.152344 L 148.199219 106.433594 L 149.917969 104.710938 L 151.632812 102.980469 L 153.351562 101.25 L 155.066406 99.515625 L 156.785156 97.78125 L 158.503906 96.042969 L 160.21875 94.300781 L 161.9375 92.558594 L 163.652344 90.816406 L 165.371094 89.070312 L 167.085938 87.324219 L 168.804688 85.578125 L 170.523438 83.828125 L 172.238281 82.078125 L 173.957031 80.328125 L 175.671875 78.574219 L 177.390625 76.824219 L 179.109375 75.070312 L 180.824219 73.316406 L 182.542969 71.5625 L 184.257812 69.804688 L 185.976562 68.050781 L 187.695312 66.292969 L 189.410156 64.539062 L 191.128906 62.78125 L 192.84375 61.023438 L 196.28125 57.507812 L 197.996094 55.75 L 199.714844 53.992188 L 201.429688 52.230469 L 203.148438 50.472656 L 204.863281 48.710938 L 206.582031 46.953125 L 208.300781 45.191406 L 210.015625 43.433594 L 211.734375 41.671875 L 213.449219 39.914062 L 216.886719 36.390625 L 218.601562 34.628906 L 220.320312 32.867188 L 220.320312 48.824219 L 218.601562 50.3125 L 216.886719 51.800781 L 215.167969 53.289062 L 213.449219 54.78125 L 211.734375 56.269531 L 210.015625 57.761719 L 208.300781 59.25 L 204.863281 62.234375 L 203.148438 63.722656 L 201.429688 65.214844 L 199.714844 66.707031 L 197.996094 68.199219 L 196.28125 69.691406 L 192.84375 72.675781 L 191.128906 74.167969 L 189.410156 75.664062 L 187.695312 77.15625 L 184.257812 80.148438 L 182.542969 81.640625 L 180.824219 83.136719 L 179.109375 84.636719 L 175.671875 87.628906 L 173.957031 89.128906 L 172.238281 90.628906 L 170.523438 92.128906 L 168.804688 93.632812 L 167.085938 95.132812 L 165.371094 96.636719 L 163.652344 98.144531 L 161.9375 99.648438 L 160.21875 101.160156 L 158.503906 102.667969 L 156.785156 104.179688 L 155.066406 105.695312 L 153.351562 107.210938 L 151.632812 108.730469 L 149.917969 110.253906 L 148.199219 111.78125 L 146.480469 113.3125 L 144.765625 114.84375 L 143.046875 116.382812 L 141.332031 117.929688 L 139.613281 119.476562 L 137.894531 121.035156 L 136.179688 122.597656 L 134.460938 124.167969 L 132.746094 125.75 L 131.027344 127.335938 L 129.308594 128.933594 L 127.59375 130.542969 L 125.875 132.160156 L 124.160156 133.789062 L 122.441406 135.425781 L 120.726562 137.074219 L 119.007812 138.730469 L 117.289062 140.398438 L 115.574219 142.074219 L 113.855469 143.757812 L 112.140625 145.449219 L 110.421875 147.144531 L 108.703125 148.847656 L 106.988281 150.558594 L 105.269531 152.273438 L 103.554688 153.988281 L 101.835938 155.710938 L 100.117188 157.4375 L 98.402344 159.167969 L 96.683594 160.902344 L 94.96875 162.636719 L 93.25 164.371094 L 91.535156 166.113281 L 89.816406 167.851562 L 88.097656 169.597656 L 86.382812 171.339844 L 84.664062 173.085938 Z M 84.664062 165.398438 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 169.242188 L 86.382812 167.617188 L 88.097656 165.992188 L 91.535156 162.742188 L 93.25 161.117188 L 94.96875 159.492188 L 96.683594 157.867188 L 98.402344 156.242188 L 100.117188 154.613281 L 103.554688 151.363281 L 105.269531 149.738281 L 106.988281 148.113281 L 108.703125 146.488281 L 112.140625 143.238281 L 113.855469 141.613281 L 115.574219 139.988281 L 117.289062 138.363281 L 120.726562 135.113281 L 122.441406 133.488281 L 124.160156 131.859375 L 125.875 130.234375 L 127.59375 128.609375 L 129.308594 126.984375 L 132.746094 123.734375 L 134.460938 122.109375 L 136.179688 120.484375 L 137.894531 118.859375 L 141.332031 115.609375 L 143.046875 113.984375 L 144.765625 112.359375 L 146.480469 110.734375 L 148.199219 109.105469 L 149.917969 107.480469 L 151.632812 105.855469 L 153.351562 104.230469 L 155.066406 102.605469 L 158.503906 99.355469 L 160.21875 97.730469 L 161.9375 96.105469 L 163.652344 94.480469 L 165.371094 92.855469 L 167.085938 91.230469 L 170.523438 87.980469 L 172.238281 86.351562 L 173.957031 84.726562 L 175.671875 83.101562 L 179.109375 79.851562 L 180.824219 78.226562 L 182.542969 76.601562 L 184.257812 74.976562 L 187.695312 71.726562 L 189.410156 70.101562 L 191.128906 68.476562 L 192.84375 66.851562 L 194.5625 65.222656 L 196.28125 63.597656 L 197.996094 61.972656 L 199.714844 60.347656 L 201.429688 58.722656 L 203.148438 57.097656 L 204.863281 55.472656 L 208.300781 52.222656 L 210.015625 50.597656 L 211.734375 48.972656 L 213.449219 47.347656 L 216.886719 44.097656 L 218.601562 42.46875 L 220.320312 40.84375 "/>
-<g clip-path="url(#clip21)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 469.847656 L 229.136719 469.847656 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 469.847656 "/>
-</g>
-<g clip-path="url(#clip22)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 439.132812 L 229.136719 439.132812 "/>
-</g>
-<g clip-path="url(#clip23)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 385.835938 L 229.136719 385.835938 "/>
-</g>
-<g clip-path="url(#clip24)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 332.535156 L 229.136719 332.535156 "/>
-</g>
-<g clip-path="url(#clip25)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 279.238281 L 229.136719 279.238281 "/>
-</g>
-<g clip-path="url(#clip26)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 469.847656 L 67.707031 258.171875 "/>
-</g>
-<g clip-path="url(#clip27)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 469.847656 L 101.621094 258.171875 "/>
-</g>
-<g clip-path="url(#clip28)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 469.847656 L 135.535156 258.171875 "/>
-</g>
-<g clip-path="url(#clip29)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 469.847656 L 169.449219 258.171875 "/>
-</g>
-<g clip-path="url(#clip30)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 469.847656 L 203.363281 258.171875 "/>
-</g>
-<g clip-path="url(#clip31)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 465.785156 L 229.136719 465.785156 "/>
-</g>
-<g clip-path="url(#clip32)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 412.484375 L 229.136719 412.484375 "/>
-</g>
-<g clip-path="url(#clip33)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 359.1875 L 229.136719 359.1875 "/>
-</g>
-<g clip-path="url(#clip34)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 305.886719 L 229.136719 305.886719 "/>
-</g>
-<g clip-path="url(#clip35)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 469.847656 L 50.75 258.171875 "/>
-</g>
-<g clip-path="url(#clip36)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 469.847656 L 84.664062 258.171875 "/>
-</g>
-<g clip-path="url(#clip37)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 469.847656 L 118.578125 258.171875 "/>
-</g>
-<g clip-path="url(#clip38)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 469.847656 L 152.492188 258.171875 "/>
-</g>
-<g clip-path="url(#clip39)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 469.847656 L 186.40625 258.171875 "/>
-</g>
-<g clip-path="url(#clip40)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 469.847656 L 220.320312 258.171875 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 391.164062 C 86.621094 393.773438 82.710938 393.773438 82.710938 391.164062 C 82.710938 388.558594 86.621094 388.558594 86.621094 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 364.515625 C 106.96875 367.121094 103.058594 367.121094 103.058594 364.515625 C 103.058594 361.910156 106.96875 361.910156 106.96875 364.515625 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 59.488281 428.472656 C 59.488281 431.082031 55.578125 431.082031 55.578125 428.472656 C 55.578125 425.867188 59.488281 425.867188 59.488281 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 401.824219 C 86.621094 404.429688 82.710938 404.429688 82.710938 401.824219 C 82.710938 399.21875 86.621094 399.21875 86.621094 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 407.15625 C 86.621094 409.761719 82.710938 409.761719 82.710938 407.15625 C 82.710938 404.546875 86.621094 404.546875 86.621094 407.15625 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 423.144531 C 79.835938 425.75 75.925781 425.75 75.925781 423.144531 C 75.925781 420.539062 79.835938 420.539062 79.835938 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 385.835938 C 106.96875 388.441406 103.058594 388.441406 103.058594 385.835938 C 103.058594 383.230469 106.96875 383.230469 106.96875 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 401.824219 C 100.183594 404.429688 96.273438 404.429688 96.273438 401.824219 C 96.273438 399.21875 100.183594 399.21875 100.183594 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 412.484375 C 86.621094 415.089844 82.710938 415.089844 82.710938 412.484375 C 82.710938 409.878906 86.621094 409.878906 86.621094 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 375.175781 C 113.75 377.78125 109.839844 377.78125 109.839844 375.175781 C 109.839844 372.570312 113.75 372.570312 113.75 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 380.503906 C 113.75 383.113281 109.839844 383.113281 109.839844 380.503906 C 109.839844 377.898438 113.75 377.898438 113.75 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 412.484375 C 79.835938 415.089844 75.925781 415.089844 75.925781 412.484375 C 75.925781 409.878906 79.835938 409.878906 79.835938 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 375.175781 C 100.183594 377.78125 96.273438 377.78125 96.273438 375.175781 C 96.273438 372.570312 100.183594 372.570312 100.183594 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 369.847656 C 106.96875 372.453125 103.058594 372.453125 103.058594 369.847656 C 103.058594 367.238281 106.96875 367.238281 106.96875 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 423.144531 C 86.621094 425.75 82.710938 425.75 82.710938 423.144531 C 82.710938 420.539062 86.621094 420.539062 86.621094 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 57.535156 440.144531 L 58.21875 439.300781 L 60.28125 436.769531 L 60.96875 435.921875 L 61.65625 435.078125 L 62.339844 434.234375 L 63.027344 433.386719 L 63.714844 432.542969 L 65.089844 430.847656 L 65.777344 430.003906 L 66.464844 429.15625 L 67.148438 428.308594 L 67.835938 427.457031 L 68.523438 426.609375 L 69.210938 425.757812 L 69.898438 424.910156 L 70.585938 424.058594 L 71.269531 423.203125 L 72.644531 421.5 L 74.019531 419.789062 L 74.707031 418.929688 L 75.390625 418.070312 L 76.765625 416.351562 L 78.140625 414.625 L 78.828125 413.757812 L 79.511719 412.890625 L 80.886719 411.148438 L 81.574219 410.273438 L 82.261719 409.394531 L 82.949219 408.511719 L 83.632812 407.628906 L 85.007812 405.847656 L 86.382812 404.050781 L 87.070312 403.140625 L 87.753906 402.230469 L 88.441406 401.3125 L 89.128906 400.390625 L 89.816406 399.460938 L 90.503906 398.523438 L 91.191406 397.578125 L 91.875 396.628906 L 92.5625 395.667969 L 93.25 394.703125 L 93.9375 393.730469 L 94.625 392.75 L 95.3125 391.761719 L 95.996094 390.765625 L 96.683594 389.765625 L 97.371094 388.757812 L 98.058594 387.742188 L 98.746094 386.722656 L 99.433594 385.699219 L 100.117188 384.667969 L 100.804688 383.632812 L 101.492188 382.59375 L 102.179688 381.550781 L 102.867188 380.503906 L 103.554688 379.453125 L 104.238281 378.402344 L 105.613281 376.285156 L 106.988281 374.160156 L 107.675781 373.09375 L 108.359375 372.027344 L 109.046875 370.960938 L 109.734375 369.886719 L 110.421875 368.816406 L 111.796875 366.667969 L 111.796875 375.09375 L 111.109375 375.949219 L 109.046875 378.527344 L 108.359375 379.390625 L 107.675781 380.253906 L 106.300781 381.988281 L 105.613281 382.859375 L 104.238281 384.609375 L 103.554688 385.484375 L 102.867188 386.367188 L 101.492188 388.140625 L 100.804688 389.03125 L 100.117188 389.929688 L 99.433594 390.832031 L 98.746094 391.738281 L 98.058594 392.648438 L 97.371094 393.566406 L 96.683594 394.488281 L 95.996094 395.421875 L 95.3125 396.355469 L 94.625 397.300781 L 93.9375 398.25 L 93.25 399.210938 L 92.5625 400.175781 L 91.875 401.148438 L 91.191406 402.128906 L 90.503906 403.117188 L 89.816406 404.113281 L 89.128906 405.113281 L 88.441406 406.121094 L 87.753906 407.136719 L 87.070312 408.15625 L 86.382812 409.179688 L 85.695312 410.210938 L 85.007812 411.246094 L 84.320312 412.285156 L 83.632812 413.328125 L 82.949219 414.375 L 82.261719 415.425781 L 80.886719 417.535156 L 80.199219 418.59375 L 79.511719 419.65625 L 78.828125 420.71875 L 77.453125 422.851562 L 75.390625 426.0625 L 74.707031 427.136719 L 73.332031 429.285156 L 71.269531 432.519531 L 70.585938 433.597656 L 67.148438 439.007812 L 66.464844 440.089844 L 65.777344 441.175781 L 65.089844 442.257812 L 62.339844 446.601562 L 61.65625 447.6875 L 60.96875 448.773438 L 60.28125 449.863281 L 59.59375 450.949219 L 58.90625 452.039062 L 58.21875 453.125 L 57.535156 454.214844 Z M 57.535156 440.144531 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 57.535156 447.179688 L 58.21875 446.210938 L 60.28125 443.316406 L 60.96875 442.347656 L 61.65625 441.382812 L 62.339844 440.417969 L 63.027344 439.453125 L 63.714844 438.484375 L 65.777344 435.589844 L 66.464844 434.621094 L 67.148438 433.65625 L 69.210938 430.761719 L 69.898438 429.792969 L 70.585938 428.828125 L 71.269531 427.863281 L 71.957031 426.898438 L 72.644531 425.929688 L 74.707031 423.035156 L 75.390625 422.066406 L 77.453125 419.171875 L 78.140625 418.203125 L 78.828125 417.238281 L 79.511719 416.273438 L 80.199219 415.308594 L 80.886719 414.339844 L 82.949219 411.445312 L 83.632812 410.476562 L 85.695312 407.582031 L 86.382812 406.613281 L 87.070312 405.648438 L 87.753906 404.683594 L 88.441406 403.71875 L 89.128906 402.75 L 91.191406 399.855469 L 91.875 398.886719 L 94.625 395.027344 L 95.3125 394.058594 L 95.996094 393.09375 L 97.371094 391.164062 L 98.058594 390.195312 L 99.433594 388.265625 L 100.117188 387.300781 L 100.804688 386.332031 L 102.867188 383.4375 L 103.554688 382.46875 L 104.238281 381.503906 L 105.613281 379.574219 L 106.300781 378.605469 L 107.675781 376.675781 L 108.359375 375.710938 L 109.046875 374.742188 L 111.109375 371.847656 L 111.796875 370.878906 "/>
-<g clip-path="url(#clip41)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 234.925781 L 428.601562 234.925781 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 234.925781 "/>
-</g>
-<g clip-path="url(#clip42)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 204.210938 L 428.601562 204.210938 "/>
-</g>
-<g clip-path="url(#clip43)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 150.910156 L 428.601562 150.910156 "/>
-</g>
-<g clip-path="url(#clip44)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 97.613281 L 428.601562 97.613281 "/>
-</g>
-<g clip-path="url(#clip45)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 44.3125 L 428.601562 44.3125 "/>
-</g>
-<g clip-path="url(#clip46)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 234.925781 L 267.171875 23.246094 "/>
-</g>
-<g clip-path="url(#clip47)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 234.925781 L 301.085938 23.246094 "/>
-</g>
-<g clip-path="url(#clip48)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 234.925781 L 335 23.246094 "/>
-</g>
-<g clip-path="url(#clip49)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 234.925781 L 368.914062 23.246094 "/>
-</g>
-<g clip-path="url(#clip50)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 234.925781 L 402.828125 23.246094 "/>
-</g>
-<g clip-path="url(#clip51)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 230.859375 L 428.601562 230.859375 "/>
-</g>
-<g clip-path="url(#clip52)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 177.558594 L 428.601562 177.558594 "/>
-</g>
-<g clip-path="url(#clip53)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 124.261719 L 428.601562 124.261719 "/>
-</g>
-<g clip-path="url(#clip54)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 70.960938 L 428.601562 70.960938 "/>
-</g>
-<g clip-path="url(#clip55)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 234.925781 L 250.214844 23.246094 "/>
-</g>
-<g clip-path="url(#clip56)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 234.925781 L 284.128906 23.246094 "/>
-</g>
-<g clip-path="url(#clip57)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 234.925781 L 318.042969 23.246094 "/>
-</g>
-<g clip-path="url(#clip58)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 234.925781 L 351.957031 23.246094 "/>
-</g>
-<g clip-path="url(#clip59)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 234.925781 L 385.871094 23.246094 "/>
-</g>
-<g clip-path="url(#clip60)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 234.925781 L 419.785156 23.246094 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 134.921875 C 320 137.527344 316.089844 137.527344 316.089844 134.921875 C 316.089844 132.316406 320 132.316406 320 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 129.589844 C 320 132.199219 316.089844 132.199219 316.089844 129.589844 C 316.089844 126.984375 320 126.984375 320 129.589844 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 318.042969 124.148438 L 318.128906 124.214844 L 318.214844 124.285156 L 318.300781 124.347656 L 318.386719 124.414062 L 318.472656 124.476562 L 318.558594 124.535156 L 318.644531 124.597656 L 318.730469 124.652344 L 318.816406 124.710938 L 318.902344 124.761719 L 318.988281 124.816406 L 319.074219 124.867188 L 319.246094 124.960938 L 319.417969 125.046875 L 319.503906 125.085938 L 319.675781 125.15625 L 319.847656 125.21875 L 320.105469 125.289062 L 320.277344 125.320312 L 320.363281 125.332031 L 320.535156 125.347656 L 320.707031 125.347656 L 320.878906 125.332031 L 320.964844 125.320312 L 321.050781 125.304688 L 321.136719 125.285156 L 321.308594 125.238281 L 321.390625 125.207031 L 321.5625 125.136719 L 321.734375 125.050781 L 321.90625 124.949219 L 321.992188 124.894531 L 322.078125 124.835938 L 322.164062 124.773438 L 322.25 124.707031 L 322.421875 124.566406 L 322.59375 124.410156 L 322.679688 124.328125 L 322.765625 124.242188 L 322.9375 124.0625 L 323.023438 123.96875 L 323.195312 123.773438 L 323.28125 123.671875 L 323.453125 123.460938 L 323.539062 123.351562 L 323.796875 123.011719 L 323.882812 122.894531 L 324.054688 122.652344 L 324.3125 122.277344 L 324.484375 122.019531 L 324.742188 121.621094 L 324.828125 121.484375 L 324.828125 137.699219 L 324.742188 137.632812 L 324.65625 137.5625 L 324.570312 137.5 L 324.484375 137.433594 L 324.398438 137.371094 L 324.3125 137.3125 L 324.226562 137.25 L 324.140625 137.195312 L 324.054688 137.136719 L 323.96875 137.085938 L 323.882812 137.03125 L 323.796875 136.980469 L 323.625 136.886719 L 323.453125 136.800781 L 323.367188 136.761719 L 323.195312 136.691406 L 323.023438 136.628906 L 322.765625 136.558594 L 322.59375 136.527344 L 322.507812 136.515625 L 322.421875 136.507812 L 322.25 136.5 L 322.164062 136.5 L 321.992188 136.515625 L 321.90625 136.527344 L 321.820312 136.542969 L 321.734375 136.5625 L 321.5625 136.609375 L 321.476562 136.640625 L 321.390625 136.675781 L 321.308594 136.710938 L 321.136719 136.796875 L 320.964844 136.898438 L 320.878906 136.953125 L 320.792969 137.011719 L 320.707031 137.074219 L 320.621094 137.140625 L 320.449219 137.28125 L 320.277344 137.4375 L 320.191406 137.519531 L 320.105469 137.605469 L 319.933594 137.785156 L 319.847656 137.878906 L 319.675781 138.074219 L 319.589844 138.175781 L 319.417969 138.386719 L 319.332031 138.496094 L 319.074219 138.835938 L 318.988281 138.953125 L 318.816406 139.195312 L 318.558594 139.570312 L 318.386719 139.828125 L 318.214844 140.09375 L 318.128906 140.230469 L 318.042969 140.363281 Z M 318.042969 124.148438 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 132.257812 L 318.214844 132.1875 L 318.300781 132.15625 L 318.472656 132.085938 L 318.558594 132.054688 L 318.644531 132.019531 L 318.730469 131.988281 L 318.902344 131.917969 L 318.988281 131.886719 L 319.160156 131.816406 L 319.246094 131.785156 L 319.417969 131.714844 L 319.503906 131.683594 L 319.589844 131.648438 L 319.675781 131.617188 L 319.847656 131.546875 L 319.933594 131.515625 L 320.105469 131.445312 L 320.191406 131.414062 L 320.363281 131.34375 L 320.449219 131.3125 L 320.535156 131.277344 L 320.621094 131.246094 L 320.792969 131.175781 L 320.878906 131.144531 L 321.050781 131.074219 L 321.136719 131.042969 L 321.308594 130.972656 L 321.390625 130.941406 L 321.476562 130.90625 L 321.5625 130.875 L 321.734375 130.804688 L 321.820312 130.773438 L 321.992188 130.703125 L 322.078125 130.671875 L 322.25 130.601562 L 322.335938 130.570312 L 322.421875 130.535156 L 322.507812 130.503906 L 322.679688 130.433594 L 322.765625 130.402344 L 322.9375 130.332031 L 323.023438 130.300781 L 323.195312 130.230469 L 323.28125 130.199219 L 323.367188 130.164062 L 323.453125 130.132812 L 323.625 130.0625 L 323.710938 130.03125 L 323.882812 129.960938 L 323.96875 129.929688 L 324.140625 129.859375 L 324.226562 129.828125 L 324.3125 129.792969 L 324.398438 129.761719 L 324.570312 129.691406 L 324.65625 129.660156 L 324.828125 129.589844 "/>
-<g clip-path="url(#clip61)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 469.847656 L 428.601562 469.847656 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 469.847656 "/>
-</g>
-<g clip-path="url(#clip62)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 439.132812 L 428.601562 439.132812 "/>
-</g>
-<g clip-path="url(#clip63)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 385.835938 L 428.601562 385.835938 "/>
-</g>
-<g clip-path="url(#clip64)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 332.535156 L 428.601562 332.535156 "/>
-</g>
-<g clip-path="url(#clip65)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 279.238281 L 428.601562 279.238281 "/>
-</g>
-<g clip-path="url(#clip66)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 469.847656 L 267.171875 258.171875 "/>
-</g>
-<g clip-path="url(#clip67)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 469.847656 L 301.085938 258.171875 "/>
-</g>
-<g clip-path="url(#clip68)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 469.847656 L 335 258.171875 "/>
-</g>
-<g clip-path="url(#clip69)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 469.847656 L 368.914062 258.171875 "/>
-</g>
-<g clip-path="url(#clip70)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 469.847656 L 402.828125 258.171875 "/>
-</g>
-<g clip-path="url(#clip71)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 465.785156 L 428.601562 465.785156 "/>
-</g>
-<g clip-path="url(#clip72)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 412.484375 L 428.601562 412.484375 "/>
-</g>
-<g clip-path="url(#clip73)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 359.1875 L 428.601562 359.1875 "/>
-</g>
-<g clip-path="url(#clip74)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 305.886719 L 428.601562 305.886719 "/>
-</g>
-<g clip-path="url(#clip75)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 469.847656 L 250.214844 258.171875 "/>
-</g>
-<g clip-path="url(#clip76)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 469.847656 L 284.128906 258.171875 "/>
-</g>
-<g clip-path="url(#clip77)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 469.847656 L 318.042969 258.171875 "/>
-</g>
-<g clip-path="url(#clip78)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 469.847656 L 351.957031 258.171875 "/>
-</g>
-<g clip-path="url(#clip79)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 469.847656 L 385.871094 258.171875 "/>
-</g>
-<g clip-path="url(#clip80)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 469.847656 L 419.785156 258.171875 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 396.496094 C 292.867188 399.101562 288.957031 399.101562 288.957031 396.496094 C 288.957031 393.890625 292.867188 393.890625 292.867188 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 428.472656 C 265.738281 431.082031 261.828125 431.082031 261.828125 428.472656 C 261.828125 425.867188 265.738281 425.867188 265.738281 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 385.835938 C 286.085938 388.441406 282.175781 388.441406 282.175781 385.835938 C 282.175781 383.230469 286.085938 383.230469 286.085938 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 391.164062 C 286.085938 393.773438 282.175781 393.773438 282.175781 391.164062 C 282.175781 388.558594 286.085938 388.558594 286.085938 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 407.15625 C 286.085938 409.761719 282.175781 409.761719 282.175781 407.15625 C 282.175781 404.546875 286.085938 404.546875 286.085938 407.15625 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 385.835938 C 292.867188 388.441406 288.957031 388.441406 288.957031 385.835938 C 288.957031 383.230469 292.867188 383.230469 292.867188 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 243.433594 452.394531 L 244.035156 451.695312 L 245.238281 450.304688 L 245.839844 449.605469 L 246.4375 448.90625 L 248.84375 446.109375 L 249.445312 445.40625 L 250.046875 444.707031 L 250.644531 444.003906 L 251.246094 443.300781 L 251.847656 442.59375 L 252.449219 441.890625 L 253.652344 440.476562 L 254.253906 439.765625 L 254.851562 439.058594 L 255.453125 438.347656 L 257.257812 436.203125 L 257.859375 435.484375 L 258.460938 434.761719 L 259.058594 434.039062 L 259.660156 433.316406 L 260.261719 432.589844 L 260.863281 431.859375 L 262.066406 430.390625 L 262.667969 429.652344 L 263.265625 428.910156 L 263.867188 428.164062 L 264.46875 427.414062 L 265.070312 426.660156 L 265.671875 425.902344 L 266.273438 425.140625 L 266.875 424.375 L 267.472656 423.601562 L 268.074219 422.828125 L 268.675781 422.050781 L 269.878906 420.480469 L 271.082031 418.894531 L 271.679688 418.09375 L 272.882812 416.484375 L 273.484375 415.675781 L 274.085938 414.863281 L 274.6875 414.046875 L 275.285156 413.226562 L 275.886719 412.40625 L 277.089844 410.757812 L 277.691406 409.929688 L 278.894531 408.265625 L 279.492188 407.433594 L 281.296875 404.925781 L 282.5 403.246094 L 283.101562 402.402344 L 283.699219 401.5625 L 284.902344 399.875 L 285.503906 399.027344 L 286.105469 398.183594 L 287.308594 396.488281 L 287.90625 395.640625 L 288.507812 394.792969 L 289.109375 393.941406 L 289.710938 393.09375 L 290.3125 392.242188 L 290.914062 391.394531 L 290.914062 398.976562 L 290.3125 399.675781 L 289.710938 400.371094 L 287.90625 402.46875 L 287.308594 403.167969 L 286.707031 403.867188 L 286.105469 404.570312 L 285.503906 405.269531 L 283.699219 407.378906 L 283.101562 408.085938 L 281.296875 410.207031 L 279.492188 412.339844 L 278.894531 413.054688 L 278.292969 413.769531 L 276.488281 415.925781 L 275.285156 417.378906 L 274.6875 418.105469 L 273.484375 419.574219 L 272.28125 421.050781 L 271.679688 421.796875 L 271.082031 422.546875 L 270.480469 423.296875 L 269.277344 424.8125 L 268.675781 425.578125 L 268.074219 426.347656 L 267.472656 427.121094 L 266.875 427.898438 L 266.273438 428.679688 L 265.671875 429.464844 L 265.070312 430.253906 L 264.46875 431.046875 L 263.867188 431.84375 L 263.265625 432.644531 L 262.667969 433.453125 L 262.066406 434.257812 L 261.464844 435.070312 L 260.261719 436.703125 L 259.660156 437.523438 L 259.058594 438.347656 L 258.460938 439.171875 L 257.257812 440.828125 L 255.453125 443.324219 L 254.851562 444.160156 L 254.253906 445 L 251.847656 448.359375 L 250.644531 450.046875 L 250.046875 450.894531 L 249.445312 451.738281 L 248.84375 452.585938 L 248.242188 453.429688 L 247.640625 454.277344 L 247.039062 455.128906 L 246.4375 455.976562 L 245.839844 456.824219 L 244.636719 458.527344 L 244.035156 459.375 L 243.433594 460.226562 Z M 243.433594 452.394531 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 243.433594 456.308594 L 245.839844 453.214844 L 246.4375 452.441406 L 250.046875 447.800781 L 250.644531 447.027344 L 251.246094 446.25 L 254.253906 442.382812 L 254.851562 441.609375 L 258.460938 436.96875 L 259.058594 436.195312 L 259.660156 435.417969 L 262.667969 431.550781 L 263.265625 430.777344 L 266.875 426.136719 L 267.472656 425.359375 L 271.082031 420.71875 L 271.679688 419.945312 L 274.6875 416.078125 L 275.285156 415.304688 L 275.886719 414.527344 L 278.894531 410.660156 L 279.492188 409.886719 L 283.101562 405.246094 L 283.699219 404.46875 L 287.308594 399.828125 L 287.90625 399.054688 L 290.914062 395.1875 "/>
-<g clip-path="url(#clip81)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 240.40625 L 35.152344 240.40625 Z M 35.152344 258.171875 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-1" x="129.644531" y="252.204102"/>
-</g>
-<g clip-path="url(#clip82)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 240.40625 L 234.617188 240.40625 Z M 234.617188 258.171875 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-2" x="329.109375" y="252.204102"/>
-</g>
-<g clip-path="url(#clip83)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 5.480469 L 35.152344 5.480469 Z M 35.152344 23.246094 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="129.644531" y="17.27832"/>
-</g>
-<g clip-path="url(#clip84)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 5.480469 L 234.617188 5.480469 Z M 234.617188 23.246094 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-4" x="329.109375" y="17.27832"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 472.589844 L 50.75 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 472.589844 L 84.664062 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 472.589844 L 118.578125 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 472.589844 L 152.492188 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 472.589844 L 186.40625 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 472.589844 L 220.320312 469.847656 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="45.75" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="50.75" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="79.664062" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="84.664062" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="113.578125" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="118.578125" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="147.492188" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="152.492188" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="181.40625" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="186.40625" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="215.320312" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="220.320312" y="481.196289"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 472.589844 L 250.214844 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 472.589844 L 284.128906 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 472.589844 L 318.042969 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 472.589844 L 351.957031 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 472.589844 L 385.871094 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 472.589844 L 419.785156 469.847656 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="245.214844" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="250.214844" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="279.128906" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="284.128906" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="313.042969" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="318.042969" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="346.957031" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="351.957031" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="380.871094" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="385.871094" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="414.785156" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="419.785156" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="20.21875" y="233.774414"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="233.774414"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="20.21875" y="180.473633"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="180.473633"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="20.21875" y="127.176758"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="127.176758"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="20.21875" y="73.875977"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="73.875977"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 230.859375 L 35.152344 230.859375 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 177.558594 L 35.152344 177.558594 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 124.261719 L 35.152344 124.261719 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 70.960938 L 35.152344 70.960938 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="20.21875" y="468.700195"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="468.700195"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="20.21875" y="415.399414"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="415.399414"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="20.21875" y="362.102539"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="362.102539"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="20.21875" y="308.801758"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="308.801758"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 465.785156 L 35.152344 465.785156 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 412.484375 L 35.152344 412.484375 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 359.1875 L 35.152344 359.1875 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 305.886719 L 35.152344 305.886719 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph1-1" x="224.875" y="494.538086"/>
-  <use xlink:href="#glyph1-2" x="230.875" y="494.538086"/>
-  <use xlink:href="#glyph1-3" x="233.875" y="494.538086"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph2-1" x="13.499023" y="256.046875"/>
-  <use xlink:href="#glyph2-2" x="13.499023" y="250.046875"/>
-  <use xlink:href="#glyph2-3" x="13.499023" y="242.046875"/>
-</g>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;" d="M 439.5625 295.328125 L 498.519531 295.328125 L 498.519531 197.769531 L 439.5625 197.769531 Z M 439.5625 295.328125 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph1-4" x="445.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-5" x="448.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-1" x="454.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-2" x="460.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-6" x="463.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-7" x="469.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-8" x="473.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-1" x="477.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-3" x="482.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-9" x="487.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-10" x="489.042969" y="212.768555"/>
-</g>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 229.367188 C 455.636719 231.972656 451.726562 231.972656 451.726562 229.367188 C 451.726562 226.761719 455.636719 226.761719 455.636719 229.367188 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 229.367188 L 460.59375 229.367188 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 246.648438 C 455.636719 249.253906 451.726562 249.253906 451.726562 246.648438 C 451.726562 244.042969 455.636719 244.042969 455.636719 246.648438 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 246.648438 L 460.59375 246.648438 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 263.925781 C 455.636719 266.535156 451.726562 266.535156 451.726562 263.925781 C 451.726562 261.320312 455.636719 261.320312 455.636719 263.925781 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 263.925781 L 460.59375 263.925781 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 281.207031 C 455.636719 283.8125 451.726562 283.8125 451.726562 281.207031 C 451.726562 278.601562 455.636719 278.601562 455.636719 281.207031 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 281.207031 L 460.59375 281.207031 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="467.800781" y="232.282227"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-4" x="467.800781" y="249.563477"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-1" x="467.800781" y="266.84082"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-2" x="467.800781" y="284.12207"/>
-</g>
-</g>
-</svg>
-
-```
-
-We may also [generate](https://scicloj.github.io/clojisr/doc/clojisr/v1/codegen-test/) the R code from a Clojure form and pass Clojure data to R, but for now, we are simply using R code using an R dataset.
-
-We are using the `mpg` dataset, which is part of the `ggplot` package.
-
-::: {.sourceClojure}
-```clojure
-(-> "mpg"
-    r
-    r->clj)
-```
-:::
-
-_unnamed [234 11]:
-
-| :manufacturer |     :model | :displ | :year | :cyl |     :trans | :drv | :cty | :hwy | :fl |     :class |
-|---------------|------------|-------:|------:|-----:|------------|------|-----:|-----:|-----|------------|
-|          audi |         a4 |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    compact |
-|          audi |         a4 |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    compact |
-|          audi |         a4 |    2.0 |  2008 |    4 | manual(m6) |    f |   20 |   31 |   p |    compact |
-|          audi |         a4 |    2.0 |  2008 |    4 |   auto(av) |    f |   21 |   30 |   p |    compact |
-|          audi |         a4 |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    compact |
-|          audi |         a4 |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    compact |
-|          audi |         a4 |    3.1 |  2008 |    6 |   auto(av) |    f |   18 |   27 |   p |    compact |
-|          audi | a4 quattro |    1.8 |  1999 |    4 | manual(m5) |    4 |   18 |   26 |   p |    compact |
-|          audi | a4 quattro |    1.8 |  1999 |    4 |   auto(l5) |    4 |   16 |   25 |   p |    compact |
-|          audi | a4 quattro |    2.0 |  2008 |    4 | manual(m6) |    4 |   20 |   28 |   p |    compact |
-|           ... |        ... |    ... |   ... |  ... |        ... |  ... |  ... |  ... | ... |        ... |
-|    volkswagen | new beetle |    2.0 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   r | subcompact |
-|    volkswagen | new beetle |    2.0 |  1999 |    4 |   auto(l4) |    f |   19 |   26 |   r | subcompact |
-|    volkswagen | new beetle |    2.5 |  2008 |    5 | manual(m5) |    f |   20 |   28 |   r | subcompact |
-|    volkswagen | new beetle |    2.5 |  2008 |    5 |   auto(s6) |    f |   20 |   29 |   r | subcompact |
-|    volkswagen |     passat |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    midsize |
-|    volkswagen |     passat |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    midsize |
-|    volkswagen |     passat |    2.0 |  2008 |    4 |   auto(s6) |    f |   19 |   28 |   p |    midsize |
-|    volkswagen |     passat |    2.0 |  2008 |    4 | manual(m6) |    f |   21 |   29 |   p |    midsize |
-|    volkswagen |     passat |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    midsize |
-|    volkswagen |     passat |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    midsize |
-|    volkswagen |     passat |    3.6 |  2008 |    6 |   auto(s6) |    f |   17 |   26 |   p |    midsize |
-
-## Representing plots as Clojure data
-
-A ggplot object is an R list of [ggproto](https://bookdown.dongzhuoer.com/hadley/ggplot2-book/introducing-ggproto) objects. We recursively unwrap this structure and convert it to Clojure.
-
-::: {.sourceClojure}
-```clojure
-(defn ggplot->clj
-  ([r-obj]
-   (ggplot->clj r-obj {} []))
-  ([r-obj
-    {:as options
-     :keys [avoid]
-     :or {avoid #{"plot_env"}}}
-    path]
-   #_(prn path)
-   (let [relevant-names (some->> r-obj
-                                 r.base/names
-                                 r->clj
-                                 (filter (complement avoid)))]
-     (cond
-       ;;
-       ;; a named list or a ggproto object
-       (seq relevant-names) (->> relevant-names
-                                 (map (fn [nam]
-                                        [(keyword nam) (-> r-obj
-                                                           (r$ nam)
-                                                           (ggplot->clj options
-                                                                        (conj path nam)))]))
-                                 (into {}))
-       ;;
-       ;; a ggproto method
-       (-> r-obj
-           r.base/class
-           r->clj
-           first
-           (= "ggproto_method"))
-       :ggproto-method
-       ;;
-       ;; an unnamed list
-       (-> r-obj
-           r.base/is-list
-           r->clj
-           first)
-       (-> r-obj
-           r.base/length
-           r->clj
-           first
-           range
-           (->> (mapv (fn [i]
-                        (-> r-obj
-                            (r/brabra (inc i))
-                            (ggplot->clj options
-                                         (conj path [i])))))))
-       ;;
-       (r.base/is-atomic r-obj) (try (r->clj r-obj)
-                                     (catch Exception e
-                                       (-> r-obj println with-out-str)))
-       :else r-obj))))
-```
-:::
-
-In the conversion, we avoid some big parts of the structure, e.g., the `"plot_env"` member. We also do no report the toplevel `"data"` member, which is simply the dataset.
-
-For example:
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy))
-         + geom_point())"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
+            [clojure.string :as str]
+            [representing]))
 ```
@@
 
-Let us explore and compare a few plots this way:
+Let us explore and compare a few plots through their Clojure representations:
 
@@
          clj (-> plot
-                 ggplot->clj
+                 representing/ggplot->clj
                  (dissoc :data))]
@@
 ```{=html}
-<img src="repesenting_files/0.png" style="width:100%;" />
+<img src="comparing_files/0.png" style="width:100%;" />
 ```
@@
 ```{=html}
-<img src="repesenting_files/1.png" style="width:100%;" />
+<img src="comparing_files/1.png" style="width:100%;" />
 ```
@@
 ```{=html}
-<img src="repesenting_files/2.png" style="width:100%;" />
+<img src="comparing_files/2.png" style="width:100%;" />
 ```
@@
 ```{=html}
-<img src="repesenting_files/3.png" style="width:100%;" />
+<img src="comparing_files/3.png" style="width:100%;" />
 ```
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55b95a21db80&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x558a1755b0f0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55b95a21db80&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
-
-```
-:::
-
-## Exploring
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy)))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers [],
- :scales {:super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy)))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers [],
- :scales {:super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy)))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers [],
- :scales {:super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
-      + geom_point(mapping=aes(color=cyl), size=5)
-      + ylim(c(20,30)))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params {:size [5.0]},
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping {:colour [~ cyl]},
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales
- {:scales
-  [{:labels [],
-    :scale_name ["position_c"],
-    :breaks [],
-    :call
-    {:labels labels,
-     :scale_name ["position_c"],
-     :breaks breaks,
-     :name name,
-     :palette identity,
-     :super ScaleContinuousPosition,
-     :guide guide,
-     :minor_breaks minor_breaks,
-     :n.breaks n.breaks,
-     : nil,
-     :aesthetics [$ ggplot_global y_aes],
-     :na.value na.value,
-     :trans trans,
-     :oob oob,
-     :position position,
-     :limits limits,
-     :expand expand},
-    :rescaler :ggproto-method,
-    :name [],
-    :palette :ggproto-method,
-    :super :ggproto-method,
-    :guide [],
-    :minor_breaks [],
-    :n.breaks nil,
-    :aesthetics
-    ["y"
-     "ymin"
-     "ymax"
-     "yend"
-     "yintercept"
-     "ymin_final"
-     "ymax_final"
-     "lower"
-     "middle"
-     "upper"
-     "y0"],
-    :na.value [nil],
-    :trans
-    {:name ["identity"],
-     :transform
-     "function (x) \nx\n&lt;bytecode: 0x55b9566f0140&gt;\n&lt;environment: namespace:base&gt;\n",
-     :inverse
-     "function (x) \nx\n&lt;bytecode: 0x55b9566f0140&gt;\n&lt;environment: namespace:base&gt;\n",
-     :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55b95a64c498&gt;\n&lt;environment: 0x55b9649d1458&gt;\n",
-     :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55b95a64fe78&gt;\n&lt;environment: 0x55b9649d12d0&gt;\n",
-     :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55b95a6591f0&gt;\n&lt;environment: 0x55b9649d1180&gt;\n",
-     :domain [##-Inf ##Inf]},
-    :oob :ggproto-method,
-    :position ["left"],
-    :limits [20.0 30.0],
-    :expand [],
-    :range {:super :ggproto-method}}],
-  :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
-      + geom_point(mapping=aes(color=factor(cyl)), size=20))"
-    r
-    plotting/plot->buffered-image)
-```
-:::
-
-```{=html}
-<img src="repesenting_files/4.png" style="width:100%;" />
-```
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
-      + geom_point(mapping=aes(color=cyl), size=5)
-      + ylim(c(20,30))
-      + scale_x_log10())"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params {:size [5.0]},
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping {:colour [~ cyl]},
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales
- {:scales
-  [{:range {:super :ggproto-method}, :super :ggproto-method}
-   {:labels [],
-    :scale_name ["position_c"],
-    :breaks [],
-    :call
-    {:labels labels,
-     :scale_name ["position_c"],
-     :breaks breaks,
-     :name name,
-     :palette identity,
-     :super ScaleContinuousPosition,
-     :guide guide,
-     :minor_breaks minor_breaks,
-     :n.breaks n.breaks,
-     : nil,
-     :aesthetics [$ ggplot_global x_aes],
-     :na.value na.value,
-     :trans trans,
-     :oob oob,
-     :position position,
-     :limits limits,
-     :expand expand},
-    :rescaler :ggproto-method,
-    :name [],
-    :palette :ggproto-method,
-    :super :ggproto-method,
-    :guide [],
-    :minor_breaks [],
-    :n.breaks nil,
-    :aesthetics
-    ["x"
-     "xmin"
-     "xmax"
-     "xend"
-     "xintercept"
-     "xmin_final"
-     "xmax_final"
-     "xlower"
-     "xmiddle"
-     "xupper"
-     "x0"],
-    :na.value [nil],
-    :trans
-    {:name ["log-10"],
-     :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55b95f192f70&gt;\n&lt;environment: 0x55b95f193750&gt;\n",
-     :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x55b95f193130&gt;\n&lt;environment: 0x55b95f193750&gt;\n",
-     :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55b95f18b830&gt;\n&lt;environment: 0x55b95f18ae80&gt;\n",
-     :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55b95a64fe78&gt;\n&lt;environment: 0x55b95f186e88&gt;\n",
-     :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55b95a6591f0&gt;\n&lt;environment: 0x55b95f186fd8&gt;\n",
-     :domain [1.0E-100 ##Inf]},
-    :oob :ggproto-method,
-    :position ["bottom"],
-    :limits nil,
-    :expand [],
-    :range {:super :ggproto-method}}],
-  :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
-      + geom_point(mapping=aes(color=cyl), size=5)
-      + ylim(c(20,30))
-      + scale_x_log10()
-      + theme_linedraw())"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params {:size [5.0]},
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping {:colour [~ cyl]},
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales
- {:scales
-  [{:range {:super :ggproto-method}, :super :ggproto-method}
-   {:range {:super :ggproto-method}, :super :ggproto-method}],
-  :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme
- {:axis.ticks
-  {:colour ["black"],
-   :linewidth [0.5],
-   :linetype nil,
-   :lineend nil,
-   :arrow [false],
-   :inherit.blank [true]},
-  :legend.justification ["center"],
-  :panel.grid.minor
-  {:colour nil,
-   :linewidth [0.05],
-   :linetype nil,
-   :lineend nil,
-   :arrow [false],
-   :inherit.blank [true]},
-  :strip.text.x.bottom nil,
-  :legend.key.width nil,
-  :panel.spacing.x nil,
-  :axis.text.y
-  {:hjust [1.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin [0.0 2.2 0.0 0.0]},
-  :panel.ontop [false],
-  :axis.ticks.x.top nil,
-  :panel.border
-  {:fill [nil],
-   :colour ["black"],
-   :linewidth [1.0],
-   :linetype nil,
-   :inherit.blank [true]},
-  :legend.key.height nil,
-  :plot.caption
-  {:hjust [1.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [0.8],
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [5.5 0.0 0.0 0.0]},
-  :panel.grid.major.y nil,
-  :panel.grid
-  {:colour ["black"],
-   :linewidth nil,
-   :linetype nil,
-   :lineend nil,
-   :arrow [false],
-   :inherit.blank [true]},
-  :axis.ticks.x.bottom nil,
-  :panel.grid.major.x nil,
-  :plot.tag
-  {:hjust [0.5],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [1.2],
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [0.5],
-   :margin nil},
-  :axis.text
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [0.8],
-   :face nil,
-   :lineheight nil,
-   :colour ["black"],
-   :vjust nil,
-   :margin nil},
-  :axis.line.x nil,
-  :panel.spacing.y nil,
-  :legend.spacing.x nil,
-  :axis.text.x
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [2.2 0.0 0.0 0.0]},
-  :axis.line.y.left nil,
-  :plot.caption.position ["panel"],
-  :plot.subtitle
-  {:hjust [0.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [0.0 0.0 5.5 0.0]},
-  :axis.ticks.y.right nil,
-  :legend.box nil,
-  :strip.text.y
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle [-90.0],
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin nil},
-  :panel.spacing [5.5],
-  :legend.background
-  {:fill nil,
-   :colour [nil],
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :strip.switch.pad.grid [2.75],
-  :axis.ticks.length.y.left nil,
-  :legend.direction nil,
-  :strip.text
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [0.8],
-   :face nil,
-   :lineheight nil,
-   :colour ["white"],
-   :vjust nil,
-   :margin [4.4 4.4 4.4 4.4]},
-  :axis.line.x.bottom nil,
-  :axis.ticks.length.x.bottom nil,
-  :axis.text.y.left nil,
-  :axis.ticks.length.x nil,
-  :plot.margin [5.5 5.5 5.5 5.5],
-  :axis.ticks.length [2.75],
-  :plot.title
-  {:hjust [0.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [1.2],
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [0.0 0.0 5.5 0.0]},
-  :axis.ticks.y nil,
-  :legend.text.align nil,
-  :legend.text
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [0.8],
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin nil},
-  :legend.key
-  {:fill ["white"],
-   :colour [nil],
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :axis.line.y nil,
-  :axis.title.y.left nil,
-  :axis.ticks.length.x.top nil,
-  :legend.box.margin [0.0 0.0 0.0 0.0],
-  :axis.title.y.right
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle [-90.0],
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [0.0],
-   :margin [0.0 0.0 0.0 2.75]},
-  :title nil,
-  :strip.clip ["inherit"],
-  :strip.background.x nil,
-  :strip.text.x nil,
-  :strip.placement ["inside"],
-  :axis.ticks.x nil,
-  :axis.line.y.right nil,
-  :axis.title.x.bottom nil,
-  :legend.key.size [1.2],
-  :axis.text.x.top
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [0.0],
-   :margin [0.0 0.0 2.2 0.0]},
-  :panel.background
-  {:fill ["white"],
-   :colour [nil],
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :plot.tag.position ["topleft"],
-  :legend.margin [5.5 5.5 5.5 5.5],
-  :plot.title.position ["panel"],
-  :line
-  {:colour ["black"],
-   :linewidth [0.5],
-   :linetype [1.0],
-   :lineend ["butt"],
-   :arrow [false],
-   :inherit.blank [true]},
-  :strip.text.y.left
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle [90.0],
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin nil},
-  :strip.background
-  {:fill ["black"],
-   :colour nil,
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :axis.title.y
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle [90.0],
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [0.0 2.75 0.0 0.0]},
-  :legend.box.background [],
-  :panel.grid.major
-  {:colour nil,
-   :linewidth [0.1],
-   :linetype nil,
-   :lineend nil,
-   :arrow [false],
-   :inherit.blank [true]},
-  :axis.title nil,
-  :strip.text.y.right nil,
-  :legend.title.align nil,
-  :plot.background
-  {:fill nil,
-   :colour ["white"],
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :aspect.ratio nil,
-  :legend.spacing [11.0],
-  :axis.title.x
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [2.75 0.0 0.0 0.0]},
-  :axis.line.x.top nil,
-  :legend.position ["right"],
-  :axis.ticks.length.y nil,
-  :axis.ticks.y.left nil,
-  :axis.ticks.length.y.right nil,
-  :legend.box.just nil,
-  :legend.title
-  {:hjust [0.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin nil},
-  :axis.text.y.right
-  {:hjust [0.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin [0.0 0.0 0.0 2.2]},
-  :axis.text.x.bottom nil,
-  :strip.background.y nil,
-  :axis.line [],
-  :rect
-  {:fill ["white"],
-   :colour ["black"],
-   :linewidth [0.5],
-   :linetype [1.0],
-   :inherit.blank [true]},
-  :legend.box.spacing [11.0],
-  :panel.grid.minor.y nil,
-  :panel.grid.minor.x nil,
-  :strip.switch.pad.wrap [2.75],
-  :axis.title.x.top
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [0.0],
-   :margin [0.0 0.0 2.75 0.0]},
-  :strip.text.x.top nil,
-  :legend.spacing.y nil,
-  :text
-  {:hjust [0.5],
-   :family [""],
-   :inherit.blank [true],
-   :debug [false],
-   :angle [0.0],
-   :size [11.0],
-   :face ["plain"],
-   :lineheight [0.9],
-   :colour ["black"],
-   :vjust [0.5],
-   :margin [0.0 0.0 0.0 0.0]}},
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(data.frame(x = rnorm(1000, 2, 2)), aes(x)) +
-      geom_histogram(aes(y=..density..)) +  # scale histogram y
-      geom_density(col = 'red', size=5))"
-    r
-    plotting/plot->buffered-image)
-```
-:::
-
-```{=html}
-<img src="repesenting_files/5.png" style="width:100%;" />
-```
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(data.frame(x = rnorm(1000, 2, 2)), aes(x)) +
-      geom_histogram(aes(y=..density..)) +  # scale histogram y
-      geom_density(col = 'red'))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat
-   {:default_aes
-    {:x [~ [after_stat count]],
-     :y [~ [after_stat count]],
-     :weight [1.0]},
-    :extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x|y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping {:y [~ ..density..]},
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_data :ggproto-method,
-    :rename_size [true],
-    :non_missing_aes ["xmin" "xmax" "ymin" "ymax"],
-    :extra_params ["just" "na.rm" "orientation"],
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method,
-    :setup_params :ggproto-method},
-   :stat_params
-   {:binwidth nil,
-    :bins nil,
-    :na.rm [false],
-    :orientation [nil],
-    :pad [false]},
-   :constructor [geom_histogram {0 aes, :y ..density..}],
-   :position
-   {:setup_data :ggproto-method,
-    :type nil,
-    :compute_panel :ggproto-method,
-    :vjust [1.0],
-    :reverse [false],
-    :super :ggproto-method,
-    :fill [false],
-    :setup_params :ggproto-method},
-   :data []}
-  {:aes_params {:colour ["red"]},
-   :stat
-   {:default_aes
-    {:x [~ [after_stat density]],
-     :y [~ [after_stat density]],
-     :fill [nil],
-     :weight nil},
-    :extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x|y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params
-   {:na.rm [false], :orientation [nil], :outline.type ["upper"]},
-   :geom
-   {:default_aes
-    {:fill [nil],
-     :weight [1.0],
-     :colour ["black"],
-     :alpha [nil],
-     :linewidth [0.5],
-     :linetype [1.0]},
-    :super :ggproto-method},
-   :stat_params {:na.rm [false], :orientation [nil]},
-   :constructor {: nil, :col ["red"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ x]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["x"], :y ["density"], :fill ["fill"], :weight ["weight"]}}
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x558a1755b0f0&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 
@@
 ```{=html}
-<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/representing.clj">projects/datavis/ggplot/notebooks/representing.clj</a></small></small></pre></div>
-```
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/comparing.clj">projects/datavis/ggplot/notebooks/comparing.clj</a></small></small></pre></div>
+```

### 2024-02-24 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

--- 2024-02-24 docs/projects/datavis/ggplot/repesenting.qmd
@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: repesenting.html}
+  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: draft.html}
 code-block-background: true
@@
 </style>
-<script src="repesenting_files/md-default6.js" type="text/javascript"></script><script src="repesenting_files/md-default7.js" type="text/javascript"></script>
-
-```{=html}
-<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
-```
-
-# Representing ggplot plots as Clojure data
-
-## Setup
-
-We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.
+<script src="draft_files/md-default2.js" type="text/javascript"></script><script src="draft_files/md-default3.js" type="text/javascript"></script>
 
@@
 ```clojure
-(ns repesenting
+(ns draft
   (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
             [clojisr.v1.applications.plotting :as plotting]
-            [scicloj.kindly.v4.kind :as kind]
-            [clojure.walk :as walk]
-            [tablecloth.api :as tc]
-            [editscript.core :as editscript]
-            [clojure.pprint :as pp]
-            [clojure.string :as str]))
-```
-:::
-
-Loading ggplot2:
-
-::: {.sourceClojure}
-```clojure
-(r/library "ggplot2")
-```
-:::
-
-::: {.printedClojure}
-```clojure
-[1] "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices" "utils"    
-[7] "datasets"  "methods"   "base"
-
-```
-:::
-
-Requireing the base R library as a Clojure namespace:
-
-::: {.sourceClojure}
-```clojure
-(r/require-r '[base])
-```
-:::
-
-::: {.printedClojure}
-```clojure
-nil
-
-```
-:::
-
-## An example plot
-
-Here is how we may generate and display a plot:
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))"
-    r
-    plotting/plot->svg
-    kind/html)
-```
-:::
-
-```{=html}
-<?xml version="1.0" encoding="UTF-8"?>
-<svg xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink" width="504pt" height="504pt" viewBox="0 0 504 504" version="1.1">
-<defs>
-<g>
-<symbol overflow="visible" id="glyph0-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph0-1">
-<path style="stroke:none;" d="M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-2">
-<path style="stroke:none;" d="M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-3">
-<path style="stroke:none;" d="M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-4">
-<path style="stroke:none;" d="M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-5">
-<path style="stroke:none;" d="M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-6">
-<path style="stroke:none;" d="M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-7">
-<path style="stroke:none;" d="M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-8">
-<path style="stroke:none;" d="M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph1-1">
-<path style="stroke:none;" d="M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-2">
-<path style="stroke:none;" d="M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-3">
-<path style="stroke:none;" d="M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-4">
-<path style="stroke:none;" d="M 2.84375 -5.765625 L 1.875 -5.765625 L 1.875 -6.671875 C 1.875 -7.046875 2.09375 -7.25 2.515625 -7.25 C 2.59375 -7.25 2.625 -7.25 2.84375 -7.234375 L 2.84375 -8 C 2.625 -8.046875 2.515625 -8.046875 2.328125 -8.046875 C 1.46875 -8.046875 0.96875 -7.5625 0.96875 -6.75 L 0.96875 -5.765625 L 0.203125 -5.765625 L 0.203125 -5.015625 L 0.96875 -5.015625 L 0.96875 0 L 1.875 0 L 1.875 -5.015625 L 2.84375 -5.015625 Z M 2.84375 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-5">
-<path style="stroke:none;" d="M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-6">
-<path style="stroke:none;" d="M 2.984375 -5.921875 C 1.359375 -5.921875 0.390625 -4.78125 0.390625 -2.84375 C 0.390625 -0.890625 1.359375 0.25 3 0.25 C 4.625 0.25 5.609375 -0.90625 5.609375 -2.796875 C 5.609375 -4.796875 4.65625 -5.921875 2.984375 -5.921875 Z M 3 -5.078125 C 4.03125 -5.078125 4.65625 -4.234375 4.65625 -2.8125 C 4.65625 -1.4375 4.015625 -0.59375 3 -0.59375 C 1.984375 -0.59375 1.359375 -1.4375 1.359375 -2.84375 C 1.359375 -4.234375 1.984375 -5.078125 3 -5.078125 Z M 3 -5.078125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-7">
-<path style="stroke:none;" d="M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-8">
-<path style="stroke:none;" d="M 2.59375 -8.015625 C 1.5 -6.578125 0.796875 -4.578125 0.796875 -2.84375 C 0.796875 -1.109375 1.5 0.890625 2.59375 2.328125 L 3.203125 2.328125 C 2.234375 0.765625 1.6875 -1.09375 1.6875 -2.84375 C 1.6875 -4.59375 2.234375 -6.453125 3.203125 -8.015625 Z M 2.59375 -8.015625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-9">
-<path style="stroke:none;" d="M 1.671875 -8.015625 L 0.75 -8.015625 L 0.75 0 L 1.671875 0 Z M 1.671875 -8.015625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-10">
-<path style="stroke:none;" d="M 1.015625 2.328125 C 2.125 0.890625 2.8125 -1.109375 2.8125 -2.84375 C 2.8125 -4.578125 2.125 -6.578125 1.015625 -8.015625 L 0.421875 -8.015625 C 1.390625 -6.453125 1.921875 -4.59375 1.921875 -2.84375 C 1.921875 -1.09375 1.390625 0.765625 0.421875 2.328125 Z M 1.015625 2.328125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph2-1">
-<path style="stroke:none;" d="M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-2">
-<path style="stroke:none;" d="M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-3">
-<path style="stroke:none;" d="M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 "/>
-</symbol>
-</g>
-<clipPath id="clip1">
-  <path d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 234.925781 L 35.152344 234.925781 Z M 35.152344 23.246094 "/>
-</clipPath>
-<clipPath id="clip2">
-  <path d="M 35.152344 203 L 229.136719 203 L 229.136719 205 L 35.152344 205 Z M 35.152344 203 "/>
-</clipPath>
-<clipPath id="clip3">
-  <path d="M 35.152344 150 L 229.136719 150 L 229.136719 152 L 35.152344 152 Z M 35.152344 150 "/>
-</clipPath>
-<clipPath id="clip4">
-  <path d="M 35.152344 97 L 229.136719 97 L 229.136719 98 L 35.152344 98 Z M 35.152344 97 "/>
-</clipPath>
-<clipPath id="clip5">
-  <path d="M 35.152344 44 L 229.136719 44 L 229.136719 45 L 35.152344 45 Z M 35.152344 44 "/>
-</clipPath>
-<clipPath id="clip6">
-  <path d="M 67 23.246094 L 68 23.246094 L 68 234.925781 L 67 234.925781 Z M 67 23.246094 "/>
-</clipPath>
-<clipPath id="clip7">
-  <path d="M 101 23.246094 L 102 23.246094 L 102 234.925781 L 101 234.925781 Z M 101 23.246094 "/>
-</clipPath>
-<clipPath id="clip8">
-  <path d="M 135 23.246094 L 136 23.246094 L 136 234.925781 L 135 234.925781 Z M 135 23.246094 "/>
-</clipPath>
-<clipPath id="clip9">
-  <path d="M 169 23.246094 L 170 23.246094 L 170 234.925781 L 169 234.925781 Z M 169 23.246094 "/>
-</clipPath>
-<clipPath id="clip10">
-  <path d="M 203 23.246094 L 204 23.246094 L 204 234.925781 L 203 234.925781 Z M 203 23.246094 "/>
-</clipPath>
-<clipPath id="clip11">
-  <path d="M 35.152344 230 L 229.136719 230 L 229.136719 232 L 35.152344 232 Z M 35.152344 230 "/>
-</clipPath>
-<clipPath id="clip12">
-  <path d="M 35.152344 177 L 229.136719 177 L 229.136719 179 L 35.152344 179 Z M 35.152344 177 "/>
-</clipPath>
-<clipPath id="clip13">
-  <path d="M 35.152344 123 L 229.136719 123 L 229.136719 125 L 35.152344 125 Z M 35.152344 123 "/>
-</clipPath>
-<clipPath id="clip14">
-  <path d="M 35.152344 70 L 229.136719 70 L 229.136719 72 L 35.152344 72 Z M 35.152344 70 "/>
-</clipPath>
-<clipPath id="clip15">
-  <path d="M 50 23.246094 L 52 23.246094 L 52 234.925781 L 50 234.925781 Z M 50 23.246094 "/>
-</clipPath>
-<clipPath id="clip16">
-  <path d="M 84 23.246094 L 86 23.246094 L 86 234.925781 L 84 234.925781 Z M 84 23.246094 "/>
-</clipPath>
-<clipPath id="clip17">
-  <path d="M 118 23.246094 L 120 23.246094 L 120 234.925781 L 118 234.925781 Z M 118 23.246094 "/>
-</clipPath>
-<clipPath id="clip18">
-  <path d="M 151 23.246094 L 154 23.246094 L 154 234.925781 L 151 234.925781 Z M 151 23.246094 "/>
-</clipPath>
-<clipPath id="clip19">
-  <path d="M 185 23.246094 L 187 23.246094 L 187 234.925781 L 185 234.925781 Z M 185 23.246094 "/>
-</clipPath>
-<clipPath id="clip20">
-  <path d="M 219 23.246094 L 221 23.246094 L 221 234.925781 L 219 234.925781 Z M 219 23.246094 "/>
-</clipPath>
-<clipPath id="clip21">
-  <path d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 469.851562 L 35.152344 469.851562 Z M 35.152344 258.171875 "/>
-</clipPath>
-<clipPath id="clip22">
-  <path d="M 35.152344 438 L 229.136719 438 L 229.136719 440 L 35.152344 440 Z M 35.152344 438 "/>
-</clipPath>
-<clipPath id="clip23">
-  <path d="M 35.152344 385 L 229.136719 385 L 229.136719 387 L 35.152344 387 Z M 35.152344 385 "/>
-</clipPath>
-<clipPath id="clip24">
-  <path d="M 35.152344 332 L 229.136719 332 L 229.136719 333 L 35.152344 333 Z M 35.152344 332 "/>
-</clipPath>
-<clipPath id="clip25">
-  <path d="M 35.152344 278 L 229.136719 278 L 229.136719 280 L 35.152344 280 Z M 35.152344 278 "/>
-</clipPath>
-<clipPath id="clip26">
-  <path d="M 67 258.171875 L 68 258.171875 L 68 469.851562 L 67 469.851562 Z M 67 258.171875 "/>
-</clipPath>
-<clipPath id="clip27">
-  <path d="M 101 258.171875 L 102 258.171875 L 102 469.851562 L 101 469.851562 Z M 101 258.171875 "/>
-</clipPath>
-<clipPath id="clip28">
-  <path d="M 135 258.171875 L 136 258.171875 L 136 469.851562 L 135 469.851562 Z M 135 258.171875 "/>
-</clipPath>
-<clipPath id="clip29">
-  <path d="M 169 258.171875 L 170 258.171875 L 170 469.851562 L 169 469.851562 Z M 169 258.171875 "/>
-</clipPath>
-<clipPath id="clip30">
-  <path d="M 203 258.171875 L 204 258.171875 L 204 469.851562 L 203 469.851562 Z M 203 258.171875 "/>
-</clipPath>
-<clipPath id="clip31">
-  <path d="M 35.152344 465 L 229.136719 465 L 229.136719 467 L 35.152344 467 Z M 35.152344 465 "/>
-</clipPath>
-<clipPath id="clip32">
-  <path d="M 35.152344 411 L 229.136719 411 L 229.136719 414 L 35.152344 414 Z M 35.152344 411 "/>
-</clipPath>
-<clipPath id="clip33">
-  <path d="M 35.152344 358 L 229.136719 358 L 229.136719 360 L 35.152344 360 Z M 35.152344 358 "/>
-</clipPath>
-<clipPath id="clip34">
-  <path d="M 35.152344 305 L 229.136719 305 L 229.136719 307 L 35.152344 307 Z M 35.152344 305 "/>
-</clipPath>
-<clipPath id="clip35">
-  <path d="M 50 258.171875 L 52 258.171875 L 52 469.851562 L 50 469.851562 Z M 50 258.171875 "/>
-</clipPath>
-<clipPath id="clip36">
-  <path d="M 84 258.171875 L 86 258.171875 L 86 469.851562 L 84 469.851562 Z M 84 258.171875 "/>
-</clipPath>
-<clipPath id="clip37">
-  <path d="M 118 258.171875 L 120 258.171875 L 120 469.851562 L 118 469.851562 Z M 118 258.171875 "/>
-</clipPath>
-<clipPath id="clip38">
-  <path d="M 151 258.171875 L 154 258.171875 L 154 469.851562 L 151 469.851562 Z M 151 258.171875 "/>
-</clipPath>
-<clipPath id="clip39">
-  <path d="M 185 258.171875 L 187 258.171875 L 187 469.851562 L 185 469.851562 Z M 185 258.171875 "/>
-</clipPath>
-<clipPath id="clip40">
-  <path d="M 219 258.171875 L 221 258.171875 L 221 469.851562 L 219 469.851562 Z M 219 258.171875 "/>
-</clipPath>
-<clipPath id="clip41">
-  <path d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 234.925781 L 234.617188 234.925781 Z M 234.617188 23.246094 "/>
-</clipPath>
-<clipPath id="clip42">
-  <path d="M 234.617188 203 L 428.601562 203 L 428.601562 205 L 234.617188 205 Z M 234.617188 203 "/>
-</clipPath>
-<clipPath id="clip43">
-  <path d="M 234.617188 150 L 428.601562 150 L 428.601562 152 L 234.617188 152 Z M 234.617188 150 "/>
-</clipPath>
-<clipPath id="clip44">
-  <path d="M 234.617188 97 L 428.601562 97 L 428.601562 98 L 234.617188 98 Z M 234.617188 97 "/>
-</clipPath>
-<clipPath id="clip45">
-  <path d="M 234.617188 44 L 428.601562 44 L 428.601562 45 L 234.617188 45 Z M 234.617188 44 "/>
-</clipPath>
-<clipPath id="clip46">
-  <path d="M 266 23.246094 L 268 23.246094 L 268 234.925781 L 266 234.925781 Z M 266 23.246094 "/>
-</clipPath>
-<clipPath id="clip47">
-  <path d="M 300 23.246094 L 302 23.246094 L 302 234.925781 L 300 234.925781 Z M 300 23.246094 "/>
-</clipPath>
-<clipPath id="clip48">
-  <path d="M 334 23.246094 L 336 23.246094 L 336 234.925781 L 334 234.925781 Z M 334 23.246094 "/>
-</clipPath>
-<clipPath id="clip49">
-  <path d="M 368 23.246094 L 370 23.246094 L 370 234.925781 L 368 234.925781 Z M 368 23.246094 "/>
-</clipPath>
-<clipPath id="clip50">
-  <path d="M 402 23.246094 L 404 23.246094 L 404 234.925781 L 402 234.925781 Z M 402 23.246094 "/>
-</clipPath>
-<clipPath id="clip51">
-  <path d="M 234.617188 230 L 428.601562 230 L 428.601562 232 L 234.617188 232 Z M 234.617188 230 "/>
-</clipPath>
-<clipPath id="clip52">
-  <path d="M 234.617188 177 L 428.601562 177 L 428.601562 179 L 234.617188 179 Z M 234.617188 177 "/>
-</clipPath>
-<clipPath id="clip53">
-  <path d="M 234.617188 123 L 428.601562 123 L 428.601562 125 L 234.617188 125 Z M 234.617188 123 "/>
-</clipPath>
-<clipPath id="clip54">
-  <path d="M 234.617188 70 L 428.601562 70 L 428.601562 72 L 234.617188 72 Z M 234.617188 70 "/>
-</clipPath>
-<clipPath id="clip55">
-  <path d="M 249 23.246094 L 251 23.246094 L 251 234.925781 L 249 234.925781 Z M 249 23.246094 "/>
-</clipPath>
-<clipPath id="clip56">
-  <path d="M 283 23.246094 L 285 23.246094 L 285 234.925781 L 283 234.925781 Z M 283 23.246094 "/>
-</clipPath>
-<clipPath id="clip57">
-  <path d="M 317 23.246094 L 319 23.246094 L 319 234.925781 L 317 234.925781 Z M 317 23.246094 "/>
-</clipPath>
-<clipPath id="clip58">
-  <path d="M 351 23.246094 L 353 23.246094 L 353 234.925781 L 351 234.925781 Z M 351 23.246094 "/>
-</clipPath>
-<clipPath id="clip59">
-  <path d="M 385 23.246094 L 387 23.246094 L 387 234.925781 L 385 234.925781 Z M 385 23.246094 "/>
-</clipPath>
-<clipPath id="clip60">
-  <path d="M 419 23.246094 L 421 23.246094 L 421 234.925781 L 419 234.925781 Z M 419 23.246094 "/>
-</clipPath>
-<clipPath id="clip61">
-  <path d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 469.851562 L 234.617188 469.851562 Z M 234.617188 258.171875 "/>
-</clipPath>
-<clipPath id="clip62">
-  <path d="M 234.617188 438 L 428.601562 438 L 428.601562 440 L 234.617188 440 Z M 234.617188 438 "/>
-</clipPath>
-<clipPath id="clip63">
-  <path d="M 234.617188 385 L 428.601562 385 L 428.601562 387 L 234.617188 387 Z M 234.617188 385 "/>
-</clipPath>
-<clipPath id="clip64">
-  <path d="M 234.617188 332 L 428.601562 332 L 428.601562 333 L 234.617188 333 Z M 234.617188 332 "/>
-</clipPath>
-<clipPath id="clip65">
-  <path d="M 234.617188 278 L 428.601562 278 L 428.601562 280 L 234.617188 280 Z M 234.617188 278 "/>
-</clipPath>
-<clipPath id="clip66">
-  <path d="M 266 258.171875 L 268 258.171875 L 268 469.851562 L 266 469.851562 Z M 266 258.171875 "/>
-</clipPath>
-<clipPath id="clip67">
-  <path d="M 300 258.171875 L 302 258.171875 L 302 469.851562 L 300 469.851562 Z M 300 258.171875 "/>
-</clipPath>
-<clipPath id="clip68">
-  <path d="M 334 258.171875 L 336 258.171875 L 336 469.851562 L 334 469.851562 Z M 334 258.171875 "/>
-</clipPath>
-<clipPath id="clip69">
-  <path d="M 368 258.171875 L 370 258.171875 L 370 469.851562 L 368 469.851562 Z M 368 258.171875 "/>
-</clipPath>
-<clipPath id="clip70">
-  <path d="M 402 258.171875 L 404 258.171875 L 404 469.851562 L 402 469.851562 Z M 402 258.171875 "/>
-</clipPath>
-<clipPath id="clip71">
-  <path d="M 234.617188 465 L 428.601562 465 L 428.601562 467 L 234.617188 467 Z M 234.617188 465 "/>
-</clipPath>
-<clipPath id="clip72">
-  <path d="M 234.617188 411 L 428.601562 411 L 428.601562 414 L 234.617188 414 Z M 234.617188 411 "/>
-</clipPath>
-<clipPath id="clip73">
-  <path d="M 234.617188 358 L 428.601562 358 L 428.601562 360 L 234.617188 360 Z M 234.617188 358 "/>
-</clipPath>
-<clipPath id="clip74">
-  <path d="M 234.617188 305 L 428.601562 305 L 428.601562 307 L 234.617188 307 Z M 234.617188 305 "/>
-</clipPath>
-<clipPath id="clip75">
-  <path d="M 249 258.171875 L 251 258.171875 L 251 469.851562 L 249 469.851562 Z M 249 258.171875 "/>
-</clipPath>
-<clipPath id="clip76">
-  <path d="M 283 258.171875 L 285 258.171875 L 285 469.851562 L 283 469.851562 Z M 283 258.171875 "/>
-</clipPath>
-<clipPath id="clip77">
-  <path d="M 317 258.171875 L 319 258.171875 L 319 469.851562 L 317 469.851562 Z M 317 258.171875 "/>
-</clipPath>
-<clipPath id="clip78">
-  <path d="M 351 258.171875 L 353 258.171875 L 353 469.851562 L 351 469.851562 Z M 351 258.171875 "/>
-</clipPath>
-<clipPath id="clip79">
-  <path d="M 385 258.171875 L 387 258.171875 L 387 469.851562 L 385 469.851562 Z M 385 258.171875 "/>
-</clipPath>
-<clipPath id="clip80">
-  <path d="M 419 258.171875 L 421 258.171875 L 421 469.851562 L 419 469.851562 Z M 419 258.171875 "/>
-</clipPath>
-<clipPath id="clip81">
-  <path d="M 35.152344 240.402344 L 229.136719 240.402344 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 240.402344 "/>
-</clipPath>
-<clipPath id="clip82">
-  <path d="M 234.617188 240.402344 L 428.601562 240.402344 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 240.402344 "/>
-</clipPath>
-<clipPath id="clip83">
-  <path d="M 35.152344 5.480469 L 229.136719 5.480469 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 5.480469 "/>
-</clipPath>
-<clipPath id="clip84">
-  <path d="M 234.617188 5.480469 L 428.601562 5.480469 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 5.480469 "/>
-</clipPath>
-</defs>
-<g id="surface69">
-<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
-<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 "/>
-<g clip-path="url(#clip1)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 234.925781 L 229.136719 234.925781 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 234.925781 "/>
-</g>
-<g clip-path="url(#clip2)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 204.210938 L 229.136719 204.210938 "/>
-</g>
-<g clip-path="url(#clip3)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 150.910156 L 229.136719 150.910156 "/>
-</g>
-<g clip-path="url(#clip4)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 97.613281 L 229.136719 97.613281 "/>
-</g>
-<g clip-path="url(#clip5)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 44.3125 L 229.136719 44.3125 "/>
-</g>
-<g clip-path="url(#clip6)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 234.925781 L 67.707031 23.246094 "/>
-</g>
-<g clip-path="url(#clip7)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 234.925781 L 101.621094 23.246094 "/>
-</g>
-<g clip-path="url(#clip8)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 234.925781 L 135.535156 23.246094 "/>
-</g>
-<g clip-path="url(#clip9)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 234.925781 L 169.449219 23.246094 "/>
-</g>
-<g clip-path="url(#clip10)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 234.925781 L 203.363281 23.246094 "/>
-</g>
-<g clip-path="url(#clip11)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 230.859375 L 229.136719 230.859375 "/>
-</g>
-<g clip-path="url(#clip12)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 177.558594 L 229.136719 177.558594 "/>
-</g>
-<g clip-path="url(#clip13)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 124.261719 L 229.136719 124.261719 "/>
-</g>
-<g clip-path="url(#clip14)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 70.960938 L 229.136719 70.960938 "/>
-</g>
-<g clip-path="url(#clip15)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 234.925781 L 50.75 23.246094 "/>
-</g>
-<g clip-path="url(#clip16)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 234.925781 L 84.664062 23.246094 "/>
-</g>
-<g clip-path="url(#clip17)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 234.925781 L 118.578125 23.246094 "/>
-</g>
-<g clip-path="url(#clip18)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 234.925781 L 152.492188 23.246094 "/>
-</g>
-<g clip-path="url(#clip19)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 234.925781 L 186.40625 23.246094 "/>
-</g>
-<g clip-path="url(#clip20)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 234.925781 L 220.320312 23.246094 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 118.933594 C 120.53125 121.539062 116.625 121.539062 116.625 118.933594 C 116.625 116.324219 120.53125 116.324219 120.53125 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 150.910156 C 93.402344 153.515625 89.492188 153.515625 89.492188 150.910156 C 89.492188 148.304688 93.402344 148.304688 93.402344 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 124.261719 C 134.097656 126.867188 130.1875 126.867188 130.1875 124.261719 C 130.1875 121.65625 134.097656 121.65625 134.097656 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 108.273438 C 174.796875 110.878906 170.886719 110.878906 170.886719 108.273438 C 170.886719 105.664062 174.796875 105.664062 174.796875 108.273438 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 113.601562 C 154.445312 116.207031 150.539062 116.207031 150.539062 113.601562 C 150.539062 110.996094 154.445312 110.996094 154.445312 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 129.589844 C 140.882812 132.199219 136.972656 132.199219 136.972656 129.589844 C 136.972656 126.984375 140.882812 126.984375 140.882812 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 102.941406 C 161.230469 105.546875 157.320312 105.546875 157.320312 102.941406 C 157.320312 100.335938 161.230469 100.335938 161.230469 102.941406 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 92.28125 C 154.445312 94.890625 150.539062 94.890625 150.539062 92.28125 C 150.539062 89.675781 154.445312 89.675781 154.445312 92.28125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 92.28125 C 147.664062 94.890625 143.753906 94.890625 143.753906 92.28125 C 143.753906 89.675781 147.664062 89.675781 147.664062 92.28125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 140.25 C 106.96875 142.859375 103.058594 142.859375 103.058594 140.25 C 103.058594 137.644531 106.96875 137.644531 106.96875 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 129.589844 C 113.75 132.199219 109.839844 132.199219 109.839844 129.589844 C 109.839844 126.984375 113.75 126.984375 113.75 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 118.933594 C 140.882812 121.539062 136.972656 121.539062 136.972656 118.933594 C 136.972656 116.324219 140.882812 116.324219 140.882812 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 113.601562 C 140.882812 116.207031 136.972656 116.207031 136.972656 113.601562 C 136.972656 110.996094 140.882812 110.996094 140.882812 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 150.910156 C 106.96875 153.515625 103.058594 153.515625 103.058594 150.910156 C 103.058594 148.304688 106.96875 148.304688 106.96875 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 145.582031 C 120.53125 148.1875 116.625 148.1875 116.625 145.582031 C 116.625 142.976562 120.53125 142.976562 120.53125 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 161.570312 C 106.96875 164.175781 103.058594 164.175781 103.058594 161.570312 C 103.058594 158.964844 106.96875 158.964844 106.96875 161.570312 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 145.582031 C 127.316406 148.1875 123.40625 148.1875 123.40625 145.582031 C 123.40625 142.976562 127.316406 142.976562 127.316406 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 150.910156 C 120.53125 153.515625 116.625 153.515625 116.625 150.910156 C 116.625 148.304688 120.53125 148.304688 120.53125 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 118.933594 C 134.097656 121.539062 130.1875 121.539062 130.1875 118.933594 C 130.1875 116.324219 134.097656 116.324219 134.097656 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 124.261719 C 147.664062 126.867188 143.753906 126.867188 143.753906 124.261719 C 143.753906 121.65625 147.664062 121.65625 147.664062 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 108.273438 C 147.664062 110.878906 143.753906 110.878906 143.753906 108.273438 C 143.753906 105.664062 147.664062 105.664062 147.664062 108.273438 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 86.953125 C 174.796875 89.558594 170.886719 89.558594 170.886719 86.953125 C 170.886719 84.347656 174.796875 84.347656 174.796875 86.953125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 166.902344 C 100.183594 169.507812 96.273438 169.507812 96.273438 166.902344 C 96.273438 164.292969 100.183594 164.292969 100.183594 166.902344 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 208.707031 49.644531 C 208.707031 52.25 204.800781 52.25 204.800781 49.644531 C 204.800781 47.035156 208.707031 47.035156 208.707031 49.644531 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 222.273438 49.644531 C 222.273438 52.25 218.363281 52.25 218.363281 49.644531 C 218.363281 47.035156 222.273438 47.035156 222.273438 49.644531 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 181.578125 65.632812 C 181.578125 68.238281 177.667969 68.238281 177.667969 65.632812 C 177.667969 63.027344 181.578125 63.027344 181.578125 65.632812 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 134.921875 C 113.75 137.527344 109.839844 137.527344 109.839844 134.921875 C 109.839844 132.316406 113.75 132.316406 113.75 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 84.664062 165.398438 L 86.382812 163.894531 L 88.097656 162.386719 L 91.535156 159.371094 L 93.25 157.859375 L 94.96875 156.347656 L 96.683594 154.832031 L 98.402344 153.3125 L 100.117188 151.792969 L 103.554688 148.738281 L 105.269531 147.207031 L 106.988281 145.671875 L 108.703125 144.128906 L 110.421875 142.582031 L 112.140625 141.027344 L 113.855469 139.46875 L 115.574219 137.902344 L 117.289062 136.328125 L 119.007812 134.742188 L 120.726562 133.148438 L 122.441406 131.546875 L 124.160156 129.933594 L 125.875 128.3125 L 127.59375 126.679688 L 129.308594 125.035156 L 131.027344 123.382812 L 132.746094 121.71875 L 134.460938 120.050781 L 136.179688 118.371094 L 137.894531 116.683594 L 139.613281 114.988281 L 141.332031 113.289062 L 143.046875 111.582031 L 144.765625 109.871094 L 146.480469 108.152344 L 148.199219 106.433594 L 149.917969 104.710938 L 151.632812 102.980469 L 153.351562 101.25 L 155.066406 99.515625 L 156.785156 97.78125 L 158.503906 96.042969 L 160.21875 94.300781 L 161.9375 92.558594 L 163.652344 90.816406 L 165.371094 89.070312 L 167.085938 87.324219 L 168.804688 85.578125 L 170.523438 83.828125 L 172.238281 82.078125 L 173.957031 80.328125 L 175.671875 78.574219 L 177.390625 76.824219 L 179.109375 75.070312 L 180.824219 73.316406 L 182.542969 71.5625 L 184.257812 69.804688 L 185.976562 68.050781 L 187.695312 66.292969 L 189.410156 64.539062 L 191.128906 62.78125 L 192.84375 61.023438 L 196.28125 57.507812 L 197.996094 55.75 L 199.714844 53.992188 L 201.429688 52.230469 L 203.148438 50.472656 L 204.863281 48.710938 L 206.582031 46.953125 L 208.300781 45.191406 L 210.015625 43.433594 L 211.734375 41.671875 L 213.449219 39.914062 L 216.886719 36.390625 L 218.601562 34.628906 L 220.320312 32.867188 L 220.320312 48.824219 L 218.601562 50.3125 L 216.886719 51.800781 L 215.167969 53.289062 L 213.449219 54.78125 L 211.734375 56.269531 L 210.015625 57.761719 L 208.300781 59.25 L 204.863281 62.234375 L 203.148438 63.722656 L 201.429688 65.214844 L 199.714844 66.707031 L 197.996094 68.199219 L 196.28125 69.691406 L 192.84375 72.675781 L 191.128906 74.167969 L 189.410156 75.664062 L 187.695312 77.15625 L 184.257812 80.148438 L 182.542969 81.640625 L 180.824219 83.136719 L 179.109375 84.636719 L 175.671875 87.628906 L 173.957031 89.128906 L 172.238281 90.628906 L 170.523438 92.128906 L 168.804688 93.632812 L 167.085938 95.132812 L 165.371094 96.636719 L 163.652344 98.144531 L 161.9375 99.648438 L 160.21875 101.160156 L 158.503906 102.667969 L 156.785156 104.179688 L 155.066406 105.695312 L 153.351562 107.210938 L 151.632812 108.730469 L 149.917969 110.253906 L 148.199219 111.78125 L 146.480469 113.3125 L 144.765625 114.84375 L 143.046875 116.382812 L 141.332031 117.929688 L 139.613281 119.476562 L 137.894531 121.035156 L 136.179688 122.597656 L 134.460938 124.167969 L 132.746094 125.75 L 131.027344 127.335938 L 129.308594 128.933594 L 127.59375 130.542969 L 125.875 132.160156 L 124.160156 133.789062 L 122.441406 135.425781 L 120.726562 137.074219 L 119.007812 138.730469 L 117.289062 140.398438 L 115.574219 142.074219 L 113.855469 143.757812 L 112.140625 145.449219 L 110.421875 147.144531 L 108.703125 148.847656 L 106.988281 150.558594 L 105.269531 152.273438 L 103.554688 153.988281 L 101.835938 155.710938 L 100.117188 157.4375 L 98.402344 159.167969 L 96.683594 160.902344 L 94.96875 162.636719 L 93.25 164.371094 L 91.535156 166.113281 L 89.816406 167.851562 L 88.097656 169.597656 L 86.382812 171.339844 L 84.664062 173.085938 Z M 84.664062 165.398438 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 169.242188 L 86.382812 167.617188 L 88.097656 165.992188 L 91.535156 162.742188 L 93.25 161.117188 L 94.96875 159.492188 L 96.683594 157.867188 L 98.402344 156.242188 L 100.117188 154.613281 L 103.554688 151.363281 L 105.269531 149.738281 L 106.988281 148.113281 L 108.703125 146.488281 L 112.140625 143.238281 L 113.855469 141.613281 L 115.574219 139.988281 L 117.289062 138.363281 L 120.726562 135.113281 L 122.441406 133.488281 L 124.160156 131.859375 L 125.875 130.234375 L 127.59375 128.609375 L 129.308594 126.984375 L 132.746094 123.734375 L 134.460938 122.109375 L 136.179688 120.484375 L 137.894531 118.859375 L 141.332031 115.609375 L 143.046875 113.984375 L 144.765625 112.359375 L 146.480469 110.734375 L 148.199219 109.105469 L 149.917969 107.480469 L 151.632812 105.855469 L 153.351562 104.230469 L 155.066406 102.605469 L 158.503906 99.355469 L 160.21875 97.730469 L 161.9375 96.105469 L 163.652344 94.480469 L 165.371094 92.855469 L 167.085938 91.230469 L 170.523438 87.980469 L 172.238281 86.351562 L 173.957031 84.726562 L 175.671875 83.101562 L 179.109375 79.851562 L 180.824219 78.226562 L 182.542969 76.601562 L 184.257812 74.976562 L 187.695312 71.726562 L 189.410156 70.101562 L 191.128906 68.476562 L 192.84375 66.851562 L 194.5625 65.222656 L 196.28125 63.597656 L 197.996094 61.972656 L 199.714844 60.347656 L 201.429688 58.722656 L 203.148438 57.097656 L 204.863281 55.472656 L 208.300781 52.222656 L 210.015625 50.597656 L 211.734375 48.972656 L 213.449219 47.347656 L 216.886719 44.097656 L 218.601562 42.46875 L 220.320312 40.84375 "/>
-<g clip-path="url(#clip21)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 469.847656 L 229.136719 469.847656 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 469.847656 "/>
-</g>
-<g clip-path="url(#clip22)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 439.132812 L 229.136719 439.132812 "/>
-</g>
-<g clip-path="url(#clip23)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 385.835938 L 229.136719 385.835938 "/>
-</g>
-<g clip-path="url(#clip24)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 332.535156 L 229.136719 332.535156 "/>
-</g>
-<g clip-path="url(#clip25)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 279.238281 L 229.136719 279.238281 "/>
-</g>
-<g clip-path="url(#clip26)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 469.847656 L 67.707031 258.171875 "/>
-</g>
-<g clip-path="url(#clip27)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 469.847656 L 101.621094 258.171875 "/>
-</g>
-<g clip-path="url(#clip28)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 469.847656 L 135.535156 258.171875 "/>
-</g>
-<g clip-path="url(#clip29)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 469.847656 L 169.449219 258.171875 "/>
-</g>
-<g clip-path="url(#clip30)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 469.847656 L 203.363281 258.171875 "/>
-</g>
-<g clip-path="url(#clip31)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 465.785156 L 229.136719 465.785156 "/>
-</g>
-<g clip-path="url(#clip32)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 412.484375 L 229.136719 412.484375 "/>
-</g>
-<g clip-path="url(#clip33)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 359.1875 L 229.136719 359.1875 "/>
-</g>
-<g clip-path="url(#clip34)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 305.886719 L 229.136719 305.886719 "/>
-</g>
-<g clip-path="url(#clip35)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 469.847656 L 50.75 258.171875 "/>
-</g>
-<g clip-path="url(#clip36)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 469.847656 L 84.664062 258.171875 "/>
-</g>
-<g clip-path="url(#clip37)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 469.847656 L 118.578125 258.171875 "/>
-</g>
-<g clip-path="url(#clip38)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 469.847656 L 152.492188 258.171875 "/>
-</g>
-<g clip-path="url(#clip39)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 469.847656 L 186.40625 258.171875 "/>
-</g>
-<g clip-path="url(#clip40)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 469.847656 L 220.320312 258.171875 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 391.164062 C 86.621094 393.773438 82.710938 393.773438 82.710938 391.164062 C 82.710938 388.558594 86.621094 388.558594 86.621094 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 364.515625 C 106.96875 367.121094 103.058594 367.121094 103.058594 364.515625 C 103.058594 361.910156 106.96875 361.910156 106.96875 364.515625 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 59.488281 428.472656 C 59.488281 431.082031 55.578125 431.082031 55.578125 428.472656 C 55.578125 425.867188 59.488281 425.867188 59.488281 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 401.824219 C 86.621094 404.429688 82.710938 404.429688 82.710938 401.824219 C 82.710938 399.21875 86.621094 399.21875 86.621094 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 407.15625 C 86.621094 409.761719 82.710938 409.761719 82.710938 407.15625 C 82.710938 404.546875 86.621094 404.546875 86.621094 407.15625 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 423.144531 C 79.835938 425.75 75.925781 425.75 75.925781 423.144531 C 75.925781 420.539062 79.835938 420.539062 79.835938 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 385.835938 C 106.96875 388.441406 103.058594 388.441406 103.058594 385.835938 C 103.058594 383.230469 106.96875 383.230469 106.96875 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 401.824219 C 100.183594 404.429688 96.273438 404.429688 96.273438 401.824219 C 96.273438 399.21875 100.183594 399.21875 100.183594 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 412.484375 C 86.621094 415.089844 82.710938 415.089844 82.710938 412.484375 C 82.710938 409.878906 86.621094 409.878906 86.621094 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 375.175781 C 113.75 377.78125 109.839844 377.78125 109.839844 375.175781 C 109.839844 372.570312 113.75 372.570312 113.75 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 380.503906 C 113.75 383.113281 109.839844 383.113281 109.839844 380.503906 C 109.839844 377.898438 113.75 377.898438 113.75 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 412.484375 C 79.835938 415.089844 75.925781 415.089844 75.925781 412.484375 C 75.925781 409.878906 79.835938 409.878906 79.835938 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 375.175781 C 100.183594 377.78125 96.273438 377.78125 96.273438 375.175781 C 96.273438 372.570312 100.183594 372.570312 100.183594 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 369.847656 C 106.96875 372.453125 103.058594 372.453125 103.058594 369.847656 C 103.058594 367.238281 106.96875 367.238281 106.96875 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 423.144531 C 86.621094 425.75 82.710938 425.75 82.710938 423.144531 C 82.710938 420.539062 86.621094 420.539062 86.621094 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 57.535156 440.144531 L 58.21875 439.300781 L 60.28125 436.769531 L 60.96875 435.921875 L 61.65625 435.078125 L 62.339844 434.234375 L 63.027344 433.386719 L 63.714844 432.542969 L 65.089844 430.847656 L 65.777344 430.003906 L 66.464844 429.15625 L 67.148438 428.308594 L 67.835938 427.457031 L 68.523438 426.609375 L 69.210938 425.757812 L 69.898438 424.910156 L 70.585938 424.058594 L 71.269531 423.203125 L 72.644531 421.5 L 74.019531 419.789062 L 74.707031 418.929688 L 75.390625 418.070312 L 76.765625 416.351562 L 78.140625 414.625 L 78.828125 413.757812 L 79.511719 412.890625 L 80.886719 411.148438 L 81.574219 410.273438 L 82.261719 409.394531 L 82.949219 408.511719 L 83.632812 407.628906 L 85.007812 405.847656 L 86.382812 404.050781 L 87.070312 403.140625 L 87.753906 402.230469 L 88.441406 401.3125 L 89.128906 400.390625 L 89.816406 399.460938 L 90.503906 398.523438 L 91.191406 397.578125 L 91.875 396.628906 L 92.5625 395.667969 L 93.25 394.703125 L 93.9375 393.730469 L 94.625 392.75 L 95.3125 391.761719 L 95.996094 390.765625 L 96.683594 389.765625 L 97.371094 388.757812 L 98.058594 387.742188 L 98.746094 386.722656 L 99.433594 385.699219 L 100.117188 384.667969 L 100.804688 383.632812 L 101.492188 382.59375 L 102.179688 381.550781 L 102.867188 380.503906 L 103.554688 379.453125 L 104.238281 378.402344 L 105.613281 376.285156 L 106.988281 374.160156 L 107.675781 373.09375 L 108.359375 372.027344 L 109.046875 370.960938 L 109.734375 369.886719 L 110.421875 368.816406 L 111.796875 366.667969 L 111.796875 375.09375 L 111.109375 375.949219 L 109.046875 378.527344 L 108.359375 379.390625 L 107.675781 380.253906 L 106.300781 381.988281 L 105.613281 382.859375 L 104.238281 384.609375 L 103.554688 385.484375 L 102.867188 386.367188 L 101.492188 388.140625 L 100.804688 389.03125 L 100.117188 389.929688 L 99.433594 390.832031 L 98.746094 391.738281 L 98.058594 392.648438 L 97.371094 393.566406 L 96.683594 394.488281 L 95.996094 395.421875 L 95.3125 396.355469 L 94.625 397.300781 L 93.9375 398.25 L 93.25 399.210938 L 92.5625 400.175781 L 91.875 401.148438 L 91.191406 402.128906 L 90.503906 403.117188 L 89.816406 404.113281 L 89.128906 405.113281 L 88.441406 406.121094 L 87.753906 407.136719 L 87.070312 408.15625 L 86.382812 409.179688 L 85.695312 410.210938 L 85.007812 411.246094 L 84.320312 412.285156 L 83.632812 413.328125 L 82.949219 414.375 L 82.261719 415.425781 L 80.886719 417.535156 L 80.199219 418.59375 L 79.511719 419.65625 L 78.828125 420.71875 L 77.453125 422.851562 L 75.390625 426.0625 L 74.707031 427.136719 L 73.332031 429.285156 L 71.269531 432.519531 L 70.585938 433.597656 L 67.148438 439.007812 L 66.464844 440.089844 L 65.777344 441.175781 L 65.089844 442.257812 L 62.339844 446.601562 L 61.65625 447.6875 L 60.96875 448.773438 L 60.28125 449.863281 L 59.59375 450.949219 L 58.90625 452.039062 L 58.21875 453.125 L 57.535156 454.214844 Z M 57.535156 440.144531 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 57.535156 447.179688 L 58.21875 446.210938 L 60.28125 443.316406 L 60.96875 442.347656 L 61.65625 441.382812 L 62.339844 440.417969 L 63.027344 439.453125 L 63.714844 438.484375 L 65.777344 435.589844 L 66.464844 434.621094 L 67.148438 433.65625 L 69.210938 430.761719 L 69.898438 429.792969 L 70.585938 428.828125 L 71.269531 427.863281 L 71.957031 426.898438 L 72.644531 425.929688 L 74.707031 423.035156 L 75.390625 422.066406 L 77.453125 419.171875 L 78.140625 418.203125 L 78.828125 417.238281 L 79.511719 416.273438 L 80.199219 415.308594 L 80.886719 414.339844 L 82.949219 411.445312 L 83.632812 410.476562 L 85.695312 407.582031 L 86.382812 406.613281 L 87.070312 405.648438 L 87.753906 404.683594 L 88.441406 403.71875 L 89.128906 402.75 L 91.191406 399.855469 L 91.875 398.886719 L 94.625 395.027344 L 95.3125 394.058594 L 95.996094 393.09375 L 97.371094 391.164062 L 98.058594 390.195312 L 99.433594 388.265625 L 100.117188 387.300781 L 100.804688 386.332031 L 102.867188 383.4375 L 103.554688 382.46875 L 104.238281 381.503906 L 105.613281 379.574219 L 106.300781 378.605469 L 107.675781 376.675781 L 108.359375 375.710938 L 109.046875 374.742188 L 111.109375 371.847656 L 111.796875 370.878906 "/>
-<g clip-path="url(#clip41)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 234.925781 L 428.601562 234.925781 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 234.925781 "/>
-</g>
-<g clip-path="url(#clip42)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 204.210938 L 428.601562 204.210938 "/>
-</g>
-<g clip-path="url(#clip43)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 150.910156 L 428.601562 150.910156 "/>
-</g>
-<g clip-path="url(#clip44)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 97.613281 L 428.601562 97.613281 "/>
-</g>
-<g clip-path="url(#clip45)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 44.3125 L 428.601562 44.3125 "/>
-</g>
-<g clip-path="url(#clip46)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 234.925781 L 267.171875 23.246094 "/>
-</g>
-<g clip-path="url(#clip47)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 234.925781 L 301.085938 23.246094 "/>
-</g>
-<g clip-path="url(#clip48)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 234.925781 L 335 23.246094 "/>
-</g>
-<g clip-path="url(#clip49)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 234.925781 L 368.914062 23.246094 "/>
-</g>
-<g clip-path="url(#clip50)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 234.925781 L 402.828125 23.246094 "/>
-</g>
-<g clip-path="url(#clip51)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 230.859375 L 428.601562 230.859375 "/>
-</g>
-<g clip-path="url(#clip52)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 177.558594 L 428.601562 177.558594 "/>
-</g>
-<g clip-path="url(#clip53)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 124.261719 L 428.601562 124.261719 "/>
-</g>
-<g clip-path="url(#clip54)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 70.960938 L 428.601562 70.960938 "/>
-</g>
-<g clip-path="url(#clip55)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 234.925781 L 250.214844 23.246094 "/>
-</g>
-<g clip-path="url(#clip56)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 234.925781 L 284.128906 23.246094 "/>
-</g>
-<g clip-path="url(#clip57)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 234.925781 L 318.042969 23.246094 "/>
-</g>
-<g clip-path="url(#clip58)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 234.925781 L 351.957031 23.246094 "/>
-</g>
-<g clip-path="url(#clip59)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 234.925781 L 385.871094 23.246094 "/>
-</g>
-<g clip-path="url(#clip60)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 234.925781 L 419.785156 23.246094 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 134.921875 C 320 137.527344 316.089844 137.527344 316.089844 134.921875 C 316.089844 132.316406 320 132.316406 320 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 129.589844 C 320 132.199219 316.089844 132.199219 316.089844 129.589844 C 316.089844 126.984375 320 126.984375 320 129.589844 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 318.042969 124.148438 L 318.128906 124.214844 L 318.214844 124.285156 L 318.300781 124.347656 L 318.386719 124.414062 L 318.472656 124.476562 L 318.558594 124.535156 L 318.644531 124.597656 L 318.730469 124.652344 L 318.816406 124.710938 L 318.902344 124.761719 L 318.988281 124.816406 L 319.074219 124.867188 L 319.246094 124.960938 L 319.417969 125.046875 L 319.503906 125.085938 L 319.675781 125.15625 L 319.847656 125.21875 L 320.105469 125.289062 L 320.277344 125.320312 L 320.363281 125.332031 L 320.535156 125.347656 L 320.707031 125.347656 L 320.878906 125.332031 L 320.964844 125.320312 L 321.050781 125.304688 L 321.136719 125.285156 L 321.308594 125.238281 L 321.390625 125.207031 L 321.5625 125.136719 L 321.734375 125.050781 L 321.90625 124.949219 L 321.992188 124.894531 L 322.078125 124.835938 L 322.164062 124.773438 L 322.25 124.707031 L 322.421875 124.566406 L 322.59375 124.410156 L 322.679688 124.328125 L 322.765625 124.242188 L 322.9375 124.0625 L 323.023438 123.96875 L 323.195312 123.773438 L 323.28125 123.671875 L 323.453125 123.460938 L 323.539062 123.351562 L 323.796875 123.011719 L 323.882812 122.894531 L 324.054688 122.652344 L 324.3125 122.277344 L 324.484375 122.019531 L 324.742188 121.621094 L 324.828125 121.484375 L 324.828125 137.699219 L 324.742188 137.632812 L 324.65625 137.5625 L 324.570312 137.5 L 324.484375 137.433594 L 324.398438 137.371094 L 324.3125 137.3125 L 324.226562 137.25 L 324.140625 137.195312 L 324.054688 137.136719 L 323.96875 137.085938 L 323.882812 137.03125 L 323.796875 136.980469 L 323.625 136.886719 L 323.453125 136.800781 L 323.367188 136.761719 L 323.195312 136.691406 L 323.023438 136.628906 L 322.765625 136.558594 L 322.59375 136.527344 L 322.507812 136.515625 L 322.421875 136.507812 L 322.25 136.5 L 322.164062 136.5 L 321.992188 136.515625 L 321.90625 136.527344 L 321.820312 136.542969 L 321.734375 136.5625 L 321.5625 136.609375 L 321.476562 136.640625 L 321.390625 136.675781 L 321.308594 136.710938 L 321.136719 136.796875 L 320.964844 136.898438 L 320.878906 136.953125 L 320.792969 137.011719 L 320.707031 137.074219 L 320.621094 137.140625 L 320.449219 137.28125 L 320.277344 137.4375 L 320.191406 137.519531 L 320.105469 137.605469 L 319.933594 137.785156 L 319.847656 137.878906 L 319.675781 138.074219 L 319.589844 138.175781 L 319.417969 138.386719 L 319.332031 138.496094 L 319.074219 138.835938 L 318.988281 138.953125 L 318.816406 139.195312 L 318.558594 139.570312 L 318.386719 139.828125 L 318.214844 140.09375 L 318.128906 140.230469 L 318.042969 140.363281 Z M 318.042969 124.148438 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 132.257812 L 318.214844 132.1875 L 318.300781 132.15625 L 318.472656 132.085938 L 318.558594 132.054688 L 318.644531 132.019531 L 318.730469 131.988281 L 318.902344 131.917969 L 318.988281 131.886719 L 319.160156 131.816406 L 319.246094 131.785156 L 319.417969 131.714844 L 319.503906 131.683594 L 319.589844 131.648438 L 319.675781 131.617188 L 319.847656 131.546875 L 319.933594 131.515625 L 320.105469 131.445312 L 320.191406 131.414062 L 320.363281 131.34375 L 320.449219 131.3125 L 320.535156 131.277344 L 320.621094 131.246094 L 320.792969 131.175781 L 320.878906 131.144531 L 321.050781 131.074219 L 321.136719 131.042969 L 321.308594 130.972656 L 321.390625 130.941406 L 321.476562 130.90625 L 321.5625 130.875 L 321.734375 130.804688 L 321.820312 130.773438 L 321.992188 130.703125 L 322.078125 130.671875 L 322.25 130.601562 L 322.335938 130.570312 L 322.421875 130.535156 L 322.507812 130.503906 L 322.679688 130.433594 L 322.765625 130.402344 L 322.9375 130.332031 L 323.023438 130.300781 L 323.195312 130.230469 L 323.28125 130.199219 L 323.367188 130.164062 L 323.453125 130.132812 L 323.625 130.0625 L 323.710938 130.03125 L 323.882812 129.960938 L 323.96875 129.929688 L 324.140625 129.859375 L 324.226562 129.828125 L 324.3125 129.792969 L 324.398438 129.761719 L 324.570312 129.691406 L 324.65625 129.660156 L 324.828125 129.589844 "/>
-<g clip-path="url(#clip61)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 469.847656 L 428.601562 469.847656 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 469.847656 "/>
-</g>
-<g clip-path="url(#clip62)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 439.132812 L 428.601562 439.132812 "/>
-</g>
-<g clip-path="url(#clip63)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 385.835938 L 428.601562 385.835938 "/>
-</g>
-<g clip-path="url(#clip64)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 332.535156 L 428.601562 332.535156 "/>
-</g>
-<g clip-path="url(#clip65)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 279.238281 L 428.601562 279.238281 "/>
-</g>
-<g clip-path="url(#clip66)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 469.847656 L 267.171875 258.171875 "/>
-</g>
-<g clip-path="url(#clip67)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 469.847656 L 301.085938 258.171875 "/>
-</g>
-<g clip-path="url(#clip68)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 469.847656 L 335 258.171875 "/>
-</g>
-<g clip-path="url(#clip69)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 469.847656 L 368.914062 258.171875 "/>
-</g>
-<g clip-path="url(#clip70)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 469.847656 L 402.828125 258.171875 "/>
-</g>
-<g clip-path="url(#clip71)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 465.785156 L 428.601562 465.785156 "/>
-</g>
-<g clip-path="url(#clip72)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 412.484375 L 428.601562 412.484375 "/>
-</g>
-<g clip-path="url(#clip73)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 359.1875 L 428.601562 359.1875 "/>
-</g>
-<g clip-path="url(#clip74)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 305.886719 L 428.601562 305.886719 "/>
-</g>
-<g clip-path="url(#clip75)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 469.847656 L 250.214844 258.171875 "/>
-</g>
-<g clip-path="url(#clip76)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 469.847656 L 284.128906 258.171875 "/>
-</g>
-<g clip-path="url(#clip77)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 469.847656 L 318.042969 258.171875 "/>
-</g>
-<g clip-path="url(#clip78)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 469.847656 L 351.957031 258.171875 "/>
-</g>
-<g clip-path="url(#clip79)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 469.847656 L 385.871094 258.171875 "/>
-</g>
-<g clip-path="url(#clip80)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 469.847656 L 419.785156 258.171875 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 396.496094 C 292.867188 399.101562 288.957031 399.101562 288.957031 396.496094 C 288.957031 393.890625 292.867188 393.890625 292.867188 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 428.472656 C 265.738281 431.082031 261.828125 431.082031 261.828125 428.472656 C 261.828125 425.867188 265.738281 425.867188 265.738281 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 385.835938 C 286.085938 388.441406 282.175781 388.441406 282.175781 385.835938 C 282.175781 383.230469 286.085938 383.230469 286.085938 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 391.164062 C 286.085938 393.773438 282.175781 393.773438 282.175781 391.164062 C 282.175781 388.558594 286.085938 388.558594 286.085938 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 407.15625 C 286.085938 409.761719 282.175781 409.761719 282.175781 407.15625 C 282.175781 404.546875 286.085938 404.546875 286.085938 407.15625 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 385.835938 C 292.867188 388.441406 288.957031 388.441406 288.957031 385.835938 C 288.957031 383.230469 292.867188 383.230469 292.867188 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 243.433594 452.394531 L 244.035156 451.695312 L 245.238281 450.304688 L 245.839844 449.605469 L 246.4375 448.90625 L 248.84375 446.109375 L 249.445312 445.40625 L 250.046875 444.707031 L 250.644531 444.003906 L 251.246094 443.300781 L 251.847656 442.59375 L 252.449219 441.890625 L 253.652344 440.476562 L 254.253906 439.765625 L 254.851562 439.058594 L 255.453125 438.347656 L 257.257812 436.203125 L 257.859375 435.484375 L 258.460938 434.761719 L 259.058594 434.039062 L 259.660156 433.316406 L 260.261719 432.589844 L 260.863281 431.859375 L 262.066406 430.390625 L 262.667969 429.652344 L 263.265625 428.910156 L 263.867188 428.164062 L 264.46875 427.414062 L 265.070312 426.660156 L 265.671875 425.902344 L 266.273438 425.140625 L 266.875 424.375 L 267.472656 423.601562 L 268.074219 422.828125 L 268.675781 422.050781 L 269.878906 420.480469 L 271.082031 418.894531 L 271.679688 418.09375 L 272.882812 416.484375 L 273.484375 415.675781 L 274.085938 414.863281 L 274.6875 414.046875 L 275.285156 413.226562 L 275.886719 412.40625 L 277.089844 410.757812 L 277.691406 409.929688 L 278.894531 408.265625 L 279.492188 407.433594 L 281.296875 404.925781 L 282.5 403.246094 L 283.101562 402.402344 L 283.699219 401.5625 L 284.902344 399.875 L 285.503906 399.027344 L 286.105469 398.183594 L 287.308594 396.488281 L 287.90625 395.640625 L 288.507812 394.792969 L 289.109375 393.941406 L 289.710938 393.09375 L 290.3125 392.242188 L 290.914062 391.394531 L 290.914062 398.976562 L 290.3125 399.675781 L 289.710938 400.371094 L 287.90625 402.46875 L 287.308594 403.167969 L 286.707031 403.867188 L 286.105469 404.570312 L 285.503906 405.269531 L 283.699219 407.378906 L 283.101562 408.085938 L 281.296875 410.207031 L 279.492188 412.339844 L 278.894531 413.054688 L 278.292969 413.769531 L 276.488281 415.925781 L 275.285156 417.378906 L 274.6875 418.105469 L 273.484375 419.574219 L 272.28125 421.050781 L 271.679688 421.796875 L 271.082031 422.546875 L 270.480469 423.296875 L 269.277344 424.8125 L 268.675781 425.578125 L 268.074219 426.347656 L 267.472656 427.121094 L 266.875 427.898438 L 266.273438 428.679688 L 265.671875 429.464844 L 265.070312 430.253906 L 264.46875 431.046875 L 263.867188 431.84375 L 263.265625 432.644531 L 262.667969 433.453125 L 262.066406 434.257812 L 261.464844 435.070312 L 260.261719 436.703125 L 259.660156 437.523438 L 259.058594 438.347656 L 258.460938 439.171875 L 257.257812 440.828125 L 255.453125 443.324219 L 254.851562 444.160156 L 254.253906 445 L 251.847656 448.359375 L 250.644531 450.046875 L 250.046875 450.894531 L 249.445312 451.738281 L 248.84375 452.585938 L 248.242188 453.429688 L 247.640625 454.277344 L 247.039062 455.128906 L 246.4375 455.976562 L 245.839844 456.824219 L 244.636719 458.527344 L 244.035156 459.375 L 243.433594 460.226562 Z M 243.433594 452.394531 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 243.433594 456.308594 L 245.839844 453.214844 L 246.4375 452.441406 L 250.046875 447.800781 L 250.644531 447.027344 L 251.246094 446.25 L 254.253906 442.382812 L 254.851562 441.609375 L 258.460938 436.96875 L 259.058594 436.195312 L 259.660156 435.417969 L 262.667969 431.550781 L 263.265625 430.777344 L 266.875 426.136719 L 267.472656 425.359375 L 271.082031 420.71875 L 271.679688 419.945312 L 274.6875 416.078125 L 275.285156 415.304688 L 275.886719 414.527344 L 278.894531 410.660156 L 279.492188 409.886719 L 283.101562 405.246094 L 283.699219 404.46875 L 287.308594 399.828125 L 287.90625 399.054688 L 290.914062 395.1875 "/>
-<g clip-path="url(#clip81)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 240.40625 L 35.152344 240.40625 Z M 35.152344 258.171875 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-1" x="129.644531" y="252.204102"/>
-</g>
-<g clip-path="url(#clip82)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 240.40625 L 234.617188 240.40625 Z M 234.617188 258.171875 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-2" x="329.109375" y="252.204102"/>
-</g>
-<g clip-path="url(#clip83)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 5.480469 L 35.152344 5.480469 Z M 35.152344 23.246094 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="129.644531" y="17.27832"/>
-</g>
-<g clip-path="url(#clip84)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 5.480469 L 234.617188 5.480469 Z M 234.617188 23.246094 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-4" x="329.109375" y="17.27832"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 472.589844 L 50.75 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 472.589844 L 84.664062 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 472.589844 L 118.578125 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 472.589844 L 152.492188 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 472.589844 L 186.40625 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 472.589844 L 220.320312 469.847656 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="45.75" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="50.75" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="79.664062" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="84.664062" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="113.578125" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="118.578125" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="147.492188" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="152.492188" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="181.40625" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="186.40625" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="215.320312" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="220.320312" y="481.196289"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 472.589844 L 250.214844 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 472.589844 L 284.128906 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 472.589844 L 318.042969 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 472.589844 L 351.957031 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 472.589844 L 385.871094 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 472.589844 L 419.785156 469.847656 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="245.214844" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="250.214844" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="279.128906" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="284.128906" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="313.042969" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="318.042969" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="346.957031" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="351.957031" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="380.871094" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="385.871094" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="414.785156" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="419.785156" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="20.21875" y="233.774414"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="233.774414"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="20.21875" y="180.473633"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="180.473633"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="20.21875" y="127.176758"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="127.176758"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="20.21875" y="73.875977"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="73.875977"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 230.859375 L 35.152344 230.859375 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 177.558594 L 35.152344 177.558594 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 124.261719 L 35.152344 124.261719 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 70.960938 L 35.152344 70.960938 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="20.21875" y="468.700195"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="468.700195"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="20.21875" y="415.399414"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="415.399414"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="20.21875" y="362.102539"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="362.102539"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="20.21875" y="308.801758"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="308.801758"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 465.785156 L 35.152344 465.785156 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 412.484375 L 35.152344 412.484375 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 359.1875 L 35.152344 359.1875 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 305.886719 L 35.152344 305.886719 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph1-1" x="224.875" y="494.538086"/>
-  <use xlink:href="#glyph1-2" x="230.875" y="494.538086"/>
-  <use xlink:href="#glyph1-3" x="233.875" y="494.538086"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph2-1" x="13.499023" y="256.046875"/>
-  <use xlink:href="#glyph2-2" x="13.499023" y="250.046875"/>
-  <use xlink:href="#glyph2-3" x="13.499023" y="242.046875"/>
-</g>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;" d="M 439.5625 295.328125 L 498.519531 295.328125 L 498.519531 197.769531 L 439.5625 197.769531 Z M 439.5625 295.328125 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph1-4" x="445.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-5" x="448.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-1" x="454.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-2" x="460.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-6" x="463.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-7" x="469.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-8" x="473.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-1" x="477.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-3" x="482.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-9" x="487.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-10" x="489.042969" y="212.768555"/>
-</g>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 229.367188 C 455.636719 231.972656 451.726562 231.972656 451.726562 229.367188 C 451.726562 226.761719 455.636719 226.761719 455.636719 229.367188 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 229.367188 L 460.59375 229.367188 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 246.648438 C 455.636719 249.253906 451.726562 249.253906 451.726562 246.648438 C 451.726562 244.042969 455.636719 244.042969 455.636719 246.648438 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 246.648438 L 460.59375 246.648438 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 263.925781 C 455.636719 266.535156 451.726562 266.535156 451.726562 263.925781 C 451.726562 261.320312 455.636719 261.320312 455.636719 263.925781 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 263.925781 L 460.59375 263.925781 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 281.207031 C 455.636719 283.8125 451.726562 283.8125 451.726562 281.207031 C 451.726562 278.601562 455.636719 278.601562 455.636719 281.207031 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 281.207031 L 460.59375 281.207031 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="467.800781" y="232.282227"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-4" x="467.800781" y="249.563477"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-1" x="467.800781" y="266.84082"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-2" x="467.800781" y="284.12207"/>
-</g>
-</g>
-</svg>
-
-```
-
-We may also [generate](https://scicloj.github.io/clojisr/doc/clojisr/v1/codegen-test/) the R code from a Clojure form and pass Clojure data to R, but for now, we are simply using R code using an R dataset.
-
-We are using the `mpg` dataset, which is part of the `ggplot` package.
-
-::: {.sourceClojure}
-```clojure
-(-> "mpg"
-    r
-    r->clj)
-```
-:::
-
-_unnamed [234 11]:
-
-| :manufacturer |     :model | :displ | :year | :cyl |     :trans | :drv | :cty | :hwy | :fl |     :class |
-|---------------|------------|-------:|------:|-----:|------------|------|-----:|-----:|-----|------------|
-|          audi |         a4 |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    compact |
-|          audi |         a4 |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    compact |
-|          audi |         a4 |    2.0 |  2008 |    4 | manual(m6) |    f |   20 |   31 |   p |    compact |
-|          audi |         a4 |    2.0 |  2008 |    4 |   auto(av) |    f |   21 |   30 |   p |    compact |
-|          audi |         a4 |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    compact |
-|          audi |         a4 |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    compact |
-|          audi |         a4 |    3.1 |  2008 |    6 |   auto(av) |    f |   18 |   27 |   p |    compact |
-|          audi | a4 quattro |    1.8 |  1999 |    4 | manual(m5) |    4 |   18 |   26 |   p |    compact |
-|          audi | a4 quattro |    1.8 |  1999 |    4 |   auto(l5) |    4 |   16 |   25 |   p |    compact |
-|          audi | a4 quattro |    2.0 |  2008 |    4 | manual(m6) |    4 |   20 |   28 |   p |    compact |
-|           ... |        ... |    ... |   ... |  ... |        ... |  ... |  ... |  ... | ... |        ... |
-|    volkswagen | new beetle |    2.0 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   r | subcompact |
-|    volkswagen | new beetle |    2.0 |  1999 |    4 |   auto(l4) |    f |   19 |   26 |   r | subcompact |
-|    volkswagen | new beetle |    2.5 |  2008 |    5 | manual(m5) |    f |   20 |   28 |   r | subcompact |
-|    volkswagen | new beetle |    2.5 |  2008 |    5 |   auto(s6) |    f |   20 |   29 |   r | subcompact |
-|    volkswagen |     passat |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    midsize |
-|    volkswagen |     passat |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    midsize |
-|    volkswagen |     passat |    2.0 |  2008 |    4 |   auto(s6) |    f |   19 |   28 |   p |    midsize |
-|    volkswagen |     passat |    2.0 |  2008 |    4 | manual(m6) |    f |   21 |   29 |   p |    midsize |
-|    volkswagen |     passat |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    midsize |
-|    volkswagen |     passat |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    midsize |
-|    volkswagen |     passat |    3.6 |  2008 |    6 |   auto(s6) |    f |   17 |   26 |   p |    midsize |
-
-## Representing plots as Clojure data
-
-A ggplot object is an R list of [ggproto](https://bookdown.dongzhuoer.com/hadley/ggplot2-book/introducing-ggproto) objects. We recursively unwrap this structure and convert it to Clojure.
-
-::: {.sourceClojure}
-```clojure
-(defn ggplot->clj
-  ([r-obj]
-   (ggplot->clj r-obj {} []))
-  ([r-obj
-    {:as options
-     :keys [avoid]
-     :or {avoid #{"plot_env"}}}
-    path]
-   #_(prn path)
-   (let [relevant-names (some->> r-obj
-                                 r.base/names
-                                 r->clj
-                                 (filter (complement avoid)))]
-     (cond
-       ;;
-       ;; a named list or a ggproto object
-       (seq relevant-names) (->> relevant-names
-                                 (map (fn [nam]
-                                        [(keyword nam) (-> r-obj
-                                                           (r$ nam)
-                                                           (ggplot->clj options
-                                                                        (conj path nam)))]))
-                                 (into {}))
-       ;;
-       ;; a ggproto method
-       (-> r-obj
-           r.base/class
-           r->clj
-           first
-           (= "ggproto_method"))
-       :ggproto-method
-       ;;
-       ;; an unnamed list
-       (-> r-obj
-           r.base/is-list
-           r->clj
-           first)
-       (-> r-obj
-           r.base/length
-           r->clj
-           first
-           range
-           (->> (mapv (fn [i]
-                        (-> r-obj
-                            (r/brabra (inc i))
-                            (ggplot->clj options
-                                         (conj path [i])))))))
-       ;;
-       (r.base/is-atomic r-obj) (try (r->clj r-obj)
-                                     (catch Exception e
-                                       (-> r-obj println with-out-str)))
-       :else r-obj))))
-```
-:::
-
-In the conversion, we avoid some big parts of the structure, e.g., the `"plot_env"` member. We also do no report the toplevel `"data"` member, which is simply the dataset.
-
-For example:
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy))
-         + geom_point())"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-## Exlploring a few plots
-
-Let us explore and compare a few plots this way:
-
-::: {.sourceClojure}
-```clojure
-(defn h3 [title] (kind/hiccup [:h3 title]))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn h4 [title] (kind/hiccup [:h4 title]))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn ggplot-summary
-  ([title r-code]
-   (ggplot-summary r-code))
-  ([title r-code prev-clj-to-compare]
-   (let [plot (r r-code)
-         clj (-> plot
-                 ggplot->clj
-                 (dissoc :data))]
-     {:title title
-      :r-code r-code
-      :image (plotting/plot->buffered-image plot)
-      :clj clj
-      :diff (when prev-clj-to-compare
-              (-> prev-clj-to-compare
-                  (editscript/diff clj)
-                  pp/pprint
-                  with-out-str
-                  (str/replace #": " ":_ ")
-                  read-string))})))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn view-summary [{:keys [title r-code image clj diff]}]
-  (kind/fragment
-   [(h3 title)
-    (h4 "R code")
-    (kind/md
-     (format "\n```\n%s\n```\n"
-             r-code))
-    (h4 "plot")
-    image
-    (h4 "clj data")
-    clj
-    (when diff
-      (kind/fragment
-       [(h4 "clj diff with previous")
-        diff]))]))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(->> [;;
-      ["A scatterplot"
-       "(ggplot(mpg, aes(cty, hwy))
-         + geom_point())"]
-      ;;
-      ["A scatterplot with colours"
-       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())"]
-      ;;
-      ["A scatterplot with colours and smoothing"
-       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\"))"]
-      ;;
-      ["A scatterplot with colours, smoothing, and facets"
-       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))"]]
-     (reductions (fn [prev-summary [title r-code]]
-                   (ggplot-summary title
-                                   r-code
-                                   (:clj prev-summary)))
-                 nil)
-     rest
-     (map view-summary)
-     kind/fragment)
-```
-:::
-
-```{=html}
-<h3>A scatterplot</h3>
-```
-
-```{=html}
-<h4>R code</h4>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy))
-         + geom_point())
-```
-
-```{=html}
-<h4>plot</h4>
-```
-
-```{=html}
-<img src="repesenting_files/0.png" style="width:100%;" />
-```
-
-```{=html}
-<h4>clj data</h4>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-```{=html}
-<h3>A scatterplot with colours</h3>
-```
-
-```{=html}
-<h4>R code</h4>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())
-```
-
-```{=html}
-<h4>plot</h4>
-```
-
-```{=html}
-<img src="repesenting_files/1.png" style="width:100%;" />
-```
-
-```{=html}
-<h4>clj data</h4>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-```{=html}
-<h4>clj diff with previous</h4>
-```
-
-::: {.printedClojure}
-```clojure
-[[[:mapping :colour] :+ [~[factor cyl]]]
- [[:labels :colour] :+ ["factor(cyl)"]]]
-
-```
-:::
-
-```{=html}
-<h3>A scatterplot with colours and smoothing</h3>
-```
-
-```{=html}
-<h4>R code</h4>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method="lm"))
-```
-
-```{=html}
-<h4>plot</h4>
-```
-
-```{=html}
-<img src="repesenting_files/2.png" style="width:100%;" />
-```
-
-```{=html}
-<h4>clj data</h4>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}
-  {:aes_params [],
-   :stat
-   {:extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x" "y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_params :ggproto-method,
-    :super :ggproto-method,
-    :draw_key :ggproto-method,
-    :extra_params ["na.rm" "orientation"],
-    :required_aes ["x" "y"],
-    :draw_group :ggproto-method,
-    :optional_aes ["ymin" "ymax"],
-    :rename_size [true],
-    :setup_data :ggproto-method,
-    :default_aes
-    {:colour ["#3366FF"],
-     :fill ["grey60"],
-     :linewidth [1.0],
-     :linetype [1.0],
-     :weight [1.0],
-     :alpha [0.4]}},
-   :stat_params
-   {:na.rm [false],
-    :method ["lm"],
-    :n [80.0],
-    :orientation [nil],
-    :level [0.95],
-    :fullrange [false],
-    :se [true],
-    :formula nil,
-    :method.args [],
-    :span [0.75]},
-   :constructor {: nil, :method ["lm"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-```{=html}
-<h4>clj diff with previous</h4>
-```
-
-::: {.printedClojure}
-```clojure
-[[[:layers 1]
-  :+
-  {:aes_params [],
-   :stat
-   {:extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x" "y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_params :ggproto-method,
-    :super :ggproto-method,
-    :draw_key :ggproto-method,
-    :extra_params ["na.rm" "orientation"],
-    :required_aes ["x" "y"],
-    :draw_group :ggproto-method,
-    :optional_aes ["ymin" "ymax"],
-    :rename_size [true],
-    :setup_data :ggproto-method,
-    :default_aes
-    {:colour ["#3366FF"],
-     :fill ["grey60"],
-     :linewidth [1.0],
-     :linetype [1.0],
-     :weight [1.0],
-     :alpha [0.4]}},
-   :stat_params
-   {:na.rm [false],
-    :method ["lm"],
-    :n [80.0],
-    :orientation [nil],
-    :level [0.95],
-    :fullrange [false],
-    :se [true],
-    :formula nil,
-    :method.args [],
-    :span [0.75]},
-   :constructor {:_ nil, :method ["lm"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}]]
-
-```
-:::
-
-```{=html}
-<h3>A scatterplot with colours, smoothing, and facets</h3>
-```
-
-```{=html}
-<h4>R code</h4>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method="lm")
-         + facet_wrap(~cyl))
-```
-
-```{=html}
-<h4>plot</h4>
-```
-
-```{=html}
-<img src="repesenting_files/3.png" style="width:100%;" />
-```
-
-```{=html}
-<h4>clj data</h4>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}
-  {:aes_params [],
-   :stat
-   {:extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x" "y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_params :ggproto-method,
-    :super :ggproto-method,
-    :draw_key :ggproto-method,
-    :extra_params ["na.rm" "orientation"],
-    :required_aes ["x" "y"],
-    :draw_group :ggproto-method,
-    :optional_aes ["ymin" "ymax"],
-    :rename_size [true],
-    :setup_data :ggproto-method,
-    :default_aes
-    {:colour ["#3366FF"],
-     :fill ["grey60"],
-     :linewidth [1.0],
-     :linetype [1.0],
-     :weight [1.0],
-     :alpha [0.4]}},
-   :stat_params
-   {:na.rm [false],
-    :method ["lm"],
-    :n [80.0],
-    :orientation [nil],
-    :level [0.95],
-    :fullrange [false],
-    :se [true],
-    :formula nil,
-    :method.args [],
-    :span [0.75]},
-   :constructor {: nil, :method ["lm"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet
- {:params
-  {:dir ["h"],
-   :nrow nil,
-   :as.table [true],
-   :free {:x [false], :y [false]},
-   :drop [true],
-   :strip.position ["top"],
-   :ncol nil,
-   :facets {:cyl [~ cyl]},
-   :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55b95a21db80&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
-  :shrink [true],
-  :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-```{=html}
-<h4>clj diff with previous</h4>
-```
-
-::: {.printedClojure}
-```clojure
-[[[:facet :params]
-  :+
-  {:dir ["h"],
-   :nrow nil,
-   :as.table [true],
-   :free {:x [false], :y [false]},
-   :drop [true],
-   :strip.position ["top"],
-   :ncol nil,
-   :facets {:cyl [~cyl]},
-   :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55b95a21db80&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
-
-```
-:::
-
-## Exploring
+            [representing]))
+```
+:::
+
+# Draft explorations
 
@@
     r
-    ggplot->clj
+    representing/ggplot->clj
     (dissoc :data))
@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x55b9566f0140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x558a0f256140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x55b9566f0140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x558a0f256140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55b95a64c498&gt;\n&lt;environment: 0x55b9649d1458&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x558a12881bc0&gt;\n&lt;environment: 0x558a16e97e18&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55b95a64fe78&gt;\n&lt;environment: 0x55b9649d12d0&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558a1288adb0&gt;\n&lt;environment: 0x558a16e97fd8&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55b95a6591f0&gt;\n&lt;environment: 0x55b9649d1180&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558a1288dbf8&gt;\n&lt;environment: 0x558a16e98128&gt;\n",
      :domain [##-Inf ##Inf]},
@@
 ```{=html}
-<img src="repesenting_files/4.png" style="width:100%;" />
+<img src="draft_files/0.png" style="width:100%;" />
 ```
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55b95f192f70&gt;\n&lt;environment: 0x55b95f193750&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x558a1d274598&gt;\n&lt;environment: 0x558a1a925bb0&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x55b95f193130&gt;\n&lt;environment: 0x55b95f193750&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x558a1d274448&gt;\n&lt;environment: 0x558a1a925bb0&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55b95f18b830&gt;\n&lt;environment: 0x55b95f18ae80&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x558a1d27de98&gt;\n&lt;environment: 0x558a1d468db0&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55b95a64fe78&gt;\n&lt;environment: 0x55b95f186e88&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558a1288adb0&gt;\n&lt;environment: 0x558a1d5a9ff0&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55b95a6591f0&gt;\n&lt;environment: 0x55b95f186fd8&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558a1288dbf8&gt;\n&lt;environment: 0x558a1d5aa1b0&gt;\n",
      :domain [1.0E-100 ##Inf]},
@@
 ```{=html}
-<img src="repesenting_files/5.png" style="width:100%;" />
+<img src="draft_files/1.png" style="width:100%;" />
 ```
@@
 ```{=html}
-<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/representing.clj">projects/datavis/ggplot/notebooks/representing.clj</a></small></small></pre></div>
-```
+<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/draft.clj">projects/datavis/ggplot/notebooks/draft.clj</a></small></small></pre></div>
+```

### 2024-02-24 docs/projects/datavis/ggplot/representing.qmd
ggplot - rerendered

--- 2024-02-24 docs/projects/datavis/ggplot/repesenting.qmd
@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: repesenting.html}
+  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: representing.html}
 code-block-background: true
@@
 </style>
-<script src="repesenting_files/md-default6.js" type="text/javascript"></script><script src="repesenting_files/md-default7.js" type="text/javascript"></script>
+<script src="representing_files/md-default0.js" type="text/javascript"></script><script src="representing_files/md-default1.js" type="text/javascript"></script>
 
@@
 
-## Setup
-
-We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.
-
 ::: {.sourceClojure}
 ```clojure
-(ns repesenting
+(ns representing
   (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
@@
 :::
-
-Loading ggplot2:
 
@@
 
-Requireing the base R library as a Clojure namespace:
-
 ::: {.sourceClojure}
@@
 
-## An example plot
-
-Here is how we may generate and display a plot:
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))"
-    r
-    plotting/plot->svg
-    kind/html)
-```
-:::
-
-```{=html}
-<?xml version="1.0" encoding="UTF-8"?>
-<svg xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink" width="504pt" height="504pt" viewBox="0 0 504 504" version="1.1">
-<defs>
-<g>
-<symbol overflow="visible" id="glyph0-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph0-1">
-<path style="stroke:none;" d="M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-2">
-<path style="stroke:none;" d="M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-3">
-<path style="stroke:none;" d="M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-4">
-<path style="stroke:none;" d="M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-5">
-<path style="stroke:none;" d="M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-6">
-<path style="stroke:none;" d="M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-7">
-<path style="stroke:none;" d="M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph0-8">
-<path style="stroke:none;" d="M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph1-1">
-<path style="stroke:none;" d="M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-2">
-<path style="stroke:none;" d="M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-3">
-<path style="stroke:none;" d="M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-4">
-<path style="stroke:none;" d="M 2.84375 -5.765625 L 1.875 -5.765625 L 1.875 -6.671875 C 1.875 -7.046875 2.09375 -7.25 2.515625 -7.25 C 2.59375 -7.25 2.625 -7.25 2.84375 -7.234375 L 2.84375 -8 C 2.625 -8.046875 2.515625 -8.046875 2.328125 -8.046875 C 1.46875 -8.046875 0.96875 -7.5625 0.96875 -6.75 L 0.96875 -5.765625 L 0.203125 -5.765625 L 0.203125 -5.015625 L 0.96875 -5.015625 L 0.96875 0 L 1.875 0 L 1.875 -5.015625 L 2.84375 -5.015625 Z M 2.84375 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-5">
-<path style="stroke:none;" d="M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-6">
-<path style="stroke:none;" d="M 2.984375 -5.921875 C 1.359375 -5.921875 0.390625 -4.78125 0.390625 -2.84375 C 0.390625 -0.890625 1.359375 0.25 3 0.25 C 4.625 0.25 5.609375 -0.90625 5.609375 -2.796875 C 5.609375 -4.796875 4.65625 -5.921875 2.984375 -5.921875 Z M 3 -5.078125 C 4.03125 -5.078125 4.65625 -4.234375 4.65625 -2.8125 C 4.65625 -1.4375 4.015625 -0.59375 3 -0.59375 C 1.984375 -0.59375 1.359375 -1.4375 1.359375 -2.84375 C 1.359375 -4.234375 1.984375 -5.078125 3 -5.078125 Z M 3 -5.078125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-7">
-<path style="stroke:none;" d="M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-8">
-<path style="stroke:none;" d="M 2.59375 -8.015625 C 1.5 -6.578125 0.796875 -4.578125 0.796875 -2.84375 C 0.796875 -1.109375 1.5 0.890625 2.59375 2.328125 L 3.203125 2.328125 C 2.234375 0.765625 1.6875 -1.09375 1.6875 -2.84375 C 1.6875 -4.59375 2.234375 -6.453125 3.203125 -8.015625 Z M 2.59375 -8.015625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-9">
-<path style="stroke:none;" d="M 1.671875 -8.015625 L 0.75 -8.015625 L 0.75 0 L 1.671875 0 Z M 1.671875 -8.015625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph1-10">
-<path style="stroke:none;" d="M 1.015625 2.328125 C 2.125 0.890625 2.8125 -1.109375 2.8125 -2.84375 C 2.8125 -4.578125 2.125 -6.578125 1.015625 -8.015625 L 0.421875 -8.015625 C 1.390625 -6.453125 1.921875 -4.59375 1.921875 -2.84375 C 1.921875 -1.09375 1.390625 0.765625 0.421875 2.328125 Z M 1.015625 2.328125 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-0">
-<path style="stroke:none;" d=""/>
-</symbol>
-<symbol overflow="visible" id="glyph2-1">
-<path style="stroke:none;" d="M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-2">
-<path style="stroke:none;" d="M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 "/>
-</symbol>
-<symbol overflow="visible" id="glyph2-3">
-<path style="stroke:none;" d="M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 "/>
-</symbol>
-</g>
-<clipPath id="clip1">
-  <path d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 234.925781 L 35.152344 234.925781 Z M 35.152344 23.246094 "/>
-</clipPath>
-<clipPath id="clip2">
-  <path d="M 35.152344 203 L 229.136719 203 L 229.136719 205 L 35.152344 205 Z M 35.152344 203 "/>
-</clipPath>
-<clipPath id="clip3">
-  <path d="M 35.152344 150 L 229.136719 150 L 229.136719 152 L 35.152344 152 Z M 35.152344 150 "/>
-</clipPath>
-<clipPath id="clip4">
-  <path d="M 35.152344 97 L 229.136719 97 L 229.136719 98 L 35.152344 98 Z M 35.152344 97 "/>
-</clipPath>
-<clipPath id="clip5">
-  <path d="M 35.152344 44 L 229.136719 44 L 229.136719 45 L 35.152344 45 Z M 35.152344 44 "/>
-</clipPath>
-<clipPath id="clip6">
-  <path d="M 67 23.246094 L 68 23.246094 L 68 234.925781 L 67 234.925781 Z M 67 23.246094 "/>
-</clipPath>
-<clipPath id="clip7">
-  <path d="M 101 23.246094 L 102 23.246094 L 102 234.925781 L 101 234.925781 Z M 101 23.246094 "/>
-</clipPath>
-<clipPath id="clip8">
-  <path d="M 135 23.246094 L 136 23.246094 L 136 234.925781 L 135 234.925781 Z M 135 23.246094 "/>
-</clipPath>
-<clipPath id="clip9">
-  <path d="M 169 23.246094 L 170 23.246094 L 170 234.925781 L 169 234.925781 Z M 169 23.246094 "/>
-</clipPath>
-<clipPath id="clip10">
-  <path d="M 203 23.246094 L 204 23.246094 L 204 234.925781 L 203 234.925781 Z M 203 23.246094 "/>
-</clipPath>
-<clipPath id="clip11">
-  <path d="M 35.152344 230 L 229.136719 230 L 229.136719 232 L 35.152344 232 Z M 35.152344 230 "/>
-</clipPath>
-<clipPath id="clip12">
-  <path d="M 35.152344 177 L 229.136719 177 L 229.136719 179 L 35.152344 179 Z M 35.152344 177 "/>
-</clipPath>
-<clipPath id="clip13">
-  <path d="M 35.152344 123 L 229.136719 123 L 229.136719 125 L 35.152344 125 Z M 35.152344 123 "/>
-</clipPath>
-<clipPath id="clip14">
-  <path d="M 35.152344 70 L 229.136719 70 L 229.136719 72 L 35.152344 72 Z M 35.152344 70 "/>
-</clipPath>
-<clipPath id="clip15">
-  <path d="M 50 23.246094 L 52 23.246094 L 52 234.925781 L 50 234.925781 Z M 50 23.246094 "/>
-</clipPath>
-<clipPath id="clip16">
-  <path d="M 84 23.246094 L 86 23.246094 L 86 234.925781 L 84 234.925781 Z M 84 23.246094 "/>
-</clipPath>
-<clipPath id="clip17">
-  <path d="M 118 23.246094 L 120 23.246094 L 120 234.925781 L 118 234.925781 Z M 118 23.246094 "/>
-</clipPath>
-<clipPath id="clip18">
-  <path d="M 151 23.246094 L 154 23.246094 L 154 234.925781 L 151 234.925781 Z M 151 23.246094 "/>
-</clipPath>
-<clipPath id="clip19">
-  <path d="M 185 23.246094 L 187 23.246094 L 187 234.925781 L 185 234.925781 Z M 185 23.246094 "/>
-</clipPath>
-<clipPath id="clip20">
-  <path d="M 219 23.246094 L 221 23.246094 L 221 234.925781 L 219 234.925781 Z M 219 23.246094 "/>
-</clipPath>
-<clipPath id="clip21">
-  <path d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 469.851562 L 35.152344 469.851562 Z M 35.152344 258.171875 "/>
-</clipPath>
-<clipPath id="clip22">
-  <path d="M 35.152344 438 L 229.136719 438 L 229.136719 440 L 35.152344 440 Z M 35.152344 438 "/>
-</clipPath>
-<clipPath id="clip23">
-  <path d="M 35.152344 385 L 229.136719 385 L 229.136719 387 L 35.152344 387 Z M 35.152344 385 "/>
-</clipPath>
-<clipPath id="clip24">
-  <path d="M 35.152344 332 L 229.136719 332 L 229.136719 333 L 35.152344 333 Z M 35.152344 332 "/>
-</clipPath>
-<clipPath id="clip25">
-  <path d="M 35.152344 278 L 229.136719 278 L 229.136719 280 L 35.152344 280 Z M 35.152344 278 "/>
-</clipPath>
-<clipPath id="clip26">
-  <path d="M 67 258.171875 L 68 258.171875 L 68 469.851562 L 67 469.851562 Z M 67 258.171875 "/>
-</clipPath>
-<clipPath id="clip27">
-  <path d="M 101 258.171875 L 102 258.171875 L 102 469.851562 L 101 469.851562 Z M 101 258.171875 "/>
-</clipPath>
-<clipPath id="clip28">
-  <path d="M 135 258.171875 L 136 258.171875 L 136 469.851562 L 135 469.851562 Z M 135 258.171875 "/>
-</clipPath>
-<clipPath id="clip29">
-  <path d="M 169 258.171875 L 170 258.171875 L 170 469.851562 L 169 469.851562 Z M 169 258.171875 "/>
-</clipPath>
-<clipPath id="clip30">
-  <path d="M 203 258.171875 L 204 258.171875 L 204 469.851562 L 203 469.851562 Z M 203 258.171875 "/>
-</clipPath>
-<clipPath id="clip31">
-  <path d="M 35.152344 465 L 229.136719 465 L 229.136719 467 L 35.152344 467 Z M 35.152344 465 "/>
-</clipPath>
-<clipPath id="clip32">
-  <path d="M 35.152344 411 L 229.136719 411 L 229.136719 414 L 35.152344 414 Z M 35.152344 411 "/>
-</clipPath>
-<clipPath id="clip33">
-  <path d="M 35.152344 358 L 229.136719 358 L 229.136719 360 L 35.152344 360 Z M 35.152344 358 "/>
-</clipPath>
-<clipPath id="clip34">
-  <path d="M 35.152344 305 L 229.136719 305 L 229.136719 307 L 35.152344 307 Z M 35.152344 305 "/>
-</clipPath>
-<clipPath id="clip35">
-  <path d="M 50 258.171875 L 52 258.171875 L 52 469.851562 L 50 469.851562 Z M 50 258.171875 "/>
-</clipPath>
-<clipPath id="clip36">
-  <path d="M 84 258.171875 L 86 258.171875 L 86 469.851562 L 84 469.851562 Z M 84 258.171875 "/>
-</clipPath>
-<clipPath id="clip37">
-  <path d="M 118 258.171875 L 120 258.171875 L 120 469.851562 L 118 469.851562 Z M 118 258.171875 "/>
-</clipPath>
-<clipPath id="clip38">
-  <path d="M 151 258.171875 L 154 258.171875 L 154 469.851562 L 151 469.851562 Z M 151 258.171875 "/>
-</clipPath>
-<clipPath id="clip39">
-  <path d="M 185 258.171875 L 187 258.171875 L 187 469.851562 L 185 469.851562 Z M 185 258.171875 "/>
-</clipPath>
-<clipPath id="clip40">
-  <path d="M 219 258.171875 L 221 258.171875 L 221 469.851562 L 219 469.851562 Z M 219 258.171875 "/>
-</clipPath>
-<clipPath id="clip41">
-  <path d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 234.925781 L 234.617188 234.925781 Z M 234.617188 23.246094 "/>
-</clipPath>
-<clipPath id="clip42">
-  <path d="M 234.617188 203 L 428.601562 203 L 428.601562 205 L 234.617188 205 Z M 234.617188 203 "/>
-</clipPath>
-<clipPath id="clip43">
-  <path d="M 234.617188 150 L 428.601562 150 L 428.601562 152 L 234.617188 152 Z M 234.617188 150 "/>
-</clipPath>
-<clipPath id="clip44">
-  <path d="M 234.617188 97 L 428.601562 97 L 428.601562 98 L 234.617188 98 Z M 234.617188 97 "/>
-</clipPath>
-<clipPath id="clip45">
-  <path d="M 234.617188 44 L 428.601562 44 L 428.601562 45 L 234.617188 45 Z M 234.617188 44 "/>
-</clipPath>
-<clipPath id="clip46">
-  <path d="M 266 23.246094 L 268 23.246094 L 268 234.925781 L 266 234.925781 Z M 266 23.246094 "/>
-</clipPath>
-<clipPath id="clip47">
-  <path d="M 300 23.246094 L 302 23.246094 L 302 234.925781 L 300 234.925781 Z M 300 23.246094 "/>
-</clipPath>
-<clipPath id="clip48">
-  <path d="M 334 23.246094 L 336 23.246094 L 336 234.925781 L 334 234.925781 Z M 334 23.246094 "/>
-</clipPath>
-<clipPath id="clip49">
-  <path d="M 368 23.246094 L 370 23.246094 L 370 234.925781 L 368 234.925781 Z M 368 23.246094 "/>
-</clipPath>
-<clipPath id="clip50">
-  <path d="M 402 23.246094 L 404 23.246094 L 404 234.925781 L 402 234.925781 Z M 402 23.246094 "/>
-</clipPath>
-<clipPath id="clip51">
-  <path d="M 234.617188 230 L 428.601562 230 L 428.601562 232 L 234.617188 232 Z M 234.617188 230 "/>
-</clipPath>
-<clipPath id="clip52">
-  <path d="M 234.617188 177 L 428.601562 177 L 428.601562 179 L 234.617188 179 Z M 234.617188 177 "/>
-</clipPath>
-<clipPath id="clip53">
-  <path d="M 234.617188 123 L 428.601562 123 L 428.601562 125 L 234.617188 125 Z M 234.617188 123 "/>
-</clipPath>
-<clipPath id="clip54">
-  <path d="M 234.617188 70 L 428.601562 70 L 428.601562 72 L 234.617188 72 Z M 234.617188 70 "/>
-</clipPath>
-<clipPath id="clip55">
-  <path d="M 249 23.246094 L 251 23.246094 L 251 234.925781 L 249 234.925781 Z M 249 23.246094 "/>
-</clipPath>
-<clipPath id="clip56">
-  <path d="M 283 23.246094 L 285 23.246094 L 285 234.925781 L 283 234.925781 Z M 283 23.246094 "/>
-</clipPath>
-<clipPath id="clip57">
-  <path d="M 317 23.246094 L 319 23.246094 L 319 234.925781 L 317 234.925781 Z M 317 23.246094 "/>
-</clipPath>
-<clipPath id="clip58">
-  <path d="M 351 23.246094 L 353 23.246094 L 353 234.925781 L 351 234.925781 Z M 351 23.246094 "/>
-</clipPath>
-<clipPath id="clip59">
-  <path d="M 385 23.246094 L 387 23.246094 L 387 234.925781 L 385 234.925781 Z M 385 23.246094 "/>
-</clipPath>
-<clipPath id="clip60">
-  <path d="M 419 23.246094 L 421 23.246094 L 421 234.925781 L 419 234.925781 Z M 419 23.246094 "/>
-</clipPath>
-<clipPath id="clip61">
-  <path d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 469.851562 L 234.617188 469.851562 Z M 234.617188 258.171875 "/>
-</clipPath>
-<clipPath id="clip62">
-  <path d="M 234.617188 438 L 428.601562 438 L 428.601562 440 L 234.617188 440 Z M 234.617188 438 "/>
-</clipPath>
-<clipPath id="clip63">
-  <path d="M 234.617188 385 L 428.601562 385 L 428.601562 387 L 234.617188 387 Z M 234.617188 385 "/>
-</clipPath>
-<clipPath id="clip64">
-  <path d="M 234.617188 332 L 428.601562 332 L 428.601562 333 L 234.617188 333 Z M 234.617188 332 "/>
-</clipPath>
-<clipPath id="clip65">
-  <path d="M 234.617188 278 L 428.601562 278 L 428.601562 280 L 234.617188 280 Z M 234.617188 278 "/>
-</clipPath>
-<clipPath id="clip66">
-  <path d="M 266 258.171875 L 268 258.171875 L 268 469.851562 L 266 469.851562 Z M 266 258.171875 "/>
-</clipPath>
-<clipPath id="clip67">
-  <path d="M 300 258.171875 L 302 258.171875 L 302 469.851562 L 300 469.851562 Z M 300 258.171875 "/>
-</clipPath>
-<clipPath id="clip68">
-  <path d="M 334 258.171875 L 336 258.171875 L 336 469.851562 L 334 469.851562 Z M 334 258.171875 "/>
-</clipPath>
-<clipPath id="clip69">
-  <path d="M 368 258.171875 L 370 258.171875 L 370 469.851562 L 368 469.851562 Z M 368 258.171875 "/>
-</clipPath>
-<clipPath id="clip70">
-  <path d="M 402 258.171875 L 404 258.171875 L 404 469.851562 L 402 469.851562 Z M 402 258.171875 "/>
-</clipPath>
-<clipPath id="clip71">
-  <path d="M 234.617188 465 L 428.601562 465 L 428.601562 467 L 234.617188 467 Z M 234.617188 465 "/>
-</clipPath>
-<clipPath id="clip72">
-  <path d="M 234.617188 411 L 428.601562 411 L 428.601562 414 L 234.617188 414 Z M 234.617188 411 "/>
-</clipPath>
-<clipPath id="clip73">
-  <path d="M 234.617188 358 L 428.601562 358 L 428.601562 360 L 234.617188 360 Z M 234.617188 358 "/>
-</clipPath>
-<clipPath id="clip74">
-  <path d="M 234.617188 305 L 428.601562 305 L 428.601562 307 L 234.617188 307 Z M 234.617188 305 "/>
-</clipPath>
-<clipPath id="clip75">
-  <path d="M 249 258.171875 L 251 258.171875 L 251 469.851562 L 249 469.851562 Z M 249 258.171875 "/>
-</clipPath>
-<clipPath id="clip76">
-  <path d="M 283 258.171875 L 285 258.171875 L 285 469.851562 L 283 469.851562 Z M 283 258.171875 "/>
-</clipPath>
-<clipPath id="clip77">
-  <path d="M 317 258.171875 L 319 258.171875 L 319 469.851562 L 317 469.851562 Z M 317 258.171875 "/>
-</clipPath>
-<clipPath id="clip78">
-  <path d="M 351 258.171875 L 353 258.171875 L 353 469.851562 L 351 469.851562 Z M 351 258.171875 "/>
-</clipPath>
-<clipPath id="clip79">
-  <path d="M 385 258.171875 L 387 258.171875 L 387 469.851562 L 385 469.851562 Z M 385 258.171875 "/>
-</clipPath>
-<clipPath id="clip80">
-  <path d="M 419 258.171875 L 421 258.171875 L 421 469.851562 L 419 469.851562 Z M 419 258.171875 "/>
-</clipPath>
-<clipPath id="clip81">
-  <path d="M 35.152344 240.402344 L 229.136719 240.402344 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 240.402344 "/>
-</clipPath>
-<clipPath id="clip82">
-  <path d="M 234.617188 240.402344 L 428.601562 240.402344 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 240.402344 "/>
-</clipPath>
-<clipPath id="clip83">
-  <path d="M 35.152344 5.480469 L 229.136719 5.480469 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 5.480469 "/>
-</clipPath>
-<clipPath id="clip84">
-  <path d="M 234.617188 5.480469 L 428.601562 5.480469 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 5.480469 "/>
-</clipPath>
-</defs>
-<g id="surface69">
-<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
-<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 "/>
-<g clip-path="url(#clip1)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 234.925781 L 229.136719 234.925781 L 229.136719 23.246094 L 35.152344 23.246094 Z M 35.152344 234.925781 "/>
-</g>
-<g clip-path="url(#clip2)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 204.210938 L 229.136719 204.210938 "/>
-</g>
-<g clip-path="url(#clip3)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 150.910156 L 229.136719 150.910156 "/>
-</g>
-<g clip-path="url(#clip4)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 97.613281 L 229.136719 97.613281 "/>
-</g>
-<g clip-path="url(#clip5)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 44.3125 L 229.136719 44.3125 "/>
-</g>
-<g clip-path="url(#clip6)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 234.925781 L 67.707031 23.246094 "/>
-</g>
-<g clip-path="url(#clip7)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 234.925781 L 101.621094 23.246094 "/>
-</g>
-<g clip-path="url(#clip8)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 234.925781 L 135.535156 23.246094 "/>
-</g>
-<g clip-path="url(#clip9)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 234.925781 L 169.449219 23.246094 "/>
-</g>
-<g clip-path="url(#clip10)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 234.925781 L 203.363281 23.246094 "/>
-</g>
-<g clip-path="url(#clip11)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 230.859375 L 229.136719 230.859375 "/>
-</g>
-<g clip-path="url(#clip12)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 177.558594 L 229.136719 177.558594 "/>
-</g>
-<g clip-path="url(#clip13)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 124.261719 L 229.136719 124.261719 "/>
-</g>
-<g clip-path="url(#clip14)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 70.960938 L 229.136719 70.960938 "/>
-</g>
-<g clip-path="url(#clip15)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 234.925781 L 50.75 23.246094 "/>
-</g>
-<g clip-path="url(#clip16)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 234.925781 L 84.664062 23.246094 "/>
-</g>
-<g clip-path="url(#clip17)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 234.925781 L 118.578125 23.246094 "/>
-</g>
-<g clip-path="url(#clip18)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 234.925781 L 152.492188 23.246094 "/>
-</g>
-<g clip-path="url(#clip19)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 234.925781 L 186.40625 23.246094 "/>
-</g>
-<g clip-path="url(#clip20)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 234.925781 L 220.320312 23.246094 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 118.933594 C 120.53125 121.539062 116.625 121.539062 116.625 118.933594 C 116.625 116.324219 120.53125 116.324219 120.53125 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 150.910156 C 93.402344 153.515625 89.492188 153.515625 89.492188 150.910156 C 89.492188 148.304688 93.402344 148.304688 93.402344 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 124.261719 C 134.097656 126.867188 130.1875 126.867188 130.1875 124.261719 C 130.1875 121.65625 134.097656 121.65625 134.097656 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 108.273438 C 174.796875 110.878906 170.886719 110.878906 170.886719 108.273438 C 170.886719 105.664062 174.796875 105.664062 174.796875 108.273438 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 113.601562 C 154.445312 116.207031 150.539062 116.207031 150.539062 113.601562 C 150.539062 110.996094 154.445312 110.996094 154.445312 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 129.589844 C 140.882812 132.199219 136.972656 132.199219 136.972656 129.589844 C 136.972656 126.984375 140.882812 126.984375 140.882812 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 113.601562 C 147.664062 116.207031 143.753906 116.207031 143.753906 113.601562 C 143.753906 110.996094 147.664062 110.996094 147.664062 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 102.941406 C 161.230469 105.546875 157.320312 105.546875 157.320312 102.941406 C 157.320312 100.335938 161.230469 100.335938 161.230469 102.941406 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 154.445312 92.28125 C 154.445312 94.890625 150.539062 94.890625 150.539062 92.28125 C 150.539062 89.675781 154.445312 89.675781 154.445312 92.28125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 92.28125 C 147.664062 94.890625 143.753906 94.890625 143.753906 92.28125 C 143.753906 89.675781 147.664062 89.675781 147.664062 92.28125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 145.582031 C 106.96875 148.1875 103.058594 148.1875 103.058594 145.582031 C 103.058594 142.976562 106.96875 142.976562 106.96875 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 140.25 C 106.96875 142.859375 103.058594 142.859375 103.058594 140.25 C 103.058594 137.644531 106.96875 137.644531 106.96875 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 124.261719 C 127.316406 126.867188 123.40625 126.867188 123.40625 124.261719 C 123.40625 121.65625 127.316406 121.65625 127.316406 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 129.589844 C 113.75 132.199219 109.839844 132.199219 109.839844 129.589844 C 109.839844 126.984375 113.75 126.984375 113.75 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 134.921875 C 120.53125 137.527344 116.625 137.527344 116.625 134.921875 C 116.625 132.316406 120.53125 132.316406 120.53125 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 140.25 C 113.75 142.859375 109.839844 142.859375 109.839844 140.25 C 109.839844 137.644531 113.75 137.644531 113.75 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 118.933594 C 140.882812 121.539062 136.972656 121.539062 136.972656 118.933594 C 136.972656 116.324219 140.882812 116.324219 140.882812 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 140.882812 113.601562 C 140.882812 116.207031 136.972656 116.207031 136.972656 113.601562 C 136.972656 110.996094 140.882812 110.996094 140.882812 113.601562 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 150.910156 C 106.96875 153.515625 103.058594 153.515625 103.058594 150.910156 C 103.058594 148.304688 106.96875 148.304688 106.96875 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 156.242188 C 106.96875 158.847656 103.058594 158.847656 103.058594 156.242188 C 103.058594 153.632812 106.96875 153.632812 106.96875 156.242188 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 145.582031 C 120.53125 148.1875 116.625 148.1875 116.625 145.582031 C 116.625 142.976562 120.53125 142.976562 120.53125 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 161.570312 C 106.96875 164.175781 103.058594 164.175781 103.058594 161.570312 C 103.058594 158.964844 106.96875 158.964844 106.96875 161.570312 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 145.582031 C 127.316406 148.1875 123.40625 148.1875 123.40625 145.582031 C 123.40625 142.976562 127.316406 142.976562 127.316406 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 150.910156 C 120.53125 153.515625 116.625 153.515625 116.625 150.910156 C 116.625 148.304688 120.53125 148.304688 120.53125 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 150.910156 C 113.75 153.515625 109.839844 153.515625 109.839844 150.910156 C 109.839844 148.304688 113.75 148.304688 113.75 150.910156 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 120.53125 140.25 C 120.53125 142.859375 116.625 142.859375 116.625 140.25 C 116.625 137.644531 120.53125 137.644531 120.53125 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 140.25 C 127.316406 142.859375 123.40625 142.859375 123.40625 140.25 C 123.40625 137.644531 127.316406 137.644531 127.316406 140.25 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 118.933594 C 127.316406 121.539062 123.40625 121.539062 123.40625 118.933594 C 123.40625 116.324219 127.316406 116.324219 127.316406 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 118.933594 C 134.097656 121.539062 130.1875 121.539062 130.1875 118.933594 C 130.1875 116.324219 134.097656 116.324219 134.097656 118.933594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 124.261719 C 147.664062 126.867188 143.753906 126.867188 143.753906 124.261719 C 143.753906 121.65625 147.664062 121.65625 147.664062 124.261719 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 147.664062 108.273438 C 147.664062 110.878906 143.753906 110.878906 143.753906 108.273438 C 143.753906 105.664062 147.664062 105.664062 147.664062 108.273438 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 174.796875 86.953125 C 174.796875 89.558594 170.886719 89.558594 170.886719 86.953125 C 170.886719 84.347656 174.796875 84.347656 174.796875 86.953125 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 161.230469 97.613281 C 161.230469 100.21875 157.320312 100.21875 157.320312 97.613281 C 157.320312 95.003906 161.230469 95.003906 161.230469 97.613281 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 177.558594 C 86.621094 180.167969 82.710938 180.167969 82.710938 177.558594 C 82.710938 174.953125 86.621094 174.953125 86.621094 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 177.558594 C 93.402344 180.167969 89.492188 180.167969 89.492188 177.558594 C 89.492188 174.953125 93.402344 174.953125 93.402344 177.558594 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 166.902344 C 100.183594 169.507812 96.273438 169.507812 96.273438 166.902344 C 96.273438 164.292969 100.183594 164.292969 100.183594 166.902344 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 208.707031 49.644531 C 208.707031 52.25 204.800781 52.25 204.800781 49.644531 C 204.800781 47.035156 208.707031 47.035156 208.707031 49.644531 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 134.097656 129.589844 C 134.097656 132.199219 130.1875 132.199219 130.1875 129.589844 C 130.1875 126.984375 134.097656 126.984375 134.097656 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 222.273438 49.644531 C 222.273438 52.25 218.363281 52.25 218.363281 49.644531 C 218.363281 47.035156 222.273438 47.035156 222.273438 49.644531 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 181.578125 65.632812 C 181.578125 68.238281 177.667969 68.238281 177.667969 65.632812 C 177.667969 63.027344 181.578125 63.027344 181.578125 65.632812 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 145.582031 C 113.75 148.1875 109.839844 148.1875 109.839844 145.582031 C 109.839844 142.976562 113.75 142.976562 113.75 145.582031 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 129.589844 C 106.96875 132.199219 103.058594 132.199219 103.058594 129.589844 C 103.058594 126.984375 106.96875 126.984375 106.96875 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 134.921875 C 113.75 137.527344 109.839844 137.527344 109.839844 134.921875 C 109.839844 132.316406 113.75 132.316406 113.75 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 127.316406 129.589844 C 127.316406 132.199219 123.40625 132.199219 123.40625 129.589844 C 123.40625 126.984375 127.316406 126.984375 127.316406 129.589844 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 84.664062 165.398438 L 86.382812 163.894531 L 88.097656 162.386719 L 91.535156 159.371094 L 93.25 157.859375 L 94.96875 156.347656 L 96.683594 154.832031 L 98.402344 153.3125 L 100.117188 151.792969 L 103.554688 148.738281 L 105.269531 147.207031 L 106.988281 145.671875 L 108.703125 144.128906 L 110.421875 142.582031 L 112.140625 141.027344 L 113.855469 139.46875 L 115.574219 137.902344 L 117.289062 136.328125 L 119.007812 134.742188 L 120.726562 133.148438 L 122.441406 131.546875 L 124.160156 129.933594 L 125.875 128.3125 L 127.59375 126.679688 L 129.308594 125.035156 L 131.027344 123.382812 L 132.746094 121.71875 L 134.460938 120.050781 L 136.179688 118.371094 L 137.894531 116.683594 L 139.613281 114.988281 L 141.332031 113.289062 L 143.046875 111.582031 L 144.765625 109.871094 L 146.480469 108.152344 L 148.199219 106.433594 L 149.917969 104.710938 L 151.632812 102.980469 L 153.351562 101.25 L 155.066406 99.515625 L 156.785156 97.78125 L 158.503906 96.042969 L 160.21875 94.300781 L 161.9375 92.558594 L 163.652344 90.816406 L 165.371094 89.070312 L 167.085938 87.324219 L 168.804688 85.578125 L 170.523438 83.828125 L 172.238281 82.078125 L 173.957031 80.328125 L 175.671875 78.574219 L 177.390625 76.824219 L 179.109375 75.070312 L 180.824219 73.316406 L 182.542969 71.5625 L 184.257812 69.804688 L 185.976562 68.050781 L 187.695312 66.292969 L 189.410156 64.539062 L 191.128906 62.78125 L 192.84375 61.023438 L 196.28125 57.507812 L 197.996094 55.75 L 199.714844 53.992188 L 201.429688 52.230469 L 203.148438 50.472656 L 204.863281 48.710938 L 206.582031 46.953125 L 208.300781 45.191406 L 210.015625 43.433594 L 211.734375 41.671875 L 213.449219 39.914062 L 216.886719 36.390625 L 218.601562 34.628906 L 220.320312 32.867188 L 220.320312 48.824219 L 218.601562 50.3125 L 216.886719 51.800781 L 215.167969 53.289062 L 213.449219 54.78125 L 211.734375 56.269531 L 210.015625 57.761719 L 208.300781 59.25 L 204.863281 62.234375 L 203.148438 63.722656 L 201.429688 65.214844 L 199.714844 66.707031 L 197.996094 68.199219 L 196.28125 69.691406 L 192.84375 72.675781 L 191.128906 74.167969 L 189.410156 75.664062 L 187.695312 77.15625 L 184.257812 80.148438 L 182.542969 81.640625 L 180.824219 83.136719 L 179.109375 84.636719 L 175.671875 87.628906 L 173.957031 89.128906 L 172.238281 90.628906 L 170.523438 92.128906 L 168.804688 93.632812 L 167.085938 95.132812 L 165.371094 96.636719 L 163.652344 98.144531 L 161.9375 99.648438 L 160.21875 101.160156 L 158.503906 102.667969 L 156.785156 104.179688 L 155.066406 105.695312 L 153.351562 107.210938 L 151.632812 108.730469 L 149.917969 110.253906 L 148.199219 111.78125 L 146.480469 113.3125 L 144.765625 114.84375 L 143.046875 116.382812 L 141.332031 117.929688 L 139.613281 119.476562 L 137.894531 121.035156 L 136.179688 122.597656 L 134.460938 124.167969 L 132.746094 125.75 L 131.027344 127.335938 L 129.308594 128.933594 L 127.59375 130.542969 L 125.875 132.160156 L 124.160156 133.789062 L 122.441406 135.425781 L 120.726562 137.074219 L 119.007812 138.730469 L 117.289062 140.398438 L 115.574219 142.074219 L 113.855469 143.757812 L 112.140625 145.449219 L 110.421875 147.144531 L 108.703125 148.847656 L 106.988281 150.558594 L 105.269531 152.273438 L 103.554688 153.988281 L 101.835938 155.710938 L 100.117188 157.4375 L 98.402344 159.167969 L 96.683594 160.902344 L 94.96875 162.636719 L 93.25 164.371094 L 91.535156 166.113281 L 89.816406 167.851562 L 88.097656 169.597656 L 86.382812 171.339844 L 84.664062 173.085938 Z M 84.664062 165.398438 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 169.242188 L 86.382812 167.617188 L 88.097656 165.992188 L 91.535156 162.742188 L 93.25 161.117188 L 94.96875 159.492188 L 96.683594 157.867188 L 98.402344 156.242188 L 100.117188 154.613281 L 103.554688 151.363281 L 105.269531 149.738281 L 106.988281 148.113281 L 108.703125 146.488281 L 112.140625 143.238281 L 113.855469 141.613281 L 115.574219 139.988281 L 117.289062 138.363281 L 120.726562 135.113281 L 122.441406 133.488281 L 124.160156 131.859375 L 125.875 130.234375 L 127.59375 128.609375 L 129.308594 126.984375 L 132.746094 123.734375 L 134.460938 122.109375 L 136.179688 120.484375 L 137.894531 118.859375 L 141.332031 115.609375 L 143.046875 113.984375 L 144.765625 112.359375 L 146.480469 110.734375 L 148.199219 109.105469 L 149.917969 107.480469 L 151.632812 105.855469 L 153.351562 104.230469 L 155.066406 102.605469 L 158.503906 99.355469 L 160.21875 97.730469 L 161.9375 96.105469 L 163.652344 94.480469 L 165.371094 92.855469 L 167.085938 91.230469 L 170.523438 87.980469 L 172.238281 86.351562 L 173.957031 84.726562 L 175.671875 83.101562 L 179.109375 79.851562 L 180.824219 78.226562 L 182.542969 76.601562 L 184.257812 74.976562 L 187.695312 71.726562 L 189.410156 70.101562 L 191.128906 68.476562 L 192.84375 66.851562 L 194.5625 65.222656 L 196.28125 63.597656 L 197.996094 61.972656 L 199.714844 60.347656 L 201.429688 58.722656 L 203.148438 57.097656 L 204.863281 55.472656 L 208.300781 52.222656 L 210.015625 50.597656 L 211.734375 48.972656 L 213.449219 47.347656 L 216.886719 44.097656 L 218.601562 42.46875 L 220.320312 40.84375 "/>
-<g clip-path="url(#clip21)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 469.847656 L 229.136719 469.847656 L 229.136719 258.167969 L 35.152344 258.167969 Z M 35.152344 469.847656 "/>
-</g>
-<g clip-path="url(#clip22)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 439.132812 L 229.136719 439.132812 "/>
-</g>
-<g clip-path="url(#clip23)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 385.835938 L 229.136719 385.835938 "/>
-</g>
-<g clip-path="url(#clip24)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 332.535156 L 229.136719 332.535156 "/>
-</g>
-<g clip-path="url(#clip25)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 279.238281 L 229.136719 279.238281 "/>
-</g>
-<g clip-path="url(#clip26)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.707031 469.847656 L 67.707031 258.171875 "/>
-</g>
-<g clip-path="url(#clip27)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 101.621094 469.847656 L 101.621094 258.171875 "/>
-</g>
-<g clip-path="url(#clip28)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 135.535156 469.847656 L 135.535156 258.171875 "/>
-</g>
-<g clip-path="url(#clip29)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 169.449219 469.847656 L 169.449219 258.171875 "/>
-</g>
-<g clip-path="url(#clip30)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 203.363281 469.847656 L 203.363281 258.171875 "/>
-</g>
-<g clip-path="url(#clip31)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 465.785156 L 229.136719 465.785156 "/>
-</g>
-<g clip-path="url(#clip32)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 412.484375 L 229.136719 412.484375 "/>
-</g>
-<g clip-path="url(#clip33)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 359.1875 L 229.136719 359.1875 "/>
-</g>
-<g clip-path="url(#clip34)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 305.886719 L 229.136719 305.886719 "/>
-</g>
-<g clip-path="url(#clip35)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 469.847656 L 50.75 258.171875 "/>
-</g>
-<g clip-path="url(#clip36)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 469.847656 L 84.664062 258.171875 "/>
-</g>
-<g clip-path="url(#clip37)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 469.847656 L 118.578125 258.171875 "/>
-</g>
-<g clip-path="url(#clip38)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 469.847656 L 152.492188 258.171875 "/>
-</g>
-<g clip-path="url(#clip39)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 469.847656 L 186.40625 258.171875 "/>
-</g>
-<g clip-path="url(#clip40)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 469.847656 L 220.320312 258.171875 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 385.835938 C 86.621094 388.441406 82.710938 388.441406 82.710938 385.835938 C 82.710938 383.230469 86.621094 383.230469 86.621094 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 391.164062 C 86.621094 393.773438 82.710938 393.773438 82.710938 391.164062 C 82.710938 388.558594 86.621094 388.558594 86.621094 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 385.835938 C 100.183594 388.441406 96.273438 388.441406 96.273438 385.835938 C 96.273438 383.230469 100.183594 383.230469 100.183594 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 364.515625 C 106.96875 367.121094 103.058594 367.121094 103.058594 364.515625 C 103.058594 361.910156 106.96875 361.910156 106.96875 364.515625 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 401.824219 C 93.402344 404.429688 89.492188 404.429688 89.492188 401.824219 C 89.492188 399.21875 93.402344 399.21875 93.402344 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 59.488281 428.472656 C 59.488281 431.082031 55.578125 431.082031 55.578125 428.472656 C 55.578125 425.867188 59.488281 425.867188 59.488281 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 401.824219 C 86.621094 404.429688 82.710938 404.429688 82.710938 401.824219 C 82.710938 399.21875 86.621094 399.21875 86.621094 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 407.15625 C 86.621094 409.761719 82.710938 409.761719 82.710938 407.15625 C 82.710938 404.546875 86.621094 404.546875 86.621094 407.15625 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 423.144531 C 79.835938 425.75 75.925781 425.75 75.925781 423.144531 C 75.925781 420.539062 79.835938 420.539062 79.835938 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 428.472656 C 73.054688 431.082031 69.144531 431.082031 69.144531 428.472656 C 69.144531 425.867188 73.054688 425.867188 73.054688 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 385.835938 C 106.96875 388.441406 103.058594 388.441406 103.058594 385.835938 C 103.058594 383.230469 106.96875 383.230469 106.96875 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 391.164062 C 93.402344 393.773438 89.492188 393.773438 89.492188 391.164062 C 89.492188 388.558594 93.402344 388.558594 93.402344 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 401.824219 C 100.183594 404.429688 96.273438 404.429688 96.273438 401.824219 C 96.273438 399.21875 100.183594 399.21875 100.183594 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 412.484375 C 86.621094 415.089844 82.710938 415.089844 82.710938 412.484375 C 82.710938 409.878906 86.621094 409.878906 86.621094 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 73.054688 417.816406 C 73.054688 420.421875 69.144531 420.421875 69.144531 417.816406 C 69.144531 415.207031 73.054688 415.207031 73.054688 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 375.175781 C 113.75 377.78125 109.839844 377.78125 109.839844 375.175781 C 109.839844 372.570312 113.75 372.570312 113.75 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 380.503906 C 113.75 383.113281 109.839844 383.113281 109.839844 380.503906 C 109.839844 377.898438 113.75 377.898438 113.75 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 385.835938 C 113.75 388.441406 109.839844 388.441406 109.839844 385.835938 C 109.839844 383.230469 113.75 383.230469 113.75 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 428.472656 C 79.835938 431.082031 75.925781 431.082031 75.925781 428.472656 C 75.925781 425.867188 79.835938 425.867188 79.835938 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 79.835938 412.484375 C 79.835938 415.089844 75.925781 415.089844 75.925781 412.484375 C 75.925781 409.878906 79.835938 409.878906 79.835938 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 375.175781 C 100.183594 377.78125 96.273438 377.78125 96.273438 375.175781 C 96.273438 372.570312 100.183594 372.570312 100.183594 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 369.847656 C 106.96875 372.453125 103.058594 372.453125 103.058594 369.847656 C 103.058594 367.238281 106.96875 367.238281 106.96875 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 113.75 369.847656 C 113.75 372.453125 109.839844 372.453125 109.839844 369.847656 C 109.839844 367.238281 113.75 367.238281 113.75 369.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 375.175781 C 106.96875 377.78125 103.058594 377.78125 103.058594 375.175781 C 103.058594 372.570312 106.96875 372.570312 106.96875 375.175781 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 428.472656 C 86.621094 431.082031 82.710938 431.082031 82.710938 428.472656 C 82.710938 425.867188 86.621094 425.867188 86.621094 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 417.816406 C 86.621094 420.421875 82.710938 420.421875 82.710938 417.816406 C 82.710938 415.207031 86.621094 415.207031 86.621094 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.621094 423.144531 C 86.621094 425.75 82.710938 425.75 82.710938 423.144531 C 82.710938 420.539062 86.621094 420.539062 86.621094 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 412.484375 C 93.402344 415.089844 89.492188 415.089844 89.492188 412.484375 C 89.492188 409.878906 93.402344 409.878906 93.402344 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 396.496094 C 93.402344 399.101562 89.492188 399.101562 89.492188 396.496094 C 89.492188 393.890625 93.402344 393.890625 93.402344 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 391.164062 C 100.183594 393.773438 96.273438 393.773438 96.273438 391.164062 C 96.273438 388.558594 100.183594 388.558594 100.183594 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 93.402344 380.503906 C 93.402344 383.113281 89.492188 383.113281 89.492188 380.503906 C 89.492188 377.898438 93.402344 377.898438 93.402344 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 106.96875 380.503906 C 106.96875 383.113281 103.058594 383.113281 103.058594 380.503906 C 103.058594 377.898438 106.96875 377.898438 106.96875 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.183594 380.503906 C 100.183594 383.113281 96.273438 383.113281 96.273438 380.503906 C 96.273438 377.898438 100.183594 377.898438 100.183594 380.503906 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 57.535156 440.144531 L 58.21875 439.300781 L 60.28125 436.769531 L 60.96875 435.921875 L 61.65625 435.078125 L 62.339844 434.234375 L 63.027344 433.386719 L 63.714844 432.542969 L 65.089844 430.847656 L 65.777344 430.003906 L 66.464844 429.15625 L 67.148438 428.308594 L 67.835938 427.457031 L 68.523438 426.609375 L 69.210938 425.757812 L 69.898438 424.910156 L 70.585938 424.058594 L 71.269531 423.203125 L 72.644531 421.5 L 74.019531 419.789062 L 74.707031 418.929688 L 75.390625 418.070312 L 76.765625 416.351562 L 78.140625 414.625 L 78.828125 413.757812 L 79.511719 412.890625 L 80.886719 411.148438 L 81.574219 410.273438 L 82.261719 409.394531 L 82.949219 408.511719 L 83.632812 407.628906 L 85.007812 405.847656 L 86.382812 404.050781 L 87.070312 403.140625 L 87.753906 402.230469 L 88.441406 401.3125 L 89.128906 400.390625 L 89.816406 399.460938 L 90.503906 398.523438 L 91.191406 397.578125 L 91.875 396.628906 L 92.5625 395.667969 L 93.25 394.703125 L 93.9375 393.730469 L 94.625 392.75 L 95.3125 391.761719 L 95.996094 390.765625 L 96.683594 389.765625 L 97.371094 388.757812 L 98.058594 387.742188 L 98.746094 386.722656 L 99.433594 385.699219 L 100.117188 384.667969 L 100.804688 383.632812 L 101.492188 382.59375 L 102.179688 381.550781 L 102.867188 380.503906 L 103.554688 379.453125 L 104.238281 378.402344 L 105.613281 376.285156 L 106.988281 374.160156 L 107.675781 373.09375 L 108.359375 372.027344 L 109.046875 370.960938 L 109.734375 369.886719 L 110.421875 368.816406 L 111.796875 366.667969 L 111.796875 375.09375 L 111.109375 375.949219 L 109.046875 378.527344 L 108.359375 379.390625 L 107.675781 380.253906 L 106.300781 381.988281 L 105.613281 382.859375 L 104.238281 384.609375 L 103.554688 385.484375 L 102.867188 386.367188 L 101.492188 388.140625 L 100.804688 389.03125 L 100.117188 389.929688 L 99.433594 390.832031 L 98.746094 391.738281 L 98.058594 392.648438 L 97.371094 393.566406 L 96.683594 394.488281 L 95.996094 395.421875 L 95.3125 396.355469 L 94.625 397.300781 L 93.9375 398.25 L 93.25 399.210938 L 92.5625 400.175781 L 91.875 401.148438 L 91.191406 402.128906 L 90.503906 403.117188 L 89.816406 404.113281 L 89.128906 405.113281 L 88.441406 406.121094 L 87.753906 407.136719 L 87.070312 408.15625 L 86.382812 409.179688 L 85.695312 410.210938 L 85.007812 411.246094 L 84.320312 412.285156 L 83.632812 413.328125 L 82.949219 414.375 L 82.261719 415.425781 L 80.886719 417.535156 L 80.199219 418.59375 L 79.511719 419.65625 L 78.828125 420.71875 L 77.453125 422.851562 L 75.390625 426.0625 L 74.707031 427.136719 L 73.332031 429.285156 L 71.269531 432.519531 L 70.585938 433.597656 L 67.148438 439.007812 L 66.464844 440.089844 L 65.777344 441.175781 L 65.089844 442.257812 L 62.339844 446.601562 L 61.65625 447.6875 L 60.96875 448.773438 L 60.28125 449.863281 L 59.59375 450.949219 L 58.90625 452.039062 L 58.21875 453.125 L 57.535156 454.214844 Z M 57.535156 440.144531 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 57.535156 447.179688 L 58.21875 446.210938 L 60.28125 443.316406 L 60.96875 442.347656 L 61.65625 441.382812 L 62.339844 440.417969 L 63.027344 439.453125 L 63.714844 438.484375 L 65.777344 435.589844 L 66.464844 434.621094 L 67.148438 433.65625 L 69.210938 430.761719 L 69.898438 429.792969 L 70.585938 428.828125 L 71.269531 427.863281 L 71.957031 426.898438 L 72.644531 425.929688 L 74.707031 423.035156 L 75.390625 422.066406 L 77.453125 419.171875 L 78.140625 418.203125 L 78.828125 417.238281 L 79.511719 416.273438 L 80.199219 415.308594 L 80.886719 414.339844 L 82.949219 411.445312 L 83.632812 410.476562 L 85.695312 407.582031 L 86.382812 406.613281 L 87.070312 405.648438 L 87.753906 404.683594 L 88.441406 403.71875 L 89.128906 402.75 L 91.191406 399.855469 L 91.875 398.886719 L 94.625 395.027344 L 95.3125 394.058594 L 95.996094 393.09375 L 97.371094 391.164062 L 98.058594 390.195312 L 99.433594 388.265625 L 100.117188 387.300781 L 100.804688 386.332031 L 102.867188 383.4375 L 103.554688 382.46875 L 104.238281 381.503906 L 105.613281 379.574219 L 106.300781 378.605469 L 107.675781 376.675781 L 108.359375 375.710938 L 109.046875 374.742188 L 111.109375 371.847656 L 111.796875 370.878906 "/>
-<g clip-path="url(#clip41)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 234.925781 L 428.601562 234.925781 L 428.601562 23.246094 L 234.617188 23.246094 Z M 234.617188 234.925781 "/>
-</g>
-<g clip-path="url(#clip42)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 204.210938 L 428.601562 204.210938 "/>
-</g>
-<g clip-path="url(#clip43)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 150.910156 L 428.601562 150.910156 "/>
-</g>
-<g clip-path="url(#clip44)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 97.613281 L 428.601562 97.613281 "/>
-</g>
-<g clip-path="url(#clip45)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 44.3125 L 428.601562 44.3125 "/>
-</g>
-<g clip-path="url(#clip46)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 234.925781 L 267.171875 23.246094 "/>
-</g>
-<g clip-path="url(#clip47)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 234.925781 L 301.085938 23.246094 "/>
-</g>
-<g clip-path="url(#clip48)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 234.925781 L 335 23.246094 "/>
-</g>
-<g clip-path="url(#clip49)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 234.925781 L 368.914062 23.246094 "/>
-</g>
-<g clip-path="url(#clip50)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 234.925781 L 402.828125 23.246094 "/>
-</g>
-<g clip-path="url(#clip51)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 230.859375 L 428.601562 230.859375 "/>
-</g>
-<g clip-path="url(#clip52)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 177.558594 L 428.601562 177.558594 "/>
-</g>
-<g clip-path="url(#clip53)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 124.261719 L 428.601562 124.261719 "/>
-</g>
-<g clip-path="url(#clip54)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 70.960938 L 428.601562 70.960938 "/>
-</g>
-<g clip-path="url(#clip55)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 234.925781 L 250.214844 23.246094 "/>
-</g>
-<g clip-path="url(#clip56)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 234.925781 L 284.128906 23.246094 "/>
-</g>
-<g clip-path="url(#clip57)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 234.925781 L 318.042969 23.246094 "/>
-</g>
-<g clip-path="url(#clip58)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 234.925781 L 351.957031 23.246094 "/>
-</g>
-<g clip-path="url(#clip59)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 234.925781 L 385.871094 23.246094 "/>
-</g>
-<g clip-path="url(#clip60)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 234.925781 L 419.785156 23.246094 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 326.78125 129.589844 C 326.78125 132.199219 322.871094 132.199219 322.871094 129.589844 C 322.871094 126.984375 326.78125 126.984375 326.78125 129.589844 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 134.921875 C 320 137.527344 316.089844 137.527344 316.089844 134.921875 C 316.089844 132.316406 320 132.316406 320 134.921875 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 320 129.589844 C 320 132.199219 316.089844 132.199219 316.089844 129.589844 C 316.089844 126.984375 320 126.984375 320 129.589844 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 318.042969 124.148438 L 318.128906 124.214844 L 318.214844 124.285156 L 318.300781 124.347656 L 318.386719 124.414062 L 318.472656 124.476562 L 318.558594 124.535156 L 318.644531 124.597656 L 318.730469 124.652344 L 318.816406 124.710938 L 318.902344 124.761719 L 318.988281 124.816406 L 319.074219 124.867188 L 319.246094 124.960938 L 319.417969 125.046875 L 319.503906 125.085938 L 319.675781 125.15625 L 319.847656 125.21875 L 320.105469 125.289062 L 320.277344 125.320312 L 320.363281 125.332031 L 320.535156 125.347656 L 320.707031 125.347656 L 320.878906 125.332031 L 320.964844 125.320312 L 321.050781 125.304688 L 321.136719 125.285156 L 321.308594 125.238281 L 321.390625 125.207031 L 321.5625 125.136719 L 321.734375 125.050781 L 321.90625 124.949219 L 321.992188 124.894531 L 322.078125 124.835938 L 322.164062 124.773438 L 322.25 124.707031 L 322.421875 124.566406 L 322.59375 124.410156 L 322.679688 124.328125 L 322.765625 124.242188 L 322.9375 124.0625 L 323.023438 123.96875 L 323.195312 123.773438 L 323.28125 123.671875 L 323.453125 123.460938 L 323.539062 123.351562 L 323.796875 123.011719 L 323.882812 122.894531 L 324.054688 122.652344 L 324.3125 122.277344 L 324.484375 122.019531 L 324.742188 121.621094 L 324.828125 121.484375 L 324.828125 137.699219 L 324.742188 137.632812 L 324.65625 137.5625 L 324.570312 137.5 L 324.484375 137.433594 L 324.398438 137.371094 L 324.3125 137.3125 L 324.226562 137.25 L 324.140625 137.195312 L 324.054688 137.136719 L 323.96875 137.085938 L 323.882812 137.03125 L 323.796875 136.980469 L 323.625 136.886719 L 323.453125 136.800781 L 323.367188 136.761719 L 323.195312 136.691406 L 323.023438 136.628906 L 322.765625 136.558594 L 322.59375 136.527344 L 322.507812 136.515625 L 322.421875 136.507812 L 322.25 136.5 L 322.164062 136.5 L 321.992188 136.515625 L 321.90625 136.527344 L 321.820312 136.542969 L 321.734375 136.5625 L 321.5625 136.609375 L 321.476562 136.640625 L 321.390625 136.675781 L 321.308594 136.710938 L 321.136719 136.796875 L 320.964844 136.898438 L 320.878906 136.953125 L 320.792969 137.011719 L 320.707031 137.074219 L 320.621094 137.140625 L 320.449219 137.28125 L 320.277344 137.4375 L 320.191406 137.519531 L 320.105469 137.605469 L 319.933594 137.785156 L 319.847656 137.878906 L 319.675781 138.074219 L 319.589844 138.175781 L 319.417969 138.386719 L 319.332031 138.496094 L 319.074219 138.835938 L 318.988281 138.953125 L 318.816406 139.195312 L 318.558594 139.570312 L 318.386719 139.828125 L 318.214844 140.09375 L 318.128906 140.230469 L 318.042969 140.363281 Z M 318.042969 124.148438 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 132.257812 L 318.214844 132.1875 L 318.300781 132.15625 L 318.472656 132.085938 L 318.558594 132.054688 L 318.644531 132.019531 L 318.730469 131.988281 L 318.902344 131.917969 L 318.988281 131.886719 L 319.160156 131.816406 L 319.246094 131.785156 L 319.417969 131.714844 L 319.503906 131.683594 L 319.589844 131.648438 L 319.675781 131.617188 L 319.847656 131.546875 L 319.933594 131.515625 L 320.105469 131.445312 L 320.191406 131.414062 L 320.363281 131.34375 L 320.449219 131.3125 L 320.535156 131.277344 L 320.621094 131.246094 L 320.792969 131.175781 L 320.878906 131.144531 L 321.050781 131.074219 L 321.136719 131.042969 L 321.308594 130.972656 L 321.390625 130.941406 L 321.476562 130.90625 L 321.5625 130.875 L 321.734375 130.804688 L 321.820312 130.773438 L 321.992188 130.703125 L 322.078125 130.671875 L 322.25 130.601562 L 322.335938 130.570312 L 322.421875 130.535156 L 322.507812 130.503906 L 322.679688 130.433594 L 322.765625 130.402344 L 322.9375 130.332031 L 323.023438 130.300781 L 323.195312 130.230469 L 323.28125 130.199219 L 323.367188 130.164062 L 323.453125 130.132812 L 323.625 130.0625 L 323.710938 130.03125 L 323.882812 129.960938 L 323.96875 129.929688 L 324.140625 129.859375 L 324.226562 129.828125 L 324.3125 129.792969 L 324.398438 129.761719 L 324.570312 129.691406 L 324.65625 129.660156 L 324.828125 129.589844 "/>
-<g clip-path="url(#clip61)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 234.617188 469.847656 L 428.601562 469.847656 L 428.601562 258.167969 L 234.617188 258.167969 Z M 234.617188 469.847656 "/>
-</g>
-<g clip-path="url(#clip62)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 439.132812 L 428.601562 439.132812 "/>
-</g>
-<g clip-path="url(#clip63)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 385.835938 L 428.601562 385.835938 "/>
-</g>
-<g clip-path="url(#clip64)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 332.535156 L 428.601562 332.535156 "/>
-</g>
-<g clip-path="url(#clip65)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 279.238281 L 428.601562 279.238281 "/>
-</g>
-<g clip-path="url(#clip66)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 267.171875 469.847656 L 267.171875 258.171875 "/>
-</g>
-<g clip-path="url(#clip67)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 301.085938 469.847656 L 301.085938 258.171875 "/>
-</g>
-<g clip-path="url(#clip68)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 335 469.847656 L 335 258.171875 "/>
-</g>
-<g clip-path="url(#clip69)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 368.914062 469.847656 L 368.914062 258.171875 "/>
-</g>
-<g clip-path="url(#clip70)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 402.828125 469.847656 L 402.828125 258.171875 "/>
-</g>
-<g clip-path="url(#clip71)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 465.785156 L 428.601562 465.785156 "/>
-</g>
-<g clip-path="url(#clip72)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 412.484375 L 428.601562 412.484375 "/>
-</g>
-<g clip-path="url(#clip73)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 359.1875 L 428.601562 359.1875 "/>
-</g>
-<g clip-path="url(#clip74)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 234.617188 305.886719 L 428.601562 305.886719 "/>
-</g>
-<g clip-path="url(#clip75)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 469.847656 L 250.214844 258.171875 "/>
-</g>
-<g clip-path="url(#clip76)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 469.847656 L 284.128906 258.171875 "/>
-</g>
-<g clip-path="url(#clip77)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 469.847656 L 318.042969 258.171875 "/>
-</g>
-<g clip-path="url(#clip78)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 469.847656 L 351.957031 258.171875 "/>
-</g>
-<g clip-path="url(#clip79)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 469.847656 L 385.871094 258.171875 "/>
-</g>
-<g clip-path="url(#clip80)" clip-rule="nonzero">
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 469.847656 L 419.785156 258.171875 "/>
-</g>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 396.496094 C 292.867188 399.101562 288.957031 399.101562 288.957031 396.496094 C 288.957031 393.890625 292.867188 393.890625 292.867188 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 428.472656 C 265.738281 431.082031 261.828125 431.082031 261.828125 428.472656 C 261.828125 425.867188 265.738281 425.867188 265.738281 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 380.503906 C 292.867188 383.113281 288.957031 383.113281 288.957031 380.503906 C 288.957031 377.898438 292.867188 377.898438 292.867188 380.503906 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 385.835938 C 286.085938 388.441406 282.175781 388.441406 282.175781 385.835938 C 282.175781 383.230469 286.085938 383.230469 286.085938 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 391.164062 C 286.085938 393.773438 282.175781 393.773438 282.175781 391.164062 C 282.175781 388.558594 286.085938 388.558594 286.085938 391.164062 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 433.804688 C 265.738281 436.410156 261.828125 436.410156 261.828125 433.804688 C 261.828125 431.199219 265.738281 431.199219 265.738281 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 433.804688 C 272.519531 436.410156 268.609375 436.410156 268.609375 433.804688 C 268.609375 431.199219 272.519531 431.199219 272.519531 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 407.15625 C 286.085938 409.761719 282.175781 409.761719 282.175781 407.15625 C 282.175781 404.546875 286.085938 404.546875 286.085938 407.15625 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 396.496094 C 286.085938 399.101562 282.175781 399.101562 282.175781 396.496094 C 282.175781 393.890625 286.085938 393.890625 286.085938 396.496094 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 286.085938 401.824219 C 286.085938 404.429688 282.175781 404.429688 282.175781 401.824219 C 282.175781 399.21875 286.085938 399.21875 286.085938 401.824219 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 412.484375 C 279.300781 415.089844 275.394531 415.089844 275.394531 412.484375 C 275.394531 409.878906 279.300781 409.878906 279.300781 412.484375 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 245.390625 455.125 C 245.390625 457.730469 241.480469 457.730469 241.480469 455.125 C 241.480469 452.515625 245.390625 452.515625 245.390625 455.125 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 417.816406 C 279.300781 420.421875 275.394531 420.421875 275.394531 417.816406 C 275.394531 415.207031 279.300781 415.207031 279.300781 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 444.464844 C 258.953125 447.070312 255.042969 447.070312 255.042969 444.464844 C 255.042969 441.859375 258.953125 441.859375 258.953125 444.464844 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 428.472656 C 258.953125 431.082031 255.042969 431.082031 255.042969 428.472656 C 255.042969 425.867188 258.953125 425.867188 258.953125 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 433.804688 C 258.953125 436.410156 255.042969 436.410156 255.042969 433.804688 C 255.042969 431.199219 258.953125 431.199219 258.953125 433.804688 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 417.816406 C 272.519531 420.421875 268.609375 420.421875 268.609375 417.816406 C 268.609375 415.207031 272.519531 415.207031 272.519531 417.816406 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 428.472656 C 272.519531 431.082031 268.609375 431.082031 268.609375 428.472656 C 268.609375 425.867188 272.519531 425.867188 272.519531 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 265.738281 423.144531 C 265.738281 425.75 261.828125 425.75 261.828125 423.144531 C 261.828125 420.539062 265.738281 420.539062 265.738281 423.144531 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 292.867188 385.835938 C 292.867188 388.441406 288.957031 388.441406 288.957031 385.835938 C 288.957031 383.230469 292.867188 383.230469 292.867188 385.835938 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 279.300781 428.472656 C 279.300781 431.082031 275.394531 431.082031 275.394531 428.472656 C 275.394531 425.867188 279.300781 425.867188 279.300781 428.472656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 258.953125 439.132812 C 258.953125 441.742188 255.042969 441.742188 255.042969 439.132812 C 255.042969 436.527344 258.953125 436.527344 258.953125 439.132812 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 272.519531 423.144531 C 272.519531 425.75 268.609375 425.75 268.609375 423.144531 C 268.609375 420.539062 272.519531 420.539062 272.519531 423.144531 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 243.433594 452.394531 L 244.035156 451.695312 L 245.238281 450.304688 L 245.839844 449.605469 L 246.4375 448.90625 L 248.84375 446.109375 L 249.445312 445.40625 L 250.046875 444.707031 L 250.644531 444.003906 L 251.246094 443.300781 L 251.847656 442.59375 L 252.449219 441.890625 L 253.652344 440.476562 L 254.253906 439.765625 L 254.851562 439.058594 L 255.453125 438.347656 L 257.257812 436.203125 L 257.859375 435.484375 L 258.460938 434.761719 L 259.058594 434.039062 L 259.660156 433.316406 L 260.261719 432.589844 L 260.863281 431.859375 L 262.066406 430.390625 L 262.667969 429.652344 L 263.265625 428.910156 L 263.867188 428.164062 L 264.46875 427.414062 L 265.070312 426.660156 L 265.671875 425.902344 L 266.273438 425.140625 L 266.875 424.375 L 267.472656 423.601562 L 268.074219 422.828125 L 268.675781 422.050781 L 269.878906 420.480469 L 271.082031 418.894531 L 271.679688 418.09375 L 272.882812 416.484375 L 273.484375 415.675781 L 274.085938 414.863281 L 274.6875 414.046875 L 275.285156 413.226562 L 275.886719 412.40625 L 277.089844 410.757812 L 277.691406 409.929688 L 278.894531 408.265625 L 279.492188 407.433594 L 281.296875 404.925781 L 282.5 403.246094 L 283.101562 402.402344 L 283.699219 401.5625 L 284.902344 399.875 L 285.503906 399.027344 L 286.105469 398.183594 L 287.308594 396.488281 L 287.90625 395.640625 L 288.507812 394.792969 L 289.109375 393.941406 L 289.710938 393.09375 L 290.3125 392.242188 L 290.914062 391.394531 L 290.914062 398.976562 L 290.3125 399.675781 L 289.710938 400.371094 L 287.90625 402.46875 L 287.308594 403.167969 L 286.707031 403.867188 L 286.105469 404.570312 L 285.503906 405.269531 L 283.699219 407.378906 L 283.101562 408.085938 L 281.296875 410.207031 L 279.492188 412.339844 L 278.894531 413.054688 L 278.292969 413.769531 L 276.488281 415.925781 L 275.285156 417.378906 L 274.6875 418.105469 L 273.484375 419.574219 L 272.28125 421.050781 L 271.679688 421.796875 L 271.082031 422.546875 L 270.480469 423.296875 L 269.277344 424.8125 L 268.675781 425.578125 L 268.074219 426.347656 L 267.472656 427.121094 L 266.875 427.898438 L 266.273438 428.679688 L 265.671875 429.464844 L 265.070312 430.253906 L 264.46875 431.046875 L 263.867188 431.84375 L 263.265625 432.644531 L 262.667969 433.453125 L 262.066406 434.257812 L 261.464844 435.070312 L 260.261719 436.703125 L 259.660156 437.523438 L 259.058594 438.347656 L 258.460938 439.171875 L 257.257812 440.828125 L 255.453125 443.324219 L 254.851562 444.160156 L 254.253906 445 L 251.847656 448.359375 L 250.644531 450.046875 L 250.046875 450.894531 L 249.445312 451.738281 L 248.84375 452.585938 L 248.242188 453.429688 L 247.640625 454.277344 L 247.039062 455.128906 L 246.4375 455.976562 L 245.839844 456.824219 L 244.636719 458.527344 L 244.035156 459.375 L 243.433594 460.226562 Z M 243.433594 452.394531 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 243.433594 456.308594 L 245.839844 453.214844 L 246.4375 452.441406 L 250.046875 447.800781 L 250.644531 447.027344 L 251.246094 446.25 L 254.253906 442.382812 L 254.851562 441.609375 L 258.460938 436.96875 L 259.058594 436.195312 L 259.660156 435.417969 L 262.667969 431.550781 L 263.265625 430.777344 L 266.875 426.136719 L 267.472656 425.359375 L 271.082031 420.71875 L 271.679688 419.945312 L 274.6875 416.078125 L 275.285156 415.304688 L 275.886719 414.527344 L 278.894531 410.660156 L 279.492188 409.886719 L 283.101562 405.246094 L 283.699219 404.46875 L 287.308594 399.828125 L 287.90625 399.054688 L 290.914062 395.1875 "/>
-<g clip-path="url(#clip81)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 240.40625 L 35.152344 240.40625 Z M 35.152344 258.171875 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-1" x="129.644531" y="252.204102"/>
-</g>
-<g clip-path="url(#clip82)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 240.40625 L 234.617188 240.40625 Z M 234.617188 258.171875 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-2" x="329.109375" y="252.204102"/>
-</g>
-<g clip-path="url(#clip83)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 5.480469 L 35.152344 5.480469 Z M 35.152344 23.246094 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="129.644531" y="17.27832"/>
-</g>
-<g clip-path="url(#clip84)" clip-rule="nonzero">
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(85.098039%,85.098039%,85.098039%);fill-opacity:1;" d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 5.480469 L 234.617188 5.480469 Z M 234.617188 23.246094 "/>
-</g>
-<g style="fill:rgb(10.196078%,10.196078%,10.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-4" x="329.109375" y="17.27832"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 50.75 472.589844 L 50.75 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 84.664062 472.589844 L 84.664062 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 118.578125 472.589844 L 118.578125 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 152.492188 472.589844 L 152.492188 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 186.40625 472.589844 L 186.40625 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 220.320312 472.589844 L 220.320312 469.847656 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="45.75" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="50.75" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="79.664062" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="84.664062" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="113.578125" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="118.578125" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="147.492188" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="152.492188" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="181.40625" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="186.40625" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="215.320312" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="220.320312" y="481.196289"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 250.214844 472.589844 L 250.214844 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 284.128906 472.589844 L 284.128906 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 318.042969 472.589844 L 318.042969 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 351.957031 472.589844 L 351.957031 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 385.871094 472.589844 L 385.871094 469.847656 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 419.785156 472.589844 L 419.785156 469.847656 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="245.214844" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="250.214844" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="279.128906" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="284.128906" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="313.042969" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="318.042969" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="346.957031" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="351.957031" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="380.871094" y="481.196289"/>
-  <use xlink:href="#glyph0-6" x="385.871094" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="414.785156" y="481.196289"/>
-  <use xlink:href="#glyph0-4" x="419.785156" y="481.196289"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="20.21875" y="233.774414"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="233.774414"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="20.21875" y="180.473633"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="180.473633"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="20.21875" y="127.176758"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="127.176758"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="20.21875" y="73.875977"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="73.875977"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 230.859375 L 35.152344 230.859375 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 177.558594 L 35.152344 177.558594 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 124.261719 L 35.152344 124.261719 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 70.960938 L 35.152344 70.960938 "/>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-5" x="20.21875" y="468.700195"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="468.700195"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-7" x="20.21875" y="415.399414"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="415.399414"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-8" x="20.21875" y="362.102539"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="362.102539"/>
-</g>
-<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="20.21875" y="308.801758"/>
-  <use xlink:href="#glyph0-6" x="25.21875" y="308.801758"/>
-</g>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 465.785156 L 35.152344 465.785156 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 412.484375 L 35.152344 412.484375 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 359.1875 L 35.152344 359.1875 "/>
-<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 305.886719 L 35.152344 305.886719 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph1-1" x="224.875" y="494.538086"/>
-  <use xlink:href="#glyph1-2" x="230.875" y="494.538086"/>
-  <use xlink:href="#glyph1-3" x="233.875" y="494.538086"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph2-1" x="13.499023" y="256.046875"/>
-  <use xlink:href="#glyph2-2" x="13.499023" y="250.046875"/>
-  <use xlink:href="#glyph2-3" x="13.499023" y="242.046875"/>
-</g>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;" d="M 439.5625 295.328125 L 498.519531 295.328125 L 498.519531 197.769531 L 439.5625 197.769531 Z M 439.5625 295.328125 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph1-4" x="445.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-5" x="448.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-1" x="454.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-2" x="460.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-6" x="463.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-7" x="469.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-8" x="473.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-1" x="477.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-3" x="482.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-9" x="487.042969" y="212.768555"/>
-  <use xlink:href="#glyph1-10" x="489.042969" y="212.768555"/>
-</g>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
-<path style="fill-rule:nonzero;fill:rgb(97.254902%,46.27451%,42.745098%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 229.367188 C 455.636719 231.972656 451.726562 231.972656 451.726562 229.367188 C 451.726562 226.761719 455.636719 226.761719 455.636719 229.367188 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 238.007812 L 462.324219 238.007812 L 462.324219 220.726562 L 445.042969 220.726562 Z M 445.042969 238.007812 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(97.254902%,46.27451%,42.745098%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 229.367188 L 460.59375 229.367188 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
-<path style="fill-rule:nonzero;fill:rgb(48.627451%,68.235294%,0%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 246.648438 C 455.636719 249.253906 451.726562 249.253906 451.726562 246.648438 C 451.726562 244.042969 455.636719 244.042969 455.636719 246.648438 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 255.289062 L 462.324219 255.289062 L 462.324219 238.007812 L 445.042969 238.007812 Z M 445.042969 255.289062 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(48.627451%,68.235294%,0%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 246.648438 L 460.59375 246.648438 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
-<path style="fill-rule:nonzero;fill:rgb(0%,74.901961%,76.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 263.925781 C 455.636719 266.535156 451.726562 266.535156 451.726562 263.925781 C 451.726562 261.320312 455.636719 261.320312 455.636719 263.925781 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 272.566406 L 462.324219 272.566406 L 462.324219 255.285156 L 445.042969 255.285156 Z M 445.042969 272.566406 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(0%,74.901961%,76.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 263.925781 L 460.59375 263.925781 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(94.901961%,94.901961%,94.901961%);fill-opacity:1;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
-<path style="fill-rule:nonzero;fill:rgb(78.039216%,48.627451%,100%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 455.636719 281.207031 C 455.636719 283.8125 451.726562 283.8125 451.726562 281.207031 C 451.726562 278.601562 455.636719 278.601562 455.636719 281.207031 "/>
-<path style=" stroke:none;fill-rule:nonzero;fill:rgb(60%,60%,60%);fill-opacity:0.4;" d="M 445.042969 289.847656 L 462.324219 289.847656 L 462.324219 272.566406 L 445.042969 272.566406 Z M 445.042969 289.847656 "/>
-<path style="fill:none;stroke-width:2.133957;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(78.039216%,48.627451%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 446.769531 281.207031 L 460.59375 281.207031 "/>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-3" x="467.800781" y="232.282227"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-4" x="467.800781" y="249.563477"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-1" x="467.800781" y="266.84082"/>
-</g>
-<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
-  <use xlink:href="#glyph0-2" x="467.800781" y="284.12207"/>
-</g>
-</g>
-</svg>
-
-```
-
-We may also [generate](https://scicloj.github.io/clojisr/doc/clojisr/v1/codegen-test/) the R code from a Clojure form and pass Clojure data to R, but for now, we are simply using R code using an R dataset.
-
-We are using the `mpg` dataset, which is part of the `ggplot` package.
-
-::: {.sourceClojure}
-```clojure
-(-> "mpg"
-    r
-    r->clj)
-```
-:::
-
-_unnamed [234 11]:
-
-| :manufacturer |     :model | :displ | :year | :cyl |     :trans | :drv | :cty | :hwy | :fl |     :class |
-|---------------|------------|-------:|------:|-----:|------------|------|-----:|-----:|-----|------------|
-|          audi |         a4 |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    compact |
-|          audi |         a4 |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    compact |
-|          audi |         a4 |    2.0 |  2008 |    4 | manual(m6) |    f |   20 |   31 |   p |    compact |
-|          audi |         a4 |    2.0 |  2008 |    4 |   auto(av) |    f |   21 |   30 |   p |    compact |
-|          audi |         a4 |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    compact |
-|          audi |         a4 |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    compact |
-|          audi |         a4 |    3.1 |  2008 |    6 |   auto(av) |    f |   18 |   27 |   p |    compact |
-|          audi | a4 quattro |    1.8 |  1999 |    4 | manual(m5) |    4 |   18 |   26 |   p |    compact |
-|          audi | a4 quattro |    1.8 |  1999 |    4 |   auto(l5) |    4 |   16 |   25 |   p |    compact |
-|          audi | a4 quattro |    2.0 |  2008 |    4 | manual(m6) |    4 |   20 |   28 |   p |    compact |
-|           ... |        ... |    ... |   ... |  ... |        ... |  ... |  ... |  ... | ... |        ... |
-|    volkswagen | new beetle |    2.0 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   r | subcompact |
-|    volkswagen | new beetle |    2.0 |  1999 |    4 |   auto(l4) |    f |   19 |   26 |   r | subcompact |
-|    volkswagen | new beetle |    2.5 |  2008 |    5 | manual(m5) |    f |   20 |   28 |   r | subcompact |
-|    volkswagen | new beetle |    2.5 |  2008 |    5 |   auto(s6) |    f |   20 |   29 |   r | subcompact |
-|    volkswagen |     passat |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    midsize |
-|    volkswagen |     passat |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    midsize |
-|    volkswagen |     passat |    2.0 |  2008 |    4 |   auto(s6) |    f |   19 |   28 |   p |    midsize |
-|    volkswagen |     passat |    2.0 |  2008 |    4 | manual(m6) |    f |   21 |   29 |   p |    midsize |
-|    volkswagen |     passat |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    midsize |
-|    volkswagen |     passat |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    midsize |
-|    volkswagen |     passat |    3.6 |  2008 |    6 |   auto(s6) |    f |   17 |   26 |   p |    midsize |
-
-## Representing plots as Clojure data
+## A representation function
 
@@
 
+## An example
+
 For example:
@@
 ```clojure
+(delay
   (-> "(ggplot(mpg, aes(cty, hwy))
@@
       ggplot->clj
-    (dissoc :data))
+      (dissoc :data)))
 ```
@@
 
-## Exlploring a few plots
-
-Let us explore and compare a few plots this way:
-
-::: {.sourceClojure}
-```clojure
-(defn h3 [title] (kind/hiccup [:h3 title]))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn h4 [title] (kind/hiccup [:h4 title]))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn ggplot-summary
-  ([title r-code]
-   (ggplot-summary r-code))
-  ([title r-code prev-clj-to-compare]
-   (let [plot (r r-code)
-         clj (-> plot
-                 ggplot->clj
-                 (dissoc :data))]
-     {:title title
-      :r-code r-code
-      :image (plotting/plot->buffered-image plot)
-      :clj clj
-      :diff (when prev-clj-to-compare
-              (-> prev-clj-to-compare
-                  (editscript/diff clj)
-                  pp/pprint
-                  with-out-str
-                  (str/replace #": " ":_ ")
-                  read-string))})))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn view-summary [{:keys [title r-code image clj diff]}]
-  (kind/fragment
-   [(h3 title)
-    (h4 "R code")
-    (kind/md
-     (format "\n```\n%s\n```\n"
-             r-code))
-    (h4 "plot")
-    image
-    (h4 "clj data")
-    clj
-    (when diff
-      (kind/fragment
-       [(h4 "clj diff with previous")
-        diff]))]))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(->> [;;
-      ["A scatterplot"
-       "(ggplot(mpg, aes(cty, hwy))
-         + geom_point())"]
-      ;;
-      ["A scatterplot with colours"
-       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())"]
-      ;;
-      ["A scatterplot with colours and smoothing"
-       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\"))"]
-      ;;
-      ["A scatterplot with colours, smoothing, and facets"
-       "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method=\"lm\")
-         + facet_wrap(~cyl))"]]
-     (reductions (fn [prev-summary [title r-code]]
-                   (ggplot-summary title
-                                   r-code
-                                   (:clj prev-summary)))
-                 nil)
-     rest
-     (map view-summary)
-     kind/fragment)
-```
-:::
-
-```{=html}
-<h3>A scatterplot</h3>
-```
-
-```{=html}
-<h4>R code</h4>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy))
-         + geom_point())
-```
-
-```{=html}
-<h4>plot</h4>
-```
-
-```{=html}
-<img src="repesenting_files/0.png" style="width:100%;" />
-```
-
-```{=html}
-<h4>clj data</h4>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-```{=html}
-<h3>A scatterplot with colours</h3>
-```
-
-```{=html}
-<h4>R code</h4>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point())
-```
-
-```{=html}
-<h4>plot</h4>
-```
-
-```{=html}
-<img src="repesenting_files/1.png" style="width:100%;" />
-```
-
-```{=html}
-<h4>clj data</h4>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-```{=html}
-<h4>clj diff with previous</h4>
-```
-
-::: {.printedClojure}
-```clojure
-[[[:mapping :colour] :+ [~[factor cyl]]]
- [[:labels :colour] :+ ["factor(cyl)"]]]
-
-```
-:::
-
-```{=html}
-<h3>A scatterplot with colours and smoothing</h3>
-```
-
-```{=html}
-<h4>R code</h4>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method="lm"))
-```
-
-```{=html}
-<h4>plot</h4>
-```
-
-```{=html}
-<img src="repesenting_files/2.png" style="width:100%;" />
-```
-
-```{=html}
-<h4>clj data</h4>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}
-  {:aes_params [],
-   :stat
-   {:extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x" "y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_params :ggproto-method,
-    :super :ggproto-method,
-    :draw_key :ggproto-method,
-    :extra_params ["na.rm" "orientation"],
-    :required_aes ["x" "y"],
-    :draw_group :ggproto-method,
-    :optional_aes ["ymin" "ymax"],
-    :rename_size [true],
-    :setup_data :ggproto-method,
-    :default_aes
-    {:colour ["#3366FF"],
-     :fill ["grey60"],
-     :linewidth [1.0],
-     :linetype [1.0],
-     :weight [1.0],
-     :alpha [0.4]}},
-   :stat_params
-   {:na.rm [false],
-    :method ["lm"],
-    :n [80.0],
-    :orientation [nil],
-    :level [0.95],
-    :fullrange [false],
-    :se [true],
-    :formula nil,
-    :method.args [],
-    :span [0.75]},
-   :constructor {: nil, :method ["lm"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-```{=html}
-<h4>clj diff with previous</h4>
-```
-
-::: {.printedClojure}
-```clojure
-[[[:layers 1]
-  :+
-  {:aes_params [],
-   :stat
-   {:extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x" "y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_params :ggproto-method,
-    :super :ggproto-method,
-    :draw_key :ggproto-method,
-    :extra_params ["na.rm" "orientation"],
-    :required_aes ["x" "y"],
-    :draw_group :ggproto-method,
-    :optional_aes ["ymin" "ymax"],
-    :rename_size [true],
-    :setup_data :ggproto-method,
-    :default_aes
-    {:colour ["#3366FF"],
-     :fill ["grey60"],
-     :linewidth [1.0],
-     :linetype [1.0],
-     :weight [1.0],
-     :alpha [0.4]}},
-   :stat_params
-   {:na.rm [false],
-    :method ["lm"],
-    :n [80.0],
-    :orientation [nil],
-    :level [0.95],
-    :fullrange [false],
-    :se [true],
-    :formula nil,
-    :method.args [],
-    :span [0.75]},
-   :constructor {:_ nil, :method ["lm"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}]]
-
-```
-:::
-
-```{=html}
-<h3>A scatterplot with colours, smoothing, and facets</h3>
-```
-
-```{=html}
-<h4>R code</h4>
-```
-
-```
-(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
-         + geom_point()
-         + stat_smooth(method="lm")
-         + facet_wrap(~cyl))
-```
-
-```{=html}
-<h4>plot</h4>
-```
-
-```{=html}
-<img src="repesenting_files/3.png" style="width:100%;" />
-```
-
-```{=html}
-<h4>clj data</h4>
-```
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor [geom_point],
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}
-  {:aes_params [],
-   :stat
-   {:extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x" "y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_params :ggproto-method,
-    :super :ggproto-method,
-    :draw_key :ggproto-method,
-    :extra_params ["na.rm" "orientation"],
-    :required_aes ["x" "y"],
-    :draw_group :ggproto-method,
-    :optional_aes ["ymin" "ymax"],
-    :rename_size [true],
-    :setup_data :ggproto-method,
-    :default_aes
-    {:colour ["#3366FF"],
-     :fill ["grey60"],
-     :linewidth [1.0],
-     :linetype [1.0],
-     :weight [1.0],
-     :alpha [0.4]}},
-   :stat_params
-   {:na.rm [false],
-    :method ["lm"],
-    :n [80.0],
-    :orientation [nil],
-    :level [0.95],
-    :fullrange [false],
-    :se [true],
-    :formula nil,
-    :method.args [],
-    :span [0.75]},
-   :constructor {: nil, :method ["lm"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet
- {:params
-  {:dir ["h"],
-   :nrow nil,
-   :as.table [true],
-   :free {:x [false], :y [false]},
-   :drop [true],
-   :strip.position ["top"],
-   :ncol nil,
-   :facets {:cyl [~ cyl]},
-   :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55b95a21db80&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
-  :shrink [true],
-  :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}
-
-```
-:::
-
-```{=html}
-<h4>clj diff with previous</h4>
-```
-
-::: {.printedClojure}
-```clojure
-[[[:facet :params]
-  :+
-  {:dir ["h"],
-   :nrow nil,
-   :as.table [true],
-   :free {:x [false], :y [false]},
-   :drop [true],
-   :strip.position ["top"],
-   :ncol nil,
-   :facets {:cyl [~cyl]},
-   :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55b95a21db80&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
-
-```
-:::
-
-## Exploring
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy)))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers [],
- :scales {:super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, aes(cty, hwy)))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers [],
- :scales {:super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy)))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers [],
- :scales {:super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
-      + geom_point(mapping=aes(color=cyl), size=5)
-      + ylim(c(20,30)))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params {:size [5.0]},
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping {:colour [~ cyl]},
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales
- {:scales
-  [{:labels [],
-    :scale_name ["position_c"],
-    :breaks [],
-    :call
-    {:labels labels,
-     :scale_name ["position_c"],
-     :breaks breaks,
-     :name name,
-     :palette identity,
-     :super ScaleContinuousPosition,
-     :guide guide,
-     :minor_breaks minor_breaks,
-     :n.breaks n.breaks,
-     : nil,
-     :aesthetics [$ ggplot_global y_aes],
-     :na.value na.value,
-     :trans trans,
-     :oob oob,
-     :position position,
-     :limits limits,
-     :expand expand},
-    :rescaler :ggproto-method,
-    :name [],
-    :palette :ggproto-method,
-    :super :ggproto-method,
-    :guide [],
-    :minor_breaks [],
-    :n.breaks nil,
-    :aesthetics
-    ["y"
-     "ymin"
-     "ymax"
-     "yend"
-     "yintercept"
-     "ymin_final"
-     "ymax_final"
-     "lower"
-     "middle"
-     "upper"
-     "y0"],
-    :na.value [nil],
-    :trans
-    {:name ["identity"],
-     :transform
-     "function (x) \nx\n&lt;bytecode: 0x55b9566f0140&gt;\n&lt;environment: namespace:base&gt;\n",
-     :inverse
-     "function (x) \nx\n&lt;bytecode: 0x55b9566f0140&gt;\n&lt;environment: namespace:base&gt;\n",
-     :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55b95a64c498&gt;\n&lt;environment: 0x55b9649d1458&gt;\n",
-     :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55b95a64fe78&gt;\n&lt;environment: 0x55b9649d12d0&gt;\n",
-     :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55b95a6591f0&gt;\n&lt;environment: 0x55b9649d1180&gt;\n",
-     :domain [##-Inf ##Inf]},
-    :oob :ggproto-method,
-    :position ["left"],
-    :limits [20.0 30.0],
-    :expand [],
-    :range {:super :ggproto-method}}],
-  :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
-      + geom_point(mapping=aes(color=factor(cyl)), size=20))"
-    r
-    plotting/plot->buffered-image)
-```
-:::
-
-```{=html}
-<img src="repesenting_files/4.png" style="width:100%;" />
-```
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
-      + geom_point(mapping=aes(color=cyl), size=5)
-      + ylim(c(20,30))
-      + scale_x_log10())"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params {:size [5.0]},
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping {:colour [~ cyl]},
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales
- {:scales
-  [{:range {:super :ggproto-method}, :super :ggproto-method}
-   {:labels [],
-    :scale_name ["position_c"],
-    :breaks [],
-    :call
-    {:labels labels,
-     :scale_name ["position_c"],
-     :breaks breaks,
-     :name name,
-     :palette identity,
-     :super ScaleContinuousPosition,
-     :guide guide,
-     :minor_breaks minor_breaks,
-     :n.breaks n.breaks,
-     : nil,
-     :aesthetics [$ ggplot_global x_aes],
-     :na.value na.value,
-     :trans trans,
-     :oob oob,
-     :position position,
-     :limits limits,
-     :expand expand},
-    :rescaler :ggproto-method,
-    :name [],
-    :palette :ggproto-method,
-    :super :ggproto-method,
-    :guide [],
-    :minor_breaks [],
-    :n.breaks nil,
-    :aesthetics
-    ["x"
-     "xmin"
-     "xmax"
-     "xend"
-     "xintercept"
-     "xmin_final"
-     "xmax_final"
-     "xlower"
-     "xmiddle"
-     "xupper"
-     "x0"],
-    :na.value [nil],
-    :trans
-    {:name ["log-10"],
-     :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55b95f192f70&gt;\n&lt;environment: 0x55b95f193750&gt;\n",
-     :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x55b95f193130&gt;\n&lt;environment: 0x55b95f193750&gt;\n",
-     :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55b95f18b830&gt;\n&lt;environment: 0x55b95f18ae80&gt;\n",
-     :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55b95a64fe78&gt;\n&lt;environment: 0x55b95f186e88&gt;\n",
-     :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55b95a6591f0&gt;\n&lt;environment: 0x55b95f186fd8&gt;\n",
-     :domain [1.0E-100 ##Inf]},
-    :oob :ggproto-method,
-    :position ["bottom"],
-    :limits nil,
-    :expand [],
-    :range {:super :ggproto-method}}],
-  :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
-      + geom_point(mapping=aes(color=cyl), size=5)
-      + ylim(c(20,30))
-      + scale_x_log10()
-      + theme_linedraw())"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params {:size [5.0]},
-   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
-   :show.legend [nil],
-   :mapping {:colour [~ cyl]},
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false]},
-   :geom
-   {:non_missing_aes ["size" "shape" "colour"],
-    :draw_key :ggproto-method,
-    :default_aes
-    {:shape [19.0],
-     :colour ["black"],
-     :size [1.5],
-     :fill [nil],
-     :alpha [nil],
-     :stroke [0.5]},
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method},
-   :stat_params {:na.rm [false]},
-   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales
- {:scales
-  [{:range {:super :ggproto-method}, :super :ggproto-method}
-   {:range {:super :ggproto-method}, :super :ggproto-method}],
-  :super :ggproto-method},
- :mapping {:x [~ cty], :y [~ hwy]},
- :theme
- {:axis.ticks
-  {:colour ["black"],
-   :linewidth [0.5],
-   :linetype nil,
-   :lineend nil,
-   :arrow [false],
-   :inherit.blank [true]},
-  :legend.justification ["center"],
-  :panel.grid.minor
-  {:colour nil,
-   :linewidth [0.05],
-   :linetype nil,
-   :lineend nil,
-   :arrow [false],
-   :inherit.blank [true]},
-  :strip.text.x.bottom nil,
-  :legend.key.width nil,
-  :panel.spacing.x nil,
-  :axis.text.y
-  {:hjust [1.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin [0.0 2.2 0.0 0.0]},
-  :panel.ontop [false],
-  :axis.ticks.x.top nil,
-  :panel.border
-  {:fill [nil],
-   :colour ["black"],
-   :linewidth [1.0],
-   :linetype nil,
-   :inherit.blank [true]},
-  :legend.key.height nil,
-  :plot.caption
-  {:hjust [1.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [0.8],
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [5.5 0.0 0.0 0.0]},
-  :panel.grid.major.y nil,
-  :panel.grid
-  {:colour ["black"],
-   :linewidth nil,
-   :linetype nil,
-   :lineend nil,
-   :arrow [false],
-   :inherit.blank [true]},
-  :axis.ticks.x.bottom nil,
-  :panel.grid.major.x nil,
-  :plot.tag
-  {:hjust [0.5],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [1.2],
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [0.5],
-   :margin nil},
-  :axis.text
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [0.8],
-   :face nil,
-   :lineheight nil,
-   :colour ["black"],
-   :vjust nil,
-   :margin nil},
-  :axis.line.x nil,
-  :panel.spacing.y nil,
-  :legend.spacing.x nil,
-  :axis.text.x
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [2.2 0.0 0.0 0.0]},
-  :axis.line.y.left nil,
-  :plot.caption.position ["panel"],
-  :plot.subtitle
-  {:hjust [0.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [0.0 0.0 5.5 0.0]},
-  :axis.ticks.y.right nil,
-  :legend.box nil,
-  :strip.text.y
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle [-90.0],
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin nil},
-  :panel.spacing [5.5],
-  :legend.background
-  {:fill nil,
-   :colour [nil],
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :strip.switch.pad.grid [2.75],
-  :axis.ticks.length.y.left nil,
-  :legend.direction nil,
-  :strip.text
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [0.8],
-   :face nil,
-   :lineheight nil,
-   :colour ["white"],
-   :vjust nil,
-   :margin [4.4 4.4 4.4 4.4]},
-  :axis.line.x.bottom nil,
-  :axis.ticks.length.x.bottom nil,
-  :axis.text.y.left nil,
-  :axis.ticks.length.x nil,
-  :plot.margin [5.5 5.5 5.5 5.5],
-  :axis.ticks.length [2.75],
-  :plot.title
-  {:hjust [0.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [1.2],
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [0.0 0.0 5.5 0.0]},
-  :axis.ticks.y nil,
-  :legend.text.align nil,
-  :legend.text
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size [0.8],
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin nil},
-  :legend.key
-  {:fill ["white"],
-   :colour [nil],
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :axis.line.y nil,
-  :axis.title.y.left nil,
-  :axis.ticks.length.x.top nil,
-  :legend.box.margin [0.0 0.0 0.0 0.0],
-  :axis.title.y.right
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle [-90.0],
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [0.0],
-   :margin [0.0 0.0 0.0 2.75]},
-  :title nil,
-  :strip.clip ["inherit"],
-  :strip.background.x nil,
-  :strip.text.x nil,
-  :strip.placement ["inside"],
-  :axis.ticks.x nil,
-  :axis.line.y.right nil,
-  :axis.title.x.bottom nil,
-  :legend.key.size [1.2],
-  :axis.text.x.top
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [0.0],
-   :margin [0.0 0.0 2.2 0.0]},
-  :panel.background
-  {:fill ["white"],
-   :colour [nil],
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :plot.tag.position ["topleft"],
-  :legend.margin [5.5 5.5 5.5 5.5],
-  :plot.title.position ["panel"],
-  :line
-  {:colour ["black"],
-   :linewidth [0.5],
-   :linetype [1.0],
-   :lineend ["butt"],
-   :arrow [false],
-   :inherit.blank [true]},
-  :strip.text.y.left
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle [90.0],
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin nil},
-  :strip.background
-  {:fill ["black"],
-   :colour nil,
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :axis.title.y
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle [90.0],
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [0.0 2.75 0.0 0.0]},
-  :legend.box.background [],
-  :panel.grid.major
-  {:colour nil,
-   :linewidth [0.1],
-   :linetype nil,
-   :lineend nil,
-   :arrow [false],
-   :inherit.blank [true]},
-  :axis.title nil,
-  :strip.text.y.right nil,
-  :legend.title.align nil,
-  :plot.background
-  {:fill nil,
-   :colour ["white"],
-   :linewidth nil,
-   :linetype nil,
-   :inherit.blank [true]},
-  :aspect.ratio nil,
-  :legend.spacing [11.0],
-  :axis.title.x
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [1.0],
-   :margin [2.75 0.0 0.0 0.0]},
-  :axis.line.x.top nil,
-  :legend.position ["right"],
-  :axis.ticks.length.y nil,
-  :axis.ticks.y.left nil,
-  :axis.ticks.length.y.right nil,
-  :legend.box.just nil,
-  :legend.title
-  {:hjust [0.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin nil},
-  :axis.text.y.right
-  {:hjust [0.0],
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust nil,
-   :margin [0.0 0.0 0.0 2.2]},
-  :axis.text.x.bottom nil,
-  :strip.background.y nil,
-  :axis.line [],
-  :rect
-  {:fill ["white"],
-   :colour ["black"],
-   :linewidth [0.5],
-   :linetype [1.0],
-   :inherit.blank [true]},
-  :legend.box.spacing [11.0],
-  :panel.grid.minor.y nil,
-  :panel.grid.minor.x nil,
-  :strip.switch.pad.wrap [2.75],
-  :axis.title.x.top
-  {:hjust nil,
-   :family nil,
-   :inherit.blank [true],
-   :debug nil,
-   :angle nil,
-   :size nil,
-   :face nil,
-   :lineheight nil,
-   :colour nil,
-   :vjust [0.0],
-   :margin [0.0 0.0 2.75 0.0]},
-  :strip.text.x.top nil,
-  :legend.spacing.y nil,
-  :text
-  {:hjust [0.5],
-   :family [""],
-   :inherit.blank [true],
-   :debug [false],
-   :angle [0.0],
-   :size [11.0],
-   :face ["plain"],
-   :lineheight [0.9],
-   :colour ["black"],
-   :vjust [0.5],
-   :margin [0.0 0.0 0.0 0.0]}},
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(data.frame(x = rnorm(1000, 2, 2)), aes(x)) +
-      geom_histogram(aes(y=..density..)) +  # scale histogram y
-      geom_density(col = 'red', size=5))"
-    r
-    plotting/plot->buffered-image)
-```
-:::
-
-```{=html}
-<img src="repesenting_files/5.png" style="width:100%;" />
-```
-
-::: {.sourceClojure}
-```clojure
-(-> "(ggplot(data.frame(x = rnorm(1000, 2, 2)), aes(x)) +
-      geom_histogram(aes(y=..density..)) +  # scale histogram y
-      geom_density(col = 'red'))"
-    r
-    ggplot->clj
-    (dissoc :data))
-```
-:::
-
-::: {.printedClojure}
-```clojure
-{:layers
- [{:aes_params [],
-   :stat
-   {:default_aes
-    {:x [~ [after_stat count]],
-     :y [~ [after_stat count]],
-     :weight [1.0]},
-    :extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x|y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping {:y [~ ..density..]},
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params {:na.rm [false], :orientation [nil]},
-   :geom
-   {:setup_data :ggproto-method,
-    :rename_size [true],
-    :non_missing_aes ["xmin" "xmax" "ymin" "ymax"],
-    :extra_params ["just" "na.rm" "orientation"],
-    :super :ggproto-method,
-    :required_aes ["x" "y"],
-    :draw_panel :ggproto-method,
-    :setup_params :ggproto-method},
-   :stat_params
-   {:binwidth nil,
-    :bins nil,
-    :na.rm [false],
-    :orientation [nil],
-    :pad [false]},
-   :constructor [geom_histogram {0 aes, :y ..density..}],
-   :position
-   {:setup_data :ggproto-method,
-    :type nil,
-    :compute_panel :ggproto-method,
-    :vjust [1.0],
-    :reverse [false],
-    :super :ggproto-method,
-    :fill [false],
-    :setup_params :ggproto-method},
-   :data []}
-  {:aes_params {:colour ["red"]},
-   :stat
-   {:default_aes
-    {:x [~ [after_stat density]],
-     :y [~ [after_stat density]],
-     :fill [nil],
-     :weight nil},
-    :extra_params ["na.rm" "orientation"],
-    :super :ggproto-method,
-    :compute_group :ggproto-method,
-    :required_aes ["x|y"],
-    :setup_params :ggproto-method,
-    :dropped_aes ["weight"]},
-   :show.legend [nil],
-   :mapping nil,
-   :super :ggproto-method,
-   :inherit.aes [true],
-   :geom_params
-   {:na.rm [false], :orientation [nil], :outline.type ["upper"]},
-   :geom
-   {:default_aes
-    {:fill [nil],
-     :weight [1.0],
-     :colour ["black"],
-     :alpha [nil],
-     :linewidth [0.5],
-     :linetype [1.0]},
-    :super :ggproto-method},
-   :stat_params {:na.rm [false], :orientation [nil]},
-   :constructor {: nil, :col ["red"]},
-   :position {:compute_layer :ggproto-method, :super :ggproto-method},
-   :data []}],
- :scales {:scales [], :super :ggproto-method},
- :mapping {:x [~ x]},
- :theme [],
- :coordinates
- {:expand [true],
-  :clip ["on"],
-  :limits {:x nil, :y nil},
-  :super :ggproto-method,
-  :default [true]},
- :facet {:shrink [true], :super :ggproto-method},
- :labels {:x ["x"], :y ["density"], :fill ["fill"], :weight ["weight"]}}
-
-```
-:::
-
 ```{=html}

### 2024-02-24 docs/projects/datavis/ggplot/comparing.qmd
ggplot - rerendered

@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x558a1755b0f0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55c9624a3570&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x558a1755b0f0&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55c9624a3570&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 

### 2024-02-24 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x558a0f256140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x55c95e987140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x558a0f256140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x55c95e987140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x558a12881bc0&gt;\n&lt;environment: 0x558a16e97e18&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55c9628d5cb8&gt;\n&lt;environment: 0x55c96a3a2bf0&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558a1288adb0&gt;\n&lt;environment: 0x558a16e97fd8&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55c9628d9698&gt;\n&lt;environment: 0x55c96a3a2d78&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558a1288dbf8&gt;\n&lt;environment: 0x558a16e98128&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55c9628debe0&gt;\n&lt;environment: 0x55c96a3a2ec8&gt;\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x558a1d274598&gt;\n&lt;environment: 0x558a1a925bb0&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55c96f403f00&gt;\n&lt;environment: 0x55c96f4046a8&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x558a1d274448&gt;\n&lt;environment: 0x558a1a925bb0&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x55c96f4040c0&gt;\n&lt;environment: 0x55c96f4046a8&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x558a1d27de98&gt;\n&lt;environment: 0x558a1d468db0&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55c96f3f51d0&gt;\n&lt;environment: 0x55c96f3ecf30&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558a1288adb0&gt;\n&lt;environment: 0x558a1d5a9ff0&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55c9628d9698&gt;\n&lt;environment: 0x55c96f3ed390&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558a1288dbf8&gt;\n&lt;environment: 0x558a1d5aa1b0&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55c9628debe0&gt;\n&lt;environment: 0x55c96f3ed4e0&gt;\n",
      :domain [1.0E-100 ##Inf]},

### 2024-02-25 docs/projects/datavis/ggplot/comparing.qmd
ggplot - rerendered

@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55c9624a3570&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x556427acf3e0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55c9624a3570&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x556427acf3e0&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 

### 2024-02-25 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x55c95e987140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x556423fbb140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x55c95e987140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x556423fbb140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55c9628d5cb8&gt;\n&lt;environment: 0x55c96a3a2bf0&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x556427f01b28&gt;\n&lt;environment: 0x5564337ddb98&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55c9628d9698&gt;\n&lt;environment: 0x55c96a3a2d78&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556427f05508&gt;\n&lt;environment: 0x5564337ddd90&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55c9628debe0&gt;\n&lt;environment: 0x55c96a3a2ec8&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556427f0aa50&gt;\n&lt;environment: 0x5564337ddee0&gt;\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55c96f403f00&gt;\n&lt;environment: 0x55c96f4046a8&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55642e5a85c8&gt;\n&lt;environment: 0x556430a69888&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x55c96f4040c0&gt;\n&lt;environment: 0x55c96f4046a8&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x55642e5a8478&gt;\n&lt;environment: 0x556430a69888&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55c96f3f51d0&gt;\n&lt;environment: 0x55c96f3ecf30&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55642e5b4280&gt;\n&lt;environment: 0x556430a64618&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55c9628d9698&gt;\n&lt;environment: 0x55c96f3ed390&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556427f05508&gt;\n&lt;environment: 0x556430a64a78&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55c9628debe0&gt;\n&lt;environment: 0x55c96f3ed4e0&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556427f0aa50&gt;\n&lt;environment: 0x556430a64c00&gt;\n",
      :domain [1.0E-100 ##Inf]},

### 2024-02-25 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: study_session_20240225.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="study_session_20240225_files/md-default3.js" type="text/javascript"></script><script src="study_session_20240225_files/md-default4.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

::: {.sourceClojure}
```clojure
(ns study-session-20240225
  (:require [clojisr.v1.r :as r :refer [r]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]
            [tablecloth.api :as tc]
            [scicloj.metamorph.ml.toydata :as toydata]
            [scicloj.metamorph.ml.toydata.ggplot :as toydata.ggplot]
            [representing]))
```
:::

# Code examples from study session 2024-02-25

Add ggplot2 to the R runtime:

::: {.sourceClojure}
```clojure
(r/library "ggplot2")
```
:::

::: {.printedClojure}
```clojure
[1] "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices" "utils"    
[7] "datasets"  "methods"   "base"

```
:::

The `mpg` dataset:

::: {.sourceClojure}
```clojure
(r "mpg")
```
:::

::: {.printedClojure}
```clojure
# A tibble: 234 × 11
   manufacturer model      displ  year   cyl trans drv     cty   hwy fl    class
   &lt;chr&gt;        &lt;chr&gt;      &lt;dbl&gt; &lt;int&gt; &lt;int&gt; &lt;chr&gt; &lt;chr&gt; &lt;int&gt; &lt;int&gt; &lt;chr&gt; &lt;chr&gt;
 1 audi         a4           1.8  1999     4 auto… f        18    29 p     comp…
 2 audi         a4           1.8  1999     4 manu… f        21    29 p     comp…
 3 audi         a4           2    2008     4 manu… f        20    31 p     comp…
 4 audi         a4           2    2008     4 auto… f        21    30 p     comp…
 5 audi         a4           2.8  1999     6 auto… f        16    26 p     comp…
 6 audi         a4           2.8  1999     6 manu… f        18    26 p     comp…
 7 audi         a4           3.1  2008     6 auto… f        18    27 p     comp…
 8 audi         a4 quattro   1.8  1999     4 manu… 4        18    26 p     comp…
 9 audi         a4 quattro   1.8  1999     4 auto… 4        16    25 p     comp…
10 audi         a4 quattro   2    2008     4 manu… 4        20    28 p     comp…
# ℹ 224 more rows

```
:::

Evaluating R and showing a plot as a bitmap image:

::: {.sourceClojure}
```clojure
(plotting/plot->buffered-image
 (r "
(ggplot(mpg, aes(x = cty, y = hwy, color = year)) +
geom_point())
"))
```
:::

```{=html}
<img src="study_session_20240225_files/0.png" style="width:100%;" />
```

Showing a plot as svg:

::: {.sourceClojure}
```clojure
(plotting/plot->svg
 (r "
(ggplot(mpg, aes(x = cty, y = hwy, color = year)) +
geom_point())
"))
```
:::

::: {.printedClojure}
```clojure
"&lt;?xml version=\"1.0\" encoding=\"UTF-8\"?&gt;\n&lt;svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\"&gt;\n&lt;defs&gt;\n&lt;g&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-7\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-8\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/&gt;\n&lt;/symbol&gt;\n&lt;/g&gt;\n&lt;clipPath id=\"clip1\"&gt;\n  &lt;path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip2\"&gt;\n  &lt;path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip3\"&gt;\n  &lt;path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip4\"&gt;\n  &lt;path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip5\"&gt;\n  &lt;path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip6\"&gt;\n  &lt;path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip7\"&gt;\n  &lt;path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip8\"&gt;\n  &lt;path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip9\"&gt;\n  &lt;path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip10\"&gt;\n  &lt;path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip11\"&gt;\n  &lt;path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip12\"&gt;\n  &lt;path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip13\"&gt;\n  &lt;path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip14\"&gt;\n  &lt;path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip15\"&gt;\n  &lt;path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip16\"&gt;\n  &lt;path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip17\"&gt;\n  &lt;path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip18\"&gt;\n  &lt;path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip19\"&gt;\n  &lt;path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip20\"&gt;\n  &lt;path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/&gt;\n&lt;/clipPath&gt;\n&lt;image id=\"image1303\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/&gt;\n&lt;pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\"&gt;\n  &lt;use xlink:href=\"#image1303\"/&gt;\n&lt;/pattern&gt;\n&lt;/defs&gt;\n&lt;g id=\"surface1299\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/&gt;\n&lt;g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/&gt;\n&lt;/g&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/&gt;\n&lt;g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/&gt;\n&lt;/g&gt;\n&lt;/svg&gt;\n"

```
:::

Use ggplot2 as a Clojure namespace:

::: {.sourceClojure}
```clojure
(r/require-r '[ggplot2 :as gg])
```
:::

::: {.printedClojure}
```clojure
nil

```
:::

The `mpg` dataset as a Clojure (tech.ml.dataset) dataset:

::: {.sourceClojure}
```clojure
toydata.ggplot/mpg
```
:::

_unnamed [234 11]:

| :manufacturer |     :model | :displ | :year | :cyl |     :trans | :drv | :cty | :hwy | :fl |     :class |
|---------------|------------|-------:|------:|-----:|------------|------|-----:|-----:|-----|------------|
|          audi |         a4 |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    compact |
|          audi |         a4 |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    compact |
|          audi |         a4 |    2.0 |  2008 |    4 | manual(m6) |    f |   20 |   31 |   p |    compact |
|          audi |         a4 |    2.0 |  2008 |    4 |   auto(av) |    f |   21 |   30 |   p |    compact |
|          audi |         a4 |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    compact |
|          audi |         a4 |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    compact |
|          audi |         a4 |    3.1 |  2008 |    6 |   auto(av) |    f |   18 |   27 |   p |    compact |
|          audi | a4 quattro |    1.8 |  1999 |    4 | manual(m5) |    4 |   18 |   26 |   p |    compact |
|          audi | a4 quattro |    1.8 |  1999 |    4 |   auto(l5) |    4 |   16 |   25 |   p |    compact |
|          audi | a4 quattro |    2.0 |  2008 |    4 | manual(m6) |    4 |   20 |   28 |   p |    compact |
|           ... |        ... |    ... |   ... |  ... |        ... |  ... |  ... |  ... | ... |        ... |
|    volkswagen | new beetle |    2.0 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   r | subcompact |
|    volkswagen | new beetle |    2.0 |  1999 |    4 |   auto(l4) |    f |   19 |   26 |   r | subcompact |
|    volkswagen | new beetle |    2.5 |  2008 |    5 | manual(m5) |    f |   20 |   28 |   r | subcompact |
|    volkswagen | new beetle |    2.5 |  2008 |    5 |   auto(s6) |    f |   20 |   29 |   r | subcompact |
|    volkswagen |     passat |    1.8 |  1999 |    4 | manual(m5) |    f |   21 |   29 |   p |    midsize |
|    volkswagen |     passat |    1.8 |  1999 |    4 |   auto(l5) |    f |   18 |   29 |   p |    midsize |
|    volkswagen |     passat |    2.0 |  2008 |    4 |   auto(s6) |    f |   19 |   28 |   p |    midsize |
|    volkswagen |     passat |    2.0 |  2008 |    4 | manual(m6) |    f |   21 |   29 |   p |    midsize |
|    volkswagen |     passat |    2.8 |  1999 |    6 |   auto(l5) |    f |   16 |   26 |   p |    midsize |
|    volkswagen |     passat |    2.8 |  1999 |    6 | manual(m5) |    f |   18 |   26 |   p |    midsize |
|    volkswagen |     passat |    3.6 |  2008 |    6 |   auto(s6) |    f |   17 |   26 |   p |    midsize |

Evaluating R code generated from the Clojure namespace,
with Clojure data.

::: {.sourceClojure}
```clojure
(-> toydata.ggplot/mpg
    (gg/ggplot (gg/aes :x 'cty
                       :y 'hwy
                       :color 'year))
    (r/r+ (gg/geom_point))
    r
    plotting/plot->buffered-image)
```
:::

```{=html}
<img src="study_session_20240225_files/1.png" style="width:100%;" />
```

Representing a ggplot plot as Clojure data:

::: {.sourceClojure}
```clojure
(-> toydata.ggplot/mpg
    (gg/ggplot (gg/aes :x 'cty
                       :y 'hwy
                       :color 'year))
    (r/r+ (gg/geom_point))
    r
    representing/ggplot->clj
    ;; (dissoc the dataset itself
    ;; to keep the structure small)
    (dissoc :data))
```
:::

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [[$ .MEM xec8790761b00443e]],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ year]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["year"]}}

```
:::

Using log scale
(keeping axis labels, changing the spacing):

::: {.sourceClojure}
```clojure
(-> toydata.ggplot/mpg
    (gg/ggplot (gg/aes :x 'cty
                       :y 'hwy
                       :color 'year))
    (r/r+ (gg/geom_point)
          (gg/scale_y_log10))
    r
    plotting/plot->buffered-image)
```
:::

```{=html}
<img src="study_session_20240225_files/2.png" style="width:100%;" />
```

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/study_session_20240225.clj">projects/datavis/ggplot/notebooks/study_session_20240225.clj</a></small></small></pre></div>
```

### 2024-02-28 docs/projects/datavis/ggplot/comparing.qmd
ggplot - rerendered

@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x556427acf3e0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55ade360f7d0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x556427acf3e0&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55ade360f7d0&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 

### 2024-02-28 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

@@
 ```clojure
+(delay
   (-> "(ggplot(mpg, aes(cty, hwy)))"
@@
       representing/ggplot->clj
-    (dissoc :data))
+      (dissoc :data)))
 ```
@@
 ```clojure
+(delay
   (-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy)))"
@@
 ```clojure
+(delay
   (-> "(ggplot(mpg, mapping=aes(x=cty, y=hwy))
@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x556423fbb140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x55addc103140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x556423fbb140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x55addc103140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x556427f01b28&gt;\n&lt;environment: 0x5564337ddb98&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55addfc71518&gt;\n&lt;environment: 0x55ade7455850&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556427f05508&gt;\n&lt;environment: 0x5564337ddd90&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55addfc78cc8&gt;\n&lt;environment: 0x55ade7455658&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556427f0aa50&gt;\n&lt;environment: 0x5564337ddee0&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55addfc85240&gt;\n&lt;environment: 0x55ade7455508&gt;\n",
      :domain [##-Inf ##Inf]},
@@
       r
-    plotting/plot->buffered-image)
+      plotting/plot->buffered-image))
 ```
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55642e5a85c8&gt;\n&lt;environment: 0x556430a69888&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55ade0f89bb0&gt;\n&lt;environment: 0x55ade6d823f0&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x55642e5a8478&gt;\n&lt;environment: 0x556430a69888&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x55ade0f89a60&gt;\n&lt;environment: 0x55ade6d823f0&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55642e5b4280&gt;\n&lt;environment: 0x556430a64618&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55ade0f93600&gt;\n&lt;environment: 0x55ade6d86770&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556427f05508&gt;\n&lt;environment: 0x556430a64a78&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55addfc78cc8&gt;\n&lt;environment: 0x55ade6d863b8&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556427f0aa50&gt;\n&lt;environment: 0x556430a64c00&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55addfc85240&gt;\n&lt;environment: 0x55ade6d86268&gt;\n",
      :domain [1.0E-100 ##Inf]},
@@
 ```clojure
+(delay
   (-> "(ggplot(data.frame(x = rnorm(1000, 2, 2)), aes(x)) +
@@
 
+# Exploring ggtrace
+
+[ggtrace](https://yjunechoe.github.io/ggtrace/) - programmatically explore, debug, and manipulate ggplot internals
+
+::: {.sourceClojure}
+```clojure
+(r/require-r '[ggtrace :as ggtrace])
+```
+:::
+
+::: {.printedClojure}
+```clojure
+nil
+
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(let [bar-plot (r "
+ggplot(mpg, aes(class, fill = class)) +
+geom_bar() +
+theme(legend.position = 'none')")]
+  (ggtrace/layer_after_stat bar-plot))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+# A tibble: 7 × 8
+  count  prop x          width flipped_aes fill       PANEL group
+  &lt;dbl&gt; &lt;dbl&gt; &lt;mppd_dsc&gt; &lt;dbl&gt; &lt;lgl&gt;       &lt;chr&gt;      &lt;fct&gt; &lt;int&gt;
+1     5     1 1            0.9 FALSE       2seater    1         1
+2    47     1 2            0.9 FALSE       compact    1         2
+3    41     1 3            0.9 FALSE       midsize    1         3
+4    11     1 4            0.9 FALSE       minivan    1         4
+5    33     1 5            0.9 FALSE       pickup     1         5
+6    35     1 6            0.9 FALSE       subcompact 1         6
+7    62     1 7            0.9 FALSE       suv        1         7
+
+```
+:::
+
 ```{=html}

### 2024-02-28 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

@@
 ```clojure
-[1] "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices" "utils"    
-[7] "datasets"  "methods"   "base"
+ [1] "ggtrace"   "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices"
+ [7] "utils"     "datasets"  "methods"   "base"
 
@@
 ```clojure
-"&lt;?xml version=\"1.0\" encoding=\"UTF-8\"?&gt;\n&lt;svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\"&gt;\n&lt;defs&gt;\n&lt;g&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-7\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-8\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/&gt;\n&lt;/symbol&gt;\n&lt;/g&gt;\n&lt;clipPath id=\"clip1\"&gt;\n  &lt;path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip2\"&gt;\n  &lt;path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip3\"&gt;\n  &lt;path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip4\"&gt;\n  &lt;path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip5\"&gt;\n  &lt;path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip6\"&gt;\n  &lt;path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip7\"&gt;\n  &lt;path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip8\"&gt;\n  &lt;path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip9\"&gt;\n  &lt;path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip10\"&gt;\n  &lt;path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip11\"&gt;\n  &lt;path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip12\"&gt;\n  &lt;path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip13\"&gt;\n  &lt;path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip14\"&gt;\n  &lt;path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip15\"&gt;\n  &lt;path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip16\"&gt;\n  &lt;path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip17\"&gt;\n  &lt;path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip18\"&gt;\n  &lt;path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip19\"&gt;\n  &lt;path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip20\"&gt;\n  &lt;path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/&gt;\n&lt;/clipPath&gt;\n&lt;image id=\"image1303\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/&gt;\n&lt;pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\"&gt;\n  &lt;use xlink:href=\"#image1303\"/&gt;\n&lt;/pattern&gt;\n&lt;/defs&gt;\n&lt;g id=\"surface1299\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/&gt;\n&lt;g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/&gt;\n&lt;/g&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/&gt;\n&lt;g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/&gt;\n&lt;/g&gt;\n&lt;/svg&gt;\n"
+"&lt;?xml version=\"1.0\" encoding=\"UTF-8\"?&gt;\n&lt;svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\"&gt;\n&lt;defs&gt;\n&lt;g&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-7\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-8\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/&gt;\n&lt;/symbol&gt;\n&lt;/g&gt;\n&lt;clipPath id=\"clip1\"&gt;\n  &lt;path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip2\"&gt;\n  &lt;path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip3\"&gt;\n  &lt;path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip4\"&gt;\n  &lt;path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip5\"&gt;\n  &lt;path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip6\"&gt;\n  &lt;path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip7\"&gt;\n  &lt;path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip8\"&gt;\n  &lt;path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip9\"&gt;\n  &lt;path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip10\"&gt;\n  &lt;path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip11\"&gt;\n  &lt;path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip12\"&gt;\n  &lt;path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip13\"&gt;\n  &lt;path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip14\"&gt;\n  &lt;path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip15\"&gt;\n  &lt;path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip16\"&gt;\n  &lt;path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip17\"&gt;\n  &lt;path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip18\"&gt;\n  &lt;path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip19\"&gt;\n  &lt;path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip20\"&gt;\n  &lt;path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/&gt;\n&lt;/clipPath&gt;\n&lt;image id=\"image249\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/&gt;\n&lt;pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\"&gt;\n  &lt;use xlink:href=\"#image249\"/&gt;\n&lt;/pattern&gt;\n&lt;/defs&gt;\n&lt;g id=\"surface245\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/&gt;\n&lt;g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/&gt;\n&lt;/g&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/&gt;\n&lt;g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/&gt;\n&lt;/g&gt;\n&lt;/svg&gt;\n"
 
@@
    :stat_params {:na.rm [false]},
-   :constructor [[$ .MEM xec8790761b00443e]],
+   :constructor [[$ .MEM xfeea946278794b6e]],
    :position {:compute_layer :ggproto-method, :super :ggproto-method},

### 2024-03-02 docs/projects/datavis/observable/codegen.qmd
observable - rendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: codegen.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="codegen_files/md-default0.js" type="text/javascript"></script><script src="codegen_files/md-default1.js" type="text/javascript"></script>

::: {.sourceClojure}
```clojure
(ns codegen
  (:require [scicloj.kindly.v4.kind :as kind]
            [clojure.string :as str]))
```
:::

# Generating Observable code

This is a draft experiment of generating [Observable](https://observablehq.com/) code from Clojure forms.

::: {.sourceClojure}
```clojure
(defn list-starting-with? [prefix form]
  (and (list? form)
       (-> form first (= prefix))))
```
:::

::: {.sourceClojure}
```clojure
(defn vector-starting-with? [prefix form]
  (and (vector? form)
       (-> form first (= prefix))))
```
:::

::: {.sourceClojure}
```clojure
(defn dot? [form]
  (list-starting-with? '. form))
```
:::

::: {.sourceClojure}
```clojure
(defn def? [form]
  (list-starting-with? 'def form))
```
:::

::: {.sourceClojure}
```clojure
(defn viewof? [form]
  (list-starting-with? 'viewof form))
```
:::

::: {.sourceClojure}
```clojure
(defn generated? [form]
  (vector-starting-with? :generated form))
```
:::

::: {.sourceClojure}
```clojure
(defn generated [string]
  (assert (string? string))
  [:generated string])
```
:::

::: {.sourceClojure}
```clojure
(defn generated->str [form]
  (second form))
```
:::

::: {.sourceClojure}
```clojure
(defn js? [form]
  (vector-starting-with? :js form))
```
:::

::: {.sourceClojure}
```clojure
(defn primitive? [form]
  (or (string? form)
      (number? form)
      (boolean? form)
      (symbol? form)))
```
:::

::: {.sourceClojure}
```clojure
(defn handle-form [form]
  (cond (generated? form) (generated->str form)
        (map? form) (->> form
                         (map (fn [[k v]]
                                (format "%s: %s"
                                        (name k) (handle-form v))))
                         (str/join ", ")
                         (format "{%s}"))
        (dot? form) (->> form
                         rest
                         (map handle-form)
                         (str/join "."))
        (def? form) (let [[lhs rhs] (rest form)]
                      (format "%s = %s"
                              (name lhs)
                              (handle-form rhs)))
        (viewof? form) (let [[lhs rhs] (rest form)]
                         (format "viewof %s = %s"
                                 (name lhs)
                                 (handle-form rhs)))
        (js? form) (-> form
                       second
                       str)
        (list? form)  (->> form
                           rest
                           (map handle-form)
                           (str/join ", ")
                           (format "%s(%s)" (-> form first name)))
        (vector? form) (->> form
                            (map handle-form)
                            (str/join ", ")
                            (format "[%s]"))
        (primitive? form) (pr-str form)))
```
:::

::: {.sourceClojure}
```clojure
(defn obs [& forms]
  (->> forms
       (map handle-form)
       (str/join "\n\n")
       kind/observable))
```
:::

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/observable/notebooks/codegen.clj">projects/datavis/observable/notebooks/codegen.clj</a></small></small></pre></div>
```

### 2024-03-02 docs/projects/datavis/observable/index.qmd
observable - rendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default0.js" type="text/javascript"></script><script src="index_files/md-default1.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

::: {.sourceClojure}
```clojure
(ns index
  (:require [codegen :refer [obs]]))
```
:::

# Observable examples

We will use the draft [codegen](./codegen) namespace.

## A basic example

Note that we read the data from a file,
that we can conveniently generate in Clojure.

We follow [a basic example]((https://quarto.org/docs/interactive/ojs/libraries.html#plot))
from Quarto's Observable docs.

::: {.sourceClojure}
```clojure
(obs
 '(def athletes
    (. (FileAttachment "notebooks/datasets/athletes.csv")
       (csv {:typed true}))))
```
:::

```{ojs}
//| echo: false
athletes = FileAttachment("notebooks/datasets/athletes.csv").csv({typed: true})
```

::: {.sourceClojure}
```clojure
(obs
 '(Plot.plot {:grid true
              :facet {:data athletes
                      :y "sex"}
              :marks [(Plot.rectY athletes
                                  (Plot.binX {:y "count"}
                                             {:x "weight" :fill "sex"}))
                      (Plot.ruleY [0])]}))
```
:::

```{ojs}
//| echo: false
Plot.plot({grid: true, facet: {data: athletes, y: "sex"}, marks: [Plot.rectY(athletes, Plot.binX({y: "count"}, {x: "weight", fill: "sex"})), Plot.ruleY([0])]})
```

## Interactions across components
Here, we reproduce
[the penguins example](https://quarto.org/docs/interactive/ojs/examples/penguins.html)
from the Quarto docs.

::: {.sourceClojure}
```clojure
(obs
 '(viewof bill_length_min
          (Inputs.range [32 50]
                        {:value 35
                         :step 1
                         :label "Bill length (min):"}))
 '(viewof islands
          (Inputs.checkbox ["Torgersen" "Biscoe" "Dream"]
                           {:value ["Torgensen" "Biscoe"]
                            :lable "Islands:"}))
 '(. (Plot.rectY filtered
                 (Plot.binX {:y "count"}
                            {:x "body_mass_g"
                             :fill "species"
                             :thresholds 20}))
     (plot {:facet {:data filtered
                    :x "sex"
                    :y "species"
                    :marginRight 80}
            :marks [(Plot.frame)]}))
 '(Inputs.table filtered)
 '(def penguins (. (FileAttachment "notebooks/datasets/palmer-penguins.csv")
                   (csv {:typed true})))
 '(def filtered (. penguins
                   (filter [:js "function(penguin) {
                                           return bill_length_min < penguin.bill_length_mm &&
                                           islands.includes(penguin.island);
                                           }"]))))
```
:::

```{ojs}
//| echo: false
viewof bill_length_min = Inputs.range([32, 50], {value: 35, step: 1, label: "Bill length (min):"})

viewof islands = Inputs.checkbox(["Torgersen", "Biscoe", "Dream"], {value: ["Torgensen", "Biscoe"], lable: "Islands:"})

Plot.rectY(filtered, Plot.binX({y: "count"}, {x: "body_mass_g", fill: "species", thresholds: 20})).plot({facet: {data: filtered, x: "sex", y: "species", marginRight: 80}, marks: [Plot.frame()]})

Inputs.table(filtered)

penguins = FileAttachment("notebooks/datasets/palmer-penguins.csv").csv({typed: true})

filtered = penguins.filter(function(penguin) {
                                           return bill_length_min < penguin.bill_length_mm &&
                                           islands.includes(penguin.island);
                                           })
```

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/observable/notebooks/index.clj">projects/datavis/observable/notebooks/index.clj</a></small></small></pre></div>
```

### 2024-03-03 docs/projects/datavis/observable/index.qmd
Observable - rerendered

@@
 
+# Observable examples - DRAFT
+
 ::: {.sourceClojure}
@@
 (ns index
-  (:require [codegen :refer [obs]]))
+  (:require [codegen :refer [obs]]
+            [scicloj.kindly.v4.kind :as kind]))
 ```
 :::
-
-# Observable examples
 
@@
 
-We follow [a basic example]((https://quarto.org/docs/interactive/ojs/libraries.html#plot))
+We follow [a basic example](https://quarto.org/docs/interactive/ojs/libraries.html#plot)
 from Quarto's Observable docs.

### 2024-03-07 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
Clay, Calva, & Noj - rerendered

@@
 <script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script>
-<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
+
+```{=html}
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+```
 
@@
 (ns index
-  (:require [scicloj.noj.v1.datasets
-             :as datasets]
+  (:require [scicloj.metamorph.ml.toydata
+             :as toydata]
             [scicloj.noj.v1.vis.hanami
@@
 
-<div style="max-height:600px;overflow-y:auto;"><iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/X_SsjhmG5Ok"></iframe></div>
+```{=html}
+<iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/X_SsjhmG5Ok"></iframe>
+```
 
@@
 ```clojure
-datasets/iris
+(def iris
+  (toydata/iris-ds))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+iris
 ```
@@
 
-| :sepal-length | :sepal-width | :petal-length | :petal-width |  :species |
-|--------------:|-------------:|--------------:|-------------:|-----------|
-|           5.1 |          3.5 |           1.4 |          0.2 |    setosa |
-|           4.9 |          3.0 |           1.4 |          0.2 |    setosa |
-|           4.7 |          3.2 |           1.3 |          0.2 |    setosa |
-|           4.6 |          3.1 |           1.5 |          0.2 |    setosa |
-|           5.0 |          3.6 |           1.4 |          0.2 |    setosa |
-|           5.4 |          3.9 |           1.7 |          0.4 |    setosa |
-|           4.6 |          3.4 |           1.4 |          0.3 |    setosa |
-|           5.0 |          3.4 |           1.5 |          0.2 |    setosa |
-|           4.4 |          2.9 |           1.4 |          0.2 |    setosa |
-|           4.9 |          3.1 |           1.5 |          0.1 |    setosa |
+| :sepal_length | :sepal_width | :petal_length | :petal_width | :species |
+|--------------:|-------------:|--------------:|-------------:|---------:|
+|           5.1 |          3.5 |           1.4 |          0.2 |        0 |
+|           4.9 |          3.0 |           1.4 |          0.2 |        0 |
+|           4.7 |          3.2 |           1.3 |          0.2 |        0 |
+|           4.6 |          3.1 |           1.5 |          0.2 |        0 |
+|           5.0 |          3.6 |           1.4 |          0.2 |        0 |
+|           5.4 |          3.9 |           1.7 |          0.4 |        0 |
+|           4.6 |          3.4 |           1.4 |          0.3 |        0 |
+|           5.0 |          3.4 |           1.5 |          0.2 |        0 |
+|           4.4 |          2.9 |           1.4 |          0.2 |        0 |
+|           4.9 |          3.1 |           1.5 |          0.1 |        0 |
 |           ... |          ... |           ... |          ... |      ... |
-|           6.9 |          3.1 |           5.4 |          2.1 | virginica |
-|           6.7 |          3.1 |           5.6 |          2.4 | virginica |
-|           6.9 |          3.1 |           5.1 |          2.3 | virginica |
-|           5.8 |          2.7 |           5.1 |          1.9 | virginica |
-|           6.8 |          3.2 |           5.9 |          2.3 | virginica |
-|           6.7 |          3.3 |           5.7 |          2.5 | virginica |
-|           6.7 |          3.0 |           5.2 |          2.3 | virginica |
-|           6.3 |          2.5 |           5.0 |          1.9 | virginica |
-|           6.5 |          3.0 |           5.2 |          2.0 | virginica |
-|           6.2 |          3.4 |           5.4 |          2.3 | virginica |
-|           5.9 |          3.0 |           5.1 |          1.8 | virginica |
+|           6.9 |          3.1 |           5.4 |          2.1 |        1 |
+|           6.7 |          3.1 |           5.6 |          2.4 |        1 |
+|           6.9 |          3.1 |           5.1 |          2.3 |        1 |
+|           5.8 |          2.7 |           5.1 |          1.9 |        1 |
+|           6.8 |          3.2 |           5.9 |          2.3 |        1 |
+|           6.7 |          3.3 |           5.7 |          2.5 |        1 |
+|           6.7 |          3.0 |           5.2 |          2.3 |        1 |
+|           6.3 |          2.5 |           5.0 |          1.9 |        1 |
+|           6.5 |          3.0 |           5.2 |          2.0 |        1 |
+|           6.2 |          3.4 |           5.4 |          2.3 |        1 |
+|           5.9 |          3.0 |           5.1 |          1.8 |        1 |
 
@@
 ```clojure
-(-> datasets/iris
-    kind/table)
+(-> iris
+    (kind/table {:element/max-height "500px"}))
 ```
@@
 
-<div style="max-height:600px;overflow-y:auto;"><table class="table"><thead><tr><th>sepal-length</th><th>sepal-width</th><th>petal-length</th><th>petal-width</th><th>species</th></tr></thead><tbody><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.3</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.0</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.5</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.6</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.3</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>7.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.7</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>6.0</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.7</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>6.3</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.6</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.3</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>6.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.9</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.2</p></div></td><td><div><p>6.0</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.9</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.4</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.6</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr></tbody></table></div>
+```{=html}
+<div style="max-height:500px;overflow-y:auto;"><table class="table table-hover table-responsive"><thead><tr><th>:sepal_length</th><th>:sepal_width</th><th>:petal_length</th><th>:petal_width</th><th>:species</th></tr></thead><tbody><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="3.5"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.9"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.7"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.6"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="3.6"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.4"></span></td><td><span data-qmd="3.9"></span></td><td><span data-qmd="1.7"></span></td><td><span data-qmd="0.4"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.6"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.3"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.4"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.9"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.1"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.4"></span></td><td><span data-qmd="3.7"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.8"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.8"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.1"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.3"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="1.1"></span></td><td><span data-qmd="0.1"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.8"></span></td><td><span data-qmd="4.0"></span></td><td><span data-qmd="1.2"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.7"></span></td><td><span data-qmd="4.4"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.4"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.4"></span></td><td><span data-qmd="3.9"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="0.4"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="3.5"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.3"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.7"></span></td><td><span data-qmd="3.8"></span></td><td><span data-qmd="1.7"></span></td><td><span data-qmd="0.3"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="3.8"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.3"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.4"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.7"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="3.7"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.4"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.6"></span></td><td><span data-qmd="3.6"></span></td><td><span data-qmd="1.0"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="3.3"></span></td><td><span data-qmd="1.7"></span></td><td><span data-qmd="0.5"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.8"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.9"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="0.4"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.2"></span></td><td><span data-qmd="3.5"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.2"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.7"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.8"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.4"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.4"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.2"></span></td><td><span data-qmd="4.1"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.1"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.5"></span></td><td><span data-qmd="4.2"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.9"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="1.2"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.5"></span></td><td><span data-qmd="3.5"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.9"></span></td><td><span data-qmd="3.6"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.1"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.4"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="3.5"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="0.3"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.5"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="0.3"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.4"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="3.5"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="0.6"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="3.8"></span></td><td><span data-qmd="1.9"></span></td><td><span data-qmd="0.4"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.8"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.3"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="3.8"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="4.6"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.3"></span></td><td><span data-qmd="3.7"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="3.3"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="0.2"></span></td><td><span data-qmd="0"></span></td></tr><tr><td><span data-qmd="7.0"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="4.7"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.4"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="4.5"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.9"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="4.9"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.5"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="4.0"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.5"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="4.6"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.7"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="4.5"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="3.3"></span></td><td><span data-qmd="4.7"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="4.9"></span></td><td><span data-qmd="2.4"></span></td><td><span data-qmd="3.3"></span></td><td><span data-qmd="1.0"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.6"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="4.6"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.2"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="3.9"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="2.0"></span></td><td><span data-qmd="3.5"></span></td><td><span data-qmd="1.0"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.9"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.2"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.0"></span></td><td><span data-qmd="2.2"></span></td><td><span data-qmd="4.0"></span></td><td><span data-qmd="1.0"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.1"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="4.7"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.6"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="3.6"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.7"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="4.4"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.6"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.5"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.8"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="4.1"></span></td><td><span data-qmd="1.0"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.2"></span></td><td><span data-qmd="2.2"></span></td><td><span data-qmd="4.5"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.6"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="3.9"></span></td><td><span data-qmd="1.1"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.9"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="4.8"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.1"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="4.0"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="4.9"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.1"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="4.7"></span></td><td><span data-qmd="1.2"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.4"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="4.3"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.6"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.4"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.8"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="4.8"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.7"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.0"></span></td><td><span data-qmd="1.7"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.0"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="4.5"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.7"></span></td><td><span data-qmd="2.6"></span></td><td><span data-qmd="3.5"></span></td><td><span data-qmd="1.0"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.5"></span></td><td><span data-qmd="2.4"></span></td><td><span data-qmd="3.8"></span></td><td><span data-qmd="1.1"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.5"></span></td><td><span data-qmd="2.4"></span></td><td><span data-qmd="3.7"></span></td><td><span data-qmd="1.0"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.8"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="3.9"></span></td><td><span data-qmd="1.2"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.0"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="5.1"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.4"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.5"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.0"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="4.5"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.7"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="4.7"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="4.4"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.6"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.1"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.5"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="4.0"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.5"></span></td><td><span data-qmd="2.6"></span></td><td><span data-qmd="4.4"></span></td><td><span data-qmd="1.2"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.1"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.6"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.8"></span></td><td><span data-qmd="2.6"></span></td><td><span data-qmd="4.0"></span></td><td><span data-qmd="1.2"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.0"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="3.3"></span></td><td><span data-qmd="1.0"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.6"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="4.2"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.7"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.2"></span></td><td><span data-qmd="1.2"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.7"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="4.2"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.2"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="4.3"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.1"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="1.1"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="5.7"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="4.1"></span></td><td><span data-qmd="1.3"></span></td><td><span data-qmd="2"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="3.3"></span></td><td><span data-qmd="6.0"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="5.8"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="5.1"></span></td><td><span data-qmd="1.9"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.1"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.9"></span></td><td><span data-qmd="2.1"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="5.6"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.5"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.8"></span></td><td><span data-qmd="2.2"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.6"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="6.6"></span></td><td><span data-qmd="2.1"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="4.9"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="4.5"></span></td><td><span data-qmd="1.7"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.3"></span></td><td><span data-qmd="2.9"></span></td><td><span data-qmd="6.3"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.7"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="5.8"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.2"></span></td><td><span data-qmd="3.6"></span></td><td><span data-qmd="6.1"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.5"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="5.1"></span></td><td><span data-qmd="2.0"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.4"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="5.3"></span></td><td><span data-qmd="1.9"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.8"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.5"></span></td><td><span data-qmd="2.1"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="5.7"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="5.0"></span></td><td><span data-qmd="2.0"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="5.8"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="5.1"></span></td><td><span data-qmd="2.4"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.4"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="5.3"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.5"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.5"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.7"></span></td><td><span data-qmd="3.8"></span></td><td><span data-qmd="6.7"></span></td><td><span data-qmd="2.2"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.7"></span></td><td><span data-qmd="2.6"></span></td><td><span data-qmd="6.9"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.0"></span></td><td><span data-qmd="2.2"></span></td><td><span data-qmd="5.0"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.9"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="5.7"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="5.6"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="4.9"></span></td><td><span data-qmd="2.0"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.7"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="6.7"></span></td><td><span data-qmd="2.0"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="4.9"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.7"></span></td><td><span data-qmd="3.3"></span></td><td><span data-qmd="5.7"></span></td><td><span data-qmd="2.1"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.2"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="6.0"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.2"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="4.8"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.1"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.9"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.4"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="5.6"></span></td><td><span data-qmd="2.1"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.2"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.8"></span></td><td><span data-qmd="1.6"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.4"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="6.1"></span></td><td><span data-qmd="1.9"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.9"></span></td><td><span data-qmd="3.8"></span></td><td><span data-qmd="6.4"></span></td><td><span data-qmd="2.0"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.4"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="5.6"></span></td><td><span data-qmd="2.2"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="2.8"></span></td><td><span data-qmd="5.1"></span></td><td><span data-qmd="1.5"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.1"></span></td><td><span data-qmd="2.6"></span></td><td><span data-qmd="5.6"></span></td><td><span data-qmd="1.4"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="7.7"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="6.1"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="5.6"></span></td><td><span data-qmd="2.4"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.4"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="5.5"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.0"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="4.8"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.9"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="5.4"></span></td><td><span data-qmd="2.1"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.7"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="5.6"></span></td><td><span data-qmd="2.4"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.9"></span></td><td><span data-qmd="3.1"></span></td><td><span data-qmd="5.1"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="5.8"></span></td><td><span data-qmd="2.7"></span></td><td><span data-qmd="5.1"></span></td><td><span data-qmd="1.9"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.8"></span></td><td><span data-qmd="3.2"></span></td><td><span data-qmd="5.9"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.7"></span></td><td><span data-qmd="3.3"></span></td><td><span data-qmd="5.7"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.7"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.2"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.3"></span></td><td><span data-qmd="2.5"></span></td><td><span data-qmd="5.0"></span></td><td><span data-qmd="1.9"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.5"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.2"></span></td><td><span data-qmd="2.0"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="6.2"></span></td><td><span data-qmd="3.4"></span></td><td><span data-qmd="5.4"></span></td><td><span data-qmd="2.3"></span></td><td><span data-qmd="1"></span></td></tr><tr><td><span data-qmd="5.9"></span></td><td><span data-qmd="3.0"></span></td><td><span data-qmd="5.1"></span></td><td><span data-qmd="1.8"></span></td><td><span data-qmd="1"></span></td></tr></tbody></table></div>
+```
 
@@
 ```clojure
-(-> datasets/iris
+(-> iris
     (hanami/linear-regression-plot
-     :petal-length
-     :petal-width
+     :petal_length
+     :petal_width
      {:line-options {:MCOLOR "brown"
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div></div>
+```{=html}
+<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal_length","type":"quantitative"},"x":{"field":"petal_width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal_length-prediction","type":"quantitative","axis":{"title":"petal_length"}},"opacity":{"value":0.5},"x":{"field":"petal_width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>
+```
 
+```{=html}
 <div style="background-color:grey;height:2px;width:100%;"></div>
+```
 
+```{=html}
 <div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj">projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj</a></small></small></pre></div>
+```

### 2024-03-15 docs/projects/datavis/ggplot/comparing.qmd
ggplot - rerendered

@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: comparing.html}
+  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: comparing.html}
 code-block-background: true
@@
 }
+</style><style>.clay-limit-image-width .clay-image {max-width: 100%}
 </style>
@@
 
+::: {.clay-image}
+
 ```{=html}
-<img src="comparing_files/0.png" style="width:100%;" />
+<img src="comparing_files/0.png" />
 ```
+
+:::
 
@@
 
+::: {.printedClojure}
+```clojure
+nil
+
+```
+:::
+
 ```{=html}
@@
 
+::: {.clay-image}
+
 ```{=html}
-<img src="comparing_files/1.png" style="width:100%;" />
+<img src="comparing_files/1.png" />
 ```
+
+:::
 
@@
 
+::: {.clay-image}
+
 ```{=html}
-<img src="comparing_files/2.png" style="width:100%;" />
+<img src="comparing_files/2.png" />
 ```
+
+:::
 
@@
 
+::: {.clay-image}
+
 ```{=html}
-<img src="comparing_files/3.png" style="width:100%;" />
+<img src="comparing_files/3.png" />
 ```
+
+:::
 
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55ade360f7d0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x64571c465368&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55ade360f7d0&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x64571c465368&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 

### 2024-03-15 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: draft.html}
+  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: draft.html}
 code-block-background: true
@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x55addc103140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x64571892e140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x55addc103140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x64571892e140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x55addfc71518&gt;\n&lt;environment: 0x55ade7455850&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x64571c897ab0&gt;\n&lt;environment: 0x6457297906a8&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55addfc78cc8&gt;\n&lt;environment: 0x55ade7455658&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x64571c89d3b0&gt;\n&lt;environment: 0x645729790830&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55addfc85240&gt;\n&lt;environment: 0x55ade7455508&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x64571c8a09d8&gt;\n&lt;environment: 0x645729790980&gt;\n",
      :domain [##-Inf ##Inf]},
@@
 
+::: {.clay-image}
+
 ```{=html}
-<img src="draft_files/0.png" style="width:100%;" />
+<img src="draft_files/0.png" />
 ```
+
+:::
 
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55ade0f89bb0&gt;\n&lt;environment: 0x55ade6d823f0&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x645722073738&gt;\n&lt;environment: 0x64572227d608&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x55ade0f89a60&gt;\n&lt;environment: 0x55ade6d823f0&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x645722073888&gt;\n&lt;environment: 0x64572227d608&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55ade0f93600&gt;\n&lt;environment: 0x55ade6d86770&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x645721fbb9d8&gt;\n&lt;environment: 0x645722279368&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x55addfc78cc8&gt;\n&lt;environment: 0x55ade6d863b8&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x64571c89d3b0&gt;\n&lt;environment: 0x645722279800&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x55addfc85240&gt;\n&lt;environment: 0x55ade6d86268&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x64571c8a09d8&gt;\n&lt;environment: 0x645722279950&gt;\n",
      :domain [1.0E-100 ##Inf]},
@@
 
+::: {.clay-image}
+
 ```{=html}
-<img src="draft_files/1.png" style="width:100%;" />
+<img src="draft_files/1.png" />
 ```
+
+:::
 

### 2024-03-15 docs/projects/datavis/ggplot/index.qmd
ggplot - rerendered

@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
+  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: index.html}
 code-block-background: true

### 2024-03-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: study_session_20240225.html}
+  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: study_session_20240225.html}
 code-block-background: true
@@
 }
+</style><style>.clay-limit-image-width .clay-image {max-width: 100%}
 </style>
-<script src="study_session_20240225_files/md-default3.js" type="text/javascript"></script><script src="study_session_20240225_files/md-default4.js" type="text/javascript"></script>
+<script src="study_session_20240225_files/md-default2.js" type="text/javascript"></script><script src="study_session_20240225_files/md-default3.js" type="text/javascript"></script>
 
@@
 
+::: {.clay-image}
+
 ```{=html}
-<img src="study_session_20240225_files/0.png" style="width:100%;" />
+<img src="study_session_20240225_files/0.png" />
 ```
+
+:::
 
@@
 ```clojure
-"&lt;?xml version=\"1.0\" encoding=\"UTF-8\"?&gt;\n&lt;svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\"&gt;\n&lt;defs&gt;\n&lt;g&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-7\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-8\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/&gt;\n&lt;/symbol&gt;\n&lt;/g&gt;\n&lt;clipPath id=\"clip1\"&gt;\n  &lt;path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip2\"&gt;\n  &lt;path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip3\"&gt;\n  &lt;path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip4\"&gt;\n  &lt;path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip5\"&gt;\n  &lt;path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip6\"&gt;\n  &lt;path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip7\"&gt;\n  &lt;path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip8\"&gt;\n  &lt;path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip9\"&gt;\n  &lt;path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip10\"&gt;\n  &lt;path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip11\"&gt;\n  &lt;path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip12\"&gt;\n  &lt;path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip13\"&gt;\n  &lt;path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip14\"&gt;\n  &lt;path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip15\"&gt;\n  &lt;path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip16\"&gt;\n  &lt;path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip17\"&gt;\n  &lt;path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip18\"&gt;\n  &lt;path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip19\"&gt;\n  &lt;path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip20\"&gt;\n  &lt;path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/&gt;\n&lt;/clipPath&gt;\n&lt;image id=\"image249\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/&gt;\n&lt;pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\"&gt;\n  &lt;use xlink:href=\"#image249\"/&gt;\n&lt;/pattern&gt;\n&lt;/defs&gt;\n&lt;g id=\"surface245\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/&gt;\n&lt;g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/&gt;\n&lt;/g&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/&gt;\n&lt;g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/&gt;\n&lt;/g&gt;\n&lt;/svg&gt;\n"
+"&lt;?xml version=\"1.0\" encoding=\"UTF-8\"?&gt;\n&lt;svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\"&gt;\n&lt;defs&gt;\n&lt;g&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-7\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-8\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/&gt;\n&lt;/symbol&gt;\n&lt;/g&gt;\n&lt;clipPath id=\"clip1\"&gt;\n  &lt;path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip2\"&gt;\n  &lt;path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip3\"&gt;\n  &lt;path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip4\"&gt;\n  &lt;path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip5\"&gt;\n  &lt;path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip6\"&gt;\n  &lt;path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip7\"&gt;\n  &lt;path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip8\"&gt;\n  &lt;path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip9\"&gt;\n  &lt;path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip10\"&gt;\n  &lt;path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip11\"&gt;\n  &lt;path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip12\"&gt;\n  &lt;path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip13\"&gt;\n  &lt;path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip14\"&gt;\n  &lt;path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip15\"&gt;\n  &lt;path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip16\"&gt;\n  &lt;path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip17\"&gt;\n  &lt;path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip18\"&gt;\n  &lt;path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip19\"&gt;\n  &lt;path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip20\"&gt;\n  &lt;path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/&gt;\n&lt;/clipPath&gt;\n&lt;image id=\"image459\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/&gt;\n&lt;pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\"&gt;\n  &lt;use xlink:href=\"#image459\"/&gt;\n&lt;/pattern&gt;\n&lt;/defs&gt;\n&lt;g id=\"surface455\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/&gt;\n&lt;g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/&gt;\n&lt;/g&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/&gt;\n&lt;g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/&gt;\n&lt;/g&gt;\n&lt;/svg&gt;\n"
 
@@
 
+::: {.clay-dataset}
 _unnamed [234 11]:
@@
 
+:::
+
 Evaluating R code generated from the Clojure namespace,
@@
 
+::: {.clay-image}
+
 ```{=html}
-<img src="study_session_20240225_files/1.png" style="width:100%;" />
+<img src="study_session_20240225_files/1.png" />
 ```
+
+:::
 
@@
    :stat_params {:na.rm [false]},
-   :constructor [[$ .MEM xfeea946278794b6e]],
+   :constructor [[$ .MEM x861a15f64ba24c00]],
    :position {:compute_layer :ggproto-method, :super :ggproto-method},
@@
 Using log scale
-(keeping axis labels, changing the spacing):
+(keeping axis labels,
+changing the spacing):
 
@@
                        :color 'year))
-    (r/r+ (gg/geom_point)
+    (r/r+ (gg/geom_point :size 5)
           (gg/scale_y_log10))
     r
-    plotting/plot->buffered-image)
+    plotting/plot->svg
+    kind/html)
 ```
@@
 ```{=html}
-<img src="study_session_20240225_files/2.png" style="width:100%;" />
+<?xml version="1.0" encoding="UTF-8"?>
+<svg xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink" width="504pt" height="504pt" viewBox="0 0 504 504" version="1.1">
+<defs>
+<g>
+<symbol overflow="visible" id="glyph0-0">
+<path style="stroke:none;" d=""/>
+</symbol>
+<symbol overflow="visible" id="glyph0-1">
+<path style="stroke:none;" d="M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 "/>
+</symbol>
+<symbol overflow="visible" id="glyph0-2">
+<path style="stroke:none;" d="M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 "/>
+</symbol>
+<symbol overflow="visible" id="glyph0-3">
+<path style="stroke:none;" d="M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 "/>
+</symbol>
+<symbol overflow="visible" id="glyph0-4">
+<path style="stroke:none;" d="M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 "/>
+</symbol>
+<symbol overflow="visible" id="glyph0-5">
+<path style="stroke:none;" d="M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 "/>
+</symbol>
+<symbol overflow="visible" id="glyph0-6">
+<path style="stroke:none;" d="M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 "/>
+</symbol>
+<symbol overflow="visible" id="glyph0-7">
+<path style="stroke:none;" d="M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 "/>
+</symbol>
+<symbol overflow="visible" id="glyph0-8">
+<path style="stroke:none;" d="M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 "/>
+</symbol>
+<symbol overflow="visible" id="glyph1-0">
+<path style="stroke:none;" d=""/>
+</symbol>
+<symbol overflow="visible" id="glyph1-1">
+<path style="stroke:none;" d="M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 "/>
+</symbol>
+<symbol overflow="visible" id="glyph1-2">
+<path style="stroke:none;" d="M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 "/>
+</symbol>
+<symbol overflow="visible" id="glyph1-3">
+<path style="stroke:none;" d="M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 "/>
+</symbol>
+<symbol overflow="visible" id="glyph1-4">
+<path style="stroke:none;" d="M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 "/>
+</symbol>
+<symbol overflow="visible" id="glyph1-5">
+<path style="stroke:none;" d="M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 "/>
+</symbol>
+<symbol overflow="visible" id="glyph1-6">
+<path style="stroke:none;" d="M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 "/>
+</symbol>
+<symbol overflow="visible" id="glyph2-0">
+<path style="stroke:none;" d=""/>
+</symbol>
+<symbol overflow="visible" id="glyph2-1">
+<path style="stroke:none;" d="M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 "/>
+</symbol>
+<symbol overflow="visible" id="glyph2-2">
+<path style="stroke:none;" d="M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 "/>
+</symbol>
+<symbol overflow="visible" id="glyph2-3">
+<path style="stroke:none;" d="M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 "/>
+</symbol>
+</g>
+<clipPath id="clip1">
+  <path d="M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 "/>
+</clipPath>
+<clipPath id="clip2">
+  <path d="M 35.152344 414 L 433.84375 414 L 433.84375 415 L 35.152344 415 Z M 35.152344 414 "/>
+</clipPath>
+<clipPath id="clip3">
+  <path d="M 35.152344 348 L 433.84375 348 L 433.84375 349 L 35.152344 349 Z M 35.152344 348 "/>
+</clipPath>
+<clipPath id="clip4">
+  <path d="M 35.152344 216 L 433.84375 216 L 433.84375 218 L 35.152344 218 Z M 35.152344 216 "/>
+</clipPath>
+<clipPath id="clip5">
+  <path d="M 35.152344 104 L 433.84375 104 L 433.84375 105 L 35.152344 105 Z M 35.152344 104 "/>
+</clipPath>
+<clipPath id="clip6">
+  <path d="M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 "/>
+</clipPath>
+<clipPath id="clip7">
+  <path d="M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 "/>
+</clipPath>
+<clipPath id="clip8">
+  <path d="M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 "/>
+</clipPath>
+<clipPath id="clip9">
+  <path d="M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 "/>
+</clipPath>
+<clipPath id="clip10">
+  <path d="M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 "/>
+</clipPath>
+<clipPath id="clip11">
+  <path d="M 35.152344 282 L 433.84375 282 L 433.84375 284 L 35.152344 284 Z M 35.152344 282 "/>
+</clipPath>
+<clipPath id="clip12">
+  <path d="M 35.152344 150 L 433.84375 150 L 433.84375 152 L 35.152344 152 Z M 35.152344 150 "/>
+</clipPath>
+<clipPath id="clip13">
+  <path d="M 35.152344 57 L 433.84375 57 L 433.84375 59 L 35.152344 59 Z M 35.152344 57 "/>
+</clipPath>
+<clipPath id="clip14">
+  <path d="M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 "/>
+</clipPath>
+<clipPath id="clip15">
+  <path d="M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 "/>
+</clipPath>
+<clipPath id="clip16">
+  <path d="M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 "/>
+</clipPath>
+<clipPath id="clip17">
+  <path d="M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 "/>
+</clipPath>
+<clipPath id="clip18">
+  <path d="M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 "/>
+</clipPath>
+<clipPath id="clip19">
+  <path d="M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 "/>
+</clipPath>
+<clipPath id="clip20">
+  <path d="M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 "/>
+</clipPath>
+<image id="image486" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
+<pattern id="pattern0" patternUnits="userSpaceOnUse" width="1" height="300"  patternTransform="matrix(17.28,0,0,0.288,450.281644,203.20411)">
+  <use xlink:href="#image486"/>
+</pattern>
+</defs>
+<g id="surface482">
+<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
+<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 "/>
+<g clip-path="url(#clip1)" clip-rule="nonzero">
+<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 "/>
+</g>
+<g clip-path="url(#clip2)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 414.507812 L 433.84375 414.507812 "/>
+</g>
+<g clip-path="url(#clip3)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 348.636719 L 433.84375 348.636719 "/>
+</g>
+<g clip-path="url(#clip4)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 216.898438 L 433.84375 216.898438 "/>
+</g>
+<g clip-path="url(#clip5)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 104.289062 L 433.84375 104.289062 "/>
+</g>
+<g clip-path="url(#clip6)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 102.0625 469.847656 L 102.0625 5.480469 "/>
+</g>
+<g clip-path="url(#clip7)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 171.765625 469.847656 L 171.765625 5.480469 "/>
+</g>
+<g clip-path="url(#clip8)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 241.46875 469.847656 L 241.46875 5.480469 "/>
+</g>
+<g clip-path="url(#clip9)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 311.167969 469.847656 L 311.167969 5.480469 "/>
+</g>
+<g clip-path="url(#clip10)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 380.871094 469.847656 L 380.871094 5.480469 "/>
+</g>
+<g clip-path="url(#clip11)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 282.765625 L 433.84375 282.765625 "/>
+</g>
+<g clip-path="url(#clip12)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 151.027344 L 433.84375 151.027344 "/>
+</g>
+<g clip-path="url(#clip13)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 57.554688 L 433.84375 57.554688 "/>
+</g>
+<g clip-path="url(#clip14)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.214844 469.847656 L 67.214844 5.480469 "/>
+</g>
+<g clip-path="url(#clip15)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 136.914062 469.847656 L 136.914062 5.480469 "/>
+</g>
+<g clip-path="url(#clip16)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 206.617188 469.847656 L 206.617188 5.480469 "/>
+</g>
+<g clip-path="url(#clip17)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 276.316406 469.847656 L 276.316406 5.480469 "/>
+</g>
+<g clip-path="url(#clip18)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 346.019531 469.847656 L 346.019531 5.480469 "/>
+</g>
+<g clip-path="url(#clip19)" clip-rule="nonzero">
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 415.722656 469.847656 L 415.722656 5.480469 "/>
+</g>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 162.042969 C 184.425781 165.183594 181.878906 167.730469 178.734375 167.730469 C 175.59375 167.730469 173.046875 165.183594 173.046875 162.042969 C 173.046875 158.898438 175.59375 156.351562 178.734375 156.351562 C 181.878906 156.351562 184.425781 158.898438 184.425781 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 140.371094 C 212.304688 143.515625 209.757812 146.0625 206.617188 146.0625 C 203.472656 146.0625 200.925781 143.515625 200.925781 140.371094 C 200.925781 137.230469 203.472656 134.683594 206.617188 134.683594 C 209.757812 134.683594 212.304688 137.230469 212.304688 140.371094 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 151.027344 C 226.246094 154.167969 223.699219 156.714844 220.558594 156.714844 C 217.414062 156.714844 214.867188 154.167969 214.867188 151.027344 C 214.867188 147.882812 217.414062 145.335938 220.558594 145.335938 C 223.699219 145.335938 226.246094 147.882812 226.246094 151.027344 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 197.523438 C 156.542969 200.664062 153.996094 203.210938 150.855469 203.210938 C 147.714844 203.210938 145.164062 200.664062 145.164062 197.523438 C 145.164062 194.378906 147.714844 191.832031 150.855469 191.832031 C 153.996094 191.832031 156.542969 194.378906 156.542969 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 185.257812 C 184.425781 188.402344 181.878906 190.949219 178.734375 190.949219 C 175.59375 190.949219 173.046875 188.402344 173.046875 185.257812 C 173.046875 182.117188 175.59375 179.570312 178.734375 179.570312 C 181.878906 179.570312 184.425781 182.117188 184.425781 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 210.265625 C 156.542969 213.40625 153.996094 215.953125 150.855469 215.953125 C 147.714844 215.953125 145.164062 213.40625 145.164062 210.265625 C 145.164062 207.125 147.714844 204.574219 150.855469 204.574219 C 153.996094 204.574219 156.542969 207.125 156.542969 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 173.441406 C 212.304688 176.585938 209.757812 179.132812 206.617188 179.132812 C 203.472656 179.132812 200.925781 176.585938 200.925781 173.441406 C 200.925781 170.300781 203.472656 167.753906 206.617188 167.753906 C 209.757812 167.753906 212.304688 170.300781 212.304688 173.441406 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 185.257812 C 198.367188 188.402344 195.816406 190.949219 192.675781 190.949219 C 189.535156 190.949219 186.988281 188.402344 186.988281 185.257812 C 186.988281 182.117188 189.535156 179.570312 192.675781 179.570312 C 195.816406 179.570312 198.367188 182.117188 198.367188 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 210.265625 C 142.605469 213.40625 140.058594 215.953125 136.914062 215.953125 C 133.773438 215.953125 131.226562 213.40625 131.226562 210.265625 C 131.226562 207.125 133.773438 204.574219 136.914062 204.574219 C 140.058594 204.574219 142.605469 207.125 142.605469 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 210.265625 C 170.484375 213.40625 167.9375 215.953125 164.796875 215.953125 C 161.652344 215.953125 159.105469 213.40625 159.105469 210.265625 C 159.105469 207.125 161.652344 204.574219 164.796875 204.574219 C 167.9375 204.574219 170.484375 207.125 170.484375 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 210.265625 C 170.484375 213.40625 167.9375 215.953125 164.796875 215.953125 C 161.652344 215.953125 159.105469 213.40625 159.105469 210.265625 C 159.105469 207.125 161.652344 204.574219 164.796875 204.574219 C 167.9375 204.574219 170.484375 207.125 170.484375 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 210.265625 C 142.605469 213.40625 140.058594 215.953125 136.914062 215.953125 C 133.773438 215.953125 131.226562 213.40625 131.226562 210.265625 C 131.226562 207.125 133.773438 204.574219 136.914062 204.574219 C 140.058594 204.574219 142.605469 207.125 142.605469 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 223.527344 C 142.605469 226.671875 140.058594 229.21875 136.914062 229.21875 C 133.773438 229.21875 131.226562 226.671875 131.226562 223.527344 C 131.226562 220.386719 133.773438 217.839844 136.914062 217.839844 C 140.058594 217.839844 142.605469 220.386719 142.605469 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 210.265625 C 170.484375 213.40625 167.9375 215.953125 164.796875 215.953125 C 161.652344 215.953125 159.105469 213.40625 159.105469 210.265625 C 159.105469 207.125 161.652344 204.574219 164.796875 204.574219 C 167.9375 204.574219 170.484375 207.125 170.484375 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 237.355469 C 156.542969 240.5 153.996094 243.046875 150.855469 243.046875 C 147.714844 243.046875 145.164062 240.5 145.164062 237.355469 C 145.164062 234.214844 147.714844 231.667969 150.855469 231.667969 C 153.996094 231.667969 156.542969 234.214844 156.542969 237.355469 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 282.765625 C 128.664062 285.910156 126.117188 288.457031 122.972656 288.457031 C 119.832031 288.457031 117.285156 285.910156 117.285156 282.765625 C 117.285156 279.625 119.832031 277.078125 122.972656 277.078125 C 126.117188 277.078125 128.664062 279.625 128.664062 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 282.765625 C 128.664062 285.910156 126.117188 288.457031 122.972656 288.457031 C 119.832031 288.457031 117.285156 285.910156 117.285156 282.765625 C 117.285156 279.625 119.832031 277.078125 122.972656 277.078125 C 126.117188 277.078125 128.664062 279.625 128.664062 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.78125 335.570312 C 100.78125 338.714844 98.234375 341.261719 95.09375 341.261719 C 91.953125 341.261719 89.40625 338.714844 89.40625 335.570312 C 89.40625 332.429688 91.953125 329.882812 95.09375 329.882812 C 98.234375 329.882812 100.78125 332.429688 100.78125 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 197.523438 C 156.542969 200.664062 153.996094 203.210938 150.855469 203.210938 C 147.714844 203.210938 145.164062 200.664062 145.164062 197.523438 C 145.164062 194.378906 147.714844 191.832031 150.855469 191.832031 C 153.996094 191.832031 156.542969 194.378906 156.542969 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 237.355469 C 142.605469 240.5 140.058594 243.046875 136.914062 243.046875 C 133.773438 243.046875 131.226562 240.5 131.226562 237.355469 C 131.226562 234.214844 133.773438 231.667969 136.914062 231.667969 C 140.058594 231.667969 142.605469 234.214844 142.605469 237.355469 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 197.523438 C 156.542969 200.664062 153.996094 203.210938 150.855469 203.210938 C 147.714844 203.210938 145.164062 200.664062 145.164062 197.523438 C 145.164062 194.378906 147.714844 191.832031 150.855469 191.832031 C 153.996094 191.832031 156.542969 194.378906 156.542969 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 210.265625 C 142.605469 213.40625 140.058594 215.953125 136.914062 215.953125 C 133.773438 215.953125 131.226562 213.40625 131.226562 210.265625 C 131.226562 207.125 133.773438 204.574219 136.914062 204.574219 C 140.058594 204.574219 142.605469 207.125 142.605469 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 223.527344 C 142.605469 226.671875 140.058594 229.21875 136.914062 229.21875 C 133.773438 229.21875 131.226562 226.671875 131.226562 223.527344 C 131.226562 220.386719 133.773438 217.839844 136.914062 217.839844 C 140.058594 217.839844 142.605469 220.386719 142.605469 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 299.433594 C 128.664062 302.574219 126.117188 305.121094 122.972656 305.121094 C 119.832031 305.121094 117.285156 302.574219 117.285156 299.433594 C 117.285156 296.292969 119.832031 293.746094 122.972656 293.746094 C 126.117188 293.746094 128.664062 296.292969 128.664062 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 398.65625 C 86.84375 401.796875 84.296875 404.34375 81.152344 404.34375 C 78.011719 404.34375 75.464844 401.796875 75.464844 398.65625 C 75.464844 395.515625 78.011719 392.964844 81.152344 392.964844 C 84.296875 392.964844 86.84375 395.515625 86.84375 398.65625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 185.257812 C 198.367188 188.402344 195.816406 190.949219 192.675781 190.949219 C 189.535156 190.949219 186.988281 188.402344 186.988281 185.257812 C 186.988281 182.117188 189.535156 179.570312 192.675781 179.570312 C 195.816406 179.570312 198.367188 182.117188 198.367188 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 240.1875 151.027344 C 240.1875 154.167969 237.640625 156.714844 234.496094 156.714844 C 231.355469 156.714844 228.808594 154.167969 228.808594 151.027344 C 228.808594 147.882812 231.355469 145.335938 234.496094 145.335938 C 237.640625 145.335938 240.1875 147.882812 240.1875 151.027344 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 162.042969 C 184.425781 165.183594 181.878906 167.730469 178.734375 167.730469 C 175.59375 167.730469 173.046875 165.183594 173.046875 162.042969 C 173.046875 158.898438 175.59375 156.351562 178.734375 156.351562 C 181.878906 156.351562 184.425781 158.898438 184.425781 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 197.523438 C 170.484375 200.664062 167.9375 203.210938 164.796875 203.210938 C 161.652344 203.210938 159.105469 200.664062 159.105469 197.523438 C 159.105469 194.378906 161.652344 191.832031 164.796875 191.832031 C 167.9375 191.832031 170.484375 194.378906 170.484375 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 223.527344 C 184.425781 226.671875 181.878906 229.21875 178.734375 229.21875 C 175.59375 229.21875 173.046875 226.671875 173.046875 223.527344 C 173.046875 220.386719 175.59375 217.839844 178.734375 217.839844 C 181.878906 217.839844 184.425781 220.386719 184.425781 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 223.527344 C 170.484375 226.671875 167.9375 229.21875 164.796875 229.21875 C 161.652344 229.21875 159.105469 226.671875 159.105469 223.527344 C 159.105469 220.386719 161.652344 217.839844 164.796875 217.839844 C 167.9375 217.839844 170.484375 220.386719 170.484375 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 251.800781 C 156.542969 254.941406 153.996094 257.488281 150.855469 257.488281 C 147.714844 257.488281 145.164062 254.941406 145.164062 251.800781 C 145.164062 248.65625 147.714844 246.109375 150.855469 246.109375 C 153.996094 246.109375 156.542969 248.65625 156.542969 251.800781 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 251.800781 C 156.542969 254.941406 153.996094 257.488281 150.855469 257.488281 C 147.714844 257.488281 145.164062 254.941406 145.164062 251.800781 C 145.164062 248.65625 147.714844 246.109375 150.855469 246.109375 C 153.996094 246.109375 156.542969 248.65625 156.542969 251.800781 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 223.527344 C 170.484375 226.671875 167.9375 229.21875 164.796875 229.21875 C 161.652344 229.21875 159.105469 226.671875 159.105469 223.527344 C 159.105469 220.386719 161.652344 217.839844 164.796875 217.839844 C 167.9375 217.839844 170.484375 220.386719 170.484375 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 223.527344 C 170.484375 226.671875 167.9375 229.21875 164.796875 229.21875 C 161.652344 229.21875 159.105469 226.671875 159.105469 223.527344 C 159.105469 220.386719 161.652344 217.839844 164.796875 217.839844 C 167.9375 217.839844 170.484375 220.386719 170.484375 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 335.570312 C 86.84375 338.714844 84.296875 341.261719 81.152344 341.261719 C 78.011719 341.261719 75.464844 338.714844 75.464844 335.570312 C 75.464844 332.429688 78.011719 329.882812 81.152344 329.882812 C 84.296875 329.882812 86.84375 332.429688 86.84375 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 251.800781 C 142.605469 254.941406 140.058594 257.488281 136.914062 257.488281 C 133.773438 257.488281 131.226562 254.941406 131.226562 251.800781 C 131.226562 248.65625 133.773438 246.109375 136.914062 246.109375 C 140.058594 246.109375 142.605469 248.65625 142.605469 251.800781 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 266.914062 C 142.605469 270.058594 140.058594 272.605469 136.914062 272.605469 C 133.773438 272.605469 131.226562 270.058594 131.226562 266.914062 C 131.226562 263.773438 133.773438 261.226562 136.914062 261.226562 C 140.058594 261.226562 142.605469 263.773438 142.605469 266.914062 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 237.355469 C 156.542969 240.5 153.996094 243.046875 150.855469 243.046875 C 147.714844 243.046875 145.164062 240.5 145.164062 237.355469 C 145.164062 234.214844 147.714844 231.667969 150.855469 231.667969 C 153.996094 231.667969 156.542969 234.214844 156.542969 237.355469 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 237.355469 C 156.542969 240.5 153.996094 243.046875 150.855469 243.046875 C 147.714844 243.046875 145.164062 240.5 145.164062 237.355469 C 145.164062 234.214844 147.714844 231.667969 150.855469 231.667969 C 153.996094 231.667969 156.542969 234.214844 156.542969 237.355469 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 299.433594 C 142.605469 302.574219 140.058594 305.121094 136.914062 305.121094 C 133.773438 305.121094 131.226562 302.574219 131.226562 299.433594 C 131.226562 296.292969 133.773438 293.746094 136.914062 293.746094 C 140.058594 293.746094 142.605469 296.292969 142.605469 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 317 C 128.664062 320.144531 126.117188 322.691406 122.972656 322.691406 C 119.832031 322.691406 117.285156 320.144531 117.285156 317 C 117.285156 313.859375 119.832031 311.3125 122.972656 311.3125 C 126.117188 311.3125 128.664062 313.859375 128.664062 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 299.433594 C 128.664062 302.574219 126.117188 305.121094 122.972656 305.121094 C 119.832031 305.121094 117.285156 302.574219 117.285156 299.433594 C 117.285156 296.292969 119.832031 293.746094 122.972656 293.746094 C 126.117188 293.746094 128.664062 296.292969 128.664062 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 299.433594 C 128.664062 302.574219 126.117188 305.121094 122.972656 305.121094 C 119.832031 305.121094 117.285156 302.574219 117.285156 299.433594 C 117.285156 296.292969 119.832031 293.746094 122.972656 293.746094 C 126.117188 293.746094 128.664062 296.292969 128.664062 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 58.960938 448.742188 C 58.960938 451.882812 56.414062 454.429688 53.273438 454.429688 C 50.132812 454.429688 47.582031 451.882812 47.582031 448.742188 C 47.582031 445.597656 50.132812 443.050781 53.273438 443.050781 C 56.414062 443.050781 58.960938 445.597656 58.960938 448.742188 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 335.570312 C 86.84375 338.714844 84.296875 341.261719 81.152344 341.261719 C 78.011719 341.261719 75.464844 338.714844 75.464844 335.570312 C 75.464844 332.429688 78.011719 329.882812 81.152344 329.882812 C 84.296875 329.882812 86.84375 332.429688 86.84375 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 58.960938 448.742188 C 58.960938 451.882812 56.414062 454.429688 53.273438 454.429688 C 50.132812 454.429688 47.582031 451.882812 47.582031 448.742188 C 47.582031 445.597656 50.132812 443.050781 53.273438 443.050781 C 56.414062 443.050781 58.960938 445.597656 58.960938 448.742188 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 355.269531 C 86.84375 358.410156 84.296875 360.960938 81.152344 360.960938 C 78.011719 360.960938 75.464844 358.410156 75.464844 355.269531 C 75.464844 352.128906 78.011719 349.582031 81.152344 349.582031 C 84.296875 349.582031 86.84375 352.128906 86.84375 355.269531 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 317 C 114.722656 320.144531 112.175781 322.691406 109.035156 322.691406 C 105.890625 322.691406 103.34375 320.144531 103.34375 317 C 103.34375 313.859375 105.890625 311.3125 109.035156 311.3125 C 112.175781 311.3125 114.722656 313.859375 114.722656 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.78125 355.269531 C 100.78125 358.410156 98.234375 360.960938 95.09375 360.960938 C 91.953125 360.960938 89.40625 358.410156 89.40625 355.269531 C 89.40625 352.128906 91.953125 349.582031 95.09375 349.582031 C 98.234375 349.582031 100.78125 352.128906 100.78125 355.269531 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 58.960938 448.742188 C 58.960938 451.882812 56.414062 454.429688 53.273438 454.429688 C 50.132812 454.429688 47.582031 451.882812 47.582031 448.742188 C 47.582031 445.597656 50.132812 443.050781 53.273438 443.050781 C 56.414062 443.050781 58.960938 445.597656 58.960938 448.742188 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.78125 355.269531 C 100.78125 358.410156 98.234375 360.960938 95.09375 360.960938 C 91.953125 360.960938 89.40625 358.410156 89.40625 355.269531 C 89.40625 352.128906 91.953125 349.582031 95.09375 349.582031 C 98.234375 349.582031 100.78125 352.128906 100.78125 355.269531 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 58.960938 448.742188 C 58.960938 451.882812 56.414062 454.429688 53.273438 454.429688 C 50.132812 454.429688 47.582031 451.882812 47.582031 448.742188 C 47.582031 445.597656 50.132812 443.050781 53.273438 443.050781 C 56.414062 443.050781 58.960938 445.597656 58.960938 448.742188 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 355.269531 C 86.84375 358.410156 84.296875 360.960938 81.152344 360.960938 C 78.011719 360.960938 75.464844 358.410156 75.464844 355.269531 C 75.464844 352.128906 78.011719 349.582031 81.152344 349.582031 C 84.296875 349.582031 86.84375 352.128906 86.84375 355.269531 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 335.570312 C 86.84375 338.714844 84.296875 341.261719 81.152344 341.261719 C 78.011719 341.261719 75.464844 338.714844 75.464844 335.570312 C 75.464844 332.429688 78.011719 329.882812 81.152344 329.882812 C 84.296875 329.882812 86.84375 332.429688 86.84375 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 335.570312 C 86.84375 338.714844 84.296875 341.261719 81.152344 341.261719 C 78.011719 341.261719 75.464844 338.714844 75.464844 335.570312 C 75.464844 332.429688 78.011719 329.882812 81.152344 329.882812 C 84.296875 329.882812 86.84375 332.429688 86.84375 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.78125 317 C 100.78125 320.144531 98.234375 322.691406 95.09375 322.691406 C 91.953125 322.691406 89.40625 320.144531 89.40625 317 C 89.40625 313.859375 91.953125 311.3125 95.09375 311.3125 C 98.234375 311.3125 100.78125 313.859375 100.78125 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 299.433594 C 142.605469 302.574219 140.058594 305.121094 136.914062 305.121094 C 133.773438 305.121094 131.226562 302.574219 131.226562 299.433594 C 131.226562 296.292969 133.773438 293.746094 136.914062 293.746094 C 140.058594 293.746094 142.605469 296.292969 142.605469 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 299.433594 C 114.722656 302.574219 112.175781 305.121094 109.035156 305.121094 C 105.890625 305.121094 103.34375 302.574219 103.34375 299.433594 C 103.34375 296.292969 105.890625 293.746094 109.035156 293.746094 C 112.175781 293.746094 114.722656 296.292969 114.722656 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 299.433594 C 114.722656 302.574219 112.175781 305.121094 109.035156 305.121094 C 105.890625 305.121094 103.34375 302.574219 103.34375 299.433594 C 103.34375 296.292969 105.890625 293.746094 109.035156 293.746094 C 112.175781 293.746094 114.722656 296.292969 114.722656 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 355.269531 C 114.722656 358.410156 112.175781 360.960938 109.035156 360.960938 C 105.890625 360.960938 103.34375 358.410156 103.34375 355.269531 C 103.34375 352.128906 105.890625 349.582031 109.035156 349.582031 C 112.175781 349.582031 114.722656 352.128906 114.722656 355.269531 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 355.269531 C 114.722656 358.410156 112.175781 360.960938 109.035156 360.960938 C 105.890625 360.960938 103.34375 358.410156 103.34375 355.269531 C 103.34375 352.128906 105.890625 349.582031 109.035156 349.582031 C 112.175781 349.582031 114.722656 352.128906 114.722656 355.269531 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 210.265625 C 184.425781 213.40625 181.878906 215.953125 178.734375 215.953125 C 175.59375 215.953125 173.046875 213.40625 173.046875 210.265625 C 173.046875 207.125 175.59375 204.574219 178.734375 204.574219 C 181.878906 204.574219 184.425781 207.125 184.425781 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 197.523438 C 170.484375 200.664062 167.9375 203.210938 164.796875 203.210938 C 161.652344 203.210938 159.105469 200.664062 159.105469 197.523438 C 159.105469 194.378906 161.652344 191.832031 164.796875 191.832031 C 167.9375 191.832031 170.484375 194.378906 170.484375 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 223.527344 C 156.542969 226.671875 153.996094 229.21875 150.855469 229.21875 C 147.714844 229.21875 145.164062 226.671875 145.164062 223.527344 C 145.164062 220.386719 147.714844 217.839844 150.855469 217.839844 C 153.996094 217.839844 156.542969 220.386719 156.542969 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 266.914062 C 142.605469 270.058594 140.058594 272.605469 136.914062 272.605469 C 133.773438 272.605469 131.226562 270.058594 131.226562 266.914062 C 131.226562 263.773438 133.773438 261.226562 136.914062 261.226562 C 140.058594 261.226562 142.605469 263.773438 142.605469 266.914062 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 251.800781 C 142.605469 254.941406 140.058594 257.488281 136.914062 257.488281 C 133.773438 257.488281 131.226562 254.941406 131.226562 251.800781 C 131.226562 248.65625 133.773438 246.109375 136.914062 246.109375 C 140.058594 246.109375 142.605469 248.65625 142.605469 251.800781 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 237.355469 C 142.605469 240.5 140.058594 243.046875 136.914062 243.046875 C 133.773438 243.046875 131.226562 240.5 131.226562 237.355469 C 131.226562 234.214844 133.773438 231.667969 136.914062 231.667969 C 140.058594 231.667969 142.605469 234.214844 142.605469 237.355469 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 251.800781 C 142.605469 254.941406 140.058594 257.488281 136.914062 257.488281 C 133.773438 257.488281 131.226562 254.941406 131.226562 251.800781 C 131.226562 248.65625 133.773438 246.109375 136.914062 246.109375 C 140.058594 246.109375 142.605469 248.65625 142.605469 251.800781 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 282.765625 C 128.664062 285.910156 126.117188 288.457031 122.972656 288.457031 C 119.832031 288.457031 117.285156 285.910156 117.285156 282.765625 C 117.285156 279.625 119.832031 277.078125 122.972656 277.078125 C 126.117188 277.078125 128.664062 279.625 128.664062 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 323.828125 120.058594 C 323.828125 123.199219 321.28125 125.75 318.140625 125.75 C 314.996094 125.75 312.449219 123.199219 312.449219 120.058594 C 312.449219 116.917969 314.996094 114.371094 318.140625 114.371094 C 321.28125 114.371094 323.828125 116.917969 323.828125 120.058594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 268.066406 130.058594 C 268.066406 133.199219 265.519531 135.746094 262.378906 135.746094 C 259.234375 135.746094 256.6875 133.199219 256.6875 130.058594 C 256.6875 126.914062 259.234375 124.367188 262.378906 124.367188 C 265.519531 124.367188 268.066406 126.914062 268.066406 130.058594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 282.007812 130.058594 C 282.007812 133.199219 279.460938 135.746094 276.316406 135.746094 C 273.175781 135.746094 270.628906 133.199219 270.628906 130.058594 C 270.628906 126.914062 273.175781 124.367188 276.316406 124.367188 C 279.460938 124.367188 282.007812 126.914062 282.007812 130.058594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 254.125 162.042969 C 254.125 165.183594 251.578125 167.730469 248.4375 167.730469 C 245.296875 167.730469 242.75 165.183594 242.75 162.042969 C 242.75 158.898438 245.296875 156.351562 248.4375 156.351562 C 251.578125 156.351562 254.125 158.898438 254.125 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 268.066406 130.058594 C 268.066406 133.199219 265.519531 135.746094 262.378906 135.746094 C 259.234375 135.746094 256.6875 133.199219 256.6875 130.058594 C 256.6875 126.914062 259.234375 124.367188 262.378906 124.367188 C 265.519531 124.367188 268.066406 126.914062 268.066406 130.058594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 295.949219 110.359375 C 295.949219 113.5 293.398438 116.046875 290.257812 116.046875 C 287.117188 116.046875 284.570312 113.5 284.570312 110.359375 C 284.570312 107.21875 287.117188 104.671875 290.257812 104.671875 C 293.398438 104.671875 295.949219 107.21875 295.949219 110.359375 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 282.007812 91.789062 C 282.007812 94.929688 279.460938 97.476562 276.316406 97.476562 C 273.175781 97.476562 270.628906 94.929688 270.628906 91.789062 C 270.628906 88.644531 273.175781 86.097656 276.316406 86.097656 C 279.460938 86.097656 282.007812 88.644531 282.007812 91.789062 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 268.066406 91.789062 C 268.066406 94.929688 265.519531 97.476562 262.378906 97.476562 C 259.234375 97.476562 256.6875 94.929688 256.6875 91.789062 C 256.6875 88.644531 259.234375 86.097656 262.378906 86.097656 C 265.519531 86.097656 268.066406 88.644531 268.066406 91.789062 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 185.257812 C 184.425781 188.402344 181.878906 190.949219 178.734375 190.949219 C 175.59375 190.949219 173.046875 188.402344 173.046875 185.257812 C 173.046875 182.117188 175.59375 179.570312 178.734375 179.570312 C 181.878906 179.570312 184.425781 182.117188 184.425781 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 151.027344 C 226.246094 154.167969 223.699219 156.714844 220.558594 156.714844 C 217.414062 156.714844 214.867188 154.167969 214.867188 151.027344 C 214.867188 147.882812 217.414062 145.335938 220.558594 145.335938 C 223.699219 145.335938 226.246094 147.882812 226.246094 151.027344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 140.371094 C 226.246094 143.515625 223.699219 146.0625 220.558594 146.0625 C 217.414062 146.0625 214.867188 143.515625 214.867188 140.371094 C 214.867188 137.230469 217.414062 134.683594 220.558594 134.683594 C 223.699219 134.683594 226.246094 137.230469 226.246094 140.371094 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 173.441406 C 198.367188 176.585938 195.816406 179.132812 192.675781 179.132812 C 189.535156 179.132812 186.988281 176.585938 186.988281 173.441406 C 186.988281 170.300781 189.535156 167.753906 192.675781 167.753906 C 195.816406 167.753906 198.367188 170.300781 198.367188 173.441406 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 197.523438 C 198.367188 200.664062 195.816406 203.210938 192.675781 203.210938 C 189.535156 203.210938 186.988281 200.664062 186.988281 197.523438 C 186.988281 194.378906 189.535156 191.832031 192.675781 191.832031 C 195.816406 191.832031 198.367188 194.378906 198.367188 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 162.042969 C 198.367188 165.183594 195.816406 167.730469 192.675781 167.730469 C 189.535156 167.730469 186.988281 165.183594 186.988281 162.042969 C 186.988281 158.898438 189.535156 156.351562 192.675781 156.351562 C 195.816406 156.351562 198.367188 158.898438 198.367188 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 173.441406 C 212.304688 176.585938 209.757812 179.132812 206.617188 179.132812 C 203.472656 179.132812 200.925781 176.585938 200.925781 173.441406 C 200.925781 170.300781 203.472656 167.753906 206.617188 167.753906 C 209.757812 167.753906 212.304688 170.300781 212.304688 173.441406 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 185.257812 C 212.304688 188.402344 209.757812 190.949219 206.617188 190.949219 C 203.472656 190.949219 200.925781 188.402344 200.925781 185.257812 C 200.925781 182.117188 203.472656 179.570312 206.617188 179.570312 C 209.757812 179.570312 212.304688 182.117188 212.304688 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 223.527344 C 170.484375 226.671875 167.9375 229.21875 164.796875 229.21875 C 161.652344 229.21875 159.105469 226.671875 159.105469 223.527344 C 159.105469 220.386719 161.652344 217.839844 164.796875 217.839844 C 167.9375 217.839844 170.484375 220.386719 170.484375 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 223.527344 C 156.542969 226.671875 153.996094 229.21875 150.855469 229.21875 C 147.714844 229.21875 145.164062 226.671875 145.164062 223.527344 C 145.164062 220.386719 147.714844 217.839844 150.855469 217.839844 C 153.996094 217.839844 156.542969 220.386719 156.542969 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 223.527344 C 170.484375 226.671875 167.9375 229.21875 164.796875 229.21875 C 161.652344 229.21875 159.105469 226.671875 159.105469 223.527344 C 159.105469 220.386719 161.652344 217.839844 164.796875 217.839844 C 167.9375 217.839844 170.484375 220.386719 170.484375 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 251.800781 C 170.484375 254.941406 167.9375 257.488281 164.796875 257.488281 C 161.652344 257.488281 159.105469 254.941406 159.105469 251.800781 C 159.105469 248.65625 161.652344 246.109375 164.796875 246.109375 C 167.9375 246.109375 170.484375 248.65625 170.484375 251.800781 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 299.433594 C 142.605469 302.574219 140.058594 305.121094 136.914062 305.121094 C 133.773438 305.121094 131.226562 302.574219 131.226562 299.433594 C 131.226562 296.292969 133.773438 293.746094 136.914062 293.746094 C 140.058594 293.746094 142.605469 296.292969 142.605469 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 282.765625 C 142.605469 285.910156 140.058594 288.457031 136.914062 288.457031 C 133.773438 288.457031 131.226562 285.910156 131.226562 282.765625 C 131.226562 279.625 133.773438 277.078125 136.914062 277.078125 C 140.058594 277.078125 142.605469 279.625 142.605469 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 58.960938 448.742188 C 58.960938 451.882812 56.414062 454.429688 53.273438 454.429688 C 50.132812 454.429688 47.582031 451.882812 47.582031 448.742188 C 47.582031 445.597656 50.132812 443.050781 53.273438 443.050781 C 56.414062 443.050781 58.960938 445.597656 58.960938 448.742188 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 299.433594 C 128.664062 302.574219 126.117188 305.121094 122.972656 305.121094 C 119.832031 305.121094 117.285156 302.574219 117.285156 299.433594 C 117.285156 296.292969 119.832031 293.746094 122.972656 293.746094 C 126.117188 293.746094 128.664062 296.292969 128.664062 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 317 C 114.722656 320.144531 112.175781 322.691406 109.035156 322.691406 C 105.890625 322.691406 103.34375 320.144531 103.34375 317 C 103.34375 313.859375 105.890625 311.3125 109.035156 311.3125 C 112.175781 311.3125 114.722656 313.859375 114.722656 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 398.65625 C 86.84375 401.796875 84.296875 404.34375 81.152344 404.34375 C 78.011719 404.34375 75.464844 401.796875 75.464844 398.65625 C 75.464844 395.515625 78.011719 392.964844 81.152344 392.964844 C 84.296875 392.964844 86.84375 395.515625 86.84375 398.65625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.78125 317 C 100.78125 320.144531 98.234375 322.691406 95.09375 322.691406 C 91.953125 322.691406 89.40625 320.144531 89.40625 317 C 89.40625 313.859375 91.953125 311.3125 95.09375 311.3125 C 98.234375 311.3125 100.78125 313.859375 100.78125 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.78125 317 C 100.78125 320.144531 98.234375 322.691406 95.09375 322.691406 C 91.953125 322.691406 89.40625 320.144531 89.40625 317 C 89.40625 313.859375 91.953125 311.3125 95.09375 311.3125 C 98.234375 311.3125 100.78125 313.859375 100.78125 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 335.570312 C 86.84375 338.714844 84.296875 341.261719 81.152344 341.261719 C 78.011719 341.261719 75.464844 338.714844 75.464844 335.570312 C 75.464844 332.429688 78.011719 329.882812 81.152344 329.882812 C 84.296875 329.882812 86.84375 332.429688 86.84375 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 355.269531 C 86.84375 358.410156 84.296875 360.960938 81.152344 360.960938 C 78.011719 360.960938 75.464844 358.410156 75.464844 355.269531 C 75.464844 352.128906 78.011719 349.582031 81.152344 349.582031 C 84.296875 349.582031 86.84375 352.128906 86.84375 355.269531 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.78125 317 C 100.78125 320.144531 98.234375 322.691406 95.09375 322.691406 C 91.953125 322.691406 89.40625 320.144531 89.40625 317 C 89.40625 313.859375 91.953125 311.3125 95.09375 311.3125 C 98.234375 311.3125 100.78125 313.859375 100.78125 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 299.433594 C 114.722656 302.574219 112.175781 305.121094 109.035156 305.121094 C 105.890625 305.121094 103.34375 302.574219 103.34375 299.433594 C 103.34375 296.292969 105.890625 293.746094 109.035156 293.746094 C 112.175781 293.746094 114.722656 296.292969 114.722656 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 299.433594 C 114.722656 302.574219 112.175781 305.121094 109.035156 305.121094 C 105.890625 305.121094 103.34375 302.574219 103.34375 299.433594 C 103.34375 296.292969 105.890625 293.746094 109.035156 293.746094 C 112.175781 293.746094 114.722656 296.292969 114.722656 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 335.570312 C 114.722656 338.714844 112.175781 341.261719 109.035156 341.261719 C 105.890625 341.261719 103.34375 338.714844 103.34375 335.570312 C 103.34375 332.429688 105.890625 329.882812 109.035156 329.882812 C 112.175781 329.882812 114.722656 332.429688 114.722656 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 185.257812 C 198.367188 188.402344 195.816406 190.949219 192.675781 190.949219 C 189.535156 190.949219 186.988281 188.402344 186.988281 185.257812 C 186.988281 182.117188 189.535156 179.570312 192.675781 179.570312 C 195.816406 179.570312 198.367188 182.117188 198.367188 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 254.125 140.371094 C 254.125 143.515625 251.578125 146.0625 248.4375 146.0625 C 245.296875 146.0625 242.75 143.515625 242.75 140.371094 C 242.75 137.230469 245.296875 134.683594 248.4375 134.683594 C 251.578125 134.683594 254.125 137.230469 254.125 140.371094 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 254.125 130.058594 C 254.125 133.199219 251.578125 135.746094 248.4375 135.746094 C 245.296875 135.746094 242.75 133.199219 242.75 130.058594 C 242.75 126.914062 245.296875 124.367188 248.4375 124.367188 C 251.578125 124.367188 254.125 126.914062 254.125 130.058594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 185.257812 C 198.367188 188.402344 195.816406 190.949219 192.675781 190.949219 C 189.535156 190.949219 186.988281 188.402344 186.988281 185.257812 C 186.988281 182.117188 189.535156 179.570312 192.675781 179.570312 C 195.816406 179.570312 198.367188 182.117188 198.367188 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 197.523438 C 198.367188 200.664062 195.816406 203.210938 192.675781 203.210938 C 189.535156 203.210938 186.988281 200.664062 186.988281 197.523438 C 186.988281 194.378906 189.535156 191.832031 192.675781 191.832031 C 195.816406 191.832031 198.367188 194.378906 198.367188 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 210.265625 C 198.367188 213.40625 195.816406 215.953125 192.675781 215.953125 C 189.535156 215.953125 186.988281 213.40625 186.988281 210.265625 C 186.988281 207.125 189.535156 204.574219 192.675781 204.574219 C 195.816406 204.574219 198.367188 207.125 198.367188 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 210.265625 C 198.367188 213.40625 195.816406 215.953125 192.675781 215.953125 C 189.535156 215.953125 186.988281 213.40625 186.988281 210.265625 C 186.988281 207.125 189.535156 204.574219 192.675781 204.574219 C 195.816406 204.574219 198.367188 207.125 198.367188 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 335.570312 C 142.605469 338.714844 140.058594 341.261719 136.914062 341.261719 C 133.773438 341.261719 131.226562 338.714844 131.226562 335.570312 C 131.226562 332.429688 133.773438 329.882812 136.914062 329.882812 C 140.058594 329.882812 142.605469 332.429688 142.605469 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 282.765625 C 128.664062 285.910156 126.117188 288.457031 122.972656 288.457031 C 119.832031 288.457031 117.285156 285.910156 117.285156 282.765625 C 117.285156 279.625 119.832031 277.078125 122.972656 277.078125 C 126.117188 277.078125 128.664062 279.625 128.664062 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 100.78125 317 C 100.78125 320.144531 98.234375 322.691406 95.09375 322.691406 C 91.953125 322.691406 89.40625 320.144531 89.40625 317 C 89.40625 313.859375 91.953125 311.3125 95.09375 311.3125 C 98.234375 311.3125 100.78125 313.859375 100.78125 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 197.523438 C 156.542969 200.664062 153.996094 203.210938 150.855469 203.210938 C 147.714844 203.210938 145.164062 200.664062 145.164062 197.523438 C 145.164062 194.378906 147.714844 191.832031 150.855469 191.832031 C 153.996094 191.832031 156.542969 194.378906 156.542969 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 185.257812 C 170.484375 188.402344 167.9375 190.949219 164.796875 190.949219 C 161.652344 190.949219 159.105469 188.402344 159.105469 185.257812 C 159.105469 182.117188 161.652344 179.570312 164.796875 179.570312 C 167.9375 179.570312 170.484375 182.117188 170.484375 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 173.441406 C 184.425781 176.585938 181.878906 179.132812 178.734375 179.132812 C 175.59375 179.132812 173.046875 176.585938 173.046875 173.441406 C 173.046875 170.300781 175.59375 167.753906 178.734375 167.753906 C 181.878906 167.753906 184.425781 170.300781 184.425781 173.441406 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 210.265625 C 156.542969 213.40625 153.996094 215.953125 150.855469 215.953125 C 147.714844 215.953125 145.164062 213.40625 145.164062 210.265625 C 145.164062 207.125 147.714844 204.574219 150.855469 204.574219 C 153.996094 204.574219 156.542969 207.125 156.542969 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 210.265625 C 184.425781 213.40625 181.878906 215.953125 178.734375 215.953125 C 175.59375 215.953125 173.046875 213.40625 173.046875 210.265625 C 173.046875 207.125 175.59375 204.574219 178.734375 204.574219 C 181.878906 204.574219 184.425781 207.125 184.425781 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 223.527344 C 184.425781 226.671875 181.878906 229.21875 178.734375 229.21875 C 175.59375 229.21875 173.046875 226.671875 173.046875 223.527344 C 173.046875 220.386719 175.59375 217.839844 178.734375 217.839844 C 181.878906 217.839844 184.425781 220.386719 184.425781 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 185.257812 C 212.304688 188.402344 209.757812 190.949219 206.617188 190.949219 C 203.472656 190.949219 200.925781 188.402344 200.925781 185.257812 C 200.925781 182.117188 203.472656 179.570312 206.617188 179.570312 C 209.757812 179.570312 212.304688 182.117188 212.304688 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 210.265625 C 198.367188 213.40625 195.816406 215.953125 192.675781 215.953125 C 189.535156 215.953125 186.988281 213.40625 186.988281 210.265625 C 186.988281 207.125 189.535156 204.574219 192.675781 204.574219 C 195.816406 204.574219 198.367188 207.125 198.367188 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 197.523438 C 212.304688 200.664062 209.757812 203.210938 206.617188 203.210938 C 203.472656 203.210938 200.925781 200.664062 200.925781 197.523438 C 200.925781 194.378906 203.472656 191.832031 206.617188 191.832031 C 209.757812 191.832031 212.304688 194.378906 212.304688 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 237.355469 C 184.425781 240.5 181.878906 243.046875 178.734375 243.046875 C 175.59375 243.046875 173.046875 240.5 173.046875 237.355469 C 173.046875 234.214844 175.59375 231.667969 178.734375 231.667969 C 181.878906 231.667969 184.425781 234.214844 184.425781 237.355469 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 197.523438 C 226.246094 200.664062 223.699219 203.210938 220.558594 203.210938 C 217.414062 203.210938 214.867188 200.664062 214.867188 197.523438 C 214.867188 194.378906 217.414062 191.832031 220.558594 191.832031 C 223.699219 191.832031 226.246094 194.378906 226.246094 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 197.523438 C 198.367188 200.664062 195.816406 203.210938 192.675781 203.210938 C 189.535156 203.210938 186.988281 200.664062 186.988281 197.523438 C 186.988281 194.378906 189.535156 191.832031 192.675781 191.832031 C 195.816406 191.832031 198.367188 194.378906 198.367188 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 197.523438 C 198.367188 200.664062 195.816406 203.210938 192.675781 203.210938 C 189.535156 203.210938 186.988281 200.664062 186.988281 197.523438 C 186.988281 194.378906 189.535156 191.832031 192.675781 191.832031 C 195.816406 191.832031 198.367188 194.378906 198.367188 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 197.523438 C 198.367188 200.664062 195.816406 203.210938 192.675781 203.210938 C 189.535156 203.210938 186.988281 200.664062 186.988281 197.523438 C 186.988281 194.378906 189.535156 191.832031 192.675781 191.832031 C 195.816406 191.832031 198.367188 194.378906 198.367188 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 210.265625 C 212.304688 213.40625 209.757812 215.953125 206.617188 215.953125 C 203.472656 215.953125 200.925781 213.40625 200.925781 210.265625 C 200.925781 207.125 203.472656 204.574219 206.617188 204.574219 C 209.757812 204.574219 212.304688 207.125 212.304688 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 185.257812 C 212.304688 188.402344 209.757812 190.949219 206.617188 190.949219 C 203.472656 190.949219 200.925781 188.402344 200.925781 185.257812 C 200.925781 182.117188 203.472656 179.570312 206.617188 179.570312 C 209.757812 179.570312 212.304688 182.117188 212.304688 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 210.265625 C 198.367188 213.40625 195.816406 215.953125 192.675781 215.953125 C 189.535156 215.953125 186.988281 213.40625 186.988281 210.265625 C 186.988281 207.125 189.535156 204.574219 192.675781 204.574219 C 195.816406 204.574219 198.367188 207.125 198.367188 210.265625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 185.257812 C 212.304688 188.402344 209.757812 190.949219 206.617188 190.949219 C 203.472656 190.949219 200.925781 188.402344 200.925781 185.257812 C 200.925781 182.117188 203.472656 179.570312 206.617188 179.570312 C 209.757812 179.570312 212.304688 182.117188 212.304688 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 282.765625 C 142.605469 285.910156 140.058594 288.457031 136.914062 288.457031 C 133.773438 288.457031 131.226562 285.910156 131.226562 282.765625 C 131.226562 279.625 133.773438 277.078125 136.914062 277.078125 C 140.058594 277.078125 142.605469 279.625 142.605469 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 282.765625 C 156.542969 285.910156 153.996094 288.457031 150.855469 288.457031 C 147.714844 288.457031 145.164062 285.910156 145.164062 282.765625 C 145.164062 279.625 147.714844 277.078125 150.855469 277.078125 C 153.996094 277.078125 156.542969 279.625 156.542969 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 299.433594 C 142.605469 302.574219 140.058594 305.121094 136.914062 305.121094 C 133.773438 305.121094 131.226562 302.574219 131.226562 299.433594 C 131.226562 296.292969 133.773438 293.746094 136.914062 293.746094 C 140.058594 293.746094 142.605469 296.292969 142.605469 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 335.570312 C 142.605469 338.714844 140.058594 341.261719 136.914062 341.261719 C 133.773438 341.261719 131.226562 338.714844 131.226562 335.570312 C 131.226562 332.429688 133.773438 329.882812 136.914062 329.882812 C 140.058594 329.882812 142.605469 332.429688 142.605469 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 282.765625 C 156.542969 285.910156 153.996094 288.457031 150.855469 288.457031 C 147.714844 288.457031 145.164062 285.910156 145.164062 282.765625 C 145.164062 279.625 147.714844 277.078125 150.855469 277.078125 C 153.996094 277.078125 156.542969 279.625 156.542969 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 128.664062 335.570312 C 128.664062 338.714844 126.117188 341.261719 122.972656 341.261719 C 119.832031 341.261719 117.285156 338.714844 117.285156 335.570312 C 117.285156 332.429688 119.832031 329.882812 122.972656 329.882812 C 126.117188 329.882812 128.664062 332.429688 128.664062 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 185.257812 C 226.246094 188.402344 223.699219 190.949219 220.558594 190.949219 C 217.414062 190.949219 214.867188 188.402344 214.867188 185.257812 C 214.867188 182.117188 217.414062 179.570312 220.558594 179.570312 C 223.699219 179.570312 226.246094 182.117188 226.246094 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 140.371094 C 226.246094 143.515625 223.699219 146.0625 220.558594 146.0625 C 217.414062 146.0625 214.867188 143.515625 214.867188 140.371094 C 214.867188 137.230469 217.414062 134.683594 220.558594 134.683594 C 223.699219 134.683594 226.246094 137.230469 226.246094 140.371094 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 140.371094 C 226.246094 143.515625 223.699219 146.0625 220.558594 146.0625 C 217.414062 146.0625 214.867188 143.515625 214.867188 140.371094 C 214.867188 137.230469 217.414062 134.683594 220.558594 134.683594 C 223.699219 134.683594 226.246094 137.230469 226.246094 140.371094 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 173.441406 C 198.367188 176.585938 195.816406 179.132812 192.675781 179.132812 C 189.535156 179.132812 186.988281 176.585938 186.988281 173.441406 C 186.988281 170.300781 189.535156 167.753906 192.675781 167.753906 C 195.816406 167.753906 198.367188 170.300781 198.367188 173.441406 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 185.257812 C 226.246094 188.402344 223.699219 190.949219 220.558594 190.949219 C 217.414062 190.949219 214.867188 188.402344 214.867188 185.257812 C 214.867188 182.117188 217.414062 179.570312 220.558594 179.570312 C 223.699219 179.570312 226.246094 182.117188 226.246094 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 140.371094 C 226.246094 143.515625 223.699219 146.0625 220.558594 146.0625 C 217.414062 146.0625 214.867188 143.515625 214.867188 140.371094 C 214.867188 137.230469 217.414062 134.683594 220.558594 134.683594 C 223.699219 134.683594 226.246094 137.230469 226.246094 140.371094 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 240.1875 140.371094 C 240.1875 143.515625 237.640625 146.0625 234.496094 146.0625 C 231.355469 146.0625 228.808594 143.515625 228.808594 140.371094 C 228.808594 137.230469 231.355469 134.683594 234.496094 134.683594 C 237.640625 134.683594 240.1875 137.230469 240.1875 140.371094 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 185.257812 C 184.425781 188.402344 181.878906 190.949219 178.734375 190.949219 C 175.59375 190.949219 173.046875 188.402344 173.046875 185.257812 C 173.046875 182.117188 175.59375 179.570312 178.734375 179.570312 C 181.878906 179.570312 184.425781 182.117188 184.425781 185.257812 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 268.066406 151.027344 C 268.066406 154.167969 265.519531 156.714844 262.378906 156.714844 C 259.234375 156.714844 256.6875 154.167969 256.6875 151.027344 C 256.6875 147.882812 259.234375 145.335938 262.378906 145.335938 C 265.519531 145.335938 268.066406 147.882812 268.066406 151.027344 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 268.066406 120.058594 C 268.066406 123.199219 265.519531 125.75 262.378906 125.75 C 259.234375 125.75 256.6875 123.199219 256.6875 120.058594 C 256.6875 116.917969 259.234375 114.371094 262.378906 114.371094 C 265.519531 114.371094 268.066406 116.917969 268.066406 120.058594 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 295.949219 100.941406 C 295.949219 104.082031 293.398438 106.628906 290.257812 106.628906 C 287.117188 106.628906 284.570312 104.082031 284.570312 100.941406 C 284.570312 97.796875 287.117188 95.25 290.257812 95.25 C 293.398438 95.25 295.949219 97.796875 295.949219 100.941406 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 323.828125 82.886719 C 323.828125 86.027344 321.28125 88.574219 318.140625 88.574219 C 314.996094 88.574219 312.449219 86.027344 312.449219 82.886719 C 312.449219 79.742188 314.996094 77.195312 318.140625 77.195312 C 321.28125 77.195312 323.828125 79.742188 323.828125 82.886719 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 295.949219 100.941406 C 295.949219 104.082031 293.398438 106.628906 290.257812 106.628906 C 287.117188 106.628906 284.570312 104.082031 284.570312 100.941406 C 284.570312 97.796875 287.117188 95.25 290.257812 95.25 C 293.398438 95.25 295.949219 97.796875 295.949219 100.941406 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 86.84375 376.238281 C 86.84375 379.382812 84.296875 381.929688 81.152344 381.929688 C 78.011719 381.929688 75.464844 379.382812 75.464844 376.238281 C 75.464844 373.097656 78.011719 370.550781 81.152344 370.550781 C 84.296875 370.550781 86.84375 373.097656 86.84375 376.238281 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 114.722656 317 C 114.722656 320.144531 112.175781 322.691406 109.035156 322.691406 C 105.890625 322.691406 103.34375 320.144531 103.34375 317 C 103.34375 313.859375 105.890625 311.3125 109.035156 311.3125 C 112.175781 311.3125 114.722656 313.859375 114.722656 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 282.765625 C 142.605469 285.910156 140.058594 288.457031 136.914062 288.457031 C 133.773438 288.457031 131.226562 285.910156 131.226562 282.765625 C 131.226562 279.625 133.773438 277.078125 136.914062 277.078125 C 140.058594 277.078125 142.605469 279.625 142.605469 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 282.765625 C 156.542969 285.910156 153.996094 288.457031 150.855469 288.457031 C 147.714844 288.457031 145.164062 285.910156 145.164062 282.765625 C 145.164062 279.625 147.714844 277.078125 150.855469 277.078125 C 153.996094 277.078125 156.542969 279.625 156.542969 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 251.800781 C 170.484375 254.941406 167.9375 257.488281 164.796875 257.488281 C 161.652344 257.488281 159.105469 254.941406 159.105469 251.800781 C 159.105469 248.65625 161.652344 246.109375 164.796875 246.109375 C 167.9375 246.109375 170.484375 248.65625 170.484375 251.800781 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 335.570312 C 142.605469 338.714844 140.058594 341.261719 136.914062 341.261719 C 133.773438 341.261719 131.226562 338.714844 131.226562 335.570312 C 131.226562 332.429688 133.773438 329.882812 136.914062 329.882812 C 140.058594 329.882812 142.605469 332.429688 142.605469 335.570312 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 299.433594 C 142.605469 302.574219 140.058594 305.121094 136.914062 305.121094 C 133.773438 305.121094 131.226562 302.574219 131.226562 299.433594 C 131.226562 296.292969 133.773438 293.746094 136.914062 293.746094 C 140.058594 293.746094 142.605469 296.292969 142.605469 299.433594 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 142.605469 317 C 142.605469 320.144531 140.058594 322.691406 136.914062 322.691406 C 133.773438 322.691406 131.226562 320.144531 131.226562 317 C 131.226562 313.859375 133.773438 311.3125 136.914062 311.3125 C 140.058594 311.3125 142.605469 313.859375 142.605469 317 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 282.765625 C 156.542969 285.910156 153.996094 288.457031 150.855469 288.457031 C 147.714844 288.457031 145.164062 285.910156 145.164062 282.765625 C 145.164062 279.625 147.714844 277.078125 150.855469 277.078125 C 153.996094 277.078125 156.542969 279.625 156.542969 282.765625 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 197.523438 C 198.367188 200.664062 195.816406 203.210938 192.675781 203.210938 C 189.535156 203.210938 186.988281 200.664062 186.988281 197.523438 C 186.988281 194.378906 189.535156 191.832031 192.675781 191.832031 C 195.816406 191.832031 198.367188 194.378906 198.367188 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 240.1875 162.042969 C 240.1875 165.183594 237.640625 167.730469 234.496094 167.730469 C 231.355469 167.730469 228.808594 165.183594 228.808594 162.042969 C 228.808594 158.898438 231.355469 156.351562 234.496094 156.351562 C 237.640625 156.351562 240.1875 158.898438 240.1875 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 223.527344 C 170.484375 226.671875 167.9375 229.21875 164.796875 229.21875 C 161.652344 229.21875 159.105469 226.671875 159.105469 223.527344 C 159.105469 220.386719 161.652344 217.839844 164.796875 217.839844 C 167.9375 217.839844 170.484375 220.386719 170.484375 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 393.53125 26.585938 C 393.53125 29.730469 390.980469 32.277344 387.839844 32.277344 C 384.699219 32.277344 382.152344 29.730469 382.152344 26.585938 C 382.152344 23.445312 384.699219 20.898438 387.839844 20.898438 C 390.980469 20.898438 393.53125 23.445312 393.53125 26.585938 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 197.523438 C 198.367188 200.664062 195.816406 203.210938 192.675781 203.210938 C 189.535156 203.210938 186.988281 200.664062 186.988281 197.523438 C 186.988281 194.378906 189.535156 191.832031 192.675781 191.832031 C 195.816406 191.832031 198.367188 194.378906 198.367188 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 240.1875 162.042969 C 240.1875 165.183594 237.640625 167.730469 234.496094 167.730469 C 231.355469 167.730469 228.808594 165.183594 228.808594 162.042969 C 228.808594 158.898438 231.355469 156.351562 234.496094 156.351562 C 237.640625 156.351562 240.1875 158.898438 240.1875 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 237.355469 C 156.542969 240.5 153.996094 243.046875 150.855469 243.046875 C 147.714844 243.046875 145.164062 240.5 145.164062 237.355469 C 145.164062 234.214844 147.714844 231.667969 150.855469 231.667969 C 153.996094 231.667969 156.542969 234.214844 156.542969 237.355469 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 223.527344 C 170.484375 226.671875 167.9375 229.21875 164.796875 229.21875 C 161.652344 229.21875 159.105469 226.671875 159.105469 223.527344 C 159.105469 220.386719 161.652344 217.839844 164.796875 217.839844 C 167.9375 217.839844 170.484375 220.386719 170.484375 223.527344 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 421.410156 26.585938 C 421.410156 29.730469 418.863281 32.277344 415.722656 32.277344 C 412.578125 32.277344 410.03125 29.730469 410.03125 26.585938 C 410.03125 23.445312 412.578125 20.898438 415.722656 20.898438 C 418.863281 20.898438 421.410156 23.445312 421.410156 26.585938 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 337.769531 49.53125 C 337.769531 52.675781 335.222656 55.222656 332.078125 55.222656 C 328.9375 55.222656 326.390625 52.675781 326.390625 49.53125 C 326.390625 46.390625 328.9375 43.84375 332.078125 43.84375 C 335.222656 43.84375 337.769531 46.390625 337.769531 49.53125 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 197.523438 C 198.367188 200.664062 195.816406 203.210938 192.675781 203.210938 C 189.535156 203.210938 186.988281 200.664062 186.988281 197.523438 C 186.988281 194.378906 189.535156 191.832031 192.675781 191.832031 C 195.816406 191.832031 198.367188 194.378906 198.367188 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 173.441406 C 212.304688 176.585938 209.757812 179.132812 206.617188 179.132812 C 203.472656 179.132812 200.925781 176.585938 200.925781 173.441406 C 200.925781 170.300781 203.472656 167.753906 206.617188 167.753906 C 209.757812 167.753906 212.304688 170.300781 212.304688 173.441406 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 162.042969 C 212.304688 165.183594 209.757812 167.730469 206.617188 167.730469 C 203.472656 167.730469 200.925781 165.183594 200.925781 162.042969 C 200.925781 158.898438 203.472656 156.351562 206.617188 156.351562 C 209.757812 156.351562 212.304688 158.898438 212.304688 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 162.042969 C 184.425781 165.183594 181.878906 167.730469 178.734375 167.730469 C 175.59375 167.730469 173.046875 165.183594 173.046875 162.042969 C 173.046875 158.898438 175.59375 156.351562 178.734375 156.351562 C 181.878906 156.351562 184.425781 158.898438 184.425781 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 198.367188 173.441406 C 198.367188 176.585938 195.816406 179.132812 192.675781 179.132812 C 189.535156 179.132812 186.988281 176.585938 186.988281 173.441406 C 186.988281 170.300781 189.535156 167.753906 192.675781 167.753906 C 195.816406 167.753906 198.367188 170.300781 198.367188 173.441406 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 156.542969 197.523438 C 156.542969 200.664062 153.996094 203.210938 150.855469 203.210938 C 147.714844 203.210938 145.164062 200.664062 145.164062 197.523438 C 145.164062 194.378906 147.714844 191.832031 150.855469 191.832031 C 153.996094 191.832031 156.542969 194.378906 156.542969 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 197.523438 C 184.425781 200.664062 181.878906 203.210938 178.734375 203.210938 C 175.59375 203.210938 173.046875 200.664062 173.046875 197.523438 C 173.046875 194.378906 175.59375 191.832031 178.734375 191.832031 C 181.878906 191.832031 184.425781 194.378906 184.425781 197.523438 "/>
+<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 170.484375 197.523438 C 170.484375 200.664062 167.9375 203.210938 164.796875 203.210938 C 161.652344 203.210938 159.105469 200.664062 159.105469 197.523438 C 159.105469 194.378906 161.652344 191.832031 164.796875 191.832031 C 167.9375 191.832031 170.484375 194.378906 170.484375 197.523438 "/>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-1" x="20.21875" y="285.680664"/>
+  <use xlink:href="#glyph0-2" x="25.21875" y="285.680664"/>
+</g>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-3" x="20.21875" y="153.942383"/>
+  <use xlink:href="#glyph0-2" x="25.21875" y="153.942383"/>
+</g>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-4" x="20.21875" y="60.469727"/>
+  <use xlink:href="#glyph0-2" x="25.21875" y="60.469727"/>
+</g>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 282.765625 L 35.152344 282.765625 "/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 151.027344 L 35.152344 151.027344 "/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 32.410156 57.554688 L 35.152344 57.554688 "/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.214844 472.589844 L 67.214844 469.847656 "/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 136.914062 472.589844 L 136.914062 469.847656 "/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 206.617188 472.589844 L 206.617188 469.847656 "/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 276.316406 472.589844 L 276.316406 469.847656 "/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 346.019531 472.589844 L 346.019531 469.847656 "/>
+<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;" d="M 415.722656 472.589844 L 415.722656 469.847656 "/>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-5" x="62.214844" y="481.196289"/>
+  <use xlink:href="#glyph0-2" x="67.214844" y="481.196289"/>
+</g>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-5" x="131.914062" y="481.196289"/>
+  <use xlink:href="#glyph0-6" x="136.914062" y="481.196289"/>
+</g>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-1" x="201.617188" y="481.196289"/>
+  <use xlink:href="#glyph0-2" x="206.617188" y="481.196289"/>
+</g>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-1" x="271.316406" y="481.196289"/>
+  <use xlink:href="#glyph0-6" x="276.316406" y="481.196289"/>
+</g>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-3" x="341.019531" y="481.196289"/>
+  <use xlink:href="#glyph0-2" x="346.019531" y="481.196289"/>
+</g>
+<g style="fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;">
+  <use xlink:href="#glyph0-3" x="410.722656" y="481.196289"/>
+  <use xlink:href="#glyph0-6" x="415.722656" y="481.196289"/>
+</g>
+<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
+  <use xlink:href="#glyph1-1" x="227.496094" y="494.538086"/>
+  <use xlink:href="#glyph1-2" x="233.496094" y="494.538086"/>
+  <use xlink:href="#glyph1-3" x="236.496094" y="494.538086"/>
+</g>
+<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
+  <use xlink:href="#glyph2-1" x="13.499023" y="247.164062"/>
+  <use xlink:href="#glyph2-2" x="13.499023" y="241.164062"/>
+  <use xlink:href="#glyph2-3" x="13.499023" y="233.164062"/>
+</g>
+<path style=" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;" d="M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 "/>
+<g clip-path="url(#clip20)" clip-rule="nonzero">
+<rect x="0" y="0" width="504" height="504" style="fill:url(#pattern0);stroke:none;"/>
+</g>
+<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
+  <use xlink:href="#glyph0-1" x="473.042969" y="282.805664"/>
+  <use xlink:href="#glyph0-2" x="478.042969" y="282.805664"/>
+  <use xlink:href="#glyph0-2" x="483.042969" y="282.805664"/>
+  <use xlink:href="#glyph0-2" x="488.042969" y="282.805664"/>
+</g>
+<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
+  <use xlink:href="#glyph0-1" x="473.042969" y="263.672852"/>
+  <use xlink:href="#glyph0-2" x="478.042969" y="263.672852"/>
+  <use xlink:href="#glyph0-2" x="483.042969" y="263.672852"/>
+  <use xlink:href="#glyph0-1" x="488.042969" y="263.672852"/>
+</g>
+<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
+  <use xlink:href="#glyph0-1" x="473.042969" y="244.536133"/>
+  <use xlink:href="#glyph0-2" x="478.042969" y="244.536133"/>
+  <use xlink:href="#glyph0-2" x="483.042969" y="244.536133"/>
+  <use xlink:href="#glyph0-4" x="488.042969" y="244.536133"/>
+</g>
+<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
+  <use xlink:href="#glyph0-1" x="473.042969" y="225.399414"/>
+  <use xlink:href="#glyph0-2" x="478.042969" y="225.399414"/>
+  <use xlink:href="#glyph0-2" x="483.042969" y="225.399414"/>
+  <use xlink:href="#glyph0-7" x="488.042969" y="225.399414"/>
+</g>
+<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
+  <use xlink:href="#glyph0-1" x="473.042969" y="206.262695"/>
+  <use xlink:href="#glyph0-2" x="478.042969" y="206.262695"/>
+  <use xlink:href="#glyph0-2" x="483.042969" y="206.262695"/>
+  <use xlink:href="#glyph0-8" x="488.042969" y="206.262695"/>
+</g>
+<g style="fill:rgb(0%,0%,0%);fill-opacity:1;">
+  <use xlink:href="#glyph1-3" x="450.28125" y="195.245117"/>
+  <use xlink:href="#glyph1-4" x="455.28125" y="195.245117"/>
+  <use xlink:href="#glyph1-5" x="461.28125" y="195.245117"/>
+  <use xlink:href="#glyph1-6" x="467.28125" y="195.245117"/>
+</g>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 450.28125 279.890625 L 453.738281 279.890625 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 450.28125 260.757812 L 453.738281 260.757812 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 450.28125 241.621094 L 453.738281 241.621094 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 450.28125 222.484375 L 453.738281 222.484375 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 450.28125 203.347656 L 453.738281 203.347656 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 464.105469 279.890625 L 467.5625 279.890625 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 464.105469 260.757812 L 467.5625 260.757812 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 464.105469 241.621094 L 467.5625 241.621094 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 464.105469 222.484375 L 467.5625 222.484375 "/>
+<path style="fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 464.105469 203.347656 L 467.5625 203.347656 "/>
+</g>
+</svg>
+
 ```

### 2024-03-19 docs/projects/datavis/ggplot/comparing.qmd
ggplot - rerendered

@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x64571c465368&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x623a23bd4218&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x64571c465368&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x623a23bd4218&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 

### 2024-03-19 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x64571892e140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x623a200a6140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x64571892e140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x623a200a6140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x64571c897ab0&gt;\n&lt;environment: 0x6457297906a8&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x623a24006960&gt;\n&lt;environment: 0x623a2f3e8728&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x64571c89d3b0&gt;\n&lt;environment: 0x645729790830&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x623a2400c260&gt;\n&lt;environment: 0x623a2f3e85a0&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x64571c8a09d8&gt;\n&lt;environment: 0x645729790980&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x623a2400f888&gt;\n&lt;environment: 0x623a2f3e8450&gt;\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x645722073738&gt;\n&lt;environment: 0x64572227d608&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x623a297efa38&gt;\n&lt;environment: 0x623a275434e8&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x645722073888&gt;\n&lt;environment: 0x64572227d608&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x623a297efb88&gt;\n&lt;environment: 0x623a275434e8&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x645721fbb9d8&gt;\n&lt;environment: 0x645722279368&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x623a29737d80&gt;\n&lt;environment: 0x623a27547910&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x64571c89d3b0&gt;\n&lt;environment: 0x645722279800&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x623a2400c260&gt;\n&lt;environment: 0x623a275474e8&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x64571c8a09d8&gt;\n&lt;environment: 0x645722279950&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x623a2400f888&gt;\n&lt;environment: 0x623a27547360&gt;\n",
      :domain [1.0E-100 ##Inf]},

### 2024-03-19 docs/projects/datavis/ggplot/ggplotly.qmd
ggplot - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: ggplotly.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style><style>.clay-limit-image-width .clay-image {max-width: 100%}
</style>
<script src="ggplotly_files/md-default0.js" type="text/javascript"></script><script src="ggplotly_files/md-default1.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/htmlwidgets-1.6.2/htmlwidgets.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/plotly-binding-4.10.4.9000/plotly.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/typedarray-0.1/typedarray.min.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/jquery-3.5.1/jquery.min.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/crosstalk-1.2.1/js/crosstalk.min.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/plotly-main-2.11.1/plotly-latest.min.js" type="text/javascript"></script><link href="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/crosstalk-1.2.1/css/crosstalk.min.css" rel="stylesheet" type="text/css" /><link href="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/plotly-htmlwidgets-css-2.11.1/plotly-htmlwidgets.css" rel="stylesheet" type="text/css" />

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

::: {.sourceClojure}
```clojure
(ns ggplotly
  (:require [scicloj.kindly.v4.kind :as kind]
            [charred.api :as charred]
            [clojure.math :as math]
            [scicloj.ggclj.geom.point :as point]
            [scicloj.ggclj.api :as gg]
            [scicloj.metamorph.ml.toydata.ggplot :as toydata.ggplot]
            [tablecloth.api :as tc]))
```
:::

# Rendering ggclj using htmlwidgets ggplotly

Here we render plots through the JS client side of [ggplotly](https://plotly.com/ggplot2/)
- an R package (part of the [htmlwidgets](https://www.htmlwidgets.org/) ecosystem) offering a Plotly fronted for ggplot2's grammar of graphics implementation.

The following is a work-in-progress attempt to generate
JSON specs of the kind consumed by ggplotly's client side.

The following spec function was generaged by mimicking R's
`ggplotlTentativey(ggplot(mtcars, aes(wt, mpg)) + geom_point())`'s output.
Therefore, some parts are hard-coded and require generalization.
Other parts are still missing (e.g., specifying colours).

::: {.sourceClojure}
```clojure
(defn ->ggplotly-spec [{:keys [layers labels]}]
  (kind/htmlwidgets-ggplotly
   (let [;; assuming one layer:
         {:keys [data xmin xmax ymin ymax]} (first layers)
         ;; an auxiliary function:
         ->tickvals (fn [l r]
                      (let [jump (-> (- r l)
                                     (/ 6)
                                     math/floor
                                     int
                                     (max 1))]
                        (-> l
                            math/ceil
                            (range r jump))))]
     {:x
      {:config
       {:doubleClick "reset",
        :modeBarButtonsToAdd ["hoverclosest" "hovercompare"],
        :showSendToCloud false},
       :layout
       {:plot_bgcolor "rgba(235,235,235,1)",
        :paper_bgcolor "rgba(255,255,255,1)",
        :legend
        {:bgcolor "rgba(255,255,255,1)",
         :bordercolor "transparent",
         :borderwidth 1.88976377952756,
         :font {:color "rgba(0,0,0,1)", :family "", :size 11.689497716895}},
        :xaxis (let [tickvals (->tickvals xmin xmax)
                     ticktext (mapv str tickvals)
                     range-len (- xmax xmin)
                     range-expansion (* 0.1 range-len)
                     expanded-range [(- xmin range-expansion)
                                     (+ xmax range-expansion)]]
                 {:linewidth 0,
                  :nticks nil,
                  :linecolor nil,
                  :ticklen 3.65296803652968,
                  :tickcolor "rgba(51,51,51,1)",
                  :tickmode "array",
                  :gridcolor "rgba(255,255,255,1)",
                  :automargin true,
                  :type "linear",
                  :tickvals tickvals
                  :zeroline false,
                  :title
                  {:text (:x labels),
                   :font {:color "rgba(0,0,0,1)", :family "", :size 14.6118721461187}},
                  :tickfont {:color "rgba(77,77,77,1)", :family "", :size 11.689497716895},
                  :autorange false,
                  :showticklabels true,
                  :showline false,
                  :showgrid true,
                  :ticktext ticktext
                  :ticks "outside",
                  :gridwidth 0.66417600664176,
                  :anchor "y",
                  :domain [0 1],
                  :hoverformat ".2f",
                  :tickangle 0,
                  :tickwidth 0.66417600664176,
                  :categoryarray ticktext,
                  :categoryorder "array",
                  :range expanded-range},)
        :font {:color "rgba(0,0,0,1)", :family "", :size 14.6118721461187},
        :showlegend false,
        :barmode "relative",
        :yaxis (let [tickvals (->tickvals ymin ymax)
                     ticktext (mapv str tickvals)
                     range-len (- ymax ymin)
                     range-expansion (* 0.1 range-len)
                     expanded-range [(- ymin range-expansion)
                                     (+ ymax range-expansion)]]
                 {:linewidth 0,
                  :nticks nil,
                  :linecolor nil,
                  :ticklen 3.65296803652968,
                  :tickcolor "rgba(51,51,51,1)",
                  :tickmode "array",
                  :gridcolor "rgba(255,255,255,1)",
                  :automargin true,
                  :type "linear",
                  :tickvals tickvals,
                  :zeroline false,
                  :title
                  {:text (:y labels),
                   :font {:color "rgba(0,0,0,1)", :family "", :size 14.6118721461187}},
                  :tickfont {:color "rgba(77,77,77,1)", :family "", :size 11.689497716895},
                  :autorange false,
                  :showticklabels true,
                  :showline false,
                  :showgrid true,
                  :ticktext ticktext,
                  :ticks "outside",
                  :gridwidth 0.66417600664176,
                  :anchor "x",
                  :domain [0 1],
                  :hoverformat ".2f",
                  :tickangle 0,
                  :tickwidth 0.66417600664176,
                  :categoryarray ticktext,
                  :categoryorder "array",
                  :range expanded-range},)
        :hovermode "closest",
        :margin
        {:t 25.7412480974125,
         :r 7.30593607305936,
         :b 39.6955859969559,
         :l 37.2602739726027},
        :shapes
        [{:yref "paper",
          :fillcolor nil,
          :xref "paper",
          :y1 1,
          :type "rect",
          :line {:color nil, :width 0, :linetype []},
          :y0 0,
          :x1 1,
          :x0 0}]},
       :highlight
       {:on "plotly_click"
        :persistent false,
        :dynamic false,
        :selectize false,
        :opacityDim 0.2,
        :selected {:opacity 1},
        :debounce 0},
       :base_url "https://plot.ly",
       :cur_data "1f2fea5b54d146",
       :source "A",
       :shinyEvents
       ["plotly_hover"
        "plotly_click"
        "plotly_selected"
        "plotly_relayout"
        "plotly_brushed"
        "plotly_brushing"
        "plotly_clickannotation"
        "plotly_doubleclick"
        "plotly_deselect"
        "plotly_afterplot"
        "plotly_sunburstclick"],
       :attrs {:1f2fea5b54d146 {:x {}, :y {}, :type "scatter"}},
       :data
       [{:y (:y data)
         :hoveron "points",
         :frame nil,
         :hoverinfo "text",
         :marker
         {:autocolorscale false,
          :color "rgba(0,0,0,1)",
          :opacity 1,
          :size 5.66929133858268,
          :symbol "circle",
          :line {:width 1.88976377952756, :color "rgba(0,0,0,1)"}},
         :mode "markers",
         :type "scatter",
         :xaxis "x",
         :showlegend false,
         :yaxis "y",
         :x (:x data)
         :text (-> data
                   (tc/select-columns [:x :y])
                   (tc/rows :as-maps)
                   (->> (mapv pr-str)))}]},
      :evals [],
      :jsHooks []})))
```
:::

Now here is how we can display a ggclj structure as a ggplotly plot.

::: {.sourceClojure}
```clojure
(defn ggplotly [ggplot]
  (-> ggplot
      gg/ggplot-build
      ->ggplotly-spec))
```
:::

Let us try it with ggplot's `mpg` dataset.

::: {.sourceClojure}
```clojure
(-> toydata.ggplot/mpg
    (gg/ggplot (gg/aes :displ :hwy))
    (point/geom-point)
    ggplotly)
```
:::

```{=html}
<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-12" style="width:100%;height:400px;"><script data-for="htmlwidget-12" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-12" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>
```

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/ggplotly.clj">projects/datavis/ggplot/notebooks/ggplotly.clj</a></small></small></pre></div>
```

### 2024-03-19 docs/projects/datavis/ggplot/representing.qmd
ggplot - rerendered

@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: representing.html}
+  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: representing.html}
 code-block-background: true

### 2024-03-19 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

@@
 ```clojure
- [1] "ggtrace"   "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices"
- [7] "utils"     "datasets"  "methods"   "base"
+[1] "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices" "utils"    
+[7] "datasets"  "methods"   "base"
 
@@
 ```clojure
-"&lt;?xml version=\"1.0\" encoding=\"UTF-8\"?&gt;\n&lt;svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\"&gt;\n&lt;defs&gt;\n&lt;g&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-7\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-8\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/&gt;\n&lt;/symbol&gt;\n&lt;/g&gt;\n&lt;clipPath id=\"clip1\"&gt;\n  &lt;path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip2\"&gt;\n  &lt;path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip3\"&gt;\n  &lt;path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip4\"&gt;\n  &lt;path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip5\"&gt;\n  &lt;path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip6\"&gt;\n  &lt;path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip7\"&gt;\n  &lt;path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip8\"&gt;\n  &lt;path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip9\"&gt;\n  &lt;path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip10\"&gt;\n  &lt;path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip11\"&gt;\n  &lt;path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip12\"&gt;\n  &lt;path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip13\"&gt;\n  &lt;path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip14\"&gt;\n  &lt;path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip15\"&gt;\n  &lt;path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip16\"&gt;\n  &lt;path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip17\"&gt;\n  &lt;path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip18\"&gt;\n  &lt;path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip19\"&gt;\n  &lt;path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip20\"&gt;\n  &lt;path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/&gt;\n&lt;/clipPath&gt;\n&lt;image id=\"image459\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/&gt;\n&lt;pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\"&gt;\n  &lt;use xlink:href=\"#image459\"/&gt;\n&lt;/pattern&gt;\n&lt;/defs&gt;\n&lt;g id=\"surface455\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/&gt;\n&lt;g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/&gt;\n&lt;/g&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/&gt;\n&lt;g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/&gt;\n&lt;/g&gt;\n&lt;/svg&gt;\n"
+"&lt;?xml version=\"1.0\" encoding=\"UTF-8\"?&gt;\n&lt;svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\"&gt;\n&lt;defs&gt;\n&lt;g&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-7\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-8\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/&gt;\n&lt;/symbol&gt;\n&lt;/g&gt;\n&lt;clipPath id=\"clip1\"&gt;\n  &lt;path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip2\"&gt;\n  &lt;path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip3\"&gt;\n  &lt;path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip4\"&gt;\n  &lt;path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip5\"&gt;\n  &lt;path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip6\"&gt;\n  &lt;path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip7\"&gt;\n  &lt;path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip8\"&gt;\n  &lt;path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip9\"&gt;\n  &lt;path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip10\"&gt;\n  &lt;path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip11\"&gt;\n  &lt;path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip12\"&gt;\n  &lt;path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip13\"&gt;\n  &lt;path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip14\"&gt;\n  &lt;path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip15\"&gt;\n  &lt;path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip16\"&gt;\n  &lt;path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip17\"&gt;\n  &lt;path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip18\"&gt;\n  &lt;path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip19\"&gt;\n  &lt;path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip20\"&gt;\n  &lt;path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/&gt;\n&lt;/clipPath&gt;\n&lt;image id=\"image217\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/&gt;\n&lt;pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\"&gt;\n  &lt;use xlink:href=\"#image217\"/&gt;\n&lt;/pattern&gt;\n&lt;/defs&gt;\n&lt;g id=\"surface213\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/&gt;\n&lt;g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/&gt;\n&lt;/g&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/&gt;\n&lt;g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/&gt;\n&lt;/g&gt;\n&lt;/svg&gt;\n"
 
@@
    :stat_params {:na.rm [false]},
-   :constructor [[$ .MEM x861a15f64ba24c00]],
+   :constructor [[$ .MEM x1a549472598b4a60]],
    :position {:compute_layer :ggproto-method, :super :ggproto-method},
@@
 </clipPath>
-<image id="image486" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
+<image id="image244" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
 <pattern id="pattern0" patternUnits="userSpaceOnUse" width="1" height="300"  patternTransform="matrix(17.28,0,0,0.288,450.281644,203.20411)">
-  <use xlink:href="#image486"/>
+  <use xlink:href="#image244"/>
 </pattern>
 </defs>
-<g id="surface482">
+<g id="surface240">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>

### 2024-03-22 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style><style>.clay-limit-image-width .clay-image {max-width: 100%}
</style>
<script src="index_files/md-default12.js" type="text/javascript"></script><script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/vega14.js" type="text/javascript"></script><script src="index_files/vega15.js" type="text/javascript"></script><script src="index_files/vega16.js" type="text/javascript"></script>

::: {.sourceClojure}
```clojure
(ns index
  (:require [tablecloth.api :as tc]
            [scicloj.noj.v1.vis.hanami :as hanami]
            [aerial.hanami.templates :as ht]
            [aerial.hanami.common :as hc]
            [clojure.string :as str]
            [tech.v3.dataset :as tmd]
            [tech.v3.datatype :as dtype]
            [tech.v3.datatype.functional :as fun]
            [fastmath-clustering.core :as clustering]
            [scicloj.kindly.v4.kind :as kind]
            [charred.api :as charred]))
```
:::

::: {.sourceClojure}
```clojure
(ns index
  (:require [tablecloth.api :as tc]
            [clojure.string :as str]
            [scicloj.noj.v1.vis.hanami :as hanami]
            [aerial.hanami.templates :as ht]
            [fastmath-clustering.core :as clustering]
            [scicloj.kindly.v4.kind :as kind]))
```
:::

::: {.sourceClojure}
```clojure
(defonce raw-trips
  (-> "data/kaggle-cyclistic/202304_divvy_tripdata.csv.gz"
      (tc/dataset {:key-fn keyword})))
```
:::

::: {.sourceClojure}
```clojure
(def coord-colnames
  [:start_lat :start_lng :end_lat :end_lng])
```
:::

::: {.sourceClojure}
```clojure
(def processed-trips
  (-> raw-trips
      (tc/map-columns :hour [:started_at]
                      (fn [s]
                        (-> s
                            (str/split #" ")
                            second
                            (str/split #":")
                            first)))
      (tc/select-rows (fn [row]
                        (->> coord-colnames
                             (map row)
                             (every? some?))))))
```
:::

::: {.sourceClojure}
```clojure
(delay
  (-> processed-trips
      (tc/group-by [:hour])
      (tc/aggregate {:n tc/row-count})
      (tc/order-by [:hour])))
```
:::

::: {.clay-dataset}
_unnamed [24 2]:

| :hour |    :n |
|-------|------:|
|    00 |  5093 |
|    01 |  3227 |
|    02 |  1871 |
|    03 |  1162 |
|    04 |   948 |
|    05 |  2801 |
|    06 |  8859 |
|    07 | 17058 |
|    08 | 22162 |
|    09 | 17299 |
|   ... |   ... |
|    13 | 24807 |
|    14 | 25866 |
|    15 | 30699 |
|    16 | 40338 |
|    17 | 46854 |
|    18 | 38245 |
|    19 | 27078 |
|    20 | 17231 |
|    21 | 14367 |
|    22 | 10810 |
|    23 |  7317 |

:::

::: {.sourceClojure}
```clojure
(defn hour-counts-plot [trips]
  (-> trips
      (tc/group-by [:hour])
      (tc/aggregate {:n tc/row-count})
      (hanami/plot ht/bar-chart
                   {:X :hour
                    :Y :n})))
```
:::

::: {.sourceClojure}
```clojure
(delay
  (hour-counts-plot processed-trips))
```
:::

```{=html}
<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>
```

::: {.sourceClojure}
```clojure
(defn as-geo [vega-lite-spec]
  (-> vega-lite-spec
      (update :encoding update-keys (fn [k]
                                      (get {:x :latitude
                                            :y :longitude
                                            :x2 :latitude2
                                            :y2 :longitude2}
                                           k k)))
      (assoc :projection {:type :mercator})))
```
:::

::: {.sourceClojure}
```clojure
(delay
  (-> processed-trips
      (tc/random 1000 {:seed 1})
      (hanami/plot ht/rule-chart
                   {:X :start_lat
                    :Y :start_lng
                    :X2 :end_lat
                    :Y2 :end_lng})
      as-geo))
```
:::

```{=html}
<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
```

::: {.sourceClojure}
```clojure
(delay
  (-> processed-trips
      (tc/random 1000 {:seed 1})
      (hanami/plot ht/layer-chart
                   {:TITLE "Chicago bike trips"
                    :LAYER [{:data {:url "notebooks/data/chicago.geojson"
                                    :format {:type "topojson"}}
                             :mark {:type "geoshape"
                                    :filled false
                                    :clip true
                                    :opacity 0.3}}
                            (as-geo
                             (hanami/plot nil
                                          ht/rule-chart
                                          {:X :start_lat
                                           :Y :start_lng
                                           :X2 :end_lat
                                           :Y2 :end_lng
                                           :OPACITY 0.1}))]})))
```
:::

```{=html}
<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
```

::: {.sourceClojure}
```clojure
(def clustering
  (-> processed-trips
      (tc/select-columns coord-colnames)
      tc/rows
      (clustering/k-means 100)
      (dissoc :data)))
```
:::

::: {.sourceClojure}
```clojure
(delay
  (-> processed-trips
      (tc/add-column :cluster (:clustering clustering))
      (tc/group-by [:cluster])
      (tc/without-grouping->
       (tc/order-by (fn [ds]
                      (-> ds :data tc/row-count))
                    :desc)
       (tc/head 5))
      (tc/aggregate {:n tc/row-count
                     :hours (fn [trips]
                              [(hour-counts-plot trips)])
                     :map (fn [trips]
                            [(-> trips
                                 (tc/random 1000 {:seed 1})
                                 (hanami/plot ht/layer-chart
                                              {:TITLE "Chicago bike trips"
                                               :LAYER [{:data {:url "notebooks/chicago.geojson"
                                                               :format {:type "topojson"}}
                                                        :mark {:type "geoshape"
                                                               :filled false
                                                               :clip true
                                                               :opacity 0.3}}
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/rule-chart
                                                                     {:X :start_lat
                                                                      :Y :start_lng
                                                                      :X2 :end_lat
                                                                      :Y2 :end_lng
                                                                      :OPACITY 0.01}))
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/point-chart
                                                                     {:X :start_lat
                                                                      :Y :start_lng
                                                                      :MCOLOR "purple"
                                                                      :OPACITY 0.01}))
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/point-chart
                                                                     {:X :end_lat
                                                                      :Y :end_lng
                                                                      :MCOLOR "green"
                                                                      :OPACITY 0.01}))]}))])})
      kind/table))
```
:::

::: {.clay-table}

```{=html}
<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>79</td><td>12193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>11476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>11174</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>10835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10360</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
```

:::

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/geography/chicago-bikes/notebooks/index.clj">projects/geography/chicago-bikes/notebooks/index.clj</a></small></small></pre></div>
```

### 2024-03-22 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 <script src="index_files/md-default12.js" type="text/javascript"></script><script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/vega14.js" type="text/javascript"></script><script src="index_files/vega15.js" type="text/javascript"></script><script src="index_files/vega16.js" type="text/javascript"></script>
+
+```{=html}
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+```
 
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>79</td><td>12193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>11476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>11174</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>10835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10360</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>15</td><td>13103</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>11728</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>11427</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>56</td><td>11393</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>36</td><td>11366</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-22 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - updated

@@
                             [(-> trips
-                                 (tc/random 1000 {:seed 1})
                                  (hanami/plot ht/layer-chart
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>15</td><td>13103</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>11728</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>11427</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>56</td><td>11393</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>36</td><td>11366</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>57</td><td>13013</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>12917</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>7</td><td>12853</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>12666</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>70</td><td>11639</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-24 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 </style>
-<script src="index_files/md-default12.js" type="text/javascript"></script><script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/vega14.js" type="text/javascript"></script><script src="index_files/vega15.js" type="text/javascript"></script><script src="index_files/vega16.js" type="text/javascript"></script>
+<script src="index_files/md-default22.js" type="text/javascript"></script><script src="index_files/md-default23.js" type="text/javascript"></script><script src="index_files/vega24.js" type="text/javascript"></script><script src="index_files/vega25.js" type="text/javascript"></script><script src="index_files/vega26.js" type="text/javascript"></script>
 
@@
 
-::: {.sourceClojure}
-```clojure
-(ns index
-  (:require [tablecloth.api :as tc]
-            [scicloj.noj.v1.vis.hanami :as hanami]
-            [aerial.hanami.templates :as ht]
-            [aerial.hanami.common :as hc]
-            [clojure.string :as str]
-            [tech.v3.dataset :as tmd]
-            [tech.v3.datatype :as dtype]
-            [tech.v3.datatype.functional :as fun]
-            [fastmath-clustering.core :as clustering]
-            [scicloj.kindly.v4.kind :as kind]
-            [charred.api :as charred]))
-```
-:::
+# Chicago bikes - DRAFT
+
+This page will be updated soon.
+
+## Data sources:
+[Kaggle - Cyclistic bike share](https://www.kaggle.com/datasets/evangower/cyclistic-bike-share)
+[Kaggle - Cyclistic bike share - 2023 update](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023)
+[Chicago neighborhoods geojson by @blackmad](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson)
+
+## Workflow
 
@@
                     :desc)
-       (tc/head 5))
+       (tc/head 10))
       (tc/aggregate {:n tc/row-count
@@
                                               {:TITLE "Chicago bike trips"
-                                               :LAYER [{:data {:url "notebooks/chicago.geojson"
+                                               :LAYER [{:data {:url "notebooks/data/chicago.geojson"
                                                                :format {:type "topojson"}}
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>57</td><td>13013</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>12917</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>7</td><td>12853</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>12666</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>70</td><td>11639</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>79</td><td>12193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>11476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>11174</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>10835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10360</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>7</td><td>10278</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>88</td><td>9522</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>56</td><td>9493</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>8931</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>8811</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-24 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

--- 2024-03-22 docs/projects/geography/chicago-bikes/index.qmd
@@
 
-::: {.sourceClojure}
-```clojure
-(ns index
-  (:require [tablecloth.api :as tc]
-            [scicloj.noj.v1.vis.hanami :as hanami]
-            [aerial.hanami.templates :as ht]
-            [aerial.hanami.common :as hc]
-            [clojure.string :as str]
-            [tech.v3.dataset :as tmd]
-            [tech.v3.datatype :as dtype]
-            [tech.v3.datatype.functional :as fun]
-            [fastmath-clustering.core :as clustering]
-            [scicloj.kindly.v4.kind :as kind]
-            [charred.api :as charred]))
-```
-:::
+# Chicago bikes - DRAFT
+
+This page will be updated soon.
+
+## Data sources:
+- [Cyclistic bike share - Kaggle](https://www.kaggle.com/datasets/evangower/cyclistic-bike-share)
+- [Cyclistic bike share - 2023 update - Kaggle](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023)
+- [Chicago neighborhoods geojson by @blackmad](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson)
+
+## Workflow
 
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>57</td><td>13013</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>12917</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>7</td><td>12853</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>12666</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>70</td><td>11639</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>15</td><td>13103</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>11728</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>11427</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>56</td><td>11393</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>36</td><td>11366</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>79</td><td>10406</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>10088</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>93</td><td>9943</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>76</td><td>9885</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>19</td><td>9390</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-24 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

--- 2024-03-22 docs/projects/geography/chicago-bikes/index.qmd
@@
                                            k k)))
-      (assoc :projection {:type :mercator})))
+      (assoc :projection {:type :mercator})
+      ;; to improve performance, we avoid rendering as SVG in this case:
+      (dissoc :usermeta)))
 ```
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
 
+A few clueters:
+
 ::: {.sourceClojure}
@@
       (tc/aggregate {:n tc/row-count
-                     :hours (fn [trips]
-                              [(hour-counts-plot trips)])
                      :map (fn [trips]
@@
                                                                       :MCOLOR "green"
-                                                                      :OPACITY 0.01}))]}))])})
+                                                                      :OPACITY 0.01}))]}))])
+                     :hours (fn [trips]
+                              [(hour-counts-plot trips)])})
       kind/table))
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>57</td><td>13013</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>12917</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>7</td><td>12853</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>12666</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>70</td><td>11639</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>79</td><td>12193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>11476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>11174</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>10835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10360</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-24 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 format:
-  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: index.html}
+  html:
+    toc: true
+    toc-depth: 4
+    theme: [cosmo, notebooks/custom.scss]
+    output-file: index.html
 code-block-background: true
 include-in-header: {text: '<link rel = "icon" href = "data:," />'}
+fontsize: 0.8em
 
@@
   (:require [tablecloth.api :as tc]
+            [tech.v3.datatype.datetime :as datetime]
             [clojure.string :as str]
@@
   (-> "data/kaggle-cyclistic/202304_divvy_tripdata.csv.gz"
-      (tc/dataset {:key-fn keyword})))
+      (tc/dataset {:parser-fn {"started_at" [:local-date-time "yyyy-MM-dd HH:mm:ss"]
+                               "ended_at" [:local-date-time "yyyy-MM-dd HH:mm:ss"]}
+                   :key-fn keyword})))
 ```
@@
   (-> raw-trips
-      (tc/map-columns :hour [:started_at]
-                      (fn [s]
-                        (-> s
-                            (str/split #" ")
-                            second
-                            (str/split #":")
-                            first)))
+      (tc/add-column :hour (fn [trips]
+                             (->> trips
+                                  :started_at
+                                  (datetime/long-temporal-field :hours))))
       (tc/select-rows (fn [row]
@@
 | :hour |    :n |
-|-------|------:|
-|    00 |  5093 |
-|    01 |  3227 |
-|    02 |  1871 |
-|    03 |  1162 |
-|    04 |   948 |
-|    05 |  2801 |
-|    06 |  8859 |
-|    07 | 17058 |
-|    08 | 22162 |
-|    09 | 17299 |
+|------:|------:|
+|     0 |  5093 |
+|     1 |  3227 |
+|     2 |  1871 |
+|     3 |  1162 |
+|     4 |   948 |
+|     5 |  2801 |
+|     6 |  8859 |
+|     7 | 17058 |
+|     8 | 22162 |
+|     9 | 17299 |
 |   ... |   ... |
@@
                                            k k)))
-      (assoc :projection {:type :mercator})
-      ;; to improve performance, we avoid rendering as SVG in this case:
-      (dissoc :usermeta)))
+      (assoc :projection {:type :mercator})))
 ```
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
 
-A few clueters:
+Let us plot a few clusters:
+
+::: {.sourceClojure}
+```clojure
+(defn as-png [vega-lite-spec]
+  ;; to improve performance, we avoid rendering as SVG in this case:
+  (-> vega-lite-spec
+      (assoc :usermeta {:embedOptions {:renderer :png}})))
+```
+:::
 
@@
                                                                       :MCOLOR "green"
-                                                                      :OPACITY 0.01}))]}))])
+                                                                      :OPACITY 0.01}))]})
+                                 as-png)])
                      :hours (fn [trips]
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>79</td><td>12193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>11476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>11174</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>10835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10360</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>53</td><td>13873</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>12624</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>12573</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>84</td><td>11463</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>11325</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-24 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>53</td><td>13873</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>12624</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>12573</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>84</td><td>11463</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>11325</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>1</td><td>11750</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>11208</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>11195</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>52</td><td>10907</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-25 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 
-## Workflow
+## Setup
 
@@
   (:require [tablecloth.api :as tc]
+            [clojure.math :as math]
             [tech.v3.datatype.datetime :as datetime]
@@
             [fastmath-clustering.core :as clustering]
-            [scicloj.kindly.v4.kind :as kind]))
+            [geo
+             [geohash :as geohash]
+             [jts :as jts]
+             [spatial :as spatial]
+             [io :as geoio]
+             [crs :as crs]]
+            [scicloj.kindly.v4.kind :as kind]
+            [scicloj.kindly.v4.api :as kindly])
+  (:import (org.locationtech.jts.geom Geometry Point Polygon Coordinate)
+           (org.locationtech.jts.geom.prep PreparedGeometry
+                                           PreparedLineString
+                                           PreparedPolygon
+                                           PreparedGeometryFactory)))
 ```
 :::
+
+## Reading the data
 
@@
 :::
+
+## Coordinate conversions
+
+The datasets uses the [WGS84](https://en.wikipedia.org/wiki/World_Geodetic_System)
+coordinate system, representing latitude and longitued over the globe.
+[EPSG:4326](https://epsg.io/4326)
+
+For metric computations we need to convert them to a coordinate system
+which is locally correct in terms of distances in a region around Chicago:
+NAD83 / Illinois East
+[EPSG:26971](https://epsg.io/26971-1742)
+
+::: {.clay-dataset}
+United States (USA) - Oregon and Washington. [1 3]:
+
+|   Center coordinates |                             Projected bounds |                   WGS84 bounds |
+|----------------------|----------------------------------------------|--------------------------------|
+| [316133.6 345590.74] | [[216692.35 43649.23] [416809.98 648476.24]] | [[-89.27 37.06] [-87.02 42.5]] |
+
+:::
+
+::: {.sourceClojure}
+```clojure
+(def crs-transform
+  (geo.crs/create-transform (geo.crs/create-crs 4326)
+                            (geo.crs/create-crs 26971)))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn wgs84->Chicago
+  "Transforming latitude-longitude coordinates
+  to local Euclidean coordinates around Seattle."
+  [geometry]
+  (geo.jts/transform-geom geometry crs-transform))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn lat-lng->local-coords [lat lng]
+  (-> (geo.jts/coordinate -89.27 37.06)
+      geo.jts/point
+      wgs84->Chicago
+      geo.jts/coord
+      ((fn [^Coordinate coord]
+         [(.getX coord)
+          (.getY coord)]))))
+```
+:::
+
+Example:
+
+::: {.sourceClojure}
+```clojure
+(delay
+  (lat-lng->local-coords -89.27 37.06))
+```
+:::
+
+::: {.printedClojure}
+```clojure
+[216692.34803057025 44059.50658557552]
+
+```
+:::
+
+## Preprocessing
 
@@
                              (map row)
-                             (every? some?))))))
+                             (every? some?))))
+      (tc/map-columns :start-local-coords [:start_lat :start_lng] lat-lng->local-coords)
+      (tc/map-columns :end-local-coords [:end_lat :end_lng] lat-lng->local-coords)
+      (tc/map-columns :start-local-x [:start-local-coords] first)
+      (tc/map-columns :start-local-y [:start-local-coords] second)
+      (tc/map-columns :end-local-x [:end-local-coords] first)
+      (tc/map-columns :end-local-y [:end-local-coords] second)))
 ```
 :::
+
+## Comparing Eucledian (L2) distances in global and local coordinates
+
+TODO
+
+## Basic analysis and visualization
 
@@
 
+## Clustering
+
 ::: {.sourceClojure}
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>1</td><td>11750</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>11208</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>11195</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>52</td><td>10907</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>92</td><td>12495</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>39</td><td>12190</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>12107</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>11723</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>45</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-25 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered after bugfix

@@
             [tech.v3.datatype.datetime :as datetime]
+            [tech.v3.datatype.functional :as fun]
             [clojure.string :as str]
@@
 
-For metric computations we need to convert them to a coordinate system
+For metric computations (e.g., k-means clustering),
+we need to convert them to a coordinate system
 which is locally correct in terms of distances in a region around Chicago:
@@
 (defn lat-lng->local-coords [lat lng]
-  (-> (geo.jts/coordinate -89.27 37.06)
+  (-> (geo.jts/coordinate lat lng)
       geo.jts/point
@@
 
-TODO
+::: {.sourceClojure}
+```clojure
+(-> processed-trips
+    (tc/add-column :local-distance #(fun/sqrt
+                                     (fun/+ (fun/sq (fun/- (:start-local-x %)
+                                                           (:end-local-x %)))
+                                            (fun/sq (fun/- (:start-local-y %)
+                                                           (:end-local-y %)))))))
+```
+:::
+
+::: {.clay-dataset}
+data/kaggle-cyclistic/202304_divvy_tripdata.csv.gz [426155 21]:
+
+|         :ride_id | :rideable_type |         :started_at |           :ended_at |        :start_station_name | :start_station_id |         :end_station_name | :end_station_id |  :start_lat |   :start_lng |    :end_lat |     :end_lng | :member_casual | :hour |                        :start-local-coords |                          :end-local-coords |  :start-local-x |  :start-local-y |    :end-local-x |    :end-local-y | :local-distance |
+|------------------|----------------|---------------------|---------------------|----------------------------|-------------------|---------------------------|-----------------|------------:|-------------:|------------:|-------------:|----------------|------:|--------------------------------------------|--------------------------------------------|----------------:|----------------:|----------------:|----------------:|----------------:|
+| 8FE8F7D9C10E88C7 |  electric_bike | 2023-04-02T08:37:28 | 2023-04-02T08:41:37 |                            |                   |                           |                 | 41.80000000 | -87.60000000 | 41.79000000 | -87.60000000 |         member |     8 |  [506107.9325773436 -1.4235352994997954E7] | [506137.42192310654 -1.4235316240199374E7] | 506107.93257734 | -1.42353530E+07 | 506137.42192311 | -1.42353162E+07 |     47.12257137 |
+| 34E4ED3ADF1D821B |  electric_bike | 2023-04-19T11:29:02 | 2023-04-19T11:52:12 |                            |                   |                           |                 | 41.87000000 | -87.65000000 | 41.93000000 | -87.68000000 |         member |    11 |  [501519.8754807859 -1.4231908162239876E7] |  [498721.7934556093 -1.4229901392452776E7] | 501519.87548079 | -1.42319082E+07 | 498721.79345561 | -1.42299014E+07 |   3443.31061597 |
+| 5296BF07A2F77CB5 |  electric_bike | 2023-04-19T08:41:22 | 2023-04-19T08:43:22 |                            |                   |                           |                 | 41.93000000 | -87.66000000 | 41.93000000 | -87.66000000 |         member |     8 | [500470.98093146156 -1.4231382653142933E7] | [500470.98093146156 -1.4231382653142933E7] | 500470.98093146 | -1.42313827E+07 | 500470.98093146 | -1.42313827E+07 |      0.00000000 |
+| 40759916B76D5D52 |  electric_bike | 2023-04-19T13:31:30 | 2023-04-19T13:35:09 |                            |                   |                           |                 | 41.92000000 | -87.65000000 | 41.91000000 | -87.65000000 |         member |    13 |  [501374.92347210384 -1.423208764589309E7] |  [501403.9254779691 -1.4232051758343631E7] | 501374.92347210 | -1.42320876E+07 | 501403.92547797 | -1.42320518E+07 |     46.14144070 |
+| 77A96F460101AC63 |  electric_bike | 2023-04-19T12:05:36 | 2023-04-19T12:10:26 |                            |                   |                           |                 | 41.91000000 | -87.65000000 | 41.91000000 | -87.63000000 |         member |    12 |  [501403.9254779691 -1.4232051758343631E7] |  [503154.9287078667 -1.4233533354956321E7] | 501403.92547797 | -1.42320518E+07 | 503154.92870787 | -1.42335334E+07 |   2293.71768835 |
+| 8D6A2328E19DC168 |  electric_bike | 2023-04-19T12:17:34 | 2023-04-19T12:21:38 |                            |                   |                           |                 | 41.91000000 | -87.63000000 | 41.92000000 | -87.65000000 |         member |    12 |  [503154.9287078667 -1.4233533354956321E7] |  [501374.92347210384 -1.423208764589309E7] | 503154.92870787 | -1.42335334E+07 | 501374.92347210 | -1.42320876E+07 |   2293.14049610 |
+| C97BBA66E07889F9 |  electric_bike | 2023-04-19T09:35:48 |    2023-04-19T09:45 |                            |                   |                           |                 | 41.93000000 | -87.66000000 | 41.91000000 | -87.65000000 |         member |     9 | [500470.98093146156 -1.4231382653142933E7] |  [501403.9254779691 -1.4232051758343631E7] | 500470.98093146 | -1.42313827E+07 | 501403.92547797 | -1.42320518E+07 |   1148.07983018 |
+| 6687AD4C575FF734 |  electric_bike | 2023-04-11T16:13:43 | 2023-04-11T16:18:41 |                            |                   |                           |                 | 42.00000000 | -87.66000000 | 41.99000000 | -87.66000000 |         member |    16 |  [500268.5489835212 -1.4231632572144713E7] | [500297.48516240803 -1.4231596883177325E7] | 500268.54898352 | -1.42316326E+07 | 500297.48516241 | -1.42315969E+07 |     45.94567272 |
+| A8FA4F73B22BC11F |  electric_bike | 2023-04-11T16:29:24 | 2023-04-11T16:40:23 |                            |                   |                           |                 | 41.99000000 | -87.66000000 | 42.00000000 | -87.66000000 |         member |    16 | [500297.48516240803 -1.4231596883177325E7] |  [500268.5489835212 -1.4231632572144713E7] | 500297.48516241 | -1.42315969E+07 | 500268.54898352 | -1.42316326E+07 |     45.94567272 |
+| 81E158FE63D99994 |  electric_bike | 2023-04-19T17:35:40 | 2023-04-19T17:36:11 |                            |                   |                           |                 | 41.88000000 | -87.65000000 | 41.88000000 | -87.65000000 |         member |    17 |   [501490.896685202 -1.4231944068150206E7] |   [501490.896685202 -1.4231944068150206E7] | 501490.89668520 | -1.42319441E+07 | 501490.89668520 | -1.42319441E+07 |      0.00000000 |
+|              ...
+|            ...
+|                 ...
+|                 ...
+|                        ...
+|               ...
+|                       ...
+|             ...
+|         ...
+|          ...
+|         ...
+|          ...
+|            ...
+|   ...
+|                                        ...
+|                                        ...
+|             ...
+|             ...
+|             ...
+|             ...
+|             ...
+|
+| BAE25DBA0CD0DF40 |  electric_bike | 2023-04-14T07:12:34 | 2023-04-14T07:42:07 | Richmond St & Diversey Ave |             15645 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.93186915 | -87.70120764 | 41.87593267 | -87.63058454 |         member |     7 |  [496862.65843494714 -1.422833795268237E7] | [503203.23756304523 -1.4233366677138694E7] | 496862.65843495 | -1.42283380E+07 | 503203.23756305 | -1.42333667E+07 |   8092.65181120 |
+| 5A98F86A573AAB2C |  electric_bike | 2023-04-24T07:27:02 | 2023-04-24T07:58:22 | Richmond St & Diversey Ave |             15645 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.93198085 | -87.70128024 | 41.87593267 | -87.63058454 |         member |     7 |  [496855.9967031725 -1.4228332970829802E7] | [503203.23756304523 -1.4233366677138694E7] | 496855.99670317 | -1.42283330E+07 | 503203.23756305 | -1.42333667E+07 |   8100.96696311 |
+| 92B02F2FBDC1FB9F |   classic_bike | 2023-04-12T08:16:48 | 2023-04-12T08:40:08 |     Michigan Ave & Lake St |      TA1305000011 |        May St & Taylor St |           13160 | 41.88602200 | -87.62439800 | 41.86948210 | -87.65548640 |         member |     8 |  [503715.7528127164 -1.4233861403126204E7] | [501040.95186117536 -1.4231500346004825E7] | 503715.75281272 | -1.42338614E+07 | 501040.95186118 | -1.42315003E+07 |   3567.79355636 |
+| 119A6C53607EAA4A |  electric_bike | 2023-04-28T07:24:54 | 2023-04-28T07:53:44 | Richmond St & Diversey Ave |             15645 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.93190396 | -87.70125461 | 41.87593267 | -87.63058454 |         member |     7 |  [496858.4550664372 -1.4228334598338569E7] | [503203.23756304523 -1.4233366677138694E7] | 496858.45506644 | -1.42283346E+07 | 503203.23756305 | -1.42333667E+07 |   8098.02951217 |
+| 9BCF1E8BA027EAFA |  electric_bike | 2023-04-21T07:15:06 | 2023-04-21T07:41:45 | Richmond St & Diversey Ave |             15645 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.93193305 | -87.70126295 | 41.87593267 | -87.63058454 |         member |     7 |  [496857.6431128598 -1.4228334082633112E7] | [503203.23756304523 -1.4233366677138694E7] | 496857.64311286 | -1.42283341E+07 | 503203.23756305 | -1.42333667E+07 |   8098.98613308 |
+| A17D800CE963661A |   classic_bike | 2023-04-11T15:46:42 | 2023-04-11T15:50:03 |     Michigan Ave & Lake St |      TA1305000011 |    Clark St & Randolph St |    TA1305000030 | 41.88602200 | -87.62439800 | 41.88457623 | -87.63188991 |         member |    15 |  [503715.7528127164 -1.4233861403126204E7] |  [503063.6502967095 -1.4233301315734675E7] | 503715.75281272 | -1.42338614E+07 | 503063.65029671 | -1.42333013E+07 |    859.61362107 |
+| 8B441A6C436E9900 |   classic_bike | 2023-04-29T21:20:21 | 2023-04-29T21:30:19 |       Halsted St & 18th St |             13099 | Blue Island Ave & 18th St |           13135 | 41.85750568 | -87.64599144 | 41.85755600 | -87.66153500 |         casual |    21 |  [501907.1861189178 -1.4232159853149524E7] | [500545.77541704464 -1.4231010242258897E7] | 501907.18611892 | -1.42321599E+07 | 500545.77541704 | -1.42310102E+07 |   1781.86539868 |
+| 3980D64BE11540F1 |   classic_bike | 2023-04-24T09:16:05 | 2023-04-24T09:22:27 |       Halsted St & 18th St |             13099 | Blue Island Ave & 18th St |           13135 | 41.85750568 | -87.64599144 | 41.85755600 | -87.66153500 |         casual |     9 |  [501907.1861189178 -1.4232159853149524E7] | [500545.77541704464 -1.4231010242258897E7] | 501907.18611892 | -1.42321599E+07 | 500545.77541704 | -1.42310102E+07 |   1781.86539868 |
+| 3EF4B49FF7DAA02C |   classic_bike | 2023-04-18T07:53:51 | 2023-04-18T07:59:16 | Franklin St & Jackson Blvd |      TA1305000025 |    Clark St & Randolph St |    TA1305000030 | 41.87770796 | -87.63532114 | 41.88457623 | -87.63188991 |         casual |     7 |  [502783.1163597462 -1.4233022413426103E7] |  [503063.6502967095 -1.4233301315734675E7] | 502783.11635975 | -1.42330224E+07 | 503063.65029671 | -1.42333013E+07 |    395.58284532 |
+| 210B2ED6583DC231 |   classic_bike | 2023-04-29T07:33:55 | 2023-04-29T07:38:57 |     Michigan Ave & Lake St |      TA1305000011 |    Clark St & Randolph St |    TA1305000030 | 41.88602200 | -87.62439800 | 41.88457623 | -87.63188991 |         casual |     7 |  [503715.7528127164 -1.4233861403126204E7] |  [503063.6502967095 -1.4233301315734675E7] | 503715.75281272 | -1.42338614E+07 | 503063.65029671 | -1.42333013E+07 |    859.61362107 |
+| D29CB39B9E3FC46A |  electric_bike | 2023-04-18T08:00:32 | 2023-04-18T08:02:35 | Franklin St & Jackson Blvd |      TA1305000025 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.87813417 | -87.63525450 | 41.87593267 | -87.63058454 |         casual |     8 | [502787.71168951405 -1.4233028887672516E7] | [503203.23756304523 -1.4233366677138694E7] | 502787.71168951 | -1.42330289E+07 | 503203.23756305 | -1.42333667E+07 |    535.50301123 |
+
+:::
 
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>92</td><td>12495</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>39</td><td>12190</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>12107</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>11723</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>45</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>79</td><td>12193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>11476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>11174</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>10835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10360</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-25 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

--- 2024-03-24 docs/projects/geography/chicago-bikes/index.qmd
@@
 </style>
-<script src="index_files/md-default12.js" type="text/javascript"></script><script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/vega14.js" type="text/javascript"></script><script src="index_files/vega15.js" type="text/javascript"></script><script src="index_files/vega16.js" type="text/javascript"></script>
+<script src="index_files/md-default43.js" type="text/javascript"></script><script src="index_files/md-default44.js" type="text/javascript"></script><script src="index_files/vega45.js" type="text/javascript"></script><script src="index_files/vega46.js" type="text/javascript"></script><script src="index_files/vega47.js" type="text/javascript"></script>
 
@@
   (:require [tablecloth.api :as tc]
+            [clojure.math :as math]
             [tech.v3.datatype.datetime :as datetime]
+            [tech.v3.datatype.functional :as fun]
             [clojure.string :as str]
@@
 
+## Coordinate conversions
+
+The datasets uses the [WGS84](https://en.wikipedia.org/wiki/World_Geodetic_System)
+coordinate system, representing latitude and longitued over the globe.
+[EPSG:4326](https://epsg.io/4326)
+
+For metric computations (e.g., k-means clustering),
+we need to convert them to a coordinate system
+which is locally correct in terms of distances in a region around Chicago:
+NAD83 / Illinois East
+[EPSG:26971](https://epsg.io/26971)
+
+::: {.clay-dataset}
+United States (USA) - Oregon and Washington. [1 3]:
+
+|   Center coordinates |                             Projected bounds |                   WGS84 bounds |
+|----------------------|----------------------------------------------|--------------------------------|
+| [316133.6 345590.74] | [[216692.35 43649.23] [416809.98 648476.24]] | [[-89.27 37.06] [-87.02 42.5]] |
+
+:::
+
 ::: {.sourceClojure}
 ```clojure
-(def coord-colnames
-  [:start_lat :start_lng :end_lat :end_lng])
+(def crs-transform
+  (geo.crs/create-transform (geo.crs/create-crs 4326)
+                            (geo.crs/create-crs 26971)))
 ```
@@
 ```clojure
+(defn wgs84->Chicago
+  "Transforming latitude-longitude coordinates
+  to local Euclidean coordinates around Seattle."
+  [geometry]
+  (geo.jts/transform-geom geometry crs-transform))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn lng-lat->local-coords [lng lat]
+  (-> (geo.jts/coordinate lng lat)
+      geo.jts/point
+      wgs84->Chicago
+      geo.jts/coord
+      ((fn [^Coordinate coord]
+         [(.getX coord)
+          (.getY coord)]))))
+```
+:::
+
+Example:
+
+::: {.sourceClojure}
+```clojure
+(delay
+  [(lng-lat->local-coords -89.27 37.06)
+   (lng-lat->local-coords -87.02 42.5)])
+```
+:::
+
+::: {.printedClojure}
+```clojure
+[[216692.34803057025 44059.50658557552]
+ [407952.845339763 648476.2402163395]]
+
+```
+:::
+
+## Preprocessing
+
+::: {.sourceClojure}
+```clojure
 (def processed-trips
   (-> raw-trips
+      ;; Compute starting hours:
       (tc/add-column :hour (fn [trips]
@@
                                   (datetime/long-temporal-field :hours))))
+      ;; Make sure the latitude and longitude are nonmissing:
       (tc/select-rows (fn [row]
-                        (->> coord-colnames
+                        (->> [:start_lat :start_lng :end_lat :end_lng]
                              (map row)
-                             (every? some?))))))
+                             (every? some?))))
+      ;; Add local Chicago coordinates:
+      (tc/map-columns :start-local-coords [:start_lng :start_lat] lng-lat->local-coords)
+      (tc/map-columns :end-local-coords [:end_lng :end_lat] lng-lat->local-coords)
+      (tc/map-columns :start-local-x [:start-local-coords] first)
+      (tc/map-columns :start-local-y [:start-local-coords] second)
+      (tc/map-columns :end-local-x [:end-local-coords] first)
+      (tc/map-columns :end-local-y [:end-local-coords] second)))
 ```
 :::
+
+## Comparing Eucledian (L2) distances in global and local coordinates
+
+::: {.sourceClojure}
+```clojure
+(-> processed-trips
+    (tc/random 1000 {:seed 1})
+    (tc/add-column :local-L2 #(fun/sqrt
+                               (fun/+ (fun/sq (fun/- (:start-local-x %)
+                                                     (:end-local-x %)))
+                                      (fun/sq (fun/- (:start-local-y %)
+                                                     (:end-local-y %))))))
+    (tc/add-column :global-L2 #(fun/sqrt
+                                (fun/+ (fun/sq (fun/- (:start_lat %)
+                                                      (:end_lat %)))
+                                       (fun/sq (fun/- (:start_lng %)
+                                                      (:end_lng %))))))
+    (hanami/plot ht/point-chart
+                 {:X :local-L2
+                  :Y :global-L2}))
+```
+:::
+
+```{=html}
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"global-L2","type":"quantitative"},"x":{"field":"local-L2","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>
+```
+
+The `local-L2` quantity, compted from the local Chicago coordinates,
+is a decent approximation of actual distance.
+We see that the `global-L2` quantity, computed accordingly
+from latitude and longitude, is not directly related to
+this quantity and might be misleading for metric tasks
+such as clustering.
+
+## Basic analysis and visualization
 
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
+```
+
+::: {.sourceClojure}
+```clojure
+(delay
+  (-> processed-trips
+      (tc/random 1000 {:seed 1})
+      (hanami/plot ht/rule-chart
+                   {:X :start-local-x
+                    :Y :start-local-y
+                    :X2 :end-local-x
+                    :Y2 :end-local-y
+                    :XSCALE {:zero false}
+                    :YSCALE {:zero false}})))
+```
+:::
+
+```{=html}
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"scale":{"zero":false},"field":"start-local-y","type":"quantitative"},"x":{"scale":{"zero":false},"field":"start-local-x","type":"quantitative"},"y2":{"scale":{"zero":false},"field":"end-local-y","type":"quantitative"},"x2":{"scale":{"zero":false},"field":"end-local-x","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
 ```
+
+## Clustering
 
@@
   (-> processed-trips
-      (tc/select-columns coord-colnames)
+      (tc/select-columns [:start-local-x
+                          :start-local-y
+                          :end-local-x
+                          :end-local-y])
       tc/rows
@@
                     :desc)
-       (tc/head 5))
+       (tc/head 20))
       (tc/aggregate {:n tc/row-count
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>1</td><td>11750</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>11208</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>11195</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>52</td><td>10907</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>15</td><td>13295</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>33</td><td>12755</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>35</td><td>12720</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>98</td><td>11474</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>31</td><td>11101</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>20</td><td>10615</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>83</td><td>10431</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>23</td><td>10279</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>10237</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>54</td><td>10084</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>80</td><td>9998</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/23.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/24.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>62</td><td>9972</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/25.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/26.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>4</td><td>9850</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/27.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/28.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>76</td><td>9422</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/29.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/30.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>11</td><td>8835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/31.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/32.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>9</td><td>8699</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/33.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/34.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>99</td><td>8191</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/35.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/36.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>96</td><td>7838</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/37.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/38.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>7468</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/39.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/40.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>57</td><td>6689</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/41.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/42.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-25 docs/projects/index/index.qmd
Chicago bikes - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}
title: Clojure Data Scrapbook

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default0.js" type="text/javascript"></script><script src="index_files/md-default1.js" type="text/javascript"></script>

```{=html}
<img align="right" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="100" />
```

The Clojure Data Scrapbook is a collection of
community-contributed examples for the emerging Clojure data stack.

You can interact with the examples by cloning this project and starting a REPL.

This project is part of the [SciCloj community](https://scicloj.github.io/docs/community/about/).

## Tutorials

```{=html}
<table class="table"><thead><tr><th>date</th><th>title</th><th>video</th><th>tags</th></tr></thead><tbody><tr><td><span data-qmd="2023-12-16"></span></td><td><div><pre><p><a href="projects/visual-tools/clay-calva-demo-20231216/index.html">Clay Calva integration - datavis demo</a></p><p><a href="https://github.com/scicloj/clojure-data-scrapbook/tree/main/projects/visual-tools/clay-calva-demo-20231216" style="background-color:#fdf6e3;">(source)</a></p></pre></div></td><td><iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/X_SsjhmG5Ok"></iframe></td><td><span data-qmd="visual-tools, clay, calva, noj, datavis, hanami, tablecloth"></span></td></tr><tr><td><span data-qmd="2023-12-17"></span></td><td><div><pre><p><a href="projects/visual-tools/clay-cider-demo-20231217/index.html">Clay CIDER integration - image processing demo</a></p><p><a href="https://github.com/scicloj/clojure-data-scrapbook/tree/main/projects/visual-tools/clay-cider-demo-20231217" style="background-color:#fdf6e3;">(source)</a></p></pre></div></td><td><iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/fd4kjlws6Ts"></iframe></td><td><span data-qmd="visual-tools, clay, cider, noj, image-processing, dtype-next, tensors"></span></td></tr><tr><td><span data-qmd="2023-12-31"></span></td><td><div><pre><p><a href="projects/data-formats/hdf/index.html">Reading HDF files</a></p><p><a href="https://github.com/scicloj/clojure-data-scrapbook/tree/main/projects/data-formats/hdf/" style="background-color:#fdf6e3;">(source)</a></p></pre></div></td><td><span data-qmd=""></span></td><td><span data-qmd="data-formats, hdf, dtype-next, tensors"></span></td></tr><tr><td><span data-qmd="2024-01-11"></span></td><td><div><pre><p><a href="projects/noj/ml.html">Machine learning - DRAFT</a></p><p><a href="https://github.com/scicloj/clojure-data-scrapbook/tree/main/projects/noj/notebooks/ml.clj" style="background-color:#fdf6e3;">(source)</a></p></pre></div></td><td><span data-qmd=""></span></td><td><span data-qmd="noj, ml, scicloj.ml, draft"></span></td></tr><tr><td><span data-qmd="2024-01-25"></span></td><td><div><pre><p><a href="projects/math/wolframite/index.html">Wolfram Lanauge interop with Wolframite</a></p><p><a href="https://github.com/scicloj/clojure-data-scrapbook/tree/main/projects/math/wolframite/" style="background-color:#fdf6e3;">(source)</a></p></pre></div></td><td><span data-qmd=""></span></td><td><span data-qmd="math, wolframite, interop, draft"></span></td></tr><tr><td><span data-qmd="2024-02-06"></span></td><td><div><pre><p><a href="projects/noj/ggplot.html">Exploring ggplot - DRAFT</a></p><p><a href="https://github.com/scicloj/clojure-data-scrapbook/tree/main/projects/noj/notebooks/ggplot.clj" style="background-color:#fdf6e3;">(source)</a></p></pre></div></td><td><span data-qmd=""></span></td><td><span data-qmd="noj, r, clojisr, interop, ggplot, datavis, draft"></span></td></tr></tbody></table>
```

## Contributing
(coming soon)

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/index/notebooks/index.clj">projects/index/notebooks/index.clj</a></small></small></pre></div>
```

### 2024-03-26 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

--- 2024-03-25 docs/projects/geography/chicago-bikes/index.qmd
@@
 
-## Data sources:
-- [Cyclistic bike share - Kaggle](https://www.kaggle.com/datasets/evangower/cyclistic-bike-share)
-- [Cyclistic bike share - 2023 update - Kaggle](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023)
-- [Chicago neighborhoods geojson by @blackmad](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson)
-
 ## Setup
@@
 
+In this notebook, we will explore the data of a bike sharing company in Chicago.
+
+The data provides information of start & end location & time for each bike trip.
+It has been used in academic papers and blog posts discussing various aspects of
+people's movement patterns in their everyday lives.
+
+Our goal here is to recognize and visualize a few movement patterns.
+
+## Background
+
+### Various openly shared datasets:
+- [Divvy Trips](https://data.cityofchicago.org/Transportation/Divvy-Trips/fg6s-gzvg/about_data) - Chicago data portal
+- [Chicago Divvy Bicycle Sharing Data](https://www.kaggle.com/datasets/yingwurenjian/chicago-divvy-bicycle-sharing-data) - Kaggle
+- [Cyclistic bike share](https://www.kaggle.com/datasets/evangower/cyclistic-bike-share) - Kaggle
+- [Cyclistic bike share - 2023 update](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023) - Kaggle
+
+### Research papers and blog posts
+- [Understanding Spatiotemporal Patterns of Biking Behavior by Analyzing Massive Bike Sharing Data in Chicago](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0137922) - Zhou 2015
+- [Bicycle-Sharing System Analysis and Trip](https://www.cs.uic.edu/~jzhang2/files/2016_mdm_paper.pdf) - Zhang el al. 2016
+- [Spatial Cluster-Based Model for Static Rebalancing Bike Sharing Problem](https://www.mdpi.com/2071-1050/11/11/3205) - Lahoorpoor et al. 2019
+- [Examining spatiotemporal changing patterns of bike-sharing usage during COVID-19 pandemic](https://www.sciencedirect.com/science/article/pii/S0966692321000508) - Hu et al. 2021
+- [Analysis: Chicago’s Divvy Bike Share](https://andrewluyt.github.io/divvy-bikeshare/analysis-report.html) - Luyt 2021
+
+## Data sources for this notebook
+
+1.
+[Chicago neighborhoods geojson](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson) - part of [a great collection](https://github.com/blackmad/neighborhoods/) by [@blackmad](https://github.com/blackmad).
+We keep this file under "notebooks/data/". By default, [Clay](https://scicloj.github.io/clay) pushed data files under "notebooks" to the target render directory.
+This will allow us to consume the file from the browser for data visualizations.
+
+2. [Cyclistic bike share - 2023 update](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023) - shared on Kaggle by Jayprakash Kumar.
+This dataset contains separate data files for different months. We will use only one of them here (Apr. 2023) and keep it under "data/".
+
 ## Reading the data
@@
 
-For metric computations we need to convert them to a coordinate system
+For metric computations (e.g., k-means clustering),
+we need to convert them to a coordinate system
 which is locally correct in terms of distances in a region around Chicago:
 NAD83 / Illinois East
-[EPSG:26971](https://epsg.io/26971-1742)
+[EPSG:26971](https://epsg.io/26971)
 
@@
 ```clojure
-(defn lat-lng->local-coords [lat lng]
-  (-> (geo.jts/coordinate -89.27 37.06)
+(defn lng-lat->local-coords [lng lat]
+  (-> (geo.jts/coordinate lng lat)
       geo.jts/point
@@
 (delay
-  (lat-lng->local-coords -89.27 37.06))
+  [(lng-lat->local-coords -89.27 37.06)
+   (lng-lat->local-coords -87.02 42.5)])
 ```
@@
 ```clojure
-[216692.34803057025 44059.50658557552]
+[[216692.34803057025 44059.50658557552]
+ [407952.845339763 648476.2402163395]]
 
@@
 ```clojure
-(def coord-colnames
-  [:start_lat :start_lng :end_lat :end_lng])
-```
-:::
-
-::: {.sourceClojure}
-```clojure
 (def processed-trips
   (-> raw-trips
+      ;; Compute starting hours:
       (tc/add-column :hour (fn [trips]
@@
                                   (datetime/long-temporal-field :hours))))
+      ;; Make sure the latitude and longitude are nonmissing:
       (tc/select-rows (fn [row]
-                        (->> coord-colnames
+                        (->> [:start_lat :start_lng :end_lat :end_lng]
                              (map row)
                              (every? some?))))
-      (tc/map-columns :start-local-coords [:start_lat :start_lng] lat-lng->local-coords)
-      (tc/map-columns :end-local-coords [:end_lat :end_lng] lat-lng->local-coords)
+      ;; Add local Chicago coordinates:
+      (tc/map-columns :start-local-coords [:start_lng :start_lat] lng-lat->local-coords)
+      (tc/map-columns :end-local-coords [:end_lng :end_lat] lng-lat->local-coords)
       (tc/map-columns :start-local-x [:start-local-coords] first)
@@
 
-TODO
+::: {.sourceClojure}
+```clojure
+(-> processed-trips
+    (tc/random 1000 {:seed 1})
+    (tc/add-column :local-L2 #(fun/sqrt
+                               (fun/+ (fun/sq (fun/- (:start-local-x %)
+                                                     (:end-local-x %)))
+                                      (fun/sq (fun/- (:start-local-y %)
+                                                     (:end-local-y %))))))
+    (tc/add-column :global-L2 #(fun/sqrt
+                                (fun/+ (fun/sq (fun/- (:start_lat %)
+                                                      (:end_lat %)))
+                                       (fun/sq (fun/- (:start_lng %)
+                                                      (:end_lng %))))))
+    (hanami/plot ht/point-chart
+                 {:X :local-L2
+                  :Y :global-L2}))
+```
+:::
+
+```{=html}
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"global-L2","type":"quantitative"},"x":{"field":"local-L2","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>
+```
+
+The `local-L2` quantity, compted from the local Chicago coordinates,
+is a decent approximation of actual distance.
+We see that the `global-L2` quantity, computed accordingly
+from latitude and longitude, is not directly related to
+this quantity and might be misleading for metric tasks
+such as clustering.
 
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/1.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>92</td><td>12495</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>39</td><td>12190</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>12107</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>11723</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>45</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>85</td><td>13738</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>24</td><td>12870</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>12561</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>33</td><td>12264</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>34</td><td>11275</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>53</td><td>10986</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>10583</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>78</td><td>10471</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>66</td><td>10244</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>3</td><td>9954</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>8496</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/23.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/24.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>30</td><td>8352</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/25.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/26.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>8328</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/27.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/28.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>83</td><td>8083</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/29.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/30.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>55</td><td>7984</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/31.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/32.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>95</td><td>7982</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/33.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/34.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>35</td><td>7639</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/35.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/36.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>25</td><td>7476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/37.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/38.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>23</td><td>6979</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/39.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/40.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>2</td><td>6773</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/41.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/42.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-26 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

--- 2024-03-25 docs/projects/geography/chicago-bikes/index.qmd
@@
 This page will be updated soon.
-
-## Data sources:
-- [Cyclistic bike share - Kaggle](https://www.kaggle.com/datasets/evangower/cyclistic-bike-share)
-- [Cyclistic bike share - 2023 update - Kaggle](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023)
-- [Chicago neighborhoods geojson by @blackmad](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson)
 
@@
 
+In this notebook, we will explore the data of a bike sharing company in Chicago.
+
+The data provides information of start & end location & time for each bike trip.
+It has been used in academic papers and blog posts discussing various aspects of
+people's movement patterns in their everyday lives.
+
+Our goal here is to recognize and visualize a few movement patterns.
+
+## Background
+
+### Various openly shared datasets:
+- [Divvy Trips](https://data.cityofchicago.org/Transportation/Divvy-Trips/fg6s-gzvg/about_data) - Chicago data portal
+- [Chicago Divvy Bicycle Sharing Data](https://www.kaggle.com/datasets/yingwurenjian/chicago-divvy-bicycle-sharing-data) - Kaggle
+- [Cyclistic bike share](https://www.kaggle.com/datasets/evangower/cyclistic-bike-share) - Kaggle
+- [Cyclistic bike share - 2023 update](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023) - Kaggle
+
+### Research papers and blog posts
+- [Understanding Spatiotemporal Patterns of Biking Behavior by Analyzing Massive Bike Sharing Data in Chicago](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0137922) - Zhou 2015
+- [Bicycle-Sharing System Analysis and Trip](https://www.cs.uic.edu/~jzhang2/files/2016_mdm_paper.pdf) - Zhang el al. 2016
+- [Spatial Cluster-Based Model for Static Rebalancing Bike Sharing Problem](https://www.mdpi.com/2071-1050/11/11/3205) - Lahoorpoor et al. 2019
+- [Examining spatiotemporal changing patterns of bike-sharing usage during COVID-19 pandemic](https://www.sciencedirect.com/science/article/pii/S0966692321000508) - Hu et al. 2021
+- [Analysis: Chicago’s Divvy Bike Share](https://andrewluyt.github.io/divvy-bikeshare/analysis-report.html) - Luyt 2021
+
+## Data sources for this notebook
+
+1.
+[Chicago neighborhoods geojson](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson) - part of [a great collection](https://github.com/blackmad/neighborhoods/) by [@blackmad](https://github.com/blackmad).
+We keep this file under "notebooks/data/". By default, [Clay](https://scicloj.github.io/clay) pushed data files under "notebooks" to the target render directory.
+This will allow us to consume the file from the browser for data visualizations.
+
+2. [Cyclistic bike share - 2023 update](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023) - shared on Kaggle by Jayprakash Kumar.
+This dataset contains separate data files for different months. We will use only one of them here (Apr. 2023) and keep it under "data/".
+
 ## Reading the data
+
+We read the raw dataset as a [Tablecloth](https://scicloj.github.io/tablecloth/) dataset
+with some proper date-time parsing and column names as keywords.
 
@@
 
-For metric computations (e.g., k-means clustering),
+For computations telated to distances (e.g., k-means clustering),
 we need to convert them to a coordinate system
-which is locally correct in terms of distances in a region around Chicago:
-NAD83 / Illinois East
-[EPSG:26971](https://epsg.io/26971-1742)
+which approximates plane geometry in a region around Chicago:
+[EPSG:26971](https://epsg.io/26971)
 
 ::: {.clay-dataset}
-United States (USA) - Oregon and Washington. [1 3]:
+NAD83 / Illinois East. [1 3]:
 
@@
 :::
+
+Let us define our coordinate transformation
+using the [Geo](https://github.com/Factual/geo) library.
 
@@
 ```clojure
-(defn lat-lng->local-coords [lat lng]
-  (-> (geo.jts/coordinate lat lng)
+(defn lng-lat->local-coords [lng lat]
+  (-> (geo.jts/coordinate lng lat)
       geo.jts/point
@@
 
-Example:
+For example, let us convert some latitude-longiute pairs
+to our local plane coordinates.
 
@@
 
-::: {.sourceClojure}
-```clojure
-(def coord-colnames
-  [:start_lat :start_lng :end_lat :end_lng])
-```
-:::
+Let us prepare our dataset for analysis.
 
@@
   (-> raw-trips
+      ;; Compute starting hours:
       (tc/add-column :hour (fn [trips]
@@
                                   (datetime/long-temporal-field :hours))))
+      ;; Make sure the latitude and longitude are nonmissing:
       (tc/select-rows (fn [row]
-                        (->> coord-colnames
+                        (->> [:start_lat :start_lng :end_lat :end_lng]
                              (map row)
                              (every? some?))))
-      (tc/map-columns :start-local-coords [:start_lat :start_lng] lat-lng->local-coords)
-      (tc/map-columns :end-local-coords [:end_lat :end_lng] lat-lng->local-coords)
+      ;; Add local plane coordinates:
+      (tc/map-columns :start-local-coords [:start_lng :start_lat] lng-lat->local-coords)
+      (tc/map-columns :end-local-coords [:end_lng :end_lat] lng-lat->local-coords)
       (tc/map-columns :start-local-x [:start-local-coords] first)
@@
 (-> processed-trips
-    (tc/add-column :local-distance #(fun/sqrt
+    (tc/random 1000 {:seed 1})
+    (tc/add-column :local-L2 #(fun/sqrt
                                (fun/+ (fun/sq (fun/- (:start-local-x %)
@@
                                       (fun/sq (fun/- (:start-local-y %)
-                                                           (:end-local-y %)))))))
+                                                     (:end-local-y %))))))
+    (tc/add-column :global-L2 #(fun/sqrt
+                                (fun/+ (fun/sq (fun/- (:start_lat %)
+                                                      (:end_lat %)))
+                                       (fun/sq (fun/- (:start_lng %)
+                                                      (:end_lng %))))))
+    (hanami/plot ht/point-chart
+                 {:X :local-L2
+                  :Y :global-L2}))
 ```
@@
 
-::: {.clay-dataset}
-data/kaggle-cyclistic/202304_divvy_tripdata.csv.gz [426155 21]:
+```{=html}
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"global-L2","type":"quantitative"},"x":{"field":"local-L2","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>
+```
 
-|         :ride_id | :rideable_type |         :started_at |           :ended_at |        :start_station_name | :start_station_id |         :end_station_name | :end_station_id |  :start_lat |   :start_lng |    :end_lat |     :end_lng | :member_casual | :hour |                        :start-local-coords |                          :end-local-coords |  :start-local-x |  :start-local-y |    :end-local-x |    :end-local-y | :local-distance |
-|------------------|----------------|---------------------|---------------------|----------------------------|-------------------|---------------------------|-----------------|------------:|-------------:|------------:|-------------:|----------------|------:|--------------------------------------------|--------------------------------------------|----------------:|----------------:|----------------:|----------------:|----------------:|
-| 8FE8F7D9C10E88C7 |  electric_bike | 2023-04-02T08:37:28 | 2023-04-02T08:41:37 |                            |                   |                           |                 | 41.80000000 | -87.60000000 | 41.79000000 | -87.60000000 |         member |     8 |  [506107.9325773436 -1.4235352994997954E7] | [506137.42192310654 -1.4235316240199374E7] | 506107.93257734 | -1.42353530E+07 | 506137.42192311 | -1.42353162E+07 |     47.12257137 |
-| 34E4ED3ADF1D821B |  electric_bike | 2023-04-19T11:29:02 | 2023-04-19T11:52:12 |                            |                   |                           |                 | 41.87000000 | -87.65000000 | 41.93000000 | -87.68000000 |         member |    11 |  [501519.8754807859 -1.4231908162239876E7] |  [498721.7934556093 -1.4229901392452776E7] | 501519.87548079 | -1.42319082E+07 | 498721.79345561 | -1.42299014E+07 |   3443.31061597 |
-| 5296BF07A2F77CB5 |  electric_bike | 2023-04-19T08:41:22 | 2023-04-19T08:43:22 |                            |                   |                           |                 | 41.93000000 | -87.66000000 | 41.93000000 | -87.66000000 |         member |     8 | [500470.98093146156 -1.4231382653142933E7] | [500470.98093146156 -1.4231382653142933E7] | 500470.98093146 | -1.42313827E+07 | 500470.98093146 | -1.42313827E+07 |      0.00000000 |
-| 40759916B76D5D52 |  electric_bike | 2023-04-19T13:31:30 | 2023-04-19T13:35:09 |                            |                   |                           |                 | 41.92000000 | -87.65000000 | 41.91000000 | -87.65000000 |         member |    13 |  [501374.92347210384 -1.423208764589309E7] |  [501403.9254779691 -1.4232051758343631E7] | 501374.92347210 | -1.42320876E+07 | 501403.92547797 | -1.42320518E+07 |     46.14144070 |
-| 77A96F460101AC63 |  electric_bike | 2023-04-19T12:05:36 | 2023-04-19T12:10:26 |                            |                   |                           |                 | 41.91000000 | -87.65000000 | 41.91000000 | -87.63000000 |         member |    12 |  [501403.9254779691 -1.4232051758343631E7] |  [503154.9287078667 -1.4233533354956321E7] | 501403.92547797 | -1.42320518E+07 | 503154.92870787 | -1.42335334E+07 |   2293.71768835 |
-| 8D6A2328E19DC168 |  electric_bike | 2023-04-19T12:17:34 | 2023-04-19T12:21:38 |                            |                   |                           |                 | 41.91000000 | -87.63000000 | 41.92000000 | -87.65000000 |         member |    12 |  [503154.9287078667 -1.4233533354956321E7] |  [501374.92347210384 -1.423208764589309E7] | 503154.92870787 | -1.42335334E+07 | 501374.92347210 | -1.42320876E+07 |   2293.14049610 |
-| C97BBA66E07889F9 |  electric_bike | 2023-04-19T09:35:48 |    2023-04-19T09:45 |                            |                   |                           |                 | 41.93000000 | -87.66000000 | 41.91000000 | -87.65000000 |         member |     9 | [500470.98093146156 -1.4231382653142933E7] |  [501403.9254779691 -1.4232051758343631E7] | 500470.98093146 | -1.42313827E+07 | 501403.92547797 | -1.42320518E+07 |   1148.07983018 |
-| 6687AD4C575FF734 |  electric_bike | 2023-04-11T16:13:43 | 2023-04-11T16:18:41 |                            |                   |                           |                 | 42.00000000 | -87.66000000 | 41.99000000 | -87.66000000 |         member |    16 |  [500268.5489835212 -1.4231632572144713E7] | [500297.48516240803 -1.4231596883177325E7] | 500268.54898352 | -1.42316326E+07 | 500297.48516241 | -1.42315969E+07 |     45.94567272 |
-| A8FA4F73B22BC11F |  electric_bike | 2023-04-11T16:29:24 | 2023-04-11T16:40:23 |                            |                   |                           |                 | 41.99000000 | -87.66000000 | 42.00000000 | -87.66000000 |         member |    16 | [500297.48516240803 -1.4231596883177325E7] |  [500268.5489835212 -1.4231632572144713E7] | 500297.48516241 | -1.42315969E+07 | 500268.54898352 | -1.42316326E+07 |     45.94567272 |
-| 81E158FE63D99994 |  electric_bike | 2023-04-19T17:35:40 | 2023-04-19T17:36:11 |                            |                   |                           |                 | 41.88000000 | -87.65000000 | 41.88000000 | -87.65000000 |         member |    17 |   [501490.896685202 -1.4231944068150206E7] |   [501490.896685202 -1.4231944068150206E7] | 501490.89668520 | -1.42319441E+07 | 501490.89668520 | -1.42319441E+07 |      0.00000000 |
-|              ...
-|            ...
-|                 ...
-|                 ...
-|                        ...
-|               ...
-|                       ...
-|             ...
-|         ...
-|          ...
-|         ...
-|          ...
-|            ...
-|   ...
-|                                        ...
-|                                        ...
-|             ...
-|             ...
-|             ...
-|             ...
-|             ...
-|
-| BAE25DBA0CD0DF40 |  electric_bike | 2023-04-14T07:12:34 | 2023-04-14T07:42:07 | Richmond St & Diversey Ave |             15645 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.93186915 | -87.70120764 | 41.87593267 | -87.63058454 |         member |     7 |  [496862.65843494714 -1.422833795268237E7] | [503203.23756304523 -1.4233366677138694E7] | 496862.65843495 | -1.42283380E+07 | 503203.23756305 | -1.42333667E+07 |   8092.65181120 |
-| 5A98F86A573AAB2C |  electric_bike | 2023-04-24T07:27:02 | 2023-04-24T07:58:22 | Richmond St & Diversey Ave |             15645 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.93198085 | -87.70128024 | 41.87593267 | -87.63058454 |         member |     7 |  [496855.9967031725 -1.4228332970829802E7] | [503203.23756304523 -1.4233366677138694E7] | 496855.99670317 | -1.42283330E+07 | 503203.23756305 | -1.42333667E+07 |   8100.96696311 |
-| 92B02F2FBDC1FB9F |   classic_bike | 2023-04-12T08:16:48 | 2023-04-12T08:40:08 |     Michigan Ave & Lake St |      TA1305000011 |        May St & Taylor St |           13160 | 41.88602200 | -87.62439800 | 41.86948210 | -87.65548640 |         member |     8 |  [503715.7528127164 -1.4233861403126204E7] | [501040.95186117536 -1.4231500346004825E7] | 503715.75281272 | -1.42338614E+07 | 501040.95186118 | -1.42315003E+07 |   3567.79355636 |
-| 119A6C53607EAA4A |  electric_bike | 2023-04-28T07:24:54 | 2023-04-28T07:53:44 | Richmond St & Diversey Ave |             15645 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.93190396 | -87.70125461 | 41.87593267 | -87.63058454 |         member |     7 |  [496858.4550664372 -1.4228334598338569E7] | [503203.23756304523 -1.4233366677138694E7] | 496858.45506644 | -1.42283346E+07 | 503203.23756305 | -1.42333667E+07 |   8098.02951217 |
-| 9BCF1E8BA027EAFA |  electric_bike | 2023-04-21T07:15:06 | 2023-04-21T07:41:45 | Richmond St & Diversey Ave |             15645 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.93193305 | -87.70126295 | 41.87593267 | -87.63058454 |         member |     7 |  [496857.6431128598 -1.4228334082633112E7] | [503203.23756304523 -1.4233366677138694E7] | 496857.64311286 | -1.42283341E+07 | 503203.23756305 | -1.42333667E+07 |   8098.98613308 |
-| A17D800CE963661A |   classic_bike | 2023-04-11T15:46:42 | 2023-04-11T15:50:03 |     Michigan Ave & Lake St |      TA1305000011 |    Clark St & Randolph St |    TA1305000030 | 41.88602200 | -87.62439800 | 41.88457623 | -87.63188991 |         member |    15 |  [503715.7528127164 -1.4233861403126204E7] |  [503063.6502967095 -1.4233301315734675E7] | 503715.75281272 | -1.42338614E+07 | 503063.65029671 | -1.42333013E+07 |    859.61362107 |
-| 8B441A6C436E9900 |   classic_bike | 2023-04-29T21:20:21 | 2023-04-29T21:30:19 |       Halsted St & 18th St |             13099 | Blue Island Ave & 18th St |           13135 | 41.85750568 | -87.64599144 | 41.85755600 | -87.66153500 |         casual |    21 |  [501907.1861189178 -1.4232159853149524E7] | [500545.77541704464 -1.4231010242258897E7] | 501907.18611892 | -1.42321599E+07 | 500545.77541704 | -1.42310102E+07 |   1781.86539868 |
-| 3980D64BE11540F1 |   classic_bike | 2023-04-24T09:16:05 | 2023-04-24T09:22:27 |       Halsted St & 18th St |             13099 | Blue Island Ave & 18th St |           13135 | 41.85750568 | -87.64599144 | 41.85755600 | -87.66153500 |         casual |     9 |  [501907.1861189178 -1.4232159853149524E7] | [500545.77541704464 -1.4231010242258897E7] | 501907.18611892 | -1.42321599E+07 | 500545.77541704 | -1.42310102E+07 |   1781.86539868 |
-| 3EF4B49FF7DAA02C |   classic_bike | 2023-04-18T07:53:51 | 2023-04-18T07:59:16 | Franklin St & Jackson Blvd |      TA1305000025 |    Clark St & Randolph St |    TA1305000030 | 41.87770796 | -87.63532114 | 41.88457623 | -87.63188991 |         casual |     7 |  [502783.1163597462 -1.4233022413426103E7] |  [503063.6502967095 -1.4233301315734675E7] | 502783.11635975 | -1.42330224E+07 | 503063.65029671 | -1.42333013E+07 |    395.58284532 |
-| 210B2ED6583DC231 |   classic_bike | 2023-04-29T07:33:55 | 2023-04-29T07:38:57 |     Michigan Ave & Lake St |      TA1305000011 |    Clark St & Randolph St |    TA1305000030 | 41.88602200 | -87.62439800 | 41.88457623 | -87.63188991 |         casual |     7 |  [503715.7528127164 -1.4233861403126204E7] |  [503063.6502967095 -1.4233301315734675E7] | 503715.75281272 | -1.42338614E+07 | 503063.65029671 | -1.42333013E+07 |    859.61362107 |
-| D29CB39B9E3FC46A |  electric_bike | 2023-04-18T08:00:32 | 2023-04-18T08:02:35 | Franklin St & Jackson Blvd |      TA1305000025 | Clark St & Ida B Wells Dr |    TA1305000009 | 41.87813417 | -87.63525450 | 41.87593267 | -87.63058454 |         casual |     8 | [502787.71168951405 -1.4233028887672516E7] | [503203.23756304523 -1.4233366677138694E7] | 502787.71168951 | -1.42330289E+07 | 503203.23756305 | -1.42333667E+07 |    535.50301123 |
-
-:::
+The `local-L2` quantity, compted from the local Chicago coordinates,
+is a decent approximation of actual distance.
+We see that the `global-L2` quantity, computed accordingly
+from latitude and longitude, is not directly related to
+this quantity and might be misleading for metric tasks
+such as clustering.
 
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>79</td><td>12193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>11476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>11174</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>10835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10360</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>4</td><td>20994</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>45</td><td>13574</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>43</td><td>12368</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>59</td><td>11569</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>37</td><td>11192</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>30</td><td>11143</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>10919</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>10116</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>71</td><td>9689</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>84</td><td>9686</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>22</td><td>9556</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/23.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/24.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>9328</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/25.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/26.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>94</td><td>8781</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/27.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/28.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>68</td><td>8051</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/29.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/30.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>80</td><td>7862</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/31.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/32.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>91</td><td>7809</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/33.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/34.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>47</td><td>7662</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/35.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/36.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>54</td><td>7623</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/37.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/38.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>57</td><td>7417</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/39.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/40.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>77</td><td>7409</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/41.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/42.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-26 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 
+This is a digression for the curious. It is not part of the actual analysis.
+
+Earlier mentioned that our `x`,`y` coordinates approximately represent
+for plane geometry in the relevant region, unlike the `latitude`,`longitude` ones.
+
+Let us check how different they actually are in measuring distances.
+We will sample 1000 bike trips, and for each trip, measure the
+L2 distance between the start and the end.
+
+L2 is the distance in our usual Eucledian plane geometry:
+the square root of the sum of square distances,
+where the sum is over our two coordinates
+(as can be justified by the Pythagorean theorem).
+
+We will compute it `x`,`y` (approximate plane coordinates),
+and then in `latitude`,`longitude` (globe coordinates).
+The former should be approximately correct, the latter - not so much.
+
+Let us compare the two in a scatterplot.
+
 ::: {.sourceClojure}
@@
 
+Here, we used the [Noj](https://scicloj.github.io/noj/) wrapper
+of [Hanami](https://github.com/jsa-aerial/hanami),
+which makes it work nicely with Tablecloth.
+
 The `local-L2` quantity, compted from the local Chicago coordinates,
@@
 this quantity and might be misleading for metric tasks
-such as clustering.
+such as clustering. They are correlated, though,
+and if one of them is small, the other one is small as well.
+
+In this section, we computed distances between pairs of coordinates.
+E.g., between the `x`,`y` of the trip start, to those of the trip end.
+Later, we will represent each trip by a quadruple of coordinates
+(both start and end), and use the 4D geometry of those quadruples
+to gather our data into clusters of similar trips.
 
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>4</td><td>20994</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>45</td><td>13574</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>43</td><td>12368</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>59</td><td>11569</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>37</td><td>11192</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>30</td><td>11143</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>10919</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>10116</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>71</td><td>9689</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>84</td><td>9686</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>22</td><td>9556</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/23.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/24.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>9328</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/25.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/26.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>94</td><td>8781</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/27.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/28.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>68</td><td>8051</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/29.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/30.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>80</td><td>7862</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/31.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/32.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>91</td><td>7809</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/33.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/34.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>47</td><td>7662</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/35.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/36.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>54</td><td>7623</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/37.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/38.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>57</td><td>7417</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/39.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/40.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>77</td><td>7409</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/41.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/42.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>16</td><td>13929</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>72</td><td>12751</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>63</td><td>12215</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>58</td><td>11783</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>62</td><td>11383</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>2</td><td>11304</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>17</td><td>10891</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10852</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>99</td><td>10500</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>11</td><td>9705</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>9202</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/23.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/24.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>9</td><td>9057</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/25.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/26.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>77</td><td>8863</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/27.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/28.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>89</td><td>8540</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/29.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/30.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>28</td><td>8011</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/31.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/32.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>35</td><td>7595</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/33.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/34.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>47</td><td>7566</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/35.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/36.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>43</td><td>7193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/37.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/38.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>8</td><td>7045</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/39.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/40.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>6839</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/41.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/42.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-26 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 of [Hanami](https://github.com/jsa-aerial/hanami),
-which makes it work nicely with Tablecloth.
+which makes it compose conveniently with Tablecloth,
+eventually generating [Vega-Lite](https://vega.github.io/) plots.
 
@@
 
-::: {.sourceClojure}
-```clojure
-(delay
-  (-> processed-trips
-      (tc/group-by [:hour])
-      (tc/aggregate {:n tc/row-count})
-      (tc/order-by [:hour])))
-```
-:::
-
-::: {.clay-dataset}
-_unnamed [24 2]:
-
-| :hour |    :n |
-|------:|------:|
-|     0 |  5093 |
-|     1 |  3227 |
-|     2 |  1871 |
-|     3 |  1162 |
-|     4 |   948 |
-|     5 |  2801 |
-|     6 |  8859 |
-|     7 | 17058 |
-|     8 | 22162 |
-|     9 | 17299 |
-|   ... |   ... |
-|    13 | 24807 |
-|    14 | 25866 |
-|    15 | 30699 |
-|    16 | 40338 |
-|    17 | 46854 |
-|    18 | 38245 |
-|    19 | 27078 |
-|    20 | 17231 |
-|    21 | 14367 |
-|    22 | 10810 |
-|    23 |  7317 |
-
-:::
+### Time
+Let us see how trip start hours are distributed along the day.
 
@@
 
+### Space
+
+We wish to plot our trips as line segments
+(Vega-Lite [Rule](https://vega.github.io/vega-lite/docs/rule.html)s)
+over a map.
+
+Hanami's templates create Vega-Lite plots with `x` and `y` coordinates,
+but we need geographical plots, with `latitude` and `longitude`.
+
+The following function will allow us to convert typical Hanami plots
+to geographical ones.
+
 ::: {.sourceClojure}
@@
                                            k k)))
-      (assoc :projection {:type :mercator})))
+      (assoc :projection {:type :mercator}
+             ;; rendering as PNG this time
+             ;; to make this page more lightweight
+             :usermeta {:embedOptions {:renderer :png}})))
 ```
 :::
+
+Let us try it out with a sample of points.
 
@@
   (-> processed-trips
-      (tc/random 1000 {:seed 1})
+      (tc/random 10000 {:seed 1})
       (hanami/plot ht/rule-chart
@@
                     :X2 :end_lat
-                    :Y2 :end_lng})
+                    :Y2 :end_lng
+                    :OPACITY 0.1})
       as-geo))
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
 ```
+
+Let us add the neighbourhood geometries as an additional layer.
 
@@
   (-> processed-trips
-      (tc/random 1000 {:seed 1})
-      (hanami/plot ht/rule-chart
-                   {:X :start-local-x
-                    :Y :start-local-y
-                    :X2 :end-local-x
-                    :Y2 :end-local-y
-                    :XSCALE {:zero false}
-                    :YSCALE {:zero false}})))
-```
-:::
-
-```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"scale":{"zero":false},"field":"start-local-y","type":"quantitative"},"x":{"scale":{"zero":false},"field":"start-local-x","type":"quantitative"},"y2":{"scale":{"zero":false},"field":"end-local-y","type":"quantitative"},"x2":{"scale":{"zero":false},"field":"end-local-x","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
-```
-
-::: {.sourceClojure}
-```clojure
-(delay
-  (-> processed-trips
-      (tc/random 1000 {:seed 1})
+      (tc/random 10000 {:seed 1})
       (hanami/plot ht/layer-chart
@@
                                     :clip true
-                                    :opacity 0.3}}
+                                    :opacity 0.5}}
                             (as-geo
-                             (hanami/plot nil
+                             (hanami/plot nil ; use the global dataset for this layer
                                           ht/rule-chart
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.5}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
 ## Clustering
+
+To recognize repeating patterns of similar trips,
+we use [k-means clustering](https://en.wikipedia.org/wiki/K-means_clustering)
+over trips, representing them as quadruple of points
+using the plane coordinates of their start and end.
 
@@
 
-Let us plot a few clusters:
-
-::: {.sourceClojure}
-```clojure
-(defn as-png [vega-lite-spec]
-  ;; to improve performance, we avoid rendering as SVG in this case:
-  (-> vega-lite-spec
-      (assoc :usermeta {:embedOptions {:renderer :png}})))
-```
-:::
+Let us plot the biggest of the resulting clusters.
+We will plot each cluster separately in time and in space as before.
+To the line segments over the map we add the start and end points,
+in purple and green, respectively.
 
@@
       (tc/group-by [:cluster])
+      ;; sort the groups in ascending order by their size,
+      ;; and take the first 20 (which are the largest ones)
+      ;; (we use `without-grouping->` to order and take
+      ;; across groups rather tan within groups):
       (tc/without-grouping->
@@
                                                                       :MCOLOR "green"
-                                                                      :OPACITY 0.01}))]})
-                                 as-png)])
+                                                                      :OPACITY 0.01}))]}))])
                      :hours (fn [trips]
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>16</td><td>13929</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>72</td><td>12751</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>63</td><td>12215</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>58</td><td>11783</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>62</td><td>11383</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>2</td><td>11304</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>17</td><td>10891</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10852</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>99</td><td>10500</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>11</td><td>9705</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>9202</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/23.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/24.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>9</td><td>9057</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/25.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/26.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>77</td><td>8863</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/27.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/28.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>89</td><td>8540</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/29.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/30.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>28</td><td>8011</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/31.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/32.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>35</td><td>7595</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/33.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/34.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>47</td><td>7566</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/35.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/36.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>43</td><td>7193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/37.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/38.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>8</td><td>7045</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/39.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/40.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>6839</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/41.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/42.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>86</td><td>12797</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>92</td><td>12091</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>9</td><td>11575</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>14</td><td>11019</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>88</td><td>10506</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>90</td><td>10220</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>19</td><td>10055</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>12</td><td>10029</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>75</td><td>9999</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>83</td><td>9213</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>55</td><td>8893</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/23.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/24.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>84</td><td>8622</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/25.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/26.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>97</td><td>8294</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/27.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/28.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>7629</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/29.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/30.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>26</td><td>7552</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/31.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/32.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>33</td><td>7466</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/33.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/34.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>71</td><td>7407</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/35.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/36.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>7366</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/37.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/38.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>10</td><td>7112</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/39.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/40.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>82</td><td>7109</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/41.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/42.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-27 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 </style>
-<script src="index_files/md-default43.js" type="text/javascript"></script><script src="index_files/md-default44.js" type="text/javascript"></script><script src="index_files/vega45.js" type="text/javascript"></script><script src="index_files/vega46.js" type="text/javascript"></script><script src="index_files/vega47.js" type="text/javascript"></script>
+<script src="index_files/md-default23.js" type="text/javascript"></script><script src="index_files/md-default24.js" type="text/javascript"></script><script src="index_files/vega25.js" type="text/javascript"></script><script src="index_files/vega26.js" type="text/javascript"></script><script src="index_files/vega27.js" type="text/javascript"></script>
 
@@
                                            k k)))
-      (assoc :projection {:type :mercator}
-             ;; rendering as PNG this time
-             ;; to make this page more lightweight
-             :usermeta {:embedOptions {:renderer :png}})))
+      (assoc :projection {:type :mercator})))
+```
+:::
+
+We will find it useful to render some Vega-Lite plots
+as PNG, rather than SVG. This will meke the whole page more lightweight.
+
+::: {.sourceClojure}
+```clojure
+(defn as-png [vega-lite-spec]
+  (-> vega-lite-spec
+      (assoc :usermeta {:embedOptions {:renderer :png}})))
 ```
@@
                     :OPACITY 0.1})
-      as-geo))
+      as-geo
+      as-png))
 ```
@@
                                            :Y2 :end_lng
-                                           :OPACITY 0.1}))]})))
+                                           :OPACITY 0.1}))]})
+      as-png))
 ```
@@
 ```{=html}
-<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.5}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
+<div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.5}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.1},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div>
 ```
@@
       ;; sort the groups in ascending order by their size,
-      ;; and take the first 20 (which are the largest ones)
+      ;; and take the first few (which are the largest ones)
       ;; (we use `without-grouping->` to order and take
@@
                     :desc)
-       (tc/head 20))
+       (tc/head 10))
       (tc/aggregate {:n tc/row-count
@@
                                                                       :MCOLOR "green"
-                                                                      :OPACITY 0.01}))]}))])
+                                                                      :OPACITY 0.01}))]})
+                                 as-png)])
                      :hours (fn [trips]
-                              [(hour-counts-plot trips)])})
+                              [(as-png
+                                (hour-counts-plot trips))])})
       kind/table))
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>86</td><td>12797</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>92</td><td>12091</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>9</td><td>11575</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>14</td><td>11019</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>88</td><td>10506</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>90</td><td>10220</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>19</td><td>10055</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>12</td><td>10029</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>75</td><td>9999</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>83</td><td>9213</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>55</td><td>8893</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/23.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/24.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>84</td><td>8622</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/25.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/26.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>97</td><td>8294</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/27.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/28.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>7629</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/29.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/30.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>26</td><td>7552</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/31.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/32.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>33</td><td>7466</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/33.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/34.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>71</td><td>7407</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/35.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/36.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>7366</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/37.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/38.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>10</td><td>7112</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/39.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/40.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>82</td><td>7109</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/41.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/42.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>66</td><td>14644</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>99</td><td>13514</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>1</td><td>11968</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>34</td><td>11804</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>98</td><td>11783</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>16</td><td>11711</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>69</td><td>11248</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>58</td><td>10783</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>4</td><td>10368</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>41</td><td>9509</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-27 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 
-# Chicago bikes - DRAFT
+# Chicago bikes
 
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>66</td><td>14644</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>99</td><td>13514</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>1</td><td>11968</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>34</td><td>11804</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>98</td><td>11783</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>16</td><td>11711</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>69</td><td>11248</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>58</td><td>10783</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>4</td><td>10368</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>41</td><td>9509</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>10</td><td>14148</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>97</td><td>12775</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>8</td><td>12617</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>66</td><td>12023</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>72</td><td>11912</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>11400</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>83</td><td>11199</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>10391</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>76</td><td>10249</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>85</td><td>9870</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 [Chicago neighborhoods geojson](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson) - part of [a great collection](https://github.com/blackmad/neighborhoods/) by [@blackmad](https://github.com/blackmad).
-We keep this file under "notebooks/data/". By default, [Clay](https://scicloj.github.io/clay) pushed data files under "notebooks" to the target render directory.
+We keep this file under "notebooks/data/". By default, [Clay](https://scicloj.github.io/clay) pushes data files under "notebooks" to the target render directory.
 This will allow us to consume the file from the browser for data visualizations.
@@
 We wish to plot our trips as line segments
-(Vega-Lite [Rule](https://vega.github.io/vega-lite/docs/rule.html)s)
+(Vega-Lite [Rules](https://vega.github.io/vega-lite/docs/rule.html))
 over a map.
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>10</td><td>14148</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>97</td><td>12775</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>8</td><td>12617</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>66</td><td>12023</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>72</td><td>11912</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>11400</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>83</td><td>11199</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>10391</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>76</td><td>10249</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>85</td><td>9870</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>87</td><td>13049</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>12816</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>10990</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>10448</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>66</td><td>10397</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>55</td><td>10359</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>20</td><td>9968</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>91</td><td>9902</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>50</td><td>9517</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>8</td><td>9497</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
 
-# Chicago bikes
+# Analysing Chicago bike trips
 
-This page will be updated soon.
+This notebook is the fruit of our explorations at the new
+[real-world-data group](https://scicloj.github.io/docs/community/groups/real-world-data/).
+It uses a few of libraries of the emerging Clojure stack for data and science:
+Tablecloth, dtype-next, Fastmath, Hanami, Geo, and Kindly.
+
+Soon we will publish a video walkthrough.
+
+Daniel Slutsky, March 2024
 
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>87</td><td>13049</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>12816</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>10990</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>10448</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>66</td><td>10397</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>55</td><td>10359</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>20</td><td>9968</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>91</td><td>9902</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>50</td><td>9517</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>8</td><td>9497</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>76</td><td>12868</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>59</td><td>10451</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>33</td><td>10387</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>50</td><td>10317</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>22</td><td>10283</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>9852</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>57</td><td>9782</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>71</td><td>9635</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>31</td><td>9481</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>9458</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendere

@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>76</td><td>12868</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>59</td><td>10451</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>33</td><td>10387</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>50</td><td>10317</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>22</td><td>10283</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>9852</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>57</td><td>9782</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>71</td><td>9635</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>31</td><td>9481</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>9458</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>57</td><td>14777</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>26</td><td>14210</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>40</td><td>12778</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>59</td><td>12457</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>54</td><td>11660</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>35</td><td>11288</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>3</td><td>10863</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>8</td><td>10400</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>43</td><td>10114</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>38</td><td>9950</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```
@@
 :::
+
+Some patterns are noticible. In future explorations, we should hope to reach
+some interpretations and hopefully discuss them with local friends who
+know something about this area.
+
+This can be considered a first step in reproducing some of the methods
+of the existing insightful articles cited above.
+
+## Conclusion, for now
+
+For now, we will stop here.
+
+This has mostly been a demonstration of a few libraries and practices
+which are central to the emerging Clojure platform for data and science.
+
+We have also had a glance into a rich dataset which can provide fruitful
+examples for our future explorations, demonstrating nontrivial
+phenomena in space and in time.
 

### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendere

@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>57</td><td>14777</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>26</td><td>14210</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>40</td><td>12778</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>59</td><td>12457</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>54</td><td>11660</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>35</td><td>11288</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>3</td><td>10863</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>8</td><td>10400</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>43</td><td>10114</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>38</td><td>9950</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>43</td><td>12096</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>25</td><td>11178</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>17</td><td>10295</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>16</td><td>10143</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>96</td><td>10010</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>70</td><td>9896</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>79</td><td>9876</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>60</td><td>9834</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>39</td><td>9760</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>46</td><td>9335</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```
@@
 Some patterns are noticible. In future explorations, we should hope to reach
-some interpretations and hopefully discuss them with local friends who
+some interpretations regarding repeating movement in certain hours,
+such as the end of the work day, in relation to certain destinations,
+like major train stations.
+We sould certainly hope to discuss them with local friends who
 know something about this area.

### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@
   (-> vega-lite-spec
-      (update :encoding update-keys (fn [k]
-                                      (get {:x :latitude
+      (update :encoding update-keys
+              #(case %
+                 :x :latitude
                  :y :longitude
                  :x2 :latitude2
-                                            :y2 :longitude2}
-                                           k k)))
+                 :y2 :longitude2
+                 %))
       (assoc :projection {:type :mercator})))
@@
 ```{=html}
-<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>43</td><td>12096</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>25</td><td>11178</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>17</td><td>10295</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>16</td><td>10143</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>96</td><td>10010</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>70</td><td>9896</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>79</td><td>9876</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>60</td><td>9834</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>39</td><td>9760</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>46</td><td>9335</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
+<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>79</td><td>12649</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>41</td><td>12396</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>10</td><td>12358</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>1</td><td>10518</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>94</td><td>10471</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>91</td><td>9935</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>78</td><td>9698</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>14</td><td>9523</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>17</td><td>9270</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>9160</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"png"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/22.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
 ```

### 2024-04-02 docs/projects/datavis/ggplot/comparing.qmd
ggplotly - rerendered

@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x623a23bd4218&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x643ee41728c8&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x623a23bd4218&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x643ee41728c8&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 

### 2024-04-02 docs/projects/datavis/ggplot/draft.qmd
ggplotly - rerendered

@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x623a200a6140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x643ee0636140&gt;\n&lt;environment: namespace:base&gt;\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x623a200a6140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n&lt;bytecode: 0x643ee0636140&gt;\n&lt;environment: namespace:base&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x623a24006960&gt;\n&lt;environment: 0x623a2f3e8728&gt;\n",
+     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x643ee45a5010&gt;\n&lt;environment: 0x643ef149d1b0&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x623a2400c260&gt;\n&lt;environment: 0x623a2f3e85a0&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x643ee45aa910&gt;\n&lt;environment: 0x643ef149d338&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x623a2400f888&gt;\n&lt;environment: 0x623a2f3e8450&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x643ee45adf38&gt;\n&lt;environment: 0x643ef149d4c0&gt;\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x623a297efa38&gt;\n&lt;environment: 0x623a275434e8&gt;\n",
+     "function (x) \nlog(x, base)\n&lt;bytecode: 0x643ee9d7fc60&gt;\n&lt;environment: 0x643ee9f9be70&gt;\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x623a297efb88&gt;\n&lt;environment: 0x623a275434e8&gt;\n",
+     "function (x) \nbase^x\n&lt;bytecode: 0x643ee9d7fdb0&gt;\n&lt;environment: 0x643ee9f9be70&gt;\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x623a29737d80&gt;\n&lt;environment: 0x623a27547910&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x643ee9cc7d78&gt;\n&lt;environment: 0x643ee9f90eb8&gt;\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x623a2400c260&gt;\n&lt;environment: 0x623a275474e8&gt;\n",
+     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x643ee45aa910&gt;\n&lt;environment: 0x643ee9f91350&gt;\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x623a2400f888&gt;\n&lt;environment: 0x623a27547360&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x643ee45adf38&gt;\n&lt;environment: 0x643ee9f914d8&gt;\n",
      :domain [1.0E-100 ##Inf]},

### 2024-04-02 docs/projects/datavis/ggplot/ggplotly.qmd
ggplotly - rerendered

@@
 ```{=html}
-<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-12" style="width:100%;height:400px;"><script data-for="htmlwidget-12" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-12" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>
+<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-170" style="width:100%;height:400px;"><script data-for="htmlwidget-170" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-170" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>
 ```

### 2024-04-02 docs/projects/datavis/ggplot/ggplotly_cont.qmd
ggplotly - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: ggplotly_cont.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style><style>.clay-limit-image-width .clay-image {max-width: 100%}
</style>
<script src="ggplotly_cont_files/md-default0.js" type="text/javascript"></script><script src="ggplotly_cont_files/md-default1.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/htmlwidgets-1.6.2/htmlwidgets.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/plotly-binding-4.10.4.9000/plotly.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/typedarray-0.1/typedarray.min.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/jquery-3.5.1/jquery.min.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/crosstalk-1.2.1/js/crosstalk.min.js" type="text/javascript"></script><script src="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/plotly-main-2.11.1/plotly-latest.min.js" type="text/javascript"></script><link href="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/crosstalk-1.2.1/css/crosstalk.min.css" rel="stylesheet" type="text/css" /><link href="htmlwidgets-ggplotly/gh-repos/scicloj/ggplotly-deps/plotly-htmlwidgets-css-2.11.1/plotly-htmlwidgets.css" rel="stylesheet" type="text/css" />

::: {.sourceClojure}
```clojure
(ns ggplotly-cont
  (:require [tablecloth.api :as tc]
            [scicloj.metamorph.ml.toydata.ggplot :as toydata.ggplot]
            [tech.v3.datatype.functional :as fun]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.string :as str]
            [clojure.math :as math]))
```
:::

# Further exploring ggplotly's client side - DRAFT

The following template was generated from the JSON file
in the HTML generated by
`ggplotly(ggplot(mpg, aes(x=hwy, y=displ, color=factor(cyl))) + geom_point() + geom_smooth(method="lm"))`
and then gradually generalizing it as a set of Clojure functions.
This is a work-in-progress draft. Some parts are still hard-coded.

::: {.sourceClojure}
```clojure
(defn layer [{:keys [type x y color text name legendgroup showlegend]}]
  (merge {:hoveron "points",
          :legendgroup legendgroup,
          :showlegend showlegend
          :frame nil,
          :hoverinfo "text",
          :name name,
          :mode (case type
                  :point "markers"
                  :line "lines")
          :type "scatter",

          :xaxis "x",
          :yaxis "y",
          :x (vec x)
          :y (vec y)
          :text (vec text)}
         (case type
           :point {:marker {:autocolorscale false,
                            :color color,
                            :opacity 1,
                            :size 5.66929133858268,
                            :symbol "circle",
                            :line {:width 1.88976377952756, :color color}}}
           :line {:line {:width 3.77952755905512,
                         :color color,
                         :dash "solid"}})))
```
:::

::: {.sourceClojure}
```clojure
(def colors
  ["rgba(248,118,109,1)"
   "rgba(124,174,0,1)"
   "rgba(0,191,196,1)"
   "rgba(199,124,255,1)"])
```
:::

::: {.sourceClojure}
```clojure
(def config
  {:doubleClick "reset",
   :modeBarButtonsToAdd ["hoverclosest" "hovercompare"],
   :showSendToCloud false},)
```
:::

::: {.sourceClojure}
```clojure
(def highlight
  {:on "plotly_click",
   :persistent false,
   :dynamic false,
   :selectize false,
   :opacityDim 0.2,
   :selected {:opacity 1},
   :debounce 0},)
```
:::

::: {.sourceClojure}
```clojure
(defn texts [ds column-names]
  (-> ds
      (tc/select-columns column-names)
      tc/rows
      (->> (map (fn [row]
                  (str/join "<br />"
                            (map (partial format "%s: %s")
                                 column-names row)))))))
```
:::

::: {.sourceClojure}
```clojure
(defn ->tickvals [l r]
  (let [jump (-> (- r l)
                 (/ 6)
                 math/floor
                 int
                 (max 1))]
    (-> l
        math/ceil
        (range r jump))))
```
:::

::: {.sourceClojure}
```clojure
(defn axis [{:keys [minval maxval anchor title]}]
  (let [tickvals (->tickvals minval maxval)
        ticktext (mapv str tickvals)
        range-len (- maxval minval)
        range-expansion (* 0.1 range-len)
        expanded-range [(- minval range-expansion)
                        (+ maxval range-expansion)]]
    {:linewidth 0,
     :ticklen 3.65296803652968,
     :tickcolor "rgba(51,51,51,1)",
     :tickmode "array",
     :gridcolor "rgba(255,255,255,1)",
     :automargin true,
     :type "linear",
     :tickvals tickvals,
     :zeroline false,
     :title
     {:text title,
      :font {:color "rgba(0,0,0,1)", :family "", :size 14.6118721461187}},
     :tickfont {:color "rgba(77,77,77,1)", :family "", :size 11.689497716895},
     :autorange false,
     :showticklabels true,
     :showline false,
     :showgrid true,
     :ticktext ticktext,
     :ticks "outside",
     :gridwidth 0.66417600664176,
     :anchor "y",
     :domain [0 1],
     :hoverformat ".2f",
     :tickangle 0,
     :tickwidth 0.66417600664176,
     :categoryarray ticktext,
     :categoryorder "array",
     :range expanded-range},))
```
:::

::: {.sourceClojure}
```clojure
(defn layout [{:keys [xaxis yaxis]}]
  {:plot_bgcolor "rgba(235,235,235,1)",
   :paper_bgcolor "rgba(255,255,255,1)",
   :legend {:bgcolor "rgba(255,255,255,1)",
            :bordercolor "transparent",
            :borderwidth 1.88976377952756,
            :font {:color "rgba(0,0,0,1)", :family "", :size 11.689497716895},
            :title {:text "factor(cyl)",
                    :font {:color "rgba(0,0,0,1)", :family "", :size 14.6118721461187}}},
   :font {:color "rgba(0,0,0,1)", :family "", :size 14.6118721461187},
   :showlegend true,
   :barmode "relative",
   :hovermode "closest",
   :margin
   {:t 25.7412480974125,
    :r 7.30593607305936,
    :b 39.6955859969559,
    :l 31.4155251141553},
   :shapes [{:yref "paper",
             :fillcolor nil,
             :xref "paper",
             :y1 1,
             :type "rect",
             :line {:color nil, :width 0, :linetype []},
             :y0 0,
             :x1 1,
             :x0 0}]
   :xaxis xaxis
   :yaxis yaxis})
```
:::

::: {.sourceClojure}
```clojure
(let [data toydata.ggplot/mpg
      point-layers (-> data
                       (tc/add-column "factor(cyl)" #(factor (:cyl %)))
                       (tc/group-by :cyl {:result-type :as-map})
                       (->> (sort-by key)
                            (map-indexed
                             (fn [i [group-name group-data]]
                               (let [base {:x (:hwy group-data),
                                           :y (:displ group-data)
                                           :color (colors i)
                                           :name group-name
                                           :legendgroup group-name}
                                     predictions (map
                                                  (fun/linear-regressor (:hwy group-data)
                                                                        (:displ group-data))
                                                  (:hwy group-data))]
                                 [(-> base
                                      (assoc :type :point
                                             :showlegend true
                                             :y (:displ group-data)
                                             :text (-> group-data
                                                       (texts [:hwy :displ "factor(cyl)"])))
                                      layer)
                                  (-> base
                                      (assoc :type :line
                                             :showlegend false
                                             :y predictions
                                             :text (-> group-data
                                                       ;; (tc/add-column :displ predictions)
                                                       (texts [:hwy :displ "factor(cyl)"])))
                                      layer)])))
                            (apply concat)))
      xmin (-> data :hwy fun/reduce-min)
      xmax (-> data :hwy fun/reduce-max)
      ymin (-> data :displ fun/reduce-min)
      ymax (-> data :displ fun/reduce-max)
      xaxis (axis {:minval xmin
                   :maxval xmax
                   :anchor "x"
                   :title :hwy})
      yaxis (axis {:minval ymin
                   :maxval ymax
                   :anchor "x"
                   :title :displ})]
  (kind/htmlwidgets-ggplotly
   {:x
    {:config config
     :highlight highlight
     :base_url "https://plot.ly",
     :layout (layout {:xaxis xaxis
                      :yaxis yaxis})
     :data point-layers},
    :evals [],
    :jsHooks []}))
```
:::

```{=html}
<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-171" style="width:100%;height:400px;"><script data-for="htmlwidget-171" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-171" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895},"title":{"text":"factor(cyl)","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}}},"xaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":true,"barmode":"relative","yaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":31.4155251141553},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"data":[{"y":[1.8,1.8,2.0,2.0,1.8,1.8,2.0,2.0,2.4,2.4,2.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.0,2.0,2.0,2.0,2.4,2.4,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,2.2,2.2,2.4,2.4,2.2,2.2,2.4,2.4,1.8,1.8,1.8,1.8,1.8,2.7,2.7,2.7,2.0,2.0,2.0,2.0,1.9,2.0,2.0,2.0,2.0,1.9,1.9,2.0,2.0,1.8,1.8,2.0,2.0],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"marker":{"autocolorscale":false,"color":"rgba(248,118,109,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(248,118,109,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.1377007978924745,2.1377007978924745,2.0569213765537713,2.0973110872231233,2.2588699299005293,2.299259640569881,2.178090508561826,2.2184802192311777,2.2184802192311777,2.0973110872231233,2.3396493512392325,1.9761419552150683,2.01653166588442,2.01653166588442,2.1377007978924745,2.01653166588442,1.9357522445457167,1.8549728232070137,1.8549728232070137,2.1377007978924745,2.2588699299005293,2.2184802192311777,2.0973110872231233,2.0569213765537713,2.2588699299005293,2.1377007978924745,2.178090508561826,2.2184802192311777,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.01653166588442,2.299259640569881,2.3396493512392325,2.2184802192311777,2.299259640569881,2.2588699299005293,2.380039061908584,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.299259640569881,2.2184802192311777,2.299259640569881,2.2184802192311777,2.5012081939166384,2.5012081939166384,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.0569213765537713,2.2184802192311777,2.1377007978924745,2.0569213765537713,2.0569213765537713,2.0973110872231233,1.9761419552150683,1.895362533876365,1.8145831125376621,1.895362533876365,2.5012081939166384,2.5012081939166384,2.4204287725779356,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,1.6530242698602557,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,2.178090508561826,2.1377007978924745],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(248,118,109,1)","dash":"solid"},"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"marker":{"autocolorscale":false,"color":"rgba(124,174,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(124,174,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(124,174,0,1)","dash":"solid"},"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.8,2.8,3.1,2.8,2.8,3.1,3.1,2.8,3.1,3.1,3.5,3.6,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,3.9,4.0,4.0,4.0,4.0,4.2,4.2,3.8,3.8,4.0,4.0,2.5,2.5,3.3,2.7,2.7,2.7,3.0,3.7,4.0,4.0,4.0,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,3.1,3.8,3.8,3.8,3.4,3.4,4.0,3.0,3.0,3.5,3.0,3.0,3.3,3.4,3.4,4.0,4.0,2.8,2.8,2.8,2.8,2.8,3.6],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"marker":{"autocolorscale":false,"color":"rgba(0,191,196,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,191,196,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[3.202020262359323,3.202020262359323,3.1369190700341694,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.33222264700963,3.2671214546844767,3.202020262359323,3.0067166853838625,3.202020262359323,3.33222264700963,3.4624250316599374,3.4624250316599374,3.33222264700963,3.33222264700963,3.787930993285705,3.4624250316599374,3.527526223985091,3.397323839334784,3.397323839334784,3.6577286086353977,3.7228298009605516,3.787930993285705,3.787930993285705,3.787930993285705,3.787930993285705,3.6577286086353977,3.787930993285705,3.6577286086353977,3.787930993285705,3.787930993285705,3.202020262359323,3.2671214546844767,3.202020262359323,3.33222264700963,3.202020262359323,3.202020262359323,3.071817877709016,3.33222264700963,3.33222264700963,3.33222264700963,3.4624250316599374,3.6577286086353977,3.5926274163102443,3.787930993285705,3.6577286086353977,3.1369190700341694,3.202020262359323,3.202020262359323,3.2671214546844767,3.2671214546844767,3.787930993285705,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.1369190700341694,3.071817877709016,3.6577286086353977,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.071817877709016,3.202020262359323,3.202020262359323,3.1369190700341694,3.787930993285705,3.6577286086353977,3.7228298009605516,3.5926274163102443,3.33222264700963,3.397323839334784,3.33222264700963,3.202020262359323,3.202020262359323,3.202020262359323],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(0,191,196,1)","dash":"solid"},"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,4.7,4.7,4.7,5.2,5.2,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.6,5.0,4.6,4.6,4.6,5.4,5.4,4.6,4.6,4.6,4.6,5.4,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.6,5.0,5.6,5.3,4.7,4.7,5.7],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"marker":{"autocolorscale":false,"color":"rgba(199,124,255,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(199,124,255,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]},{"y":[5.360007003346041,5.2331413897751125,5.021698700490232,5.2331413897751125,5.106275776204184,5.106275776204184,5.486872616916969,5.360007003346041,5.486872616916969,5.444584079059993,5.402295541203017,5.1908528519181365,4.979410162633256,5.021698700490232,5.106275776204184,5.1908528519181365,5.1908528519181365,4.894833086919303,5.106275776204184,5.021698700490232,5.106275776204184,4.894833086919303,5.106275776204184,5.063987238347208,5.14856431406116,5.021698700490232,5.063987238347208,4.894833086919303,5.106275776204184,5.106275776204184,5.063987238347208,4.894833086919303,5.021698700490232,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.106275776204184,5.14856431406116,5.1908528519181365,5.106275776204184,5.063987238347208,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.275429927632088,5.317718465489064,5.360007003346041,5.317718465489064,5.2331413897751125,5.106275776204184,4.894833086919303,5.1908528519181365,5.14856431406116,4.979410162633256,5.021698700490232,5.14856431406116,5.14856431406116,5.021698700490232,5.106275776204184,5.063987238347208,5.14856431406116,5.1908528519181365,5.106275776204184,5.14856431406116,5.444584079059993,5.106275776204184,5.021698700490232,5.14856431406116],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(199,124,255,1)","dash":"solid"},"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]}]},"evals":[],"jsHooks":[]}</script></div>
```

::: {.sourceClojure}
```clojure
(defn factor [column]
  (vary-meta column
             assoc :gg/factor? true))
```
:::

::: {.sourceClojure}
```clojure
(defn factor? [column]
  (:gg/factor? column))
```
:::

::: {.sourceClojure}
```clojure
:ok
```
:::

::: {.printedClojure}
```clojure
:ok

```
:::

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/ggplotly_cont.clj">projects/datavis/ggplot/notebooks/ggplotly_cont.clj</a></small></small></pre></div>
```

### 2024-04-02 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplotly - rerendered

--- 2024-03-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
@@
    :stat_params {:na.rm [false]},
-   :constructor [[$ .MEM x861a15f64ba24c00]],
+   :constructor [[$ .MEM xd44ee531f87f4fc5]],
    :position {:compute_layer :ggproto-method, :super :ggproto-method},

### 2024-04-08 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
clay-cider demo - rerendered

--- 2024-01-17 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
@@
 format:
-  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
-highlight-style: solarized
+  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: index.html}
+fontsize: 0.9em
 code-block-background: true
@@
 }
+</style><style>.clay-limit-image-width .clay-image {max-width: 100%}
 </style>
 <script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/md-default14.js" type="text/javascript"></script>
-<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>
+
+```{=html}
+<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
+```
 
@@
             [tech.v3.datatype.functional :as fun]
-            [scicloj.noj.v1.vis.image :as vis.image]
             [scicloj.kindly.v4.kind :as kind]))
@@
 :::
+
+::: {.sourceClojure}
+```clojure
+(kind/hiccup [:style "img {max-width: 100%}"])
+```
+:::
+
+```{=html}
+<style>img {max-width: 100%}</style>
+```
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/fd4kjlws6Ts"></iframe></div>
+```{=html}
+<iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/fd4kjlws6Ts"></iframe>
+```
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><img src="index_files/0.png" style="width:100%;" /></div>
+::: {.clay-image}
+
+```{=html}
+<img src="index_files/0.png" />
+```
+
+:::
 
@@
 ```clojure
+(kind/fragment
  [raw-image
@@
       (fun/* 0.5)
-     (vis.image/tensor->image :byte-bgr))]
+      (bufimg/tensor->image :byte-bgr))])
 ```
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><img src="index_files/0.png" style="width:100%;" /></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/1.png" style="width:100%;" /></div></div><p>\]</p></div></div>
+::: {.clay-image}
+
+```{=html}
+<img src="index_files/0.png" />
+```
+
+:::
+
+::: {.clay-image}
+
+```{=html}
+<img src="index_files/1.png" />
+```
+
+:::
 
@@
       (fun/* 0.5)
-      (vis.image/tensor->image :byte-bgr))])
+      (bufimg/tensor->image :byte-bgr))])
 ```
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><h3>raw image</h3><div style="max-height:600px;overflow-y:auto;"><img src="index_files/0.png" style="width:100%;" /></div><h3>darkened image</h3><div style="max-height:600px;overflow-y:auto;"><img src="index_files/2.png" style="width:100%;" /></div></div></div>
+```{=html}
+<div><h3>raw image</h3><img class="clay-image" src="index_files/0.png" /><h3>darkened image</h3><img class="clay-image" src="index_files/2.png" /></div>
+```
 
@@
                            :uint8)
-    (vis.image/tensor->image :byte-bgr))
+    (bufimg/tensor->image :byte-bgr))
 ```
@@
 
-<div style="max-height:600px;overflow-y:auto;"><img src="index_files/3.png" style="width:100%;" /></div>
+::: {.clay-image}
+
+```{=html}
+<img src="index_files/3.png" />
+```
+
+:::
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><img src="index_files/4.png" style="width:100%;" /></div>
+::: {.clay-image}
+
+```{=html}
+<img src="index_files/4.png" />
+```
+
+:::
 
@@
 
-<div style="max-height:600px;overflow-y:auto;"><img src="index_files/5.png" style="width:100%;" /></div>
+::: {.clay-image}
+
+```{=html}
+<img src="index_files/5.png" />
+```
+
+:::
 
@@
                                         :uint8)
-                 (vis.image/tensor->image :byte-bgr))])))
+                 (bufimg/tensor->image :byte-bgr))])))
 ```
@@
 
-<div style="max-height:600px;overflow-y:auto;"><div><p>(</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.7
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/6.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.8
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/7.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">0.9
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/8.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/9.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.1
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/10.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.2
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/11.png" style="width:100%;" /></div></div><p>\]</p></div></div><div style="max-height:600px;overflow-y:auto;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="language-clojure">1.3
-</code></pre></div></div><div style="max-height:600px;overflow-y:auto;"><img src="index_files/12.png" style="width:100%;" /></div></div><p>\]</p></div></div></div><p>)</p></div></div>
+```{=html}
+<div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">0.7
+</code></pre></div><img class="clay-image" src="index_files/6.png" /></div><p>]</p></div><div><p>[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">0.8
+</code></pre></div><img class="clay-image" src="index_files/7.png" /></div><p>]</p></div><div><p>[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">0.9
+</code></pre></div><img class="clay-image" src="index_files/8.png" /></div><p>]</p></div><div><p>[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">1
+</code></pre></div><img class="clay-image" src="index_files/9.png" /></div><p>]</p></div><div><p>[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">1.1
+</code></pre></div><img class="clay-image" src="index_files/10.png" /></div><p>]</p></div><div><p>[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">1.2
+</code></pre></div><img class="clay-image" src="index_files/11.png" /></div><p>]</p></div><div><p>[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">1.3
+</code></pre></div><img class="clay-image" src="index_files/12.png" /></div><p>]</p></div></div><p>)</p></div>
+```
 
+```{=html}
 <div style="background-color:grey;height:2px;width:100%;"></div>
+```
 
+```{=html}
 <div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj">projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj</a></small></small></pre></div>
+```

### 2024-04-15 docs/projects/datavis/ggplot/comparing.qmd
ggplot - rerendered

@@
   html: {toc: true, toc-depth: 4, theme: cosmo, output-file: comparing.html}
+fontsize: 0.9em
 code-block-background: true
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x643ee41728c8&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels <- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n<bytecode: 0x58d461871fd0>\n<environment: namespace:ggplot2>\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x643ee41728c8&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels <- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n<bytecode:_ 0x58d461871fd0>\n<environment:_ namespace:ggplot2>\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 

### 2024-04-15 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

@@
   html: {toc: true, toc-depth: 4, theme: cosmo, output-file: draft.html}
+fontsize: 0.9em
 code-block-background: true
@@
      :transform
-     "function (x) \nx\n&lt;bytecode: 0x643ee0636140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n<bytecode: 0x58d45dd43140>\n<environment: namespace:base>\n",
      :inverse
-     "function (x) \nx\n&lt;bytecode: 0x643ee0636140&gt;\n&lt;environment: namespace:base&gt;\n",
+     "function (x) \nx\n<bytecode: 0x58d45dd43140>\n<environment: namespace:base>\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x643ee45a5010&gt;\n&lt;environment: 0x643ef149d1b0&gt;\n",
+     "function (x, n = n_default) \n{\n    x <- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng <- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n<bytecode: 0x58d461ca4718>\n<environment: 0x58d46d4d35d8>\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x643ee45aa910&gt;\n&lt;environment: 0x643ef149d338&gt;\n",
+     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x58d461caa018>\n<environment: 0x58d46d4d3760>\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x643ee45adf38&gt;\n&lt;environment: 0x643ef149d4c0&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x58d461cad640>\n<environment: 0x58d46d4d38b0>\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n&lt;bytecode: 0x643ee9d7fc60&gt;\n&lt;environment: 0x643ee9f9be70&gt;\n",
+     "function (x) \nlog(x, base)\n<bytecode: 0x58d467489ac8>\n<environment: 0x58d46f8464a8>\n",
      :inverse
-     "function (x) \nbase^x\n&lt;bytecode: 0x643ee9d7fdb0&gt;\n&lt;environment: 0x643ee9f9be70&gt;\n",
+     "function (x) \nbase^x\n<bytecode: 0x58d467489c18>\n<environment: 0x58d46f8464a8>\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x643ee9cc7d78&gt;\n&lt;environment: 0x643ee9f90eb8&gt;\n",
+     "function (x, n = n_default) \n{\n    raw_rng <- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng <- log(raw_rng, base = base)\n    min <- floor(rng[1])\n    max <- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by <- floor((max - min)/n) + 1\n    breaks <- base^seq(min, max, by = by)\n    relevant_breaks <- base^rng[1] <= breaks & breaks <= base^rng[2]\n    if (sum(relevant_breaks) >= (n - 2)) {\n        return(breaks)\n    }\n    while (by > 1) {\n        by <- by - 1\n        breaks <- base^seq(min, max, by = by)\n        relevant_breaks <- base^rng[1] <= breaks & breaks <= \n            base^rng[2]\n        if (sum(relevant_breaks) >= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n<bytecode: 0x58d4673d5710>\n<environment: 0x58d46fe22dc8>\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x643ee45aa910&gt;\n&lt;environment: 0x643ee9f91350&gt;\n",
+     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x58d461caa018>\n<environment: 0x58d46fe22a10>\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x643ee45adf38&gt;\n&lt;environment: 0x643ee9f914d8&gt;\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x58d461cad640>\n<environment: 0x58d46fe228c0>\n",
      :domain [1.0E-100 ##Inf]},
@@
   count  prop x          width flipped_aes fill       PANEL group
-  &lt;dbl&gt; &lt;dbl&gt; &lt;mppd_dsc&gt; &lt;dbl&gt; &lt;lgl&gt;       &lt;chr&gt;      &lt;fct&gt; &lt;int&gt;
+  <dbl> <dbl> <mppd_dsc> <dbl> <lgl>       <chr>      <fct> <int>
 1     5     1 1            0.9 FALSE       2seater    1         1

### 2024-04-15 docs/projects/datavis/ggplot/ggplotly.qmd
ggplot - rerendered

--- 2024-03-19 docs/projects/datavis/ggplot/ggplotly.qmd
@@
   html: {toc: true, toc-depth: 4, theme: cosmo, output-file: ggplotly.html}
+fontsize: 0.9em
 code-block-background: true
@@
 ```{=html}
-<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-12" style="width:100%;height:400px;"><script data-for="htmlwidget-12" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-12" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>
+<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-13" style="width:100%;height:400px;"><script data-for="htmlwidget-13" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-13" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>
 ```

### 2024-04-15 docs/projects/datavis/ggplot/ggplotly_cont.qmd
ggplot - rerendered

@@
   html: {toc: true, toc-depth: 4, theme: cosmo, output-file: ggplotly_cont.html}
+fontsize: 0.9em
 code-block-background: true
@@
             [clojure.string :as str]
-            [clojure.math :as math]))
+            [clojure.math :as math]
+            [clojure2d.color :as color]))
 ```
@@
                          :dash "solid"}})))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(color/palette )
+```
+:::
+
+::: {.printedClojure}
+```clojure
+[[223.0 46.0 40.0 255.0]
+ [254.0 128.0 26.0 255.0]
+ [233.0 191.0 53.0 255.0]
+ [129.0 187.0 66.0 255.0]
+ [50.0 199.0 169.0 255.0]
+ [74.0 155.0 220.0 255.0]]
+
 ```
@@
 ```clojure
+(defn factor [column]
+  (vary-meta column
+             assoc :gg/factor? true))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
+(defn factor? [column]
+  (:gg/factor? column))
+```
+:::
+
+::: {.sourceClojure}
+```clojure
 (let [data toydata.ggplot/mpg
@@
 ```{=html}
-<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-171" style="width:100%;height:400px;"><script data-for="htmlwidget-171" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-171" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895},"title":{"text":"factor(cyl)","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}}},"xaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":true,"barmode":"relative","yaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":31.4155251141553},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"data":[{"y":[1.8,1.8,2.0,2.0,1.8,1.8,2.0,2.0,2.4,2.4,2.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.0,2.0,2.0,2.0,2.4,2.4,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,2.2,2.2,2.4,2.4,2.2,2.2,2.4,2.4,1.8,1.8,1.8,1.8,1.8,2.7,2.7,2.7,2.0,2.0,2.0,2.0,1.9,2.0,2.0,2.0,2.0,1.9,1.9,2.0,2.0,1.8,1.8,2.0,2.0],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"marker":{"autocolorscale":false,"color":"rgba(248,118,109,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(248,118,109,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.1377007978924745,2.1377007978924745,2.0569213765537713,2.0973110872231233,2.2588699299005293,2.299259640569881,2.178090508561826,2.2184802192311777,2.2184802192311777,2.0973110872231233,2.3396493512392325,1.9761419552150683,2.01653166588442,2.01653166588442,2.1377007978924745,2.01653166588442,1.9357522445457167,1.8549728232070137,1.8549728232070137,2.1377007978924745,2.2588699299005293,2.2184802192311777,2.0973110872231233,2.0569213765537713,2.2588699299005293,2.1377007978924745,2.178090508561826,2.2184802192311777,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.01653166588442,2.299259640569881,2.3396493512392325,2.2184802192311777,2.299259640569881,2.2588699299005293,2.380039061908584,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.299259640569881,2.2184802192311777,2.299259640569881,2.2184802192311777,2.5012081939166384,2.5012081939166384,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.0569213765537713,2.2184802192311777,2.1377007978924745,2.0569213765537713,2.0569213765537713,2.0973110872231233,1.9761419552150683,1.895362533876365,1.8145831125376621,1.895362533876365,2.5012081939166384,2.5012081939166384,2.4204287725779356,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,1.6530242698602557,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,2.178090508561826,2.1377007978924745],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(248,118,109,1)","dash":"solid"},"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"marker":{"autocolorscale":false,"color":"rgba(124,174,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(124,174,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(124,174,0,1)","dash":"solid"},"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.8,2.8,3.1,2.8,2.8,3.1,3.1,2.8,3.1,3.1,3.5,3.6,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,3.9,4.0,4.0,4.0,4.0,4.2,4.2,3.8,3.8,4.0,4.0,2.5,2.5,3.3,2.7,2.7,2.7,3.0,3.7,4.0,4.0,4.0,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,3.1,3.8,3.8,3.8,3.4,3.4,4.0,3.0,3.0,3.5,3.0,3.0,3.3,3.4,3.4,4.0,4.0,2.8,2.8,2.8,2.8,2.8,3.6],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"marker":{"autocolorscale":false,"color":"rgba(0,191,196,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,191,196,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[3.202020262359323,3.202020262359323,3.1369190700341694,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.33222264700963,3.2671214546844767,3.202020262359323,3.0067166853838625,3.202020262359323,3.33222264700963,3.4624250316599374,3.4624250316599374,3.33222264700963,3.33222264700963,3.787930993285705,3.4624250316599374,3.527526223985091,3.397323839334784,3.397323839334784,3.6577286086353977,3.7228298009605516,3.787930993285705,3.787930993285705,3.787930993285705,3.787930993285705,3.6577286086353977,3.787930993285705,3.6577286086353977,3.787930993285705,3.787930993285705,3.202020262359323,3.2671214546844767,3.202020262359323,3.33222264700963,3.202020262359323,3.202020262359323,3.071817877709016,3.33222264700963,3.33222264700963,3.33222264700963,3.4624250316599374,3.6577286086353977,3.5926274163102443,3.787930993285705,3.6577286086353977,3.1369190700341694,3.202020262359323,3.202020262359323,3.2671214546844767,3.2671214546844767,3.787930993285705,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.1369190700341694,3.071817877709016,3.6577286086353977,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.071817877709016,3.202020262359323,3.202020262359323,3.1369190700341694,3.787930993285705,3.6577286086353977,3.7228298009605516,3.5926274163102443,3.33222264700963,3.397323839334784,3.33222264700963,3.202020262359323,3.202020262359323,3.202020262359323],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(0,191,196,1)","dash":"solid"},"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,4.7,4.7,4.7,5.2,5.2,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.6,5.0,4.6,4.6,4.6,5.4,5.4,4.6,4.6,4.6,4.6,5.4,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.6,5.0,5.6,5.3,4.7,4.7,5.7],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"marker":{"autocolorscale":false,"color":"rgba(199,124,255,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(199,124,255,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]},{"y":[5.360007003346041,5.2331413897751125,5.021698700490232,5.2331413897751125,5.106275776204184,5.106275776204184,5.486872616916969,5.360007003346041,5.486872616916969,5.444584079059993,5.402295541203017,5.1908528519181365,4.979410162633256,5.021698700490232,5.106275776204184,5.1908528519181365,5.1908528519181365,4.894833086919303,5.106275776204184,5.021698700490232,5.106275776204184,4.894833086919303,5.106275776204184,5.063987238347208,5.14856431406116,5.021698700490232,5.063987238347208,4.894833086919303,5.106275776204184,5.106275776204184,5.063987238347208,4.894833086919303,5.021698700490232,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.106275776204184,5.14856431406116,5.1908528519181365,5.106275776204184,5.063987238347208,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.275429927632088,5.317718465489064,5.360007003346041,5.317718465489064,5.2331413897751125,5.106275776204184,4.894833086919303,5.1908528519181365,5.14856431406116,4.979410162633256,5.021698700490232,5.14856431406116,5.14856431406116,5.021698700490232,5.106275776204184,5.063987238347208,5.14856431406116,5.1908528519181365,5.106275776204184,5.14856431406116,5.444584079059993,5.106275776204184,5.021698700490232,5.14856431406116],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(199,124,255,1)","dash":"solid"},"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]}]},"evals":[],"jsHooks":[]}</script></div>
+<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-14" style="width:100%;height:400px;"><script data-for="htmlwidget-14" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-14" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895},"title":{"text":"factor(cyl)","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}}},"xaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":true,"barmode":"relative","yaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":31.4155251141553},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"data":[{"y":[1.8,1.8,2.0,2.0,1.8,1.8,2.0,2.0,2.4,2.4,2.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.0,2.0,2.0,2.0,2.4,2.4,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,2.2,2.2,2.4,2.4,2.2,2.2,2.4,2.4,1.8,1.8,1.8,1.8,1.8,2.7,2.7,2.7,2.0,2.0,2.0,2.0,1.9,2.0,2.0,2.0,2.0,1.9,1.9,2.0,2.0,1.8,1.8,2.0,2.0],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"marker":{"autocolorscale":false,"color":"rgba(248,118,109,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(248,118,109,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.1377007978924745,2.1377007978924745,2.0569213765537713,2.0973110872231233,2.2588699299005293,2.299259640569881,2.178090508561826,2.2184802192311777,2.2184802192311777,2.0973110872231233,2.3396493512392325,1.9761419552150683,2.01653166588442,2.01653166588442,2.1377007978924745,2.01653166588442,1.9357522445457167,1.8549728232070137,1.8549728232070137,2.1377007978924745,2.2588699299005293,2.2184802192311777,2.0973110872231233,2.0569213765537713,2.2588699299005293,2.1377007978924745,2.178090508561826,2.2184802192311777,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.01653166588442,2.299259640569881,2.3396493512392325,2.2184802192311777,2.299259640569881,2.2588699299005293,2.380039061908584,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.299259640569881,2.2184802192311777,2.299259640569881,2.2184802192311777,2.5012081939166384,2.5012081939166384,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.0569213765537713,2.2184802192311777,2.1377007978924745,2.0569213765537713,2.0569213765537713,2.0973110872231233,1.9761419552150683,1.895362533876365,1.8145831125376621,1.895362533876365,2.5012081939166384,2.5012081939166384,2.4204287725779356,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,1.6530242698602557,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,2.178090508561826,2.1377007978924745],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(248,118,109,1)","dash":"solid"},"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"marker":{"autocolorscale":false,"color":"rgba(124,174,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(124,174,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(124,174,0,1)","dash":"solid"},"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.8,2.8,3.1,2.8,2.8,3.1,3.1,2.8,3.1,3.1,3.5,3.6,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,3.9,4.0,4.0,4.0,4.0,4.2,4.2,3.8,3.8,4.0,4.0,2.5,2.5,3.3,2.7,2.7,2.7,3.0,3.7,4.0,4.0,4.0,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,3.1,3.8,3.8,3.8,3.4,3.4,4.0,3.0,3.0,3.5,3.0,3.0,3.3,3.4,3.4,4.0,4.0,2.8,2.8,2.8,2.8,2.8,3.6],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"marker":{"autocolorscale":false,"color":"rgba(0,191,196,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,191,196,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[3.202020262359323,3.202020262359323,3.1369190700341694,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.33222264700963,3.2671214546844767,3.202020262359323,3.0067166853838625,3.202020262359323,3.33222264700963,3.4624250316599374,3.4624250316599374,3.33222264700963,3.33222264700963,3.787930993285705,3.4624250316599374,3.527526223985091,3.397323839334784,3.397323839334784,3.6577286086353977,3.7228298009605516,3.787930993285705,3.787930993285705,3.787930993285705,3.787930993285705,3.6577286086353977,3.787930993285705,3.6577286086353977,3.787930993285705,3.787930993285705,3.202020262359323,3.2671214546844767,3.202020262359323,3.33222264700963,3.202020262359323,3.202020262359323,3.071817877709016,3.33222264700963,3.33222264700963,3.33222264700963,3.4624250316599374,3.6577286086353977,3.5926274163102443,3.787930993285705,3.6577286086353977,3.1369190700341694,3.202020262359323,3.202020262359323,3.2671214546844767,3.2671214546844767,3.787930993285705,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.1369190700341694,3.071817877709016,3.6577286086353977,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.071817877709016,3.202020262359323,3.202020262359323,3.1369190700341694,3.787930993285705,3.6577286086353977,3.7228298009605516,3.5926274163102443,3.33222264700963,3.397323839334784,3.33222264700963,3.202020262359323,3.202020262359323,3.202020262359323],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(0,191,196,1)","dash":"solid"},"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,4.7,4.7,4.7,5.2,5.2,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.6,5.0,4.6,4.6,4.6,5.4,5.4,4.6,4.6,4.6,4.6,5.4,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.6,5.0,5.6,5.3,4.7,4.7,5.7],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"marker":{"autocolorscale":false,"color":"rgba(199,124,255,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(199,124,255,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]},{"y":[5.360007003346041,5.2331413897751125,5.021698700490232,5.2331413897751125,5.106275776204184,5.106275776204184,5.486872616916969,5.360007003346041,5.486872616916969,5.444584079059993,5.402295541203017,5.1908528519181365,4.979410162633256,5.021698700490232,5.106275776204184,5.1908528519181365,5.1908528519181365,4.894833086919303,5.106275776204184,5.021698700490232,5.106275776204184,4.894833086919303,5.106275776204184,5.063987238347208,5.14856431406116,5.021698700490232,5.063987238347208,4.894833086919303,5.106275776204184,5.106275776204184,5.063987238347208,4.894833086919303,5.021698700490232,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.106275776204184,5.14856431406116,5.1908528519181365,5.106275776204184,5.063987238347208,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.275429927632088,5.317718465489064,5.360007003346041,5.317718465489064,5.2331413897751125,5.106275776204184,4.894833086919303,5.1908528519181365,5.14856431406116,4.979410162633256,5.021698700490232,5.14856431406116,5.14856431406116,5.021698700490232,5.106275776204184,5.063987238347208,5.14856431406116,5.1908528519181365,5.106275776204184,5.14856431406116,5.444584079059993,5.106275776204184,5.021698700490232,5.14856431406116],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(199,124,255,1)","dash":"solid"},"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]}]},"evals":[],"jsHooks":[]}</script></div>
 ```
-
-::: {.sourceClojure}
-```clojure
-(defn factor [column]
-  (vary-meta column
-             assoc :gg/factor? true))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn factor? [column]
-  (:gg/factor? column))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-:ok
-```
-:::
-
-::: {.printedClojure}
-```clojure
-:ok
-
-```
-:::
 

### 2024-04-15 docs/projects/datavis/ggplot/index.qmd
ggplot - rerendered

@@
   html: {toc: true, toc-depth: 4, theme: cosmo, output-file: index.html}
+fontsize: 0.9em
 code-block-background: true

### 2024-04-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

@@
   html: {toc: true, toc-depth: 4, theme: cosmo, output-file: study_session_20240225.html}
+fontsize: 0.9em
 code-block-background: true
@@
    manufacturer model      displ  year   cyl trans drv     cty   hwy fl    class
-   &lt;chr&gt;        &lt;chr&gt;      &lt;dbl&gt; &lt;int&gt; &lt;int&gt; &lt;chr&gt; &lt;chr&gt; &lt;int&gt; &lt;int&gt; &lt;chr&gt; &lt;chr&gt;
+   <chr>        <chr>      <dbl> <int> <int> <chr> <chr> <int> <int> <chr> <chr>
  1 audi         a4           1.8  1999     4 auto… f        18    29 p     comp…
@@
 ```clojure
-"&lt;?xml version=\"1.0\" encoding=\"UTF-8\"?&gt;\n&lt;svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\"&gt;\n&lt;defs&gt;\n&lt;g&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-7\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph0-8\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-4\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-5\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph1-6\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-0\"&gt;\n&lt;path style=\"stroke:none;\" d=\"\"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-1\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-2\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/&gt;\n&lt;/symbol&gt;\n&lt;symbol overflow=\"visible\" id=\"glyph2-3\"&gt;\n&lt;path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/&gt;\n&lt;/symbol&gt;\n&lt;/g&gt;\n&lt;clipPath id=\"clip1\"&gt;\n  &lt;path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip2\"&gt;\n  &lt;path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip3\"&gt;\n  &lt;path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip4\"&gt;\n  &lt;path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip5\"&gt;\n  &lt;path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip6\"&gt;\n  &lt;path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip7\"&gt;\n  &lt;path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip8\"&gt;\n  &lt;path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip9\"&gt;\n  &lt;path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip10\"&gt;\n  &lt;path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip11\"&gt;\n  &lt;path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip12\"&gt;\n  &lt;path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip13\"&gt;\n  &lt;path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip14\"&gt;\n  &lt;path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip15\"&gt;\n  &lt;path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip16\"&gt;\n  &lt;path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip17\"&gt;\n  &lt;path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip18\"&gt;\n  &lt;path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip19\"&gt;\n  &lt;path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/&gt;\n&lt;/clipPath&gt;\n&lt;clipPath id=\"clip20\"&gt;\n  &lt;path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/&gt;\n&lt;/clipPath&gt;\n&lt;image id=\"image459\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/&gt;\n&lt;pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\"&gt;\n  &lt;use xlink:href=\"#image459\"/&gt;\n&lt;/pattern&gt;\n&lt;/defs&gt;\n&lt;g id=\"surface455\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/&gt;\n&lt;g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\"&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/&gt;\n&lt;path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/&gt;\n  &lt;use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/&gt;\n  &lt;use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/&gt;\n&lt;/g&gt;\n&lt;path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/&gt;\n&lt;g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\"&gt;\n&lt;rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/&gt;\n  &lt;use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/&gt;\n  &lt;use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/&gt;\n  &lt;use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/&gt;\n&lt;/g&gt;\n&lt;g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\"&gt;\n  &lt;use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/&gt;\n  &lt;use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/&gt;\n&lt;/g&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/&gt;\n&lt;path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/&gt;\n&lt;/g&gt;\n&lt;/svg&gt;\n"
+"<?xml version=\"1.0\" encoding=\"UTF-8\"?>\n<svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\">\n<defs>\n<g>\n<symbol overflow=\"visible\" id=\"glyph0-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-1\">\n<path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-2\">\n<path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-3\">\n<path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-4\">\n<path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-5\">\n<path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-6\">\n<path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-7\">\n<path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-8\">\n<path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-1\">\n<path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-2\">\n<path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-3\">\n<path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-4\">\n<path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-5\">\n<path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-6\">\n<path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-1\">\n<path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-2\">\n<path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-3\">\n<path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/>\n</symbol>\n</g>\n<clipPath id=\"clip1\">\n  <path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip2\">\n  <path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/>\n</clipPath>\n<clipPath id=\"clip3\">\n  <path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/>\n</clipPath>\n<clipPath id=\"clip4\">\n  <path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/>\n</clipPath>\n<clipPath id=\"clip5\">\n  <path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/>\n</clipPath>\n<clipPath id=\"clip6\">\n  <path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip7\">\n  <path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip8\">\n  <path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip9\">\n  <path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip10\">\n  <path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip11\">\n  <path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/>\n</clipPath>\n<clipPath id=\"clip12\">\n  <path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/>\n</clipPath>\n<clipPath id=\"clip13\">\n  <path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/>\n</clipPath>\n<clipPath id=\"clip14\">\n  <path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip15\">\n  <path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip16\">\n  <path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip17\">\n  <path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip18\">\n  <path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip19\">\n  <path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip20\">\n  <path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/>\n</clipPath>\n<image id=\"image460\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/>\n<pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\">\n  <use xlink:href=\"#image460\"/>\n</pattern>\n</defs>\n<g id=\"surface456\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/>\n<g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\">\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/>\n</g>\n<g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/>\n</g>\n<g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/>\n</g>\n<g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/>\n</g>\n<g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/>\n</g>\n<g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/>\n</g>\n<g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/>\n</g>\n<g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/>\n</g>\n<g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/>\n</g>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/>\n</g>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/>\n  <use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/>\n  <use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/>\n</g>\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/>\n<g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/>\n</g>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/>\n</g>\n</svg>\n"
 
@@
    :stat_params {:na.rm [false]},
-   :constructor [[$ .MEM xd44ee531f87f4fc5]],
+   :constructor [[$ .MEM x06c5570df1b44c78]],
    :position {:compute_layer :ggproto-method, :super :ggproto-method},
@@
 </clipPath>
-<image id="image486" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
+<image id="image487" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
 <pattern id="pattern0" patternUnits="userSpaceOnUse" width="1" height="300"  patternTransform="matrix(17.28,0,0,0.288,450.281644,203.20411)">
-  <use xlink:href="#image486"/>
+  <use xlink:href="#image487"/>
 </pattern>
 </defs>
-<g id="surface482">
+<g id="surface483">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>

### 2024-04-15 docs/projects/datavis/ggplot/comparing.qmd
ggplot - rerendered

@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels <- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n<bytecode: 0x58d461871fd0>\n<environment: namespace:ggplot2>\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
+   "function (labels, multi_line = TRUE) \n{\n    labels <- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n<bytecode: 0x5b75b1efa660>\n<environment: namespace:ggplot2>\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
   :shrink [true],
@@
    :labeller
-   "function (labels, multi_line = TRUE) \n{\n    labels <- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n<bytecode:_ 0x58d461871fd0>\n<environment:_ namespace:ggplot2>\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
+   "function (labels, multi_line = TRUE) \n{\n    labels <- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n<bytecode:_ 0x5b75b1efa660>\n<environment:_ namespace:ggplot2>\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]
 

### 2024-04-15 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

@@
      :transform
-     "function (x) \nx\n<bytecode: 0x58d45dd43140>\n<environment: namespace:base>\n",
+     "function (x) \nx\n<bytecode: 0x5b75ae3c23a0>\n<environment: namespace:base>\n",
      :inverse
-     "function (x) \nx\n<bytecode: 0x58d45dd43140>\n<environment: namespace:base>\n",
+     "function (x) \nx\n<bytecode: 0x5b75ae3c23a0>\n<environment: namespace:base>\n",
      :breaks
-     "function (x, n = n_default) \n{\n    x <- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng <- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n<bytecode: 0x58d461ca4718>\n<environment: 0x58d46d4d35d8>\n",
+     "function (x, n = n_default) \n{\n    x <- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng <- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n<bytecode: 0x5b75b232cda8>\n<environment: 0x5b75bd6e2898>\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x58d461caa018>\n<environment: 0x58d46d4d3760>\n",
+     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75bd6e2710>\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x58d461cad640>\n<environment: 0x58d46d4d38b0>\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75bd6e2198>\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n<bytecode: 0x58d467489ac8>\n<environment: 0x58d46f8464a8>\n",
+     "function (x) \nlog(x, base)\n<bytecode: 0x5b75b7b00b30>\n<environment: 0x5b75b582d0a0>\n",
      :inverse
-     "function (x) \nbase^x\n<bytecode: 0x58d467489c18>\n<environment: 0x58d46f8464a8>\n",
+     "function (x) \nbase^x\n<bytecode: 0x5b75b7b00f90>\n<environment: 0x5b75b582d0a0>\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng <- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng <- log(raw_rng, base = base)\n    min <- floor(rng[1])\n    max <- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by <- floor((max - min)/n) + 1\n    breaks <- base^seq(min, max, by = by)\n    relevant_breaks <- base^rng[1] <= breaks & breaks <= base^rng[2]\n    if (sum(relevant_breaks) >= (n - 2)) {\n        return(breaks)\n    }\n    while (by > 1) {\n        by <- by - 1\n        breaks <- base^seq(min, max, by = by)\n        relevant_breaks <- base^rng[1] <= breaks & breaks <= \n            base^rng[2]\n        if (sum(relevant_breaks) >= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n<bytecode: 0x58d4673d5710>\n<environment: 0x58d46fe22dc8>\n",
+     "function (x, n = n_default) \n{\n    raw_rng <- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng <- log(raw_rng, base = base)\n    min <- floor(rng[1])\n    max <- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by <- floor((max - min)/n) + 1\n    breaks <- base^seq(min, max, by = by)\n    relevant_breaks <- base^rng[1] <= breaks & breaks <= base^rng[2]\n    if (sum(relevant_breaks) >= (n - 2)) {\n        return(breaks)\n    }\n    while (by > 1) {\n        by <- by - 1\n        breaks <- base^seq(min, max, by = by)\n        relevant_breaks <- base^rng[1] <= breaks & breaks <= \n            base^rng[2]\n        if (sum(relevant_breaks) >= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n<bytecode: 0x5b75b7a46af8>\n<environment: 0x5b75b58310d8>\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x58d461caa018>\n<environment: 0x58d46fe22a10>\n",
+     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75b5830ce8>\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x58d461cad640>\n<environment: 0x58d46fe228c0>\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75b5830b98>\n",
      :domain [1.0E-100 ##Inf]},

### 2024-04-15 docs/projects/datavis/ggplot/ggplotly_cont.qmd
ggplot - rerendered

@@
 
-# Further exploring ggplotly's client side - DRAFT
+# Further exploring ggplotly's client side
 
@@
 and then gradually generalizing it as a set of Clojure functions.
-This is a work-in-progress draft. Some parts are still hard-coded.
+This is a work-in-progress draft. Some parts are still hard-coded (e.g., colours).
 
@@
 ```clojure
-(color/palette )
-```
-:::
-
-::: {.printedClojure}
-```clojure
-[[223.0 46.0 40.0 255.0]
- [254.0 128.0 26.0 255.0]
- [233.0 191.0 53.0 255.0]
- [129.0 187.0 66.0 255.0]
- [50.0 199.0 169.0 255.0]
- [74.0 155.0 220.0 255.0]]
-
-```
-:::
-
-::: {.sourceClojure}
-```clojure
 (def colors
-  ["rgba(248,118,109,1)"
-   "rgba(124,174,0,1)"
-   "rgba(0,191,196,1)"
-   "rgba(199,124,255,1)"])
+  (->> :category10
+       color/palette
+       (mapv (fn [[r g b a]]
+               (format "rgba(%d,%d,%d,%f)"
+                       (int r)
+                       (int g)
+                       (int b)
+                       (/ a 255.0))))))
 ```
@@
 ```clojure
-(defn factor [column]
-  (vary-meta column
-             assoc :gg/factor? true))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
-(defn factor? [column]
-  (:gg/factor? column))
-```
-:::
-
-::: {.sourceClojure}
-```clojure
+(delay
   (let [data toydata.ggplot/mpg
         point-layers (-> data
-                       (tc/add-column "factor(cyl)" #(factor (:cyl %)))
+                         (tc/add-column "factor(cyl)" #(:cyl %))
                          (tc/group-by :cyl {:result-type :as-map})
@@
       :evals [],
-    :jsHooks []}))
+      :jsHooks []})))
 ```
@@
 ```{=html}
-<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-14" style="width:100%;height:400px;"><script data-for="htmlwidget-14" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-14" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895},"title":{"text":"factor(cyl)","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}}},"xaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":true,"barmode":"relative","yaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":31.4155251141553},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"data":[{"y":[1.8,1.8,2.0,2.0,1.8,1.8,2.0,2.0,2.4,2.4,2.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.0,2.0,2.0,2.0,2.4,2.4,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,2.2,2.2,2.4,2.4,2.2,2.2,2.4,2.4,1.8,1.8,1.8,1.8,1.8,2.7,2.7,2.7,2.0,2.0,2.0,2.0,1.9,2.0,2.0,2.0,2.0,1.9,1.9,2.0,2.0,1.8,1.8,2.0,2.0],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"marker":{"autocolorscale":false,"color":"rgba(248,118,109,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(248,118,109,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.1377007978924745,2.1377007978924745,2.0569213765537713,2.0973110872231233,2.2588699299005293,2.299259640569881,2.178090508561826,2.2184802192311777,2.2184802192311777,2.0973110872231233,2.3396493512392325,1.9761419552150683,2.01653166588442,2.01653166588442,2.1377007978924745,2.01653166588442,1.9357522445457167,1.8549728232070137,1.8549728232070137,2.1377007978924745,2.2588699299005293,2.2184802192311777,2.0973110872231233,2.0569213765537713,2.2588699299005293,2.1377007978924745,2.178090508561826,2.2184802192311777,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.01653166588442,2.299259640569881,2.3396493512392325,2.2184802192311777,2.299259640569881,2.2588699299005293,2.380039061908584,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.299259640569881,2.2184802192311777,2.299259640569881,2.2184802192311777,2.5012081939166384,2.5012081939166384,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.0569213765537713,2.2184802192311777,2.1377007978924745,2.0569213765537713,2.0569213765537713,2.0973110872231233,1.9761419552150683,1.895362533876365,1.8145831125376621,1.895362533876365,2.5012081939166384,2.5012081939166384,2.4204287725779356,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,1.6530242698602557,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,2.178090508561826,2.1377007978924745],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(248,118,109,1)","dash":"solid"},"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"marker":{"autocolorscale":false,"color":"rgba(124,174,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(124,174,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(124,174,0,1)","dash":"solid"},"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.8,2.8,3.1,2.8,2.8,3.1,3.1,2.8,3.1,3.1,3.5,3.6,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,3.9,4.0,4.0,4.0,4.0,4.2,4.2,3.8,3.8,4.0,4.0,2.5,2.5,3.3,2.7,2.7,2.7,3.0,3.7,4.0,4.0,4.0,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,3.1,3.8,3.8,3.8,3.4,3.4,4.0,3.0,3.0,3.5,3.0,3.0,3.3,3.4,3.4,4.0,4.0,2.8,2.8,2.8,2.8,2.8,3.6],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"marker":{"autocolorscale":false,"color":"rgba(0,191,196,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,191,196,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[3.202020262359323,3.202020262359323,3.1369190700341694,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.33222264700963,3.2671214546844767,3.202020262359323,3.0067166853838625,3.202020262359323,3.33222264700963,3.4624250316599374,3.4624250316599374,3.33222264700963,3.33222264700963,3.787930993285705,3.4624250316599374,3.527526223985091,3.397323839334784,3.397323839334784,3.6577286086353977,3.7228298009605516,3.787930993285705,3.787930993285705,3.787930993285705,3.787930993285705,3.6577286086353977,3.787930993285705,3.6577286086353977,3.787930993285705,3.787930993285705,3.202020262359323,3.2671214546844767,3.202020262359323,3.33222264700963,3.202020262359323,3.202020262359323,3.071817877709016,3.33222264700963,3.33222264700963,3.33222264700963,3.4624250316599374,3.6577286086353977,3.5926274163102443,3.787930993285705,3.6577286086353977,3.1369190700341694,3.202020262359323,3.202020262359323,3.2671214546844767,3.2671214546844767,3.787930993285705,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.1369190700341694,3.071817877709016,3.6577286086353977,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.071817877709016,3.202020262359323,3.202020262359323,3.1369190700341694,3.787930993285705,3.6577286086353977,3.7228298009605516,3.5926274163102443,3.33222264700963,3.397323839334784,3.33222264700963,3.202020262359323,3.202020262359323,3.202020262359323],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(0,191,196,1)","dash":"solid"},"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,4.7,4.7,4.7,5.2,5.2,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.6,5.0,4.6,4.6,4.6,5.4,5.4,4.6,4.6,4.6,4.6,5.4,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.6,5.0,5.6,5.3,4.7,4.7,5.7],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"marker":{"autocolorscale":false,"color":"rgba(199,124,255,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(199,124,255,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]},{"y":[5.360007003346041,5.2331413897751125,5.021698700490232,5.2331413897751125,5.106275776204184,5.106275776204184,5.486872616916969,5.360007003346041,5.486872616916969,5.444584079059993,5.402295541203017,5.1908528519181365,4.979410162633256,5.021698700490232,5.106275776204184,5.1908528519181365,5.1908528519181365,4.894833086919303,5.106275776204184,5.021698700490232,5.106275776204184,4.894833086919303,5.106275776204184,5.063987238347208,5.14856431406116,5.021698700490232,5.063987238347208,4.894833086919303,5.106275776204184,5.106275776204184,5.063987238347208,4.894833086919303,5.021698700490232,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.106275776204184,5.14856431406116,5.1908528519181365,5.106275776204184,5.063987238347208,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.275429927632088,5.317718465489064,5.360007003346041,5.317718465489064,5.2331413897751125,5.106275776204184,4.894833086919303,5.1908528519181365,5.14856431406116,4.979410162633256,5.021698700490232,5.14856431406116,5.14856431406116,5.021698700490232,5.106275776204184,5.063987238347208,5.14856431406116,5.1908528519181365,5.106275776204184,5.14856431406116,5.444584079059993,5.106275776204184,5.021698700490232,5.14856431406116],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(199,124,255,1)","dash":"solid"},"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]}]},"evals":[],"jsHooks":[]}</script></div>
+<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-14" style="width:100%;height:400px;"><script data-for="htmlwidget-14" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-14" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895},"title":{"text":"factor(cyl)","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}}},"xaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":true,"barmode":"relative","yaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":31.4155251141553},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"data":[{"y":[1.8,1.8,2.0,2.0,1.8,1.8,2.0,2.0,2.4,2.4,2.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.0,2.0,2.0,2.0,2.4,2.4,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,2.2,2.2,2.4,2.4,2.2,2.2,2.4,2.4,1.8,1.8,1.8,1.8,1.8,2.7,2.7,2.7,2.0,2.0,2.0,2.0,1.9,2.0,2.0,2.0,2.0,1.9,1.9,2.0,2.0,1.8,1.8,2.0,2.0],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"marker":{"autocolorscale":false,"color":"rgba(31,119,180,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(31,119,180,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.1377007978924745,2.1377007978924745,2.0569213765537713,2.0973110872231233,2.2588699299005293,2.299259640569881,2.178090508561826,2.2184802192311777,2.2184802192311777,2.0973110872231233,2.3396493512392325,1.9761419552150683,2.01653166588442,2.01653166588442,2.1377007978924745,2.01653166588442,1.9357522445457167,1.8549728232070137,1.8549728232070137,2.1377007978924745,2.2588699299005293,2.2184802192311777,2.0973110872231233,2.0569213765537713,2.2588699299005293,2.1377007978924745,2.178090508561826,2.2184802192311777,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.01653166588442,2.299259640569881,2.3396493512392325,2.2184802192311777,2.299259640569881,2.2588699299005293,2.380039061908584,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.299259640569881,2.2184802192311777,2.299259640569881,2.2184802192311777,2.5012081939166384,2.5012081939166384,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.0569213765537713,2.2184802192311777,2.1377007978924745,2.0569213765537713,2.0569213765537713,2.0973110872231233,1.9761419552150683,1.895362533876365,1.8145831125376621,1.895362533876365,2.5012081939166384,2.5012081939166384,2.4204287725779356,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,1.6530242698602557,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,2.178090508561826,2.1377007978924745],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(31,119,180,1.000000)","dash":"solid"},"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"marker":{"autocolorscale":false,"color":"rgba(255,127,14,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(255,127,14,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(255,127,14,1.000000)","dash":"solid"},"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.8,2.8,3.1,2.8,2.8,3.1,3.1,2.8,3.1,3.1,3.5,3.6,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,3.9,4.0,4.0,4.0,4.0,4.2,4.2,3.8,3.8,4.0,4.0,2.5,2.5,3.3,2.7,2.7,2.7,3.0,3.7,4.0,4.0,4.0,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,3.1,3.8,3.8,3.8,3.4,3.4,4.0,3.0,3.0,3.5,3.0,3.0,3.3,3.4,3.4,4.0,4.0,2.8,2.8,2.8,2.8,2.8,3.6],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"marker":{"autocolorscale":false,"color":"rgba(44,160,44,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(44,160,44,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[3.202020262359323,3.202020262359323,3.1369190700341694,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.33222264700963,3.2671214546844767,3.202020262359323,3.0067166853838625,3.202020262359323,3.33222264700963,3.4624250316599374,3.4624250316599374,3.33222264700963,3.33222264700963,3.787930993285705,3.4624250316599374,3.527526223985091,3.397323839334784,3.397323839334784,3.6577286086353977,3.7228298009605516,3.787930993285705,3.787930993285705,3.787930993285705,3.787930993285705,3.6577286086353977,3.787930993285705,3.6577286086353977,3.787930993285705,3.787930993285705,3.202020262359323,3.2671214546844767,3.202020262359323,3.33222264700963,3.202020262359323,3.202020262359323,3.071817877709016,3.33222264700963,3.33222264700963,3.33222264700963,3.4624250316599374,3.6577286086353977,3.5926274163102443,3.787930993285705,3.6577286086353977,3.1369190700341694,3.202020262359323,3.202020262359323,3.2671214546844767,3.2671214546844767,3.787930993285705,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.1369190700341694,3.071817877709016,3.6577286086353977,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.071817877709016,3.202020262359323,3.202020262359323,3.1369190700341694,3.787930993285705,3.6577286086353977,3.7228298009605516,3.5926274163102443,3.33222264700963,3.397323839334784,3.33222264700963,3.202020262359323,3.202020262359323,3.202020262359323],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(44,160,44,1.000000)","dash":"solid"},"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,4.7,4.7,4.7,5.2,5.2,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.6,5.0,4.6,4.6,4.6,5.4,5.4,4.6,4.6,4.6,4.6,5.4,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.6,5.0,5.6,5.3,4.7,4.7,5.7],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"marker":{"autocolorscale":false,"color":"rgba(214,39,40,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(214,39,40,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]},{"y":[5.360007003346041,5.2331413897751125,5.021698700490232,5.2331413897751125,5.106275776204184,5.106275776204184,5.486872616916969,5.360007003346041,5.486872616916969,5.444584079059993,5.402295541203017,5.1908528519181365,4.979410162633256,5.021698700490232,5.106275776204184,5.1908528519181365,5.1908528519181365,4.894833086919303,5.106275776204184,5.021698700490232,5.106275776204184,4.894833086919303,5.106275776204184,5.063987238347208,5.14856431406116,5.021698700490232,5.063987238347208,4.894833086919303,5.106275776204184,5.106275776204184,5.063987238347208,4.894833086919303,5.021698700490232,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.106275776204184,5.14856431406116,5.1908528519181365,5.106275776204184,5.063987238347208,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.275429927632088,5.317718465489064,5.360007003346041,5.317718465489064,5.2331413897751125,5.106275776204184,4.894833086919303,5.1908528519181365,5.14856431406116,4.979410162633256,5.021698700490232,5.14856431406116,5.14856431406116,5.021698700490232,5.106275776204184,5.063987238347208,5.14856431406116,5.1908528519181365,5.106275776204184,5.14856431406116,5.444584079059993,5.106275776204184,5.021698700490232,5.14856431406116],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(214,39,40,1.000000)","dash":"solid"},"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]}]},"evals":[],"jsHooks":[]}</script></div>
 ```

### 2024-04-15 docs/projects/datavis/ggplot/representing.qmd
ggplotly - rerendered
ggplot - rerendered

@@
   html: {toc: true, toc-depth: 4, theme: cosmo, output-file: representing.html}
+fontsize: 0.9em
 code-block-background: true

### 2024-04-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

@@
 ```clojure
-"<?xml version=\"1.0\" encoding=\"UTF-8\"?>\n<svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\">\n<defs>\n<g>\n<symbol overflow=\"visible\" id=\"glyph0-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-1\">\n<path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-2\">\n<path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-3\">\n<path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-4\">\n<path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-5\">\n<path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-6\">\n<path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-7\">\n<path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-8\">\n<path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-1\">\n<path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-2\">\n<path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-3\">\n<path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-4\">\n<path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-5\">\n<path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-6\">\n<path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-1\">\n<path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-2\">\n<path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-3\">\n<path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/>\n</symbol>\n</g>\n<clipPath id=\"clip1\">\n  <path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip2\">\n  <path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/>\n</clipPath>\n<clipPath id=\"clip3\">\n  <path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/>\n</clipPath>\n<clipPath id=\"clip4\">\n  <path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/>\n</clipPath>\n<clipPath id=\"clip5\">\n  <path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/>\n</clipPath>\n<clipPath id=\"clip6\">\n  <path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip7\">\n  <path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip8\">\n  <path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip9\">\n  <path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip10\">\n  <path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip11\">\n  <path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/>\n</clipPath>\n<clipPath id=\"clip12\">\n  <path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/>\n</clipPath>\n<clipPath id=\"clip13\">\n  <path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/>\n</clipPath>\n<clipPath id=\"clip14\">\n  <path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip15\">\n  <path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip16\">\n  <path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip17\">\n  <path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip18\">\n  <path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip19\">\n  <path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip20\">\n  <path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/>\n</clipPath>\n<image id=\"image460\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/>\n<pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\">\n  <use xlink:href=\"#image460\"/>\n</pattern>\n</defs>\n<g id=\"surface456\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/>\n<g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\">\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/>\n</g>\n<g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/>\n</g>\n<g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/>\n</g>\n<g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/>\n</g>\n<g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/>\n</g>\n<g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/>\n</g>\n<g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/>\n</g>\n<g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/>\n</g>\n<g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/>\n</g>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/>\n</g>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/>\n  <use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/>\n  <use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/>\n</g>\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/>\n<g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/>\n</g>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/>\n</g>\n</svg>\n"
+"<?xml version=\"1.0\" encoding=\"UTF-8\"?>\n<svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\">\n<defs>\n<g>\n<symbol overflow=\"visible\" id=\"glyph0-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-1\">\n<path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-2\">\n<path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-3\">\n<path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-4\">\n<path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-5\">\n<path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-6\">\n<path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-7\">\n<path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-8\">\n<path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-1\">\n<path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-2\">\n<path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-3\">\n<path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-4\">\n<path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-5\">\n<path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-6\">\n<path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-1\">\n<path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-2\">\n<path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-3\">\n<path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/>\n</symbol>\n</g>\n<clipPath id=\"clip1\">\n  <path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip2\">\n  <path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/>\n</clipPath>\n<clipPath id=\"clip3\">\n  <path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/>\n</clipPath>\n<clipPath id=\"clip4\">\n  <path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/>\n</clipPath>\n<clipPath id=\"clip5\">\n  <path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/>\n</clipPath>\n<clipPath id=\"clip6\">\n  <path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip7\">\n  <path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip8\">\n  <path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip9\">\n  <path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip10\">\n  <path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip11\">\n  <path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/>\n</clipPath>\n<clipPath id=\"clip12\">\n  <path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/>\n</clipPath>\n<clipPath id=\"clip13\">\n  <path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/>\n</clipPath>\n<clipPath id=\"clip14\">\n  <path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip15\">\n  <path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip16\">\n  <path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip17\">\n  <path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip18\">\n  <path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip19\">\n  <path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip20\">\n  <path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/>\n</clipPath>\n<image id=\"image217\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/>\n<pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\">\n  <use xlink:href=\"#image217\"/>\n</pattern>\n</defs>\n<g id=\"surface213\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/>\n<g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\">\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/>\n</g>\n<g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/>\n</g>\n<g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/>\n</g>\n<g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/>\n</g>\n<g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/>\n</g>\n<g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/>\n</g>\n<g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/>\n</g>\n<g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/>\n</g>\n<g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/>\n</g>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/>\n</g>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/>\n  <use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/>\n  <use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/>\n</g>\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/>\n<g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/>\n</g>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/>\n</g>\n</svg>\n"
 
@@
    :stat_params {:na.rm [false]},
-   :constructor [[$ .MEM x06c5570df1b44c78]],
+   :constructor [[$ .MEM x7d06b286781f4e75]],
    :position {:compute_layer :ggproto-method, :super :ggproto-method},
@@
 </clipPath>
-<image id="image487" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
+<image id="image244" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
 <pattern id="pattern0" patternUnits="userSpaceOnUse" width="1" height="300"  patternTransform="matrix(17.28,0,0,0.288,450.281644,203.20411)">
-  <use xlink:href="#image487"/>
+  <use xlink:href="#image244"/>
 </pattern>
 </defs>
-<g id="surface483">
+<g id="surface240">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>

### 2024-04-15 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

@@
      :breaks
-     "function (x, n = n_default) \n{\n    x <- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng <- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n<bytecode: 0x5b75b232cda8>\n<environment: 0x5b75bd6e2898>\n",
+     "function (x, n = n_default) \n{\n    x <- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng <- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n<bytecode: 0x5b75b232cda8>\n<environment: 0x5b75bd974a08>\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75bd6e2710>\n",
+     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75bd974b90>\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75bd6e2198>\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75bd974ce0>\n",
      :domain [##-Inf ##Inf]},
@@
      :transform
-     "function (x) \nlog(x, base)\n<bytecode: 0x5b75b7b00b30>\n<environment: 0x5b75b582d0a0>\n",
+     "function (x) \nlog(x, base)\n<bytecode: 0x5b75b7b00b30>\n<environment: 0x5b75bbf72268>\n",
      :inverse
-     "function (x) \nbase^x\n<bytecode: 0x5b75b7b00f90>\n<environment: 0x5b75b582d0a0>\n",
+     "function (x) \nbase^x\n<bytecode: 0x5b75b7b00f90>\n<environment: 0x5b75bbf72268>\n",
      :breaks
-     "function (x, n = n_default) \n{\n    raw_rng <- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng <- log(raw_rng, base = base)\n    min <- floor(rng[1])\n    max <- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by <- floor((max - min)/n) + 1\n    breaks <- base^seq(min, max, by = by)\n    relevant_breaks <- base^rng[1] <= breaks & breaks <= base^rng[2]\n    if (sum(relevant_breaks) >= (n - 2)) {\n        return(breaks)\n    }\n    while (by > 1) {\n        by <- by - 1\n        breaks <- base^seq(min, max, by = by)\n        relevant_breaks <- base^rng[1] <= breaks & breaks <= \n            base^rng[2]\n        if (sum(relevant_breaks) >= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n<bytecode: 0x5b75b7a46af8>\n<environment: 0x5b75b58310d8>\n",
+     "function (x, n = n_default) \n{\n    raw_rng <- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng <- log(raw_rng, base = base)\n    min <- floor(rng[1])\n    max <- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by <- floor((max - min)/n) + 1\n    breaks <- base^seq(min, max, by = by)\n    relevant_breaks <- base^rng[1] <= breaks & breaks <= base^rng[2]\n    if (sum(relevant_breaks) >= (n - 2)) {\n        return(breaks)\n    }\n    while (by > 1) {\n        by <- by - 1\n        breaks <- base^seq(min, max, by = by)\n        relevant_breaks <- base^rng[1] <= breaks & breaks <= \n            base^rng[2]\n        if (sum(relevant_breaks) >= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n<bytecode: 0x5b75b7a46af8>\n<environment: 0x5b75bbf8dcc8>\n",
      :minor_breaks
-     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75b5830ce8>\n",
+     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75bbfa2f60>\n",
      :format
-     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75b5830b98>\n",
+     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75bbfa2e10>\n",
      :domain [1.0E-100 ##Inf]},

### 2024-04-15 docs/projects/datavis/ggplot/ggplotly.qmd
ggplot - rerendered

@@
 ```{=html}
-<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-13" style="width:100%;height:400px;"><script data-for="htmlwidget-13" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-13" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>
+<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-16" style="width:100%;height:400px;"><script data-for="htmlwidget-16" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-16" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>
 ```

### 2024-04-15 docs/projects/datavis/ggplot/ggplotly_cont.qmd
ggplot - rerendered

@@
             [clojure.math :as math]
-            [clojure2d.color :as color]))
+            [clojure2d.color :as color]
+            [tablecloth.column.api :as tcc]))
 ```
@@
                               (apply concat)))
-        xmin (-> data :hwy fun/reduce-min)
-        xmax (-> data :hwy fun/reduce-max)
-        ymin (-> data :displ fun/reduce-min)
-        ymax (-> data :displ fun/reduce-max)
+        xmin (-> data :hwy tcc/reduce-min)
+        xmax (-> data :hwy tcc/reduce-max)
+        ymin (-> data :displ tcc/reduce-min)
+        ymax (-> data :displ tcc/reduce-max)
         xaxis (axis {:minval xmin
@@
 ```{=html}
-<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-14" style="width:100%;height:400px;"><script data-for="htmlwidget-14" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-14" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895},"title":{"text":"factor(cyl)","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}}},"xaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":true,"barmode":"relative","yaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":31.4155251141553},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"data":[{"y":[1.8,1.8,2.0,2.0,1.8,1.8,2.0,2.0,2.4,2.4,2.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.0,2.0,2.0,2.0,2.4,2.4,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,2.2,2.2,2.4,2.4,2.2,2.2,2.4,2.4,1.8,1.8,1.8,1.8,1.8,2.7,2.7,2.7,2.0,2.0,2.0,2.0,1.9,2.0,2.0,2.0,2.0,1.9,1.9,2.0,2.0,1.8,1.8,2.0,2.0],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"marker":{"autocolorscale":false,"color":"rgba(31,119,180,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(31,119,180,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.1377007978924745,2.1377007978924745,2.0569213765537713,2.0973110872231233,2.2588699299005293,2.299259640569881,2.178090508561826,2.2184802192311777,2.2184802192311777,2.0973110872231233,2.3396493512392325,1.9761419552150683,2.01653166588442,2.01653166588442,2.1377007978924745,2.01653166588442,1.9357522445457167,1.8549728232070137,1.8549728232070137,2.1377007978924745,2.2588699299005293,2.2184802192311777,2.0973110872231233,2.0569213765537713,2.2588699299005293,2.1377007978924745,2.178090508561826,2.2184802192311777,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.01653166588442,2.299259640569881,2.3396493512392325,2.2184802192311777,2.299259640569881,2.2588699299005293,2.380039061908584,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.299259640569881,2.2184802192311777,2.299259640569881,2.2184802192311777,2.5012081939166384,2.5012081939166384,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.0569213765537713,2.2184802192311777,2.1377007978924745,2.0569213765537713,2.0569213765537713,2.0973110872231233,1.9761419552150683,1.895362533876365,1.8145831125376621,1.895362533876365,2.5012081939166384,2.5012081939166384,2.4204287725779356,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,1.6530242698602557,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,2.178090508561826,2.1377007978924745],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(31,119,180,1.000000)","dash":"solid"},"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"marker":{"autocolorscale":false,"color":"rgba(255,127,14,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(255,127,14,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(255,127,14,1.000000)","dash":"solid"},"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.8,2.8,3.1,2.8,2.8,3.1,3.1,2.8,3.1,3.1,3.5,3.6,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,3.9,4.0,4.0,4.0,4.0,4.2,4.2,3.8,3.8,4.0,4.0,2.5,2.5,3.3,2.7,2.7,2.7,3.0,3.7,4.0,4.0,4.0,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,3.1,3.8,3.8,3.8,3.4,3.4,4.0,3.0,3.0,3.5,3.0,3.0,3.3,3.4,3.4,4.0,4.0,2.8,2.8,2.8,2.8,2.8,3.6],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"marker":{"autocolorscale":false,"color":"rgba(44,160,44,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(44,160,44,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[3.202020262359323,3.202020262359323,3.1369190700341694,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.33222264700963,3.2671214546844767,3.202020262359323,3.0067166853838625,3.202020262359323,3.33222264700963,3.4624250316599374,3.4624250316599374,3.33222264700963,3.33222264700963,3.787930993285705,3.4624250316599374,3.527526223985091,3.397323839334784,3.397323839334784,3.6577286086353977,3.7228298009605516,3.787930993285705,3.787930993285705,3.787930993285705,3.787930993285705,3.6577286086353977,3.787930993285705,3.6577286086353977,3.787930993285705,3.787930993285705,3.202020262359323,3.2671214546844767,3.202020262359323,3.33222264700963,3.202020262359323,3.202020262359323,3.071817877709016,3.33222264700963,3.33222264700963,3.33222264700963,3.4624250316599374,3.6577286086353977,3.5926274163102443,3.787930993285705,3.6577286086353977,3.1369190700341694,3.202020262359323,3.202020262359323,3.2671214546844767,3.2671214546844767,3.787930993285705,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.1369190700341694,3.071817877709016,3.6577286086353977,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.071817877709016,3.202020262359323,3.202020262359323,3.1369190700341694,3.787930993285705,3.6577286086353977,3.7228298009605516,3.5926274163102443,3.33222264700963,3.397323839334784,3.33222264700963,3.202020262359323,3.202020262359323,3.202020262359323],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(44,160,44,1.000000)","dash":"solid"},"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,4.7,4.7,4.7,5.2,5.2,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.6,5.0,4.6,4.6,4.6,5.4,5.4,4.6,4.6,4.6,4.6,5.4,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.6,5.0,5.6,5.3,4.7,4.7,5.7],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"marker":{"autocolorscale":false,"color":"rgba(214,39,40,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(214,39,40,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]},{"y":[5.360007003346041,5.2331413897751125,5.021698700490232,5.2331413897751125,5.106275776204184,5.106275776204184,5.486872616916969,5.360007003346041,5.486872616916969,5.444584079059993,5.402295541203017,5.1908528519181365,4.979410162633256,5.021698700490232,5.106275776204184,5.1908528519181365,5.1908528519181365,4.894833086919303,5.106275776204184,5.021698700490232,5.106275776204184,4.894833086919303,5.106275776204184,5.063987238347208,5.14856431406116,5.021698700490232,5.063987238347208,4.894833086919303,5.106275776204184,5.106275776204184,5.063987238347208,4.894833086919303,5.021698700490232,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.106275776204184,5.14856431406116,5.1908528519181365,5.106275776204184,5.063987238347208,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.275429927632088,5.317718465489064,5.360007003346041,5.317718465489064,5.2331413897751125,5.106275776204184,4.894833086919303,5.1908528519181365,5.14856431406116,4.979410162633256,5.021698700490232,5.14856431406116,5.14856431406116,5.021698700490232,5.106275776204184,5.063987238347208,5.14856431406116,5.1908528519181365,5.106275776204184,5.14856431406116,5.444584079059993,5.106275776204184,5.021698700490232,5.14856431406116],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(214,39,40,1.000000)","dash":"solid"},"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]}]},"evals":[],"jsHooks":[]}</script></div>
+<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-17" style="width:100%;height:400px;"><script data-for="htmlwidget-17" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-17" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895},"title":{"text":"factor(cyl)","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}}},"xaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":true,"barmode":"relative","yaxis":{"linewidth":0,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":31.4155251141553},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"data":[{"y":[1.8,1.8,2.0,2.0,1.8,1.8,2.0,2.0,2.4,2.4,2.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.0,2.0,2.0,2.0,2.4,2.4,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,2.2,2.2,2.4,2.4,2.2,2.2,2.4,2.4,1.8,1.8,1.8,1.8,1.8,2.7,2.7,2.7,2.0,2.0,2.0,2.0,1.9,2.0,2.0,2.0,2.0,1.9,1.9,2.0,2.0,1.8,1.8,2.0,2.0],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"marker":{"autocolorscale":false,"color":"rgba(31,119,180,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(31,119,180,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.1377007978924745,2.1377007978924745,2.0569213765537713,2.0973110872231233,2.2588699299005293,2.299259640569881,2.178090508561826,2.2184802192311777,2.2184802192311777,2.0973110872231233,2.3396493512392325,1.9761419552150683,2.01653166588442,2.01653166588442,2.1377007978924745,2.01653166588442,1.9357522445457167,1.8549728232070137,1.8549728232070137,2.1377007978924745,2.2588699299005293,2.2184802192311777,2.0973110872231233,2.0569213765537713,2.2588699299005293,2.1377007978924745,2.178090508561826,2.2184802192311777,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.01653166588442,2.299259640569881,2.3396493512392325,2.2184802192311777,2.299259640569881,2.2588699299005293,2.380039061908584,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.2588699299005293,2.299259640569881,2.2184802192311777,2.299259640569881,2.2184802192311777,2.5012081939166384,2.5012081939166384,2.1377007978924745,2.2184802192311777,2.0569213765537713,2.0569213765537713,2.2184802192311777,2.1377007978924745,2.0569213765537713,2.0569213765537713,2.0973110872231233,1.9761419552150683,1.895362533876365,1.8145831125376621,1.895362533876365,2.5012081939166384,2.5012081939166384,2.4204287725779356,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,1.5318551378522012,1.6530242698602557,2.1377007978924745,2.2588699299005293,2.1377007978924745,2.1377007978924745,2.178090508561826,2.1377007978924745],"hoveron":"points","legendgroup":4,"frame":null,"hoverinfo":"text","name":4,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(31,119,180,1.000000)","dash":"solid"},"yaxis":"y","x":[29,29,31,30,26,25,28,27,27,30,24,33,32,32,29,32,34,36,36,29,26,27,30,31,26,29,28,27,29,27,31,32,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,29,27,31,31,27,29,31,31,30,33,35,37,35,20,20,22,29,26,29,29,44,29,26,29,29,44,41,29,26,29,29,28,29],"text":[":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 1.6<br \/>factor(cyl): 4",":hwy: 34<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 36<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 32<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 24<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 23<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 25<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.5<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 27<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.2<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 31<br \/>:displ: 2.4<br \/>factor(cyl): 4",":hwy: 30<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 33<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 37<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 35<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 20<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 22<br \/>:displ: 2.7<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 44<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 41<br \/>:displ: 1.9<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 26<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 1.8<br \/>factor(cyl): 4",":hwy: 28<br \/>:displ: 2.0<br \/>factor(cyl): 4",":hwy: 29<br \/>:displ: 2.0<br \/>factor(cyl): 4"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"marker":{"autocolorscale":false,"color":"rgba(255,127,14,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(255,127,14,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.5,2.5,2.5,2.5],"hoveron":"points","legendgroup":5,"frame":null,"hoverinfo":"text","name":5,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(255,127,14,1.000000)","dash":"solid"},"yaxis":"y","x":[29,29,28,29],"text":[":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 28<br \/>:displ: 2.5<br \/>factor(cyl): 5",":hwy: 29<br \/>:displ: 2.5<br \/>factor(cyl): 5"]},{"y":[2.8,2.8,3.1,2.8,2.8,3.1,3.1,2.8,3.1,3.1,3.5,3.6,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,3.9,4.0,4.0,4.0,4.0,4.2,4.2,3.8,3.8,4.0,4.0,2.5,2.5,3.3,2.7,2.7,2.7,3.0,3.7,4.0,4.0,4.0,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,3.1,3.8,3.8,3.8,3.4,3.4,4.0,3.0,3.0,3.5,3.0,3.0,3.3,3.4,3.4,4.0,4.0,2.8,2.8,2.8,2.8,2.8,3.6],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"marker":{"autocolorscale":false,"color":"rgba(44,160,44,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(44,160,44,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[3.202020262359323,3.202020262359323,3.1369190700341694,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.2671214546844767,3.33222264700963,3.2671214546844767,3.202020262359323,3.0067166853838625,3.202020262359323,3.33222264700963,3.4624250316599374,3.4624250316599374,3.33222264700963,3.33222264700963,3.787930993285705,3.4624250316599374,3.527526223985091,3.397323839334784,3.397323839334784,3.6577286086353977,3.7228298009605516,3.787930993285705,3.787930993285705,3.787930993285705,3.787930993285705,3.6577286086353977,3.787930993285705,3.6577286086353977,3.787930993285705,3.787930993285705,3.202020262359323,3.2671214546844767,3.202020262359323,3.33222264700963,3.202020262359323,3.202020262359323,3.071817877709016,3.33222264700963,3.33222264700963,3.33222264700963,3.4624250316599374,3.6577286086353977,3.5926274163102443,3.787930993285705,3.6577286086353977,3.1369190700341694,3.202020262359323,3.202020262359323,3.2671214546844767,3.2671214546844767,3.787930993285705,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.1369190700341694,3.071817877709016,3.6577286086353977,3.787930993285705,3.5926274163102443,3.202020262359323,3.202020262359323,3.071817877709016,3.202020262359323,3.202020262359323,3.1369190700341694,3.787930993285705,3.6577286086353977,3.7228298009605516,3.5926274163102443,3.33222264700963,3.397323839334784,3.33222264700963,3.202020262359323,3.202020262359323,3.202020262359323],"hoveron":"points","legendgroup":6,"frame":null,"hoverinfo":"text","name":6,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(44,160,44,1.000000)","dash":"solid"},"yaxis":"y","x":[26,26,27,25,25,25,25,24,25,26,29,26,24,22,22,24,24,17,22,21,23,23,19,18,17,17,17,17,19,17,19,17,17,26,25,26,24,26,26,28,24,24,24,22,19,20,17,19,27,26,26,25,25,17,17,20,26,26,27,28,19,17,20,26,26,28,26,26,27,17,19,18,20,24,23,24,26,26,26],"text":[":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 29<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 21<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.9<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.2<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.5<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.7<br \/>factor(cyl): 6",":hwy: 22<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.7<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 25<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.1<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.8<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 28<br \/>:displ: 3.5<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.0<br \/>factor(cyl): 6",":hwy: 27<br \/>:displ: 3.3<br \/>factor(cyl): 6",":hwy: 17<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 19<br \/>:displ: 3.4<br \/>factor(cyl): 6",":hwy: 18<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 20<br \/>:displ: 4.0<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 23<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 24<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 2.8<br \/>factor(cyl): 6",":hwy: 26<br \/>:displ: 3.6<br \/>factor(cyl): 6"]},{"y":[4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,4.7,4.7,4.7,5.2,5.2,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.6,5.0,4.6,4.6,4.6,5.4,5.4,4.6,4.6,4.6,4.6,5.4,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.6,5.0,5.6,5.3,4.7,4.7,5.7],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"marker":{"autocolorscale":false,"color":"rgba(214,39,40,1.000000)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(214,39,40,1.000000)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":true,"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]},{"y":[5.360007003346041,5.2331413897751125,5.021698700490232,5.2331413897751125,5.106275776204184,5.106275776204184,5.486872616916969,5.360007003346041,5.486872616916969,5.444584079059993,5.402295541203017,5.1908528519181365,4.979410162633256,5.021698700490232,5.106275776204184,5.1908528519181365,5.1908528519181365,4.894833086919303,5.106275776204184,5.021698700490232,5.106275776204184,4.894833086919303,5.106275776204184,5.063987238347208,5.14856431406116,5.021698700490232,5.063987238347208,4.894833086919303,5.106275776204184,5.106275776204184,5.063987238347208,4.894833086919303,5.021698700490232,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.106275776204184,5.14856431406116,5.1908528519181365,5.106275776204184,5.063987238347208,5.063987238347208,5.106275776204184,5.021698700490232,5.106275776204184,5.275429927632088,5.317718465489064,5.360007003346041,5.317718465489064,5.2331413897751125,5.106275776204184,4.894833086919303,5.1908528519181365,5.14856431406116,4.979410162633256,5.021698700490232,5.14856431406116,5.14856431406116,5.021698700490232,5.106275776204184,5.063987238347208,5.14856431406116,5.1908528519181365,5.106275776204184,5.14856431406116,5.444584079059993,5.106275776204184,5.021698700490232,5.14856431406116],"hoveron":"points","legendgroup":8,"frame":null,"hoverinfo":"text","name":8,"mode":"lines","type":"scatter","xaxis":"x","showlegend":false,"line":{"width":3.77952755905512,"color":"rgba(214,39,40,1.000000)","dash":"solid"},"yaxis":"y","x":[23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,19,19,12,17,15,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,19,17,16,16,17,15,17,21,22,23,22,20,17,12,19,18,14,15,18,18,15,17,16,18,19,17,18,25,17,15,18],"text":[":hwy: 23<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.0<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 26<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 6.2<br \/>factor(cyl): 8",":hwy: 24<br \/>:displ: 7.0<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 6.5<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.2<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.9<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 21<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 23<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 22<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 20<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 12<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8",":hwy: 14<br \/>:displ: 6.1<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.2<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 4.4<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 16<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.4<br \/>factor(cyl): 8",":hwy: 19<br \/>:displ: 4.6<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 5.0<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.6<br \/>factor(cyl): 8",":hwy: 25<br \/>:displ: 5.3<br \/>factor(cyl): 8",":hwy: 17<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 15<br \/>:displ: 4.7<br \/>factor(cyl): 8",":hwy: 18<br \/>:displ: 5.7<br \/>factor(cyl): 8"]}]},"evals":[],"jsHooks":[]}</script></div>
 ```

### 2024-04-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

--- 2024-04-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
@@
 ```clojure
-"<?xml version=\"1.0\" encoding=\"UTF-8\"?>\n<svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\">\n<defs>\n<g>\n<symbol overflow=\"visible\" id=\"glyph0-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-1\">\n<path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-2\">\n<path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-3\">\n<path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-4\">\n<path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-5\">\n<path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-6\">\n<path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-7\">\n<path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-8\">\n<path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-1\">\n<path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-2\">\n<path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-3\">\n<path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-4\">\n<path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-5\">\n<path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-6\">\n<path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-1\">\n<path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-2\">\n<path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-3\">\n<path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/>\n</symbol>\n</g>\n<clipPath id=\"clip1\">\n  <path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip2\">\n  <path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/>\n</clipPath>\n<clipPath id=\"clip3\">\n  <path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/>\n</clipPath>\n<clipPath id=\"clip4\">\n  <path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/>\n</clipPath>\n<clipPath id=\"clip5\">\n  <path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/>\n</clipPath>\n<clipPath id=\"clip6\">\n  <path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip7\">\n  <path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip8\">\n  <path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip9\">\n  <path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip10\">\n  <path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip11\">\n  <path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/>\n</clipPath>\n<clipPath id=\"clip12\">\n  <path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/>\n</clipPath>\n<clipPath id=\"clip13\">\n  <path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/>\n</clipPath>\n<clipPath id=\"clip14\">\n  <path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip15\">\n  <path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip16\">\n  <path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip17\">\n  <path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip18\">\n  <path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip19\">\n  <path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip20\">\n  <path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/>\n</clipPath>\n<image id=\"image460\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/>\n<pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\">\n  <use xlink:href=\"#image460\"/>\n</pattern>\n</defs>\n<g id=\"surface456\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/>\n<g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\">\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/>\n</g>\n<g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/>\n</g>\n<g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/>\n</g>\n<g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/>\n</g>\n<g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/>\n</g>\n<g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/>\n</g>\n<g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/>\n</g>\n<g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/>\n</g>\n<g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/>\n</g>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/>\n</g>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/>\n  <use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/>\n  <use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/>\n</g>\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/>\n<g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/>\n</g>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/>\n</g>\n</svg>\n"
+"<?xml version=\"1.0\" encoding=\"UTF-8\"?>\n<svg xmlns=\"http://www.w3.org/2000/svg\" xmlns:xlink=\"http://www.w3.org/1999/xlink\" width=\"504pt\" height=\"504pt\" viewBox=\"0 0 504 504\" version=\"1.1\">\n<defs>\n<g>\n<symbol overflow=\"visible\" id=\"glyph0-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-1\">\n<path style=\"stroke:none;\" d=\"M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-2\">\n<path style=\"stroke:none;\" d=\"M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-3\">\n<path style=\"stroke:none;\" d=\"M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-4\">\n<path style=\"stroke:none;\" d=\"M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-5\">\n<path style=\"stroke:none;\" d=\"M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-6\">\n<path style=\"stroke:none;\" d=\"M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-7\">\n<path style=\"stroke:none;\" d=\"M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph0-8\">\n<path style=\"stroke:none;\" d=\"M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-1\">\n<path style=\"stroke:none;\" d=\"M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-2\">\n<path style=\"stroke:none;\" d=\"M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-3\">\n<path style=\"stroke:none;\" d=\"M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-4\">\n<path style=\"stroke:none;\" d=\"M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-5\">\n<path style=\"stroke:none;\" d=\"M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph1-6\">\n<path style=\"stroke:none;\" d=\"M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-0\">\n<path style=\"stroke:none;\" d=\"\"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-1\">\n<path style=\"stroke:none;\" d=\"M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-2\">\n<path style=\"stroke:none;\" d=\"M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 \"/>\n</symbol>\n<symbol overflow=\"visible\" id=\"glyph2-3\">\n<path style=\"stroke:none;\" d=\"M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 \"/>\n</symbol>\n</g>\n<clipPath id=\"clip1\">\n  <path d=\"M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip2\">\n  <path d=\"M 35.152344 408 L 433.84375 408 L 433.84375 410 L 35.152344 410 Z M 35.152344 408 \"/>\n</clipPath>\n<clipPath id=\"clip3\">\n  <path d=\"M 35.152344 276 L 433.84375 276 L 433.84375 278 L 35.152344 278 Z M 35.152344 276 \"/>\n</clipPath>\n<clipPath id=\"clip4\">\n  <path d=\"M 35.152344 145 L 433.84375 145 L 433.84375 146 L 35.152344 146 Z M 35.152344 145 \"/>\n</clipPath>\n<clipPath id=\"clip5\">\n  <path d=\"M 35.152344 13 L 433.84375 13 L 433.84375 14 L 35.152344 14 Z M 35.152344 13 \"/>\n</clipPath>\n<clipPath id=\"clip6\">\n  <path d=\"M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip7\">\n  <path d=\"M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip8\">\n  <path d=\"M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip9\">\n  <path d=\"M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip10\">\n  <path d=\"M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip11\">\n  <path d=\"M 35.152344 342 L 433.84375 342 L 433.84375 344 L 35.152344 344 Z M 35.152344 342 \"/>\n</clipPath>\n<clipPath id=\"clip12\">\n  <path d=\"M 35.152344 210 L 433.84375 210 L 433.84375 212 L 35.152344 212 Z M 35.152344 210 \"/>\n</clipPath>\n<clipPath id=\"clip13\">\n  <path d=\"M 35.152344 78 L 433.84375 78 L 433.84375 80 L 35.152344 80 Z M 35.152344 78 \"/>\n</clipPath>\n<clipPath id=\"clip14\">\n  <path d=\"M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip15\">\n  <path d=\"M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip16\">\n  <path d=\"M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip17\">\n  <path d=\"M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip18\">\n  <path d=\"M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip19\">\n  <path d=\"M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 \"/>\n</clipPath>\n<clipPath id=\"clip20\">\n  <path d=\"M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 \"/>\n</clipPath>\n<image id=\"image459\" width=\"1\" height=\"300\" xlink:href=\"data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg==\"/>\n<pattern id=\"pattern0\" patternUnits=\"userSpaceOnUse\" width=\"1\" height=\"300\"  patternTransform=\"matrix(17.28,0,0,0.288,450.281644,203.20411)\">\n  <use xlink:href=\"#image459\"/>\n</pattern>\n</defs>\n<g id=\"surface455\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;\"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 \"/>\n<g clip-path=\"url(#clip1)\" clip-rule=\"nonzero\">\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;\" d=\"M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 \"/>\n</g>\n<g clip-path=\"url(#clip2)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 409.164062 L 433.84375 409.164062 \"/>\n</g>\n<g clip-path=\"url(#clip3)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 277.242188 L 433.84375 277.242188 \"/>\n</g>\n<g clip-path=\"url(#clip4)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 145.316406 L 433.84375 145.316406 \"/>\n</g>\n<g clip-path=\"url(#clip5)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 13.394531 L 433.84375 13.394531 \"/>\n</g>\n<g clip-path=\"url(#clip6)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 102.0625 469.847656 L 102.0625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip7)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 171.765625 469.847656 L 171.765625 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip8)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 241.46875 469.847656 L 241.46875 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip9)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 311.167969 469.847656 L 311.167969 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip10)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 380.871094 469.847656 L 380.871094 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip11)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 343.203125 L 433.84375 343.203125 \"/>\n</g>\n<g clip-path=\"url(#clip12)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 211.28125 L 433.84375 211.28125 \"/>\n</g>\n<g clip-path=\"url(#clip13)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 35.152344 79.355469 L 433.84375 79.355469 \"/>\n</g>\n<g clip-path=\"url(#clip14)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 469.847656 L 67.214844 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip15)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 469.847656 L 136.914062 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip16)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 469.847656 L 206.617188 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip17)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 469.847656 L 276.316406 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip18)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 469.847656 L 346.019531 5.480469 \"/>\n</g>\n<g clip-path=\"url(#clip19)\" clip-rule=\"nonzero\">\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 469.847656 L 415.722656 5.480469 \"/>\n</g>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 198.085938 C 208.570312 200.695312 204.660156 200.695312 204.660156 198.085938 C 204.660156 195.480469 208.570312 195.480469 208.570312 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 277.242188 C 166.75 279.847656 162.839844 279.847656 162.839844 277.242188 C 162.839844 274.636719 166.75 274.636719 166.75 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 382.78125 C 97.046875 385.386719 93.140625 385.386719 93.140625 382.78125 C 93.140625 380.171875 97.046875 380.171875 97.046875 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 277.242188 C 138.871094 279.847656 134.960938 279.847656 134.960938 277.242188 C 134.960938 274.636719 138.871094 274.636719 138.871094 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 290.433594 C 138.871094 293.039062 134.960938 293.039062 134.960938 290.433594 C 134.960938 287.828125 138.871094 287.828125 138.871094 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 211.28125 C 236.453125 213.886719 232.542969 213.886719 232.542969 211.28125 C 232.542969 208.671875 236.453125 208.671875 236.453125 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 316.816406 C 152.808594 319.425781 148.898438 319.425781 148.898438 316.816406 C 148.898438 314.210938 152.808594 314.210938 152.808594 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 369.585938 C 124.929688 372.195312 121.019531 372.195312 121.019531 369.585938 C 121.019531 366.980469 124.929688 366.980469 124.929688 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 395.972656 C 97.046875 398.578125 93.140625 398.578125 93.140625 395.972656 C 93.140625 393.367188 97.046875 393.367188 97.046875 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 395.972656 C 110.988281 398.578125 107.078125 398.578125 107.078125 395.972656 C 107.078125 393.367188 110.988281 393.367188 110.988281 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 330.011719 C 138.871094 332.617188 134.960938 332.617188 134.960938 330.011719 C 134.960938 327.402344 138.871094 327.402344 138.871094 330.011719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 303.625 C 138.871094 306.230469 134.960938 306.230469 134.960938 303.625 C 134.960938 301.019531 138.871094 301.019531 138.871094 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 316.816406 C 138.871094 319.425781 134.960938 319.425781 134.960938 316.816406 C 134.960938 314.210938 138.871094 314.210938 138.871094 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 171.703125 C 320.09375 174.308594 316.183594 174.308594 316.183594 171.703125 C 316.183594 169.097656 320.09375 169.097656 320.09375 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 184.894531 C 278.273438 187.5 274.363281 187.5 274.363281 184.894531 C 274.363281 182.289062 278.273438 182.289062 278.273438 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 224.472656 C 250.390625 227.078125 246.484375 227.078125 246.484375 224.472656 C 246.484375 221.867188 250.390625 221.867188 250.390625 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 184.894531 C 264.332031 187.5 260.421875 187.5 260.421875 184.894531 C 260.421875 182.289062 264.332031 182.289062 264.332031 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 158.511719 C 292.214844 161.117188 288.304688 161.117188 288.304688 158.511719 C 288.304688 155.902344 292.214844 155.902344 292.214844 158.511719 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 278.273438 132.125 C 278.273438 134.730469 274.363281 134.730469 274.363281 132.125 C 274.363281 129.519531 278.273438 129.519531 278.273438 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 132.125 C 264.332031 134.730469 260.421875 134.730469 260.421875 132.125 C 260.421875 129.519531 264.332031 129.519531 264.332031 132.125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 211.28125 C 222.511719 213.886719 218.601562 213.886719 218.601562 211.28125 C 218.601562 208.671875 222.511719 208.671875 222.511719 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 224.472656 C 194.632812 227.078125 190.722656 227.078125 190.722656 224.472656 C 190.722656 221.867188 194.632812 221.867188 194.632812 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 290.433594 C 152.808594 293.039062 148.898438 293.039062 148.898438 290.433594 C 148.898438 287.828125 152.808594 287.828125 152.808594 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 55.226562 448.742188 C 55.226562 451.347656 51.316406 451.347656 51.316406 448.742188 C 51.316406 446.136719 55.226562 446.136719 55.226562 448.742188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 356.394531 C 124.929688 359 121.019531 359 121.019531 356.394531 C 121.019531 353.789062 124.929688 353.789062 124.929688 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 422.355469 C 83.109375 424.964844 79.199219 424.964844 79.199219 422.355469 C 79.199219 419.75 83.109375 419.75 83.109375 422.355469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 382.78125 C 83.109375 385.386719 79.199219 385.386719 79.199219 382.78125 C 79.199219 380.171875 83.109375 380.171875 83.109375 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 395.972656 C 83.109375 398.578125 79.199219 398.578125 79.199219 395.972656 C 79.199219 393.367188 83.109375 393.367188 83.109375 395.972656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 356.394531 C 110.988281 359 107.078125 359 107.078125 356.394531 C 107.078125 353.789062 110.988281 353.789062 110.988281 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 382.78125 C 110.988281 385.386719 107.078125 385.386719 107.078125 382.78125 C 107.078125 380.171875 110.988281 380.171875 110.988281 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 198.085938 C 250.390625 200.695312 246.484375 200.695312 246.484375 198.085938 C 246.484375 195.480469 250.390625 195.480469 250.390625 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 250.390625 184.894531 C 250.390625 187.5 246.484375 187.5 246.484375 184.894531 C 246.484375 182.289062 250.390625 182.289062 250.390625 184.894531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 250.855469 C 194.632812 253.464844 190.722656 253.464844 190.722656 250.855469 C 190.722656 248.25 194.632812 248.25 194.632812 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 343.203125 C 124.929688 345.808594 121.019531 345.808594 121.019531 343.203125 C 121.019531 340.597656 124.929688 340.597656 124.929688 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 97.046875 369.585938 C 97.046875 372.195312 93.140625 372.195312 93.140625 369.585938 C 93.140625 366.980469 97.046875 366.980469 97.046875 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 250.855469 C 166.75 253.464844 162.839844 253.464844 162.839844 250.855469 C 162.839844 248.25 166.75 248.25 166.75 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 237.664062 C 180.691406 240.269531 176.78125 240.269531 176.78125 237.664062 C 176.78125 235.058594 180.691406 235.058594 180.691406 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 277.242188 C 152.808594 279.847656 148.898438 279.847656 148.898438 277.242188 C 148.898438 274.636719 152.808594 274.636719 152.808594 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 277.242188 C 180.691406 279.847656 176.78125 279.847656 176.78125 277.242188 C 176.78125 274.636719 180.691406 274.636719 180.691406 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 290.433594 C 180.691406 293.039062 176.78125 293.039062 176.78125 290.433594 C 176.78125 287.828125 180.691406 287.828125 180.691406 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 264.050781 C 208.570312 266.65625 204.660156 266.65625 204.660156 264.050781 C 204.660156 261.441406 208.570312 261.441406 208.570312 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 303.625 C 180.691406 306.230469 176.78125 306.230469 176.78125 303.625 C 176.78125 301.019531 180.691406 301.019531 180.691406 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 264.050781 C 222.511719 266.65625 218.601562 266.65625 218.601562 264.050781 C 218.601562 261.441406 222.511719 261.441406 222.511719 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 277.242188 C 208.570312 279.847656 204.660156 279.847656 204.660156 277.242188 C 204.660156 274.636719 208.570312 274.636719 208.570312 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 277.242188 C 194.632812 279.847656 190.722656 279.847656 190.722656 277.242188 C 190.722656 274.636719 194.632812 274.636719 194.632812 277.242188 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 250.855469 C 208.570312 253.464844 204.660156 253.464844 204.660156 250.855469 C 204.660156 248.25 208.570312 248.25 208.570312 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 124.929688 382.78125 C 124.929688 385.386719 121.019531 385.386719 121.019531 382.78125 C 121.019531 380.171875 124.929688 380.171875 124.929688 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 250.855469 C 222.511719 253.464844 218.601562 253.464844 218.601562 250.855469 C 218.601562 248.25 222.511719 248.25 222.511719 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 198.085938 C 222.511719 200.695312 218.601562 200.695312 218.601562 198.085938 C 218.601562 195.480469 222.511719 195.480469 222.511719 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 198.085938 C 236.453125 200.695312 232.542969 200.695312 232.542969 198.085938 C 232.542969 195.480469 236.453125 195.480469 236.453125 198.085938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 250.855469 C 180.691406 253.464844 176.78125 253.464844 176.78125 250.855469 C 176.78125 248.25 180.691406 248.25 180.691406 250.855469 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 211.28125 C 264.332031 213.886719 260.421875 213.886719 260.421875 211.28125 C 260.421875 208.671875 264.332031 208.671875 264.332031 211.28125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 264.332031 171.703125 C 264.332031 174.308594 260.421875 174.308594 260.421875 171.703125 C 260.421875 169.097656 264.332031 169.097656 264.332031 171.703125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 320.09375 118.933594 C 320.09375 121.539062 316.183594 121.539062 316.183594 118.933594 C 316.183594 116.328125 320.09375 116.328125 320.09375 118.933594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 292.214844 145.316406 C 292.214844 147.925781 288.304688 147.925781 288.304688 145.316406 C 288.304688 142.710938 292.214844 142.710938 292.214844 145.316406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 83.109375 409.164062 C 83.109375 411.769531 79.199219 411.769531 79.199219 409.164062 C 79.199219 406.558594 83.109375 406.558594 83.109375 409.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 110.988281 369.585938 C 110.988281 372.195312 107.078125 372.195312 107.078125 369.585938 C 107.078125 366.980469 110.988281 366.980469 110.988281 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 343.203125 C 138.871094 345.808594 134.960938 345.808594 134.960938 343.203125 C 134.960938 340.597656 138.871094 340.597656 138.871094 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 316.816406 C 166.75 319.425781 162.839844 319.425781 162.839844 316.816406 C 162.839844 314.210938 166.75 314.210938 166.75 316.816406 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 382.78125 C 138.871094 385.386719 134.960938 385.386719 134.960938 382.78125 C 134.960938 380.171875 138.871094 380.171875 138.871094 382.78125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 356.394531 C 138.871094 359 134.960938 359 134.960938 356.394531 C 134.960938 353.789062 138.871094 353.789062 138.871094 356.394531 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 138.871094 369.585938 C 138.871094 372.195312 134.960938 372.195312 134.960938 369.585938 C 134.960938 366.980469 138.871094 366.980469 138.871094 369.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 343.203125 C 152.808594 345.808594 148.898438 345.808594 148.898438 343.203125 C 148.898438 340.597656 152.808594 340.597656 152.808594 343.203125 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 389.796875 26.585938 C 389.796875 29.195312 385.886719 29.195312 385.886719 26.585938 C 385.886719 23.980469 389.796875 23.980469 389.796875 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 236.453125 224.472656 C 236.453125 227.078125 232.542969 227.078125 232.542969 224.472656 C 232.542969 221.867188 236.453125 221.867188 236.453125 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 303.625 C 152.808594 306.230469 148.898438 306.230469 148.898438 303.625 C 148.898438 301.019531 152.808594 301.019531 152.808594 303.625 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 290.433594 C 166.75 293.039062 162.839844 293.039062 162.839844 290.433594 C 162.839844 287.828125 166.75 287.828125 166.75 290.433594 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 417.675781 26.585938 C 417.675781 29.195312 413.765625 29.195312 413.765625 26.585938 C 413.765625 23.980469 417.675781 23.980469 417.675781 26.585938 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 334.035156 66.164062 C 334.035156 68.769531 330.125 68.769531 330.125 66.164062 C 330.125 63.558594 334.035156 63.558594 334.035156 66.164062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 264.050781 C 194.632812 266.65625 190.722656 266.65625 190.722656 264.050781 C 190.722656 261.441406 194.632812 261.441406 194.632812 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 237.664062 C 208.570312 240.269531 204.660156 240.269531 204.660156 237.664062 C 204.660156 235.058594 208.570312 235.058594 208.570312 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 208.570312 224.472656 C 208.570312 227.078125 204.660156 227.078125 204.660156 224.472656 C 204.660156 221.867188 208.570312 221.867188 208.570312 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 224.472656 C 180.691406 227.078125 176.78125 227.078125 176.78125 224.472656 C 176.78125 221.867188 180.691406 221.867188 180.691406 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 194.632812 237.664062 C 194.632812 240.269531 190.722656 240.269531 190.722656 237.664062 C 190.722656 235.058594 194.632812 235.058594 194.632812 237.664062 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 222.511719 224.472656 C 222.511719 227.078125 218.601562 227.078125 218.601562 224.472656 C 218.601562 221.867188 222.511719 221.867188 222.511719 224.472656 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 152.808594 264.050781 C 152.808594 266.65625 148.898438 266.65625 148.898438 264.050781 C 148.898438 261.441406 152.808594 261.441406 152.808594 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 180.691406 264.050781 C 180.691406 266.65625 176.78125 266.65625 176.78125 264.050781 C 176.78125 261.441406 180.691406 261.441406 180.691406 264.050781 \"/>\n<path style=\"fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 166.75 264.050781 C 166.75 266.65625 162.839844 266.65625 162.839844 264.050781 C 162.839844 261.441406 166.75 261.441406 166.75 264.050781 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"20.21875\" y=\"346.118164\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"346.118164\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"20.21875\" y=\"214.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"214.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-4\" x=\"20.21875\" y=\"82.270508\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"25.21875\" y=\"82.270508\"/>\n</g>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 343.203125 L 35.152344 343.203125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 211.28125 L 35.152344 211.28125 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 32.410156 79.355469 L 35.152344 79.355469 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 67.214844 472.589844 L 67.214844 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 136.914062 472.589844 L 136.914062 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 206.617188 472.589844 L 206.617188 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 276.316406 472.589844 L 276.316406 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 346.019531 472.589844 L 346.019531 469.847656 \"/>\n<path style=\"fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(20%,20%,20%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 415.722656 472.589844 L 415.722656 469.847656 \"/>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"62.214844\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"67.214844\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-5\" x=\"131.914062\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"136.914062\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"201.617188\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"206.617188\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"271.316406\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"276.316406\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"341.019531\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"346.019531\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(30.196078%,30.196078%,30.196078%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-3\" x=\"410.722656\" y=\"481.196289\"/>\n  <use xlink:href=\"#glyph0-6\" x=\"415.722656\" y=\"481.196289\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-1\" x=\"227.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-2\" x=\"233.496094\" y=\"494.538086\"/>\n  <use xlink:href=\"#glyph1-3\" x=\"236.496094\" y=\"494.538086\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph2-1\" x=\"13.499023\" y=\"247.164062\"/>\n  <use xlink:href=\"#glyph2-2\" x=\"13.499023\" y=\"241.164062\"/>\n  <use xlink:href=\"#glyph2-3\" x=\"13.499023\" y=\"233.164062\"/>\n</g>\n<path style=\" stroke:none;fill-rule:nonzero;fill:rgb(100%,100%,100%);fill-opacity:1;\" d=\"M 444.800781 295.082031 L 498.519531 295.082031 L 498.519531 180.242188 L 444.800781 180.242188 Z M 444.800781 295.082031 \"/>\n<g clip-path=\"url(#clip20)\" clip-rule=\"nonzero\">\n<rect x=\"0\" y=\"0\" width=\"504\" height=\"504\" style=\"fill:url(#pattern0);stroke:none;\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"282.805664\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"488.042969\" y=\"282.805664\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"263.672852\"/>\n  <use xlink:href=\"#glyph0-1\" x=\"488.042969\" y=\"263.672852\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"244.536133\"/>\n  <use xlink:href=\"#glyph0-4\" x=\"488.042969\" y=\"244.536133\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"225.399414\"/>\n  <use xlink:href=\"#glyph0-7\" x=\"488.042969\" y=\"225.399414\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph0-1\" x=\"473.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"478.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-2\" x=\"483.042969\" y=\"206.262695\"/>\n  <use xlink:href=\"#glyph0-8\" x=\"488.042969\" y=\"206.262695\"/>\n</g>\n<g style=\"fill:rgb(0%,0%,0%);fill-opacity:1;\">\n  <use xlink:href=\"#glyph1-3\" x=\"450.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-4\" x=\"455.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-5\" x=\"461.28125\" y=\"195.245117\"/>\n  <use xlink:href=\"#glyph1-6\" x=\"467.28125\" y=\"195.245117\"/>\n</g>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 279.890625 L 453.738281 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 260.757812 L 453.738281 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 241.621094 L 453.738281 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 222.484375 L 453.738281 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 450.28125 203.347656 L 453.738281 203.347656 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 279.890625 L 467.5625 279.890625 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 260.757812 L 467.5625 260.757812 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 241.621094 L 467.5625 241.621094 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 222.484375 L 467.5625 222.484375 \"/>\n<path style=\"fill:none;stroke-width:0.375;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;\" d=\"M 464.105469 203.347656 L 467.5625 203.347656 \"/>\n</g>\n</svg>\n"
 
@@
    :stat_params {:na.rm [false]},
-   :constructor [[$ .MEM x06c5570df1b44c78]],
+   :constructor [[$ .MEM x04d1ec48fa8b4a52]],
    :position {:compute_layer :ggproto-method, :super :ggproto-method},
@@
 </clipPath>
-<image id="image487" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
+<image id="image486" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
 <pattern id="pattern0" patternUnits="userSpaceOnUse" width="1" height="300"  patternTransform="matrix(17.28,0,0,0.288,450.281644,203.20411)">
-  <use xlink:href="#image487"/>
+  <use xlink:href="#image486"/>
 </pattern>
 </defs>
-<g id="surface483">
+<g id="surface482">
 <rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>

### 2024-04-16 docs/projects/data-processing/index.qmd
many json lines - rendered

--- 2024-04-15 docs/projects/datavis/ggplot/index.qmd
@@
 
-In this series of notebooks, we explore [ggplot2](https://ggplot2.tidyverse.org/), a famous R package for grammar-of-graphics data visualization, from within Clojure.
+These notes offers various demonstrations of data processing in Clojure.
 
@@
 ```{=html}
-<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/index.clj">projects/datavis/ggplot/notebooks/index.clj</a></small></small></pre></div>
+<div><pre><small><small>source: projects/data-processing/notebooks/index.clj</small></small></pre></div>
 ```

### 2024-04-16 docs/projects/data-processing/many_json_lines.qmd
many json lines - rendered

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: many_json_lines.html}
fontsize: 0.9em
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style><style>.clay-limit-image-width .clay-image {max-width: 100%}
</style>
<script src="many_json_lines_files/md-default0.js" type="text/javascript"></script><script src="many_json_lines_files/md-default1.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

# Processing many JSON lines

::: {.sourceClojure}
```clojure
(ns many-json-lines
  (:require [charred.api :as charred]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.java.io :as io]))
```
:::

Let us create a file with many JSON lines.

::: {.sourceClojure}
```clojure
(def path "/tmp/lines.jsonl")
```
:::

::: {.sourceClojure}
```clojure
(with-open [writer ((charred/json-writer-fn {}) path)]
  (dotimes [i 3]
    (.writeObject writer
                  {:i i
                   :x (rand)})
    (.write (.w writer)
            "\n")))
```
:::

::: {.printedClojure}
```clojure
nil

```
:::

Let us look at a few of those lines we wrote.

::: {.sourceClojure}
```clojure
(with-open [reader (io/reader path)]
  (->> reader
       line-seq
       (take 4)
       vec))
```
:::

::: {.printedClojure}
```clojure
["{\"i\":0,\"x\":0.8833069538053755}"
 "{\"i\":1,\"x\":0.016778130034834637}"
 "{\"i\":2,\"x\":0.751953143790835}"]

```
:::

Now we will demonstrate processing the data.
We will read all lines, extract the relevant part of each line,
and sum these parts up.

::: {.sourceClojure}
```clojure
(defn extract-relevant-data [json-data]
  (get json-data "x"))
```
:::

::: {.sourceClojure}
```clojure
(with-open [json-fn (-> path
                        io/reader
                        (charred/read-json-supplier {:eof-error? false}))]
  (doall
   (map extract-relevant-data json-fn)))
```
:::

::: {.printedClojure}
```clojure
(0.8833069538053755 0.016778130034834637 0.751953143790835 nil)

```
:::

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: projects/data-processing/notebooks/many_json_lines.clj</small></small></pre></div>
```
